### 2020-03-01 paper.tex
First set of notes

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[capitalise]{cleveref}
\usepackage{bm}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\Crefname{property}{Property}{Properties}
\DeclareMathOperator{\WMC}{WMC}
\DeclareMathOperator{\nWMC}{nWMC}
\DeclareMathOperator{\id}{id}

\title{Statistical Relational Models as Polyadic Measure Algebras}
\author{Paulius Dilkas}

\begin{document}
\maketitle

%\section{Introduction}

%Contributions
%\begin{itemize}
%\item Equip polyadic algebras with a measure.
%\item Show that it is equivalent to WMC.
%\end{itemize}

\section{Propositional Logic and Boolean Algebras}

\subsection{Preliminaries}

\begin{definition}
  A \emph{Boolean algebra} is a tuple $(\mathbf{B}, \land, \lor, \neg, 0, 1)$ of
  a set $\mathbf{B}$ with operations $\land, \lor, \neg$ and elements $0, 1 \in
  \mathbf{B}$ such that the following axioms hold for all $a, b, \in
  \mathbf{B}$:
  \begin{itemize}
  \item both $\land$ and $\lor$ are associative and commutative;
  \item $a \lor (a \land b) = a$, and $a \land (a \lor b) = a$;
  \item $0$ is the identity of $\lor$, and $1$ is the identity of $\land$;
  \item $\lor$ distributes over $\land$ and vice versa;
  \item $a \lor \neg a = 1$, and $a \land \neg a = 0$.
  \end{itemize}

  Let $a, b \in \mathbf{B}$ be arbitrary. Let $\le$ be a partial order on
  $\mathbf{B}$ defined by $a \le b$ if $a = b \land a$ (or, equivalently, $a
  \lor b = b$), and let $a < b$ denote $a \le b$ and $a \ne b$.
\end{definition}

\begin{definition}[\cite{DBLP:books/daglib/0090259}]
  An element $a \ne 0$ of a Boolean algebra $\mathbf{B}$ is an \emph{atom} if
  there is no $x \in \mathbf{B}$ such that $0 < x < a$. A Boolean algebra is
  \emph{atomic} if for every $a \in \mathbf{B} \setminus \{ 0 \}$, there is an
  atom $x$ such that $x \le a$.
\end{definition}

\begin{lemma}[\cite{ganesh2006introduction}]
  For any two distinct atoms $a$, $b$ in a Boolean algebra, $a \land b = 0$.
\end{lemma}

\begin{lemma}[\cite{givant2008introduction}]
  All finite Boolean algebras are atomic.
\end{lemma}

\begin{theorem}[\cite{ganesh2006introduction}] \label{thm:representation}
  Let $\mathbf{B}$ be a finite Boolean algebra. Then every $a \in \mathbf{B}
  \setminus \{ 0 \}$ can be uniquely expressed as $a = \bigvee_{i \in I} m_i$
  for some set of atoms $\{m_i\}_{i \in I}$.
\end{theorem}

\begin{definition}[\cite{gaifman1964concerning}] \label{def:measure}
  A \emph{(strictly positive) measure} on a Boolean algebra $\mathbf{B}$ is a
  function $m : \mathbf{B} \to [0, 1]$ such that:
  \begin{enumerate}
  \item $m(1) = 1$, and $m(x) > 0$ for $x \ne
    0$; \label[property]{property:values}
  \item $m(x \lor y) = m(x) + m(y)$ for all $x, y \in \mathbf{B}$ whenever $x
    \land y = 0$. \label[property]{property:additive}
  \end{enumerate}
\end{definition}

\subsection{New Results}

\begin{definition}
  Let $\mathbf{B}$ be a finite Boolean algebra, let $L$ be a subset of
  $\mathbf{B}$ such that every atom $m$ can be uniquely expressed as $m =
  \bigwedge_{i \in I} l_i$ for some $\{ l_i \}_{i \in I} \subseteq L$, and let
  $w : L \to \mathbb{R}_{>0}$ be arbitrary. The \emph{weighted model count}
  $\WMC : \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
  \[
    \WMC(a) = \begin{cases}
      0 & \text{if } a = 0 \\
      \prod_{i \in I} w(l_i) & \text{if } M \ni a = \bigwedge_{i \in I} l_i \\
      \sum_{i \in I} \WMC(m_i) & \text{if } \mathbf{B} \setminus (M \cup \{ 0
      \}) \ni a = \bigvee_{i \in I} m_i
    \end{cases}
  \]
  for any $a \in \mathbf{B}$. Furthermore, we define the \emph{normalised
    weighted model count} $\nWMC : \mathbf{B} \to [0, 1]$ as $\nWMC(a) =
  \frac{\WMC(a)}{\WMC(1)}$ for all $a \in \mathbf{B}$.
\end{definition}

\begin{proposition}
  $\nWMC$ is a measure for any finite Boolean algebra $\mathbf{B}$.
\end{proposition}
\begin{proof}
  First, note that \cref{property:values} of \cref{def:measure} is satisfied by
  the definition of $\nWMC$. Next, in order to prove \cref{property:additive},
  let $x, y \in \mathbf{B}$ be such that $x \land y = 0$. We want to show that
  \[
    \nWMC(x \lor y) = \nWMC(x) + \nWMC(y)
  \]
  which is equivalent to
  \begin{equation} \label{eq:additivity_proof}
    \WMC(x \lor y) = \WMC(x) + \WMC(y).
  \end{equation}
  If, say, $x = 0$, then \cref{eq:additivity_proof} becomes
  \[
    \WMC(y) = \WMC(0) + \WMC(y) = \WMC(y)
  \]
  (and likewise for $y = 0$). Thus we can assume that $x \ne 0 \ne y$ and use
  \cref{thm:representation} to write
  \[
    x = \bigvee_{i \in I} x_i \quad \text{and} \quad y = \bigvee_{j \in J} y_j
  \]
  for some sequences of atoms $(x_i)_{i \in I}$ and $(y_j)_{j \in J}$. If
  $x_{i'} = y_{j'}$ for some $i' \in I$ and $j' \in J$, then
  \[
    x \land y = \bigvee_{i \in I} \bigvee_{j \in J} x_i \land y_j = x_{i'} \land
    y_{j'} \ne 0,
  \]
  contradicting the assumption. This is enough to show that
  \begin{align*}
    \WMC(x \lor y) &= \WMC\left( \left( \bigvee_{i \in I} x_i \right) \lor \left(\bigvee_{j \in J} y_j \right) \right) = \sum_{i \in I} \WMC(x_i) + \sum_{j \in J} \WMC(y_j) \\
                   &= \WMC(x) + \WMC(y),
  \end{align*}
  finishing the proof.
\end{proof}

\section{First-Order Logic and Polyadic Algebras}

\subsection{Preliminaries}

What follows is a summary of \cite{halmos2016algebraic}.

% Generic stuff
Let $\mathbf{B}$ be a Boolean algebra (of propositions). Let $X$ be the
(non-empty) domain of discourse. Let $I$ be an index set, elements of which can
be interpreted as variables. The elements of $X^I$ are functions from $I$ to
$X$. For any $x \in X^I$ and $i \in I$, we write $x_i$ to represent $x(i) \in
X$. Let $\mathbf{A^*}$ be the set of all functions $X^I \to \mathbf{B}$, and
note that it forms a Boolean algebra with operations defined pointwise.

% Defining S
Let $T$ be the semigroup of all $I \to I$ transformations. For any $\tau \in
T$, let $\tau_* : X^I \to X^I$ be defined by
\[
  (\tau_* x)_i = x_{\tau i}
\]
for all $x \in X^I$ and $i \in I$. We can then define $\mathbf{S}$ to be a map
from $T$ to Boolean endomorphisms of $\mathbf{A^*}$ defined by
\[
  \mathbf{S}(\tau)p(x) = p(\tau_* x)
\]
for all $x \in X^I$ and $p \in \mathbf{A^*}$.

% Defining E
For any $J \subseteq I$, let $J_*$ be the relation on $X_I$ defined by
\[
  xJ_*y \quad \iff \quad x_i = y_i \quad \text{for all } i \in I \setminus J
\]
for all $x, y \in X^I$. For any $J \subseteq I$, we then define $\bm\exists(J)$
to be a transformation $\mathbf{A^*} \to \mathbf{A^*}$ defined by
\[
  \bm\exists(J)p(x) = \bigvee_{\substack{y \in X^I,\\ xJ_*y}} p(y)
\]
for all $p \in \mathbf{A^*}$, provided this supremum exists for all $x \in
X^I$\footnote{The universal quantifier $\bm\forall(J)$ is then defined as
  $\bm\forall(J)p = \neg(\bm\exists(J)\neg p)$ for all $p \in \mathbf{A^*}$.}.

Finally, a \emph{functional polyadic (Boolean) algebra}\footnote{To be more
  explicit, a $\mathbf{B}$-valued functional polyadic algebra with domain $X$
  and variables $I$.} is a subalgebra
$\mathbf{A}$ of $\mathbf{A^*}$ such that:
\begin{itemize}
\item $\mathbf{S}(\tau)p \in \mathbf{A}$ for all $p \in \mathbf{A}$ and $\tau
  \in T$;
\item $\bm\exists(J)p \in \mathbf{A}$ for all $p \in \mathbf{A}$ and $J
  \subseteq I$.
\end{itemize}

\begin{definition}
  Similarly to $\bm\exists$, a \emph{constant} $c$ is a mapping from
  $\mathcal{P}(I)$ to Boolean endomorphisms of $\mathbf{A}$ such that:
  \begin{itemize}
  \item $c(\emptyset) = \id_{\mathbf{A}}$;
  \item $c(J \cup K) = c(J)c(K)$;
  \item $c(J)\bm\exists(K) = \bm\exists(K)c(J \setminus K)$;
  \item $\bm\exists(J)c(K) = c(K)\bm\exists(J \setminus K)$;
  \item $c(J)\mathbf{S}(\tau) = \mathbf{S}(\tau)c(\tau^{-1}J)$
  \end{itemize}
  for all $J, K \in \mathcal{P}(I)$ and $\tau \in T$. If $J$ is a singleton
  set $\{ i \}$, we will simply write $c(i)$ instead of $c(J)$.
\end{definition}

\subsection{New Results}

\begin{proposition}
  Let $\mathbf{B}$ be a finite Boolean algebra with a measure $m :
  \mathbf{B} \to [0, 1]$. Let $\mathbf{A}$ be a $\mathbf{B}$-valued functional
  polyadic algebra with domain $X$ and variables $I$. For any $p \in
  \mathbf{A}$, let $\sup(p) = \bigvee_{x \in X^I} p(x)$. Let $m^* : \mathbf{A}
  \to [0, 1]$ be defined by
  \[
    m^*(p) = \sum_{\substack{\text{atom } y \in \mathbf{B}:\\ y \le \sup(p)}}
    m(y)
  \]
  for all $p \in \mathbf{A}$. Then $m^*$ is a measure on $\mathbf{A}$.
\end{proposition}

\begin{remark}
  While defining $m^*$ as $m^*(p) = m(\sup(p))$ might look tempting, this
  definition is not additive.
\end{remark}

\begin{proof} % TODO: update the proof
  First, since $1 \in \mathbf{A}$ is a function $1 : X^I \to \mathbf{B}$ defined
  as $1(x) = 1$, we have that $m^*(1) = m(1) = 1$. If $m^*(p) = 0$ for some $p
  \in \mathbf{A}$, then it must be the case that
  \[
    \bigvee_{x \in X^I} p(x) = 0
  \]
  which means that for all $x \in X^I$, $p(x) = 0$, which is equivalent to
  saying that $p = 0$. Thus, $m^*(p) > 0$ for $p \in \mathbf{A} \setminus \{ 0
  \}$.
\end{proof}

% TODO: how to interpret first-order sentences in this algebra
% TODO: define WMC: connect my definition of WMC with the original one
% TODO: condition for a measurable BA to be representable as WMC
% TODO: can I show that WMC is the only possible probability measure?
% TODO: abstraction refinements as homomorphisms.
% TODO: definition of a measure-preserving homomorphism from Thomas Jech
% TODO: a Boolean algebra is approximable if its Stone space is approximable

\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2020-03-02 paper.tex
Proof that a measure can be transferred from the BA to the PA

@@
 
-\begin{definition}
+\begin{definition} \label{def:ba}
   A \emph{Boolean algebra} is a tuple $(\mathbf{B}, \land, \lor, \neg, 0, 1)$ of
@@
 
-\begin{definition}[\cite{DBLP:books/daglib/0090259}]
+% TODO: Which definition do I actually need?
+\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
   An element $a \ne 0$ of a Boolean algebra $\mathbf{B}$ is an \emph{atom} if
-  there is no $x \in \mathbf{B}$ such that $0 < x < a$. A Boolean algebra is
-  \emph{atomic} if for every $a \in \mathbf{B} \setminus \{ 0 \}$, there is an
-  atom $x$ such that $x \le a$.
+  there is no $x \in \mathbf{B}$ such that $0 < x < a$. Equivalently, $a \ne 0$
+  is an atom if, for all $x \in \mathbf{B}$, either $x \land a = a$ or $x \land
+  a = 0$. A Boolean algebra is \emph{atomic} if for every $a \in \mathbf{B}
+  \setminus \{0 \}$, there is an atom $x$ such that $x \le a$.
 \end{definition}
@@
 % Defining E
-For any $J \subseteq I$, let $J_*$ be the relation on $X_I$ defined by
+For any $J \subseteq I$, let $J_*$ be the relation on $X^I$ defined by
 \[
@@
   \mathbf{B} \to [0, 1]$. Let $\mathbf{A}$ be a $\mathbf{B}$-valued functional
-  polyadic algebra with domain $X$ and variables $I$. For any $p \in
-  \mathbf{A}$, let $\sup(p) = \bigvee_{x \in X^I} p(x)$. Let $m^* : \mathbf{A}
-  \to [0, 1]$ be defined by
+  polyadic algebra with domain $X$ and variables $I$. Let $m^* : \mathbf{A} \to
+  \mathbb{R}_{\ge 0}$ be defined by
   \[
-    m^*(p) = \sum_{\substack{\text{atom } y \in \mathbf{B}:\\ y \le \sup(p)}}
-    m(y)
+    m^*(p) = \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(y)
   \]
@@
 \begin{remark}
-  While defining $m^*$ as $m^*(p) = m(\sup(p))$ might look tempting, this
-  definition is not additive.
+  While definitions of $m^*$ such as
+  \[
+    m^*(p) = m \left( \bigvee_{x \in X^I} p(x) \right)
+  \]
+  might look tempting, they are not additive.
 \end{remark}
@@
 \begin{proof} % TODO: update the proof
-  First, since $1 \in \mathbf{A}$ is a function $1 : X^I \to \mathbf{B}$ defined
-  as $1(x) = 1$, we have that $m^*(1) = m(1) = 1$. If $m^*(p) = 0$ for some $p
-  \in \mathbf{A}$, then it must be the case that
+  First, we can show that $m^*(1) = 1$ by observing that
   \[
-    \bigvee_{x \in X^I} p(x) = 0
+    m^*(1) = \sum_{\text{atoms } y \in \mathbf{B}} m(y) = m \left(
+      \bigvee_{\text{atoms } y \in \mathbf{B}} y \right) = m(1) = 1,
   \]
-  which means that for all $x \in X^I$, $p(x) = 0$, which is equivalent to
-  saying that $p = 0$. Thus, $m^*(p) > 0$ for $p \in \mathbf{A} \setminus \{ 0
-  \}$.
+  where we use \cref{thm:representation} and express $1 \in \mathbf{B}$ as the
+  supremum of all atoms in $\mathbf{B}$ \cite{ganesh2006introduction}. Clearly
+  $m^*(p) \ge 0$ for all $p \in \mathbf{A}$, so we can restrict the codomain of
+  $m^*$ to $[0, 1]$.
+
+  Next, we want to show that $m^*(p) > 0$ for all $p \in \mathbf{A} \setminus \{
+  0 \}$. If $p \ne 0$, then there must be some $x' \in X^I$ such that $p(x') \ne
+  0$. But then, since finite Boolean algebras are atomic, there must also be an
+  atom $y \in \mathbf{B}$ such that $y \le p(x')$. Therefore, $m^*(p) \ge m(y) >
+  0$, finishing this part of the proof.
+
+  Let $p, q \in \mathbf{A}$ be such that $p \land q = 0$. We want to show
+  that $m^*(p \lor q) = m^*(p) \lor m^*(q)$. First, note that
+  \[
+    y \le (p \lor q)(x) = p(x) \lor q(x)
+  \]
+  if and only if
+  \[
+    y = (p(x) \lor q(x)) \land y = (p(x) \land y) \lor (q(x) \land y)
+  \]
+  by \cref{def:ba}. Also note that
+  \[
+    (p(x) \land y) \land (q(x) \land y) = p(x) \land q(x) \land y = (p \land
+    q)(x) \land y = 0 \land y = 0,
+  \]
+  so
+  \[
+    m(y) = m((p(x) \land y) \lor (q(x) \land y)) = m(p(x) \land y) + m(q(x) \land y)
+  \]
+  by \cref{def:measure} which then leads to
+  \begin{align*}
+    m^*(p \lor q) &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(y) = \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(p(x) \land y) + m(q(x) \land y) \\
+                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(q(x) \land y).
+  \end{align*}
+  Since $y$ is an atom,
+  \[
+    p(x) \land y  = \begin{cases}
+      y & \text{if } y \le p(x) \\
+      0 & \text{otherwise,}
+    \end{cases}
+  \]
+  so
+  \begin{align*}
+    m^*(p \lor q) &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x) \text{ and } y \le p(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x) \text{ and } y \le q(x)}} m(q(x) \land y) \\
+                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le q(x)}} m(q(x) \land y) \\
+                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le q(x)}} m(y) = m^*(p) + m^*(q),
+  \end{align*}
+  finishing the proof that $m^*$ is a measure.
 \end{proof}
@@
 % TODO: condition for a measurable BA to be representable as WMC
-% TODO: can I show that WMC is the only possible probability measure?
+% TODO: can I show that a generalisation of WMC is the only possible probability measure (when it exists)?
 % TODO: abstraction refinements as homomorphisms.

### 2020-03-06 paper.tex
The start of an example

@@
 \usepackage{bm}
+\usepackage{booktabs}
 
@@
 \DeclareMathOperator{\id}{id}
+\DeclareMathOperator{\End}{End}
 
@@
 
+% TODO: remove the requirement for being strictly positive
 \begin{definition}[\cite{gaifman1964concerning}] \label{def:measure}
@@
 
+% TODO: weight can be zero
 \begin{definition}
@@
 \]
-for all $x \in X^I$ and $i \in I$. We can then define $\mathbf{S}$ to be a map
-from $T$ to Boolean endomorphisms of $\mathbf{A^*}$ defined by
+for all $x \in X^I$ and $i \in I$. For any (Boolean/polyadic) algebra
+$\mathbf{C}$, let $\End(\mathbf{C})$ denote the set of all its endomorphisms. We
+can then define $\mathbf{S}$ to be a map $\mathbf{S} : T \to \End(\mathbf{A^*})$
+defined by
 \[
@@
 \begin{definition}
-  Similarly to $\bm\exists$, a \emph{constant} $c$ is a mapping from
-  $\mathcal{P}(I)$ to Boolean endomorphisms of $\mathbf{A}$ such that:
+  Similarly to $\bm\exists$, a \emph{constant} $c$ is a map $c: \mathcal{P}(I)
+  \to \End(\mathbf{A})$ (Boolean endomorphisms?) such that:
   \begin{itemize}
@@
 
-% TODO: how to interpret first-order sentences in this algebra
-% TODO: define WMC: connect my definition of WMC with the original one
+\section{From First-Order Logic to Polyadic Algebras}
+
+\subsection{Preliminaries}
+
+\begin{definition}[\cite{givant2008introduction}] \label{def:boolean_ideal}
+  An \emph{ideal} in a Boolean algebra $\mathbf{B}$ is a subset $M \subseteq
+  \mathbf{B}$ such that:
+  \begin{itemize}
+  \item $0 \in M$;
+  \item $x \lor y \in M$ for all $x, y \in M$;
+  \item $x \land y \in M$ for all $x \in M$ and $y \in \mathbf{B}$.
+  \end{itemize}
+  For any subset $S \subseteq \mathbf{B}$, the \emph{ideal generated by $S$} is
+  the smallest ideal $M$ such that $S \subseteq M$.
+\end{definition}
+
+Note that \cref{def:boolean_ideal} gives us a simple characterisation of an
+ideal generated by a set of atoms.
+
+\begin{lemma}
+  Let $\mathbf{B}$ be a Boolean algebra, and let $S \subseteq \mathbf{B}$ be a
+  set of atoms. The ideal $I$ generated by $S$ is defined by the following:
+  \begin{itemize}
+  \item $0 \in I$,
+  \item $S \subseteq I$,
+  \item $x \lor y \in I$ for all $x, y \in I$.
+  \end{itemize}
+\end{lemma}
+
+\begin{definition}[\cite{givant2008introduction}]
+  Let $\mathbf{B}$ be a Boolean algebra, and let $I$ be an ideal in
+  $\mathbf{B}$. The \emph{quotient algebra} $\mathbf{B}/I$ is a Boolean algebra
+  on equivalence classes of elements of $\mathbf{B}$ (with operations defined
+  pointwise) based on the equivalence relation
+  \[
+    x \sim y \quad \iff \quad x + y \in I
+  \]
+  where $x + y = (x \land \neg y) \lor (y \land \neg x)$ is the symmetric
+  difference operation (written as a sum because it can interpreted as the
+  `additive' part of the corresponding Boolean ring).
+\end{definition}
+
+\subsection{New Results}
+
+In order to make the example algebras easily describable, our example programs
+will have to be tiny. Consider the following ProbLog
+\cite{DBLP:conf/ijcai/RaedtKT07} program:
+\begin{align*}
+  1.0 &\dblcolon \mathsf{p}(a, b).\\
+  0.5 &\dblcolon \mathsf{p}(X, X) \coloneq \mathsf{p}(X, Y);\, \mathsf{p}(Y, X).
+\end{align*}
+Let $L = \{ \mathsf{p}(a, a), \mathsf{p}(a, b), \mathsf{p}(b, a), \mathsf{p}(b,
+b) \}$ be the set of all possible ground atoms. Let $\mathbf{B}$ be the
+Boolean algebra freely generated by $L$ (see, e.g.,
+\cite{givant2008introduction} for more on free Boolean algebras). Then
+$\mathbf{B}$ will have sixteen atoms ranging from $\mathsf{p}(a, a) \land
+\mathsf{p}(a, b) \land \mathsf{p}(b, a) \land \mathsf{p}(b, b)$ to
+$\neg\mathsf{p}(a, a) \land \neg\mathsf{p}(a, b) \land \neg\mathsf{p}(b, a)
+\land \neg\mathsf{p}(b, b)$. The weight function $w : L \to \mathbb{R}_{\ge 0}$
+defined by
+\[
+  w(l) = \begin{cases}
+    1 & \text{if } l = \mathsf{p}(a, b) \\
+    0.5 & \text{if } l \in \{ \mathsf{p}(a, a), \mathsf{p}(b, b) \} \\
+    0 & \text{if } l = \mathsf{p}(b, a) \\
+    1-w(l') & \text{if } l = \neg l'
+  \end{cases}
+\]
+for all $l \in L$ defines a WMC measure over $\mathbf{B}$. Note that while we
+could define an ideal generated by $\{ \mathsf{p}(b, a), \neg\mathsf{p}(a, b)
+\}$ and take the quotient of $\mathbf{B}$ by that ideal to get a Boolean algebra
+with a strictly positive measure, this would put zero-probability queries
+outside of our algebras, i.e., we would not be able to ask a question whose
+answer is zero.
+
+\begin{table}
+  \centering
+  \caption{Example elements of $\mathbf{A}$ as maps $X^I \to \mathbf{B}$, with
+    $a : \mathcal{P}(I) \to \End(\mathbf{A})$ as one of two possible constants.}
+  \label{tbl:examples}
+  \begin{tabular}{ll}
+    \toprule
+    Element of $\mathbf{A}$ & Action on $X^I$ \\
+    \midrule
+    $p = \mathbf{S}(\id)p = \bm\exists(\emptyset)p = a(\emptyset)p = b(\emptyset)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_2)$ \\
+    $\bm\exists(1)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, x_2) \lor \mathsf{p}(b, x_2)$ \\
+    $\bm\exists(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, a) \lor \mathsf{p}(x_1, b)$ \\
+    $\bm\exists(I)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, a) \lor \mathsf{p}(a, b) \lor \mathsf{p}(b, a) \lor \mathsf{p}(b, b)$ \\
+    $\mathbf{S}(\{ 1 \mapsto 1, 2 \mapsto 1 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_1)$ \\
+    $\mathbf{S}(\{ 1 \mapsto 2, 2 \mapsto 1 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_2, x_1)$ \\
+    $\mathbf{S}(\{ 1 \mapsto 2, 2 \mapsto 2 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_2, x_2)$ \\
+    $a(1)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, x_2)$ \\
+    $a(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, a)$ \\
+    $a(I)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, a)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Finally, let $\mathbf{A}$ be the functional polyadic algebra $X^I \to
+\mathbf{B}$ for $I = \{1, 2\}$ and $X = \{ a, b \}$\footnote{$X$ cannot (or
+  should not) have constants that do not occur in $\mathbf{B}$.}. The elements
+of $X^I$ can then be represented as tuples $(x_1, x_2)$ for some $x_1, x_2 \in
+X$. See \cref{tbl:examples} for example elements of $\mathbf{A}$ which consists
+of a single predicate function $p$ and operators $\bm\exists, \mathbf{S}, a, b,
+\neg, \land, \lor$, the last three of which are defined pointwise.
+
+% TODO: 1-2 examples of how a probability is calculated
 % TODO: condition for a measurable BA to be representable as WMC
@@
 % TODO: a Boolean algebra is approximable if its Stone space is approximable
+% TODO: maybe the measure on BA should not be normalised?
+% TODO: how do measures transfer to quotient algebras? Naturally!
+% TODO: extension to infinite atomic Boolean algebras
+
+\section{Homomorphisms}
+
+\begin{definition}[\cite{givant2008introduction}]
+  Let $\mathbf{A}$ and $\mathbf{B}$ be Boolean algebras. A \emph{Boolean
+    homomorphism} from $\mathbf{A}$ to $\mathbf{B}$ is a map $f : \mathbf{A} \to
+  \mathbf{B}$ such that:
+  \begin{itemize}
+  \item $f(x \land y) = f(x) \land f(y)$,
+  \item $f(x \lor y) = f(x) \lor f(y)$,
+  \item $f(\neg x) = \neg f(x)$
+  \end{itemize}
+  for all $x, y \in \mathbf{A}$.
+\end{definition}
+
+\begin{definition}[\cite{halmos2016algebraic}]
+  Given two polyadic algebras $\mathbf{A}$ and $\mathbf{B}$, a \emph{polyadic
+    homomorphism} from $\mathbf{A}$ to $\mathbf{B}$ is a Boolean homomorphism $f
+  : \mathbf{A} \to \mathbf{B}$ such that
+  \begin{itemize}
+  \item $f\mathbf{S}(\tau)p = \mathbf{S}(\tau)fp$,
+  \item $f\bm\exists(J)p = \bm\exists(J)fp$
+  \end{itemize}
+  for all $\tau \in T$, $p \in \mathbf{A}$, and $J \subseteq I$.
+\end{definition}
 

### 2020-03-07 paper.tex
A detailed example of how a probability is computed

@@
 \usepackage{booktabs}
+\usepackage[backgroundcolor=lightgray]{todonotes}
 
@@
 
-\title{Statistical Relational Models as Polyadic Measure Algebras}
+\title{Weighted Model Counting as a Special Case of Polyadic Measure Algebras}
 \author{Paulius Dilkas}
@@
 
-% TODO: Which definition do I actually need?
+\todo[inline]{Which definition do I actually need?}
 \begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
@@
 
-\begin{lemma}[\cite{givant2008introduction}]
+\begin{lemma}[\cite{givant2008introduction}] \label{lemma:atomic}
   All finite Boolean algebras are atomic.
@@
 
-\begin{theorem}[\cite{ganesh2006introduction}] \label{thm:representation}
+\begin{theorem} \label{thm:representation}
   Let $\mathbf{B}$ be a finite Boolean algebra. Then every $a \in \mathbf{B}
-  \setminus \{ 0 \}$ can be uniquely expressed as $a = \bigvee_{i \in I} m_i$
-  for some set of atoms $\{m_i\}_{i \in I}$.
+  \setminus \{ 0 \}$ can be uniquely expressed as $a = \bigvee_{i \in I} a_i$,
+  where $\{ a_i \}_{i \in I}$ is the set of atoms in $\mathbf{B}$ such that $a_i
+  \le a$ for all $i \in I$.
 \end{theorem}
+\begin{proof}
+  A simple consequence of the theorem that every finite Boolean algebra is
+  isomorphic to a field of subsets of a set, where the cardinality of the set is
+  equal to the number of atoms in the Boolean algebra.
+\end{proof}
 
-% TODO: remove the requirement for being strictly positive
+\todo[inline]{Remove the requirement for being strictly positive}
 \begin{definition}[\cite{gaifman1964concerning}] \label{def:measure}
@@
 
-% TODO: weight can be zero
+\todo[inline]{Allow weight to be zero}
 \begin{definition}
-  Let $\mathbf{B}$ be a finite Boolean algebra, let $L$ be a subset of
-  $\mathbf{B}$ such that every atom $m$ can be uniquely expressed as $m =
-  \bigwedge_{i \in I} l_i$ for some $\{ l_i \}_{i \in I} \subseteq L$, and let
-  $w : L \to \mathbb{R}_{>0}$ be arbitrary. The \emph{weighted model count}
-  $\WMC : \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
+  Let $\mathbf{B}$ be a finite Boolean algebra, and let $M \subseteq \mathbf{B}$
+  be its set of atoms. Let $L \subseteq \mathbf{B}$ be such that every atom $m
+  \in M$ can be uniquely expressed as $m = \bigwedge_{i \in I} l_i$ for some $\{
+  l_i \}_{i \in I} \subseteq L$, and let $w : L \to \mathbb{R}_{>0}$ be
+  arbitrary. The \emph{weighted model count} $\WMC : \mathbf{B} \to
+  \mathbb{R}_{\ge 0}$ is defined as
   \[
@@
 
-\begin{proposition}
+\begin{proposition} \label{prop:polyadic_measure}
   Let $\mathbf{B}$ be a finite Boolean algebra with a measure $m :
@@
 
-\begin{proof} % TODO: update the proof
+\begin{proof}\todo[inline]{Update the proof w.r.t. definitions}
   First, we can show that $m^*(1) = 1$ by observing that
@@
 
+\begin{lemma} \label{lemma:simple_measure}
+  Given the setup of \cref{prop:polyadic_measure} and $p \in \mathbf{A}$, if
+  $p(x) = p(y)$ for all $x, y \in X^I$ (i.e., $p$ has no free variables), then
+  \[
+    m^*(p) = m(p(x))
+  \]
+  (for some $x \in X^I$) is an alternative (i.e., equivalent and simpler)
+  definition of $m^*$.
+\end{lemma}
+\begin{proof}
+  Fix some $x \in X^I$. Then
+  \[
+    m(p(x)) = m \left( \bigvee_{\substack{\text{atoms } y \in \mathbf{B} \text{
+            s.t.}\\
+          y \le p(x)}} y \right) = \sum_{\substack{\text{atoms } y \in \mathbf{B}
+        \text{ s.t.}\\
+        y \le p(x)}} m(y) =\sum_{\substack{\text{atoms } y \in \mathbf{B}
+        \text{ s.t.}\\
+        \exists x' \in X^I : y \le p(x')}} m(y) = m^*(p),
+  \]
+  where we use \cref{thm:representation} for the first step,
+  \cref{def:measure} and \cref{lemma:atomic} for the second step, the
+  assumptions of \cref{lemma:simple_measure} for the third step, and the
+  definition of $m^*$ for the fourth one.
+\end{proof}
+
 \section{From First-Order Logic to Polyadic Algebras}
@@
 
-\subsection{New Results}
+\subsection{New Results (an Example)}
 
@@
 
-% TODO: 1-2 examples of how a probability is calculated
-% TODO: condition for a measurable BA to be representable as WMC
-% TODO: can I show that a generalisation of WMC is the only possible probability measure (when it exists)?
-% TODO: abstraction refinements as homomorphisms.
-% TODO: definition of a measure-preserving homomorphism from Thomas Jech
-% TODO: a Boolean algebra is approximable if its Stone space is approximable
-% TODO: maybe the measure on BA should not be normalised?
-% TODO: how do measures transfer to quotient algebras? Naturally!
-% TODO: extension to infinite atomic Boolean algebras
+\begin{table}
+  \centering
+  \caption{Step-by-step derivation of how a more complex element of
+    $\mathbf{A}$ acts on elements of $X^I$}
+  \label{tbl:derivation}
+  \begin{tabular}{ll}
+    \toprule
+    Element of $\mathbf{A}$ & Action on $X^I$ \\
+    \midrule
+    $p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_2)$ \\
+    $b(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, b)$ \\
+    $\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\mathsf{p}(x_1, b)$ \\
+    $\bm\exists(1)\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\mathsf{p}(a, b) \lor \neg\mathsf{p}(b, b) = \neg(\mathsf{p}(a, b) \land \mathsf{p}(b, b))$ \\
+    $\bm\forall(1)b(2)p = \neg\bm\exists(1)\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\neg(\mathsf{p}(a, b) \land \mathsf{p}(b, b)) = \mathsf{p}(a, b) \land \mathsf{p}(b, b)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}
+  \centering
+  \caption{Atoms $y \in \mathbf{B}$ (and their measures) such that $y \le
+    \mathsf{p}(a, b) \land \mathsf{p}(b, b)$}
+  \label{tbl:atoms}
+  \begin{tabular}{lc}
+    \toprule
+    Atom $y \in \mathbf{B}$ & $m(y)$ \\
+    \midrule
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \mathsf{p}(a, a) \land \mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 0 = 0$ \\
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \neg\mathsf{p}(a, a) \land \mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 0 = 0$ \\
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \mathsf{p}(a, a) \land \neg\mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 1 = 0.25$ \\
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \neg\mathsf{p}(a, a) \land \neg\mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 1 = 0.25$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Let us calculate the probability $\Pr(\forall x_1 \in X, \mathsf{p}(x_1, b))$.
+The same expression can be translated into the notation for our polyadic algebra
+$\mathbf{A}$ as $m^*(\bm\forall(1)b(2)p)$. Recall that $\bm\forall(1)b(2)p =
+\neg\bm\exists(1)\neg b(2)p$. The effect of this function on an arbitrary
+element of $X^I$ is derived step-by-step in \cref{tbl:derivation}. Since the
+resulting function is constant (i.e., the logical formula has no free
+variables), \cref{lemma:simple_measure} tells us that
+\[
+  m^*(\bm\forall(1)b(2)p) = m(\mathsf{p}(a, b) \land \mathsf{p}(b, b)) = m
+  \left( \bigvee_{\substack{\text{atoms } y \in \mathbf{B} \text{ s.t.}\\
+        y \le \mathsf{p}(a, b) \land \mathsf{p}(b, b)}} y \right) = \sum
+  _{\substack{\text{atoms } y \in \mathbf{B} \text{ s.t.}\\
+      y \le \mathsf{p}(a, b) \land \mathsf{p}(b, b)}} m(y).
+\]
+The resulting sum is over four atoms; these atoms and their probabilities are
+listed in \cref{tbl:atoms}. Thus, we get that
+\[
+  m^*(\bm\forall(1)b(2)p) = 0 + 0 + 0.25 + 0.25 = 0.5.
+\]
+
+\todo[inline,caption={}]{The big TODO list
+  \begin{itemize}
+  \item Condition for a measurable Boolean algebra to be representable as WMC.
+    Note: if all atoms are in $L$, then WMC can define any distribution.
+  \item Extension to infinite (atomic?) Boolean algebras.
+  \item How many extra variable do you need to add to make any probability
+    distribution representable using WMC?
+  \item Abstraction refinements as homomorphisms.
+  \item Definition of a measure-preserving homomorphism from Jech's set theory
+    book.
+  \item A Boolean algebra is approximable if its Stone space is approximable.
+  \end{itemize}
+}
 

### 2020-03-09 paper.tex
Proof of the obvious result: part 1

@@
 \Crefname{property}{Property}{Properties}
+\Crefname{condition}{Condition}{Conditions}
+\creflabelformat{condition}{#2(#1)#3}
+
 \DeclareMathOperator{\WMC}{WMC}
@@
 %\end{itemize}
+
+% Big advantage: using algebras we can represent an incomplete state of
+% knowledge, e.g., we know m(a \/ b), but not m(a) or m(b). In infinite BAs, one
+% can have measure undefined for some elements.
 
@@
 
+% TODO: we don't have to treat 0 as an exception we state that \/ of an empty set is 0 (and /\ of an empty set is 1).
+% TODO: use bigvee and bigwedge directly with sets.
 \begin{theorem} \label{thm:representation}
-  Let $\mathbf{B}$ be a finite Boolean algebra. Then every $a \in \mathbf{B}
-  \setminus \{ 0 \}$ can be uniquely expressed as $a = \bigvee_{i \in I} a_i$,
-  where $\{ a_i \}_{i \in I}$ is the set of atoms in $\mathbf{B}$ such that $a_i
-  \le a$ for all $i \in I$.
+  Let $\mathbf{B}$ be a finite Boolean algebra. Then every $x \in \mathbf{B}
+  \setminus \{ 0 \}$ can be uniquely expressed as
+  \[
+  x = \bigvee_{\text{atoms } a \le x} a.
+  \]
 \end{theorem}
@@
 \todo[inline]{Allow weight to be zero}
-\begin{definition}
+\begin{definition} \label{def:wmc}
   Let $\mathbf{B}$ be a finite Boolean algebra, and let $M \subseteq \mathbf{B}$
@@
 
+% TODO: maybe I should gives this kind of a BA a name? A synonym of 'complete',
+% perhaps.
+% TODO: a special case for weight=0.
+\begin{proposition}
+  Let $\mathbf{B}$ be a finite measure algebra with measure $m : \mathbf{B} \to
+  \mathbb{R}_{\ge 0}$. Let $L \subset \mathbf{B}$ be defined as
+  \[
+  L = \{ l_i \mid i \in [n] \} \cup \{ \neg l_i \mid i \in [n] \}
+  \]
+  for some $n \in \mathbb{N}$. Finally, assume that $\mathbf{B}$ has $2^n$
+  atoms, where each atom $a \in \mathbf{B}$ is an infimum
+  \[
+    a = \bigwedge_{i=1}^n a_i
+  \]
+  such that $a_i \in \{ l_i, \neg l_i \}$ for $i \in [n]$. Then there exists a
+  weight function $w : L \to \mathbb{R}_{>0}$ that makes $m$ a WMC measure if
+  and only if
+  \begin{equation} \label{eq:wmccondition}
+  m(l \land l') = m(l)m(l')
+  \end{equation}
+  for all distinct $l, l' \in L$ such that $l \ne \neg l'$.
+\end{proposition}
+
+\begin{remark}
+  Note that if $n = 1$, then \cref{eq:wmccondition} is vacuously satisfied and
+  so any valid measure can be expressed as WMC.
+\end{remark}
+
+\begin{proof}
+  Let us begin with the `if' part of the statement. Let $w : L \to
+  \mathbb{R}_{>0}$ be defined by
+  \begin{equation} \label{eq:assumption}
+    w(l) = m(l)
+  \end{equation}
+  for all $l \in L$. We are going
+  to show that $\nWMC = m$. First, note that $\nWMC(0) = 0 = m(0)$ by the
+  definitions of both $\nWMC$ and $m$. Second, let
+  \begin{equation} \label{eq:def_of_a}
+    a = \bigwedge_{i=1}^n a_i
+  \end{equation}
+  be an atom in $\mathbf{B}$ such that $a_i \in \{ l_i, \neg l_i \}$ for all $i
+  \in [n]$. Then
+  \[
+    \nWMC(a) = \frac{\WMC(a)}{\WMC(1)} = \frac{1}{\WMC(1)} \prod_{i=1}^n w(a_i)
+    = \frac{1}{\WMC(1)} \prod_{i=1}^n m(a_i) = \frac{1}{\WMC(1)} m \left(
+      \bigwedge_{i=1}^n a_i \right) = \frac{m(a)}{\WMC(1)}
+  \]
+  by \cref{def:wmc,eq:assumption,eq:wmccondition,eq:def_of_a}. Now we just need
+  to show that $\WMC(1) = 1$. Indeed,
+  \begin{align*}
+    \WMC(1) &= \sum_{\text{atoms } a \in \mathbf{B}} \WMC(a) = \sum_{\text{atoms
+      } a \in \mathbf{B}} \prod_{i=1}^n w(a_i) = \sum_{\text{atoms } a \in
+      \mathbf{B}} \prod_{i=1}^n m(a_i) \\
+    &= \sum_{\text{atoms } a \in
+      \mathbf{B}} m \left( \bigwedge_{i=1}^n a_i \right) = \sum_{\text{atoms } a
+      \in \mathbf{B}} m(a) = m \left( \bigvee_{\text{atoms } a \in \mathbf{B}}
+    \right) = m(1) = 1.
+  \end{align*}
+  Finally, note that if $\nWMC$ and $m$ agree on all atoms, then they must also
+  agree on all other non-zero elements of the Boolean algebra.
+
+  % TODO: the other direction
+\end{proof}
+
 \todo[inline,caption={}]{The big TODO list
   \begin{itemize}
-  \item Condition for a measurable Boolean algebra to be representable as WMC.
-    Note: if all atoms are in $L$, then WMC can define any distribution.
   \item Extension to infinite (atomic?) Boolean algebras.

### 2020-03-10 paper.tex
And here's the second part of the proof

@@
 
-  % TODO: the other direction
+  For the other direction, we are given a weight function $w : L \to
+  \mathbb{R}_{>0}$ that induces a measure $m = \nWMC : \mathbf{B} \to
+  \mathbb{R}_{\ge 0}$, and we want to show that \cref{eq:wmccondition} is
+  satisfied. Let $k_i, k_j \in L$ be such that $k_i \in \{ l_i, \neg l_i \}$,
+  $k_j \in \{ l_j, \neg l_j \}$, and $i \ne j$. We will first prove an auxiliary
+  result that
+  \begin{equation} \label{eq:to_prove}
+    m(k_i \land k_j) = m(k_i)m(k_j)
+  \end{equation}
+  is equivalent to
+  \begin{equation} \label{eq:to_prove2}
+    m(k_i \land k_j) \cdot m(\neg k_i \land \neg k_j) = m(k_i \land \neg k_j)
+    \cdot m(\neg k_i \land k_j).
+  \end{equation}
+  First, note that $k_i$ can be expressed as
+  \[
+    k_i = (k_i \land k_j) \lor (k_i \land \neg k_j)
+  \]
+  with the condition that
+  \[
+    (k_i \land k_j) \land (k_i \land \neg k_j) = 0,
+  \]
+  so, by properties of a measure,
+  \begin{equation} \label{eq:temp}
+    m(k_i) = m(k_i \land k_j) + m(k_i \land \neg k_j).
+  \end{equation}
+  Applying \cref{eq:temp} and the equivalent expression for $m(k_j)$ allows us
+  to rewrite \cref{eq:to_prove} as
+  \begin{align*}
+    m(k_i \land k_j) &= [m(k_i \land k_j) + m(k_i \land \neg k_j)] \cdot [m(k_i \land k_j) + m(\neg k_i \land k_j)] \\
+                     &= m(k_i \land k_j)^2 + m(k_i \land k_j)[m(k_i \land \neg k_j) + m(\neg k_i \land k_j)] + m(k_i \land \neg k_j)m(\neg k_i \land k_j)
+  \end{align*}
+  Dividing both sides by $m(k_i \land k_j)$ gives
+  \begin{equation} \label{eq:temp2}
+    1 = m(k_i \land k_j) + m(k_i \land \neg k_j) + m(\neg k_i \land k_j) +
+    \frac{m(k_i \land \neg k_j)m(\neg k_i \land k_j)}{m(k_i \land k_j)}.
+  \end{equation}
+  Since $k_i \land k_j \land k_i \land \neg k_j = 0$, and
+  \[
+    (k_i \land k_j) \lor (k_i \land \neg k_j) = k_i \land (k_j \lor \neg k_j) =
+    k_i \land 1 = k_i,
+  \]
+  we have that
+  \[
+    m(k_i \land k_j) + m(k_i \land \neg k_j) = m(k_i).
+  \]
+  Similarly, $k_i \land \neg k_i \land k_j = 0$, and
+  \[
+    k_i \lor (\neg k_i \land k_j) = (k_i \lor \neg k_i) \land (k_i \lor k_j) =
+    k_i \lor k_j,
+  \]
+  so
+  \[
+    m(k_i) + m(\neg k_i \land k_j) = m(k_i \lor k_j).
+  \]
+  Finally, note that
+  \[
+    (k_i \lor k_j) \land \neg(k_i \lor k_j) = 0,
+  \]
+  and
+  \[
+    (k_i \lor k_j) \lor \neg(k_i \lor k_j) = 1,
+  \]
+  so
+  \[
+    m(k_i \lor k_j) + m(\neg(k_i \lor k_j)) = m(1) = 1.
+  \]
+  This allows us to rewrite \cref{eq:temp2} as
+  \[
+    \frac{m(k_i \land \neg k_j)m(\neg k_i \land k_j)}{m(k_i \land k_j)} = 1 -
+    m(k_i \lor k_j) = m(\neg(k_i \lor k_j)) = m(\neg k_i \land \neg k_j)
+  \]
+  which immediately gives us \cref{eq:to_prove2}.
+
+  Now recall that $m = \nWMC$ and note that \cref{eq:to_prove2} can be
+  multiplied by $\WMC(1)^2$ to turn the equation into one for $\WMC$ instead of
+  $\nWMC$. Then
+  \begin{align*}
+    \WMC(k_i \land k_j) &= \sum_{\text{atoms } a \le k_i \land k_j} \WMC(a) = \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n]} w(a_m) \\
+                        &= \sum_{\text{atoms } a \le k_i \land k_j} w(a_i)w(a_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = \sum_{\text{atoms } a \le k_i \land k_j} w(k_i)w(k_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) \\
+    &= w(k_i)w(k_j) \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = w(k_i)w(k_j)C,
+  \end{align*}
+  where $C$ denotes the part of $\WMC(k_i \land k_j)$ that will be the same for
+  $\WMC(\neg k_i \land k_j)$, $\WMC(k_i \land \neg k_j)$, and $\WMC(\neg k_i
+  \land \neg k_j)$ as well. But then \cref{eq:to_prove2} becomes
+  \[
+    w(k_i)w(k_j)w(\neg k_i)w(\neg k_j)C^2 = w(k_i)w(\neg k_j)w(\neg k_i)w(k_j)C^2
+  \]
+  which is trivially true. By showing that WMC satisfies \cref{eq:to_prove2}, we
+  also showed that it satisfies \cref{eq:to_prove}, finishing the second part of
+  the proof.
+  \todo[inline]{Adapt the proof to zero measure events}
 \end{proof}

### 2020-03-11 paper.tex
Some new results on extending BAs to make measures WMC-computable

@@
 \usepackage{booktabs}
+\usepackage{tikz}
+\usepackage{xcolor}
 \usepackage[backgroundcolor=lightgray]{todonotes}
@@
 
-\title{Weighted Model Counting as a Special Case of Polyadic Measure Algebras}
+\usetikzlibrary{cd}
+
+\tikzset{
+  Subset/.style={
+    draw=none,
+    every to/.append style={
+      edge node={node [sloped, allow upside down, auto=false]{$\subset$}}}
+  }
+}
+
+\title{On the Limitations of Weighted Model Counting}
 \author{Paulius Dilkas}
@@
 
-\section{Propositional Logic and Boolean Algebras}
+\section{WMC as a Measure}
 
@@
 
-\section{First-Order Logic and Polyadic Algebras}
+\section{An Extension to First-Order Logic}
 
@@
 
-\section{From First-Order Logic to Polyadic Algebras}
+\section{How Probabilities Are Computed}
 
@@
 
+\section{What Measures Are WMC-Computable?}
+
+\subsection{WMC Requires Independent Literals}
+
 % TODO: maybe I should gives this kind of a BA a name? A synonym of 'complete',
@@
 % TODO: a special case for weight=0.
+
 \begin{proposition}
@@
   the proof.
-  \todo[inline]{Adapt the proof to zero measure events}
 \end{proof}
+% TODO: the auxiliary result should be a 'claim' in-between the theorem and the proof.
 
-\todo[inline,caption={}]{The big TODO list
-  \begin{itemize}
-  \item Extension to infinite (atomic?) Boolean algebras.
-  \item How many extra variable do you need to add to make any probability
-    distribution representable using WMC?
-  \item Abstraction refinements as homomorphisms.
-  \item Definition of a measure-preserving homomorphism from Jech's set theory
-    book.
-  \item A Boolean algebra is approximable if its Stone space is approximable.
-  \end{itemize}
-}
+\subsection{Extending the Algebra}
 
-\section{Homomorphisms}
+\subsubsection{Preliminaries}
 
@@
 
+\subsubsection{New Results}
+
+A well-known way to overcome this limitation of independence is by adding more
+literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending the set $L$ covered
+by the WMC weight function $w : L \to \mathbb{R}_{>0}$. Let us translate this
+idea to the language of Boolean algebras.
+
+\begin{theorem} \label{thm:extension} % TODO: cite the fact about atoms
+  Let $\mathbf{B}$ be a finite Boolean algebra freely generated by some set of
+  `literals' $L$, and let $m : \mathbf{B} \to \mathbb{R}_{\ge 0}$ be an
+  arbitrary measure. We know that $\mathbf{B}$ has $n = 2^{|L|}$ atoms. Let
+  $(a_i)_{i=1}^n$ be those atoms. Let $L' = L \cup \{ \phi_i \mid i \in [n] \}$
+  be the set $L$ extended with $n$ new literals. Let $\mathbf{B'} =
+  \mathbf{C}/I$ be the quotient of the Boolean algebra $\mathbf{C}$ freely
+  generated by $L'$ and the ideal $I$ generated by
+  \[
+    \{\phi_i \land \phi_j \mid i, j \in [n], i \ne j \} \cup \{ a_i \land \phi_j
+    \mid i, j \in [n], i \ne j \}.
+  \]
+  Let $h : \mathbf{B} \to \mathbf{B'}$ be the Boolean homomorphism defined by
+  $h(l) = l$ for all $l \in L$ (note that this indeed defines a homomorphism).
+  Let $w : L' \to \mathbb{R}_{> 0}$ be defined by
+  \[
+    w(l) = \begin{cases}
+      m(a_i) & \text{if } l = \phi_i \text{ for some } i \in [n] \\
+      1 & \text{otherwise}
+    \end{cases}
+  \]
+  for all $l \in L'$. This defines a WMC measure $m' : \mathbf{B'} \to
+  \mathbb{R}_{\ge 0}$. Furthermore,
+  \[
+    m(a) = m'(h(a)).
+  \]
+\end{theorem}
+
+In simpler terms, any measure can be computed using WMC by extending the Boolean
+algebra with more literals and connecting the two via a homomorphism. More
+precisely, we are given the red part in
+\[
+  \begin{tikzcd}
+    & \textcolor{red}{\mathbb{R}_{\ge 0}} & & \\
+    \textcolor{red}{\mathbf{B}} \arrow[red]{ur}{m} \arrow{rr}{h} & & \mathbf{B'}
+    \arrow{ul}[swap]{m'} & \\
+    \textcolor{red}{L} \arrow[Subset,red]{u}{} \arrow[Subset]{rr}{} & & L'
+    \arrow[Subset]{u}{} \arrow{r}{w} & \mathbb{R}_{>0}
+  \end{tikzcd}
+\]
+and construct the black part in such a way that the triangle commutes.
+
+\begin{proof}
+  % TODO
+\end{proof}
+
+% TODO: proof that n is the smallest number (in the worst case, without
+% independence assumptions)
+%\begin{proposition}
+%  In \cref{thm:extension}, if $L'$ has less than $n$ additional elements, then
+%  there exists a measure $$
+%\end{proposition}
+
+% TODO: describe how my approach is better in the worst case than that by
+% Darwiche
+
+\todo[inline,caption={}]{The big TODO list
+  \begin{itemize}
+  \item Extension to infinite (atomic?) Boolean algebras.
+  \item Compare my polyadic measures with first-order WMC.
+  \item Abstraction refinements as homomorphisms.
+  \item Definition of a measure-preserving homomorphism from Jech's set theory
+    book.
+  \item A Boolean algebra is approximable if its Stone space is approximable.
+  \end{itemize}
+}
+
 \bibliographystyle{plain}

### 2020-03-12 paper.tex
Feedback from Vaishak (not that I asked for it...)

@@
 
-%\section{Introduction}
+\section{Introduction}
+
+% Feedback: What are the main claims, what are the main takeaways, intuitive
+% [???] of theorems to follow. To do this, we appeal to algebraic constructions
+% to define the main concepts for introducing measures on Boolean algebras.
 
@@
 
-% TODO: we don't have to treat 0 as an exception we state that \/ of an empty set is 0 (and /\ of an empty set is 1).
+% TODO: we don't have to treat 0 as an exception we state that \/ of an empty
+% set is 0 (and /\ of an empty set is 1).
 % TODO: use bigvee and bigwedge directly with sets.
@@
 
+% TODO: Feedback: Probably a good idea to explain how elements of the Boolean
+% algebra map to models in WMC formulations. Probably do an example:
+% 0.3 p; 0.2 q => M = <p, qbar> has weight o3 * (1-0.2)
+% then it corresponds to an atom in an algebra defined over the language defined
+% over propositions p and q.
+
 \subsection{New Results}
@@
 \end{definition}
+% TODO: Feedback: maybe NWMC or WMC^*, as nWMC looks like a typo. Also clarify
+% the relationship between NWMC and the probability induced by a WMC
+% formulation, i.e., Pr_{\Delta, w}(q) = \frac{WMC(\Delta \land q,
+% w)}{WMC(\Delta, w)}.
 
@@
 
+% TODO: Feedback: Can you say something here about factorized vs non-factorized
+% weight function definitions? That is, factorized is when w maps literals to
+% R_>=0, non-factorized is when w maps models to R_>=0 and show:
+% a) come up with nice example when non-factorized weights are intuitive
+% b) what if weight functions are negative/complex?
+% c) clarify that the factorized definition have is w.r.t. models, in case some
+% one gets confused [It doesn't have to be, if the BA is not free -- P.]
+% d) can you say something about WMI
+
 \section{An Extension to First-Order Logic}
+
+% TODO: Feedback: My general remark here is that this section looks very [???]
+% for SRL/WMC/PRM readers. The first-order [???] may not be justified if we are
+% only doing essentially propositional models. If we also consider full FoL,
+% i.e., infinite domains, and make this a separate paper for KR-type audience.
+% That is, let us do the WMC/WMI bit separately and do FO-version in another
+% paper for KR track. Title for second paper: "Measures on first-order
+% structures via WMC" (or similar...).
 
@@
   arbitrary measure. We know that $\mathbf{B}$ has $n = 2^{|L|}$ atoms. Let
-  $(a_i)_{i=1}^n$ be those atoms. Let $L' = L \cup \{ \phi_i \mid i \in [n] \}$
-  be the set $L$ extended with $n$ new literals. Let $\mathbf{B'} =
-  \mathbf{C}/I$ be the quotient of the Boolean algebra $\mathbf{C}$ freely
-  generated by $L'$ and the ideal $I$ generated by
+  $(a_i)_{i=1}^n$ denote those atoms in some arbitrary order. Let $L' = L \cup
+  \{ \phi_i \mid i \in [n] \}$ be the set $L$ extended with $n$ new literals.
+  Let $\mathbf{B'}$ be the unique Boolean algebra with
   \[
-    \{\phi_i \land \phi_j \mid i, j \in [n], i \ne j \} \cup \{ a_i \land \phi_j
-    \mid i, j \in [n], i \ne j \}.
+    \{ a_i \land \phi_i \mid i \in [n] \} \cup \{ a_i \land \neg \phi_i \mid i
+    \in [n] \}
   \]
-  Let $h : \mathbf{B} \to \mathbf{B'}$ be the Boolean homomorphism defined by
-  $h(l) = l$ for all $l \in L$ (note that this indeed defines a homomorphism).
-  Let $w : L' \to \mathbb{R}_{> 0}$ be defined by
+  as its set of atoms. Let $\iota : \mathbf{B} \to \mathbf{B'}$ be the inclusion
+  homomorphism (i.e., $\iota(a) = a$ for all $a \in \mathbf{B}$). Let $w : L'
+  \to \mathbb{R}_{> 0}$ be defined by
   \[
     w(l) = \begin{cases}
-      m(a_i) & \text{if } l = \phi_i \text{ for some } i \in [n] \\
+      \frac{m(a_i)}{2} & \text{if } l = \phi_i \text{ or } l = \neg\phi_i \text{
+        for some } i \in [n] \\
       1 & \text{otherwise}
@@
   \]
-  for all $l \in L'$. This defines a WMC measure $m' : \mathbf{B'} \to
-  \mathbb{R}_{\ge 0}$. Furthermore,
+  for all $l \in L'$, and note that this defines a WMC measure $m' : \mathbf{B'}
+  \to \mathbb{R}_{\ge 0}$. Then
   \[
-    m(a) = m'(h(a)).
+    m(a) = (m' \circ \iota)(a)
   \]
+  for all $a \in \mathbf{B}$.
 \end{theorem}
@@
 In simpler terms, any measure can be computed using WMC by extending the Boolean
-algebra with more literals and connecting the two via a homomorphism. More
-precisely, we are given the red part in
+algebra with more literals. More precisely, we are given the red part in
 \[
   \begin{tikzcd}
-    & \textcolor{red}{\mathbb{R}_{\ge 0}} & & \\
-    \textcolor{red}{\mathbf{B}} \arrow[red]{ur}{m} \arrow{rr}{h} & & \mathbf{B'}
-    \arrow{ul}[swap]{m'} & \\
-    \textcolor{red}{L} \arrow[Subset,red]{u}{} \arrow[Subset]{rr}{} & & L'
+    \textcolor{red}{\mathbb{R}_{\ge 0}} & & \\
+    \textcolor{red}{\mathbf{B}} \arrow[red]{u}{m} \arrow{r}{\iota} &
+    \mathbf{B'} \arrow{lu}[swap]{m'} & \\
+    \textcolor{red}{L} \arrow[Subset,red]{u}{} \arrow[Subset]{r}{} & L'
     \arrow[Subset]{u}{} \arrow{r}{w} & \mathbb{R}_{>0}
@@
 % independence assumptions)
-%\begin{proposition}
+\begin{proposition}
+  In the worst case (i.e., with no independence assumptions), adding $2^{|L|}$
+  literals is the best we can do.
 %  In \cref{thm:extension}, if $L'$ has less than $n$ additional elements, then
 %  there exists a measure $$
-%\end{proposition}
+\end{proposition}
 
@@
 % Darwiche
+% TODO: what about ENC2?
+Let us note how our lower bound on the number of added literals compares to ENC1
+\cite{DBLP:conf/kr/Darwiche02} and ENC2
 

### 2020-03-12 paper.tex
Narrowing the scope of the paper

@@
 % d) can you say something about WMI
-
-\section{An Extension to First-Order Logic}
-
-% TODO: Feedback: My general remark here is that this section looks very [???]
-% for SRL/WMC/PRM readers. The first-order [???] may not be justified if we are
-% only doing essentially propositional models. If we also consider full FoL,
-% i.e., infinite domains, and make this a separate paper for KR-type audience.
-% That is, let us do the WMC/WMI bit separately and do FO-version in another
-% paper for KR track. Title for second paper: "Measures on first-order
-% structures via WMC" (or similar...).
-
-\subsection{Preliminaries}
-
-What follows is a summary of \cite{halmos2016algebraic}.
-
-% Generic stuff
-Let $\mathbf{B}$ be a Boolean algebra (of propositions). Let $X$ be the
-(non-empty) domain of discourse. Let $I$ be an index set, elements of which can
-be interpreted as variables. The elements of $X^I$ are functions from $I$ to
-$X$. For any $x \in X^I$ and $i \in I$, we write $x_i$ to represent $x(i) \in
-X$. Let $\mathbf{A^*}$ be the set of all functions $X^I \to \mathbf{B}$, and
-note that it forms a Boolean algebra with operations defined pointwise.
-
-% Defining S
-Let $T$ be the semigroup of all $I \to I$ transformations. For any $\tau \in
-T$, let $\tau_* : X^I \to X^I$ be defined by
-\[
-  (\tau_* x)_i = x_{\tau i}
-\]
-for all $x \in X^I$ and $i \in I$. For any (Boolean/polyadic) algebra
-$\mathbf{C}$, let $\End(\mathbf{C})$ denote the set of all its endomorphisms. We
-can then define $\mathbf{S}$ to be a map $\mathbf{S} : T \to \End(\mathbf{A^*})$
-defined by
-\[
-  \mathbf{S}(\tau)p(x) = p(\tau_* x)
-\]
-for all $x \in X^I$ and $p \in \mathbf{A^*}$.
-
-% Defining E
-For any $J \subseteq I$, let $J_*$ be the relation on $X^I$ defined by
-\[
-  xJ_*y \quad \iff \quad x_i = y_i \quad \text{for all } i \in I \setminus J
-\]
-for all $x, y \in X^I$. For any $J \subseteq I$, we then define $\bm\exists(J)$
-to be a transformation $\mathbf{A^*} \to \mathbf{A^*}$ defined by
-\[
-  \bm\exists(J)p(x) = \bigvee_{\substack{y \in X^I,\\ xJ_*y}} p(y)
-\]
-for all $p \in \mathbf{A^*}$, provided this supremum exists for all $x \in
-X^I$\footnote{The universal quantifier $\bm\forall(J)$ is then defined as
-  $\bm\forall(J)p = \neg(\bm\exists(J)\neg p)$ for all $p \in \mathbf{A^*}$.}.
-
-Finally, a \emph{functional polyadic (Boolean) algebra}\footnote{To be more
-  explicit, a $\mathbf{B}$-valued functional polyadic algebra with domain $X$
-  and variables $I$.} is a subalgebra
-$\mathbf{A}$ of $\mathbf{A^*}$ such that:
-\begin{itemize}
-\item $\mathbf{S}(\tau)p \in \mathbf{A}$ for all $p \in \mathbf{A}$ and $\tau
-  \in T$;
-\item $\bm\exists(J)p \in \mathbf{A}$ for all $p \in \mathbf{A}$ and $J
-  \subseteq I$.
-\end{itemize}
-
-\begin{definition}
-  Similarly to $\bm\exists$, a \emph{constant} $c$ is a map $c: \mathcal{P}(I)
-  \to \End(\mathbf{A})$ (Boolean endomorphisms?) such that:
-  \begin{itemize}
-  \item $c(\emptyset) = \id_{\mathbf{A}}$;
-  \item $c(J \cup K) = c(J)c(K)$;
-  \item $c(J)\bm\exists(K) = \bm\exists(K)c(J \setminus K)$;
-  \item $\bm\exists(J)c(K) = c(K)\bm\exists(J \setminus K)$;
-  \item $c(J)\mathbf{S}(\tau) = \mathbf{S}(\tau)c(\tau^{-1}J)$
-  \end{itemize}
-  for all $J, K \in \mathcal{P}(I)$ and $\tau \in T$. If $J$ is a singleton
-  set $\{ i \}$, we will simply write $c(i)$ instead of $c(J)$.
-\end{definition}
-
-\subsection{New Results}
-
-\begin{proposition} \label{prop:polyadic_measure}
-  Let $\mathbf{B}$ be a finite Boolean algebra with a measure $m :
-  \mathbf{B} \to [0, 1]$. Let $\mathbf{A}$ be a $\mathbf{B}$-valued functional
-  polyadic algebra with domain $X$ and variables $I$. Let $m^* : \mathbf{A} \to
-  \mathbb{R}_{\ge 0}$ be defined by
-  \[
-    m^*(p) = \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(y)
-  \]
-  for all $p \in \mathbf{A}$. Then $m^*$ is a measure on $\mathbf{A}$.
-\end{proposition}
-
-\begin{remark}
-  While definitions of $m^*$ such as
-  \[
-    m^*(p) = m \left( \bigvee_{x \in X^I} p(x) \right)
-  \]
-  might look tempting, they are not additive.
-\end{remark}
-
-\begin{proof}\todo[inline]{Update the proof w.r.t. definitions}
-  First, we can show that $m^*(1) = 1$ by observing that
-  \[
-    m^*(1) = \sum_{\text{atoms } y \in \mathbf{B}} m(y) = m \left(
-      \bigvee_{\text{atoms } y \in \mathbf{B}} y \right) = m(1) = 1,
-  \]
-  where we use \cref{thm:representation} and express $1 \in \mathbf{B}$ as the
-  supremum of all atoms in $\mathbf{B}$ \cite{ganesh2006introduction}. Clearly
-  $m^*(p) \ge 0$ for all $p \in \mathbf{A}$, so we can restrict the codomain of
-  $m^*$ to $[0, 1]$.
-
-  Next, we want to show that $m^*(p) > 0$ for all $p \in \mathbf{A} \setminus \{
-  0 \}$. If $p \ne 0$, then there must be some $x' \in X^I$ such that $p(x') \ne
-  0$. But then, since finite Boolean algebras are atomic, there must also be an
-  atom $y \in \mathbf{B}$ such that $y \le p(x')$. Therefore, $m^*(p) \ge m(y) >
-  0$, finishing this part of the proof.
-
-  Let $p, q \in \mathbf{A}$ be such that $p \land q = 0$. We want to show
-  that $m^*(p \lor q) = m^*(p) \lor m^*(q)$. First, note that
-  \[
-    y \le (p \lor q)(x) = p(x) \lor q(x)
-  \]
-  if and only if
-  \[
-    y = (p(x) \lor q(x)) \land y = (p(x) \land y) \lor (q(x) \land y)
-  \]
-  by \cref{def:ba}. Also note that
-  \[
-    (p(x) \land y) \land (q(x) \land y) = p(x) \land q(x) \land y = (p \land
-    q)(x) \land y = 0 \land y = 0,
-  \]
-  so
-  \[
-    m(y) = m((p(x) \land y) \lor (q(x) \land y)) = m(p(x) \land y) + m(q(x) \land y)
-  \]
-  by \cref{def:measure} which then leads to
-  \begin{align*}
-    m^*(p \lor q) &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(y) = \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(p(x) \land y) + m(q(x) \land y) \\
-                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(q(x) \land y).
-  \end{align*}
-  Since $y$ is an atom,
-  \[
-    p(x) \land y  = \begin{cases}
-      y & \text{if } y \le p(x) \\
-      0 & \text{otherwise,}
-    \end{cases}
-  \]
-  so
-  \begin{align*}
-    m^*(p \lor q) &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x) \text{ and } y \le p(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x) \text{ and } y \le q(x)}} m(q(x) \land y) \\
-                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le q(x)}} m(q(x) \land y) \\
-                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le q(x)}} m(y) = m^*(p) + m^*(q),
-  \end{align*}
-  finishing the proof that $m^*$ is a measure.
-\end{proof}
-
-\begin{lemma} \label{lemma:simple_measure}
-  Given the setup of \cref{prop:polyadic_measure} and $p \in \mathbf{A}$, if
-  $p(x) = p(y)$ for all $x, y \in X^I$ (i.e., $p$ has no free variables), then
-  \[
-    m^*(p) = m(p(x))
-  \]
-  (for some $x \in X^I$) is an alternative (i.e., equivalent and simpler)
-  definition of $m^*$.
-\end{lemma}
-\begin{proof}
-  Fix some $x \in X^I$. Then
-  \[
-    m(p(x)) = m \left( \bigvee_{\substack{\text{atoms } y \in \mathbf{B} \text{
-            s.t.}\\
-          y \le p(x)}} y \right) = \sum_{\substack{\text{atoms } y \in \mathbf{B}
-        \text{ s.t.}\\
-        y \le p(x)}} m(y) =\sum_{\substack{\text{atoms } y \in \mathbf{B}
-        \text{ s.t.}\\
-        \exists x' \in X^I : y \le p(x')}} m(y) = m^*(p),
-  \]
-  where we use \cref{thm:representation} for the first step,
-  \cref{def:measure} and \cref{lemma:atomic} for the second step, the
-  assumptions of \cref{lemma:simple_measure} for the third step, and the
-  definition of $m^*$ for the fourth one.
-\end{proof}
-
-\section{How Probabilities Are Computed}
-
-\subsection{Preliminaries}
-
-\begin{definition}[\cite{givant2008introduction}] \label{def:boolean_ideal}
-  An \emph{ideal} in a Boolean algebra $\mathbf{B}$ is a subset $M \subseteq
-  \mathbf{B}$ such that:
-  \begin{itemize}
-  \item $0 \in M$;
-  \item $x \lor y \in M$ for all $x, y \in M$;
-  \item $x \land y \in M$ for all $x \in M$ and $y \in \mathbf{B}$.
-  \end{itemize}
-  For any subset $S \subseteq \mathbf{B}$, the \emph{ideal generated by $S$} is
-  the smallest ideal $M$ such that $S \subseteq M$.
-\end{definition}
-
-Note that \cref{def:boolean_ideal} gives us a simple characterisation of an
-ideal generated by a set of atoms.
-
-\begin{lemma}
-  Let $\mathbf{B}$ be a Boolean algebra, and let $S \subseteq \mathbf{B}$ be a
-  set of atoms. The ideal $I$ generated by $S$ is defined by the following:
-  \begin{itemize}
-  \item $0 \in I$,
-  \item $S \subseteq I$,
-  \item $x \lor y \in I$ for all $x, y \in I$.
-  \end{itemize}
-\end{lemma}
-
-\begin{definition}[\cite{givant2008introduction}]
-  Let $\mathbf{B}$ be a Boolean algebra, and let $I$ be an ideal in
-  $\mathbf{B}$. The \emph{quotient algebra} $\mathbf{B}/I$ is a Boolean algebra
-  on equivalence classes of elements of $\mathbf{B}$ (with operations defined
-  pointwise) based on the equivalence relation
-  \[
-    x \sim y \quad \iff \quad x + y \in I
-  \]
-  where $x + y = (x \land \neg y) \lor (y \land \neg x)$ is the symmetric
-  difference operation (written as a sum because it can interpreted as the
-  `additive' part of the corresponding Boolean ring).
-\end{definition}
-
-\subsection{New Results (an Example)}
-
-In order to make the example algebras easily describable, our example programs
-will have to be tiny. Consider the following ProbLog
-\cite{DBLP:conf/ijcai/RaedtKT07} program:
-\begin{align*}
-  1.0 &\dblcolon \mathsf{p}(a, b).\\
-  0.5 &\dblcolon \mathsf{p}(X, X) \coloneq \mathsf{p}(X, Y);\, \mathsf{p}(Y, X).
-\end{align*}
-Let $L = \{ \mathsf{p}(a, a), \mathsf{p}(a, b), \mathsf{p}(b, a), \mathsf{p}(b,
-b) \}$ be the set of all possible ground atoms. Let $\mathbf{B}$ be the
-Boolean algebra freely generated by $L$ (see, e.g.,
-\cite{givant2008introduction} for more on free Boolean algebras). Then
-$\mathbf{B}$ will have sixteen atoms ranging from $\mathsf{p}(a, a) \land
-\mathsf{p}(a, b) \land \mathsf{p}(b, a) \land \mathsf{p}(b, b)$ to
-$\neg\mathsf{p}(a, a) \land \neg\mathsf{p}(a, b) \land \neg\mathsf{p}(b, a)
-\land \neg\mathsf{p}(b, b)$. The weight function $w : L \to \mathbb{R}_{\ge 0}$
-defined by
-\[
-  w(l) = \begin{cases}
-    1 & \text{if } l = \mathsf{p}(a, b) \\
-    0.5 & \text{if } l \in \{ \mathsf{p}(a, a), \mathsf{p}(b, b) \} \\
-    0 & \text{if } l = \mathsf{p}(b, a) \\
-    1-w(l') & \text{if } l = \neg l'
-  \end{cases}
-\]
-for all $l \in L$ defines a WMC measure over $\mathbf{B}$. Note that while we
-could define an ideal generated by $\{ \mathsf{p}(b, a), \neg\mathsf{p}(a, b)
-\}$ and take the quotient of $\mathbf{B}$ by that ideal to get a Boolean algebra
-with a strictly positive measure, this would put zero-probability queries
-outside of our algebras, i.e., we would not be able to ask a question whose
-answer is zero.
-
-\begin{table}
-  \centering
-  \caption{Example elements of $\mathbf{A}$ as maps $X^I \to \mathbf{B}$, with
-    $a : \mathcal{P}(I) \to \End(\mathbf{A})$ as one of two possible constants.}
-  \label{tbl:examples}
-  \begin{tabular}{ll}
-    \toprule
-    Element of $\mathbf{A}$ & Action on $X^I$ \\
-    \midrule
-    $p = \mathbf{S}(\id)p = \bm\exists(\emptyset)p = a(\emptyset)p = b(\emptyset)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_2)$ \\
-    $\bm\exists(1)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, x_2) \lor \mathsf{p}(b, x_2)$ \\
-    $\bm\exists(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, a) \lor \mathsf{p}(x_1, b)$ \\
-    $\bm\exists(I)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, a) \lor \mathsf{p}(a, b) \lor \mathsf{p}(b, a) \lor \mathsf{p}(b, b)$ \\
-    $\mathbf{S}(\{ 1 \mapsto 1, 2 \mapsto 1 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_1)$ \\
-    $\mathbf{S}(\{ 1 \mapsto 2, 2 \mapsto 1 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_2, x_1)$ \\
-    $\mathbf{S}(\{ 1 \mapsto 2, 2 \mapsto 2 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_2, x_2)$ \\
-    $a(1)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, x_2)$ \\
-    $a(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, a)$ \\
-    $a(I)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, a)$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Finally, let $\mathbf{A}$ be the functional polyadic algebra $X^I \to
-\mathbf{B}$ for $I = \{1, 2\}$ and $X = \{ a, b \}$\footnote{$X$ cannot (or
-  should not) have constants that do not occur in $\mathbf{B}$.}. The elements
-of $X^I$ can then be represented as tuples $(x_1, x_2)$ for some $x_1, x_2 \in
-X$. See \cref{tbl:examples} for example elements of $\mathbf{A}$ which consists
-of a single predicate function $p$ and operators $\bm\exists, \mathbf{S}, a, b,
-\neg, \land, \lor$, the last three of which are defined pointwise.
-
-\begin{table}
-  \centering
-  \caption{Step-by-step derivation of how a more complex element of
-    $\mathbf{A}$ acts on elements of $X^I$}
-  \label{tbl:derivation}
-  \begin{tabular}{ll}
-    \toprule
-    Element of $\mathbf{A}$ & Action on $X^I$ \\
-    \midrule
-    $p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_2)$ \\
-    $b(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, b)$ \\
-    $\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\mathsf{p}(x_1, b)$ \\
-    $\bm\exists(1)\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\mathsf{p}(a, b) \lor \neg\mathsf{p}(b, b) = \neg(\mathsf{p}(a, b) \land \mathsf{p}(b, b))$ \\
-    $\bm\forall(1)b(2)p = \neg\bm\exists(1)\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\neg(\mathsf{p}(a, b) \land \mathsf{p}(b, b)) = \mathsf{p}(a, b) \land \mathsf{p}(b, b)$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}
-  \centering
-  \caption{Atoms $y \in \mathbf{B}$ (and their measures) such that $y \le
-    \mathsf{p}(a, b) \land \mathsf{p}(b, b)$}
-  \label{tbl:atoms}
-  \begin{tabular}{lc}
-    \toprule
-    Atom $y \in \mathbf{B}$ & $m(y)$ \\
-    \midrule
-    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \mathsf{p}(a, a) \land \mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 0 = 0$ \\
-    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \neg\mathsf{p}(a, a) \land \mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 0 = 0$ \\
-    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \mathsf{p}(a, a) \land \neg\mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 1 = 0.25$ \\
-    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \neg\mathsf{p}(a, a) \land \neg\mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 1 = 0.25$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Let us calculate the probability $\Pr(\forall x_1 \in X, \mathsf{p}(x_1, b))$.
-The same expression can be translated into the notation for our polyadic algebra
-$\mathbf{A}$ as $m^*(\bm\forall(1)b(2)p)$. Recall that $\bm\forall(1)b(2)p =
-\neg\bm\exists(1)\neg b(2)p$. The effect of this function on an arbitrary
-element of $X^I$ is derived step-by-step in \cref{tbl:derivation}. Since the
-resulting function is constant (i.e., the logical formula has no free
-variables), \cref{lemma:simple_measure} tells us that
-\[
-  m^*(\bm\forall(1)b(2)p) = m(\mathsf{p}(a, b) \land \mathsf{p}(b, b)) = m
-  \left( \bigvee_{\substack{\text{atoms } y \in \mathbf{B} \text{ s.t.}\\
-        y \le \mathsf{p}(a, b) \land \mathsf{p}(b, b)}} y \right) = \sum
-  _{\substack{\text{atoms } y \in \mathbf{B} \text{ s.t.}\\
-      y \le \mathsf{p}(a, b) \land \mathsf{p}(b, b)}} m(y).
-\]
-The resulting sum is over four atoms; these atoms and their probabilities are
-listed in \cref{tbl:atoms}. Thus, we get that
-\[
-  m^*(\bm\forall(1)b(2)p) = 0 + 0 + 0.25 + 0.25 = 0.5.
-\]
 

### 2020-03-13 paper.tex
Moving on to the proof of the lower bound of extensions of BAs

@@
 \section{Introduction}
+% TODO: use \colon instead of :
 
@@
   $(a_i)_{i=1}^n$ denote those atoms in some arbitrary order. Let $L' = L \cup
-  \{ \phi_i \mid i \in [n] \}$ be the set $L$ extended with $n$ new literals.
-  Let $\mathbf{B'}$ be the unique Boolean algebra with
+  \{ \phi_i \mid i \in [n] \} \cup \{ \neg \phi_i \mid i \in [n] \}$ be the set
+  $L$ extended with $2n$ new literals. Let $\mathbf{B'}$ be the unique Boolean
+  algebra with
   \[
-    \{ a_i \land \phi_i \mid i \in [n] \} \cup \{ a_i \land \neg \phi_i \mid i
+    \{ \phi_i \land a_i \mid i \in [n] \} \cup \{ \neg \phi_i \land a_i \mid i
     \in [n] \}
@@
 
-\begin{proof}
-  % TODO
+% TODO: make J depend on i
+\begin{proof} % TODO: find a reference for this first claim
+  Since $\mathbf{B}$ is freely generated by $L$, each atom $a_i \in \mathbf{B}$
+  is an infimum of elements in $L$, i.e.,
+  \[
+    a_i = \bigwedge_{j \in J} a_{i,j}
+  \]
+  for some $\{ a_{i,j} \}_{j \in J} \subset L$. Moreover, each atom $b \in
+  \mathbf{B'}$ can be represented as either
+  \[
+    b = \phi_i \land a_i \quad \text{or} \quad b = \neg\phi_i \land a_i
+  \]
+  for some atom $a_i \in \mathbf{B}$, also making it an infimum over a subset of
+  $L'$. Then, for any $b \in \mathbf{B}$,
+  \[
+    (m' \circ \iota)(b) = \sum_{\substack{\text{atoms } a_i \in \mathbf{B}:\\
+        \phi_i \land a_i \le \iota(b)}} (w(\phi_i) + w(\neg\phi_i)) \prod_{j \in
+    J} w(a_{i,j}),
+  \]
+  recognising that, for any $\iota(b)$, any atom $a_i \in \mathbf{B}$ satisfies
+  \[
+    \phi_i \land a_i \le \iota(b)
+  \]
+  if and only if it satisfies
+  \[
+    \neg\phi_i \land a_i \le \iota(b).
+  \]
+  Then, according to the definition of $w$,
+  \[
+    (m' \circ \iota)(b) = \sum_{\substack{\text{atoms } a_i \in \mathbf{B}:\\
+        \phi_i \land a_i \le \iota(b)}} (w(\phi_i) + w(\neg\phi_i)) =
+    \sum_{\substack{\text{atoms } a_i \in \mathbf{B}:\\ \phi_i \land a_i \le
+        \iota(b)}} m(a_i) = m(b),
+  \]
+  provided that
+  \[
+    \phi_i \land a_i \le \iota(b) \quad \text{if and only if} \quad a_i \le b,
+  \]
+  but this is equivalent to
+  \[
+    \phi_i \land a_i = \phi_i \land a_i \land b \quad \text{if and only if}
+    \quad a_i = a_i \land b
+  \]
+  which is true because $\phi_i \not\in L$.
 \end{proof}
+
+Now we can show that the construction in \cref{thm:extension} is smallest
+possible.
 
@@
 \begin{proposition}
-  In the worst case (i.e., with no independence assumptions), adding $2^{|L|}$
-  literals is the best we can do.
-%  In \cref{thm:extension}, if $L'$ has less than $n$ additional elements, then
-%  there exists a measure $$
+  Let $\mathbf{B}$ and $\mathbf{B'}$ be Boolean algebras, and $\iota :
+  \mathbf{B} \to \mathbf{B'}$ be the inclusion map such that $\mathbf{B}$ is
+  freely generated by $L$, all atoms of $\mathbf{B'}$ can be expressed as
+  meets of elements of $L'$, and the following subset relations are satisfied:
+  \[
+    \begin{tikzcd}
+      \mathbf{B} \arrow{r}{\iota} & \mathbf{B'} \\
+      L \arrow[Subset]{u}{} \arrow[Subset]{r}{} & L' \arrow[Subset]{u}{}
+    \end{tikzcd}
+  \]
+  If, for any measure $m : \mathbf{B} \to \mathbb{R}_{\ge 0}$, one can
+  construct a weight function $w : L' \to \mathbb{R}_{>0}$ such that the WMC
+  measure $\WMC : \mathbf{B'} \to \mathbb{R}_{\ge 0}$ with respect to $w$
+  satisfies
+  \[
+    m = \WMC \circ \iota,
+  \]
+  then $|L' \setminus L| \ge 2^{|L|+1}$.
 \end{proposition}
+\begin{proof}
+  % 1. An atom in B' must have more than just elements of L.
+  Let $a$ be an atom in $\mathbf{B}$, and let $b$ be an atom in $\mathbf{B'}$
+  such that $b \le a$. First, let us notice that as long as $|L| \ge
+  4$\footnote{Note that $|L|$ has to be an even number.}, $b \ne a$. Indeed, let
+  $p, r, \neg p, \neg r \in L$. Then
+  \begin{align*}
+    (\WMC \circ \iota)(p \land r) &= w(p)w(r), \\
+    (\WMC \circ \iota)(p \land \neg r) &= w(p)w(\neg r), \\
+    (\WMC \circ \iota)(\neg p \land r) &= w(\neg p)w(r), \\
+    (\WMC \circ \iota)(\neg p \land \neg r) &= w(\neg p)w(\neg r), \\
+  \end{align*}
+  But then we have that
+  \[
+    \frac{m(p \land r)}{m(\neg p \land r)} = \frac{w(p)}{w(\neg p)} =
+    \frac{m(p \land \neg r)}{m(\neg p \land \neg r)}.
+  \]
+  This places a condition on $m$, contradicting the assumption that the
+  construction works for an arbitrary $m$. Hence $b < a$.
+
+  % 2. If we add phi, then we must also add -phi.
+  % 3. Extension to multiple literals: we must have all (2^n) combinations of
+  % added literals).
+  % 4. Profit
+\end{proof}
 

### 2020-03-14 paper.tex
Comparison to other encodings

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{conjecture}{Conjecture}
 \theoremstyle{definition}
@@
 
-% TODO: proof that n is the smallest number (in the worst case, without
-% independence assumptions)
-\begin{proposition}
+\begin{conjecture}
   Let $\mathbf{B}$ and $\mathbf{B'}$ be Boolean algebras, and $\iota :
@@
   then $|L' \setminus L| \ge 2^{|L|+1}$.
-\end{proposition}
-\begin{proof}
-  % 1. An atom in B' must have more than just elements of L.
-  Let $a$ be an atom in $\mathbf{B}$, and let $b$ be an atom in $\mathbf{B'}$
-  such that $b \le a$. First, let us notice that as long as $|L| \ge
-  4$\footnote{Note that $|L|$ has to be an even number.}, $b \ne a$. Indeed, let
-  $p, r, \neg p, \neg r \in L$. Then
-  \begin{align*}
-    (\WMC \circ \iota)(p \land r) &= w(p)w(r), \\
-    (\WMC \circ \iota)(p \land \neg r) &= w(p)w(\neg r), \\
-    (\WMC \circ \iota)(\neg p \land r) &= w(\neg p)w(r), \\
-    (\WMC \circ \iota)(\neg p \land \neg r) &= w(\neg p)w(\neg r), \\
-  \end{align*}
-  But then we have that
+\end{conjecture}
+% \begin{proof}
+%   % 1. An atom in B' must have more than just elements of L.
+%   Let $a$ be an atom in $\mathbf{B}$, and let $b$ be an atom in $\mathbf{B'}$
+%   such that $b \le a$. First, let us notice that as long as $|L| \ge
+%   4$\footnote{Note that $|L|$ has to be an even number.}, $b \ne a$. Indeed, let
+%   $p, r, \neg p, \neg r \in L$. Then
+%   \begin{align*}
+%     (\WMC \circ \iota)(p \land r) &= w(p)w(r), \\
+%     (\WMC \circ \iota)(p \land \neg r) &= w(p)w(\neg r), \\
+%     (\WMC \circ \iota)(\neg p \land r) &= w(\neg p)w(r), \\
+%     (\WMC \circ \iota)(\neg p \land \neg r) &= w(\neg p)w(\neg r), \\
+%   \end{align*}
+%   But then we have that
+%   \[
+%     \frac{m(p \land r)}{m(\neg p \land r)} = \frac{w(p)}{w(\neg p)} =
+%     \frac{m(p \land \neg r)}{m(\neg p \land \neg r)}.
+%   \]
+%   This places a condition on $m$, contradicting the assumption that the
+%   construction works for an arbitrary $m$. Hence $b < a$.
+
+%   Second, we can show that if $b = a \land \bigwedge_{i = 1}^k \phi_i$ for some
+%   positive integer $k$, then there must also be $2^k - 1$ other atoms in
+%   $\mathbf{B'}$ that correspond to every possible way to negate a subset of
+%   $\phi_i$'s, i.e., ranging from
+
+%   % 2. If we add phi, then we must also add -phi.
+%   % 3. Extension to multiple literals: we must have all (2^n) combinations of
+%   % added literals).
+%   % 4. Profit
+% \end{proof}
+
+Let us note how our lower bound on the number of added literals compares to two
+methods of translating a discrete probability distribution into a WMC problem
+over a propositional knowledge base proposed by Darwiche
+\cite{DBLP:conf/kr/Darwiche02} and Sang et al. \cite{sang2005solving}. Suppose
+we have a discrete probability distribution with  $n$ variables, and the $i$-th
+variable has $v_i$ values, for each $i \in [n]$. Interpreted as a logical
+system, it has $\prod_{i=1}^n v_i$ models. My expansion would then use
 \[
-    \frac{m(p \land r)}{m(\neg p \land r)} = \frac{w(p)}{w(\neg p)} =
-    \frac{m(p \land \neg r)}{m(\neg p \land \neg r)}.
+  \sum_{i=1}^n v_i + 2\prod_{i=1}^n v_i
 \]
-  This places a condition on $m$, contradicting the assumption that the
-  construction works for an arbitrary $m$. Hence $b < a$.
-
-  % 2. If we add phi, then we must also add -phi.
-  % 3. Extension to multiple literals: we must have all (2^n) combinations of
-  % added literals).
-  % 4. Profit
-\end{proof}
-
-% TODO: describe how my approach is better in the worst case than that by
-% Darwiche
-% TODO: what about ENC2?
-Let us note how our lower bound on the number of added literals compares to ENC1
-\cite{DBLP:conf/kr/Darwiche02} and ENC2
+variables, i.e., a variable for each possible variable-value assignment, and two
+additional variables for each model. Without making any independence
+assumptions, the encoding by Darwiche \cite{DBLP:conf/kr/Darwiche02} would use
+\[
+  \sum_{i=1}^n v_i + \sum_{i=1}^n \prod_{j=1}^i v_j
+\]
+variables, while for the encoding by Sang et al. \cite{sang2005solving},
+\[
+  \sum_{i=1}^n v_i + \sum_{i=1}^n (v_i - 1) \prod_{j=1}^{i-1} v_j
+\]
+variables would suffice.
 

### 2020-03-19 paper.tex
Some references

@@
 
-\title{On the Limitations of Weighted Model Counting}
+%\title{On the Limitations of Weighted Model Counting}
+\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
+%\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
 \author{Paulius Dilkas}
@@
 \section{Introduction}
-% TODO: use \colon instead of :
-
 % Feedback: What are the main claims, what are the main takeaways, intuitive
@@
 
-%Contributions
-%\begin{itemize}
-%\item Equip polyadic algebras with a measure.
-%\item Show that it is equivalent to WMC.
-%\end{itemize}
+% Contributions:
+% 1. A generalisation of WMC adapted to Boolean algebras.
+% 2. We show that it is a valid measure.
+% 3. We show that WMC assumes independence, i.e., cannot represent all measures.
+% 4. We show how the BA can be extended with new 'literals' to represent any measure.
+% 5. (Maybe) we establish a lower bound on the number of new literals, if we
+% make no assumptions about independence.
+% 6. (I guess I could) show how evidence = quotiening by a filter, and how
+% quotiening by an ideal works
+% 7. (WMI) If all weights are 1, we extend Boolean variables to discrete
+% variables, and continuous variables are arbitrary subsets (in the
+% sigma-algebra), then the WMI process calculates the probability of any event
+% and doesn't require going down to the level of models (assuming a suitable
+% probability measure).
+% 8. If the weight of a literal (and its negation) is 1, then we don't need to
+% look at its models--the probability can be calculated at any level. This
+% extends to any number of variables.
+% 9. How WMI transforms to our algebras. The boring version and what's wrong
+% with it.
 
-% Big advantage: using algebras we can represent an incomplete state of
-% knowledge, e.g., we know m(a \/ b), but not m(a) or m(b). In infinite BAs, one
-% can have measure undefined for some elements.
+Previous/related work:
+\begin{itemize}
+\item Hailperin's approach to probability logic
+  \cite{DBLP:journals/ndjfl/Hailperin84}
+\item Nilsson's (somewhat successful) probabilistic logic
+  \cite{DBLP:journals/ai/Nilsson86}
+\item Semiring programming \cite{DBLP:journals/corr/BelleR16}
+\item WMC with functions \cite{DBLP:conf/uai/Belle17}
+\item WMI \cite{DBLP:conf/ijcai/BellePB15}
+\item Measures on Boolean algebras: overview articles (from most cited to least
+  cited)
+  \begin{itemize}
+  \item Horn and Tarski \cite{horn1948measures}
+  \item Concerning measures on Boolean algebras \cite{gaifman1964concerning}
+  \item Jech -- Measures on Boolean algebras (arXiv) \cite{jech2017measures}
+  \end{itemize}
+\item Measures on Boolean algebras: more specific articles
+  \begin{itemize}
+  \item On possibility and probability measures in finite Boolean algebras
+    \cite{DBLP:journals/soco/CastineiraCT02}
+  \item Representation of conditional probability measures
+    \cite{krauss1968representation}
+  \end{itemize}
+\end{itemize}
 
@@
 \begin{definition} \label{def:ba}
-  A \emph{Boolean algebra} is a tuple $(\mathbf{B}, \land, \lor, \neg, 0, 1)$ of
-  a set $\mathbf{B}$ with operations $\land, \lor, \neg$ and elements $0, 1 \in
-  \mathbf{B}$ such that the following axioms hold for all $a, b, \in
+  A \emph{Boolean algebra} (BA) is a tuple $(\mathbf{B}, \land, \lor, \neg, 0,
+  1)$ of a set $\mathbf{B}$ with operations $\land, \lor, \neg$ and elements $0,
+  1 \in \mathbf{B}$ such that the following axioms hold for all $a, b, \in
   \mathbf{B}$:
@@
 
-  Let $a, b \in \mathbf{B}$ be arbitrary. Let $\le$ be a partial order on
-  $\mathbf{B}$ defined by $a \le b$ if $a = b \land a$ (or, equivalently, $a
-  \lor b = b$), and let $a < b$ denote $a \le b$ and $a \ne b$.
+  We can also define a partial order $\le$ on $\mathbf{B}$ as $a \le b$ if $a =
+  b \land a$ (or, equivalently, $a \lor b = b$) for $a, b \in \mathbf{B}$.
+  Furthermore, let $a < b$ denote $a \le b$ and $a \ne b$.
 \end{definition}
 
-\todo[inline]{Which definition do I actually need?}
+For the rest of this paper, let $\mathbf{B}$ refer to the BA $(\mathbf{B},
+\land, \lor, \neg, 0, 1)$.
+
 \begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
-  An element $a \ne 0$ of a Boolean algebra $\mathbf{B}$ is an \emph{atom} if
-  there is no $x \in \mathbf{B}$ such that $0 < x < a$. Equivalently, $a \ne 0$
-  is an atom if, for all $x \in \mathbf{B}$, either $x \land a = a$ or $x \land
-  a = 0$. A Boolean algebra is \emph{atomic} if for every $a \in \mathbf{B}
-  \setminus \{0 \}$, there is an atom $x$ such that $x \le a$.
+  An element $a \ne 0$ of $\mathbf{B}$ is an \emph{atom} if, for all $x \in
+  \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
+  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. A BA
+  $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
+  \}$, there is an atom $x$ such that $x \le a$.
 \end{definition}
@@
 \begin{lemma}[\cite{ganesh2006introduction}]
-  For any two distinct atoms $a$, $b$ in a Boolean algebra, $a \land b = 0$.
+  For any two distinct atoms $a$, $b \in \mathbf{B}$, $a \land b = 0$.
 \end{lemma}
@@
 \begin{lemma}[\cite{givant2008introduction}] \label{lemma:atomic}
-  All finite Boolean algebras are atomic.
+  All finite BAs are atomic.
 \end{lemma}
+
+% TODO: all finite Boolean algebras are isomorphic to fields of sets
 
@@
   A \emph{(strictly positive) measure} on a Boolean algebra $\mathbf{B}$ is a
-  function $m : \mathbf{B} \to [0, 1]$ such that:
+  function $m\colon \mathbf{B} \to [0, 1]$ such that:
   \begin{enumerate}
@@
 % over propositions p and q.
+% TODO:  Mention Lindenbaum-Tarski algebra somewhere
 
@@
   \in M$ can be uniquely expressed as $m = \bigwedge_{i \in I} l_i$ for some $\{
-  l_i \}_{i \in I} \subseteq L$, and let $w : L \to \mathbb{R}_{>0}$ be
-  arbitrary. The \emph{weighted model count} $\WMC : \mathbf{B} \to
+  l_i \}_{i \in I} \subseteq L$, and let $w\colon L \to \mathbb{R}_{>0}$ be
+  arbitrary. The \emph{weighted model count} $\WMC\colon \mathbf{B} \to
   \mathbb{R}_{\ge 0}$ is defined as
@@
   for any $a \in \mathbf{B}$. Furthermore, we define the \emph{normalised
-    weighted model count} $\nWMC : \mathbf{B} \to [0, 1]$ as $\nWMC(a) =
+    weighted model count} $\nWMC\colon \mathbf{B} \to [0, 1]$ as $\nWMC(a) =
   \frac{\WMC(a)}{\WMC(1)}$ for all $a \in \mathbf{B}$.
@@
 \begin{proposition}
-  Let $\mathbf{B}$ be a finite measure algebra with measure $m : \mathbf{B} \to
+  Let $\mathbf{B}$ be a finite measure algebra with measure $m\colon \mathbf{B} \to
   \mathbb{R}_{\ge 0}$. Let $L \subset \mathbf{B}$ be defined as
@@
   such that $a_i \in \{ l_i, \neg l_i \}$ for $i \in [n]$. Then there exists a
-  weight function $w : L \to \mathbb{R}_{>0}$ that makes $m$ a WMC measure if
+  weight function $w\colon L \to \mathbb{R}_{>0}$ that makes $m$ a WMC measure if
   and only if
@@
 \begin{proof}
-  Let us begin with the `if' part of the statement. Let $w : L \to
+  Let us begin with the `if' part of the statement. Let $w\colon L \to
   \mathbb{R}_{>0}$ be defined by
@@
 
-  For the other direction, we are given a weight function $w : L \to
-  \mathbb{R}_{>0}$ that induces a measure $m = \nWMC : \mathbf{B} \to
+  For the other direction, we are given a weight function $w\colon L \to
+  \mathbb{R}_{>0}$ that induces a measure $m = \nWMC\colon \mathbf{B} \to
   \mathbb{R}_{\ge 0}$, and we want to show that \cref{eq:wmccondition} is
@@
 
-\subsubsection{Preliminaries}
-
-\begin{definition}[\cite{givant2008introduction}]
-  Let $\mathbf{A}$ and $\mathbf{B}$ be Boolean algebras. A \emph{Boolean
-    homomorphism} from $\mathbf{A}$ to $\mathbf{B}$ is a map $f : \mathbf{A} \to
-  \mathbf{B}$ such that:
-  \begin{itemize}
-  \item $f(x \land y) = f(x) \land f(y)$,
-  \item $f(x \lor y) = f(x) \lor f(y)$,
-  \item $f(\neg x) = \neg f(x)$
-  \end{itemize}
-  for all $x, y \in \mathbf{A}$.
-\end{definition}
-
-\begin{definition}[\cite{halmos2016algebraic}]
-  Given two polyadic algebras $\mathbf{A}$ and $\mathbf{B}$, a \emph{polyadic
-    homomorphism} from $\mathbf{A}$ to $\mathbf{B}$ is a Boolean homomorphism $f
-  : \mathbf{A} \to \mathbf{B}$ such that
-  \begin{itemize}
-  \item $f\mathbf{S}(\tau)p = \mathbf{S}(\tau)fp$,
-  \item $f\bm\exists(J)p = \bm\exists(J)fp$
-  \end{itemize}
-  for all $\tau \in T$, $p \in \mathbf{A}$, and $J \subseteq I$.
-\end{definition}
-
-\subsubsection{New Results}
-
 A well-known way to overcome this limitation of independence is by adding more
 literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending the set $L$ covered
-by the WMC weight function $w : L \to \mathbb{R}_{>0}$. Let us translate this
+by the WMC weight function $w\colon L \to \mathbb{R}_{>0}$. Let us translate this
 idea to the language of Boolean algebras.
@@
   Let $\mathbf{B}$ be a finite Boolean algebra freely generated by some set of
-  `literals' $L$, and let $m : \mathbf{B} \to \mathbb{R}_{\ge 0}$ be an
+  `literals' $L$, and let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be an
   arbitrary measure. We know that $\mathbf{B}$ has $n = 2^{|L|}$ atoms. Let
@@
   \]
-  as its set of atoms. Let $\iota : \mathbf{B} \to \mathbf{B'}$ be the inclusion
-  homomorphism (i.e., $\iota(a) = a$ for all $a \in \mathbf{B}$). Let $w : L'
+  as its set of atoms. Let $\iota\colon \mathbf{B} \to \mathbf{B'}$ be the inclusion
+  homomorphism (i.e., $\iota(a) = a$ for all $a \in \mathbf{B}$). Let $w\colon L'
   \to \mathbb{R}_{> 0}$ be defined by
@@
   \]
-  for all $l \in L'$, and note that this defines a WMC measure $m' : \mathbf{B'}
+  for all $l \in L'$, and note that this defines a WMC measure $m'\colon \mathbf{B'}
   \to \mathbb{R}_{\ge 0}$. Then
@@
 \begin{conjecture}
-  Let $\mathbf{B}$ and $\mathbf{B'}$ be Boolean algebras, and $\iota :
+  Let $\mathbf{B}$ and $\mathbf{B'}$ be Boolean algebras, and $\iota\colon
   \mathbf{B} \to \mathbf{B'}$ be the inclusion map such that $\mathbf{B}$ is
@@
   \]
-  If, for any measure $m : \mathbf{B} \to \mathbb{R}_{\ge 0}$, one can
-  construct a weight function $w : L' \to \mathbb{R}_{>0}$ such that the WMC
-  measure $\WMC : \mathbf{B'} \to \mathbb{R}_{\ge 0}$ with respect to $w$
+  If, for any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$, one can
+  construct a weight function $w\colon L' \to \mathbb{R}_{>0}$ such that the WMC
+  measure $\WMC\colon \mathbf{B'} \to \mathbb{R}_{\ge 0}$ with respect to $w$
   satisfies
@@
 
-\todo[inline,caption={}]{The big TODO list
-  \begin{itemize}
-  \item Extension to infinite (atomic?) Boolean algebras.
-  \item Compare my polyadic measures with first-order WMC.
-  \item Abstraction refinements as homomorphisms.
-  \item Definition of a measure-preserving homomorphism from Jech's set theory
-    book.
-  \item A Boolean algebra is approximable if its Stone space is approximable.
-  \end{itemize}
-}
+% TODO: a section on WMI: 3 results
+% TODO: introducing evidence can be done by taking a quotient w.r.t. the ideal
+% that contradicts the evidence (equivalently, the filter generated by the
+% evidence).
 

### 2020-03-20 paper.tex
A nice diagram

@@
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 \theoremstyle{remark}
 \newtheorem*{remark}{Remark}
+
+\definecolor{color1}{HTML}{fbb4ae}
+\definecolor{color2}{HTML}{b3cde3}
+\definecolor{color3}{HTML}{ccebc5}
+\definecolor{color4}{HTML}{decbe4}
 
@@
 \DeclareMathOperator{\WMC}{WMC}
-\DeclareMathOperator{\nWMC}{nWMC}
+\DeclareMathOperator{\nWMC}{NWMC}
 \DeclareMathOperator{\id}{id}
@@
 
-\section{WMC as a Measure}
-
-\subsection{Preliminaries}
+\section{Preliminaries}
 
@@
   A \emph{Boolean algebra} (BA) is a tuple $(\mathbf{B}, \land, \lor, \neg, 0,
-  1)$ of a set $\mathbf{B}$ with operations $\land, \lor, \neg$ and elements $0,
-  1 \in \mathbf{B}$ such that the following axioms hold for all $a, b, \in
+  1)$ consisting of a set $\mathbf{B}$ with binary operations \emph{meet}
+  $\land$ and \emph{join} $\lor$, unary operation $\neg$ and elements $0, 1 \in
+  \mathbf{B}$ such that the following axioms hold for all $a, b, \in
   \mathbf{B}$:
@@
   \end{itemize}
-
-  We can also define a partial order $\le$ on $\mathbf{B}$ as $a \le b$ if $a =
-  b \land a$ (or, equivalently, $a \lor b = b$) for $a, b \in \mathbf{B}$.
-  Furthermore, let $a < b$ denote $a \le b$ and $a \ne b$.
 \end{definition}
 
-For the rest of this paper, let $\mathbf{B}$ refer to the BA $(\mathbf{B},
-\land, \lor, \neg, 0, 1)$.
+For clarity and succinctness, we will occasionally use three other operations
+that can be defined using the original three\footnote{We use $+$ to denote
+  symmetric difference because it is the additive operation of a Boolean ring.}:
+\begin{align*}
+  a \to b &= \neg a \lor b, \\
+  a \leftrightarrow b &= (a \to b) \land (b \to a), \\
+  a + b &= (a \land \neg b) \lor (\neg a \land b).
+\end{align*}
+We can also define a partial order $\le$ on $\mathbf{B}$ as $a \le b$ if $a = b
+\land a$ (or, equivalently, $a \lor b = b$) for $a, b \in \mathbf{B}$.
+Furthermore, let $a < b$ denote $a \le b$ and $a \ne b$. For the rest of this
+paper, let $\mathbf{B}$ refer to the BA $(\mathbf{B}, \land, \lor, \neg, 0, 1)$.
+For any $S \subseteq \mathbf{B}$, we write $\bigvee S$ for $\bigvee_{x \in S} x$
+and call it the \emph{supremum} of $S$. Similarly, $\bigwedge S = \bigwedge_{x
+  \in S} x$ is the \emph{infimum}. By convention, $\bigwedge \emptyset = 1$ and
+$\bigvee \emptyset = 0$.
 
@@
 
+\begin{lemma}[\cite{givant2008introduction}] \label{thm:representation}
+  The following are equivalent:
+  \begin{itemize}
+  \item $\mathbf{B}$ is atomic.
+  \item For any $x \in \mathbf{B}$,
+    \[
+      x = \bigvee_{\text{atoms } a \le x} a.
+    \]
+  \item $1$ is the supremum of all atoms.
+  \end{itemize}
+\end{lemma}
+
 \begin{lemma}[\cite{givant2008introduction}] \label{lemma:atomic}
@@
 
-% TODO: all finite Boolean algebras are isomorphic to fields of sets
+\begin{definition}[\cite{gaifman1964concerning,DBLP:books/daglib/0090259}] \label{def:measure}
+  A \emph{measure} on $\mathbf{B}$ is a function $m\colon
+  \mathbf{B} \to \mathbb{R}_{\ge 0}$ such that:
+  \begin{itemize}
+  \item $m(0) = 0$;
+  \item $m(x \lor y) = m(x) + m(y)$ for all $x, y \in \mathbf{B}$ whenever $x
+    \land y = 0$.
+  \end{itemize}
+  If $m(1) = 1$, we call $m$ a \emph{probability measure}. Also, if $m(x) > 0$
+  for all $x \ne 0$, then $m$ is \emph{strictly positive}.
+\end{definition}
 
-% TODO: we don't have to treat 0 as an exception we state that \/ of an empty
-% set is 0 (and /\ of an empty set is 1).
-% TODO: use bigvee and bigwedge directly with sets.
-\begin{theorem} \label{thm:representation}
-  Let $\mathbf{B}$ be a finite Boolean algebra. Then every $x \in \mathbf{B}
-  \setminus \{ 0 \}$ can be uniquely expressed as
+\section{WMC as a Measure}
+
+\begin{definition} \label{def:algebra_from_logic}
+  Let $\mathcal{L}$ be a propositional (or first-order) logic, and let
+  $\Delta$ be a theory in $\mathcal{L}$. We can define an equivalence
+  relation on formulas in $\mathcal{L}$ as
   \[
-  x = \bigvee_{\text{atoms } a \le x} a.
+    \alpha \sim \beta \quad \text{if and only if} \quad \Delta \vdash \alpha
+    \leftrightarrow \beta
   \]
-\end{theorem}
-\begin{proof}
-  A simple consequence of the theorem that every finite Boolean algebra is
-  isomorphic to a field of subsets of a set, where the cardinality of the set is
-  equal to the number of atoms in the Boolean algebra.
-\end{proof}
+  for all $\alpha, \beta \in \mathcal{L}$. Let $[\alpha]$ denote the equivalence
+  class of $\alpha \in \mathcal{L}$ with respect to $\sim$. We can then let
+  $B(\Delta) = \{ [\alpha] \mid \alpha \in \mathcal{L} \}$ and define the
+  structure of a BA on $B(\Delta)$ as
+  \begin{align*}
+    [\alpha] \lor [\beta] &= [\alpha \lor \beta], \\
+    [\alpha] \land [\beta] &= [\alpha \land \beta], \\
+    \neg[\alpha] &= [\neg\alpha], \\
+    1 &= [\alpha \to \alpha], \\
+    0 &= [\alpha \land \neg\alpha]
+  \end{align*}
+  for all $\alpha, \beta \in \mathcal{L}$. Then $B(\Delta)$ is the
+  \emph{Lindenbaum-Tarski algebra} of $\Delta$
+  \cite{koppelberg1989handbook,tarski1983logic}.
+\end{definition}
 
-\todo[inline]{Remove the requirement for being strictly positive}
-\begin{definition}[\cite{gaifman1964concerning}] \label{def:measure}
-  A \emph{(strictly positive) measure} on a Boolean algebra $\mathbf{B}$ is a
-  function $m\colon \mathbf{B} \to [0, 1]$ such that:
-  \begin{enumerate}
-  \item $m(1) = 1$, and $m(x) > 0$ for $x \ne
-    0$; \label[property]{property:values}
-  \item $m(x \lor y) = m(x) + m(y)$ for all $x, y \in \mathbf{B}$ whenever $x
-    \land y = 0$. \label[property]{property:additive}
-  \end{enumerate}
-\end{definition}
+\begin{figure}
+  \[
+    \begin{tikzcd}
+      & & & & & \colorbox{color3}{$1$} \ar[dlll,dash,gray] \ar[dl,dash,gray]
+      \ar[dr,dash,gray] \ar[drrr,dash,gray] & & & \\
+      & & \colorbox{color3}{$p \lor q$} & & \colorbox{color3}{$q \to p$} & &
+      \colorbox{color2}{$p \to q$} & & \colorbox{color4}{$\neg p \lor \neg q$}
+      \\
+      \colorbox{color3}{$p$} \ar[urr,dash,gray] \ar[urrrr,dash,gray] & &
+      \colorbox{color2}{$q$} \ar[u,dash,gray] \ar[urrrr,dash,gray] & &
+      \colorbox{color2}{$p \leftrightarrow q$} \ar[u,dash,gray]
+      \ar[urr,dash,gray] & & \colorbox{color4}{$p + q$} \ar[ullll,dash,gray]
+      \ar[urr,dash,gray] & & \colorbox{color4}{$\neg q$} \ar[ullll,dash,gray]
+      \ar[u,dash,gray] & & \colorbox{color1}{$\neg p$} \ar[ullll,dash,gray]
+      \ar[ull,dash,gray] \\
+      & & \fcolorbox{black}{color2}{$p \land q$} \ar[ull,dash,gray]
+      \ar[u,dash,gray] \ar[urr,dash,gray] & & \fcolorbox{black}{color4}{$p \land
+        \neg q$} \ar[ullll,dash,gray] \ar[urr,dash,gray] \ar[urrrr,dash,gray] &
+      & \fcolorbox{black}{color1}{$\neg p \land q$} \ar[ullll,dash,gray]
+      \ar[u,dash,gray] \ar[urrrr,dash,gray] & & \fcolorbox{black}{color1}{$\neg
+        p \land \neg q$} \ar[ullll,dash,gray] \ar[u,dash,gray]
+      \ar[urr,dash,gray] \\
+      & & & & & \colorbox{color1}{$0$} \ar[ulll,dash,gray] \ar[ul,dash,gray]
+      \ar[ur,dash,gray] \ar[urrr,dash,gray] & & &
+    \end{tikzcd}
+  \]
+  \[
+    \begin{tikzcd}
+      & \colorbox{color3}{$\left[1\right]$} \ar[dl,dash,gray] \ar[dr,dash,gray]
+      & \\
+      \fcolorbox{black}{color2}{$\left[q\right]$} & &
+      \fcolorbox{black}{color4}{$\left[\neg q\right]$} \\
+      & \colorbox{color1}{$\left[0\right]$} \ar[ul,dash,gray] \ar[ur,dash,gray]
+      &
+    \end{tikzcd}
+  \]
+  \caption{Two BAs from \cref{example:construction}: $B(\mathcal{L})$ at the top
+    and $B(\Delta)$ at the bottom. An edge between elements $a$ and $b$ (with
+    $a$ positioned lower than $b$) means that $a \le b$. Each element of
+    $B(\Delta)$ is an equivalence class of elements of $B(\mathcal{L})$, and the
+    colours show which elements of $B(\mathcal{L})$ belong to which class. In
+    both algebras, atoms have borders around them.}
+  \label{fig:example}
+\end{figure}
+
+\begin{example} \label{example:construction}
+  Let $\mathcal{L}$ be a propositional logic with $p$ and $q$ as its only atoms.
+  Then $L = \{ p, q, \neg p, \neg q \}$ is its set of literals. Let $w : L \to
+  \mathbb{R}_{\ge 0}$ be the \emph{weight function} defined by
+  \begin{align*}
+    w(p) = 0.3, \\
+    w(\neg p) = 0.7, \\
+    w(q) = 0.2, \\
+    w(\neg q) = 0.8.
+  \end{align*}
+  Let $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $p$. Then
+  $\Delta$ has two models, i.e., $\{ p, q \}$ and $\{ p, \neg q \}$. The
+  \emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of $\Delta$ is
+  then
+  \[
+    \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) =
+    w(p)w(q) + w(p)w(\neg q) = 0.3.
+  \]
+
+  The corresponding BA $B(\Delta)$ can then be constructed using
+  \cref{def:algebra_from_logic}. Alternatively, one can first construct the free
+  BA generated by the set $\{ p, q \}$---this corresponds to $B(\mathcal{L})$ in
+  \cref{fig:example}---and then take a quotient with respect to either the
+  filter generated by $p$ or the ideal\footnote{More details on these concepts
+    can be found in many books on BAs
+    \cite{givant2008introduction,koppelberg1989handbook}.} generated by $\neg
+  p$. In any case, the resulting BA is pictured at the bottom of
+  \cref{fig:example}. To summarise, 
+\end{example}
+% TODO: could talk about how each element can be seen as a set of models.
+% TODO: the number of elements in the algebra.
 
@@
 % algebra map to models in WMC formulations. Probably do an example:
-% 0.3 p; 0.2 q => M = <p, qbar> has weight o3 * (1-0.2)
+% 0.3 p; 0.2 q => M = <p, qbar> has weight 0.3 * (1-0.2)
 % then it corresponds to an atom in an algebra defined over the language defined
 % over propositions p and q.
-% TODO:  Mention Lindenbaum-Tarski algebra somewhere
+% TODO: connect the two definitions of WMC
 
-\subsection{New Results}
-
-\todo[inline]{Allow weight to be zero}
 \begin{definition} \label{def:wmc}
-  Let $\mathbf{B}$ be a finite Boolean algebra, and let $M \subseteq \mathbf{B}$
-  be its set of atoms. Let $L \subseteq \mathbf{B}$ be such that every atom $m
-  \in M$ can be uniquely expressed as $m = \bigwedge_{i \in I} l_i$ for some $\{
-  l_i \}_{i \in I} \subseteq L$, and let $w\colon L \to \mathbb{R}_{>0}$ be
-  arbitrary. The \emph{weighted model count} $\WMC\colon \mathbf{B} \to
-  \mathbb{R}_{\ge 0}$ is defined as
+  Let $\mathbf{B}$ be an atomic BA, and let $M \subset \mathbf{B}$ be its set of
+  atoms. Let $L \subset \mathbf{B}$ be such that every atom $m \in M$ can be
+  uniquely expressed as $m = \bigwedge L'$ for some $L' \subseteq L$, and let
+  $w\colon L \to \mathbb{R}_{\ge 0}$ be arbitrary. The \emph{weighted model
+    count} $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
   \[
-    \WMC(a) = \begin{cases}
-      0 & \text{if } a = 0 \\
-      \prod_{i \in I} w(l_i) & \text{if } M \ni a = \bigwedge_{i \in I} l_i \\
-      \sum_{i \in I} \WMC(m_i) & \text{if } \mathbf{B} \setminus (M \cup \{ 0
-      \}) \ni a = \bigvee_{i \in I} m_i
+    \WMC_w(x) = \begin{cases}
+      0 & \text{if } x = 0 \\
+      \prod_{l \in L'} w(l) & \text{if } M \ni x = \bigwedge L' \\
+      \sum_{\text{atoms } a \le x} \WMC_w(a) & \text{otherwise}
     \end{cases}
   \]
-  for any $a \in \mathbf{B}$. Furthermore, we define the \emph{normalised
-    weighted model count} $\nWMC\colon \mathbf{B} \to [0, 1]$ as $\nWMC(a) =
-  \frac{\WMC(a)}{\WMC(1)}$ for all $a \in \mathbf{B}$.
+  for any $x \in \mathbf{B}$. Furthermore, we define the \emph{normalised
+    weighted model count} $\nWMC_w\colon \mathbf{B} \to [0, 1]$ as $\nWMC_w(x) =
+  \frac{\WMC_w(x)}{\WMC_w(1)}$ for all $x \in \mathbf{B}$. For both $\WMC_w$ and
+  $\nWMC_w$, we will drop the subscript when doing so results in no potential
+  confusion.
 \end{definition}
-% TODO: Feedback: maybe NWMC or WMC^*, as nWMC looks like a typo. Also clarify
-% the relationship between NWMC and the probability induced by a WMC
-% formulation, i.e., Pr_{\Delta, w}(q) = \frac{WMC(\Delta \land q,
-% w)}{WMC(\Delta, w)}.
+
+% TODO: Feedback: clarify the relationship between NWMC and the probability
+% induced by a WMC formulation, i.e., Pr_{\Delta, w}(q) = \frac{WMC(\Delta \land
+% q, w)}{WMC(\Delta, w)}.
 
 \begin{proposition}
-  $\nWMC$ is a measure for any finite Boolean algebra $\mathbf{B}$.
+  $\WMC$ is a measure and $\nWMC$ is a probability measure.
 \end{proposition}
 \begin{proof}
-  First, note that \cref{property:values} of \cref{def:measure} is satisfied by
-  the definition of $\nWMC$. Next, in order to prove \cref{property:additive},
+  First, note that $\WMC$ is non-negative and $\WMC(0) = 0$ by definition. Next,
   let $x, y \in \mathbf{B}$ be such that $x \land y = 0$. We want to show that
-  \[
-    \nWMC(x \lor y) = \nWMC(x) + \nWMC(y)
-  \]
-  which is equivalent to
   \begin{equation} \label{eq:additivity_proof}
@@
   \end{align*}
-  finishing the proof.
+  finishing the proof that $\WMC$ is a measure. This immediately shows that
+  $\nWMC$ is a probability measure since, by definition, $\nWMC(1) = 1$.
 \end{proof}
@@
   such that $a_i \in \{ l_i, \neg l_i \}$ for $i \in [n]$. Then there exists a
-  weight function $w\colon L \to \mathbb{R}_{>0}$ that makes $m$ a WMC measure if
+  weight function $w\colon L \to \mathbb{R}_{\ge 0}$ that makes $m$ a WMC measure if
   and only if
@@
   Let us begin with the `if' part of the statement. Let $w\colon L \to
-  \mathbb{R}_{>0}$ be defined by
+  \mathbb{R}_{\ge 0}$ be defined by
   \begin{equation} \label{eq:assumption}
@@
   For the other direction, we are given a weight function $w\colon L \to
-  \mathbb{R}_{>0}$ that induces a measure $m = \nWMC\colon \mathbf{B} \to
+  \mathbb{R}_{\ge 0}$ that induces a measure $m = \nWMC\colon \mathbf{B} \to
   \mathbb{R}_{\ge 0}$, and we want to show that \cref{eq:wmccondition} is
@@
 literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending the set $L$ covered
-by the WMC weight function $w\colon L \to \mathbb{R}_{>0}$. Let us translate this
+by the WMC weight function $w\colon L \to \mathbb{R}_{\ge 0}$. Let us translate this
 idea to the language of Boolean algebras.
@@
   homomorphism (i.e., $\iota(a) = a$ for all $a \in \mathbf{B}$). Let $w\colon L'
-  \to \mathbb{R}_{> 0}$ be defined by
+  \to \mathbb{R}_{\ge 0}$ be defined by
   \[
@@
     \textcolor{red}{L} \arrow[Subset,red]{u}{} \arrow[Subset]{r}{} & L'
-    \arrow[Subset]{u}{} \arrow{r}{w} & \mathbb{R}_{>0}
+    \arrow[Subset]{u}{} \arrow{r}{w} & \mathbb{R}_{\ge 0}
   \end{tikzcd}
@@
   If, for any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$, one can
-  construct a weight function $w\colon L' \to \mathbb{R}_{>0}$ such that the WMC
+  construct a weight function $w\colon L' \to \mathbb{R}_{\ge 0}$ such that the WMC
   measure $\WMC\colon \mathbf{B'} \to \mathbb{R}_{\ge 0}$ with respect to $w$

### 2020-03-20 paper.tex
First version of the introductory example

@@
     and $B(\Delta)$ at the bottom. An edge between elements $a$ and $b$ (with
-    $a$ positioned lower than $b$) means that $a \le b$. Each element of
+    $a$ positioned lower than $b$) means that $a < b$. Each element of
     $B(\Delta)$ is an equivalence class of elements of $B(\mathcal{L})$, and the
@@
   p$. In any case, the resulting BA is pictured at the bottom of
-  \cref{fig:example}. To summarise, 
+  \cref{fig:example}.
+
+  Each element of $B(\mathcal{L})$ can also be seen as a subset of the set of
+  all models of $\mathcal{L}$, with $0$ representing $\emptyset$, $1$
+  representing the set of all (four) models, each atom representing a single
+  model, and each edge going upward representing a subset relation. Thus,
+  the Boolean-algebraic way of calculating the WMC of $\Delta$ consists of:
+  \begin{enumerate} % TODO: why is step 1 always possible?
+  \item Identifying an element $a \in B(\mathcal{L})$ that corresponds to
+    $\Delta$.
+  \item Finding all atoms of $B(\mathcal{L})$ that are `dominated' by $a$
+    according to the partial order.
+  \item Using $w$ to calculate the weight of each such atom.
+  \item Adding the weights of these atoms.
+  \end{enumerate}
+  This motivates the following definition of WMC generalised to BAs.
 \end{example}
-% TODO: could talk about how each element can be seen as a set of models.
-% TODO: the number of elements in the algebra.
-
-% TODO: Feedback: Probably a good idea to explain how elements of the Boolean
-% algebra map to models in WMC formulations. Probably do an example:
-% 0.3 p; 0.2 q => M = <p, qbar> has weight 0.3 * (1-0.2)
-% then it corresponds to an atom in an algebra defined over the language defined
-% over propositions p and q.
-% TODO: connect the two definitions of WMC
+% TODO: how to compute the number of elements in the algebra.
+% TODO: clarify what B(L) means. And whether B(Delta) is even necessary.
+% TODO: reference for the set/subset thing.
 

### 2020-03-22 paper.tex
Statements for some new results

@@
 % with it.
+% 10. Show how to transfer the measure to a quotient algebra and that the answer
+% match with each other and with the original definition of WMC.
 
@@
 \item Semiring programming \cite{DBLP:journals/corr/BelleR16}
-\item WMC with functions \cite{DBLP:conf/uai/Belle17}
 \item WMI \cite{DBLP:conf/ijcai/BellePB15}
@@
   a \to b &= \neg a \lor b, \\
-  a \leftrightarrow b &= (a \to b) \land (b \to a), \\
+  a \leftrightarrow b &= (a \land b) \lor (\neg a \land \neg b), \\
   a + b &= (a \land \neg b) \lor (\neg a \land b).
@@
   for all $x \ne 0$, then $m$ is \emph{strictly positive}.
+\end{definition}
+
+% TODO: Start here. Define filters (ref the undergraduate book), filter
+% generation (same ref, but read it first), and quotients.
+\begin{definition}
 \end{definition}
@@
 
-% TODO: Feedback: clarify the relationship between NWMC and the probability
-% induced by a WMC formulation, i.e., Pr_{\Delta, w}(q) = \frac{WMC(\Delta \land
-% q, w)}{WMC(\Delta, w)}.
-
 \begin{proposition}
-  $\WMC$ is a measure and $\nWMC$ is a probability measure.
+  $\WMC$ is a measure, and $\nWMC$ is a probability measure.
 \end{proposition}
@@
 \end{proof}
+
+Given a theory $\Delta$ in a logic $\mathcal{L}$, the usual way of using WMC to
+compute the probability of a query $q$ is
+\cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
+\[
+  \Pr_{\Delta, w}(q) = \frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}.
+\]
+In our algebraic formulation, this can be computed in two different ways:
+\begin{itemize}
+\item as $\frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}$ in $B(\mathcal{L})$,
+\item and as $\nWMC_w([q])$ in $B(\Delta)$.
+\end{itemize}
+But how does the measure defined on $B(\mathcal{L})$ transfer to $B(\Delta)$?
+
+\begin{lemma}
+  Let $\mathbf{B}$ be a BA, and let $F$ be a filter in $\mathbf{B}$ generated by
+  $p \in \mathbf{B}$. Then, for any $a, b \in \mathbf{B}$, if $a/F = b/F$, then
+  $a \land p = b \land p$.
+\end{lemma}
+\begin{proof}
+  % TODO: reference for a/F = b/F iff a <-> b \in F
+  % TODO: reference for the definition of a filter
+\end{proof}
+
+\begin{definition}[Measures on quotients] \label{def:measures_on_quotients}
+  Let $\mathbf{B}$ be a BA with a measure $m : \mathbf{B} \to \mathbb{R}_{\ge
+    0}$, and let $F$ be a filter in $\mathbf{B}$ generated by some $p \in
+  \mathbf{B}$. We can define a measure $m^*$ on $\mathbf{B}/F$ as
+  \[
+    m^*([a]) = m(a \land p).
+  \]
+\end{definition}
+
+\begin{proposition}
+  The function $m^*$ in \cref{def:measures_on_quotients} is well-defined.
+  Furthermore, if $m$ is a WMC measure, then so is $m^*$.
+\end{proposition}
+\begin{proof}
+\end{proof}
+% TODO: prove that the two ways to compute the probability give the same answer.
+
+% Feedback: Clarify the relationship between $\nWMC$ and the probability induced
+% by a WMC formulation.
 
@@
 over a propositional knowledge base proposed by Darwiche
-\cite{DBLP:conf/kr/Darwiche02} and Sang et al. \cite{sang2005solving}. Suppose
-we have a discrete probability distribution with  $n$ variables, and the $i$-th
-variable has $v_i$ values, for each $i \in [n]$. Interpreted as a logical
+\cite{DBLP:conf/kr/Darwiche02} and Sang et al. \cite{DBLP:conf/aaai/SangBK05}.
+Suppose we have a discrete probability distribution with  $n$ variables, and the
+$i$th variable has $v_i$ values, for each $i \in [n]$. Interpreted as a logical
 system, it has $\prod_{i=1}^n v_i$ models. My expansion would then use
@@
 \]
-variables, while for the encoding by Sang et al. \cite{sang2005solving},
+variables, while for the encoding by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
 \[

### 2020-03-24 paper.tex
Proof of the lemma

@@
   \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
-  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. A BA
+  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. The BA
   $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
@@
 
-% TODO: Start here. Define filters (ref the undergraduate book), filter
-% generation (same ref, but read it first), and quotients.
-\begin{definition}
+\begin{definition}[\cite{givant2008introduction}] \label{def:filter}
+  A \emph{(Boolean) filter} is a non-empty subset $F \subseteq \mathbf{B}$ such
+  that
+  \begin{itemize}
+  \item $f \land g \in F$ for all $f, g \in F$,
+  \item $f \lor a \in F$ for all $f \in F$ and $a \in \mathbf{B}$.
+  \end{itemize}
+  For any $p \in \mathbf{B}$, the \emph{principal filter of $p$} is the
+  intersection $I$ of all filters that contain $p$. It also has the property
+  that $p \le a$ for all $a \in I$.
+\end{definition}
+
+\begin{definition}[\cite{sikorski1969boolean}] \label{def:quotient}
+  Let $F \subseteq \mathbf{B}$ be a filter. The \emph{quotient} $\mathbf{B}/F$
+  is a BA of equivalence classes of elements of $\mathbf{B}$ with respect to the
+  equivalence relation
+  \[
+    a \sim b \qquad \iff \qquad a \to b \in F \quad \text{and} \quad b \to a \in F
+  \]
+  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/F$ are usually denoted
+  by $a/F$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
+  a$ (for some $b \in \mathbf{B}$), then $b/F = a/F$.
 \end{definition}
@@
 \begin{lemma}
-  Let $\mathbf{B}$ be a BA, and let $F$ be a filter in $\mathbf{B}$ generated by
-  $p \in \mathbf{B}$. Then, for any $a, b \in \mathbf{B}$, if $a/F = b/F$, then
-  $a \land p = b \land p$.
+  Let $\mathbf{B}$ be a BA, and let $F$ be the principal filter of $p \in
+  \mathbf{B}$. Then, for any $a, b \in \mathbf{B}$, if $a/F = b/F$, then $a
+  \land p = b \land p$.
 \end{lemma}
 \begin{proof}
-  % TODO: reference for a/F = b/F iff a <-> b \in F
-  % TODO: reference for the definition of a filter
+  If $a/F = b/F$, then $a \to b \in F$ by \cref{def:quotient}. Then $p \le a \to
+  b$ by \cref{def:filter}, and $(a \to b) \land p = p$ by the definition of
+  $\le$. Then
+  \[
+    1 = p \lor \neg p = ((a \to b) \lor \neg p) \land (p \lor \neg p) = \neg a
+    \lor b \lor \neg p = \neg (a \land p) \lor b.
+  \]
+  So
+  \[
+    \neg b = (\neg(a \land p) \land \neg b) \lor (b \land \neg b) = \neg((a
+    \land p) \lor b),
+  \]
+  and thus $b = (a \land p) \lor b$, and
+  \[
+    b \land p = (a \land p) \lor (b \land p) = (a \lor b) \land p.
+  \]
+  Similarly, $a \land p = (a \lor b) \land p$ which proves that $a \land p = b
+  \land p$.
 \end{proof}
 
-\begin{definition}[Measures on quotients] \label{def:measures_on_quotients}
+\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
   Let $\mathbf{B}$ be a BA with a measure $m : \mathbf{B} \to \mathbb{R}_{\ge
-    0}$, and let $F$ be a filter in $\mathbf{B}$ generated by some $p \in
-  \mathbf{B}$. We can define a measure $m^*$ on $\mathbf{B}/F$ as
+    0}$, and let $F$ be the principal filter of $p \in \mathbf{B}$. Let us
+  define $m^*\colon \mathbf{B}/F \to \mathbb{R}_{\ge 0}$ as
   \[
-    m^*([a]) = m(a \land p).
+    m^*(a/F) = m(a \land p)
   \]
-\end{definition}
+  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
+  if $m$ is a WMC measure, then so is $m^*$.
+\end{proposition}
 
-\begin{proposition}
-  The function $m^*$ in \cref{def:measures_on_quotients} is well-defined.
-  Furthermore, if $m$ is a WMC measure, then so is $m^*$.
-\end{proposition}
-\begin{proof}
-\end{proof}
 % TODO: prove that the two ways to compute the probability give the same answer.
-
-% Feedback: Clarify the relationship between $\nWMC$ and the probability induced
-% by a WMC formulation.
 

### 2020-03-24 paper.tex
It's about ideals, not filters!

@@
 % make no assumptions about independence.
-% 6. (I guess I could) show how evidence = quotiening by a filter, and how
-% quotiening by an ideal works
+% 6. show how evidence = quotiening by a filter, and how quotiening by an ideal works
 % 7. (WMI) If all weights are 1, we extend Boolean variables to discrete
@@
 
-\begin{definition}[\cite{givant2008introduction}] \label{def:filter}
-  A \emph{(Boolean) filter} is a non-empty subset $F \subseteq \mathbf{B}$ such
-  that
+%\begin{definition}[\cite{givant2008introduction}] \label{def:filter}
+%  A \emph{(Boolean) filter} is a non-empty subset $F \subseteq \mathbf{B}$ such
+%  that
+%  \begin{itemize}
+%  \item $f \land g \in F$ for all $f, g \in F$,
+%  \item $f \lor a \in F$ for all $f \in F$ and $a \in \mathbf{B}$.
+%  \end{itemize}
+%  For any $p \in \mathbf{B}$, the \emph{principal filter of $p$} is the
+%  intersection $I$ of all filters that contain $p$. It also has the property
+%  that $p \le a$ for all $a \in I$.
+%\end{definition}
+%\begin{definition}[\cite{sikorski1969boolean}] \label{def:quotient}
+%  Let $F \subseteq \mathbf{B}$ be a filter. The \emph{quotient} $\mathbf{B}/F$
+%  is a BA of equivalence classes of elements of $\mathbf{B}$ with respect to the
+%  equivalence relation
+%  \[
+%    a \sim b \qquad \iff \qquad a \to b \in F \quad \text{and} \quad b \to a \in F
+%  \]
+%  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/F$ are usually denoted
+%  by $a/F$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
+%  a$ (for some $b \in \mathbf{B}$), then $b/F = a/F$.
+%\end{definition}
+
+\begin{definition}[\cite{givant2008introduction}] \label{def:ideal}
+  An \emph{ideal} is a non-empty subset $I \subseteq \mathbf{B}$ such that
   \begin{itemize}
-  \item $f \land g \in F$ for all $f, g \in F$,
-  \item $f \lor a \in F$ for all $f \in F$ and $a \in \mathbf{B}$.
+  \item $i \lor j \in I$ for all $i, j \in I$;
+  \item $i \land a \in I$ for all $i \in I$ and $a \in \mathbf{B}$.
   \end{itemize}
-  For any $p \in \mathbf{B}$, the \emph{principal filter of $p$} is the
-  intersection $I$ of all filters that contain $p$. It also has the property
-  that $p \le a$ for all $a \in I$.
+  For any $p \in \mathbf{B}$, the \emph{principal ideal of $p$}---denoted by
+  $(p)$---is the smallest ideal that contains $p$. It can also be expressed as
+  $(p) = \{ a \in \mathbf{B} \mid a \le p \}$.
 \end{definition}
 
-\begin{definition}[\cite{sikorski1969boolean}] \label{def:quotient}
-  Let $F \subseteq \mathbf{B}$ be a filter. The \emph{quotient} $\mathbf{B}/F$
-  is a BA of equivalence classes of elements of $\mathbf{B}$ with respect to the
+\begin{definition}[\cite{givant2008introduction}]
+  Let $I$ be an ideal in $\mathbf{B}$. The \emph{quotient algebra of
+    $\mathbf{B}$ modulo the ideal $I$} $\mathbf{B}/I$ is a BA
+  of equivalence classes of elements of $\mathbf{B}$ with respect to the
   equivalence relation
   \[
-    a \sim b \qquad \iff \qquad a \to b \in F \quad \text{and} \quad b \to a \in F
+    a \sim b \quad \iff \quad a + b \in I
   \]
-  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/F$ are usually denoted
-  by $a/F$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
-  a$ (for some $b \in \mathbf{B}$), then $b/F = a/F$.
+  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/I$ are usually denoted
+  by $a/I$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
+  a$ (for some $b \in \mathbf{B}$), then $b/I = a/I$. The three algebraic
+  operations on $\mathbf{B}/I$ are defined as
+  \begin{align*}
+    a/I \land b/I &= a \land b / I, \\
+    a/I \lor b/I &= a \lor b / I, \\
+    \neg(a/I) &= (\neg a)/I.
+  \end{align*}
 \end{definition}
@@
 \begin{lemma}
-  Let $\mathbf{B}$ be a BA, and let $F$ be the principal filter of $p \in
-  \mathbf{B}$. Then, for any $a, b \in \mathbf{B}$, if $a/F = b/F$, then $a
-  \land p = b \land p$.
+  For any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ and elements $a, b
+  \in \mathbf{B}$,
+  \[
+    m(a \lor b) = m(a) + m(b) - m(a \land b).
+  \]
 \end{lemma}
 \begin{proof}
+  By \cref{def:measure},
+  \begin{align*}
+    m(a) &= m(a \land b) + m(a \land \neg b), \\
+    m(b) &= m(a \land b) + m(\neg a \land b), \\
+    m(a \lor b) &= m(a \land b) + m(a \land \neg b) + m(\neg a \land b),
+  \end{align*}
+  so
+  \[
+    m(a) + m(b) - m(a \land b) = m(a \land b) + m(a \land \neg b) + m(\neg a
+    \land b) = m(a \lor b)
+  \]
+  as required.
+\end{proof}
+
+\begin{lemma} \label{lemma:well-defined}
+  For any $a, b \in \mathbf{B}$ and any principal ideal $(p)$, if $a/(p) =
+  b/(p)$, then $a \lor p = b \lor p$.
+\end{lemma}
+\begin{proof} % TODO: update
   If $a/F = b/F$, then $a \to b \in F$ by \cref{def:quotient}. Then $p \le a \to
@@
 \begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
-  Let $\mathbf{B}$ be a BA with a measure $m : \mathbf{B} \to \mathbb{R}_{\ge
-    0}$, and let $F$ be the principal filter of $p \in \mathbf{B}$. Let us
-  define $m^*\colon \mathbf{B}/F \to \mathbb{R}_{\ge 0}$ as
+  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, and let $(p)$ be
+  a principal ideal. Let $m^*\colon \mathbf{B}/(p) \to \mathbb{R}_{\ge 0}$ be
+  defined as
   \[
-    m^*(a/F) = m(a \land p)
+    m^*(a/(p)) = m(a \lor p)
   \]
   for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
-  if $m$ is a WMC measure, then so is $m^*$.
+  it is a measure on $\mathbf{B}/(p)$ if and only if $m(p) = 0$. Moreover, if it
+  is a measure, then the following properties transfer from $m$ to $m^*$:
+  \begin{itemize}
+  \item if $m$ is a probability measure, then so is $m^*$;
+  \item if $m$ is strictly positive, then so is $m^*$;
+  \item if $m$ is a WMC measure, then so is $m^*$.
+  \end{itemize}
 \end{proposition}
+\begin{proof} % TODO: prove this
+  \Cref{lemma:well-defined} proves that the function is well-defined.
+\end{proof}
 
@@
 % TODO: a section on WMI: 3 results
-% TODO: introducing evidence can be done by taking a quotient w.r.t. the ideal
-% that contradicts the evidence (equivalently, the filter generated by the
-% evidence).
 

### 2020-03-27 paper.tex
A few proven and/or stated lemmas

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
 \newtheorem{conjecture}{Conjecture}
@@
 
-%\title{On the Limitations of Weighted Model Counting}
-\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
+\title{On the Limitations of Weighted Model Counting}
+%\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
 %\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
@@
   \cite{DBLP:journals/ai/Nilsson86}
+\item Logical induction: a huge paper with a good overview of previous attempts
+  to assign probabilities to logical sentences in a way that makes sense
+  \cite{DBLP:journals/eccc/GarrabrantBCST16}.
 \item Semiring programming \cite{DBLP:journals/corr/BelleR16}
 \item WMI \cite{DBLP:conf/ijcai/BellePB15}
-\item Measures on Boolean algebras: overview articles (from most cited to least
-  cited)
-  \begin{itemize}
-  \item Horn and Tarski \cite{horn1948measures}
-  \item Concerning measures on Boolean algebras \cite{gaifman1964concerning}
-  \item Jech -- Measures on Boolean algebras (arXiv) \cite{jech2017measures}
-  \end{itemize}
 \item Measures on Boolean algebras: more specific articles
@@
   \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
-  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. The BA
-  $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
+  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. We say
+  that $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
   \}$, there is an atom $x$ such that $x \le a$.
@@
   \item $m(0) = 0$;
-  \item $m(x \lor y) = m(x) + m(y)$ for all $x, y \in \mathbf{B}$ whenever $x
-    \land y = 0$.
+  \item $m(a \lor b) = m(a) + m(b)$ for all $a, b \in \mathbf{B}$ whenever $a
+    \land b = 0$.
   \end{itemize}
@@
 \end{definition}
+
+\begin{lemma}[\cite{horn1948measures}] \label{lemma:m_and_order}
+  Let $m: \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. For any $a, b \in
+  \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
+\end{lemma}
 
@@
 
-\begin{definition}[\cite{givant2008introduction}]
+\begin{definition}[\cite{givant2008introduction}] \label{def:quotient}
   Let $I$ be an ideal in $\mathbf{B}$. The \emph{quotient algebra of
@@
 \end{definition}
+
+\begin{definition}[\cite{givant2008introduction}]
+  Let $\mathbf{A}$ and $\mathbf{B}$ be BAs. A \emph{(Boolean) homomorphism} from
+  $\mathbf{A}$ to $\mathbf{B}$ is a map $f\colon \mathbf{A} \to \mathbf{B}$ such
+  that:
+  \begin{itemize}
+  \item $f(x \land y) = f(x) \land f(y)$,
+  \item $f(x \lor y) = f(x) \lor f(y)$,
+  \item $f(\neg x) = \neg f(x)$
+  \end{itemize}
+  for all $x, y \in \mathbf{A}$.
+\end{definition}
+
+\begin{lemma}[\cite{givant2008introduction}] \label{lemma:canonical_homomorphism}
+  Let $I \subseteq \mathbf{B}$ be an ideal. The map $f\colon \mathbf{B} \to
+  \mathbf{B}/I$ defined by $f(x) = x/I$ is a homomorphism.
+\end{lemma}
+
+\begin{lemma}[Homomorphisms preserve order
+  \cite{givant2008introduction}] \label{lemma:homomorphisms_and_order}
+  Let $f\colon \mathbf{A} \to \mathbf{B}$ be a homomorphism between two BAs
+  $\mathbf{A}$ and $\mathbf{B}$. Then, for any $x, y \in \mathbf{A}$, if $x \le
+  y$, then $f(x) \le f(y)$.
+\end{lemma}
+
+\begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:order}
+  For any $a, b \in \mathbf{B}$, $a \le b$ if and only if $a \land \neg b = 0$.
+\end{lemma}
+
+% TODO: make up my mind about a,b vs x,y and stick to it (maybe x,y?)
+% TODO: perhaps reorder things into paragraphs, i.e., a paragraph for order, for
+% homomorphisms, for ideals and quotients. This would take up less space.
 
@@
   confusion.
+%  Finally, we say that a measure $m\colon \mathbf{B} \to
+%  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-computable}) if
+%  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
+%  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
 \end{definition}
+% TODO: mention that the definition can be reduced to a single formula (i.e.,
+% without cases)
+% TODO: any measure is a WMC measure if all atoms are in L
 
@@
 
-\begin{lemma}
+\begin{lemma} \label{lemma:sum}
   For any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ and elements $a, b
@@
 \end{lemma}
-\begin{proof} % TODO: update
-  If $a/F = b/F$, then $a \to b \in F$ by \cref{def:quotient}. Then $p \le a \to
-  b$ by \cref{def:filter}, and $(a \to b) \land p = p$ by the definition of
-  $\le$. Then
+\begin{proof}
+  Note that
   \[
-    1 = p \lor \neg p = ((a \to b) \lor \neg p) \land (p \lor \neg p) = \neg a
-    \lor b \lor \neg p = \neg (a \land p) \lor b.
+    a/(p) = b/(p) \quad \iff \quad a+b \in (p) \quad \iff \quad a+b \le p \quad
+    \iff \quad (a+b) \lor p = p
   \]
-  So
+  by \cref{def:quotient,def:ideal}, and the definition of $\le$. So $p = (a
+  \land \neg b) \lor (\neg a \land b) \lor p$, and thus
   \[
-    \neg b = (\neg(a \land p) \land \neg b) \lor (b \land \neg b) = \neg((a
-    \land p) \lor b),
+    0 = p \land \neg p = (a \land \neg b \land \neg p) \lor (\neg a \land b
+    \land \neg p) \lor (p \land \neg p) = (a \land \neg (b \lor p)) \lor (b
+    \land \neg (a \lor p)).
   \]
-  and thus $b = (a \land p) \lor b$, and
+  It follows that
   \[
-    b \land p = (a \land p) \lor (b \land p) = (a \lor b) \land p.
+    a \land \neg (b \lor p) = 0 \quad \text{and} \quad b \land \neg (a \lor p) =
+    0.
   \]
-  Similarly, $a \land p = (a \lor b) \land p$ which proves that $a \land p = b
-  \land p$.
+  Focusing on the first equation,
+  \[
+    \neg a = (\neg a \lor a) \land [\neg a \lor \neg (b \lor p)] = \neg [a \land
+    (b \lor p)],
+  \]
+  and so $a = a \land (b \lor p)$, and
+  \[
+    a \lor p = (a \lor p) \land (b \lor p) = (a \land b) \lor p.
+  \]
+  By similar arguments, $b \lor p = (a \land b) \lor p$ as well which shows that
+  $a \lor p = b \lor p$ as required.
 \end{proof}
@@
   \begin{itemize}
-  \item if $m$ is a probability measure, then so is $m^*$;
-  \item if $m$ is strictly positive, then so is $m^*$;
-  \item if $m$ is a WMC measure, then so is $m^*$.
+  \item if $m$ is a \emph{probability measure}, then so is $m^*$;
+  \item if $m$ is \emph{strictly positive}, then so is $m^*$.
   \end{itemize}
 \end{proposition}
-\begin{proof} % TODO: prove this
-  \Cref{lemma:well-defined} proves that the function is well-defined.
+\begin{proof}
+  \Cref{lemma:well-defined} proves that the function is well-defined. Next,
+  note that
+  \[
+    m^*(0/(p)) = m(0 \lor p) = m(p),
+  \]
+  so $m^*(0/(p)) = 0$ if and only if $m(p) = 0$. For the second part of
+  \cref{def:measure}, let $a/(p), b/(p) \in \mathbf{B}/(p)$ be such that
+  \[
+    a/(p) \land b/(p) = a \land b / (p) = 0 / (p).
+  \]
+  This condition is equivalent to $a \land b \in (p)$ and $(a \land b) \lor p =
+  p$ by well-known properties of quotients and ideals
+  \cite{givant2008introduction}, \cref{def:ideal}, and the definition of $\le$,
+  respectively. Now
+  \begin{align*}
+    m^*(a/(p) \lor b/(p)) &= m^*(a \lor b / (p)) = m(a \lor b \lor p) = m((a \lor p) \lor (b \lor p)) \\
+                          &= m(a \lor p) + m(b \lor p) - m((a \lor p) \land (b \lor p)) \\
+                          &= m^*(a/(p)) + m^*(b/(p)) - m((a \lor p) \land (b \lor p))
+  \end{align*}
+  by \cref{lemma:sum}. However
+  \[
+    (a \lor p) \land (b \lor p) = (a \land b) \lor p = p,
+  \]
+  so $m^*(a/(p) \lor b/(p)) = m^*(a/(p)) + m^*(b/(p))$ if and only if $m(p) = 0$.
+
+  The two remaining properties are easy to prove:
+  \begin{itemize}
+  \item If $m(1) = 1$, then $m^*(1/(p)) = m(1 \lor p) = m (1) = 1$.
+  \item Suppose that $m$ is strictly positive, and let $a/(p) \in
+    \mathbf{B}/(p)$ be such that $a/(p) \ne 0/(p)$. Then
+    \[
+      m^*(a/(p)) = m(a \lor p) \ge m(a) > 0,
+    \]
+    where the first inequality comes from an elementary property of $\le$ that
+    $x \le x \lor y$ for any $x, y \in \mathbf{B}$ \cite{sikorski1969boolean}
+    and \cref{lemma:m_and_order}; and the second inequality follows because
+    $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be strictly
+    positive.
+  \end{itemize}
+\end{proof}
+% TODO: add parentheses around quotients (e.g., (a+b)/I).
+% TODO: I think I need to cite something for: a/I = 0/I <=> a \in I
+
+\subsection{Lots of Lemmas}
+
+% TODO: maybe 'unite' this with the result about a \/ p, i.e., a ~ a \/ p ~ a /\
+% ~p.
+% TODO: maybe I should state that A,B are assumed to be BAs with no additional
+% properties unless stated otherwise.
+\begin{lemma} \label{lemma:elements_in_quotients}
+  Let $(p)$ be a principal ideal. Then for any $a \in \mathbf{B}$, $(a \land
+  \neg p)/(p) = a/(p)$.
+\end{lemma}
+\begin{proof}
+  Note that
+  \[
+    (a \land \neg p)/(p) = a/(p) \quad \iff \quad (a \land \neg p) + a \in (p)
+    \quad \iff \quad (a \land \neg p) + a \le p.
+  \]
+  We also have that
+  \[
+    (a \land \neg p) + a = (a \land \neg p \land \neg a) \lor (\neg(a \land \neg
+    p) \land a) = (\neg a \lor p) \land a = (\neg a \land a) \lor (p \land a) =
+    p \land a.
+  \]
+  And, since $p \land a \le p$, we have that $(a \land \neg p) + a \le p$ as
+  required.
+\end{proof} % TODO: why? (the last bit) It's elementary
+
+% TODO: maybe I can rephrase this into a stronger result specifically about
+% a /\ ~p. Do I even want to do that?
+\begin{lemma}
+  Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
+  b/(p)$ if and only if there exist $a', b' \in \mathbf{B}$ such that $a'/(p) =
+  a/(p)$, $b'/(p) = b/(p)$, and $a' \le b'$.
+\end{lemma}
+\begin{proof}
+  Let us begin with the `only of' direction, and let $f\colon \mathbf{B} \to
+  \mathbf{B}/(p)$ be defined as $f(x) = x/(p)$. If $a' \le b'$, then $f(a') \le
+  f(b')$ by \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order}.
+  Thus $a'/(p) \le b'/(p)$, and $a/(p) \le b/(p)$ as required.
+
+  For the other direction, let $a, b \in \mathbf{B}$ be such that $a/(p) \le
+  b/(p)$. Then, by \cref{lemma:order},
+  \[
+    [a/(p)] \land \neg [b/(p)] = (a \land \neg b)/(p) = 0/(p),
+  \]
+  i.e.,
+  \[
+    a \land \neg b \in (p) \quad \iff \quad a \land \neg b \le p \quad \iff
+    \quad a \land \neg b \land \neg p = 0
+  \]
+  by \cref{def:ideal,lemma:order}. Let us pick $a' = a \land \neg p$ and $b' = b
+  \land \neg p$ since they satisfy $a'/(p) = a/(p)$ and $b'/(p) = b/(p)$ by
+  \cref{lemma:elements_in_quotients}. It remains to show that $a \land \neg p
+  \le b \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land
+  \neg p \land \neg(b \land \neg p) = 0$. But
+  \[
+    a \land \neg p \land \neg(b \land \neg p) = a \land \neg p \land (\neg b
+    \lor p) = (a \land \neg p \land \neg b) \lor (a \land \neg p \land p) = a
+    \land \neg p \land \neg b,
+  \]
+  and we already have that $a \land \neg p \land \neg b = 0$ by assumption.
 \end{proof}
 
-% TODO: prove that the two ways to compute the probability give the same answer.
+\begin{corollary}
+  Let $I \subseteq \mathbf{B}$ be an ideal. If $\mathbf{B}$ is atomic, then so
+  is $\mathbf{B}/I$.
+\end{corollary}
+
+\begin{lemma}
+  Let $(p)$ be a principal ideal. For any $a \in \mathbf{B}$, if $a/(p)$ is an
+  atom in $\mathbf{B}/(p)$, then $a \land \neg p$ is an atom in $\mathbf{B}$
+  such that $(a \land \neg p)/I = a/I$, and $m^*(a/(p)) = m(a \land \neg p)$.
+\end{lemma}
+
+\begin{theorem}[Using the previous three results]
+  Let $L \subset \mathbf{B}$ and $w\colon L \to \mathbb{R}_{\ge 0}$ be such that
+  $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge0}$ is a WMC measure. Let $p \in
+  \mathbf{B}$ be such that $\WMC(p) = 0$, and let $g\colon \mathbf{B}/(p) \to
+  \mathbf{B}$ be defined as $g(a/(p)) = a \land \neg p$. Then $\WMC \circ g$
+  is a WMC measure on $\mathbf{B}/(p)$ with respect to the same $L$ and $w$
+  such that
+  \[
+    \begin{tikzcd}
+      \mathbf{B} \arrow{d}[swap]{\WMC} & \mathbf{B}/(p) \arrow{l}[swap]{g}
+      \arrow{dl}{\WMC \circ g} \\
+      \mathbb{R}_{\ge 0}
+    \end{tikzcd}
+  \]
+  commutes.
+\end{theorem}
+
+% TODO: how can WMC compute something in the quotient algebra?
+% 1) The highlighted lemma from my notes.
+% 2) the results about <=
+% TODO: prove that the two ways to compute the probability give the same answer,
+% i.e., how B(Delta) = B(L)/(not Delta).
+% TODO: need an example of how we can compute probabilities in the quotient
+% algebra.
+% TODO: we can then move through the quotient BA using representatives we get
+% from mapping true things to 1 and false things to 0.
 

### 2020-03-28 paper.tex
One more lemma

@@
   \in S} x$ is the \emph{infimum}. By convention, $\bigwedge \emptyset = 1$ and
-$\bigvee \emptyset = 0$.
+$\bigvee \emptyset = 0$. For any $a, b \in \mathbf{B}$, we say that $a$ and $b$
+are \emph{disjoint} if $a \land b = 0$.
 
@@
   For any $a, b \in \mathbf{B}$, $a \le b$ if and only if $a \land \neg b = 0$.
+\end{lemma}
+
+\begin{lemma}[\cite{givant2008introduction}] \label{lemma:measure_and_order}
+  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. Then for all $a,
+  b \in \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
 \end{lemma}
@@
 
-\begin{corollary}
-  Let $I \subseteq \mathbf{B}$ be an ideal. If $\mathbf{B}$ is atomic, then so
-  is $\mathbf{B}/I$.
-\end{corollary}
+% TODO: do I need this?
+%\begin{corollary}
+%  Let $I \subseteq \mathbf{B}$ be an ideal. If $\mathbf{B}$ is atomic, then so
+%  is $\mathbf{B}/I$.
+%\end{corollary}
 
 \begin{lemma}
-  Let $(p)$ be a principal ideal. For any $a \in \mathbf{B}$, if $a/(p)$ is an
-  atom in $\mathbf{B}/(p)$, then $a \land \neg p$ is an atom in $\mathbf{B}$
-  such that $(a \land \neg p)/I = a/I$, and $m^*(a/(p)) = m(a \land \neg p)$.
-\end{lemma}
-
-\begin{theorem}[Using the previous three results]
+  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, let $p \in
+  \mathbf{B}$ be such that $m(p) = 0$, and let $m^*\colon \mathbf{B}/(p) \to
+  \mathbb{R}_{\ge 0}$ be a measure defined by $m^*(a/(p)) = m(a \lor p)$. Then
+  for any $a \in \mathbf{B}$, if $a/(p)$ is an atom in $\mathbf{B}/(p)$, then $a
+  \land \neg p$ is an atom in $\mathbf{B}$ such that $m^*(a/(p)) = m(a \land
+  \neg p)$.
+\end{lemma}
+\begin{proof} % TODO: This proof is a mess and needs more citations.
+  First, we want to show that if $a/(p)$ is an atom, then $a \land \neg p$ is an
+  atom. We can instead prove the contrapositive statement, i.e., if there exists
+  a $b \in \mathbf{B}$ such that $0 < b < a \land \neg p$, then there exists a
+  $b' \in \mathbf{B}$ such that $0/(p) < b'/(p) < a/(p)$. We will show that, in
+  fact, we set $b' = b$.
+  \Cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order} already tell
+  us that $b/(p) \le a/(p)$, so we only need to show that $0/(p) < b/(p) \ne
+  a/(p)$. For the first part, note that
+  \[
+    0/(p) < b/(p) \quad \iff \quad b/(p) \ne 0/(p) \quad \iff \quad b \not\in
+    (p) \quad \iff \quad b \not\le p \quad \iff \quad b \land \neg p \ne 0
+  \]
+  by \cref{lemma:order}. But if $b \land \neg p = 0$, then $b \land a \land \neg
+  p = 0$. This contradicts either that $b \le a \land \neg p$ (i.e., $b \land a
+  \land \neg p = b$) or that $b \ne 0$. For the second part, i.e., $b/(p) \ne
+  a/(p)$, we will show that if $b/(p) = a/(p)$, and $b \le a \land \neg p$, then
+  $b = a \land \neg p$. Indeed,
+  \[
+    b/(p) = a/(p) \quad \iff \quad a + b \in (p) \quad \iff \quad a+b \le p
+    \quad \iff \quad (a+b) \land \neg p = 0,
+  \]
+  and
+  \[
+    (a+b) \land \neg p = [(a \land \neg b) \lor (\neg a \land b)] \land \neg p =
+    (a \land \neg b \land \neg p) \lor (\neg a \land b \land \neg p),
+  \]
+  so $(a+b) \land \neg p = 0$ implies that $a \land \neg b \land \neg p = 0$
+  which is equivalent to $a \land \neg p \le b$. Therefore we have that $a \land
+  \neg p \le b \le a \land \neg p$, so $b = a \land \neg p$ which, by
+  contradiction, shows that $b/(p) \ne a/(p)$ and finishes the proof that $0/(p)
+  < b/(p) < a/(p)$.
+
+  In order to show that $m^*(a/(p)) = m(a \land \neg p)$, note that $a \land p$,
+  $a \land \neg p$, and $\neg a \land p$ are pairwise disjoint and their
+  supremum is $a \lor p$, so we have that
+  \[
+    m^*(a/(p)) = m(a \lor p) =  m(a \land p) + m(a \land \neg p) + m(\neg a
+    \land p).
+  \]
+  Furthermore, since $a \land p \le p$, $m(a \land p) \le m(p) = 0$. Similarly,
+  $m(\neg a \land p) = 0$, so $m^*(a/(p)) = m(a \land \neg p)$ as required.
+\end{proof}
+% TODO: the undergraduate book vaguely mentions that, when taking a quotient
+% w.r.t. an ideal of elements with measure zero, all elements in an equivalence
+% class will have the same measure.
+
+\begin{theorem}[Using the previous results]
   Let $L \subset \mathbf{B}$ and $w\colon L \to \mathbb{R}_{\ge 0}$ be such that

### 2020-03-28 paper.tex
Update a lemma into a stronger result

@@
 
-% TODO: maybe I can rephrase this into a stronger result specifically about
-% a /\ ~p. Do I even want to do that?
 \begin{lemma}
   Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
-  b/(p)$ if and only if there exist $a', b' \in \mathbf{B}$ such that $a'/(p) =
-  a/(p)$, $b'/(p) = b/(p)$, and $a' \le b'$.
+  b/(p)$ if and only if $a \land \neg p \le b \land \neg p$.
 \end{lemma}
 \begin{proof}
-  Let us begin with the `only of' direction, and let $f\colon \mathbf{B} \to
-  \mathbf{B}/(p)$ be defined as $f(x) = x/(p)$. If $a' \le b'$, then $f(a') \le
-  f(b')$ by \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order}.
-  Thus $a'/(p) \le b'/(p)$, and $a/(p) \le b/(p)$ as required.
+  Let us begin with the `only of' direction. \Cref{lemma:elements_in_quotients}
+  tells us that $(a \land \neg p)/(p) = a/(p)$. Combining this with
+  \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order} shows that
+  \[
+    a \land \neg p \le b \land \neg p \quad \implies \quad (a \land \neg p)/(p)
+    \le (b \land \neg p)/(p) \quad \iff \quad a/(p) \le b/(p)
+  \]
+  as required.
 
@@
   \]
-  by \cref{def:ideal,lemma:order}. Let us pick $a' = a \land \neg p$ and $b' = b
-  \land \neg p$ since they satisfy $a'/(p) = a/(p)$ and $b'/(p) = b/(p)$ by
-  \cref{lemma:elements_in_quotients}. It remains to show that $a \land \neg p
-  \le b \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land
-  \neg p \land \neg(b \land \neg p) = 0$. But
+  by \cref{def:ideal,lemma:order}. We need to show that $a \land \neg p \le b
+  \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land \neg p
+  \land \neg(b \land \neg p) = 0$. But
   \[
@@
 \end{proof}
-
-% TODO: do I need this?
-%\begin{corollary}
-%  Let $I \subseteq \mathbf{B}$ be an ideal. If $\mathbf{B}$ is atomic, then so
-%  is $\mathbf{B}/I$.
-%\end{corollary}
 
@@
 % TODO: how can WMC compute something in the quotient algebra?
-% 1) The highlighted lemma from my notes.
-% 2) the results about <=
 % TODO: prove that the two ways to compute the probability give the same answer,

### 2020-03-29 paper.tex
Two more lemmas

@@
 
-\subsection{Lots of Lemmas}
+\subsection{Lemma Galore}
 
@@
 \end{proof} % TODO: why? (the last bit) It's elementary
-
-\begin{lemma}
+% TODO: remove all those 'let (p) be a principal ideal'.
+
+\begin{lemma} \label{lemma:min_element_and_order}
   Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
@@
 
-\begin{lemma}
+\begin{lemma} \label{lemma:measure_of_atom}
   Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, let $p \in
@@
 % class will have the same measure.
+
+\begin{lemma} \label{lemma:minimal_in_quotient} % TODO: define completeness
+  Let $\mathbf{B}$ be a complete BA. For any $a, b \in \mathbf{B}$, if $a/(p) =
+  b/(p)$, then $a \land \neg p = b \land \neg p$. As a consequence, $a \land
+  \neg p \le b$.
+\end{lemma}
+\begin{proof} % TODO: rename b to something else
+  As in the proof of \cref{lemma:measure_of_atom}, $a/(p) = b/(p)$ implies that
+  $a \land \neg p \le b$. Since $\mathbf{B}$ is complete, let $b = \bigwedge \{
+  c \in \mathbf{B} \mid c/(p) = a/(p) \}$; then we still have that $b/(p) =
+  a/(p)$. But then $b \le a \land \neg p \le b$, so $a \land \neg p = b$. This
+  defines $a \land \neg p$ independently of $a$ as the least element in $\{c \in
+  \mathbf{B} \mid c/(p) = a/(p) \}$.
+\end{proof}
+
+\begin{corollary}
+  For any complete BA $\mathbf{B}$, if $a \in \mathbf{B}$ is an atom, then
+  $a/(p)$ is either an atom or $0/(p)$. In the former case, $a = a \land \neg
+  p$.
+\end{corollary}
+\begin{proof}
+  Since \cref{lemma:minimal_in_quotient} tells us that for all $b \in
+  \mathbf{B}$, if $b/(p) = a/(p)$, then $b \ge a \land \neg p$, if there is an
+  atom $b \in \mathbf{B}$ such that $b/(p) = a/(p)$, then it must be $a \land
+  \neg p$. If $a$ is an atom, then $a \land \neg p \le a$ implies that either $a
+  = a \land \neg p$ or $a \land \neg p = 0$. The latter is equivalent to $a/(p)
+  = 0/(p)$ by \cref{lemma:order}. The former, combined with the assumption that
+  $a$ is an atom and \cref{lemma:min_element_and_order}, implies that $a/(p)$ is
+  an atom.
+\end{proof}
 

### 2020-04-01 paper.tex
Add back the polyadic stuff and add some notes

@@
 
+Potential directions to explore (no good ones, really):
+\begin{itemize}
+\item Infinite BAs.
+  \begin{itemize}
+  \item For example, the BA of finite and cofinite sets could be interesting.
+  \item OUWMC requires infinite logics to be compact (whatever that means). My
+    algebraic angle suggests that completeness should be enough. Topologically,
+    compactness implies completeness, but I have no idea how this translates to
+    logics and algebras.
+  \end{itemize}
+\item WMI
+\item Measures with something other than $\mathbb{R}_{\ge 0}$ as the codomain
+  (doesn't look promising).
+\end{itemize}
+
 Previous/related work:
@@
   \cite{DBLP:journals/ai/Nilsson86}
-\item Logical induction: a huge paper with a good overview of previous attempts
-  to assign probabilities to logical sentences in a way that makes sense
-  \cite{DBLP:journals/eccc/GarrabrantBCST16}.
+\item Logical induction: a big paper with a good overview of previous attempts
+  to assign probabilities to logical sentences in a sensible way
+  \cite{DBLP:journals/eccc/GarrabrantBCST16}
 \item Semiring programming \cite{DBLP:journals/corr/BelleR16}
 \item WMI \cite{DBLP:conf/ijcai/BellePB15}
-\item Measures on Boolean algebras: more specific articles
+\item Measures on Boolean algebras
   \begin{itemize}
@@
 
+\todo[inline]{This should be replaced with inner sums (a.k.a. free products)}
 \begin{definition} \label{def:wmc}
@@
 
+\todo[inline]{Outdated. $m(a \land \neg p)$ is better than $m (a \lor p)$.}
 \begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
@@
 \subsection{Lemma Galore}
+
+\todo[inline]{This section made me realise that I was using the wrong definition}
 
@@
 
-\begin{theorem}[Using the previous results]
-  Let $L \subset \mathbf{B}$ and $w\colon L \to \mathbb{R}_{\ge 0}$ be such that
-  $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge0}$ is a WMC measure. Let $p \in
-  \mathbf{B}$ be such that $\WMC(p) = 0$, and let $g\colon \mathbf{B}/(p) \to
-  \mathbf{B}$ be defined as $g(a/(p)) = a \land \neg p$. Then $\WMC \circ g$
-  is a WMC measure on $\mathbf{B}/(p)$ with respect to the same $L$ and $w$
-  such that
-  \[
-    \begin{tikzcd}
-      \mathbf{B} \arrow{d}[swap]{\WMC} & \mathbf{B}/(p) \arrow{l}[swap]{g}
-      \arrow{dl}{\WMC \circ g} \\
-      \mathbb{R}_{\ge 0}
-    \end{tikzcd}
-  \]
-  commutes.
-\end{theorem}
-
-% TODO: how can WMC compute something in the quotient algebra?
-% TODO: prove that the two ways to compute the probability give the same answer,
-% i.e., how B(Delta) = B(L)/(not Delta).
-% TODO: need an example of how we can compute probabilities in the quotient
-% algebra.
+% TODO: start here
+%\[
+%  \begin{tikzcd}
+%    \mathbf{B}/(p) \arrow[rr, shift left, "x/(p) \mapsto x \lor p"] \arrow[rr,
+%    shift right, swap, "x/(p) \mapsto x \land \neg p"] & & \mathbf{B} \arrow{r}{\WMC} & \mathbb{R}_{\ge 0}
+%  \end{tikzcd}
+%\]
+
+%\begin{theorem}[Using the previous results]
+%  Let $L \subset \mathbf{B}$ and $w\colon L \to \mathbb{R}_{\ge 0}$ be such that
+%  $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge0}$ is a WMC measure. Let $p \in
+%  \mathbf{B}$ be such that $\WMC(p) = 0$, and let $g\colon \mathbf{B}/(p) \to
+%  \mathbf{B}$ be defined as $g(a/(p)) = a \land \neg p$. Then $\WMC \circ g$
+%  is a WMC measure on $\mathbf{B}/(p)$ with respect to the same $L$ and $w$
+%  such that
+%  \[
+%    \begin{tikzcd}
+%      \mathbf{B} \arrow{d}[swap]{\WMC} & \mathbf{B}/(p) \arrow{l}[swap]{g}
+%      \arrow{dl}{\WMC \circ g} \\
+%      \mathbb{R}_{\ge 0}
+%    \end{tikzcd}
+%  \]
+%  commutes.
+%\end{theorem}
+
+% TODO: how can WMC compute something in the quotient algebra? Add an example.
 % TODO: we can then move through the quotient BA using representatives we get
@@
 \section{What Measures Are WMC-Computable?}
+
+\todo[inline]{Proofs need to be updated and propositions could be phrased in a
+  better way, but the gist should be the same.}
 
@@
 
-% TODO: a section on WMI: 3 results
+\section{Polyadic Measure Algebras}
+
+Potential directions to explore:
+\begin{itemize}
+\item Representing independence and exchangeability. This seems important.
+\item (More detail below.) Inequalities as bounds for probabilities. This seems
+  to be somewhat explored with other setups.
+\item Implementation in SageMath. I would need to define prenex normal forms,
+  equality, and lots of other things.
+\item Alternative compact ways to define a probability distribution over $N$
+  models without assuming that everything is independent. Declaring a measure on
+  a FO formula defines a linear equation over the probabilities of models, so
+  using this method by itself would require $N-1$ equations, but maybe combining
+  this with information about independence and exchangeability can help.
+\end{itemize}
+
+\todo[inline]{I'm not sure if it's wise to develop this idea further}
+
+We show how the measure on the models of a FO theory can be extended to a
+measure over FO formulas. Two outcomes:
+\begin{itemize}
+\item For any $p, q \in \mathbf{A}$, if $p \land q = 0$, then $m^*(p \lor q) =
+  m^*(p) + m^*(q)$.
+\item If $p \le q$, then $m^*(p) \le m^*(q)$. This can be useful in two
+  situations:
+  \begin{itemize}
+  \item If $m^*(q) = 0$ or $m^*(p) = 1$, then this immediately tells us the
+    measure on the other sentence.
+  \item If we want to find $m^*(p)$, finding $q, r \in \mathbf{A}$ such that $r
+    \le p \le q$ bounds the answer.
+  \end{itemize}
+\end{itemize}
+
+\begin{definition}[\cite{halmos2016algebraic}]
+  Given two polyadic algebras $\mathbf{A}$ and $\mathbf{B}$, a \emph{polyadic
+    homomorphism} from $\mathbf{A}$ to $\mathbf{B}$ is a Boolean homomorphism
+  $f\colon \mathbf{A} \to \mathbf{B}$ such that
+  \begin{itemize}
+  \item $f\mathbf{S}(\tau)p = \mathbf{S}(\tau)fp$,
+  \item $f\bm\exists(J)p = \bm\exists(J)fp$
+  \end{itemize}
+  for all $\tau \in T$, $p \in \mathbf{A}$, and $J \subseteq I$.
+\end{definition}
+
+% by considering several X's, we can have several domains
+% I needs to be infinite in order to support arbitrarily complex sentences
+
+\subsection{The Set-Up}
+
+% TODO: Feedback: My general remark here is that this section looks very [???]
+% for SRL/WMC/PRM readers. The first-order [???] may not be justified if we are
+% only doing essentially propositional models. If we also consider full FoL,
+% i.e., infinite domains, and make this a separate paper for KR-type audience.
+% That is, let us do the WMC/WMI bit separately and do FO-version in another
+% paper for KR track. Title for second paper: "Measures on first-order
+% structures via WMC" (or similar...).
+
+\subsubsection{Preliminaries}
+
+What follows is a summary of \cite{halmos2016algebraic}.
+
+% Generic stuff
+Let $\mathbf{B}$ be a Boolean algebra (of propositions). Let $X$ be the
+(non-empty) domain of discourse. Let $I$ be an index set, elements of which can
+be interpreted as variables. The elements of $X^I$ are functions from $I$ to
+$X$. For any $x \in X^I$ and $i \in I$, we write $x_i$ to represent $x(i) \in
+X$. Let $\mathbf{A^*}$ be the set of all functions $X^I \to \mathbf{B}$, and
+note that it forms a Boolean algebra with operations defined pointwise.
+
+% Defining S
+Let $T$ be the semigroup of all $I \to I$ transformations. For any $\tau \in
+T$, let $\tau_* : X^I \to X^I$ be defined by
+\[
+  (\tau_* x)_i = x_{\tau i}
+\]
+for all $x \in X^I$ and $i \in I$. For any (Boolean/polyadic) algebra
+$\mathbf{C}$, let $\End(\mathbf{C})$ denote the set of all its endomorphisms. We
+can then define $\mathbf{S}$ to be a map $\mathbf{S} : T \to \End(\mathbf{A^*})$
+defined by
+\[
+  \mathbf{S}(\tau)p(x) = p(\tau_* x)
+\]
+for all $x \in X^I$ and $p \in \mathbf{A^*}$.
+
+% Defining E
+For any $J \subseteq I$, let $J_*$ be the relation on $X^I$ defined by
+\[
+  xJ_*y \quad \iff \quad x_i = y_i \quad \text{for all } i \in I \setminus J
+\]
+for all $x, y \in X^I$. For any $J \subseteq I$, we then define $\bm\exists(J)$
+to be a transformation $\mathbf{A^*} \to \mathbf{A^*}$ defined by
+\[
+  \bm\exists(J)p(x) = \bigvee_{\substack{y \in X^I,\\ xJ_*y}} p(y)
+\]
+for all $p \in \mathbf{A^*}$, provided this supremum exists for all $x \in
+X^I$\footnote{The universal quantifier $\bm\forall(J)$ is then defined as
+  $\bm\forall(J)p = \neg(\bm\exists(J)\neg p)$ for all $p \in \mathbf{A^*}$.}.
+
+Finally, a \emph{functional polyadic (Boolean) algebra}\footnote{To be more
+  explicit, a $\mathbf{B}$-valued functional polyadic algebra with domain $X$
+  and variables $I$.} is a subalgebra
+$\mathbf{A}$ of $\mathbf{A^*}$ such that:
+\begin{itemize}
+\item $\mathbf{S}(\tau)p \in \mathbf{A}$ for all $p \in \mathbf{A}$ and $\tau
+  \in T$;
+\item $\bm\exists(J)p \in \mathbf{A}$ for all $p \in \mathbf{A}$ and $J
+  \subseteq I$.
+\end{itemize}
+
+\begin{proposition}
+  For all finite $J, K \subseteq I$, finite $\sigma, \tau \in T$, and all $p \in
+  \mathbf{A}$,
+  \begin{itemize}
+  \item $\bm\exists(\emptyset)p = p$;
+  \item $\bm\exists(J)\bm\exists(K) = \bm\exists(J \cup K)$;
+  \item $\mathbf{S}(\id)p = p$;
+  \item $(\sigma\tau)p = \sigma(\tau p)$;
+  \item if $\sigma_{|I \setminus J} = \tau_{|I \setminus J}$, then $\sigma
+    \bm\exists(J) = \tau \bm\exists(J)$;
+  \item if $\tau$ is injective on $\tau^{-1}J$, then $\bm\exists(J)\tau = \tau
+    \bm\exists(\tau^{-1}J)$;
+  \item for every $p \in \mathbf{A}$, there exists a finite $J \subseteq I$ such
+    that $\bm\exists(i)p = p$ whenever $i \not\in J$.
+  \end{itemize}
+\end{proposition}
+
+\begin{definition}
+  Similarly to $\bm\exists$, a \emph{constant} $c$ is a map $c: \mathcal{P}(I)
+  \to \End(\mathbf{A})$ such that:
+  \begin{itemize}
+  \item $c(\emptyset) = \id_{\mathbf{A}}$;
+  \item $c(J \cup K) = c(J)c(K)$;
+  \item $c(J)\bm\exists(K) = \bm\exists(K)c(J \setminus K)$;
+  \item $\bm\exists(J)c(K) = c(K)\bm\exists(J \setminus K)$;
+  \item $c(J)\mathbf{S}(\tau) = \mathbf{S}(\tau)c(\tau^{-1}J)$
+  \end{itemize}
+  for all $J, K \in \mathcal{P}(I)$ and $\tau \in T$. If $J$ is a singleton
+  set $\{ i \}$, we will simply write $c(i)$ instead of $c(J)$.
+\end{definition}
+
+\subsubsection{New Results}
+
+\begin{proposition} \label{prop:polyadic_measure}
+  Let $\mathbf{B}$ be a finite Boolean algebra with a measure $m :
+  \mathbf{B} \to [0, 1]$. Let $\mathbf{A}$ be a $\mathbf{B}$-valued functional
+  polyadic algebra with domain $X$ and variables $I$. Let $m^* : \mathbf{A} \to
+  \mathbb{R}_{\ge 0}$ be defined by
+  \[
+    m^*(p) = \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(y)
+  \]
+  for all $p \in \mathbf{A}$. Then $m^*$ is a measure on $\mathbf{A}$.
+\end{proposition}
+
+\begin{remark}
+  While definitions of $m^*$ such as
+  \[
+    m^*(p) = m \left( \bigvee_{x \in X^I} p(x) \right)
+  \]
+  might look tempting, they are not additive.
+\end{remark}
+
+\begin{proof} % TODO: Update the proof w.r.t. definitions
+  First, we can show that $m^*(1) = 1$ by observing that
+  \[
+    m^*(1) = \sum_{\text{atoms } y \in \mathbf{B}} m(y) = m \left(
+      \bigvee_{\text{atoms } y \in \mathbf{B}} y \right) = m(1) = 1,
+  \]
+  where we use \cref{thm:representation} and express $1 \in \mathbf{B}$ as the
+  supremum of all atoms in $\mathbf{B}$ \cite{ganesh2006introduction}. Clearly
+  $m^*(p) \ge 0$ for all $p \in \mathbf{A}$, so we can restrict the codomain of
+  $m^*$ to $[0, 1]$.
+
+  Next, we want to show that $m^*(p) > 0$ for all $p \in \mathbf{A} \setminus \{
+  0 \}$. If $p \ne 0$, then there must be some $x' \in X^I$ such that $p(x') \ne
+  0$. But then, since finite Boolean algebras are atomic, there must also be an
+  atom $y \in \mathbf{B}$ such that $y \le p(x')$. Therefore, $m^*(p) \ge m(y) >
+  0$, finishing this part of the proof.
+
+  Let $p, q \in \mathbf{A}$ be such that $p \land q = 0$. We want to show
+  that $m^*(p \lor q) = m^*(p) \lor m^*(q)$. First, note that
+  \[
+    y \le (p \lor q)(x) = p(x) \lor q(x)
+  \]
+  if and only if
+  \[
+    y = (p(x) \lor q(x)) \land y = (p(x) \land y) \lor (q(x) \land y)
+  \]
+  by \cref{def:ba}. Also note that
+  \[
+    (p(x) \land y) \land (q(x) \land y) = p(x) \land q(x) \land y = (p \land
+    q)(x) \land y = 0 \land y = 0,
+  \]
+  so
+  \[
+    m(y) = m((p(x) \land y) \lor (q(x) \land y)) = m(p(x) \land y) + m(q(x) \land y)
+  \]
+  by \cref{def:measure} which then leads to
+  \begin{align*}
+    m^*(p \lor q) &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(y) = \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(p(x) \land y) + m(q(x) \land y) \\
+                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x)}} m(q(x) \land y).
+  \end{align*}
+  Since $y$ is an atom,
+  \[
+    p(x) \land y  = \begin{cases}
+      y & \text{if } y \le p(x) \\
+      0 & \text{otherwise,}
+    \end{cases}
+  \]
+  so
+  \begin{align*}
+    m^*(p \lor q) &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x) \text{ and } y \le p(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le (p \lor q)(x) \text{ and } y \le q(x)}} m(q(x) \land y) \\
+                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(p(x) \land y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le q(x)}} m(q(x) \land y) \\
+                  &= \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{ s.t.}\\ \exists x \in X^I:\, y \le p(x)}} m(y) + \sum_{\substack{\text{atoms }y \in \mathbf{B} \text{s.t.}\\ \exists x \in X^I:\, y \le q(x)}} m(y) = m^*(p) + m^*(q),
+  \end{align*}
+  finishing the proof that $m^*$ is a measure.
+\end{proof}
+
+\begin{lemma} \label{lemma:simple_measure}
+  Given the setup of \cref{prop:polyadic_measure} and $p \in \mathbf{A}$, if
+  $p(x) = p(y)$ for all $x, y \in X^I$ (i.e., $p$ has no free variables), then
+  \[
+    m^*(p) = m(p(x))
+  \]
+  (for some $x \in X^I$) is an alternative (i.e., equivalent and simpler)
+  definition of $m^*$.
+\end{lemma}
+\begin{proof}
+  Fix some $x \in X^I$. Then
+  \[
+    m(p(x)) = m \left( \bigvee_{\substack{\text{atoms } y \in \mathbf{B} \text{
+            s.t.}\\
+          y \le p(x)}} y \right) = \sum_{\substack{\text{atoms } y \in \mathbf{B}
+        \text{ s.t.}\\
+        y \le p(x)}} m(y) =\sum_{\substack{\text{atoms } y \in \mathbf{B}
+        \text{ s.t.}\\
+        \exists x' \in X^I : y \le p(x')}} m(y) = m^*(p),
+  \]
+  where we use \cref{thm:representation} for the first step,
+  \cref{def:measure} and \cref{lemma:atomic} for the second step, the
+  assumptions of \cref{lemma:simple_measure} for the third step, and the
+  definition of $m^*$ for the fourth one.
+\end{proof}
+
+\begin{proposition}
+  The following identities are true for any $p \in \mathbf{A}$, $J \subseteq I$,
+  $\tau \in T$, and constant $c : \mathcal{P}(I) \to \End(A)$:
+  \begin{itemize}
+  \item $c \neg = \neg c$ (i.e., constants commute with negation);
+  \item $\mathbf{S}(\tau) \neg = \neg \mathbf{S}(\tau)$;
+  \item $\bm\forall(J)p \le c(J)p \le \bm\exists(J)p$;
+  \end{itemize}
+\end{proposition}
+\begin{proof}
+  \begin{itemize}
+  \item Obvious.
+  \item Ditto.
+  \item The first part can be derived from $p \le q \implies \neg q \le \neg p$.
+    The second part comes from the definition of $\bm\exists$.
+  \end{itemize}
+\end{proof}
+
+\subsection{How Probabilities Are Computed}
+
+In order to make the example algebras easily describable, our example programs
+will have to be tiny. Consider the following ProbLog
+\cite{DBLP:conf/ijcai/RaedtKT07} program:
+\begin{align*}
+  1.0 &\dblcolon \mathsf{p}(a, b).\\
+  0.5 &\dblcolon \mathsf{p}(X, X) \coloneq \mathsf{p}(X, Y);\, \mathsf{p}(Y, X).
+\end{align*}
+Let $L = \{ \mathsf{p}(a, a), \mathsf{p}(a, b), \mathsf{p}(b, a), \mathsf{p}(b,
+b) \}$ be the set of all possible ground atoms. Let $\mathbf{B}$ be the
+Boolean algebra freely generated by $L$ (see, e.g.,
+\cite{givant2008introduction} for more on free Boolean algebras). Then
+$\mathbf{B}$ will have sixteen atoms ranging from $\mathsf{p}(a, a) \land
+\mathsf{p}(a, b) \land \mathsf{p}(b, a) \land \mathsf{p}(b, b)$ to
+$\neg\mathsf{p}(a, a) \land \neg\mathsf{p}(a, b) \land \neg\mathsf{p}(b, a)
+\land \neg\mathsf{p}(b, b)$. The weight function $w : L \to \mathbb{R}_{\ge 0}$
+defined by
+\[
+  w(l) = \begin{cases}
+    1 & \text{if } l = \mathsf{p}(a, b) \\
+    0.5 & \text{if } l \in \{ \mathsf{p}(a, a), \mathsf{p}(b, b) \} \\
+    0 & \text{if } l = \mathsf{p}(b, a) \\
+    1-w(l') & \text{if } l = \neg l'
+  \end{cases}
+\]
+for all $l \in L$ defines a WMC measure over $\mathbf{B}$. Note that while we
+could define an ideal generated by $\{ \mathsf{p}(b, a), \neg\mathsf{p}(a, b)
+\}$ and take the quotient of $\mathbf{B}$ by that ideal to get a Boolean algebra
+with a strictly positive measure, this would put zero-probability queries
+outside of our algebras, i.e., we would not be able to ask a question whose
+answer is zero.
+
+\begin{table}
+  \centering
+  \caption{Example elements of $\mathbf{A}$ as maps $X^I \to \mathbf{B}$, with
+    $a : \mathcal{P}(I) \to \End(\mathbf{A})$ as one of two possible constants.}
+  \label{tbl:examples}
+  \begin{tabular}{ll}
+    \toprule
+    Element of $\mathbf{A}$ & Action on $X^I$ \\
+    \midrule
+    $p = \mathbf{S}(\id)p = \bm\exists(\emptyset)p = a(\emptyset)p = b(\emptyset)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_2)$ \\
+    $\bm\exists(1)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, x_2) \lor \mathsf{p}(b, x_2)$ \\
+    $\bm\exists(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, a) \lor \mathsf{p}(x_1, b)$ \\
+    $\bm\exists(I)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, a) \lor \mathsf{p}(a, b) \lor \mathsf{p}(b, a) \lor \mathsf{p}(b, b)$ \\
+    $\mathbf{S}(\{ 1 \mapsto 1, 2 \mapsto 1 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_1)$ \\
+    $\mathbf{S}(\{ 1 \mapsto 2, 2 \mapsto 1 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_2, x_1)$ \\
+    $\mathbf{S}(\{ 1 \mapsto 2, 2 \mapsto 2 \})p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_2, x_2)$ \\
+    $a(1)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, x_2)$ \\
+    $a(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, a)$ \\
+    $a(I)p$ & $(x_1, x_2) \mapsto \mathsf{p}(a, a)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Finally, let $\mathbf{A}$ be the functional polyadic algebra $X^I \to
+\mathbf{B}$ for $I = \{1, 2\}$ and $X = \{ a, b \}$\footnote{$X$ cannot (or
+  should not) have constants that do not occur in $\mathbf{B}$.}. The elements
+of $X^I$ can then be represented as tuples $(x_1, x_2)$ for some $x_1, x_2 \in
+X$. See \cref{tbl:examples} for example elements of $\mathbf{A}$ which consists
+of a single predicate function $p$ and operators $\bm\exists, \mathbf{S}, a, b,
+\neg, \land, \lor$, the last three of which are defined pointwise.
+
+\begin{table}
+  \centering
+  \caption{Step-by-step derivation of how a more complex element of
+    $\mathbf{A}$ acts on elements of $X^I$}
+  \label{tbl:derivation}
+  \begin{tabular}{ll}
+    \toprule
+    Element of $\mathbf{A}$ & Action on $X^I$ \\
+    \midrule
+    $p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, x_2)$ \\
+    $b(2)p$ & $(x_1, x_2) \mapsto \mathsf{p}(x_1, b)$ \\
+    $\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\mathsf{p}(x_1, b)$ \\
+    $\bm\exists(1)\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\mathsf{p}(a, b) \lor \neg\mathsf{p}(b, b) = \neg(\mathsf{p}(a, b) \land \mathsf{p}(b, b))$ \\
+    $\bm\forall(1)b(2)p = \neg\bm\exists(1)\neg b(2)p$ & $(x_1, x_2) \mapsto \neg\neg(\mathsf{p}(a, b) \land \mathsf{p}(b, b)) = \mathsf{p}(a, b) \land \mathsf{p}(b, b)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}
+  \centering
+  \caption{Atoms $y \in \mathbf{B}$ (and their measures) such that $y \le
+    \mathsf{p}(a, b) \land \mathsf{p}(b, b)$}
+  \label{tbl:atoms}
+  \begin{tabular}{lc}
+    \toprule
+    Atom $y \in \mathbf{B}$ & $m(y)$ \\
+    \midrule
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \mathsf{p}(a, a) \land \mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 0 = 0$ \\
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \neg\mathsf{p}(a, a) \land \mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 0 = 0$ \\
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \mathsf{p}(a, a) \land \neg\mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 1 = 0.25$ \\
+    $\mathsf{p}(a, b) \land \mathsf{p}(b, b) \land \neg\mathsf{p}(a, a) \land \neg\mathsf{p}(b, a)$ & $1 \times 0.5 \times 0.5 \times 1 = 0.25$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Let us calculate the probability $\Pr(\forall x_1 \in X, \mathsf{p}(x_1, b))$.
+The same expression can be translated into the notation for our polyadic algebra
+$\mathbf{A}$ as $m^*(\bm\forall(1)b(2)p)$. Recall that $\bm\forall(1)b(2)p =
+\neg\bm\exists(1)\neg b(2)p$. The effect of this function on an arbitrary
+element of $X^I$ is derived step-by-step in \cref{tbl:derivation}. Since the
+resulting function is constant (i.e., the logical formula has no free
+variables), \cref{lemma:simple_measure} tells us that
+\[
+  m^*(\bm\forall(1)b(2)p) = m(\mathsf{p}(a, b) \land \mathsf{p}(b, b)) = m
+  \left( \bigvee_{\substack{\text{atoms } y \in \mathbf{B} \text{ s.t.}\\
+        y \le \mathsf{p}(a, b) \land \mathsf{p}(b, b)}} y \right) = \sum
+  _{\substack{\text{atoms } y \in \mathbf{B} \text{ s.t.}\\
+      y \le \mathsf{p}(a, b) \land \mathsf{p}(b, b)}} m(y).
+\]
+The resulting sum is over four atoms; these atoms and their probabilities are
+listed in \cref{tbl:atoms}. Thus, we get that
+\[
+  m^*(\bm\forall(1)b(2)p) = 0 + 0 + 0.25 + 0.25 = 0.5.
+\]
+
+% TODO: use I^I for transformations
+% TODO: extra notation for transformations: (i/j) sends j to i, (i, j)
+% interchanges i and j.
 

### 2020-04-02 paper.tex
Sums of BAs

@@
 
+\section{Implications for Lifted Inference}
+
+\begin{definition}
+  Given a BA $\mathbf{A}$, a \emph{subalgebra} is a subset $\mathbf{B} \subseteq
+  \mathbf{A}$ that, together with the operations, zero, and one of $\mathbf{A}$,
+  is a BA.
+\end{definition}
+
+\begin{definition}
+  Let $\mathbf{A},$ $\mathbf{B}$, and $\mathbf{C}$ be BAs such that $\mathbf{B}$
+  is a subalgebra of $\mathbf{A}$. Let $f\colon \mathbf{A} \to \mathbf{C}$ and
+  $g\colon \mathbf{B} \to \mathbf{C}$ be homomorphisms. Then $f$ is an
+  \emph{extension} of $g$ if $f(x) = g(x)$ for all $x \in \mathbf{B}$. If $f$ is
+  an extension of each member of a family $\{ g_i \}_{i \in I}$ of
+  homomorphisms, then $f$ is called a \emph{common extension} of $\{ g_i \}_{i
+    \in I}$.
+\end{definition}
+
+\begin{definition}
+  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
+  $\mathbf{A}$ with a family of inclusion maps $\{ \iota_i\colon \mathbf{A}_i
+  \to \mathbf{A} \}_{i \in I}$. If for any BA $\mathbf{B}$ with a family of
+  homomorphisms $\{ f_i\colon \mathbf{A} \to \mathbf{B} \}_{i \in I}$ there
+  exists a unique common extension of $\{ f_i\colon \mathbf{A} \to \mathbf{B}
+  \}_{i \in I}$ ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
+  \[
+    \begin{tikzcd}
+      \mathbf{A}_i \arrow{r}{\iota_i} \arrow{rd}[swap]{f_i} & \mathbf{A} \arrow[d,dashed,"f"] \\
+      & \mathbf{B}
+    \end{tikzcd}
+  \]
+  then $\mathbf{A}$ is the \emph{internal sum}\footnote{It is also known as the
+    \emph{free product} and as the coproduct in the category of BAs.} of $\{
+  \mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
+  \mathbf{A}_i$.
+\end{definition}
+
 \section{Polyadic Measure Algebras}

### 2020-04-09 paper.tex
More feedback

--- 2020-03-29 paper.tex
@@
 
-\title{On the Limitations of Weighted Model Counting}
+\title{Generalising Weighted Model Counting to Boolean Algebras}
+%\title{On the Limitations of Weighted Model Counting}
 %\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
@@
 
+% Feedback 2: WMC-Computable -> WMC-Definable
+
+% Feedback 2: The paper at this stage is very technical - the danger is that
+% WMC/SRL people may not be able to follow it and so would be hard to get
+% accepted. Without clear target audience, [???] get work accepted. My main high
+% level suggestion is that let us tease apart what you have and see if a story
+% emerges. That is, let us attempt to write a paper *with examples* and see
+% whether with significant motivation, we have a story emerging. Below, sample
+% text needed to adequately motivate [???] for WMC/SRL community.
+
 % Contributions:
-% 1. A generalisation of WMC adapted to Boolean algebras.
+% 1. A generalisation of WMC to Boolean algebras. We show how WMC makes
+% independence assumptions and how we can make some but not all literals
+% independent.
+% 1.5. We show how the lifted inference techniques stem from the underlying
+% algebraic structure.
+% 1.6. Do we add more inference rules?
 % 2. We show that it is a valid measure.
@@
 
+Potential directions to explore (no good ones, really):
+\begin{itemize}
+\item Infinite BAs.
+  % TODO: Feedback 2: understanding this is the key for formulating the
+  % relevance/significance of this work
+  \begin{itemize}
+  \item For example, the BA of finite and cofinite sets could be interesting.
+  \item OUWMC requires infinite logics to be compact (whatever that means). My
+    algebraic angle suggests that completeness should be enough. Topologically,
+    compactness implies completeness, but I have no idea how this translates to
+    logics and algebras.
+  \end{itemize}
+\item WMI
+\item Measures with something other than $\mathbb{R}_{\ge 0}$ as the codomain
+  (doesn't look promising).
+\end{itemize}
+
 Previous/related work:
@@
 \section{Preliminaries}
+
+% TODO: Feedback 2: Explain with examples: models = elements [atoms] of algebra
 
@@
 \end{definition}
-
-\begin{lemma}[\cite{horn1948measures}] \label{lemma:m_and_order}
-  Let $m: \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. For any $a, b \in
-  \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
-\end{lemma}
 
@@
 
+% TODO: Feedback 2: I did a high level read to get the big picture but found
+% this discussion on ideals distracting. Specifically, w.r.t. the main claims
+% when do these things get used?
+
 \section{WMC as a Measure}
+
+% TODO: Feedback 2: Result #1: What are the conditions under which WMC defines a
+% measure as introduced above? [Non-negativity should be enough so this is not a
+% result.]
 
@@
 
+% TODO: Feedback 2: You need to explain what precisely these mean in logic and
+% models and weight functions are usually defined and understood.
+\todo[inline]{This should be replaced with inner sums (a.k.a. free products)}
 \begin{definition} \label{def:wmc}
@@
 
-\begin{proposition}
+\begin{theorem}
   $\WMC$ is a measure, and $\nWMC$ is a probability measure.
-\end{proposition}
+\end{theorem}
+% TODO: Feedback 2: Need to explain how WMC and NWMC connects to standard
+% definitions of WMC and Pr(phi|e) = WMC(phi /\ e)/WMC(e).
 \begin{proof}
@@
 But how does the measure defined on $B(\mathcal{L})$ transfer to $B(\Delta)$?
+
+% TODO: Feedback 2: I look the significance of the below results. Proving
+% properties that don't [???] the "roadmap" means (AI) readers will lose
+% interest. [This applies until the beginning of the next section.]
 
@@
 
+% TODO: Feedback 2: Where is this helping?
+\todo[inline]{Outdated. $m(a \land \neg p)$ is better than $m (a \lor p)$.}
 \begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
@@
     $x \le x \lor y$ for any $x, y \in \mathbf{B}$ \cite{sikorski1969boolean}
-    and \cref{lemma:m_and_order}; and the second inequality follows because
-    $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be strictly
-    positive.
+    and \cref{lemma:measure_and_order}; and the second inequality follows
+    because $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be
+    strictly positive.
   \end{itemize}
@@
 
+\todo[inline]{Proofs need to be updated and propositions could be phrased in a
+  better way, but the gist should be the same.}
+
+% TODO: Feedback 2: Result #2: WMC c measures. That is, WMC wight weights on
+% literals is less expressive than (a) WMC with weights on models is less
+% expressive than (b) measures on Boolean algebras?  Results only link at (a).
+% Is (c) true? Proof? [It could cover (some sort of) infinite cases...]
+
 \subsection{WMC Requires Independent Literals}
@@
 
-\begin{proposition}
+\begin{theorem}
   Let $\mathbf{B}$ be a finite measure algebra with measure $m\colon \mathbf{B} \to
@@
   for all distinct $l, l' \in L$ such that $l \ne \neg l'$.
-\end{proposition}
+\end{theorem}
 
@@
 \end{proof}
-% TODO: the auxiliary result should be a 'claim' in-between the theorem and the proof.
+% TODO: the auxiliary result should be a 'claim' in-between the theorem and the
+% proof.
 
 \subsection{Extending the Algebra}
+
+% TODO: Feedback 2: If you prove (b) above, you could motivate why weights on
+% literals is attractive and whether there is a way to augment the expressivity
+% of WMC while still maintaining literal level weights. Hence this action.
 
@@
 
-% TODO: a section on WMI: 3 results
+% TODO: Feedback 2: You need to explain the significance of this result. Result
+% #3: Augmented approach recovers the expressivity of (b). [This is a result,
+% although not a big one.]
+
+\section{Implications for Lifted Inference}
+
+\subsection{Preliminaries}
+
+\begin{definition}
+  Given a BA $\mathbf{A}$, a \emph{subalgebra} is a subset $\mathbf{B} \subseteq
+  \mathbf{A}$ that, together with the operations, zero, and one of $\mathbf{A}$,
+  is a BA.
+\end{definition}
+
+\begin{definition}[\cite{givant2008introduction}]
+  Let $\mathbf{A},$ $\mathbf{B}$, and $\mathbf{C}$ be BAs such that $\mathbf{B}$
+  is a subalgebra of $\mathbf{A}$. Let $f\colon \mathbf{A} \to \mathbf{C}$ and
+  $g\colon \mathbf{B} \to \mathbf{C}$ be homomorphisms. Then $f$ is an
+  \emph{extension} of $g$ if $f(x) = g(x)$ for all $x \in \mathbf{B}$. If $f$ is
+  an extension of each member of a family $\{ g_i \}_{i \in I}$ of
+  homomorphisms, then $f$ is called a \emph{common extension} of $\{ g_i \}_{i
+    \in I}$.
+\end{definition}
+
+\begin{definition}[\cite{givant2008introduction}]
+  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
+  $\mathbf{A}$ with a family of inclusion maps $\{ \iota_i\colon \mathbf{A}_i
+  \to \mathbf{A} \}_{i \in I}$. If for any BA $\mathbf{B}$ with a family of
+  homomorphisms $\{ f_i\colon \mathbf{A} \to \mathbf{B} \}_{i \in I}$ there
+  exists a unique common extension of $\{ f_i\colon \mathbf{A} \to \mathbf{B}
+  \}_{i \in I}$ ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
+  \[
+    \begin{tikzcd}
+      \mathbf{A}_i \arrow{r}{\iota_i} \arrow{rd}[swap]{f_i} & \mathbf{A} \arrow[d,dashed,"f"] \\
+      & \mathbf{B}
+    \end{tikzcd}
+  \]
+  then $\mathbf{A}$ is the \emph{internal sum}\footnote{A slightly more general
+    version of this definition is also known as the free product, the Boolean
+    product, and the coproduct in the category of BAs
+    \cite{givant2008introduction,koppelberg1989handbook,sikorski1969boolean}.}
+  of $\{\mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
+  \mathbf{A}_i$.
+\end{definition}
+
+\begin{proposition}[\cite{sikorski1969boolean}]
+  Let $\mathbf{A}$ be the internal sum of a family of BAs $\{ \mathbf{A}_i \}_{i
+    \in I}$, and let $\{m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in
+    I}$ be a family of measures. Then there exists a unique measure $m\colon
+  \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any finite subset $J
+  \subseteq I$ and family of elements $\{ x_j \in \mathbf{A}_j \}_{j \in J}$,
+  \[
+    m \left( \bigwedge_{j \in J} x_j \right) = \prod_{j \in J} m_j(x_j).
+  \]
+\end{proposition}
+% TODO: this suggest a new rule for lifted inference.
+
+\subsection{New Results}
 

### 2020-04-11 paper.tex
A bit of progress

@@
 
-\section{Implications for Lifted Inference}
-
-\subsection{Preliminaries}
+\section{Representing Independence and Conditional Independence}
+
+\subsection{Independence (all known results)}
 
@@
   Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
-  $\mathbf{A}$ with a family of inclusion maps $\{ \iota_i\colon \mathbf{A}_i
-  \to \mathbf{A} \}_{i \in I}$. If for any BA $\mathbf{B}$ with a family of
-  homomorphisms $\{ f_i\colon \mathbf{A} \to \mathbf{B} \}_{i \in I}$ there
-  exists a unique common extension of $\{ f_i\colon \mathbf{A} \to \mathbf{B}
-  \}_{i \in I}$ ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
+  $\mathbf{A}$. If for any BA $\mathbf{B}$ with a family of homomorphisms $\{
+  f_i\colon \mathbf{A}_i \to \mathbf{B} \}_{i \in I}$ there exists a unique
+  common extension of $\{ f_i\colon \mathbf{A}_i \to \mathbf{B} \}_{i \in I}$
+  ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
   \[
     \begin{tikzcd}
-      \mathbf{A}_i \arrow{r}{\iota_i} \arrow{rd}[swap]{f_i} & \mathbf{A} \arrow[d,dashed,"f"] \\
+      \mathbf{A}_i \ar[r,hookrightarrow] \arrow{rd}[swap]{f_i} & \mathbf{A}
+      \arrow[d,dashed,"f"] \\
       & \mathbf{B}
@@
 \end{proposition}
-% TODO: this suggest a new rule for lifted inference.
-
-\subsection{New Results}
+
+\subsection{Conditional Independence}
+
+\begin{definition}[\cite{koppelberg1989handbook}]
+  Let $\mathbf{A}$ be a BA. Let $\mathbf{B}$ be a subalgebra of $\mathbf{A}$,
+  and let $(\mathbf{A}_i)_{i \in I}$ be a family of subalgebras of $\mathbf{A}$
+  such that $\mathbf{A}_i \cap \mathbf{A}_j = \mathbf{B}$ for all $i \ne j$ in
+  $I$. Let $\{ \iota_i \colon \mathbf{B} \to \mathbf{A}_i \}$ be a family of
+  inclusion homomorphisms. Then $\mathbf{A}$ is the \emph{amalgamated free
+    product\footnote{Also known as a (wide) pushout in the category of BAs.} of
+    $\{\mathbf{A}_{i} \}_{i \in I}$ over $\mathbf{B}$} if, for any Boolean
+  algebra $\mathbf{C}$ with a family of homomorphisms $\{ f_i\colon \mathbf{A}_i
+  \to \mathbf{C} \}_{i \in I}$ such that $f_i \circ \iota_i = f_j \circ \iota_j$
+  for all $i, j \in I$, there is a unique homomorphism $f\colon \mathbf{A} \to
+  \mathbf{C}$ such that the triangle in
+  \[
+    \begin{tikzcd}
+      \mathbf{B} \ar[r,hookrightarrow,"\iota_i"] & \mathbf{A}_i
+      \ar[r,hookrightarrow] \ar[d,swap,"f_i"] & \mathbf{A} \ar[ld,dashed,"f"] \\
+      & \mathbf{C}
+    \end{tikzcd}
+  \]
+  commutes for all $i \in I$. We will denote this product as
+  \[
+    \mathbf{A} = \bigoplus_{\substack{\mathbf{B}\\ i \in I}} \mathbf{A}_i.
+  \]
+\end{definition}
+
+\subsubsection{New Results}
+
+\begin{theorem}
+  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of BAs with measures $\{
+  m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in I}$, let $\mathbf{B}$
+  be a BA, and let $\mathbf{A}$ be the amalgamated free product of $\{
+  \mathbf{A}_i \}_{i \in I}$ over $\mathbf{B}$. Then there is a unique measure
+  $m\colon \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any element $b \in
+  \mathbf{B}$, finite subset $J \subseteq I$, and elements $\{ a_j \in
+  \mathbf{A}_j \}_{j \in J}$,
+  \[
+    m \left(b \land \bigwedge_{j \in J} a_j \right) = \prod_{j \in J} m_j(b
+    \land a_j).
+  \]
+\end{theorem}
 
@@
 \bibliography{paper}
+% TODO: curly brackets or parentheses for families? Maybe curly brackets
 

### 2020-04-12 paper.tex
Free algebras and pushouts/coproducts

@@
 
-\title{Generalising Weighted Model Counting to Boolean Algebras}
+\title{What Boolean Algebras Can Teach Us About Weighted Model Counting}
+%\title{Generalising Weighted Model Counting to Boolean Algebras}
 %\title{On the Limitations of Weighted Model Counting}
@@
 % to define the main concepts for introducing measures on Boolean algebras.
+
+% Feedback: Can you say something here about factorized vs non-factorized
+% weight function definitions? That is, factorized is when w maps literals to
+% R_>=0, non-factorized is when w maps models to R_>=0 and show:
+% a) come up with nice example when non-factorized weights are intuitive
+% b) what if weight functions are negative/complex?
+% c) clarify that the factorized definition have is w.r.t. models, in case some
+% one gets confused [It doesn't have to be, if the BA is not free -- P.]
 
@@
 
-% Contributions:
-% 1. A generalisation of WMC to Boolean algebras. We show how WMC makes
-% independence assumptions and how we can make some but not all literals
-% independent.
-% 1.5. We show how the lifted inference techniques stem from the underlying
-% algebraic structure.
-% 1.6. Do we add more inference rules?
-% 2. We show that it is a valid measure.
-% 3. We show that WMC assumes independence, i.e., cannot represent all measures.
-% 4. We show how the BA can be extended with new 'literals' to represent any measure.
-% 5. (Maybe) we establish a lower bound on the number of new literals, if we
-% make no assumptions about independence.
-% 6. show how evidence = quotiening by a filter, and how quotiening by an ideal works
-% 7. (WMI) If all weights are 1, we extend Boolean variables to discrete
-% variables, and continuous variables are arbitrary subsets (in the
-% sigma-algebra), then the WMI process calculates the probability of any event
-% and doesn't require going down to the level of models (assuming a suitable
-% probability measure).
-% 8. If the weight of a literal (and its negation) is 1, then we don't need to
-% look at its models--the probability can be calculated at any level. This
-% extends to any number of variables.
-% 9. How WMI transforms to our algebras. The boring version and what's wrong
-% with it.
-% 10. Show how to transfer the measure to a quotient algebra and that the answer
-% match with each other and with the original definition of WMC.
-
-Potential directions to explore (no good ones, really):
+% Feedback 2: I did a high level read to get the big picture but found
+% this discussion on ideals distracting. Specifically, w.r.t. the main claims
+% when do these things get used?
+
+% TODO:
+% 1) theorem: a pushout of free algebras is a free algebra. Same for
+% coproducts. This extends to coproducts because they are a special case of
+% pushouts.
+% TODO for later:
+% 2) curly brackets or parentheses for families? Maybe curly brackets
+% 3) make up my mind about a,b vs x,y and stick to it (maybe x,y?)
+% 4) add parentheses around quotients (e.g., (a+b)/I).
+% 5) perhaps reorder the section of preliminaries into paragraphs, i.e., a
+% paragraph for order, for homomorphisms, for ideals and quotients. This would
+% take up less space.
+
+\paragraph{Contributions.}
 \begin{itemize}
-\item Infinite BAs.
-  % TODO: Feedback 2: understanding this is the key for formulating the
-  % relevance/significance of this work
-  \begin{itemize}
-  \item For example, the BA of finite and cofinite sets could be interesting.
-  \item OUWMC requires infinite logics to be compact (whatever that means). My
-    algebraic angle suggests that completeness should be enough. Topologically,
-    compactness implies completeness, but I have no idea how this translates to
-    logics and algebras.
+\item WMC defines a measure over a BA.
+\item WMC with weights on literals imposes an independence assumption. (Measures
+  are `slightly' more expressive than WMC with weights on models because they
+  apply to non-atomic BAs.)
+\item A BA can be augmented with new literals in order to support any measure.
+\item (Maybe) a lower bound on the number of new literals needed in order to
+  support any measure.
+\item Alternatively, one can use coproducts and pushouts to define a BA with
+  precisely the right independence and conditional independence conditions.
+  (This requires a relaxed version of WMC.)
+\item This results in a smaller problem for WMC algorithms (w.r.t. both the
+  number of literals and the length of the theory) and is optimal for, e.g.,
+  Bayesian networks.
+\item (Maybe) this results in faster inference (?)
 \end{itemize}
-\item WMI
-\item Measures with something other than $\mathbb{R}_{\ge 0}$ as the codomain
-  (doesn't look promising).
-\end{itemize}
-
-Previous/related work:
+
+\paragraph{Notable previous/related work.}
 \begin{itemize}
@@
   \cite{DBLP:journals/eccc/GarrabrantBCST16}
-\item Semiring programming \cite{DBLP:journals/corr/BelleR16}
-\item WMI \cite{DBLP:conf/ijcai/BellePB15}
 \item Measures on Boolean algebras
@@
   \item $\mathbf{B}$ is atomic.
-  \item For any $x \in \mathbf{B}$,
-    \[
-      x = \bigvee_{\text{atoms } a \le x} a.
-    \]
+  \item For any $x \in \mathbf{B}$, $x = \bigvee_{\text{atoms } a \le x} a$.
   \item $1$ is the supremum of all atoms.
@@
 
-% TODO: make up my mind about a,b vs x,y and stick to it (maybe x,y?)
-% TODO: perhaps reorder things into paragraphs, i.e., a paragraph for order, for
-% homomorphisms, for ideals and quotients. This would take up less space.
-
-% TODO: Feedback 2: I did a high level read to get the big picture but found
-% this discussion on ideals distracting. Specifically, w.r.t. the main claims
-% when do these things get used?
-
 \section{WMC as a Measure}
-
-% TODO: Feedback 2: Result #1: What are the conditions under which WMC defines a
-% measure as introduced above? [Non-negativity should be enough so this is not a
-% result.]
 
@@
 % models and weight functions are usually defined and understood.
-\todo[inline]{This should be replaced with inner sums (a.k.a. free products)}
+% TODO: This should be replaced with inner sums (a.k.a. free products)
 \begin{definition} \label{def:wmc}
@@
 
-% TODO: Feedback 2: I look the significance of the below results. Proving
+% TODO: Feedback 2: I [???] the significance of the below results. Proving
 % properties that don't [???] the "roadmap" means (AI) readers will lose
@@
 \end{proof}
-% TODO: add parentheses around quotients (e.g., (a+b)/I).
 % TODO: I think I need to cite something for: a/I = 0/I <=> a \in I
@@
 
-% TODO: start here
+% we can then move through the quotient BA using representatives we get
+% from mapping true things to 1 and false things to 0.
+
 %\[
@@
 
-% TODO: how can WMC compute something in the quotient algebra? Add an example.
-% TODO: we can then move through the quotient BA using representatives we get
-% from mapping true things to 1 and false things to 0.
-
-% TODO: Feedback: Can you say something here about factorized vs non-factorized
-% weight function definitions? That is, factorized is when w maps literals to
-% R_>=0, non-factorized is when w maps models to R_>=0 and show:
-% a) come up with nice example when non-factorized weights are intuitive
-% b) what if weight functions are negative/complex?
-% c) clarify that the factorized definition have is w.r.t. models, in case some
-% one gets confused [It doesn't have to be, if the BA is not free -- P.]
-% d) can you say something about WMI
-
 \section{What Measures Are WMC-Computable?}
 
-\todo[inline]{Proofs need to be updated and propositions could be phrased in a
-  better way, but the gist should be the same.}
-
-% TODO: Feedback 2: Result #2: WMC c measures. That is, WMC wight weights on
-% literals is less expressive than (a) WMC with weights on models is less
-% expressive than (b) measures on Boolean algebras?  Results only link at (a).
-% Is (c) true? Proof? [It could cover (some sort of) infinite cases...]
+% TODO: Proofs need to be updated and propositions could be phrased in a better
+% way, but the gist should be the same.
 
@@
     \textcolor{red}{\mathbb{R}_{\ge 0}} & & \\
-    \textcolor{red}{\mathbf{B}} \arrow[red]{u}{m} \arrow{r}{\iota} &
-    \mathbf{B'} \arrow{lu}[swap]{m'} & \\
-    \textcolor{red}{L} \arrow[Subset,red]{u}{} \arrow[Subset]{r}{} & L'
-    \arrow[Subset]{u}{} \arrow{r}{w} & \mathbb{R}_{\ge 0}
+    \textcolor{red}{\mathbf{B}} \arrow[red]{u}{m} \ar[r,hookrightarrow,"\iota"]
+    & \mathbf{B'} \arrow{lu}[swap]{m'} & \\
+    \textcolor{red}{L} \ar[u,red,hookrightarrow] \ar[r,hookrightarrow] & L'
+    \ar[u,hookrightarrow] \arrow{r}{w} & \mathbb{R}_{\ge 0}
   \end{tikzcd}
@@
 
-% TODO: Feedback 2: You need to explain the significance of this result. Result
-% #3: Augmented approach recovers the expressivity of (b). [This is a result,
-% although not a big one.]
+% TODO: Feedback 2: You need to explain the significance of this result.
 
@@
 
+\begin{theorem}
+  The number of weights needed to encode a Bayesian network using
+  coproducts and pushouts is equal to the number of entries in the tables of the
+  network (and the resulting theory is shorter).
+\end{theorem}
+
+% TODO: make sure that the definition of 'free' is sufficient
+\begin{theorem}[Pushouts of free BAs are free]
+  Let
+  \[
+    \mathbf{A} = \bigoplus_{\substack{\mathbf{B}\\ i \in I}} \mathbf{A}_i
+  \]
+  be an amalgamated free product such that $\{ \mathbf{A}_{i} \}_{i \in I}$ are
+  free BAs with $\{ S_i \}_{i \in I}$ as their respective sets of generators.
+  Let $S = \bigcup_{i \in I} S_i$. Then $\mathbf{A}$ is a free BA with
+  generating set $S$.
+\end{theorem}
+\begin{proof}
+  Suppose we have a map from $S$ to an arbitrary BA $\mathbf{C}$, as in
+  \[
+    \begin{tikzcd}
+      S_i \ar[r,hookrightarrow] \ar[d,hookrightarrow] & S \ar[d,hookrightarrow]
+      \ar[ddr,bend left] & \\
+      \mathbf{A}_i \ar[r,hookrightarrow] \ar[rrd,dashed,bend right] & \mathbf{A}
+      \ar[rd,dashed]& \\
+      & & \mathbf{C}.
+    \end{tikzcd}
+  \]
+  We want to show that there exists a unique homomorphism $\mathbf{A} \to
+  \mathbf{C}$. For $i \in I$, from $S_i \hookrightarrow S$ and $S \to
+  \mathbf{C}$ we get a map $S_i \to \mathbf{C}$, so---by the definition of a
+  free BA---there is a unique homomorphism $\mathbf{A}_i \to \mathbf{C}$.
+  Furthermore, a family of homomorphisms $\{ \mathbf{A}_i \to \mathbf{C} \}_{i
+    \in I}$ uniquely determine a homomorphism $\mathbf{A} \to \mathbf{C}$ by the
+  universal mapping property of a (wide) pushout. Thus $\mathbf{A}$ is a free BA
+  with generating set $S$.
+\end{proof}
+
+\begin{corollary}
+  Similarly, coproducts of free BAs are free.
+\end{corollary}
+
 \bibliographystyle{plain}
 \bibliography{paper}
-% TODO: curly brackets or parentheses for families? Maybe curly brackets
 

### 2020-04-13 paper.tex
Declutter + update/improve

@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{conjecture}[theorem]{Conjecture}
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
 \theoremstyle{remark}
 \newtheorem*{remark}{Remark}
-
-\definecolor{color1}{HTML}{fbb4ae}
-\definecolor{color2}{HTML}{b3cde3}
-\definecolor{color3}{HTML}{ccebc5}
-\definecolor{color4}{HTML}{decbe4}
 
@@
 % a) come up with nice example when non-factorized weights are intuitive
-% b) what if weight functions are negative/complex?
 % c) clarify that the factorized definition have is w.r.t. models, in case some
 % one gets confused [It doesn't have to be, if the BA is not free -- P.]
-
-% Feedback 2: WMC-Computable -> WMC-Definable
 
@@
 
-% Feedback 2: I did a high level read to get the big picture but found
-% this discussion on ideals distracting. Specifically, w.r.t. the main claims
-% when do these things get used?
-
-% TODO:
-% 1) theorem: a pushout of free algebras is a free algebra. Same for
-% coproducts. This extends to coproducts because they are a special case of
-% pushouts.
 % TODO for later:
-% 2) curly brackets or parentheses for families? Maybe curly brackets
-% 3) make up my mind about a,b vs x,y and stick to it (maybe x,y?)
-% 4) add parentheses around quotients (e.g., (a+b)/I).
-% 5) perhaps reorder the section of preliminaries into paragraphs, i.e., a
-% paragraph for order, for homomorphisms, for ideals and quotients. This would
-% take up less space.
+% 1) make up my mind about a,b vs x,y and stick to it (maybe x,y?)
 
@@
 
-% TODO: Feedback 2: Explain with examples: models = elements [atoms] of algebra
+% TODO
+% 1) Feedback 2: Explain with examples: models = elements [atoms] of algebra
+% 2) Perhaps reorder the section of preliminaries into paragraphs, i.e., a
+% paragraph for order, for homomorphisms, etc. This would take up less space.
+% 3) how to compute the number of elements in the algebra.
 
@@
 We can also define a partial order $\le$ on $\mathbf{B}$ as $a \le b$ if $a = b
-\land a$ (or, equivalently, $a \lor b = b$) for $a, b \in \mathbf{B}$.
+\land a$ (or, equivalently, $a \lor b = b$) for all $a, b \in \mathbf{B}$.
 Furthermore, let $a < b$ denote $a \le b$ and $a \ne b$. For the rest of this
@@
 
-%\begin{definition}[\cite{givant2008introduction}] \label{def:filter}
-%  A \emph{(Boolean) filter} is a non-empty subset $F \subseteq \mathbf{B}$ such
-%  that
-%  \begin{itemize}
-%  \item $f \land g \in F$ for all $f, g \in F$,
-%  \item $f \lor a \in F$ for all $f \in F$ and $a \in \mathbf{B}$.
-%  \end{itemize}
-%  For any $p \in \mathbf{B}$, the \emph{principal filter of $p$} is the
-%  intersection $I$ of all filters that contain $p$. It also has the property
-%  that $p \le a$ for all $a \in I$.
-%\end{definition}
-%\begin{definition}[\cite{sikorski1969boolean}] \label{def:quotient}
-%  Let $F \subseteq \mathbf{B}$ be a filter. The \emph{quotient} $\mathbf{B}/F$
-%  is a BA of equivalence classes of elements of $\mathbf{B}$ with respect to the
-%  equivalence relation
-%  \[
-%    a \sim b \qquad \iff \qquad a \to b \in F \quad \text{and} \quad b \to a \in F
-%  \]
-%  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/F$ are usually denoted
-%  by $a/F$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
-%  a$ (for some $b \in \mathbf{B}$), then $b/F = a/F$.
-%\end{definition}
-
-\begin{definition}[\cite{givant2008introduction}] \label{def:ideal}
-  An \emph{ideal} is a non-empty subset $I \subseteq \mathbf{B}$ such that
-  \begin{itemize}
-  \item $i \lor j \in I$ for all $i, j \in I$;
-  \item $i \land a \in I$ for all $i \in I$ and $a \in \mathbf{B}$.
-  \end{itemize}
-  For any $p \in \mathbf{B}$, the \emph{principal ideal of $p$}---denoted by
-  $(p)$---is the smallest ideal that contains $p$. It can also be expressed as
-  $(p) = \{ a \in \mathbf{B} \mid a \le p \}$.
-\end{definition}
-
-\begin{definition}[\cite{givant2008introduction}] \label{def:quotient}
-  Let $I$ be an ideal in $\mathbf{B}$. The \emph{quotient algebra of
-    $\mathbf{B}$ modulo the ideal $I$} $\mathbf{B}/I$ is a BA
-  of equivalence classes of elements of $\mathbf{B}$ with respect to the
-  equivalence relation
-  \[
-    a \sim b \quad \iff \quad a + b \in I
-  \]
-  for all $a, b \in \mathbf{B}$. Elements of $\mathbf{B}/I$ are usually denoted
-  by $a/I$ (for some $a \in \mathbf{B}$) with the understanding that if $b \sim
-  a$ (for some $b \in \mathbf{B}$), then $b/I = a/I$. The three algebraic
-  operations on $\mathbf{B}/I$ are defined as
-  \begin{align*}
-    a/I \land b/I &= a \land b / I, \\
-    a/I \lor b/I &= a \lor b / I, \\
-    \neg(a/I) &= (\neg a)/I.
-  \end{align*}
-\end{definition}
-
 \begin{definition}[\cite{givant2008introduction}]
@@
 
-\begin{lemma}[\cite{givant2008introduction}] \label{lemma:canonical_homomorphism}
-  Let $I \subseteq \mathbf{B}$ be an ideal. The map $f\colon \mathbf{B} \to
-  \mathbf{B}/I$ defined by $f(x) = x/I$ is a homomorphism.
-\end{lemma}
-
 \begin{lemma}[Homomorphisms preserve order
@@
 \section{WMC as a Measure}
+% TODO: Feedback 2: Need to explain how WMC and NWMC connects to standard
+% definitions of WMC and Pr(phi|e) = WMC(phi /\ e)/WMC(e).
 
@@
 
-\begin{figure}
-  \[
-    \begin{tikzcd}
-      & & & & & \colorbox{color3}{$1$} \ar[dlll,dash,gray] \ar[dl,dash,gray]
-      \ar[dr,dash,gray] \ar[drrr,dash,gray] & & & \\
-      & & \colorbox{color3}{$p \lor q$} & & \colorbox{color3}{$q \to p$} & &
-      \colorbox{color2}{$p \to q$} & & \colorbox{color4}{$\neg p \lor \neg q$}
-      \\
-      \colorbox{color3}{$p$} \ar[urr,dash,gray] \ar[urrrr,dash,gray] & &
-      \colorbox{color2}{$q$} \ar[u,dash,gray] \ar[urrrr,dash,gray] & &
-      \colorbox{color2}{$p \leftrightarrow q$} \ar[u,dash,gray]
-      \ar[urr,dash,gray] & & \colorbox{color4}{$p + q$} \ar[ullll,dash,gray]
-      \ar[urr,dash,gray] & & \colorbox{color4}{$\neg q$} \ar[ullll,dash,gray]
-      \ar[u,dash,gray] & & \colorbox{color1}{$\neg p$} \ar[ullll,dash,gray]
-      \ar[ull,dash,gray] \\
-      & & \fcolorbox{black}{color2}{$p \land q$} \ar[ull,dash,gray]
-      \ar[u,dash,gray] \ar[urr,dash,gray] & & \fcolorbox{black}{color4}{$p \land
-        \neg q$} \ar[ullll,dash,gray] \ar[urr,dash,gray] \ar[urrrr,dash,gray] &
-      & \fcolorbox{black}{color1}{$\neg p \land q$} \ar[ullll,dash,gray]
-      \ar[u,dash,gray] \ar[urrrr,dash,gray] & & \fcolorbox{black}{color1}{$\neg
-        p \land \neg q$} \ar[ullll,dash,gray] \ar[u,dash,gray]
-      \ar[urr,dash,gray] \\
-      & & & & & \colorbox{color1}{$0$} \ar[ulll,dash,gray] \ar[ul,dash,gray]
-      \ar[ur,dash,gray] \ar[urrr,dash,gray] & & &
-    \end{tikzcd}
-  \]
-  \[
-    \begin{tikzcd}
-      & \colorbox{color3}{$\left[1\right]$} \ar[dl,dash,gray] \ar[dr,dash,gray]
-      & \\
-      \fcolorbox{black}{color2}{$\left[q\right]$} & &
-      \fcolorbox{black}{color4}{$\left[\neg q\right]$} \\
-      & \colorbox{color1}{$\left[0\right]$} \ar[ul,dash,gray] \ar[ur,dash,gray]
-      &
-    \end{tikzcd}
-  \]
-  \caption{Two BAs from \cref{example:construction}: $B(\mathcal{L})$ at the top
-    and $B(\Delta)$ at the bottom. An edge between elements $a$ and $b$ (with
-    $a$ positioned lower than $b$) means that $a < b$. Each element of
-    $B(\Delta)$ is an equivalence class of elements of $B(\mathcal{L})$, and the
-    colours show which elements of $B(\mathcal{L})$ belong to which class. In
-    both algebras, atoms have borders around them.}
-  \label{fig:example}
-\end{figure}
-
 \begin{example} \label{example:construction}
@@
 
+  % TODO: be careful about mentioning ideals, filters, and quotients
   The corresponding BA $B(\Delta)$ can then be constructed using
   \cref{def:algebra_from_logic}. Alternatively, one can first construct the free
-  BA generated by the set $\{ p, q \}$---this corresponds to $B(\mathcal{L})$ in
-  \cref{fig:example}---and then take a quotient with respect to either the
-  filter generated by $p$ or the ideal\footnote{More details on these concepts
-    can be found in many books on BAs
+  BA generated by the set $\{ p, q \}$ and then take a quotient with respect to
+  either the filter generated by $p$ or the ideal\footnote{More details on these
+    concepts can be found in many books on BAs
     \cite{givant2008introduction,koppelberg1989handbook}.} generated by $\neg
-  p$. In any case, the resulting BA is pictured at the bottom of
-  \cref{fig:example}.
+  p$.
 
@@
 \end{example}
-% TODO: how to compute the number of elements in the algebra.
 % TODO: clarify what B(L) means. And whether B(Delta) is even necessary.
@@
   $\nWMC_w$, we will drop the subscript when doing so results in no potential
-  confusion.
-%  Finally, we say that a measure $m\colon \mathbf{B} \to
-%  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-computable}) if
-%  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
-%  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
+  confusion. Finally, we say that a measure $m\colon \mathbf{B} \to
+  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-definable}) if
+  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
+  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
 \end{definition}
@@
 \end{theorem}
-% TODO: Feedback 2: Need to explain how WMC and NWMC connects to standard
-% definitions of WMC and Pr(phi|e) = WMC(phi /\ e)/WMC(e).
 \begin{proof}
@@
 
-% TODO: Feedback 2: I [???] the significance of the below results. Proving
-% properties that don't [???] the "roadmap" means (AI) readers will lose
-% interest. [This applies until the beginning of the next section.]
-
-\begin{lemma} \label{lemma:sum}
+\section{What Measures Are WMC-Definable?}
+
+% TODO: Proofs need to be updated and propositions could be phrased in a better
+% way, but the gist should be the same.
+
+\subsection{WMC Requires Independent Literals}
+
+\begin{lemma} \label{lemma:before_theorem}
   For any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ and elements $a, b
   \in \mathbf{B}$,
-  \[
-    m(a \lor b) = m(a) + m(b) - m(a \land b).
-  \]
+  \begin{equation} \label{eq:to_prove}
+    m(a \land b) = m(a)m(b)
+  \end{equation}
+  if and only if
+  \begin{equation} \label{eq:to_prove2}
+    m(a \land b) \cdot m(\neg a \land \neg b) = m(a \land \neg b)
+    \cdot m(\neg a \land b).
+  \end{equation}
 \end{lemma}
 \begin{proof}
-  By \cref{def:measure},
-  \begin{align*}
-    m(a) &= m(a \land b) + m(a \land \neg b), \\
-    m(b) &= m(a \land b) + m(\neg a \land b), \\
-    m(a \lor b) &= m(a \land b) + m(a \land \neg b) + m(\neg a \land b),
-  \end{align*}
-  so
-  \[
-    m(a) + m(b) - m(a \land b) = m(a \land b) + m(a \land \neg b) + m(\neg a
-    \land b) = m(a \lor b)
-  \]
-  as required.
+  First, note that $a = (a \land b) \lor (a \land \neg b)$ and $(a \land b)
+  \land (a \land \neg b) = 0$, so, by properties of a measure,
+  \begin{equation} \label{eq:temp}
+    m(a) = m(a \land b) + m(a \land \neg b).
+  \end{equation}
+  Applying \cref{eq:temp} and the equivalent expression for $m(b)$ allows us
+  to rewrite \cref{eq:to_prove} as
+  \[
+    m(a \land b) = [m(a \land b) + m(a \land \neg b)][m(a \land b) + m(\neg a
+    \land b)]
+  \]
+  which is equivalent to
+  \begin{equation} \label{eq:temp6}
+    m(a \land b)[1 - m(a \land b) - m(a \land \neg b) - m(\neg a \land b)] = m(a
+    \land \neg b)m(\neg a \land b).
+  \end{equation}
+  Since $a \land b$, $a \land \neg b$, $\neg a \land b$, $\neg a \land \neg b$
+  are pairwise disjoint and their supremum is $1$,
+  \[
+    m(a \land b) + m(a \land \neg b) + m(\neg a \land b) + m(\neg a \land \neg
+    b) = 1,
+  \]
+  and this allows us to rewrite \cref{eq:temp6} into \cref{eq:to_prove2}. As all
+  transformations are invertible, the two expressions are equivalent.
 \end{proof}
 
-\begin{lemma} \label{lemma:well-defined}
-  For any $a, b \in \mathbf{B}$ and any principal ideal $(p)$, if $a/(p) =
-  b/(p)$, then $a \lor p = b \lor p$.
-\end{lemma}
-\begin{proof}
-  Note that
-  \[
-    a/(p) = b/(p) \quad \iff \quad a+b \in (p) \quad \iff \quad a+b \le p \quad
-    \iff \quad (a+b) \lor p = p
-  \]
-  by \cref{def:quotient,def:ideal}, and the definition of $\le$. So $p = (a
-  \land \neg b) \lor (\neg a \land b) \lor p$, and thus
-  \[
-    0 = p \land \neg p = (a \land \neg b \land \neg p) \lor (\neg a \land b
-    \land \neg p) \lor (p \land \neg p) = (a \land \neg (b \lor p)) \lor (b
-    \land \neg (a \lor p)).
-  \]
-  It follows that
-  \[
-    a \land \neg (b \lor p) = 0 \quad \text{and} \quad b \land \neg (a \lor p) =
-    0.
-  \]
-  Focusing on the first equation,
-  \[
-    \neg a = (\neg a \lor a) \land [\neg a \lor \neg (b \lor p)] = \neg [a \land
-    (b \lor p)],
-  \]
-  and so $a = a \land (b \lor p)$, and
-  \[
-    a \lor p = (a \lor p) \land (b \lor p) = (a \land b) \lor p.
-  \]
-  By similar arguments, $b \lor p = (a \land b) \lor p$ as well which shows that
-  $a \lor p = b \lor p$ as required.
-\end{proof}
-
-% TODO: Feedback 2: Where is this helping?
-\todo[inline]{Outdated. $m(a \land \neg p)$ is better than $m (a \lor p)$.}
-\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
-  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, and let $(p)$ be
-  a principal ideal. Let $m^*\colon \mathbf{B}/(p) \to \mathbb{R}_{\ge 0}$ be
-  defined as
-  \[
-    m^*(a/(p)) = m(a \lor p)
-  \]
-  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
-  it is a measure on $\mathbf{B}/(p)$ if and only if $m(p) = 0$. Moreover, if it
-  is a measure, then the following properties transfer from $m$ to $m^*$:
-  \begin{itemize}
-  \item if $m$ is a \emph{probability measure}, then so is $m^*$;
-  \item if $m$ is \emph{strictly positive}, then so is $m^*$.
-  \end{itemize}
-\end{proposition}
-\begin{proof}
-  \Cref{lemma:well-defined} proves that the function is well-defined. Next,
-  note that
-  \[
-    m^*(0/(p)) = m(0 \lor p) = m(p),
-  \]
-  so $m^*(0/(p)) = 0$ if and only if $m(p) = 0$. For the second part of
-  \cref{def:measure}, let $a/(p), b/(p) \in \mathbf{B}/(p)$ be such that
-  \[
-    a/(p) \land b/(p) = a \land b / (p) = 0 / (p).
-  \]
-  This condition is equivalent to $a \land b \in (p)$ and $(a \land b) \lor p =
-  p$ by well-known properties of quotients and ideals
-  \cite{givant2008introduction}, \cref{def:ideal}, and the definition of $\le$,
-  respectively. Now
-  \begin{align*}
-    m^*(a/(p) \lor b/(p)) &= m^*(a \lor b / (p)) = m(a \lor b \lor p) = m((a \lor p) \lor (b \lor p)) \\
-                          &= m(a \lor p) + m(b \lor p) - m((a \lor p) \land (b \lor p)) \\
-                          &= m^*(a/(p)) + m^*(b/(p)) - m((a \lor p) \land (b \lor p))
-  \end{align*}
-  by \cref{lemma:sum}. However
-  \[
-    (a \lor p) \land (b \lor p) = (a \land b) \lor p = p,
-  \]
-  so $m^*(a/(p) \lor b/(p)) = m^*(a/(p)) + m^*(b/(p))$ if and only if $m(p) = 0$.
-
-  The two remaining properties are easy to prove:
-  \begin{itemize}
-  \item If $m(1) = 1$, then $m^*(1/(p)) = m(1 \lor p) = m (1) = 1$.
-  \item Suppose that $m$ is strictly positive, and let $a/(p) \in
-    \mathbf{B}/(p)$ be such that $a/(p) \ne 0/(p)$. Then
-    \[
-      m^*(a/(p)) = m(a \lor p) \ge m(a) > 0,
-    \]
-    where the first inequality comes from an elementary property of $\le$ that
-    $x \le x \lor y$ for any $x, y \in \mathbf{B}$ \cite{sikorski1969boolean}
-    and \cref{lemma:measure_and_order}; and the second inequality follows
-    because $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be
-    strictly positive.
-  \end{itemize}
-\end{proof}
-% TODO: I think I need to cite something for: a/I = 0/I <=> a \in I
-
-\subsection{Lemma Galore}
-
-\todo[inline]{This section made me realise that I was using the wrong definition}
-
-% TODO: maybe 'unite' this with the result about a \/ p, i.e., a ~ a \/ p ~ a /\
-% ~p.
-% TODO: maybe I should state that A,B are assumed to be BAs with no additional
-% properties unless stated otherwise.
-\begin{lemma} \label{lemma:elements_in_quotients}
-  Let $(p)$ be a principal ideal. Then for any $a \in \mathbf{B}$, $(a \land
-  \neg p)/(p) = a/(p)$.
-\end{lemma}
-\begin{proof}
-  Note that
-  \[
-    (a \land \neg p)/(p) = a/(p) \quad \iff \quad (a \land \neg p) + a \in (p)
-    \quad \iff \quad (a \land \neg p) + a \le p.
-  \]
-  We also have that
-  \[
-    (a \land \neg p) + a = (a \land \neg p \land \neg a) \lor (\neg(a \land \neg
-    p) \land a) = (\neg a \lor p) \land a = (\neg a \land a) \lor (p \land a) =
-    p \land a.
-  \]
-  And, since $p \land a \le p$, we have that $(a \land \neg p) + a \le p$ as
-  required.
-\end{proof} % TODO: why? (the last bit) It's elementary
-% TODO: remove all those 'let (p) be a principal ideal'.
-
-\begin{lemma} \label{lemma:min_element_and_order}
-  Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
-  b/(p)$ if and only if $a \land \neg p \le b \land \neg p$.
-\end{lemma}
-\begin{proof}
-  Let us begin with the `only of' direction. \Cref{lemma:elements_in_quotients}
-  tells us that $(a \land \neg p)/(p) = a/(p)$. Combining this with
-  \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order} shows that
-  \[
-    a \land \neg p \le b \land \neg p \quad \implies \quad (a \land \neg p)/(p)
-    \le (b \land \neg p)/(p) \quad \iff \quad a/(p) \le b/(p)
-  \]
-  as required.
-
-  For the other direction, let $a, b \in \mathbf{B}$ be such that $a/(p) \le
-  b/(p)$. Then, by \cref{lemma:order},
-  \[
-    [a/(p)] \land \neg [b/(p)] = (a \land \neg b)/(p) = 0/(p),
-  \]
-  i.e.,
-  \[
-    a \land \neg b \in (p) \quad \iff \quad a \land \neg b \le p \quad \iff
-    \quad a \land \neg b \land \neg p = 0
-  \]
-  by \cref{def:ideal,lemma:order}. We need to show that $a \land \neg p \le b
-  \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land \neg p
-  \land \neg(b \land \neg p) = 0$. But
-  \[
-    a \land \neg p \land \neg(b \land \neg p) = a \land \neg p \land (\neg b
-    \lor p) = (a \land \neg p \land \neg b) \lor (a \land \neg p \land p) = a
-    \land \neg p \land \neg b,
-  \]
-  and we already have that $a \land \neg p \land \neg b = 0$ by assumption.
-\end{proof}
-
-\begin{lemma} \label{lemma:measure_of_atom}
-  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, let $p \in
-  \mathbf{B}$ be such that $m(p) = 0$, and let $m^*\colon \mathbf{B}/(p) \to
-  \mathbb{R}_{\ge 0}$ be a measure defined by $m^*(a/(p)) = m(a \lor p)$. Then
-  for any $a \in \mathbf{B}$, if $a/(p)$ is an atom in $\mathbf{B}/(p)$, then $a
-  \land \neg p$ is an atom in $\mathbf{B}$ such that $m^*(a/(p)) = m(a \land
-  \neg p)$.
-\end{lemma}
-\begin{proof} % TODO: This proof is a mess and needs more citations.
-  First, we want to show that if $a/(p)$ is an atom, then $a \land \neg p$ is an
-  atom. We can instead prove the contrapositive statement, i.e., if there exists
-  a $b \in \mathbf{B}$ such that $0 < b < a \land \neg p$, then there exists a
-  $b' \in \mathbf{B}$ such that $0/(p) < b'/(p) < a/(p)$. We will show that, in
-  fact, we set $b' = b$.
-  \Cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order} already tell
-  us that $b/(p) \le a/(p)$, so we only need to show that $0/(p) < b/(p) \ne
-  a/(p)$. For the first part, note that
-  \[
-    0/(p) < b/(p) \quad \iff \quad b/(p) \ne 0/(p) \quad \iff \quad b \not\in
-    (p) \quad \iff \quad b \not\le p \quad \iff \quad b \land \neg p \ne 0
-  \]
-  by \cref{lemma:order}. But if $b \land \neg p = 0$, then $b \land a \land \neg
-  p = 0$. This contradicts either that $b \le a \land \neg p$ (i.e., $b \land a
-  \land \neg p = b$) or that $b \ne 0$. For the second part, i.e., $b/(p) \ne
-  a/(p)$, we will show that if $b/(p) = a/(p)$, and $b \le a \land \neg p$, then
-  $b = a \land \neg p$. Indeed,
-  \[
-    b/(p) = a/(p) \quad \iff \quad a + b \in (p) \quad \iff \quad a+b \le p
-    \quad \iff \quad (a+b) \land \neg p = 0,
-  \]
-  and
-  \[
-    (a+b) \land \neg p = [(a \land \neg b) \lor (\neg a \land b)] \land \neg p =
-    (a \land \neg b \land \neg p) \lor (\neg a \land b \land \neg p),
-  \]
-  so $(a+b) \land \neg p = 0$ implies that $a \land \neg b \land \neg p = 0$
-  which is equivalent to $a \land \neg p \le b$. Therefore we have that $a \land
-  \neg p \le b \le a \land \neg p$, so $b = a \land \neg p$ which, by
-  contradiction, shows that $b/(p) \ne a/(p)$ and finishes the proof that $0/(p)
-  < b/(p) < a/(p)$.
-
-  In order to show that $m^*(a/(p)) = m(a \land \neg p)$, note that $a \land p$,
-  $a \land \neg p$, and $\neg a \land p$ are pairwise disjoint and their
-  supremum is $a \lor p$, so we have that
-  \[
-    m^*(a/(p)) = m(a \lor p) =  m(a \land p) + m(a \land \neg p) + m(\neg a
-    \land p).
-  \]
-  Furthermore, since $a \land p \le p$, $m(a \land p) \le m(p) = 0$. Similarly,
-  $m(\neg a \land p) = 0$, so $m^*(a/(p)) = m(a \land \neg p)$ as required.
-\end{proof}
-% TODO: the undergraduate book vaguely mentions that, when taking a quotient
-% w.r.t. an ideal of elements with measure zero, all elements in an equivalence
-% class will have the same measure.
-
-\begin{lemma} \label{lemma:minimal_in_quotient} % TODO: define completeness
-  Let $\mathbf{B}$ be a complete BA. For any $a, b \in \mathbf{B}$, if $a/(p) =
-  b/(p)$, then $a \land \neg p = b \land \neg p$. As a consequence, $a \land
-  \neg p \le b$.
-\end{lemma}
-\begin{proof} % TODO: rename b to something else
-  As in the proof of \cref{lemma:measure_of_atom}, $a/(p) = b/(p)$ implies that
-  $a \land \neg p \le b$. Since $\mathbf{B}$ is complete, let $b = \bigwedge \{
-  c \in \mathbf{B} \mid c/(p) = a/(p) \}$; then we still have that $b/(p) =
-  a/(p)$. But then $b \le a \land \neg p \le b$, so $a \land \neg p = b$. This
-  defines $a \land \neg p$ independently of $a$ as the least element in $\{c \in
-  \mathbf{B} \mid c/(p) = a/(p) \}$.
-\end{proof}
-
-\begin{corollary}
-  For any complete BA $\mathbf{B}$, if $a \in \mathbf{B}$ is an atom, then
-  $a/(p)$ is either an atom or $0/(p)$. In the former case, $a = a \land \neg
-  p$.
-\end{corollary}
-\begin{proof}
-  Since \cref{lemma:minimal_in_quotient} tells us that for all $b \in
-  \mathbf{B}$, if $b/(p) = a/(p)$, then $b \ge a \land \neg p$, if there is an
-  atom $b \in \mathbf{B}$ such that $b/(p) = a/(p)$, then it must be $a \land
-  \neg p$. If $a$ is an atom, then $a \land \neg p \le a$ implies that either $a
-  = a \land \neg p$ or $a \land \neg p = 0$. The latter is equivalent to $a/(p)
-  = 0/(p)$ by \cref{lemma:order}. The former, combined with the assumption that
-  $a$ is an atom and \cref{lemma:min_element_and_order}, implies that $a/(p)$ is
-  an atom.
-\end{proof}
-
-% we can then move through the quotient BA using representatives we get
-% from mapping true things to 1 and false things to 0.
-
-%\[
-%  \begin{tikzcd}
-%    \mathbf{B}/(p) \arrow[rr, shift left, "x/(p) \mapsto x \lor p"] \arrow[rr,
-%    shift right, swap, "x/(p) \mapsto x \land \neg p"] & & \mathbf{B} \arrow{r}{\WMC} & \mathbb{R}_{\ge 0}
-%  \end{tikzcd}
-%\]
-
-%\begin{theorem}[Using the previous results]
-%  Let $L \subset \mathbf{B}$ and $w\colon L \to \mathbb{R}_{\ge 0}$ be such that
-%  $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge0}$ is a WMC measure. Let $p \in
-%  \mathbf{B}$ be such that $\WMC(p) = 0$, and let $g\colon \mathbf{B}/(p) \to
-%  \mathbf{B}$ be defined as $g(a/(p)) = a \land \neg p$. Then $\WMC \circ g$
-%  is a WMC measure on $\mathbf{B}/(p)$ with respect to the same $L$ and $w$
-%  such that
-%  \[
-%    \begin{tikzcd}
-%      \mathbf{B} \arrow{d}[swap]{\WMC} & \mathbf{B}/(p) \arrow{l}[swap]{g}
-%      \arrow{dl}{\WMC \circ g} \\
-%      \mathbb{R}_{\ge 0}
-%    \end{tikzcd}
-%  \]
-%  commutes.
-%\end{theorem}
-
-\section{What Measures Are WMC-Computable?}
-
-% TODO: Proofs need to be updated and propositions could be phrased in a better
-% way, but the gist should be the same.
-
-\subsection{WMC Requires Independent Literals}
-
-% TODO: maybe I should gives this kind of a BA a name? A synonym of 'complete',
-% perhaps.
 % TODO: a special case for weight=0.
-
 \begin{theorem}
-  Let $\mathbf{B}$ be a finite measure algebra with measure $m\colon \mathbf{B} \to
-  \mathbb{R}_{\ge 0}$. Let $L \subset \mathbf{B}$ be defined as
-  \[
-  L = \{ l_i \mid i \in [n] \} \cup \{ \neg l_i \mid i \in [n] \}
-  \]
-  for some $n \in \mathbb{N}$. Finally, assume that $\mathbf{B}$ has $2^n$
-  atoms, where each atom $a \in \mathbf{B}$ is an infimum
-  \[
-    a = \bigwedge_{i=1}^n a_i
-  \]
-  such that $a_i \in \{ l_i, \neg l_i \}$ for $i \in [n]$. Then there exists a
-  weight function $w\colon L \to \mathbb{R}_{\ge 0}$ that makes $m$ a WMC measure if
-  and only if
+  Let $\mathbf{B}$ be a free BA on $n$ generators $\{ l_i \}_{i=1}^n$ (for some
+  $n \in \mathbb{N}$) with measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$,
+  and let $L = \{ l_i \}_{i = 1}^n \cup \{ \neg l_i \}_{i = 1}^n$. Then there
+  exists a weight function $w\colon L \to \mathbb{R}_{\ge 0}$ such that $m =
+  \WMC_w$ if and only if
   \begin{equation} \label{eq:wmccondition}
@@
 \begin{proof}
-  Let us begin with the `if' part of the statement. Let $w\colon L \to
-  \mathbb{R}_{\ge 0}$ be defined by
+  ($\Leftarrow$) Let $w\colon L \to \mathbb{R}_{\ge 0}$ be defined by
   \begin{equation} \label{eq:assumption}
@@
   \end{equation}
-  for all $l \in L$. We are going
-  to show that $\nWMC = m$. First, note that $\nWMC(0) = 0 = m(0)$ by the
-  definitions of both $\nWMC$ and $m$. Second, let
+  for all $l \in L$. We are going to show that $\WMC_w = m$. First, note that
+  $\WMC_w(0) = 0 = m(0)$ by the definitions of both $\WMC_w$ and $m$. Second,
+  let
   \begin{equation} \label{eq:def_of_a}
@@
   \[
-    \nWMC(a) = \frac{\WMC(a)}{\WMC(1)} = \frac{1}{\WMC(1)} \prod_{i=1}^n w(a_i)
-    = \frac{1}{\WMC(1)} \prod_{i=1}^n m(a_i) = \frac{1}{\WMC(1)} m \left(
-      \bigwedge_{i=1}^n a_i \right) = \frac{m(a)}{\WMC(1)}
-  \]
-  by \cref{def:wmc,eq:assumption,eq:wmccondition,eq:def_of_a}. Now we just need
-  to show that $\WMC(1) = 1$. Indeed,
-  \begin{align*}
-    \WMC(1) &= \sum_{\text{atoms } a \in \mathbf{B}} \WMC(a) = \sum_{\text{atoms
-      } a \in \mathbf{B}} \prod_{i=1}^n w(a_i) = \sum_{\text{atoms } a \in
-      \mathbf{B}} \prod_{i=1}^n m(a_i) \\
-    &= \sum_{\text{atoms } a \in
-      \mathbf{B}} m \left( \bigwedge_{i=1}^n a_i \right) = \sum_{\text{atoms } a
-      \in \mathbf{B}} m(a) = m \left( \bigvee_{\text{atoms } a \in \mathbf{B}}
-    \right) = m(1) = 1.
-  \end{align*}
-  Finally, note that if $\nWMC$ and $m$ agree on all atoms, then they must also
-  agree on all other non-zero elements of the Boolean algebra.
-
-  For the other direction, we are given a weight function $w\colon L \to
-  \mathbb{R}_{\ge 0}$ that induces a measure $m = \nWMC\colon \mathbf{B} \to
-  \mathbb{R}_{\ge 0}$, and we want to show that \cref{eq:wmccondition} is
-  satisfied. Let $k_i, k_j \in L$ be such that $k_i \in \{ l_i, \neg l_i \}$,
-  $k_j \in \{ l_j, \neg l_j \}$, and $i \ne j$. We will first prove an auxiliary
-  result that
-  \begin{equation} \label{eq:to_prove}
+    \WMC(a) = \prod_{i=1}^n w(a_i) = \prod_{i=1}^n m(a_i) = m
+    \left(\bigwedge_{i=1}^n a_i \right) = m(a)
+  \]
+  by \cref{def:wmc,eq:assumption,eq:wmccondition,eq:def_of_a}. Finally, note
+  that if $\WMC$ and $m$ agree on all atoms, then they must also agree on all
+  other non-zero elements of the Boolean algebra.
+
+  ($\Rightarrow$) For the other direction, we are given a weight function
+  $w\colon L \to \mathbb{R}_{\ge 0}$ that induces a measure $m = \WMC_w\colon
+  \mathbf{B} \to \mathbb{R}_{\ge 0}$, and we want to show that
+  \cref{eq:wmccondition} is satisfied. Let $k_i, k_j \in L$ be such that $k_i
+  \in \{ l_i, \neg l_i \}$, $k_j \in \{ l_j, \neg l_j \}$, and $i \ne j$ for
+  some $i, j \in [n]$. We then want to show that
+  \begin{equation} \label{eq:to_prove3}
     m(k_i \land k_j) = m(k_i)m(k_j)
   \end{equation}
-  is equivalent to
-  \begin{equation} \label{eq:to_prove2}
+  which is equivalent to
+  \begin{equation} \label{eq:to_prove4}
     m(k_i \land k_j) \cdot m(\neg k_i \land \neg k_j) = m(k_i \land \neg k_j)
-    \cdot m(\neg k_i \land k_j).
-  \end{equation}
-  First, note that $k_i$ can be expressed as
-  \[
-    k_i = (k_i \land k_j) \lor (k_i \land \neg k_j)
-  \]
-  with the condition that
-  \[
-    (k_i \land k_j) \land (k_i \land \neg k_j) = 0,
-  \]
-  so, by properties of a measure,
-  \begin{equation} \label{eq:temp}
-    m(k_i) = m(k_i \land k_j) + m(k_i \land \neg k_j).
-  \end{equation}
-  Applying \cref{eq:temp} and the equivalent expression for $m(k_j)$ allows us
-  to rewrite \cref{eq:to_prove} as
-  \begin{align*}
-    m(k_i \land k_j) &= [m(k_i \land k_j) + m(k_i \land \neg k_j)] \cdot [m(k_i \land k_j) + m(\neg k_i \land k_j)] \\
-                     &= m(k_i \land k_j)^2 + m(k_i \land k_j)[m(k_i \land \neg k_j) + m(\neg k_i \land k_j)] + m(k_i \land \neg k_j)m(\neg k_i \land k_j)
-  \end{align*}
-  Dividing both sides by $m(k_i \land k_j)$ gives
-  \begin{equation} \label{eq:temp2}
-    1 = m(k_i \land k_j) + m(k_i \land \neg k_j) + m(\neg k_i \land k_j) +
-    \frac{m(k_i \land \neg k_j)m(\neg k_i \land k_j)}{m(k_i \land k_j)}.
-  \end{equation}
-  Since $k_i \land k_j \land k_i \land \neg k_j = 0$, and
-  \[
-    (k_i \land k_j) \lor (k_i \land \neg k_j) = k_i \land (k_j \lor \neg k_j) =
-    k_i \land 1 = k_i,
-  \]
-  we have that
-  \[
-    m(k_i \land k_j) + m(k_i \land \neg k_j) = m(k_i).
-  \]
-  Similarly, $k_i \land \neg k_i \land k_j = 0$, and
-  \[
-    k_i \lor (\neg k_i \land k_j) = (k_i \lor \neg k_i) \land (k_i \lor k_j) =
-    k_i \lor k_j,
-  \]
-  so
-  \[
-    m(k_i) + m(\neg k_i \land k_j) = m(k_i \lor k_j).
-  \]
-  Finally, note that
-  \[
-    (k_i \lor k_j) \land \neg(k_i \lor k_j) = 0,
-  \]
-  and
-  \[
-    (k_i \lor k_j) \lor \neg(k_i \lor k_j) = 1,
-  \]
-  so
-  \[
-    m(k_i \lor k_j) + m(\neg(k_i \lor k_j)) = m(1) = 1.
-  \]
-  This allows us to rewrite \cref{eq:temp2} as
-  \[
-    \frac{m(k_i \land \neg k_j)m(\neg k_i \land k_j)}{m(k_i \land k_j)} = 1 -
-    m(k_i \lor k_j) = m(\neg(k_i \lor k_j)) = m(\neg k_i \land \neg k_j)
-  \]
-  which immediately gives us \cref{eq:to_prove2}.
-
-  Now recall that $m = \nWMC$ and note that \cref{eq:to_prove2} can be
-  multiplied by $\WMC(1)^2$ to turn the equation into one for $\WMC$ instead of
-  $\nWMC$. Then
+    \cdot m(\neg k_i \land k_j)
+  \end{equation}
+  by \cref{lemma:before_theorem}. Then
   \begin{align*}
@@
   $\WMC(\neg k_i \land k_j)$, $\WMC(k_i \land \neg k_j)$, and $\WMC(\neg k_i
-  \land \neg k_j)$ as well. But then \cref{eq:to_prove2} becomes
+  \land \neg k_j)$ as well. But then \cref{eq:to_prove4} becomes
   \[
@@
   \]
-  which is trivially true. By showing that WMC satisfies \cref{eq:to_prove2}, we
-  also showed that it satisfies \cref{eq:to_prove}, finishing the second part of
-  the proof.
+  which is trivially true.
 \end{proof}
-% TODO: the auxiliary result should be a 'claim' in-between the theorem and the
-% proof.
 
@@
 
-In simpler terms, any measure can be computed using WMC by extending the Boolean
-algebra with more literals. More precisely, we are given the red part in
+In simpler terms, any measure can be computed using WMC by extending the BA with
+more literals. More precisely, we are given the red part in
 \[
@@
   for some $\{ a_{i,j} \}_{j \in J} \subset L$. Moreover, each atom $b \in
-  \mathbf{B'}$ can be represented as either
-  \[
-    b = \phi_i \land a_i \quad \text{or} \quad b = \neg\phi_i \land a_i
-  \]
-  for some atom $a_i \in \mathbf{B}$, also making it an infimum over a subset of
-  $L'$. Then, for any $b \in \mathbf{B}$,
+  \mathbf{B'}$ can be represented as either $b = \phi_i \land a_i$ or $b =
+  \neg\phi_i \land a_i$ for some atom $a_i \in \mathbf{B}$, also making it an
+  infimum over a subset of $L'$. Then, for any $b \in \mathbf{B}$,
   \[
@@
   recognising that, for any $\iota(b)$, any atom $a_i \in \mathbf{B}$ satisfies
-  \[
-    \phi_i \land a_i \le \iota(b)
-  \]
-  if and only if it satisfies
-  \[
-    \neg\phi_i \land a_i \le \iota(b).
-  \]
-  Then, according to the definition of $w$,
+  $\phi_i \land a_i \le \iota(b)$ if and only if it satisfies $\neg\phi_i \land
+  a_i \le \iota(b)$. Then, according to the definition of $w$,
   \[
@@
   Let $\mathbf{B}$ and $\mathbf{B'}$ be Boolean algebras, and $\iota\colon
-  \mathbf{B} \to \mathbf{B'}$ be the inclusion map such that $\mathbf{B}$ is
-  freely generated by $L$, all atoms of $\mathbf{B'}$ can be expressed as
-  meets of elements of $L'$, and the following subset relations are satisfied:
+  \mathbf{B} \hookrightarrow \mathbf{B'}$ be the inclusion map such that
+  $\mathbf{B}$ is freely generated by $L$, all atoms of $\mathbf{B'}$ can be
+  expressed as meets of elements of $L'$, and the following subset relations are
+  satisfied:
   \[
     \begin{tikzcd}
-      \mathbf{B} \arrow{r}{\iota} & \mathbf{B'} \\
+      \mathbf{B} \ar[r,hookrightarrow,"\iota"] & \mathbf{B'} \\
       L \arrow[Subset]{u}{} \arrow[Subset]{r}{} & L' \arrow[Subset]{u}{}
@@
   Let $\mathbf{A}$ be a BA. Let $\mathbf{B}$ be a subalgebra of $\mathbf{A}$,
-  and let $(\mathbf{A}_i)_{i \in I}$ be a family of subalgebras of $\mathbf{A}$
+  and let $\{ \mathbf{A}_i\}_{i \in I}$ be a family of subalgebras of $\mathbf{A}$
   such that $\mathbf{A}_i \cap \mathbf{A}_j = \mathbf{B}$ for all $i \ne j$ in
@@
   We want to show that there exists a unique homomorphism $\mathbf{A} \to
-  \mathbf{C}$. For $i \in I$, from $S_i \hookrightarrow S$ and $S \to
+  \mathbf{C}$. For all $i \in I$, from $S_i \hookrightarrow S$ and $S \to
   \mathbf{C}$ we get a map $S_i \to \mathbf{C}$, so---by the definition of a

### 2020-06-01 paper.tex
Experimental data

@@
 
+% Feedback from the panel: Clear up questions about independence between
+% literals.
+
 % TODO for later:
 % 1) make up my mind about a,b vs x,y and stick to it (maybe x,y?)
+% 2) Coproducts/pushouts vs (amalgamated) free products. Probably the former.
+% 3) 'with generating set S' -> 'over S'
 
@@
   b \in \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
+\end{lemma}
+
+\begin{definition}[\cite{koppelberg1989handbook}]
+  Let $S$ be a set, and let $\mathbf{B}$ be a BA. Then $\mathbf{B}$ is a
+  \emph{free BA over $S$} if there is a map $S \to \mathbf{B}$ such that for any
+  BA $\mathbf{C}$ and map $S \to \mathbf{C}$, there is a unique homomorphism
+  $\mathbf{B} \to \mathbf{C}$ that makes
+  \[
+    \begin{tikzcd}
+      S \ar[rd] \ar[r] & \mathbf{B} \ar[d,dashed] \\
+      & \mathbf{C}.
+    \end{tikzcd}
+  \]
+  commute. A BA $\mathbf{B}$ is \emph{free} if $S$ exists.
+\end{definition}
+
+\begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:finite_and_free}
+  A finite BA is free if and only if it has $2^{2^n}$ elements for some $n \in
+  \mathbb{N}$. It then has $2^n$ atoms and $n$ generators.
 \end{lemma}
@@
 \begin{theorem}
-  Let $\mathbf{B}$ be a free BA on $n$ generators $\{ l_i \}_{i=1}^n$ (for some
-  $n \in \mathbb{N}$) with measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$,
-  and let $L = \{ l_i \}_{i = 1}^n \cup \{ \neg l_i \}_{i = 1}^n$. Then there
-  exists a weight function $w\colon L \to \mathbb{R}_{\ge 0}$ such that $m =
-  \WMC_w$ if and only if
+  Let $\mathbf{B}$ be a free BA over $\{ l_i \}_{i=1}^n$ (for some $n \in
+  \mathbb{N}$) with measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$, and let
+  $L = \{ l_i \}_{i = 1}^n \cup \{ \neg l_i \}_{i = 1}^n$. Then there exists a
+  weight function $w\colon L \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$ if
+  and only if
   \begin{equation} \label{eq:wmccondition}
@@
 
-A well-known way to overcome this limitation of independence is by adding more
-literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending the set $L$ covered
-by the WMC weight function $w\colon L \to \mathbb{R}_{\ge 0}$. Let us translate this
-idea to the language of Boolean algebras.
+Given this requirement for independence, a well-known way to represent
+probability distributions that do not consist entirely of independent variables
+is by adding more literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending
+the set $L$ covered by the WMC weight function $w\colon L \to \mathbb{R}_{\ge
+  0}$. Let us translate this idea to the language of BAs.
 
-\begin{theorem} \label{thm:extension} % TODO: cite the fact about atoms
-  Let $\mathbf{B}$ be a finite Boolean algebra freely generated by some set of
-  `literals' $L$, and let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be an
-  arbitrary measure. We know that $\mathbf{B}$ has $n = 2^{|L|}$ atoms. Let
-  $(a_i)_{i=1}^n$ denote those atoms in some arbitrary order. Let $L' = L \cup
-  \{ \phi_i \mid i \in [n] \} \cup \{ \neg \phi_i \mid i \in [n] \}$ be the set
-  $L$ extended with $2n$ new literals. Let $\mathbf{B'}$ be the unique Boolean
-  algebra with
-  \[
-    \{ \phi_i \land a_i \mid i \in [n] \} \cup \{ \neg \phi_i \land a_i \mid i
-    \in [n] \}
-  \]
-  as its set of atoms. Let $\iota\colon \mathbf{B} \to \mathbf{B'}$ be the inclusion
-  homomorphism (i.e., $\iota(a) = a$ for all $a \in \mathbf{B}$). Let $w\colon L'
-  \to \mathbb{R}_{\ge 0}$ be defined by
+% TODO: If L denotes literals, then it doesn't denote a generating set
+\begin{theorem} \label{thm:extension}
+  Let $\mathbf{B}$ be a free BA over a finite set $S$, and let $m\colon
+  \mathbf{B} \to \mathbb{R}_{\ge 0}$ be an arbitrary measure. Let $L = \{ s \mid
+  s \in S \} \cup \{ \neg s \mid s \in S \}$. By \cref{lemma:finite_and_free},
+  we know that $\mathbf{B}$ has $n = 2^{|S|}$ atoms. Let $\{a_i\}_{i=1}^n$
+  denote those atoms in some arbitrary order. Let $L' = L \cup \{ \phi_i
+  \}_{i=1}^n \cup \{\neg \phi_i \}_{i=1}^n$ be the set $L$ extended with $2n$
+  new elements. Let $\mathbf{B'}$ be the unique Boolean algebra with $\{ \phi_i
+  \land a_i \}_{i=1}^n \cup \{ \neg \phi_i \land a_i \}_{i=1}^n$ as its set of
+  atoms. Let $\iota\colon \mathbf{B} \hookrightarrow \mathbf{B'}$ be the
+  inclusion homomorphism. Let $w\colon L' \to \mathbb{R}_{\ge 0}$ be defined by
   \[
     w(l) = \begin{cases}
-      \frac{m(a_i)}{2} & \text{if } l = \phi_i \text{ or } l = \neg\phi_i \text{
-        for some } i \in [n] \\
+      m(a_i)/2 & \text{if } l = \phi_i \text{ or } l = \neg\phi_i \text{ for
+        some } i \in [n] \\
       1 & \text{otherwise}
@@
   \]
-  for all $l \in L'$, and note that this defines a WMC measure $m'\colon \mathbf{B'}
-  \to \mathbb{R}_{\ge 0}$. Then
+  for all $l \in L'$, and note that this defines a WMC measure $m' =
+  \WMC_{w}\colon \mathbf{B'} \to \mathbb{R}_{\ge 0}$. Then
   \[
@@
 
-In simpler terms, any measure can be computed using WMC by extending the BA with
-more literals. More precisely, we are given the red part in
+In other words, any measure can be computed using WMC by extending the BA with
+more literals. More precisely, we are given the left-hand column in
 \[
@@
 \]
-and construct the black part in such a way that the triangle commutes.
+and construct the remaining part in such a way that the triangle commutes.
 
@@
 \begin{proof} % TODO: find a reference for this first claim
-  Since $\mathbf{B}$ is freely generated by $L$, each atom $a_i \in \mathbf{B}$
-  is an infimum of elements in $L$, i.e.,
+  Since $\mathbf{B}$ is free over $S$, each atom $a_i \in \mathbf{B}$ is an
+  infimum of elements in $L$, i.e.,
   \[
@@
   \mathbf{B} \hookrightarrow \mathbf{B'}$ be the inclusion map such that
-  $\mathbf{B}$ is freely generated by $L$, all atoms of $\mathbf{B'}$ can be
+  $\mathbf{B}$ is free over $L$, all atoms of $\mathbf{B'}$ can be
   expressed as meets of elements of $L'$, and the following subset relations are
@@
 
-\subsection{Independence (all known results)}
+\subsection{Preliminaries}
 
@@
 
-\subsection{Conditional Independence}
-
 \begin{definition}[\cite{koppelberg1989handbook}]
@@
 
-\subsubsection{New Results}
+\subsection{New Results}
 
+% TODO: make sure that this is enough to guarantee a pushout
 \begin{theorem}
-  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of BAs with measures $\{
-  m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in I}$, let $\mathbf{B}$
-  be a BA, and let $\mathbf{A}$ be the amalgamated free product of $\{
-  \mathbf{A}_i \}_{i \in I}$ over $\mathbf{B}$. Then there is a unique measure
-  $m\colon \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any element $b \in
-  \mathbf{B}$, finite subset $J \subseteq I$, and elements $\{ a_j \in
-  \mathbf{A}_j \}_{j \in J}$,
+  Let $\{ S_i \}_{i=0}^n$ be a finite set of finite sets for some $n > 1$ such
+  that for all distinct positive integers $i$ and $j$, $S_i \cap S_j = S_0$, and
+  let
+  \[
+    \mathbf{A} = \bigoplus_{\substack{\mathcal{F}(S_0)\\ 1 \le i \le n}}
+    \mathcal{F}(S_i).
+  \]
+  Let $(m_i\colon \mathcal{F}(S_i) \to \mathbb{R}_{\ge 0})_{i=1}^n$ be arbitrary
+  measures. Then there is a unique measure $m\colon \mathbf{A} \to
+  \mathbb{R}_{\ge 0}$ such that, for any element $b \in \mathcal{F}(S_0)$,
+  subset $J \subseteq \{ 1, 2, \dots, n \}$, and elements $\{ a_j \in
+  \mathcal{F}(S_j \setminus S_0) \}_{j \in J}$,
   \[
@@
 \end{theorem}
+\begin{proof}
+  % TODO: start here
+\end{proof}
 
@@
 
-% TODO: make sure that the definition of 'free' is sufficient
 \begin{theorem}[Pushouts of free BAs are free]

### 2020-06-04 paper.tex
ADDMC

@@
 \usepackage[backgroundcolor=lightgray]{todonotes}
+\usepackage{complexity}
 
@@
 \usetikzlibrary{cd}
+\usetikzlibrary{bayesnet}
+\usetikzlibrary{calc}
 
@@
 
+\section{How to represent a Bayesian network}
+
+Let $G = (V, E)$ be a DAG, and let $(X_v)_{v \in V}$ be the discrete random
+variables (RVs). Let $(d_v)_{v \in V}$ denote the numbers of values that each RV
+can take and assume that $d_v$ is a power of two for all $v \in V$.
+\begin{enumerate}
+\item For each $v \in V$, let $A_v$ be a set of $\log_2 d_v$ Boolean variables.
+  (If $d_v$ is not a power of two, we would need to manually forbid each illegal
+  value, e.g., by adding formulas such as $\neg(x_1 \land x_2 \land x_3 \land
+  \neg x_4)$ to the theory. Alternatively, we could set their probability to
+  zero, but the former should be better.)
+\item For $v \in V$:
+  \begin{enumerate}
+  \item If $v$ has no parents, we can directly provide a probability measure on
+    $\mathcal{F}(A_v)$.
+  \item Otherwise, we need a probability measure on
+    \[
+      \mathcal{F} \left( A_v \cup \bigcup_{(u, v) \in E} A_u \right).
+    \]
+    For any element $a_u \land a_v$ in this free Boolean algebra such that $a_v
+    \in A_v \setminus \{ 0, 1 \}$, and $a_u \not\in A_v$, we can set
+    \[
+      m(a_u \land a_v) = \Pr(a_v \mid a_u)\Pr(a_u).
+    \]
+  \end{enumerate}
+\item When a \#\SAT{} algorithm asks for the weight of a model $\bigwedge_{v \in
+    V} l_v$, split it into segments that correspond to each leaf, take the
+  probabilities from each such node, and multiply them. NB: The segments will
+  intersect, e.g., with
+  \[
+    \begin{tikzpicture}
+      \node[latent] (C) {$C$};
+      \node[latent, below left = of C] (A) {$A$};
+      \node[latent, below right = of C] (B) {$B$};
+      \node[latent, right = 2 of C] (D) {$D$};
+      \edge {C} {A, B};
+    \end{tikzpicture}
+  \]
+  $a \land b \land c \land d$ will be split into $(a \land c) \land (b \land c)
+  \land d$.
+\end{enumerate}
+
+\subsection{Bayesian networks as Boolean algebras}
+
+\begin{table}
+  \caption{Examples of how Bayesian networks encode as Boolean algebras. Here,
+    $A$ denotes $\mathcal{F}\{a\}$ and $AB$ denotes $\mathcal{F}\{a, b\}$.}
+  \centering
+  \begin{tabular}{cc}
+    \toprule
+    Bayesian network & Boolean algebra \\
+    \midrule \\[-1.3em]
+    \begin{tikzpicture}[baseline={(A.base)}]
+      \node[latent] (A) {$A$};
+    \end{tikzpicture} & $A$ \\
+    \midrule \\[-1.3em]
+    \begin{tikzpicture}[baseline={(A.base)}]
+      \node[latent] (A) {$A$};
+      \node[latent,right =of A] (B) {$B$};
+    \end{tikzpicture} & $A + B$ \\
+    \midrule \\[-1.3em]
+    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
+      \node[latent] (A) {$A$};
+      \node[latent,below =of A] (B) {$B$};
+      \edge {A} {B};
+    \end{tikzpicture} & $AB$ \\
+    \midrule \\[-1.3em]
+    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
+      \node[latent] (A) {$A$};
+      \node[latent,below =of A] (B) {$B$};
+      \node[latent,right =of A] (C) {$C$};
+      \edge {A} {B};
+    \end{tikzpicture} & $B +_A C$ \\
+    \midrule \\[-1.3em]
+    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
+      \node[latent] (A) {$A$};
+      \node[latent,below =of A] (B) {$B$};
+      \node[latent,right =of A] (C) {$C$};
+      \node[latent,below =of C] (D) {$D$};
+      \edge {A} {B};
+      \edge {C} {D};
+    \end{tikzpicture} & $B +_{A+C} D$ \\
+    \midrule \\[-1.3em]
+    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
+      \node[latent] (A) {$A$};
+      \node[latent,below left =of A] (B) {$B$};
+      \node[latent,below right=of A] (C) {$C$};
+      \node[latent,right = 2 of A] (D) {$D$};
+      \node[latent,below =of D] (E) {$E$};
+      \edge {A} {B,C};
+      \edge {D} {E};
+    \end{tikzpicture} & $B +_{A+D} C +_{A+D} E$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+To turn a Bayesian network into a Boolean algebra, run $f(\{ v \in V \mid
+\mathrm{outdeg}(v) = 0 \})$, where $f$ works as follows on an arbitrary $A
+\subseteq V$:
+\begin{enumerate}
+\item $S \gets \{ u \mid (u, v) \in E\text{, } v \in A \}$ (i.e., $S$ is the set
+  of parents of the elements in $A$).
+\item If $S = \emptyset$, return $\sum A$ (a coproduct).
+\item Otherwise, return $\sum_{f(S)} A$ (a pushout).
+\end{enumerate}
+
 \bibliographystyle{plain}

### 2020-06-08 experiments/ADDMC/counting/implementation/counter.cpp
Interface cleanup

@@ -92,11 +92,6 @@ void Counter::abstractCube(ADD &add, const SetT<int_t> &addVars, const MapT<int_
   }
 }
 
-double Counter::count(const std::string &filePath, WeightFormat weightFormat) {
-  Formula formula(filePath, weightFormat, mgr, addVarOrderingHeuristic, inverseAddVarOrdering);
-  return count(formula);
-}
-
 /* class MonolithicCounter ****************************************************/
 
 void MonolithicCounter::setMonolithicClauseAdds(VectorT<ADD> &clauseAdds, Formula &formula) {
@@ -141,10 +136,8 @@ double MonolithicCounter::count(Formula &formula) {
   return modelCount;
 }
 
-MonolithicCounter::MonolithicCounter(Cudd *mgr, VarOrderingHeuristic addVarOrderingHeuristic, bool inverseAddVarOrdering) {
+MonolithicCounter::MonolithicCounter(Cudd *mgr) {
   this->mgr = mgr;
-  this->addVarOrderingHeuristic = addVarOrderingHeuristic;
-  this->inverseAddVarOrdering = inverseAddVarOrdering;
 }
 
 /* class FactoredCounter ******************************************************/
@@ -193,10 +186,8 @@ double LinearCounter::count(Formula &formula) {
   return modelCount;
 }
 
-LinearCounter::LinearCounter(Cudd *mgr, VarOrderingHeuristic addVarOrderingHeuristic, bool inverseAddVarOrdering) {
+LinearCounter::LinearCounter(Cudd *mgr) {
   this->mgr = mgr;
-  this->addVarOrderingHeuristic = addVarOrderingHeuristic;
-  this->inverseAddVarOrdering = inverseAddVarOrdering;
 }
 
 /* class NonlinearCounter ********************************************************/
@@ -395,13 +386,11 @@ double BucketCounter::count(Formula &formula) {
   return clusterTree ? NonlinearCounter::countWithTree(formula, minRank) : NonlinearCounter::countWithList(formula, minRank);
 }
 
-BucketCounter::BucketCounter(Cudd *mgr, bool clusterTree, VarOrderingHeuristic formulaVarOrderingHeuristic, bool inverseFormulaVarOrdering, VarOrderingHeuristic addVarOrderingHeuristic, bool inverseAddVarOrdering) {
[…]

### 2020-06-08 experiments/ADDMC/counting/implementation/main.cpp

@@ -67,12 +67,12 @@ void testing::test() {
     std::cout << "\n";
   }
 
-  MonolithicCounter monolithicCounter(mgr, addVarOrderingHeuristic, false);
-  LinearCounter linearCounter(mgr, addVarOrderingHeuristic, false);
-  BucketCounter bucketListCounter(mgr, false, formularVarOrderingHeuristic, false, addVarOrderingHeuristic, false);
-  BucketCounter bucketTreeCounter(mgr, true, formularVarOrderingHeuristic, false, addVarOrderingHeuristic, false);
-  BouquetCounter bouquetListCounter(mgr, false, formularVarOrderingHeuristic, false, addVarOrderingHeuristic, false);
-  BouquetCounter bouquetTreeCounter(mgr, true, formularVarOrderingHeuristic, false, addVarOrderingHeuristic, false);
+  MonolithicCounter monolithicCounter(mgr);
+  LinearCounter linearCounter(mgr);
+  BucketCounter bucketListCounter(mgr, false, formularVarOrderingHeuristic, false);
+  BucketCounter bucketTreeCounter(mgr, true, formularVarOrderingHeuristic, false);
+  BouquetCounter bouquetListCounter(mgr, false, formularVarOrderingHeuristic, false);
+  BouquetCounter bouquetTreeCounter(mgr, true, formularVarOrderingHeuristic, false);
 
   int_t m = monolithicCounter.count(formula);
   int_t l = linearCounter.count(formula);
@@ -122,32 +122,32 @@ void solving::solveFile(const std::string &filePath, WeightFormat weightFormat, 
   double modelCount;
   switch (clusteringHeuristic) {
     case ClusteringHeuristic::MONOLITHIC: {
-      MonolithicCounter monolithicCounter(mgr, addVarOrderingHeuristic, inverseAddVarOrdering);
+      MonolithicCounter monolithicCounter(mgr);
       modelCount = monolithicCounter.count(formula);
       break;
     }
     case ClusteringHeuristic::LINEAR: {
-      LinearCounter linearCounter(mgr, addVarOrderingHeuristic, inverseAddVarOrdering);
+      LinearCounter linearCounter(mgr);
         modelCount = linearCounter.count(formula);
       break;
     }
     case ClusteringHeuristic::BUCKET_LIST: {
[…]

### 2020-06-08 paper.tex
Interface cleanup
Fix memory leak

@@
 
+Notes on the implementation of the algorithm
+\begin{itemize}
+\item We extend the Gaifman graph to add edges when two variables occur in the
+  same CPT (e.g., including the edge from $A$ to $B$ when the CPT is $\Pr(A \mid
+  B)$).
+\item Extra benefit: one does not need to come up with a way to turn some probability
+distribution to into a fully independent one.
+\item Trivial CPTs such as $\Pr(A \mid B) = \Pr(\neg A \mid B) = 0.5$, the ADDs
+  of which simplify to a single number, are put in the first cluster.
+\item TODO: Look into ways to theoretically justify the performance benefits (I
+  have some suggestions in my notes).
+\item TODO: when performing experiments, measure memory usage as well.
+\item TODO: Along with comparing the (3?) encodings, I could also compare this
+  to using ADDs directly on Bayesian networks.
+\item TODO: Feedback: Give a concrete example of something impossible to
+  represent using WMC.
+\end{itemize}
+
 \bibliographystyle{plain}

### 2020-06-08 experiments/ADDMC/counting/implementation/main.cpp

@@ -59,20 +59,20 @@ void testing::test() {
   VarOrderingHeuristic addVarOrderingHeuristic = VAR_ORDERING_HEURISTIC_OPTIONS.at(DEFAULT_ADD_VAR_ORDERING_HEURISTIC_OPTION);
   VarOrderingHeuristic formularVarOrderingHeuristic = VAR_ORDERING_HEURISTIC_OPTIONS.at(DEFAULT_FORMULA_VAR_ORDERING_HEURISTIC_OPTION);
 
-  Cudd *mgr = new Cudd();
-  Formula formula(TEST_DIR + "weighted.cnf", WeightFormat::CACHET, mgr, addVarOrderingHeuristic, false);
+  Cudd mgr;
+  Formula formula(TEST_DIR + "weighted.cnf", WeightFormat::CACHET, &mgr, addVarOrderingHeuristic, false);
   if (VERBOSITY >= 1) {
     std::cout << "DIMACS declared var count: " << formula.getDeclaredVarCount() << "\n";
     util::printCnf(formula.getCnf());
     std::cout << "\n";
   }
 
-  MonolithicCounter monolithicCounter(mgr);
-  LinearCounter linearCounter(mgr);
-  BucketCounter bucketListCounter(mgr, false, formularVarOrderingHeuristic, false);
-  BucketCounter bucketTreeCounter(mgr, true, formularVarOrderingHeuristic, false);
-  BouquetCounter bouquetListCounter(mgr, false, formularVarOrderingHeuristic, false);
-  BouquetCounter bouquetTreeCounter(mgr, true, formularVarOrderingHeuristic, false);
+  MonolithicCounter monolithicCounter(&mgr);
+  LinearCounter linearCounter(&mgr);
+  BucketCounter bucketListCounter(&mgr, false, formularVarOrderingHeuristic, false);
+  BucketCounter bucketTreeCounter(&mgr, true, formularVarOrderingHeuristic, false);
+  BouquetCounter bouquetListCounter(&mgr, false, formularVarOrderingHeuristic, false);
+  BouquetCounter bouquetTreeCounter(&mgr, true, formularVarOrderingHeuristic, false);
 
   int_t m = monolithicCounter.count(formula);
   int_t l = linearCounter.count(formula);
@@ -103,8 +103,8 @@ void testing::test() {
[…]

### 2020-06-11 paper.tex
Some preliminary experimental results and reordering my notes and TODOs

--- 2020-06-04 paper.tex
@@
 \usepackage{mathtools}
+\usepackage{hyperref}
 \usepackage[capitalise]{cleveref}
@@
 \usepackage{complexity}
+\usepackage{soul} % temp
 
@@
 
-\title{What Boolean Algebras Can Teach Us About Weighted Model Counting}
-%\title{Generalising Weighted Model Counting to Boolean Algebras}
-%\title{On the Limitations of Weighted Model Counting}
-%\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
-%\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
+\title{Weighted Model Counting with Conditional Probabilities}
 \author{Paulius Dilkas}
@@
 \section{Introduction}
-% Feedback: What are the main claims, what are the main takeaways, intuitive
-% [???] of theorems to follow. To do this, we appeal to algebraic constructions
-% to define the main concepts for introducing measures on Boolean algebras.
 
-% Feedback: Can you say something here about factorized vs non-factorized
-% weight function definitions? That is, factorized is when w maps literals to
-% R_>=0, non-factorized is when w maps models to R_>=0 and show:
-% a) come up with nice example when non-factorized weights are intuitive
-% c) clarify that the factorized definition have is w.r.t. models, in case some
-% one gets confused [It doesn't have to be, if the BA is not free -- P.]
+\paragraph{Legend.}
+\begin{description}
+\item[F] Feedback (round 1).
+\item[F2] Feedback (round 2).
+\item[FP] Feedback from the review panel.
+\item[\textbullet] My own idea.
+\end{description}
 
-% Feedback 2: The paper at this stage is very technical - the danger is that
-% WMC/SRL people may not be able to follow it and so would be hard to get
-% accepted. Without clear target audience, [???] get work accepted. My main high
-% level suggestion is that let us tease apart what you have and see if a story
-% emerges. That is, let us attempt to write a paper *with examples* and see
-% whether with significant motivation, we have a story emerging. Below, sample
-% text needed to adequately motivate [???] for WMC/SRL community.
+\paragraph{The big TODO list.}
+\begin{itemize}
+\item Look into ways to theoretically justify the performance benefits. Some
+  suggestions:
+  \begin{itemize}
+  \item the number of variables,
+  \item the number of clauses/CPTs/lines in CPTs,
+  \item the proportion of edges that exist,
+  \item average degree,
+  \item average number of clauses that a variable is in,
+  \item the number of clusters in the linear/tree-like decomposition.
+  \end{itemize}
+\item Have an example of how the ADDs function in this situation. If not for the
+  paper, then at least for slides. Use the framework to check its correctness.
+\item Along with comparing the (3?) encodings, I could also compare this
+  to using ADDs directly on Bayesian networks.
+\item[F] Give a concrete example of something impossible to represent using WMC.
+\item Describe the changes to the Cachet DIMACS CNF format (and mention that, if
+  needed, the assumption that $\Pr(A) + \Pr(\neg A) = 1$ can be discarded).
+  Instead of \texttt{w 1 0.1}, we have \texttt{w 1 2 0.1} and \texttt{w 1 -2
+    0.5}. This provides half of the information; the remaining half can be
+  deduced, but the algorithm itself can support weights that are not necessarily
+  probabilities.
+\item Rename the repository into `conditional-wmc'.
+\item Give some examples (and/or a proof) of why this is correct when combined
+  with arbitrary clauses (i.e., conjunctions of disjunctions).
+\item Turn the saved PDFs into citations.
+\item Add a mini theorem: my model can express any probability distribution on
+  the BA (just like BNs can express any discrete distribution).
+\item[F] What are the main claims, what are the main takeaways, intuitive [???]
+  of theorems to follow. To do this, we appeal to algebraic constructions to
+  define the main concepts for introducing measures on Boolean algebras.
+\item[F] Can you say something here about factorized vs non-factorized
+  weight function definitions? That is, factorized is when $w$ maps literals to
+  $R_{\ge 0}$, non-factorized is when $w$ maps models to $R_{\ge 0}$ and
+  \begin{itemize}
+  \item come up with nice example when non-factorized weights are intuitive;
+  \item clarify that the factorized definition have is w.r.t. models, in case some
+    one gets confused. [It doesn't have to be, if the BA is not free---P.]
+  \end{itemize}
+\item[F2] The paper at this stage is very technical---the danger is that WMC/SRL
+  people may not be able to follow it and so would be hard to get accepted.
+  Without clear target audience, [???] get work accepted. My main high level
+  suggestion is that let us tease apart what you have and see if a story
+  emerges. That is, let us attempt to write a paper {\bf with examples} and
+  see whether with significant motivation, we have a story emerging. Below,
+  sample text needed to adequately motivate [???] for WMC/SRL community.
+\item[FP] Clear up questions about independence between literals.
+\item[F2] Preliminaries: explain with examples: models $=$ elements [atoms] of
+  algebra.
+\item WMC as a Measure
+  \begin{itemize}
+  \item[F2] Need to explain how WMC and NWMC connects to standard definitions of
+    WMC and $\Pr(\phi \mid e) = \WMC(\phi \land e)/\WMC(e)$.
+  \item[F2] You need to explain what precisely these mean in logic and models
+    and weight functions are usually defined and understood.
+  \item Be careful about mentioning ideals, filters, and quotients.
+  \end{itemize}
+\item What Measures are WMC-Definable: proofs need to be updated and
+  propositions could be phrased in a better way, but the gist should be the
+  same.
+\item Extending the Algebra.
+  \begin{itemize}
+  \item[F2] If you prove (b) above, you could motivate why weights on literals
+    is attractive and whether there is a way to augment the expressivity of WMC
+    while still maintaining literal level weights. Hence this action.
+  \item[F2] You need to explain the significance of this result.
+  \end{itemize}
+\item Make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x, y$?).
+\item Decide on terminology: coproducts/pushouts vs (amalgamated) free products.
+  Probably the former.
+\item Terminology: `with generating set $S$' $\to$ `over $S$'.
+\item Perhaps reorder the section of preliminaries into paragraphs, i.e., a
+  paragraph for order, for homomorphisms, etc. This would take up less space.
+\item Notation: if $L$ denotes literals, then it doesn't denote a generating
+  set.
+\end{itemize}
 
-% Feedback from the panel: Clear up questions about independence between
-% literals.
-
-% TODO for later:
-% 1) make up my mind about a,b vs x,y and stick to it (maybe x,y?)
-% 2) Coproducts/pushouts vs (amalgamated) free products. Probably the former.
-% 3) 'with generating set S' -> 'over S'
+\paragraph{Experimental setup.}
+\begin{itemize}
+\item
+  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
+  (highlighted the initial setup, can expand later):
+  \begin{itemize}
+  \item \hl{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
+    multiplicativity of BAs in different words) (with optimal settings)
+  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
+  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
+  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
+  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
+  \end{itemize}
+\item Encodings:
+  \begin{itemize}
+  \item Darwiche \cite{DBLP:conf/kr/Darwiche02}
+  \item \hl{Sang et al.} \cite{DBLP:conf/aaai/SangBK05}
+  \item \hl{mine}
+  \end{itemize}
+\item Datasets\footnote{There might be more at
+    \url{https://meelgroup.github.io/}.}
+  \begin{itemize}
+  \item binary Bayesian networks from Sang et
+    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
+    \cite{DBLP:conf/aaai/SangBK05}
+    \begin{itemize}
+    \item \hl{Grid networks}: computing marginal probability of the last node in
+      the grid.
+    \item Plan recognition problems.
+    \item Deterministic quick medical reference.
+    \end{itemize}
+    For the last two, the task can be to calculate the marginal probability of a
+    randomly chosen node (so, repeat at least ten times).
+  \item non-binary Bayesian networks?
+  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
+  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
+  \end{itemize}
+\end{itemize}
 
@@
 
+\paragraph{Notes.}
+\begin{itemize}
+\item Thesis: many important computational problems are solved by encoding them
+  as WMC. But if the weight function is extended to `conditional probabilities',
+  the problem becomes easier because current approaches need workarounds in
+  order to be independent.
+\item Shorter thesis: many important problems are encoded as WMC, but they can
+  be encoded in a better way if we allow for conditional probabilities.
+\item We extend the Gaifman graph to add edges when two variables occur in the
+  same CPT (e.g., including the edge from $A$ to $B$ when the CPT is $\Pr(A \mid
+  B)$).
+\item Extra benefit: one does not need to come up with a way to turn some probability
+distribution to into a fully independent one.
+\item Trivial CPTs such as $\Pr(A \mid B) = \Pr(\neg A \mid B) = 0.5$, the ADDs
+  of which simplify to a single number, are put in the first cluster.
+\item Observation: by inspecting the BN, we could identify CPTs that could be
+  completely ignored, but maybe good heuristics take care of that anyway.
+\item Observation: ADDs have a restrict command. I'm not going to use it, but it
+  could be nice.
+\item Alternative scenario to consider for future work: \#\SAT{} solver
+  generates solutions which are then used to restrict the ADDs that calculate
+  probabilities.
+\item Important future work: replacing ADDs with
+  AADDs\footnote{\url{https://github.com/ssanner/dd-inference}} is likely to
+  bring performance benefits. Other extensions:
+  \begin{itemize}
+  \item FOADDs can represent first order statements;
+  \item XADDs can replace WMI for continuous variables;
+  \item ADDs with intervals can do approximations.
+  \end{itemize}
+\end{itemize}
+
 \section{Preliminaries}
-
-% TODO
-% 1) Feedback 2: Explain with examples: models = elements [atoms] of algebra
-% 2) Perhaps reorder the section of preliminaries into paragraphs, i.e., a
-% paragraph for order, for homomorphisms, etc. This would take up less space.
-% 3) how to compute the number of elements in the algebra.
 
@@
 \section{WMC as a Measure}
-% TODO: Feedback 2: Need to explain how WMC and NWMC connects to standard
-% definitions of WMC and Pr(phi|e) = WMC(phi /\ e)/WMC(e).
 
@@
 
-  % TODO: be careful about mentioning ideals, filters, and quotients
   The corresponding BA $B(\Delta)$ can then be constructed using
@@
   the Boolean-algebraic way of calculating the WMC of $\Delta$ consists of:
-  \begin{enumerate} % TODO: why is step 1 always possible?
+  \begin{enumerate}
   \item Identifying an element $a \in B(\mathcal{L})$ that corresponds to
@@
 \end{example}
-% TODO: clarify what B(L) means. And whether B(Delta) is even necessary.
-% TODO: reference for the set/subset thing.
+\todo[inline,caption={}]{
+  \begin{itemize}
+  \item Why is Step 1 always possible?
+  \item Clarify what $B(L)$ means and whether $B(\Delta)$ is even necessary.
+  \item Find a reference for the set/subset thing.
+  \item This should be replaced with inner sums (a.k.a. free products).
+  \item Mention that the subsequent definition can be reduced to a single
+    formula (i.e., without cases).
+  \item Any measure is a WMC measure if all atoms are in $L$.
+  \end{itemize}
+}
 
-% TODO: Feedback 2: You need to explain what precisely these mean in logic and
-% models and weight functions are usually defined and understood.
-% TODO: This should be replaced with inner sums (a.k.a. free products)
 \begin{definition} \label{def:wmc}
@@
 \end{definition}
-% TODO: mention that the definition can be reduced to a single formula (i.e.,
-% without cases)
-% TODO: any measure is a WMC measure if all atoms are in L
 
@@
 
-% TODO: Proofs need to be updated and propositions could be phrased in a better
-% way, but the gist should be the same.
-
 \subsection{WMC Requires Independent Literals}
@@
 
-% TODO: a special case for weight=0.
+\todo[inline]{This theorem needs a special case for zero weights.}
 \begin{theorem}
@@
 
-% TODO: Feedback 2: If you prove (b) above, you could motivate why weights on
-% literals is attractive and whether there is a way to augment the expressivity
-% of WMC while still maintaining literal level weights. Hence this action.
-
 Given this requirement for independence, a well-known way to represent
@@
 
-% TODO: If L denotes literals, then it doesn't denote a generating set
 \begin{theorem} \label{thm:extension}
@@
 
-% TODO: make J depend on i
-\begin{proof} % TODO: find a reference for this first claim
+\todo[inline,caption={}]{
+  \begin{itemize}
+  \item Make $J$ depend on $i$.
+  \item Find a reference for this first claim in the following proof.
+  \end{itemize}
+}
+\begin{proof}
   Since $\mathbf{B}$ is free over $S$, each atom $a_i \in \mathbf{B}$ is an
@@
 
-% TODO: Feedback 2: You need to explain the significance of this result.
-
 \section{Representing Independence and Conditional Independence}
@@
 
-% TODO: make sure that this is enough to guarantee a pushout
+\todo[inline]{Make sure that this is enough to guarantee a pushout.}
 \begin{theorem}
@@
 \end{theorem}
-\begin{proof}
-  % TODO: start here
-\end{proof}
 

### 2020-06-11 experiments/ADDMC/counting/interface/util.hpp

@@ -28,7 +28,7 @@ template<typename T> using VectorT = std::vector<T>;
 
 /* constants ******************************************************************/
 
-const int_t VERBOSITY = 1; /* 0: prints warnings/errors, 1: prints debugging info */
+const int_t VERBOSITY = 0; /* 0: prints warnings/errors, 1: prints debugging info */
 
 const std::string REQUIRED_OPTION_GROUP = "Required";
 const std::string CNF_FILE_OPTION = "cf";

### 2020-06-11 experiments/analyse.R

@@ -1,0 +1,48 @@
+require(ggplot2)
+require(scales)
+
+df <- read.csv("results/all.csv", header = TRUE, sep = ",")
+
+sang.data <- df[df$encoding == "sang",]
+conditional.data <- df[df$encoding == "conditional",]
+
+# Numbers of unsolved instances (incomplete)
+sum(is.na(sang.data$answer))
+sum(is.na(conditional.data$answer))
+
+summary(sang.data$time)
+summary(conditional.data$time)
+
+# NOTE: Some timed out instances are omitted from this
+merged <- merge(sang.data, conditional.data, by = "instance")
+merged$difference <- merged$time.x - merged$time.y
+merged$relative.difference <- merged$difference / merged$time.x
+# The percentage of instances where my encoding is better
+nrow(merged[merged$time.y < merged$time.x,])/nrow(merged)
+summary(merged$difference)
+
+ggplot(merged, aes(x = time.x, y = time.y)) +
+  geom_point() +
+  geom_abline(slope = 1, intercept = 0) +
+#  scale_x_continuous(trans = log2_trans()) +
+#  scale_y_continuous(trans = log2_trans()) +
+  xlab("Inference time for the encoding by Sang et al.") +
+  ylab("Inference time for the conditional encoding")
+
+ggplot(df, aes(x = time, y = encoding)) +
+  geom_boxplot()
+
+ggplot(merged, aes(x = difference)) +
+  geom_histogram(binwidth = 1)
+
+ggplot(merged, aes(x = relative.difference)) +
+  geom_histogram(binwidth = 0.1) +
+  scale_x_continuous(breaks = round(seq(min(merged$relative.difference, na.rm = TRUE), max(merged$relative.difference, na.rm = TRUE), by = 0.5), 1))
+
+quantile(merged$relative.difference, 0.90, na.rm = TRUE)
+quantile(merged$relative.difference, 0.10, na.rm = TRUE)
+summary(merged$relative.difference)
+median(merged$relative.difference, na.rm = TRUE)
+# The running time of a typical instance is reduced by 74%
+
+# TL;DR: Almost never worse. Usually better by only a small amount, but sometimes significantly better.

### 2020-06-21 experiments/dne2cnf.py
Some work on DNE->CNF conversion

@@ -2,7 +2,7 @@ import itertools
 import os
 import re
 
-def convert(text):
+def my_encoding(text):
     names = []
     clauses = []
     def name2int(name):
@@ -30,6 +30,63 @@ def convert(text):
     goal = clauses[-1].split(' ')[1]
     return 'p cnf {} {}\n'.format(len(names), 1) + '{} 0\n'.format(goal) + '\n'.join(clauses)
 
+def darwiche_encoding(text):
+    next_var_index = 1
+    lambda_names = {}
+    def get_lambda_index(variable, value):
+        index = lambda_names[(variable, value)]
+        return str(index + 1)
+    def probability_conditions(negation_pattern, parents):
+        conditions = []
+        for negate, parent in zip(negation_pattern, parents):
+            conditions.append(get_lambda_index(parent, 'false' if negate else 'true'))
+        return conditions
+
+    clauses = []
+    for node in re.finditer(r'\nnode (\w+)', text):
+        end_of_name = node.end()
+        name = node.group(1)
+
+        states = re.search(r'states = \(([^()]*)\)', text[end_of_name:]).group(1)
+        assert(states == 'true, false')
+        states = states.split(', ')
+        for state in states:
+            lambda_names[(name, state)] = next_var_index
+            next_var_index += 1
+        # Clause (1)
+        clauses.append(' '.join([get_lambda_index(name, state) for state in states]) + ' 0')
+        # Clause (2)
+        for state1, state2 in itertools.combinations(states, 2):
+            clauses.append('-{} -{} 0'.format(get_lambda_index(name, state1),
+                                              get_lambda_index(name, state2)))
+
+        parents = [s for s in re.search(r'parents = \(([^()]*)\)', text[end_of_name:]).group(1).split(', ')
+                   if s != '']
+        # Parse only the numbers and discard every other one
+        probs_str = re.search(r'probs = ([^;]*);', text[end_of_name:]).group(1)
+        probs = [p for p in re.split(r'[, ()\n\t]+', probs_str) if p != ''][0::2]
+        assert(len(probs) == 2**len(parents))
+        possible_negations = itertools.product([False, True], repeat=len(parents))
+        weight_lines = zip(possible_negations, probs)
+        for negation_pattern, prob in weight_lines: # for each theta variable
+            for value in states:
+                conditions = probability_conditions(negation_pattern, parents)
+                # Clause (3)
[…]

### 2020-07-01 paper.tex
Some work on DNE->CNF conversion
Rearrange experimental data

@@
 \begin{itemize}
+\item For both DQMR and Plan Recognition, I will need two DNE $\to$ CNF
+  encoders. I should formalise the algorithms behind them as well, since they
+  are described informally.
 \item Look into ways to theoretically justify the performance benefits. Some
@@
   \begin{itemize}
-  \item Darwiche \cite{DBLP:conf/kr/Darwiche02}
-  \item \hl{Sang et al.} \cite{DBLP:conf/aaai/SangBK05}
-  \item \hl{mine}
-  \end{itemize}
+  \item \texttt{-d02} \cite{DBLP:conf/kr/Darwiche02}
+  \item \texttt{-sbk05} \cite{DBLP:conf/aaai/SangBK05}
+  \item \texttt{-cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
+  \item \texttt{-cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
+  \item mine
+  \end{itemize}
+  All except mine are from Ace
+  3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be compiled
+  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
+  \texttt{-noEclause} (i.e., only use standard syntax) flags. Ace also has its
+  own benchmarks (with evidence) but they're still binary.
 \item Datasets\footnote{There might be more at
@@
     \item \hl{Grid networks}: computing marginal probability of the last node in
-      the grid.
-    \item Plan recognition problems.
-    \item Deterministic quick medical reference.
+      the grid (DNE).
+    \item Plan recognition problems (DNE + XML).
+    \item Deterministic quick medical reference (DNE + XML).
     \end{itemize}
@@
     randomly chosen node (so, repeat at least ten times).
-  \item non-binary Bayesian networks?
+  \item Bayesian networks \emph{with evidence} (some binary, some non-binary)
+    \begin{itemize}
+    \item \texttt{2004-pgm}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
+    \item \texttt{2005-ijcai}: XDSL/NET/Hugin + inst (\cite{DBLP:conf/ijcai/ChaviraD05})
+    \item \texttt{2006-ijar}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
+    \end{itemize}
   \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}

### 2020-07-01 paper.tex
Add weights to the Ace encodings

@@
   \begin{itemize}
-  \item \hl{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
+  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
     multiplicativity of BAs in different words) (with optimal settings)
@@
     \begin{itemize}
-    \item \hl{Grid networks}: computing marginal probability of the last node in
+    \item Grid networks: computing marginal probability of the last node in
       the grid (DNE).
-    \item Plan recognition problems (DNE + XML).
-    \item Deterministic quick medical reference (DNE + XML).
+    \item Plan recognition problems (DNE + inst).
+    \item Deterministic quick medical reference (DNE + inst).
     \end{itemize}
@@
     randomly chosen node (so, repeat at least ten times).
-  \item Bayesian networks \emph{with evidence} (some binary, some non-binary)
+  \item Bayesian networks available with Ace (some binary, some non-binary)
     \begin{itemize}

### 2020-07-01 experiments/dne2cnf.py

@@ -2,10 +2,12 @@ import itertools
 import os
 import random
 import re
+import subprocess
 import sys
 import xml.etree.ElementTree as ET
 from optparse import OptionParser
 
+ACE = ['./ace/compile', '-encodeOnly', '-noEclause']
 names = []
 def name2int(name):
     return str(names.index(name)+1)
@@ -35,8 +37,6 @@ def encode_dne(filename):
             conditions = list(probability_conditions(negation_pattern, parents))
             clauses.append('w ' + ' '.join([name2int(name)] + conditions + [prob]))
     return clauses
-# TODO: formatting things such as in the line above should be done outside this function
-# This should just return a list of clauses (most likely in string form)
 
 def encode_inst_evidence(filename):
     clauses = []
@@ -50,43 +50,46 @@ def encode_inst_evidence(filename):
         clauses.append(sign + name2int(inst.attrib['id']) + ' 0')
     return clauses
 
-def encode(network, evidence=None, last_node_as_goal=False):
+def encode(network, evidence=None):
     clauses = encode_dne(network)
-    goal = clauses[-1].split(' ')[1] if last_node_as_goal else name2int(random.choice(names))
     if evidence:
         evidence_clauses += encode_inst_evidence(evidence)
-        num_clauses = len(evidence_clauses) + 1
+        num_clauses = len(evidence_clauses)
     else:
+        clauses.append(clauses[-1].split(' ')[1] + ' 0')
         num_clauses = 1
-    clauses.append(goal + ' 0')
     return 'p cnf {} {}\n'.format(len(names), num_clauses) + '\n'.join(clauses) + '\n'
 
-# Let's start with the Grid networks. Other datasets require computing all/most
-# marginals and it's not clear what the CNF encoding represents.
-# Grid/{Dne,Cnf}/{Ratio_50,Ratio_75,Ratio_90}/*
-# DQMR/{qmr-100,qmr-50,qmr-60,qmr-70}/*.{dne,cnf} (ignore cnfs that are not coupled with dnes)
-# Plan_Recognition/*.{cnf,dne}
-
-# directory = 'data/Grid/'
-# for ratio in ['Ratio_50/', 'Ratio_75/', 'Ratio_90/']:
-#     for filename in os.listdir(directory + ratio):
-#         if not filename.endswith('.dne'):
-#             continue
-#         with open(directory + ratio + filename) as f:
-#             encoding = my_encoding(f.read())
[…]

### 2020-07-02 paper.tex
Ditto for Plan Recognition

@@
   with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
-  \texttt{-noEclause} (i.e., only use standard syntax) flags. Ace also has its
-  own benchmarks (with evidence) but they're still binary.
+  \texttt{-noEclause} (i.e., only use standard syntax) flags.
 \item Datasets\footnote{There might be more at
@@
   \end{itemize}
+\item In preliminary results, the SBK05 encoding gives the wrong asnwer in 60
+  QMR instances (all with evidence files). Sometimes that answer is $\gg 1$.
+\item Similarly, cd06 is supposed to be the fastest, but seems to be one of the
+  slowest (along with cd05). Perhaps the best encoding for arithmetic circuits
+  has very little to do with the best encoding for CNF WMC solvers?
 \end{itemize}

### 2020-07-02 experiments/parse.py

@@ -31,6 +31,8 @@ data += parse_dir('results/DQMR/qmr-100/', {'dataset': 'DQMR-100'})
 data += parse_dir('results/DQMR/qmr-50/', {'dataset': 'DQMR-50'})
 data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
 data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
+data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
+data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
 
 fieldnames = set()
 for d in data:

### 2020-07-03 paper.tex
The 2004 dataset seems to be working

@@
   has very little to do with the best encoding for CNF WMC solvers?
+\item When the Bayesian network has an evidence file, we compute the probability
+  of evidence. Otherwise, we pick the last (i.e., last to be mentioned) node in
+  the Bayesian network to be the goal. This applies to the Grid data set (as
+  intended) and also to two instances of Plan Reconstruction. Check if these two
+  answers match.
 \end{itemize}

### 2020-07-03 experiments/analyse.R

@@ -4,7 +4,6 @@ require(dplyr)
 require(maditr)
 
 df <- read.csv("results.csv", header = TRUE, sep = ",")
-
 answers <- dcast(data = df, formula = instance ~ encoding, fun.aggregate = sum, value.var = "answer")
 time <- dcast(data = df, formula = instance ~ encoding, fun.aggregate = sum, value.var = "time")
 

### 2020-07-03 experiments/encode.py

@@ -34,7 +34,7 @@ def encode_dne(text):
                    for s in re.search(r'parents = \(([^()]*)\)', text[end_of_name:]).group(1).split(', ') if s != '']
         # Parse only the numbers and discard every other one
         probs_str = re.search(r'probs = ([^;]*);', text[end_of_name:]).group(1)
-        probs = [p for p in re.split(r'[, ()\n\t]+', probs_str) if p != ''][0::2]
+        probs = [p for p in re.split(r'[, ()\n\t]+', probs_str) if p != ''][::2]
         clauses += construct_cpt(name, parents, probs)
     return clauses
 
@@ -48,12 +48,15 @@ def encode_net(text):
         assert(states == '"false" "true"')
     for potential in re.finditer(r'\npotential([^{]*){([^}]*)}', text):
         header = re.findall(r'\w+', potential.group(1))
+        # First false, then true
         probabilities = re.findall(r'\d+\.?\d*', potential.group(2))[1::2]
         assert(len(probabilities) == 2**(len(header) - 1))
-        clauses += construct_cpt(header[0], header[1:], probabilities)
+        clauses += construct_cpt(header[0], header[1:], probabilities, reverse=True)
     return clauses
 
 def encode_inst_evidence(filename):
+    if filename is None:
+        return []
     clauses = []
     for inst in ET.parse(filename).findall('inst'):
         assert(inst.attrib['value'] in ['true', 'false'])
@@ -67,13 +70,15 @@ def encode(network, evidence):
         text = f.read()
         clauses = encode_dne(text) if network.endswith('.dne') else encode_net(text)
 
-    if evidence:
-        evidence_clauses = encode_inst_evidence(evidence)
+    # Add a goal clause if necessary
+    evidence_clauses = encode_inst_evidence(evidence)
+    if evidence_clauses:
         num_clauses = len(evidence_clauses)
         clauses += evidence_clauses
     else:
         clauses.append(clauses[-1].split(' ')[1] + ' 0')
         num_clauses = 1
+
     encoding = 'p cnf {} {}\n'.format(len(names), num_clauses) + '\n'.join(clauses) + '\n'
     with open(network + '.cnf', 'w') as f:
         f.write(encoding)
@@ -107,7 +112,7 @@ def encode_using_ace(network, evidence, encoding):
         weights_line += [weights[literal], weights[-literal]]
     encoding = 'c weights ' + ' '.join(weights_line) + '\n'
[…]

### 2020-07-03 experiments/parse.py

@@ -33,6 +33,9 @@ data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
 data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
 data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
 data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
+data += parse_dir('results/2004-pgm/', {'dataset': '2004-PGM'})
+data += parse_dir('results/2005-ijcai/', {'dataset': '2005-IJCAI'})
+data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
 
 fieldnames = set()
 for d in data:

### 2020-07-03 experiments/analyse.R
File format conversion (and updated data analysis)

@@ -3,56 +3,33 @@ require(scales)
 require(dplyr)
 require(maditr)
 
+TIMEOUT <- 1
 df <- read.csv("results.csv", header = TRUE, sep = ",")
+df$time[df$time > TIMEOUT] <- TIMEOUT
+df$time[is.na(df$time)] <- TIMEOUT
 answers <- dcast(data = df, formula = instance ~ encoding, fun.aggregate = sum, value.var = "answer")
-time <- dcast(data = df, formula = instance ~ encoding, fun.aggregate = sum, value.var = "time")
+time <- dcast(data = df, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = "time")
 
-answers[answers$db20 - answers$d02 > 0.01,]
-interesting <- answers[answers$db20 - answers$sbk05 > 0.01,]
+# Where answers don't match
+interesting <- answers[abs(answers$db20 - answers$cd05) > 0.01,]
+answers[abs(answers$db20 - answers$cd06) > 0.01,]
+answers[abs(answers$db20 - answers$d02) > 0.01,]
+answers[abs(answers$db20 - answers$sbk05) > 0.01,]
 
-# ================= older stuff =======================
+# Proportion of instances where my encoding is the best
+time$min <- apply(time, 1, min)
+sum(time$db20 == time$min)/nrow(time)
 
-sang.data <- df[df$encoding == "sang",]
-conditional.data <- df[df$encoding == "conditional",]
+# Proportion unsolved
+sum(is.na(answers$cd05))/nrow(answers)
+sum(is.na(answers$cd06))/nrow(answers)
+sum(is.na(answers$d02))/nrow(answers)
+sum(is.na(answers$db20))/nrow(answers)
+sum(is.na(answers$sbk05))/nrow(answers)
 
-# Numbers of unsolved instances (incomplete)
-sum(is.na(sang.data$answer))
-sum(is.na(conditional.data$answer))
-
-summary(sang.data$time)
-summary(conditional.data$time)
-
-# NOTE: Some timed out instances are omitted from this
-merged <- merge(sang.data, conditional.data, by = "instance")
-merged$difference <- merged$time.x - merged$time.y
-merged$relative.difference <- merged$difference / merged$time.x
-# The percentage of instances where my encoding is better
-nrow(merged[merged$time.y < merged$time.x,])/nrow(merged)
-summary(merged$difference)
-
-ggplot(merged, aes(x = time.x, y = time.y)) +
[…]

### 2020-07-03 experiments/encode.py

@@ -65,9 +65,10 @@ def encode_inst_evidence(filename):
     return clauses
 
 def encode(network, evidence):
-    assert(network.endswith('.dne') or network.endswith('.net'))
+    assert(network.endswith('.dne') or network.endswith('.net') or network.endswith('.hugin'))
     with open(network) as f:
         text = f.read()
+        # Hugin and NET are equivalent formats
         clauses = encode_dne(text) if network.endswith('.dne') else encode_net(text)
 
     # Add a goal clause if necessary
@@ -119,7 +120,7 @@ def encode_using_ace(network, evidence, encoding):
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(
         description='Encode Bayesian networks into instances of weighted model counting (WMC)')
-    parser.add_argument('network', metavar='network', help='a Bayesian network (in either DNE or NET format)')
+    parser.add_argument('network', metavar='network', help='a Bayesian network (in one of DNE/NET/Hugin formats)')
     parser.add_argument('encoding', choices=['d02', 'sbk05', 'cd05', 'cd06', 'db20'], help='a WMC encoding')
     parser.add_argument('-e', dest='evidence', help="evidence file (in the INST format)")
     args = parser.parse_args()

### 2020-07-04 paper.tex
File format conversion (and updated data analysis)
2004-pgm dataset

@@
   set.
+\item Are they called Boolean Bayesian networks or binary Bayesian networks?
 \end{itemize}
@@
   Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
-  (highlighted the initial setup, can expand later):
   \begin{itemize}
@@
     \begin{itemize}
-    \item Grid networks: computing marginal probability of the last node in
-      the grid (DNE).
-    \item Plan recognition problems (DNE + inst).
-    \item Deterministic quick medical reference (DNE + inst).
-    \end{itemize}
-    For the last two, the task can be to calculate the marginal probability of a
-    randomly chosen node (so, repeat at least ten times).
-  \item Bayesian networks available with Ace (some binary, some non-binary)
-    \begin{itemize}
-    \item \texttt{2004-pgm}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
-    \item \texttt{2005-ijcai}: XDSL/NET/Hugin + inst (\cite{DBLP:conf/ijcai/ChaviraD05})
-    \item \texttt{2006-ijar}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
+    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
+      deterministic),
+    \item Plan recognition (problems),
+    \item Deterministic quick medical reference (what do the numbers mean? the
+      README doesn't say).
+    \end{itemize}
+  \item Bayesian networks available with Ace
+    \begin{itemize}
+    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06}
+    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
+      files have their own citation data that I should probably extract. This is
+      the only dataset that has some non-binary networks.
+    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06}
     \end{itemize}
@@
   the Bayesian network to be the goal. This applies to the Grid data set (as
-  intended) and also to two instances of Plan Reconstruction. Check if these two
-  answers match.
+  intended) and also to two instances of Plan Reconstruction and roughly half of
+  2004-PGM.
 \end{itemize}

### 2020-07-04 experiments/analyse.R

@@ -11,12 +11,13 @@ answers <- dcast(data = df, formula = instance ~ encoding, fun.aggregate = sum, 
 time <- dcast(data = df, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = "time")
 
 # Where answers don't match
-interesting <- answers[abs(answers$db20 - answers$cd05) > 0.01,]
+interesting <- answers[abs(answers$db20 - answers$sbk05) > 0.01,]
 answers[abs(answers$db20 - answers$cd06) > 0.01,]
 answers[abs(answers$db20 - answers$d02) > 0.01,]
 answers[abs(answers$db20 - answers$sbk05) > 0.01,]
 
 # Proportion of instances where my encoding is the best
+# TODO: ignore rows with all NAs
 time$min <- apply(time, 1, min)
 sum(time$db20 == time$min)/nrow(time)
 

### 2020-07-04 experiments/encode.py

@@ -7,6 +7,7 @@ import xml.etree.ElementTree as ET
 
 ACE = ['./ace/compile', '-encodeOnly', '-noEclause']
 names = []
+values_per_variable = {}
 def name2int(name):
     return str(names.index(name)+1)
 
@@ -14,11 +15,21 @@ def probability_conditions(negation_pattern, parents):
     for negate, parent in zip(negation_pattern, parents):
         yield ('-' if negate else '') + name2int(parent)
 
-def construct_cpt(name, parents, probabilities, reverse=False):
+def construct_binary_cpt(name, parents, probabilities, reverse=False):
     assert(len(probabilities) == 2**len(parents))
     possible_negations = itertools.product([True, False] if reverse else [False, True], repeat=len(parents))
     return ['w ' + ' '.join([name2int(name)] + list(probability_conditions(negation_pattern, parents)) + [prob])
             for negation_pattern, prob in zip(possible_negations, probabilities)]
+
+# def construct_general_cpt(name, parents, probabilities):
+#   parent_patterns = itertools.product(values_per_variable[p] for p in parents)
+#   clauses = []
+#   i = 0
+#   for pattern in parent_patterns:
+#     for value in values_per_variable[name]:
+#       conditions = [name2int((parent, parent_value)) for parent, parent_value in zip(parents, parent_patterns)]
+#       clauses.append('w' + ' '.join([name2int((name, value))] + conditions + [probabilities[i]]))
+#       i += 1
 
 def encode_dne(text):
     clauses = []
@@ -43,15 +54,31 @@ def encode_net(text):
     for node in re.finditer(r'\nnode (\w+)', text):
         end_of_name = node.end()
         name = node.group(1).lstrip().rstrip()
+
+        # states = re.search(r'states = \(\s*"([^()]*)"\s*\)', text[end_of_name:]).group(1).split(' " ')
+        # if len(states) == 2:
+        #   assert(states == ['false', 'true'])
         names.append(name)
+        # else:
+        #   names += [(name, v) for v in states]
+        #   values_per_variable[name] = states
+        #   # Add all the extra rules
+        #   clauses.append(' '.join(name2int((name, value)) for value in states) + ' 0')
+        #   for v1, v2 in itertools.combinations(values, 2):
+        #     clauses.append('-{} -{} 0'.format(name2int((name, v1)), name2int((name, v2))))
+
+        # TODO: replace the below with the above
[…]

### 2020-07-05 paper.tex
Non-Boolean Bayesian networks: version 1

@@
 \usepackage{complexity}
-\usepackage{soul} % temp
+\usepackage{soul}
 
@@
 \begin{itemize}
-\item For both DQMR and Plan Recognition, I will need two DNE $\to$ CNF
-  encoders. I should formalise the algorithms behind them as well, since they
-  are described informally.
 \item Look into ways to theoretically justify the performance benefits. Some
@@
   paper, then at least for slides. Use the framework to check its correctness.
-\item Along with comparing the (3?) encodings, I could also compare this
-  to using ADDs directly on Bayesian networks.
 \item[F] Give a concrete example of something impossible to represent using WMC.
@@
   deduced, but the algorithm itself can support weights that are not necessarily
-  probabilities.
+  probabilities. Ditto for non-binary values (the shorter version).
 \item Rename the repository into `conditional-wmc'.
@@
   of evidence. Otherwise, we pick the last (i.e., last to be mentioned) node in
-  the Bayesian network to be the goal. This applies to the Grid data set (as
+  the Bayesian network to be the goal (the positive value for binary networks
+  and the last value in the general case). This applies to the Grid data set (as
   intended) and also to two instances of Plan Reconstruction and roughly half of
   2004-PGM.
+\item Bayesian networks are often solved in a compile once, query many times
+  fashion. This can be achieved using ADDMC by selecting a subset $S$ of
+  variable we may want to query over and running ADDMC while excluding $S$ from
+  variable elimination/projection/$\exists$.
 \end{itemize}
@@
 
-\section{How to represent a Bayesian network}
-
-Let $G = (V, E)$ be a DAG, and let $(X_v)_{v \in V}$ be the discrete random
-variables (RVs). Let $(d_v)_{v \in V}$ denote the numbers of values that each RV
-can take and assume that $d_v$ is a power of two for all $v \in V$.
-\begin{enumerate}
-\item For each $v \in V$, let $A_v$ be a set of $\log_2 d_v$ Boolean variables.
-  (If $d_v$ is not a power of two, we would need to manually forbid each illegal
-  value, e.g., by adding formulas such as $\neg(x_1 \land x_2 \land x_3 \land
-  \neg x_4)$ to the theory. Alternatively, we could set their probability to
-  zero, but the former should be better.)
-\item For $v \in V$:
-  \begin{enumerate}
-  \item If $v$ has no parents, we can directly provide a probability measure on
-    $\mathcal{F}(A_v)$.
-  \item Otherwise, we need a probability measure on
-    \[
-      \mathcal{F} \left( A_v \cup \bigcup_{(u, v) \in E} A_u \right).
-    \]
-    For any element $a_u \land a_v$ in this free Boolean algebra such that $a_v
-    \in A_v \setminus \{ 0, 1 \}$, and $a_u \not\in A_v$, we can set
-    \[
-      m(a_u \land a_v) = \Pr(a_v \mid a_u)\Pr(a_u).
-    \]
-  \end{enumerate}
-\item When a \#\SAT{} algorithm asks for the weight of a model $\bigwedge_{v \in
-    V} l_v$, split it into segments that correspond to each leaf, take the
-  probabilities from each such node, and multiply them. NB: The segments will
-  intersect, e.g., with
+\section{Representation of conditional probability tables}
+
+The probability of a variable with $n$ values $x_1, \dots, x_n$ (whether
+conditioned on something or not) can be represented with an ADD of size
+$\Theta(n^2)$ by representing each of $\Pr(x_1), \Pr(x_2 \mid x_1), \dots,
+\Pr(x_n \mid x_1, \dots, x_{n-1})$ by a separate ADD. For example, if $n=3$, the
+last of the three ADDs would look like this
 \[
   \begin{tikzpicture}
-      \node[latent] (C) {$C$};
-      \node[latent, below left = of C] (A) {$A$};
-      \node[latent, below right = of C] (B) {$B$};
-      \node[latent, right = 2 of C] (D) {$D$};
-      \edge {C} {A, B};
+    \node[ellipse,draw] (x3) {$x_3$};
+    \node[ellipse,draw,below left = of x3] (x21) {$x_2$};
+    \node[ellipse,draw,below right = of x3] (x22) {$x_2$};
+    \node[ellipse,draw,below = of x21] (x11) {$x_1$};
+    \node[ellipse,draw,below = of x22] (x12) {$x_1$};
+    \node[rectangle,draw,below = of x11] (n2) {$0.7$};
+    \node[rectangle,draw,left = of n2] (n1) {$0$};
+    \node[rectangle,draw,below = of x12] (n3) {$0.3$};
+    \node[rectangle,draw,right = of n3] (n4) {$1$};
+
+    \draw (x3) edge (x21);
+    \draw (x21) edge (n1);
+    \draw (x11) edge (n1);
+    \draw[dashed] (x21) edge (x11);
+    \draw[dashed] (x11) edge (n2);
+
+    \draw[dashed] (x3) edge (x22);
+    \draw[dashed] (x22) edge (x12);
+    \draw[dashed] (x12) edge (n3);
+    \draw (x22) edge (n4);
+    \draw (x12) edge (n4);
   \end{tikzpicture}
 \]
-  $a \land b \land c \land d$ will be split into $(a \land c) \land (b \land c)
-  \land d$.
-\end{enumerate}
-
-\subsection{Bayesian networks as Boolean algebras}
-
-\begin{table}
-  \caption{Examples of how Bayesian networks encode as Boolean algebras. Here,
-    $A$ denotes $\mathcal{F}\{a\}$ and $AB$ denotes $\mathcal{F}\{a, b\}$.}
-  \centering
-  \begin{tabular}{cc}
-    \toprule
-    Bayesian network & Boolean algebra \\
-    \midrule \\[-1.3em]
-    \begin{tikzpicture}[baseline={(A.base)}]
-      \node[latent] (A) {$A$};
-    \end{tikzpicture} & $A$ \\
-    \midrule \\[-1.3em]
-    \begin{tikzpicture}[baseline={(A.base)}]
-      \node[latent] (A) {$A$};
-      \node[latent,right =of A] (B) {$B$};
-    \end{tikzpicture} & $A + B$ \\
-    \midrule \\[-1.3em]
-    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
-      \node[latent] (A) {$A$};
-      \node[latent,below =of A] (B) {$B$};
-      \edge {A} {B};
-    \end{tikzpicture} & $AB$ \\
-    \midrule \\[-1.3em]
-    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
-      \node[latent] (A) {$A$};
-      \node[latent,below =of A] (B) {$B$};
-      \node[latent,right =of A] (C) {$C$};
-      \edge {A} {B};
-    \end{tikzpicture} & $B +_A C$ \\
-    \midrule \\[-1.3em]
-    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
-      \node[latent] (A) {$A$};
-      \node[latent,below =of A] (B) {$B$};
-      \node[latent,right =of A] (C) {$C$};
-      \node[latent,below =of C] (D) {$D$};
-      \edge {A} {B};
-      \edge {C} {D};
-    \end{tikzpicture} & $B +_{A+C} D$ \\
-    \midrule \\[-1.3em]
-    \begin{tikzpicture}[baseline={($(A.base)!.5!(B.base)$)}]
-      \node[latent] (A) {$A$};
-      \node[latent,below left =of A] (B) {$B$};
-      \node[latent,below right=of A] (C) {$C$};
-      \node[latent,right = 2 of A] (D) {$D$};
-      \node[latent,below =of D] (E) {$E$};
-      \edge {A} {B,C};
-      \edge {D} {E};
-    \end{tikzpicture} & $B +_{A+D} C +_{A+D} E$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-To turn a Bayesian network into a Boolean algebra, run $f(\{ v \in V \mid
-\mathrm{outdeg}(v) = 0 \})$, where $f$ works as follows on an arbitrary $A
-\subseteq V$:
-\begin{enumerate}
-\item $S \gets \{ u \mid (u, v) \in E\text{, } v \in A \}$ (i.e., $S$ is the set
-  of parents of the elements in $A$).
-\item If $S = \emptyset$, return $\sum A$ (a coproduct).
-\item Otherwise, return $\sum_{f(S)} A$ (a pushout).
-\end{enumerate}
+Such an ADD for $x_n$ has $2n+3$ nodes and $4n-2$ edges. The same information
+can be represented in textual form as
+\begin{align*}
+  &\texttt{w 3 1 0} \\
+  &\texttt{w 3 2 0} \\
+  &\texttt{w 3 -1 -2 0.7}
+\end{align*}
 

### 2020-07-05 experiments/ADDMC/counting/interface/util.hpp

@@ -80,8 +80,8 @@ const int_t DUMMY_MAX_INT = std::numeric_limits<int_t>::max();
 
 const std::string DUMMY_STR = "DUMMY_STR";
 
-const std::string DOT_DIR = "../tests/";
-const std::string TEST_DIR = "../tests/test/";
+const std::string DOT_DIR = "tests/";
+const std::string TEST_DIR = "tests/test/";
 
 /* namespaces *****************************************************************/
 

### 2020-07-05 experiments/encode.py

@@ -6,6 +6,15 @@ import subprocess
 import xml.etree.ElementTree as ET
 
 ACE = ['./ace/compile', '-encodeOnly', '-noEclause']
+NODE_RE = r'\nnode (\w+)'
+NET_STATES_RE = r'states = \(\s*"([^()]*)"\s*\)'
+DNE_STATES_RE = r'states = \(([^()]*)\)'
+PARENTS_RE = r'parents = \(([^()]*)\)'
+PROBS_RE = r'probs = ([^;]*);'
+POTENTIAL_RE = r'\npotential([^{]*){([^}]*)}'
+NUMBER_RE = r'\d+\.?\d*'
+PROB_SPLITTER_RE = r'[, ()\n\t]+'
+
 names = []
 values_per_variable = {}
 def name2int(name):
@@ -21,64 +30,64 @@ def construct_binary_cpt(name, parents, probabilities, reverse=False):
     return ['w ' + ' '.join([name2int(name)] + list(probability_conditions(negation_pattern, parents)) + [prob])
             for negation_pattern, prob in zip(possible_negations, probabilities)]
 
-# def construct_general_cpt(name, parents, probabilities):
-#   parent_patterns = itertools.product(values_per_variable[p] for p in parents)
-#   clauses = []
-#   i = 0
-#   for pattern in parent_patterns:
-#     for value in values_per_variable[name]:
-#       conditions = [name2int((parent, parent_value)) for parent, parent_value in zip(parents, parent_patterns)]
-#       clauses.append('w' + ' '.join([name2int((name, value))] + conditions + [probabilities[i]]))
-#       i += 1
+def construct_general_cpt(name, parents, probabilities):
+    parent_patterns = itertools.product(*[values_per_variable[p] for p in parents])
+    clauses = []
+    i = 0
+    for pattern in parent_patterns:
+        probability_denominator = 1
+        probability = 0
+        conditions = [name2int((parent, parent_value)) for parent, parent_value in zip(parents, pattern)]
+        for j in range(len(values_per_variable[name])):
+            current_value = name2int((name, values_per_variable[name][j]))
+            previous_values = [name2int((name, value)) for value in values_per_variable[name][:j]]
+            clauses += ['w {} {} 0'.format(current_value, previous_value) for previous_value in previous_values]
+            negated_previous = ['-{}'.format(v) for v in previous_values]
+            probability = float(probabilities[i]) / probability_denominator
+            probability_denominator *= 1 - probability
[…]

### 2020-07-07 paper.tex
Some automatic tests

@@
   set.
-\item Are they called Boolean Bayesian networks or binary Bayesian networks?
+\item There is a new version of ADDMC.
 \end{itemize}
@@
   variable elimination/projection/$\exists$.
+\item \texttt{cd05} relaxes the encoding so much that extra models become
+  possible. They are supposed to be filtered out by the algorithm, but mine
+  can't do that because it doesn't deal with models. Same for \texttt{cd06}
+  because it's based on \texttt{cd05}.
+\item For ground ProbLog, we can encode a program
+\begin{verbatim}
+p :: a :- b
+q :: a :- c
+\end{verbatim}
+  into $P(a \mid b)=p$, $P(a \mid c)=q$ instead of having clauses $b \Rightarrow
+  a$, $c \Rightarrow a$. Some logical structure is likely to remain.
+\item Potential criticism may be that this is a step backwards and doesn't allow
+  us to use SAT-based techniques for probabilistic inference. However, they can
+  still be used for the 'theory+query' part.
+\item We don't compare 'compile times' because our encoding time is linear, so
+  we would easily beat everyone else.
+\item The claim behind this paper is that allowing for conditional probabilities
+  in the context of weighted model counting seems to be a good idea. Bayesian
+  networks and ADDMC are only particular examples. This should also work with
+  Cachet.
 \end{itemize}
@@
 \end{align*}
+The encoding weights depend on the probabilities in the CPT as in
+\[
+  w(x_n \mid \neg x_1, \dots, \neg x_{n-1}) = \Pr(X = x_n) \prod_{i=1}^{n-1}
+  \frac{1}{1 - w(x_i \mid \neg x_1, \dots, \neg x_{i-1})}.
+\]
 

### 2020-07-08 experiments/encode.py
Tests with evidence

@@ -7,120 +7,101 @@ import xml.etree.ElementTree as ET
 
 ACE = ['./ace/compile', '-encodeOnly', '-noEclause']
 NODE_RE = r'\nnode (\w+)'
-NET_STATES_RE = r'states = \(\s*"([^()]*)"\s*\)'
-DNE_STATES_RE = r'states = \(([^()]*)\)'
 PARENTS_RE = r'parents = \(([^()]*)\)'
 PROBS_RE = r'probs = ([^;]*);'
 POTENTIAL_RE = r'\npotential([^{]*){([^}]*)}'
 NUMBER_RE = r'\d+\.?\d*'
 PROB_SPLITTER_RE = r'[, ()\n\t]+'
+STATES_RE = {'dne': r'states = \(([^()]*)\)', 'net': r'states = \(\s*"([^()]*)"\s*\)'}
+STATE_SPLITTER_RE = {'net': r'"\s*"', 'dne': r',\s*'}
 
-names = []
+variables = []
 values_per_variable = {}
-def name2int(name):
-    return str(names.index(name)+1)
+def bayesian2logical(node, value):
+    if (node, value) in variables:
+        return str(variables.index((node, value)) + 1)
+    index = next(i for i, (n, v) in enumerate(variables) if n == node)
+    return '-{}'.format(index + 1)
 
-def probability_conditions(negation_pattern, parents):
-    for negate, parent in zip(negation_pattern, parents):
-        yield ('-' if negate else '') + name2int(parent)
-
-def construct_binary_cpt(name, parents, probabilities, reverse=False):
-    assert(len(probabilities) == 2**len(parents))
-    possible_negations = itertools.product([True, False] if reverse else [False, True], repeat=len(parents))
-    return ['w ' + ' '.join([name2int(name)] + list(probability_conditions(negation_pattern, parents)) + [prob])
-            for negation_pattern, prob in zip(possible_negations, probabilities)]
-
-def construct_general_cpt(name, parents, probabilities):
+def construct_cpt(name, parents, probabilities):
     parent_patterns = itertools.product(*[values_per_variable[p] for p in parents])
     clauses = []
     i = 0
     for pattern in parent_patterns:
         probability_denominator = 1
         probability = 0
-        conditions = [name2int((parent, parent_value)) for parent, parent_value in zip(parents, pattern)]
+        conditions = [bayesian2logical(parent, parent_value) for parent, parent_value in zip(parents, pattern)]
         for j in range(len(values_per_variable[name])):
[…]

### 2020-07-09 paper.tex
Tests with evidence
Fix a bug related to zero-probability values

@@
   Cachet.
+\item For the ProbLog $\to$ WMC conversion, check out this
+  guy.\footnote{\url{https://users.ics.aalto.fi/ttj/}}
 \end{itemize}
@@
 \end{align*}
-The encoding weights depend on the probabilities in the CPT as in
-\[
-  w(x_n \mid \neg x_1, \dots, \neg x_{n-1}) = \Pr(X = x_n) \prod_{i=1}^{n-1}
-  \frac{1}{1 - w(x_i \mid \neg x_1, \dots, \neg x_{i-1})}.
-\]
+The encoding weights depend on the probabilities in the CPT as follows. For each
+value $x_n$, if $\Pr(X = x_n) = 0$, then $w(x_n) = 0$. Otherwise, let $I_n = \{ 1
+\le i \le n - 1 \mid \Pr(X = x_i) \ne 0 \}$. Then
+\[
+  w \left( x_n \;\middle|\; \bigwedge_{i \in I_n} \neg x_i \right) = \Pr(X =
+  x_n) \prod_{i \in I_n} \frac{1}{1 - w \left( x_i \;\middle|\; \bigwedge_{j \in
+        I_i} \neg x_j \right)}.
+\]
+All of these weights/probabilities may have other conditions that come from the
+structure of the Bayesian network.
 

### 2020-07-09 experiments/encode.py

@@ -36,8 +36,13 @@ def construct_cpt(name, parents, probabilities):
             if current_value.startswith('-'):
                 i += 1
                 continue
-            previous_values = [bayesian2logical(name, value) for value in
-                               values_per_variable[name][:j]] if len(values_per_variable[name]) > 2 else []
+            if probabilities[i] == '0':
+                clauses.append('w {} {}'.format(' '.join([current_value] + conditions), probabilities[i]))
+                continue
+            previous_values = [bayesian2logical(name, value)
+                               for k, value in enumerate(values_per_variable[name][:j])
+                               if probabilities[i-len(values_per_variable[name][:j])+k] != '0'] if len(
+                                       values_per_variable[name]) > 2 else []
             clauses += ['w {} {} 0'.format(current_value, previous_value) for previous_value in previous_values]
             negated_previous = [(v[1:] if v.startswith('-') else '-' + v) for v in previous_values]
             probability = float(probabilities[i]) / probability_denominator
@@ -92,9 +97,11 @@ def encode(network, evidence):
     if evidence_clauses:
         num_clauses = len(evidence_clauses)
         clauses += evidence_clauses
-    else:
-        # Add a goal clause if necessary
-        clauses.append(clauses[-1].split(' ')[1] + ' 0')
+    else: # Add a goal clause if necessary (the first value of the last node (or 'true', if available))
+        variable = variables[-1][0]
+        literal = (variables.index((variable, 'true')) if (variable, 'true') in variables else
+                   next(i for i, t in enumerate(variables) if t[0] == variable)) + 1
+        clauses.append('{} 0'.format(literal))
         num_clauses = 1
 
     encoding = 'p cnf {} {}\n'.format(len(variables), num_clauses) + '\n'.join(clauses) + '\n'

### 2020-07-13 paper.tex
Workaround for sbk05 and evidence files: attempt 1

--- 2020-07-05 paper.tex
@@
 \item When the Bayesian network has an evidence file, we compute the probability
-  of evidence. Otherwise, we pick the last (i.e., last to be mentioned) node in
-  the Bayesian network to be the goal (the positive value for binary networks
-  and the last value in the general case). This applies to the Grid data set (as
+  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
+  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
+  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
+  and calculate its marginal probability. This applies to the Grid data set (as
   intended) and also to two instances of Plan Reconstruction and roughly half of
-  2004-PGM.
+  the instances from 2004-PGM that have empty evidence files.
 \item Bayesian networks are often solved in a compile once, query many times
@@
   variable elimination/projection/$\exists$.
+\item \texttt{cd05} relaxes the encoding so much that extra models become
+  possible. They are supposed to be filtered out by the algorithm, but mine
+  can't do that because it doesn't deal with models. Same for \texttt{cd06}
+  because it's based on \texttt{cd05}.
+\item For ground ProbLog, we can encode a program
+\begin{verbatim}
+p :: a :- b
+q :: a :- c
+\end{verbatim}
+  into $P(a \mid b)=p$, $P(a \mid c)=q$ instead of having clauses $b \Rightarrow
+  a$, $c \Rightarrow a$. Some logical structure is likely to remain.
+\item Potential criticism may be that this is a step backwards and doesn't allow
+  us to use SAT-based techniques for probabilistic inference. However, they can
+  still be used for the 'theory+query' part.
+\item We don't compare 'compile times' because our encoding time is linear, so
+  we would easily beat everyone else.
+\item The claim behind this paper is that allowing for conditional probabilities
+  in the context of weighted model counting seems to be a good idea. Bayesian
+  networks and ADDMC are only particular examples. This should also work with
+  Cachet.
+\item For the ProbLog $\to$ WMC conversion, check out this
+  guy.\footnote{\url{https://users.ics.aalto.fi/ttj/}}
 \end{itemize}
@@
 \end{align*}
+The encoding weights depend on the probabilities in the CPT as follows. For each
+value $x_n$, if $\Pr(X = x_n) = 0$, then $w(x_n) = 0$. Otherwise, let $I_n = \{ 1
+\le i \le n - 1 \mid \Pr(X = x_i) \ne 0 \}$. Then
+\[
+  w \left( x_n \;\middle|\; \bigwedge_{i \in I_n} \neg x_i \right) = \Pr(X =
+  x_n) \prod_{i \in I_n} \frac{1}{1 - w \left( x_i \;\middle|\; \bigwedge_{j \in
+        I_i} \neg x_j \right)}.
+\]
+All of these weights/probabilities may have other conditions that come from the
+structure of the Bayesian network.
 

### 2020-07-13 experiments/analyse.R

@@ -11,9 +11,8 @@ df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate =
 
 # Where answers don't match
 interesting <- df[abs(df$answer_db20 - df$answer_sbk05) > 0.01,]
-df[abs(df$answer_db20 - df$answer_cd06) > 0.01,]
 df[abs(df$answer_db20 - df$answer_d02) > 0.01,]
-df[abs(df$answer_db20 - df$answer_sbk05) > 0.01,]
+df[abs(df$answer_db20 - df$answer_cd06) > 0.01,]
 
 # Proportion of instances where my encoding is the best
 # TODO: ignore rows with all NAs

### 2020-07-13 experiments/encode.py

@@ -15,13 +15,44 @@ PROB_SPLITTER_RE = r'[, ()\n\t]+'
 STATES_RE = {'dne': r'states = \(([^()]*)\)', 'net': r'states = \(\s*"([^()]*)"\s*\)'}
 STATE_SPLITTER_RE = {'net': r'"\s*"', 'dne': r',\s*'}
 
-variables = []
+class LiteralDict:
+    _lit2var = {}
+    _var2lit = {}
+    _next_lit = 1
+
+    def add_literal(self, variable, value, literal):
+        assert literal >= self._next_lit
+        self._lit2var[literal] = (variable, value)
+        self._var2lit[(variable, value)] = literal
+        self._next_lit = literal + 1
+
+    def add(self, variable, value):
+        self.add_literal(variable, value, self._next_lit)
+
+    def __contains__(self, variableAndValue):
+        return variableAndValue in self._var2lit
+
+    def get_literal(self, variable, value):
+        return self._var2lit[(variable, value)]
+
+    def get_min_literal(self, variable):
+        return min(lit for lit, (var, val) in self._lit2var.items() if var == variable)
+
+    def get_true_or_min_literal(self, variable):
+        return self.get_literal(variable, 'true') if (variable, 'true') in self else self.get_min_literal(variable)
+
+    def get_literal_string(self, variable, value):
+        return (str(self.get_literal(variable, value)) if (variable, value) in self else
+                '-{}'.format(self.get_min_literal(variable)))
+
+    def get_last_variable(self):
+        return self._lit2var[self._next_lit - 1][0]
+
+    def __len__(self):
+        return self._next_lit - 1
+
+variables = LiteralDict()
 values_per_variable = {}
-def bayesian2logical(node, value):
-    if (node, value) in variables:
-        return str(variables.index((node, value)) + 1)
-    index = next(i for i, (n, v) in enumerate(variables) if n == node)
-    return '-{}'.format(index + 1)
 
 def construct_cpt(name, parents, probabilities):
     parent_patterns = itertools.product(*[values_per_variable[p] for p in parents])
@@ -30,16 +61,17 @@ def construct_cpt(name, parents, probabilities):
     for pattern in parent_patterns:
         probability_denominator = 1
         probability = 0
-        conditions = [bayesian2logical(parent, parent_value) for parent, parent_value in zip(parents, pattern)]
+        conditions = [variables.get_literal_string(parent, parent_value)
+                      for parent, parent_value in zip(parents, pattern)]
         for j in range(len(values_per_variable[name])):
[…]

### 2020-07-14 paper.tex
Smart probability rounding

--- 2020-07-09 paper.tex
@@
   probabilities. Ditto for non-binary values (the shorter version).
-\item Rename the repository into `conditional-wmc'.
 \item Give some examples (and/or a proof) of why this is correct when combined
@@
   \end{itemize}
-\item In preliminary results, the SBK05 encoding gives the wrong asnwer in 60
-  QMR instances (all with evidence files). Sometimes that answer is $\gg 1$.
-\item Similarly, cd06 is supposed to be the fastest, but seems to be one of the
-  slowest (along with cd05). Perhaps the best encoding for arithmetic circuits
-  has very little to do with the best encoding for CNF WMC solvers?
+\item cd06 is supposed to be the fastest, but seems to be one of the slowest
+  (along with cd05). Perhaps the best encoding for arithmetic circuits has very
+  little to do with the best encoding for CNF WMC solvers?
 \item When the Bayesian network has an evidence file, we compute the probability
-  of evidence. Otherwise, we pick the last (i.e., last to be mentioned) node in
-  the Bayesian network to be the goal (the positive value for binary networks
-  and the last value in the general case). This applies to the Grid data set (as
+  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
+  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
+  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
+  and calculate its marginal probability. This applies to the Grid data set (as
   intended) and also to two instances of Plan Reconstruction and roughly half of
-  2004-PGM.
+  the instances from 2004-PGM that have empty evidence files.
 \item Bayesian networks are often solved in a compile once, query many times

### 2020-07-14 experiments/encode.py

@@ -4,6 +4,7 @@ import os
 import re
 import subprocess
 import xml.etree.ElementTree as ET
+from fractions import Fraction
 
 ACE = ['./ace/compile', '-encodeOnly', '-noEclause']
 NODE_RE = r'\nnode (\w+)'
@@ -58,8 +59,8 @@ def construct_cpt(name, parents, probabilities):
     parent_patterns = itertools.product(*[values_per_variable[p] for p in parents])
     clauses = []
     i = 0
-    for pattern in parent_patterns:
-        probability_denominator = 1
+    for pattern_index, pattern in enumerate(parent_patterns):
+        probability_denominator = Fraction(1)
         probability = 0
         conditions = [variables.get_literal_string(parent, parent_value)
                       for parent, parent_value in zip(parents, pattern)]
@@ -76,11 +77,12 @@ def construct_cpt(name, parents, probabilities):
                                for k, value in enumerate(values_per_variable[name][:j])
                                if float(probabilities[i-len(values_per_variable[name][:j])+k]) != 0] if len(
                                        values_per_variable[name]) > 2 else []
-            clauses += ['w {} {} 0'.format(current_value, previous_value) for previous_value in previous_values]
+            if pattern_index == 0:
+                clauses += ['w {} {} 0'.format(current_value, previous_value) for previous_value in previous_values]
             negated_previous = [(v[1:] if v.startswith('-') else '-' + v) for v in previous_values]
-            probability = float(probabilities[i]) / probability_denominator
-            probability_denominator *= 1 - probability
-            clauses.append('w {} {}'.format(' '.join([current_value] + negated_previous + conditions), probability))
+            probability = Fraction(min(1, max(0, float(probabilities[i]) / probability_denominator))).limit_denominator()
+            probability_denominator = Fraction(probability_denominator * (1 - probability)).limit_denominator()
+            clauses.append('w {} {}'.format(' '.join([current_value] + negated_previous + conditions), float(probability)))
             i += 1
     return clauses
 

### 2020-07-14 paper.tex
Fix an encoding bug caused by overly eager optimisation

--- 2020-07-13 paper.tex
@@
   \end{itemize}
-\item In preliminary results, the SBK05 encoding gives the wrong asnwer in 60
-  QMR instances (all with evidence files). Sometimes that answer is $\gg 1$.
-\item Similarly, cd06 is supposed to be the fastest, but seems to be one of the
-  slowest (along with cd05). Perhaps the best encoding for arithmetic circuits
-  has very little to do with the best encoding for CNF WMC solvers?
+\item cd06 is supposed to be the fastest, but seems to be one of the slowest
+  (along with cd05). Perhaps the best encoding for arithmetic circuits has very
+  little to do with the best encoding for CNF WMC solvers?
 \item When the Bayesian network has an evidence file, we compute the probability
@@
   guy.\footnote{\url{https://users.ics.aalto.fi/ttj/}}
+\item Zero-probability weights and one-probability weights can be interpreted as
+  logical clauses. This doesn't affect ADDMC but could be useful for other
+  solvers.
+\item Filtering out ADDs that have nothing to do with the answer helps
+  tremendously, but I'm not sure if I should do that.
+\item For each row in each CPT, we order values by decreasing probabilities.
+  Need to check if this makes the solver more accurate.
 \end{itemize}

### 2020-07-15 paper.tex
A new test
Experimental results for the new non-binary encoding are somewhat encouraging

@@
     \begin{itemize}
-    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06}
+    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
     \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
@@
       the only dataset that has some non-binary networks.
-    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06}
+    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
     \end{itemize}
@@
 \item Filtering out ADDs that have nothing to do with the answer helps
-  tremendously, but I'm not sure if I should do that.
+  tremendously, but I'm not sure if I should do that. Could a heuristic do the
+  same thing?
 \item For each row in each CPT, we order values by decreasing probabilities.
   Need to check if this makes the solver more accurate.
+\item In the encoding:
+  \begin{itemize}
+  \item We assume that the first literal after `w' is positive.
+  \item The last two numbers are the positive and the negative probabilities,
+    respectively---sometimes they add to one, and sometimes the negative
+    probability is one, regardless of the value of the first probability.
+  \end{itemize}
+\item My encoding for non-binary BNs should still be faster because it doesn't
+  have those `equivalence' clauses.
+\item Guess: what makes the problem easier is:
+  \begin{enumerate}
+  \item short clauses,
+  \item low number of clauses.
+  \end{enumerate}
+  This explains why my first version of encoding non-binary CPTs was too slow.
+\item With all encodings (including mine non-binary encoding), they live on a
+  measure Boolean algebra where the measure is not probabilistic (so $\Pr(\neg
+  A) \ne 1 - \Pr(A)$).
 \end{itemize}

### 2020-07-15 experiments/analyse.R

@@ -3,16 +3,14 @@ require(scales)
 require(dplyr)
 require(maditr)
 
-TIMEOUT <- 1
+TIMEOUT <- 60
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
 df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
 df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time"))
 
 # Where answers don't match
-interesting <- df[abs(df$answer_db20 - df$answer_sbk05) > 0.01,]
-df[abs(df$answer_db20 - df$answer_d02) > 0.01,]
-df[abs(df$answer_db20 - df$answer_cd06) > 0.01,]
+interesting <- df[abs(df$answer_db20 - df$answer_d02) > 0.01,]
 
 # Proportion of instances where my encoding is the best
 # TODO: ignore rows with all NAs
@@ -29,7 +27,15 @@ sum(is.na(df$answer_sbk05))/nrow(df)
 # By dataset
 ggplot(df, aes(x = time_db20, y = time_d02, col = dataset)) +
   geom_point() +
-  geom_abline(slope = 1, intercept = 0)
+  geom_abline(slope = 1, intercept = 0) +
+  xlim(0, TIMEOUT) +
+  ylim(0, TIMEOUT)
+
+ggplot(df[df$dataset == "2005-IJCAI"], aes(x = time_db20, y = time_d02)) +
+  geom_point() +
+  geom_abline(slope = 1, intercept = 0) +
+  xlim(0, TIMEOUT) +
+  ylim(0, TIMEOUT)
 
 ggplot(df0, aes(x = encoding, y = time)) +
   geom_boxplot()

### 2020-07-16 experiments/analyse.R
Prepare for big experiments

@@ -2,18 +2,26 @@ require(ggplot2)
 require(scales)
 require(dplyr)
 require(maditr)
+require(purrr)
 
-TIMEOUT <- 60
+TIMEOUT <- 600
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
 df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
-df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time"))
+df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time", "memory"))
+df$major.dataset <- df$dataset
+df$major.dataset[df$dataset == "DQMR-50"] <- "DQMR"
+df$major.dataset[df$dataset == "DQMR-60"] <- "DQMR"
+df$major.dataset[df$dataset == "DQMR-70"] <- "DQMR"
+df$major.dataset[df$dataset == "DQMR-100"] <- "DQMR"
+df$major.dataset[df$dataset == "Grid-50"] <- "Grid"
+df$major.dataset[df$dataset == "Grid-75"] <- "Grid"
+df$major.dataset[df$dataset == "Grid-90"] <- "Grid"
 
 # Where answers don't match
 interesting <- df[abs(df$answer_db20 - df$answer_d02) > 0.01,]
 
 # Proportion of instances where my encoding is the best
-# TODO: ignore rows with all NAs
 #time$min <- apply(time, 1, min)
 #sum(time$db20 == time$min)/nrow(time)
 
@@ -24,18 +32,56 @@ sum(is.na(df$answer_d02))/nrow(df)
 sum(is.na(df$answer_db20))/nrow(df)
 sum(is.na(df$answer_sbk05))/nrow(df)
 
-# By dataset
-ggplot(df, aes(x = time_db20, y = time_d02, col = dataset)) +
-  geom_point() +
+# Scatter plot: by dataset
+min.time <- min(df0$time) + 0.001
+ggplot(df[df$time_d02 > 0,], aes(x = time_db20, y = time_d02, col = major.dataset)) +
+  geom_point(alpha = 0.5) +
   geom_abline(slope = 1, intercept = 0) +
-  xlim(0, TIMEOUT) +
-  ylim(0, TIMEOUT)
+  scale_x_continuous(trans = log10_trans(), limits = c(min.time, TIMEOUT)) +
[…]

### 2020-07-16 experiments/cachet/SAT_C.h

@@ -1,471 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
- associated documentation, even if Princeton University has been advised
- of the possibility of those damages.
-*********************************************************************/
-
-#ifndef __SAT_HEADER__
-#define __SAT_HEADER__
-
-#define	SAT_Manager void * 	
-
-typedef long long long64; //this is for 32 bit unix machines
-//typedef long long64;	    //this is for Windows or 64 bit unix machines
-
[…]

### 2020-07-16 experiments/cachet/big_num.cpp

@@ -1,127 +1,0 @@
-#include "big_num.h"
-#include <iostream>
-
-void BigNum::add(BigNum & r, BigNum & x, BigNum & y)	// result of x + y will be stored in r, x and y will be changed
-{
-	//r.denominator = x.denominator + y.denominator;
-	if (x.denominator >= y.denominator)
-	{
-		r.denominator = x.denominator;
-		mpz_mul_2exp(y.numerator, y.numerator, x.denominator - y.denominator);
-		
-	}
-	else
-	{
-		r.denominator = y.denominator;
-		mpz_mul_2exp(x.numerator, x.numerator, y.denominator - x.denominator);
-	}
-	mpz_add(r.numerator, x.numerator, y.numerator);
-	r.zero_flag = false;	// any result should be > 0
-
-	unsigned index = 0;
-	while(!mpz_tstbit(r.numerator, index))	// mpz_tstbit(r.numerator, index) == 0, test 0 bit by bit
-		++index;
-	if (index > 0)	// reduce numerator and denominator as much as possible
-	{
-		mpz_tdiv_q_2exp(r.numerator, r.numerator, index);
-		r.denominator = r.denominator - index;
-	}
-	
-	return;
-}
-
-void BigNum::mul(BigNum & r, BigNum & x, BigNum & y)	// result of x * y will be stored in x, r is unused
-{
-	/*cout << "x.numerator = "; 
-	mpz_out_str(stdout, 10, x.numerator);
-	cout << ", y.numerator = "; 
-	mpz_out_str(stdout, 10, y.numerator); 
-	cout << endl;
-	cout << "x.denominator = " << x.denominator;
-	cout << ", y.denominator = " << y.denominator << endl;
-
-	double dx = mpz_get_d(x.numerator);
-	for (int k = 0; k < x.denominator; ++k)
-		dx *= 0.5;
-	double dy = mpz_get_d(y.numerator);
-	for (int k = 0; k < y.denominator; ++k)
-		dy *= 0.5;*/
-
-	//r.denominator = x.denominator + y.denominator;
-	x.denominator = x.denominator + y.denominator;
-	//mpz_mul(r.numerator, x.numerator, y.numerator);
-	mpz_mul(x.numerator, x.numerator, y.numerator);
-	//r.zero_flag = false;	// any result should be > 0
[…]

### 2020-07-16 experiments/cachet/big_num.h

@@ -1,46 +1,0 @@
-//#include "zchaff_base.h"
-#include "stdio.h"
-#include "gmp.h"
-
-class BigNum
-{
-public:
-	mpz_t numerator;
-	unsigned denominator;	// exponent of 2
-	bool zero_flag;			// zero_flag == 1 if the big_num is 0
-
-	BigNum()
-	{
-		mpz_init(numerator);
-		//mpz_init2(numerator, 512);
-		mpz_set_ui(numerator, 0);
-		denominator = 0;
-		zero_flag = true;
-	}
-	BigNum(unsigned long numer, unsigned denom, bool zero)
-	{
-		zero_flag = zero;
-		mpz_init(numerator);
-		//mpz_init2(numerator, 512);
-		mpz_set_ui(numerator, numer);
-		denominator = denom;
-	}
-	BigNum(mpz_t & numer, unsigned denom, bool zero)
-	{
-		zero_flag = zero;
-		mpz_init(numerator);
-		//mpz_init2(numerator, 512);
-		mpz_set(numerator, numer);
-		denominator = denom;
-	}
-
-	~BigNum()
-	{
-		mpz_clear(numerator);
-	}
-
-	static void add(BigNum & r, BigNum & x, BigNum & y);
-	static void mul(BigNum & r, BigNum & x, BigNum & y);
-};
-
-

### 2020-07-16 experiments/cachet/hash.cpp

@@ -1,609 +1,0 @@
-#include "hash.h"
-#include "crc32.h"
-#include "stdio.h"
-#include <algorithm>
-
-
-bool CHashTable::set_hash_table_entry(unsigned hash_index, Component_value_pair & content)
-{
-	unsigned index = hash_index;
-	if (hash_table[index])
-	{
-		//	cout << "warning: entry " << index << " is not empty!" << endl;
-		content.next = hash_table[index];	// insert content af front
-		hash_table[index] = & content;
-	}
-	else
-	{
-		content.next = NULL;
-		hash_table[index] = & content;
-	}
-	content.sequence_number = active_entries;
-	//content_usage = content_usage + (8 + content.f.capacity() * sizeof(content.f[0])) + sizeof(vector<vector<int> *>);
-	//for (int i = content.f.capacity()-1; i >= 0; --i)
-	//	literal_usage = literal_usage + content.f[i]->capacity() * sizeof ((* content.f[0])[0]) + sizeof(vector<int>);
-	//mem_usage = content_usage + literal_usage;
-	//cout << "literal_usage = " << literal_usage << endl;
-	//for (int i = content.f.size()-1; i >= 0; --i)
-	//	num_literals = num_literals + content.f[i]->size();
-	if (++active_entries >= bound)
-	{
-		if (!quiet)
-		cout << "Added cache entries: " << active_entries << endl;
-		bound = bound + 100000;
-	}
-	if (active_entries - num_removed_entries >= clean_limit)	// if more than 20*oldest entries exist, clean cache
-	{
-		int temp = oldest;
-		//oldest = 0;	// empty cache
-		oldest = (active_entries - num_removed_entries)/4;		// keep 1/4 entries
-		//if (!quiet)
-		//	cout << "more than " << clean_limit << " entries exist, cache cleaning triggered" << endl;
-		int removed = clean_cache();
-		//if (!quiet)
-		//	cout << removed << " cache entries removed by cleaning cache"
-		//		 << ", removed entries = " << num_removed_entries << endl; 
-		oldest = temp;	// restore oldest
-	}
-	return true;
-}
-
-
-#ifndef APPROXIMATE_HASHING
-#ifdef BIG_NUM
-bool CHashTable::in_hash_table(formula & f, unsigned & hash_index, BigNum & value)
-#else
-bool CHashTable::in_hash_table(formula & f, unsigned & hash_index, long double & value)
-#endif
-{
-	bool result = false;
-	char buf;
[…]

### 2020-07-16 experiments/cachet/hash.h

@@ -1,111 +1,0 @@
-#include <assert.h>
-#include <iostream>
-#include <vector>
-#include <list>
-
-//#include <linux/kernel.h>
-//#include <linux/sys.h>
-//#include <sys/sysinfo.h>
-
-#include "zchaff_header.h"
-#include "zchaff_base.h"
-		
-class CHashTable {
-public:
-	vector<Component_value_pair *> hash_table;
-	unsigned num_literals;
-	unsigned mem_usage;
-	unsigned content_usage;
-	unsigned literal_usage;
-	unsigned hashtable_size;
-	unsigned num_collisions;
-	unsigned active_entries;
-	unsigned num_removed_entries;
-	unsigned num_hit;
-	unsigned pos_hit;
-	unsigned neg_hit;
-	unsigned bound;
-	unsigned hit_bound;
-	unsigned del_bound;
-	unsigned max_entry;
-	unsigned oldest;
-	unsigned clean_limit;
-	unsigned clean_interval;
-	bool full;
-	bool quiet;
-	double load_factor;
-	//struct sysinfo si;
-
-	void test();
-	int clean_cache();	// return the number of entries removed during the cleaning
-	bool removeChildren(child_to_remove &); // remove all children of a node(component)
-
-	// add a formula associated with value to the specified entry in hash table
-	bool set_hash_table_entry(unsigned, Component_value_pair &);
-#ifdef APPROXIMATE_HASHING
-#ifdef BIG_NUM
-	bool in_hash_table(formula &, unsigned &, unsigned long &, BigNum &);
-#else
-	bool in_hash_table(formula &, unsigned &, unsigned long &, long double &);
-#endif
-#else
-#ifdef BIG_NUM
-	bool in_hash_table(formula &, unsigned &, BigNum &);	// return true and value if found, if not found hash index
-#else
-	bool in_hash_table(formula &, unsigned &, long double &);	// return true and value if found, if not found hash index
-#endif	// end ifdef BIG_NUM
-#endif	// end ifdef APPROXIMATE_HASHING
-
-	bool compare_formula(formula &, formula &); // check if two formulas are indentical
-	void print_formula(formula &);	// print the formulared stored in a hash entry
-	void dump_formula_stack(vector<Component_value_pair *> &, int &); // output current formula stack
-
-	// quicksort	//	added by sang
[…]

### 2020-07-16 experiments/cachet/sat_solver.cpp

@@ -1,441 +1,0 @@
-/* =========FOR INTERNAL USE ONLY. NO DISTRIBUTION PLEASE ========== */
-
-/*********************************************************************
- Copyright 2000-2001, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
[…]

### 2020-07-16 experiments/cachet/zchaff_base.cpp

@@ -1,109 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
- associated documentation, even if Princeton University has been advised
- of the possibility of those damages.
-*********************************************************************/
-
-
-#include "zchaff_base.h"
-
-//===================================================================
-void CLitPoolElement::dump(ostream & os)
-{ 
-    os << (var_sign()?" -":" +") << var_index();
[…]

### 2020-07-16 experiments/cachet/zchaff_c_wrapper.cpp

@@ -1,770 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
[…]

### 2020-07-16 experiments/cachet/zchaff_cpp_wrapper.cpp

@@ -1,823 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
[…]

### 2020-07-16 experiments/cachet/zchaff_dbase.h

@@ -1,269 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
- associated documentation, even if Princeton University has been advised
- of the possibility of those damages.
-*********************************************************************/
-#ifndef __ZCHAFF_DATABASE__
-#define __ZCHAFF_DATABASE__
-
-#include <queue>
-#include "zchaff_base.h"
-
-#define STARTUP_LIT_POOL_SIZE 0x8000
-
[…]

### 2020-07-16 experiments/cachet/zchaff_solver.h

@@ -1,612 +1,0 @@
-/*********************************************************************
- Copyright 2000-2001, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
- associated documentation, even if Princeton University has been advised
- of the possibility of those damages.
-*********************************************************************/
-
-
-#define LEVEL_MAX 500
-
-#ifndef __SAT_SOLVER__
-#define __SAT_SOLVER__
-
-#include <set>
-#include <stack>
-#include <list>
-#include <algorithm>
-
-using namespace std;
-
-#include "zchaff_version.h"
-#include "zchaff_dbase.h"
-#include "hash.h"	//	added by sang
-//#include "big_num.h"
[…]

### 2020-07-16 experiments/cachet/zchaff_utils.cpp

@@ -1,107 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark,  service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
- associated documentation, even if Princeton University has been advised
- of the possibility of those damages.
-*********************************************************************/
-
-#include <stdio.h>
-#include <stdarg.h>
-#include <stdlib.h>
-#include <unistd.h>
-#include <sys/time.h>
-#include <sys/resource.h>
-
[…]

### 2020-07-16 experiments/cachet/zchaff_version.h

@@ -1,38 +1,0 @@
-/*********************************************************************
- Copyright 2000-2003, Princeton University.  All rights reserved. 
- By using this software the USER indicates that he or she has read, 
- understood and will comply with the following:
-
- --- Princeton University hereby grants USER nonexclusive permission 
- to use, copy and/or modify this software for internal, noncommercial,
- research purposes only. Any distribution, including commercial sale 
- or license, of this software, copies of the software, its associated 
- documentation and/or modifications of either is strictly prohibited 
- without the prior consent of Princeton University.  Title to copyright
- to this software and its associated documentation shall at all times 
- remain with Princeton University.  Appropriate copyright notice shall 
- be placed on all software copies, and a complete copy of this notice 
- shall be included in all copies of the associated documentation.  
- No right is  granted to use in advertising, publicity or otherwise 
- any trademark, service mark, or the name of Princeton University. 
-
-
- --- This software and any associated documentation is provided "as is" 
-
- PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS 
- OR IMPLIED, INCLUDING THOSE OF MERCHANTABILITY OR FITNESS FOR A 
- PARTICULAR PURPOSE, OR THAT  USE OF THE SOFTWARE, MODIFICATIONS, OR 
- ASSOCIATED DOCUMENTATION WILL NOT INFRINGE ANY PATENTS, COPYRIGHTS, 
- TRADEMARKS OR OTHER INTELLECTUAL PROPERTY RIGHTS OF A THIRD PARTY.  
-
- Princeton University shall not be liable under any circumstances for 
- any direct, indirect, special, incidental, or consequential damages 
- with respect to any claim by USER or any third party on account of 
- or arising from the use, or inability to use, this software or its 
- associated documentation, even if Princeton University has been advised
- of the possibility of those damages.
-*********************************************************************/
-
-#ifndef __ZCHAFF_VERSION__
-#define __ZCHAFF_VERSION__ "ZChaff 2003.7.1"
-#endif

### 2020-07-16 experiments/encode.py

@@ -55,17 +55,6 @@ class LiteralDict:
 variables = LiteralDict()
 values_per_variable = {}
 
-# 1. If the variable is binary
-# 1.1. For each row of the CPT
-# 1.1.1. w var [conditions] positive_weight negative_weight
-# 2. Else
-# 2.1. v1 ... vn 0
-# 2.2. For i<j
-# 2.2.1. -vi -vj 0
-# 2.3 For each value
-# 2.3.1. For each row of the CPT
-# 2.3.1.1. w value [conditions] positive_weight negative_weight
-
 def construct_weights(literal, num_values, parents, probabilities, probability_index, negate_probability):
     rows_of_cpt = itertools.product(*[values_per_variable[p] for p in parents])
     clauses = []

### 2020-07-16 experiments/jobscript.sh

@@ -1,0 +1,13 @@
+#!/bin/sh
+#$ -N cwmc
+#$ -cwd
+#$ -pe sharedmem 16
+#$ -l h_rt=33:00:00
+#$ -l h_vmem=8G
+
+. /etc/profile.d/modules.sh
+module load python/3.4.3
+module load java/jdk/1.8.0
+
+lscpu > cpuinfo.txt
+make -j 16

### 2020-07-18 paper.tex
Prepare for big experiments
Proof that the encoding is correct

@@
 \usepackage{soul}
+\usepackage[ruled,vlined]{algorithm2e}
 
@@
 \DeclareMathOperator{\End}{End}
+\DeclareMathOperator{\im}{im}
 
@@
 \item There is a new version of ADDMC.
+\item Prove that we have an algebra of functions with one additional operation.
+\item The function $\phi$ created by the algorithm can be seen as a measure on
+  the BA $2^U$. Can I at least show that this BA has fewer elements as a measure
+  of compactness w.r.t. the measure?
+\item Note that we're going to use logical notation for BAs. Give an example of
+  the two notations.
+\item Show how the $\phi$ from the algorithm can be encoded in the typical
+  DIMACS CNF format.
 \end{itemize}
@@
   A) \ne 1 - \Pr(A)$).
+\item We assume that all variables in the Bayesian network have at least two
+  values.
 \end{itemize}
@@
 
+\section{Encoding Bayesian networks}
+
+Let $V$ denote the set of random variables in a Bayesian network. For any random
+variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of parents of $X$ and
+$\im X$ denote the set of possible values.
+
+\begin{definition}[Indicator variables]
+  Let $X \in V$ be a random variable. If $X$ is binary (i.e., $|\im X| = 2$), we
+  can arbitrary identify one of the values as $1$ and the other one as $0$ (i.e,
+  $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
+  \emph{indicator variable} $\lambda_{X=1}$. If we interpret
+  $2^{\{\lambda_{X=1}\}}$ as a Boolean algebra, we can let $\lambda_{X=0} =
+  \neg\lambda_{X=1}$ in the algebraic notation, or, equivalently, $\lambda_{X=0}
+  = \emptyset \in 2^{\{\lambda_{X=1}\}}$ in the set-theoretic notation. On the
+  other hand, if $X$ is not binary, we represent $X$ with $|\im X|$ indicator
+  variables, one for each value. We let
+  \[
+    E(X) = \begin{cases}
+      \{ \lambda_{X=1} \} & \text{if } |\im X| = 2 \\
+      \{ \lambda_{X=x} \mid x \in \im X \} & \text{otherwise.}
+    \end{cases}
+  \]
+  denote the set of indicator variables for $X$ and
+  \[
+    E^*(X) = E(X) \cup \bigcup_{Y \in \mathrm{pa}(X)} E(Y).
+  \]
+  denote the set of indicator variables for $X$ and its parents in the Bayesian
+  network. Finally, let
+  \[
+    U = \bigcup_{X \in V} E(X)
+  \]
+  denote the set of all indicator variables for all random variables in the
+  Bayesian network.
+\end{definition}
+
+\begin{definition}[Operations on functions]
+  Let $A\colon 2^X \to [0, 1]$ and $B\colon 2^Y \to [0, 1]$ be Boolean
+  functions, $\alpha \in [0, 1]$, and $x \in X$. We define the following
+  operations:
+  \begin{description}
+  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to [0, 1]$ such
+    that
+    \[
+      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
+    \]
+    for all $\tau \in 2^{X \cup Y}$.
+  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to [0,
+    1]$ such that
+    \[
+      \overline{A}(\tau) = 1 - A(\tau)
+    \]
+    for all $\tau \in 2^X$.
+  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
+    \to [0, 1]$ such that
+    \[
+      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
+    \]
+    for all $\tau \in 2^{X \cup Y}$.
+  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
+    [0, 1]$ such that
+    \[
+      (\alpha A)(\tau) = \alpha \cdot A(\tau)
+    \]
+    for all $\tau \in 2^X$.
+  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
+      \{ x \}} \to [0, 1]$ such that
+    \[
+      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
+    \]
+    for all $\tau \in 2^{X \setminus \{x \}}$.
+  \end{description}
+\end{definition}
+\begin{remark}
+  Note that $A + \overline{A} = 1$.
+\end{remark}
+
+\begin{definition}[Special functions]
+  \phantom{}
+  \begin{itemize}
+  \item unit $1\colon 2^\emptyset \to [0, 1]$, $1(\tau) = 1$.
+  \item zero $0\colon 2^\emptyset \to [0, 1]$, $0(\tau) = 0$.
+  \item constant $[a]\colon 2^{\{a\}} \to [0, 1]$,
+    \[
+      [a](\tau) =
+      \begin{cases}
+        1 & \text{if } a \in \tau \\
+        0 & \text{if } a \not\in \tau.
+      \end{cases}
+    \]
+  \end{itemize}
+\end{definition}
+
+\begin{algorithm}
+  $\phi \gets 1$\;
+  \For{$X \in V$}{
+    \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
+    \eIf{$|\im X| = 2$}{
+      \For{$(y_1, \dots, y_n) \in \prod_{i = 1}^n \im Y_i$}{
+        $p_1 \gets \Pr(X = 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
+        $p_0 \gets \Pr(X \ne 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
+        $\phi \gets \phi \cdot \left( p_1[\lambda_{X=1}] \cdot \prod_{i=1}^n
+          [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
+          \prod_{i=1}^n [\lambda_{Y_i=y_i}] \right)$\;
+      }
+    }{
+      \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
+      $\phi \gets \phi \cdot \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)
+      \cdot \prod_{i=1}^m \prod_{j=i+1}^m (\overline{[\lambda_{X = x_i}]} +
+      \overline{[\lambda_{X = x_j}]})$\;
+      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i = 1}^n \im
+        Y_i$}{
+        $p_x \gets \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
+        $\phi \gets \phi \cdot \left( p_x[\lambda_{X=x}] \cdot \prod_{i=1}^n
+          [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot \prod_{i=1}^n
+          [\lambda_{Y_i=y_i}] \right)$\;
+      }
+    }
+  }
+  \Return{$\phi$}\;
+\end{algorithm}
+
+\begin{lemma} \label{lemma:cpt}
+  Let $X \in V$ be a random variable with $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n
+  \}$. Then the iteration of the main loop of the algorithm (when run on $X$)
+  multiplies $\phi$ by a function $\mathrm{CPT}_X\colon 2^{E^*(X)} \to [0, 1]$
+  such that
+  \[
+    \mathrm{CPT}_X(\tau) =
+    \begin{cases}
+      \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n) &
+      \begin{aligned}
+        &\text{if } \textstyle \tau = \lambda_{X=x} \land \bigwedge_{i=1}^n
+        \lambda_{Y_i=y_i} \\
+        &\text{for some } \textstyle (x, y_1, \dots, y_n) \in \im X \times
+        \prod_{i=1}^n \im Y_i
+        \end{aligned} \\
+      0 & \text{otherwise.}
+    \end{cases}
+  \]
+  for all $\tau \in 2^{E^*(X)}$.
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+\begin{proposition} \label{lemma:full_distribution}
+  $\prod_{X \in V} \mathrm{CPT}_X\colon 2^U \to [0, 1]$ represents the full
+  probability distribution of the Bayesian network, i.e., if $V = \{ X_1, \dots,
+  X_n\}$, then
+  \[
+    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) =
+    \begin{cases}
+      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } \tau = \bigwedge_{i=1}^n
+      \lambda_{X_i = x_i} \text{ for some } (x_1, \dots, x_n) \in \prod_{i=1}^n
+      \im X_i \\
+      0 & \text{otherwise,}
+    \end{cases}
+  \]
+  for all $\tau \in 2^U$.
+\end{proposition}
+\begin{proof}
+  We have that
+  \[
+    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = \prod_{X \in V}
+    \mathrm{CPT}_X(\tau \cap E^*(X)).
+  \]
+  If $\mathrm{CPT}_X(\tau \cap E^*(X)) = 0$ for some $X \in V$, then $\left(
+    \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = 0$. Otherwise, for each $X
+  \in V$, $\tau \cap E^*(X)$ can be expressed as a conjunction of indicator
+  variables. Moreover, those indicator variables must match, i.e.,
+  \[
+    \tau = \bigwedge_{X \in V} \lambda_{X = v_X}
+  \]
+  for some $(v_X)_{X \in V} \in \prod_{X \in V} \im X$. Then, by
+  \cref{lemma:cpt},
+  \[
+    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = \prod_{X \in V} \Pr
+    \left( X=v_X \;\middle|\; \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) =
+    \Pr \left( \bigwedge_{X \in V} X=v_X \right),
+  \]
+  where the last step follows from the definition of a Bayesian network.
+\end{proof}
+
+\begin{theorem}
+  Let $\phi\colon 2^U \to [0, 1]$ be a function generated by the algorithm. Then
+  \[
+    (\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset) = \Pr(X = x).
+  \]
+\end{theorem}
+\begin{proof}
+  Let $V = \{ X, Y_1, \dots, Y_n \}$. Then
+  \begin{align*}
+    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{\tau \in 2^U} (\phi \cdot [\lambda_{X=x}])(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \phi(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \left( \prod_{Y \in V} \mathrm{CPT}_Y \right)(\tau) \\
+    &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
+  \end{align*}
+  by the following arguments:
+  \begin{itemize}
+  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
+  \item if $\lambda_{X=x} \not\in \tau \in 2^U$, then $(\phi \cdot
+    [\lambda_{X=x}])(\tau) = \phi(\tau) \cdot [\lambda_{X=x}](\tau \cap \{
+    \lambda_{X=x} \}) = \phi(\tau) \cdot 0 = 0$;
+  \item \cref{lemma:full_distribution};
+  \item marginalisation of a probability distribution.
+  \end{itemize}
+\end{proof}
+
+% Acknowledgments. This work has made use of the resources provided by the
+% Edinburgh Compute and Data Facility (ECDF) (http://www.ecdf.ed.ac.uk/).
+
 \bibliographystyle{plain}

### 2020-07-18 experiments/jobscript.sh

@@ -6,8 +6,9 @@
 #$ -l h_vmem=8G
 
 . /etc/profile.d/modules.sh
-module load python/3.4.3
 module load java/jdk/1.8.0
+module load roslin/python/3.8.1
+module load phys/EXPERIMENTAL/compilers/gcc/10.1.0
 
 lscpu > cpuinfo.txt
 make -j 16

### 2020-07-19 paper.tex
A detailed example

@@
 \usepackage[ruled,vlined]{algorithm2e}
+\usepackage{subcaption}
 
@@
 \item[F] Give a concrete example of something impossible to represent using WMC.
-\item Describe the changes to the Cachet DIMACS CNF format (and mention that, if
-  needed, the assumption that $\Pr(A) + \Pr(\neg A) = 1$ can be discarded).
-  Instead of \texttt{w 1 0.1}, we have \texttt{w 1 2 0.1} and \texttt{w 1 -2
-    0.5}. This provides half of the information; the remaining half can be
-  deduced, but the algorithm itself can support weights that are not necessarily
-  probabilities. Ditto for non-binary values (the shorter version).
-\item Give some examples (and/or a proof) of why this is correct when combined
-  with arbitrary clauses (i.e., conjunctions of disjunctions).
 \item Turn the saved PDFs into citations.
-\item Add a mini theorem: my model can express any probability distribution on
-  the BA (just like BNs can express any discrete distribution).
 \item[F] What are the main claims, what are the main takeaways, intuitive [???]
@@
 \item Make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x, y$?).
-\item Decide on terminology: coproducts/pushouts vs (amalgamated) free products.
-  Probably the former.
 \item Terminology: `with generating set $S$' $\to$ `over $S$'.
@@
   set.
-\item There is a new version of ADDMC.
-\item Prove that we have an algebra of functions with one additional operation.
+\item Prove that we have an algebra of functions with two (?) additional
+  operations. Or maybe just cite the original paper for this.
 \item The function $\phi$ created by the algorithm can be seen as a measure on
@@
   the two notations.
-\item Show how the $\phi$ from the algorithm can be encoded in the typical
-  DIMACS CNF format.
+\item Could clarify why $[\lambda_{X=0}] = \overline{[\lambda_{X=1}]}$. This
+  follows from the definition. Or should I avoid the overline notation?
+\item After the experiments are finished, note the processor, memory per thread,
+  and add the following acknowledgment. This work has made use of the resources
+  provided by the Edinburgh Compute and Data Facility (ECDF)
+  (\url{http://www.ecdf.ed.ac.uk/}).
 \end{itemize}
@@
   values.
+\item Remark: for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A +
+  \overline{A} = 1$.
 \end{itemize}
@@
 \begin{definition}[Operations on functions]
-  Let $A\colon 2^X \to [0, 1]$ and $B\colon 2^Y \to [0, 1]$ be Boolean
-  functions, $\alpha \in [0, 1]$, and $x \in X$. We define the following
-  operations:
+  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
+    0}$ be Boolean functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We
+  define the following operations:
   \begin{description}
-  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to [0, 1]$ such
-    that
+  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
+    \mathbb{R}_{\ge 0}$ such that
     \[
@@
     for all $\tau \in 2^{X \cup Y}$.
-  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to [0,
-    1]$ such that
+  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
+    \mathbb{R}_{\ge 0}$ such that
     \[
@@
   \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
-    \to [0, 1]$ such that
+    \to \mathbb{R}_{\ge 0}$ such that
     \[
@@
   \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
-    [0, 1]$ such that
+    \mathbb{R}_{\ge 0}$ such that
     \[
@@
   \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
-      \{ x \}} \to [0, 1]$ such that
+      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
     \[
@@
 \end{definition}
-\begin{remark}
-  Note that $A + \overline{A} = 1$.
-\end{remark}
+Note that both addition and multiplication commute.
 
@@
   \begin{itemize}
-  \item unit $1\colon 2^\emptyset \to [0, 1]$, $1(\tau) = 1$.
-  \item zero $0\colon 2^\emptyset \to [0, 1]$, $0(\tau) = 0$.
-  \item constant $[a]\colon 2^{\{a\}} \to [0, 1]$,
+  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\tau) = 1$.
+  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\tau) = 0$.
+  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
     \[
@@
 
+Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
+$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
+
 \begin{algorithm}
@@
     \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
+    $\mathrm{CPT}_X \gets 0$\;
     \eIf{$|\im X| = 2$}{
@@
         $p_0 \gets \Pr(X \ne 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
-        $\phi \gets \phi \cdot \left( p_1[\lambda_{X=1}] \cdot \prod_{i=1}^n
-          [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
-          \prod_{i=1}^n [\lambda_{Y_i=y_i}] \right)$\;
+        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_1[\lambda_{X=1}] \cdot
+        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
+        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
       }
@@
       \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
-      $\phi \gets \phi \cdot \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)
-      \cdot \prod_{i=1}^m \prod_{j=i+1}^m (\overline{[\lambda_{X = x_i}]} +
-      \overline{[\lambda_{X = x_j}]})$\;
-      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i = 1}^n \im
-        Y_i$}{
+      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i =
+          1}^n \im Y_i$}{
         $p_x \gets \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
-        $\phi \gets \phi \cdot \left( p_x[\lambda_{X=x}] \cdot \prod_{i=1}^n
-          [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot \prod_{i=1}^n
-          [\lambda_{Y_i=y_i}] \right)$\;
+        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_x[\lambda_{X=x}] \cdot
+        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot
+        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
       }
+      $\mathrm{CPT}_X \gets \mathrm{CPT}_X \cdot \left( \sum_{i=1}^m [\lambda_{X
+          = x_i}] \right) \cdot \prod_{i=1}^m \prod_{j=i+1}^m
+      (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})$\;
     }
+    $\phi \gets \phi \cdot \mathrm{CPT}_X$\;
   }
@@
 \begin{lemma} \label{lemma:cpt}
-  Let $X \in V$ be a random variable with $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n
-  \}$. Then the iteration of the main loop of the algorithm (when run on $X$)
-  multiplies $\phi$ by a function $\mathrm{CPT}_X\colon 2^{E^*(X)} \to [0, 1]$
-  such that
-  \[
-    \mathrm{CPT}_X(\tau) =
-    \begin{cases}
-      \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n) &
-      \begin{aligned}
-        &\text{if } \textstyle \tau = \lambda_{X=x} \land \bigwedge_{i=1}^n
-        \lambda_{Y_i=y_i} \\
-        &\text{for some } \textstyle (x, y_1, \dots, y_n) \in \im X \times
-        \prod_{i=1}^n \im Y_i
-        \end{aligned} \\
-      0 & \text{otherwise.}
-    \end{cases}
-  \]
-  for all $\tau \in 2^{E^*(X)}$.
+  Let $X \in V$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
+  \dots, Y_n \}$. Then $\mathrm{CPT}_X\colon 2^{E^*(X)} \to \mathbb{R}_{\ge 0}$
+  is such that for any $x \in \im X$ and $(y_1, \dots, y_n) \in \prod_{i=1}^n
+  \im Y_i$,
+  \[
+    \mathrm{CPT}_X \left( \lambda_{X=x} \land \bigwedge_{i=1}^n
+      \lambda_{Y_i=y_i} \right) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
+  \]
 \end{lemma}
 \begin{proof}
+  Let
+  \[
+    \tau = \lambda_{X=x} \land \bigwedge_{i=1}^n \lambda_{Y_i=y_i}.
+  \]
+  If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im Y_i|$
+  terms, one for each possible assignment of values to variables $X, Y_1, \dots,
+  Y_n$. Exactly one of these terms is nonzero when applied to $\tau$, and it is
+  equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
+
+  If $X$ is not binary, then
+  \[
+    \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(\tau) = 1,
+  \]
+  and
+  \[
+    \left( \prod_{i=1}^m \prod_{j=i+1}^m (\overline{[\lambda_{X = x_i}]} +
+      \overline{[\lambda_{X = x_j}]}) \right)(\tau) = 1,
+  \]
+  so, by a similar argument as before,
+  \[
+    \mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
+  \]
 \end{proof}
@@
 \begin{proposition} \label{lemma:full_distribution}
-  $\prod_{X \in V} \mathrm{CPT}_X\colon 2^U \to [0, 1]$ represents the full
-  probability distribution of the Bayesian network, i.e., if $V = \{ X_1, \dots,
-  X_n\}$, then
-  \[
-    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) =
+  $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ represents the full probability
+  distribution of the Bayesian network, i.e., if $V = \{ X_1, \dots, X_n\}$,
+  then
+  \[
+    \phi(\tau) =
     \begin{cases}
@@
 \begin{proof}
-  We have that
-  \[
-    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = \prod_{X \in V}
-    \mathrm{CPT}_X(\tau \cap E^*(X)).
-  \]
-  If $\mathrm{CPT}_X(\tau \cap E^*(X)) = 0$ for some $X \in V$, then $\left(
-    \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = 0$. Otherwise, for each $X
-  \in V$, $\tau \cap E^*(X)$ can be expressed as a conjunction of indicator
-  variables. Moreover, those indicator variables must match, i.e.,
+  If
   \[
@@
   \]
-  for some $(v_X)_{X \in V} \in \prod_{X \in V} \im X$. Then, by
-  \cref{lemma:cpt},
-  \[
-    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = \prod_{X \in V} \Pr
-    \left( X=v_X \;\middle|\; \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) =
-    \Pr \left( \bigwedge_{X \in V} X=v_X \right),
-  \]
-  where the last step follows from the definition of a Bayesian network.
+  for some $(v_X)_{X \in V} \in \prod_{X \in V} \im X$, then
+  \[
+    \phi(\tau) = \prod_{X \in V} \Pr \left( X=v_X \;\middle|\; \bigwedge_{Y \in
+        \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X \in V} X=v_X
+    \right)
+  \]
+  by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
+  must be some non-binary random variable $X \in V$ such that $|E(X) \cap \tau|
+  \ne 1$. If $E(X) \cap \tau = \emptyset$, then
+  \[
+    \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(\tau) = 0,
+  \]
+  and so $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$. If $|E(X) \cap
+  \tau| > 1$, then we must have two different values $x_1, x_2 \in \im X$ such
+  that $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq \tau$ which means that
+  \[
+    (\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(\tau) = 0,
+  \]
+  and so, again, $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$.
 \end{proof}
@@
 \begin{theorem}
-  Let $\phi\colon 2^U \to [0, 1]$ be a function generated by the algorithm. Then
+  Let $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ be a function generated by the
+  algorithm. Then
   \[
@@
 
-% Acknowledgments. This work has made use of the resources provided by the
-% Edinburgh Compute and Data Facility (ECDF) (http://www.ecdf.ed.ac.uk/).
+\begin{example}
+  \begin{figure}
+    \centering
+    \begin{subfigure}{0.2\textwidth}
+      \centering
+      \begin{tikzpicture}
+        \node[latent] (W) {W};
+        \node[latent, below right=of W] (T) {T};
+        \node[latent, below left=of W] (F) {F};
+        \edge {W} {F};
+        \edge {W} {T};
+      \end{tikzpicture}
+    \end{subfigure}%
+    \begin{subfigure}{0.8\textwidth}
+      \centering
+      \begin{tabular}[t]{cc}
+        \toprule
+        $w$ & $\Pr(W = w)$ \\
+        \midrule
+        1 & 0.5 \\
+        0 & 0.5 \\
+        \bottomrule
+      \end{tabular}
+      \begin{tabular}[t]{ccc}
+        \toprule
+        $w$ & $f$ & $\Pr(F = f \mid W = w)$ \\
+        \midrule
+        1 & 1 & 0.6 \\
+        1 & 0 & 0.4 \\
+        0 & 1 & 0.1 \\
+        0 & 0 & 0.9 \\
+        \bottomrule
+      \end{tabular}
+      \begin{tabular}[t]{ccc}
+        \toprule
+        $w$ & $t$ & $\Pr(T = t \mid W = w)$ \\
+        \midrule
+        1 & $l$ & 0.2 \\
+        1 & $m$ & 0.4 \\
+        1 & $h$ & 0.4 \\
+        0 & $l$ & 0.6 \\
+        0 & $m$ & 0.3 \\
+        0 & $h$ & 0.1 \\
+        \bottomrule
+      \end{tabular}
+    \end{subfigure}
+    \caption{An example Bayesian network with its CPTs}
+    \label{fig:example_bn}
+  \end{figure}
+
+  The Bayesian network in \cref{fig:example_bn} has
+  \begin{align*}
+    V &= \{ W, F, T \}, \\
+    \mathrm{pa}(W) &= \emptyset, \\
+    \mathrm{pa}(F) &= \mathrm{pa}(T) = \{ W \}, \\
+    \im W &= \im F = \{ 0, 1 \}, \\
+    \im T &= \{ l, m, h \}, \\
+    E(W) &= \{ \lambda_{W=1} \}, \\
+    E(F) &= \{ \lambda_{F=1} \}, \\
+    E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
+    E^*(W) &= \{ \lambda_{W=1} \}, \\
+    E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
+    E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}, \\
+    \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
+    \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
+      &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
+    \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots),
+  \end{align*}
+  and can be encoded in a DIMACS-like CNF format as
+  \[
+    \begin{array}{l r r l l}
+      \lambda\sb{T=l} &\lambda\sb{T=m} &\lambda\sb{T=h} & &0 \\
+                      &-\lambda\sb{T=l} &-\lambda\sb{T=m} & &0 \\
+                      &-\lambda\sb{T=l} &-\lambda\sb{T=h} & &0 \\
+                      &-\lambda\sb{T=m} &-\lambda\sb{T=h} & &0 \\
+      w &\lambda\sb{W=1} & &0.5 &0.5 \\
+      w &\lambda\sb{F=1} &\lambda\sb{W=1} &0.6 &0.4 \\
+      w &\lambda\sb{F=1} &-\lambda\sb{W=1} &0.1 &0.9 \\
+      w &\lambda\sb{T=l} &\lambda\sb{W=1} &0.2 &1 \\
+      w &\lambda\sb{T=m} &\lambda\sb{W=1} &0.4 &1 \\
+      w &\lambda\sb{T=h} &\lambda\sb{W=1} &0.4 &1 \\
+      w &\lambda\sb{T=l} &\lambda\sb{W=0} &0.6 &1 \\
+      w &\lambda\sb{T=m} &\lambda\sb{W=0} &0.3 &1 \\
+      w &\lambda\sb{T=h} &\lambda\sb{W=0} &0.1 &1
+    \end{array}
+  \]
+  with each $\lambda$ replaced with a unique positive integer.
+\end{example}
 

### 2020-07-20 paper.tex
Move things around

@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{conjecture}{Conjecture}
 \theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 \theoremstyle{remark}
@@
 
-\title{Weighted Model Counting with Conditional Probabilities}
+\title{Weighted Model Counting with Conditional Measures}
 \author{Paulius Dilkas}
@@
 
-\paragraph{Legend.}
-\begin{description}
-\item[F] Feedback (round 1).
-\item[F2] Feedback (round 2).
-\item[FP] Feedback from the review panel.
-\item[\textbullet] My own idea.
-\end{description}
-
-\paragraph{The big TODO list.}
-\begin{itemize}
-\item Look into ways to theoretically justify the performance benefits. Some
-  suggestions:
-  \begin{itemize}
-  \item the number of variables,
-  \item the number of clauses/CPTs/lines in CPTs,
-  \item the proportion of edges that exist,
-  \item average degree,
-  \item average number of clauses that a variable is in,
-  \item the number of clusters in the linear/tree-like decomposition.
-  \end{itemize}
-\item Have an example of how the ADDs function in this situation. If not for the
-  paper, then at least for slides. Use the framework to check its correctness.
-\item[F] Give a concrete example of something impossible to represent using WMC.
-\item Turn the saved PDFs into citations.
+\begin{itemize}
+\item Thesis: many important computational problems are solved by encoding them
+  as WMC. But if the weight function is extended to `conditional probabilities',
+  the problem becomes easier because current approaches need workarounds in
+  order to be independent.
+\item Shorter thesis: many important problems are encoded as WMC, but they can
+  be encoded in a better way if we allow for conditional probabilities.
+\item The claim behind this paper is that allowing for conditional probabilities
+  in the context of weighted model counting seems to be a good idea. Bayesian
+  networks and ADDMC are only particular examples. This should also work with
+  Cachet.
+\item Potential criticism may be that this is a step backwards and doesn't allow
+  us to use SAT-based techniques for probabilistic inference. However, they can
+  still be used for the 'theory+query' part.
+  \begin{itemize}
+  \item Zero-probability weights and one-probability weights can be interpreted
+    as logical clauses. This doesn't affect ADDMC but could be useful for other
+    solvers.
+  \end{itemize}
 \item[F] What are the main claims, what are the main takeaways, intuitive [???]
@@
   define the main concepts for introducing measures on Boolean algebras.
-\item[F] Can you say something here about factorized vs non-factorized
-  weight function definitions? That is, factorized is when $w$ maps literals to
-  $R_{\ge 0}$, non-factorized is when $w$ maps models to $R_{\ge 0}$ and
-  \begin{itemize}
-  \item come up with nice example when non-factorized weights are intuitive;
-  \item clarify that the factorized definition have is w.r.t. models, in case some
-    one gets confused. [It doesn't have to be, if the BA is not free---P.]
+\item
+  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
+  \begin{itemize}
+  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
+    multiplicativity of BAs in different words) (with optimal settings)
+  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
+  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
+  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
+  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
+  \end{itemize}
+\item Contributions
+  \begin{itemize}
+  \item WMC defines a measure over a BA.
+  \item WMC with weights on literals imposes an independence assumption.
+    (Measures are `slightly' more expressive than WMC with weights on models
+    because they apply to non-atomic BAs.)
+  \item A BA can be augmented with new literals in order to support any measure.
+  \item (Maybe) a lower bound on the number of new literals needed in order to
+    support any measure.
+  \item This results in a smaller problem for WMC algorithms (w.r.t. both the
+    number of literals and the length of the theory) and thus faster inference.
+  \end{itemize}
+\item Notable previous/related work
+  \begin{itemize}
+  \item Hailperin's approach to probability logic
+    \cite{DBLP:journals/ndjfl/Hailperin84}
+  \item Nilsson's (somewhat successful) probabilistic logic
+    \cite{DBLP:journals/ai/Nilsson86,DBLP:journals/ai/Nilsson93}
+  \item Logical induction: a big paper with a good overview of previous attempts
+    to assign probabilities to logical sentences in a sensible way
+    \cite{DBLP:journals/eccc/GarrabrantBCST16}
+  \item Measures on Boolean algebras
+    \begin{itemize}
+    \item On possibility and probability measures in finite Boolean algebras
+      \cite{DBLP:journals/soco/CastineiraCT02}
+    \item Representation of conditional probability measures
+      \cite{krauss1968representation}
+    \end{itemize}
   \end{itemize}
@@
   sample text needed to adequately motivate [???] for WMC/SRL community.
-\item[FP] Clear up questions about independence between literals.
-\item[F2] Preliminaries: explain with examples: models $=$ elements [atoms] of
-  algebra.
-\item WMC as a Measure
-  \begin{itemize}
-  \item[F2] Need to explain how WMC and NWMC connects to standard definitions of
-    WMC and $\Pr(\phi \mid e) = \WMC(\phi \land e)/\WMC(e)$.
-  \item[F2] You need to explain what precisely these mean in logic and models
-    and weight functions are usually defined and understood.
-  \item Be careful about mentioning ideals, filters, and quotients.
-  \end{itemize}
-\item What Measures are WMC-Definable: proofs need to be updated and
-  propositions could be phrased in a better way, but the gist should be the
-  same.
-\item Extending the Algebra.
-  \begin{itemize}
-  \item[F2] If you prove (b) above, you could motivate why weights on literals
-    is attractive and whether there is a way to augment the expressivity of WMC
-    while still maintaining literal level weights. Hence this action.
-  \item[F2] You need to explain the significance of this result.
-  \end{itemize}
+\end{itemize}
+
+\section{Preliminaries}
+
+\begin{itemize}
+\item[F2] Explain with examples: models $=$ elements [atoms] of algebra.
+\item Perhaps reorder the section of preliminaries into paragraphs, i.e., a
+  paragraph for order, for homomorphisms, etc. This would take up less space.
 \item Make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x, y$?).
 \item Terminology: `with generating set $S$' $\to$ `over $S$'.
-\item Perhaps reorder the section of preliminaries into paragraphs, i.e., a
-  paragraph for order, for homomorphisms, etc. This would take up less space.
 \item Notation: if $L$ denotes literals, then it doesn't denote a generating
-  set.
-\item Prove that we have an algebra of functions with two (?) additional
-  operations. Or maybe just cite the original paper for this.
-\item The function $\phi$ created by the algorithm can be seen as a measure on
-  the BA $2^U$. Can I at least show that this BA has fewer elements as a measure
-  of compactness w.r.t. the measure?
-\item Note that we're going to use logical notation for BAs. Give an example of
-  the two notations.
-\item Could clarify why $[\lambda_{X=0}] = \overline{[\lambda_{X=1}]}$. This
-  follows from the definition. Or should I avoid the overline notation?
-\item After the experiments are finished, note the processor, memory per thread,
-  and add the following acknowledgment. This work has made use of the resources
-  provided by the Edinburgh Compute and Data Facility (ECDF)
-  (\url{http://www.ecdf.ed.ac.uk/}).
-\end{itemize}
-
-\paragraph{Experimental setup.}
-\begin{itemize}
-\item
-  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
-  \begin{itemize}
-  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
-    multiplicativity of BAs in different words) (with optimal settings)
-  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
-  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
-  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
-  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
-  \end{itemize}
-\item Encodings:
-  \begin{itemize}
-  \item \texttt{-d02} \cite{DBLP:conf/kr/Darwiche02}
-  \item \texttt{-sbk05} \cite{DBLP:conf/aaai/SangBK05}
-  \item \texttt{-cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
-  \item \texttt{-cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
-  \item mine
-  \end{itemize}
-  All except mine are from Ace
-  3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be compiled
-  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
-  \texttt{-noEclause} (i.e., only use standard syntax) flags.
-\item Datasets\footnote{There might be more at
-    \url{https://meelgroup.github.io/}.}
-  \begin{itemize}
-  \item binary Bayesian networks from Sang et
-    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
-    \cite{DBLP:conf/aaai/SangBK05}
-    \begin{itemize}
-    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
-      deterministic),
-    \item Plan recognition (problems),
-    \item Deterministic quick medical reference (what do the numbers mean? the
-      README doesn't say).
-    \end{itemize}
-  \item Bayesian networks available with Ace
-    \begin{itemize}
-    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
-    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
-      files have their own citation data that I should probably extract. This is
-      the only dataset that has some non-binary networks.
-    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
-    \end{itemize}
-  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
-  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
-  \end{itemize}
-\end{itemize}
-
-\paragraph{Contributions.}
-\begin{itemize}
-\item WMC defines a measure over a BA.
-\item WMC with weights on literals imposes an independence assumption. (Measures
-  are `slightly' more expressive than WMC with weights on models because they
-  apply to non-atomic BAs.)
-\item A BA can be augmented with new literals in order to support any measure.
-\item (Maybe) a lower bound on the number of new literals needed in order to
-  support any measure.
-\item Alternatively, one can use coproducts and pushouts to define a BA with
-  precisely the right independence and conditional independence conditions.
-  (This requires a relaxed version of WMC.)
-\item This results in a smaller problem for WMC algorithms (w.r.t. both the
-  number of literals and the length of the theory) and is optimal for, e.g.,
-  Bayesian networks.
-\item (Maybe) this results in faster inference (?)
-\end{itemize}
-
-\paragraph{Notable previous/related work.}
-\begin{itemize}
-\item Hailperin's approach to probability logic
-  \cite{DBLP:journals/ndjfl/Hailperin84}
-\item Nilsson's (somewhat successful) probabilistic logic
-  \cite{DBLP:journals/ai/Nilsson86}
-\item Logical induction: a big paper with a good overview of previous attempts
-  to assign probabilities to logical sentences in a sensible way
-  \cite{DBLP:journals/eccc/GarrabrantBCST16}
-\item Measures on Boolean algebras
-  \begin{itemize}
-  \item On possibility and probability measures in finite Boolean algebras
-    \cite{DBLP:journals/soco/CastineiraCT02}
-  \item Representation of conditional probability measures
-    \cite{krauss1968representation}
-  \end{itemize}
-\end{itemize}
-
-\paragraph{Notes.}
-\begin{itemize}
-\item Thesis: many important computational problems are solved by encoding them
-  as WMC. But if the weight function is extended to `conditional probabilities',
-  the problem becomes easier because current approaches need workarounds in
-  order to be independent.
-\item Shorter thesis: many important problems are encoded as WMC, but they can
-  be encoded in a better way if we allow for conditional probabilities.
-\item We extend the Gaifman graph to add edges when two variables occur in the
-  same CPT (e.g., including the edge from $A$ to $B$ when the CPT is $\Pr(A \mid
-  B)$).
-\item Extra benefit: one does not need to come up with a way to turn some probability
-distribution to into a fully independent one.
-\item Trivial CPTs such as $\Pr(A \mid B) = \Pr(\neg A \mid B) = 0.5$, the ADDs
-  of which simplify to a single number, are put in the first cluster.
-\item Observation: by inspecting the BN, we could identify CPTs that could be
-  completely ignored, but maybe good heuristics take care of that anyway.
-\item Observation: ADDs have a restrict command. I'm not going to use it, but it
-  could be nice.
-\item Alternative scenario to consider for future work: \#\SAT{} solver
-  generates solutions which are then used to restrict the ADDs that calculate
-  probabilities.
-\item Important future work: replacing ADDs with
-  AADDs\footnote{\url{https://github.com/ssanner/dd-inference}} is likely to
-  bring performance benefits. Other extensions:
-  \begin{itemize}
-  \item FOADDs can represent first order statements;
-  \item XADDs can replace WMI for continuous variables;
-  \item ADDs with intervals can do approximations.
-  \end{itemize}
-\item cd06 is supposed to be the fastest, but seems to be one of the slowest
-  (along with cd05). Perhaps the best encoding for arithmetic circuits has very
-  little to do with the best encoding for CNF WMC solvers?
-\item When the Bayesian network has an evidence file, we compute the probability
-  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
-  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
-  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
-  and calculate its marginal probability. This applies to the Grid data set (as
-  intended) and also to two instances of Plan Reconstruction and roughly half of
-  the instances from 2004-PGM that have empty evidence files.
-\item Bayesian networks are often solved in a compile once, query many times
-  fashion. This can be achieved using ADDMC by selecting a subset $S$ of
-  variable we may want to query over and running ADDMC while excluding $S$ from
-  variable elimination/projection/$\exists$.
-\item \texttt{cd05} relaxes the encoding so much that extra models become
-  possible. They are supposed to be filtered out by the algorithm, but mine
-  can't do that because it doesn't deal with models. Same for \texttt{cd06}
-  because it's based on \texttt{cd05}.
-\item For ground ProbLog, we can encode a program
-\begin{verbatim}
-p :: a :- b
-q :: a :- c
-\end{verbatim}
-  into $P(a \mid b)=p$, $P(a \mid c)=q$ instead of having clauses $b \Rightarrow
-  a$, $c \Rightarrow a$. Some logical structure is likely to remain.
-\item Potential criticism may be that this is a step backwards and doesn't allow
-  us to use SAT-based techniques for probabilistic inference. However, they can
-  still be used for the 'theory+query' part.
-\item We don't compare 'compile times' because our encoding time is linear, so
-  we would easily beat everyone else.
-\item The claim behind this paper is that allowing for conditional probabilities
-  in the context of weighted model counting seems to be a good idea. Bayesian
-  networks and ADDMC are only particular examples. This should also work with
-  Cachet.
-\item For the ProbLog $\to$ WMC conversion, check out this
-  guy.\footnote{\url{https://users.ics.aalto.fi/ttj/}}
-\item Zero-probability weights and one-probability weights can be interpreted as
-  logical clauses. This doesn't affect ADDMC but could be useful for other
-  solvers.
-\item Filtering out ADDs that have nothing to do with the answer helps
-  tremendously, but I'm not sure if I should do that. Could a heuristic do the
-  same thing?
-\item For each row in each CPT, we order values by decreasing probabilities.
-  Need to check if this makes the solver more accurate.
-\item In the encoding:
-  \begin{itemize}
-  \item We assume that the first literal after `w' is positive.
-  \item The last two numbers are the positive and the negative probabilities,
-    respectively---sometimes they add to one, and sometimes the negative
-    probability is one, regardless of the value of the first probability.
-  \end{itemize}
-\item My encoding for non-binary BNs should still be faster because it doesn't
-  have those `equivalence' clauses.
-\item Guess: what makes the problem easier is:
-  \begin{enumerate}
-  \item short clauses,
-  \item low number of clauses.
-  \end{enumerate}
-  This explains why my first version of encoding non-binary CPTs was too slow.
-\item With all encodings (including mine non-binary encoding), they live on a
-  measure Boolean algebra where the measure is not probabilistic (so $\Pr(\neg
-  A) \ne 1 - \Pr(A)$).
-\item We assume that all variables in the Bayesian network have at least two
-  values.
-\item Remark: for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A +
-  \overline{A} = 1$.
-\end{itemize}
-
-\section{Preliminaries}
+  set. Literals should be $U$.
+\end{itemize}
 
@@
 
-\section{WMC as a Measure}
+\section{Weighted Model Counting as a Measure}
+
+\begin{itemize}
+\item Any function $2^U \to \mathbb{R}_{\ge 0}$ induces a measure on
+  $2^{2^U}$---the full Boolean algebra. This measure is not necessarily
+  probabilistic.
+\item[F2] Need to explain how WMC and NWMC connects to standard definitions of
+  WMC and $\Pr(\phi \mid e) = \WMC(\phi \land e)/\WMC(e)$.
+\item[F2] You need to explain what precisely these mean in logic and models
+  and weight functions are usually defined and understood.
+\item Be careful about mentioning ideals, filters, and quotients.
+\item Note that we're going to use logical notation for BAs. Give an example of
+  the two notations.
+\end{itemize}
 
@@
 
-\section{What Measures Are WMC-Definable?}
+\section{Limitations of Literal-Based Weighted Model Counting}
+
+\begin{itemize}
+\item[F] Give a concrete example of something impossible to represent using WMC.
+\item[F] Can you say something here about factorized vs non-factorized
+  weight function definitions? That is, factorized is when $w$ maps literals to
+  $R_{\ge 0}$, non-factorized is when $w$ maps models to $R_{\ge 0}$ and
+  \begin{itemize}
+  \item come up with nice example when non-factorized weights are intuitive;
+  \item clarify that the factorized definition have is w.r.t. models, in case some
+    one gets confused. [It doesn't have to be, if the BA is not free---P.]
+  \end{itemize}
+\item What Measures are WMC-Definable: proofs need to be updated and
+  propositions could be phrased in a better way, but the gist should be the
+  same.
+\end{itemize}
 
@@
 
+\begin{itemize}
+\item[F2] If you prove (b) above, you could motivate why weights on literals
+  is attractive and whether there is a way to augment the expressivity of WMC
+  while still maintaining literal level weights. Hence this action.
+\item[F2] You need to explain the significance of this result.
+\end{itemize}
+
 Given this requirement for independence, a well-known way to represent
@@
 
-\section{Representing Independence and Conditional Independence}
-
-\subsection{Preliminaries}
-
-\begin{definition}
-  Given a BA $\mathbf{A}$, a \emph{subalgebra} is a subset $\mathbf{B} \subseteq
-  \mathbf{A}$ that, together with the operations, zero, and one of $\mathbf{A}$,
-  is a BA.
-\end{definition}
-
-\begin{definition}[\cite{givant2008introduction}]
-  Let $\mathbf{A},$ $\mathbf{B}$, and $\mathbf{C}$ be BAs such that $\mathbf{B}$
-  is a subalgebra of $\mathbf{A}$. Let $f\colon \mathbf{A} \to \mathbf{C}$ and
-  $g\colon \mathbf{B} \to \mathbf{C}$ be homomorphisms. Then $f$ is an
-  \emph{extension} of $g$ if $f(x) = g(x)$ for all $x \in \mathbf{B}$. If $f$ is
-  an extension of each member of a family $\{ g_i \}_{i \in I}$ of
-  homomorphisms, then $f$ is called a \emph{common extension} of $\{ g_i \}_{i
-    \in I}$.
-\end{definition}
-
-\begin{definition}[\cite{givant2008introduction}]
-  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
-  $\mathbf{A}$. If for any BA $\mathbf{B}$ with a family of homomorphisms $\{
-  f_i\colon \mathbf{A}_i \to \mathbf{B} \}_{i \in I}$ there exists a unique
-  common extension of $\{ f_i\colon \mathbf{A}_i \to \mathbf{B} \}_{i \in I}$
-  ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
-  \[
-    \begin{tikzcd}
-      \mathbf{A}_i \ar[r,hookrightarrow] \arrow{rd}[swap]{f_i} & \mathbf{A}
-      \arrow[d,dashed,"f"] \\
-      & \mathbf{B}
-    \end{tikzcd}
-  \]
-  then $\mathbf{A}$ is the \emph{internal sum}\footnote{A slightly more general
-    version of this definition is also known as the free product, the Boolean
-    product, and the coproduct in the category of BAs
-    \cite{givant2008introduction,koppelberg1989handbook,sikorski1969boolean}.}
-  of $\{\mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
-  \mathbf{A}_i$.
-\end{definition}
-
-\begin{proposition}[\cite{sikorski1969boolean}]
-  Let $\mathbf{A}$ be the internal sum of a family of BAs $\{ \mathbf{A}_i \}_{i
-    \in I}$, and let $\{m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in
-    I}$ be a family of measures. Then there exists a unique measure $m\colon
-  \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any finite subset $J
-  \subseteq I$ and family of elements $\{ x_j \in \mathbf{A}_j \}_{j \in J}$,
-  \[
-    m \left( \bigwedge_{j \in J} x_j \right) = \prod_{j \in J} m_j(x_j).
-  \]
-\end{proposition}
-
-\begin{definition}[\cite{koppelberg1989handbook}]
-  Let $\mathbf{A}$ be a BA. Let $\mathbf{B}$ be a subalgebra of $\mathbf{A}$,
-  and let $\{ \mathbf{A}_i\}_{i \in I}$ be a family of subalgebras of $\mathbf{A}$
-  such that $\mathbf{A}_i \cap \mathbf{A}_j = \mathbf{B}$ for all $i \ne j$ in
-  $I$. Let $\{ \iota_i \colon \mathbf{B} \to \mathbf{A}_i \}$ be a family of
-  inclusion homomorphisms. Then $\mathbf{A}$ is the \emph{amalgamated free
-    product\footnote{Also known as a (wide) pushout in the category of BAs.} of
-    $\{\mathbf{A}_{i} \}_{i \in I}$ over $\mathbf{B}$} if, for any Boolean
-  algebra $\mathbf{C}$ with a family of homomorphisms $\{ f_i\colon \mathbf{A}_i
-  \to \mathbf{C} \}_{i \in I}$ such that $f_i \circ \iota_i = f_j \circ \iota_j$
-  for all $i, j \in I$, there is a unique homomorphism $f\colon \mathbf{A} \to
-  \mathbf{C}$ such that the triangle in
-  \[
-    \begin{tikzcd}
-      \mathbf{B} \ar[r,hookrightarrow,"\iota_i"] & \mathbf{A}_i
-      \ar[r,hookrightarrow] \ar[d,swap,"f_i"] & \mathbf{A} \ar[ld,dashed,"f"] \\
-      & \mathbf{C}
-    \end{tikzcd}
-  \]
-  commutes for all $i \in I$. We will denote this product as
-  \[
-    \mathbf{A} = \bigoplus_{\substack{\mathbf{B}\\ i \in I}} \mathbf{A}_i.
-  \]
-\end{definition}
-
-\subsection{New Results}
-
-\todo[inline]{Make sure that this is enough to guarantee a pushout.}
-\begin{theorem}
-  Let $\{ S_i \}_{i=0}^n$ be a finite set of finite sets for some $n > 1$ such
-  that for all distinct positive integers $i$ and $j$, $S_i \cap S_j = S_0$, and
-  let
-  \[
-    \mathbf{A} = \bigoplus_{\substack{\mathcal{F}(S_0)\\ 1 \le i \le n}}
-    \mathcal{F}(S_i).
-  \]
-  Let $(m_i\colon \mathcal{F}(S_i) \to \mathbb{R}_{\ge 0})_{i=1}^n$ be arbitrary
-  measures. Then there is a unique measure $m\colon \mathbf{A} \to
-  \mathbb{R}_{\ge 0}$ such that, for any element $b \in \mathcal{F}(S_0)$,
-  subset $J \subseteq \{ 1, 2, \dots, n \}$, and elements $\{ a_j \in
-  \mathcal{F}(S_j \setminus S_0) \}_{j \in J}$,
-  \[
-    m \left(b \land \bigwedge_{j \in J} a_j \right) = \prod_{j \in J} m_j(b
-    \land a_j).
-  \]
-\end{theorem}
-
-\begin{theorem}
-  The number of weights needed to encode a Bayesian network using
-  coproducts and pushouts is equal to the number of entries in the tables of the
-  network (and the resulting theory is shorter).
-\end{theorem}
-
-\begin{theorem}[Pushouts of free BAs are free]
-  Let
-  \[
-    \mathbf{A} = \bigoplus_{\substack{\mathbf{B}\\ i \in I}} \mathbf{A}_i
-  \]
-  be an amalgamated free product such that $\{ \mathbf{A}_{i} \}_{i \in I}$ are
-  free BAs with $\{ S_i \}_{i \in I}$ as their respective sets of generators.
-  Let $S = \bigcup_{i \in I} S_i$. Then $\mathbf{A}$ is a free BA with
-  generating set $S$.
-\end{theorem}
-\begin{proof}
-  Suppose we have a map from $S$ to an arbitrary BA $\mathbf{C}$, as in
-  \[
-    \begin{tikzcd}
-      S_i \ar[r,hookrightarrow] \ar[d,hookrightarrow] & S \ar[d,hookrightarrow]
-      \ar[ddr,bend left] & \\
-      \mathbf{A}_i \ar[r,hookrightarrow] \ar[rrd,dashed,bend right] & \mathbf{A}
-      \ar[rd,dashed]& \\
-      & & \mathbf{C}.
-    \end{tikzcd}
-  \]
-  We want to show that there exists a unique homomorphism $\mathbf{A} \to
-  \mathbf{C}$. For all $i \in I$, from $S_i \hookrightarrow S$ and $S \to
-  \mathbf{C}$ we get a map $S_i \to \mathbf{C}$, so---by the definition of a
-  free BA---there is a unique homomorphism $\mathbf{A}_i \to \mathbf{C}$.
-  Furthermore, a family of homomorphisms $\{ \mathbf{A}_i \to \mathbf{C} \}_{i
-    \in I}$ uniquely determine a homomorphism $\mathbf{A} \to \mathbf{C}$ by the
-  universal mapping property of a (wide) pushout. Thus $\mathbf{A}$ is a free BA
-  with generating set $S$.
-\end{proof}
-
-\begin{corollary}
-  Similarly, coproducts of free BAs are free.
-\end{corollary}
-
-\section{Representation of conditional probability tables}
-
-The probability of a variable with $n$ values $x_1, \dots, x_n$ (whether
-conditioned on something or not) can be represented with an ADD of size
-$\Theta(n^2)$ by representing each of $\Pr(x_1), \Pr(x_2 \mid x_1), \dots,
-\Pr(x_n \mid x_1, \dots, x_{n-1})$ by a separate ADD. For example, if $n=3$, the
-last of the three ADDs would look like this
-\[
-  \begin{tikzpicture}
-    \node[ellipse,draw] (x3) {$x_3$};
-    \node[ellipse,draw,below left = of x3] (x21) {$x_2$};
-    \node[ellipse,draw,below right = of x3] (x22) {$x_2$};
-    \node[ellipse,draw,below = of x21] (x11) {$x_1$};
-    \node[ellipse,draw,below = of x22] (x12) {$x_1$};
-    \node[rectangle,draw,below = of x11] (n2) {$0.7$};
-    \node[rectangle,draw,left = of n2] (n1) {$0$};
-    \node[rectangle,draw,below = of x12] (n3) {$0.3$};
-    \node[rectangle,draw,right = of n3] (n4) {$1$};
-
-    \draw (x3) edge (x21);
-    \draw (x21) edge (n1);
-    \draw (x11) edge (n1);
-    \draw[dashed] (x21) edge (x11);
-    \draw[dashed] (x11) edge (n2);
-
-    \draw[dashed] (x3) edge (x22);
-    \draw[dashed] (x22) edge (x12);
-    \draw[dashed] (x12) edge (n3);
-    \draw (x22) edge (n4);
-    \draw (x12) edge (n4);
-  \end{tikzpicture}
-\]
-Such an ADD for $x_n$ has $2n+3$ nodes and $4n-2$ edges. The same information
-can be represented in textual form as
-\begin{align*}
-  &\texttt{w 3 1 0} \\
-  &\texttt{w 3 2 0} \\
-  &\texttt{w 3 -1 -2 0.7}
-\end{align*}
-The encoding weights depend on the probabilities in the CPT as follows. For each
-value $x_n$, if $\Pr(X = x_n) = 0$, then $w(x_n) = 0$. Otherwise, let $I_n = \{ 1
-\le i \le n - 1 \mid \Pr(X = x_i) \ne 0 \}$. Then
-\[
-  w \left( x_n \;\middle|\; \bigwedge_{i \in I_n} \neg x_i \right) = \Pr(X =
-  x_n) \prod_{i \in I_n} \frac{1}{1 - w \left( x_i \;\middle|\; \bigwedge_{j \in
-        I_i} \neg x_j \right)}.
-\]
-All of these weights/probabilities may have other conditions that come from the
-structure of the Bayesian network.
-
-\section{Encoding Bayesian networks}
+\section{Previous Work}
+
+\subsection{Bayesian Network Encodings}
+
+\begin{itemize}
+\item All encodings (including my non-binary encoding) live on a measure Boolean
+  algebra where the measure is not probabilistic (so $\Pr(\neg A) \ne 1 -
+  \Pr(A)$).
+\item \texttt{cd05} relaxes the encoding so much that extra models become
+  possible. They are supposed to be filtered out by the algorithm, but mine
+  can't do that because it doesn't deal with models. Same for \texttt{cd06}
+  because it's based on \texttt{cd05}.
+\item \texttt{sbk05} uses my trick with dividing probabilities. That could
+  explain small inaccuracies in its answers.
+\item Encodings:
+  \begin{itemize}
+  \item \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}
+  \item \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}
+  \item \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
+  \item \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
+  \item \texttt{db20} (mine)
+  \end{itemize}
+\end{itemize}
+
+\subsection{Algebraic Decision Diagrams and ADDMC}
+
+\section{The Algebra of Functions on Boolean Algebras}
+
+\begin{itemize}
+\item Could clarify why $[\lambda_{X=0}] = \overline{[\lambda_{X=1}]}$. This
+  follows from the definition. Or should I avoid the overline notation?
+\item Prove that we have an algebra of functions with two (?) additional
+  operations. Or maybe just cite the original paper for this.
+\end{itemize}
 
@@
 
+\begin{remark}
+  For any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A + \overline{A} = 1$.
+\end{remark}
+
 Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
 $\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
+
+\section{Encoding Bayesian Networks Using Conditional Measures}
+
+\begin{itemize}
+\item We assume that the first literal after `w' is positive.
+\item The last two numbers are the positive and the negative probabilities,
+  respectively---sometimes they add to one, and sometimes the negative
+  probability is one, regardless of the value of the first probability.
+\item We assume that all variables in the Bayesian network have at least two
+  values.
+\item Have an example of how the ADDs function in this situation. If not for the
+  paper, then at least for slides. Use the framework to check its correctness.
+\item The function $\phi$ created by the algorithm can be seen as a measure on
+  the BA $2^U$.
+\item We extend the Gaifman graph to add edges when two variables occur in the
+  same CPT (e.g., including the edge from $A$ to $B$ when the CPT is $\Pr(A \mid
+  B)$).
+\end{itemize}
 
@@
 
+\section{Experimental Comparison}
+
+\begin{itemize}
+\item We don't compare 'compile times' because our encoding time is linear, so
+  we would easily beat everyone else.
+\item When the Bayesian network has an evidence file, we compute the probability
+  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
+  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
+  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
+  and calculate its marginal probability. This applies to the Grid data set (as
+  intended) and also to two instances of Plan Reconstruction and roughly half of
+  the instances from 2004-PGM that have empty evidence files.
+\item After the experiments are finished, note the processor, memory per thread,
+  and add the following acknowledgment.
+\item All other encodings are implemented in
+  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be
+  compiled with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC)
+  and \texttt{-noEclause} (i.e., only use standard syntax) flags.
+\item Datasets
+  \begin{itemize}
+  \item binary Bayesian networks from Sang et
+    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
+    \cite{DBLP:conf/aaai/SangBK05}
+    \begin{itemize}
+    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
+      deterministic),
+    \item Plan recognition (problems),
+    \item Deterministic quick medical reference (what do the numbers mean? the
+      README doesn't say).
+    \end{itemize}
+  \item Bayesian networks available with Ace
+    \begin{itemize}
+    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
+    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
+      files have their own citation data that I should probably extract. This is
+      the only dataset that has some non-binary networks.
+    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
+    \end{itemize}
+  \end{itemize}
+\end{itemize}
+
+\section{Explaining The Performance Benefits}
+
+\begin{itemize}
+\item \texttt{d02} has
+  \[
+    \sum_{X \in V} |\im X| + |\im X|\prod_{Y \in \mathrm{pa}(X)}|\im Y|
+  \]
+  variables and
+  \[
+    \sum_{X \in V} 1 + \binom{|\im X|}{2} + |\im X|(2 +
+    |\mathrm{pa}(X)|)\prod_{Y \in \mathrm{pa}(X)} |\im Y|
+  \]
+  clauses (along with one ADD per variable to encode the weights).
+\item \texttt{sbk05} is a bit harder to evaluate due to a handful of small
+  optimisations in the encoding. Could find an upper bound anyway.
+\item \texttt{db20} (my encoding) has
+  \[
+    \sum_{X \in V} |\im X|
+  \]
+  variables (less for binary) and
+  \[
+    \sum_{X \in V} |\im X| + 1 + \binom{|\im X|}{2}
+  \]
+  ADDs.
+\item Let:
+  \begin{itemize}
+  \item $N = |V|$ (i.e., the number of nodes in the Bayesian network),
+  \item $D = \max_{X \in V} |\mathrm{pa}(X)|$ (i.e., the maximum in-degree or
+    the number of parents),
+  \item $V = \max_{X \in V} |\im X|$ (i.e., the maximum number of values per
+    variables).
+  \end{itemize}
+\item Then my encoding has $\mathcal{O}(NV)$ variables and $\mathcal{O}(NV^2)$
+  ADDs while \texttt{d02} has $\mathcal{O}(NV^{D+1})$ variables and
+  $\mathcal{O}(NDV^{D+1})$ ADDs.
+\end{itemize}
+
+\todo[inline]{Calculate numVariables/numClauses (or the other way around) for
+  each instance and plot this ratio vs runtime (for each encoding, or at least
+  mine and D02)}
+
+\section{Conclusion and Future Work}
+
+\begin{itemize}
+\item Extra benefit: one does not need to come up with a way to turn some
+  probability distribution to into a fully independent one.
+\item Important future work: replacing ADDs with
+  AADDs\footnote{\url{https://github.com/ssanner/dd-inference}} is likely to
+  bring performance benefits. Other extensions:
+  \begin{itemize}
+  \item FOADDs can represent first order statements;
+  \item XADDs can replace WMI for continuous variables;
+  \item ADDs with intervals can do approximations.
+  \end{itemize}
+\item Filtering out ADDs that have nothing to do with the answer helps
+  tremendously, but I'm purposefully not doing that. Perhaps a heuristic could
+  do the same thing?
+\item Encodings for everything else
+  \begin{itemize}
+  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
+  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
+    \begin{itemize}
+    \item For the ProbLog to WMC conversion, check out this guy:
+      \url{https://users.ics.aalto.fi/ttj/}.
+    \item proof-based \cite{DBLP:conf/iclp/MantadelisJ10}
+    \item rule-based \cite{DBLP:conf/ecai/Janhunen04}
+    \item For ground ProbLog, we can encode a program
+\begin{verbatim}
+p :: a :- b
+q :: a :- c
+\end{verbatim}
+      into $P(a \mid b)=p$, $P(a \mid c)=q$ instead of having clauses $b
+      \Rightarrow a$, $c \Rightarrow a$. Some logical structure is likely to
+      remain.
+    \end{itemize}
+  \end{itemize}
+\item Bayesian networks are often solved in a compile once, query many times
+  fashion. This can be achieved using ADDMC by selecting a subset $S$ of
+  variable we may want to query over and running ADDMC while excluding $S$ from
+  variable elimination/projection/$\exists$.
+\item More references
+  \begin{itemize}
+  \item Measures on/in Boolean algebras: Horn and Tarski
+    \cite{horn1948measures}, Jech \cite{jech2017measures}
+  \item On Boolean algebras and their role in analysis \cite{winkowska1996boolean}
+  \item Infinite domains
+    \begin{itemize}
+    \item Markov Logic in Infinite Domains (Singla and Domingos)
+      \cite{DBLP:conf/uai/SinglaD07}
+    \item Objective Bayesian probabilistic logic (Williamson)
+      \cite{DBLP:journals/jal/Williamson08}
+    \item Unifying Logic and Probability (Russell)
+      \cite{DBLP:journals/cacm/Russell15}
+    \end{itemize}
+  \item Logical induction \cite{DBLP:journals/eccc/GarrabrantBCST16}
+  \item Quantum probabilistic logic programming \cite{balu2015quantum}
+  \item WMC
+    \begin{itemize}
+    \item algebraic model counting \cite{DBLP:journals/japll/KimmigBR17}
+    \item Explanation-Based Approximate Weighted Model Counting for
+      Probabilistic Logics \cite{DBLP:conf/aaai/RenkensKBR14}
+    \item OUWMC \cite{DBLP:conf/aaai/Belle17}
+    \item Formula-Based Probabilistic Inference \cite{DBLP:conf/uai/GogateD10}
+    \item Parallel Probabilistic Inference by WMC \cite{DBLP:conf/pgm/DalLL18}
+    \item Semiring Programming \cite{DBLP:journals/corr/BelleR16}
+    \item theoretical extension: WMC beyond two-variable logic
+      \cite{DBLP:conf/lics/KuusistoL18}
+    \item from weighted to unweighted model counting
+      \cite{DBLP:conf/ijcai/ChakrabortyFMV15}
+    \item theory behind WMC algorithms: solving \#\SAT{} and Bayesian inference
+      with backtracking search \cite{DBLP:journals/jair/BacchusDP09}
+    \end{itemize}
+  \end{itemize}
+\end{itemize}
+
+\paragraph{Acknowledgements.} This work has made use of the resources provided
+by the Edinburgh Compute and Data Facility (ECDF)
+(\url{http://www.ecdf.ed.ac.uk/}).
+
 \bibliographystyle{plain}

### 2020-07-21 paper.tex
Edit

@@
 \usepackage{booktabs}
+\usepackage[table]{xcolor}
 \usepackage{tikz}
-\usepackage{xcolor}
 \usepackage[backgroundcolor=lightgray]{todonotes}
@@
 \usepackage{subcaption}
+\usepackage{multirow}
 
 \newtheorem{theorem}{Theorem}
+\newtheorem{observation}{Observation}
 \newtheorem{lemma}{Lemma}
@@
 \begin{itemize}
-\item Thesis: many important computational problems are solved by encoding them
-  as WMC. But if the weight function is extended to `conditional probabilities',
-  the problem becomes easier because current approaches need workarounds in
-  order to be independent.
-\item Shorter thesis: many important problems are encoded as WMC, but they can
-  be encoded in a better way if we allow for conditional probabilities.
-\item The claim behind this paper is that allowing for conditional probabilities
-  in the context of weighted model counting seems to be a good idea. Bayesian
-  networks and ADDMC are only particular examples. This should also work with
-  Cachet.
+\item The Main Narrative
+  \begin{enumerate}
+  \item When weights are defined on literals, the measure on the free BA is
+    fully independent.
+  \item This means that the BA itself must be larger (i.e., have additional
+    `meaningless' literals) to turn any probability distribution into an
+    independent one.
+  \item We show how we can define conditional weights on literals, allowing us
+    to encode any probability distribution into a Boolean algebra that's not
+    necessarily independent and thus can be smaller.
+  \item We demonstrate a specific example of this by presenting a new way to
+    encode Bayesian networks into instances of WMC and adapting a WMC algorithm
+    (ADDMC) to run on the new format.
+  \item We show that this results in significantly faster inference.
+  \item We show that our encoding results in asymptotically fewer literals and
+    fewer ADDs, and thus a simpler problem.
+  \item (Maybe) we experimentally demonstrate a phase transition based on the
+    number of variables per ADD.
+  \end{enumerate}
 \item Potential criticism may be that this is a step backwards and doesn't allow
@@
   \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
-  \end{itemize}
-\item Contributions
-  \begin{itemize}
-  \item WMC defines a measure over a BA.
-  \item WMC with weights on literals imposes an independence assumption.
-    (Measures are `slightly' more expressive than WMC with weights on models
-    because they apply to non-atomic BAs.)
-  \item A BA can be augmented with new literals in order to support any measure.
-  \item (Maybe) a lower bound on the number of new literals needed in order to
-    support any measure.
-  \item This results in a smaller problem for WMC algorithms (w.r.t. both the
-    number of literals and the length of the theory) and thus faster inference.
   \end{itemize}
@@
   \end{itemize}
-\item[F2] The paper at this stage is very technical---the danger is that WMC/SRL
-  people may not be able to follow it and so would be hard to get accepted.
-  Without clear target audience, [???] get work accepted. My main high level
-  suggestion is that let us tease apart what you have and see if a story
-  emerges. That is, let us attempt to write a paper {\bf with examples} and
-  see whether with significant motivation, we have a story emerging. Below,
-  sample text needed to adequately motivate [???] for WMC/SRL community.
+\item Intuitively, a measure is just like a probability, except it's in
+  $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
+\item ADDMC should probably be in textsc mode.
 \end{itemize}
@@
 \begin{itemize}
-\item[F2] Explain with examples: models $=$ elements [atoms] of algebra.
-\item Perhaps reorder the section of preliminaries into paragraphs, i.e., a
-  paragraph for order, for homomorphisms, etc. This would take up less space.
 \item Make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x, y$?).
@@
 \end{itemize}
+
+\begin{table}
+  \caption{(in the same order)}
+  \centering
+  \begin{tabular}{lcc}
+    \toprule
+    & Set-theoretic notation & Boolean-algebraic notation \\
+    \midrule
+    Atoms (elements of $U$) & $a, b$ & $a, b$ \\
+    \rowcolor{gray!10} Models (elements of $2^U$) & $\emptyset, \{a\}, \{b\}, \{a, b\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
+    & $\{ \emptyset, \{a\}, \{b\}, \{a, b\} \}$ & $\top$ \\
+    & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{a\}, \{a, b\} \}$ & $\neg a \lor \neg b, a \to b$ \\
+    & $\{ \emptyset, \{b\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ & $b \to a, a \lor b$ \\
+    & $\{\emptyset, \{a\}\}, \{\emptyset, \{b\}\}, \{\emptyset, \{a, b\}\}$ & $\neg b, \neg a, a \leftrightarrow b$ \\
+    & $\{\{a\}, \{b\}\}, \{\{a\}, \{a, b\}\}, \{\{b\}, \{a, b\}\}$ & $(a \land \neg b) \lor (b \land \neg a), a, b$ \\
+    & $\{\emptyset\}, \{\{a\}\}, \{\{b\}\}, \{\{a, b\}\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
+    \multirow{-7}{*}{Formulas (elements of $2^{2^U}$)} & $\emptyset$ & $\bot$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
-\begin{definition}[\cite{givant2008introduction}]
-  Let $\mathbf{A}$ and $\mathbf{B}$ be BAs. A \emph{(Boolean) homomorphism} from
-  $\mathbf{A}$ to $\mathbf{B}$ is a map $f\colon \mathbf{A} \to \mathbf{B}$ such
-  that:
-  \begin{itemize}
-  \item $f(x \land y) = f(x) \land f(y)$,
-  \item $f(x \lor y) = f(x) \lor f(y)$,
-  \item $f(\neg x) = \neg f(x)$
-  \end{itemize}
-  for all $x, y \in \mathbf{A}$.
-\end{definition}
-
-\begin{lemma}[Homomorphisms preserve order
-  \cite{givant2008introduction}] \label{lemma:homomorphisms_and_order}
-  Let $f\colon \mathbf{A} \to \mathbf{B}$ be a homomorphism between two BAs
-  $\mathbf{A}$ and $\mathbf{B}$. Then, for any $x, y \in \mathbf{A}$, if $x \le
-  y$, then $f(x) \le f(y)$.
-\end{lemma}
-
 \begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:order}
@@
 
-\begin{definition}[\cite{koppelberg1989handbook}]
-  Let $S$ be a set, and let $\mathbf{B}$ be a BA. Then $\mathbf{B}$ is a
-  \emph{free BA over $S$} if there is a map $S \to \mathbf{B}$ such that for any
-  BA $\mathbf{C}$ and map $S \to \mathbf{C}$, there is a unique homomorphism
-  $\mathbf{B} \to \mathbf{C}$ that makes
-  \[
-    \begin{tikzcd}
-      S \ar[rd] \ar[r] & \mathbf{B} \ar[d,dashed] \\
-      & \mathbf{C}.
-    \end{tikzcd}
-  \]
-  commute. A BA $\mathbf{B}$ is \emph{free} if $S$ exists.
+\subsection{The Space of Functions on Boolean Algebras}
+
+\begin{definition}[Operations on functions]
+  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
+    0}$ be Boolean functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We
+  define the following operations:
+  \begin{description}
+  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
+    \mathbb{R}_{\ge 0}$ such that
+    \[
+      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
+    \]
+    for all $\tau \in 2^{X \cup Y}$.
+  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
+    \mathbb{R}_{\ge 0}$ such that
+    \[
+      \overline{A}(\tau) = 1 - A(\tau)
+    \]
+    for all $\tau \in 2^X$.
+  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
+    \to \mathbb{R}_{\ge 0}$ such that
+    \[
+      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
+    \]
+    for all $\tau \in 2^{X \cup Y}$.
+  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
+    \mathbb{R}_{\ge 0}$ such that
+    \[
+      (\alpha A)(\tau) = \alpha \cdot A(\tau)
+    \]
+    for all $\tau \in 2^X$.
+  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
+      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
+    \[
+      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
+    \]
+    for all $\tau \in 2^{X \setminus \{x \}}$.
+  \end{description}
 \end{definition}
 
-\begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:finite_and_free}
-  A finite BA is free if and only if it has $2^{2^n}$ elements for some $n \in
-  \mathbb{N}$. It then has $2^n$ atoms and $n$ generators.
-\end{lemma}
+\begin{observation}
+  Let $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0} \mid X \subseteq U
+  \}$. Then $\mathcal{V}$ is a semi-vector space with three additional
+  operations: inverse, (non-scalar) multiplication, and projection.
+  Specifically, note that both addition and multiplication are both associative
+  and commutative.
+\end{observation}
+
+\begin{definition}[Special functions]
+  \phantom{}
+  \begin{itemize}
+  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\tau) = 1$.
+  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\tau) = 0$.
+  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
+    \[
+      [a](\tau) =
+      \begin{cases}
+        1 & \text{if } a \in \tau \\
+        0 & \text{if } a \not\in \tau.
+      \end{cases}
+    \]
+  \end{itemize}
+\end{definition}
+
+\begin{remark}
+  For any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A + \overline{A} = 1$.
+\end{remark}
+
+Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
+$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
 
@@
 \begin{itemize}
-\item Any function $2^U \to \mathbb{R}_{\ge 0}$ induces a measure on
-  $2^{2^U}$---the full Boolean algebra. This measure is not necessarily
-  probabilistic.
-\item[F2] Need to explain how WMC and NWMC connects to standard definitions of
-  WMC and $\Pr(\phi \mid e) = \WMC(\phi \land e)/\WMC(e)$.
-\item[F2] You need to explain what precisely these mean in logic and models
-  and weight functions are usually defined and understood.
-\item Be careful about mentioning ideals, filters, and quotients.
+\item[F2] Explain with examples: models $=$ elements [atoms] of algebra.
+\item Be careful about mentioning ideals and quotients.
 \item Note that we're going to use logical notation for BAs. Give an example of
@@
 
-\begin{definition} \label{def:algebra_from_logic}
-  Let $\mathcal{L}$ be a propositional (or first-order) logic, and let
-  $\Delta$ be a theory in $\mathcal{L}$. We can define an equivalence
-  relation on formulas in $\mathcal{L}$ as
-  \[
-    \alpha \sim \beta \quad \text{if and only if} \quad \Delta \vdash \alpha
-    \leftrightarrow \beta
-  \]
-  for all $\alpha, \beta \in \mathcal{L}$. Let $[\alpha]$ denote the equivalence
-  class of $\alpha \in \mathcal{L}$ with respect to $\sim$. We can then let
-  $B(\Delta) = \{ [\alpha] \mid \alpha \in \mathcal{L} \}$ and define the
-  structure of a BA on $B(\Delta)$ as
-  \begin{align*}
-    [\alpha] \lor [\beta] &= [\alpha \lor \beta], \\
-    [\alpha] \land [\beta] &= [\alpha \land \beta], \\
-    \neg[\alpha] &= [\neg\alpha], \\
-    1 &= [\alpha \to \alpha], \\
-    0 &= [\alpha \land \neg\alpha]
-  \end{align*}
-  for all $\alpha, \beta \in \mathcal{L}$. Then $B(\Delta)$ is the
-  \emph{Lindenbaum-Tarski algebra} of $\Delta$
-  \cite{koppelberg1989handbook,tarski1983logic}.
-\end{definition}
-
 \begin{example} \label{example:construction}
+  % TODO: keep this, but might need a lot of editing.
   Let $\mathcal{L}$ be a propositional logic with $p$ and $q$ as its only atoms.
@@
 
-  The corresponding BA $B(\Delta)$ can then be constructed using
-  \cref{def:algebra_from_logic}. Alternatively, one can first construct the free
+  The corresponding BA $B(\Delta)$ can then be constructed as a
+  Lindenbaum-Tarski algebra. Alternatively, one can first construct the free
   BA generated by the set $\{ p, q \}$ and then take a quotient with respect to
@@
   \item Find a reference for the set/subset thing.
-  \item This should be replaced with inner sums (a.k.a. free products).
-  \item Mention that the subsequent definition can be reduced to a single
-    formula (i.e., without cases).
-  \item Any measure is a WMC measure if all atoms are in $L$.
   \end{itemize}
@@
 \begin{definition} \label{def:wmc}
-  Let $\mathbf{B}$ be an atomic BA, and let $M \subset \mathbf{B}$ be its set of
-  atoms. Let $L \subset \mathbf{B}$ be such that every atom $m \in M$ can be
-  uniquely expressed as $m = \bigwedge L'$ for some $L' \subseteq L$, and let
-  $w\colon L \to \mathbb{R}_{\ge 0}$ be arbitrary. The \emph{weighted model
-    count} $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
-  \[
-    \WMC_w(x) = \begin{cases}
-      0 & \text{if } x = 0 \\
-      \prod_{l \in L'} w(l) & \text{if } M \ni x = \bigwedge L' \\
-      \sum_{\text{atoms } a \le x} \WMC_w(a) & \text{otherwise}
+  Let $U$ be an arbitrary set. Then
+  \begin{itemize}
+  \item a \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$,
+  \item a \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
+      0}$.
+  \item a weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
+    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
+  \item every weight function induces a measure:
+    \[
+      M_W(x) = \begin{cases}
+        0 & \text{if } x = \emptyset \\
+        W(u) & \text{if } x = \{ u \} \\
+        \sum_{\{u\} \le x} W(u) & \text{otherwise.}
       \end{cases}
     \]
-  for any $x \in \mathbf{B}$. Furthermore, we define the \emph{normalised
-    weighted model count} $\nWMC_w\colon \mathbf{B} \to [0, 1]$ as $\nWMC_w(x) =
-  \frac{\WMC_w(x)}{\WMC_w(1)}$ for all $x \in \mathbf{B}$. For both $\WMC_w$ and
-  $\nWMC_w$, we will drop the subscript when doing so results in no potential
-  confusion. Finally, we say that a measure $m\colon \mathbf{B} \to
-  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-definable}) if
-  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
-  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
+    The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$
+    with a given definition of $W$ is known as \emph{weighted model counting}.
+  \end{itemize}
 \end{definition}
-
-\begin{theorem}
-  $\WMC$ is a measure, and $\nWMC$ is a probability measure.
-\end{theorem}
-\begin{proof}
-  First, note that $\WMC$ is non-negative and $\WMC(0) = 0$ by definition. Next,
-  let $x, y \in \mathbf{B}$ be such that $x \land y = 0$. We want to show that
-  \begin{equation} \label{eq:additivity_proof}
-    \WMC(x \lor y) = \WMC(x) + \WMC(y).
-  \end{equation}
-  If, say, $x = 0$, then \cref{eq:additivity_proof} becomes
-  \[
-    \WMC(y) = \WMC(0) + \WMC(y) = \WMC(y)
-  \]
-  (and likewise for $y = 0$). Thus we can assume that $x \ne 0 \ne y$ and use
-  \cref{thm:representation} to write
-  \[
-    x = \bigvee_{i \in I} x_i \quad \text{and} \quad y = \bigvee_{j \in J} y_j
-  \]
-  for some sequences of atoms $(x_i)_{i \in I}$ and $(y_j)_{j \in J}$. If
-  $x_{i'} = y_{j'}$ for some $i' \in I$ and $j' \in J$, then
-  \[
-    x \land y = \bigvee_{i \in I} \bigvee_{j \in J} x_i \land y_j = x_{i'} \land
-    y_{j'} \ne 0,
-  \]
-  contradicting the assumption. This is enough to show that
-  \begin{align*}
-    \WMC(x \lor y) &= \WMC\left( \left( \bigvee_{i \in I} x_i \right) \lor \left(\bigvee_{j \in J} y_j \right) \right) = \sum_{i \in I} \WMC(x_i) + \sum_{j \in J} \WMC(y_j) \\
-                   &= \WMC(x) + \WMC(y),
-  \end{align*}
-  finishing the proof that $\WMC$ is a measure. This immediately shows that
-  $\nWMC$ is a probability measure since, by definition, $\nWMC(1) = 1$.
-\end{proof}
 
@@
 
-\section{Limitations of Literal-Based Weighted Model Counting}
+\section{Limitations of Factored Weighted Model Counting}
 
@@
   \end{itemize}
-\item What Measures are WMC-Definable: proofs need to be updated and
-  propositions could be phrased in a better way, but the gist should be the
-  same.
-\end{itemize}
-
-\subsection{WMC Requires Independent Literals}
+\end{itemize}
 
@@
 
-\subsection{Extending the Algebra}
-
-\begin{itemize}
-\item[F2] If you prove (b) above, you could motivate why weights on literals
-  is attractive and whether there is a way to augment the expressivity of WMC
-  while still maintaining literal level weights. Hence this action.
-\item[F2] You need to explain the significance of this result.
-\end{itemize}
-
 Given this requirement for independence, a well-known way to represent
@@
 the set $L$ covered by the WMC weight function $w\colon L \to \mathbb{R}_{\ge
-  0}$. Let us translate this idea to the language of BAs.
-
-\begin{theorem} \label{thm:extension}
-  Let $\mathbf{B}$ be a free BA over a finite set $S$, and let $m\colon
-  \mathbf{B} \to \mathbb{R}_{\ge 0}$ be an arbitrary measure. Let $L = \{ s \mid
-  s \in S \} \cup \{ \neg s \mid s \in S \}$. By \cref{lemma:finite_and_free},
-  we know that $\mathbf{B}$ has $n = 2^{|S|}$ atoms. Let $\{a_i\}_{i=1}^n$
-  denote those atoms in some arbitrary order. Let $L' = L \cup \{ \phi_i
-  \}_{i=1}^n \cup \{\neg \phi_i \}_{i=1}^n$ be the set $L$ extended with $2n$
-  new elements. Let $\mathbf{B'}$ be the unique Boolean algebra with $\{ \phi_i
-  \land a_i \}_{i=1}^n \cup \{ \neg \phi_i \land a_i \}_{i=1}^n$ as its set of
-  atoms. Let $\iota\colon \mathbf{B} \hookrightarrow \mathbf{B'}$ be the
-  inclusion homomorphism. Let $w\colon L' \to \mathbb{R}_{\ge 0}$ be defined by
-  \[
-    w(l) = \begin{cases}
-      m(a_i)/2 & \text{if } l = \phi_i \text{ or } l = \neg\phi_i \text{ for
-        some } i \in [n] \\
-      1 & \text{otherwise}
-    \end{cases}
-  \]
-  for all $l \in L'$, and note that this defines a WMC measure $m' =
-  \WMC_{w}\colon \mathbf{B'} \to \mathbb{R}_{\ge 0}$. Then
-  \[
-    m(a) = (m' \circ \iota)(a)
-  \]
-  for all $a \in \mathbf{B}$.
-\end{theorem}
-
-In other words, any measure can be computed using WMC by extending the BA with
-more literals. More precisely, we are given the left-hand column in
+  0}$. More precisely, we are given the left-hand column in
 \[
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-  \item Make $J$ depend on $i$.
-  \item Find a reference for this first claim in the following proof.
-  \end{itemize}
-}
-\begin{proof}
-  Since $\mathbf{B}$ is free over $S$, each atom $a_i \in \mathbf{B}$ is an
-  infimum of elements in $L$, i.e.,
-  \[
-    a_i = \bigwedge_{j \in J} a_{i,j}
-  \]
-  for some $\{ a_{i,j} \}_{j \in J} \subset L$. Moreover, each atom $b \in
-  \mathbf{B'}$ can be represented as either $b = \phi_i \land a_i$ or $b =
-  \neg\phi_i \land a_i$ for some atom $a_i \in \mathbf{B}$, also making it an
-  infimum over a subset of $L'$. Then, for any $b \in \mathbf{B}$,
-  \[
-    (m' \circ \iota)(b) = \sum_{\substack{\text{atoms } a_i \in \mathbf{B}:\\
-        \phi_i \land a_i \le \iota(b)}} (w(\phi_i) + w(\neg\phi_i)) \prod_{j \in
-    J} w(a_{i,j}),
-  \]
-  recognising that, for any $\iota(b)$, any atom $a_i \in \mathbf{B}$ satisfies
-  $\phi_i \land a_i \le \iota(b)$ if and only if it satisfies $\neg\phi_i \land
-  a_i \le \iota(b)$. Then, according to the definition of $w$,
-  \[
-    (m' \circ \iota)(b) = \sum_{\substack{\text{atoms } a_i \in \mathbf{B}:\\
-        \phi_i \land a_i \le \iota(b)}} (w(\phi_i) + w(\neg\phi_i)) =
-    \sum_{\substack{\text{atoms } a_i \in \mathbf{B}:\\ \phi_i \land a_i \le
-        \iota(b)}} m(a_i) = m(b),
-  \]
-  provided that
-  \[
-    \phi_i \land a_i \le \iota(b) \quad \text{if and only if} \quad a_i \le b,
-  \]
-  but this is equivalent to
-  \[
-    \phi_i \land a_i = \phi_i \land a_i \land b \quad \text{if and only if}
-    \quad a_i = a_i \land b
-  \]
-  which is true because $\phi_i \not\in L$.
-\end{proof}
-
-Now we can show that the construction in \cref{thm:extension} is smallest
-possible.
-
-\begin{conjecture}
-  Let $\mathbf{B}$ and $\mathbf{B'}$ be Boolean algebras, and $\iota\colon
-  \mathbf{B} \hookrightarrow \mathbf{B'}$ be the inclusion map such that
-  $\mathbf{B}$ is free over $L$, all atoms of $\mathbf{B'}$ can be
-  expressed as meets of elements of $L'$, and the following subset relations are
-  satisfied:
-  \[
-    \begin{tikzcd}
-      \mathbf{B} \ar[r,hookrightarrow,"\iota"] & \mathbf{B'} \\
-      L \arrow[Subset]{u}{} \arrow[Subset]{r}{} & L' \arrow[Subset]{u}{}
-    \end{tikzcd}
-  \]
-  If, for any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$, one can
-  construct a weight function $w\colon L' \to \mathbb{R}_{\ge 0}$ such that the WMC
-  measure $\WMC\colon \mathbf{B'} \to \mathbb{R}_{\ge 0}$ with respect to $w$
-  satisfies
-  \[
-    m = \WMC \circ \iota,
-  \]
-  then $|L' \setminus L| \ge 2^{|L|+1}$.
-\end{conjecture}
-% \begin{proof}
-%   % 1. An atom in B' must have more than just elements of L.
-%   Let $a$ be an atom in $\mathbf{B}$, and let $b$ be an atom in $\mathbf{B'}$
-%   such that $b \le a$. First, let us notice that as long as $|L| \ge
-%   4$\footnote{Note that $|L|$ has to be an even number.}, $b \ne a$. Indeed, let
-%   $p, r, \neg p, \neg r \in L$. Then
-%   \begin{align*}
-%     (\WMC \circ \iota)(p \land r) &= w(p)w(r), \\
-%     (\WMC \circ \iota)(p \land \neg r) &= w(p)w(\neg r), \\
-%     (\WMC \circ \iota)(\neg p \land r) &= w(\neg p)w(r), \\
-%     (\WMC \circ \iota)(\neg p \land \neg r) &= w(\neg p)w(\neg r), \\
-%   \end{align*}
-%   But then we have that
-%   \[
-%     \frac{m(p \land r)}{m(\neg p \land r)} = \frac{w(p)}{w(\neg p)} =
-%     \frac{m(p \land \neg r)}{m(\neg p \land \neg r)}.
-%   \]
-%   This places a condition on $m$, contradicting the assumption that the
-%   construction works for an arbitrary $m$. Hence $b < a$.
-
-%   Second, we can show that if $b = a \land \bigwedge_{i = 1}^k \phi_i$ for some
-%   positive integer $k$, then there must also be $2^k - 1$ other atoms in
-%   $\mathbf{B'}$ that correspond to every possible way to negate a subset of
-%   $\phi_i$'s, i.e., ranging from
-
-%   % 2. If we add phi, then we must also add -phi.
-%   % 3. Extension to multiple literals: we must have all (2^n) combinations of
-%   % added literals).
-%   % 4. Profit
-% \end{proof}
-
-Let us note how our lower bound on the number of added literals compares to two
-methods of translating a discrete probability distribution into a WMC problem
-over a propositional knowledge base proposed by Darwiche
-\cite{DBLP:conf/kr/Darwiche02} and Sang et al. \cite{DBLP:conf/aaai/SangBK05}.
-Suppose we have a discrete probability distribution with  $n$ variables, and the
-$i$th variable has $v_i$ values, for each $i \in [n]$. Interpreted as a logical
-system, it has $\prod_{i=1}^n v_i$ models. My expansion would then use
-\[
-  \sum_{i=1}^n v_i + 2\prod_{i=1}^n v_i
-\]
-variables, i.e., a variable for each possible variable-value assignment, and two
-additional variables for each model. Without making any independence
-assumptions, the encoding by Darwiche \cite{DBLP:conf/kr/Darwiche02} would use
-\[
-  \sum_{i=1}^n v_i + \sum_{i=1}^n \prod_{j=1}^i v_j
-\]
-variables, while for the encoding by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
-\[
-  \sum_{i=1}^n v_i + \sum_{i=1}^n (v_i - 1) \prod_{j=1}^{i-1} v_j
-\]
-variables would suffice.
+\todo[inline]{Must quotient the BA w.r.t. some rules.}
 
@@
 \begin{itemize}
-\item All encodings (including my non-binary encoding) live on a measure Boolean
-  algebra where the measure is not probabilistic (so $\Pr(\neg A) \ne 1 -
-  \Pr(A)$).
 \item \texttt{cd05} relaxes the encoding so much that extra models become
@@
 
-\section{The Algebra of Functions on Boolean Algebras}
-
-\begin{itemize}
-\item Could clarify why $[\lambda_{X=0}] = \overline{[\lambda_{X=1}]}$. This
-  follows from the definition. Or should I avoid the overline notation?
-\item Prove that we have an algebra of functions with two (?) additional
-  operations. Or maybe just cite the original paper for this.
-\end{itemize}
-
-Let $V$ denote the set of random variables in a Bayesian network. For any random
-variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of parents of $X$ and
-$\im X$ denote the set of possible values.
-
-\begin{definition}[Indicator variables]
-  Let $X \in V$ be a random variable. If $X$ is binary (i.e., $|\im X| = 2$), we
-  can arbitrary identify one of the values as $1$ and the other one as $0$ (i.e,
-  $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
-  \emph{indicator variable} $\lambda_{X=1}$. If we interpret
-  $2^{\{\lambda_{X=1}\}}$ as a Boolean algebra, we can let $\lambda_{X=0} =
-  \neg\lambda_{X=1}$ in the algebraic notation, or, equivalently, $\lambda_{X=0}
-  = \emptyset \in 2^{\{\lambda_{X=1}\}}$ in the set-theoretic notation. On the
-  other hand, if $X$ is not binary, we represent $X$ with $|\im X|$ indicator
-  variables, one for each value. We let
-  \[
-    E(X) = \begin{cases}
-      \{ \lambda_{X=1} \} & \text{if } |\im X| = 2 \\
-      \{ \lambda_{X=x} \mid x \in \im X \} & \text{otherwise.}
-    \end{cases}
-  \]
-  denote the set of indicator variables for $X$ and
-  \[
-    E^*(X) = E(X) \cup \bigcup_{Y \in \mathrm{pa}(X)} E(Y).
-  \]
-  denote the set of indicator variables for $X$ and its parents in the Bayesian
-  network. Finally, let
-  \[
-    U = \bigcup_{X \in V} E(X)
-  \]
-  denote the set of all indicator variables for all random variables in the
-  Bayesian network.
-\end{definition}
-
-\begin{definition}[Operations on functions]
-  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
-    0}$ be Boolean functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We
-  define the following operations:
-  \begin{description}
-  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
-    \mathbb{R}_{\ge 0}$ such that
-    \[
-      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
-    \]
-    for all $\tau \in 2^{X \cup Y}$.
-  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
-    \mathbb{R}_{\ge 0}$ such that
-    \[
-      \overline{A}(\tau) = 1 - A(\tau)
-    \]
-    for all $\tau \in 2^X$.
-  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
-    \to \mathbb{R}_{\ge 0}$ such that
-    \[
-      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
-    \]
-    for all $\tau \in 2^{X \cup Y}$.
-  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
-    \mathbb{R}_{\ge 0}$ such that
-    \[
-      (\alpha A)(\tau) = \alpha \cdot A(\tau)
-    \]
-    for all $\tau \in 2^X$.
-  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
-      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
-    \[
-      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
-    \]
-    for all $\tau \in 2^{X \setminus \{x \}}$.
-  \end{description}
-\end{definition}
-Note that both addition and multiplication commute.
-
-\begin{definition}[Special functions]
-  \phantom{}
-  \begin{itemize}
-  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\tau) = 1$.
-  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\tau) = 0$.
-  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
-    \[
-      [a](\tau) =
-      \begin{cases}
-        1 & \text{if } a \in \tau \\
-        0 & \text{if } a \not\in \tau.
-      \end{cases}
-    \]
-  \end{itemize}
-\end{definition}
-
-\begin{remark}
-  For any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A + \overline{A} = 1$.
-\end{remark}
-
-Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
-$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
-
-\section{Encoding Bayesian Networks Using Conditional Measures}
-
-\begin{itemize}
-\item We assume that the first literal after `w' is positive.
-\item The last two numbers are the positive and the negative probabilities,
-  respectively---sometimes they add to one, and sometimes the negative
-  probability is one, regardless of the value of the first probability.
+References
+\begin{itemize}
+\item ADDs \cite{DBLP:journals/fmsd/BaharFGHMPS97}
+\item background reading
+  \begin{itemize}
+  \item Compiling Bayesian Networks Using Variable Elimination (Chavira and
+    Darwiche) \cite{DBLP:conf/ijcai/ChaviraD07}
+  \item On the Relationship between Sum-Product Networks and Bayesian Networks
+    (Zhao et al.) \cite{DBLP:conf/icml/ZhaoMP15}
+  \end{itemize}
+\end{itemize}
+
+\section{Encoding Bayesian Networks Using Conditional Weights}
+
+\begin{itemize}
+
 \item We assume that all variables in the Bayesian network have at least two
@@
 \item The function $\phi$ created by the algorithm can be seen as a measure on
-  the BA $2^U$.
+  the BA $2^{2^U}$.
 \item We extend the Gaifman graph to add edges when two variables occur in the
@@
 \end{itemize}
+
+Let $V$ denote the set of random variables in a Bayesian network. For any random
+variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of parents of $X$ and
+$\im X$ denote the set of possible values.
+
+\begin{definition}[Indicator variables]
+  Let $X \in V$ be a random variable. If $X$ is binary (i.e., $|\im X| = 2$), we
+  can arbitrary identify one of the values as $1$ and the other one as $0$ (i.e,
+  $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
+  \emph{indicator variable} $\lambda_{X=1}$. For notational simplicity, for any
+  set $S$, whenever we write $\lambda_{X=0} \in S$ or $S = \{ \lambda_{X=0},
+  \dots \}$, we actually mean $\lambda_{X=1} \not\in S$,
+
+  On the other hand, if $X$ is not binary, we represent $X$ with $|\im X|$
+  indicator variables, one for each value. We let
+  \[
+    E(X) = \begin{cases}
+      \{ \lambda_{X=1} \} & \text{if } |\im X| = 2 \\
+      \{ \lambda_{X=x} \mid x \in \im X \} & \text{otherwise.}
+    \end{cases}
+  \]
+  denote the set of indicator variables for $X$ and
+  \[
+    E^*(X) = E(X) \cup \bigcup_{Y \in \mathrm{pa}(X)} E(Y).
+  \]
+  denote the set of indicator variables for $X$ and its parents in the Bayesian
+  network. Finally, let
+  \[
+    U = \bigcup_{X \in V} E(X)
+  \]
+  denote the set of all indicator variables for all random variables in the
+  Bayesian network.
+\end{definition}
 
@@
   \[
-    \mathrm{CPT}_X \left( \lambda_{X=x} \land \bigwedge_{i=1}^n
-      \lambda_{Y_i=y_i} \right) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
+    \mathrm{CPT}_X (\{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1,
+    \dots, n \}) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
   \]
@@
 \begin{proof}
-  Let
-  \[
-    \tau = \lambda_{X=x} \land \bigwedge_{i=1}^n \lambda_{Y_i=y_i}.
-  \]
-  If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im Y_i|$
-  terms, one for each possible assignment of values to variables $X, Y_1, \dots,
-  Y_n$. Exactly one of these terms is nonzero when applied to $\tau$, and it is
-  equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
+  Let $\tau = \{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1, \dots, n
+  \}$. If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
+  Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
+  \dots, Y_n$. Exactly one of these terms is nonzero when applied to $\tau$, and
+  it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
 
@@
     \begin{cases}
-      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } \tau = \bigwedge_{i=1}^n
-      \lambda_{X_i = x_i} \text{ for some } (x_1, \dots, x_n) \in \prod_{i=1}^n
-      \im X_i \\
+      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } \tau = \{ \lambda_{X_i=x_i}
+      \mid i = 1, \dots, n \} \text{ for some } (x_1, \dots, x_n) \in
+      \prod_{i=1}^n \im X_i \\
       0 & \text{otherwise,}
@@
 \begin{proof}
-  If
-  \[
-    \tau = \bigwedge_{X \in V} \lambda_{X = v_X}
-  \]
-  for some $(v_X)_{X \in V} \in \prod_{X \in V} \im X$, then
+  If $\tau = \{ \lambda_{X=v_X} \mid X \in V \}$ for some $(v_X)_{X \in V} \in
+  \prod_{X \in V} \im X$, then
   \[
@@
 
+The last two numbers are the positive and the negative probabilities,
+respectively---sometimes they add to one, and sometimes the negative probability
+is one, regardless of the value of the first probability.
+
 \section{Experimental Comparison}
@@
 \begin{itemize}
+\item Bayesian networks and ADDMC are only particular examples. This should also
+  work with Cachet.
 \item Extra benefit: one does not need to come up with a way to turn some
@@
 \item Important future work: replacing ADDs with
-  AADDs\footnote{\url{https://github.com/ssanner/dd-inference}} is likely to
-  bring performance benefits. Other extensions:
+  AADDs\footnote{\url{https://github.com/ssanner/dd-inference}}
+  \cite{DBLP:conf/ijcai/SannerM05} is likely to bring performance benefits.
+  Other extensions:
   \begin{itemize}

### 2020-07-21 paper.tex
Partial updates to the old proofs

@@
   $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
-\item ADDMC should probably be in textsc mode.
 \end{itemize}
@@
   set. Literals should be $U$.
+\item Describe the parallel between BAs and powersets.
+\item Describe \cref{tbl:notation_example} as an example. We will use
+  set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$
+  (except for atoms).
 \end{itemize}
@@
   \caption{(in the same order)}
+  \label{tbl:notation_example}
   \centering
@@
 
-\begin{definition} \label{def:ba}
-  A \emph{Boolean algebra} (BA) is a tuple $(\mathbf{B}, \land, \lor, \neg, 0,
-  1)$ consisting of a set $\mathbf{B}$ with binary operations \emph{meet}
-  $\land$ and \emph{join} $\lor$, unary operation $\neg$ and elements $0, 1 \in
-  \mathbf{B}$ such that the following axioms hold for all $a, b, \in
-  \mathbf{B}$:
-  \begin{itemize}
-  \item both $\land$ and $\lor$ are associative and commutative;
-  \item $a \lor (a \land b) = a$, and $a \land (a \lor b) = a$;
-  \item $0$ is the identity of $\lor$, and $1$ is the identity of $\land$;
-  \item $\lor$ distributes over $\land$ and vice versa;
-  \item $a \lor \neg a = 1$, and $a \land \neg a = 0$.
-  \end{itemize}
-\end{definition}
-
-For clarity and succinctness, we will occasionally use three other operations
-that can be defined using the original three\footnote{We use $+$ to denote
-  symmetric difference because it is the additive operation of a Boolean ring.}:
-\begin{align*}
-  a \to b &= \neg a \lor b, \\
-  a \leftrightarrow b &= (a \land b) \lor (\neg a \land \neg b), \\
-  a + b &= (a \land \neg b) \lor (\neg a \land b).
-\end{align*}
-We can also define a partial order $\le$ on $\mathbf{B}$ as $a \le b$ if $a = b
-\land a$ (or, equivalently, $a \lor b = b$) for all $a, b \in \mathbf{B}$.
-Furthermore, let $a < b$ denote $a \le b$ and $a \ne b$. For the rest of this
-paper, let $\mathbf{B}$ refer to the BA $(\mathbf{B}, \land, \lor, \neg, 0, 1)$.
-For any $S \subseteq \mathbf{B}$, we write $\bigvee S$ for $\bigvee_{x \in S} x$
-and call it the \emph{supremum} of $S$. Similarly, $\bigwedge S = \bigwedge_{x
-  \in S} x$ is the \emph{infimum}. By convention, $\bigwedge \emptyset = 1$ and
-$\bigvee \emptyset = 0$. For any $a, b \in \mathbf{B}$, we say that $a$ and $b$
-are \emph{disjoint} if $a \land b = 0$.
+Consider the Boolean algebra $(2^{2^U}, \land, \lor, \neg, \bot, \top)$. A
+partial order $\le$ on $2^{2^U}$ is defined by $a \le b$ if $a = b \land a$ (or,
+equivalently, $a \lor b = b$) for all $a, b \in 2^{2^U}$.
 
 \begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
-  An element $a \ne 0$ of $\mathbf{B}$ is an \emph{atom} if, for all $x \in
-  \mathbf{B}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne
-  0$ is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$. We say
-  that $\mathbf{B}$ is \emph{atomic} if for every $a \in \mathbf{B} \setminus \{0
-  \}$, there is an atom $x$ such that $x \le a$.
+  An element $a \ne 0$ of $2^{2^U}$ is an \emph{atom} if, for all $x \in
+  2^{2^U}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne 0$
+  is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$.
+  Equivalently, $a \ne 0$ is an atom if $|a| = 1$, i.e., $a = \{ u \}$ for some
+  $u \in 2^U$ (this is how we will denote atoms in the remainder of the paper).
+  Note that atoms in Boolean algebras correspond to models.
 \end{definition}
-
-\begin{lemma}[\cite{ganesh2006introduction}]
-  For any two distinct atoms $a$, $b \in \mathbf{B}$, $a \land b = 0$.
-\end{lemma}
 
@@
   \end{itemize}
-\end{lemma}
-
-\begin{lemma}[\cite{givant2008introduction}] \label{lemma:atomic}
-  All finite BAs are atomic.
 \end{lemma}
@@
 \item Be careful about mentioning ideals and quotients.
-\item Note that we're going to use logical notation for BAs. Give an example of
-  the two notations.
 \end{itemize}
 
+\begin{definition} \label{def:wmc}
+  Let $U$ be an arbitrary set. Then
+  \begin{itemize}
+  \item a \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$,
+  \item a \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
+      0}$.
+  \item a weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
+    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
+  \item every weight function induces a measure:
+    \[
+      M_W(x) = \begin{cases}
+        0 & \text{if } x = \bot \\
+        W(u) & \text{if } x = \{ u \} \\
+        \sum_{\{u\} \le x} W(u) & \text{otherwise.}
+      \end{cases}
+    \]
+    The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$
+    with a given definition of $W$ is known as \emph{weighted model counting}.
+  \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
+    \emph{factorable} if there exists a factored weight function $W\colon 2^U
+    \to \mathbb{R}_{\ge 0}$ that induces $M$.
+  \end{itemize}
+\end{definition}
+
 \begin{example} \label{example:construction}
-  % TODO: keep this, but might need a lot of editing.
   Let $\mathcal{L}$ be a propositional logic with $p$ and $q$ as its only atoms.
@@
 
-\begin{definition} \label{def:wmc}
-  Let $U$ be an arbitrary set. Then
-  \begin{itemize}
-  \item a \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$,
-  \item a \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
-      0}$.
-  \item a weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
-    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
-  \item every weight function induces a measure:
-    \[
-      M_W(x) = \begin{cases}
-        0 & \text{if } x = \emptyset \\
-        W(u) & \text{if } x = \{ u \} \\
-        \sum_{\{u\} \le x} W(u) & \text{otherwise.}
-      \end{cases}
-    \]
-    The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$
-    with a given definition of $W$ is known as \emph{weighted model counting}.
-  \end{itemize}
-\end{definition}
-
 Given a theory $\Delta$ in a logic $\mathcal{L}$, the usual way of using WMC to
@@
 
-\section{Limitations of Factored Weighted Model Counting}
+\section{Limitations of Factorable Measures}
 
@@
 \begin{lemma} \label{lemma:before_theorem}
-  For any measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ and elements $a, b
-  \in \mathbf{B}$,
+  For any measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ and elements $a, b
+  \in 2^{2^U}$,
   \begin{equation} \label{eq:to_prove}
-    m(a \land b) = m(a)m(b)
+    M(a \land b) = M(a)M(b)
   \end{equation}
@@
   \begin{equation} \label{eq:to_prove2}
-    m(a \land b) \cdot m(\neg a \land \neg b) = m(a \land \neg b)
-    \cdot m(\neg a \land b).
+    M(a \land b) \cdot M(\neg a \land \neg b) = M(a \land \neg b)
+    \cdot M(\neg a \land b).
   \end{equation}
@@
   \begin{equation} \label{eq:temp}
-    m(a) = m(a \land b) + m(a \land \neg b).
+    M(a) = M(a \land b) + M(a \land \neg b).
   \end{equation}
-  Applying \cref{eq:temp} and the equivalent expression for $m(b)$ allows us
+  Applying \cref{eq:temp} and the equivalent expression for $M(b)$ allows us
   to rewrite \cref{eq:to_prove} as
   \[
-    m(a \land b) = [m(a \land b) + m(a \land \neg b)][m(a \land b) + m(\neg a
+    M(a \land b) = [M(a \land b) + M(a \land \neg b)][M(a \land b) + M(\neg a
     \land b)]
@@
   \begin{equation} \label{eq:temp6}
-    m(a \land b)[1 - m(a \land b) - m(a \land \neg b) - m(\neg a \land b)] = m(a
-    \land \neg b)m(\neg a \land b).
+    M(a \land b)[1 - M(a \land b) - M(a \land \neg b) - M(\neg a \land b)] = M(a
+    \land \neg b)M(\neg a \land b).
   \end{equation}
@@
   \[
-    m(a \land b) + m(a \land \neg b) + m(\neg a \land b) + m(\neg a \land \neg
+    M(a \land b) + M(a \land \neg b) + M(\neg a \land b) + M(\neg a \land \neg
     b) = 1,
@@
 \begin{theorem}
-  Let $\mathbf{B}$ be a free BA over $\{ l_i \}_{i=1}^n$ (for some $n \in
-  \mathbb{N}$) with measure $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$, and let
-  $L = \{ l_i \}_{i = 1}^n \cup \{ \neg l_i \}_{i = 1}^n$. Then there exists a
-  weight function $w\colon L \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$ if
-  and only if
+  A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is factorable if and only
+  if
   \begin{equation} \label{eq:wmccondition}
-  m(l \land l') = m(l)m(l')
+  M(u \land v) = M(u)M(v)
   \end{equation}
-  for all distinct $l, l' \in L$ such that $l \ne \neg l'$.
+  for all distinct $u, v \in U \cup \{ \neg w \mid w \in U \}$ such that $u \ne
+  \neg v$.
 \end{theorem}
+\begin{proof}
+  ($\Leftarrow$) For each $x \in U$, let $W_x\colon 2^{\{x\}} \to
+  \mathbb{R}_{\ge 0}$ be defined by $W_x(\{ x \}) = M(x)$ and $W_x(\emptyset) =
+  M(\neg x)$. Let $M_W$ be the measure induced by
+  \[
+    W = \prod_{x \in U} W_x.
+  \]
+  We will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by the
+  definitions of both $M_w$ and $M$. Second, let
+  \begin{equation} \label{eq:def_of_a}
+    a = \bigwedge_{u \in U} a_u
+  \end{equation}
+  be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$.
+  Then
+  \[
+    M_W(a) = \prod_{u \in U} W_u(a_u) = \prod_{u \in U} M(a_u) = M
+    \left(\bigwedge_{u \in U} a_u \right) = M(a)
+  \] % TODO: by what?
+  by \cref{def:wmc,eq:wmccondition,eq:def_of_a}. Finally, note that if $M_W$ and
+  $M$ agree on all atoms, then they must also agree on all other non-zero
+  elements of the Boolean algebra.
 
-\begin{remark}
-  Note that if $n = 1$, then \cref{eq:wmccondition} is vacuously satisfied and
-  so any valid measure can be expressed as WMC.
-\end{remark}
-
-\begin{proof}
-  ($\Leftarrow$) Let $w\colon L \to \mathbb{R}_{\ge 0}$ be defined by
-  \begin{equation} \label{eq:assumption}
-    w(l) = m(l)
-  \end{equation}
-  for all $l \in L$. We are going to show that $\WMC_w = m$. First, note that
-  $\WMC_w(0) = 0 = m(0)$ by the definitions of both $\WMC_w$ and $m$. Second,
-  let
-  \begin{equation} \label{eq:def_of_a}
-    a = \bigwedge_{i=1}^n a_i
-  \end{equation}
-  be an atom in $\mathbf{B}$ such that $a_i \in \{ l_i, \neg l_i \}$ for all $i
-  \in [n]$. Then
+  ($\Rightarrow$) For the other direction, we are given a factored weight
+  function
   \[
-    \WMC(a) = \prod_{i=1}^n w(a_i) = \prod_{i=1}^n m(a_i) = m
-    \left(\bigwedge_{i=1}^n a_i \right) = m(a)
+    W = \prod_{x \in U} W_x,
   \]
-  by \cref{def:wmc,eq:assumption,eq:wmccondition,eq:def_of_a}. Finally, note
-  that if $\WMC$ and $m$ agree on all atoms, then they must also agree on all
-  other non-zero elements of the Boolean algebra.
-
-  ($\Rightarrow$) For the other direction, we are given a weight function
-  $w\colon L \to \mathbb{R}_{\ge 0}$ that induces a measure $m = \WMC_w\colon
-  \mathbf{B} \to \mathbb{R}_{\ge 0}$, and we want to show that
-  \cref{eq:wmccondition} is satisfied. Let $k_i, k_j \in L$ be such that $k_i
-  \in \{ l_i, \neg l_i \}$, $k_j \in \{ l_j, \neg l_j \}$, and $i \ne j$ for
-  some $i, j \in [n]$. We then want to show that
+  and we want to show that its induced measure $M_W$ satisfies
+  \cref{eq:wmccondition}. Let $k_u, k_v \in U \cup \{ \neg w \mid w \in U \}$ be
+  such that $k_u \in \{ u, \neg u \}$, $k_v \in \{ v, \neg v \}$, and $u \ne v$.
+  We then want to show that
   \begin{equation} \label{eq:to_prove3}
-    m(k_i \land k_j) = m(k_i)m(k_j)
+    M_W(k_u \land k_v) = M_W(k_u)M_W(k_v)
   \end{equation}
@@
   \begin{equation} \label{eq:to_prove4}
-    m(k_i \land k_j) \cdot m(\neg k_i \land \neg k_j) = m(k_i \land \neg k_j)
-    \cdot m(\neg k_i \land k_j)
+    M_W(k_u \land k_v) \cdot M_W(\neg k_u \land \neg k_v) = M_W(k_u \land \neg k_v) \cdot M_w(\neg k_u \land k_v)
   \end{equation}
@@
   \begin{align*}
-    \WMC(k_i \land k_j) &= \sum_{\text{atoms } a \le k_i \land k_j} \WMC(a) = \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n]} w(a_m) \\
-                        &= \sum_{\text{atoms } a \le k_i \land k_j} w(a_i)w(a_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = \sum_{\text{atoms } a \le k_i \land k_j} w(k_i)w(k_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) \\
-    &= w(k_i)w(k_j) \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = w(k_i)w(k_j)C,
+    M_W(k_u \land k_v) &= \sum_{\{a\} \le k_u \land k_v} W(a) = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U} W_x(a) \\
+                        &= \sum_{\{a\} \le k_u \land k_v} W_u(a_u)W_v(a_v) \prod_{x \in U \setminus \{ u, v \}} W_x(a) = \sum_{\{a\} \le k_u \land k_v} W_u(k_u)W_v(k_v) \prod_{x \in U \setminus \{ u, v \}} W_x(a) \\
+    &= W_u(k_u)W_v(k_v) \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}} W_x(a) = W_u(k_u)W_v(k_v)C,
   \end{align*}
-  where $C$ denotes the part of $\WMC(k_i \land k_j)$ that will be the same for
-  $\WMC(\neg k_i \land k_j)$, $\WMC(k_i \land \neg k_j)$, and $\WMC(\neg k_i
-  \land \neg k_j)$ as well. But then \cref{eq:to_prove4} becomes
+  where $C$ denotes the part of $M_W(k_u \land k_v)$ that will be the same for
+  $M_W(\neg k_u \land k_v)$, $M_W(k_u \land \neg k_v)$, and $M_W(\neg k_u \land
+  \neg k_v)$ as well. But then \cref{eq:to_prove4} becomes
   \[
-    w(k_i)w(k_j)w(\neg k_i)w(\neg k_j)C^2 = w(k_i)w(\neg k_j)w(\neg k_i)w(k_j)C^2
+    W_u(k_u)W_v(k_v)W_u(\neg k_u)W_v(\neg k_v)C^2 = W_u(k_u)W_v(\neg
+    k_v)W_u(\neg k_u)W_v(k_v)C^2
   \]

### 2020-07-25 paper.tex
Make the paper 5% more readable

@@
 
-\section{Preliminaries}
+\section{Boolean Algebras and Power Sets}
 
-\begin{itemize}
-\item Make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x, y$?).
-\item Terminology: `with generating set $S$' $\to$ `over $S$'.
-\item Notation: if $L$ denotes literals, then it doesn't denote a generating
-  set. Literals should be $U$.
-\item Describe the parallel between BAs and powersets.
-\item Describe \cref{tbl:notation_example} as an example. We will use
-  set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$
-  (except for atoms).
-\end{itemize}
+\todo[inline]{
+  Notation: make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x,
+  y$?).
+}
 
 \begin{table}
-  \caption{(in the same order)}
-  \label{tbl:notation_example}
   \centering
-  \begin{tabular}{lcc}
+  \caption{A comparison of Boolean-algebraic (BA) and set-theoretic (ST)
+    concepts for $2^X$ for some set $X$}
+  \label{tbl:notation}
+  \begin{tabular}{lccl}
     \toprule
-    & Set-theoretic notation & Boolean-algebraic notation \\
+    BA name & BA symbol & ST symbol & ST name \\
     \midrule
-    Atoms (elements of $U$) & $a, b$ & $a, b$ \\
-    \rowcolor{gray!10} Models (elements of $2^U$) & $\emptyset, \{a\}, \{b\}, \{a, b\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
-    & $\{ \emptyset, \{a\}, \{b\}, \{a, b\} \}$ & $\top$ \\
-    & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{a\}, \{a, b\} \}$ & $\neg a \lor \neg b, a \to b$ \\
-    & $\{ \emptyset, \{b\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ & $b \to a, a \lor b$ \\
-    & $\{\emptyset, \{a\}\}, \{\emptyset, \{b\}\}, \{\emptyset, \{a, b\}\}$ & $\neg b, \neg a, a \leftrightarrow b$ \\
-    & $\{\{a\}, \{b\}\}, \{\{a\}, \{a, b\}\}, \{\{b\}, \{a, b\}\}$ & $(a \land \neg b) \lor (b \land \neg a), a, b$ \\
-    & $\{\emptyset\}, \{\{a\}\}, \{\{b\}\}, \{\{a, b\}\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
-    \multirow{-7}{*}{Formulas (elements of $2^{2^U}$)} & $\emptyset$ & $\bot$ \\
+    bottom & $\bot$ & $\emptyset$ & empty set \\
+    top & $\top$ & $X$ & \\
+    meet, and & $\land$ & $\cap$ & intersection \\
+    join, or & $\lor$ & $\cup$ & union \\
+    complement, not & $\neg$ & $^c$ & complement \\
+            & $\le$ & $\subseteq$ & subset relation, set inclusion \\
+    atom & & & singleton, unit set \\
     \bottomrule
@@
 
-Consider the Boolean algebra $(2^{2^U}, \land, \lor, \neg, \bot, \top)$. A
-partial order $\le$ on $2^{2^U}$ is defined by $a \le b$ if $a = b \land a$ (or,
-equivalently, $a \lor b = b$) for all $a, b \in 2^{2^U}$.
-
-\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
-  An element $a \ne 0$ of $2^{2^U}$ is an \emph{atom} if, for all $x \in
-  2^{2^U}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne 0$
-  is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$.
-  Equivalently, $a \ne 0$ is an atom if $|a| = 1$, i.e., $a = \{ u \}$ for some
-  $u \in 2^U$ (this is how we will denote atoms in the remainder of the paper).
-  Note that atoms in Boolean algebras correspond to models.
-\end{definition}
-
-\begin{lemma}[\cite{givant2008introduction}] \label{thm:representation}
-  The following are equivalent:
-  \begin{itemize}
-  \item $\mathbf{B}$ is atomic.
-  \item For any $x \in \mathbf{B}$, $x = \bigvee_{\text{atoms } a \le x} a$.
-  \item $1$ is the supremum of all atoms.
-  \end{itemize}
-\end{lemma}
-
-\begin{definition}[\cite{gaifman1964concerning,DBLP:books/daglib/0090259}] \label{def:measure}
-  A \emph{measure} on $\mathbf{B}$ is a function $m\colon
-  \mathbf{B} \to \mathbb{R}_{\ge 0}$ such that:
-  \begin{itemize}
-  \item $m(0) = 0$;
-  \item $m(a \lor b) = m(a) + m(b)$ for all $a, b \in \mathbf{B}$ whenever $a
-    \land b = 0$.
-  \end{itemize}
-  If $m(1) = 1$, we call $m$ a \emph{probability measure}. Also, if $m(x) > 0$
-  for all $x \ne 0$, then $m$ is \emph{strictly positive}.
-\end{definition}
-
-\begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:order}
-  For any $a, b \in \mathbf{B}$, $a \le b$ if and only if $a \land \neg b = 0$.
-\end{lemma}
-
-\begin{lemma}[\cite{givant2008introduction}] \label{lemma:measure_and_order}
-  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. Then for all $a,
-  b \in \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
-\end{lemma}
+Let $X$ be a set and let $2^X$ be its power set. We can equivalently interpret
+$2^X$ as a Boolean algebra. See \cref{tbl:notation} for a summary of the
+differences in terminology and notation. We will use both.
 
@@
   Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
-    0}$ be Boolean functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We
-  define the following operations:
+    0}$ be arbitrary functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$.
+  We define the following operations:
   \begin{description}
@@
 \begin{observation}
-  Let $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0} \mid X \subseteq U
-  \}$. Then $\mathcal{V}$ is a semi-vector space with three additional
-  operations: inverse, (non-scalar) multiplication, and projection.
+  Let $U$ be a set, and $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0}
+  \mid X \subseteq U \}$. Then $\mathcal{V}$ is a semi-vector space with three
+  additional operations: inverse, (non-scalar) multiplication, and projection.
   Specifically, note that both addition and multiplication are both associative
@@
   \begin{itemize}
-  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\tau) = 1$.
-  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\tau) = 0$.
-  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
-    \[
-      [a](\tau) =
-      \begin{cases}
-        1 & \text{if } a \in \tau \\
-        0 & \text{if } a \not\in \tau.
-      \end{cases}
-    \]
+  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\emptyset) = 1$.
+  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\emptyset) = 0$.
+  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$, $[a](\emptyset) =
+    0$, $[a](\{a\}) = 1$.
   \end{itemize}
 \end{definition}
+
+Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
+$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
 
@@
 
-Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
-$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
-
 \section{Weighted Model Counting as a Measure}
@@
 \begin{itemize}
-\item[F2] Explain with examples: models $=$ elements [atoms] of algebra.
-\item Be careful about mentioning ideals and quotients.
+\item Describe \cref{tbl:notation_example} as an example.
+\item[F] Feedback: explain with examples: models $=$ atoms of algebra, formulas
+  $=$ all elements.
 \end{itemize}
@@
 \begin{definition} \label{def:wmc}
-  Let $U$ be an arbitrary set. Then
+  Let $U$ be a set.
   \begin{itemize}
-  \item a \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$,
-  \item a \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
+  \item A \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$
+    such that $M(\bot) = 0$ and
+    \[
+      M(a \lor b) = M(a) + M(b)
+    \]
+    for all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$.
+  \item A \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
       0}$.
-  \item a weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
+  \item A weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
     some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
-  \item every weight function induces a measure:
+  \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
+    \emph{factorable} if there exists a factored weight function $W\colon 2^U
+    \to \mathbb{R}_{\ge 0}$ that induces $M$.
+  \end{itemize}
+\end{definition}
+
+\begin{proposition}
+  Every weight function induces a measure:
   \[
@@
   \]
-    The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$
-    with a given definition of $W$ is known as \emph{weighted model counting}.
-  \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
-    \emph{factorable} if there exists a factored weight function $W\colon 2^U
-    \to \mathbb{R}_{\ge 0}$ that induces $M$.
-  \end{itemize}
-\end{definition}
+\end{proposition}
+The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$ with a
+given definition of $W$ is known as \emph{weighted model counting}.
+\begin{proof}
+  \todo[inline]{Prove that $M_W$ satisfies the definition of a measure.}
+\end{proof}
 
-\begin{example} \label{example:construction}
-  Let $\mathcal{L}$ be a propositional logic with $p$ and $q$ as its only atoms.
-  Then $L = \{ p, q, \neg p, \neg q \}$ is its set of literals. Let $w : L \to
-  \mathbb{R}_{\ge 0}$ be the \emph{weight function} defined by
+\begin{table}
+  \caption{(in the same order)}
+  \label{tbl:notation_example}
+  \centering
+  \begin{tabular}{lcc}
+    \toprule
+    & Set-theoretic notation & Boolean-algebraic notation \\
+    \midrule
+    Atoms (elements of $U$) & $a, b$ & $a, b$ \\
+    \rowcolor{gray!10} Models (elements of $2^U$) & $\emptyset, \{a\}, \{b\}, \{a, b\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
+    & $\{ \emptyset, \{a\}, \{b\}, \{a, b\} \}$ & $\top$ \\
+    & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{a\}, \{a, b\} \}$ & $\neg a \lor \neg b, a \to b$ \\
+    & $\{ \emptyset, \{b\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ & $b \to a, a \lor b$ \\
+    & $\{\emptyset, \{a\}\}, \{\emptyset, \{b\}\}, \{\emptyset, \{a, b\}\}$ & $\neg b, \neg a, a \leftrightarrow b$ \\
+    & $\{\{a\}, \{b\}\}, \{\{a\}, \{a, b\}\}, \{\{b\}, \{a, b\}\}$ & $(a \land \neg b) \lor (b \land \neg a), a, b$ \\
+    & $\{\emptyset\}, \{\{a\}\}, \{\{b\}\}, \{\{a, b\}\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
+    \multirow{-7}{*}{Formulas (elements of $2^{2^U}$)} & $\emptyset$ & $\bot$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{example}[Relation to the classical view of WMC] \label{example:construction}
+  Let $\mathcal{L}$ be a propositional logic with a set of atoms $U = \{ p, q
+  \}$. Let $w : \{ p, q, \neg p, \neg q \} \to \mathbb{R}_{\ge 0}$ be the
+  \emph{weight function} defined by
   \begin{align*}
-    w(p) = 0.3, \\
-    w(\neg p) = 0.7, \\
-    w(q) = 0.2, \\
-    w(\neg q) = 0.8.
+    w(p) = 0.3, \quad w(\neg p) = 0.7, \quad w(q) = 0.2, \quad w(\neg q) = 0.8.
   \end{align*}
@@
   $\Delta$ has two models, i.e., $\{ p, q \}$ and $\{ p, \neg q \}$. The
-  \emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of $\Delta$ is
-  then
-  \[
+  \emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of
+  $\Delta$ is then
+  \begin{equation} \label{eq:wmc_example}
     \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) =
     w(p)w(q) + w(p)w(\neg q) = 0.3.
+  \end{equation}
+
+  Alternatively, we can define $W_p\colon 2^{\{p\}} \to \mathbb{R}_{\ge 0}$ as
+  \[
+    W_p(\{ p \}) = 0.3, \quad W_p(\emptyset) = 0.7
   \]
+  and $W_q\colon 2^{\{q\}} \to \mathbb{R}_{\ge 0}$ as
+  \[
+    W_q(\{ q \}) = 0.2, \quad W_q(\emptyset) = 0.8.
+  \]
+  Let $M$ be the measure on $2^{2^U}$ induced by $W = W_p \cdot W_q$. Then,
+  equivalently to \cref{eq:wmc_example}, we can write
+  \[
+    M(p) = W(\{ p, q \}) + W(\{ p, \neg q \}) = W_p(\{p\})W_q(\{q\}) +
+    W_p(\{p\})W_q(\{\neg q\}) = 0.3.
+  \]
+\end{example}
 
-  The corresponding BA $B(\Delta)$ can then be constructed as a
-  Lindenbaum-Tarski algebra. Alternatively, one can first construct the free
-  BA generated by the set $\{ p, q \}$ and then take a quotient with respect to
-  either the filter generated by $p$ or the ideal\footnote{More details on these
-    concepts can be found in many books on BAs
-    \cite{givant2008introduction,koppelberg1989handbook}.} generated by $\neg
-  p$.
+For the rest of the paper, we let $U$ be the set of (logical) atoms. We use
+set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$,
+except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some
+model $x \in 2^U$.
 
-  Each element of $B(\mathcal{L})$ can also be seen as a subset of the set of
-  all models of $\mathcal{L}$, with $0$ representing $\emptyset$, $1$
-  representing the set of all (four) models, each atom representing a single
-  model, and each edge going upward representing a subset relation. Thus,
-  the Boolean-algebraic way of calculating the WMC of $\Delta$ consists of:
-  \begin{enumerate}
-  \item Identifying an element $a \in B(\mathcal{L})$ that corresponds to
-    $\Delta$.
-  \item Finding all atoms of $B(\mathcal{L})$ that are `dominated' by $a$
-    according to the partial order.
-  \item Using $w$ to calculate the weight of each such atom.
-  \item Adding the weights of these atoms.
-  \end{enumerate}
-  This motivates the following definition of WMC generalised to BAs.
-\end{example}
-\todo[inline,caption={}]{
-  \begin{itemize}
-  \item Why is Step 1 always possible?
-  \item Clarify what $B(L)$ means and whether $B(\Delta)$ is even necessary.
-  \item Find a reference for the set/subset thing.
-  \end{itemize}
-}
-
+\todo[inline]{Include this in the example.}
 Given a theory $\Delta$ in a logic $\mathcal{L}$, the usual way of using WMC to
@@
 \]
-In our algebraic formulation, this can be computed in two different ways:
-\begin{itemize}
-\item as $\frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}$ in $B(\mathcal{L})$,
-\item and as $\nWMC_w([q])$ in $B(\Delta)$.
-\end{itemize}
-But how does the measure defined on $B(\mathcal{L})$ transfer to $B(\Delta)$?
+In our algebraic formulation, this can be computed...
 
@@
     \left(\bigwedge_{u \in U} a_u \right) = M(a)
-  \] % TODO: by what?
+  \]
+  \todo{by what?}
   by \cref{def:wmc,eq:wmccondition,eq:def_of_a}. Finally, note that if $M_W$ and
@@
 
-Given this requirement for independence, a well-known way to represent
-probability distributions that do not consist entirely of independent variables
-is by adding more literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending
-the set $L$ covered by the WMC weight function $w\colon L \to \mathbb{R}_{\ge
-  0}$. More precisely, we are given the left-hand column in
-\[
-  \begin{tikzcd}
-    \textcolor{red}{\mathbb{R}_{\ge 0}} & & \\
-    \textcolor{red}{\mathbf{B}} \arrow[red]{u}{m} \ar[r,hookrightarrow,"\iota"]
-    & \mathbf{B'} \arrow{lu}[swap]{m'} & \\
-    \textcolor{red}{L} \ar[u,red,hookrightarrow] \ar[r,hookrightarrow] & L'
-    \ar[u,hookrightarrow] \arrow{r}{w} & \mathbb{R}_{\ge 0}
-  \end{tikzcd}
-\]
-and construct the remaining part in such a way that the triangle commutes.
-
-\todo[inline]{Must quotient the BA w.r.t. some rules.}
-
 \section{Previous Work}
@@
 \begin{itemize}
-\item \texttt{cd05} relaxes the encoding so much that extra models become
-  possible. They are supposed to be filtered out by the algorithm, but mine
-  can't do that because it doesn't deal with models. Same for \texttt{cd06}
-  because it's based on \texttt{cd05}.
-\item \texttt{sbk05} uses my trick with dividing probabilities. That could
-  explain small inaccuracies in its answers.
 \item Encodings:
@@
   \end{itemize}
+\item \texttt{cd05} relaxes the encoding so much that extra models become
+  possible. They are supposed to be filtered out by the algorithm, but mine
+  can't do that because it doesn't deal with models. Same for \texttt{cd06}
+  because it's based on \texttt{cd05}.
+\item \texttt{sbk05} uses my trick with dividing probabilities. That could
+  explain small inaccuracies in its answers.
 \end{itemize}
@@
   each instance and plot this ratio vs runtime (for each encoding, or at least
-  mine and D02)}
+  mine and D02). The new CP paper kind of beat me to it...}
 

### 2020-07-26 paper.tex
Some writing and editing

@@
 \usepackage{hyperref}
+\usepackage[ruled,vlined]{algorithm2e}
 \usepackage[capitalise]{cleveref}
@@
 \usepackage{soul}
-\usepackage[ruled,vlined]{algorithm2e}
 \usepackage{subcaption}
@@
 
-\begin{itemize}
-\item Describe \cref{tbl:notation_example} as an example.
-\item[F] Feedback: explain with examples: models $=$ atoms of algebra, formulas
-  $=$ all elements.
-\end{itemize}
+\todo[inline]{Describe \cref{tbl:notation_example} as an example.}
+\todo[inline]{Feedback: explain with examples: models $=$ atoms of algebra,
+  formulas $=$ all elements.}
 
@@
 
-\begin{proposition}
-  Every weight function induces a measure:
+\begin{proposition} \label{prop:measure}
+  Every weight function induces a measure, i.e, for any weight function $W\colon
+  2^U \to \mathbb{R}_{\ge 0}$, the function $M_W\colon 2^{2^U} \to
+  \mathbb{R}_{\ge 0}$, defined as
   \[
@@
       W(u) & \text{if } x = \{ u \} \\
-      \sum_{\{u\} \le x} W(u) & \text{otherwise.}
+      \sum_{\{u\} \le x} W(u) & \text{otherwise,}
     \end{cases}
   \]
+  is a measure.
 \end{proposition}
-The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$ with a
-given definition of $W$ is known as \emph{weighted model counting}.
 \begin{proof}
@@
 \end{proof}
+
+The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$ with a
+given definition of $W$ is known as \emph{weighted model counting}.
 
@@
   \begin{equation} \label{eq:wmc_example}
-    \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) =
-    w(p)w(q) + w(p)w(\neg q) = 0.3.
+    \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(p)w(q) + w(p)w(\neg q) = 0.3.
   \end{equation}
@@
   \[
-    M(p) = W(\{ p, q \}) + W(\{ p, \neg q \}) = W_p(\{p\})W_q(\{q\}) +
-    W_p(\{p\})W_q(\{\neg q\}) = 0.3.
+    M(p) = W(\{ p, q \}) + W(\{ p \}) = W_p(\{p\})W_q(\{q\}) +
+    W_p(\{p\})W_q(\emptyset) = 0.3.
   \]
+
+  Given the theory $\Delta$, we can compute the probability of a query $q$ as
+  \cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
+  \[
+    \Pr_{\Delta, w}(q) = \frac{\WMC(\Delta \land q)}{\WMC(\Delta)}.
+  \]
+  The same thing can be accomplished using the algebraic formulation, with $M$
+  replacing $\mathrm{WMC}$.
 \end{example}
@@
 model $x \in 2^U$.
-
-\todo[inline]{Include this in the example.}
-Given a theory $\Delta$ in a logic $\mathcal{L}$, the usual way of using WMC to
-compute the probability of a query $q$ is
-\cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
-\[
-  \Pr_{\Delta, w}(q) = \frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}.
-\]
-In our algebraic formulation, this can be computed...
 
@@
 
-\todo[inline]{This theorem needs a special case for zero weights.}
 \begin{theorem}
@@
 \begin{proof}
+  \todo[inline]{Check if the proof is valid for zero weights.}
   ($\Leftarrow$) For each $x \in U$, let $W_x\colon 2^{\{x\}} \to
@@
   \]
-  We will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by the
-  definitions of both $M_w$ and $M$. Second, let
-  \begin{equation} \label{eq:def_of_a}
+  We will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by
+  \cref{def:wmc,prop:measure}. Second, let
+  \[
     a = \bigwedge_{u \in U} a_u
-  \end{equation}
+  \]
   be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$.
@@
   \[
-    M_W(a) = \prod_{u \in U} W_u(a_u) = \prod_{u \in U} M(a_u) = M
-    \left(\bigwedge_{u \in U} a_u \right) = M(a)
+    M_W(a) = W(\{ a_u \mid u \in U \}) = \prod_{u \in U} W_u(\{a_u\}) = \prod_{u
+      \in U} M(a_u) = M \left(\bigwedge_{u \in U} a_u \right) = M(a)
   \]
-  \todo{by what?}
-  by \cref{def:wmc,eq:wmccondition,eq:def_of_a}. Finally, note that if $M_W$ and
+
+  Finally, note that if $M_W$ and
   $M$ agree on all atoms, then they must also agree on all other non-zero
@@
   because it's based on \texttt{cd05}.
-\item \texttt{sbk05} uses my trick with dividing probabilities. That could
-  explain small inaccuracies in its answers.
 \end{itemize}
 
-\subsection{Algebraic Decision Diagrams and ADDMC}
+\subsection{Algebraic Decision Diagrams and Their Use in Probabilistic
+  Inference}
 
-References
+Cover:
 \begin{itemize}
-\item ADDs \cite{DBLP:journals/fmsd/BaharFGHMPS97}
+\item ADDs provide an efficient way to manipulate functions from BAs/power sets
+  \cite{DBLP:journals/fmsd/BaharFGHMPS97}.
 \item background reading
@@
 \section{Encoding Bayesian Networks Using Conditional Weights}
-
-\begin{itemize}
-
-\item We assume that all variables in the Bayesian network have at least two
-  values.
-\item Have an example of how the ADDs function in this situation. If not for the
-  paper, then at least for slides. Use the framework to check its correctness.
-\item The function $\phi$ created by the algorithm can be seen as a measure on
-  the BA $2^{2^U}$.
-\item We extend the Gaifman graph to add edges when two variables occur in the
-  same CPT (e.g., including the edge from $A$ to $B$ when the CPT is $\Pr(A \mid
-  B)$).
-\end{itemize}
 
@@
 \begin{algorithm}
+  \caption{Encoding a Bayesian network as a function $2^U \to \mathbb{R}_{\ge
+      0}$}
+  \label{alg:encoding}
+  \KwData{a Bayesian network with vertices $V$ and probability distribution
+    $\Pr$}
+  \KwResult{a function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
   $\phi \gets 1$\;
@@
 \end{algorithm}
+
+\todo[inline]{Describe \cref{alg:encoding}}
+
+\subsection{Proof of Correctness}
 
@@
 
-\begin{example}
+\subsection{An Example}
+
+\todo[inline]{Reformulate this as a running example throughout the section.}
+
 \begin{figure}
@@
     \centering
-      \begin{tikzpicture}
-        \node[latent] (W) {W};
-        \node[latent, below right=of W] (T) {T};
-        \node[latent, below left=of W] (F) {F};
-        \edge {W} {F};
-        \edge {W} {T};
+    \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
+      \node[draw,circle] {$W$}
+      child {node[draw,circle] {$F$}}
+      child {node[draw,circle] {$T$}};
     \end{tikzpicture}
@@
 \end{align*}
-  and can be encoded in a DIMACS-like CNF format as
+and can be represented in a textual format as
 \[
@@
 \]
-  with each $\lambda$ replaced with a unique positive integer.
-\end{example}
+with each $\lambda$ replaced with a unique positive integer. This format is
+based on the format used by the Cachet solver \cite{DBLP:conf/sat/SangBBKP04}
+to encode WMC problems, which extends the DIMACS format for CNF formulas with
+weight clauses. Subsequently, we extend it in two ways:
+\begin{itemize}
+\item a single weight clause now supports an arbitrary number of literals,
+\item and each weight clause has two probabilities instead of one (i.e., we no
+  longer assume that $\Pr(v) + \Pr(\neg v) = 1$ for all variables $v \in U$).
+\end{itemize}
+The way we use this encoding, it is always the case that either both
+probabilities sum to one, or the second probability (i.e., the probability for
+the complement of the variable) is equal to one.
 
-The last two numbers are the positive and the negative probabilities,
-respectively---sometimes they add to one, and sometimes the negative probability
-is one, regardless of the value of the first probability.
+\subsection{Adjusting ADDMC to Work with the New Format}
+
+ADDMC constructs the \emph{Gaifman graph} of the input CNF formula as an aid for
+the algorithm's heuristics. This graph has as vertices the variables of the
+formula, and there is an edge between two variables $u$ and $v$ if there is a
+clause in the formula that contains both $u$ and $v$. We extend this definition
+to functions on Boolean algebras, i.e., the factors of $\phi$. For any pair of
+distinct variables $u, v \in U$, we draw an edge between them in the Gaifman
+graph if there is a function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ that is a
+factor of $\phi$ such that $u \in X$ and $v \in X$. For instance, a factor such
+as $\mathrm{CPT}_X$ will enable edges between all distinct pairs of variables in
+$E^*(X)$.
 

### 2020-07-26 paper.tex
Same

@@
 
-\todo[inline]{
-  Notation: make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x,
-  y$?).
-}
-
 \begin{table}
@@
 
-\begin{remark}
-  For any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A + \overline{A} = 1$.
-\end{remark}
-
 \section{Weighted Model Counting as a Measure}
 
-\todo[inline]{Describe \cref{tbl:notation_example} as an example.}
-\todo[inline]{Feedback: explain with examples: models $=$ atoms of algebra,
-  formulas $=$ all elements.}
-
-\begin{definition} \label{def:wmc}
+\begin{definition}[Measures and weight functions] \label{def:wmc}
   Let $U$ be a set.
@@
   \item A weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
-    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
+    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$.
+  \item We say that a weight function $W\colon 2^U \to \mathbb{R}_{\ge 0}$
+    \emph{induces} a measure $M_W\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
+    \begin{equation} \label{eq:induced_measure}
+      M_W(x) = \sum_{\{u\} \le x} W(u).
+    \end{equation}
   \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
@@
 
-\begin{proposition} \label{prop:measure}
-  Every weight function induces a measure, i.e, for any weight function $W\colon
-  2^U \to \mathbb{R}_{\ge 0}$, the function $M_W\colon 2^{2^U} \to
-  \mathbb{R}_{\ge 0}$, defined as
+\begin{lemma} \label{prop:measure}
+  The function $M_W$, as defined by \cref{eq:induced_measure}, is a measure.
+\end{lemma}
+\begin{proof}
+  Note that $M_W(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b \in
+  2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
+  Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
+  $b$. Moreover, none of them can be below both $a$ and $b$ because then they
+  would have to be below $a \land b = \bot$. Thus
   \[
-    M_W(x) = \begin{cases}
-      0 & \text{if } x = \bot \\
-      W(u) & \text{if } x = \{ u \} \\
-      \sum_{\{u\} \le x} W(u) & \text{otherwise,}
-    \end{cases}
+    M_W(a \lor b) = \sum_{\{u\} \le a \lor b} W(u) = \sum_{\{u\} \le a} W(u) +
+    \sum_{\{u\} \le b} = M_W(a) + M_W(b)
   \]
-  is a measure.
-\end{proposition}
-\begin{proof}
-  \todo[inline]{Prove that $M_W$ satisfies the definition of a measure.}
+  as required.
 \end{proof}
 
-The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$ with a
-given definition of $W$ is known as \emph{weighted model counting}.
+In this formulation, the process of calculating the value of $M_W(x)$ for some
+$x \in 2^{2^U}$ with a given definition of $W$ is known as \emph{weighted model
+  counting}.
+
+\subsection{Relation to the Classical (Logic-Based) View of WMC}
+
+\todo[inline]{Would it be more accurate to replace the word `model' with
+  `interpretation' in most situations?}
 
 \begin{table}
-  \caption{(in the same order)}
+  \caption{An overview of notation for a logic defined over two atoms. The
+    elements in both columns are listed in the same order.}
   \label{tbl:notation_example}
@@
     \toprule
-    & Set-theoretic notation & Boolean-algebraic notation \\
+    Name in logic & Set-theoretic notation & Boolean-algebraic notation \\
     \midrule
@@
 
-\begin{example}[Relation to the classical view of WMC] \label{example:construction}
-  Let $\mathcal{L}$ be a propositional logic with a set of atoms $U = \{ p, q
-  \}$. Let $w : \{ p, q, \neg p, \neg q \} \to \mathbb{R}_{\ge 0}$ be the
-  \emph{weight function} defined by
+Let $\mathcal{L}$ be a propositional logic with atoms $U = \{ a, b \}$. See
+\cref{tbl:notation_example} for an overview of the models and formulas in
+$\mathcal{L}$ as well as their set-theoretic and Boolean-algebraic
+representations. Note the differences in the meaning of the word `atom' between
+the logical and the Boolean-theoretic interpretations. In the Boolean algebra
+$2^{2^U}$, an atom is a set with a single element which corresponds to a model
+of $\mathcal{L}$ (also known as an element of $2^U$); whereas an atom of
+$\mathcal{L}$ is an atomic formula, i.e., an element of $U$. We will primarily
+use the term `atom' to mean the former.
+
+Let $w\colon \{ a, b, \neg a, \neg b \} \to \mathbb{R}_{\ge 0}$
+be the \emph{weight function} defined by
 \begin{align*}
-    w(p) = 0.3, \quad w(\neg p) = 0.7, \quad w(q) = 0.2, \quad w(\neg q) = 0.8.
+  w(a) = 0.3, \quad w(\neg a) = 0.7, \quad w(b) = 0.2, \quad w(\neg b) = 0.8.
 \end{align*}
-  Let $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $p$. Then
-  $\Delta$ has two models, i.e., $\{ p, q \}$ and $\{ p, \neg q \}$. The
+Let $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $a$. Then
+$\Delta$ has two models, i.e., $\{ a, b \}$ and $\{ a, \neg b \}$. The
 \emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of
@@
 \begin{equation} \label{eq:wmc_example}
-    \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(p)w(q) + w(p)w(\neg q) = 0.3.
+  \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(a)w(b) + w(a)w(\neg b) = 0.3.
 \end{equation}
 
-  Alternatively, we can define $W_p\colon 2^{\{p\}} \to \mathbb{R}_{\ge 0}$ as
+Alternatively, we can define $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ as
 \[
-    W_p(\{ p \}) = 0.3, \quad W_p(\emptyset) = 0.7
+  W_a(\{ a \}) = 0.3, \quad W_a(\emptyset) = 0.7
 \]
-  and $W_q\colon 2^{\{q\}} \to \mathbb{R}_{\ge 0}$ as
+and $W_b\colon 2^{\{q\}} \to \mathbb{R}_{\ge 0}$ as
 \[
-    W_q(\{ q \}) = 0.2, \quad W_q(\emptyset) = 0.8.
+  W_b(\{ b \}) = 0.2, \quad W_b(\emptyset) = 0.8.
 \]
-  Let $M$ be the measure on $2^{2^U}$ induced by $W = W_p \cdot W_q$. Then,
+Let $M$ be the measure on $2^{2^U}$ induced by $W = W_a \cdot W_b$. Then,
 equivalently to \cref{eq:wmc_example}, we can write
 \[
-    M(p) = W(\{ p, q \}) + W(\{ p \}) = W_p(\{p\})W_q(\{q\}) +
-    W_p(\{p\})W_q(\emptyset) = 0.3.
+  M(a) = W(\{ a, b \}) + W(\{ a \}) = W_a(\{a\})W_b(\{b\}) +
+  W_a(\{a\})W_b(\emptyset) = 0.3.
 \]
 
-  Given the theory $\Delta$, we can compute the probability of a query $q$ as
+Given the theory $\Delta$, we can also compute the probability of a query $b$ as
 \cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
 \[
-    \Pr_{\Delta, w}(q) = \frac{\WMC(\Delta \land q)}{\WMC(\Delta)}.
+  \Pr_{\Delta, w}(b) = \frac{\WMC(\Delta \land b)}{\WMC(\Delta)}.
 \]
@@
 replacing $\mathrm{WMC}$.
-\end{example}
 
-For the rest of the paper, we let $U$ be the set of (logical) atoms. We use
-set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$,
-except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some
-model $x \in 2^U$.
+In the rest of the paper, for any set $U$, we will use set-theoretic notation
+for $2^U$ and Boolean-algebraic notation for $2^{2^U}$, except for (Boolean)
+atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some model $x \in 2^U$.
 
@@
   \item come up with nice example when non-factorized weights are intuitive;
-  \item clarify that the factorized definition have is w.r.t. models, in case some
-    one gets confused. [It doesn't have to be, if the BA is not free---P.]
   \end{itemize}
@@
 
-\subsection{Bayesian Network Encodings}
+\subsection{Using WMC to Perform Inference on Bayesian Networks}
 
-\begin{itemize}
-\item Encodings:
-  \begin{itemize}
-  \item \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}
-  \item \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}
-  \item \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
-  \item \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
-  \item \texttt{db20} (mine)
-  \end{itemize}
-\item \texttt{cd05} relaxes the encoding so much that extra models become
-  possible. They are supposed to be filtered out by the algorithm, but mine
-  can't do that because it doesn't deal with models. Same for \texttt{cd06}
-  because it's based on \texttt{cd05}.
-\end{itemize}
+\todo[inline]{Provide a reference (and an explanation) for d-DNNF.}
+\todo[inline]{If I'm citing Cachet, then maybe I should also mention what
+  compilation tools they're using in their experiments.}
+
+Hitherto, four techniques have been proposed for encoding Bayesian networks into
+instances of WMC. We will identify them based on the initials of authors as well
+as publications years: \texttt{d02} \cite{DBLP:conf/kr/Darwiche02},
+\texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}, \texttt{cd05}
+\cite{DBLP:conf/ijcai/ChaviraD05}, and \texttt{cd06}
+\cite{DBLP:conf/sat/ChaviraD06}. Below we friendly summarise the observed
+performance differences among them. Sang et al. \cite{DBLP:conf/aaai/SangBK05}
+claim that \texttt{sbk05} is a smaller encoding than \texttt{d02} with respect
+to both the number of clauses and the number of variables but provide no
+experimental comparison. Chavira and Darwiche \cite{DBLP:conf/ijcai/ChaviraD05}
+compare \texttt{cd05} with \texttt{d02} by measuring the time it takes to
+compile either encoding into an arithmetic circuit (but do not measure inference
+time). The more recent encoding \texttt{cd05} always compiles faster and results
+in a smaller arithmetic circuit (as measured by the number of edges). In their
+subsequent paper, the same authors perform two sets of experiments (that are
+relevant to this summary) \cite{DBLP:conf/sat/ChaviraD06}. First, they compile
+\texttt{cd05} and \texttt{cd06} encodings into d-DNNF, measuring both
+compilation time and numbers of edges in the d-DNNF diagram. The results are
+mostly in favour of \texttt{cd06}. Second, they compare the inference time of
+\texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04} with the compile
+times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
+In these experiments, \texttt{cd06} is always faster than \texttt{cd05}, while
+the comparison with \texttt{sbk05} is mixed. Sometimes \texttt{cd06} is orders
+of magnitude faster than \texttt{sbk05}, sometimes slightly slower. The
+performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
+to judge: \texttt{sbk05} is better on three out of five instances and worse on
+the remaining two. Based on this description, one would expect \texttt{cd06} to
+be faster than both \texttt{cd05} and \texttt{sbk05}, both of which should be
+faster than \texttt{d02}. The experiments in \cref{sec:experiments}, however,
+strongly disagree with this prediction, showing that the quality of an encoding
+depends strongly on the underlying search algorithm or compilation technique.
 
@@
   \item On the Relationship between Sum-Product Networks and Bayesian Networks
-    (Zhao et al.) \cite{DBLP:conf/icml/ZhaoMP15}
+    \cite{DBLP:conf/icml/ZhaoMP15}
+  \item Using ROBDDs for Inference in Bayesian Networks with Troubleshooting as
+    an Example \cite{DBLP:conf/uai/NielsenWJK00}
+  \item SPUDD: Stochastic Planning using Decision Diagrams
+    \cite{DBLP:conf/uai/HoeySHB99}
   \end{itemize}
@@
 
+\todo[inline]{Even though a lot of papers don't do this, I want a reference and
+  a bit of a (historical/contextual) description here.}
+
 ADDMC constructs the \emph{Gaifman graph} of the input CNF formula as an aid for
@@
 
-\section{Experimental Comparison}
+\section{Experimental Comparison} \label{sec:experiments}
 
@@
   \end{itemize}
+\item \texttt{cd05} relaxes the encoding so much that extra models become
+  possible. They are supposed to be filtered out by the algorithm, but mine
+  can't do that because it doesn't deal with models. Same for \texttt{cd06}
+  because it's based on \texttt{cd05}.
 \end{itemize}

### 2020-07-26 paper.tex
Mostly editing

@@
 \usepackage{multirow}
+\usepackage[binary-units]{siunitx}
 
@@
   $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
+\item Somewhere: explain things line CNF, CPT, etc.
 \end{itemize}
@@
 
+\todo[inline,caption={}]{
   \begin{itemize}
-\item[F] Give a concrete example of something impossible to represent using WMC.
-\item[F] Can you say something here about factorized vs non-factorized
-  weight function definitions? That is, factorized is when $w$ maps literals to
+  \item[F] Give a concrete example of something impossible to represent
+    using WMC.
+  \item[F] Can you say something here about factorized vs non-factorized weight
+    function definitions? That is, factorized is when $w$ maps literals to
     $R_{\ge 0}$, non-factorized is when $w$ maps models to $R_{\ge 0}$ and
@@
   \end{itemize}
+}
 
@@
 
-\todo[inline]{Provide a reference (and an explanation) for d-DNNF.}
-\todo[inline]{If I'm citing Cachet, then maybe I should also mention what
-  compilation tools they're using in their experiments.}
-
 Hitherto, four techniques have been proposed for encoding Bayesian networks into
@@
 relevant to this summary) \cite{DBLP:conf/sat/ChaviraD06}. First, they compile
-\texttt{cd05} and \texttt{cd06} encodings into d-DNNF, measuring both
-compilation time and numbers of edges in the d-DNNF diagram. The results are
-mostly in favour of \texttt{cd06}. Second, they compare the inference time of
-\texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04} with the compile
-times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
-In these experiments, \texttt{cd06} is always faster than \texttt{cd05}, while
-the comparison with \texttt{sbk05} is mixed. Sometimes \texttt{cd06} is orders
-of magnitude faster than \texttt{sbk05}, sometimes slightly slower. The
-performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
-to judge: \texttt{sbk05} is better on three out of five instances and worse on
-the remaining two. Based on this description, one would expect \texttt{cd06} to
-be faster than both \texttt{cd05} and \texttt{sbk05}, both of which should be
-faster than \texttt{d02}. The experiments in \cref{sec:experiments}, however,
-strongly disagree with this prediction, showing that the quality of an encoding
-depends strongly on the underlying search algorithm or compilation technique.
+\texttt{cd05} and \texttt{cd06} encodings into d-DNNF (i.e., deterministic
+decomposable negation normal form \cite{DBLP:journals/jancl/Darwiche01}),
+measuring both compilation time and numbers of edges in the d-DNNF diagram. The
+results are mostly in favour of \texttt{cd06}. Second, they compare the
+inference time of \texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04}
+with the compile times of \texttt{cd05} and \texttt{cd06}, but only on five
+(types of) instances. In these experiments, \texttt{cd06} is always faster than
+\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
+\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
+slightly slower. The performance difference between \texttt{sbk05} and
+\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
+five instances and worse on the remaining two. Based on this description, one
+would expect \texttt{cd06} to be faster than both \texttt{cd05} and
+\texttt{sbk05}, both of which should be faster than \texttt{d02}. The
+experiments in \cref{sec:experiments}, however, strongly disagree with this
+prediction, showing that the quality of an encoding depends strongly on the
+underlying search algorithm or compilation technique.
 
@@
 
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.2\textwidth}
+    \centering
+    \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
+      \node[draw,circle] {$W$}
+      child {node[draw,circle] {$F$}}
+      child {node[draw,circle] {$T$}};
+    \end{tikzpicture}
+  \end{subfigure}%
+  \begin{subfigure}{0.8\textwidth}
+    \centering
+    \begin{tabular}[t]{cc}
+      \toprule
+      $w$ & $\Pr(W = w)$ \\
+      \midrule
+      1 & 0.5 \\
+      0 & 0.5 \\
+      \bottomrule
+    \end{tabular}
+    \begin{tabular}[t]{ccc}
+      \toprule
+      $w$ & $f$ & $\Pr(F = f \mid W = w)$ \\
+      \midrule
+      1 & 1 & 0.6 \\
+      1 & 0 & 0.4 \\
+      0 & 1 & 0.1 \\
+      0 & 0 & 0.9 \\
+      \bottomrule
+    \end{tabular}
+    \begin{tabular}[t]{ccc}
+      \toprule
+      $w$ & $t$ & $\Pr(T = t \mid W = w)$ \\
+      \midrule
+      1 & $l$ & 0.2 \\
+      1 & $m$ & 0.4 \\
+      1 & $h$ & 0.4 \\
+      0 & $l$ & 0.6 \\
+      0 & $m$ & 0.3 \\
+      0 & $h$ & 0.1 \\
+      \bottomrule
+    \end{tabular}
+  \end{subfigure}
+  \caption{An example Bayesian network with its CPTs}
+  \label{fig:example_bn}
+\end{figure}
+
 Let $V$ denote the set of random variables in a Bayesian network. For any random
 variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of parents of $X$ and
-$\im X$ denote the set of possible values.
+$\im X$ denote the set of possible values. We will use the Bayesian network in
+\cref{fig:example_bn} (loosely based on an example by Sang et al.
+\cite{DBLP:conf/aaai/SangBK05}) as a running example throughout this section.
+For the Bayesian network in \cref{fig:example_bn}, we have:
+\begin{align*}
+  V &= \{ W, F, T \}, \\
+  \mathrm{pa}(W) &= \emptyset, \\
+  \mathrm{pa}(F) &= \mathrm{pa}(T) = \{ W \}, \\
+  \im W &= \im F = \{ 0, 1 \}, \\
+  \im T &= \{ l, m, h \}.
+\end{align*}
 
@@
 \end{definition}
+
+\todo[inline]{Come up with a less repetitive wording.}
+For the Bayesian network in \cref{fig:example_bn}, we have:
+\begin{align*}
+  E(W) &= \{ \lambda_{W=1} \}, \\
+  E(F) &= \{ \lambda_{F=1} \}, \\
+  E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
+  E^*(W) &= \{ \lambda_{W=1} \}, \\
+  E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
+  E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
+\end{align*}
 
@@
 \end{algorithm}
+
+\todo[inline]{Ditto.}
+For the Bayesian network in \cref{fig:example_bn}, we have:
+\begin{align*}
+  \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
+  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
+    &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
+  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
+\end{align*}
 
@@
 
-\subsection{An Example}
+\subsection{Textual Representation}
 
-\todo[inline]{Reformulate this as a running example throughout the section.}
-
-\begin{figure}
-  \centering
-  \begin{subfigure}{0.2\textwidth}
-    \centering
-    \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
-      \node[draw,circle] {$W$}
-      child {node[draw,circle] {$F$}}
-      child {node[draw,circle] {$T$}};
-    \end{tikzpicture}
-  \end{subfigure}%
-  \begin{subfigure}{0.8\textwidth}
-    \centering
-    \begin{tabular}[t]{cc}
-      \toprule
-      $w$ & $\Pr(W = w)$ \\
-      \midrule
-      1 & 0.5 \\
-      0 & 0.5 \\
-      \bottomrule
-    \end{tabular}
-    \begin{tabular}[t]{ccc}
-      \toprule
-      $w$ & $f$ & $\Pr(F = f \mid W = w)$ \\
-      \midrule
-      1 & 1 & 0.6 \\
-      1 & 0 & 0.4 \\
-      0 & 1 & 0.1 \\
-      0 & 0 & 0.9 \\
-      \bottomrule
-    \end{tabular}
-    \begin{tabular}[t]{ccc}
-      \toprule
-      $w$ & $t$ & $\Pr(T = t \mid W = w)$ \\
-      \midrule
-      1 & $l$ & 0.2 \\
-      1 & $m$ & 0.4 \\
-      1 & $h$ & 0.4 \\
-      0 & $l$ & 0.6 \\
-      0 & $m$ & 0.3 \\
-      0 & $h$ & 0.1 \\
-      \bottomrule
-    \end{tabular}
-  \end{subfigure}
-  \caption{An example Bayesian network with its CPTs}
-  \label{fig:example_bn}
-\end{figure}
-
-The Bayesian network in \cref{fig:example_bn} has
-\begin{align*}
-  V &= \{ W, F, T \}, \\
-  \mathrm{pa}(W) &= \emptyset, \\
-  \mathrm{pa}(F) &= \mathrm{pa}(T) = \{ W \}, \\
-  \im W &= \im F = \{ 0, 1 \}, \\
-  \im T &= \{ l, m, h \}, \\
-  E(W) &= \{ \lambda_{W=1} \}, \\
-  E(F) &= \{ \lambda_{F=1} \}, \\
-  E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
-  E^*(W) &= \{ \lambda_{W=1} \}, \\
-  E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
-  E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}, \\
-  \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
-  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
-    &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
-  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots),
-\end{align*}
-and can be represented in a textual format as
+The Bayesian network in \cref{fig:example_bn} can be represented in a textual
+format as
 \[
@@
 
-\todo[inline]{Even though a lot of papers don't do this, I want a reference and
-  a bit of a (historical/contextual) description here.}
-
-ADDMC constructs the \emph{Gaifman graph} of the input CNF formula as an aid for
-the algorithm's heuristics. This graph has as vertices the variables of the
-formula, and there is an edge between two variables $u$ and $v$ if there is a
-clause in the formula that contains both $u$ and $v$. We extend this definition
-to functions on Boolean algebras, i.e., the factors of $\phi$. For any pair of
-distinct variables $u, v \in U$, we draw an edge between them in the Gaifman
-graph if there is a function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ that is a
-factor of $\phi$ such that $u \in X$ and $v \in X$. For instance, a factor such
-as $\mathrm{CPT}_X$ will enable edges between all distinct pairs of variables in
-$E^*(X)$.
+ADDMC constructs the \emph{Gaifman graph} \cite{gaifman1982local} of the input
+CNF formula as an aid for the algorithm's heuristics. This graph has as vertices
+the variables of the formula, and there is an edge between two variables $u$ and
+$v$ if there is a clause in the formula that contains both $u$ and $v$. We
+extend this definition to functions on Boolean algebras, i.e., the factors of
+$\phi$. For any pair of distinct variables $u, v \in U$, we draw an edge between
+them in the Gaifman graph if there is a function $A\colon 2^X \to
+\mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v \in
+X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges between
+all distinct pairs of variables in $E^*(X)$.
 
@@
   the instances from 2004-PGM that have empty evidence files.
-\item After the experiments are finished, note the processor, memory per thread,
-  and add the following acknowledgment.
+\item After the experiments are finished, note the processor, memory per thread.
+\item The experiments were run on Intel Xeon Gold 6138 processor with an
+  \SI{8}{\giga\byte} memory limit.
+\item I will call my encoding \texttt{db20}.
 \item All other encodings are implemented in
-  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be
-  compiled with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC)
-  and \texttt{-noEclause} (i.e., only use standard syntax) flags.
+  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and were compiled
+  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
+  \texttt{-noEclause} (i.e., only use standard syntax) flags.
 \item Datasets

### 2020-07-28 paper.tex
A bugfix (and a few other things)

@@
   \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\emptyset) = 0$.
-  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$, $[a](\emptyset) =
-    0$, $[a](\{a\}) = 1$.
+  \item logical constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
+    $[a](\emptyset) = 0$, $[a](\{a\}) = 1$.
   \end{itemize}
@@
 \begin{proof}
-  \todo[inline]{Check if the proof is valid for zero weights.}
   ($\Leftarrow$) For each $x \in U$, let $W_x\colon 2^{\{x\}} \to
@@
   \end{align*}
-  where $C$ denotes the part of $M_W(k_u \land k_v)$ that will be the same for
-  $M_W(\neg k_u \land k_v)$, $M_W(k_u \land \neg k_v)$, and $M_W(\neg k_u \land
-  \neg k_v)$ as well. But then \cref{eq:to_prove4} becomes
+  where
+  \[
+    C = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}} W_x(a),
+  \]
+  and is the same for $M_W(\neg k_u \land k_v)$, $M_W(k_u \land \neg k_v)$, and
+  $M_W(\neg k_u \land \neg k_v)$ as well. But then \cref{eq:to_prove4} becomes
   \[
@@
 
-\subsection{Adjusting ADDMC to Work with the New Format}
+\subsection{Changes to ADDMC}
 
@@
 all distinct pairs of variables in $E^*(X)$.
+
+\todo[inline]{This needs rewriting.}
+ADDMC multiplies the final answer by $w(u)+w(-u)$ for every $u \in U$ that was
+`simplified out' of the ADD for $\phi$ and so is not featured in the $\exists_U$
+projection. In our format, for every such $u \in U$, we multiply the answer by
+two. Each such $u \in U$ must satisfy two properties:
+\begin{itemize}
+\item all the probabilities/weights associated with $u$ are equal to $0.5$
+  (otherwise the corresponding CPT would depend on $u$),
+\item and all other CPTs are independent of $u$ (or they may have a trivial
+  dependence, where the probability stays the same if $u$ is replaced with its
+  complement).
+\end{itemize}
+Thus, the CPT that corresponds to $u$ still multiplies every model by $0.5$, but
+the number of models being considered by the ADDMC is halved. To correct for
+this, we need to perform this multiplication.
 

### 2020-07-28 experiments/ADDMC/counting/implementation/formula.cpp

@@ -342,7 +342,8 @@ Formula::Formula(const std::string &filePath, WeightFormat weightFormat,
     util::showError("miniC2D weight line not found");
   }
 
-  if (weightFormat == WeightFormat::UNWEIGHTED) { /* populates literalWeights with 1s */
+  /* populates literalWeights with 1s */
+  if (weightFormat == WeightFormat::UNWEIGHTED || weightFormat == WeightFormat::CONDITIONAL) {
      for (int_t var = 1; var <= declaredVarCount; var++) {
        literalWeights[var] = 1;
        literalWeights[-var] = 1;

### 2020-07-28 experiments/ADDMC/counting/interface/util.hpp

@@ -203,8 +203,6 @@ namespace util {
   template <typename T>
   double adjustModelCount(double apparentModelCount, const T &projectedFormulaVars,
                           const MapT<int_t, double> &literalWeights, WeightFormat weightFormat) {
-    if (weightFormat == WeightFormat::CONDITIONAL)
-      return apparentModelCount;
     double totalModelCount = apparentModelCount;
 
     int_t totalLiteralCount = literalWeights.size();

### 2020-07-28 experiments/analyse.R

@@ -4,7 +4,7 @@ require(dplyr)
 require(maditr)
 require(purrr)
 
-TIMEOUT <- 600
+TIMEOUT <- 1000
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
 df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
@@ -19,7 +19,7 @@ df$major.dataset[df$dataset == "Grid-75"] <- "Grid"
 df$major.dataset[df$dataset == "Grid-90"] <- "Grid"
 
 # Where answers don't match
-interesting <- df[abs(df$answer_db20 - df$answer_d02) > 0.01,]
+interesting <- df[abs(df$answer_db20 - df$answer_sbk05) > 0.01,]
 
 # Proportion of instances where my encoding is the best
 #time$min <- apply(time, 1, min)
@@ -47,8 +47,17 @@ ggplot(df[df$time_d02 > 0,], aes(x = time_db20, y = time_d02, col = major.datase
 # 2. Adjust the alpha value.
 # 3. Make sure that the PDF output is square.
 
+ggplot(df, aes(x = time_db20, y = time_sbk05, col = major.dataset)) +
+  geom_point(alpha = 0.5) +
+  geom_abline(slope = 1, intercept = 0) +
+  scale_x_continuous(trans = log10_trans(), limits = c(min.time, TIMEOUT)) +
+  scale_y_continuous(trans = log10_trans(), limits = c(min.time, TIMEOUT)) +
+  xlab("db20 time (s)") +
+  ylab("sbk05 time (s)") +
+  scale_color_brewer(palette = "Dark2", name = "Data set")
+
 # Scatter plot: for a specific dataset
-ggplot(df[df$dataset == "2005-IJCAI"], aes(x = time_db20, y = time_d02)) +
+ggplot(df[df$dataset == "2004-PGM"], aes(x = time_db20, y = time_sbk05)) +
   geom_point() +
   geom_abline(slope = 1, intercept = 0) +
   xlim(0, TIMEOUT) +

### 2020-07-28 experiments/nullify_large_files.py

@@ -1,0 +1,8 @@
+import os
+from pathlib import Path
+
+for path in Path('results').rglob('*'):
+    size = os.path.getsize(path)
+    if path.suffix != '' and size > 10 * 2**20: # 10 MB
+        with open(path, 'w') as f:
+            f.write('')

### 2020-07-28 paper/scatter_d02.tex
Preliminary experimental results

% Created by tikzDevice version 0.12.3 on 2020-07-28 10:41:15
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,216.81);
\begin{scope}
\path[clip] (  6.04,  0.00) rectangle (340.86,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  6.04,  0.00) rectangle (340.86,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 46.55, 30.69) rectangle (227.17,211.31);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 46.55, 30.69) rectangle (227.17,211.31);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.55, 33.95) --
	(227.17, 33.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.55,101.61) --
	(227.17,101.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.55,169.27) --
	(227.17,169.27);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.82, 30.69) --
	( 49.82,211.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] (117.48, 30.69) --
	(117.48,211.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] (185.13, 30.69) --
	(185.13,211.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.55, 67.78) --
	(227.17, 67.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.55,135.44) --
	(227.17,135.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.55,203.10) --
	(227.17,203.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 83.65, 30.69) --
	( 83.65,211.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.30, 30.69) --
	(151.30,211.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.96, 30.69) --
	(218.96,211.31);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.84) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 98.79) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.84) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (106.13, 93.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.90, 94.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 95.36, 93.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.75,106.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.18, 93.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.16) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,105.87) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.25) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.31) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.81,100.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.67, 99.40) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.73, 99.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.07,111.39) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.03, 99.80) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (115.07,101.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.69,114.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.78, 99.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.05,100.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.60, 99.82) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.48, 93.61) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.48,103.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.38,114.16) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.38,102.51) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.71,111.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.26,101.80) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (120.65,114.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (120.66,113.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (132.66,117.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.43,113.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.86,114.13) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.45,115.35) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.18,104.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.67,100.19) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.26,121.91) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.38,104.94) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.97,105.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.33,117.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.32,103.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.26,103.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (122.81,103.01) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.30,111.28) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,155.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,167.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,155.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.87,155.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.47,166.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (155.73,155.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.08,155.82) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.85,155.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,181.94) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,173.47) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.26) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,179.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,170.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,157.82) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.29,170.59) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.43,158.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.45,158.14) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.68,158.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.77,158.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.91) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,174.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.29) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,196.92) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.31,160.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (177.17,160.29) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (164.81,160.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.23,160.18) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.94) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (206.65,187.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.61) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,181.62) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,201.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.01) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.06) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.25) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.91,189.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (207.97,189.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.81,197.35) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (207.13,189.48) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,193.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,186.91) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,185.87) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,191.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (209.39,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.80,191.39) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.26,191.61) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,191.26) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.27) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,191.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,102.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,105.01) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,117.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,108.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.44,119.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,109.44) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.50,110.84) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (169.98,110.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,120.33) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,120.64) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,126.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,121.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,159.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (135.15,130.29) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,123.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,124.92) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.70,140.35) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,136.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,136.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,151.39) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.50,142.47) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.11,141.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.18,149.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,149.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,124.02) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,170.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,122.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,144.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,142.01) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (140.74,114.47) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.38,127.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (133.65,114.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.64,114.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,154.16) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,125.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (170.06,133.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,129.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (150.57,132.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,147.98) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,168.40) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,178.06) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,168.48) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,123.27) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.99,117.71) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (131.00,129.67) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (200.44,116.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.19,118.15) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,122.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,128.98) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,116.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,116.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,115.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,118.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,121.64) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (205.60,120.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (168.77,121.65) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,158.11) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,141.82) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,141.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.66,133.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.02) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,161.01) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 75.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 75.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.40) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.75) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.75) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.83) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.40) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 74.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 75.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.41, 78.18) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 47.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 57.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 60.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 47.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.14) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.14) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.14) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 59.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 60.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 59.26) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 59.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 60.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 62.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 57.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 60.76) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 57.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 58.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 47.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 47.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 46.19) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 58.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.14) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 46.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 47.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 61.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 47.41) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 47.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 62.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 50.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 61.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 58.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 55.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.86, 55.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 61.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 58.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.76) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 66.56) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 61.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 61.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 65.39) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 65.22) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 72.83) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 67.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 61.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 69.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 69.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 68.64) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 66.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 63.56) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 70.94) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 62.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 55.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 55.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 48.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 59.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 58.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 64.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 59.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 65.22) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 67.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 65.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 60.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 61.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 59.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 59.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 58.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.96, 61.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 58.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 63.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 64.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 65.22) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 67.33) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 62.54) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 70.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.96, 66.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 59.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.94) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 66.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 67.33) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 62.75) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 68.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 65.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.77, 68.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.90, 66.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 66.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 66.40) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 61.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 61.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 65.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 67.18) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.56) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 62.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 65.74) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 59.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 55.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.76) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 66.40) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.24, 63.75) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 66.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.64, 65.39) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 67.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 63.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58, 66.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 54.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 61.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 57.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 54.32) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 62.33) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 55.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 51.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 61.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 53.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 58.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 55.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.93) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.77) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.18, 94.16) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.18,127.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58,104.65) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14, 91.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.90, 94.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,158.71) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.89,107.80) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.62,121.34) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 88.48) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43,114.15) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.44,168.24) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (107.44,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.28,165.11) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.80,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 96.87,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.48,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.82, 97.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.18,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.01,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.82,172.71) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (134.10,181.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (145.66,182.59) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.39,145.83) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.22,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.11,155.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (137.17,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.23,130.80) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.84,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (144.52,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.80,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (136.77,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (137.02,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.88,166.84) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (129.71,160.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.63,195.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (145.43,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (148.29,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.09,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (144.51,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (153.57,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (161.55,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (144.32,198.42) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.28,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (154.56,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (132.08,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (138.49,197.16) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (145.84,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.29,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.62,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (181.07,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.52,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (164.08,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.28,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (173.36,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.10,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (169.22,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (178.90,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (183.77,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.20,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (177.80,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (178.55,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (174.64,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (188.81,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (189.51,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (155.30,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (183.00,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (178.39,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.48,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (195.99,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (184.35,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (184.25,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (182.20,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (199.46,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (182.81,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (186.37,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (188.89,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (181.67,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (182.90,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (194.44,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (202.83,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (204.09,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (183.77,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.91,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (200.13,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (202.61,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (204.40,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (194.04,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 56.72, 70.82) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 56.72, 78.61) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 63.75) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 77.44) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 70.09) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72,105.31) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 76.74) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81, 79.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.27,133.13) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46,158.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.86,162.46) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.08, 92.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.13,144.66) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.19, 87.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79, 89.48) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.32,139.81) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.70,139.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.91,146.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 88.26) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.24,191.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.15,132.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.98,161.30) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.81,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.55,101.34) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.44,125.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 93.90,178.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.66,166.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.73,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.60,186.16) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.57,169.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.09,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.95,137.49) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44,173.42) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.08,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.95,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 95.23,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 93.38,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.67,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.22,165.44) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.58,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.63,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.26,198.72) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.39,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.00,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.08,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.10,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.97,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.92,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.69,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (144.69,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (109.42,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.18,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.54,190.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.63,195.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.76,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.71,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.75,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (155.80,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.67,182.06) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.44,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.21,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (115.28,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (136.31,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (142.71,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (140.26,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (151.51,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.59,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (167.52,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (147.42,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.45,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.92,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.41,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (165.26,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (149.91,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (131.43,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (138.69,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.41,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.09,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (149.79,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (153.76,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.18,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (142.57,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (167.77,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.39,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (154.53,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.12,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (167.90,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.11,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (134.99,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (173.59,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (161.17,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.71,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (171.31,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (176.82,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.75,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.07,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (170.38,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.87,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (184.02,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (170.17,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (176.43,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (173.34,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (169.19,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (164.58,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (176.38,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (186.62,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (165.10,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (186.35,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (180.66,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.19,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (184.85,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (187.65,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (182.57,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (186.67,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.98,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (165.62,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.54,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (197.79,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.06,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.41,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (174.28,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (185.66,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (205.07,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (186.36,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (177.78,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (192.50,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (206.07,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (202.80,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (206.26,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (179.69,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (197.93,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (200.47,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (178.37,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (203.74,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (191.79,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.00,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 50.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 83.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 55.77, 58.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 59.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 57.89) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 67.33) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 96.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 74.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 77.06) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 62.12) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 59.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94,119.15) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46,128.79) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81, 79.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 71.75) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.17,108.53) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,142.06) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04,116.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 95.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94,160.78) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.89,163.47) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,111.99) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 97.35) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 80.73,129.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.38,101.84) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.62, 80.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.42,119.92) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.18, 95.79) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.31,113.64) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,120.08) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58,132.04) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43,120.96) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.46, 78.61) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 98.05) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46,108.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.10,121.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,122.39) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.24, 81.36) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.35,113.43) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14,142.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.91,108.98) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.18, 96.33) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,136.38) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,113.06) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.08, 98.46) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.43,111.18) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.90,125.57) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,175.37) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.89,120.69) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.80,124.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 79.81, 93.17) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,178.28) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,165.73) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.32,135.47) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.78,130.15) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.59,185.63) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.13,169.48) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.75,140.14) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.61,147.60) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,146.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.10,167.91) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,134.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.96,179.76) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.60,179.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.89,110.65) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (127.01,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.92,166.86) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.42,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14,168.74) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.76,147.55) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,160.53) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.31,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.05,198.34) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (110.59,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.86,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,196.23) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.41,166.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.43,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.43,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 79.61,127.11) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (110.40,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 84.36,176.02) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.93,180.83) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.58,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.12,178.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 84.36,183.68) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.53,196.28) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.05,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.08,146.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 80.18,183.92) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.28,192.48) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.50,163.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.55,119.00) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.60,143.52) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.05,145.44) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.46,153.18) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (107.02,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (109.47,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.12,134.74) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.40,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.83,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.50,155.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.20,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.31,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (106.07,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 93.68,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.98,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.92,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.75,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.17,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.31,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (111.01,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.05,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.72,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.20,178.21) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.00,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 93.90,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.88,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.88,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.70,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.28,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 96.39,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.03,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.34,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (151.46,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.58,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.05,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.98,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.91,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (149.58,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.48,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.36,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.07,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.91,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (161.50,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.84,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.45,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (138.99,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (149.54,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (153.84,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.87,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (128.09,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.20,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.59,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (179.71,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.81,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (173.68,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (145.68,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.45,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (109.85,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.26,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.75,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (127.35,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (156.74,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.64,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (131.65,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.44,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (156.04,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.87,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (179.35,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.48,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.06,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (212.59,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (157.11,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.55,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.08,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (123.27,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.86,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (206.57,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.55,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.14,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (123.85,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (179.45,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (174.37,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (170.51,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (149.33,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.74,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (177.92,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (149.59,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (169.89,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (197.25,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.18,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.63,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.17,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (176.57,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.24,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (123.06,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (184.86,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (176.56,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (167.30,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.05,117.88) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.16,183.79) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,155.65) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (123.38,131.70) circle (  1.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (136.57,143.41) circle (  1.96);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.55, 30.69) -- (227.17,211.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.27, 30.69) -- ( 48.27, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.82, 30.69) -- ( 49.82, 39.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.00, 30.69) -- ( 60.00, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.96, 30.69) -- ( 65.96, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.18, 30.69) -- ( 70.18, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 73.46, 30.69) -- ( 73.46, 36.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 76.14, 30.69) -- ( 76.14, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 78.41, 30.69) -- ( 78.41, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 80.37, 30.69) -- ( 80.37, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.10, 30.69) -- ( 82.10, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 83.65, 30.69) -- ( 83.65, 39.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 93.83, 30.69) -- ( 93.83, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 99.79, 30.69) -- ( 99.79, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (104.01, 30.69) -- (104.01, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (107.29, 30.69) -- (107.29, 36.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (109.97, 30.69) -- (109.97, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.24, 30.69) -- (112.24, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.20, 30.69) -- (114.20, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (115.93, 30.69) -- (115.93, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (117.48, 30.69) -- (117.48, 39.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (127.66, 30.69) -- (127.66, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (133.62, 30.69) -- (133.62, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (137.84, 30.69) -- (137.84, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (141.12, 30.69) -- (141.12, 36.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (143.80, 30.69) -- (143.80, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (146.06, 30.69) -- (146.06, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (148.03, 30.69) -- (148.03, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.76, 30.69) -- (149.76, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.30, 30.69) -- (151.30, 39.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (161.49, 30.69) -- (161.49, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (167.45, 30.69) -- (167.45, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (171.67, 30.69) -- (171.67, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (174.95, 30.69) -- (174.95, 36.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.63, 30.69) -- (177.63, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.89, 30.69) -- (179.89, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (181.86, 30.69) -- (181.86, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (183.59, 30.69) -- (183.59, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.13, 30.69) -- (185.13, 39.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.32, 30.69) -- (195.32, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (201.27, 30.69) -- (201.27, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (205.50, 30.69) -- (205.50, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.78, 30.69) -- (208.78, 36.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (211.46, 30.69) -- (211.46, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.72, 30.69) -- (213.72, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (215.69, 30.69) -- (215.69, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (217.42, 30.69) -- (217.42, 33.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (218.96, 30.69) -- (218.96, 39.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 32.40) -- ( 49.39, 32.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 33.95) -- ( 55.09, 33.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 44.14) -- ( 49.39, 44.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 50.09) -- ( 49.39, 50.09);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 54.32) -- ( 49.39, 54.32);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 57.60) -- ( 52.24, 57.60);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 60.28) -- ( 49.39, 60.28);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 62.54) -- ( 49.39, 62.54);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 64.50) -- ( 49.39, 64.50);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 66.23) -- ( 49.39, 66.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 67.78) -- ( 55.09, 67.78);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 77.97) -- ( 49.39, 77.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 83.92) -- ( 49.39, 83.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 88.15) -- ( 49.39, 88.15);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 91.43) -- ( 52.24, 91.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 94.11) -- ( 49.39, 94.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 96.37) -- ( 49.39, 96.37);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55, 98.33) -- ( 49.39, 98.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,100.06) -- ( 49.39,100.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,101.61) -- ( 55.09,101.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,111.80) -- ( 49.39,111.80);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,117.75) -- ( 49.39,117.75);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,121.98) -- ( 49.39,121.98);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,125.26) -- ( 52.24,125.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,127.94) -- ( 49.39,127.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,130.20) -- ( 49.39,130.20);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,132.16) -- ( 49.39,132.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,133.89) -- ( 49.39,133.89);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,135.44) -- ( 55.09,135.44);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,145.62) -- ( 49.39,145.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,151.58) -- ( 49.39,151.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,155.81) -- ( 49.39,155.81);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,159.09) -- ( 52.24,159.09);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,161.77) -- ( 49.39,161.77);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,164.03) -- ( 49.39,164.03);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,165.99) -- ( 49.39,165.99);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,167.72) -- ( 49.39,167.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,169.27) -- ( 55.09,169.27);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,179.45) -- ( 49.39,179.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,185.41) -- ( 49.39,185.41);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,189.64) -- ( 49.39,189.64);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,192.92) -- ( 52.24,192.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,195.59) -- ( 49.39,195.59);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,197.86) -- ( 49.39,197.86);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,199.82) -- ( 49.39,199.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,201.55) -- ( 49.39,201.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.55,203.10) -- ( 55.09,203.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.60, 64.75) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.60,132.41) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.60,200.07) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.80, 67.78) --
	( 46.55, 67.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.80,135.44) --
	( 46.55,135.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.80,203.10) --
	( 46.55,203.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 83.65, 27.94) --
	( 83.65, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.30, 27.94) --
	(151.30, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.96, 27.94) --
	(218.96, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 83.65, 19.68) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (151.30, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.96, 19.68) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (136.86,  7.64) {db20 time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 19.12,121.00) {d02 time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (238.17, 78.98) rectangle (335.36,163.01);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (243.67,148.87) {Data set};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{fillColor}{gray}{0.95}

\path[fill=fillColor] (243.67,127.84) rectangle (258.13,142.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (250.90,135.07) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{fillColor}{gray}{0.95}

\path[fill=fillColor] (243.67,113.39) rectangle (258.13,127.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (250.90,120.62) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{fillColor}{gray}{0.95}

\path[fill=fillColor] (243.67, 98.94) rectangle (258.13,113.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (250.90,106.16) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{fillColor}{gray}{0.95}

\path[fill=fillColor] (243.67, 84.48) rectangle (258.13, 98.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (250.90, 91.71) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (263.63,132.04) {2004-PGM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (263.63,117.59) {DQMR};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (263.63,103.13) {Grid};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (263.63, 88.68) {Plan Recognition};
\end{scope}
\end{tikzpicture}

### 2020-07-28 paper/scatter_sbk05.tex
Preliminary experimental results

--- 2020-07-28 paper/scatter_d02.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-07-28 10:41:15
+% Created by tikzDevice version 0.12.3 on 2020-07-28 10:41:18
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.84) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 98.79) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.84) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.07) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.97) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.95) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.88) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 96.70) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (106.13, 88.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.90, 87.66) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 95.36, 87.70) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.75, 97.54) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.18, 88.62) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (106.13, 93.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.90, 94.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 95.36, 93.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.75,106.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.18, 93.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.16) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,105.87) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.25) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 91.31) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.81,100.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.67, 99.40) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.73, 99.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.07,111.39) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.03, 99.80) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (115.07,101.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.69,114.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.78, 99.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.05,100.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.60, 99.82) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.48, 93.61) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.48,103.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.38,114.16) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.38,102.51) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.71,111.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.26,101.80) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (120.65,114.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (120.66,113.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (132.66,117.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.43,113.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.86,114.13) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.45,115.35) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.18,104.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.67,100.19) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.26,121.91) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.38,104.94) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.97,105.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.33,117.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.32,103.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.26,103.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (122.81,103.01) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.30,111.28) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,155.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,167.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,155.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.87,155.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.47,166.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (155.73,155.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.08,155.82) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.85,155.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,181.94) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,173.47) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.26) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,179.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,170.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,157.82) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.29,170.59) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.43,158.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.45,158.14) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.68,158.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.77,158.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.91) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,174.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.29) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,196.92) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.31,160.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (177.17,160.29) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (164.81,160.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.23,160.18) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.94) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (206.65,187.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.61) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,181.62) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,201.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.01) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.06) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.25) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.91,189.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (207.97,189.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.81,197.35) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (207.13,189.48) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,193.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,186.91) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,185.87) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,191.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (209.39,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.80,191.39) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.26,191.61) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,191.26) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.27) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,191.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,102.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,105.01) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,117.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,108.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.44,119.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,109.44) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.50,110.84) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (169.98,110.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,120.33) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,120.64) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,126.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,121.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,159.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (135.15,130.29) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,123.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,124.92) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.70,140.35) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,136.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,136.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,151.39) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.50,142.47) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.11,141.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.18,149.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,149.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,124.02) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,170.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,122.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,144.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,142.01) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (140.74,114.47) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.38,127.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (133.65,114.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.64,114.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,154.16) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,125.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (170.06,133.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,129.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (150.57,132.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,147.98) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,168.40) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,178.06) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,168.48) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,123.27) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.99,117.71) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (131.00,129.67) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (200.44,116.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.19,118.15) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,122.78) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,128.98) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,116.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,116.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,115.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,118.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,121.64) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (205.60,120.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (168.77,121.65) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,158.11) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,141.82) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,141.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.66,133.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.02) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,132.78) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,161.01) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.97) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,107.59) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96, 95.62) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.81,100.43) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.67, 99.08) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.73, 99.60) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.07,109.71) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.03, 99.70) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (115.07,100.53) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.69,102.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.78, 94.11) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.05, 95.24) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (100.60, 93.88) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.48, 96.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.48, 99.48) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.38,107.55) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.38, 99.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.71,108.43) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.26, 97.81) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (120.65,113.71) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (120.66,113.46) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (132.66,123.50) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.43,112.67) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.86,113.89) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.45,114.79) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.18, 98.77) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.67, 99.93) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (125.26,117.44) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.38, 99.07) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (104.97, 98.73) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.33,120.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.32,107.34) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.26,107.25) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (122.81,107.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.30,108.66) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.87,153.90) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.47,161.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (155.73,149.91) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.08,151.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.85,149.73) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.08) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,200.17) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.92) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,189.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,197.39) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,197.99) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (172.29,165.24) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (160.43,153.01) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.45,153.64) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (162.68,153.73) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (158.77,152.85) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.64) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,188.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.96) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.46) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,187.06) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (166.31,155.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (177.17,156.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (164.81,156.15) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (163.23,155.83) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,201.96) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,201.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,183.26) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (206.65,183.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,183.49) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,182.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,192.59) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.12) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,201.91) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,201.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.91,186.18) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (207.97,184.45) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (201.81,195.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (207.13,184.08) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,195.00) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,186.50) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (209.39,197.86) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.80,187.68) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (196.26,187.37) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.44,145.01) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.50,117.27) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (169.98,130.14) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (135.15,163.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (193.70,179.46) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.50,138.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.11,195.79) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (159.18,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (140.74,202.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.38,162.14) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (133.65,113.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.64,120.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,202.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (170.06,144.68) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (150.57,136.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,199.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.99,133.67) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (131.00,144.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (200.44,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.19,126.77) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,197.24) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (205.60,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (168.77,185.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (152.66,129.39) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,139.14) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,177.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 75.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 75.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.40) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.75) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.75) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.83) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.40) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 74.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 75.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 75.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.41, 78.18) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 75.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 47.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 54.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 72.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.08) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 72.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 74.96) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.73) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 72.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 72.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.62) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 73.24) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.62) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 71.97) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.62) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 84.50) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 72.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.19) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.41, 72.73) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 72.62) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 57.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 60.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 47.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.14) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.14) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.14) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 59.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.60) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.89) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 57.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 58.45) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 57.00) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 56.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 56.37) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.05) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.68) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 60.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 59.26) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 59.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 60.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 62.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 57.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 60.76) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.69) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.72) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 57.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 54.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 58.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 47.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 56.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 47.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.19) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 46.19) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 58.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.14) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 46.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 46.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 47.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 45.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 44.85) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 56.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 55.04) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 55.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 61.45) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.26) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 61.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.26) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.26) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.86, 83.68) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 61.23) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 61.68) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 62.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.00) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.26) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 59.78) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 47.41) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 47.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 62.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 50.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 61.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 58.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 55.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.86, 55.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 61.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 58.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.76) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 66.56) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 61.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 61.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 65.39) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 65.22) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 72.83) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 67.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 61.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 69.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 69.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 68.64) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 66.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 63.56) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 70.94) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 57.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 62.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 55.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 55.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 51.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 48.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 49.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 59.78) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 58.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 64.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 59.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 65.22) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 67.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 65.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 60.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 61.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 59.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 60.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 59.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 58.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 56.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.96, 61.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 58.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 63.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 64.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 65.22) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 67.33) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 62.54) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 70.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.96, 66.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 59.78) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 59.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 61.40, 59.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 64.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 64.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 64.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.50) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.96, 70.34) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 81.01) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 64.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 65.39) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 69.71) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.96, 64.87) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 65.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 64.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 71.29) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 67.93) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.77, 64.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.90, 75.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 65.39) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.24, 70.09) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 84.55) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.64, 69.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58, 71.86) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 64.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.75) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 66.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 67.33) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 62.75) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 68.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 65.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.77, 68.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.90, 66.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 66.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 66.40) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 61.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 61.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 65.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 67.18) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.56) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44, 62.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 65.74) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 59.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 55.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 60.76) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.80, 66.40) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.24, 63.75) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 66.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.64, 65.39) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 67.78) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 63.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58, 66.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 54.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 60.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.64, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 61.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 57.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 54.32) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 56.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 56.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 62.33) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 55.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 51.49) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 61.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 57.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 53.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 58.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 57.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 55.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 53.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 51.93) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 52.77) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 64.32) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 64.69) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.85, 63.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 63.94) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 64.13) circle (  1.96);
 \definecolor{drawColor}{RGB}{117,112,179}
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.18, 94.16) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.18,127.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58,104.65) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14, 91.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.90, 94.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,158.71) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.89,107.80) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.62,121.34) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 88.48) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43,114.15) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.44,168.24) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (107.44,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.28,165.11) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.18,103.01) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.18, 75.14) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58, 96.64) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14, 86.64) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.90, 71.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,138.59) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.89, 95.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.62, 81.42) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.41, 73.24) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43, 75.66) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.44,176.65) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (107.44,168.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.28,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.48,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.82, 97.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.18,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.48,121.09) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.82,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.96,151.37) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.18,196.81) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.82,172.71) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (134.10,181.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (145.66,182.59) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.39,145.83) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (121.82,192.85) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (134.10,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (145.66,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (124.39,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.11,155.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (137.17,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.23,130.80) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.84,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.11,185.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (137.17,165.45) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.23,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.84,120.18) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.88,166.84) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (129.71,160.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.63,195.38) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (126.88,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (129.71,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (143.63,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (144.32,198.42) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (144.32,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (138.49,197.16) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (138.49,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 56.72, 70.82) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 56.72, 78.61) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 63.75) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 77.44) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 70.09) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72,105.31) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 76.74) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81, 79.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.27,133.13) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46,158.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.86,162.46) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.08, 92.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.13,144.66) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.19, 87.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79, 89.48) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.32,139.81) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.70,139.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.91,146.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05, 88.26) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.24,191.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.15,132.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.98,161.30) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.81,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.55,101.34) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.44,125.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 93.90,178.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.66,166.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.73,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.60,186.16) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.57,169.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.09,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.95,137.49) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 56.72, 84.31) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 56.72, 93.66) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76,123.81) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25,130.79) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94,139.54) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72,111.83) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 58.45, 78.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,137.15) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.27,141.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 85.76) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.86,107.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.08,190.62) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.13, 81.54) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.19,174.87) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79, 90.71) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.32,140.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.70, 84.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.91,103.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.05,166.02) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.24,147.07) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.15,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.98,116.64) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.81,145.18) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.55,176.31) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.44,186.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 93.90,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.66,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (118.73,196.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.60,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.57,133.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.09,199.99) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,152.31) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.95,172.93) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44,173.42) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.08,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 66.44,107.96) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 86.08,107.45) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 95.23,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 95.23,170.73) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.67,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.22,165.44) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.67,144.93) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.22,170.78) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.26,198.72) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.39,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.26,136.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.39,183.72) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.08,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 99.08,158.94) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.97,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.92,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (130.97,186.20) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.92,118.24) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.54,190.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.63,195.03) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.54,181.80) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (119.63,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.71,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.71,180.50) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.67,182.06) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.67,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 50.58) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 83.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 55.77, 58.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 59.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 57.89) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 67.33) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 96.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 74.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 77.06) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 62.12) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 59.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94,119.15) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46,128.79) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81, 79.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 71.75) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.17,108.53) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,142.06) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04,116.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 95.03) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94,160.78) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.89,163.47) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,111.99) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 97.35) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 80.73,129.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.38,101.84) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.62, 80.77) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.42,119.92) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.18, 95.79) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.31,113.64) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,120.08) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58,132.04) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43,120.96) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.46, 78.61) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25, 98.05) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46,108.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.10,121.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,122.39) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.24, 81.36) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.35,113.43) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14,142.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.91,108.98) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.18, 96.33) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,136.38) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,113.06) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.08, 98.46) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.43,111.18) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.90,125.57) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,175.37) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.89,120.69) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.80,124.95) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 79.81, 93.17) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,178.28) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,165.73) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.32,135.47) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.78,130.15) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.59,185.63) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.13,169.48) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.75,140.14) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.61,147.60) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,146.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.10,167.91) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,134.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.96,179.76) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.60,179.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.89,110.65) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (127.01,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.92,166.86) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.42,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14,168.74) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.76,147.55) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,160.53) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.31,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.05,198.34) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (110.59,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.86,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,196.23) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.41,166.77) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 47.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 60.52) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 55.77, 52.77) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 58.45) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 54.76, 49.60) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 69.84) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 67.36, 69.18) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 62.68, 88.08) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.00, 60.28) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 60.72, 75.58) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 59.25, 70.09) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 61.68) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 63.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81, 78.54) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 57.61, 55.72) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.17, 84.45) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,126.65) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.04, 90.61) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94, 72.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 64.94,130.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.89,168.14) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,127.16) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.28, 95.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 80.73,146.79) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.38,150.08) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.62, 86.68) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.42,150.38) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.18,132.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.31,123.43) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,100.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.58,118.63) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.43,142.71) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.46,188.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,101.93) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 65.46, 92.61) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.10,126.92) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22,114.47) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.24, 87.89) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.35, 87.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14,178.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.91,104.81) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.18,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 69.81,165.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 68.22, 81.07) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 90.08,115.85) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.43,113.13) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 70.90, 74.60) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,126.57) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.89,164.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.80,164.84) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 79.81, 84.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 71.25,123.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.32,151.01) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.78,161.55) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 74.59,102.29) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.13,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 73.75,145.22) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.61,140.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09, 79.70) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 82.10,161.03) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 78.82,167.59) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.96,167.63) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.60,180.50) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 75.89,138.75) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (127.01,179.21) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.92,126.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (102.42,194.48) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.14,102.27) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.76, 96.33) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 77.09,155.06) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.31,177.78) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.05,155.35) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (110.59,175.98) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 76.86,183.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,159.79) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 89.41,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.43,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 79.61,127.11) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (114.43,168.26) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 79.61,169.93) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 84.36,176.02) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.93,180.83) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.58,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.12,178.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 84.36,183.68) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.53,196.28) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.05,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.08,146.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 80.18,183.92) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.28,192.48) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.50,163.90) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.55,119.00) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.60,143.52) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.05,145.44) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.46,153.18) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 84.36, 83.12) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.93,161.27) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.58,142.95) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.12,154.35) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 84.36,182.40) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (141.53,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (113.05,135.81) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.08,189.67) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 80.18,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.28,196.60) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.50,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (117.55,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 81.60,168.88) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.05,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.46,203.10) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.12,134.74) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.40,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.83,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.50,155.07) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.20,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.31,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (106.07,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.79,150.99) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.12,157.61) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 98.40,165.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 94.48,158.05) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (112.83,199.70) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.50,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.20,182.24) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 85.31,165.56) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (106.07,161.61) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.92,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.75,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.17,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 92.92,171.36) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (103.75,167.80) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (116.17,168.01) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (111.01,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (111.01,170.51) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.72,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.20,178.21) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.00,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 87.72,172.30) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (108.20,112.86) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 91.00,175.68) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.28,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 96.39,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (101.28,162.01) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 96.39,176.73) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.34,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 97.34,179.90) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.58,203.10) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (105.58,197.60) circle (  1.96);
 
@@
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.05,117.88) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.16,183.79) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,155.65) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (123.38,131.70) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (136.57,143.41) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 83.05,117.29) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 88.16,157.74) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (218.96,203.10) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (123.38,127.80) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (136.57,140.58) circle (  1.96);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 19.12,121.00) {d02 time (s)};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 19.12,121.00) {sbk05 time (s)};
 \end{scope}

### 2020-07-28 analyse.R

@@ -3,11 +3,13 @@ require(scales)
 require(dplyr)
 require(maditr)
 require(purrr)
+require(tikzDevice)
 
 TIMEOUT <- 1000
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
 df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
+df0$memory[is.na(df0$memory)] <- max(df0$memory)
 df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time", "memory"))
 df$major.dataset <- df$dataset
 df$major.dataset[df$dataset == "DQMR-50"] <- "DQMR"
@@ -17,47 +19,77 @@ df$major.dataset[df$dataset == "DQMR-100"] <- "DQMR"
 df$major.dataset[df$dataset == "Grid-50"] <- "Grid"
 df$major.dataset[df$dataset == "Grid-75"] <- "Grid"
 df$major.dataset[df$dataset == "Grid-90"] <- "Grid"
+df$time_min <- as.numeric(apply(df, 1, function (row) min(row["time_cd05"], row["time_cd06"],
+                                                          row["time_d02"], row["time_db20"], row["time_sbk05"])))
+
+# ============ Numerical investigations ================
 
 # Where answers don't match
 interesting <- df[abs(df$answer_db20 - df$answer_sbk05) > 0.01,]
 
-# Proportion of instances where my encoding is the best
-#time$min <- apply(time, 1, min)
-#sum(time$db20 == time$min)/nrow(time)
+# Unique
+sum(is.na(df$answer_db20) & !is.na(df$answer_cd05) & is.na(df$answer_cd06) &
+      is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cd05
+sum(is.na(df$answer_db20) & is.na(df$answer_cd05) & !is.na(df$answer_cd06) &
+      is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cd06
+sum(is.na(df$answer_db20) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
+      !is.na(df$answer_d02) & is.na(df$answer_sbk05)) # d02
+sum(!is.na(df$answer_db20) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
[…]

### 2020-07-28 analyse.R
Better plots

@@ -4,6 +4,7 @@ require(dplyr)
 require(maditr)
 require(purrr)
 require(tikzDevice)
+require(ggpubr)
 
 TIMEOUT <- 1000
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
@@ -21,11 +22,12 @@ df$major.dataset[df$dataset == "Grid-75"] <- "Grid"
 df$major.dataset[df$dataset == "Grid-90"] <- "Grid"
 df$time_min <- as.numeric(apply(df, 1, function (row) min(row["time_cd05"], row["time_cd06"],
                                                           row["time_d02"], row["time_db20"], row["time_sbk05"])))
-
 # ============ Numerical investigations ================
 
 # Where answers don't match
 interesting <- df[abs(df$answer_db20 - df$answer_sbk05) > 0.01,]
+
+nrow(df)
 
 # Unique
 sum(is.na(df$answer_db20) & !is.na(df$answer_cd05) & is.na(df$answer_cd06) &
@@ -59,39 +61,35 @@ sum(!is.na(df$answer_sbk05))
 # Consider:
 # 1. Shapes as well as colors (set manually).
 # 2. Adjust the alpha value.
-# TODO: consider gray log ticks
-# TODO: merge this into a single plot, with a legend either to the side or inside each plot
+
 min.time <- min(df0$time) + 0.001
-
-# d02
-tikz(file = "paper/scatter_d02.tex", width = 4.8, height = 3)
-ggplot(df[df$time_d02 > 0,], aes(x = time_db20, y = time_d02, col = major.dataset)) +
-  geom_point(alpha = 0.5) +
-  geom_abline(slope = 1, intercept = 0) +
+p1 <- ggplot(df[df$time_d02 > 0,], aes(x = time_d02, y = time_db20, col = major.dataset)) +
+  geom_point(alpha = 0.5, size = 1) +
+  geom_abline(slope = 1, intercept = 0, colour = "#989898") +
   scale_x_continuous(trans = log10_trans(), limits = c(min.time, TIMEOUT), breaks = c(0.1, 10, 1000), labels = c("0.1", "10", "1000")) +
   scale_y_continuous(trans = log10_trans(), limits = c(min.time, TIMEOUT), breaks = c(0.1, 10, 1000), labels = c("0.1", "10", "1000")) +
-  xlab("db20 time (s)") +
-  ylab("d02 time (s)") +
[…]

### 2020-07-28 paper/paper.tex
Move things around
Preliminary experimental results
Better plots
Describe experimental data

--- 2020-07-28 paper.tex
@@
 \usepackage[binary-units]{siunitx}
+\usepackage[inline]{enumitem}
 
@@
 
+\begin{figure}
+  \centering
+  \input{scatter.tex}
+  \caption{Scatter plots}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{cumulative.tex}
+  \caption{Cumulative plot}
+\end{figure}
+
+\begin{table}
+  \caption{Out of 1216 instances}
+  \centering
+  \begin{tabular}{lrrr}
+    \toprule
+    Encoding & Unique & Fastest & Solved \\
+    \midrule
+    \texttt{cd05} & 2 & 3 & 372 \\
+    \texttt{cd06} & 0 & 1 & 351 \\
+    \texttt{d02} & 41 & 99 & 726 \\
+    \texttt{db20} & 228 & 871 & 901 \\
+    \texttt{sbk05} & 6 & 36 & 687 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \begin{itemize}
@@
   \texttt{-noEclause} (i.e., only use standard syntax) flags.
-\item Datasets
-  \begin{itemize}
-  \item binary Bayesian networks from Sang et
-    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
-    \cite{DBLP:conf/aaai/SangBK05}
-    \begin{itemize}
-    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
-      deterministic),
-    \item Plan recognition (problems),
-    \item Deterministic quick medical reference (what do the numbers mean? the
-      README doesn't say).
-    \end{itemize}
-  \item Bayesian networks available with Ace
-    \begin{itemize}
-    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
-    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
-      files have their own citation data that I should probably extract. This is
-      the only dataset that has some non-binary networks.
-    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
-    \end{itemize}
-  \end{itemize}
+\item We don't use Ace's evidence-encoding mechanism because it has multiple
+  significant bugs (and the code is closed-source). Ace's implementation
+  (depending on the exact encoding) is supposed to perform some simplifications
+  when encoding evidence. We just do the trivial thing---no simplifications.
 \item \texttt{cd05} relaxes the encoding so much that extra models become
@@
 \end{itemize}
+
+\paragraph{Data.} For experiments, we use the Bayesian networks available
+with Ace\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and
+Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
+which happen to be binary. We classify them into the following seven categories:
+\begin{itemize*}
+\item DQMR and
+\item grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
+\item friends and smokers,
+\item mastermind, and
+\item random blocks from the work of Chavira et al.
+  \cite{DBLP:journals/ijar/ChaviraDJ06},
+\item remaining binary Bayesian networks that include plan recognition
+  \cite{DBLP:conf/aaai/SangBK05}, students and professors
+  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
+\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
+  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
+  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
+\end{itemize*}
+% DQMR
+% Friends and smokers (2006)
+% Grid
+% Mastermind (2004 & some of 2005)
+% Random blocks (2004 & some of 2005)
+% Non-binary: most of 2005
+% Other binary (whatever remains, including Plan Recognition)
 

### 2020-07-28 analyse.R

@@ -20,6 +20,8 @@ df$major.dataset[df$dataset == "DQMR-100"] <- "DQMR"
 df$major.dataset[df$dataset == "Grid-50"] <- "Grid"
 df$major.dataset[df$dataset == "Grid-75"] <- "Grid"
 df$major.dataset[df$dataset == "Grid-90"] <- "Grid"
+df$major.dataset[df$dataset == "2006-IJAR"] <- "Friends and smokers"
+df$major.dataset[df$dataset == "Plan Recognition"] <- "Plan recognition"
 df$time_min <- as.numeric(apply(df, 1, function (row) min(row["time_cd05"], row["time_cd06"],
                                                           row["time_d02"], row["time_db20"], row["time_sbk05"])))
 # ============ Numerical investigations ================
@@ -62,7 +64,7 @@ sum(!is.na(df$answer_sbk05))
 # 1. Shapes as well as colors (set manually).
 # 2. Adjust the alpha value.
 
-min.time <- min(df0$time) + 0.001
+min.time <- min(df0$time)
 p1 <- ggplot(df[df$time_d02 > 0,], aes(x = time_d02, y = time_db20, col = major.dataset)) +
   geom_point(alpha = 0.5, size = 1) +
   geom_abline(slope = 1, intercept = 0, colour = "#989898") +

### 2020-07-29 paper/paper.tex
Change how the data instances are grouped

@@
   \centering
-  \input{scatter.tex}
-  \caption{Scatter plots}
-\end{figure}
-
-\begin{figure}
+  \begin{minipage}{0.59\textwidth}
     \centering
-  \input{cumulative.tex}
-  \caption{Cumulative plot}
-\end{figure}
-
-\begin{table}
-  \caption{Out of 1216 instances}
+    \input{cumulative.tex}%
+    \captionof{figure}{Cumulative plot}
+  \end{minipage}
+  \begin{minipage}{0.39\textwidth}
     \centering
+    \captionof{table}{Out of 1216 instances}%
     \begin{tabular}{lrrr}
@@
     \end{tabular}
-\end{table}
+  \end{minipage}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{scatter.tex}%
+  \caption{Scatter plots}
+\end{figure}
 
@@
   the instances from 2004-PGM that have empty evidence files.
-\item After the experiments are finished, note the processor, memory per thread.
 \item The experiments were run on Intel Xeon Gold 6138 processor with an
@@
   because it's based on \texttt{cd05}.
+\item Observations
+  \begin{itemize}
+  \item The order of the encodings from best to worst is exactly the opposite of
+    that in the previous literature.
+  \item Our encoding is particularly promising on instances of Grid networks.
+    They are set up so that the entire Bayesian network is relevant to the
+    query.
+  \item However, \texttt{db20} struggles with instances from Mastermind and
+    Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
+    is so either because the particular structure of these problems confuse the
+    algorithm's heuristics or because these instances allow for significant
+    simplifications that are exploited by $\mathtt{d02}$ but not
+    $\mathtt{db20}$.
+  \end{itemize}
 \end{itemize}
@@
 \item DQMR and
-\item grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
-\item friends and smokers,
-\item mastermind, and
-\item random blocks from the work of Chavira et al.
+\item Grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
+\item Friends and Smokers,
+\item Mastermind, and
+\item Random Blocks from the work of Chavira et al.
   \cite{DBLP:journals/ijar/ChaviraDJ06},
-\item remaining binary Bayesian networks that include plan recognition
-  \cite{DBLP:conf/aaai/SangBK05}, students and professors
+\item remaining binary Bayesian networks that include Plan Recognition
+  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
   \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
@@
 \end{itemize*}
-% DQMR
-% Friends and smokers (2006)
-% Grid
-% Mastermind (2004 & some of 2005)
-% Random blocks (2004 & some of 2005)
-% Non-binary: most of 2005
-% Other binary (whatever remains, including Plan Recognition)
 

### 2020-07-29 analyse.R

@@ -12,18 +12,19 @@ df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
 df0$memory[is.na(df0$memory)] <- max(df0$memory)
 df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time", "memory"))
-df$major.dataset <- df$dataset
-df$major.dataset[df$dataset == "DQMR-50"] <- "DQMR"
-df$major.dataset[df$dataset == "DQMR-60"] <- "DQMR"
-df$major.dataset[df$dataset == "DQMR-70"] <- "DQMR"
-df$major.dataset[df$dataset == "DQMR-100"] <- "DQMR"
-df$major.dataset[df$dataset == "Grid-50"] <- "Grid"
-df$major.dataset[df$dataset == "Grid-75"] <- "Grid"
-df$major.dataset[df$dataset == "Grid-90"] <- "Grid"
-df$major.dataset[df$dataset == "2006-IJAR"] <- "Friends and smokers"
-df$major.dataset[df$dataset == "Plan Recognition"] <- "Plan recognition"
 df$time_min <- as.numeric(apply(df, 1, function (row) min(row["time_cd05"], row["time_cd06"],
                                                           row["time_d02"], row["time_db20"], row["time_sbk05"])))
+
+df$major.dataset <- "Non-binary"
+df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
+df$major.dataset[grepl("Grid", df$instance, fixed = TRUE)] <- "Grid"
+df$major.dataset[grepl("mastermind", df$instance, fixed = TRUE)] <- "Mastermind"
+df$major.dataset[grepl("blockmap", df$instance, fixed = TRUE)] <- "Random blocks"
+df$major.dataset[grepl("fs-", df$instance, fixed = TRUE)] <- "Friends and smokers"
+df$major.dataset[grepl("Plan_Recognition", df$instance, fixed = TRUE)] <- "Other binary"
+df$major.dataset[grepl("students", df$instance, fixed = TRUE)] <- "Other binary"
+df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
+
 # ============ Numerical investigations ================
 
 # Where answers don't match
[…]

### 2020-07-29 paper/paper.tex
A bit of writing

@@
 
-\title{Weighted Model Counting with Conditional Measures}
+\title{Weighted Model Counting with Conditional Weights}
 \author{Paulius Dilkas}
@@
 \item[F] What are the main claims, what are the main takeaways, intuitive [???]
-  of theorems to follow. To do this, we appeal to algebraic constructions to
-  define the main concepts for introducing measures on Boolean algebras.
+  of theorems to follow.
 \item
-  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
+  Algorithms
   \begin{itemize}
@@
     \cite{DBLP:journals/ai/Nilsson86,DBLP:journals/ai/Nilsson93}
-  \item Logical induction: a big paper with a good overview of previous attempts
-    to assign probabilities to logical sentences in a sensible way
-    \cite{DBLP:journals/eccc/GarrabrantBCST16}
   \item Measures on Boolean algebras
@@
   $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
-\item Somewhere: explain things line CNF, CPT, etc.
 \end{itemize}
@@
 \todo[inline,caption={}]{
-  \begin{itemize}
-  \item[F] Give a concrete example of something impossible to represent
-    using WMC.
-  \item[F] Can you say something here about factorized vs non-factorized weight
-    function definitions? That is, factorized is when $w$ maps literals to
-    $R_{\ge 0}$, non-factorized is when $w$ maps models to $R_{\ge 0}$ and
-    \begin{itemize}
-    \item come up with nice example when non-factorized weights are intuitive;
-    \end{itemize}
-  \end{itemize}
+  Examples (must):
+  \begin{itemize}
+  \item an example of a measure that cannot be expressed using a factored weight
+    function,
+  \item an example of how to express it using conditional weight functions.
+  \end{itemize}
+  Also, define `conditional weight function'.
 }
@@
 
-Let $V$ denote the set of random variables in a Bayesian network. For any random
-variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of parents of $X$ and
-$\im X$ denote the set of possible values. We will use the Bayesian network in
-\cref{fig:example_bn} (loosely based on an example by Sang et al.
-\cite{DBLP:conf/aaai/SangBK05}) as a running example throughout this section.
-For the Bayesian network in \cref{fig:example_bn}, we have:
-\begin{align*}
-  V &= \{ W, F, T \}, \\
-  \mathrm{pa}(W) &= \emptyset, \\
-  \mathrm{pa}(F) &= \mathrm{pa}(T) = \{ W \}, \\
-  \im W &= \im F = \{ 0, 1 \}, \\
-  \im T &= \{ l, m, h \}.
-\end{align*}
+\todo[inline]{Define 'CPT'}
+
+In line with the names of previous encodings, we shall call this encoding
+\texttt{db20}. Let $V$ denote the set of random variables in a Bayesian network.
+For any random variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of
+parents of $X$ and $\im X$ denote the set of possible values. We will use the
+Bayesian network in \cref{fig:example_bn} as a running example throughout this
+section. For this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
+$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
+$\im T = \{ l, m, h \}$.
 
@@
   \emph{indicator variable} $\lambda_{X=1}$. For notational simplicity, for any
-  set $S$, whenever we write $\lambda_{X=0} \in S$ or $S = \{ \lambda_{X=0},
-  \dots \}$, we actually mean $\lambda_{X=1} \not\in S$,
+  set $S$, we write $\lambda_{X=0} \in S$ or $S = \{ \lambda_{X=0}, \dots \}$ to
+  mean $\lambda_{X=1} \not\in S$,
 
@@
 
-\todo[inline]{Come up with a less repetitive wording.}
-For the Bayesian network in \cref{fig:example_bn}, we have:
+For the Bayesian network in \cref{fig:example_bn}, this gives us:
 \begin{align*}
@@
 
-\todo[inline]{Ditto.}
+\todo[inline]{Describe the algorithm and the CPT functions.}
+
 For the Bayesian network in \cref{fig:example_bn}, we have:
@@
 \end{align*}
-
-\todo[inline]{Describe \cref{alg:encoding}}
 
@@
 
-\subsection{Textual Representation}
+\subsection{Textual Representation} \label{sec:textual_representation}
+
+\todo[inline]{Describe how this is an intermediate step before we get the $\phi$
+from the algorithm. Each CPT is treated as a clause.}
 
@@
 based on the format used by the Cachet solver \cite{DBLP:conf/sat/SangBBKP04}
-to encode WMC problems, which extends the DIMACS format for CNF formulas with
-weight clauses. Subsequently, we extend it in two ways:
+to encode WMC problems, which extends the DIMACS format for conjunctive normal
+form (CNF) formulas with weight clauses. Subsequently, we extend it in two
+ways:
 \begin{itemize}
@@
 \begin{itemize}
-\item We don't compare 'compile times' because our encoding time is linear, so
-  we would easily beat everyone else.
-\item When the Bayesian network has an evidence file, we compute the probability
-  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
-  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
-  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
-  and calculate its marginal probability. This applies to the Grid data set (as
-  intended) and also to two instances of Plan Reconstruction and roughly half of
-  the instances from 2004-PGM that have empty evidence files.
+\item We chose not to measure or compare encoding time because of different
+  languages of implementation and the fact that our encoding algorithm (i.e.,
+  the process that converts a Bayesian network into a textual encoding such as
+  in \cref{sec:textual_representation}) is linear in the total number of CPT
+  rows and so is unlikely to be slower than, e.g., \texttt{cd06}, which relies
+  on solving $\NP$-complete problems as part of the encoding process
+  \cite{DBLP:conf/sat/ChaviraD06}.
+\item Whenever a Bayesian network comes with an evidence file, we compute the
+  probability of evidence. Otherwise, let $X$ denote the last-mentioned node in
+  the Bayesian network. If $\mathsf{true}$ is a valid value of $X$, we compute
+  the marginal probability of $X = \mathsf{true}$. Otherwise, we pick the value
+  of $X$ which is listed first and calculate its marginal probability.
 \item The experiments were run on Intel Xeon Gold 6138 processor with an
   \SI{8}{\giga\byte} memory limit.
-\item I will call my encoding \texttt{db20}.
-\item All other encodings are implemented in
-  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and were compiled
-  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
-  \texttt{-noEclause} (i.e., only use standard syntax) flags.
-\item We don't use Ace's evidence-encoding mechanism because it has multiple
-  significant bugs (and the code is closed-source). Ace's implementation
-  (depending on the exact encoding) is supposed to perform some simplifications
-  when encoding evidence. We just do the trivial thing---no simplifications.
-\item \texttt{cd05} relaxes the encoding so much that extra models become
-  possible. They are supposed to be filtered out by the algorithm, but mine
-  can't do that because it doesn't deal with models. Same for \texttt{cd06}
-  because it's based on \texttt{cd05}.
-\item Observations
-  \begin{itemize}
-  \item The order of the encodings from best to worst is exactly the opposite of
-    that in the previous literature.
-  \item Our encoding is particularly promising on instances of Grid networks.
-    They are set up so that the entire Bayesian network is relevant to the
-    query.
-  \item However, \texttt{db20} struggles with instances from Mastermind and
-    Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
-    is so either because the particular structure of these problems confuse the
-    algorithm's heuristics or because these instances allow for significant
-    simplifications that are exploited by $\mathtt{d02}$ but not
-    $\mathtt{db20}$.
-  \end{itemize}
+\item For all other encodings, we use their implementation in
+  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
+  \texttt{-encodeOnly} and \texttt{-noEclause} flags. However, Ace was not used
+  to encode evidence, as preliminary experiments revealed that the
+  evidence-encoding implementation contains bugs that can lead to incorrect
+  answers or a Java exception being thrown on some instances of the data set
+  (and the source code is not publicly available). Instead, we simply list all
+  the evidence as additional clauses in the encoding (regardless of which
+  encoding is used).
+\item Note that \texttt{cd05} and \texttt{cd06} purposefully produce overly
+  relaxed encodings that contain extra models and thus yield incorrect
+  probabilities \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.
+  These additional models are supposed to be filtered out during circuit
+  compilation \cite{DBLP:conf/ijcai/ChaviraD05}, but this is not easily
+  achievable with ADDMC. Nonetheless, we include both encodings in our timing
+  experiments.
 \end{itemize}
@@
 \paragraph{Data.} For experiments, we use the Bayesian networks available
-with Ace\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and
+with Ace and
 Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
@@
 
+\paragraph{Observations.}
+\begin{itemize}
+\item The order of the encodings from best to worst is exactly the opposite of
+  that in the previous literature.
+\item Our encoding is particularly promising on instances of Grid networks.
+  They are set up so that the entire Bayesian network is relevant to the
+  query.
+\item However, \texttt{db20} struggles with instances from Mastermind and
+  Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
+  is so either because the particular structure of these problems confuse the
+  algorithm's heuristics or because these instances allow for significant
+  simplifications that are exploited by $\mathtt{d02}$ but not
+  $\mathtt{db20}$.
+\end{itemize}
+
 \section{Explaining The Performance Benefits}

### 2020-07-29 paper/paper.tex
Writing and editing about BNs and function spaces

@@
   Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
-    0}$ be arbitrary functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$.
-  We define the following operations:
+    0}$ be functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We define
+  the following operations:
   \begin{description}
-  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
-    \mathbb{R}_{\ge 0}$ such that
-    \[
-      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
-    \]
-    for all $\tau \in 2^{X \cup Y}$.
-  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
-    \mathbb{R}_{\ge 0}$ such that
-    \[
-      \overline{A}(\tau) = 1 - A(\tau)
-    \]
-    for all $\tau \in 2^X$.
-  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
-    \to \mathbb{R}_{\ge 0}$ such that
-    \[
-      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
-    \]
-    for all $\tau \in 2^{X \cup Y}$.
-  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
-    \mathbb{R}_{\ge 0}$ such that
-    \[
-      (\alpha A)(\tau) = \alpha \cdot A(\tau)
-    \]
-    for all $\tau \in 2^X$.
-  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
-      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
-    \[
-      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
-    \]
-    for all $\tau \in 2^{X \setminus \{x \}}$.
+  \item[Addition:] $A+B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$ is a function
+    such that $(A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)$ for all $\tau \in
+    2^{X \cup Y}$.
+  \item[Inverse:] $\overline{A}\colon 2^X \to \mathbb{R}_{\ge 0}$ is a function
+    such that $\overline{A}(\tau) = 1 - A(\tau)$ for all $\tau \in 2^X$.
+  \item[Multiplication:] $A \cdot B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$
+    is a function such that $(A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau
+    \cap Y)$ for all $\tau \in 2^{X \cup Y}$.
+  \item[Scalar multiplication:] $\alpha A\colon 2^X \to \mathbb{R}_{\ge 0}$ is a
+    function such that $(\alpha A)(\tau) = \alpha \cdot A(\tau)$ for all $\tau
+    \in 2^X$.
+  \item[Projection:] $\exists_xA\colon 2^{X \setminus \{ x \}} \to
+    \mathbb{R}_{\ge 0}$ is a function such that $(\exists_xA)(\tau) = A(\tau) +
+    A(\tau \cup \{ x \})$ for all $\tau \in 2^{X \setminus \{x \}}$.
   \end{description}
@@
 
-\todo[inline]{Define 'CPT'}
-
-In line with the names of previous encodings, we shall call this encoding
-\texttt{db20}. Let $V$ denote the set of random variables in a Bayesian network.
-For any random variable $X \in V$, let $\mathrm{pa}(X)$ denote the set of
-parents of $X$ and $\im X$ denote the set of possible values. We will use the
-Bayesian network in \cref{fig:example_bn} as a running example throughout this
-section. For this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
-$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
-$\im T = \{ l, m, h \}$.
+\todo[inline]{In line with the names of previous encodings, we shall call this
+  encoding \texttt{db20}.}
+
+A \emph{Bayesian network} is a directed acyclic graph with random variables as
+vertices that defines a probability distribution over them. Let $V$ denote the
+set of random variables and $X \in V$ be a random variable. Let $\im X$ denote
+the set of possible values of $X$ and $\mathrm{pa}(X)$ denote the set of its
+parents. The full probability distribution is then equal to
+\begin{equation} \label{eq:factorisation}
+  \prod_{X \in V} \Pr(X \mid \mathrm{pa}(X)).
+\end{equation}
+If all random variables are discrete (and we only consider discrete Bayesian
+networks in this paper), the probabilities contained in each factor of
+\cref{eq:factorisation} can be summarised in a table known as a
+\emph{conditional probability table} (CPT). See \cref{fig:example_bn} for an
+example Bayesian network which we will refer to throughout this section. For
+this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F)
+= \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m,
+h \}$.
 

### 2020-07-30 paper/paper.tex
Black-and-white-friendly plots

@@
   \item We show that our encoding results in asymptotically fewer literals and
-    fewer ADDs, and thus a simpler problem.
-  \item (Maybe) we experimentally demonstrate a phase transition based on the
-    number of variables per ADD.
+    fewer ADDs.
   \end{enumerate}
-\item Potential criticism may be that this is a step backwards and doesn't allow
-  us to use SAT-based techniques for probabilistic inference. However, they can
-  still be used for the 'theory+query' part.
+\item Potential criticism may be that this doesn't allow us to use SAT-based
+  techniques for probabilistic inference. However, they can still be used for a
+  significant part of the encoding.
   \begin{itemize}
@@
   \item A \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$
-    such that $M(\bot) = 0$ and
-    \[
-      M(a \lor b) = M(a) + M(b)
-    \]
-    for all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$.
+    such that $M(\bot) = 0$, and $M(a \lor b) = M(a) + M(b)$ for all $a, b \in
+    2^{2^U}$ whenever $a \land b = \bot$.
   \item A \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
@@
     \toprule
-    Name in logic & Set-theoretic notation & Boolean-algebraic notation \\
+    Name in logic & Boolean-algebraic notation & Set-theoretic notation \\
     \midrule
     Atoms (elements of $U$) & $a, b$ & $a, b$ \\
-    \rowcolor{gray!10} Models (elements of $2^U$) & $\emptyset, \{a\}, \{b\}, \{a, b\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
-    & $\{ \emptyset, \{a\}, \{b\}, \{a, b\} \}$ & $\top$ \\
-    & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{a\}, \{a, b\} \}$ & $\neg a \lor \neg b, a \to b$ \\
-    & $\{ \emptyset, \{b\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ & $b \to a, a \lor b$ \\
-    & $\{\emptyset, \{a\}\}, \{\emptyset, \{b\}\}, \{\emptyset, \{a, b\}\}$ & $\neg b, \neg a, a \leftrightarrow b$ \\
-    & $\{\{a\}, \{b\}\}, \{\{a\}, \{a, b\}\}, \{\{b\}, \{a, b\}\}$ & $(a \land \neg b) \lor (b \land \neg a), a, b$ \\
-    & $\{\emptyset\}, \{\{a\}\}, \{\{b\}\}, \{\{a, b\}\}$ & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ \\
-    \multirow{-7}{*}{Formulas (elements of $2^{2^U}$)} & $\emptyset$ & $\bot$ \\
+    \rowcolor{gray!10} Models (elements of $2^U$) & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ & $\emptyset, \{a\}, \{b\}, \{a, b\}$ \\
+    & $\top$ & $\{ \emptyset, \{a\}, \{b\}, \{a, b\} \}$ \\
+    & $\neg a \lor \neg b, a \to b$ & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{a\}, \{a, b\} \}$ \\
+    & $b \to a, a \lor b$ & $\{ \emptyset, \{b\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ \\
+    & $\neg b, \neg a, a \leftrightarrow b$ & $\{\emptyset, \{a\}\}, \{\emptyset, \{b\}\}, \{\emptyset, \{a, b\}\}$ \\
+    & $(a \land \neg b) \lor (b \land \neg a), a, b$ & $\{\{a\}, \{b\}\}, \{\{a\}, \{a, b\}\}, \{\{b\}, \{a, b\}\}$ \\
+    & $\neg a \land \neg b, a \land \neg b, \neg a \land b, a \land b$ & $\{\emptyset\}, \{\{a\}\}, \{\{b\}\}, \{\{a, b\}\}$ \\
+    \multirow{-7}{*}{Formulas (elements of $2^{2^U}$)} & $\bot$ & $\emptyset$ \\
     \bottomrule
@@
 Given the theory $\Delta$, we can also compute the probability of a query $b$ as
-\cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
+\cite{DBLP:conf/aaai/SangBK05}
 \[
@@
 
-\section{Limitations of Factorable Measures}
+\subsection{Limitations of Factorable Measures}
 
 \todo[inline,caption={}]{
-  Examples (must):
-  \begin{itemize}
-  \item an example of a measure that cannot be expressed using a factored weight
-    function,
-  \item an example of how to express it using conditional weight functions.
-  \end{itemize}
-  Also, define `conditional weight function'.
+  Clarify what is meant by`conditional weight function'.
 }
+
+\begin{example}
+  Let $U = \{a, b\}$ be a set of atoms and $M\colon 2^{2^U} \to \mathbb{R}_{\ge
+    0}$ a measure defined as:\footnote{The value of $M$ on any other element of
+    the Boolean algebra can be deduced using the definition.}
+  \begin{align*}
+    M(a \land b) &= 0.72, \\
+    M(a \land \neg b) &= 0.18, \\
+    M(\neg a \land b) &= 0.07, \\
+    M(\neg a \land \neg b) &= 0.03.
+  \end{align*}
+  If $M$ could be represented using traditional (factored) WMC, we would have to
+  find two weight functions $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and
+  $W_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $W = W_a \cdot W_b$
+  induces $M$, i.e., $W_a$ and $W_b$ would have to satisfy this system of
+  equations:
+  \begin{align*}
+    W_a(\{a\}) \cdot W_b(\{b\}) &= 0.72 \\
+    W_a(\{a\}) \cdot W_b(\emptyset) &= 0.18 \\
+    W_a(\emptyset) \cdot W_b(\{b\}) &= 0.07 \\
+    W_a(\emptyset) \cdot W_b(\emptyset) &= 0.03,
+  \end{align*}
+  which has no solutions.
+
+  Alternatively, we can let $b$ depend on $a$ and consider weight functions
+  $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and $W_b\colon 2^{\{a, b\}} \to
+  \mathbb{R}_{\ge 0}$ defined as
+  \begin{align*}
+    W_a(\{a\}) &= 0.9, \\
+    W_a(\emptyset) &= 0.1,
+  \end{align*}
+  and
+  \begin{align*}
+    W_b(\{a, b\}) &= 0.8, \\
+    W_b(\{a\}) &= 0.2, \\
+    W_b(\{b\}) &= 0.7, \\
+    W_b(\emptyset) &= 0.3.
+  \end{align*}
+  One can easily check that with these definitions $W$ indeed induces $M$.
+\end{example}
 
@@
   \mathbb{R}_{\ge 0}$ be defined by $W_x(\{ x \}) = M(x)$ and $W_x(\emptyset) =
-  M(\neg x)$. Let $M_W$ be the measure induced by
-  \[
-    W = \prod_{x \in U} W_x.
-  \]
-  We will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by
-  \cref{def:wmc,prop:measure}. Second, let
-  \[
-    a = \bigwedge_{u \in U} a_u
-  \]
-  be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$.
-  Then
+  M(\neg x)$. Let $M_W$ be the measure induced by $W = \prod_{x \in U} W_x$. We
+  will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by
+  \cref{def:wmc,prop:measure}. Second, let $a = \bigwedge_{u \in U} a_u$ be an
+  atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$. Then
   \[
@@
   ($\Rightarrow$) For the other direction, we are given a factored weight
-  function
-  \[
-    W = \prod_{x \in U} W_x,
-  \]
-  and we want to show that its induced measure $M_W$ satisfies
-  \cref{eq:wmccondition}. Let $k_u, k_v \in U \cup \{ \neg w \mid w \in U \}$ be
-  such that $k_u \in \{ u, \neg u \}$, $k_v \in \{ v, \neg v \}$, and $u \ne v$.
-  We then want to show that
+  function $W = \prod_{x \in U} W_x$, and we want to show that its induced
+  measure $M_W$ satisfies \cref{eq:wmccondition}. Let $k_u, k_v \in U \cup \{
+  \neg w \mid w \in U \}$ be such that $k_u \in \{ u, \neg u \}$, $k_v \in \{ v,
+  \neg v \}$, and $u \ne v$. We then want to show that
   \begin{equation} \label{eq:to_prove3}
@@
   \end{align*}
-  where
-  \[
-    C = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}} W_x(a),
-  \]
-  and is the same for $M_W(\neg k_u \land k_v)$, $M_W(k_u \land \neg k_v)$, and
-  $M_W(\neg k_u \land \neg k_v)$ as well. But then \cref{eq:to_prove4} becomes
+  where $C = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}}
+  W_x(a)$, and is the same for $M_W(\neg k_u \land k_v)$, $M_W(k_u \land \neg
+  k_v)$, and $M_W(\neg k_u \land \neg k_v)$ as well. But then
+  \cref{eq:to_prove4} becomes
   \[
@@
 A \emph{Bayesian network} is a directed acyclic graph with random variables as
-vertices that defines a probability distribution over them. Let $V$ denote the
-set of random variables and $X \in V$ be a random variable. Let $\im X$ denote
-the set of possible values of $X$ and $\mathrm{pa}(X)$ denote the set of its
-parents. The full probability distribution is then equal to
+vertices that defines a probability distribution over them. Let $\mathcal{V}$
+denote the set of random variables and $X \in \mathcal{V}$ be a random variable.
+Let $\im X$ denote the set of possible values of $X$ and $\mathrm{pa}(X)$ denote
+the set of its parents. The full probability distribution is then equal to
 \begin{equation} \label{eq:factorisation}
-  \prod_{X \in V} \Pr(X \mid \mathrm{pa}(X)).
+  \prod_{X \in \mathcal{V}} \Pr(X \mid \mathrm{pa}(X)).
 \end{equation}
@@
 example Bayesian network which we will refer to throughout this section. For
-this network, $V = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F)
-= \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m,
-h \}$.
+this network, $\mathcal{V} = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
+$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
+$\im T = \{ l, m, h \}$.
 
 \begin{definition}[Indicator variables]
-  Let $X \in V$ be a random variable. If $X$ is binary (i.e., $|\im X| = 2$), we
-  can arbitrary identify one of the values as $1$ and the other one as $0$ (i.e,
-  $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
+  Let $X \in \mathcal{V}$ be a random variable. If $X$ is binary (i.e., $|\im X|
+  = 2$), we can arbitrary identify one of the values as $1$ and the other one as
+  $0$ (i.e, $\im X \cong \{ 0, 1 \}$). Then $X$ can be represented by a single
   \emph{indicator variable} $\lambda_{X=1}$. For notational simplicity, for any
   set $S$, we write $\lambda_{X=0} \in S$ or $S = \{ \lambda_{X=0}, \dots \}$ to
-  mean $\lambda_{X=1} \not\in S$,
+  mean $\lambda_{X=1} \not\in S$.
 
@@
   \]
-  denote the set of indicator variables for $X$ and
-  \[
-    E^*(X) = E(X) \cup \bigcup_{Y \in \mathrm{pa}(X)} E(Y).
-  \]
-  denote the set of indicator variables for $X$ and its parents in the Bayesian
-  network. Finally, let
-  \[
-    U = \bigcup_{X \in V} E(X)
-  \]
-  denote the set of all indicator variables for all random variables in the
-  Bayesian network.
+  denote the set of indicator variables for $X$ and $E^*(X) = E(X) \cup
+  \bigcup_{Y \in \mathrm{pa}(X)} E(Y)$ denote the set of indicator variables for
+  $X$ and its parents in the Bayesian network. Finally, let $U = \bigcup_{X \in
+    \mathcal{V}} E(X)$ denote the set of all indicator variables for all random
+  variables in the Bayesian network.
 \end{definition}
@@
   \label{alg:encoding}
-  \KwData{a Bayesian network with vertices $V$ and probability distribution
-    $\Pr$}
+  \KwData{a Bayesian network with vertices $\mathcal{V}$ and probability
+    distribution $\Pr$}
   \KwResult{a function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
   $\phi \gets 1$\;
-  \For{$X \in V$}{
+  \For{$X \in \mathcal{V}$}{
     \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
@@
 \begin{lemma} \label{lemma:cpt}
-  Let $X \in V$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
+  Let $X \in \mathcal{V}$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
   \dots, Y_n \}$. Then $\mathrm{CPT}_X\colon 2^{E^*(X)} \to \mathbb{R}_{\ge 0}$
@@
 
-  If $X$ is not binary, then
-  \[
-    \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(\tau) = 1,
-  \]
-  and
+  If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
+  \right)(\tau) = 1$, and
   \[
@@
   \]
-  so, by a similar argument as before,
-  \[
-    \mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
-  \]
+  so $\mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by a
+  similar argument as before.
 \end{proof}
@@
   $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ represents the full probability
-  distribution of the Bayesian network, i.e., if $V = \{ X_1, \dots, X_n\}$,
-  then
+  distribution of the Bayesian network, i.e., if $\mathcal{V} = \{ X_1, \dots,
+  X_n\}$, then
   \[
@@
 \begin{proof}
-  If $\tau = \{ \lambda_{X=v_X} \mid X \in V \}$ for some $(v_X)_{X \in V} \in
-  \prod_{X \in V} \im X$, then
-  \[
-    \phi(\tau) = \prod_{X \in V} \Pr \left( X=v_X \;\middle|\; \bigwedge_{Y \in
-        \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X \in V} X=v_X
-    \right)
+  If $\tau = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
+    \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
+  \[
+    \phi(\tau) = \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\;
+      \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X
+        \in \mathcal{V}} X=v_X \right)
   \]
   by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
-  must be some non-binary random variable $X \in V$ such that $|E(X) \cap \tau|
-  \ne 1$. If $E(X) \cap \tau = \emptyset$, then
-  \[
-    \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(\tau) = 0,
-  \]
-  and so $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$. If $|E(X) \cap
-  \tau| > 1$, then we must have two different values $x_1, x_2 \in \im X$ such
-  that $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq \tau$ which means that
-  \[
-    (\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(\tau) = 0,
-  \]
-  and so, again, $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$.
+  must be some non-binary random variable $X \in \mathcal{V}$ such that $|E(X)
+  \cap \tau| \ne 1$. If $E(X) \cap \tau = \emptyset$, then $\left( \sum_{i=1}^m
+    [\lambda_{X = x_i}] \right)(\tau) = 0$, and so $\mathrm{CPT}_X(\tau) = 0$,
+  and $\phi(\tau) = 0$. If $|E(X) \cap \tau| > 1$, then we must have two
+  different values $x_1, x_2 \in \im X$ such that $\{\lambda_{X=x_1},
+  \lambda_{X=x_2} \} \subseteq \tau$ which means that
+  $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(\tau) = 0$, and
+  so, again, $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$.
 \end{proof}
@@
 \begin{theorem}
-  Let $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ be a function generated by the
-  algorithm. Then
-  \[
-    (\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset) = \Pr(X = x).
-  \]
+  Let $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ be the function generated by
+  \cref{alg:encoding}. Then $(\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset)
+  = \Pr(X = x)$.
 \end{theorem}
 \begin{proof}
-  Let $V = \{ X, Y_1, \dots, Y_n \}$. Then
+  Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
   \begin{align*}
-    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{\tau \in 2^U} (\phi \cdot [\lambda_{X=x}])(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \phi(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \left( \prod_{Y \in V} \mathrm{CPT}_Y \right)(\tau) \\
+    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{\tau \in 2^U} (\phi \cdot [\lambda_{X=x}])(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \phi(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(\tau) \\
     &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
@@
     \input{cumulative.tex}%
-    \captionof{figure}{Cumulative plot}
+    \captionof{figure}{Cumulative number of instances solved by ADDMC over time
+      using each encoding}
   \end{minipage}
@@
     \centering
-    \captionof{table}{Out of 1216 instances}%
+    \captionof{table}{The numbers of instances solved by ADDMC with each
+      encoding (uniquely, faster than with others, and in total) under the
+      described time and memory constraints (out of 1216 instances)}%
     \begin{tabular}{lrrr}
       \toprule
-      Encoding & Unique & Fastest & Solved \\
+      Encoding & Unique & Fastest & Total \\
       \midrule
@@
   \input{scatter.tex}%
-  \caption{Scatter plots}
+  \caption{ADDMC inference time using \texttt{db20} compared to \texttt{d02}
+    (left) and \texttt{sbk05} (right) on an instance-by-instance basis across
+    all data sets.}
 \end{figure}
@@
 \item Whenever a Bayesian network comes with an evidence file, we compute the
-  probability of evidence. Otherwise, let $X$ denote the last-mentioned node in
-  the Bayesian network. If $\mathsf{true}$ is a valid value of $X$, we compute
-  the marginal probability of $X = \mathsf{true}$. Otherwise, we pick the value
-  of $X$ which is listed first and calculate its marginal probability.
+  probability of evidence. Otherwise, let $X$ denote the last-mentioned vertex
+  in the Bayesian network. If $\mathsf{true}$ is a valid value of $X$, we
+  compute the marginal probability of $X = \mathsf{true}$. Otherwise, we pick
+  the value of $X$ which is listed first and calculate its marginal probability.
 \item The experiments were run on Intel Xeon Gold 6138 processor with an
@@
   is so either because the particular structure of these problems confuse the
-  algorithm's heuristics or because these instances allow for significant
+  heuristics used by ADDMC or because these instances allow for significant
   simplifications that are exploited by $\mathtt{d02}$ but not
   $\mathtt{db20}$.
-\end{itemize}
-
-\section{Explaining The Performance Benefits}
-
-\begin{itemize}
-\item \texttt{d02} has
-  \[
-    \sum_{X \in V} |\im X| + |\im X|\prod_{Y \in \mathrm{pa}(X)}|\im Y|
-  \]
-  variables and
-  \[
-    \sum_{X \in V} 1 + \binom{|\im X|}{2} + |\im X|(2 +
-    |\mathrm{pa}(X)|)\prod_{Y \in \mathrm{pa}(X)} |\im Y|
-  \]
-  clauses (along with one ADD per variable to encode the weights).
-\item \texttt{sbk05} is a bit harder to evaluate due to a handful of small
-  optimisations in the encoding. Could find an upper bound anyway.
-\item \texttt{db20} (my encoding) has
-  \[
-    \sum_{X \in V} |\im X|
-  \]
-  variables (less for binary) and
-  \[
-    \sum_{X \in V} |\im X| + 1 + \binom{|\im X|}{2}
-  \]
-  ADDs.
-\item Let:
-  \begin{itemize}
-  \item $N = |V|$ (i.e., the number of nodes in the Bayesian network),
-  \item $D = \max_{X \in V} |\mathrm{pa}(X)|$ (i.e., the maximum in-degree or
-    the number of parents),
-  \item $V = \max_{X \in V} |\im X|$ (i.e., the maximum number of values per
-    variables).
-  \end{itemize}
-\item Then my encoding has $\mathcal{O}(NV)$ variables and $\mathcal{O}(NV^2)$
-  ADDs while \texttt{d02} has $\mathcal{O}(NV^{D+1})$ variables and
-  $\mathcal{O}(NDV^{D+1})$ ADDs.
-\end{itemize}
-
-\todo[inline]{Calculate numVariables/numClauses (or the other way around) for
-  each instance and plot this ratio vs runtime (for each encoding, or at least
-  mine and D02). The new CP paper kind of beat me to it...}
+\item Everything \texttt{d02} can do in \SI{1000}{\second}, \texttt{db20} can do
+  in \SI{10}{\second} (find the exact number).
+\end{itemize}
+
+\begin{table}
+  \centering
+  \caption{Asymptotic upper bounds on the numbers of variables and clauses/ADDs
+    for each encoding}
+  \label{tbl:asymptotes}
+  \begin{tabular}{lcc}
+    \toprule
+    Encoding(s) & Variables & Clauses/ADDs \\
+    \midrule
+    \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(nv^{d+1})$ \\
+    \texttt{d02} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(ndv^{d+1})$ \\
+    \texttt{db20} & $\mathcal{O}(nv)$ & $\mathcal{O}(nv^2)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\paragraph{Explaining The Performance Benefits.} Let $n = |\mathcal{V}|$ be the
+number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
+|\mathrm{pa}(X)|$ the maximum in-degree (i.e., number of parents), and $v =
+\max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
+Then... \cref{tbl:asymptotes}.
+
+\todo[inline]{Remember that these are upper bounds! Some of these encoding have
+  a lot of optimisations that are not captured by three parameters!}
+
+\todo[inline]{Explain why clauses and ADDs are alike.}
 
@@
 \item Important future work: replacing ADDs with
-  AADDs\footnote{\url{https://github.com/ssanner/dd-inference}}
-  \cite{DBLP:conf/ijcai/SannerM05} is likely to bring performance benefits.
+  AADDs \cite{DBLP:conf/ijcai/SannerM05} is likely to bring performance
+  benefits.
   Other extensions:
@@
     \begin{itemize}
-    \item For the ProbLog to WMC conversion, check out this guy:
-      \url{https://users.ics.aalto.fi/ttj/}.
     \item proof-based \cite{DBLP:conf/iclp/MantadelisJ10}
     \item rule-based \cite{DBLP:conf/ecai/Janhunen04}
-    \item For ground ProbLog, we can encode a program
-\begin{verbatim}
-p :: a :- b
-q :: a :- c
-\end{verbatim}
-      into $P(a \mid b)=p$, $P(a \mid c)=q$ instead of having clauses $b
-      \Rightarrow a$, $c \Rightarrow a$. Some logical structure is likely to
-      remain.
     \end{itemize}
@@
   variable elimination/projection/$\exists$.
-\item More references
-  \begin{itemize}
-  \item Measures on/in Boolean algebras: Horn and Tarski
-    \cite{horn1948measures}, Jech \cite{jech2017measures}
-  \item On Boolean algebras and their role in analysis \cite{winkowska1996boolean}
-  \item Infinite domains
-    \begin{itemize}
-    \item Markov Logic in Infinite Domains (Singla and Domingos)
-      \cite{DBLP:conf/uai/SinglaD07}
-    \item Objective Bayesian probabilistic logic (Williamson)
-      \cite{DBLP:journals/jal/Williamson08}
-    \item Unifying Logic and Probability (Russell)
-      \cite{DBLP:journals/cacm/Russell15}
-    \end{itemize}
-  \item Logical induction \cite{DBLP:journals/eccc/GarrabrantBCST16}
-  \item Quantum probabilistic logic programming \cite{balu2015quantum}
-  \item WMC
-    \begin{itemize}
-    \item algebraic model counting \cite{DBLP:journals/japll/KimmigBR17}
-    \item Explanation-Based Approximate Weighted Model Counting for
-      Probabilistic Logics \cite{DBLP:conf/aaai/RenkensKBR14}
-    \item OUWMC \cite{DBLP:conf/aaai/Belle17}
-    \item Formula-Based Probabilistic Inference \cite{DBLP:conf/uai/GogateD10}
-    \item Parallel Probabilistic Inference by WMC \cite{DBLP:conf/pgm/DalLL18}
-    \item Semiring Programming \cite{DBLP:journals/corr/BelleR16}
-    \item theoretical extension: WMC beyond two-variable logic
-      \cite{DBLP:conf/lics/KuusistoL18}
-    \item from weighted to unweighted model counting
-      \cite{DBLP:conf/ijcai/ChakrabortyFMV15}
-    \item theory behind WMC algorithms: solving \#\SAT{} and Bayesian inference
-      with backtracking search \cite{DBLP:journals/jair/BacchusDP09}
-    \end{itemize}
-  \end{itemize}
+\item I could also add a memory usage cumulative plot, but it doesn't add any
+  extra info except for the fact that inference is memory-intensive.
 \end{itemize}

### 2020-07-30 analyse.R

@@ -10,7 +10,7 @@ TIMEOUT <- 1000
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
 df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
-df0$memory[is.na(df0$memory)] <- max(df0$memory)
+df0$memory[is.na(df0$memory)] <- max(df0$memory, na.rm = TRUE)
 df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time", "memory"))
 df$time_min <- as.numeric(apply(df, 1, function (row) min(row["time_cd05"], row["time_cd06"],
                                                           row["time_d02"], row["time_db20"], row["time_sbk05"])))
@@ -61,12 +61,8 @@ sum(!is.na(df$answer_sbk05))
 # ================ Plots ==========================
 
 # Scatter plot: by dataset
-# Consider:
-# 1. Shapes as well as colors (set manually).
-# 2. Adjust the alpha value.
-
 min.time <- min(df0$time)
-p1 <- ggplot(df[df$time_d02 > 0,], aes(x = time_d02, y = time_db20, col = major.dataset)) +
+p1 <- ggplot(df[df$time_d02 > 0,], aes(x = time_d02, y = time_db20, col = major.dataset, shape = major.dataset)) +
   geom_point(alpha = 0.5, size = 1) +
   geom_abline(slope = 1, intercept = 0, colour = "#989898") +
   scale_x_continuous(trans = log10_trans(), limits = c(min.time, TIMEOUT), breaks = c(0.1, 10, 1000), labels = c("0.1", "10", "1000")) +
@@ -76,8 +72,9 @@ p1 <- ggplot(df[df$time_d02 > 0,], aes(x = time_d02, y = time_db20, col = major.
   scale_color_brewer(palette = "Dark2", name = "Data set") +
   coord_fixed() +
   annotation_logticks(colour = "#b3b3b3") +
-  theme_light()
-p2 <- ggplot(df[df$time_sbk05 > 0,], aes(x = time_sbk05, y = time_db20, col = major.dataset)) +
+  theme_light() +
+  labs(color = "Data set", shape = "Data set")
+p2 <- ggplot(df[df$time_sbk05 > 0,], aes(x = time_sbk05, y = time_db20, col = major.dataset, shape = major.dataset)) +
[…]

### 2020-07-31 paper/paper.tex
Writing

@@
 \usepackage{complexity}
-\usepackage{soul}
 \usepackage{subcaption}
@@
 \usepackage[inline]{enumitem}
+
+\usetikzlibrary{cd}
+\usetikzlibrary{bayesnet}
+\usetikzlibrary{calc}
 
@@
 \newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
 \theoremstyle{definition}
@@
 
-\Crefname{property}{Property}{Properties}
-\Crefname{condition}{Condition}{Conditions}
-\creflabelformat{condition}{#2(#1)#3}
-
-\DeclareMathOperator{\WMC}{WMC}
-\DeclareMathOperator{\nWMC}{NWMC}
-\DeclareMathOperator{\id}{id}
-\DeclareMathOperator{\End}{End}
 \DeclareMathOperator{\im}{im}
-
-\usetikzlibrary{cd}
-\usetikzlibrary{bayesnet}
-\usetikzlibrary{calc}
-
-\tikzset{
-  Subset/.style={
-    draw=none,
-    every to/.append style={
-      edge node={node [sloped, allow upside down, auto=false]{$\subset$}}}
-  }
-}
 
@@
   \end{enumerate}
-\item Potential criticism may be that this doesn't allow us to use SAT-based
-  techniques for probabilistic inference. However, they can still be used for a
-  significant part of the encoding.
+\item Introduce
   \begin{itemize}
-  \item Zero-probability weights and one-probability weights can be interpreted
-    as logical clauses. This doesn't affect ADDMC but could be useful for other
-    solvers.
+  \item WMC
+  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} and ADDs
+    \cite{DBLP:journals/fmsd/BaharFGHMPS97}
+  \item A Bayesian network is a directed acyclic graph with random variables as
+    vertices that defines a probability distribution over them. The full
+    probability distribution can be expressed as the product of the conditional
+    probability distributions of all random variables. For discrete Bayesian
+    networks (and we only consider discrete networks in this paper), each such
+    distribution can be represented by a table known as a conditional
+    probability table (CPT).
   \end{itemize}
@@
   of theorems to follow.
-\item
-  Algorithms
-  \begin{itemize}
-  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
-    multiplicativity of BAs in different words) (with optimal settings)
-  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
-  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
-  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
-  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
-  \end{itemize}
 \item Notable previous/related work
@@
   \end{itemize}
-\item Intuitively, a measure is just like a probability, except it's in
-  $\mathbb{R}_{\ge 0}$ instead of $[0, 1]$.
+\item Our work is, in spirit, similar to... using ROBDDs for Inference in
+  Bayesian Networks with Troubleshooting as an Example
+  \cite{DBLP:conf/uai/NielsenWJK00}: this is an interesting approach where
+  deterministic parts of a BN are expressed as Boolean functions, i.e.,
+  extracting the logical from the probabilistic. Maybe I can make a case that my
+  encoding (the textual version) kind of does the same, even though the
+  algorithm doesn't.
 \end{itemize}
 
-\section{Boolean Algebras and Power Sets}
+\section{Related Work}
+
+\paragraph{Using WMC to perform inference on Bayesian networks.} Hitherto, four
+techniques have been proposed for encoding Bayesian networks into instances of
+WMC. We will identify them based on the initials of authors as well as
+publications years: \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}, \texttt{sbk05}
+\cite{DBLP:conf/aaai/SangBK05}, \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05},
+and \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}. Below we friendly summarise
+the observed performance differences among them. Sang et al.
+\cite{DBLP:conf/aaai/SangBK05} claim that \texttt{sbk05} is a smaller encoding
+than \texttt{d02} with respect to both the number of clauses and the number of
+variables but provide no experimental comparison. Chavira and Darwiche
+\cite{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with \texttt{d02} by
+measuring the time it takes to compile either encoding into an arithmetic
+circuit (but do not measure inference time). The more recent encoding
+\texttt{cd05} always compiles faster and results in a smaller arithmetic circuit
+(as measured by the number of edges). In their subsequent paper, the same
+authors perform two sets of experiments (that are relevant to this summary)
+\cite{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
+\texttt{cd06} encodings into d-DNNF (i.e., deterministic decomposable negation
+normal form \cite{DBLP:journals/jancl/Darwiche01}), measuring both compilation
+time and numbers of edges in the d-DNNF diagram. The results are mostly in
+favour of \texttt{cd06}. Second, they compare the inference time of
+\texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04} with the compile
+times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
+In these experiments, \texttt{cd06} is always faster than \texttt{cd05}, while
+the comparison with \texttt{sbk05} is mixed. Sometimes \texttt{cd06} is orders
+of magnitude faster than \texttt{sbk05}, sometimes slightly slower. The
+performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
+to judge: \texttt{sbk05} is better on three out of five instances and worse on
+the remaining two. Based on this description, one would expect \texttt{cd06} to
+be faster than both \texttt{cd05} and \texttt{sbk05}, both of which should be
+faster than \texttt{d02}. The experiments in \cref{sec:experiments}, however,
+strongly disagree with this prediction, showing that the quality of an encoding
+depends strongly on the underlying search algorithm or compilation technique.
+
+\paragraph{ADDs and their use in probabilistic inference.} ADDs provide an
+efficient way to manipulate functions from a Boolean algebra to any algebraic
+structure (most commonly $\mathbb{R}$) \cite{DBLP:journals/fmsd/BaharFGHMPS97}.
+They have been used to represent value functions in Markov decision processes
+\cite{DBLP:conf/uai/HoeySHB99} and, for Bayesian network inference, to represent
+each CPT as an ADD \cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs
+and arithmetic circuits into a  single representation
+\cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous in this
+situation because of their ability to fully exploit context-specific
+independence, i.e., observable structure within a CPT that is not inherited from
+the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
+
+\section{Boolean Algebras, Power Sets, and Propositional
+  Logic} \label{sec:prelims}
 
@@
 
-Let $X$ be a set and let $2^X$ be its power set. We can equivalently interpret
-$2^X$ as a Boolean algebra. See \cref{tbl:notation} for a summary of the
-differences in terminology and notation. We will use both.
-
-\subsection{The Space of Functions on Boolean Algebras}
-
-\begin{definition}[Operations on functions]
-  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
-    0}$ be functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We define
-  the following operations:
-  \begin{description}
-  \item[Addition:] $A+B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$ is a function
-    such that $(A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)$ for all $\tau \in
-    2^{X \cup Y}$.
-  \item[Inverse:] $\overline{A}\colon 2^X \to \mathbb{R}_{\ge 0}$ is a function
-    such that $\overline{A}(\tau) = 1 - A(\tau)$ for all $\tau \in 2^X$.
-  \item[Multiplication:] $A \cdot B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$
-    is a function such that $(A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau
-    \cap Y)$ for all $\tau \in 2^{X \cup Y}$.
-  \item[Scalar multiplication:] $\alpha A\colon 2^X \to \mathbb{R}_{\ge 0}$ is a
-    function such that $(\alpha A)(\tau) = \alpha \cdot A(\tau)$ for all $\tau
-    \in 2^X$.
-  \item[Projection:] $\exists_xA\colon 2^{X \setminus \{ x \}} \to
-    \mathbb{R}_{\ge 0}$ is a function such that $(\exists_xA)(\tau) = A(\tau) +
-    A(\tau \cup \{ x \})$ for all $\tau \in 2^{X \setminus \{x \}}$.
-  \end{description}
-\end{definition}
-
-\begin{observation}
-  Let $U$ be a set, and $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0}
-  \mid X \subseteq U \}$. Then $\mathcal{V}$ is a semi-vector space with three
-  additional operations: inverse, (non-scalar) multiplication, and projection.
-  Specifically, note that both addition and multiplication are both associative
-  and commutative.
-\end{observation}
-
-\begin{definition}[Special functions]
-  \phantom{}
-  \begin{itemize}
-  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\emptyset) = 1$.
-  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\emptyset) = 0$.
-  \item logical constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
-    $[a](\emptyset) = 0$, $[a](\{a\}) = 1$.
-  \end{itemize}
-\end{definition}
-
-Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
-$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
-
-\section{Weighted Model Counting as a Measure}
-
-\begin{definition}[Measures and weight functions] \label{def:wmc}
-  Let $U$ be a set.
-  \begin{itemize}
-  \item A \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$
-    such that $M(\bot) = 0$, and $M(a \lor b) = M(a) + M(b)$ for all $a, b \in
-    2^{2^U}$ whenever $a \land b = \bot$.
-  \item A \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
-      0}$.
-  \item A weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
-    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$.
-  \item We say that a weight function $W\colon 2^U \to \mathbb{R}_{\ge 0}$
-    \emph{induces} a measure $M_W\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
-    \begin{equation} \label{eq:induced_measure}
-      M_W(x) = \sum_{\{u\} \le x} W(u).
-    \end{equation}
-  \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
-    \emph{factorable} if there exists a factored weight function $W\colon 2^U
-    \to \mathbb{R}_{\ge 0}$ that induces $M$.
-  \end{itemize}
-\end{definition}
-
-\begin{lemma} \label{prop:measure}
-  The function $M_W$, as defined by \cref{eq:induced_measure}, is a measure.
-\end{lemma}
-\begin{proof}
-  Note that $M_W(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b \in
-  2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
-  Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
-  $b$. Moreover, none of them can be below both $a$ and $b$ because then they
-  would have to be below $a \land b = \bot$. Thus
-  \[
-    M_W(a \lor b) = \sum_{\{u\} \le a \lor b} W(u) = \sum_{\{u\} \le a} W(u) +
-    \sum_{\{u\} \le b} = M_W(a) + M_W(b)
-  \]
-  as required.
-\end{proof}
-
-In this formulation, the process of calculating the value of $M_W(x)$ for some
-$x \in 2^{2^U}$ with a given definition of $W$ is known as \emph{weighted model
-  counting}.
-
-\subsection{Relation to the Classical (Logic-Based) View of WMC}
-
-\todo[inline]{Would it be more accurate to replace the word `model' with
-  `interpretation' in most situations?}
-
 \begin{table}
-  \caption{An overview of notation for a logic defined over two atoms. The
-    elements in both columns are listed in the same order.}
+  \caption{Notation for a logic with two atoms. The elements in both columns are
+    listed in the same order.}
   \label{tbl:notation_example}
@@
 
+\todo[inline]{Completely rewrite this section. It needs to be very clear and
+  introduce all relevant terminology.}
+\todo[inline]{Would it be more accurate to replace the word `model' with
+  `interpretation' in most situations?}
+
+For any set $X$, we can interpret $2^X$ as either a power set or a Boolean
+algebra---see \cref{tbl:notation} for a summary of the differences in
+terminology and notation.
+
 Let $\mathcal{L}$ be a propositional logic with atoms $U = \{ a, b \}$. See
@@
 
-Let $w\colon \{ a, b, \neg a, \neg b \} \to \mathbb{R}_{\ge 0}$
-be the \emph{weight function} defined by
-\begin{align*}
-  w(a) = 0.3, \quad w(\neg a) = 0.7, \quad w(b) = 0.2, \quad w(\neg b) = 0.8.
-\end{align*}
-Let $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $a$. Then
-$\Delta$ has two models, i.e., $\{ a, b \}$ and $\{ a, \neg b \}$. The
-\emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of
-$\Delta$ is then
+In the rest of the paper, for any set $U$, we will use set-theoretic notation
+for $2^U$ and Boolean-algebraic notation for $2^{2^U}$, except for (Boolean)
+atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some model $x \in 2^U$.
+
+\subsection{The Space of Functions on Boolean Algebras}
+
+We build on the definitions of multiplication and projection in the ADDMC paper
+\cite{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
+manipulate functions from Boolean algebras to non-negative reals. All of these
+operations have efficient implementations in the CUDD \cite{somenzi1998cudd}
+package for manipulating ADDs (among other things) that is used by ADDMC
+{\cite{DBLP:conf/aaai/DudekPV20}.
+
+\begin{definition}[Operations on functions]
+  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
+    0}$ be functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We define
+  the following operations:
+  \begin{description}
+  \item[Addition:] $A+B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$ is
+    such that $(A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)$ for all $\tau \in
+    2^{X \cup Y}$.
+  \item[Multiplication:] $A \cdot B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$
+    is such that $(A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau
+    \cap Y)$ for all $\tau \in 2^{X \cup Y}$.
+  \item[Scalar multiplication:] $\alpha A\colon 2^X \to \mathbb{R}_{\ge 0}$ is
+    such that $(\alpha A)(\tau) = \alpha \cdot A(\tau)$ for all $\tau
+    \in 2^X$.
+  \item[Complement:] $\overline{A}\colon 2^X \to \mathbb{R}_{\ge 0}$ is
+    such that $\overline{A}(\tau) = 1 - A(\tau)$ for all $\tau \in 2^X$.
+  \item[Projection:] $\exists_xA\colon 2^{X \setminus \{ x \}} \to
+    \mathbb{R}_{\ge 0}$ is such that $(\exists_xA)(\tau) = A(\tau) +
+    A(\tau \cup \{ x \})$ for all $\tau \in 2^{X \setminus \{x \}}$.
+  \end{description}
+\end{definition}
+
+\begin{observation}
+  Let $U$ be a set, and $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0}
+  \mid X \subseteq U \}$. Then $\mathcal{V}$ is a semi-vector space with three
+  additional operations: inverse, (non-scalar) multiplication, and projection.
+  Specifically, note that both addition and multiplication are both associative
+  and commutative.
+\end{observation}
+
+\begin{definition}[Special functions]
+  We define several special functions:
+  \begin{itemize}
+  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\emptyset) = 1$;
+  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\emptyset) = 0$;
+  \item and $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$, $[a](\emptyset) = 0$,
+    $[a](\{a\}) = 1$ for any $a$.
+  \end{itemize}
+\end{definition}
+
+Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
+$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
+
+\section{WMC as a Measure}
+
+Let $U$ be a set. A \emph{measure} is a function $M\colon 2^{2^U} \to
+\mathbb{R}_{\ge 0}$ such that $M(\bot) = 0$, and $M(a \lor b) = M(a) + M(b)$ for
+all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$. A \emph{weight function} is
+a function $W\colon 2^U \to \mathbb{R}_{\ge 0}$. A weight function is
+\emph{factored} if $W = \prod_{x \in U} W_x$ for some functions $W_x\colon
+2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$. We say that a weight function
+$W\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a measure $M_W\colon 2^{2^U}
+\to \mathbb{R}_{\ge 0}$ if
+\begin{equation} \label{eq:induced_measure}
+  M_W(x) = \sum_{\{u\} \le x} W(u).
+\end{equation}
+Finally, a measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is \emph{factorable}
+if there exists a factored weight function $W\colon 2^U \to \mathbb{R}_{\ge 0}$
+that induces $M$.
+
+\begin{lemma} \label{prop:measure}
+  The function $M_W$, as defined by \cref{eq:induced_measure}, is a measure.
+\end{lemma}
+\begin{proof}
+  Note that $M_W(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b \in
+  2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
+  Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
+  $b$. Moreover, none of them can be below both $a$ and $b$ because then they
+  would have to be below $a \land b = \bot$. Thus
+  \[
+    M_W(a \lor b) = \sum_{\{u\} \le a \lor b} W(u) = \sum_{\{u\} \le a} W(u) +
+    \sum_{\{u\} \le b} = M_W(a) + M_W(b)
+  \]
+  as required.
+\end{proof}
+
+In this formulation, the process of calculating the value of $M_W(x)$ for some
+$x \in 2^{2^U}$ with a given definition of $W$ is known as WMC.
+
+\paragraph{Relation to the classical (logic-based) view of WMC.} Let
+$\mathcal{L}$ be a propositional logic with two atoms $a$ and $b$ as in
+\cref{sec:prelims} and $w\colon \{ a, b, \neg a, \neg b \} \to \mathbb{R}_{\ge
+  0}$ a \emph{weight function} defined as $w(a) = 0.3$, $w(\neg a) = 0.7$, $w(b)
+= 0.2$, $w(\neg b) = 0.8$. Furthermore, let $\Delta$ be a theory in
+$\mathcal{L}$ with a sole axiom $a$. Then $\Delta$ has two models: $\{ a, b \}$
+and $\{ a, \neg b \}$ and its WMC \cite{DBLP:journals/ai/ChaviraD08} is
 \begin{equation} \label{eq:wmc_example}
@@
 \end{equation}
-
 Alternatively, we can define $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ as
-\[
-  W_a(\{ a \}) = 0.3, \quad W_a(\emptyset) = 0.7
-\]
-and $W_b\colon 2^{\{q\}} \to \mathbb{R}_{\ge 0}$ as
-\[
-  W_b(\{ b \}) = 0.2, \quad W_b(\emptyset) = 0.8.
-\]
-Let $M$ be the measure on $2^{2^U}$ induced by $W = W_a \cdot W_b$. Then,
-equivalently to \cref{eq:wmc_example}, we can write
+$W_a(\{ a \}) = 0.3$, $W_a(\emptyset) = 0.7$ and $W_b\colon 2^{\{q\}} \to
+\mathbb{R}_{\ge 0}$ as $W_b(\{ b \}) = 0.2$, $W_b(\emptyset) = 0.8$. Let $M$ be
+the measure on $2^{2^U}$ induced by $W = W_a \cdot W_b$. Then, equivalently to
+\cref{eq:wmc_example}, we can write
 \[
@@
 
-Given the theory $\Delta$, we can also compute the probability of a query $b$ as
-\cite{DBLP:conf/aaai/SangBK05}
-\[
-  \Pr_{\Delta, w}(b) = \frac{\WMC(\Delta \land b)}{\WMC(\Delta)}.
-\]
-The same thing can be accomplished using the algebraic formulation, with $M$
-replacing $\mathrm{WMC}$.
-
-In the rest of the paper, for any set $U$, we will use set-theoretic notation
-for $2^U$ and Boolean-algebraic notation for $2^{2^U}$, except for (Boolean)
-atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some model $x \in 2^U$.
-
 \subsection{Limitations of Factorable Measures}
-
-\todo[inline,caption={}]{
-  Clarify what is meant by`conditional weight function'.
-}
 
@@
   $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and $W_b\colon 2^{\{a, b\}} \to
-  \mathbb{R}_{\ge 0}$ defined as
-  \begin{align*}
-    W_a(\{a\}) &= 0.9, \\
-    W_a(\emptyset) &= 0.1,
-  \end{align*}
-  and
-  \begin{align*}
-    W_b(\{a, b\}) &= 0.8, \\
-    W_b(\{a\}) &= 0.2, \\
-    W_b(\{b\}) &= 0.7, \\
-    W_b(\emptyset) &= 0.3.
-  \end{align*}
-  One can easily check that with these definitions $W$ indeed induces $M$.
+  \mathbb{R}_{\ge 0}$ defined as $W_a(\{a\}) = 0.9$, $W_a(\emptyset) = 0.1$, and
+  $W_b(\{a, b\}) = 0.8$, $W_b(\{a\}) = 0.2$, $W_b(\{b\}) = 0.7$, $W_b(\emptyset)
+  = 0.3$. One can easily check that with these definitions $W$ indeed induces
+  $M$.
 \end{example}
+
+Note that in this case we chose to interpret $W_b$ as $\Pr(B \mid A)$
+while---with a different definition of $W_b$ that represents the joint
+probability distribution $\Pr(A, B)$---$W_b$ by itself could induce $M$. In
+general, however, factorising the full weight function into several smaller
+functions often results in weight functions with smaller domains which leads to
+increased efficiency and decreased memory usage \cite{DBLP:conf/aaai/DudekPV20}.
 
@@
   will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by
-  \cref{def:wmc,prop:measure}. Second, let $a = \bigwedge_{u \in U} a_u$ be an
-  atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$. Then
+  \cref{prop:measure} and the definition of a measure. Second, let $a =
+  \bigwedge_{u \in U} a_u$ be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg
+  u \}$ for all $u \in U$. Then
   \[
@@
 \end{proof}
-
-\section{Previous Work}
-
-\subsection{Using WMC to Perform Inference on Bayesian Networks}
-
-Hitherto, four techniques have been proposed for encoding Bayesian networks into
-instances of WMC. We will identify them based on the initials of authors as well
-as publications years: \texttt{d02} \cite{DBLP:conf/kr/Darwiche02},
-\texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}, \texttt{cd05}
-\cite{DBLP:conf/ijcai/ChaviraD05}, and \texttt{cd06}
-\cite{DBLP:conf/sat/ChaviraD06}. Below we friendly summarise the observed
-performance differences among them. Sang et al. \cite{DBLP:conf/aaai/SangBK05}
-claim that \texttt{sbk05} is a smaller encoding than \texttt{d02} with respect
-to both the number of clauses and the number of variables but provide no
-experimental comparison. Chavira and Darwiche \cite{DBLP:conf/ijcai/ChaviraD05}
-compare \texttt{cd05} with \texttt{d02} by measuring the time it takes to
-compile either encoding into an arithmetic circuit (but do not measure inference
-time). The more recent encoding \texttt{cd05} always compiles faster and results
-in a smaller arithmetic circuit (as measured by the number of edges). In their
-subsequent paper, the same authors perform two sets of experiments (that are
-relevant to this summary) \cite{DBLP:conf/sat/ChaviraD06}. First, they compile
-\texttt{cd05} and \texttt{cd06} encodings into d-DNNF (i.e., deterministic
-decomposable negation normal form \cite{DBLP:journals/jancl/Darwiche01}),
-measuring both compilation time and numbers of edges in the d-DNNF diagram. The
-results are mostly in favour of \texttt{cd06}. Second, they compare the
-inference time of \texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04}
-with the compile times of \texttt{cd05} and \texttt{cd06}, but only on five
-(types of) instances. In these experiments, \texttt{cd06} is always faster than
-\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
-\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
-slightly slower. The performance difference between \texttt{sbk05} and
-\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
-five instances and worse on the remaining two. Based on this description, one
-would expect \texttt{cd06} to be faster than both \texttt{cd05} and
-\texttt{sbk05}, both of which should be faster than \texttt{d02}. The
-experiments in \cref{sec:experiments}, however, strongly disagree with this
-prediction, showing that the quality of an encoding depends strongly on the
-underlying search algorithm or compilation technique.
-
-\subsection{Algebraic Decision Diagrams and Their Use in Probabilistic
-  Inference}
-
-Cover:
-\begin{itemize}
-\item ADDs provide an efficient way to manipulate functions from BAs/power sets
-  \cite{DBLP:journals/fmsd/BaharFGHMPS97}.
-\item background reading
-  \begin{itemize}
-  \item Compiling Bayesian Networks Using Variable Elimination (Chavira and
-    Darwiche) \cite{DBLP:conf/ijcai/ChaviraD07}
-  \item On the Relationship between Sum-Product Networks and Bayesian Networks
-    \cite{DBLP:conf/icml/ZhaoMP15}
-  \item Using ROBDDs for Inference in Bayesian Networks with Troubleshooting as
-    an Example \cite{DBLP:conf/uai/NielsenWJK00}
-  \item SPUDD: Stochastic Planning using Decision Diagrams
-    \cite{DBLP:conf/uai/HoeySHB99}
-  \end{itemize}
-\end{itemize}
 
@@
 
-\todo[inline]{In line with the names of previous encodings, we shall call this
-  encoding \texttt{db20}.}
+In this section, we describe a way to encode Bayesian networks into WMC without
+restricting oneself to factorable measures and thus having to add extra
+variables to maintain literal independence. In line with the names of previous
+encodings, we shall call this encoding \texttt{db20}.
 
-A \emph{Bayesian network} is a directed acyclic graph with random variables as
-vertices that defines a probability distribution over them. Let $\mathcal{V}$
-denote the set of random variables and $X \in \mathcal{V}$ be a random variable.
-Let $\im X$ denote the set of possible values of $X$ and $\mathrm{pa}(X)$ denote
-the set of its parents. The full probability distribution is then equal to
-\begin{equation} \label{eq:factorisation}
-  \prod_{X \in \mathcal{V}} \Pr(X \mid \mathrm{pa}(X)).
-\end{equation}
-If all random variables are discrete (and we only consider discrete Bayesian
-networks in this paper), the probabilities contained in each factor of
-\cref{eq:factorisation} can be summarised in a table known as a
-\emph{conditional probability table} (CPT). See \cref{fig:example_bn} for an
-example Bayesian network which we will refer to throughout this section. For
-this network, $\mathcal{V} = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
-$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
-$\im T = \{ l, m, h \}$.
+Recall that a Bayesian network is a directed acyclic graph with random variables
+as vertices. Let $\mathcal{V}$ denote the set of random variables. For any
+random variable $X \in \mathcal{V}$, let $\im X$ denote its set of possible
+values and $\mathrm{pa}(X)$ the set of its parents. The full probability
+distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X \mid
+\mathrm{pa}(X))$. See \cref{fig:example_bn} for an example Bayesian network
+which we will refer to throughout this section. For this network, $\mathcal{V} =
+\{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) =
+\{ W \}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
 
@@
 
-\todo[inline]{Describe the algorithm and the CPT functions.}
+\todo[inline]{Describe the algorithm and the CPT functions. In fact, we call
+  each CPT function (i.e., a function that represents a CPT) a \emph{conditional
+    weight function} (and this is more of a semantic rather than practical
+  distinction).}
 
@@
   If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
-  \right)(\tau) = 1$, and
-  \[
-    \left( \prod_{i=1}^m \prod_{j=i+1}^m (\overline{[\lambda_{X = x_i}]} +
-      \overline{[\lambda_{X = x_j}]}) \right)(\tau) = 1,
-  \]
-  so $\mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by a
-  similar argument as before.
+  \right)(\tau) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
+    (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
+  \right)(\tau) = 1$, so $\mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1,
+  \dots, Y_n = y_n)$ by a similar argument as before.
 \end{proof}
@@
 \begin{proposition} \label{lemma:full_distribution}
-  $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ represents the full probability
-  distribution of the Bayesian network, i.e., if $\mathcal{V} = \{ X_1, \dots,
-  X_n\}$, then
+  The function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ represents the full
+  probability distribution of the Bayesian network, i.e., if $\mathcal{V} = \{
+  X_1, \dots, X_n\}$, then
   \[
@@
 
+\todo[inline]{Maybe replace `upper bound' with `worst-case'.}
+
 \begin{table}
@@
 
-\paragraph{Explaining The Performance Benefits.} Let $n = |\mathcal{V}|$ be the
+\paragraph{Explaining the performance benefits.} Let $n = |\mathcal{V}|$ be the
 number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
@@
 \max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
-Then... \cref{tbl:asymptotes}.
-
-\todo[inline]{Remember that these are upper bounds! Some of these encoding have
-  a lot of optimisations that are not captured by three parameters!}
+Then... \cref{tbl:asymptotes}. However, note that these are upper bounds and
+most encodings (including \texttt{db20}) can be smaller in certain situations
+(e.g., with binary random variables or when a CPT has repeating probabilities).
 
@@
 \item Bayesian networks and ADDMC are only particular examples. This should also
-  work with Cachet.
+  work with Cachet \cite{DBLP:conf/sat/SangBBKP04}.
+  \begin{itemize}
+  \item Potential criticism may be that this doesn't allow us to use SAT-based
+    techniques for probabilistic inference. However, they can still be used for
+    a significant part of the encoding.
+    \begin{itemize}
+    \item Zero-probability weights and one-probability weights can be
+      interpreted as logical clauses. This doesn't affect ADDMC but could be
+      useful for other solvers.
+    \end{itemize}
+  \end{itemize}
 \item Extra benefit: one does not need to come up with a way to turn some
@@
 \item Filtering out ADDs that have nothing to do with the answer helps
-  tremendously, but I'm purposefully not doing that. Perhaps a heuristic could
-  do the same thing?
-\item Encodings for everything else
-  \begin{itemize}
-  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
-  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
-    \begin{itemize}
-    \item proof-based \cite{DBLP:conf/iclp/MantadelisJ10}
-    \item rule-based \cite{DBLP:conf/ecai/Janhunen04}
-    \end{itemize}
-  \end{itemize}
-\item Bayesian networks are often solved in a compile once, query many times
-  fashion. This can be achieved using ADDMC by selecting a subset $S$ of
-  variable we may want to query over and running ADDMC while excluding $S$ from
-  variable elimination/projection/$\exists$.
-\item I could also add a memory usage cumulative plot, but it doesn't add any
-  extra info except for the fact that inference is memory-intensive.
+  tremendously, but I'm purposefully not doing that.
+\item Other things can be compiled into WMC, e.g., probabilistic programs
+  \cite{DBLP:journals/corr/abs-2005-09089}, ProbLog
+  \cite{DBLP:conf/uai/FierensBTGR11}.
 \end{itemize}

### 2020-07-31 paper/paper.tex
Improvements to notation

@@
   \begin{itemize}
-  \item WMC
+  \item WMC \cite{DBLP:conf/aaai/SangBK05}
   \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} and ADDs
@@
   of theorems to follow.
-\item Notable previous/related work
-  \begin{itemize}
-  \item Hailperin's approach to probability logic
-    \cite{DBLP:journals/ndjfl/Hailperin84}
-  \item Nilsson's (somewhat successful) probabilistic logic
-    \cite{DBLP:journals/ai/Nilsson86,DBLP:journals/ai/Nilsson93}
-  \item Measures on Boolean algebras
-    \begin{itemize}
-    \item On possibility and probability measures in finite Boolean algebras
-      \cite{DBLP:journals/soco/CastineiraCT02}
-    \item Representation of conditional probability measures
-      \cite{krauss1968representation}
-    \end{itemize}
-  \end{itemize}
 \item Our work is, in spirit, similar to... using ROBDDs for Inference in
@@
 \cite{DBLP:conf/aaai/SangBK05}, \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05},
-and \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}. Below we friendly summarise
-the observed performance differences among them. Sang et al.
+and \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}. Below we summarise the
+observed performance differences among them. Sang et al.
 \cite{DBLP:conf/aaai/SangBK05} claim that \texttt{sbk05} is a smaller encoding
@@
 efficient way to manipulate functions from a Boolean algebra to any algebraic
-structure (most commonly $\mathbb{R}$) \cite{DBLP:journals/fmsd/BaharFGHMPS97}.
-They have been used to represent value functions in Markov decision processes
-\cite{DBLP:conf/uai/HoeySHB99} and, for Bayesian network inference, to represent
-each CPT as an ADD \cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs
-and arithmetic circuits into a  single representation
-\cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous in this
-situation because of their ability to fully exploit context-specific
-independence, i.e., observable structure within a CPT that is not inherited from
-the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
+structure (most commonly the real numbers)
+\cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been used to represent value
+functions in Markov decision processes \cite{DBLP:conf/uai/HoeySHB99} and, for
+Bayesian network inference, to represent each CPT as an ADD
+\cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs and arithmetic
+circuits into a  single representation \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs
+are particularly advantageous in this situation because of their ability to
+fully exploit context-specific independence, i.e., observable structure within a
+CPT that is not inherited from the structure of the Bayesian network
+\cite{DBLP:conf/uai/BoutilierFGK96}.
 
@@
 \begin{definition}[Operations on functions]
-  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
-    0}$ be functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We define
-  the following operations:
+  Let $\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ and $\beta\colon 2^Y \to
+  \mathbb{R}_{\ge 0}$ be functions, $p \in \mathbb{R}_{\ge 0}$, and $x \in X$.
+  We define the following operations:
   \begin{description}
-  \item[Addition:] $A+B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$ is
-    such that $(A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)$ for all $\tau \in
-    2^{X \cup Y}$.
-  \item[Multiplication:] $A \cdot B\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$
-    is such that $(A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau
-    \cap Y)$ for all $\tau \in 2^{X \cup Y}$.
-  \item[Scalar multiplication:] $\alpha A\colon 2^X \to \mathbb{R}_{\ge 0}$ is
-    such that $(\alpha A)(\tau) = \alpha \cdot A(\tau)$ for all $\tau
-    \in 2^X$.
-  \item[Complement:] $\overline{A}\colon 2^X \to \mathbb{R}_{\ge 0}$ is
-    such that $\overline{A}(\tau) = 1 - A(\tau)$ for all $\tau \in 2^X$.
-  \item[Projection:] $\exists_xA\colon 2^{X \setminus \{ x \}} \to
-    \mathbb{R}_{\ge 0}$ is such that $(\exists_xA)(\tau) = A(\tau) +
-    A(\tau \cup \{ x \})$ for all $\tau \in 2^{X \setminus \{x \}}$.
+  \item[Addition:] $\alpha + \beta\colon 2^{X \cup Y} \to \mathbb{R}_{\ge 0}$ is
+    such that $(\alpha + \beta)(T) = \alpha(T \cap X) + \beta(T \cap Y)$ for all
+    $T \in 2^{X \cup Y}$.
+  \item[Multiplication:] $\alpha \cdot \beta\colon 2^{X \cup Y} \to
+    \mathbb{R}_{\ge 0}$ is such that $(\alpha \cdot \beta)(T) = \alpha(T \cap X)
+    \cdot \beta(T \cap Y)$ for all $T \in 2^{X \cup Y}$.
+  \item[Scalar multiplication:] $p\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ is
+    such that $(p\alpha)(T) = p \cdot \alpha(T)$ for all $T \in 2^X$.
+  \item[Complement:] $\overline{\alpha}\colon 2^X \to \mathbb{R}_{\ge 0}$ is
+    such that $\overline{\alpha}(T) = 1 - \alpha(T)$ for all $T \in 2^X$.
+  \item[Projection:] $\exists_x\alpha\colon 2^{X \setminus \{ x \}} \to
+    \mathbb{R}_{\ge 0}$ is such that $(\exists_x\alpha)(T) = \alpha(T) +
+    \alpha(T \cup \{ x \})$ for all $T \in 2^{X \setminus \{x \}}$.
   \end{description}
@@
 \begin{observation}
-  Let $U$ be a set, and $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0}
+  Let $U$ be a set, and $\mathcal{V} = \{ \alpha\colon 2^X \to \mathbb{R}_{\ge 0}
   \mid X \subseteq U \}$. Then $\mathcal{V}$ is a semi-vector space with three
-  additional operations: inverse, (non-scalar) multiplication, and projection.
+  additional operations: (non-scalar) multiplication, complement, and projection.
   Specifically, note that both addition and multiplication are both associative
@@
 
-Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
-$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.
+Henceforth, for any function $\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ and any
+set $T$, we will write $\alpha(T)$ to mean $\alpha(T \cap X)$.
 
@@
 
-Let $U$ be a set. A \emph{measure} is a function $M\colon 2^{2^U} \to
-\mathbb{R}_{\ge 0}$ such that $M(\bot) = 0$, and $M(a \lor b) = M(a) + M(b)$ for
-all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$. A \emph{weight function} is
-a function $W\colon 2^U \to \mathbb{R}_{\ge 0}$. A weight function is
-\emph{factored} if $W = \prod_{x \in U} W_x$ for some functions $W_x\colon
-2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$. We say that a weight function
-$W\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a measure $M_W\colon 2^{2^U}
-\to \mathbb{R}_{\ge 0}$ if
+Let $U$ be a set. A \emph{measure} is a function $\mu\colon 2^{2^U} \to
+\mathbb{R}_{\ge 0}$ such that $\mu(\bot) = 0$, and $\mu(a \lor b) = \mu(a) +
+\mu(b)$ for all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$. A \emph{weight
+  function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$. A weight
+function is \emph{factored} if $\nu = \prod_{x \in U} \nu_x$ for some functions
+$\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$. We say that a weight
+function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a measure
+$\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
 \begin{equation} \label{eq:induced_measure}
-  M_W(x) = \sum_{\{u\} \le x} W(u).
+  \mu_\nu(x) = \sum_{\{u\} \le x} \nu(u).
 \end{equation}
-Finally, a measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is \emph{factorable}
-if there exists a factored weight function $W\colon 2^U \to \mathbb{R}_{\ge 0}$
-that induces $M$.
+Finally, a measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
+\emph{factorable} if there exists a factored weight function $\nu\colon 2^U \to
+\mathbb{R}_{\ge 0}$ that induces $\mu$.
 
 \begin{lemma} \label{prop:measure}
-  The function $M_W$, as defined by \cref{eq:induced_measure}, is a measure.
+  The function $\mu_\nu$, as defined by \cref{eq:induced_measure}, is a measure.
 \end{lemma}
 \begin{proof}
-  Note that $M_W(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b \in
-  2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
+  Note that $\mu_\nu(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b
+  \in 2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
   Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
@@
   \[
-    M_W(a \lor b) = \sum_{\{u\} \le a \lor b} W(u) = \sum_{\{u\} \le a} W(u) +
-    \sum_{\{u\} \le b} = M_W(a) + M_W(b)
+    \mu_\nu(a \lor b) = \sum_{\{u\} \le a \lor b} \nu(u) = \sum_{\{u\} \le a}
+    \nu(u) + \sum_{\{u\} \le b} \nu(u) = \mu_\nu(a) + \mu_\nu(b)
   \]
@@
 
-In this formulation, the process of calculating the value of $M_W(x)$ for some
-$x \in 2^{2^U}$ with a given definition of $W$ is known as WMC.
+In this formulation, the process of calculating the value of $\mu_\nu(x)$ for
+some $x \in 2^{2^U}$ with a given definition of $\nu$ is known as WMC.
 
@@
 \end{equation}
-Alternatively, we can define $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ as
-$W_a(\{ a \}) = 0.3$, $W_a(\emptyset) = 0.7$ and $W_b\colon 2^{\{q\}} \to
-\mathbb{R}_{\ge 0}$ as $W_b(\{ b \}) = 0.2$, $W_b(\emptyset) = 0.8$. Let $M$ be
-the measure on $2^{2^U}$ induced by $W = W_a \cdot W_b$. Then, equivalently to
-\cref{eq:wmc_example}, we can write
+Alternatively, we can define $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ as
+$\nu_a(\{ a \}) = 0.3$, $\nu_a(\emptyset) = 0.7$ and $\nu_b\colon 2^{\{b\}} \to
+\mathbb{R}_{\ge 0}$ as $\nu_b(\{ b \}) = 0.2$, $\nu_b(\emptyset) = 0.8$. Let
+$\mu$ be the measure on $2^{2^U}$ induced by $\nu = \nu_a \cdot \nu_b$. Then,
+equivalently to \cref{eq:wmc_example}, we can write
 \[
-  M(a) = W(\{ a, b \}) + W(\{ a \}) = W_a(\{a\})W_b(\{b\}) +
-  W_a(\{a\})W_b(\emptyset) = 0.3.
+  \mu(a) = \nu(\{ a, b \}) + \nu(\{ a \}) = \nu_a(\{a\})\nu_b(\{b\}) +
+  \nu_a(\{a\})\nu_b(\emptyset) = 0.3.
 \]
@@
 \begin{example}
-  Let $U = \{a, b\}$ be a set of atoms and $M\colon 2^{2^U} \to \mathbb{R}_{\ge
-    0}$ a measure defined as:\footnote{The value of $M$ on any other element of
-    the Boolean algebra can be deduced using the definition.}
+  Let $U = \{a, b\}$ be a set of atoms and $\mu\colon 2^{2^U} \to
+  \mathbb{R}_{\ge 0}$ a measure defined as:\footnote{The value of $\mu$ on any
+    other element of the Boolean algebra can be deduced using the definition.}
   \begin{align*}
-    M(a \land b) &= 0.72, \\
-    M(a \land \neg b) &= 0.18, \\
-    M(\neg a \land b) &= 0.07, \\
-    M(\neg a \land \neg b) &= 0.03.
+    \mu(a \land b) &= 0.72, \\
+    \mu(a \land \neg b) &= 0.18, \\
+    \mu(\neg a \land b) &= 0.07, \\
+    \mu(\neg a \land \neg b) &= 0.03.
   \end{align*}
-  If $M$ could be represented using traditional (factored) WMC, we would have to
-  find two weight functions $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and
-  $W_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $W = W_a \cdot W_b$
-  induces $M$, i.e., $W_a$ and $W_b$ would have to satisfy this system of
-  equations:
+  If $\mu$ could be represented using traditional (factored) WMC, we would have
+  to find two weight functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$
+  and $\nu_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu = \nu_a
+  \cdot \nu_b$ induces $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to satisfy
+  this system of equations:
   \begin{align*}
-    W_a(\{a\}) \cdot W_b(\{b\}) &= 0.72 \\
-    W_a(\{a\}) \cdot W_b(\emptyset) &= 0.18 \\
-    W_a(\emptyset) \cdot W_b(\{b\}) &= 0.07 \\
-    W_a(\emptyset) \cdot W_b(\emptyset) &= 0.03,
+    \nu_a(\{a\}) \cdot \nu_b(\{b\}) &= 0.72 \\
+    \nu_a(\{a\}) \cdot \nu_b(\emptyset) &= 0.18 \\
+    \nu_a(\emptyset) \cdot \nu_b(\{b\}) &= 0.07 \\
+    \nu_a(\emptyset) \cdot \nu_b(\emptyset) &= 0.03,
   \end{align*}
@@
   Alternatively, we can let $b$ depend on $a$ and consider weight functions
-  $W_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and $W_b\colon 2^{\{a, b\}} \to
-  \mathbb{R}_{\ge 0}$ defined as $W_a(\{a\}) = 0.9$, $W_a(\emptyset) = 0.1$, and
-  $W_b(\{a, b\}) = 0.8$, $W_b(\{a\}) = 0.2$, $W_b(\{b\}) = 0.7$, $W_b(\emptyset)
-  = 0.3$. One can easily check that with these definitions $W$ indeed induces
-  $M$.
+  $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and $\nu_b\colon 2^{\{a, b\}}
+  \to \mathbb{R}_{\ge 0}$ defined as $\nu_a(\{a\}) = 0.9$, $\nu_a(\emptyset) =
+  0.1$, and $\nu_b(\{a, b\}) = 0.8$, $\nu_b(\{a\}) = 0.2$, $\nu_b(\{b\}) = 0.7$,
+  $\nu_b(\emptyset) = 0.3$. One can easily check that with these definitions
+  $\nu$ indeed induces $\mu$.
 \end{example}
 
-Note that in this case we chose to interpret $W_b$ as $\Pr(B \mid A)$
-while---with a different definition of $W_b$ that represents the joint
-probability distribution $\Pr(A, B)$---$W_b$ by itself could induce $M$. In
+Note that in this case we chose to interpret $\nu_b$ as $\Pr(b \mid a)$
+while---with a different definition of $\nu_b$ that represents the joint
+probability distribution $\Pr(a, b)$---$\nu_b$ by itself could induce $\mu$. In
 general, however, factorising the full weight function into several smaller
@@
 \begin{lemma} \label{lemma:before_theorem}
-  For any measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ and elements $a, b
+  For any measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ and elements $a, b
   \in 2^{2^U}$,
   \begin{equation} \label{eq:to_prove}
-    M(a \land b) = M(a)M(b)
+    \mu(a \land b) = \mu(a)\mu(b)
   \end{equation}
@@
   \begin{equation} \label{eq:to_prove2}
-    M(a \land b) \cdot M(\neg a \land \neg b) = M(a \land \neg b)
-    \cdot M(\neg a \land b).
+    \mu(a \land b) \cdot \mu(\neg a \land \neg b) = \mu(a \land \neg b)
+    \cdot \mu(\neg a \land b).
   \end{equation}
@@
   \begin{equation} \label{eq:temp}
-    M(a) = M(a \land b) + M(a \land \neg b).
+    \mu(a) = \mu(a \land b) + \mu(a \land \neg b).
   \end{equation}
-  Applying \cref{eq:temp} and the equivalent expression for $M(b)$ allows us
+  Applying \cref{eq:temp} and the equivalent expression for $\mu(b)$ allows us
   to rewrite \cref{eq:to_prove} as
   \[
-    M(a \land b) = [M(a \land b) + M(a \land \neg b)][M(a \land b) + M(\neg a
-    \land b)]
+    \mu(a \land b) = [\mu(a \land b) + \mu(a \land \neg b)][\mu(a \land b) +
+    \mu(\neg a \land b)]
   \]
@@
   \begin{equation} \label{eq:temp6}
-    M(a \land b)[1 - M(a \land b) - M(a \land \neg b) - M(\neg a \land b)] = M(a
-    \land \neg b)M(\neg a \land b).
+    \mu(a \land b)[1 - \mu(a \land b) - \mu(a \land \neg b) - \mu(\neg a \land b)] = \mu(a \land \neg b)\mu(\neg a \land b).
   \end{equation}
   Since $a \land b$, $a \land \neg b$, $\neg a \land b$, $\neg a \land \neg b$
-  are pairwise disjoint and their supremum is $1$,
+  are pairwise disjoint and their supremum is $\top$,
   \[
-    M(a \land b) + M(a \land \neg b) + M(\neg a \land b) + M(\neg a \land \neg
-    b) = 1,
+    \mu(a \land b) + \mu(a \land \neg b) + \mu(\neg a \land b) + \mu(\neg a
+    \land \neg b) = 1,
   \]
@@
 
+\todo[inline]{The proof is only valid for probability measures!}
+
 \begin{theorem}
-  A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is factorable if and only
+  A measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is factorable if and only
   if
   \begin{equation} \label{eq:wmccondition}
-  M(u \land v) = M(u)M(v)
+  \mu(u \land v) = \mu(u)\mu(v)
   \end{equation}
@@
 \begin{proof}
-  ($\Leftarrow$) For each $x \in U$, let $W_x\colon 2^{\{x\}} \to
-  \mathbb{R}_{\ge 0}$ be defined by $W_x(\{ x \}) = M(x)$ and $W_x(\emptyset) =
-  M(\neg x)$. Let $M_W$ be the measure induced by $W = \prod_{x \in U} W_x$. We
-  will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by
-  \cref{prop:measure} and the definition of a measure. Second, let $a =
-  \bigwedge_{u \in U} a_u$ be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg
-  u \}$ for all $u \in U$. Then
+  ($\Leftarrow$) For each $x \in U$, let $\nu_x\colon 2^{\{x\}} \to
+  \mathbb{R}_{\ge 0}$ be defined by $\nu_x(\{ x \}) = \mu(x)$ and
+  $\nu_x(\emptyset) = \mu(\neg x)$. Let $\mu_\nu$ be the measure induced by $\nu
+  = \prod_{x \in U} \nu_x$. We will show that $\mu = \mu_\nu$. First, note that
+  $\mu_\nu(\bot) = 0 = \mu(\bot)$ by \cref{prop:measure} and the definition of a
+  measure. Second, let $a = \bigwedge_{u \in U} a_u$ be an atom in $2^{2^U}$
+  such that $a_u \in \{ u, \neg u \}$ for all $u \in U$. Then
   \[
-    M_W(a) = W(\{ a_u \mid u \in U \}) = \prod_{u \in U} W_u(\{a_u\}) = \prod_{u
-      \in U} M(a_u) = M \left(\bigwedge_{u \in U} a_u \right) = M(a)
+    \mu_\nu(a) = \nu(\{ a_u \mid u \in U \}) = \prod_{u \in U} \nu_u(\{a_u\}) =
+    \prod_{u \in U} \mu(a_u) = \mu\left(\bigwedge_{u \in U} a_u \right) = \mu(a)
   \]
 
-  Finally, note that if $M_W$ and
-  $M$ agree on all atoms, then they must also agree on all other non-zero
-  elements of the Boolean algebra.
+  Finally, note that if $\mu_\nu$ and $\mu$ agree on all atoms, then they must
+  also agree on all other non-zero elements of the Boolean algebra.
 
   ($\Rightarrow$) For the other direction, we are given a factored weight
-  function $W = \prod_{x \in U} W_x$, and we want to show that its induced
-  measure $M_W$ satisfies \cref{eq:wmccondition}. Let $k_u, k_v \in U \cup \{
-  \neg w \mid w \in U \}$ be such that $k_u \in \{ u, \neg u \}$, $k_v \in \{ v,
-  \neg v \}$, and $u \ne v$. We then want to show that
+  function $\nu = \prod_{x \in U} \nu_x$, and we want to show that its induced
+  measure $\mu_\nu$ satisfies \cref{eq:wmccondition}. Let $k_u, k_v \in U \cup
+  \{\neg w \mid w \in U \}$ be such that $k_u \in \{ u, \neg u \}$, $k_v \in \{
+  v, \neg v \}$, and $u \ne v$. We then want to show that
   \begin{equation} \label{eq:to_prove3}
-    M_W(k_u \land k_v) = M_W(k_u)M_W(k_v)
+    \mu_\nu(k_u \land k_v) = \mu_\nu(k_u)\mu_\nu(k_v)
   \end{equation}
@@
   \begin{equation} \label{eq:to_prove4}
-    M_W(k_u \land k_v) \cdot M_W(\neg k_u \land \neg k_v) = M_W(k_u \land \neg k_v) \cdot M_w(\neg k_u \land k_v)
+    \mu_\nu(k_u \land k_v) \cdot \mu_\nu(\neg k_u \land \neg k_v) = \mu_\nu(k_u \land \neg k_v) \cdot \mu_\nu(\neg k_u \land k_v)
   \end{equation}
@@
   \begin{align*}
-    M_W(k_u \land k_v) &= \sum_{\{a\} \le k_u \land k_v} W(a) = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U} W_x(a) \\
-                        &= \sum_{\{a\} \le k_u \land k_v} W_u(a_u)W_v(a_v) \prod_{x \in U \setminus \{ u, v \}} W_x(a) = \sum_{\{a\} \le k_u \land k_v} W_u(k_u)W_v(k_v) \prod_{x \in U \setminus \{ u, v \}} W_x(a) \\
-    &= W_u(k_u)W_v(k_v) \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}} W_x(a) = W_u(k_u)W_v(k_v)C,
+    \mu_\nu(k_u \land k_v) &= \sum_{\{a\} \le k_u \land k_v} \nu(a) = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U} \nu_x(a) \\
+                        &= \sum_{\{a\} \le k_u \land k_v} \nu_u(a_u)\nu_v(a_v) \prod_{x \in U \setminus \{ u, v \}} \nu_x(a) = \sum_{\{a\} \le k_u \land k_v} \nu_u(k_u)\nu_v(k_v) \prod_{x \in U \setminus \{ u, v \}} \nu_x(a) \\
+    &= \nu_u(k_u)\nu_v(k_v) \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}} \nu_x(a) = \nu_u(k_u)\nu_v(k_v)c,
   \end{align*}
-  where $C = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}}
-  W_x(a)$, and is the same for $M_W(\neg k_u \land k_v)$, $M_W(k_u \land \neg
-  k_v)$, and $M_W(\neg k_u \land \neg k_v)$ as well. But then
+  where $c = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}}
+  \nu_x(a)$, and is the same for $\mu_\nu(\neg k_u \land k_v)$, $\mu_\nu(k_u
+  \land \neg k_v)$, and $\mu_\nu(\neg k_u \land \neg k_v)$ as well. But then
   \cref{eq:to_prove4} becomes
   \[
-    W_u(k_u)W_v(k_v)W_u(\neg k_u)W_v(\neg k_v)C^2 = W_u(k_u)W_v(\neg
-    k_v)W_u(\neg k_u)W_v(k_v)C^2
+    \nu_u(k_u)\nu_v(k_v)\nu_u(\neg k_u)\nu_v(\neg k_v)c^2 = \nu_u(k_u)\nu_v(\neg
+    k_v)\nu_u(\neg k_u)\nu_v(k_v)c^2
   \]
@@
   \[
-    E(X) = \begin{cases}
+    \mathcal{E}(X) = \begin{cases}
       \{ \lambda_{X=1} \} & \text{if } |\im X| = 2 \\
@@
   \]
-  denote the set of indicator variables for $X$ and $E^*(X) = E(X) \cup
-  \bigcup_{Y \in \mathrm{pa}(X)} E(Y)$ denote the set of indicator variables for
-  $X$ and its parents in the Bayesian network. Finally, let $U = \bigcup_{X \in
-    \mathcal{V}} E(X)$ denote the set of all indicator variables for all random
-  variables in the Bayesian network.
+  denote the set of indicator variables for $X$ and $\mathcal{E}^*(X) =
+  \mathcal{E}(X) \cup \bigcup_{Y \in \mathrm{pa}(X)} \mathcal{E}(Y)$ denote the
+  set of indicator variables for $X$ and its parents in the Bayesian network.
+  Finally, let $U = \bigcup_{X \in \mathcal{V}} \mathcal{E}(X)$ denote the set
+  of all indicator variables for all random variables in the Bayesian network.
 \end{definition}
@@
 \begin{align*}
-  E(W) &= \{ \lambda_{W=1} \}, \\
-  E(F) &= \{ \lambda_{F=1} \}, \\
-  E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
-  E^*(W) &= \{ \lambda_{W=1} \}, \\
-  E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
-  E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
+  \mathcal{E}(W) &= \{ \lambda_{W=1} \}, \\
+  \mathcal{E}(F) &= \{ \lambda_{F=1} \}, \\
+  \mathcal{E}(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
+  \mathcal{E}^*(W) &= \{ \lambda_{W=1} \}, \\
+  \mathcal{E}^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
+  \mathcal{E}^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
 \end{align*}
@@
 
-\todo[inline]{Describe the algorithm and the CPT functions. In fact, we call
-  each CPT function (i.e., a function that represents a CPT) a \emph{conditional
-    weight function} (and this is more of a semantic rather than practical
-  distinction).}
+\Cref{alg:encoding} shows how a Bayesian network with vertices $\mathcal{V}$
+can be represented as a weight function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$.
+The algorithm begins with the unit function and multiplies it by
+$\mathrm{CPT}_X\colon 2^{\mathcal{E}^*(X)} \to \mathbb{R}_{\ge 0}$ for each
+random variable $X \in \mathcal{V}$. We call each such function a
+\emph{conditional weight function} as it represents a conditional probability
+distribution. However, the distinction is primarily a semantic one: a function
+$2^{\{a, b\}} \to \mathbb{R}_{\ge 0}$ can represent $\Pr(a \mid b)$, $\Pr(b \mid
+a)$, or something else entirely.
 
-For the Bayesian network in \cref{fig:example_bn}, we have:
+For a binary random variable $X$, $\mathrm{CPT}_X$ is simply a sum of smaller
+functions, one for each row of the CPT. If $X$ has more than two values, we also
+multiply $\mathrm{CPT}_X$ by some `clause' functions that restrict the value of
+$\phi(T)$ to zero whenever $|\mathcal{E}(X) \cap T| \ne 1$. For the Bayesian
+network in \cref{fig:example_bn}, we get:
 \begin{align*}
@@
 
+\todo[inline]{Introduce what this subsection is all about (and each result
+  separately).}
+
 \begin{lemma} \label{lemma:cpt}
   Let $X \in \mathcal{V}$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
-  \dots, Y_n \}$. Then $\mathrm{CPT}_X\colon 2^{E^*(X)} \to \mathbb{R}_{\ge 0}$
-  is such that for any $x \in \im X$ and $(y_1, \dots, y_n) \in \prod_{i=1}^n
-  \im Y_i$,
+  \dots, Y_n \}$. Then $\mathrm{CPT}_X\colon 2^{\mathcal{E}^*(X)} \to
+  \mathbb{R}_{\ge 0}$ is such that for any $x \in \im X$ and $(y_1, \dots, y_n)
+  \in \prod_{i=1}^n \im Y_i$,
   \[
@@
 \begin{proof}
-  Let $\tau = \{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1, \dots, n
+  Let $T = \{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1, \dots, n
   \}$. If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
   Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
-  \dots, Y_n$. Exactly one of these terms is nonzero when applied to $\tau$, and
+  \dots, Y_n$. Exactly one of these terms is nonzero when applied to $T$, and
   it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
@@
   If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
-  \right)(\tau) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
+  \right)(T) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
     (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
-  \right)(\tau) = 1$, so $\mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1,
+  \right)(T) = 1$, so $\mathrm{CPT}_X(T) = \Pr(X = x \mid Y_1 = y_1,
   \dots, Y_n = y_n)$ by a similar argument as before.
@@
   \[
-    \phi(\tau) =
+    \phi(T) =
     \begin{cases}
-      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } \tau = \{ \lambda_{X_i=x_i}
+      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } T = \{ \lambda_{X_i=x_i}
       \mid i = 1, \dots, n \} \text{ for some } (x_1, \dots, x_n) \in
@@
   \]
-  for all $\tau \in 2^U$.
+  for all $T \in 2^U$.
 \end{proposition}
 \begin{proof}
-  If $\tau = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
+  If $T = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
     \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
   \[
-    \phi(\tau) = \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\;
+    \phi(T) = \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\;
       \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X
@@
   by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
-  must be some non-binary random variable $X \in \mathcal{V}$ such that $|E(X)
-  \cap \tau| \ne 1$. If $E(X) \cap \tau = \emptyset$, then $\left( \sum_{i=1}^m
-    [\lambda_{X = x_i}] \right)(\tau) = 0$, and so $\mathrm{CPT}_X(\tau) = 0$,
-  and $\phi(\tau) = 0$. If $|E(X) \cap \tau| > 1$, then we must have two
-  different values $x_1, x_2 \in \im X$ such that $\{\lambda_{X=x_1},
-  \lambda_{X=x_2} \} \subseteq \tau$ which means that
-  $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(\tau) = 0$, and
-  so, again, $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$.
+  must be some non-binary random variable $X \in \mathcal{V}$ such that
+  $|\mathcal{E}(X) \cap T| \ne 1$. If $\mathcal{E}(X) \cap T = \emptyset$, then
+  $\left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(T) = 0$, and so
+  $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$. If $|\mathcal{E}(X) \cap T| > 1$,
+  then we must have two different values $x_1, x_2 \in \im X$ such that
+  $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq T$ which means that
+  $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(T) = 0$, and
+  so, again, $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$.
 \end{proof}
@@
   \begin{align*}
-    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{\tau \in 2^U} (\phi \cdot [\lambda_{X=x}])(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \phi(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(\tau) \\
+    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
     &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
@@
   \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
-  \item if $\lambda_{X=x} \not\in \tau \in 2^U$, then $(\phi \cdot
-    [\lambda_{X=x}])(\tau) = \phi(\tau) \cdot [\lambda_{X=x}](\tau \cap \{
-    \lambda_{X=x} \}) = \phi(\tau) \cdot 0 = 0$;
+  \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
+    [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
+    \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
   \item \cref{lemma:full_distribution};
@@
 to encode WMC problems, which extends the DIMACS format for conjunctive normal
-form (CNF) formulas with weight clauses. Subsequently, we extend it in two
-ways:
-\begin{itemize}
-\item a single weight clause now supports an arbitrary number of literals,
-\item and each weight clause has two probabilities instead of one (i.e., we no
-  longer assume that $\Pr(v) + \Pr(\neg v) = 1$ for all variables $v \in U$).
-\end{itemize}
-The way we use this encoding, it is always the case that either both
-probabilities sum to one, or the second probability (i.e., the probability for
-the complement of the variable) is equal to one.
+form (CNF) formulas with weight clauses. Subsequently, we extend it in two ways:
+a single weight clause now supports an arbitrary number of literals, and each
+weight clause has two probabilities instead of one (i.e., we no longer assume
+that $\Pr(v) + \Pr(\neg v) = 1$ for all $v \in U$). In our use of the encoding,
+it is always the case that either both probabilities sum to one, or the second
+probability (i.e., the probability for the complement of the variable) is equal
+to one.
 
@@
 X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges between
-all distinct pairs of variables in $E^*(X)$.
+all distinct pairs of variables in $\mathcal{E}^*(X)$.
 
@@
 
+\subsection{Explaining the Performance Benefits}
+
 \todo[inline]{Maybe replace `upper bound' with `worst-case'.}
@@
 
-\paragraph{Explaining the performance benefits.} Let $n = |\mathcal{V}|$ be the
-number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
-|\mathrm{pa}(X)|$ the maximum in-degree (i.e., number of parents), and $v =
-\max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
-Then... \cref{tbl:asymptotes}. However, note that these are upper bounds and
-most encodings (including \texttt{db20}) can be smaller in certain situations
-(e.g., with binary random variables or when a CPT has repeating probabilities).
+Let $n = |\mathcal{V}|$ be the number of vertices in the Bayesian network, $d =
+\max_{X \in \mathcal{V}} |\mathrm{pa}(X)|$ the maximum in-degree (i.e., number
+of parents), and $v = \max_{X \in \mathcal{V}} |\im X|$ the maximum number of
+values per variable. Then... \cref{tbl:asymptotes}. However, note that these are
+upper bounds and most encodings (including \texttt{db20}) can be smaller in
+certain situations (e.g., with binary random variables or when a CPT has
+repeating probabilities).
 
-\todo[inline]{Explain why clauses and ADDs are alike.}
+We equate clauses and ADDs (more specifically, factors of the function $\phi$
+from \cref{alg:encoding}) here because ADDMC interprets each clause of any WMC
+encoding as a multiplicative factor of the ADD that represents the entire WMC
+instance \cite{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings, each
+weight is also a factor, but that has no effect on the asymptotic bounds in the
+table.
 

### 2020-08-01 paper/paper.tex
Make some things clearer

@@
 \begin{itemize}
-\item The Main Narrative
+\item The main narrative
   \begin{enumerate}
-  \item When weights are defined on literals, the measure on the free BA is
-    fully independent.
-  \item This means that the BA itself must be larger (i.e., have additional
-    `meaningless' literals) to turn any probability distribution into an
-    independent one.
+  \item Putting weights on literals is restrictive.
+  \item To overcome this, it is common practice to add more literals.
+  \item This is indeed always possible but much slower.
   \item We show how we can define conditional weights on literals, allowing us
-    to encode any probability distribution into a Boolean algebra that's not
-    necessarily independent and thus can be smaller.
+    to encode any measure.
   \item We demonstrate a specific example of this by presenting a new way to
@@
   \caption{A comparison of Boolean-algebraic (BA) and set-theoretic (ST)
-    concepts for $2^X$ for some set $X$}
+    concepts for $2^U$ for any set $U$}
   \label{tbl:notation}
@@
     bottom & $\bot$ & $\emptyset$ & empty set \\
-    top & $\top$ & $X$ & \\
+    top & $\top$ & $U$ & \\
     meet, and & $\land$ & $\cap$ & intersection \\
@@
 
-\todo[inline]{Completely rewrite this section. It needs to be very clear and
-  introduce all relevant terminology.}
-\todo[inline]{Would it be more accurate to replace the word `model' with
-  `interpretation' in most situations?}
-
-For any set $X$, we can interpret $2^X$ as either a power set or a Boolean
-algebra---see \cref{tbl:notation} for a summary of the differences in
-terminology and notation.
-
-Let $\mathcal{L}$ be a propositional logic with atoms $U = \{ a, b \}$. See
-\cref{tbl:notation_example} for an overview of the models and formulas in
-$\mathcal{L}$ as well as their set-theoretic and Boolean-algebraic
-representations. Note the differences in the meaning of the word `atom' between
-the logical and the Boolean-theoretic interpretations. In the Boolean algebra
-$2^{2^U}$, an atom is a set with a single element which corresponds to a model
-of $\mathcal{L}$ (also known as an element of $2^U$); whereas an atom of
-$\mathcal{L}$ is an atomic formula, i.e., an element of $U$. We will primarily
-use the term `atom' to mean the former.
-
-In the rest of the paper, for any set $U$, we will use set-theoretic notation
-for $2^U$ and Boolean-algebraic notation for $2^{2^U}$, except for (Boolean)
-atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some model $x \in 2^U$.
+Let $\mathcal{L}$ be a propositional logic with atoms $a$ and $b$, and let $U =
+\{ a, b \}$. Then $2^U$, the power set of $U$, is the set of all models of
+$\mathcal{L}$, and $2^{2^U}$ is the set of all formulas. These sets can also be
+represented as Boolean algebras---see \cref{tbl:notation} for an overview of
+notational differences and \cref{tbl:notation_example} for examples of how
+various elements can be represented in both notations. Most importantly, note
+that the word \emph{atom} has completely different meanings in logic and in
+Boolean algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an
+element of $U$, whereas an atom in a Boolean algebra is (in set-theoretic terms)
+a singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
+$\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
+logic, we will use the algebraic definition of an atom while referring to
+logical atoms as \emph{variables}. In the rest of the paper, for any set $U$, we
+will use set-theoretic notation for $2^U$ and Boolean-algebraic notation for
+$2^{2^U}$, except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$
+for some model $x \in 2^U$.
 
@@
 \cite{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
-manipulate functions from Boolean algebras to non-negative reals. All of these
-operations have efficient implementations in the CUDD \cite{somenzi1998cudd}
-package for manipulating ADDs (among other things) that is used by ADDMC
-{\cite{DBLP:conf/aaai/DudekPV20}.
+manipulate functions from Boolean algebras to non-negative real numbers. All of
+these operations have efficient implementations in the CUDD
+\cite{somenzi1998cudd} package for manipulating ADDs (among other things) that
+is used by ADDMC {\cite{DBLP:conf/aaai/DudekPV20}.
 
@@
 
-\subsection{Limitations of Factorable Measures}
+\subsection{Not All Measures Are Factorable}
 
@@
 
-\begin{lemma} \label{lemma:before_theorem}
-  For any measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ and elements $a, b
-  \in 2^{2^U}$,
-  \begin{equation} \label{eq:to_prove}
-    \mu(a \land b) = \mu(a)\mu(b)
-  \end{equation}
-  if and only if
-  \begin{equation} \label{eq:to_prove2}
-    \mu(a \land b) \cdot \mu(\neg a \land \neg b) = \mu(a \land \neg b)
-    \cdot \mu(\neg a \land b).
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  First, note that $a = (a \land b) \lor (a \land \neg b)$ and $(a \land b)
-  \land (a \land \neg b) = 0$, so, by properties of a measure,
-  \begin{equation} \label{eq:temp}
-    \mu(a) = \mu(a \land b) + \mu(a \land \neg b).
-  \end{equation}
-  Applying \cref{eq:temp} and the equivalent expression for $\mu(b)$ allows us
-  to rewrite \cref{eq:to_prove} as
-  \[
-    \mu(a \land b) = [\mu(a \land b) + \mu(a \land \neg b)][\mu(a \land b) +
-    \mu(\neg a \land b)]
-  \]
-  which is equivalent to
-  \begin{equation} \label{eq:temp6}
-    \mu(a \land b)[1 - \mu(a \land b) - \mu(a \land \neg b) - \mu(\neg a \land b)] = \mu(a \land \neg b)\mu(\neg a \land b).
-  \end{equation}
-  Since $a \land b$, $a \land \neg b$, $\neg a \land b$, $\neg a \land \neg b$
-  are pairwise disjoint and their supremum is $\top$,
-  \[
-    \mu(a \land b) + \mu(a \land \neg b) + \mu(\neg a \land b) + \mu(\neg a
-    \land \neg b) = 1,
-  \]
-  and this allows us to rewrite \cref{eq:temp6} into \cref{eq:to_prove2}. As all
-  transformations are invertible, the two expressions are equivalent.
-\end{proof}
-
-\todo[inline]{The proof is only valid for probability measures!}
-
-\begin{theorem}
-  A measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is factorable if and only
-  if
-  \begin{equation} \label{eq:wmccondition}
-  \mu(u \land v) = \mu(u)\mu(v)
-  \end{equation}
-  for all distinct $u, v \in U \cup \{ \neg w \mid w \in U \}$ such that $u \ne
-  \neg v$.
-\end{theorem}
-\begin{proof}
-  ($\Leftarrow$) For each $x \in U$, let $\nu_x\colon 2^{\{x\}} \to
-  \mathbb{R}_{\ge 0}$ be defined by $\nu_x(\{ x \}) = \mu(x)$ and
-  $\nu_x(\emptyset) = \mu(\neg x)$. Let $\mu_\nu$ be the measure induced by $\nu
-  = \prod_{x \in U} \nu_x$. We will show that $\mu = \mu_\nu$. First, note that
-  $\mu_\nu(\bot) = 0 = \mu(\bot)$ by \cref{prop:measure} and the definition of a
-  measure. Second, let $a = \bigwedge_{u \in U} a_u$ be an atom in $2^{2^U}$
-  such that $a_u \in \{ u, \neg u \}$ for all $u \in U$. Then
-  \[
-    \mu_\nu(a) = \nu(\{ a_u \mid u \in U \}) = \prod_{u \in U} \nu_u(\{a_u\}) =
-    \prod_{u \in U} \mu(a_u) = \mu\left(\bigwedge_{u \in U} a_u \right) = \mu(a)
-  \]
-
-  Finally, note that if $\mu_\nu$ and $\mu$ agree on all atoms, then they must
-  also agree on all other non-zero elements of the Boolean algebra.
-
-  ($\Rightarrow$) For the other direction, we are given a factored weight
-  function $\nu = \prod_{x \in U} \nu_x$, and we want to show that its induced
-  measure $\mu_\nu$ satisfies \cref{eq:wmccondition}. Let $k_u, k_v \in U \cup
-  \{\neg w \mid w \in U \}$ be such that $k_u \in \{ u, \neg u \}$, $k_v \in \{
-  v, \neg v \}$, and $u \ne v$. We then want to show that
-  \begin{equation} \label{eq:to_prove3}
-    \mu_\nu(k_u \land k_v) = \mu_\nu(k_u)\mu_\nu(k_v)
-  \end{equation}
-  which is equivalent to
-  \begin{equation} \label{eq:to_prove4}
-    \mu_\nu(k_u \land k_v) \cdot \mu_\nu(\neg k_u \land \neg k_v) = \mu_\nu(k_u \land \neg k_v) \cdot \mu_\nu(\neg k_u \land k_v)
-  \end{equation}
-  by \cref{lemma:before_theorem}. Then
-  \begin{align*}
-    \mu_\nu(k_u \land k_v) &= \sum_{\{a\} \le k_u \land k_v} \nu(a) = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U} \nu_x(a) \\
-                        &= \sum_{\{a\} \le k_u \land k_v} \nu_u(a_u)\nu_v(a_v) \prod_{x \in U \setminus \{ u, v \}} \nu_x(a) = \sum_{\{a\} \le k_u \land k_v} \nu_u(k_u)\nu_v(k_v) \prod_{x \in U \setminus \{ u, v \}} \nu_x(a) \\
-    &= \nu_u(k_u)\nu_v(k_v) \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}} \nu_x(a) = \nu_u(k_u)\nu_v(k_v)c,
-  \end{align*}
-  where $c = \sum_{\{a\} \le k_u \land k_v} \prod_{x \in U \setminus \{ u, v \}}
-  \nu_x(a)$, and is the same for $\mu_\nu(\neg k_u \land k_v)$, $\mu_\nu(k_u
-  \land \neg k_v)$, and $\mu_\nu(\neg k_u \land \neg k_v)$ as well. But then
-  \cref{eq:to_prove4} becomes
-  \[
-    \nu_u(k_u)\nu_v(k_v)\nu_u(\neg k_u)\nu_v(\neg k_v)c^2 = \nu_u(k_u)\nu_v(\neg
-    k_v)\nu_u(\neg k_u)\nu_v(k_v)c^2
-  \]
-  which is trivially true.
-\end{proof}
+\todo[inline]{Add the proof that one can always go from any measure to a
+  factorable measure by adding more literals and say: Not all measures are
+  factorable but it is common practice to add more literals to make the measure
+  factorable. We show that it's always possible and yet it can be faster not to
+  do it.}
 
@@
 \end{proof}
+\todo[inline]{Need to make the proof nicer.}
 
@@
 
-\todo[inline]{Describe how this is an intermediate step before we get the $\phi$
-from the algorithm. Each CPT is treated as a clause.}
-
-The Bayesian network in \cref{fig:example_bn} can be represented in a textual
-format as
+\Cref{alg:encoding} encodes a Bayesian network into a function on a Boolean
+algebra, but how does it relate to the standard interpretation of a WMC encoding
+as a formula in conjunctive normal form (CNF) together with a collection of
+weights? The factors of $\phi$ that restrict the values of indicator variables
+for non-binary random variables are already expressed as a product of sums of
+0/1-valued functions, i.e., a kind of CNF. Disregarding these functions, each
+conditional weight function $\mathrm{CPT}_X$ is represented by a sum with a term
+for every subset of $\mathcal{E}^*(X)$. To encode these terms, we introduce
+\emph{extended weight clauses} to the WMC format used by Cachet
+\cite{DBLP:conf/sat/SangBBKP04}. For instance, here is a representation of the
+Bayesian network from \cref{fig:example_bn}:
 \[
-  \begin{array}{l r r l l}
+  \begin{array}{lrrll}
     \lambda\sb{T=l} &\lambda\sb{T=m} &\lambda\sb{T=h} & &0 \\
@@
     w &\lambda\sb{T=h} &\lambda\sb{W=1} &0.4 &1 \\
-    w &\lambda\sb{T=l} &\lambda\sb{W=0} &0.6 &1 \\
-    w &\lambda\sb{T=m} &\lambda\sb{W=0} &0.3 &1 \\
-    w &\lambda\sb{T=h} &\lambda\sb{W=0} &0.1 &1
+    w &\lambda\sb{T=l} &-\lambda\sb{W=1} &0.6 &1 \\
+    w &\lambda\sb{T=m} &-\lambda\sb{W=1} &0.3 &1 \\
+    w &\lambda\sb{T=h} &-\lambda\sb{W=1} &0.1 &1
   \end{array}
 \]
-with each $\lambda$ replaced with a unique positive integer. This format is
-based on the format used by the Cachet solver \cite{DBLP:conf/sat/SangBBKP04}
-to encode WMC problems, which extends the DIMACS format for conjunctive normal
-form (CNF) formulas with weight clauses. Subsequently, we extend it in two ways:
-a single weight clause now supports an arbitrary number of literals, and each
-weight clause has two probabilities instead of one (i.e., we no longer assume
-that $\Pr(v) + \Pr(\neg v) = 1$ for all $v \in U$). In our use of the encoding,
-it is always the case that either both probabilities sum to one, or the second
-probability (i.e., the probability for the complement of the variable) is equal
-to one.
+where each indicator variable is eventually replaced with a unique positive
+integer. Each line prefixed with a $w$ can be split into four parts: the `main'
+variable (always not negated), conditions (possibly none), and two weights. For
+example, the line
+\[
+  \begin{array}{lrrll}
+    w &\lambda\sb{T=m} &-\lambda\sb{W=1} &0.3 &1
+  \end{array}
+\]
+encodes the function $0.3[\lambda_{T=m}] \cdot \overline{[\lambda_{W=1}]} +
+1\overline{[\lambda_{T=m}]} \cdot \overline{[\lambda_{W=1}]}$ and can be
+interpreted as defining two conditional weights: $\nu(T = m \mid W = 0) = 0.3$,
+and $\nu(T \ne m \mid W = 0) = 1$, the former of which corresponds to a row in
+the CPT of $T$ while the latter is artificially added as part of the encoding.
+In our encoding of Bayesian networks, it is always the case that, in each weight
+clause, either both weights sum to one, or the second weight is equal to one.
+Finally, note that (without any additional restrictions), the measure induced by
+these weight functions is not probabilistic (i.e., $\mu(\top)$ may not be equal
+to one).
 
@@
 $\phi$. For any pair of distinct variables $u, v \in U$, we draw an edge between
-them in the Gaifman graph if there is a function $A\colon 2^X \to
+them in the Gaifman graph if there is a function $\alpha\colon 2^X \to
 \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v \in
@@
 
-\todo[inline]{This needs rewriting.}
-ADDMC multiplies the final answer by $w(u)+w(-u)$ for every $u \in U$ that was
-`simplified out' of the ADD for $\phi$ and so is not featured in the $\exists_U$
-projection. In our format, for every such $u \in U$, we multiply the answer by
-two. Each such $u \in U$ must satisfy two properties:
-\begin{itemize}
-\item all the probabilities/weights associated with $u$ are equal to $0.5$
-  (otherwise the corresponding CPT would depend on $u$),
-\item and all other CPTs are independent of $u$ (or they may have a trivial
-  dependence, where the probability stays the same if $u$ is replaced with its
-  complement).
-\end{itemize}
+Even though the function $\phi$ produced by \cref{alg:encoding} is constructed
+to have $2^U$ as its domain, sometimes the domain is effectively reduced to
+$2^V$ for some $V \subset U$ by the ADD manipulation algorithms that optimise
+the ADD representation of a function. For a simple example, consider $\alpha:
+2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as $\alpha(\{a\}) = \alpha(\emptyset)
+= 0.5$. Then $\alpha$ can be reduced to $\alpha'\colon 2^{\emptyset} \to
+\mathbb{R}_{\ge 0}$ defined as $\alpha'(\emptyset) = 0.5$. To compensate for
+these reductions, for the original WMC format with a weight function $w\colon U
+\cup \{ \neg u \mid u \in U \} \to \mathbb{R}_{\ge 0}$, ADDMC would multiply its
+computed answer by $\prod_{u \in U \setminus V} w(u) + w(\neg u)$. With the new
+WMC format, we instead multiply the answer by $2^{|U \setminus V|}$. Each
+`excluded' variable $u \in U \setminus V$ satisfies two properties:
+all weights associated with $u$ are equal to $0.5$ (otherwise the corresponding
+CPT would depend on $u$, and $u$ would not be excluded), and all other CPTs are
+independent of $u$ (or they may have a trivial dependence, where the probability
+stays the same if $u$ is replaced with its complement).
 Thus, the CPT that corresponds to $u$ still multiplies every model by $0.5$, but
 the number of models being considered by the ADDMC is halved. To correct for
-this, we need to perform this multiplication.
+this, we multiply the final answer by two for every $u \in U \setminus V$.
 
@@
   $\mathtt{db20}$.
-\item Everything \texttt{d02} can do in \SI{1000}{\second}, \texttt{db20} can do
-  in \SI{10}{\second} (find the exact number).
+\item An observation from the cumulative plot: \texttt{db20} solves the same
+  number of instances in \SI{6.374}{\second} as \texttt{d02} does in
+  \SI{1000}{\second}.
 \end{itemize}
-
-\subsection{Explaining the Performance Benefits}
-
-\todo[inline]{Maybe replace `upper bound' with `worst-case'.}
 
@@
 
-Let $n = |\mathcal{V}|$ be the number of vertices in the Bayesian network, $d =
-\max_{X \in \mathcal{V}} |\mathrm{pa}(X)|$ the maximum in-degree (i.e., number
-of parents), and $v = \max_{X \in \mathcal{V}} |\im X|$ the maximum number of
-values per variable. Then... \cref{tbl:asymptotes}. However, note that these are
-upper bounds and most encodings (including \texttt{db20}) can be smaller in
-certain situations (e.g., with binary random variables or when a CPT has
-repeating probabilities).
+\todo[inline]{It could be confusing to use the word `variable' here. I'm using
+  it as a synonym to `logical atom'.}
 
-We equate clauses and ADDs (more specifically, factors of the function $\phi$
-from \cref{alg:encoding}) here because ADDMC interprets each clause of any WMC
+\paragraph{Explaining the performance benefits.} Let $n = |\mathcal{V}|$ be the
+number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
+|\mathrm{pa}(X)|$ the maximum in-degree (i.e., number of parents), and $v =
+\max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
+\Cref{tbl:asymptotes} shows how \texttt{db20} has both fewer variables and fewer
+ADDs than any other encoding. However, note that these are upper bounds and most
+encodings (including \texttt{db20}) can be smaller in certain situations (e.g.,
+with binary random variables or when a CPT has repeating probabilities). We
+equate clauses and ADDs (more specifically, factors of the function $\phi$ from
+\cref{alg:encoding}) here because ADDMC interprets each clause of any WMC
 encoding as a multiplicative factor of the ADD that represents the entire WMC
@@
 
-\section{Conclusion and Future Work}
+% While some ADDs may be larger as a result, experimental evidence still shows
+% significant performance benefits.
+
+\section{Conclusions and Future Work}
 

### 2020-08-01 paper/paper.tex
Rename

@@
     \mathbb{R}_{\ge 0}$ is such that $(\exists_x\alpha)(T) = \alpha(T) +
-    \alpha(T \cup \{ x \})$ for all $T \in 2^{X \setminus \{x \}}$.
+    \alpha(T \cup \{ x \})$ for all $T \in 2^{X \setminus \{x \}}$. For any $Z =
+    \{ z_1, \dots, z_n \} \subseteq X$, we write $\exists_Z$ to mean
+    $\exists_{z_1}\dots\exists_{z_n}$.
   \end{description}
@@
 
-\begin{definition}[Special functions]
-  We define several special functions:
-  \begin{itemize}
-  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\emptyset) = 1$;
-  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\emptyset) = 0$;
-  \item and $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$, $[a](\emptyset) = 0$,
-    $[a](\{a\}) = 1$ for any $a$.
-  \end{itemize}
-\end{definition}
-
-Henceforth, for any function $\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ and any
-set $T$, we will write $\alpha(T)$ to mean $\alpha(T \cap X)$.
+We end the discussion on function spaces by defining several special functions:
+unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$ defined as $1(\emptyset) = 1$,
+zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$ defined as $0(\emptyset) = 0$,
+and function $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as
+$[a](\emptyset) = 0$, $[a](\{a\}) = 1$ for any $a$. Henceforth, for any function
+$\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set $T$, we will write
+$\alpha(T)$ to mean $\alpha(T \cap X)$.
 
@@
 \subsection{Not All Measures Are Factorable}
+
+\todo[inline]{Introduce the subsection and give it some context.}
 
@@
 variables to maintain literal independence. In line with the names of previous
-encodings, we shall call this encoding \texttt{db20}.
-
-Recall that a Bayesian network is a directed acyclic graph with random variables
-as vertices. Let $\mathcal{V}$ denote the set of random variables. For any
-random variable $X \in \mathcal{V}$, let $\im X$ denote its set of possible
-values and $\mathrm{pa}(X)$ the set of its parents. The full probability
-distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X \mid
-\mathrm{pa}(X))$. See \cref{fig:example_bn} for an example Bayesian network
-which we will refer to throughout this section. For this network, $\mathcal{V} =
-\{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) =
-\{ W \}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
+encodings, we shall call this encoding \texttt{db21}. Recall that a Bayesian
+network is a directed acyclic graph with random variables as vertices. Let
+$\mathcal{V}$ denote the set of random variables. For any random variable $X \in
+\mathcal{V}$, let $\im X$ denote its set of possible values and $\mathrm{pa}(X)$
+the set of its parents. The full probability distribution is then equal to
+$\prod_{X \in \mathcal{V}} \Pr(X \mid \mathrm{pa}(X))$. See
+\cref{fig:example_bn} for an example Bayesian network which we will refer to
+throughout this section. For this network, $\mathcal{V} = \{ W, F, T \}$,
+$\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im
+W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
 
@@
 
-\todo[inline]{Introduce what this subsection is all about (and each result
-  separately).}
+\Cref{alg:encoding} produces a function with a Boolean algebra as its domain.
+This function can be represented by an ADD. The core of ADDMC works by taking an
+ADD $\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product of smaller
+ADDs) and returning $(\exists_U\psi)(\emptyset)$
+\cite{DBLP:conf/aaai/DudekPV20}. In this section, we prove that the function
+$\phi$ produced by \cref{alg:encoding} can be used by ADDMC to correctly compute
+any marginal probability of the Bayesian network that was encoded as
+$\phi$.\footnote{It can just as well compute any probability expressed using the
+random variables in $\mathcal{V}$, but we focus mostly on marginal probabilities
+in our experiments.} First, \cref{lemma:cpt} shows that any conditional weight function
+produces the right answer when given an appropriate encoding of
+variable-value assignments for a conditional probability in the Bayesian
+network. Then, \cref{lemma:full_distribution} shows that $\phi$ represents the
+full probability distribution of the Bayesian network, i.e., it gives the right
+probabilities for the right inputs and zero otherwise. We end with
+\cref{thm:correctness} that shows how $\phi$ can be combined with an encoding of
+a single variable-value assignment so that ADDMC would compute its marginal
+probability.
 
@@
 \begin{proposition} \label{lemma:full_distribution}
-  The function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ represents the full
-  probability distribution of the Bayesian network, i.e., if $\mathcal{V} = \{
-  X_1, \dots, X_n\}$, then
+  Let $\mathcal{V} = \{X_1, \dots, X_n\}$. Then
   \[
@@
 
-\begin{theorem}
-  Let $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ be the function generated by
-  \cref{alg:encoding}. Then $(\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset)
-  = \Pr(X = x)$.
+\begin{theorem} \label{thm:correctness}
+  For any $X \in \mathcal{V}$ and $x \in \im X$, $(\exists_U(\phi \cdot
+  [\lambda_{X=x}]))(\emptyset) = \Pr(X = x)$.
 \end{theorem}
@@
       \texttt{d02} & 41 & 99 & 726 \\
-      \texttt{db20} & 228 & 871 & 901 \\
+      \texttt{db21} & 228 & 871 & 901 \\
       \texttt{sbk05} & 6 & 36 & 687 \\
@@
   \input{scatter.tex}%
-  \caption{ADDMC inference time using \texttt{db20} compared to \texttt{d02}
+  \caption{ADDMC inference time using \texttt{db21} compared to \texttt{d02}
     (left) and \texttt{sbk05} (right) on an instance-by-instance basis across
@@
 \end{figure}
+
+\todo[inline]{Write an introductory paragraph.}
 
@@
   query.
-\item However, \texttt{db20} struggles with instances from Mastermind and
+\item However, \texttt{db21} struggles with instances from Mastermind and
   Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
@@
   simplifications that are exploited by $\mathtt{d02}$ but not
-  $\mathtt{db20}$.
-\item An observation from the cumulative plot: \texttt{db20} solves the same
+  $\mathtt{db21}$.
+\item An observation from the cumulative plot: \texttt{db21} solves the same
   number of instances in \SI{6.374}{\second} as \texttt{d02} does in
@@
     \texttt{d02} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(ndv^{d+1})$ \\
-    \texttt{db20} & $\mathcal{O}(nv)$ & $\mathcal{O}(nv^2)$ \\
+    \texttt{db21} & $\mathcal{O}(nv)$ & $\mathcal{O}(nv^2)$ \\
     \bottomrule
@@
 \end{table}
-
-\todo[inline]{It could be confusing to use the word `variable' here. I'm using
-  it as a synonym to `logical atom'.}
 
@@
 \max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
-\Cref{tbl:asymptotes} shows how \texttt{db20} has both fewer variables and fewer
+\Cref{tbl:asymptotes} shows how \texttt{db21} has both fewer variables and fewer
 ADDs than any other encoding. However, note that these are upper bounds and most
-encodings (including \texttt{db20}) can be smaller in certain situations (e.g.,
+encodings (including \texttt{db21}) can be smaller in certain situations (e.g.,
 with binary random variables or when a CPT has repeating probabilities). We

### 2020-08-01 encode.py

@@ -200,10 +200,10 @@ if __name__ == '__main__':
     parser = argparse.ArgumentParser(
         description='Encode Bayesian networks into instances of weighted model counting (WMC)')
     parser.add_argument('network', metavar='network', help='a Bayesian network (in one of DNE/NET/Hugin formats)')
-    parser.add_argument('encoding', choices=['d02', 'sbk05', 'cd05', 'cd06', 'db20'], help='a WMC encoding')
+    parser.add_argument('encoding', choices=['d02', 'sbk05', 'cd05', 'cd06', 'db21'], help='a WMC encoding')
     parser.add_argument('-e', dest='evidence', help="evidence file (in the INST format)")
     args = parser.parse_args()
-    if args.encoding == 'db20':
+    if args.encoding == 'db21':
         encode(args.network, args.evidence)
     else:
         encode_using_ace(args.network, args.evidence, args.encoding)

### 2020-08-02 paper/paper.tex
Two-column mode

@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-\usepackage[UKenglish]{babel}
-\usepackage[UKenglish]{isodate}
-\usepackage{fullpage}
+\def\year{2020}\relax
+%File: formatting-instruction.tex
+\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
+\usepackage{aaai20}  % DO NOT CHANGE THIS
+\usepackage{times}  % DO NOT CHANGE THIS
+\usepackage{helvet} % DO NOT CHANGE THIS
+\usepackage{courier}  % DO NOT CHANGE THIS
+\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
+\usepackage{graphicx} % DO NOT CHANGE THIS
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\usepackage{graphicx}  % DO NOT CHANGE THIS
+\frenchspacing  % DO NOT CHANGE THIS
+\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
+\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
+%\nocopyright
+%PDF Info Is REQUIRED.
+% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
+% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
+ \pdfinfo{
+/Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
+/Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen)
+} %Leave this	
+% /Title ()
+% Put your actual complete title (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case
+% Leave the space between \Title and the beginning parenthesis alone
+% /Author ()
+% Put your actual complete list of authors (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case. 
+% Each author should be only by a comma. If the name contains accents, remove them. If there are any LaTeX commands, 
+% remove them.
+
+% DISALLOWED PACKAGES
+% \usepackage{authblk} -- This package is specifically forbidden
+% \usepackage{balance} -- This package is specifically forbidden
+% \usepackage{caption} -- This package is specifically forbidden
+% \usepackage{color (if used in text)
+% \usepackage{CJK} -- This package is specifically forbidden
+% \usepackage{float} -- This package is specifically forbidden
+% \usepackage{flushend} -- This package is specifically forbidden
+% \usepackage{fontenc} -- This package is specifically forbidden
+% \usepackage{fullpage} -- This package is specifically forbidden
+% \usepackage{geometry} -- This package is specifically forbidden
+% \usepackage{grffile} -- This package is specifically forbidden
+% \usepackage{hyperref} -- This package is specifically forbidden
+% \usepackage{navigator} -- This package is specifically forbidden
+% (or any other package that embeds links such as navigator or hyperref)
+% \indentfirst} -- This package is specifically forbidden
+% \layout} -- This package is specifically forbidden
+% \multicol} -- This package is specifically forbidden
+% \nameref} -- This package is specifically forbidden
+% \natbib} -- This package is specifically forbidden -- use the following workaround:
+% \usepackage{savetrees} -- This package is specifically forbidden
+% \usepackage{setspace} -- This package is specifically forbidden
+% \usepackage{stfloats} -- This package is specifically forbidden
+% \usepackage{tabu} -- This package is specifically forbidden
+% \usepackage{titlesec} -- This package is specifically forbidden
+% \usepackage{tocbibind} -- This package is specifically forbidden
+% \usepackage{ulem} -- This package is specifically forbidden
+% \usepackage{wrapfig} -- This package is specifically forbidden
+% DISALLOWED COMMANDS
+% \nocopyright -- Your paper will not be published if you use this command
+% \addtolength -- This command may not be used
+% \balance -- This command may not be used
+% \baselinestretch -- Your paper will not be published if you use this command
+% \clearpage -- No page breaks of any kind may be used for the final version of your paper
+% \columnsep -- This command may not be used
+% \newpage -- No page breaks of any kind may be used for the final version of your paper
+% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
+% \pagestyle -- This command may not be used
+% \tiny -- This is not an acceptable font size.
+% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
+% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
+
+\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.
+
 \usepackage{amsthm}
@@
 \usepackage{mathtools}
-\usepackage{hyperref}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \usepackage[inline]{enumitem}
-
 \usetikzlibrary{cd}
@@
 \usetikzlibrary{calc}
-
+\DeclareMathOperator{\im}{im}
 \newtheorem{theorem}{Theorem}
@@
 
-\DeclareMathOperator{\im}{im}
-
+% The file aaai20.sty is the style file for AAAI Press 
+% proceedings, working notes, and technical reports.
+%
+\setlength\titlebox{2.5in} % If your paper contains an overfull \vbox too high warning at the beginning of the document, use this
+% command to correct it. You may not alter the value below 2.5 in
 \title{Weighted Model Counting with Conditional Weights}
-\author{Paulius Dilkas}
+%Your title must be in mixed case, not sentence case. 
+% That means all verbs (including short verbs like be, is, using,and go), 
+% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
+% articles, conjunctions, and prepositions are lower case unless they
+% directly follow a colon or long dash
+\author{Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{Primarily Mike Hamilton of the Live Oak Press, LLC, with help from the AAAI Publications Committee}\\ \Large \textbf{AAAI Style Contributions by
+Pater Patel Schneider,} \\ \Large \textbf{Sunil Issar, J.
+Scott Penberthy, George Ferguson, Hans Guesgen}\\ % All authors must be in the same font size and format.
+Use \Large and \textbf to achieve this result when breaking a line
+\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\ %If you have multiple authors and multiple affiliations
+% use superscripts in text and roman font to identify them.
+For example, Sunil Issar,\textsuperscript{\rm 2} J.
+Scott Penberthy\textsuperscript{\rm 3} George Ferguson,\textsuperscript{\rm 4} Hans Guesgen\textsuperscript{\rm 5}.
+Note that the comma should be placed BEFORE the superscript for optimum readability
+2275 East Bayshore Road, Suite 160\\
+Palo Alto, California 94303\\
+publications20@aaai.org % email address must be in roman text type, not monospace or sans serif
+}
 
@@
 
+\begin{abstract}
+AAAI creates proceedings, working notes, and technical reports directly from
+electronic source furnished by the authors. To ensure that all papers in the
+publication have a uniform appearance, authors must adhere to the following
+instructions.
+\end{abstract}
+
 \section{Introduction}
 
+\noindent Foo
 \begin{itemize}
@@
   algorithm doesn't.
+\item Replace things like `Darwiche (Darwiche, 2005)' with `Darwiche (2005)' if
+  possible (without natbib).
 \end{itemize}
@@
 
-\paragraph{Using WMC to perform inference on Bayesian networks.} Hitherto, four
-techniques have been proposed for encoding Bayesian networks into instances of
-WMC. We will identify them based on the initials of authors as well as
-publications years: \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}, \texttt{sbk05}
+\paragraph{WMC for Bayesian networks.} Hitherto, four techniques have been
+proposed for encoding Bayesian networks into instances of WMC. We will identify
+them based on the initials of authors as well as publications years:
+\texttt{d02} \cite{DBLP:conf/kr/Darwiche02}, \texttt{sbk05}
 \cite{DBLP:conf/aaai/SangBK05}, \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05},
@@
 
-\begin{table}
-  \centering
-  \caption{A comparison of Boolean-algebraic (BA) and set-theoretic (ST)
-    concepts for $2^U$ for any set $U$}
-  \label{tbl:notation}
-  \begin{tabular}{lccl}
-    \toprule
-    BA name & BA symbol & ST symbol & ST name \\
-    \midrule
-    bottom & $\bot$ & $\emptyset$ & empty set \\
-    top & $\top$ & $U$ & \\
-    meet, and & $\land$ & $\cap$ & intersection \\
-    join, or & $\lor$ & $\cup$ & union \\
-    complement, not & $\neg$ & $^c$ & complement \\
-            & $\le$ & $\subseteq$ & subset relation, set inclusion \\
-    atom & & & singleton, unit set \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+\todo[inline]{Describe BA-PS duality without the table.}
 
-\begin{table}
+% \begin{table}
+%   \centering
+%   \caption{A comparison of Boolean-algebraic (BA) and set-theoretic (ST)
+%     concepts for $2^U$ for any set $U$}
+%   \label{tbl:notation}
+%   \begin{tabular}{lccl}
+%     \toprule
+%     BA name & BA symbol & ST symbol & ST name \\
+%     \midrule
+%     bottom & $\bot$ & $\emptyset$ & empty set \\
+%     top & $\top$ & $U$ & \\
+%     meet, and & $\land$ & $\cap$ & intersection \\
+%     join, or & $\lor$ & $\cup$ & union \\
+%     complement, not & $\neg$ & $^c$ & complement \\
+%             & $\le$ & $\subseteq$ & subset relation, set inclusion \\
+%     atom & & & singleton, unit set \\
+%     \bottomrule
+%   \end{tabular}
+% \end{table}
+
+\begin{table*}
   \caption{Notation for a logic with two atoms. The elements in both columns are
@@
   \end{tabular}
-\end{table}
+\end{table*}
 
@@
 \begin{lemma} \label{prop:measure}
-  The function $\mu_\nu$, as defined by \cref{eq:induced_measure}, is a measure.
+  The function $\mu_\nu$, (from \cref{eq:induced_measure}), is a measure.
 \end{lemma}
-\begin{proof}
-  Note that $\mu_\nu(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b
-  \in 2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
-  Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
-  $b$. Moreover, none of them can be below both $a$ and $b$ because then they
-  would have to be below $a \land b = \bot$. Thus
-  \[
-    \mu_\nu(a \lor b) = \sum_{\{u\} \le a \lor b} \nu(u) = \sum_{\{u\} \le a}
-    \nu(u) + \sum_{\{u\} \le b} \nu(u) = \mu_\nu(a) + \mu_\nu(b)
-  \]
-  as required.
-\end{proof}
+% \begin{proof}
+%   Note that $\mu_\nu(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b
+%   \in 2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
+%   Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
+%   $b$. Moreover, none of them can be below both $a$ and $b$ because then they
+%   would have to be below $a \land b = \bot$. Thus
+%   \[
+%     \mu_\nu(a \lor b) = \sum_{\{u\} \le a \lor b} \nu(u) = \sum_{\{u\} \le a}
+%     \nu(u) + \sum_{\{u\} \le b} \nu(u) = \mu_\nu(a) + \mu_\nu(b)
+%   \]
+%   as required.
+% \end{proof}
 
@@
 \begin{equation} \label{eq:wmc_example}
-  \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(a)w(b) + w(a)w(\neg b) = 0.3.
+  \begin{split}
+    \mathrm{WMC}(\Delta) &= \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) \\
+    &= w(a)w(b) + w(a)w(\neg b) = 0.3.
+  \end{split}
 \end{equation}
@@
 equivalently to \cref{eq:wmc_example}, we can write
-\[
-  \mu(a) = \nu(\{ a, b \}) + \nu(\{ a \}) = \nu_a(\{a\})\nu_b(\{b\}) +
-  \nu_a(\{a\})\nu_b(\emptyset) = 0.3.
-\]
+\begin{align*}
+  \mu(a) &= \nu(\{ a, b \}) + \nu(\{ a \}) \\
+         &= \nu_a(\{a\})\nu_b(\{b\}) + \nu_a(\{a\})\nu_b(\emptyset) = 0.3.
+\end{align*}
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:example_bn}
-\end{figure}
+\end{figure*}
 
@@
 \begin{algorithm}
-  \caption{Encoding a Bayesian network as a function $2^U \to \mathbb{R}_{\ge
-      0}$}
+  \caption{Encoding a Bayesian network}
   \label{alg:encoding}
-  \KwData{a Bayesian network with vertices $\mathcal{V}$ and probability
-    distribution $\Pr$}
+  \KwData{vertices $\mathcal{V}$, probability distribution $\Pr$}
   \KwResult{a function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
@@
       \For{$(y_1, \dots, y_n) \in \prod_{i = 1}^n \im Y_i$}{
-        $p_1 \gets \Pr(X = 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
-        $p_0 \gets \Pr(X \ne 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
+        $p_1 \gets \Pr(X = 1 \mid y_1, \dots, y_n)$\;
+        $p_0 \gets \Pr(X \ne 1 \mid y_1, \dots, y_n)$\;
         $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_1[\lambda_{X=1}] \cdot
@@
           1}^n \im Y_i$}{
-        $p_x \gets \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
+        $p_x \gets \Pr(X = x \mid y_1, \dots, y_n)$\;
         $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_x[\lambda_{X=x}] \cdot
@@
   \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
-  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
-    &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
-  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
+  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] \\
+                 &+ 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
+                 &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] \\
+                 &+ 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
+  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \\
+                 &\cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \\
+                 &\cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
 \end{align*}
@@
   \[
-    \mathrm{CPT}_X (\{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1,
-    \dots, n \}) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
+    \mathrm{CPT}_X (T) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n),
   \]
+  where $T = \{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1, \dots, n
+  \}$.
 \end{lemma}
-\begin{proof}
-  Let $T = \{ \lambda_{X=x} \} \cup \{ \lambda_{Y_i=y_i} \mid i = 1, \dots, n
-  \}$. If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
-  Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
-  \dots, Y_n$. Exactly one of these terms is nonzero when applied to $T$, and
-  it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
+% \begin{proof}
+% If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
+%   Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
+%   \dots, Y_n$. Exactly one of these terms is nonzero when applied to $T$, and
+%   it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
 
-  If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
-  \right)(T) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
-    (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
-  \right)(T) = 1$, so $\mathrm{CPT}_X(T) = \Pr(X = x \mid Y_1 = y_1,
-  \dots, Y_n = y_n)$ by a similar argument as before.
-\end{proof}
+%   If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
+%   \right)(T) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
+%     (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
+%   \right)(T) = 1$, so $\mathrm{CPT}_X(T) = \Pr(X = x \mid Y_1 = y_1,
+%   \dots, Y_n = y_n)$ by a similar argument as before.
+% \end{proof}
 
@@
     \begin{cases}
-      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } T = \{ \lambda_{X_i=x_i}
-      \mid i = 1, \dots, n \} \text{ for some } (x_1, \dots, x_n) \in
-      \prod_{i=1}^n \im X_i \\
+      \Pr(x_1, \dots, x_n) &
+      \begin{aligned}
+        &\text{if } T = \{ \lambda_{X_i=x_i} \}_{i = 1}^n \text{ for} \\
+        &\text{some } \textstyle (x_i)_{i=1}^n \in \prod_{i=1}^n \im X_i
+      \end{aligned} \\
       0 & \text{otherwise,}
@@
 \end{proposition}
-\begin{proof}
-  If $T = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
-    \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
-  \[
-    \phi(T) = \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\;
-      \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X
-        \in \mathcal{V}} X=v_X \right)
-  \]
-  by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
-  must be some non-binary random variable $X \in \mathcal{V}$ such that
-  $|\mathcal{E}(X) \cap T| \ne 1$. If $\mathcal{E}(X) \cap T = \emptyset$, then
-  $\left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(T) = 0$, and so
-  $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$. If $|\mathcal{E}(X) \cap T| > 1$,
-  then we must have two different values $x_1, x_2 \in \im X$ such that
-  $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq T$ which means that
-  $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(T) = 0$, and
-  so, again, $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$.
-\end{proof}
+% \begin{proof}
+%   If $T = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
+%     \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
+%   \[
+%     \phi(T) = \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\;
+%       \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X
+%         \in \mathcal{V}} X=v_X \right)
+%   \]
+%   by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
+%   must be some non-binary random variable $X \in \mathcal{V}$ such that
+%   $|\mathcal{E}(X) \cap T| \ne 1$. If $\mathcal{E}(X) \cap T = \emptyset$, then
+%   $\left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(T) = 0$, and so
+%   $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$. If $|\mathcal{E}(X) \cap T| > 1$,
+%   then we must have two different values $x_1, x_2 \in \im X$ such that
+%   $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq T$ which means that
+%   $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(T) = 0$, and
+%   so, again, $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$.
+% \end{proof}
+
+\todo[inline]{Try to be consistent about the usage of $\Pr$.}
 
 \begin{theorem} \label{thm:correctness}
-  For any $X \in \mathcal{V}$ and $x \in \im X$, $(\exists_U(\phi \cdot
-  [\lambda_{X=x}]))(\emptyset) = \Pr(X = x)$.
+  For any $X \in \mathcal{V}$ and $x \in \im X$,
+  \[
+    (\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset) = \Pr(X = x).
+  \]
 \end{theorem}
-\begin{proof}
-  Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
-  \begin{align*}
-    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
-    &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
-  \end{align*}
-  by the following arguments:
-  \begin{itemize}
-  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
-  \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
-    [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
-    \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
-  \item \cref{lemma:full_distribution};
-  \item marginalisation of a probability distribution.
-  \end{itemize}
-\end{proof}
-\todo[inline]{Need to make the proof nicer.}
+% \begin{proof}
+%   Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
+%   \begin{align*}
+%     (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
+%     &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
+%   \end{align*}
+%   by the following arguments:
+%   \begin{itemize}
+%   \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
+%   \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
+%     [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
+%     \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
+%   \item \cref{lemma:full_distribution};
+%   \item marginalisation of a probability distribution.
+%   \end{itemize}
+% \end{proof}
+% TODO: need to make the proof nicer.
 
@@
   \centering
-  \begin{minipage}{0.59\textwidth}
+  \input{cumulative.tex}%
+  \caption{Cumulative number of instances solved by ADDMC over time using each
+    encoding}
+\end{figure}
+
+\begin{table}
   \centering
-    \input{cumulative.tex}%
-    \captionof{figure}{Cumulative number of instances solved by ADDMC over time
-      using each encoding}
-  \end{minipage}
-  \begin{minipage}{0.39\textwidth}
-    \centering
-    \captionof{table}{The numbers of instances solved by ADDMC with each
-      encoding (uniquely, faster than with others, and in total) under the
-      described time and memory constraints (out of 1216 instances)}%
+  \caption{The numbers of instances solved by ADDMC with each encoding
+    (uniquely, faster than with others, and in total) under the described time
+    and memory constraints (out of 1216 instances)}%
   \begin{tabular}{lrrr}
@@
   \end{tabular}
-  \end{minipage}
-\end{figure}
+\end{table}
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \caption{ADDMC inference time using \texttt{db21} compared to \texttt{d02}
-    (left) and \texttt{sbk05} (right) on an instance-by-instance basis across
-    all data sets.}
-\end{figure}
+    (left) and \texttt{sbk05} (right) for each instance in all data sets.}
+\end{figure*}
 
@@
 
-\paragraph{Acknowledgements.} This work has made use of the resources provided
-by the Edinburgh Compute and Data Facility (ECDF)
-(\url{http://www.ecdf.ed.ac.uk/}).
+\todo[inline]{Have an appendix with proofs.}
 
-\bibliographystyle{plain}
+%\paragraph{Acknowledgements.} This work has made use of the resources provided
+%by the Edinburgh Compute and Data Facility (ECDF)
+%(\url{http://www.ecdf.ed.ac.uk/}).
+
+\bibliographystyle{aaai}
 \bibliography{paper}
-
 \end{document}

### 2020-08-02 analyse.R

@@ -116,12 +116,7 @@ cumulative$time <- as.numeric(cumulative$time)
 cumulative$count <- as.numeric(cumulative$count)
 cumulative <- cumulative[cumulative$time < TIMEOUT, ]
 
-max_d02 <- max(cumulative$count[cumulative$encoding == "\\texttt{d02}"])
-interpolation <- approx(x = cumulative$count[cumulative$encoding == "\\texttt{db21}"],
-                        y = cumulative$time[cumulative$encoding == "\\texttt{db21}"],
-                        xout = max_d02)$y
-
-tikz(file = "paper/cumulative.tex", width = 3.85, height = 2.5)
+tikz(file = "paper/cumulative.tex", width = 3, height = 1.6)
 ggplot(cumulative, aes(x = time, y = count, color = encoding)) +
   geom_line(aes(linetype = encoding)) +
   scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 10, 1000), labels = c("0.1", "10", "1000")) +
@@ -134,6 +129,11 @@ ggplot(cumulative, aes(x = time, y = count, color = encoding)) +
   theme_light() +
   labs(color = "Encoding", linetype = "Encoding")
 dev.off()
+
+max_d02 <- max(cumulative$count[cumulative$encoding == "\\texttt{d02}"])
+interpolation <- approx(x = cumulative$count[cumulative$encoding == "\\texttt{db21}"],
+                        y = cumulative$time[cumulative$encoding == "\\texttt{db21}"],
+                        xout = max_d02)$y
 
 # Scatter plot for memory usage (not interesting)
 ggplot(df, aes(x = memory_db21, y = memory_cd06, col = major.dataset)) +

### 2020-08-04 paper/paper.tex
New template

@@
-\def\year{2020}\relax
-%File: formatting-instruction.tex
+\def\year{2021}\relax
 \documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai20}  % DO NOT CHANGE THIS
+\usepackage{aaai21}  % DO NOT CHANGE THIS
 \usepackage{times}  % DO NOT CHANGE THIS
@@
 \usepackage{graphicx}  % DO NOT CHANGE THIS
+\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
 \frenchspacing  % DO NOT CHANGE THIS
@@
 \pdfinfo{
-/Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
-/Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen)
+/Title (Weighted Model Counting with Conditional Weights)
+/Author ()
+/TemplateVersion (2021.1)
 } %Leave this
@@
 % \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{caption} -- This package is specifically forbidden
 % \usepackage{color (if used in text)
@@
 % \nameref} -- This package is specifically forbidden
-% \natbib} -- This package is specifically forbidden -- use the following workaround:
 % \usepackage{savetrees} -- This package is specifically forbidden
@@
 
+% The file aaai21.sty is the style file for AAAI Press
+% proceedings, working notes, and technical reports.
+%
+
 \usepackage{amsthm}
+\usepackage{thmtools,thm-restate}
 \usepackage{amsfonts}
@@
 \usepackage{tikz}
-\usepackage[backgroundcolor=lightgray]{todonotes}
 \usepackage{complexity}
@@
 
-% The file aaai20.sty is the style file for AAAI Press 
-% proceedings, working notes, and technical reports.
-%
-\setlength\titlebox{2.5in} % If your paper contains an overfull \vbox too high warning at the beginning of the document, use this
-% command to correct it. You may not alter the value below 2.5 in
 \title{Weighted Model Counting with Conditional Weights}
-%Your title must be in mixed case, not sentence case. 
-% That means all verbs (including short verbs like be, is, using,and go), 
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-\author{Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{Primarily Mike Hamilton of the Live Oak Press, LLC, with help from the AAAI Publications Committee}\\ \Large \textbf{AAAI Style Contributions by
-Pater Patel Schneider,} \\ \Large \textbf{Sunil Issar, J.
-Scott Penberthy, George Ferguson, Hans Guesgen}\\ % All authors must be in the same font size and format.
-Use \Large and \textbf to achieve this result when breaking a line
-\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\ %If you have multiple authors and multiple affiliations
-% use superscripts in text and roman font to identify them.
-For example, Sunil Issar,\textsuperscript{\rm 2} J.
-Scott Penberthy\textsuperscript{\rm 3} George Ferguson,\textsuperscript{\rm 4} Hans Guesgen\textsuperscript{\rm 5}.
-Note that the comma should be placed BEFORE the superscript for optimum readability
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\
-publications20@aaai.org % email address must be in roman text type, not monospace or sans serif
-}
+%\author{
+%  Paulius Dilkas, \textsuperscript{\rm 1}
+%  Vaishak Belle \textsuperscript{\rm 1,2} \\
+%}
+%\affiliations{
+%    \textsuperscript{\rm 1} University of Edinburgh \\
+%    \textsuperscript{\rm 2} Alan Turing Institute \\
+%    p.dilkas@sms.ed.ac.uk, vaishak@ed.ac.uk
+%}
+\begin{document}
 
-\begin{document}
 \maketitle
 
-\begin{abstract}
+\begin{abstract} % TODO
   AAAI creates proceedings, working notes, and technical reports directly from
@@
 
-\noindent Foo
-\begin{itemize}
-\item The main narrative
-  \begin{enumerate}
-  \item Putting weights on literals is restrictive.
-  \item To overcome this, it is common practice to add more literals.
-  \item This is indeed always possible but much slower.
-  \item We show how we can define conditional weights on literals, allowing us
-    to encode any measure.
-  \item We demonstrate a specific example of this by presenting a new way to
+Introduce WMC \cite{DBLP:conf/aaai/SangBK05}
+
+Over the last fifteen years, WMC has been extended and generalised in many ways,
+e.g., to handle continuous probability distributions
+\cite{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
+\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
+domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, WMC has been generalised
+from weights in the interval $[0, 1]$ or positive real numbers to an arbitrary
+semiring, making it applicable to domains such as parsing, dynamic programming,
+constraint programming, databases, networks, etc.
+\cite{DBLP:journals/japll/KimmigBR17}. It has been applied to Bayesian networks
+\cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906} and probabilistic
+graphical models more generally \cite{DBLP:conf/ecsqaru/ChoiKD13}, probabilistic
+logic programming languages \cite{DBLP:journals/tplp/FierensBRSGTJR15} and
+probabilistic programs with discrete probability distributions
+\cite{DBLP:journals/corr/abs-2005-09089}. Many WMC algorithms have been proposed
+based primarily either on knowledge compilation
+\cite{DBLP:conf/ecai/Darwiche04,DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17}
+or search \cite{DBLP:conf/aaai/SangBK05}.
+
+The most well-studied version of WMC assigns weights to models based on
+weights on literals, i.e., the weight of a model is the product of the weights
+of all literals in it. This severely restricts what probability distributions
+can be represented, and this limitation is usually overcome by increasing the
+size of the problem, i.e., adding more literals.
+
+We show that while this workaround is always possible, it can be significantly
+more efficient to consider \emph{conditional weights} on literals. Similarly to
+conditional probabilities, conditional weights allow us to represent
+probabilities in a manner that is both efficient and interpretable. Not having
+additional variables that are only needed to manipulate the representation into
+a specific format helps with both efficiency and interpretability. Similarly to
+Bayesian networks, the size of the representation scales with independence and
+literal-weight WMC is a special case when everything is independent.
+
+We demonstrate a specific example of this by presenting a new way to
 encode Bayesian networks into instances of WMC and adapting a WMC algorithm
-    (ADDMC) to run on the new format.
-  \item We show that this results in significantly faster inference.
-  \item We show that our encoding results in asymptotically fewer literals and
-    fewer ADDs.
-  \end{enumerate}
-\item Introduce
-  \begin{itemize}
-  \item WMC \cite{DBLP:conf/aaai/SangBK05}
-  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} and ADDs
-    \cite{DBLP:journals/fmsd/BaharFGHMPS97}
-  \item A Bayesian network is a directed acyclic graph with random variables as
-    vertices that defines a probability distribution over them. The full
-    probability distribution can be expressed as the product of the conditional
-    probability distributions of all random variables. For discrete Bayesian
-    networks (and we only consider discrete networks in this paper), each such
-    distribution can be represented by a table known as a conditional
-    probability table (CPT).
-  \end{itemize}
-\item[F] What are the main claims, what are the main takeaways, intuitive [???]
-  of theorems to follow.
-\item Our work is, in spirit, similar to... using ROBDDs for Inference in
-  Bayesian Networks with Troubleshooting as an Example
-  \cite{DBLP:conf/uai/NielsenWJK00}: this is an interesting approach where
-  deterministic parts of a BN are expressed as Boolean functions, i.e.,
-  extracting the logical from the probabilistic. Maybe I can make a case that my
-  encoding (the textual version) kind of does the same, even though the
-  algorithm doesn't.
-\item Replace things like `Darwiche (Darwiche, 2005)' with `Darwiche (2005)' if
-  possible (without natbib).
-\end{itemize}
+ADDMC to run on the new format. ADDMC \cite{DBLP:conf/aaai/DudekPV20} is a
+recently-proposed algorithm for WMC based on manipulating functions on Boolean
+algebras using an efficient representation for such functions known as
+\emph{algebraic decision diagrams} (ADDs)
+\cite{DBLP:journals/fmsd/BaharFGHMPS97}. We show that with a few minor
+modifications the algorithm can be adapted to work on our new WMC format
+
+Showing that the new encoding produces an asymptotically smaller problem (w.r.t.
+the numbers of literals and ADDs) and results in faster inferences.
+
+% TODO: an overview of all results, with forward references
 
 \section{Related Work}
+
+% TODO: introduce this section and explain why there's so much about BNs
+A Bayesian network is a directed acyclic graph with random variables as vertices
+that defines a probability distribution over them. The full probability
+distribution can be expressed as the product of the conditional probability
+distributions of all random variables. For discrete Bayesian networks (and we
+only consider discrete networks in this paper), each such distribution can be
+represented by a table known as a conditional probability table (CPT).
 
@@
 and \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}. Below we summarise the
-observed performance differences among them. Sang et al.
-\cite{DBLP:conf/aaai/SangBK05} claim that \texttt{sbk05} is a smaller encoding
-than \texttt{d02} with respect to both the number of clauses and the number of
-variables but provide no experimental comparison. Chavira and Darwiche
-\cite{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with \texttt{d02} by
-measuring the time it takes to compile either encoding into an arithmetic
-circuit (but do not measure inference time). The more recent encoding
-\texttt{cd05} always compiles faster and results in a smaller arithmetic circuit
-(as measured by the number of edges). In their subsequent paper, the same
-authors perform two sets of experiments (that are relevant to this summary)
-\cite{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
-\texttt{cd06} encodings into d-DNNF (i.e., deterministic decomposable negation
-normal form \cite{DBLP:journals/jancl/Darwiche01}), measuring both compilation
-time and numbers of edges in the d-DNNF diagram. The results are mostly in
-favour of \texttt{cd06}. Second, they compare the inference time of
-\texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04} with the compile
-times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
-In these experiments, \texttt{cd06} is always faster than \texttt{cd05}, while
-the comparison with \texttt{sbk05} is mixed. Sometimes \texttt{cd06} is orders
-of magnitude faster than \texttt{sbk05}, sometimes slightly slower. The
-performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
-to judge: \texttt{sbk05} is better on three out of five instances and worse on
-the remaining two. Based on this description, one would expect \texttt{cd06} to
-be faster than both \texttt{cd05} and \texttt{sbk05}, both of which should be
-faster than \texttt{d02}. The experiments in \cref{sec:experiments}, however,
-strongly disagree with this prediction, showing that the quality of an encoding
-depends strongly on the underlying search algorithm or compilation technique.
+observed performance differences among them. \citet{DBLP:conf/aaai/SangBK05}
+claim that \texttt{sbk05} is a smaller encoding than \texttt{d02} with respect
+to both the number of clauses and the number of variables but provide no
+experimental comparison. \citet{DBLP:conf/ijcai/ChaviraD05} compare
+\texttt{cd05} with \texttt{d02} by measuring the time it takes to compile either
+encoding into an arithmetic circuit (but do not measure inference time). The
+more recent encoding \texttt{cd05} always compiles faster and results in a
+smaller arithmetic circuit (as measured by the number of edges). In their
+subsequent paper, the same authors perform two sets of experiments (that are
+relevant to this summary) \cite{DBLP:conf/sat/ChaviraD06}. First, they compile
+\texttt{cd05} and \texttt{cd06} encodings into d-DNNF (i.e., deterministic
+decomposable negation normal form \cite{DBLP:journals/jancl/Darwiche01}),
+measuring both compilation time and numbers of edges in the d-DNNF diagram. The
+results are mostly in favour of \texttt{cd06}. Second, they compare the
+inference time of \texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04}
+with the compile times of \texttt{cd05} and \texttt{cd06}, but only on five
+(types of) instances. In these experiments, \texttt{cd06} is always faster than
+\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
+\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
+slightly slower. The performance difference between \texttt{sbk05} and
+\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
+five instances and worse on the remaining two. Based on this description, one
+would expect \texttt{cd06} to be faster than both \texttt{cd05} and
+\texttt{sbk05}, both of which should be faster than \texttt{d02}. The
+experiments in \cref{sec:experiments}, however, strongly disagree with this
+prediction, showing that the quality of an encoding depends strongly on the
+underlying search algorithm or compilation technique.
 
@@
   Logic} \label{sec:prelims}
-
-\todo[inline]{Describe BA-PS duality without the table.}
-
-% \begin{table}
-%   \centering
-%   \caption{A comparison of Boolean-algebraic (BA) and set-theoretic (ST)
-%     concepts for $2^U$ for any set $U$}
-%   \label{tbl:notation}
-%   \begin{tabular}{lccl}
-%     \toprule
-%     BA name & BA symbol & ST symbol & ST name \\
-%     \midrule
-%     bottom & $\bot$ & $\emptyset$ & empty set \\
-%     top & $\top$ & $U$ & \\
-%     meet, and & $\land$ & $\cap$ & intersection \\
-%     join, or & $\lor$ & $\cup$ & union \\
-%     complement, not & $\neg$ & $^c$ & complement \\
-%             & $\le$ & $\subseteq$ & subset relation, set inclusion \\
-%     atom & & & singleton, unit set \\
-%     \bottomrule
-%   \end{tabular}
-% \end{table}
 
@@
 $\mathcal{L}$, and $2^{2^U}$ is the set of all formulas. These sets can also be
-represented as Boolean algebras---see \cref{tbl:notation} for an overview of
-notational differences and \cref{tbl:notation_example} for examples of how
-various elements can be represented in both notations. Most importantly, note
-that the word \emph{atom} has completely different meanings in logic and in
-Boolean algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an
-element of $U$, whereas an atom in a Boolean algebra is (in set-theoretic terms)
-a singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
-$\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
-logic, we will use the algebraic definition of an atom while referring to
-logical atoms as \emph{variables}. In the rest of the paper, for any set $U$, we
-will use set-theoretic notation for $2^U$ and Boolean-algebraic notation for
-$2^{2^U}$, except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$
-for some model $x \in 2^U$.
+represented as Boolean algebras (e.g., $(2^{2^U}, \land, \lor, \neg, \bot,
+\top)$)---see \cref{tbl:notation_example} for examples of how various elements
+can be represented in both notations. Most importantly, note that the word
+\emph{atom} has completely different meanings in logic and in Boolean algebras.
+An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of $U$, whereas
+an atom in a Boolean algebra is (in set-theoretic terms) a singleton set. For
+instance, an atom in $2^{2^U}$ corresponds to a model of $\mathcal{L}$, i.e., an
+element of $2^U$. Unless referring specifically to a logic, we will use the
+algebraic definition of an atom while referring to logical atoms as
+\emph{variables}. In the rest of the paper, for any set $U$, we will use
+set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$,
+except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some
+model $x \in 2^U$.
 
@@
 function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a measure
-$\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
-\begin{equation} \label{eq:induced_measure}
-  \mu_\nu(x) = \sum_{\{u\} \le x} \nu(u).
-\end{equation}
+$\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if $\mu_\nu(x) = \sum_{\{u\} \le
+  x} \nu(u)$.
+
+\begin{restatable}{theorem}{measure} \label{prop:measure}
+  The function $\mu_\nu$ is a measure.
+\end{restatable}
+
 Finally, a measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
 \emph{factorable} if there exists a factored weight function $\nu\colon 2^U \to
-\mathbb{R}_{\ge 0}$ that induces $\mu$.
-
-\begin{lemma} \label{prop:measure}
-  The function $\mu_\nu$, (from \cref{eq:induced_measure}), is a measure.
-\end{lemma}
-% \begin{proof}
-%   Note that $\mu_\nu(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b
-%   \in 2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
-%   Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
-%   $b$. Moreover, none of them can be below both $a$ and $b$ because then they
-%   would have to be below $a \land b = \bot$. Thus
-%   \[
-%     \mu_\nu(a \lor b) = \sum_{\{u\} \le a \lor b} \nu(u) = \sum_{\{u\} \le a}
-%     \nu(u) + \sum_{\{u\} \le b} \nu(u) = \mu_\nu(a) + \mu_\nu(b)
-%   \]
-%   as required.
-% \end{proof}
-
-In this formulation, the process of calculating the value of $\mu_\nu(x)$ for
-some $x \in 2^{2^U}$ with a given definition of $\nu$ is known as WMC.
+\mathbb{R}_{\ge 0}$ that induces $\mu$. In this formulation, the process of
+calculating the value of $\mu_\nu(x)$ for some $x \in 2^{2^U}$ with a given
+definition of $\nu$ is known as WMC.
 
@@
 
-\todo[inline]{Introduce the subsection and give it some context.}
+WMC with weights defined on literals is only able to capture a subset of all
+possible measures on the Boolean algebra. This can be illustrated with a simple
+example.
 
@@
 
-\todo[inline]{Add the proof that one can always go from any measure to a
-  factorable measure by adding more literals and say: Not all measures are
-  factorable but it is common practice to add more literals to make the measure
-  factorable. We show that it's always possible and yet it can be faster not to
-  do it.}
+Since many measures of interests may not be factorable, a well-known way to
+encode them into instances of WMC is by adding more literals
+\cite{DBLP:journals/ai/ChaviraD08}. We can indeed show that this is always
+possible, however, as ensuing sections will demonstrate, it often makes the
+inference task much harder.
+
+\begin{restatable}{theorem}{extendable}
+  For any set $U$ and measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$, there
+  exists a set $V \supseteq U$ and a factorable measure $\mu'\colon 2^{2^V} \to
+  \mathbb{R}_{\ge 0}$ such that $\mu = \mu' \circ \iota$, where $\iota\colon
+  2^{2^U} \to 2^{2^V}$ is the inclusion homomorphism.
+\end{restatable}
 
@@
 
-\subsection{Proof of Correctness}
+\subsection{Correctness}
 
@@
 
-\begin{lemma} \label{lemma:cpt}
+\begin{restatable}{lemma}{cptlemma} \label{lemma:cpt}
   Let $X \in \mathcal{V}$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
@@
   \}$.
-\end{lemma}
-% \begin{proof}
-% If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
-%   Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
-%   \dots, Y_n$. Exactly one of these terms is nonzero when applied to $T$, and
-%   it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
+\end{restatable}
 
-%   If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
-%   \right)(T) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
-%     (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
-%   \right)(T) = 1$, so $\mathrm{CPT}_X(T) = \Pr(X = x \mid Y_1 = y_1,
-%   \dots, Y_n = y_n)$ by a similar argument as before.
-% \end{proof}
-
-\begin{proposition} \label{lemma:full_distribution}
+\begin{restatable}{lemma}{fulldistribution} \label{lemma:full_distribution}
   Let $\mathcal{V} = \{X_1, \dots, X_n\}$. Then
@@
   for all $T \in 2^U$.
-\end{proposition}
-% \begin{proof}
-%   If $T = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
-%     \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
-%   \[
-%     \phi(T) = \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\;
-%       \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X
-%         \in \mathcal{V}} X=v_X \right)
-%   \]
-%   by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
-%   must be some non-binary random variable $X \in \mathcal{V}$ such that
-%   $|\mathcal{E}(X) \cap T| \ne 1$. If $\mathcal{E}(X) \cap T = \emptyset$, then
-%   $\left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(T) = 0$, and so
-%   $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$. If $|\mathcal{E}(X) \cap T| > 1$,
-%   then we must have two different values $x_1, x_2 \in \im X$ such that
-%   $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq T$ which means that
-%   $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(T) = 0$, and
-%   so, again, $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$.
-% \end{proof}
+\end{restatable}
 
-\todo[inline]{Try to be consistent about the usage of $\Pr$.}
-
-\begin{theorem} \label{thm:correctness}
+\begin{restatable}{theorem}{correctness} \label{thm:correctness}
   For any $X \in \mathcal{V}$ and $x \in \im X$,
@@
   \]
-\end{theorem}
-% \begin{proof}
-%   Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
-%   \begin{align*}
-%     (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) = \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
-%     &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
-%   \end{align*}
-%   by the following arguments:
-%   \begin{itemize}
-%   \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
-%   \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
-%     [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
-%     \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
-%   \item \cref{lemma:full_distribution};
-%   \item marginalisation of a probability distribution.
-%   \end{itemize}
-% \end{proof}
-% TODO: need to make the proof nicer.
+\end{restatable}
 
@@
 
+In this section, we describe an experimental study comparing the five WMC
+encodings for Bayesian networks when run with ADDMC. The experiments were run on
+Intel Xeon Gold 6138 processor with an \SI{8}{\giga\byte} memory limit.
+
+For each Bayesian network, we need to choose a probability to compute. Whenever
+a Bayesian network comes with an evidence file, we compute the probability of
+evidence. Otherwise, let $X$ denote the last-mentioned vertex in the Bayesian
+network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
+probability of $X = \mathsf{true}$. Otherwise, we pick the value of $X$ which is
+listed first and calculate its marginal probability.
+
+For all encodings other than \texttt{db21}, we use their implementation in
+Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
+\texttt{-encodeOnly} and \texttt{-noEclause} flags. However, Ace was not used to
+encode evidence, as preliminary experiments revealed that the evidence-encoding
+implementation contains bugs that can lead to incorrect answers or a Java
+exception being thrown on some instances of the data set (and the source code is
+not publicly available). Instead, we simply list all the evidence as additional
+clauses in the encoding.
+
+Note that both \texttt{cd05} and \texttt{cd06} purposefully produce overly
+relaxed encodings that contain extra models and thus yield incorrect
+probabilities \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}. These
+additional models are supposed to be filtered out during circuit compilation
+\cite{DBLP:conf/ijcai/ChaviraD05}, but this is not easily achievable with ADDMC.
+Nonetheless, we include both encodings in the experiments.
+
+While encoding time itself was not measured because of different languages of
+implementation, it is worth noting that \texttt{db21} is linear in the total
+number of CPT rows and so is unlikely to be slower than, e.g., \texttt{cd06},
+which relies on solving $\NP$-complete problems as part of the encoding process
+\cite{DBLP:conf/sat/ChaviraD06}.
+
+\paragraph{Data.} For experimental data, we use the Bayesian networks available
+with Ace and
+Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
+which happen to be binary. We classify them into the following seven categories:
+\begin{itemize*}
+\item DQMR and
+\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
+\item Friends and Smokers,
+\item Mastermind, and
+\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
+\item remaining binary Bayesian networks that include Plan Recognition
+  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
+  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
+\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
+  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
+  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
+\end{itemize*}
+
 \begin{figure}
@@
 \end{figure}
+
+% TODO: To follow formatting requirements, I will need to remove the
+% nput command. Each figure will have to be separately compiled to a PDF (maybe
+% create a Makefile for that).
+% TODO: look up how to scale figures
+% TODO: reformat all colours to CMYK from RGB (in R)
 
@@
 \end{figure*}
-
-\todo[inline]{Write an introductory paragraph.}
-
-\begin{itemize}
-\item We chose not to measure or compare encoding time because of different
-  languages of implementation and the fact that our encoding algorithm (i.e.,
-  the process that converts a Bayesian network into a textual encoding such as
-  in \cref{sec:textual_representation}) is linear in the total number of CPT
-  rows and so is unlikely to be slower than, e.g., \texttt{cd06}, which relies
-  on solving $\NP$-complete problems as part of the encoding process
-  \cite{DBLP:conf/sat/ChaviraD06}.
-\item Whenever a Bayesian network comes with an evidence file, we compute the
-  probability of evidence. Otherwise, let $X$ denote the last-mentioned vertex
-  in the Bayesian network. If $\mathsf{true}$ is a valid value of $X$, we
-  compute the marginal probability of $X = \mathsf{true}$. Otherwise, we pick
-  the value of $X$ which is listed first and calculate its marginal probability.
-\item The experiments were run on Intel Xeon Gold 6138 processor with an
-  \SI{8}{\giga\byte} memory limit.
-\item For all other encodings, we use their implementation in
-  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
-  \texttt{-encodeOnly} and \texttt{-noEclause} flags. However, Ace was not used
-  to encode evidence, as preliminary experiments revealed that the
-  evidence-encoding implementation contains bugs that can lead to incorrect
-  answers or a Java exception being thrown on some instances of the data set
-  (and the source code is not publicly available). Instead, we simply list all
-  the evidence as additional clauses in the encoding (regardless of which
-  encoding is used).
-\item Note that \texttt{cd05} and \texttt{cd06} purposefully produce overly
-  relaxed encodings that contain extra models and thus yield incorrect
-  probabilities \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.
-  These additional models are supposed to be filtered out during circuit
-  compilation \cite{DBLP:conf/ijcai/ChaviraD05}, but this is not easily
-  achievable with ADDMC. Nonetheless, we include both encodings in our timing
-  experiments.
-\end{itemize}
-
-\paragraph{Data.} For experiments, we use the Bayesian networks available
-with Ace and
-Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
-which happen to be binary. We classify them into the following seven categories:
-\begin{itemize*}
-\item DQMR and
-\item Grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
-\item Friends and Smokers,
-\item Mastermind, and
-\item Random Blocks from the work of Chavira et al.
-  \cite{DBLP:journals/ijar/ChaviraDJ06},
-\item remaining binary Bayesian networks that include Plan Recognition
-  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
-  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
-\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
-  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
-  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
-\end{itemize*}
 
@@
 
-\section{Conclusions and Future Work}
+\section{Conclusions and Future Work} % TODO:write
 
@@
   tremendously, but I'm purposefully not doing that.
-\item Other things can be compiled into WMC, e.g., probabilistic programs
-  \cite{DBLP:journals/corr/abs-2005-09089}, ProbLog
-  \cite{DBLP:conf/uai/FierensBTGR11}.
 \end{itemize}
 
-\todo[inline]{Have an appendix with proofs.}
+% \section*{Acknowledgements}
 
-%\paragraph{Acknowledgements.} This work has made use of the resources provided
-%by the Edinburgh Compute and Data Facility (ECDF)
-%(\url{http://www.ecdf.ed.ac.uk/}).
+% This work has made use of the resources provided by the Edinburgh Compute and
+% Data Facility (ECDF) (\url{http://www.ecdf.ed.ac.uk/}).
 
-\bibliographystyle{aaai}
+\appendix
+\section{Proofs}
+
+\measure*
+\begin{proof}
+  Note that $\mu_\nu(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b
+  \in 2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
+  Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
+  $b$. Moreover, none of them can be below both $a$ and $b$ because then they
+  would have to be below $a \land b = \bot$. Thus
+  \begin{align*}
+    \mu_\nu(a \lor b) &= \sum_{\{u\} \le a \lor b} \nu(u) = \sum_{\{u\} \le a} \nu(u) + \sum_{\{u\} \le b} \nu(u) \\
+                      &= \mu_\nu(a) + \mu_\nu(b)
+  \end{align*}
+  as required.
+\end{proof}
+
+\extendable*
+\begin{proof}
+  TODO
+\end{proof}
+
+\cptlemma*
+\begin{proof}
+  If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
+  Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
+  \dots, Y_n$. Exactly one of these terms is nonzero when applied to $T$, and
+  it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
+
+  If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
+  \right)(T) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
+    (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
+  \right)(T) = 1$, so $\mathrm{CPT}_X(T) = \Pr(X = x \mid Y_1 = y_1,
+  \dots, Y_n = y_n)$ by a similar argument as before.
+\end{proof}
+
+\fulldistribution*
+\begin{proof}
+  If $T = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
+    \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
+  \begin{align*}
+    \phi(T) &= \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\; \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) \\
+            &= \Pr \left( \bigwedge_{X \in \mathcal{V}} X=v_X \right)
+  \end{align*}
+  by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
+  must be some non-binary random variable $X \in \mathcal{V}$ such that
+  $|\mathcal{E}(X) \cap T| \ne 1$. If $\mathcal{E}(X) \cap T = \emptyset$, then
+  $\left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(T) = 0$, and so
+  $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$. If $|\mathcal{E}(X) \cap T| > 1$,
+  then we must have two different values $x_1, x_2 \in \im X$ such that
+  $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq T$ which means that
+  $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(T) = 0$, and
+  so, again, $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$.
+\end{proof}
+
+\correctness*
+\begin{proof}
+  Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
+  \begin{align*}
+    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) \\
+                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) \\
+                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
+                                                        &= \sum_{(y_i)_{i=1}^n \in \prod_{i=1}^n \im Y_i} \Pr(x, y_1, \dots, y_n) \\
+                                                        &= \Pr(X = x)
+  \end{align*}
+  by the following arguments:
+  \begin{itemize}
+  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
+  \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
+    [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
+    \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
+  \item \cref{lemma:full_distribution};
+  \item marginalisation of a probability distribution.
+  \end{itemize}
+\end{proof}
+% TODO: need to make the proof nicer.
+
 \bibliography{paper}

### 2020-08-05 paper/paper.tex
Proof of theorem 2

@@
 \newtheorem*{remark}{Remark}
+\makeatletter
+\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
+\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
+\newcommand{\pushline}{\Indp}% Indent
+\newcommand{\popline}{\Indm\dosemic}% Undent
+\makeatother
 
@@
 
+% TODO
 Introduce WMC \cite{DBLP:conf/aaai/SangBK05}
@@
 
-% TODO: introduce this section and explain why there's so much about BNs
-A Bayesian network is a directed acyclic graph with random variables as vertices
-that defines a probability distribution over them. The full probability
-distribution can be expressed as the product of the conditional probability
-distributions of all random variables. For discrete Bayesian networks (and we
-only consider discrete networks in this paper), each such distribution can be
-represented by a table known as a conditional probability table (CPT).
-
 \paragraph{WMC for Bayesian networks.} Hitherto, four techniques have been
@@
 functions in Markov decision processes \cite{DBLP:conf/uai/HoeySHB99} and, for
-Bayesian network inference, to represent each CPT as an ADD
-\cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs and arithmetic
-circuits into a  single representation \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs
-are particularly advantageous in this situation because of their ability to
-fully exploit context-specific independence, i.e., observable structure within a
-CPT that is not inherited from the structure of the Bayesian network
-\cite{DBLP:conf/uai/BoutilierFGK96}.
+Bayesian network inference, to represent each conditional probability table
+(CPT) as an ADD \cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs and
+arithmetic circuits into a  single representation
+\cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous in this
+situation because of their ability to fully exploit context-specific
+independence, i.e., observable structure within a CPT that is not inherited from
+the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
 
@@
 represented as Boolean algebras (e.g., $(2^{2^U}, \land, \lor, \neg, \bot,
-\top)$)---see \cref{tbl:notation_example} for examples of how various elements
-can be represented in both notations. Most importantly, note that the word
-\emph{atom} has completely different meanings in logic and in Boolean algebras.
-An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of $U$, whereas
-an atom in a Boolean algebra is (in set-theoretic terms) a singleton set. For
-instance, an atom in $2^{2^U}$ corresponds to a model of $\mathcal{L}$, i.e., an
-element of $2^U$. Unless referring specifically to a logic, we will use the
-algebraic definition of an atom while referring to logical atoms as
-\emph{variables}. In the rest of the paper, for any set $U$, we will use
-set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$,
-except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some
-model $x \in 2^U$.
+\top)$) with a partial order $\le$ that corresponds to set inclusion
+$\subseteq$---see \cref{tbl:notation_example} for examples of how various
+elements can be represented in both notations. Most importantly, note that the
+word \emph{atom} has completely different meanings in logic and in Boolean
+algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of
+$U$, whereas an atom in a Boolean algebra is (in set-theoretic terms) a
+singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
+$\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
+logic, we will use the algebraic definition of an atom while referring to
+logical atoms as \emph{variables}. In the rest of the paper, for any set $U$, we
+will use set-theoretic notation for $2^U$ and Boolean-algebraic notation for
+$2^{2^U}$, except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$
+for some model $x \in 2^U$.
 
@@
 
-We build on the definitions of multiplication and projection in the ADDMC paper
-\cite{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
+We build on the definitions of multiplication and projection by
+\citet{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
 manipulate functions from Boolean algebras to non-negative real numbers. All of
@@
   For any set $U$ and measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$, there
-  exists a set $V \supseteq U$ and a factorable measure $\mu'\colon 2^{2^V} \to
-  \mathbb{R}_{\ge 0}$ such that $\mu = \mu' \circ \iota$, where $\iota\colon
-  2^{2^U} \to 2^{2^V}$ is the inclusion homomorphism.
+  exists a set $V \supseteq U$, a factorable measure $\mu'\colon 2^{2^V} \to
+  \mathbb{R}_{\ge 0}$, and a formula $f \in 2^{2^V}$ such that $\mu(x) = \mu'(x
+  \land f)$ for all formulas $x \in 2^{2^U}$.
 \end{restatable}
@@
 variables to maintain literal independence. In line with the names of previous
-encodings, we shall call this encoding \texttt{db21}. Recall that a Bayesian
-network is a directed acyclic graph with random variables as vertices. Let
-$\mathcal{V}$ denote the set of random variables. For any random variable $X \in
-\mathcal{V}$, let $\im X$ denote its set of possible values and $\mathrm{pa}(X)$
-the set of its parents. The full probability distribution is then equal to
-$\prod_{X \in \mathcal{V}} \Pr(X \mid \mathrm{pa}(X))$. See
-\cref{fig:example_bn} for an example Bayesian network which we will refer to
-throughout this section. For this network, $\mathcal{V} = \{ W, F, T \}$,
-$\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im
-W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
+encodings, we shall call this encoding \texttt{db21}.
+
+A Bayesian network is a directed acyclic graph with random variables as vertices
+that defines a probability distribution over them. Let $\mathcal{V}$ denote this
+set of random variables. For any random variable $X \in \mathcal{V}$, let $\im
+X$ denote its set of values and $\mathrm{pa}(X)$ its set of parents. The
+full probability distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X
+\mid \mathrm{pa}(X))$. For discrete Bayesian networks (and we only consider
+discrete networks in this paper), each factor of this product can be represented
+by a CPT. See \cref{fig:example_bn} for an example Bayesian network which we
+will refer to throughout this section. For this network, $\mathcal{V} = \{ W, F,
+T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W
+\}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
 
@@
 
-For the Bayesian network in \cref{fig:example_bn}, this gives us:
-\begin{align*}
-  \mathcal{E}(W) &= \{ \lambda_{W=1} \}, \\
-  \mathcal{E}(F) &= \{ \lambda_{F=1} \}, \\
-  \mathcal{E}(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
-  \mathcal{E}^*(W) &= \{ \lambda_{W=1} \}, \\
-  \mathcal{E}^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
-  \mathcal{E}^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
-\end{align*}
+For example, in the Bayesian network from \cref{fig:example_bn},
+$\mathcal{E}^*(T) = \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h},
+\lambda_{W=1} \}$.
 
@@
   \KwData{vertices $\mathcal{V}$, probability distribution $\Pr$}
-  \KwResult{a function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
+  \KwResult{$\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
   $\phi \gets 1$\;
@@
     \eIf{$|\im X| = 2$}{
-      \For{$(y_1, \dots, y_n) \in \prod_{i = 1}^n \im Y_i$}{
+      \For{$(y_i)_{i=1}^n \in \prod_{i = 1}^n \im Y_i$}{
         $p_1 \gets \Pr(X = 1 \mid y_1, \dots, y_n)$\;
         $p_0 \gets \Pr(X \ne 1 \mid y_1, \dots, y_n)$\;
-        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_1[\lambda_{X=1}] \cdot
-        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
-        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
+        \nosemic $\mathrm{CPT}_X \gets \mathrm{CPT}_X$\;
+        \pushline $+ p_1[\lambda_{X=1}] \cdot \prod_{i=1}^n
+        [\lambda_{Y_i=y_i}]$\;
+        \dosemic $+ p_0 \overline{[\lambda_{X=1}]} \cdot \prod_{i=1}^n
+        [\lambda_{Y_i=y_i}]$\;
       }
@@
       \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
-      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i =
-          1}^n \im Y_i$}{
+      \For{$x \in \im X$ {\rm \textbf{and}} $(y_i)_{i=1}^n \in \prod_{i = 1}^n
+        \im Y_i$}{
         $p_x \gets \Pr(X = x \mid y_1, \dots, y_n)$\;
-        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_x[\lambda_{X=x}] \cdot
-        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot
-        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
+        \nosemic $\mathrm{CPT}_X \gets \mathrm{CPT}_X$\;
+        \pushline $+ p_x[\lambda_{X=x}] \cdot \prod_{i=1}^n
+        [\lambda_{Y_i=y_i}]$\;
+        \dosemic $+ \overline{[\lambda_{X=x}]} \cdot \prod_{i=1}^n
+        [\lambda_{Y_i=y_i}]$\;
       }
-      $\mathrm{CPT}_X \gets \mathrm{CPT}_X \cdot \left( \sum_{i=1}^m [\lambda_{X
-          = x_i}] \right) \cdot \prod_{i=1}^m \prod_{j=i+1}^m
+      \nosemic $\mathrm{CPT}_X \gets \mathrm{CPT}_X \cdot \left( \sum_{i=1}^m
+        [\lambda_{X = x_i}] \right)$\;
+      \pushline\dosemic $\cdot \prod_{i=1}^m \prod_{j=i+1}^m
       (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})$\;
@@
 \begin{align*}
-  \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
   \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] \\
-                 &+ 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
-                 &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] \\
-                 &+ 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
+                 &+ 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}], \\
   \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \\
                  &\cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \\
-                 &\cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
+                 &\cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot \dots.
 \end{align*}
@@
 % nput command. Each figure will have to be separately compiled to a PDF (maybe
-% create a Makefile for that).
-% TODO: look up how to scale figures
-% TODO: reformat all colours to CMYK from RGB (in R)
+% create a Makefile for that). Look up how to scale figures. Reformat all
+% colours to CMYK from RGB (in R).
 
@@
 \begin{proof}
-  TODO
+  Let $V = U \cup \{ f_m \mid m \in 2^U \}$, and $f = \bigwedge_{m \in 2^U} \{ m
+  \} \leftrightarrow f_m$. We define weight function $\nu\colon 2^V \to
+  \mathbb{R}_{\ge 0}$ as $\nu = \prod_{v \in V} \nu_v$, where $\nu_v(\{v\}) =
+  \mu(\{m\})$ if $v = f_m$ for some $m \in 2^U$ and $\nu_v(x) = 1$ for all other
+  $v \in V$ and $x \in 2^{\{v\}}$. Let $\mu'\colon 2^{2^V} \to \mathbb{R}_{\ge
+    0}$ be the measure induced by $\nu$. It is enough to show that $\mu$ and $x
+  \mapsto \mu'(x \land f)$ agree on the atoms in $2^{2^U}$. For any $\{ a \} \in
+  2^{2^U}$,
+  \begin{align*}
+    \mu'(\{ a \} \land f) &= \sum_{\{ x \} \le \{ a \} \land f} \nu(x) = \nu(a \cup \{ f_a \}) \\
+                          &= \nu_{f_a}(\{ f_a \}) = \mu(\{ a \})
+  \end{align*}
+  as required.
 \end{proof}
@@
   \begin{itemize}
-  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
+  \item the proof of Theorem~1 by \citet{DBLP:conf/aaai/DudekPV20};
   \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot

### 2020-08-05 paper/paper.tex
Improve the introduction

@@
 
-% TODO
-Introduce WMC \cite{DBLP:conf/aaai/SangBK05}
+%Many WMC algorithms have been proposed
+%based primarily either on knowledge compilation
+%\cite{DBLP:conf/ecai/Darwiche04,DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17}
+%or search \cite{DBLP:conf/aaai/SangBK05}.
 
-Over the last fifteen years, WMC has been extended and generalised in many ways,
-e.g., to handle continuous probability distributions
-\cite{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
-\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
-domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, WMC has been generalised
-from weights in the interval $[0, 1]$ or positive real numbers to an arbitrary
-semiring, making it applicable to domains such as parsing, dynamic programming,
-constraint programming, databases, networks, etc.
-\cite{DBLP:journals/japll/KimmigBR17}. It has been applied to Bayesian networks
+\emph{Weighted model counting} (WMC), i.e., an extension of model counting
+($\#\SAT$) that assigns a weight to every model \cite{DBLP:conf/aaai/SangBK05}
+has emerged as the unifying inference mechanism across many (probabilistic)
+domains. It has been applied to Bayesian networks
 \cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906} and probabilistic
@@
 probabilistic programs with discrete probability distributions
-\cite{DBLP:journals/corr/abs-2005-09089}. Many WMC algorithms have been proposed
-based primarily either on knowledge compilation
-\cite{DBLP:conf/ecai/Darwiche04,DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17}
-or search \cite{DBLP:conf/aaai/SangBK05}.
+\cite{DBLP:journals/corr/abs-2005-09089}. Over the last fifteen years, WMC has
+been extended and generalised in many ways, e.g., to handle continuous
+probability distributions \cite{DBLP:conf/ijcai/BellePB15}, first-order
+probabilistic theories
+\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
+domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, the idea of weights in WMC
+has been generalised from non-negative real numbers to an arbitrary semiring,
+making it applicable to domains such as parsing, dynamic programming, constraint
+programming, databases, and networks \cite{DBLP:journals/japll/KimmigBR17}.
 
@@
 weights on literals, i.e., the weight of a model is the product of the weights
-of all literals in it. This severely restricts what probability distributions
-can be represented, and this limitation is usually overcome by increasing the
-size of the problem, i.e., adding more literals.
+of all literals in it. This simplification is motivated by the fact that the
+number of models scales exponentially with the number of atoms, so listing the
+weight of every model is intractable. However, this also severely restricts what
+probability distributions can be represented. A common way to overcome this
+limitation is by adding more literals. While we show that this is always
+possible, the rest of the paper demonstrates that it can be significantly more
+efficient to encode weights in a more flexible way instead.
 
-We show that while this workaround is always possible, it can be significantly
-more efficient to consider \emph{conditional weights} on literals. Similarly to
-conditional probabilities, conditional weights allow us to represent
-probabilities in a manner that is both efficient and interpretable. Not having
-additional variables that are only needed to manipulate the representation into
-a specific format helps with both efficiency and interpretability. Similarly to
-Bayesian networks, the size of the representation scales with independence and
-literal-weight WMC is a special case when everything is independent.
+\Cref{sec:prelims} describes three equivalent perspectives on the subject based
+on logic, set theory, and Boolean algebras. Furthermore, we describe the space
+of functions on Boolean algebras and various operations on those functions. In
+\cref{sec:wmc_as_measure}, WMC is introduced as the problem of computing the
+value of a measure on a Boolean algebra. We show that not all measures can be
+represented using literal-based WMC, but all Boolean algebras can be extended to
+make any measure representable in such a manner.
 
-We demonstrate a specific example of this by presenting a new way to
-encode Bayesian networks into instances of WMC and adapting a WMC algorithm
-ADDMC to run on the new format. ADDMC \cite{DBLP:conf/aaai/DudekPV20} is a
-recently-proposed algorithm for WMC based on manipulating functions on Boolean
-algebras using an efficient representation for such functions known as
-\emph{algebraic decision diagrams} (ADDs)
-\cite{DBLP:journals/fmsd/BaharFGHMPS97}. We show that with a few minor
-modifications the algorithm can be adapted to work on our new WMC format
+In \cref{sec:bns}, we introduce \emph{conditional weights} on literals (in the
+spirit of conditional probabilities) that have literal-based WMC as a special
+case. As a particular example, we show how conditional weights can be used to
+encode Bayesian networks. We prove the correctness of the encoding and show
+how a state-of-the-art WMC solver ADDMC \cite{DBLP:conf/aaai/DudekPV20} can be
+adapted to the new format. ADDMC is a recently-proposed algorithm for WMC based
+on manipulating functions on Boolean algebras using an efficient representation
+for such functions known as \emph{algebraic decision diagrams} (ADDs)
+\cite{DBLP:journals/fmsd/BaharFGHMPS97}.
 
-Showing that the new encoding produces an asymptotically smaller problem (w.r.t.
-the numbers of literals and ADDs) and results in faster inferences.
+Finally, in \cref{sec:experiments}, we show how the new encoding results in
+significantly improved inference speed on most instances, often by one or two
+orders of magnitude. We explain the performance benefits by showing how the new
+encoding has asymptotically fewer variables and ADDs.
 
-% TODO: an overview of all results, with forward references
+%conditional weights allow us to represent
+%probabilities in a manner that is both efficient and interpretable. Not having
+%additional variables that are only needed to manipulate the representation into
+%a specific format helps with both efficiency and interpretability. Similarly to
+%Bayesian networks, the size of the representation scales with independence.
 
@@
 
-\section{WMC as a Measure}
+\section{WMC as a Measure} \label{sec:wmc_as_measure}
 
@@
 \emph{factorable} if there exists a factored weight function $\nu\colon 2^U \to
-\mathbb{R}_{\ge 0}$ that induces $\mu$. In this formulation, the process of
-calculating the value of $\mu_\nu(x)$ for some $x \in 2^{2^U}$ with a given
-definition of $\nu$ is known as WMC.
+\mathbb{R}_{\ge 0}$ that induces $\mu$. In this formulation, WMC corresponds to
+the process of calculating the value of $\mu_\nu(x)$ for some $x \in 2^{2^U}$
+with a given definition of $\nu$.
 
@@
 
-\section{Encoding Bayesian Networks Using Conditional Weights}
+\section{Encoding Bayesian Networks Using Conditional Weights} \label{sec:bns}
 
@@
   \end{align*}
-  by the following arguments:
+  by:
   \begin{itemize}
@@
 \end{proof}
-% TODO: need to make the proof nicer.
 

### 2020-08-07 paper/paper.tex
Conclusions + editing

@@
 \begin{abstract} % TODO
-  AAAI creates proceedings, working notes, and technical reports directly from
-  electronic source furnished by the authors. To ensure that all papers in the
-  publication have a uniform appearance, authors must adhere to the following
-  instructions.
+%1. Introduction. In one sentence, what’s the topic?
+  % WMC
+%2. State the problem you tackle.
+  % Not using additional literals
+%3. Summarize (in one sentence) why nobody else has adequately answered the research question yet.
+  % The dominant definition of WMC severely restricts what measures can be represented
+%4. Explain, in one sentence, how you tackled the research question.
+  % Defining weights akin to conditional probabilities.
+%5. In one sentence, how did you go about doing the research that follows from your big idea.
+  % ADDMC + Bayesian networks
+%6. As a single sentence, what’s the key impact of your research?
+  % Big improvements in inference speed that can be applied to other algorithms
+  % and application domains.
 \end{abstract}
@@
 
-\emph{Weighted model counting} (WMC), i.e., an extension of model counting
-($\#\SAT$) that assigns a weight to every model \cite{DBLP:conf/aaai/SangBK05}
-has emerged as the unifying inference mechanism across many (probabilistic)
-domains. It has been applied to Bayesian networks
+Weighted model counting (WMC), i.e., an extension of model counting ($\#\SAT{}$)
+that assigns a weight to every model \cite{DBLP:conf/aaai/SangBK05} has emerged
+as the unifying inference mechanism across many (probabilistic) domains. It has
+been applied to Bayesian networks
 \cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906} and probabilistic
@@
 limitation is by adding more literals. While we show that this is always
-possible, the rest of the paper demonstrates that it can be significantly more
-efficient to encode weights in a more flexible way instead.
+possible in \cref{sec:wmc_as_measure}, the rest of the paper demonstrates that
+it can be significantly more efficient to encode weights in a more flexible
+format instead.
+
+% TODO: highlight the main strengths
 
@@
 
-Let $\mathcal{L}$ be a propositional logic with atoms $a$ and $b$, and let $U =
-\{ a, b \}$. Then $2^U$, the power set of $U$, is the set of all models of
-$\mathcal{L}$, and $2^{2^U}$ is the set of all formulas. These sets can also be
-represented as Boolean algebras (e.g., $(2^{2^U}, \land, \lor, \neg, \bot,
+In this section, we give a brief introduction to two alternative ways to think
+about logical constructs such as models and formulas. Let $\mathcal{L}$ be a
+propositional logic with atoms $a$ and $b$, and let $U = \{ a, b \}$. Then
+$2^U$, the power set of $U$, is the set of all models of $\mathcal{L}$, and
+$2^{2^U}$ is the set of all formulas. These sets can also be represented as
+Boolean algebras (e.g., using the syntax $(2^{2^U}, \land, \lor, \neg, \bot,
 \top)$) with a partial order $\le$ that corresponds to set inclusion
@@
 $\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
-logic, we will use the algebraic definition of an atom while referring to
-logical atoms as \emph{variables}. In the rest of the paper, for any set $U$, we
-will use set-theoretic notation for $2^U$ and Boolean-algebraic notation for
+logic, we will use the algebraic definition of an atom and refer to logical
+atoms as \emph{variables}. In the rest of the paper, for any set $U$, we will
+use set-theoretic notation for $2^U$ and Boolean-algebraic notation for
 $2^{2^U}$, except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$
@@
 \subsection{The Space of Functions on Boolean Algebras}
-
-We build on the definitions of multiplication and projection by
-\citet{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
-manipulate functions from Boolean algebras to non-negative real numbers. All of
+% TODO: clarify why this is needed
+
+We also consider the space of all functions from any Boolean algebra to
+$\mathbb{R}_{\ge 0}$ together with some operations on those functions. All of
 these operations have efficient implementations in the CUDD
 \cite{somenzi1998cudd} package for manipulating ADDs (among other things) that
-is used by ADDMC {\cite{DBLP:conf/aaai/DudekPV20}.
+is used by ADDMC \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
+multiplication and projection are as defined by \citet{DBLP:conf/aaai/DudekPV20}
+while others are new.
 
@@
 
-\section{WMC as a Measure} \label{sec:wmc_as_measure}
-
-Let $U$ be a set. A \emph{measure} is a function $\mu\colon 2^{2^U} \to
-\mathbb{R}_{\ge 0}$ such that $\mu(\bot) = 0$, and $\mu(a \lor b) = \mu(a) +
-\mu(b)$ for all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$. A \emph{weight
-  function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$. A weight
-function is \emph{factored} if $\nu = \prod_{x \in U} \nu_x$ for some functions
-$\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$. We say that a weight
-function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a measure
-$\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if $\mu_\nu(x) = \sum_{\{u\} \le
-  x} \nu(u)$.
+\section{WMC as a Measure on a Boolean Algebra} \label{sec:wmc_as_measure}
+
+In this section, we introduce an alternative definition of WMC and demonstrate
+how it relates to the standard one. Let $U$ be a set. A \emph{measure} is a
+function $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ such that $\mu(\bot) = 0$,
+and $\mu(a \lor b) = \mu(a) + \mu(b)$ for all $a, b \in 2^{2^U}$ whenever $a
+\land b = \bot$ \cite{gaifman1964concerning,DBLP:books/daglib/0090259}. A
+\emph{weight function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$. A
+weight function is \emph{factored} if $\nu = \prod_{x \in U} \nu_x$ for some
+functions $\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$. We say that
+a weight function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a
+measure $\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if $\mu_\nu(x) =
+\sum_{\{u\} \le x} \nu(u)$.
 
@@
 \cref{sec:prelims} and $w\colon \{ a, b, \neg a, \neg b \} \to \mathbb{R}_{\ge
-  0}$ a \emph{weight function} defined as $w(a) = 0.3$, $w(\neg a) = 0.7$, $w(b)
+  0}$ a weight function defined as $w(a) = 0.3$, $w(\neg a) = 0.7$, $w(b)
 = 0.2$, $w(\neg b) = 0.8$. Furthermore, let $\Delta$ be a theory in
@@
 \end{align*}
+Thus, one can equivalently think of WMC as summing over models of a theory or
+over atoms below an element of a Boolean algebra.
 
@@
 
-WMC with weights defined on literals is only able to capture a subset of all
-possible measures on the Boolean algebra. This can be illustrated with a simple
-example.
+Using this new definition of WMC, we can show that WMC with weights defined on
+literals is only able to capture a subset of all possible measures on a
+Boolean algebra. This can be demonstrated with a simple example.
 
@@
   \mathbb{R}_{\ge 0}$ a measure defined as:\footnote{The value of $\mu$ on any
-    other element of the Boolean algebra can be deduced using the definition.}
+    other element of $2^{2^U}$ can be deduced from the definition of a measure.}
   \begin{align*}
@@
   \end{align*}
-  If $\mu$ could be represented using traditional (factored) WMC, we would have
-  to find two weight functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$
-  and $\nu_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu = \nu_a
-  \cdot \nu_b$ induces $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to satisfy
-  this system of equations:
+  If $\mu$ could be represented using literal-weight (factored) WMC, we would
+  have to find two weight functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge
+    0}$ and $\nu_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu =
+  \nu_a \cdot \nu_b$ induces $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to
+  satisfy this system of equations:
   \begin{align*}
@@
 
-Since many measures of interests may not be factorable, a well-known way to
+Since many measures of interest may not be factorable, a well-known way to
 encode them into instances of WMC is by adding more literals
@@
 restricting oneself to factorable measures and thus having to add extra
-variables to maintain literal independence. In line with the names of previous
-encodings, we shall call this encoding \texttt{db21}.
+variables. In line with the names of the previous encodings, we shall call this
+encoding \texttt{db21}.
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[t]
   \caption{Encoding a Bayesian network}
@@
 \Cref{alg:encoding} produces a function with a Boolean algebra as its domain.
-This function can be represented by an ADD. The core of ADDMC works by taking an
+This function can be represented by an ADD
+\cite{DBLP:journals/fmsd/BaharFGHMPS97}. The core of ADDMC works by taking an
 ADD $\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product of smaller
@@
 any marginal probability of the Bayesian network that was encoded as
-$\phi$.\footnote{It can just as well compute any probability expressed using the
-random variables in $\mathcal{V}$, but we focus mostly on marginal probabilities
-in our experiments.} First, \cref{lemma:cpt} shows that any conditional weight function
-produces the right answer when given an appropriate encoding of
-variable-value assignments for a conditional probability in the Bayesian
-network. Then, \cref{lemma:full_distribution} shows that $\phi$ represents the
-full probability distribution of the Bayesian network, i.e., it gives the right
-probabilities for the right inputs and zero otherwise. We end with
-\cref{thm:correctness} that shows how $\phi$ can be combined with an encoding of
-a single variable-value assignment so that ADDMC would compute its marginal
-probability.
+$\phi$.\footnote{It can just as well compute \emph{any} probability expressed
+  using the random variables in $\mathcal{V}$. We only focus on marginal
+  probabilities for notational simplicity.} We begin with \cref{lemma:cpt} which
+shows that any conditional weight function produces the right answer when given
+a valid encoding of variable-value assignments relevant to the CPT.
 
@@
 \end{restatable}
+
+Now, \cref{lemma:full_distribution} shows that $\phi$ represents the full
+probability distribution of the Bayesian network, i.e., it gives the right
+probabilities for the right inputs and zero otherwise.
 
@@
 \end{restatable}
+
+We end with \cref{thm:correctness} that shows how $\phi$ can be combined with an
+encoding of a single variable-value assignment so that ADDMC would compute its
+marginal probability.
 
@@
 clause, either both weights sum to one, or the second weight is equal to one.
-Finally, note that (without any additional restrictions), the measure induced by
-these weight functions is not probabilistic (i.e., $\mu(\top)$ may not be equal
-to one).
+Finally, note that the measure induced by these weights is not probabilistic
+(i.e., $\mu(\top) \ne 1$) by itself, but it becomes probabilistic when combined
+with the additional clauses that restrict what combinations of indicator
+variables can co-occur.
 
@@
 
-ADDMC constructs the \emph{Gaifman graph} \cite{gaifman1982local} of the input
-CNF formula as an aid for the algorithm's heuristics. This graph has as vertices
-the variables of the formula, and there is an edge between two variables $u$ and
-$v$ if there is a clause in the formula that contains both $u$ and $v$. We
-extend this definition to functions on Boolean algebras, i.e., the factors of
-$\phi$. For any pair of distinct variables $u, v \in U$, we draw an edge between
-them in the Gaifman graph if there is a function $\alpha\colon 2^X \to
-\mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v \in
-X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges between
-all distinct pairs of variables in $\mathcal{E}^*(X)$.
-
-Even though the function $\phi$ produced by \cref{alg:encoding} is constructed
-to have $2^U$ as its domain, sometimes the domain is effectively reduced to
-$2^V$ for some $V \subset U$ by the ADD manipulation algorithms that optimise
-the ADD representation of a function. For a simple example, consider $\alpha:
-2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as $\alpha(\{a\}) = \alpha(\emptyset)
-= 0.5$. Then $\alpha$ can be reduced to $\alpha'\colon 2^{\emptyset} \to
-\mathbb{R}_{\ge 0}$ defined as $\alpha'(\emptyset) = 0.5$. To compensate for
-these reductions, for the original WMC format with a weight function $w\colon U
-\cup \{ \neg u \mid u \in U \} \to \mathbb{R}_{\ge 0}$, ADDMC would multiply its
-computed answer by $\prod_{u \in U \setminus V} w(u) + w(\neg u)$. With the new
-WMC format, we instead multiply the answer by $2^{|U \setminus V|}$. Each
-`excluded' variable $u \in U \setminus V$ satisfies two properties:
-all weights associated with $u$ are equal to $0.5$ (otherwise the corresponding
-CPT would depend on $u$, and $u$ would not be excluded), and all other CPTs are
-independent of $u$ (or they may have a trivial dependence, where the probability
-stays the same if $u$ is replaced with its complement).
-Thus, the CPT that corresponds to $u$ still multiplies every model by $0.5$, but
-the number of models being considered by the ADDMC is halved. To correct for
-this, we multiply the final answer by two for every $u \in U \setminus V$.
+Here we describe two changes to
+ADDMC\footnote{\url{https://github.com/vardigroup/ADDMC}}
+\cite{DBLP:conf/aaai/DudekPV20} needed to adapt it to the new format.
+
+First, ADDMC constructs the \emph{Gaifman graph} \cite{gaifman1982local} of the
+input CNF formula as an aid for the algorithm's heuristics. This graph has as
+vertices the variables of the formula, and there is an edge between two
+variables $u$ and $v$ if there is a clause in the formula that contains both $u$
+and $v$. We extend this definition to functions on Boolean algebras, i.e., the
+factors of $\phi$. For any pair of distinct variables $u, v \in U$, we draw an
+edge between them in the Gaifman graph if there is a function $\alpha\colon 2^X
+\to \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v
+\in X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges
+between all distinct pairs of variables in $\mathcal{E}^*(X)$.
+
+Second, even though the function $\phi$ produced by \cref{alg:encoding} is
+constructed to have $2^U$ as its domain, sometimes the domain is effectively
+reduced to $2^V$ for some $V \subset U$ by the ADD manipulation algorithms that
+optimise the ADD representation of a function. For a simple example, consider
+$\alpha: 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as $\alpha(\{a\}) =
+\alpha(\emptyset) = 0.5$. Then $\alpha$ can be reduced to $\alpha'\colon
+2^{\emptyset} \to \mathbb{R}_{\ge 0}$ defined as $\alpha'(\emptyset) = 0.5$. To
+compensate for these reductions, for the original WMC format with a weight
+function $w\colon U \cup \{ \neg u \mid u \in U \} \to \mathbb{R}_{\ge 0}$,
+ADDMC would multiply its computed answer by $\prod_{u \in U \setminus V} w(u) +
+w(\neg u)$. With the new WMC format, we instead multiply the answer by $2^{|U
+  \setminus V|}$. Each `excluded' variable $u \in U \setminus V$ satisfies two
+properties: all weights associated with $u$ are equal to $0.5$ (otherwise the
+corresponding CPT would depend on $u$, and $u$ would not be excluded), and all
+other CPTs are independent of $u$ (or they may have a trivial dependence, where
+the probability stays the same if $u$ is replaced with its complement). Thus,
+the CPT that corresponds to $u$ still multiplies the weight of every atom in the
+Boolean algebra by $0.5$, but the number of atoms being considered is halved. To
+correct for this, we multiply the final answer by two for every $u \in U
+\setminus V$.
 
@@
 number of CPT rows and so is unlikely to be slower than, e.g., \texttt{cd06},
-which relies on solving $\NP$-complete problems as part of the encoding process
+which relies on solving $\NP{}$-complete problems as part of the encoding process
 \cite{DBLP:conf/sat/ChaviraD06}.
@@
 
-\section{Conclusions and Future Work} % TODO:write
-
-\begin{itemize}
-\item Bayesian networks and ADDMC are only particular examples. This should also
-  work with Cachet \cite{DBLP:conf/sat/SangBBKP04}.
-  \begin{itemize}
-  \item Potential criticism may be that this doesn't allow us to use SAT-based
-    techniques for probabilistic inference. However, they can still be used for
-    a significant part of the encoding.
-    \begin{itemize}
-    \item Zero-probability weights and one-probability weights can be
-      interpreted as logical clauses. This doesn't affect ADDMC but could be
-      useful for other solvers.
-    \end{itemize}
-  \end{itemize}
-\item Extra benefit: one does not need to come up with a way to turn some
-  probability distribution to into a fully independent one.
-\item Important future work: replacing ADDs with
-  AADDs \cite{DBLP:conf/ijcai/SannerM05} is likely to bring performance
-  benefits.
-  Other extensions:
-  \begin{itemize}
-  \item FOADDs can represent first order statements;
-  \item XADDs can replace WMI for continuous variables;
-  \item ADDs with intervals can do approximations.
-  \end{itemize}
-\item Filtering out ADDs that have nothing to do with the answer helps
-  tremendously, but I'm purposefully not doing that.
-\end{itemize}
+\section{Discussion and Conclusions}
+
+WMC was originally motivated by an appeal to the success of \SAT{} solvers in
+efficiently tackling an $\NP{}$-complete problem \cite{DBLP:conf/aaai/SangBK05}.
+ADDMC does not rely on \SAT{}-based algorithmic techniques, and our proposed
+format diverges even more from the DIMACS CNF format for Boolean formulas. To
+what extent are \SAT{}-based methods still applicable? The answer depends
+significantly on the problem domain. For Bayesian networks, the rules describing
+that each random variable can only be associated with exactly one value were
+still encoded as clauses. As has been noted previously
+\cite{DBLP:conf/sat/ChaviraD06}, rows in CPTs with probabilities equal to zero
+or one can be represented as clauses as well. Therefore, our work can be seen as
+proposing a middle ground between $\#\SAT{}$ and probabilistic inference.
+
+While we chose to use ADDMC \cite{DBLP:conf/aaai/DudekPV20} as the WMC algorithm
+and Bayesian networks as a canonical example of a probabilistic inference task,
+these are only examples meant to illustrate the broader idea that choosing a
+more expressive representation of weights can outperform increasing the size of
+the problem to keep the weights simple. The same idea can be adapted to
+search-based solvers such as Cachet \cite{DBLP:conf/sat/SangBBKP04} as well as
+to other inference problem domains such as probabilistic programs.
+
+% TODO: a few optimistic parting words
+
+%An additional benefit of conditional weights is that a more expressive format
+%makes it easier to invent new WMC encodings.
+%Filtering out ADDs that have nothing to do with the answer helps
+%  tremendously, but I'm purposefully not doing that.
 

### 2020-08-07 paper/paper.tex
The abstract + grammar

@@
 
-\begin{abstract} % TODO
-%1. Introduction. In one sentence, what’s the topic?
-  % WMC
-%2. State the problem you tackle.
-  % Not using additional literals
-%3. Summarize (in one sentence) why nobody else has adequately answered the research question yet.
-  % The dominant definition of WMC severely restricts what measures can be represented
-%4. Explain, in one sentence, how you tackled the research question.
-  % Defining weights akin to conditional probabilities.
-%5. In one sentence, how did you go about doing the research that follows from your big idea.
-  % ADDMC + Bayesian networks
-%6. As a single sentence, what’s the key impact of your research?
-  % Big improvements in inference speed that can be applied to other algorithms
-  % and application domains.
+\begin{abstract}
+  Weighted model counting (WMC) has emerged as the unifying inference mechanism
+  across many (probabilistic) domains. Encoding an inference problem as an
+  instance of WMC typically necessitates adding extra literals and clauses. This
+  is partly so because the predominant definition of WMC assigns weights to
+  models based on weights on literals, and this severely restricts what
+  probability distributions can be represented. We propose a way to encode
+  conditional weights on literals analogously to conditional probabilities. This
+  representation can be as succinct as standard WMC with weights on literals but
+  can also expand as needed to represent probability distributions with less
+  structure. To demonstrate the performance benefits of conditional weights over
+  the addition of extra literals, we develop a new WMC encoding for Bayesian
+  networks and adapt a state-of-the-art WMC algorithm ADDMC to the new format.
+  Our experiments show that the new encoding results in significantly faster
+  inference on most benchmark instances. Furthermore, the same idea can
+  be adapted to other WMC algorithms and other problem domains.
 \end{abstract}
@@
 on logic, set theory, and Boolean algebras. Furthermore, we describe the space
-of functions on Boolean algebras and various operations on those functions. In
-\cref{sec:wmc_as_measure}, WMC is introduced as the problem of computing the
-value of a measure on a Boolean algebra. We show that not all measures can be
+of functions on Boolean algebras and various operations on those functions.
+\Cref{sec:wmc_as_measure} introduces WMC as the problem of computing the value
+of a measure on a Boolean algebra. We show that not all measures can be
 represented using literal-based WMC, but all Boolean algebras can be extended to
@@
 Finally, in \cref{sec:experiments}, we show how the new encoding results in
-significantly improved inference speed on most instances, often by one or two
-orders of magnitude. We explain the performance benefits by showing how the new
-encoding has asymptotically fewer variables and ADDs.
+significantly improved inference speed on most benchmark instances, often by one
+or two orders of magnitude. We explain the performance benefits by showing how
+the new encoding has asymptotically fewer variables and ADDs.
 
@@
 situation because of their ability to fully exploit context-specific
-independence, i.e., observable structure within a CPT that is not inherited from
-the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
+independence, i.e., the observable structure within a CPT that is not inherited
+from the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
 
@@
 \subsection{The Space of Functions on Boolean Algebras}
-% TODO: clarify why this is needed
+% TODO: clarify why this is needed (and run a grammar check on this section)
 
@@
 
-Note that in this case we chose to interpret $\nu_b$ as $\Pr(b \mid a)$
+Note that in this case, we chose to interpret $\nu_b$ as $\Pr(b \mid a)$
 while---with a different definition of $\nu_b$ that represents the joint
@@
 the CPT that corresponds to $u$ still multiplies the weight of every atom in the
-Boolean algebra by $0.5$, but the number of atoms being considered is halved. To
-correct for this, we multiply the final answer by two for every $u \in U
+Boolean algebra by $0.5$, but the number of atoms under consideration is halved.
+To correct for this, we multiply the final answer by two for every $u \in U
 \setminus V$.
@@
 
+% TODO: write. then run through a grammar checker.
 \paragraph{Observations.}
@@
 instance \cite{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings, each
-weight is also a factor, but that has no effect on the asymptotic bounds in the
+weight is also a factor, but that does not affect the asymptotic bounds in the
 table.

### 2020-08-08 paper/paper.tex
A bug fix related to encodings

@@
 \subsection{The Space of Functions on Boolean Algebras}
-% TODO: clarify why this is needed (and run a grammar check on this section)
 
 We also consider the space of all functions from any Boolean algebra to
-$\mathbb{R}_{\ge 0}$ together with some operations on those functions. All of
-these operations have efficient implementations in the CUDD
-\cite{somenzi1998cudd} package for manipulating ADDs (among other things) that
-is used by ADDMC \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
-multiplication and projection are as defined by \citet{DBLP:conf/aaai/DudekPV20}
-while others are new.
+$\mathbb{R}_{\ge 0}$ together with some operations on those functions. They will
+be instrumental in defining WMC as a measure in \cref{sec:wmc_as_measure} and
+can be efficiently represented using ADDs. Furthermore, all of the operations
+are supported by the CUDD \cite{somenzi1998cudd} package that is used by ADDMC
+for ADD manipulation \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
+multiplication and projection are as defined by
+\citet{DBLP:conf/aaai/DudekPV20}, while others are new.
 
@@
   Let $U = \{a, b\}$ be a set of atoms and $\mu\colon 2^{2^U} \to
-  \mathbb{R}_{\ge 0}$ a measure defined as:\footnote{The value of $\mu$ on any
-    other element of $2^{2^U}$ can be deduced from the definition of a measure.}
-  \begin{align*}
-    \mu(a \land b) &= 0.72, \\
-    \mu(a \land \neg b) &= 0.18, \\
-    \mu(\neg a \land b) &= 0.07, \\
-    \mu(\neg a \land \neg b) &= 0.03.
-  \end{align*}
-  If $\mu$ could be represented using literal-weight (factored) WMC, we would
-  have to find two weight functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge
-    0}$ and $\nu_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu =
-  \nu_a \cdot \nu_b$ induces $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to
-  satisfy this system of equations:
+  \mathbb{R}_{\ge 0}$ a measure defined as $\mu(a \land b) = 0.72$, $\mu(a \land
+  \neg b) = 0.18$, $\mu(\neg a \land b) = 0.07$, $\mu(\neg a \land \neg b) =
+  0.03$.\footnote{The value of $\mu$ on any other element of $2^{2^U}$ can be
+    deduced from the definition of a measure.} If $\mu$ could be represented
+  using literal-weight (factored) WMC, we would have to find two weight
+  functions $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ and $\nu_b\colon
+  2^{\{b\}} \to \mathbb{R}_{\ge 0}$ such that $\nu = \nu_a \cdot \nu_b$ induces
+  $\mu$, i.e., $\nu_a$ and $\nu_b$ would have to satisfy this system of
+  equations:
   \begin{align*}
@@
 
-% TODO: To follow formatting requirements, I will need to remove the
-% nput command. Each figure will have to be separately compiled to a PDF (maybe
-% create a Makefile for that). Look up how to scale figures. Reformat all
-% colours to CMYK from RGB (in R).
+% TODO: (needed to follow formatting requirements)
+% 1. Remove the \input command.
+% 2. R should compile the tex files to be standalone.
+% 3. Edit the tex files to replace RGB colours with CMYK.
+% 4. Compile the tex files to PDFs.
+% 5. Include the PDFs (look up how to do that in the formatting guidelines).
 
@@
 
-\section{Discussion and Conclusions}
+\section{Discussion and Conclusion}
 
@@
 to other inference problem domains such as probabilistic programs.
-
-% TODO: a few optimistic parting words
 

### 2020-08-12 paper/paper.tex
Revision based on feedback

@@
   models based on weights on literals, and this severely restricts what
-  probability distributions can be represented. We propose a way to encode
-  conditional weights on literals analogously to conditional probabilities. This
-  representation can be as succinct as standard WMC with weights on literals but
-  can also expand as needed to represent probability distributions with less
-  structure. To demonstrate the performance benefits of conditional weights over
-  the addition of extra literals, we develop a new WMC encoding for Bayesian
-  networks and adapt a state-of-the-art WMC algorithm ADDMC to the new format.
-  Our experiments show that the new encoding results in significantly faster
-  inference on most benchmark instances. Furthermore, the same idea can
-  be adapted to other WMC algorithms and other problem domains.
+  probability distributions can be represented. We develop a measure-theoretic
+  perspective on WMC and propose a way to encode conditional weights on literals
+  analogously to conditional probabilities. This representation can be as
+  succinct as standard WMC with weights on literals but can also expand as
+  needed to represent probability distributions with less structure. To
+  demonstrate the performance benefits of conditional weights over the addition
+  of extra literals, we develop a new WMC encoding for Bayesian networks and
+  adapt a state-of-the-art WMC algorithm ADDMC to the new format. Our
+  experiments show that the new encoding results in significantly faster
+  inference on most benchmark instances. Furthermore, the same idea can be
+  adapted to other WMC algorithms and other problem domains.
 \end{abstract}
@@
 
-%Many WMC algorithms have been proposed
-%based primarily either on knowledge compilation
-%\cite{DBLP:conf/ecai/Darwiche04,DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17}
-%or search \cite{DBLP:conf/aaai/SangBK05}.
+% TODO: Feedback: our empirical evaluations show a x% improvement
 
 Weighted model counting (WMC), i.e., an extension of model counting ($\#\SAT{}$)
-that assigns a weight to every model \cite{DBLP:conf/aaai/SangBK05} has emerged
-as the unifying inference mechanism across many (probabilistic) domains. It has
-been applied to Bayesian networks
-\cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906} and probabilistic
-graphical models more generally \cite{DBLP:conf/ecsqaru/ChoiKD13}, probabilistic
-logic programming languages \cite{DBLP:journals/tplp/FierensBRSGTJR15} and
-probabilistic programs with discrete probability distributions
-\cite{DBLP:journals/corr/abs-2005-09089}. Over the last fifteen years, WMC has
-been extended and generalised in many ways, e.g., to handle continuous
-probability distributions \cite{DBLP:conf/ijcai/BellePB15}, first-order
-probabilistic theories
+that assigns a weight to every model \cite{DBLP:conf/aaai/SangBK05}, has emerged
+as one of the most dominant and competitive approaches for handling inference
+tasks in a wide range of formalisms including Bayesian networks
+\cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906}, probabilistic
+graphical models more generally \cite{DBLP:conf/ecsqaru/ChoiKD13}, and
+probabilistic programs
+\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089}.
+Over the last fifteen years, WMC has been extended and generalised in many ways,
+e.g., to handle continuous probability distributions
+\cite{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
 \cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
-domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, the idea of weights in WMC
-has been generalised from non-negative real numbers to an arbitrary semiring,
-making it applicable to domains such as parsing, dynamic programming, constraint
-programming, databases, and networks \cite{DBLP:journals/japll/KimmigBR17}.
+domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, by generalising the notion
+of weights to an arbitrary semiring, a range of other problems are also captured
+\cite{DBLP:journals/japll/KimmigBR17}. Exact WMC solvers typically rely on
+either knowledge compilation
+\cite{DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17} or exhaustive DPLL
+search \cite{DBLP:conf/aaai/SangBK05}, whereas approximate solvers work by
+sampling \cite{DBLP:conf/aaai/ChakrabortyFMSV14} and performing local search
+\cite{DBLP:conf/sat/WeiS05}.
 
@@
 
-% TODO: highlight the main strengths
-
 \Cref{sec:prelims} describes three equivalent perspectives on the subject based
@@
 the new encoding has asymptotically fewer variables and ADDs.
+
+%making it applicable to domains such as parsing, dynamic programming, constraint
+%programming, databases, and networks.
 
@@
 
-\paragraph{ADDs and their use in probabilistic inference.} ADDs provide an
-efficient way to manipulate functions from a Boolean algebra to any algebraic
-structure (most commonly the real numbers)
-\cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been used to represent value
-functions in Markov decision processes \cite{DBLP:conf/uai/HoeySHB99} and, for
-Bayesian network inference, to represent each conditional probability table
-(CPT) as an ADD \cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs and
-arithmetic circuits into a  single representation
-\cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous in this
-situation because of their ability to fully exploit context-specific
+\paragraph{ADDs and their use in inference.} ADDs provide an efficient way to
+manipulate functions from a Boolean algebra to any algebraic structure (most
+commonly real numbers) \cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been
+used to represent value functions in Markov decision processes (MDPs)
+\cite{DBLP:conf/uai/HoeySHB99} and extended to handle first-order MDPs
+\cite{DBLP:journals/ai/SannerB09} and discrete and continuous state MDPs
+\cite{DBLP:conf/uai/SannerDB11}. The latter extension has also been used for
+weighted model integration---an extension of WMC that can handle continuous
+variables \cite{DBLP:conf/ijcai/KolbMSBK18}. For Bayesian networks, ADDS have
+been used to represent each conditional probability table (CPT) as an ADD
+\cite{DBLP:conf/icml/ZhaoMP15} and as a combination of ADDs and arithmetic
+circuits \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous
+in this situation because of their ability to fully exploit context-specific
 independence, i.e., the observable structure within a CPT that is not inherited
@@
 increased efficiency and decreased memory usage \cite{DBLP:conf/aaai/DudekPV20}.
+We can easily generalise this example further.
+
+\begin{theorem}
+  For any set $U$ such that $|U| \ge 2$, there exists a non-factorable measure
+  $2^{2^{U}} \to \mathbb{R}_{\ge 0}$.
+\end{theorem}
 
@@
 encode them into instances of WMC is by adding more literals
-\cite{DBLP:journals/ai/ChaviraD08}. We can indeed show that this is always
-possible, however, as ensuing sections will demonstrate, it often makes the
-inference task much harder.
+\cite{DBLP:journals/ai/ChaviraD08}. We can use the measure-theoretic perspective
+on WMC to show that this is always possible, however, as ensuing sections will
+demonstrate, it often makes the inference task much harder in
+practice.\footnote{The proofs of this and other theoretical results can be found
+in the technical appendix.}
 
@@
 restricting oneself to factorable measures and thus having to add extra
-variables. In line with the names of the previous encodings, we shall call this
-encoding \texttt{db21}.
+variables. We will refer to it as \texttt{cw}.
 
@@
 full probability distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X
-\mid \mathrm{pa}(X))$. For discrete Bayesian networks (and we only consider
-discrete networks in this paper), each factor of this product can be represented
-by a CPT. See \cref{fig:example_bn} for an example Bayesian network which we
-will refer to throughout this section. For this network, $\mathcal{V} = \{ W, F,
-T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W
-\}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
+\mid \mathrm{pa}(X))$ \cite{DBLP:books/daglib/0023820}. For discrete Bayesian
+networks (and we only consider discrete networks in this paper), each factor of
+this product can be represented by a CPT. See \cref{fig:example_bn} for an
+example Bayesian network that we will refer to throughout this section. For
+this network, $\mathcal{V} = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
+$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
+$\im T = \{ l, m, h \}$.
 
@@
 functions, one for each row of the CPT. If $X$ has more than two values, we also
-multiply $\mathrm{CPT}_X$ by some `clause' functions that restrict the value of
+multiply $\mathrm{CPT}_X$ by `clause' functions that restrict the value of
 $\phi(T)$ to zero whenever $|\mathcal{E}(X) \cap T| \ne 1$. For the Bayesian
@@
 any marginal probability of the Bayesian network that was encoded as
-$\phi$.\footnote{It can just as well compute \emph{any} probability expressed
-  using the random variables in $\mathcal{V}$. We only focus on marginal
-  probabilities for notational simplicity.} We begin with \cref{lemma:cpt} which
-shows that any conditional weight function produces the right answer when given
-a valid encoding of variable-value assignments relevant to the CPT.
+$\phi$.\footnote{Note that it can just as well compute \emph{any} probability
+  expressed using the random variables in $\mathcal{V}$.} We begin with
+\cref{lemma:cpt} which shows that any conditional weight function produces the
+right answer when given a valid encoding of variable-value assignments relevant
+to the CPT.
 
@@
 
-For all encodings other than \texttt{db21}, we use their implementation in
+For all encodings other than \texttt{cw}, we use their implementation in
 Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
@@
 While encoding time itself was not measured because of different languages of
-implementation, it is worth noting that \texttt{db21} is linear in the total
+implementation, it is worth noting that \texttt{cw} is linear in the total
 number of CPT rows and so is unlikely to be slower than, e.g., \texttt{cd06},
@@
     \texttt{cd06} & 0 & 1 & 351 \\
+    \texttt{cw} & 228 & 871 & 901 \\
     \texttt{d02} & 41 & 99 & 726 \\
-    \texttt{db21} & 228 & 871 & 901 \\
     \texttt{sbk05} & 6 & 36 & 687 \\
@@
   \input{scatter.tex}%
-  \caption{ADDMC inference time using \texttt{db21} compared to \texttt{d02}
+  \caption{ADDMC inference time using \texttt{cw} compared to \texttt{d02}
     (left) and \texttt{sbk05} (right) for each instance in all data sets.}
@@
   query.
-\item However, \texttt{db21} struggles with instances from Mastermind and
+\item However, \texttt{cw} struggles with instances from Mastermind and
   Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
@@
   heuristics used by ADDMC or because these instances allow for significant
-  simplifications that are exploited by $\mathtt{d02}$ but not
-  $\mathtt{db21}$.
-\item An observation from the cumulative plot: \texttt{db21} solves the same
+  simplifications that are exploited by \texttt{d02} but not \texttt{cw}.
+\item An observation from the cumulative plot: \texttt{cw} solves the same
   number of instances in \SI{6.374}{\second} as \texttt{d02} does in
@@
     \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(nv^{d+1})$ \\
+    \texttt{cw} & $\mathcal{O}(nv)$ & $\mathcal{O}(nv^2)$ \\
     \texttt{d02} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(ndv^{d+1})$ \\
-    \texttt{db21} & $\mathcal{O}(nv)$ & $\mathcal{O}(nv^2)$ \\
     \bottomrule
@@
 \max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
-\Cref{tbl:asymptotes} shows how \texttt{db21} has both fewer variables and fewer
+\Cref{tbl:asymptotes} shows how \texttt{cw} has both fewer variables and fewer
 ADDs than any other encoding. However, note that these are upper bounds and most
-encodings (including \texttt{db21}) can be smaller in certain situations (e.g.,
+encodings (including \texttt{cw}) can be smaller in certain situations (e.g.,
 with binary random variables or when a CPT has repeating probabilities). We

### 2020-08-12 analyse.R

@@ -8,12 +8,13 @@ require(ggpubr)
 
 TIMEOUT <- 1000
 df0 <- read.csv("results.csv", header = TRUE, sep = ",")
+df0$encoding[df0$encoding == "db21"] <- "cw"
 df0$time[df0$time > TIMEOUT] <- TIMEOUT
 df0$time[is.na(df0$time)] <- TIMEOUT
 df0$memory[is.na(df0$memory)] <- max(df0$memory, na.rm = TRUE)
 df <- dcast(data = df0, formula = instance + dataset ~ encoding, fun.aggregate = sum, value.var = c("answer", "time", "memory"))
 df$time_min <- as.numeric(apply(df, 1, function (row) min(row["time_cd05"], row["time_cd06"],
-                                                          row["time_d02"], row["time_db21"], row["time_sbk05"])))
+                                                          row["time_d02"], row["time_cw"], row["time_sbk05"])))
 
 df$major.dataset <- "Non-binary"
 df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
@@ -28,58 +29,58 @@ df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
 # ============ Numerical investigations ================
 
 # Where answers don't match
-interesting <- df[abs(df$answer_db21 - df$answer_sbk05) > 0.01,]
+interesting <- df[abs(df$answer_cw - df$answer_sbk05) > 0.01,]
 
 nrow(df)
 
 # Unique
-sum(is.na(df$answer_db21) & !is.na(df$answer_cd05) & is.na(df$answer_cd06) &
+sum(is.na(df$answer_cw) & !is.na(df$answer_cd05) & is.na(df$answer_cd06) &
       is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cd05
-sum(is.na(df$answer_db21) & is.na(df$answer_cd05) & !is.na(df$answer_cd06) &
+sum(is.na(df$answer_cw) & is.na(df$answer_cd05) & !is.na(df$answer_cd06) &
       is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cd06
-sum(is.na(df$answer_db21) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
+sum(is.na(df$answer_cw) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
[…]

### 2020-08-12 analyse.R
A bit more experimental data

@@ -20,8 +20,8 @@ df$major.dataset <- "Non-binary"
 df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
 df$major.dataset[grepl("Grid", df$instance, fixed = TRUE)] <- "Grid"
 df$major.dataset[grepl("mastermind", df$instance, fixed = TRUE)] <- "Mastermind"
-df$major.dataset[grepl("blockmap", df$instance, fixed = TRUE)] <- "Random blocks"
-df$major.dataset[grepl("fs-", df$instance, fixed = TRUE)] <- "Friends and smokers"
+df$major.dataset[grepl("blockmap", df$instance, fixed = TRUE)] <- "Random Blocks"
+df$major.dataset[grepl("fs-", df$instance, fixed = TRUE)] <- "Friends and Smokers"
 df$major.dataset[grepl("Plan_Recognition", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("students", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
@@ -92,7 +92,7 @@ ggarrange(p1, p2, ncol = 2, common.legend = TRUE, legend = "right")
 dev.off()
 
 # Scatter plot: for a specific data set
-ggplot(df[df$dataset == "2004-PGM"], aes(x = time_cw, y = time_sbk05)) +
+ggplot(df[df$dataset == "2005-PGM"], aes(x = time_cw, y = time_sbk05)) +
   geom_point() +
   geom_abline(slope = 1, intercept = 0) +
   xlim(0, TIMEOUT) +

### 2020-08-12 parse.py

@@ -24,25 +24,25 @@ def parse_dir(directory, additional_data = {}):
     return data
 
 data = []
-data += parse_dir('results/Grid/Ratio_50/', {'dataset': 'Grid-50'})
-data += parse_dir('results/Grid/Ratio_75/', {'dataset': 'Grid-75'})
-data += parse_dir('results/Grid/Ratio_90/', {'dataset': 'Grid-90'})
-data += parse_dir('results/DQMR/qmr-100/', {'dataset': 'DQMR-100'})
-data += parse_dir('results/DQMR/qmr-50/', {'dataset': 'DQMR-50'})
-data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
-data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
-data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
-data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
-data += parse_dir('results/2004-pgm/', {'dataset': '2004-PGM'})
+#data += parse_dir('results/Grid/Ratio_50/', {'dataset': 'Grid-50'})
+#data += parse_dir('results/Grid/Ratio_75/', {'dataset': 'Grid-75'})
+#data += parse_dir('results/Grid/Ratio_90/', {'dataset': 'Grid-90'})
+#data += parse_dir('results/DQMR/qmr-100/', {'dataset': 'DQMR-100'})
+#data += parse_dir('results/DQMR/qmr-50/', {'dataset': 'DQMR-50'})
+#data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
+#data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
+#data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
+#data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
+#data += parse_dir('results/2004-pgm/', {'dataset': '2004-PGM'})
 data += parse_dir('results/2005-ijcai/', {'dataset': '2005-IJCAI'})
-data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
+#data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
 
 fieldnames = set()
 for d in data:
[…]

### 2020-08-16 paper/paper.tex
A bit more experimental data
New data

@@
 encodings for Bayesian networks when run with ADDMC. The experiments were run on
-Intel Xeon Gold 6138 processor with an \SI{8}{\giga\byte} memory limit.
+Intel Xeon Gold 6138 and Intel Xeon E5-2630 processors\footnote{Each instance is
+run on the same processor for all encodings.} with an \SI{8}{\gibi\byte} memory
+limit.
 
@@
 \item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
-\item Friends and Smokers,
 \item Mastermind, and
@@
 \item remaining binary Bayesian networks that include Plan Recognition
-  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
+  \cite{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
   \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
@@
 \end{itemize*}
+% TODO: make sure to talk about the table (and mention that cd06 has its niche)
 
@@
 % 5. Include the PDFs (look up how to do that in the formatting guidelines).
+% 6. make sure that there are no duplicates in the bib files (look at LaTex output)
+
+% TODO: check if the total checks out
 
@@
   \centering
-  \caption{The numbers of instances solved by ADDMC with each encoding
-    (uniquely, faster than with others, and in total) under the described time
-    and memory constraints (out of 1216 instances)}%
+  \caption{The numbers of instances (out of 1451) solved by ADDMC with each
+    encoding (uniquely, faster than with others, and in total) under the
+    described time and memory constraints}%
   \begin{tabular}{lrrr}
@@
     \midrule
-    \texttt{cd05} & 2 & 3 & 372 \\
-    \texttt{cd06} & 0 & 1 & 351 \\
-    \texttt{cw} & 228 & 871 & 901 \\
-    \texttt{d02} & 41 & 99 & 726 \\
-    \texttt{sbk05} & 6 & 36 & 687 \\
+    \texttt{cd05} & 2 & 76 & 380 \\
+    \texttt{cd06} & 0 & 214 & 363 \\
+    \texttt{cw} & 234 & 633 & 965 \\
+    \texttt{d02} & 40 & 58 & 782 \\
+    \texttt{sbk05} & 12 & 16 & 750 \\
     \bottomrule
@@
 \item An observation from the cumulative plot: \texttt{cw} solves the same
-  number of instances in \SI{6.374}{\second} as \texttt{d02} does in
+  number of instances in \SI{8.144}{\second} as \texttt{d02} does in
   \SI{1000}{\second}.

### 2020-08-16 analyse.R

@@ -21,7 +21,7 @@ df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
 df$major.dataset[grepl("Grid", df$instance, fixed = TRUE)] <- "Grid"
 df$major.dataset[grepl("mastermind", df$instance, fixed = TRUE)] <- "Mastermind"
 df$major.dataset[grepl("blockmap", df$instance, fixed = TRUE)] <- "Random Blocks"
-df$major.dataset[grepl("fs-", df$instance, fixed = TRUE)] <- "Friends and Smokers"
+df$major.dataset[grepl("fs-", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("Plan_Recognition", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("students", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
@@ -38,25 +38,25 @@ sum(is.na(df$answer_cw) & !is.na(df$answer_cd05) & is.na(df$answer_cd06) &
       is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cd05
 sum(is.na(df$answer_cw) & is.na(df$answer_cd05) & !is.na(df$answer_cd06) &
       is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cd06
-sum(is.na(df$answer_cw) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
-      !is.na(df$answer_d02) & is.na(df$answer_sbk05)) # d02
 sum(!is.na(df$answer_cw) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
       is.na(df$answer_d02) & is.na(df$answer_sbk05)) # cw
+sum(is.na(df$answer_cw) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
+      !is.na(df$answer_d02) & is.na(df$answer_sbk05)) # d02
 sum(is.na(df$answer_cw) & is.na(df$answer_cd05) & is.na(df$answer_cd06) &
       is.na(df$answer_d02) & !is.na(df$answer_sbk05)) # sbk05
 
 # Fastest
 sum(!is.na(df$answer_cd05) & abs(df$time_cd05 - df$time_min) < 1e-5)
[…]

### 2020-08-16 parse.py

@@ -31,11 +31,11 @@ data = []
 #data += parse_dir('results/DQMR/qmr-50/', {'dataset': 'DQMR-50'})
 #data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
 #data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
-#data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
-#data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
+data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
+data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
 #data += parse_dir('results/2004-pgm/', {'dataset': '2004-PGM'})
 data += parse_dir('results/2005-ijcai/', {'dataset': '2005-IJCAI'})
-#data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
+data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
 
 fieldnames = set()
 for d in data:

### 2020-08-17 paper/paper.tex
Fix a bug in parsing experimental data

@@
   \centering
-  \caption{The numbers of instances (out of 1451) solved by ADDMC with each
+  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
     encoding (uniquely, faster than with others, and in total) under the
@@
     \midrule
-    \texttt{cd05} & 2 & 76 & 380 \\
-    \texttt{cd06} & 0 & 214 & 363 \\
-    \texttt{cw} & 234 & 633 & 965 \\
-    \texttt{d02} & 40 & 58 & 782 \\
-    \texttt{sbk05} & 12 & 16 & 750 \\
+    \texttt{cd05} & 2 & 3 & 380 \\
+    \texttt{cd06} & 0 & 0 & 363 \\
+    \texttt{cw} & 234 & 935 & 980 \\
+    \texttt{d02} & 40 & 111 & 797 \\
+    \texttt{sbk05} & 12 & 44 & 765 \\
     \bottomrule
@@
 \end{table}
+% TODO: another observation: cw was the fastest in 935 out of the 980 instances
+% that it solved (95.4%)
 

### 2020-08-17 parse.py

@@ -18,7 +18,9 @@ def parse_dir(directory, additional_data = {}):
     for filename in os.listdir(directory):
         d = parse(directory + filename)
         d.update(additional_data)
-        d['instance'] = directory + filename.split('.')[0]
+        parts = filename.split('.')
+        instance = parts[0] if parts[1] in ['inst', 'cd05', 'cd06', 'sbk05', 'd02', 'db21'] else parts[0] + '.' + parts[1]
+        d['instance'] = directory + instance
         d['encoding'] = filename[filename.rindex('.')+1:]
         data.append(d)
     return data

### 2020-08-19 paper/paper.tex
Describe experimental results

@@
 
-\section{Related Work}
+\section{Related Work} \label{sec:related}
 
@@
 encodings for Bayesian networks when run with ADDMC. The experiments were run on
-Intel Xeon Gold 6138 and Intel Xeon E5-2630 processors\footnote{Each instance is
-run on the same processor for all encodings.} with an \SI{8}{\gibi\byte} memory
-limit.
+servers with Intel Xeon Gold 6138 and Intel Xeon E5-2630
+processors\footnote{Each instance is run on the same processor for all
+  encodings.} with an \SI{8}{\gibi\byte} memory limit and a \SI{1000}{\second}
+timeout.
 
@@
 evidence. Otherwise, let $X$ denote the last-mentioned vertex in the Bayesian
-network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
-probability of $X = \mathsf{true}$. Otherwise, we pick the value of $X$ which is
-listed first and calculate its marginal probability.
+network. If $\mathsf{true} \in \im X$, then we compute the marginal probability
+of $X = \mathsf{true}$. Otherwise, we pick the value of $X$ which is listed
+first and calculate its marginal probability.
 
@@
 
-\paragraph{Data.} For experimental data, we use the Bayesian networks available
-with Ace and
+For experimental data, we use the Bayesian networks available with Ace and
 Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
@@
 \end{itemize*}
-% TODO: make sure to talk about the table (and mention that cd06 has its niche)
 
@@
     encoding}
+  \label{fig:cumulative}
 \end{figure}
@@
 
-% TODO: check if the total checks out
-
 \begin{table}
@@
     encoding (uniquely, faster than with others, and in total) under the
-    described time and memory constraints}%
+    described constraints}%
   \begin{tabular}{lrrr}
@@
   \end{tabular}
+  \label{tbl:tallies}
 \end{table}
-% TODO: another observation: cw was the fastest in 935 out of the 980 instances
-% that it solved (95.4%)
 
@@
     (left) and \texttt{sbk05} (right) for each instance in all data sets.}
+  \label{fig:scatter}
 \end{figure*}
 
-% TODO: write. then run through a grammar checker.
-\paragraph{Observations.}
-\begin{itemize}
-\item The order of the encodings from best to worst is exactly the opposite of
-  that in the previous literature.
-\item Our encoding is particularly promising on instances of Grid networks.
-  They are set up so that the entire Bayesian network is relevant to the
-  query.
-\item However, \texttt{cw} struggles with instances from Mastermind and
-  Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
-  is so either because the particular structure of these problems confuse the
-  heuristics used by ADDMC or because these instances allow for significant
-  simplifications that are exploited by \texttt{d02} but not \texttt{cw}.
-\item An observation from the cumulative plot: \texttt{cw} solves the same
-  number of instances in \SI{8.144}{\second} as \texttt{d02} does in
-  \SI{1000}{\second}.
-\end{itemize}
+According to the cumulative plot in \cref{fig:cumulative}, \texttt{cw} is
+consistently able to solve more instances with any given time limit than any
+other encoding, while the order of the remaining encodings from best to worst is
+exactly the opposite of that in previous literature (cf. \cref{sec:related}).
+Specifically, \texttt{cw} solves the same number of instances in
+\SI{8.144}{\second} as \texttt{d02} does in \SI{1000}{\second}, which is the
+second-best encoding in our experiments. Furthermore, \cref{tbl:tallies} shows
+that \texttt{cw} was the fastest in 935 out of the 980 (i.e.,
+\SI{95.4}{\percent}) instances that it managed to solve. Finally, according to
+the scatter plots in \cref{fig:scatter}, \texttt{cw} is particularly promising
+on Grid networks while losing to \texttt{d02} on some instances of the
+Mastermind data set. We conjecture that this is so either because the particular
+structure of the problem confuses the heuristics used by ADDMC or because these
+instances allow for significant simplifications that are exploited by
+\texttt{d02} but not \texttt{cw}.
 
@@
 number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
-|\mathrm{pa}(X)|$ the maximum in-degree (i.e., number of parents), and $v =
+|\mathrm{pa}(X)|$ the maximum in-degree (i.e., the number of parents), and $v =
 \max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
-\Cref{tbl:asymptotes} shows how \texttt{cw} has both fewer variables and fewer
+\Cref{tbl:asymptotes} shows how \texttt{cw} has fewer variables and fewer
 ADDs than any other encoding. However, note that these are upper bounds and most

### 2020-08-27 paper/paper.tex
Some editing

@@
 \pdfinfo{
-/Title (Weighted Model Counting with Conditional Weights)
+/Title (Weighted Model Counting with Conditional Weights for Bayesian Networks)
 /Author ()
@@
 
-\title{Weighted Model Counting with Conditional Weights}
+\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
 %\author{
@@
 limitation is by adding more literals. While we show that this is always
-possible in \cref{sec:wmc_as_measure}, the rest of the paper demonstrates that
-it can be significantly more efficient to encode weights in a more flexible
-format instead.
-
-\Cref{sec:prelims} describes three equivalent perspectives on the subject based
-on logic, set theory, and Boolean algebras. Furthermore, we describe the space
-of functions on Boolean algebras and various operations on those functions.
-\Cref{sec:wmc_as_measure} introduces WMC as the problem of computing the value
-of a measure on a Boolean algebra. We show that not all measures can be
-represented using literal-based WMC, but all Boolean algebras can be extended to
-make any measure representable in such a manner.
-
-In \cref{sec:bns}, we introduce \emph{conditional weights} on literals (in the
+possible, we also demonstrate that it can be significantly more efficient to
+encode weights in a more flexible format instead.
+
+After briefly reviewing the background in \cref{sec:related}, in
+\cref{sec:prelims} we  describe three equivalent perspectives on the subject
+based on logic, set theory, and Boolean algebras. Furthermore, we describe the
+space of functions on Boolean algebras and various operations on those
+functions. \Cref{sec:wmc_as_measure} introduces WMC as the problem of computing
+the value of a measure on a Boolean algebra. We show that not all measures can
+be represented using literal-based WMC, but all Boolean algebras can be extended
+to make any measure representable in such a manner.
+
+This new measure-theoretic perspective allows us to not only encode any
+discrete probability distribution but also improve inference speed. In
+\cref{sec:bns}, we demonstrate this by developing a new WMC encoding for
+Bayesian networks that uses \emph{conditional weights} on literals (in the
 spirit of conditional probabilities) that have literal-based WMC as a special
-case. As a particular example, we show how conditional weights can be used to
-encode Bayesian networks. We prove the correctness of the encoding and show
-how a state-of-the-art WMC solver ADDMC \cite{DBLP:conf/aaai/DudekPV20} can be
-adapted to the new format. ADDMC is a recently-proposed algorithm for WMC based
-on manipulating functions on Boolean algebras using an efficient representation
-for such functions known as \emph{algebraic decision diagrams} (ADDs)
-\cite{DBLP:journals/fmsd/BaharFGHMPS97}.
-
-Finally, in \cref{sec:experiments}, we show how the new encoding results in
-significantly improved inference speed on most benchmark instances, often by one
-or two orders of magnitude. We explain the performance benefits by showing how
-the new encoding has asymptotically fewer variables and ADDs.
+case. We prove the correctness of the encoding and show how a state-of-the-art
+WMC solver ADDMC \cite{DBLP:conf/aaai/DudekPV20} can be adapted to the new
+format. ADDMC is a recently-proposed algorithm for WMC based on manipulating
+functions on Boolean algebras using an efficient representation for such
+functions known as algebraic decision diagrams (ADDs)
+\cite{DBLP:journals/fmsd/BaharFGHMPS97}. Finally, in \cref{sec:experiments}, we
+show how the new encoding results in faster inference on the vast majority of
+benchmark instances, often by one or two orders of magnitude. We explain the
+performance benefits by showing how our encoding has asymptotically fewer
+variables and ADDs.
 
@@
 In this section, we give a brief introduction to two alternative ways to think
-about logical constructs such as models and formulas. Let $\mathcal{L}$ be a
-propositional logic with atoms $a$ and $b$, and let $U = \{ a, b \}$. Then
-$2^U$, the power set of $U$, is the set of all models of $\mathcal{L}$, and
-$2^{2^U}$ is the set of all formulas. These sets can also be represented as
-Boolean algebras (e.g., using the syntax $(2^{2^U}, \land, \lor, \neg, \bot,
-\top)$) with a partial order $\le$ that corresponds to set inclusion
-$\subseteq$---see \cref{tbl:notation_example} for examples of how various
-elements can be represented in both notations. Most importantly, note that the
-word \emph{atom} has completely different meanings in logic and in Boolean
-algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of
-$U$, whereas an atom in a Boolean algebra is (in set-theoretic terms) a
-singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
+about logical constructs such as models and formulas. Let us consider a simple
+example of a propositional logic $\mathcal{L}$ with only two atoms $a$ and $b$,
+and let $U = \{ a, b \}$. Then $2^U$, the power set of $U$, is the set of all
+models of $\mathcal{L}$, and $2^{2^U}$ is the set of all formulas. These sets
+can also be represented as Boolean algebras (e.g., using the syntax $(2^{2^U},
+\land, \lor, \neg, \bot, \top)$) with a partial order $\le$ that corresponds to
+set inclusion $\subseteq$---see \cref{tbl:notation_example} for examples of how
+various elements can be represented in both notations. Most importantly, note
+that the word \emph{atom} has completely different meanings in logic and in
+Boolean algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an
+element of $U$, whereas an atom in a Boolean algebra is (in set-theoretic terms)
+a singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
 $\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
@@
 
-\begin{observation}
-  Let $U$ be a set, and $\mathcal{V} = \{ \alpha\colon 2^X \to \mathbb{R}_{\ge 0}
-  \mid X \subseteq U \}$. Then $\mathcal{V}$ is a semi-vector space with three
+Note that if $U$ is any set, then $\mathcal{V} = \{ \alpha\colon 2^X \to
+\mathbb{R}_{\ge 0} \mid X \subseteq U \}$ is a semi-vector space with three
 additional operations: (non-scalar) multiplication, complement, and projection.
@@
 and commutative.
-\end{observation}
 
@@
 $2^{\{a, b\}} \to \mathbb{R}_{\ge 0}$ can represent $\Pr(a \mid b)$, $\Pr(b \mid
-a)$, or something else entirely.
+a)$, or something else entirely, e.g., $\Pr(a \land b)$, $\Pr(a \lor b)$, etc.
 
@@
 processors\footnote{Each instance is run on the same processor for all
-  encodings.} with an \SI{8}{\gibi\byte} memory limit and a \SI{1000}{\second}
-timeout.
+  encodings.} running Scientific~Linux~7 with an \SI{8}{\gibi\byte} memory limit
+and a \SI{1000}{\second} timeout.
 
@@
 \end{itemize*}
+We run ADDMC with each of the five encodings once on each Bayesian network.
 
@@
 more expressive representation of weights can outperform increasing the size of
-the problem to keep the weights simple. The same idea can be adapted to
+the problem to keep the weights simple. Indeed, in this work, we have provided a
+new theoretical perspective on the expressive power of WMC and illustrated the
+empirical benefits of that perspective. The same idea can be adapted to
 search-based solvers such as Cachet \cite{DBLP:conf/sat/SangBBKP04} as well as
-to other inference problem domains such as probabilistic programs.
+to other inference problem domains such as probabilistic programs
+\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089}.
 
@@
 
+\newpage
+\bibliography{paper}
+
+\newpage
 \appendix
@@
 
-\bibliography{paper}
 \end{document}

### 2020-11-14 talk/talk.tex
A short talk

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz-cd}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{mathtools}

\beamertemplatenavigationsymbolsempty
\usetheme{default}
\usecolortheme{whale}

\author{Paulius Dilkas}
\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
\date{27th November 2020}

\begin{document}

\frame{\titlepage}

\begin{frame}{Boolean Algebras and Propositional Logic}
  Let \structure{$U = \{ a, b \}$}. Then \structure{$2^{2^U}$} is a Boolean
  algebra with the following Hasse diagram (\structure{$x \le y$} if
  \structure{$x \subseteq y$} or, equivalently, \structure{$x = x \land y$}).
  \[
    \begin{tikzcd}[ampersand replacement=\&, column sep=tiny]
      \& \& \& \& \& \top \ar[dlll,dash,gray] \ar[dl,dash,gray]
      \ar[dr,dash,gray] \ar[drrr,dash,gray] \& \& \& \\
      \& \& a \lor b \& \& b \to a \& \& a \to b \& \& \neg a \lor \neg
      b \\
      a \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& b \ar[u,dash,gray]
      \ar[urrrr,dash,gray] \& \& a \leftrightarrow b \ar[u,dash,gray]
      \ar[urr,dash,gray] \& \& a + b \ar[ullll,dash,gray] \ar[urr,dash,gray]
      \& \& \neg b \ar[ullll,dash,gray] \ar[u,dash,gray] \& \& \neg a
      \ar[ullll,dash,gray] \ar[ull,dash,gray] \\
      \& \& \fbox{$a \land b$} \ar[ull,dash,gray] \ar[u,dash,gray]
      \ar[urr,dash,gray] \& \& \fbox{$a \land \neg b$} \ar[ullll,dash,gray]
      \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& \fbox{$\neg a \land b$}
      \ar[ullll,dash,gray] \ar[u,dash,gray] \ar[urrrr,dash,gray] \& \&
      \fbox{$\neg a \land \neg b$} \ar[ullll,dash,gray] \ar[u,dash,gray]
      \ar[urr,dash,gray] \\
      \& \& \& \& \& \bot \ar[ulll,dash,gray] \ar[ul,dash,gray]
      \ar[ur,dash,gray] \ar[urrr,dash,gray] \& \& \&
    \end{tikzcd}
  \]
\end{frame}

\begin{frame}{Some Definitions}
  \begin{itemize}
  \item A \alert{measure} is a function \structure{$\mu\colon 2^{2^U} \to
    \mathbb{R}_{\ge 0}$} such that:
    \begin{itemize}
    \item \structure{$\mu(\bot) = 0$};
    \item \structure{$\mu(x \lor y) = \mu(x) + \mu(y)$} whenever \structure{$x
        \land y = \bot$}.
    \end{itemize}
    \pause
  \item A \alert{weight function} is any function \structure{$\nu\colon 2^U \to
      \mathbb{R}_{\ge 0}$}.
    \pause
    \begin{itemize}
    \item It is \alert{factored} if
      \[
        \nu = \prod_{x \in U} \nu_x
      \]
      for some functions \structure{$\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge
          0}$}, \structure{$x \in U$}.
    \end{itemize}
    \pause
  \item We say that \structure{$\nu$} \alert{induces} \structure{$\mu$} if
    \[
      \mu(x) = \sum_{\{u\} \le x} \nu(u)
    \]
    for all \structure{$x \in 2^{2^U}$}.
    \pause
  \item A measure \structure{$\mu$} is \alert{factorable} if there exists a
    factored weight function \structure{$\nu$} that induces \structure{$\mu$}.
  \end{itemize}
\end{frame}

\begin{frame}{WMC as a Measure on a Boolean Algebra}
  \begin{itemize}
  \item \alert{Weighted model count} (WMC) of a theory \structure{$\Delta$},
    i.e.,
    \[
      \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models
        l} w(l)
    \]
    computes \structure{$\mu(x)$} for some \structure{$x \in 2^{2^U}$}.
    \pause
  \item WMC with weights on literals can only compute \alert{factorable}
    measures (c.f. independent probability distributions).
  \item Traditional workaround: expanding the Boolean algebra.
    \pause
    \begin{itemize}
    \item But we don't need to do that!
    \item Instead, we can use \alert{conditional weight functions} in the spirit
      of conditional probabilities.
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Example: Encoding Bayesian Networks}
  \begin{figure}
    \begin{subfigure}{0.2\textwidth}
      \centering
      \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
        \node[draw,circle] {$A$}
        child {node[draw,circle] {$B$}};
      \end{tikzpicture}
    \end{subfigure}%
    \begin{subfigure}{0.8\textwidth}
      \centering
      \begin{tabular}[t]{cc}
        \toprule
        $a$ & $\Pr(A = a)$ \\
        \midrule
        1 & 0.5 \\
        0 & 0.5 \\
        \bottomrule
      \end{tabular}
      \begin{tabular}[t]{ccc}
        \toprule
        $a$ & $b$ & $\Pr(B = b \mid A = a)$ \\
        \midrule
        1 & 1 & 0.6 \\
        1 & 0 & 0.4 \\
        0 & 1 & 0.1 \\
        0 & 0 & 0.9 \\
        \bottomrule
      \end{tabular}
    \end{subfigure}
    \caption{A Bayesian network with its conditional probability tables}
  \end{figure}
  \pause
  Let \structure{$U = \{ \lambda_{A=1}, \lambda_{B=1} \}$}. The weight function
  \structure{$\nu\colon 2^U \to \mathbb{R}_{\ge 0}$} for this network can be
  defined as \structure{$\nu \coloneqq \nu_A \cdot \nu_B$}, where
  \structure{$\nu_A = 0.5$}, and
  \begin{align*}
    \nu_B &= 0.6[\lambda_{B=1}] \cdot [\lambda_{A=1}] + 0.4\overline{[\lambda_{B=1}]} \cdot [\lambda_{A=1}] \\
          &+ 0.1[\lambda_{B=1}] \cdot \overline{[\lambda_{A=1}]} + 0.9\overline{[\lambda_{B=1}]} \cdot \overline{[\lambda_{A=1}]}.
  \end{align*}
\end{frame}

\begin{frame}{Experimental Results}
  \centering
  \scalebox{0.8}{\input{../paper/cumulative.tex}}
  \vfill
  \centering
  \scalebox{0.6}{\input{../paper/scatter.tex}}
\end{frame}

\end{document}

### 2020-11-25 paper2/paper.tex
Transfer the paper to the new format

--- 2020-08-27 paper/paper.tex
@@
-\def\year{2021}\relax
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai21}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{graphicx}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-/Title (Weighted Model Counting with Conditional Weights for Bayesian Networks)
-/Author ()
-/TemplateVersion (2021.1)
-} %Leave this
-% /Title ()
-% Put your actual complete title (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case
-% Leave the space between \Title and the beginning parenthesis alone
-% /Author ()
-% Put your actual complete list of authors (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case.
-% Each author should be only by a comma. If the name contains accents, remove them. If there are any LaTeX commands,
-% remove them.
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai21.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
+\documentclass{article}
+\pdfpagewidth=8.5in
+\pdfpageheight=11in
+\usepackage{ijcai21}
+\usepackage{times}
+\usepackage{soul}
+\usepackage{url}
+\usepackage[hidelinks]{hyperref}
+\usepackage[utf8]{inputenc}
+\usepackage[small]{caption}
+\usepackage{graphicx}
+\usepackage{amsmath}
 \usepackage{amsthm}
-\usepackage{thmtools,thm-restate}
+\usepackage{booktabs}
+\urlstyle{same}
+
+\usepackage{complexity}
+\usepackage[capitalise]{cleveref}
 \usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{mathtools}
+\usepackage{thmtools}
+\usepackage{thm-restate}
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage[capitalise]{cleveref}
-\usepackage{bm}
-\usepackage{booktabs}
-\usepackage[table]{xcolor}
-\usepackage{tikz}
-\usepackage{complexity}
-\usepackage{subcaption}
-\usepackage{multirow}
 \usepackage[binary-units]{siunitx}
 \usepackage[inline]{enumitem}
-\usetikzlibrary{cd}
-\usetikzlibrary{bayesnet}
-\usetikzlibrary{calc}
+\usepackage[table]{xcolor}
+\usepackage{multirow}
+\usepackage{subcaption}
+\usepackage{tikz}
+
+% the following package is optional:
+%\usepackage{latexsym}
+
+% See https://www.overleaf.com/learn/latex/theorems_and_proofs
+% for a nice explanation of how to define new theorems, but keep
+% in mind that the amsthm package is already included in this
+% template and that you must *not* alter the styling.
+\newtheorem{example}{Example}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{definition}{Definition}
+
 \DeclareMathOperator{\im}{im}
-\newtheorem{theorem}{Theorem}
-\newtheorem{observation}{Observation}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
+\newcommand{\etal}{\textit{et al}.}
+\Crefname{algocf}{Algorithm}{Algorithms}
+\Crefname{figure}{Figure}{Figures}
+
 \makeatletter
@@
 
+% Following comment is from ijcai97-submit.tex:
+% The preparation of these files was supported by Schlumberger Palo Alto
+% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
+% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
+% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
+% preparation.
+
+% These instructions can be modified and used in other conferences as long
+% as credit to the authors and supporting agencies is retained, this notice
+% is not changed, and further modification or reuse is not restricted.
+% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
+% contacts for providing assistance without their prior permission.
+
+% To use for other conferences, change references to files and the
+% conference appropriate and use other authors, contacts, publishers, and
+% organizations.
+% Also change the deadline and address for returning papers and the length and
+% page charge instructions.
+% Put where the files are available in the appropriate places.
+
+%PDF Info Is REQUIRED.
+\pdfinfo{
+/TemplateVersion (IJCAI.2021.0)
+}
+
 \title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
-%\author{
-%  Paulius Dilkas, \textsuperscript{\rm 1}
-%  Vaishak Belle \textsuperscript{\rm 1,2} \\
-%}
-%\affiliations{
-%    \textsuperscript{\rm 1} University of Edinburgh \\
-%    \textsuperscript{\rm 2} Alan Turing Institute \\
-%    p.dilkas@sms.ed.ac.uk, vaishak@ed.ac.uk
-%}
+
+% Single author syntax
+% \author{
+%     Zhi-Hua Zhou
+%     \affiliations
+%     Nanjing University
+%     \emails
+%     pcchair@ijcai-21.org
+% }
+
+% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
+% Check the ijcai21-multiauthor.tex file for detailed instructions
+% \iffalse
+% \author{
+% First Author$^1$
+% \and
+% Second Author$^2$\and
+% Third Author$^{2,3}$\And
+% Fourth Author$^4$
+% \affiliations
+% $^1$First Affiliation\\
+% $^2$Second Affiliation\\
+% $^3$Third Affiliation\\
+% $^4$Fourth Affiliation
+% \emails
+% \{first, second\}@example.com,
+% third@other.example.com,
+% fourth@example.com
+% }
+% \fi
+
 \begin{document}
@@
 \section{Introduction}
-
-% TODO: Feedback: our empirical evaluations show a x% improvement
 
@@
 and \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}. Below we summarise the
-observed performance differences among them. \citet{DBLP:conf/aaai/SangBK05}
-claim that \texttt{sbk05} is a smaller encoding than \texttt{d02} with respect
-to both the number of clauses and the number of variables but provide no
-experimental comparison. \citet{DBLP:conf/ijcai/ChaviraD05} compare
-\texttt{cd05} with \texttt{d02} by measuring the time it takes to compile either
-encoding into an arithmetic circuit (but do not measure inference time). The
-more recent encoding \texttt{cd05} always compiles faster and results in a
-smaller arithmetic circuit (as measured by the number of edges). In their
-subsequent paper, the same authors perform two sets of experiments (that are
-relevant to this summary) \cite{DBLP:conf/sat/ChaviraD06}. First, they compile
-\texttt{cd05} and \texttt{cd06} encodings into d-DNNF (i.e., deterministic
-decomposable negation normal form \cite{DBLP:journals/jancl/Darwiche01}),
-measuring both compilation time and numbers of edges in the d-DNNF diagram. The
-results are mostly in favour of \texttt{cd06}. Second, they compare the
-inference time of \texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04}
-with the compile times of \texttt{cd05} and \texttt{cd06}, but only on five
-(types of) instances. In these experiments, \texttt{cd06} is always faster than
-\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
-\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
-slightly slower. The performance difference between \texttt{sbk05} and
-\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
-five instances and worse on the remaining two. Based on this description, one
-would expect \texttt{cd06} to be faster than both \texttt{cd05} and
-\texttt{sbk05}, both of which should be faster than \texttt{d02}. The
-experiments in \cref{sec:experiments}, however, strongly disagree with this
-prediction, showing that the quality of an encoding depends strongly on the
-underlying search algorithm or compilation technique.
+observed performance differences among them. Sang
+\etal{}~\shortcite{DBLP:conf/aaai/SangBK05} claim that \texttt{sbk05} is a
+smaller encoding than \texttt{d02} with respect to both the number of clauses
+and the number of variables but provide no experimental comparison. Chavira and
+Darwiche~\shortcite{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with
+\texttt{d02} by measuring the time it takes to compile either encoding into an
+arithmetic circuit (but do not measure inference time). The more recent encoding
+\texttt{cd05} always compiles faster and results in a smaller arithmetic circuit
+(as measured by the number of edges). In their subsequent paper, the same
+authors perform two sets of experiments (that are relevant to this summary)
+\cite{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
+\texttt{cd06} encodings into d-DNNF (i.e., deterministic decomposable negation
+normal form \cite{DBLP:journals/jancl/Darwiche01}), measuring both compilation
+time and numbers of edges in the d-DNNF diagram. The results are mostly in
+favour of \texttt{cd06}. Second, they compare the inference time of
+\texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04} with the compile
+times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
+In these experiments, \texttt{cd06} is always faster than \texttt{cd05}, while
+the comparison with \texttt{sbk05} is mixed. Sometimes \texttt{cd06} is orders
+of magnitude faster than \texttt{sbk05}, sometimes slightly slower. The
+performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
+to judge: \texttt{sbk05} is better on three out of five instances and worse on
+the remaining two. Based on this description, one would expect \texttt{cd06} to
+be faster than both \texttt{cd05} and \texttt{sbk05}, both of which should be
+faster than \texttt{d02}. The experiments in \cref{sec:experiments}, however,
+strongly disagree with this prediction, showing that the quality of an encoding
+depends strongly on the underlying search algorithm or compilation technique.
 
@@
 \begin{table*}
-  \caption{Notation for a logic with two atoms. The elements in both columns are
-    listed in the same order.}
-  \label{tbl:notation_example}
   \centering
@@
   \end{tabular}
+  \caption{Notation for a logic with two atoms. The elements in both columns are
+    listed in the same order.}
+  \label{tbl:notation_example}
 \end{table*}
@@
 multiplication and projection are as defined by
-\citet{DBLP:conf/aaai/DudekPV20}, while others are new.
+Dudek \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20}, while others are new.
 
@@
 \begin{algorithm}[t]
-  \caption{Encoding a Bayesian network}
-  \label{alg:encoding}
   \KwData{vertices $\mathcal{V}$, probability distribution $\Pr$}
@@
   \Return{$\phi$}\;
+  \caption{Encoding a Bayesian network}
+  \label{alg:encoding}
 \end{algorithm}
@@
 \item DQMR and
-\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
+\item Grid networks as described by Sang
+  \etal{}~\shortcite{DBLP:conf/aaai/SangBK05},
 \item Mastermind, and
-\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
+\item Random Blocks from the work of Chavira
+  \etal{}~\shortcite{DBLP:journals/ijar/ChaviraDJ06},
 \item remaining binary Bayesian networks that include Plan Recognition
@@
 
-\begin{figure}
+\begin{figure} % TODO: update
   \centering
-  \input{cumulative.tex}%
+  \input{../paper1/cumulative.tex}%
   \caption{Cumulative number of instances solved by ADDMC over time using each
@@
 
-% TODO: (needed to follow formatting requirements)
-% 1. Remove the \input command.
-% 2. R should compile the tex files to be standalone.
-% 3. Edit the tex files to replace RGB colours with CMYK.
-% 4. Compile the tex files to PDFs.
-% 5. Include the PDFs (look up how to do that in the formatting guidelines).
-% 6. make sure that there are no duplicates in the bib files (look at LaTex output)
-
 \begin{table}
   \centering
-  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
-    encoding (uniquely, faster than with others, and in total) under the
-    described constraints}%
   \begin{tabular}{lrrr}
@@
   \end{tabular}
+  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
+    encoding (uniquely, faster than with others, and in total) under the
+    described constraints}%
   \label{tbl:tallies}
@@
 
-\begin{figure*}
+\begin{figure*} % TODO: update
   \centering
-  \input{scatter.tex}%
+  \input{../paper1/scatter.tex}%
   \caption{ADDMC inference time using \texttt{cw} compared to \texttt{d02}
@@
   \centering
-  \caption{Asymptotic upper bounds on the numbers of variables and clauses/ADDs
-    for each encoding}
-  \label{tbl:asymptotes}
   \begin{tabular}{lcc}
@@
   \end{tabular}
+  \caption{Asymptotic upper bounds on the numbers of variables and clauses/ADDs
+    for each encoding}
+  \label{tbl:asymptotes}
 \end{table}
@@
 new theoretical perspective on the expressive power of WMC and illustrated the
-empirical benefits of that perspective. The same idea can be adapted to
-search-based solvers such as Cachet \cite{DBLP:conf/sat/SangBBKP04} as well as
-to other inference problem domains such as probabilistic programs
-\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089}.
+empirical benefits of that perspective. The same idea can be adapted to other
+inference problem domains such as probabilistic programs
+\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
+well as to search-based solvers such as Cachet \cite{DBLP:conf/sat/SangBBKP04},
+although the extension may be less straightforward for other WMC techniques.
 
@@
 
-\newpage
-\bibliography{paper}
-
-\newpage
 \appendix
@@
   \begin{itemize}
-  \item the proof of Theorem~1 by \citet{DBLP:conf/aaai/DudekPV20};
+  \item the proof of Theorem~1 by Dudek
+    \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20};
   \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
@@
 
+\bibliographystyle{named}
+\bibliography{paper}
+
 \end{document}

### 2020-11-25 tools/analyse.R

@@ -162,8 +162,10 @@ cumulative_plot <- function(column_name, pretty_column_name, column_values,
   cumulative$count <- as.numeric(cumulative$count)
   cumulative <- cumulative[cumulative$time < TIMEOUT, ]
   ggplot(cumulative, aes(x = time, y = count, color = .data[[column_name]])) +
-    geom_line(aes(linetype = .data[[column_name]])) +
+#    geom_line(aes(linetype = .data[[column_name]])) +
+    geom_line() +
 #    scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 10, 1000), labels = c("0.1", "10", "1000")) +
+    scale_x_continuous(trans = log10_trans()) +
     xlab("Time (s)") +
     ylab("Instances solved") +
 #    scale_colour_brewer(palette = "Dark2") +

### 2020-11-27 tools/bklm16_wrapper.py
Fix two bugs in d-DNNF inference

@@ -2,25 +2,30 @@ import argparse
 import resource
 import subprocess
 
+SOFT_MEMORY_LIMIT = 0.95 # As a proportion of the hard limit
+
 parser = argparse.ArgumentParser(
     description='A wrapper for query-dnnf to perform inference on the BKLM16 encoding (compiled to d-DNNF format)')
 parser.add_argument('network', metavar='network', help='a Bayesian network')
-parser.add_argument('-m', dest='memory', help='the maximum amount of virtual memory available to underlying encoders (in kiB)')
+parser.add_argument('-m', dest='memory', help='the maximum amount of virtual memory available to query-dnnf (in GiB)')
 args = parser.parse_args()
 
 if args.memory:
+    mem = int(args.memory) * 1024**3
     process = subprocess.Popen('./deps/query-dnnf/query-dnnf',
                                stdin=subprocess.PIPE, stdout=subprocess.PIPE,
                                preexec_fn=lambda:
                                resource.setrlimit(resource.RLIMIT_AS,
-                                                  (int(args.memory) * 1024,
-                                                   resource.RLIM_INFINITY)))
+                                                  (int(SOFT_MEMORY_LIMIT * mem),
+                                                   mem)))
 else:
     process = subprocess.Popen('./deps/query-dnnf/query-dnnf',
                                stdin=subprocess.PIPE, stdout=subprocess.PIPE)
 
+# Apparently, query-dnnf only computes the right WMC if you ask it to print the
+# d-DNNF first
 output, _ = process.communicate(
-    'load {}.cnf.nnf\nw {}.uai.weights\nmc'.format(args.network,
+    'load {}.cnf.nnf\np\nw {}.uai.weights\nmc'.format(args.network,
                                                    args.network).encode())
 output_probability = float(output.decode('utf-8').split()[-1])
 

### 2020-11-27 tools/encode.py

@@ -360,7 +360,6 @@ def encode_using_bn2cnf(args):
     with open(variables_filename) as f:
         text = f.read()
     for line in re.finditer(VARIABLE_MAP_RE, text):
-        #.group(1)[2:-2]
         variable = line.group(1)
         values = [v.split(', ') for v in line.group(2)[2:-2].split('][')]
         for value in range(len(values)):

### 2020-11-27 tools/parse.py

@@ -56,7 +56,7 @@ data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Pla
 data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
 #data += parse_dir('results/2004-pgm/', {'dataset': '2004-PGM'})
 #data += parse_dir('results/2005-ijcai/', {'dataset': '2005-IJCAI'})
-#data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
+data += parse_dir('results/2006-ijar/', {'dataset': '2006-IJAR'})
 
 fieldnames = set()
 for d in data:

### 2020-11-28 paper2/paper.tex
Fix two bugs in d-DNNF inference
Add TODOs to the paper
Remove half of the references

@@
 \section{Introduction}
-
+% TODO: mention more recent papers
+% TODO: emphasise the contributions (even more)
+% TODO: write ADDMC, Ace, query-dnnf, Cachet, bn2cnf, c2d in a tt font
+% TODO: double-check the capitalisation of, e.g., c2d
+% TODO: relate non-factorable measures to VCSPs, provenance/probabilistic
+% databases
+% TODO: simplify the introductory explanations (take inspiration from the
+% comments of reviewer #5) (this is more about the next two sections)
+
+% Over the last fifteen years, WMC has been extended and generalised in many
+% ways, e.g., to handle continuous probability distributions
+% \cite{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
+% \cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
+% domains \cite{DBLP:conf/aaai/Belle17}.
+
+% , whereas approximate solvers work by sampling
+% \cite{DBLP:conf/aaai/ChakrabortyFMSV14} and performing local search
+% \cite{DBLP:conf/sat/WeiS05}.
+
+% TODO: rephrase
 Weighted model counting (WMC), i.e., an extension of model counting ($\#\SAT{}$)
@@
 tasks in a wide range of formalisms including Bayesian networks
-\cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906}, probabilistic
-graphical models more generally \cite{DBLP:conf/ecsqaru/ChoiKD13}, and
-probabilistic programs
-\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089}.
-Over the last fifteen years, WMC has been extended and generalised in many ways,
-e.g., to handle continuous probability distributions
-\cite{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
-\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
-domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, by generalising the notion
-of weights to an arbitrary semiring, a range of other problems are also captured
-\cite{DBLP:journals/japll/KimmigBR17}. Exact WMC solvers typically rely on
-either knowledge compilation
-\cite{DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17} or exhaustive DPLL
-search \cite{DBLP:conf/aaai/SangBK05}, whereas approximate solvers work by
-sampling \cite{DBLP:conf/aaai/ChakrabortyFMSV14} and performing local search
-\cite{DBLP:conf/sat/WeiS05}.
+\cite{DBLP:conf/aaai/SangBK05} and probabilistic programs
+\cite{DBLP:journals/tplp/FierensBRSGTJR15}. Furthermore, by generalising the
+notion of weights to an arbitrary semiring, a range of other problems are also
+captured \cite{DBLP:journals/japll/KimmigBR17}. Exact WMC solvers typically rely
+on either knowledge compilation \cite{DBLP:conf/ijcai/LagniezM17} or exhaustive
+DPLL search \cite{DBLP:conf/aaai/SangBK05}.
 
@@
 
-\paragraph{ADDs and their use in inference.} ADDs provide an efficient way to
-manipulate functions from a Boolean algebra to any algebraic structure (most
-commonly real numbers) \cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been
-used to represent value functions in Markov decision processes (MDPs)
-\cite{DBLP:conf/uai/HoeySHB99} and extended to handle first-order MDPs
-\cite{DBLP:journals/ai/SannerB09} and discrete and continuous state MDPs
-\cite{DBLP:conf/uai/SannerDB11}. The latter extension has also been used for
-weighted model integration---an extension of WMC that can handle continuous
-variables \cite{DBLP:conf/ijcai/KolbMSBK18}. For Bayesian networks, ADDS have
-been used to represent each conditional probability table (CPT) as an ADD
-\cite{DBLP:conf/icml/ZhaoMP15} and as a combination of ADDs and arithmetic
-circuits \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous
-in this situation because of their ability to fully exploit context-specific
-independence, i.e., the observable structure within a CPT that is not inherited
-from the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
+% TODO: maybe summarise this in one sentence
+% \paragraph{ADDs and their use in inference.} ADDs provide an efficient way to
+% manipulate functions from a Boolean algebra to any algebraic structure (most
+% commonly real numbers) \cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been
+% used to represent value functions in Markov decision processes (MDPs)
+% \cite{DBLP:conf/uai/HoeySHB99} and extended to handle first-order MDPs
+% \cite{DBLP:journals/ai/SannerB09} and discrete and continuous state MDPs
+% \cite{DBLP:conf/uai/SannerDB11}. The latter extension has also been used for
+% weighted model integration---an extension of WMC that can handle continuous
+% variables \cite{DBLP:conf/ijcai/KolbMSBK18}. For Bayesian networks, ADDS have
+% been used to represent each conditional probability table (CPT) as an ADD
+% \cite{DBLP:conf/icml/ZhaoMP15} and as a combination of ADDs and arithmetic
+% circuits \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous
+% in this situation because of their ability to fully exploit context-specific
+% independence, i.e., the observable structure within a CPT that is not inherited
+% from the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
 
@@
 
+% TODO: add a link to CUDD
 We also consider the space of all functions from any Boolean algebra to
@@
 can be efficiently represented using ADDs. Furthermore, all of the operations
-are supported by the CUDD \cite{somenzi1998cudd} package that is used by ADDMC
-for ADD manipulation \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
-multiplication and projection are as defined by
-Dudek \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20}, while others are new.
+are supported by CUDD package that is used by ADDMC for ADD manipulation
+\cite{DBLP:conf/aaai/DudekPV20}. The definitions of multiplication and
+projection are as defined by Dudek \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20},
+while others are new.
 
@@
 \section{WMC as a Measure on a Boolean Algebra} \label{sec:wmc_as_measure}
-
+% TODO beginning of section 4: a weight function is *any* function; end the
+% paragraph with 'for all x \in U'.
+
+% TODO: mention that putting a measure on a BA is a well-known idea
 In this section, we introduce an alternative definition of WMC and demonstrate
@@
 and $\mu(a \lor b) = \mu(a) + \mu(b)$ for all $a, b \in 2^{2^U}$ whenever $a
-\land b = \bot$ \cite{gaifman1964concerning,DBLP:books/daglib/0090259}. A
-\emph{weight function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$. A
-weight function is \emph{factored} if $\nu = \prod_{x \in U} \nu_x$ for some
-functions $\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in U$. We say that
-a weight function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$ \emph{induces} a
-measure $\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if $\mu_\nu(x) =
-\sum_{\{u\} \le x} \nu(u)$.
+\land b = \bot$. A \emph{weight function} is a function $\nu\colon 2^U \to
+\mathbb{R}_{\ge 0}$. A weight function is \emph{factored} if $\nu = \prod_{x \in
+  U} \nu_x$ for some functions $\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$,
+$x \in U$. We say that a weight function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$
+\emph{induces} a measure $\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
+$\mu_\nu(x) = \sum_{\{u\} \le x} \nu(u)$.
 
@@
   \end{align*}
-  which has no solutions.
+  which has no solution.
 
@@
 \section{Encoding Bayesian Networks Using Conditional Weights} \label{sec:bns}
+% TODO: make it clear which parts of the encoding are not new
+% TODO: rewrite the encoding without using an algorithm (look into the feedback
+% of reviewer #5 and someone before him)
+% TODO: explain/prove why it's impossible for the all-zero encoding to represent
+% the last value (a.k.a. the -implicit flag)
 
@@
 full probability distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X
-\mid \mathrm{pa}(X))$ \cite{DBLP:books/daglib/0023820}. For discrete Bayesian
-networks (and we only consider discrete networks in this paper), each factor of
-this product can be represented by a CPT. See \cref{fig:example_bn} for an
-example Bayesian network that we will refer to throughout this section. For
-this network, $\mathcal{V} = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
-$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
-$\im T = \{ l, m, h \}$.
+\mid \mathrm{pa}(X))$. For discrete Bayesian networks (and we only consider
+discrete networks in this paper), each factor of this product can be represented
+by a CPT. See \cref{fig:example_bn} for an example Bayesian network that we will
+refer to throughout this section. For this network, $\mathcal{V} = \{ W, F, T
+\}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$,
+$\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
 
@@
 \subsection{Changes to ADDMC}
+% TODO: clarify that both variable orders are handled by the ADDMC heuristics
 
@@
 
-First, ADDMC constructs the \emph{Gaifman graph} \cite{gaifman1982local} of the
-input CNF formula as an aid for the algorithm's heuristics. This graph has as
-vertices the variables of the formula, and there is an edge between two
-variables $u$ and $v$ if there is a clause in the formula that contains both $u$
-and $v$. We extend this definition to functions on Boolean algebras, i.e., the
-factors of $\phi$. For any pair of distinct variables $u, v \in U$, we draw an
-edge between them in the Gaifman graph if there is a function $\alpha\colon 2^X
-\to \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v
-\in X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges
-between all distinct pairs of variables in $\mathcal{E}^*(X)$.
+% TODO: Gaifman graph is also known as the primal graph
+First, ADDMC constructs the \emph{Gaifman graph} of the input CNF formula as an
+aid for the algorithm's heuristics. This graph has as vertices the variables of
+the formula, and there is an edge between two variables $u$ and $v$ if there is
+a clause in the formula that contains both $u$ and $v$. We extend this
+definition to functions on Boolean algebras, i.e., the factors of $\phi$. For
+any pair of distinct variables $u, v \in U$, we draw an edge between them in the
+Gaifman graph if there is a function $\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$
+that is a factor of $\phi$ such that $u \in X$ and $v \in X$. For instance, a
+factor such as $\mathrm{CPT}_X$ will enable edges between all distinct pairs of
+variables in $\mathcal{E}^*(X)$.
 
@@
 \section{Experimental Comparison} \label{sec:experiments}
+% TODO: stacked bar charts: 1) mention that the error bars denote 0.1 * standard
+% deviation
+% 2) and that only successfully run instances are included
+% 3) and that the top error bar relates only to inference (and not the sum of
+% the two)
+% TODO: note: I'm unable to replicate the experiments from bklm. This could be
+% due to two reasons:
+% 1) I'm measuring running time rather than compiled structure size <- more
+% likely
+% 2) I'm not using the -implicit flag.
+% TODO: We use Ace to compile the BN together with its evidence (as opposed to
+% compiling just the BN and using evidence during inference) as this more
+% closely resembles the behaviour of ADDMC
+% TODO: we run cd05 only with dtBnMinfill, as that's the more commonly used
+% setting (although another one was used as well)
+% TODO: The -implicit flag of bklm16 cannot be used because even a small
+% Bayesian network with seven independent binary variables with 0.1/0.9
+% probabilities is already big enough to drive the scaling factor down to zero.
+% The last step of this encoding is a multiplication of a huge number (on the
+% order of 10^30 for some of the smaller DQMR instances) by a number
+% equivalently close to zero (so that their product lands in the interval [0,
+% 1]). Thus, we disable this flag (thus making the algorithm slower but
+% correct).
+% TODO: the legacy mode encoding of bklm16 also runs c2d (as packaged with Ace)
+% TODO: query-dnnf: http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html
+% TODO: bn2cnf http://www.cril.univ-artois.fr/KC/bn2cnf.html
+% TODO: Note that our encoder was implemented in Python with no concern for
+% efficiency, so encoding could easily be improved by one or two orders of
+% magnitude.
+% TODO: Python, Java, gcc versions (maybe also all the software that I'm using
+% (e.g., bn2cnf, Cachet))
+% TODO: 85% is as recommended in the README of Ace (might have to go lower than that)
+% TODO: for each encoding, mention:
+% 1) software
+% 2) encoding options
+% 3) additional data processing
+% 4) inference options
 
@@
 
-\begin{figure} % TODO: update
+\begin{figure}
   \centering
@@
 
-\begin{figure*} % TODO: update
+\begin{figure*}
   \centering
@@
 
+% TODO: Either remove the 'conjecture' (preferable), or explain why those
+% instances perform worse
 According to the cumulative plot in \cref{fig:cumulative}, \texttt{cw} is
@@
 
+% TODO: clarify what 'more expressive' means
 While we chose to use ADDMC \cite{DBLP:conf/aaai/DudekPV20} as the WMC algorithm
@@
 inference problem domains such as probabilistic programs
-\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
+\cite{DBLP:journals/tplp/FierensBRSGTJR15} as
 well as to search-based solvers such as Cachet \cite{DBLP:conf/sat/SangBBKP04},
@@
 
-%An additional benefit of conditional weights is that a more expressive format
-%makes it easier to invent new WMC encodings.
-%Filtering out ADDs that have nothing to do with the answer helps
+% TODO: emphasise that the simplicity of the BN encoding implies the strength of
+% the general principle.
+% An additional benefit of conditional weights is that a more expressive format
+% makes it easier to invent new WMC encodings.
+% Filtering out ADDs that have nothing to do with the answer helps
 %  tremendously, but I'm purposefully not doing that.

### 2020-12-01 paper2/paper.tex
All kinds of minor changes

@@
 
-\section{Boolean Algebras, Power Sets, and Propositional
-  Logic} \label{sec:prelims}
+\section{Boolean Algebras and Propositional Logic} \label{sec:prelims}
 
@@
 
-% TODO: add a link to CUDD
+% TODO: explain what CUDD is
 We also consider the space of all functions from any Boolean algebra to
@@
 
-\section{Encoding Bayesian Networks Using Conditional Weights} \label{sec:bns}
+\section{Example: Bayesian Networks} \label{sec:bns}
 % TODO: make it clear which parts of the encoding are not new
@@
 % TODO: the legacy mode encoding of bklm16 also runs c2d (as packaged with Ace)
-% TODO: query-dnnf: http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html
-% TODO: bn2cnf http://www.cril.univ-artois.fr/KC/bn2cnf.html
 % TODO: Note that our encoder was implemented in Python with no concern for
@@
 % 4) inference options
+
+TODO: Things I will need to mention:
+\begin{itemize}
+\item
+  \texttt{query-dnnf}\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
+\item
+  \texttt{bn2cnf}\footnote{\url{http://www.cril.univ-artois.fr/KC/bn2cnf.html}}
+  and \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}
+\end{itemize}
 

### 2020-12-01 tools/analyse.R

@@ -9,6 +9,7 @@ require(tidyr)
 
 TIMEOUT <- 1000
 data <- read.csv("../results.csv", header = TRUE, sep = ",")
+data$inference_time[is.na(data$inference_time)] <- TIMEOUT
 min.time <- min(min(data$encoding_time[data$encoding_time > 0]),
                 min(data$inference_time[data$inference_time > 0]))
 data$encoding_time[data$encoding_time == 0] <- min.time
@@ -32,7 +33,9 @@ df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
             fun.aggregate = sum,
             value.var = c("answer", "time"))
 time_columns <- Filter(function(x) startsWith(x, "time_"), names(df))
+time_columns0 <- time_columns[time_columns != "time_new_cw"]
 df$time_min <- as.numeric(apply(df, 1, function (row) min(row[time_columns])))
+df$time_min0 <- as.numeric(apply(df, 1, function (row) min(row[time_columns0])))
 df$major.dataset <- "Non-binary"
 df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
 df$major.dataset[grepl("Grid", df$instance, fixed = TRUE)] <- "Grid"
@@ -43,12 +46,27 @@ df$major.dataset[grepl("Plan_Recognition", df$instance, fixed = TRUE)] <- "Other
 df$major.dataset[grepl("students", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
 
+# instance_to_min_time <- df$time_min
+# names(instance_to_min_time) <- df$instance
+# instance_to_min_time0 <- df$time_min0
+# names(instance_to_min_time0) <- df$instance
+# df.temp <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS1", answer = NA, time = instance_to_min_time[df$instance])
+# df.temp2 <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS0", answer = NA, time = instance_to_min_time0[df$instance])
+# data_sum <- rbind(data_sum, df.temp, df.temp2)
+
 # ============ Numerical investigations ================
 
 df %>% group_by(df$dataset) %>% tally()
 
 # Where answers don't match
-interesting <- df[abs(df$answer_d02 - df$answer_bklm16) > 0.01,]
+interesting <- df[abs(df$answer_new_cw - df$answer_new_bklm16) > 0.01,]
[…]

### 2020-12-01 tools/parse.py

@@ -24,7 +24,10 @@ def parse(filename):
             answer = line.split()[2] # Cachet answer
         elif filename.endswith('.old_inf') and line.startswith('Pr(e) ='):
             # Ace evaluation answer
-            answer = re.match(r'[\d\.eE-]+', line.split()[2]).group(0)
+            try:
+                answer = re.match(r'[\d\.eE-]+', line.split()[2]).group(0)
+            except AttributeError:
+                answer = 'Inf'
     return time, answer
 
 def parse_dir(directory, additional_data = {}):
@@ -45,17 +48,17 @@ def parse_dir(directory, additional_data = {}):
     return data
 
 data = []
-#data += parse_dir('results/Grid/Ratio_50/', {'dataset': 'Grid-50'})
-#data += parse_dir('results/Grid/Ratio_75/', {'dataset': 'Grid-75'})
-#data += parse_dir('results/Grid/Ratio_90/', {'dataset': 'Grid-90'})
-#data += parse_dir('results/DQMR/qmr-100/', {'dataset': 'DQMR-100'})
-#data += parse_dir('results/DQMR/qmr-50/', {'dataset': 'DQMR-50'})
-#data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
-#data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
+data += parse_dir('results/Grid/Ratio_50/', {'dataset': 'Grid-50'})
+data += parse_dir('results/Grid/Ratio_75/', {'dataset': 'Grid-75'})
+data += parse_dir('results/Grid/Ratio_90/', {'dataset': 'Grid-90'})
+data += parse_dir('results/DQMR/qmr-100/', {'dataset': 'DQMR-100'})
+data += parse_dir('results/DQMR/qmr-50/', {'dataset': 'DQMR-50'})
+data += parse_dir('results/DQMR/qmr-60/', {'dataset': 'DQMR-60'})
+data += parse_dir('results/DQMR/qmr-70/', {'dataset': 'DQMR-70'})
 data += parse_dir('results/Plan_Recognition/without_evidence/', {'dataset': 'Plan Recognition'})
 data += parse_dir('results/Plan_Recognition/with_evidence/', {'dataset': 'Plan Recognition'})
-#data += parse_dir('results/2004-pgm/', {'dataset': '2004-PGM'})
[…]

### 2020-12-16 doc/paper1/paper.tex
Initial setup for a new BN preprocessor (and moving some files around)

--- 2020-08-27 paper/paper.tex
@@
 \appendix
-\section{Proofs}
+\section{Technical Appendix}
+
+\subsection{Proofs}
 
@@
 
+\subsection{Reproducibility Checklist}
+
+Here we provide the rationale behind some of our answers to the questions in the
+reproducibility checklist.
+\begin{itemize}
+%\item The authors are not aware of any significant limitations or technical
+%  assumptions worth mentioning.
+\item The proof of Theorem~2 is not explicitly included as the idea behind the
+  proof is illustrated via an example.
+\item While we provide citations for papers that describe and/or introduce most
+  of the Bayesian networks used in our experiments, some of the classical
+  Bayesian networks used in the experiments are widely used and never cited.
+  Their origin can sometimes be traced to groups of people but not specific
+  papers.
+\item For our evaluation metrics, we count numbers of instances that were
+  solved using each encoding, numbers of instances where each encoding
+  outperformed others (including situations when multiple runs of the algorithm
+  result in exactly the same amount of time), and numbers of instances that are
+  solved by using only one encoding. As these metrics are quite elementary and
+  secondary to the cumulative and scatter plots, we do not describe the
+  motivation for using them.
+\item None of the plots or metrics in the paper have any measure of error
+  associated with them. For Figure~2 and Table~2, this is because each curve or
+  number is interpreted as a statistic of a single experiment. Figure~3, on the
+  other hand, provides a visual summary of every single experimental run.
+\end{itemize}
+
 \end{document}

### 2020-12-16 tools/analyse.R

@@ -8,7 +8,7 @@ require(ggpubr)
 require(tidyr)
 
 TIMEOUT <- 1000
-data <- read.csv("../results.csv", header = TRUE, sep = ",")
+data <- read.csv("../results/results.csv", header = TRUE, sep = ",")
 data$inference_time[is.na(data$inference_time)] <- TIMEOUT
 min.time <- min(min(data$encoding_time[data$encoding_time > 0]),
                 min(data$inference_time[data$inference_time > 0]))

### 2020-12-16 tools/parse.py

@@ -65,7 +65,7 @@ fieldnames = set()
 for d in data:
     fieldnames.update(d.keys())
 
-with open('results.csv', 'w', newline='') as csvfile:
+with open('results/results.csv', 'w', newline='') as csvfile:
     writer = csv.DictWriter(csvfile, fieldnames=fieldnames)
     writer.writeheader()
     for d in data:

### 2020-12-16 tools/trim_bn/trim_bn.cpp

@@ -1,0 +1,14 @@
+#include "../../deps/cxxopts.hpp"
+
+int main(int argc, char *argv[]) {
+  cxxopts::Options options("./trim_bn", "Trim a Bayesian network by removing variables irrelevant to the query");
+  options.add_options()
+    ("n,network", "a Bayesian network (in one of DNE/NET/Hugin formats)", cxxopts::value<std::string>())
+    ("e,evidence", "(optional) evidence file (in the INST format)", cxxopts::value<std::string>())
+    ;
+  auto result = options.parse(argc, argv);
+  if (!result.count("network")) {
+    std::cout << options.help() << std::endl;
+    return 0;
+  }
+}

### 2021-02-07 doc/paper2/paper.tex
New paper v1

--- 2020-11-25 paper2/paper.tex
@@
-\documentclass{article}
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
-\usepackage{ijcai21}
-\usepackage{times}
-\usepackage{soul}
-\usepackage{url}
-\usepackage[hidelinks]{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage[small]{caption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{booktabs}
-\urlstyle{same}
+\documentclass{uai2021} % for initial submission
+% \documentclass[accepted]{uai2021} % after acceptance, for a revised
+                                    % version; also before submission to
+                                    % see how the non-anonymous paper
+                                    % would look like
+%% There is a class option to choose the math font
+% \documentclass[mathfont=cm]{uai2021} % Computer Modern math instead of
+                                       % ptmx, like default for UAI ≤2020
+% \documentclass[mathfont=newtx]{uai2021} % newtx fonts (improves upon
+                                          % ptmx; less tested, no support)
+% NOTE: Only keep *one* line above as appropriate, as it will be replaced
+%       automatically for papers to be published. Do not make any other
+%       change above this note for an accepted version.
+
+%% Choose your variant of English; be consistent
+% \usepackage[american]{babel}
+\usepackage[british]{babel}
+
+%% Some suggested packages, as needed:
+\usepackage{natbib} % has a nice set of citation styles and commands
+    \bibliographystyle{plainnat}
+    \renewcommand{\bibsection}{\subsubsection*{References}}
+\usepackage{mathtools} % amsmath with fixes and additions
+\usepackage[binary-units]{siunitx} % for proper typesetting of numbers and units
+\usepackage{booktabs} % commands to create good-looking tables
+\usepackage[table]{xcolor}
+\usepackage{tikz} % nice language for creating drawings and diagrams
 
@@
 \usepackage[capitalise]{cleveref}
+\usepackage{multirow}
 \usepackage{amsfonts}
-\usepackage{thmtools}
+\usepackage{amsthm}
 \usepackage{thm-restate}
+\usepackage{subcaption}
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage[binary-units]{siunitx}
-\usepackage[inline]{enumitem}
-\usepackage[table]{xcolor}
-\usepackage{multirow}
-\usepackage{subcaption}
-\usepackage{tikz}
-
-% the following package is optional:
-%\usepackage{latexsym}
-
-% See https://www.overleaf.com/learn/latex/theorems_and_proofs
-% for a nice explanation of how to define new theorems, but keep
-% in mind that the amsthm package is already included in this
-% template and that you must *not* alter the styling.
-\newtheorem{example}{Example}
+
 \newtheorem{theorem}{Theorem}
 \newtheorem{lemma}{Lemma}
+\theoremstyle{definition}
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
 \DeclareMathOperator{\im}{im}
-\newcommand{\etal}{\textit{et al}.}
-\Crefname{algocf}{Algorithm}{Algorithms}
-\Crefname{figure}{Figure}{Figures}
 
@@
 
-% Following comment is from ijcai97-submit.tex:
-% The preparation of these files was supported by Schlumberger Palo Alto
-% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
-% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
-% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
-% preparation.
-
-% These instructions can be modified and used in other conferences as long
-% as credit to the authors and supporting agencies is retained, this notice
-% is not changed, and further modification or reuse is not restricted.
-% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
-% contacts for providing assistance without their prior permission.
-
-% To use for other conferences, change references to files and the
-% conference appropriate and use other authors, contacts, publishers, and
-% organizations.
-% Also change the deadline and address for returning papers and the length and
-% page charge instructions.
-% Put where the files are available in the appropriate places.
-
-%PDF Info Is REQUIRED.
-\pdfinfo{
-/TemplateVersion (IJCAI.2021.0)
+\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
+
+% The standard author block has changed for UAI 2021 to provide
+% more space for long author lists and allow for complex affiliations
+%
+% All author information is authomatically removed by the class for the
+% anonymous submission version of your paper, so you can already add your
+% information below.
+%
+% Add authors in order of decreasing contribution
+\author[1]{\href{mailto:Harry Q. Bovik <harryq@example.edu>?Subject=Your UAI 2021 paper}{Harry~Q.~Bovik}{}} % Lead author
+\author[2]{Coauthor~One}
+\author[1,2]{Coauthor~Two}
+\author[3]{Further~Coauthor}
+\author[1]{Further~Coauthor}
+\author[3]{Further~Coauthor}
+\author[3,1]{Further~Coauthor}
+% Add affiliations after the authors
+\affil[1]{%
+    Computer Science Dept.\\
+    Cranberry University\\
+    Pittsburgh, Pennsylvania, USA
 }
-
-\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
-
-% Single author syntax
-% \author{
-%     Zhi-Hua Zhou
-%     \affiliations
-%     Nanjing University
-%     \emails
-%     pcchair@ijcai-21.org
-% }
-
-% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
-% Check the ijcai21-multiauthor.tex file for detailed instructions
-% \iffalse
-% \author{
-% First Author$^1$
-% \and
-% Second Author$^2$\and
-% Third Author$^{2,3}$\And
-% Fourth Author$^4$
-% \affiliations
-% $^1$First Affiliation\\
-% $^2$Second Affiliation\\
-% $^3$Third Affiliation\\
-% $^4$Fourth Affiliation
-% \emails
-% \{first, second\}@example.com,
-% third@other.example.com,
-% fourth@example.com
-% }
-% \fi
+\affil[2]{%
+    Affiliation\\
+    Address\\
+    …
+}
+\affil[3]{…}
 
 \begin{document}
-
 \maketitle
@@
 Weighted model counting (WMC), i.e., an extension of model counting ($\#\SAT{}$)
-that assigns a weight to every model \cite{DBLP:conf/aaai/SangBK05}, has emerged
-as one of the most dominant and competitive approaches for handling inference
-tasks in a wide range of formalisms including Bayesian networks
-\cite{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906}, probabilistic
-graphical models more generally \cite{DBLP:conf/ecsqaru/ChoiKD13}, and
+that assigns a weight to every model \citep{DBLP:conf/aaai/SangBK05}, has
+emerged as one of the most dominant and competitive approaches for handling
+inference tasks in a wide range of formalisms including Bayesian networks
+\citep{DBLP:conf/aaai/SangBK05,DBLP:books/daglib/0024906}, probabilistic
+graphical models more generally \citep{DBLP:conf/ecsqaru/ChoiKD13}, and
 probabilistic programs
-\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089}.
+\citep{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089}.
 Over the last fifteen years, WMC has been extended and generalised in many ways,
 e.g., to handle continuous probability distributions
-\cite{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
-\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
-domains \cite{DBLP:conf/aaai/Belle17}. Furthermore, by generalising the notion
+\citep{DBLP:conf/ijcai/BellePB15}, first-order probabilistic theories
+\citep{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}, and infinite
+domains \citep{DBLP:conf/aaai/Belle17}. Furthermore, by generalising the notion
 of weights to an arbitrary semiring, a range of other problems are also captured
-\cite{DBLP:journals/japll/KimmigBR17}. Exact WMC solvers typically rely on
+\citep{DBLP:journals/japll/KimmigBR17}. Exact WMC solvers typically rely on
 either knowledge compilation
-\cite{DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17} or exhaustive DPLL
-search \cite{DBLP:conf/aaai/SangBK05}, whereas approximate solvers work by
-sampling \cite{DBLP:conf/aaai/ChakrabortyFMSV14} and performing local search
-\cite{DBLP:conf/sat/WeiS05}.
+\citep{DBLP:conf/ijcai/OztokD15,DBLP:conf/ijcai/LagniezM17} or exhaustive DPLL
+search \citep{DBLP:conf/aaai/SangBK05}, whereas approximate solvers work by
+sampling \citep{DBLP:conf/aaai/ChakrabortyFMSV14} and performing local search
+\citep{DBLP:conf/sat/WeiS05}.
 
@@
 case. We prove the correctness of the encoding and show how a state-of-the-art
-WMC solver ADDMC \cite{DBLP:conf/aaai/DudekPV20} can be adapted to the new
+WMC solver ADDMC \citep{DBLP:conf/aaai/DudekPV20} can be adapted to the new
 format. ADDMC is a recently-proposed algorithm for WMC based on manipulating
@@
 functions known as algebraic decision diagrams (ADDs)
-\cite{DBLP:journals/fmsd/BaharFGHMPS97}. Finally, in \cref{sec:experiments}, we
+\citep{DBLP:journals/fmsd/BaharFGHMPS97}. Finally, in \cref{sec:experiments}, we
 show how the new encoding results in faster inference on the vast majority of
@@
 
-%making it applicable to domains such as parsing, dynamic programming, constraint
-%programming, databases, and networks.
-
-%conditional weights allow us to represent
-%probabilities in a manner that is both efficient and interpretable. Not having
-%additional variables that are only needed to manipulate the representation into
-%a specific format helps with both efficiency and interpretability. Similarly to
-%Bayesian networks, the size of the representation scales with independence.
-
 \section{Related Work} \label{sec:related}
 
-\paragraph{WMC for Bayesian networks.} Hitherto, four techniques have been
-proposed for encoding Bayesian networks into instances of WMC. We will identify
-them based on the initials of authors as well as publications years:
-\texttt{d02} \cite{DBLP:conf/kr/Darwiche02}, \texttt{sbk05}
-\cite{DBLP:conf/aaai/SangBK05}, \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05},
-and \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}. Below we summarise the
-observed performance differences among them. Sang
-\etal{}~\shortcite{DBLP:conf/aaai/SangBK05} claim that \texttt{sbk05} is a
-smaller encoding than \texttt{d02} with respect to both the number of clauses
-and the number of variables but provide no experimental comparison. Chavira and
-Darwiche~\shortcite{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with
+Hitherto, four techniques have been proposed for encoding Bayesian networks into
+instances of WMC. We will identify them based on the initials of authors as well
+as publications years: \texttt{d02} \citep{DBLP:conf/kr/Darwiche02},
+\texttt{sbk05} \citep{DBLP:conf/aaai/SangBK05}, \texttt{cd05}
+\citep{DBLP:conf/ijcai/ChaviraD05}, and \texttt{cd06}
+\citep{DBLP:conf/sat/ChaviraD06}. Below we summarise the observed performance
+differences among them. \citet{DBLP:conf/aaai/SangBK05} claim that
+\texttt{sbk05} is a smaller encoding than \texttt{d02} with respect to both the
+number of clauses and the number of variables but provide no experimental
+comparison. \citet{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with
 \texttt{d02} by measuring the time it takes to compile either encoding into an
@@
 authors perform two sets of experiments (that are relevant to this summary)
-\cite{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
+\citep{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
 \texttt{cd06} encodings into d-DNNF (i.e., deterministic decomposable negation
-normal form \cite{DBLP:journals/jancl/Darwiche01}), measuring both compilation
+normal form \citep{DBLP:journals/jancl/Darwiche01}), measuring both compilation
 time and numbers of edges in the d-DNNF diagram. The results are mostly in
 favour of \texttt{cd06}. Second, they compare the inference time of
-\texttt{sbk05} run with Cachet \cite{DBLP:conf/sat/SangBBKP04} with the compile
+\texttt{sbk05} run with Cachet \citep{DBLP:conf/sat/SangBBKP04} with the compile
 times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
@@
 
-\paragraph{ADDs and their use in inference.} ADDs provide an efficient way to
-manipulate functions from a Boolean algebra to any algebraic structure (most
-commonly real numbers) \cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been
-used to represent value functions in Markov decision processes (MDPs)
-\cite{DBLP:conf/uai/HoeySHB99} and extended to handle first-order MDPs
-\cite{DBLP:journals/ai/SannerB09} and discrete and continuous state MDPs
-\cite{DBLP:conf/uai/SannerDB11}. The latter extension has also been used for
-weighted model integration---an extension of WMC that can handle continuous
-variables \cite{DBLP:conf/ijcai/KolbMSBK18}. For Bayesian networks, ADDS have
-been used to represent each conditional probability table (CPT) as an ADD
-\cite{DBLP:conf/icml/ZhaoMP15} and as a combination of ADDs and arithmetic
-circuits \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous
-in this situation because of their ability to fully exploit context-specific
-independence, i.e., the observable structure within a CPT that is not inherited
-from the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.
+% \paragraph{ADDs and their use in inference.} ADDs provide an efficient way to
+% manipulate functions from a Boolean algebra to any algebraic structure (most
+% commonly real numbers) \citep{DBLP:journals/fmsd/BaharFGHMPS97}. They have been
+% used to represent value functions in Markov decision processes (MDPs)
+% \citep{DBLP:conf/uai/HoeySHB99} and extended to handle first-order MDPs
+% \citep{DBLP:journals/ai/SannerB09} and discrete and continuous state MDPs
+% \citep{DBLP:conf/uai/SannerDB11}. The latter extension has also been used for
+% weighted model integration---an extension of WMC that can handle continuous
+% variables \citep{DBLP:conf/ijcai/KolbMSBK18}. For Bayesian networks, ADDS have
+% been used to represent each conditional probability table (CPT) as an ADD
+% \citep{DBLP:conf/icml/ZhaoMP15} and as a combination of ADDs and arithmetic
+% circuits \citep{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous
+% in this situation because of their ability to fully exploit context-specific
+% independence, i.e., the observable structure within a CPT that is not inherited
+% from the structure of the Bayesian network \citep{DBLP:conf/uai/BoutilierFGK96}.
 
@@
 \begin{table*}
+  \caption{Notation for a logic with two atoms. The elements in both columns are
+    listed in the same order.}
+  \label{tbl:notation_example}
   \centering
@@
   \end{tabular}
-  \caption{Notation for a logic with two atoms. The elements in both columns are
-    listed in the same order.}
-  \label{tbl:notation_example}
 \end{table*}
@@
 can be efficiently represented using ADDs. Furthermore, all of the operations
-are supported by the CUDD \cite{somenzi1998cudd} package that is used by ADDMC
-for ADD manipulation \cite{DBLP:conf/aaai/DudekPV20}. The definitions of
+are supported by the CUDD \citep{somenzi1998cudd} package that is used by ADDMC
+for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The definitions of
 multiplication and projection are as defined by
-Dudek \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20}, while others are new.
+\citet{DBLP:conf/aaai/DudekPV20}, while others are new.
 
@@
 and $\mu(a \lor b) = \mu(a) + \mu(b)$ for all $a, b \in 2^{2^U}$ whenever $a
-\land b = \bot$ \cite{gaifman1964concerning,DBLP:books/daglib/0090259}. A
+\land b = \bot$ \citep{gaifman1964concerning,DBLP:books/daglib/0090259}. A
 \emph{weight function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$. A
@@
 $\mathcal{L}$ with a sole axiom $a$. Then $\Delta$ has two models: $\{ a, b \}$
-and $\{ a, \neg b \}$ and its WMC \cite{DBLP:journals/ai/ChaviraD08} is
+and $\{ a, \neg b \}$ and its WMC \citep{DBLP:journals/ai/ChaviraD08} is
 \begin{equation} \label{eq:wmc_example}
@@
 functions often results in weight functions with smaller domains which leads to
-increased efficiency and decreased memory usage \cite{DBLP:conf/aaai/DudekPV20}.
-We can easily generalise this example further.
+increased efficiency and decreased memory usage
+\citep{DBLP:conf/aaai/DudekPV20}. We can easily generalise this example further.
 
@@
 encode them into instances of WMC is by adding more literals
-\cite{DBLP:journals/ai/ChaviraD08}. We can use the measure-theoretic perspective
-on WMC to show that this is always possible, however, as ensuing sections will
-demonstrate, it often makes the inference task much harder in
+\citep{DBLP:journals/ai/ChaviraD08}. We can use the measure-theoretic
+perspective on WMC to show that this is always possible, however, as ensuing
+sections will demonstrate, it often makes the inference task much harder in
 practice.\footnote{The proofs of this and other theoretical results can be found
@@
   \end{subfigure}
-  \caption{An example Bayesian network with its CPTs}
+  \caption{An example Bayesian network with its CPTs.}
   \label{fig:example_bn}
@@
 full probability distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X
-\mid \mathrm{pa}(X))$ \cite{DBLP:books/daglib/0023820}. For discrete Bayesian
+\mid \mathrm{pa}(X))$ \citep{DBLP:books/daglib/0023820}. For discrete Bayesian
 networks (and we only consider discrete networks in this paper), each factor of
@@
 \begin{algorithm}[t]
+  \caption{Encoding a Bayesian network.}
+  \label{alg:encoding}
   \KwData{vertices $\mathcal{V}$, probability distribution $\Pr$}
@@
   \Return{$\phi$}\;
-  \caption{Encoding a Bayesian network}
-  \label{alg:encoding}
 \end{algorithm}
@@
 This function can be represented by an ADD
-\cite{DBLP:journals/fmsd/BaharFGHMPS97}. The core of ADDMC works by taking an
+\citep{DBLP:journals/fmsd/BaharFGHMPS97}. The core of ADDMC works by taking an
 ADD $\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product of smaller
 ADDs) and returning $(\exists_U\psi)(\emptyset)$
-\cite{DBLP:conf/aaai/DudekPV20}. In this section, we prove that the function
+\citep{DBLP:conf/aaai/DudekPV20}. In this section, we prove that the function
 $\phi$ produced by \cref{alg:encoding} can be used by ADDMC to correctly compute
@@
 \emph{extended weight clauses} to the WMC format used by Cachet
-\cite{DBLP:conf/sat/SangBBKP04}. For instance, here is a representation of the
+\citep{DBLP:conf/sat/SangBBKP04}. For instance, here is a representation of the
 Bayesian network from \cref{fig:example_bn}:
@@
 ADDMC\footnote{\url{https://github.com/vardigroup/ADDMC}}
-\cite{DBLP:conf/aaai/DudekPV20} needed to adapt it to the new format.
-
-First, ADDMC constructs the \emph{Gaifman graph} \cite{gaifman1982local} of the
+\citep{DBLP:conf/aaai/DudekPV20} needed to adapt it to the new format.
+
+First, ADDMC constructs the \emph{Gaifman graph} \citep{gaifman1982local} of the
 input CNF formula as an aid for the algorithm's heuristics. This graph has as
@@
 relaxed encodings that contain extra models and thus yield incorrect
-probabilities \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}. These
+probabilities \citep{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}. These
 additional models are supposed to be filtered out during circuit compilation
-\cite{DBLP:conf/ijcai/ChaviraD05}, but this is not easily achievable with ADDMC.
-Nonetheless, we include both encodings in the experiments.
+\citep{DBLP:conf/ijcai/ChaviraD05}, but this is not easily achievable with
+ADDMC. Nonetheless, we include both encodings in the experiments.
 
@@
 which relies on solving $\NP{}$-complete problems as part of the encoding process
-\cite{DBLP:conf/sat/ChaviraD06}.
+\citep{DBLP:conf/sat/ChaviraD06}.
 
@@
 \item DQMR and
-\item Grid networks as described by Sang
-  \etal{}~\shortcite{DBLP:conf/aaai/SangBK05},
+\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
 \item Mastermind, and
-\item Random Blocks from the work of Chavira
-  \etal{}~\shortcite{DBLP:journals/ijar/ChaviraDJ06},
+\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
 \item remaining binary Bayesian networks that include Plan Recognition
-  \cite{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
-  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
+  \citep{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
+  \citep{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
 \item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
@@
 
-\begin{figure} % TODO: update
+\begin{figure}
   \centering
-  \input{../paper1/cumulative.tex}%
+  \input{cumulative.tex}%
   \caption{Cumulative number of instances solved by ADDMC over time using each
-    encoding}
+    encoding.}
   \label{fig:cumulative}
@@
   \centering
+  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
+    encoding (uniquely, faster than with others, and in total) under the
+    described constraints.}%
   \begin{tabular}{lrrr}
@@
   \end{tabular}
-  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
-    encoding (uniquely, faster than with others, and in total) under the
-    described constraints}%
   \label{tbl:tallies}
@@
 
-\begin{figure*} % TODO: update
+\begin{figure*}
   \centering
-  \input{../paper1/scatter.tex}%
+  \input{scatter.tex}%
   \caption{ADDMC inference time using \texttt{cw} compared to \texttt{d02}
@@
   \centering
+  \caption{Asymptotic upper bounds on the numbers of variables and clauses/ADDs
+    for each encoding.}
+  \label{tbl:asymptotes}
   \begin{tabular}{lcc}
@@
     \midrule
-    \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(nv^{d+1})$ \\
-    \texttt{cw} & $\mathcal{O}(nv)$ & $\mathcal{O}(nv^2)$ \\
-    \texttt{d02} & $\mathcal{O}(nv^{d+1})$ & $\mathcal{O}(ndv^{d+1})$ \\
+    \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $O(nv^{d+1})$ & $O(nv^{d+1})$ \\
+    \texttt{cw} & $O(nv)$ & $O(nv^2)$ \\
+    \texttt{d02} & $O(nv^{d+1})$ & $O(ndv^{d+1})$ \\
     \bottomrule
   \end{tabular}
-  \caption{Asymptotic upper bounds on the numbers of variables and clauses/ADDs
-    for each encoding}
-  \label{tbl:asymptotes}
 \end{table}
@@
 encoding as a multiplicative factor of the ADD that represents the entire WMC
-instance \cite{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings, each
+instance \citep{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings, each
 weight is also a factor, but that does not affect the asymptotic bounds in the
@@
 
-% While some ADDs may be larger as a result, experimental evidence still shows
-% significant performance benefits.
-
 \section{Discussion and Conclusion}
@@
 WMC was originally motivated by an appeal to the success of \SAT{} solvers in
-efficiently tackling an $\NP{}$-complete problem \cite{DBLP:conf/aaai/SangBK05}.
-ADDMC does not rely on \SAT{}-based algorithmic techniques, and our proposed
-format diverges even more from the DIMACS CNF format for Boolean formulas. To
-what extent are \SAT{}-based methods still applicable? The answer depends
-significantly on the problem domain. For Bayesian networks, the rules describing
-that each random variable can only be associated with exactly one value were
-still encoded as clauses. As has been noted previously
-\cite{DBLP:conf/sat/ChaviraD06}, rows in CPTs with probabilities equal to zero
-or one can be represented as clauses as well. Therefore, our work can be seen as
-proposing a middle ground between $\#\SAT{}$ and probabilistic inference.
-
-While we chose to use ADDMC \cite{DBLP:conf/aaai/DudekPV20} as the WMC algorithm
-and Bayesian networks as a canonical example of a probabilistic inference task,
-these are only examples meant to illustrate the broader idea that choosing a
-more expressive representation of weights can outperform increasing the size of
-the problem to keep the weights simple. Indeed, in this work, we have provided a
-new theoretical perspective on the expressive power of WMC and illustrated the
-empirical benefits of that perspective. The same idea can be adapted to other
-inference problem domains such as probabilistic programs
-\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
-well as to search-based solvers such as Cachet \cite{DBLP:conf/sat/SangBBKP04},
+efficiently tackling an $\NP{}$-complete problem
+\citep{DBLP:conf/aaai/SangBK05}. ADDMC does not rely on \SAT{}-based algorithmic
+techniques, and our proposed format diverges even more from the DIMACS CNF
+format for Boolean formulas. To what extent are \SAT{}-based methods still
+applicable? The answer depends significantly on the problem domain. For Bayesian
+networks, the rules describing that each random variable can only be associated
+with exactly one value were still encoded as clauses. As has been noted
+previously \citep{DBLP:conf/sat/ChaviraD06}, rows in CPTs with probabilities
+equal to zero or one can be represented as clauses as well. Therefore, our work
+can be seen as proposing a middle ground between $\#\SAT{}$ and probabilistic
+inference.
+
+While we chose to use ADDMC \citep{DBLP:conf/aaai/DudekPV20} as the WMC
+algorithm and Bayesian networks as a canonical example of a probabilistic
+inference task, these are only examples meant to illustrate the broader idea
+that choosing a more expressive representation of weights can outperform
+increasing the size of the problem to keep the weights simple. Indeed, in this
+work, we have provided a new theoretical perspective on the expressive power of
+WMC and illustrated the empirical benefits of that perspective. The same idea
+can be adapted to other inference problem domains such as probabilistic programs
+\citep{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
+well as to search-based solvers such as Cachet \citep{DBLP:conf/sat/SangBBKP04},
 although the extension may be less straightforward for other WMC techniques.
 
-%An additional benefit of conditional weights is that a more expressive format
-%makes it easier to invent new WMC encodings.
-%Filtering out ADDs that have nothing to do with the answer helps
-%  tremendously, but I'm purposefully not doing that.
-
-% \section*{Acknowledgements}
-
-% This work has made use of the resources provided by the Edinburgh Compute and
-% Data Facility (ECDF) (\url{http://www.ecdf.ed.ac.uk/}).
-
+\begin{contributions} % will be removed in pdf for initial submission,
+                      % so you can already fill it to test with the
+                      % ‘accepted’ class option
+    Briefly list author contributions.
+    This is a nice way of making clear who did what and to give proper credit.
+
+    H.~Q.~Bovik conceived the idea and wrote the paper.
+    Coauthor One created the code.
+    Coauthor Two created the figures.
+\end{contributions}
+
+\begin{acknowledgements} % will be removed in pdf for initial submission,
+                         % so you can already fill it to test with the
+                         % ‘accepted’ class option
+    Briefly acknowledge people and organizations here.
+
+    \emph{All} acknowledgements go in this section.
+\end{acknowledgements}
+
+\newpage
+\bibliography{paper}
+
+\newpage
 \appendix
@@
   \begin{itemize}
-  \item the proof of Theorem~1 by Dudek
-    \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20};
+  \item the proof of Theorem~1 by \citet{DBLP:conf/aaai/DudekPV20};
   \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
@@
 
-\bibliographystyle{named}
-\bibliography{paper}
-
 \end{document}

### 2021-02-07 tools/analyse.R

@@ -87,10 +87,10 @@ instance_to_min_time0 <- df$time_min0
 names(instance_to_min_time0) <- df$instance
 df.temp <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS",
                       answer = NA, time = instance_to_min_time[df$instance],
-                      add_width= max(data$add_width))
+                      add_width= max(data$add_width), treewidth = max(data$treewidth))
 df.temp2 <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS*",
                        answer = NA, time = instance_to_min_time0[df$instance],
-                       add_width = max(data$add_width))
+                       add_width = max(data$add_width), treewidth = max(data$treewidth))
 data_sum <- rbind(data_sum, df.temp, df.temp2)
 rownames(data_sum) <- c()
 
@@ -131,10 +131,11 @@ for (column in answer_columns) {
 
 # Fastest
 sum(!is.na(df$answer_new_bklm16) & abs(df$time_new_bklm16 - df$time_min) < 1e-5)
-sum(!is.na(df$answer_new_cd05) & abs(df$time_new_cd05 - df$time_min) < 1e-5)
-sum(!is.na(df$answer_new_cd06) & abs(df$time_new_cd06 - df$time_min) < 1e-5)
-sum(!is.na(df$answer_new_cw) & abs(df$time_new_cw - df$time_min) < 1e-5)
+sum(!is.na(df$answer_new_bklm16pp) & abs(df$time_new_bklm16pp - df$time_min) < 1e-5)
+sum(!is.na(df$answer_new_cd05pp) & abs(df$time_new_cd05pp - df$time_min) < 1e-5)
+sum(!is.na(df$answer_new_cd06pp) & abs(df$time_new_cd06pp - df$time_min) < 1e-5)
 sum(!is.na(df$answer_new_d02) & abs(df$time_new_d02 - df$time_min) < 1e-5)
+sum(!is.na(df$answer_new_d02pp) & abs(df$time_new_d02pp - df$time_min) < 1e-5)
 sum(!is.na(df$answer_new_sbk05) & abs(df$time_new_sbk05 - df$time_min) < 1e-5)
 
 sum(!is.na(df$answer_old_bklm16) & abs(df$time_old_bklm16 - df$time_min) < 1e-5)
@@ -145,10 +146,11 @@ sum(!is.na(df$answer_old_sbk05) & abs(df$time_old_sbk05 - df$time_min) < 1e-5)
 
[…]

### 2021-02-08 tools/analyse.R
Updated plots

@@ -1,14 +1,14 @@
-require(ggplot2)
-require(scales)
-require(dplyr)
-require(maditr)
-require(purrr)
-require(tikzDevice)
-require(ggpubr)
-require(tidyr)
+library(ggplot2)
+library(scales)
+library(dplyr)
+library(maditr)
+library(purrr)
+library(tikzDevice)
+library(ggpubr)
+library(tidyr)
 
 # TODO: plot treewidth vs add width
-data <- read.csv("../results/results.csv", header = TRUE, sep = ",")
+data <- read.csv("../results/old_results.csv", header = TRUE, sep = ",")
 
 # TODO: remove (just for testing)
 data <- data[data$dataset != "2004-PGM",]
@@ -49,9 +49,12 @@ data_sum <- data_merged
 data_sum$time <- data_sum$encoding_time + data_sum$inference_time
 data_sum <- subset(data_sum, select = -c(inference_time, encoding_time))
 
+# df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
+#             fun.aggregate = NULL,
+#             value.var = c("answer", "time", "add_width"))
 df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
             fun.aggregate = NULL,
-            value.var = c("answer", "time", "add_width"))
+            value.var = c("answer", "time"))
 time_columns <- Filter(function(x) startsWith(x, "time_"), names(df))
 time_columns0 <- time_columns[!grepl('pp$', time_columns)]
 for (column in time_columns) {
@@ -85,12 +88,16 @@ instance_to_min_time <- df$time_min
 names(instance_to_min_time) <- df$instance
 instance_to_min_time0 <- df$time_min0
 names(instance_to_min_time0) <- df$instance
+# df.temp <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS",
+#                       answer = NA, time = instance_to_min_time[df$instance],
+#                       add_width= max(data$add_width), treewidth = max(data$treewidth))
+# df.temp2 <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS*",
+#                        answer = NA, time = instance_to_min_time0[df$instance],
+#                        add_width = max(data$add_width), treewidth = max(data$treewidth))
 df.temp <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS",
[…]

### 2021-02-08 tools/analyse_addmc.R

@@ -1,0 +1,139 @@
+library(ggplot2)
+library(scales)
+library(dplyr)
+library(maditr)
+library(purrr)
+library(tikzDevice)
+library(ggpubr)
+library(tidyr)
+library(RColorBrewer)
+
+data <- read.csv("../results/old_results.csv", header = TRUE, sep = ",")
+data <- data[!(data$encoding == "cd05" & data$novelty == "new"),]
+data <- data[!(data$encoding == "cd06" & data$novelty == "new"),]
+
+TIMEOUT <- 1000
+data$inference_time[is.na(data$inference_time)] <- TIMEOUT
+min.time <- min(min(data$encoding_time[data$encoding_time > 0]),
+                min(data$inference_time[data$inference_time > 0]))
+data$encoding_time[data$encoding_time == 0] <- min.time
+data$inference_time[data$inference_time == 0] <- min.time
+data$answer[data$encoding_time >= TIMEOUT] <- NA
+data$answer[data$inference_time >= TIMEOUT] <- NA
+data$encoding_time[is.na(data$answer)] <- TIMEOUT
+data$inference_time[is.na(data$answer)] <- TIMEOUT
+
+# Merge 'novelty' and 'encoding' columns
+data_merged <- data
+data_merged$encoding <- paste(data_merged$novelty, data_merged$encoding, sep = "_")
+data_merged <- subset(data_merged, select = -c(novelty))
+
+# Add encoding and inference times
+data_sum <- data_merged
+data_sum$time <- data_sum$encoding_time + data_sum$inference_time
+data_sum <- subset(data_sum, select = -c(inference_time, encoding_time))
+
+df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
+            fun.aggregate = min,
+            value.var = c("answer", "time"))
+time_columns <- Filter(function(x) startsWith(x, "time_"), names(df))
+for (column in time_columns) {
+  df[is.na(df[[column]]), column] <- 2 * TIMEOUT
+}
+
+df$major.dataset <- "Non-binary"
+df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
+df$major.dataset[grepl("Grid", df$instance, fixed = TRUE)] <- "Grid"
+df$major.dataset[grepl("mastermind", df$instance, fixed = TRUE)] <- "Mastermind"
+df$major.dataset[grepl("blockmap", df$instance, fixed = TRUE)] <- "Random Blocks"
[…]

### 2021-02-08 doc/paper2/paper.tex
Updated plots
Fonts, references, etc.

@@
 \DeclareMathOperator{\im}{im}
+\Crefname{algocf}{Algorithm}{Algorithms}
 
@@
   of extra literals, we develop a new WMC encoding for Bayesian networks and
-  adapt a state-of-the-art WMC algorithm ADDMC to the new format. Our
+  adapt a state-of-the-art WMC algorithm \textsf{ADDMC} to the new format. Our
   experiments show that the new encoding results in significantly faster
@@
 \section{Introduction}
+
+TODO: introduce (also talk more about how Cachet and Ace are used)
+\begin{itemize}
+\item \texttt{bklm16} \citep{DBLP:conf/ecai/BartKLM16}
+\item \textsf{query-dnnf}
+  \footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
+\item \textsf{DPMC} \citep{DBLP:conf/cp/DudekPV20}
+\item tackle a comparable problem, but their encoding was never implemented or
+  empirically tested (i.e., the implementation is left as future work)
+  \citep{DBLP:conf/scai/VomlelT13}
+\end{itemize}
 
@@
 case. We prove the correctness of the encoding and show how a state-of-the-art
-WMC solver ADDMC \citep{DBLP:conf/aaai/DudekPV20} can be adapted to the new
-format. ADDMC is a recently-proposed algorithm for WMC based on manipulating
-functions on Boolean algebras using an efficient representation for such
-functions known as algebraic decision diagrams (ADDs)
+WMC solver \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} can be adapted to the
+new format. \textsf{ADDMC} is a recently-proposed algorithm for WMC based on
+manipulating functions on Boolean algebras using an efficient representation for
+such functions known as algebraic decision diagrams (ADDs)
 \citep{DBLP:journals/fmsd/BaharFGHMPS97}. Finally, in \cref{sec:experiments}, we
@@
 favour of \texttt{cd06}. Second, they compare the inference time of
-\texttt{sbk05} run with Cachet \citep{DBLP:conf/sat/SangBBKP04} with the compile
-times of \texttt{cd05} and \texttt{cd06}, but only on five (types of) instances.
-In these experiments, \texttt{cd06} is always faster than \texttt{cd05}, while
-the comparison with \texttt{sbk05} is mixed. Sometimes \texttt{cd06} is orders
-of magnitude faster than \texttt{sbk05}, sometimes slightly slower. The
-performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
-to judge: \texttt{sbk05} is better on three out of five instances and worse on
-the remaining two. Based on this description, one would expect \texttt{cd06} to
-be faster than both \texttt{cd05} and \texttt{sbk05}, both of which should be
-faster than \texttt{d02}. The experiments in \cref{sec:experiments}, however,
-strongly disagree with this prediction, showing that the quality of an encoding
-depends strongly on the underlying search algorithm or compilation technique.
-
-% \paragraph{ADDs and their use in inference.} ADDs provide an efficient way to
-% manipulate functions from a Boolean algebra to any algebraic structure (most
-% commonly real numbers) \citep{DBLP:journals/fmsd/BaharFGHMPS97}. They have been
-% used to represent value functions in Markov decision processes (MDPs)
-% \citep{DBLP:conf/uai/HoeySHB99} and extended to handle first-order MDPs
-% \citep{DBLP:journals/ai/SannerB09} and discrete and continuous state MDPs
-% \citep{DBLP:conf/uai/SannerDB11}. The latter extension has also been used for
-% weighted model integration---an extension of WMC that can handle continuous
-% variables \citep{DBLP:conf/ijcai/KolbMSBK18}. For Bayesian networks, ADDS have
-% been used to represent each conditional probability table (CPT) as an ADD
-% \citep{DBLP:conf/icml/ZhaoMP15} and as a combination of ADDs and arithmetic
-% circuits \citep{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous
-% in this situation because of their ability to fully exploit context-specific
-% independence, i.e., the observable structure within a CPT that is not inherited
-% from the structure of the Bayesian network \citep{DBLP:conf/uai/BoutilierFGK96}.
+\texttt{sbk05} run with \textsf{Cachet} \citep{DBLP:conf/sat/SangBBKP04} with
+the compile times of \texttt{cd05} and \texttt{cd06}, but only on five (types
+of) instances. In these experiments, \texttt{cd06} is always faster than
+\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
+\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
+slightly slower. The performance difference between \texttt{sbk05} and
+\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
+five instances and worse on the remaining two. Based on this description, one
+would expect \texttt{cd06} to be faster than both \texttt{cd05} and
+\texttt{sbk05}, both of which should be faster than \texttt{d02}. The
+experiments in \cref{sec:experiments}, however, strongly disagree with this
+prediction, showing that the quality of an encoding depends strongly on the
+underlying search algorithm or compilation technique.
 
@@
 can be efficiently represented using ADDs. Furthermore, all of the operations
-are supported by the CUDD \citep{somenzi1998cudd} package that is used by ADDMC
-for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The definitions of
-multiplication and projection are as defined by
+are supported by the CUDD \citep{somenzi1998cudd} package that is used by
+\textsf{ADDMC} for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The
+definitions of multiplication and projection are as defined by
 \citet{DBLP:conf/aaai/DudekPV20}, while others are new.
@@
 This function can be represented by an ADD
-\citep{DBLP:journals/fmsd/BaharFGHMPS97}. The core of ADDMC works by taking an
-ADD $\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product of smaller
-ADDs) and returning $(\exists_U\psi)(\emptyset)$
+\citep{DBLP:journals/fmsd/BaharFGHMPS97}. The core of \textsf{ADDMC} works by
+taking an ADD $\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product
+of smaller ADDs) and returning $(\exists_U\psi)(\emptyset)$
 \citep{DBLP:conf/aaai/DudekPV20}. In this section, we prove that the function
-$\phi$ produced by \cref{alg:encoding} can be used by ADDMC to correctly compute
-any marginal probability of the Bayesian network that was encoded as
-$\phi$.\footnote{Note that it can just as well compute \emph{any} probability
-  expressed using the random variables in $\mathcal{V}$.} We begin with
-\cref{lemma:cpt} which shows that any conditional weight function produces the
-right answer when given a valid encoding of variable-value assignments relevant
-to the CPT.
+$\phi$ produced by \cref{alg:encoding} can be used by \textsf{ADDMC} to
+correctly compute any marginal probability of the Bayesian network that was
+encoded as $\phi$.\footnote{Note that it can just as well compute \emph{any}
+  probability expressed using the random variables in $\mathcal{V}$.} We begin
+with \cref{lemma:cpt} which shows that any conditional weight function produces
+the right answer when given a valid encoding of variable-value assignments
+relevant to the CPT.
 
@@
 We end with \cref{thm:correctness} that shows how $\phi$ can be combined with an
-encoding of a single variable-value assignment so that ADDMC would compute its
-marginal probability.
+encoding of a single variable-value assignment so that \textsf{ADDMC} would
+compute its marginal probability.
 
@@
 for every subset of $\mathcal{E}^*(X)$. To encode these terms, we introduce
-\emph{extended weight clauses} to the WMC format used by Cachet
+\emph{extended weight clauses} to the WMC format used by \textsf{Cachet}
 \citep{DBLP:conf/sat/SangBBKP04}. For instance, here is a representation of the
@@
 
-\subsection{Changes to ADDMC}
+\subsection{Changes to \textsf{ADDMC}}
 
 Here we describe two changes to
-ADDMC\footnote{\url{https://github.com/vardigroup/ADDMC}}
+\textsf{ADDMC}\footnote{\url{https://github.com/vardigroup/ADDMC}}
 \citep{DBLP:conf/aaai/DudekPV20} needed to adapt it to the new format.
 
-First, ADDMC constructs the \emph{Gaifman graph} \citep{gaifman1982local} of the
-input CNF formula as an aid for the algorithm's heuristics. This graph has as
-vertices the variables of the formula, and there is an edge between two
-variables $u$ and $v$ if there is a clause in the formula that contains both $u$
-and $v$. We extend this definition to functions on Boolean algebras, i.e., the
-factors of $\phi$. For any pair of distinct variables $u, v \in U$, we draw an
-edge between them in the Gaifman graph if there is a function $\alpha\colon 2^X
-\to \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v
-\in X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges
-between all distinct pairs of variables in $\mathcal{E}^*(X)$.
-
-Second, even though the function $\phi$ produced by \cref{alg:encoding} is
-constructed to have $2^U$ as its domain, sometimes the domain is effectively
-reduced to $2^V$ for some $V \subset U$ by the ADD manipulation algorithms that
-optimise the ADD representation of a function. For a simple example, consider
-$\alpha: 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as $\alpha(\{a\}) =
-\alpha(\emptyset) = 0.5$. Then $\alpha$ can be reduced to $\alpha'\colon
-2^{\emptyset} \to \mathbb{R}_{\ge 0}$ defined as $\alpha'(\emptyset) = 0.5$. To
-compensate for these reductions, for the original WMC format with a weight
-function $w\colon U \cup \{ \neg u \mid u \in U \} \to \mathbb{R}_{\ge 0}$,
-ADDMC would multiply its computed answer by $\prod_{u \in U \setminus V} w(u) +
-w(\neg u)$. With the new WMC format, we instead multiply the answer by $2^{|U
-  \setminus V|}$. Each `excluded' variable $u \in U \setminus V$ satisfies two
-properties: all weights associated with $u$ are equal to $0.5$ (otherwise the
-corresponding CPT would depend on $u$, and $u$ would not be excluded), and all
-other CPTs are independent of $u$ (or they may have a trivial dependence, where
-the probability stays the same if $u$ is replaced with its complement). Thus,
-the CPT that corresponds to $u$ still multiplies the weight of every atom in the
-Boolean algebra by $0.5$, but the number of atoms under consideration is halved.
-To correct for this, we multiply the final answer by two for every $u \in U
-\setminus V$.
+First, \textsf{ADDMC} constructs the \emph{Gaifman graph}
+of the input CNF formula as an aid for the algorithm's
+heuristics. This graph has as vertices the variables of the formula, and there
+is an edge between two variables $u$ and $v$ if there is a clause in the formula
+that contains both $u$ and $v$. We extend this definition to functions on
+Boolean algebras, i.e., the factors of $\phi$. For any pair of distinct
+variables $u, v \in U$, we draw an edge between them in the Gaifman graph if
+there is a function $\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ that is a factor
+of $\phi$ such that $u \in X$ and $v \in X$. For instance, a factor such as
+$\mathrm{CPT}_X$ will enable edges between all distinct pairs of variables in
+$\mathcal{E}^*(X)$. Second, even though the function $\phi$ produced by
+\cref{alg:encoding} is constructed to have $2^U$ as its domain, sometimes the
+domain is effectively reduced to $2^V$ for some $V \subset U$ by the ADD
+manipulation algorithms that optimise the ADD representation of a function. For
+a simple example, consider $\alpha: 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as
+$\alpha(\{a\}) = \alpha(\emptyset) = 0.5$. Then $\alpha$ can be reduced to
+$\alpha'\colon 2^{\emptyset} \to \mathbb{R}_{\ge 0}$ defined as
+$\alpha'(\emptyset) = 0.5$. To compensate for these reductions, for the original
+WMC format with a weight function $w\colon U \cup \{ \neg u \mid u \in U \} \to
+\mathbb{R}_{\ge 0}$, \textsf{ADDMC} would multiply its computed answer by
+$\prod_{u \in U \setminus V} w(u) + w(\neg u)$. With the new WMC format, we
+instead multiply the answer by $2^{|U \setminus V|}$. Each `excluded' variable
+$u \in U \setminus V$ satisfies two properties: all weights associated with $u$
+are equal to $0.5$ (otherwise the corresponding CPT would depend on $u$, and $u$
+would not be excluded), and all other CPTs are independent of $u$ (or they may
+have a trivial dependence, where the probability stays the same if $u$ is
+replaced with its complement). Thus, the CPT that corresponds to $u$ still
+multiplies the weight of every atom in the Boolean algebra by $0.5$, but the
+number of atoms under consideration is halved. To correct for this, we multiply
+the final answer by two for every $u \in U \setminus V$.
 
@@
 In this section, we describe an experimental study comparing the five WMC
-encodings for Bayesian networks when run with ADDMC. The experiments were run on
-servers with Intel Xeon Gold 6138 and Intel Xeon E5-2630
+encodings for Bayesian networks when run with \textsf{ADDMC}. The experiments
+were run on servers with Intel Xeon Gold 6138 and Intel Xeon E5-2630
 processors\footnote{Each instance is run on the same processor for all
@@
 For all encodings other than \texttt{cw}, we use their implementation in
-Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
-\texttt{-encodeOnly} and \texttt{-noEclause} flags. However, Ace was not used to
-encode evidence, as preliminary experiments revealed that the evidence-encoding
-implementation contains bugs that can lead to incorrect answers or a Java
-exception being thrown on some instances of the data set (and the source code is
-not publicly available). Instead, we simply list all the evidence as additional
-clauses in the encoding.
+\textsf{Ace}~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
+\texttt{-encodeOnly} and \texttt{-noEclause} flags. However, \textsf{Ace} was
+not used to encode evidence, as preliminary experiments revealed that the
+evidence-encoding implementation contains bugs that can lead to incorrect
+answers or a Java exception being thrown on some instances of the data set (and
+the source code is not publicly available). Instead, we simply list all the
+evidence as additional clauses in the encoding.
 
@@
 \citep{DBLP:conf/ijcai/ChaviraD05}, but this is not easily achievable with
-ADDMC. Nonetheless, we include both encodings in the experiments.
+\textsf{ADDMC}. Nonetheless, we include both encodings in the experiments.
 
@@
 
-For experimental data, we use the Bayesian networks available with Ace and
-Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
-which happen to be binary. We classify them into the following seven categories:
+For experimental data, we use the Bayesian networks available with \textsf{Ace}
+and
+\textsf{Cachet}\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}},
+most of which happen to be binary. We classify them into the following seven
+categories:
 \begin{itemize*}
@@
 \end{itemize*}
-We run ADDMC with each of the five encodings once on each Bayesian network.
+We run \textsf{ADDMC} with each of the five encodings once on each Bayesian
+network.
 
-\begin{figure}
+\begin{figure*}[t]
   \centering
   \input{cumulative.tex}%
-  \caption{Cumulative number of instances solved by ADDMC over time using each
-    encoding.}
+  \caption{Cumulative number of instances solved by \textsf{ADDMC} over time
+    using each encoding.}
   \label{fig:cumulative}
-\end{figure}
+\end{figure*}
 
-\begin{table}
+\begin{table} % TODO: update or remove
   \centering
-  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
-    encoding (uniquely, faster than with others, and in total) under the
+  \caption{The numbers of instances (out of 1466) solved by \textsf{ADDMC} with
+    each encoding (uniquely, faster than with others, and in total) under the
     described constraints.}%
@@
 
-\begin{figure*}
+\begin{figure*}[t]
   \centering
   \input{scatter.tex}%
-  \caption{ADDMC inference time using \texttt{cw} compared to \texttt{d02}
-    (left) and \texttt{sbk05} (right) for each instance in all data sets.}
+  \caption{\textsf{ADDMC} inference time using \texttt{cw} compared to
+    \texttt{d02} (left) and \texttt{sbk05} (right) for each instance in all data
+    sets.}
   \label{fig:scatter}
@@
 Mastermind data set. We conjecture that this is so either because the particular
-structure of the problem confuses the heuristics used by ADDMC or because these
-instances allow for significant simplifications that are exploited by
-\texttt{d02} but not \texttt{cw}.
+structure of the problem confuses the heuristics used by \textsf{ADDMC} or
+because these instances allow for significant simplifications that are exploited
+by \texttt{d02} but not \texttt{cw}.
 
@@
 equate clauses and ADDs (more specifically, factors of the function $\phi$ from
-\cref{alg:encoding}) here because ADDMC interprets each clause of any WMC
-encoding as a multiplicative factor of the ADD that represents the entire WMC
-instance \citep{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings, each
-weight is also a factor, but that does not affect the asymptotic bounds in the
-table.
+\cref{alg:encoding}) here because \textsf{ADDMC} interprets each clause of any
+WMC encoding as a multiplicative factor of the ADD that represents the entire
+WMC instance \citep{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings,
+each weight is also a factor, but that does not affect the asymptotic bounds in
+the table.
 
 \section{Discussion and Conclusion}
+% TODO: mention that DPMC is the next step
 
@@
 efficiently tackling an $\NP{}$-complete problem
-\citep{DBLP:conf/aaai/SangBK05}. ADDMC does not rely on \SAT{}-based algorithmic
-techniques, and our proposed format diverges even more from the DIMACS CNF
-format for Boolean formulas. To what extent are \SAT{}-based methods still
-applicable? The answer depends significantly on the problem domain. For Bayesian
-networks, the rules describing that each random variable can only be associated
-with exactly one value were still encoded as clauses. As has been noted
-previously \citep{DBLP:conf/sat/ChaviraD06}, rows in CPTs with probabilities
-equal to zero or one can be represented as clauses as well. Therefore, our work
-can be seen as proposing a middle ground between $\#\SAT{}$ and probabilistic
-inference.
+\citep{DBLP:conf/aaai/SangBK05}. \textsf{ADDMC} does not rely on \SAT{}-based
+algorithmic techniques, and our proposed format diverges even more from the
+DIMACS CNF format for Boolean formulas. To what extent are \SAT{}-based methods
+still applicable? The answer depends significantly on the problem domain. For
+Bayesian networks, the rules describing that each random variable can only be
+associated with exactly one value were still encoded as clauses. As has been
+noted previously \citep{DBLP:conf/sat/ChaviraD06}, rows in CPTs with
+probabilities equal to zero or one can be represented as clauses as well.
+Therefore, our work can be seen as proposing a middle ground between $\#\SAT{}$
+and probabilistic inference.
 
-While we chose to use ADDMC \citep{DBLP:conf/aaai/DudekPV20} as the WMC
+While we chose to use \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} as the WMC
 algorithm and Bayesian networks as a canonical example of a probabilistic
@@
 \citep{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
-well as to search-based solvers such as Cachet \citep{DBLP:conf/sat/SangBBKP04},
-although the extension may be less straightforward for other WMC techniques.
+well as to search-based solvers such as \textsf{Cachet}
+\citep{DBLP:conf/sat/SangBBKP04}, although the extension may be less
+straightforward for other WMC techniques.
 
@@
 
-\newpage
+\clearpage
 \bibliography{paper}
 
-\newpage
+\clearpage
 \appendix

### 2021-02-09 doc/paper2/paper.tex
Tables, figures, etc.

@@
 \section{Introduction}
-
-TODO: introduce (also talk more about how Cachet and Ace are used)
-\begin{itemize}
-\item \texttt{bklm16} \citep{DBLP:conf/ecai/BartKLM16}
-\item \textsf{query-dnnf}
-  \footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
-\item \textsf{DPMC} \citep{DBLP:conf/cp/DudekPV20}
-\item tackle a comparable problem, but their encoding was never implemented or
-  empirically tested (i.e., the implementation is left as future work)
-  \citep{DBLP:conf/scai/VomlelT13}
-\end{itemize}
+% TODO: introduce \textsf{DPMC} \citep{DBLP:conf/cp/DudekPV20}
 
@@
 \section{Related Work} \label{sec:related}
+% TODO: tackle a comparable problem, but their encoding was never implemented or
+% empirically tested (i.e., the implementation is left as future work)
+% \citep{DBLP:conf/scai/VomlelT13}
+
+% TODO: introduce \texttt{bklm16} \citep{DBLP:conf/ecai/BartKLM16}
 
@@
 \subsection{The Space of Functions on Boolean Algebras}
+% TODO: properly define what logical operations on ADDs do. Mistake in the
+% paper: an ADD is just a pseudo-boolean function: All operations on ADDs
+% (whatever they are) are pointwise (perhaps /\, \/, ~ may be exceptions).
 
@@
 practice.\footnote{The proofs of this and other theoretical results can be found
-  in the technical appendix.}
+  in the appendix.}
 
@@
 
-First, \textsf{ADDMC} constructs the \emph{Gaifman graph}
-of the input CNF formula as an aid for the algorithm's
-heuristics. This graph has as vertices the variables of the formula, and there
-is an edge between two variables $u$ and $v$ if there is a clause in the formula
-that contains both $u$ and $v$. We extend this definition to functions on
-Boolean algebras, i.e., the factors of $\phi$. For any pair of distinct
-variables $u, v \in U$, we draw an edge between them in the Gaifman graph if
-there is a function $\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ that is a factor
-of $\phi$ such that $u \in X$ and $v \in X$. For instance, a factor such as
-$\mathrm{CPT}_X$ will enable edges between all distinct pairs of variables in
-$\mathcal{E}^*(X)$. Second, even though the function $\phi$ produced by
-\cref{alg:encoding} is constructed to have $2^U$ as its domain, sometimes the
-domain is effectively reduced to $2^V$ for some $V \subset U$ by the ADD
-manipulation algorithms that optimise the ADD representation of a function. For
-a simple example, consider $\alpha: 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as
-$\alpha(\{a\}) = \alpha(\emptyset) = 0.5$. Then $\alpha$ can be reduced to
-$\alpha'\colon 2^{\emptyset} \to \mathbb{R}_{\ge 0}$ defined as
-$\alpha'(\emptyset) = 0.5$. To compensate for these reductions, for the original
-WMC format with a weight function $w\colon U \cup \{ \neg u \mid u \in U \} \to
-\mathbb{R}_{\ge 0}$, \textsf{ADDMC} would multiply its computed answer by
-$\prod_{u \in U \setminus V} w(u) + w(\neg u)$. With the new WMC format, we
-instead multiply the answer by $2^{|U \setminus V|}$. Each `excluded' variable
-$u \in U \setminus V$ satisfies two properties: all weights associated with $u$
-are equal to $0.5$ (otherwise the corresponding CPT would depend on $u$, and $u$
-would not be excluded), and all other CPTs are independent of $u$ (or they may
-have a trivial dependence, where the probability stays the same if $u$ is
-replaced with its complement). Thus, the CPT that corresponds to $u$ still
-multiplies the weight of every atom in the Boolean algebra by $0.5$, but the
-number of atoms under consideration is halved. To correct for this, we multiply
-the final answer by two for every $u \in U \setminus V$.
+First, \textsf{ADDMC} constructs the \emph{primal} (a.k.a. Gaifman) \emph{graph}
+of the input CNF formula as an aid for the algorithm's heuristics. This graph
+has as vertices the variables of the formula, and there is an edge between two
+variables $u$ and $v$ if there is a clause in the formula that contains both $u$
+and $v$. We extend this definition to functions on Boolean algebras, i.e., the
+factors of $\phi$. For any pair of distinct variables $u, v \in U$, we draw an
+edge between them in the primal graph if there is a function $\alpha\colon 2^X
+\to \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v
+\in X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges
+between all distinct pairs of variables in $\mathcal{E}^*(X)$. Second, even
+though the function $\phi$ produced by \cref{alg:encoding} is constructed to
+have $2^U$ as its domain, sometimes the domain is effectively reduced to $2^V$
+for some $V \subset U$ by the ADD manipulation algorithms that optimise the ADD
+representation of a function. For a simple example, consider $\alpha: 2^{\{a\}}
+\to \mathbb{R}_{\ge 0}$ defined as $\alpha(\{a\}) = \alpha(\emptyset) = 0.5$.
+Then $\alpha$ can be reduced to $\alpha'\colon 2^{\emptyset} \to \mathbb{R}_{\ge
+  0}$ defined as $\alpha'(\emptyset) = 0.5$. To compensate for these reductions,
+for the original WMC format with a weight function $w\colon U \cup \{ \neg u
+\mid u \in U \} \to \mathbb{R}_{\ge 0}$, \textsf{ADDMC} would multiply its
+computed answer by $\prod_{u \in U \setminus V} w(u) + w(\neg u)$. With the new
+WMC format, we instead multiply the answer by $2^{|U \setminus V|}$. Each
+`excluded' variable $u \in U \setminus V$ satisfies two properties: all weights
+associated with $u$ are equal to $0.5$ (otherwise the corresponding CPT would
+depend on $u$, and $u$ would not be excluded), and all other CPTs are
+independent of $u$ (or they may have a trivial dependence, where the probability
+stays the same if $u$ is replaced with its complement). Thus, the CPT that
+corresponds to $u$ still multiplies the weight of every atom in the Boolean
+algebra by $0.5$, but the number of atoms under consideration is halved. To
+correct for this, we multiply the final answer by two for every $u \in U
+\setminus V$.
 
 \section{Experimental Comparison} \label{sec:experiments}
+% TODO: introduce \textsf{query-dnnf}
+% \footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}} (also
+% talk more about how Cachet and Ace are used)
+% TODO: included original WMC algorithms
+% TODO: Even instances that are solved in less than 0.1 s are too big for edge
+% count to be efficiently calculated.
+% TODO: my plot's sbk05 data should match (and matches) the ADDMC/DPMC vs c2d
+% comparison in the paper (although my sbk05 data only roughly corresponds to
+% half of their dataset)
+% TODO: mention that both encoding and inference times are limited to 1000 s
+% TODO: mention that we don't run ADDMC+cd05 and ADDMC+cd06 because they don't produce correct answers
+
+\begin{figure*}[t]
+  \centering
+  \input{cumulative.tex}%
+  \caption{Cumulative numbers of instances solved by combinations of algorithms
+    and encodings over time.}
+  \label{fig:cumulative}
+\end{figure*}
+
+\begin{table}
+  \centering
+  \caption{The numbers of instances (out of 1466) solved by
+    each combination of algorithm and encoding (uniquely, faster than others, and in total).}%
+  \begin{tabular}{lrrr}
+    \toprule
+    Algorithm \& Encoding & Unique & Fastest & Total \\
+    \midrule
+    $\textsf{Ace} + \texttt{cd05}$ & \textcolor{gray}{0} & 55 & 1169 \\
+    $\textsf{Ace} + \texttt{cd06}$ & \textcolor{red}{34} & 218 & \textcolor{red}{1259} \\
+    $\textsf{Ace} + \texttt{d02}$ & \textcolor{gray}{0} & 46 & 993 \\
+    $\textsf{ADDMC} + \texttt{bklm16}$ & \textcolor{gray}{0} & 29 & \textcolor{blue}{617} \\
+    $\textsf{ADDMC} + \texttt{cw}$ & 14 & \textcolor{red}{770} & 919 \\
+    $\textsf{ADDMC} + \texttt{d02}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 703 \\
+    $\textsf{ADDMC} + \texttt{sbk05}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 729 \\
+    $\textsf{Cachet} + \texttt{sbk05}$ & 13 & 229 & 928 \\
+    $\textsf{query-dnnf} + \texttt{bklm16}$ & \textcolor{gray}{0} & 3 & 1017 \\
+    \bottomrule
+  \end{tabular}
+  \label{tbl:tallies}
+\end{table}
+
+\begin{figure*}[t]
+  \centering
+  \input{scatter.tex}%
+  \caption{An instance-by-instance comparison between $\textsf{ADDMC} +
+    \texttt{cw}$ and the best overall combination of algorithm and encoding
+    ($\textsf{Ace} + \texttt{cd06}$, on the left) as well as the second-best
+    encoding for \textsf{ADDMC} (\texttt{sbk05}, on the right).}
+  \label{fig:scatter}
+\end{figure*}
+
+\begin{figure*}[t]
+  \centering
+  \input{melt.tex}%
+  \caption{TODO: describe this in the text}
+  \label{fig:melted}
+\end{figure*}
 
@@
 processors\footnote{Each instance is run on the same processor for all
-  encodings.} running Scientific~Linux~7 with an \SI{8}{\gibi\byte} memory limit
+  encodings.} running Scientific~Linux~7 with a \SI{32}{\gibi\byte} memory limit
 and a \SI{1000}{\second} timeout.
@@
 
-\begin{figure*}[t]
-  \centering
-  \input{cumulative.tex}%
-  \caption{Cumulative number of instances solved by \textsf{ADDMC} over time
-    using each encoding.}
-  \label{fig:cumulative}
-\end{figure*}
-
-\begin{table} % TODO: update or remove
-  \centering
-  \caption{The numbers of instances (out of 1466) solved by \textsf{ADDMC} with
-    each encoding (uniquely, faster than with others, and in total) under the
-    described constraints.}%
-  \begin{tabular}{lrrr}
-    \toprule
-    Encoding & Unique & Fastest & Total \\
-    \midrule
-    \texttt{cd05} & 2 & 3 & 380 \\
-    \texttt{cd06} & 0 & 0 & 363 \\
-    \texttt{cw} & 234 & 935 & 980 \\
-    \texttt{d02} & 40 & 111 & 797 \\
-    \texttt{sbk05} & 12 & 44 & 765 \\
-    \bottomrule
-  \end{tabular}
-  \label{tbl:tallies}
-\end{table}
-
-\begin{figure*}[t]
-  \centering
-  \input{scatter.tex}%
-  \caption{\textsf{ADDMC} inference time using \texttt{cw} compared to
-    \texttt{d02} (left) and \texttt{sbk05} (right) for each instance in all data
-    sets.}
-  \label{fig:scatter}
-\end{figure*}
-
 According to the cumulative plot in \cref{fig:cumulative}, \texttt{cw} is
@@
 
-\begin{table}
+\begin{table} % TODO: add bklm16
   \centering
@@
 
-\clearpage
 \bibliography{paper}

### 2021-02-09 tools/analyse_addmc.R

@@ -37,6 +37,7 @@ df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
             fun.aggregate = min,
             value.var = c("answer", "time"))
 time_columns <- Filter(function(x) startsWith(x, "time_"), names(df))
+df$time_min <- as.numeric(apply(df, 1, function (row) min(row[time_columns])))
 for (column in time_columns) {
   df[is.na(df[[column]]), column] <- 2 * TIMEOUT
 }
@@ -137,3 +138,59 @@ p2 <- scatter_plot(df, "time_new_sbk05", "time_new_cw", "\\textsf{ADDMC} + \\tex
 tikz(file = "../doc/paper2/scatter.tex", width = 6.5, height = 2.4)
 ggarrange(p1, p2, ncol = 2, nrow = 1, common.legend = TRUE, legend = "right")
 dev.off()
+
+data_melted <- melt(data[!is.na(data$answer),], id = c("encoding", "novelty"),
+                    measure = c("encoding_time", "inference_time")) %>%
+  group_by(encoding, novelty, variable) %>%
+  summarize(time = mean(value), lower = mean(value) - 0.1 * sd(value),
+            upper = mean(value) + 0.1 * sd(value))
+data_melted$encoding <- paste0("\\texttt{", data_melted$encoding, "}", sep = "")
+data_melted$lower[data_melted$variable =="inference_time"] <- with(data_melted, lower[variable == "encoding_time"] + lower[variable == "inference_time"])
+data_melted$upper[data_melted$variable =="inference_time"] <- with(data_melted, upper[variable == "encoding_time"] + upper[variable == "inference_time"])
+data_melted$novelty <- factor(data_melted$novelty, levels = c("old", "new"))
+novelties <- c("Originally", "With \\textsf{ADDMC}")
+names(novelties) <- c("old", "new")
+
+tikz(file = "../doc/paper2/melt.tex", width = 6.5, height = 2.4)
+ggplot(data_melted, aes(encoding, time, fill = variable)) +
+  geom_bar(stat="identity", position = position_stack(reverse = TRUE)) +
+  facet_grid(cols = vars(novelty), labeller = labeller(novelty = novelties)) +
[…]

### 2021-02-09 doc/paper2/paper.tex
Related work section

@@
 \section{Introduction}
-% TODO: introduce \textsf{DPMC} \citep{DBLP:conf/cp/DudekPV20}
 
@@
 \section{Related Work} \label{sec:related}
-% TODO: tackle a comparable problem, but their encoding was never implemented or
-% empirically tested (i.e., the implementation is left as future work)
-% \citep{DBLP:conf/scai/VomlelT13}
-
-% TODO: introduce \texttt{bklm16} \citep{DBLP:conf/ecai/BartKLM16}
-
-Hitherto, four techniques have been proposed for encoding Bayesian networks into
-instances of WMC. We will identify them based on the initials of authors as well
-as publications years: \texttt{d02} \citep{DBLP:conf/kr/Darwiche02},
-\texttt{sbk05} \citep{DBLP:conf/aaai/SangBK05}, \texttt{cd05}
-\citep{DBLP:conf/ijcai/ChaviraD05}, and \texttt{cd06}
-\citep{DBLP:conf/sat/ChaviraD06}. Below we summarise the observed performance
-differences among them. \citet{DBLP:conf/aaai/SangBK05} claim that
+
+Performing inference on Bayesian networks by encoding them into instances of WMC
+is a well-established idea with a history of almost twenty years. Five encodings
+have been proposed so far (we will identify them based on the initials of
+authors as well as publications years): \texttt{d02}
+\citep{DBLP:conf/kr/Darwiche02}, \texttt{sbk05} \citep{DBLP:conf/aaai/SangBK05},
+\texttt{cd05} \citep{DBLP:conf/ijcai/ChaviraD05}, \texttt{cd06}
+\citep{DBLP:conf/sat/ChaviraD06}, and \texttt{bklm16}
+\citep{DBLP:conf/ecai/BartKLM16}\footnote{\citet{DBLP:conf/scai/VomlelT13} also
+  propose an encoding, but only for networks of a particular bipartite structure
+  and without any evaluation.}. Below we summarise the observed performance
+differences among them.
+
+\citet{DBLP:conf/aaai/SangBK05} claim that
 \texttt{sbk05} is a smaller encoding than \texttt{d02} with respect to both the
@@
 \texttt{d02} by measuring the time it takes to compile either encoding into an
-arithmetic circuit (but do not measure inference time). The more recent encoding
+arithmetic circuit. They show that
 \texttt{cd05} always compiles faster and results in a smaller arithmetic circuit
@@
 \texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
-five instances and worse on the remaining two. Based on this description, one
-would expect \texttt{cd06} to be faster than both \texttt{cd05} and
-\texttt{sbk05}, both of which should be faster than \texttt{d02}. The
-experiments in \cref{sec:experiments}, however, strongly disagree with this
-prediction, showing that the quality of an encoding depends strongly on the
-underlying search algorithm or compilation technique.
+five instances and worse on the remaining two. Finally,
+\citet{DBLP:conf/ecai/BartKLM16} introduce \texttt{bklm16} and show that it has
+both fewer variables and fewer clauses than \texttt{cd06}. Their experiments
+show \texttt{bklm16} to be superior to \texttt{cd06} with respect to both
+compilation time and encoding size when both are compiled using \textsf{c2d}
+\citep{DBLP:conf/ecai/Darwiche04} but inferior to \texttt{cd06} when
+\texttt{cd06} is compiled using
+\textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} (which still uses
+\textsf{c2d} but considers the structure of the Bayesian network along with its
+encoding).
+
+Our experiments in \cref{sec:experiments} compare the five previous encodings
+along with a newly proposed one---with originally-proposed WMC algorithms as
+well as with \textsf{ADDMC}---with respect to the total time it takes to encode
+a Bayesian network, compile it or run a WMC algorithm on it, and extract the
+(numerical) answer. We confirm some of the findings outlined in this section
+while also observing that the (relative and absolute) performance of each
+encoding depends on the WMC algorithm in use, and smaller encodings are not
+necessarily faster.
 
@@
 % TODO: mention that we don't run ADDMC+cd05 and ADDMC+cd06 because they don't produce correct answers
+% TODO: the -implicit flag is disabled for good reasons for bklm16
+% TODO: potential appendix: exact arguments to each piece of software
 
@@
     $\textsf{Ace} + \texttt{cd05}$ & \textcolor{gray}{0} & 55 & 1169 \\
-    $\textsf{Ace} + \texttt{cd06}$ & \textcolor{red}{34} & 218 & \textcolor{red}{1259} \\
+    $\textsf{Ace} + \texttt{cd06}$ & \textbf{34} & 218 & \textbf{1259} \\
     $\textsf{Ace} + \texttt{d02}$ & \textcolor{gray}{0} & 46 & 993 \\
-    $\textsf{ADDMC} + \texttt{bklm16}$ & \textcolor{gray}{0} & 29 & \textcolor{blue}{617} \\
-    $\textsf{ADDMC} + \texttt{cw}$ & 14 & \textcolor{red}{770} & 919 \\
+    $\textsf{ADDMC} + \texttt{bklm16}$ & \textcolor{gray}{0} & 29 & \textcolor{gray}{617} \\
+    $\textsf{ADDMC} + \texttt{cw}$ & 14 & \textbf{770} & 919 \\
     $\textsf{ADDMC} + \texttt{d02}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 703 \\
@@
 
-\begin{figure*}[t]
-  \centering
-  \input{melt.tex}%
-  \caption{TODO: describe this in the text}
-  \label{fig:melted}
-\end{figure*}
+%\begin{figure*}[t] % TODO: describe this in the text
+%  \centering
+%  \input{melt.tex}%
+%  \caption{Average encoding and inference time of each encoding with their
+%    original WMC algorithm (on the left) and with \textsf{ADDMC} (on the right)
+%    on \emph{solved} instances. The error bars denote \SI{10}{\percent} of
+%    standard deviation.}
+%  \label{fig:melted}
+%\end{figure*}
 
@@
 For all encodings other than \texttt{cw}, we use their implementation in
-\textsf{Ace}~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} with
+\textsf{Ace}~3.0 with
 \texttt{-encodeOnly} and \texttt{-noEclause} flags. However, \textsf{Ace} was
@@
 
-\begin{table} % TODO: add bklm16
+\begin{table}
   \centering
@@
   \label{tbl:asymptotes}
-  \begin{tabular}{lcc}
+  \begin{tabular}{m{0.4\linewidth} c c}
     \toprule
@@
     \midrule
-    \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $O(nv^{d+1})$ & $O(nv^{d+1})$ \\
+    \texttt{bklm16}, \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $O(nv^{d+1})$ & $O(nv^{d+1})$ \\
     \texttt{cw} & $O(nv)$ & $O(nv^2)$ \\
@@
 % TODO: mention that DPMC is the next step
+% TODO: which algorithm comes out on top depends on the data set
+% TODO: emphasise that BN encodings have never been compared w.r.t. time before
 

### 2021-02-10 doc/paper2/paper.tex
Rewrite the experiments section

@@
 show \texttt{bklm16} to be superior to \texttt{cd06} with respect to both
-compilation time and encoding size when both are compiled using \textsf{c2d}
+compilation time and encoding size when both are compiled using
+\textsf{c2d}\footnote{\url{http://reasoning.cs.ucla.edu/c2d/}}
 \citep{DBLP:conf/ecai/Darwiche04} but inferior to \texttt{cd06} when
@@
 \textsf{c2d} but considers the structure of the Bayesian network along with its
-encoding).
-
-Our experiments in \cref{sec:experiments} compare the five previous encodings
-along with a newly proposed one---with originally-proposed WMC algorithms as
-well as with \textsf{ADDMC}---with respect to the total time it takes to encode
-a Bayesian network, compile it or run a WMC algorithm on it, and extract the
-(numerical) answer. We confirm some of the findings outlined in this section
-while also observing that the (relative and absolute) performance of each
-encoding depends on the WMC algorithm in use, and smaller encodings are not
-necessarily faster.
+encoding). Our experiments in \cref{sec:experiments} confirm some of the
+findings outlined in this section while also observing that the (relative and
+absolute) performance of each encoding depends on the WMC algorithm in use, and
+smaller encodings are not necessarily faster.
 
@@
 \subsection{The Space of Functions on Boolean Algebras}
-% TODO: properly define what logical operations on ADDs do. Mistake in the
-% paper: an ADD is just a pseudo-boolean function: All operations on ADDs
-% (whatever they are) are pointwise (perhaps /\, \/, ~ may be exceptions).
+% TODO: it would be easier to talk about pseudo-Boolean functions instead, but
+% maybe it's not necessary.
 
@@
 can be efficiently represented using ADDs. Furthermore, all of the operations
-are supported by the CUDD \citep{somenzi1998cudd} package that is used by
-\textsf{ADDMC} for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The
-definitions of multiplication and projection are as defined by
+are supported by CUDD \citep{somenzi1998cudd}---a package used by \textsf{ADDMC}
+for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The definitions of
+multiplication and projection are as defined by
 \citet{DBLP:conf/aaai/DudekPV20}, while others are new.
@@
 
-Note that if $U$ is any set, then $\mathcal{V} = \{ \alpha\colon 2^X \to
-\mathbb{R}_{\ge 0} \mid X \subseteq U \}$ is a semi-vector space with three
-additional operations: (non-scalar) multiplication, complement, and projection.
-Specifically, note that both addition and multiplication are both associative
-and commutative.
-
-We end the discussion on function spaces by defining several special functions:
-unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$ defined as $1(\emptyset) = 1$,
-zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$ defined as $0(\emptyset) = 0$,
-and function $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as
-$[a](\emptyset) = 0$, $[a](\{a\}) = 1$ for any $a$. Henceforth, for any function
-$\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set $T$, we will write
-$\alpha(T)$ to mean $\alpha(T \cap X)$.
+In summary, addition, multiplication, and scalar multiplication are defined
+pointwise, while complement and projection interact with the algebraic structure
+of the domains $2^X$ and $2^Y$. Specifically, note that both addition and
+multiplication are both associative and commutative. We end the discussion on
+function spaces by defining several special functions: unit $1\colon 2^\emptyset
+\to \mathbb{R}_{\ge 0}$ defined as $1(\emptyset) = 1$, zero $0\colon 2^\emptyset
+\to \mathbb{R}_{\ge 0}$ defined as $0(\emptyset) = 0$, and function $[a]\colon
+2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as $[a](\emptyset) = 0$, $[a](\{a\}) =
+1$ for any $a$. Henceforth, for any function $\alpha\colon 2^X \to
+\mathbb{R}_{\ge 0}$ and any set $T$, we will write $\alpha(T)$ to mean $\alpha(T
+\cap X)$.
 
@@
 \section{Experimental Comparison} \label{sec:experiments}
-% TODO: introduce \textsf{query-dnnf}
-% \footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}} (also
-% talk more about how Cachet and Ace are used)
-% TODO: included original WMC algorithms
-% TODO: Even instances that are solved in less than 0.1 s are too big for edge
-% count to be efficiently calculated.
-% TODO: my plot's sbk05 data should match (and matches) the ADDMC/DPMC vs c2d
-% comparison in the paper (although my sbk05 data only roughly corresponds to
-% half of their dataset)
-% TODO: mention that both encoding and inference times are limited to 1000 s
-% TODO: mention that we don't run ADDMC+cd05 and ADDMC+cd06 because they don't produce correct answers
-% TODO: the -implicit flag is disabled for good reasons for bklm16
-% TODO: potential appendix: exact arguments to each piece of software
 
@@
     $\textsf{ADDMC} + \texttt{sbk05}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 729 \\
+    $\textsf{c2d} + \texttt{bklm16}$ & \textcolor{gray}{0} & 3 & 1017 \\
     $\textsf{Cachet} + \texttt{sbk05}$ & 13 & 229 & 928 \\
-    $\textsf{query-dnnf} + \texttt{bklm16}$ & \textcolor{gray}{0} & 3 & 1017 \\
     \bottomrule
@@
 
-In this section, we describe an experimental study comparing the five WMC
-encodings for Bayesian networks when run with \textsf{ADDMC}. The experiments
-were run on servers with Intel Xeon Gold 6138 and Intel Xeon E5-2630
-processors\footnote{Each instance is run on the same processor for all
-  encodings.} running Scientific~Linux~7 with a \SI{32}{\gibi\byte} memory limit
-and a \SI{1000}{\second} timeout.
+% TODO: keep mentioning citations along with algorithm and encoding names
+
+In this section, we describe an experimental study comparing the six WMC
+encodings for Bayesian networks when run with both \textsf{ADDMC} and the
+WMC algorithms used in the original papers.\footnote{Both
+  \texttt{cd05} and \texttt{cd06} cannot be run with most WMC algorithms
+  including \textsf{ADDMC} because these encodings allow for additional models
+  that the WMC algorithm is supposed to ignore
+  \citep{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.} We compare the
+encodings with respect to the total time it takes to encode a Bayesian network,
+compile it or run a WMC algorithm on it, and extract the (numerical) answer.
+Note that while all five papers that introduce other encodings include
+experimental comparisons of encoding size, that is not feasible with
+\textsf{ADDMC} as even instances that are fully solved in less than
+\SI{0.1}{\second} are too big to build the full ADD within reasonable time and
+memory limits. The experiments were run on a computing cluster with Intel Xeon
+Gold 6138 and Intel Xeon E5-2630 processors\footnote{Each instance is run on the
+  same processor for all encodings.} running Scientific~Linux~7 with a
+\SI{32}{\gibi\byte} memory limit and a \SI{1000}{\second} timeout on both
+encoding and inference. For inference, we use \textsf{Ace} for \texttt{cd05},
+\texttt{cd06}, and \texttt{d02};
+\textsf{Cachet}\footnote{\url{https://cs.rochester.edu/u/kautz/Cachet/}}
+\citep{DBLP:conf/sat/SangBBKP04} for \texttt{sbk05}; and \textsf{c2d}
+\citep{DBLP:conf/ecai/Darwiche04} for compilation and \textsf{query-dnnf}
+\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}} for
+answer computation for \texttt{bklm16}. For encoding, we use \textsf{bn2cnf}
+\footnote{\url{http://www.cril.univ-artois.fr/KC/bn2cnf.html}} for
+\texttt{bklm16}, and \textsf{Ace} for all other encodings (except for
+\texttt{cw}, which is implemented in Python).
+
+\paragraph{Workarounds.} \textsf{Ace} was not used to encode evidence, as
+preliminary experiments revealed that the evidence-encoding implementation
+contains bugs that can lead to incorrect answers or a Java exception being
+thrown on some instances of the data set (and the source code is not publicly
+available). Instead, we simply list all the evidence as additional clauses in
+the encoding. Furthermore, to ensure that \texttt{bklm16} (whether run with
+\textsf{ADDMC} or \textsf{c2d}) returns correct answers on most instances, we
+had to disable one of the improvements that \texttt{bklm16} brings over
+\texttt{cd06}, namely, the construction of a scaling factor that `absorbs' one
+probability from each CDT \citep{DBLP:conf/ecai/BartKLM16}. For realistic
+benchmark instances, this scaling factor can easily be below $10^{-30}$, and
+thus would require arbitrary-precision floating-point arithmetic to be usable.
+Even a toy Bayesian network with seven binary independent variables with
+probabilities $0.1$ and $0.9$ is enough for \textsf{bn2cnf} to output precisely
+zero as the scaling factor. We note that this issue likely remained unnoticed
+because \citet{DBLP:conf/ecai/BartKLM16} did not attempt to compute numerical
+answers in their experiments.
 
@@
 
-For all encodings other than \texttt{cw}, we use their implementation in
-\textsf{Ace}~3.0 with
-\texttt{-encodeOnly} and \texttt{-noEclause} flags. However, \textsf{Ace} was
-not used to encode evidence, as preliminary experiments revealed that the
-evidence-encoding implementation contains bugs that can lead to incorrect
-answers or a Java exception being thrown on some instances of the data set (and
-the source code is not publicly available). Instead, we simply list all the
-evidence as additional clauses in the encoding.
-
-Note that both \texttt{cd05} and \texttt{cd06} purposefully produce overly
-relaxed encodings that contain extra models and thus yield incorrect
-probabilities \citep{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}. These
-additional models are supposed to be filtered out during circuit compilation
-\citep{DBLP:conf/ijcai/ChaviraD05}, but this is not easily achievable with
-\textsf{ADDMC}. Nonetheless, we include both encodings in the experiments.
-
-While encoding time itself was not measured because of different languages of
-implementation, it is worth noting that \texttt{cw} is linear in the total
-number of CPT rows and so is unlikely to be slower than, e.g., \texttt{cd06},
-which relies on solving $\NP{}$-complete problems as part of the encoding process
-\citep{DBLP:conf/sat/ChaviraD06}.
-
-For experimental data, we use the Bayesian networks available with \textsf{Ace}
-and
-\textsf{Cachet}\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}},
-most of which happen to be binary. We classify them into the following seven
-categories:
+\paragraph{Instances.} For experimental data, we use the Bayesian networks
+available with \textsf{Ace} and \textsf{Cachet}, most of which happen to be
+binary. We classify them into the following seven categories:
 \begin{itemize*}
@@
 
-According to the cumulative plot in \cref{fig:cumulative}, \texttt{cw} is
-consistently able to solve more instances with any given time limit than any
-other encoding, while the order of the remaining encodings from best to worst is
-exactly the opposite of that in previous literature (cf. \cref{sec:related}).
-Specifically, \texttt{cw} solves the same number of instances in
-\SI{8.144}{\second} as \texttt{d02} does in \SI{1000}{\second}, which is the
-second-best encoding in our experiments. Furthermore, \cref{tbl:tallies} shows
-that \texttt{cw} was the fastest in 935 out of the 980 (i.e.,
-\SI{95.4}{\percent}) instances that it managed to solve. Finally, according to
-the scatter plots in \cref{fig:scatter}, \texttt{cw} is particularly promising
-on Grid networks while losing to \texttt{d02} on some instances of the
-Mastermind data set. We conjecture that this is so either because the particular
-structure of the problem confuses the heuristics used by \textsf{ADDMC} or
-because these instances allow for significant simplifications that are exploited
-by \texttt{d02} but not \texttt{cw}.
+%Specifically, \texttt{cw} solves the same number of
+%instances in \SI{8.144}{\second} as \texttt{d02} does in \SI{1000}{\second},
+%which is the second-best encoding in our experiments.
+
+% TODO: need to update
+\paragraph{Results.} \Cref{fig:cumulative} shows that \texttt{cd05} and
+\texttt{cd06} (when run with \textsf{Ace}) are in the lead, while \textsf{ADDMC}
+significantly underperforms when combined with any of the previous encodings.
+Our encoding \texttt{cw} significantly improves the performance of
+\textsf{ADDMC}, making $\textsf{ADDMC}+\texttt{cw}$ comparable to
+$\textsf{Ace}+\texttt{d02}$, $\textsf{c2d}+\texttt{bklm16}$, and
+$\textsf{Cachet}+\texttt{sbk05}$. Furthermore,
+\cref{tbl:tallies} shows that, while $\textsf{Ace}+\texttt{cd06}$ managed to
+solve the most instances, $\textsf{ADDMC}+\texttt{cw}$ was the best-performing
+algorithm-encoding combination on the largest number of instances. The scatter
+plot on the left hand side of \cref{fig:scatter} add to this by showing that
+\texttt{cw} is particularly promising on Grid networks and tackles all DQMR
+instances in less than a second. The scatter plot on the right hand side of
+\cref{fig:scatter} shows that \texttt{cw} is better than \texttt{sbk05} (i.e.,
+the second best performing encoding for \textsf{ADDMC}) on the majority of
+instances. Seeing how, e.g., DQMR instances are trivial for
+$\textsf{ADDMC}+\texttt{cw}$ but hard for $\textsf{Ace}+\texttt{cd06}$, and
+vice versa for Mastermind instances, we conclude that the best-performing
+algorithm-encoding combination depends significantly on (as-of-yet unknown)
+properties of the Bayesian networks.
 
@@
 
-\paragraph{Explaining the performance benefits.} Let $n = |\mathcal{V}|$ be the
-number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
-|\mathrm{pa}(X)|$ the maximum in-degree (i.e., the number of parents), and $v =
-\max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
-\Cref{tbl:asymptotes} shows how \texttt{cw} has fewer variables and fewer
-ADDs than any other encoding. However, note that these are upper bounds and most
-encodings (including \texttt{cw}) can be smaller in certain situations (e.g.,
-with binary random variables or when a CPT has repeating probabilities). We
-equate clauses and ADDs (more specifically, factors of the function $\phi$ from
-\cref{alg:encoding}) here because \textsf{ADDMC} interprets each clause of any
-WMC encoding as a multiplicative factor of the ADD that represents the entire
-WMC instance \citep{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings,
-each weight is also a factor, but that does not affect the asymptotic bounds in
-the table.
+We attempt to explain what makes \textsf{ADDMC} run hundreds of times faster
+with \texttt{cw} than with any other encoding by considering asymptotic upper
+bounds on the numbers of variables and ADDs based on the size and structure of
+the Bayesian network. Let $n = |\mathcal{V}|$ be the number of vertices in the
+Bayesian network, $d = \max_{X \in \mathcal{V}} |\mathrm{pa}(X)|$ the maximum
+in-degree (i.e., the number of parents), and $v = \max_{X \in \mathcal{V}} |\im
+X|$ the maximum number of values per variable. \Cref{tbl:asymptotes} shows how
+\texttt{cw} has fewer variables and fewer ADDs than any other encoding. We
+conjecture that it is primarily the reduced number of variables that makes the
+\textsf{ADDMC} variable ordering heuristics much more effective. Note that these
+are upper bounds and most encodings (including \texttt{cw}) can be smaller in
+certain situations (e.g., with binary random variables or when a CPT has
+repeating probabilities). We equate clauses and ADDs (more specifically, factors
+of the function $\phi$ from \cref{alg:encoding}) here because \textsf{ADDMC}
+interprets each clause of any WMC encoding as a multiplicative factor of the ADD
+that represents the entire WMC instance \citep{DBLP:conf/aaai/DudekPV20}. For
+literal-weight encodings, each weight is also a factor, but that does not affect
+the asymptotic bounds in the table.
 
@@
 
+% TODO: potential appendix: exact arguments to each piece of software
 \end{document}

### 2021-02-10 tools/analyse_addmc.R

@@ -56,7 +56,7 @@ data_sum$encoding[data_sum$encoding == "new_bklm16"] <- "\\textsf{ADDMC} + \\tex
 data_sum$encoding[data_sum$encoding == "new_cw"] <- "\\textsf{ADDMC} + \\texttt{cw}"
 data_sum$encoding[data_sum$encoding == "new_d02"] <- "\\textsf{ADDMC} + \\texttt{d02}"
 data_sum$encoding[data_sum$encoding == "new_sbk05"] <- "\\textsf{ADDMC} + \\texttt{sbk05}"
-data_sum$encoding[data_sum$encoding == "old_bklm16"] <- "\\textsf{query-dnnf} + \\texttt{bklm16}"
+data_sum$encoding[data_sum$encoding == "old_bklm16"] <- "\\textsf{c2d} + \\texttt{bklm16}"
 data_sum$encoding[data_sum$encoding == "old_cd05"] <- "\\textsf{Ace} + \\texttt{cd05}"
 data_sum$encoding[data_sum$encoding == "old_cd06"] <- "\\textsf{Ace} + \\texttt{cd06}"
 data_sum$encoding[data_sum$encoding == "old_d02"] <- "\\textsf{Ace} + \\texttt{d02}"

### 2021-02-11 doc/paper2/paper.tex
Early draft of the third paper

@@
   adapt a state-of-the-art WMC algorithm \textsf{ADDMC} to the new format. Our
-  experiments show that the new encoding results in significantly faster
-  inference on most benchmark instances. Furthermore, the same idea can be
-  adapted to other WMC algorithms and other problem domains.
+  experiments show that the new encoding significantly improves the performance
+  of the algorithm on most benchmark instances. Furthermore, the same idea can
+  be adapted to other WMC algorithms and other problem domains.
 \end{abstract}
@@
 \section{Introduction}
+% TODO: keep mentioning citations along with algorithm and encoding names
 
@@
 various elements can be represented in both notations. Most importantly, note
-that the word \emph{atom} has completely different meanings in logic and in
-Boolean algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an
-element of $U$, whereas an atom in a Boolean algebra is (in set-theoretic terms)
-a singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
+that the word \emph{atom} has completely different meanings in logic and Boolean
+algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of
+$U$, whereas an atom in a Boolean algebra is (in set-theoretic terms) a
+singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
 $\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
@@
 
-\subsection{The Space of Functions on Boolean Algebras}
-% TODO: it would be easier to talk about pseudo-Boolean functions instead, but
-% maybe it's not necessary.
+\subsection{Functions on Boolean Algebras}
+% TODO: maybe: it would be easier to talk about pseudo-Boolean functions
+% instead, but maybe it's not necessary.
 
@@
 perspective on WMC to show that this is always possible, however, as ensuing
-sections will demonstrate, it often makes the inference task much harder in
+sections will demonstrate, it can make the inference task much harder in
 practice.\footnote{The proofs of this and other theoretical results can be found
@@
 restricting oneself to factorable measures and thus having to add extra
-variables. We will refer to it as \texttt{cw}.
-
-A Bayesian network is a directed acyclic graph with random variables as vertices
-that defines a probability distribution over them. Let $\mathcal{V}$ denote this
-set of random variables. For any random variable $X \in \mathcal{V}$, let $\im
-X$ denote its set of values and $\mathrm{pa}(X)$ its set of parents. The
-full probability distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X
-\mid \mathrm{pa}(X))$ \citep{DBLP:books/daglib/0023820}. For discrete Bayesian
-networks (and we only consider discrete networks in this paper), each factor of
-this product can be represented by a CPT. See \cref{fig:example_bn} for an
-example Bayesian network that we will refer to throughout this section. For
-this network, $\mathcal{V} = \{ W, F, T \}$, $\mathrm{pa}(W) = \emptyset$,
-$\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im W = \im F = \{0, 1 \}$, and
-$\im T = \{ l, m, h \}$.
+variables. We will refer to it as \texttt{cw}. A Bayesian network is a directed
+acyclic graph with random variables as vertices that defines a probability
+distribution over them. Let $\mathcal{V}$ denote this set of random variables.
+For any random variable $X \in \mathcal{V}$, let $\im X$ denote its set of
+values and $\mathrm{pa}(X)$ its set of parents. The full probability
+distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X \mid
+\mathrm{pa}(X))$. For discrete Bayesian networks (and we only consider discrete
+networks in this paper), each factor of this product can be represented by a
+CPT. See \cref{fig:example_bn} for an example Bayesian network that we will
+refer to throughout this section. For this network, $\mathcal{V} = \{ W, F, T
+\}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$,
+$\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.
 
@@
   of all indicator variables for all random variables in the Bayesian network.
-\end{definition}
-
   For example, in the Bayesian network from \cref{fig:example_bn},
@@
   \lambda_{W=1} \}$.
+\end{definition}
 
@@
 This function can be represented by an ADD
-\citep{DBLP:journals/fmsd/BaharFGHMPS97}. The core of \textsf{ADDMC} works by
-taking an ADD $\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product
-of smaller ADDs) and returning $(\exists_U\psi)(\emptyset)$
-\citep{DBLP:conf/aaai/DudekPV20}. In this section, we prove that the function
-$\phi$ produced by \cref{alg:encoding} can be used by \textsf{ADDMC} to
-correctly compute any marginal probability of the Bayesian network that was
-encoded as $\phi$.\footnote{Note that it can just as well compute \emph{any}
-  probability expressed using the random variables in $\mathcal{V}$.} We begin
-with \cref{lemma:cpt} which shows that any conditional weight function produces
-the right answer when given a valid encoding of variable-value assignments
-relevant to the CPT.
+\citep{DBLP:journals/fmsd/BaharFGHMPS97}. \textsf{ADDMC} takes an ADD
+$\psi\colon 2^{U} \to \mathbb{R}_{\ge 0}$ (expressed as a product of smaller
+ADDs) and returns $(\exists_U\psi)(\emptyset)$ \citep{DBLP:conf/aaai/DudekPV20}.
+In this section, we prove that the function $\phi$ produced by
+\cref{alg:encoding} can be used by \textsf{ADDMC} to correctly compute any
+marginal probability of the Bayesian network that was encoded as
+$\phi$.\footnote{Note that it can just as well compute \emph{any} probability
+  expressed using the random variables in $\mathcal{V}$.} We begin with
+\cref{lemma:cpt} which shows that any conditional weight function produces the
+right answer when given a valid encoding of variable-value assignments relevant
+to the CPT.
 
@@
 edge between them in the primal graph if there is a function $\alpha\colon 2^X
-\to \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u \in X$ and $v
-\in X$. For instance, a factor such as $\mathrm{CPT}_X$ will enable edges
-between all distinct pairs of variables in $\mathcal{E}^*(X)$. Second, even
-though the function $\phi$ produced by \cref{alg:encoding} is constructed to
-have $2^U$ as its domain, sometimes the domain is effectively reduced to $2^V$
-for some $V \subset U$ by the ADD manipulation algorithms that optimise the ADD
+\to \mathbb{R}_{\ge 0}$ that is a factor of $\phi$ such that $u, v \in X$. For
+instance, a factor such as $\mathrm{CPT}_X$ will enable edges between all
+distinct pairs of variables in $\mathcal{E}^*(X)$. Second, even though the
+function $\phi$ produced by \cref{alg:encoding} is constructed to have $2^U$ as
+its domain, sometimes the domain is effectively reduced to $2^V$ for some $V
+\subset U$ by the ADD manipulation algorithms that optimise the ADD
 representation of a function. For a simple example, consider $\alpha: 2^{\{a\}}
@@
 
-%\begin{figure*}[t] % TODO: describe this in the text
+%\begin{figure*}[t] % TODO: maybe not: describe this in the text
 %  \centering
@@
 
-% TODO: keep mentioning citations along with algorithm and encoding names
-
-In this section, we describe an experimental study comparing the six WMC
-encodings for Bayesian networks when run with both \textsf{ADDMC} and the
-WMC algorithms used in the original papers.\footnote{Both
+We compare the six WMC encodings for Bayesian networks when run with both
+\textsf{ADDMC} and the WMC algorithms used in the original papers.\footnote{Both
   \texttt{cd05} and \texttt{cd06} cannot be run with most WMC algorithms
@@
 
-\paragraph{Workarounds.} \textsf{Ace} was not used to encode evidence, as
+\textsf{Ace} was not used to encode evidence, as
 preliminary experiments revealed that the evidence-encoding implementation
@@
 
-\paragraph{Instances.} For experimental data, we use the Bayesian networks
+For experimental data, we use the Bayesian networks
 available with \textsf{Ace} and \textsf{Cachet}, most of which happen to be
@@
 
-% TODO: need to update
-\paragraph{Results.} \Cref{fig:cumulative} shows that \texttt{cd05} and
+\Cref{fig:cumulative} shows that \texttt{cd05} and
 \texttt{cd06} (when run with \textsf{Ace}) are in the lead, while \textsf{ADDMC}
@@
 algorithm-encoding combination on the largest number of instances. The scatter
-plot on the left hand side of \cref{fig:scatter} add to this by showing that
+plot on the left-hand side of \cref{fig:scatter} add to this by showing that
 \texttt{cw} is particularly promising on Grid networks and tackles all DQMR
-instances in less than a second. The scatter plot on the right hand side of
+instances in less than a second. The scatter plot on the right-hand side of
 \cref{fig:scatter} shows that \texttt{cw} is better than \texttt{sbk05} (i.e.,
-the second best performing encoding for \textsf{ADDMC}) on the majority of
+the second-best encoding for \textsf{ADDMC}) on the majority of
 instances. Seeing how, e.g., DQMR instances are trivial for
@@
 literal-weight encodings, each weight is also a factor, but that does not affect
-the asymptotic bounds in the table.
-
-\section{Discussion and Conclusion}
-% TODO: mention that DPMC is the next step
-% TODO: which algorithm comes out on top depends on the data set
-% TODO: emphasise that BN encodings have never been compared w.r.t. time before
+our asymptotic bounds.
+
+\section{Conclusions and Future Work}
+% TODO: maybe: emphasise that BN encodings have never been compared w.r.t. time
+% before
 
@@
 \citep{DBLP:conf/aaai/SangBK05}. \textsf{ADDMC} does not rely on \SAT{}-based
-algorithmic techniques, and our proposed format diverges even more from the
-DIMACS CNF format for Boolean formulas. To what extent are \SAT{}-based methods
-still applicable? The answer depends significantly on the problem domain. For
-Bayesian networks, the rules describing that each random variable can only be
-associated with exactly one value were still encoded as clauses. As has been
-noted previously \citep{DBLP:conf/sat/ChaviraD06}, rows in CPTs with
-probabilities equal to zero or one can be represented as clauses as well.
-Therefore, our work can be seen as proposing a middle ground between $\#\SAT{}$
-and probabilistic inference.
-
-While we chose to use \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} as the WMC
-algorithm and Bayesian networks as a canonical example of a probabilistic
-inference task, these are only examples meant to illustrate the broader idea
-that choosing a more expressive representation of weights can outperform
-increasing the size of the problem to keep the weights simple. Indeed, in this
-work, we have provided a new theoretical perspective on the expressive power of
-WMC and illustrated the empirical benefits of that perspective. The same idea
-can be adapted to other inference problem domains such as probabilistic programs
+algorithmic techniques \citep{DBLP:conf/aaai/DudekPV20}, and our proposed format
+diverges even more from the DIMACS CNF format for Boolean formulas. To what
+extent are \SAT{}-based methods still applicable? The answer depends
+significantly on the problem domain. For Bayesian networks, the rules describing
+that each random variable can only be associated with exactly one value were
+still encoded as clauses. As has been noted previously
+\citep{DBLP:conf/sat/ChaviraD06}, rows in CPTs with probabilities equal to zero
+or one can be represented as clauses as well. Therefore, our work can be seen as
+proposing a middle ground between $\#\SAT{}$ and probabilistic inference.
+
+While we chose \textsf{ADDMC} as the WMC algorithm and Bayesian networks as a
+canonical example of a probabilistic inference task, these are only examples
+meant to illustrate the broader idea that choosing a more expressive
+representation of weights can outperform increasing the size of the problem to
+keep the weights simple. Indeed, in this work, we have provided a new
+theoretical perspective on the expressive power of WMC and illustrated the
+empirical benefits of that perspective. The same idea can be adapted to other
+inference problem domains such as probabilistic programs
 \citep{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
 well as to search-based solvers such as \textsf{Cachet}
-\citep{DBLP:conf/sat/SangBBKP04}, although the extension may be less
-straightforward for other WMC techniques.
+\citep{DBLP:conf/sat/SangBBKP04} and \textsf{DPMC}
+---an extension to \textsf{ADDMC} that adds support for computations based on
+tensors (rather than ADDs) and planning based on tree decompositions
+\cite{DBLP:conf/cp/DudekPV20}. Another important direction for future work is to
+develop a better understanding of what properties of Bayesian networks make an
+instance easy for some algorithm-encoding combinations more than others.
 
@@
 
+\clearpage
 \bibliography{paper}

### 2021-02-11 doc/paper3/paper.tex
Early draft of the third paper

\documentclass{article}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[UKenglish]{babel}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[capitalise]{cleveref}
\usepackage{dashbox}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{isodate}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{soul}
\usepackage{mathrsfs}
\usepackage{capt-of}
\usepackage{siunitx}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\title{Weighted Model Counting Without Parameter Variables}

\begin{document}

\maketitle

% TODO: make introduce an acronym: project-join tree = PJT
\section{Main Results}

\paragraph{Notation.} For any propositional formula $\phi$ and $p, q \in
\mathbb{R}_{\ge 0}$,
\[
  [\phi]^p_q \coloneqq
  \begin{cases}
    p & \text{if } \phi \\
    q & \text{otherwise.}
  \end{cases}
\]

\todo[inline]{Formal definition of a previous WMC instance (CNF, literal weight
  function) and the new definition (set of $2^{X} \to \mathbb{R}_{\ge 0}$
  pseudo-Boolean functions and a constant). Note that the constant idea is
  borrowed from \texttt{bklm16}.}

\paragraph{References.}
\begin{itemize}
\item `Apply' is quadratic \cite{DBLP:journals/tc/Bryant86}.
\item Related work without publicly available implementations:
  \begin{itemize}
  \item direct compilation to SDDs \cite{DBLP:conf/ecsqaru/ChoiKD13}
  \item direct compilation to PSDDs, also eliminating parameter variables (a thesis)
  \item maybe two more papers
  \end{itemize}
\end{itemize}
% TODO: do a literature search focused around these papers

\paragraph{Notes.}
\begin{itemize}
\item Let $X_P$ be the set of parameter variable and $X_I$ be the set of
  indicator variables.
\item Parameter variables are either taken from the LMAP file (for encodings
  produced by Ace) or assumed to be the variables that have both weights equal
  to 1.
\item If a parameter variable in a clause is `negated', we can ignore the
  clause. We assume that there are no clauses with more than one instance of
  parameter variables.
\item The second \textbf{foreach} loop can be performed in constant time by
  representing $\phi'$ as a list and assuming that the two 'clauses' are
  adjacent in that list (and incorporating it into the first loop).
\item The $d$ map is constructed in $\mathcal{O}(|X_P|\log|X_P|)$ time (we want
  to use a data structure based on binary search trees rather than hashing).
\item \texttt{rename} can be implemented in $\mathcal{O}(\log |X_P|)$ time.
\item Apparently, the DPMC paper already shows that taking the first offered
  decomposition tree is best.
\item This may look like preprocessing, but all the transformations are local
  and thus can be incorporated into an encoding algorithm with no slowdown. In
  fact, if anything, the resulting algorithm would be slightly faster, as it
  would have less data to output.
\item It is already well-known that WMC is FPT.
\end{itemize}

\begin{algorithm}
  \caption{WMC instance transformation}
  \SetKwFunction{rename}{rename}
  \SetKwProg{Fn}{Function}{:}{}
  \KwData{an (old-format) WMC instance $(\phi, X_I, X_P, W)$}
  \KwResult{a (new-format) WMC instance $(\phi', \omega)$}
  $\phi' \gets \emptyset$\;
  $\omega \gets 1$\;
  let $d\colon X_P \to \mathbb{N}$ be defined as $v \mapsto |\{ u \in X_P \mid u
  \le v \}|$\;
  \ForEach{clause $c \in \phi$}{
    \uIf{$c \cap X_P = \{ v \}$ for some $v$ \textnormal{\textbf{and}} $W(v) \ne
      1$}{
      \uIf{$|c| = 1$}{$\omega \gets \omega \times W(v)$\;}
      \Else{
        $\phi' \gets \phi' \cup \left\{ \left[ \bigwedge_{l \in c \setminus
              \{v\}} \neg l \right]^{W(v)}_1 \right\}$\;
      }
    }
    \ElseIf{$\{v \mid \neg v \in c\} \cap X_P  = \emptyset$}{
      $\phi' \gets \phi' \cup \{ [c]^1_0 \}$\;
    }
  }
  \ForEach{indicator variable $v \in X_I$}{
    \If{$\{[v]_1^p, [\neg v]_1^q\} \subseteq \phi'$ for some $p$ and $q$}{
      $\phi' \gets \phi' \setminus \{ [v]_1^p, [\neg v]_1^q \} \cup \{ [v]_q^p
      \}$\;
    }
  }
  replace every variable $v$ in $\phi'$ with $\rename{$v$}$\;
  \Return{$(\phi', \omega)$}\;
  \Fn{\rename{$v$}}{
    $S \gets \{u \in X_P \mid u \le v\}$\;
    \lIf{$S = \emptyset$}{\Return{$v$}}
    \Return{$v - d(\max S)$}\;
  }
\end{algorithm}

\section{Parameterised Complexity of DPMC}

% NOTE: By DPMC, we always mean DMC+lg.
% TODO: maybe use texttt for DPMC?

Summary:
\begin{itemize}
\item We establish DPMC inference as fixed-parameter tractable.
\item We show that, in the case of cw, the parameter is the same as in the BN lower bound,
\item and, in the case of d02, the DPMC parameter is exponentially higher.
\item We experimentally show that cw+DPMC is best on low-to-moderate treewidth
  instances, and cd06+c2d overtakes cw+DPMC on higher treewidth instances.
\end{itemize}

Define:
\begin{itemize}
\item treewidth of a graph,
\item Boolean formula in CNF (perhaps this is too trivial to define),
\item primal graph of a CNF formula (a.k.a.
  Gaifman/(variable) interaction/connectivity/clique/representing graph),
\item Bayesian network (I already have a definition of these last two),
\item moralisation of a Bayesian network (or of any DAG),
\end{itemize}

\begin{theorem}[\cite{DBLP:conf/ecai/KwisthoutBG10}, rephrased]
  BN Inference (for all algorithms that accept arbitrary instances) has a lower
  bound that's linear in the size of the BN and exponential in the treewidth of
  its moralisation (provide the exact formula).
\end{theorem}

\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}, verbatim]
  Let $X$ be a set of Boolean variables and $\phi$ be a CNF formula over $X$. A
  \emph{project-join tree} (PJT) of $\phi$ is a tuple $(T, r, \gamma, \pi)$
  where:
  \begin{itemize}
  \item $T$ is a tree with root $r \in \mathcal{V}(T)$,
  \item $\gamma\colon \mathcal{L}(T) \to \phi$ is a bijection between the leaves
    of $T$ and the clauses of $\phi$, and
  \item $\pi\colon \mathcal{V}(T) \setminus \mathcal{L}(T) \to 2^X$ is a
    labelling function on internal nodes.
  \end{itemize}
  Moreover, $(T, r, \gamma, \pi)$ must satisfy the following two properties:
  \begin{enumerate}
  \item $\{\pi(n) : n \in \mathcal{V}(T) \setminus \mathcal{L}(T)\}$ is a
    partition of $X$, and
  \item for each internal node $n \in \mathcal{V}(T) \setminus \mathcal{L}(T)$,
    variable $x \in \pi(n)$, and clause $c \in \phi$ such that $x$ appears in
    $c$, the leaf node $\gamma^{-1}(c)$ must be a descendant of $n$ in $T$.
  \end{enumerate}
\end{definition}

\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}]
  \[
    \mathtt{Vars}(n) \coloneqq
    \begin{cases}
      \mathtt{Vars}(\gamma(n)) & \text{if } n \in \mathcal{L}(T) \\
      \left( \bigcup_{o \in \mathcal{C}(n)} \mathtt{Vars}(o) \right) \setminus
      \pi(n) & \text{if } n \not\in \mathcal{L}(T).
    \end{cases}
  \]
  \[
    \mathtt{size}(n) \coloneqq
    \begin{cases}
      |\mathtt{Vars}(n)| & \text{if } n \in \mathcal{L}(T) \\
      |\mathtt{Vars}(n) \cup \pi(n)| & \text{if } n \not\in \mathcal{L}(T).
    \end{cases}
  \]
  The \emph{width} of a PJT $(T, r, \gamma, \pi)$ is
  $\mathtt{width}(T) \coloneqq \max_{n \in \mathcal{V}(T)} \mathtt{size}(n)$.
\end{definition}

\begin{theorem}[\cite{DBLP:conf/cp/DudekPV20}, paraphrased, `ADD width is equal
  to the treewidth of the primal graph']
  Given a CNF formula $\phi$ with a tree decomposition of its primal graph of
  width $w$, Algorithm~2 (from \cite{DBLP:conf/cp/DudekPV20}) returns a
  PJT of $\phi$ of width at most $w+1$.
\end{theorem}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node[circle,draw] {$\exists$}
    child {node (a) {$\vdots$}
      child {node[circle,draw] {$c_1$}}
    }
    child {node (b) {$\vdots$}
      child {node[circle,draw] {$\ast$}
        child {node {$\vdots$}
          child {node[circle,draw] {$c_i$}}
        }
      }
    }
    child {node (c) {$\vdots$}
      child {node[circle,draw] {$c_l$}}
    }
    ;
    \path (a) -- (b) node[midway] {$\cdots$};
    \path (b) -- (c) node[midway] {$\cdots$};
  \end{tikzpicture}
  \caption{An example PJT with clauses $c_1, \dots, c_i, \dots, c_l$ that all
    contain the same variable, its projection node $\exists$, and a node under
    consideration $\ast$.}
\end{figure}

\begin{lemma}
  The number of variables that can appear in the ADDs within a PJT node is $\le
  k+1$.
\end{lemma}
\begin{proof}
  All such variables are introduced in a `clause' below and projected either in
  this node or in one of its ancestors. Each such variable would be in the bag
  of each clause that introduced it. By the tree decomposition properties, it
  will also be in the bag of both the projection node and the current node
  because they are on the path between the clause nodes (see the figure).
\end{proof}

\begin{theorem}
  \textsc{DPMC} is FPT w.r.t. the PJT width. More specifically,
  \textsc{DPMC} running time is $\mathcal{O}(4^km(n+k))$, where $k$ is the
  width, $n$ is the number of clauses, and $m$ is the number of variables.
\end{theorem}
\begin{proof} % TODO: finish
  \begin{itemize}
  \item An ADD with $k$ variables can have up to $2^0 + 2^1 + \dots + 2^k =
    2^{k+1} - 1 = \mathcal{O}(2^k)$ nodes (including leaves).
  \item Multiplying $m$ ADDs can then take up to $(m-1)(2^{k+1}-1)^2 =
    \mathcal{O}(m4^k)$ (since one multiplication takes up to $(2^{k+1}-1)^2$
    time and the and the result will have up to $2^{k+1} - 1$ nodes because the
    domain stays the same).
  \item Each projection consists of two linear operations and a quadratic
    operation, so projecting $m$ variables will take $\mathcal{O}(4^km)$ time.
  \item In total, operations on a PJT node with $m$ ADDs, $k$ variables, $n$ of
    which are projected takes $\mathcal{O}(4^k(m+n))$ time.
  \item The total time taken by the DPMC execution stage is the sum of the time
    taken `inside' each PJT node. The number of such nodes is upper bounded by
    $m$, so the total time complexity of DPMC is $\mathcal{O}(4^km(n+k))$.
  \end{itemize}
\end{proof}

\bibliographystyle{acm}
\bibliography{paper}

\end{document}

### 2021-02-14 doc/paper2/paper.tex
Some writing and editing

@@
 
-The most well-studied version of WMC assigns weights to models based on
+The most well-known version of WMC assigns weights to models based on
 weights on literals, i.e., the weight of a model is the product of the weights
@@
 limitation is by adding more literals. While we show that this is always
-possible, we also demonstrate that it can be significantly more efficient to
+possible, we demonstrate that it can be significantly more efficient to
 encode weights in a more flexible format instead.
@@
 
-This new measure-theoretic perspective allows us to not only encode any
-discrete probability distribution but also improve inference speed. In
-\cref{sec:bns}, we demonstrate this by developing a new WMC encoding for
-Bayesian networks that uses \emph{conditional weights} on literals (in the
-spirit of conditional probabilities) that have literal-based WMC as a special
-case. We prove the correctness of the encoding and show how a state-of-the-art
-WMC solver \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} can be adapted to the
-new format. \textsf{ADDMC} is a recently-proposed algorithm for WMC based on
+This new perspective allows us to not only encode any discrete probability
+distribution but also improve inference speed. In \cref{sec:bns} we demonstrate
+this by developing a new WMC encoding for Bayesian networks that uses
+\emph{conditional weights} on literals (in the spirit of conditional
+probabilities) that have literal-based WMC as a special case. We prove the
+correctness of the encoding and show how a state-of-the-art WMC solver
+\textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} can be adapted to the new
+format. \textsf{ADDMC} is a recently-proposed algorithm for WMC based on
 manipulating functions on Boolean algebras using an efficient representation for
 such functions known as algebraic decision diagrams (ADDs)
-\citep{DBLP:journals/fmsd/BaharFGHMPS97}. Finally, in \cref{sec:experiments}, we
-show how the new encoding results in faster inference on the vast majority of
-benchmark instances, often by one or two orders of magnitude. We explain the
-performance benefits by showing how our encoding has asymptotically fewer
-variables and ADDs.
+\citep{DBLP:journals/fmsd/BaharFGHMPS97}. \textsf{ADDMC} was already shown to be
+capable of solving instances other solvers fail at and being the fastest solver
+on the largest number of instances \citep{DBLP:conf/aaai/DudekPV20}. Our
+experiments in \cref{sec:experiments} focus on further improving the performance
+of \textsf{ADDMC} on instances that originate from Bayesian networks. We show
+how our new encoding improves inference on the vast majority of benchmark
+instances, often by one or two orders of magnitude. We explain the performance
+benefits by showing how our encoding has asymptotically fewer variables and
+ADDs.
 
@@
 of) instances. In these experiments, \texttt{cd06} is always faster than
-\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
-\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
-slightly slower. The performance difference between \texttt{sbk05} and
-\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
-five instances and worse on the remaining two. Finally,
-\citet{DBLP:conf/ecai/BartKLM16} introduce \texttt{bklm16} and show that it has
-both fewer variables and fewer clauses than \texttt{cd06}. Their experiments
-show \texttt{bklm16} to be superior to \texttt{cd06} with respect to both
-compilation time and encoding size when both are compiled using
+\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed.  The
+performance difference between \texttt{sbk05} and \texttt{cd05} is even harder
+to judge: \texttt{sbk05} is better on three out of five instances and worse on
+the remaining two. Finally, \citet{DBLP:conf/ecai/BartKLM16} introduce
+\texttt{bklm16} and show that it has both fewer variables and fewer clauses than
+\texttt{cd06}. Their experiments show \texttt{bklm16} to be superior to
+\texttt{cd06} with respect to both compilation time and encoding size when both
+are compiled using
 \textsf{c2d}\footnote{\url{http://reasoning.cs.ucla.edu/c2d/}}
@@
 encoding). Our experiments in \cref{sec:experiments} confirm some of the
-findings outlined in this section while also observing that the (relative and
-absolute) performance of each encoding depends on the WMC algorithm in use, and
-smaller encodings are not necessarily faster.
+findings outlined in this section while also showing that the performance of
+each encoding depends on the WMC algorithm in use, and smaller encodings are not
+necessarily faster.
 
@@
 
-We attempt to explain what makes \textsf{ADDMC} run hundreds of times faster
-with \texttt{cw} than with any other encoding by considering asymptotic upper
-bounds on the numbers of variables and ADDs based on the size and structure of
-the Bayesian network. Let $n = |\mathcal{V}|$ be the number of vertices in the
+We can explain what makes \textsf{ADDMC} run significantly faster with
+\texttt{cw} than with any other encoding by considering asymptotic upper bounds
+on the numbers of variables and ADDs based on the size and structure of the
+Bayesian network. Let $n = |\mathcal{V}|$ be the number of vertices in the
 Bayesian network, $d = \max_{X \in \mathcal{V}} |\mathrm{pa}(X)|$ the maximum

### 2021-02-14 doc/paper3/paper.tex
Some writing and editing

@@
 
-% TODO: make introduce an acronym: project-join tree = PJT
-\section{Main Results}
+\section{Introduction}
 
 \paragraph{Notation.} For any propositional formula $\phi$ and $p, q \in
-\mathbb{R}_{\ge 0}$,
+\mathbb{R}_{\ge 0}$, let $[\phi]^p_q\colon 2^X \to \mathbb{R}$ be a
+pseudo-Boolean function defined as
 \[
@@
 
-\todo[inline]{Formal definition of a previous WMC instance (CNF, literal weight
-  function) and the new definition (set of $2^{X} \to \mathbb{R}_{\ge 0}$
-  pseudo-Boolean functions and a constant). Note that the constant idea is
-  borrowed from \texttt{bklm16}.}
-
 \paragraph{References.}
 \begin{itemize}
-\item `Apply' is quadratic \cite{DBLP:journals/tc/Bryant86}.
 \item Related work without publicly available implementations:
@@
 % TODO: do a literature search focused around these papers
+% TODO : use mathcal on V, L, E (and introduce them)
+% TODO: maybe use texttt for DPMC?
+
+\paragraph{Notes.}
+\begin{itemize}
+\item Apparently, the DPMC paper already shows that taking the first offered
+  decomposition tree is best.
+\item It is already well-known that WMC is FPT.
+\end{itemize}
+
+\section{Parameter Variable Elimination}
 
@@
 \item \texttt{rename} can be implemented in $\mathcal{O}(\log |X_P|)$ time.
-\item Apparently, the DPMC paper already shows that taking the first offered
-  decomposition tree is best.
 \item This may look like preprocessing, but all the transformations are local
@@
   would have less data to output.
-\item It is already well-known that WMC is FPT.
 \end{itemize}
@@
 
-% NOTE: By DPMC, we always mean DMC+lg.
-% TODO: maybe use texttt for DPMC?
-
-Summary:
+\paragraph{Notes.}
+\begin{itemize}
+\item Summary of results
   \begin{itemize}
   \item We establish DPMC inference as fixed-parameter tractable.
-\item We show that, in the case of cw, the parameter is the same as in the BN lower bound,
-\item and, in the case of d02, the DPMC parameter is exponentially higher.
   \item We experimentally show that cw+DPMC is best on low-to-moderate treewidth
@@
   \end{itemize}
+\item By DPMC, we always mean DMC+lg.
+\end{itemize}
 
-Define:
+\paragraph{TODO: Define:}
 \begin{itemize}
-\item treewidth of a graph,
+\item Formal definition of a previous WMC instance (CNF, literal weight
+  function) and the new definition (set of $2^{X} \to \mathbb{R}_{\ge 0}$
+  pseudo-Boolean functions and a constant). Note that the constant idea is
+  borrowed from \texttt{bklm16}.
 \item Boolean formula in CNF (perhaps this is too trivial to define),
@@
 
-\begin{theorem}[\cite{DBLP:conf/cp/DudekPV20}, paraphrased, `ADD width is equal
+\begin{theorem}[\cite{DBLP:conf/cp/DudekPV20}, rephrased, `ADD width is equal
   to the treewidth of the primal graph']
@@
 \end{theorem}
+
+\begin{definition}[\cite{DBLP:journals/jct/RobertsonS84}, rephrased]
+  A \emph{tree decomposition} of a graph $G$ is a pair $(T, \chi)$, where $T$ is
+  a tree and $\chi\colon V(T) \to 2^{V(G)}$ is a labelling function, with the
+  following properties:
+  \begin{itemize}
+  \item $\bigcup_{t \in V(T)} \chi(t) = V(G)$;
+  \item for every edge $e \in E(G)$, there exists $t \in V(T)$ such that $e$ has
+    both endpoints in $\chi(t)$;
+  \item for all $t, t', t'' \in V(T)$, if $t'$ is on the path between $t$ and
+    $t''$, then $\chi(t) \cap \chi(t'') \subseteq \chi(t')$.
+  \end{itemize}
+  The \emph{width} of tree decomposition $(T, \chi)$ is $\max_{t \in V(T)}
+  |\chi(t)| - 1)$. The \emph{treewidth} of graph $G$ is the smallest $w$ such
+  that $G$ has a tree decomposition of width $w$.
+\end{definition}
 
@@
     consideration $\ast$.}
+  \label{fig:example_pjt}
 \end{figure}
+
+\begin{definition}
+  Let $f, g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions. Operations
+  such as addition and multiplication are defined pointwise as
+  \[
+    (f+g)(Y) \coloneqq f(Y)+g(Y),
+  \]
+  and
+  \[
+    (fg)(Y) \coloneqq f(Y)g(Y)
+  \]
+  for all $Y \subseteq X$.
+\end{definition}
+% TODO: do I need to formally consider extending a pseudo-Boolean function to a
+% bigger domain?
+
+\begin{definition}
+  Let $f\colon 2^X \to \mathbb{R}$ be a pseudo-Boolean function, and $x \in X$.
+  Then $f|_{x=0}, f|_{x=1}\colon 2^X \to \mathbb{R}$ are \emph{restrictions} of
+  $f$ defined as
+  \[
+    f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\}),
+  \]
+  and
+  \[
+    f|_{x=1}(Y) \coloneqq f(Y \cup \{x\})
+  \]
+  for all $Y \subseteq X$.
+\end{definition}
+
+\begin{definition} \label{def:projection}
+  Let $X$ be a set. For any $x \in X$, \emph{projection} $\exists_x$ is an
+  endomorphism $\exists_x\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined
+  as
+  \[
+    \exists_xf = f|_{x=1} + f|_{x=0}
+  \]
+  for any $f\colon 2^X \to \mathbb{R}$.
+\end{definition}
+% TODO: gamma will have to point to ADDs instead (and not be a bijection)
+
+\begin{lemma}
+  Let $f,g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions represented by
+  ADDs with $n$ and $m$ nodes, respectively, and $x \in X$. Then $f+g$ and $fg$
+  can be computed in $\mathcal{O}(mn)$ time, and $\exists_xf$ can be computed in
+  $\mathcal{O}(n^2)$ time.
+\end{lemma}
+\begin{proof}
+  Addition and multiplication are implemented by \texttt{apply} algorithm which
+  takes $\mathcal{O}(mn)$ time \cite{DBLP:journals/tc/Bryant86}. Projection
+  consists of two restrictions and an addition by \cref{def:projection}. The
+  computational complexity of restriction is dominated by the reduction
+  operation that transforms a decision diagram into a minimal canonical form
+  \cite{DBLP:journals/tc/Bryant86}. While the original reduction algorithm had a
+  $\mathcal{O}(n \log n)$ complexity, caching can reduce it to $\mathcal{O}(n)$
+  \cite{somenzi1998cudd}. Either way, the complexity of projection is still
+  $\mathcal{O}(n^2)$.
+\end{proof}
+
+\begin{definition}
+  Let $(T, r, \gamma, \pi)$ be a PJT, and $X$ be the set of variables. The
+  functionality of DPMC execution (i.e., Algorithm~1 in the ADDMC paper
+  \cite{DBLP:conf/aaai/DudekPV20}) can be represented by $\delta(r)$, where
+  $\delta\colon \mathcal{V}(T) \to \mathbb{R}^{2^X}$ is a recursive function
+  defined as
+  \[
+    \delta(t) =
+    \begin{cases}
+      \gamma(t) & \text{if } t \in \mathcal{L}(T) \\
+      \exists_{\pi(t)} \prod_{u \in \mathcal{C}(t)} \delta(u) & \text{otherwise.}
+    \end{cases}
+  \]
+  The range of $\delta(r)$ then contains a single real number, i.e., the answer.
+\end{definition}
 
@@
   will also be in the bag of both the projection node and the current node
-  because they are on the path between the clause nodes (see the figure).
+  because they are on the path between the clause nodes (see
+  \cref{fig:example_pjt}).
+  \todo[inline]{How do I formalise this argument?}
 \end{proof}

### 2021-02-14 tools/analyse.R

@@ -8,7 +8,7 @@ library(ggpubr)
 library(tidyr)
 
 # TODO: plot treewidth vs add width
-data <- read.csv("../results/old_results.csv", header = TRUE, sep = ",")
+data <- read.csv("../results/results.csv", header = TRUE, sep = ",")
 
 # TODO: remove (just for testing)
 data <- data[data$dataset != "2004-PGM",]
@@ -184,16 +184,16 @@ scatter_plot <- function(df, x_column, y_column, x_name, y_name,
                                       shape = dataset)) +
     geom_jitter(alpha = 1, size = 1, width = 0.1, height = 0.1) +
     geom_abline(slope = 1, intercept = 0, colour = "#989898") +
-#    scale_x_continuous(trans = log10_trans(), limits = c(min.time, max.time),
-#                       breaks = c(0.1, 10, 1000),
-#                       labels = c("0.1", "10", "1000")) +
-#    scale_y_continuous(trans = log10_trans(), limits = c(min.time, max.time),
-#                       breaks = c(0.1, 10, 1000),
-#                       labels = c("0.1", "10", "1000")) +
+    scale_x_continuous(trans = log10_trans(), limits = c(min.time, max.time),
+                       breaks = c(0.1, 10, 1000),
+                       labels = c("0.1", "10", "1000")) +
+    scale_y_continuous(trans = log10_trans(), limits = c(min.time, max.time),
+                       breaks = c(0.1, 10, 1000),
+                       labels = c("0.1", "10", "1000")) +
     ylab(y_name) +
     xlab(x_name) +
     coord_fixed() +
-#    annotation_logticks(colour = "#b3b3b3") +
+    annotation_logticks(colour = "#b3b3b3") +
     theme_light() +
     labs(shape = "Data set", colour = "Treewidth") +
 #    scale_color_distiller("Treewidth", trans = "log") + # TODO: add breaks
@@ -202,8 +202,8 @@ scatter_plot <- function(df, x_column, y_column, x_name, y_name,
 
 scatter_plot(df, "time_old_cd06", "time_new_bklm16pp", "\\texttt{old_cd06} time (s)",
                    "\\texttt{new_bklm16++} time (s)", 2 * TIMEOUT)
-scatter_plot(df, "time_new_d02", "time_new_d02pp", "\\texttt{d02} time (s)",
-                   "\\texttt{d02++} time (s)", 2 * TIMEOUT)
[…]

### 2021-02-14 tools/analyse_changes.R

@@ -18,7 +18,7 @@ changes$dataset[grepl("Plan_Recognition", changes$instance, fixed = TRUE)] <- "O
 changes$dataset[grepl("students", changes$instance, fixed = TRUE)] <- "Other binary"
 changes$dataset[grepl("tcc4f", changes$instance, fixed = TRUE)] <- "Other binary"
 
-# Note: jitter is added because many data points have exactly the same before/after numbers
+# Note: count is used because many data points have exactly the same before/after numbers
 scatter <- function(data, x_var, y_var) {
   limits <- c(min(data[[x_var]], data[[y_var]], na.rm = TRUE), max(data[[x_var]], data[[y_var]], na.rm = TRUE))
   ggplot(data, aes(.data[[x_var]], .data[[y_var]], col = dataset)) +
@@ -36,12 +36,14 @@ scatter <- function(data, x_var, y_var) {
 # Before/after comparison of the number of variables
 # Note: the same plot for other encodings looks very similar
 scatter(changes[changes$encoding == "bklm16",], "before_variables", "after_variables")
-scatter(changes[data$encoding == "bklm16",], "before_clauses", "after_clauses")
+scatter(changes[changes$encoding == "bklm16",], "before_clauses", "after_clauses")
 
 # Comparison of encodings after optimisation
 df <- dcast(data = changes, formula = instance + dataset ~ encoding,
             fun.aggregate = NULL,
             value.var = c("before_variables", "before_clauses", "after_variables", "after_clauses"))
+
+df %>% group_by(df$dataset) %>% tally()
 
 scatter(df, "after_variables_bklm16", "after_variables_cd06")
 scatter(df, "after_variables_bklm16", "after_variables_cd05")

### 2021-02-15 doc/paper3/paper.tex
Fleshing out some lemmas

@@
 \paragraph{Notation.} For any propositional formula $\phi$ and $p, q \in
-\mathbb{R}_{\ge 0}$, let $[\phi]^p_q\colon 2^X \to \mathbb{R}$ be a
+\mathbb{R}$, let $[\phi]^p_q\colon 2^X \to \mathbb{R}$ be a
 pseudo-Boolean function defined as
 \[
-  [\phi]^p_q \coloneqq
+  [\phi]^p_q(Y) \coloneqq
   \begin{cases}
-    p & \text{if } \phi \\
-    q & \text{otherwise.}
+    p & \text{if } Y \models \phi \\
+    q & \text{otherwise}
   \end{cases}
 \]
+for any $Y \subseteq X$.
+
+\begin{lemma} \label{lemma:add_size}
+  An ADD with $n$ variables has $\mathcal{O}(2^n)$ nodes.
+\end{lemma}
+\begin{proof}
+  An ADD with $n$ variables can be, at most, a complete binary tree of height
+  $n+1$ (as measured by the number of vertices). It would then have $2^0 + 2^1 +
+  \dots + 2^n = 2^{n=1} = \mathcal{O}(2^n)$ nodes.
+\end{proof}
+
+\begin{lemma}
+  Let $\phi$ be a conjunction of $n$ literals. Then the ADD representation of
+  $[\phi]^p_q$ can be constructed in $\mathcal{O}(2^n)$ time for any $p, q \in
+  \mathbb{R}$ such that $p \ne q$.
+\end{lemma}
+\begin{proof}
+  The ADD representation of $\phi$ itself can be constructed with a sequence of
+  $n-1$ calls to \texttt{apply} with one of the two operands in each call always
+  a literal. The number of variables in the other operand then follows the
+  sequence $1, 2, 3, \dots, n-1$. By \cref{lemma:add_size}, the numbers of nodes
+  in the ADD representations of these operands is then $\mathcal{O}(2^1),
+  \mathcal{O}(2^2), \dots, \mathcal{O}(2^{n-1})$. Since one of the operands is
+  of constant size, the overall time complexity of all calls to \texttt{apply}
+  is then
+  \[
+    \mathcal{O}(2^1) + \mathcal{O}(2^2) + \dots + \mathcal{O}(2^{n-1}) =
+    \mathcal{O}(2^n).
+  \]
+
+  Let $\alpha$ be the ADD representation of $\phi$. Then the ADD representation
+  of $[\phi]_q^p$ is $(p-q)\alpha + q$. As scalar operations can obviously be
+  implemented in linear time, the overall complexity remains $\mathcal{O}(2^n)$.
+\end{proof}
+% TODO: will need to define scalar operations on ADDs
 
@@
 \end{itemize}
-% TODO: do a literature search focused around these papers
-% TODO : use mathcal on V, L, E (and introduce them)
-% TODO: maybe use texttt for DPMC?
 
@@
 
-\paragraph{TODO: Define:}
+\paragraph{TODO}
 \begin{itemize}
+\item do a literature search focused around these papers
+\item use mathcal on V, L, E (and introduce them)
+\item maybe use texttt for DPMC?
+\item do I need to formally consider extending a pseudo-Boolean function to a
+  bigger domain?
+\item Define:
+  \begin{itemize}
+  \item an ADD as a DAG.
+  \item What does it mean for an ADD to `have' variables? Maybe refer to
+    pseudo-Boolean function sensitivity.
   \item Formal definition of a previous WMC instance (CNF, literal weight
@@
   \end{itemize}
+\end{itemize}
 
@@
 
-\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}, verbatim]
+\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}, verbatim but with one change]
   Let $X$ be a set of Boolean variables and $\phi$ be a CNF formula over $X$. A
@@
   \item $T$ is a tree with root $r \in \mathcal{V}(T)$,
-  \item $\gamma\colon \mathcal{L}(T) \to \phi$ is a bijection between the leaves
-    of $T$ and the clauses of $\phi$, and
+  \item $\gamma\colon \mathcal{L}(T) \to \mathbb{R}^{2^X}$ maps leaves of $T$ to
+    pseudo-Boolean functions, and
   \item $\pi\colon \mathcal{V}(T) \setminus \mathcal{L}(T) \to 2^X$ is a
@@
 \end{definition}
+
+Note that while Dudek et al. \cite{DBLP:conf/cp/DudekPV20} define $\gamma$ to be
+a bijection between leaves of a PJT and clauses, our definition is more
+general.
 
@@
   \]
+  (Note that $\mathtt{size}(n)$ is the number of variables that can appear
+  during the computation of $\delta(n)$ (excluding recursive calls).)
   The \emph{width} of a PJT $(T, r, \gamma, \pi)$ is
@@
 \end{definition}
-% TODO: do I need to formally consider extending a pseudo-Boolean function to a
-% bigger domain?
 
@@
 \end{definition}
-% TODO: gamma will have to point to ADDs instead (and not be a bijection)
 
-\begin{lemma}
+\begin{lemma} \label{lemma:basic_ops}
   Let $f,g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions represented by
@@
 
-\begin{definition}
+% NOTE: this is a rehash of equation (2) from the DPMC paper
+\begin{definition} \label{def:abstraction}
   Let $(T, r, \gamma, \pi)$ be a PJT, and $X$ be the set of variables. The
-  functionality of DPMC execution (i.e., Algorithm~1 in the ADDMC paper
-  \cite{DBLP:conf/aaai/DudekPV20}) can be represented by $\delta(r)$, where
+  functionality of DPMC execution can be represented by $\delta(r)$, where
   $\delta\colon \mathcal{V}(T) \to \mathbb{R}^{2^X}$ is a recursive function
   defined as
-  \[
+  \begin{equation} \label{eq:execution}
     \delta(t) =
@@
     \end{cases}
-  \]
+  \end{equation}
   The range of $\delta(r)$ then contains a single real number, i.e., the answer.
@@
 
-\begin{lemma}
-  The number of variables that can appear in the ADDs within a PJT node is $\le
-  k+1$.
-\end{lemma}
-\begin{proof}
-  All such variables are introduced in a `clause' below and projected either in
-  this node or in one of its ancestors. Each such variable would be in the bag
-  of each clause that introduced it. By the tree decomposition properties, it
-  will also be in the bag of both the projection node and the current node
-  because they are on the path between the clause nodes (see
-  \cref{fig:example_pjt}).
-  \todo[inline]{How do I formalise this argument?}
-\end{proof}
+% TODO: will need to rephrase this to fit my context
+\begin{theorem}[Theorem~4 in \cite{DBLP:conf/cp/DudekPV20}, almost verbatim]
+  Let $\phi$ be a CNF formula over a set $X$ of variables and $(S, \chi)$ be a
+  tree decomposition of the primal graph of $\phi$ of width $w$. Then
+  Algorithm~2 returns a PJT of $\phi$ of width at most $w+1$.
+\end{theorem}
+
+% \begin{lemma} % NOTE: this lemma is already proven above
+%   Let $(S, \chi)$ be a tree decomposition, and $(T, r, \gamma, \pi)$ be its PJT
+%   generated by Algorithm~2 in \cite{DBLP:conf/cp/DudekPV20}. For any $t \in T$,
+%   the number of variables that appear in the ADDs within a PJT node is at
+%   most $k+1$.
+% \end{lemma}
+% \begin{proof}
+%   All such variables are introduced in a `clause' below and not projected in
+%   descendants. Each such variable would be in the bag of each clause that
+%   introduced it. By the tree decomposition properties, it will also be in the
+%   bag of both the projection node and the current node because they are on the
+%   path between the clause nodes (see \cref{fig:example_pjt}).
+% \end{proof}
 
 \begin{theorem}
-  \textsc{DPMC} is FPT w.r.t. the PJT width. More specifically,
-  \textsc{DPMC} running time is $\mathcal{O}(4^km(n+k))$, where $k$ is the
-  width, $n$ is the number of clauses, and $m$ is the number of variables.
+  Let $(T, r, \gamma, \pi)$ be a PJT of width $k$. Then \textsc{DPMC} execution
+  is fixed-parameter tractable with respect to the $k$. Specifically,
+  \textsc{DPMC} execution time complexity is $\mathcal{O}(4^km(n+k))$, where $n
+  = |\mathcal{L}(T)|$ is the number of clauses/leaves, and $m$ is the number of
+  variables.
 \end{theorem}
-\begin{proof} % TODO: finish
+% TODO: start here. Use theorem 4 to show that the number of variables is
+% bounded by primal treewidth
+\begin{proof}
   \begin{itemize}
-  \item An ADD with $k$ variables can have up to $2^0 + 2^1 + \dots + 2^k =
-    2^{k+1} - 1 = \mathcal{O}(2^k)$ nodes (including leaves).
+  \item Let us consider the overall complexity of all multiplications and
+    projections throughout the recursive calls of $\delta$ in
+    \cref{def:abstraction}. Clearly, the overall complexity is the sum of the
+    complexity of operations performed within each call to $\delta$.
+  \item Let $t \in \mathcal{V}(T)$ be an arbitrary vertex of $T$. If $t$ is a
+    leaf,
+  \item The total time taken by the DPMC execution stage is the sum of the time
+    taken `inside' each PJT node. The number of such nodes is upper bounded by
+    $m$, so the total time complexity of DPMC is $\mathcal{O}(4^km(n+k))$.
   \item Multiplying $m$ ADDs can then take up to $(m-1)(2^{k+1}-1)^2 =
@@
     domain stays the same).
-  \item Each projection consists of two linear operations and a quadratic
-    operation, so projecting $m$ variables will take $\mathcal{O}(4^km)$ time.
-  \item In total, operations on a PJT node with $m$ ADDs, $k$ variables, $n$ of
+  \item Then, by \cref{lemma:basic_ops}, projecting $m$ variables will take
+    $\mathcal{O}(4^km)$ time.
+  \item In total, operations on a PJT node with $m$ children, $k$ variables, $n$ of
     which are projected takes $\mathcal{O}(4^k(m+n))$ time.
-  \item The total time taken by the DPMC execution stage is the sum of the time
-    taken `inside' each PJT node. The number of such nodes is upper bounded by
-    $m$, so the total time complexity of DPMC is $\mathcal{O}(4^km(n+k))$.
   \end{itemize}

### 2021-02-16 doc/paper3/paper.tex
Writing and editing

@@
 
+\DeclareMathOperator{\im}{im}
+
 \title{Weighted Model Counting Without Parameter Variables}
@@
   $n+1$ (as measured by the number of vertices). It would then have $2^0 + 2^1 +
-  \dots + 2^n = 2^{n=1} = \mathcal{O}(2^n)$ nodes.
+  \dots + 2^n = 2^{n+1} = \mathcal{O}(2^n)$ nodes.
 \end{proof}
 
-\begin{lemma}
+\begin{lemma} \label{lemma:clause_time}
   Let $\phi$ be a conjunction of $n$ literals. Then the ADD representation of
@@
 \end{proof}
-% TODO: will need to define scalar operations on ADDs
+
+% NOTE: weights on literals other than the positive literals that correspond to
+% variables in $X_P$ are redundant as they either are equal to one or duplicate
+% an already-defined weight.
+\begin{definition}[old WMC instance]
+  An old WMC instance is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is the set
+  of indicator variables, $X_P$ is the set of parameter variables, $\phi$ is a
+  propositional formula over $X_I \cup X_P$, and $w\colon X_P \to \mathbb{R}$ is
+  the weight function.
+\end{definition}
+
+\begin{definition}[new WMC instance]
+  A new WMC instance is a tuple $(F, X, \omega)$, where $X$ is the set of
+  variables, $F$ is a set of pseudo-Boolean functions $2^X \to \mathbb{R}$, and
+  $\omega \in \mathbb{R}$ is the scaling factor.
+\end{definition}
 
@@
 \begin{itemize}
-\item Apparently, the DPMC paper already shows that taking the first offered
-  decomposition tree is best.
+\item Apparently, the \textsc{DPMC} paper already shows that taking the first
+  offered decomposition tree is best.
 \item It is already well-known that WMC is FPT.
@@
   \SetKwProg{Fn}{Function}{:}{}
-  \KwData{an (old-format) WMC instance $(\phi, X_I, X_P, W)$}
-  \KwResult{a (new-format) WMC instance $(\phi', \omega)$}
-  $\phi' \gets \emptyset$\;
+  \KwData{an (old-format) WMC instance $(\phi, X_I, X_P, w)$}
+  \KwResult{a (new-format) WMC instance $(F, X, \omega)$}
+  $F \gets \emptyset$\;
   $\omega \gets 1$\;
@@
   \ForEach{clause $c \in \phi$}{
-    \uIf{$c \cap X_P = \{ v \}$ for some $v$ \textnormal{\textbf{and}} $W(v) \ne
+    \uIf{$c \cap X_P = \{ v \}$ for some $v$ \textnormal{\textbf{and}} $w(v) \ne
       1$}{
-      \uIf{$|c| = 1$}{$\omega \gets \omega \times W(v)$\;}
+      \uIf{$|c| = 1$}{$\omega \gets \omega \times w(v)$\;}
       \Else{
-        $\phi' \gets \phi' \cup \left\{ \left[ \bigwedge_{l \in c \setminus
-              \{v\}} \neg l \right]^{W(v)}_1 \right\}$\;
+        $F \gets F \cup \left\{ \left[ \bigwedge_{l \in c \setminus
+              \{v\}} \neg l \right]^{w(v)}_1 \right\}$\;
       }
@@
     \ElseIf{$\{v \mid \neg v \in c\} \cap X_P  = \emptyset$}{
-      $\phi' \gets \phi' \cup \{ [c]^1_0 \}$\;
+      $F \gets F \cup \{ [c]^1_0 \}$\;
     }
@@
   \ForEach{indicator variable $v \in X_I$}{
-    \If{$\{[v]_1^p, [\neg v]_1^q\} \subseteq \phi'$ for some $p$ and $q$}{
-      $\phi' \gets \phi' \setminus \{ [v]_1^p, [\neg v]_1^q \} \cup \{ [v]_q^p
+    \If{$\{[v]_1^p, [\neg v]_1^q\} \subseteq F$ for some $p$ and $q$}{
+      $F \gets F \setminus \{ [v]_1^p, [\neg v]_1^q \} \cup \{ [v]_q^p
       \}$\;
@@
   }
-  replace every variable $v$ in $\phi'$ with $\rename{$v$}$\;
-  \Return{$(\phi', \omega)$}\;
+  replace every variable $v$ in $F$ with $\rename{$v$}$\;
+  \Return{$(F, X_I, \omega)$}\;
   \Fn{\rename{$v$}}{
@@
 
-\section{Parameterised Complexity of DPMC}
+\section{Parameterised Complexity of \textsc{DPMC}}
 
@@
   \begin{itemize}
-  \item We establish DPMC inference as fixed-parameter tractable.
-  \item We experimentally show that cw+DPMC is best on low-to-moderate treewidth
-    instances, and cd06+c2d overtakes cw+DPMC on higher treewidth instances.
+  \item We establish \textsc{DPMC} inference as fixed-parameter tractable.
+  \item We experimentally show that \textsc{DPMC} is best on low-to-moderate
+    treewidth instances, and cd06+c2d overtakes on higher treewidth instances.
   \end{itemize}
-\item By DPMC, we always mean DMC+lg.
+\item By \textsc{DPMC}, we always mean DMC+lg.
 \end{itemize}
@@
 \item do a literature search focused around these papers
-\item use mathcal on V, L, E (and introduce them)
-\item maybe use texttt for DPMC?
 \item do I need to formally consider extending a pseudo-Boolean function to a
   bigger domain?
+\item Introduce all the notation surrounding graphs ($\mathcal{V}$,
+  $\mathcal{L}$, $\mathcal{C}$, etc.) (and be consistent with its usage)
 \item Define:
   \begin{itemize}
+  \item scalar operations on ADDs
   \item an ADD as a DAG.
@@
 
-\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}, verbatim but with one change]
-  Let $X$ be a set of Boolean variables and $\phi$ be a CNF formula over $X$. A
-  \emph{project-join tree} (PJT) of $\phi$ is a tuple $(T, r, \gamma, \pi)$
-  where:
+\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}, with some changes]
+  Let $X$ be a set of Boolean variables, and $F$ be a set of pseudo-Boolean
+  functions $2^X \to \mathbb{R}$. A \emph{project-join tree} (PJT) of $F$ is a
+  tuple $(T, r, \gamma, \pi)$ where:
   \begin{itemize}
   \item $T$ is a tree with root $r \in \mathcal{V}(T)$,
-  \item $\gamma\colon \mathcal{L}(T) \to \mathbb{R}^{2^X}$ maps leaves of $T$ to
-    pseudo-Boolean functions, and
+  \item $\gamma\colon \mathcal{L}(T) \to F$ is a bijection between the leaves of
+    $T$ and the pseudo-Boolean functions in $F$, and
   \item $\pi\colon \mathcal{V}(T) \setminus \mathcal{L}(T) \to 2^X$ is a
@@
   \item for each internal node $n \in \mathcal{V}(T) \setminus \mathcal{L}(T)$,
-    variable $x \in \pi(n)$, and clause $c \in \phi$ such that $x$ appears in
-    $c$, the leaf node $\gamma^{-1}(c)$ must be a descendant of $n$ in $T$.
+    variable $x \in \pi(n)$, and `clause' $c \in \im \gamma$ such that $x$
+    appears in $c$, the leaf node $\gamma^{-1}(c)$ must be a descendant of $n$
+    in $T$.
   \end{enumerate}
@@
 
-Note that while Dudek et al. \cite{DBLP:conf/cp/DudekPV20} define $\gamma$ to be
-a bijection between leaves of a PJT and clauses, our definition is more
-general.
-
-\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}]
+\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}] \label{def:size}
   \[
@@
   A \emph{tree decomposition} of a graph $G$ is a pair $(T, \chi)$, where $T$ is
-  a tree and $\chi\colon V(T) \to 2^{V(G)}$ is a labelling function, with the
-  following properties:
+  a tree and $\chi\colon \mathcal{V}(T) \to 2^{\mathcal{V}(G)}$ is a labelling
+  function, with the following properties:
   \begin{itemize}
-  \item $\bigcup_{t \in V(T)} \chi(t) = V(G)$;
-  \item for every edge $e \in E(G)$, there exists $t \in V(T)$ such that $e$ has
-    both endpoints in $\chi(t)$;
-  \item for all $t, t', t'' \in V(T)$, if $t'$ is on the path between $t$ and
-    $t''$, then $\chi(t) \cap \chi(t'') \subseteq \chi(t')$.
+  \item $\bigcup_{t \in \mathcal{V}(T)} \chi(t) = \mathcal{V}(G)$;
+  \item for every edge $e \in \mathcal{E}(G)$, there exists $t \in
+    \mathcal{V}(T)$ such that $e$ has both endpoints in $\chi(t)$;
+  \item for all $t, t', t'' \in \mathcal{V}(T)$, if $t'$ is on the path between
+    $t$ and $t''$, then $\chi(t) \cap \chi(t'') \subseteq \chi(t')$.
   \end{itemize}
-  The \emph{width} of tree decomposition $(T, \chi)$ is $\max_{t \in V(T)}
-  |\chi(t)| - 1)$. The \emph{treewidth} of graph $G$ is the smallest $w$ such
-  that $G$ has a tree decomposition of width $w$.
+  The \emph{width} of tree decomposition $(T, \chi)$ is $\max_{t \in
+    \mathcal{V}(T)} |\chi(t)| - 1)$. The \emph{treewidth} of graph $G$ is the
+  smallest $w$ such that $G$ has a tree decomposition of width $w$.
 \end{definition}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-    \node[circle,draw] {$\exists$}
-    child {node (a) {$\vdots$}
-      child {node[circle,draw] {$c_1$}}
-    }
-    child {node (b) {$\vdots$}
-      child {node[circle,draw] {$\ast$}
-        child {node {$\vdots$}
-          child {node[circle,draw] {$c_i$}}
-        }
-      }
-    }
-    child {node (c) {$\vdots$}
-      child {node[circle,draw] {$c_l$}}
-    }
-    ;
-    \path (a) -- (b) node[midway] {$\cdots$};
-    \path (b) -- (c) node[midway] {$\cdots$};
-  \end{tikzpicture}
-  \caption{An example PJT with clauses $c_1, \dots, c_i, \dots, c_l$ that all
-    contain the same variable, its projection node $\exists$, and a node under
-    consideration $\ast$.}
-  \label{fig:example_pjt}
-\end{figure}
 
@@
   Let $(T, r, \gamma, \pi)$ be a PJT, and $X$ be the set of variables. The
-  functionality of DPMC execution can be represented by $\delta(r)$, where
-  $\delta\colon \mathcal{V}(T) \to \mathbb{R}^{2^X}$ is a recursive function
-  defined as
+  functionality of \textsc{DPMC} execution can be represented by $\delta(r)$,
+  where $\delta\colon \mathcal{V}(T) \to \mathbb{R}^{2^X}$ is a recursive
+  function defined as
   \begin{equation} \label{eq:execution}
@@
 
-% \begin{lemma} % NOTE: this lemma is already proven above
-%   Let $(S, \chi)$ be a tree decomposition, and $(T, r, \gamma, \pi)$ be its PJT
-%   generated by Algorithm~2 in \cite{DBLP:conf/cp/DudekPV20}. For any $t \in T$,
-%   the number of variables that appear in the ADDs within a PJT node is at
-%   most $k+1$.
-% \end{lemma}
-% \begin{proof}
-%   All such variables are introduced in a `clause' below and not projected in
-%   descendants. Each such variable would be in the bag of each clause that
-%   introduced it. By the tree decomposition properties, it will also be in the
-%   bag of both the projection node and the current node because they are on the
-%   path between the clause nodes (see \cref{fig:example_pjt}).
-% \end{proof}
-
 \begin{theorem}
@@
   is fixed-parameter tractable with respect to the $k$. Specifically,
-  \textsc{DPMC} execution time complexity is $\mathcal{O}(4^km(n+k))$, where $n
+  \textsc{DPMC} execution time complexity is $\mathcal{O}(4^knm)$, where $n
   = |\mathcal{L}(T)|$ is the number of clauses/leaves, and $m$ is the number of
@@
 \end{theorem}
-% TODO: start here. Use theorem 4 to show that the number of variables is
+% TODO: Use theorem 4 to show that the number of variables is
 % bounded by primal treewidth
@@
     complexity of operations performed within each call to $\delta$.
-  \item Let $t \in \mathcal{V}(T)$ be an arbitrary vertex of $T$. If $t$ is a
-    leaf,
-  \item The total time taken by the DPMC execution stage is the sum of the time
-    taken `inside' each PJT node. The number of such nodes is upper bounded by
-    $m$, so the total time complexity of DPMC is $\mathcal{O}(4^km(n+k))$.
-  \item Multiplying $m$ ADDs can then take up to $(m-1)(2^{k+1}-1)^2 =
-    \mathcal{O}(m4^k)$ (since one multiplication takes up to $(2^{k+1}-1)^2$
-    time and the and the result will have up to $2^{k+1} - 1$ nodes because the
-    domain stays the same).
-  \item Then, by \cref{lemma:basic_ops}, projecting $m$ variables will take
-    $\mathcal{O}(4^km)$ time.
-  \item In total, operations on a PJT node with $m$ children, $k$ variables, $n$ of
-    which are projected takes $\mathcal{O}(4^k(m+n))$ time.
+  \item Let $t \in \mathcal{L}(T)$ be a leaf. Note that
+    $|\mathtt{Vars}(\gamma(t))| \le k$ by \cref{def:size}. Assuming that clauses
+    have no repeating variables, it takes $\mathcal{O}(2^k)$ time to construct
+    $\delta(t)$ by \cref{lemma:clause_time} and $\mathcal{O}(2^kn)$ time to
+    construct all leaves of the PJT.
+  \item Now let $t \in \mathcal{V}(T) \setminus \mathcal{L}(T)$ be an internal
+    vertex, in which case we perform $|\mathcal{C}(t)|-1$ multiplications and
+    $|\pi(t)|$ projections. Note that $|\mathcal{C}(t)| \le |\mathcal{L}(T)| =
+    n$, $|\pi(t)| \le k$, and the ADDs involved can have up to $k$ variables.
+    This means that each ADD has $\mathcal{O}(2^k)$ nodes (regardless of whether
+    it comes from $\mathcal{C}(t)$ or from multiplications). Each such
+    multiplication then takes $\mathcal{O}(4^k)$ time by \cref{lemma:basic_ops},
+    and so all multiplications will take $\mathcal{O}(4^kn)$ time for $t$ and
+    $\mathcal{O}(4^knm)$ time across all $t \in \mathcal{V}(T) \setminus
+    \mathcal{L}(T)$ since the number of vertices in the PJT is bounded by the
+    number of variables.
+  \item Each variable is projected exactly once and is always projected from
+    an ADD with at most $\mathcal{O}(2^k)$ nodes. Thus, the time complexity of
+    projecting all variables is $\mathcal{O}(4^km)$.
+  \item In total, we get $\mathcal{O}(2^kn)$ time for the leaves,
+    $\mathcal{O}(4^knm)$ for multiplications, and $\mathcal{O}(4^km)$ for
+    projections, resulting in $\mathcal{O}(4^knm)$ time in total.
   \end{itemize}

### 2021-02-17 doc/paper3/paper.tex
Towards proof of correctness

@@
 \documentclass{article}
-\usepackage[ruled,vlined]{algorithm2e}
-\usepackage{amsfonts}
+\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
 \usepackage{amsmath}
@@
 \usepackage[UKenglish]{babel}
-\usepackage{bm}
-\usepackage{booktabs}
 \usepackage[capitalise]{cleveref}
-\usepackage{dashbox}
 \usepackage{fullpage}
@@
 \usepackage{mathtools}
-\usepackage{tikz}
-\usepackage{xcolor}
-\usepackage{xfrac}
 \usepackage[backgroundcolor=lightgray]{todonotes}
-\usepackage{soul}
-\usepackage{mathrsfs}
-\usepackage{capt-of}
-\usepackage{siunitx}
 
@@
 
-\DeclareMathOperator{\im}{im}
+\crefname{enumii}{Condition}{Conditions}
 
@@
 
-\begin{lemma} \label{lemma:add_size}
-  An ADD with $n$ variables has $\mathcal{O}(2^n)$ nodes.
-\end{lemma}
-\begin{proof}
-  An ADD with $n$ variables can be, at most, a complete binary tree of height
-  $n+1$ (as measured by the number of vertices). It would then have $2^0 + 2^1 +
-  \dots + 2^n = 2^{n+1} = \mathcal{O}(2^n)$ nodes.
-\end{proof}
-
-\begin{lemma} \label{lemma:clause_time}
-  Let $\phi$ be a conjunction of $n$ literals. Then the ADD representation of
-  $[\phi]^p_q$ can be constructed in $\mathcal{O}(2^n)$ time for any $p, q \in
-  \mathbb{R}$ such that $p \ne q$.
-\end{lemma}
-\begin{proof}
-  The ADD representation of $\phi$ itself can be constructed with a sequence of
-  $n-1$ calls to \texttt{apply} with one of the two operands in each call always
-  a literal. The number of variables in the other operand then follows the
-  sequence $1, 2, 3, \dots, n-1$. By \cref{lemma:add_size}, the numbers of nodes
-  in the ADD representations of these operands is then $\mathcal{O}(2^1),
-  \mathcal{O}(2^2), \dots, \mathcal{O}(2^{n-1})$. Since one of the operands is
-  of constant size, the overall time complexity of all calls to \texttt{apply}
-  is then
-  \[
-    \mathcal{O}(2^1) + \mathcal{O}(2^2) + \dots + \mathcal{O}(2^{n-1}) =
-    \mathcal{O}(2^n).
-  \]
-
-  Let $\alpha$ be the ADD representation of $\phi$. Then the ADD representation
-  of $[\phi]_q^p$ is $(p-q)\alpha + q$. As scalar operations can obviously be
-  implemented in linear time, the overall complexity remains $\mathcal{O}(2^n)$.
-\end{proof}
-
 % NOTE: weights on literals other than the positive literals that correspond to
@@
 \begin{definition}[old WMC instance]
-  An old WMC instance is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is the set
-  of indicator variables, $X_P$ is the set of parameter variables, $\phi$ is a
-  propositional formula over $X_I \cup X_P$, and $w\colon X_P \to \mathbb{R}$ is
-  the weight function.
-\end{definition}
+  An \emph{old WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
+  the set of indicator variables, $X_P$ is the set of parameter variables (with
+  $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula in CNF over
+  $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
+  X_P\} \to \mathbb{R}$ is the weight function. The \emph{answer} of the
+  instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
+\end{definition} % TODO: add a citation for this.
 
-\begin{definition}[new WMC instance]
-  A new WMC instance is a tuple $(F, X, \omega)$, where $X$ is the set of
+\begin{remark}
+  Encodings such as \texttt{cd05} and \texttt{cd06} are \emph{not} WMC
+  encodings. Instead, they encode Bayesian network inference into instances of
+  the \emph{minimum-cardinality} WMC problem, where the answer is defined to be
+  $\sum_{Y \models \phi\text{, }|Y| = k} \prod_{Y \models l}
+  w(l)$, where $k = \min_{Y \models \phi\text{, }Y \ne \emptyset}
+  |Y|$, if $k$ exists, otherwise the answer is zero. This additional
+  condition on model cardinality becomes necessary because these encodings
+  eliminate clauses of the form $p \Rightarrow i$, where $p \in X_P$ is a
+  parameter variable, and $i \in X_I$ is an indicator variable. Nonetheless, our
+  transformation algorithm still works on such encodings, although the
+  experimental results are discouraging because they use approximately twice as
+  many indicator variables. For instance, each binary variable of a Bayesian
+  network is encoded using two indicator variables while one would suffice.
+\end{remark} % TODO: perhaps add this claim as a corollary
+
+\begin{definition}[new WMC instance] \label{def:new_wmc}
+  A \emph{new WMC instance} is a tuple $(F, X, \omega)$, where $X$ is the set of
   variables, $F$ is a set of pseudo-Boolean functions $2^X \to \mathbb{R}$, and
-  $\omega \in \mathbb{R}$ is the scaling factor.
+  $\omega \in \mathbb{R}$ is the scaling factor. The \emph{answer} of the
+  instance is $\omega \cdot \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
 \end{definition}
@@
   \caption{WMC instance transformation}
+  \label{alg:transformation}
   \SetKwFunction{rename}{rename}
@@
   $\omega \gets 1$\;
-  let $d\colon X_P \to \mathbb{N}$ be defined as $v \mapsto |\{ u \in X_P \mid u
-  \le v \}|$\;
-  \ForEach{clause $c \in \phi$}{
-    \uIf{$c \cap X_P = \{ v \}$ for some $v$ \textnormal{\textbf{and}} $w(v) \ne
+  let $d\colon X_P \to \mathbb{N}$ be defined as $p \mapsto |\{ o \in X_P \mid o
+  \le p \}|$\;
+  \ForEach{clause $c \in \phi$\label{line:foreach1start}}{
+    \uIf{$c \cap X_P = \{ p \}$ for some $p$ \textnormal{\textbf{and}} $w(p) \ne
       1$}{
-      \uIf{$|c| = 1$}{$\omega \gets \omega \times w(v)$\;}
+      \uIf{$|c| = 1$}{$\omega \gets \omega \times w(p)$\;}
       \Else{
         $F \gets F \cup \left\{ \left[ \bigwedge_{l \in c \setminus
-              \{v\}} \neg l \right]^{w(v)}_1 \right\}$\;
+              \{p\}} \neg l \right]^{w(p)}_1 \right\}$\;
       }
     }
-    \ElseIf{$\{v \mid \neg v \in c\} \cap X_P  = \emptyset$}{
-      $F \gets F \cup \{ [c]^1_0 \}$\;
+    \ElseIf{$\{p \mid \neg p \in c\} \cap X_P  = \emptyset$}{
+      $F \gets F \cup \{ [c]^1_0 \}$\; \label{line:foreach1end}
     }
@@
 
+\subsection{Correctness}
+
+\begin{theorem}[Early Projection
+  \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20}, verbatim]
+  Let $X$ and $Y$ be sets of variables. For all functions $f\colon 2^X \to
+  \mathbb{R}$ and $g\colon 2^Y \to \mathbb{R}$, if $x \in X \setminus Y$, then
+  $\exists_x (f \cdot g) = (\exists_x f) \cdot g$.
+\end{theorem}
+% TODO: mention that formulas, clauses, and models are all treated as sets
+
+\begin{lemma} \label{lemma:sum}
+  For any pseudo-Boolean function $f\colon 2^X \to \mathbb{R}$, $(\exists_X
+  f)(\emptyset) = \sum_{Y \subseteq X} f(Y)$.
+\end{lemma}
+\begin{proof}
+  For base case, let $X = \{x\}$. Then
+  \[
+    \exists_xf = f|_{x=1} + f|_{x=0},
+  \]
+  by \cref{def:projection} and so
+  \[
+    (\exists_xf)(\emptyset) = f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset)
+  \]
+  by \cref{def:operations}. Then
+  \[
+    f|_{x=1}(\emptyset) = f(\{x\}), \quad \text{and} \quad f|_{x=0}(\emptyset) =
+    f(\emptyset)
+  \]
+  by \cref{def:restriction}. It follows that
+  \[
+    (\exists_xf)(\emptyset) = f(\{x\}) + f(\emptyset) = \sum_{Y \subseteq \{x\}}
+    f(Y)
+  \]
+  as required. This easily extends to $|X| > 1$ by the definition of projection
+  on sets of variables. % TODO: once I've defined it, add a reference here.
+\end{proof}
+% TODO: must mention that operations like +/x are commutative, associative, etc.
+
+% NOTE: mention that this is similar (but not equal) to the DPMC/ADDMC result
+\begin{proposition}
+  Let $(\phi, X_I, X_P, w)$ be an old WMC instance. Then
+  \begin{equation}
+  \left(\left\{[c]_0^1 \;\middle|\; c \in \phi\right\} \cup \left\{[x]_{w(\neg
+        x)}^{w(x)} \;\middle|\; x \in X_I \cup X_P\right\}, X_I \cup X_P,
+    1\right) \label{eq:new_wmc}
+  \end{equation}
+  is a new WMC instance with the same answer.
+\end{proposition}
+\begin{proof}
+  The answer of \cref{eq:new_wmc} is
+  \begin{align*}
+    \left(\exists_{X_I \cup X_P} \prod_{c \in \phi} [c]_0^1 \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset) &= \sum_{Y \subseteq X_I \cup X_P} \left(\prod_{c \in \phi} [c]_0^1 \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)(Y) \\
+&= \sum_{Y \subseteq X_I \cup X_P} \underbrace{\left(\prod_{c \in \phi} [c]_0^1\right)}_f(Y) \underbrace{\left(\prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)}_g(Y)
+  \end{align*}
+  by \cref{def:new_wmc,lemma:sum,def:operations}. Note that
+  \[
+    f(Y) =
+    \begin{cases}
+      1 & \text{if } Y \models \phi, \\
+      0 & \text{otherwise},
+    \end{cases}
+    \quad
+    \text{and}
+    \quad
+    g(Y) = \prod_{Y \models l} w(l),
+  \]
+  which means that
+  \[
+    \sum_{Y \subseteq X_I \cup X_P} f(Y)g(Y) = \sum_{Y \models \phi} \prod_{Y
+      \models l} w(l)
+  \]
+  as required.
+\end{proof}
+
+\begin{theorem}[Correctness]
+  \Cref{alg:transformation}, when given an old WMC instance $(\phi, X_I, X_P,
+  w)$, returns a new WMC instance with the same answer, provided the following
+  conditions are satisfied:
+  \begin{enumerate}
+  \item for all indicator variables $i \in X_I$, $w(i) = w(\neg i) = 1$,
+  \item and either
+    \begin{enumerate}
+    \item for all parameter variables $p \in X_P$, there is a family of literals
+      $(l_i)_{i=1}^n$ such that \label{condition:d02}
+      \begin{enumerate}
+      \item $w(\neg p) = 1$,
+      \item $l_i \in X_I$ or $\neg l_i \in X_I$ for all $i = 1, \dots, n$,
+      \item and $\{ c \in \phi \mid p \in c \text{ or } \neg p \in c \} =
+        \left\{p \lor \bigvee_{i=1}^n \neg l_i \right\} \cup \{ l_i \lor \neg p
+        \mid i = 1, \dots, n \}$;
+      \end{enumerate}
+    \item or \label{condition:bklm16}
+      \begin{enumerate}
+      \item $w(p) + w(\neg p) = 1$,
+      \item there is no clause $c \in \phi$ with $\neg p \in c$,
+      \item and for any pair of clauses $c, d \in \phi$ such that $c \ne d$, $p
+        \in c$ and $p \in d$, $\mathtt{Vars}(c) \cap \mathtt{Vars}(d) = \{ p
+        \}$.
+      \end{enumerate}
+    \end{enumerate}
+  \end{enumerate}
+\end{theorem}
+\begin{proof}
+  % TODO: finish the proof
+  First, let us assume that \cref{condition:d02} applies and consider the
+  collective effect of the loop on
+  \crefrange{line:foreach1start}{line:foreach1end} for: 1) clauses that have a
+  positive parameter variable, 2) clauses that have a negative parameter
+  variable (removed), 3) clauses that don't have parameter variables (left
+  unchanged).
+\end{proof}
+
+\paragraph{Notes.}
+\begin{itemize}
+\item The family of literals could be empty.
+\item This just says that $p$ is equivalent to a conjunction.
+\item The first group of conditions applies to \texttt{d02}, while the second
+  group applies to \texttt{bklm16}.
+\item For \texttt{cd05} and \texttt{cd06}, condition $2bi$ should be replaced
+  with $w(\neg p) = 1$.
+\end{itemize}
+
 \section{Parameterised Complexity of \textsc{DPMC}}
@@
 \item By \textsc{DPMC}, we always mean DMC+lg.
+\item The constant is inspired by the \texttt{bklm16} encoding.
 \end{itemize}
@@
 \begin{itemize}
-\item do a literature search focused around these papers
-\item do I need to formally consider extending a pseudo-Boolean function to a
+\item Do I need to formally consider extending a pseudo-Boolean function to a
   bigger domain?
 \item Introduce all the notation surrounding graphs ($\mathcal{V}$,
-  $\mathcal{L}$, $\mathcal{C}$, etc.) (and be consistent with its usage)
+  $\mathcal{E}$ $\mathcal{L}$, $\mathcal{C}$, etc.) (and be consistent with its
+  usage) and formulas (variable, literal, clause, CNF, etc.)
+\item Use \cref{thm:connection} to show the connection between primal treewidth
+  and the width of the PJT (linking the complexity of BN inference with the DPMC
+  complexity).
+\item Come up with better names for old/new WMC instances.
 \item Define:
   \begin{itemize}
-  \item scalar operations on ADDs
-  \item an ADD as a DAG.
+  \item scalar operations on ADDs,
+  \item an ADD as a DAG,
   \item What does it mean for an ADD to `have' variables? Maybe refer to
     pseudo-Boolean function sensitivity.
-  \item Formal definition of a previous WMC instance (CNF, literal weight
-    function) and the new definition (set of $2^{X} \to \mathbb{R}_{\ge 0}$
-    pseudo-Boolean functions and a constant). Note that the constant idea is
-    borrowed from \texttt{bklm16}.
-  \item Boolean formula in CNF (perhaps this is too trivial to define),
   \item primal graph of a CNF formula (a.k.a.
@@
   \item moralisation of a Bayesian network (or of any DAG),
+  \item projection of a set of variables.
   \end{itemize}
 \end{itemize}
+
+\begin{lemma} \label{lemma:add_size}
+  An ADD with $n$ variables has $\mathcal{O}(2^n)$ nodes.
+\end{lemma}
+\begin{proof}
+  An ADD with $n$ variables can be, at most, a complete binary tree of height
+  $n+1$ (as measured by the number of vertices). It would then have $2^0 + 2^1 +
+  \dots + 2^n = 2^{n+1} = \mathcal{O}(2^n)$ nodes.
+\end{proof}
+
+\begin{lemma} \label{lemma:clause_time}
+  Let $\phi$ be a conjunction of $n$ literals. Then the ADD representation of
+  $[\phi]^p_q$ can be constructed in $\mathcal{O}(2^n)$ time for any $p, q \in
+  \mathbb{R}$ such that $p \ne q$.
+\end{lemma}
+\begin{proof}
+  The ADD representation of $\phi$ itself can be constructed with a sequence of
+  $n-1$ calls to \texttt{apply} with one of the two operands in each call always
+  a literal. The number of variables in the other operand then follows the
+  sequence $1, 2, 3, \dots, n-1$. By \cref{lemma:add_size}, the numbers of nodes
+  in the ADD representations of these operands is then $\mathcal{O}(2^1),
+  \mathcal{O}(2^2), \dots, \mathcal{O}(2^{n-1})$. Since one of the operands is
+  of constant size, the overall time complexity of all calls to \texttt{apply}
+  is then
+  \[
+    \mathcal{O}(2^1) + \mathcal{O}(2^2) + \dots + \mathcal{O}(2^{n-1}) =
+    \mathcal{O}(2^n).
+  \]
+
+  Let $\alpha$ be the ADD representation of $\phi$. Then the ADD representation
+  of $[\phi]_q^p$ is $(p-q)\alpha + q$. As scalar operations can obviously be
+  implemented in linear time, the overall complexity remains $\mathcal{O}(2^n)$.
+\end{proof}
 
@@
   \item for each internal node $n \in \mathcal{V}(T) \setminus \mathcal{L}(T)$,
-    variable $x \in \pi(n)$, and `clause' $c \in \im \gamma$ such that $x$
+    variable $x \in \pi(n)$, and `clause' $c \in F$ such that $x$
     appears in $c$, the leaf node $\gamma^{-1}(c)$ must be a descendant of $n$
@@
   $\mathtt{width}(T) \coloneqq \max_{n \in \mathcal{V}(T)} \mathtt{size}(n)$.
-\end{definition}
+\end{definition} % TODO: don't actually need this much notation.
 
@@
 
-\begin{definition}
+\begin{definition} \label{def:operations}
   Let $f, g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions. Operations
@@
 
-\begin{definition}
+\begin{definition} \label{def:restriction}
   Let $f\colon 2^X \to \mathbb{R}$ be a pseudo-Boolean function, and $x \in X$.
@@
 % TODO: will need to rephrase this to fit my context
-\begin{theorem}[Theorem~4 in \cite{DBLP:conf/cp/DudekPV20}, almost verbatim]
-  Let $\phi$ be a CNF formula over a set $X$ of variables and $(S, \chi)$ be a
-  tree decomposition of the primal graph of $\phi$ of width $w$. Then
-  Algorithm~2 returns a PJT of $\phi$ of width at most $w+1$.
+\begin{theorem}[Theorem~4 in \cite{DBLP:conf/cp/DudekPV20}, almost
+  verbatim] \label{thm:connection}
+  Let $\phi$ be a propositional formula in CNF over a set $X$ of variables and
+  $(S, \chi)$ be a tree decomposition of the primal graph of $\phi$ of width
+  $w$. Then Algorithm~2 returns a PJT of $\phi$ of width at most $w+1$.
 \end{theorem}
@@
 \begin{theorem}
-  Let $(T, r, \gamma, \pi)$ be a PJT of width $k$. Then \textsc{DPMC} execution
-  is fixed-parameter tractable with respect to the $k$. Specifically,
-  \textsc{DPMC} execution time complexity is $\mathcal{O}(4^knm)$, where $n
-  = |\mathcal{L}(T)|$ is the number of clauses/leaves, and $m$ is the number of
-  variables.
+  Let $(F, X, \omega)$ be a WMC instance, and $(T, r, \gamma, \pi)$ be its PJT
+  of width $k$. Then \textsc{DPMC} execution is fixed-parameter tractable with
+  respect to $k$. Specifically, \textsc{DPMC} execution time complexity is
+  $\mathcal{O}(4^knm)$, where $n = |\mathcal{L}(T)| = |F|$, and $m = |X|$ is the
+  number of variables.
 \end{theorem}
-% TODO: Use theorem 4 to show that the number of variables is
-% bounded by primal treewidth
 \begin{proof}
   \begin{itemize}
-  \item Let us consider the overall complexity of all multiplications and
-    projections throughout the recursive calls of $\delta$ in
-    \cref{def:abstraction}. Clearly, the overall complexity is the sum of the
-    complexity of operations performed within each call to $\delta$.
+  \item We consider the complexity of constructing ADD representations of the
+    pseudo-Boolean functions in $F$ and the complexity of multiplication and
+    projection operations throughout the recursive calls of $\delta$ in
+    \cref{def:abstraction}.
   \item Let $t \in \mathcal{L}(T)$ be a leaf. Note that
@@
     projecting all variables is $\mathcal{O}(4^km)$.
-  \item In total, we get $\mathcal{O}(2^kn)$ time for the leaves,
+  \item In total, we get $\mathcal{O}(2^kn)$ time for constructing initial ADDs,
     $\mathcal{O}(4^knm)$ for multiplications, and $\mathcal{O}(4^km)$ for

### 2021-02-18 doc/paper3/paper.tex
The correctness proof is almost complete

@@
 \begin{theorem}[Early Projection
-  \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20}, verbatim]
+  \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20},
+  verbatim] \label{thm:early}
   Let $X$ and $Y$ be sets of variables. For all functions $f\colon 2^X \to
@@
 % NOTE: mention that this is similar (but not equal) to the DPMC/ADDMC result
-\begin{proposition}
+\begin{proposition} \label{prop:equivalence}
   Let $(\phi, X_I, X_P, w)$ be an old WMC instance. Then
@@
     \begin{enumerate}
-    \item for all parameter variables $p \in X_P$, there is a family of literals
-      $(l_i)_{i=1}^n$ such that \label{condition:d02}
+    \item for all parameter variables $p \in X_P$, there is a non-empty family
+      of literals $(l_i)_{i=1}^n$ such that \label{condition:d02}
       \begin{enumerate}
@@
       \item $l_i \in X_I$ or $\neg l_i \in X_I$ for all $i = 1, \dots, n$,
+        \label{condition:equivalence1}
       \item and $\{ c \in \phi \mid p \in c \text{ or } \neg p \in c \} =
         \left\{p \lor \bigvee_{i=1}^n \neg l_i \right\} \cup \{ l_i \lor \neg p
-        \mid i = 1, \dots, n \}$;
+        \mid i = 1, \dots, n \}$; \label{condition:equivalence2}
       \end{enumerate}
-    \item or \label{condition:bklm16}
+    \item or for all parameter variables $p \in X_P$, \label{condition:bklm16}
       \begin{enumerate}
       \item $w(p) + w(\neg p) = 1$,
-      \item there is no clause $c \in \phi$ with $\neg p \in c$,
+      \item for any clause $c \in \phi$, $|c \cap X_P| \le 1$,
+      \item there is no clause $c \in \phi$ such that $\neg p \in c$,
       \item and for any pair of clauses $c, d \in \phi$ such that $c \ne d$, $p
@@
   \end{enumerate}
-\end{theorem}
-\begin{proof}
-  % TODO: finish the proof
-  First, let us assume that \cref{condition:d02} applies and consider the
-  collective effect of the loop on
-  \crefrange{line:foreach1start}{line:foreach1end} for: 1) clauses that have a
-  positive parameter variable, 2) clauses that have a negative parameter
-  variable (removed), 3) clauses that don't have parameter variables (left
-  unchanged).
+\end{theorem} % TODO: add parentheses around products
+% TODO: maybe give a name to (2) since it's wrong to call it an equation
+\begin{proof} % TODO: check if each condition is actually used
+  % TODO: start here: consider how the transformation changes the 'normal form'.
+  % We will show that every iteration keeps the answer the same as in the normal form.
+  By \cref{prop:equivalence},
+  \begin{equation}
+    \left(\left\{[c]_0^1 \;\middle|\; c \in \phi\right\} \cup \left\{[x]_{w(\neg
+          x)}^{w(x)} \;\middle|\; x \in X_I \cup X_P\right\}, X_I \cup X_P,
+      1\right) \label{eq:new_wmc}
+  \end{equation}
+  is a new WMC instance with the same answer as the given old WMC instance. By
+  \cref{def:new_wmc}, its answer is
+  \begin{equation} \label{eq:answer}
+    \left(\exists_{X_I \cup X_P} \prod_{c \in \phi} [c]_0^1 \prod_{x \in X_I
+        \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset)
+  \end{equation}
+  Since both \cref{condition:d02,condition:bklm16} ensure that each clause in
+  $\phi$ has at most one parameter variable, we can partition $\phi$ into
+  $\phi_* \coloneqq \{c \in \phi \mid \mathtt{Vars}(c) \cap X_P = \emptyset \}$
+  and $\phi_p \coloneqq \{ c \in \phi \mid \mathtt{Vars}(c) \cap X_P = \{ p \}
+  \}$ for all $p \in X_P$. We can then use \cref{thm:early} to reorder
+  \cref{eq:answer} into
+  \[
+    \left(\exists_{X_I} \left( \prod_{x \in X_I} [x]_{w(\neg x)}^{w(x)} \right)
+      \left( \prod_{c \in \phi_*} [c]_0^1 \right) \prod_{p \in X_P} \exists_p
+      [p]_{w(\neg p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 \right)(\emptyset).
+  \]
+
+  Let us first consider how the unfinished WMC instance $(F, X_I, \omega)$ after
+  the loop on \crefrange{line:foreach1start}{line:foreach1end} differs from
+  \cref{eq:new_wmc}. Note that \cref{alg:transformation} leaves each $c \in
+  \phi_*$ unchanged, i.e., adds $[c]_0^1$ to $F$. We can then fix an arbitrary
+  $p \in X_P$ and let $F_p$ be the set of functions added to $F$ as a
+  replacement of $\phi_p$. It is sufficient to show that
+  \begin{equation} \label{eq:to_show}
+    \omega \prod_{f \in F_p} f = \exists_p [p]_{w(\neg p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1.
+  \end{equation}
+  Note that under \cref{condition:d02},
+  \[
+    \bigwedge_{c \in \phi_p} c \equiv p \Leftrightarrow \bigwedge_{i=1}^n l_i
+  \]
+  for some family of indicator variable literals $(l_i)_{i=1}^n$. Thus,
+  \[
+    \exists_p [p]_{w(\neg p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 = \exists_p
+    [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1.
+  \]
+  If $w(p) = 1$, then
+  \begin{equation} \label{eq:bigsums}
+    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
+    \right]_0^1 = \exists_p \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
+    \right]_0^1 = \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
+    \right]_0^1\right|_{p=1} + \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n
+      l_i \right]_0^1\right|_{p=0}
+  \end{equation}
+  by \cref{def:projection}. Since for any input, $\bigwedge_{i=1}^n l_i$ is
+  either true or false, exactly one of the two summands in \cref{eq:bigsums}
+  will be equal to one, and the other will be equal to zero, and so
+  \[
+    \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
+      \right]_0^1\right|_{p=1} + \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n
+        l_i \right]_0^1\right|_{p=0} = 1,
+  \]
+  where $1$ is a pseudo-Boolean function that always returns one. On the other
+  side of \cref{eq:to_show}, since $F_p = \emptyset$, and $\omega$ is unchanged,
+  we get $\omega\prod_{f \in F_p} f = 1$, and so \cref{eq:to_show} is satisfied
+  under \cref{condition:d02} when $w(p) = 1$.
+
+  If $w(p) \ne 1$, then
+  \[
+    F_p = \left\{ \left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} \right\},
+  \]
+  and so we want to show that
+  \[
+    \left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} = \exists_p [p]_1^{w(p)}
+    \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1.
+  \]
+  By \cref{def:projection},
+  \begin{align*}
+    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 &= \left.\left( [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 \right)\right|_{p=1} + \left.\left([p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 \right)\right|_{p=0} \\
+                                                                                      &= w(p) \cdot \left[ \bigwedge_{i=1}^n l_i \right]_0^1 + \left[ \bigwedge_{i=1}^n l_i \right]_1^0 = \left[ \bigwedge_{i=1}^n l_i \right]_1^{w(p)}
+  \end{align*}
+  as required. This finishes the proof of the correctness of the first `foreach'
+  loop under \cref{condition:d02}.
+
+  Now let us assume \cref{condition:bklm16}. We still want to prove
+  \cref{eq:to_show}.
 \end{proof}
+% TODO: now consider the second for loop
+% TODO: condition 1 is necessary in both cases because we're ignore the weights
+% of indicator variables
 
@@
 \begin{itemize}
-\item The family of literals could be empty.
 \item This just says that $p$ is equivalent to a conjunction.
@@
   \[
-    (f+g)(Y) \coloneqq f(Y)+g(Y),
-  \]
-  and
-  \[
-    (fg)(Y) \coloneqq f(Y)g(Y)
+    (f+g)(Y) \coloneqq f(Y)+g(Y), \quad \text{and} \quad (fg)(Y) \coloneqq
+    f(Y)g(Y)
   \]
@@
   \[
-    f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\}),
-  \]
-  and
-  \[
+    f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\}), \quad \text{and} \quad
     f|_{x=1}(Y) \coloneqq f(Y \cup \{x\})
@@
   \[
-    \exists_xf = f|_{x=1} + f|_{x=0}
+    \exists_xf \coloneqq f|_{x=1} + f|_{x=0}
   \]
@@
   \begin{equation} \label{eq:execution}
-    \delta(t) =
+    \delta(t) \coloneqq
     \begin{cases}

### 2021-02-20 doc/paper3/paper.tex
The big proof is mostly complete!

@@
 
-\paragraph{Notation.} For any propositional formula $\phi$ and $p, q \in
-\mathbb{R}$, let $[\phi]^p_q\colon 2^X \to \mathbb{R}$ be a
-pseudo-Boolean function defined as
+\paragraph{Notation.} For any propositional formula $\phi$ over a set of
+variables $X$ and $p, q \in \mathbb{R}$, let $[\phi]^p_q\colon 2^X \to
+\mathbb{R}$ be a pseudo-Boolean function defined as
 \[
@@
 
-% NOTE: weights on literals other than the positive literals that correspond to
-% variables in $X_P$ are redundant as they either are equal to one or duplicate
-% an already-defined weight.
+% NOTE: ...that we will need.
+% NOTE: The proof immediately comes from the definition (of operations).
+\begin{proposition}[Basic properties] \label{prop:basic}
+  For any propositional formulas $\phi$ and $\psi$, and $a, b, c, d \in
+  \mathbb{R}$,
+  \begin{itemize}
+  \item $[\phi]^a_b = [\neg \phi]^b_a$;
+  \item $c + [\phi]^a_b = [\phi]^{a+c}_{b+c}$;
+  \item $c \cdot [\phi]^a_b = [\phi]^{ac}_{bc}$;
+  \item $[\phi]^a_b \cdot [\phi]^c_d = [\phi]^{ac}_{bd}$;
+  \item $[\phi]^1_0 \cdot [\psi]_0^1 = [\phi \land \psi]_0^1$.
+  \end{itemize}
+\end{proposition}
+
 \begin{definition}[old WMC instance]
@@
 \item It is already well-known that WMC is FPT.
+\item Weights on literals other than the positive literals that correspond to
+  variables in $X_P$ are redundant as they either are equal to one or duplicate
+  an already-defined weight.
+\item Mention that formulas, clauses, and models are all treated as sets.
 \end{itemize}
@@
 \end{theorem}
-% TODO: mention that formulas, clauses, and models are all treated as sets
 
@@
 \end{proof}
-% TODO: must mention that operations like +/x are commutative, associative, etc.
 
@@
       \item there is no clause $c \in \phi$ such that $\neg p \in c$,
-      \item and for any pair of clauses $c, d \in \phi$ such that $c \ne d$, $p
-        \in c$ and $p \in d$, $\mathtt{Vars}(c) \cap \mathtt{Vars}(d) = \{ p
-        \}$.
+      \item if $\{ p \} \in \phi$, then there is no clause $c \in \phi$ such
+        that $c \ne \{ p \}$ and $p \in c$, \label{cond:just_parameter}
+        % 'prime implicants are logically disjoint'
+      \item and for any $c, d \in \phi$ such that $c \ne d$, $p \in c$ and $p
+        \in d$, $\bigwedge_{l \in c \setminus \{ p \}} \neg l \land \bigwedge_{l
+          \in d \setminus \{ p \}} \neg l$ is false. \label{cond:disjoint}
       \end{enumerate}
@@
 % TODO: maybe give a name to (2) since it's wrong to call it an equation
-\begin{proof} % TODO: check if each condition is actually used
-  % TODO: start here: consider how the transformation changes the 'normal form'.
-  % We will show that every iteration keeps the answer the same as in the normal form.
+% TODO: check if each condition is actually used. Maybe turn this into a
+% paragraph that gives an overview of the proof.
+\begin{proof}
   By \cref{prop:equivalence},
@@
   \]
-  and so we want to show that
+  and $\omega = 1$, and so we want to show that
   \[
@@
   Now let us assume \cref{condition:bklm16}. We still want to prove
-  \cref{eq:to_show}.
+  \cref{eq:to_show}. If $w(p) = 1$, then $F_p = \emptyset$, and $\omega = 1$,
+  and so the left-hand side of \cref{eq:to_show} is equal to one. Then the
+  right-hand side is
+  \[
+    \exists_p [p]_0^1 \prod_{c \in \phi_p} [c]_0^1 = \exists_p \left[ p \land
+      \bigwedge_{c \in \phi_p} c \right]_0^1 = \exists_p [p]_0^1 = 0 + 1 = 1
+  \]
+  by \cref{prop:basic,def:projection}, and because $p \in c$ for every clause $c
+  \in \phi_p$.
+
+  If $w(p) \ne 1$, and $\{ p \} \in \phi_p$, then, by
+  \cref{cond:just_parameter}, $\phi_p = \{ \{ p \} \}$, and
+  \cref{alg:transformation} produces $F_p = \emptyset$ and $\omega = w(p)$, and
+  so
+  \[
+    \omega \prod_{f \in F_p} f = w(p).
+  \]
+  Whereas on the other side of \cref{eq:to_show},
+  \[
+    \exists_p [p]_{w(\neg p)}^{w(p)} [p]_0^1 = \exists_p [p]^{w(p)}_0 = w(p)
+  \]
+  by \cref{prop:basic,def:projection}.
+
+  The only remaining case is when $w(p) \ne 1$ and $\{ p \} \not \in \phi_p$.
+  Then $\omega = 1$, and
+  \[
+    F_p = \left\{ \left[\bigwedge_{l \in c \setminus \{ p \}} \neg
+        l\right]_1^{w(p)} \;\middle|\; c \in \phi_p \right\},
+  \]
+  so need to show that
+  \[
+    \prod_{c \in \phi_p} \left[\bigwedge_{l \in c \setminus \{ p \}} \neg
+      l\right]_1^{w(p)} = \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p}
+    [c]_0^1.
+  \]
+  We can rearrange the right-hand-side as
+  \begin{align*}
+    \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 &= \exists_p [p]_{1-w(p)}^{w(p)} \left[\bigwedge_{c \in \phi_p} c\right]_0^1 = \exists_p [p]_{1-w(p)}^{w(p)} \left[ p \lor \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 \\
+                                                               &= w(p) + (1-w(p)) \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 = w(p) + \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^{1-w(p)} \\
+                                                               &= \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_{w(p)}^1 = \left[ \neg \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \neg(c \setminus \{ p \}) \right]_1^{w(p)} \\
+                                                               &= \left[ \bigvee_{c \in \phi_p} \neg \bigvee_{l \in c \setminus \{ p \}} l \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}
+  \end{align*}
+   by \cref{prop:basic,def:projection}. By \cref{cond:disjoint}, $\bigwedge_{l
+     \in c \setminus \{ p \}} \neg l$ can be true for at most one $c \in
+   \phi_p$, and so
+   \[
+     \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l
+     \right]_1^{w(p)} = \prod_{c \in \phi_p} \left[ \bigwedge_{l \in c \setminus
+         \{ p \}} \neg l \right]_1^{w(p)}
+   \]
+   which is exactly what we needed to show.
 \end{proof}
@@
 % of indicator variables
+% NOTE: benefits of having the proof in the paper:
+% 1) it puts all the encodings on a common ground
+% 2) it illustrates the convenience of our notation for reasoning about (certain
+% types of) pseudo-Boolean functions (stress this!!!)
+% 3) it's too big and too important to be left for the appendix
+% NOTE: we don't make a distinction between a real number and a (PB) function
+% that always returns that number.
+% NOTE: projection is assumed to have lowest precedence (i.e., \exists_x fg =
+% \exists_x (fg) and not (\exists_x f)g).
+% TODO: need another basic property: (fg)|_{x=i} = f|_{x=i} * g|_{x=i} for i=0, 1.
+% TODO: \times -> \cdot
 
@@
   \]
-  for all $Y \subseteq X$.
+  for all $Y \subseteq X$. This means that binary operations on pseudo-Boolean
+  functions inherit properties such as associativity and commutativity.
 \end{definition}

### 2021-02-20 doc/paper3/paper.tex
New template

@@
-\documentclass{article}
+\documentclass[runningheads]{llncs}
+
+\usepackage{graphicx}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+\usepackage{amssymb}
+\usepackage{mathtools}
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage[UKenglish]{babel}
 \usepackage[capitalise]{cleveref}
-\usepackage{fullpage}
-\usepackage[utf8]{inputenc}
-\usepackage[UKenglish]{isodate}
-\usepackage{mathtools}
-\usepackage[backgroundcolor=lightgray]{todonotes}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
 
@@
 
+\begin{document}
+
+%\title{Contribution Title\thanks{Supported by organization x.}}
 \title{Weighted Model Counting Without Parameter Variables}
 
-\begin{document}
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
 
-\maketitle
+%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
+%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
+%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+
+%\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+
+%\institute{Princeton University, Princeton NJ 08544, USA \and
+%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+%\email{lncs@springer.com}\\
+%\url{http://www.springer.com/gp/computer-science/lncs} \and
+%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+%\email{\{abc,lncs\}@uni-heidelberg.de}}
+
+\maketitle              % typeset the header of the contribution
+
+\begin{abstract}
+  The abstract should briefly summarize the contents of the paper in
+  150--250 words.
+
+  \keywords{First keyword  \and Second keyword \and Another keyword.}
+\end{abstract}
 
@@
 
+\begin{definition} \label{def:operations}
+  Let $f, g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions. Operations
+  such as addition and multiplication are defined pointwise as
+  \[
+    (f+g)(Y) \coloneqq f(Y)+g(Y), \quad \text{and} \quad (fg)(Y) \coloneqq
+    f(Y)g(Y)
+  \]
+  for all $Y \subseteq X$. This means that binary operations on pseudo-Boolean
+  functions inherit properties such as associativity and commutativity.
+\end{definition}
+
+\begin{definition} \label{def:restriction}
+  Let $f\colon 2^X \to \mathbb{R}$ be a pseudo-Boolean function, and $x \in X$.
+  Then $f|_{x=0}, f|_{x=1}\colon 2^X \to \mathbb{R}$ are \emph{restrictions} of
+  $f$ defined as
+  \[
+    f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\}), \quad \text{and} \quad
+    f|_{x=1}(Y) \coloneqq f(Y \cup \{x\})
+  \]
+  for all $Y \subseteq X$.
+\end{definition}
+
+\begin{definition} \label{def:projection}
+  Let $X$ be a set. For any $x \in X$, \emph{projection} $\exists_x$ is an
+  endomorphism $\exists_x\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined
+  as
+  \[
+    \exists_xf \coloneqq f|_{x=1} + f|_{x=0}
+  \]
+  for any $f\colon 2^X \to \mathbb{R}$.
+\end{definition}
+
 % NOTE: ...that we will need.
@@
   \end{itemize}
+  And for any pair of pseudo-Boolean functions $f, g \colon 2^X \to \mathbb{R}$
+  and $x \in  X$, $(fg)|_{x=i} = f|_{x=i} \cdot g|_{x=i}$ for $i = 0, 1$.
 \end{proposition}
@@
 \item Mention that formulas, clauses, and models are all treated as sets.
+\item The constant is inspired by the \texttt{bklm16} encoding.
+\item We don't make a distinction between a real number and a (pseudo-Boolean)
+  function that always returns that number.
+\item Throughout the paper, projection is assumed to have the lowest precedence
+  (e.g., $\exists_x fg = \exists_x (fg)$ and not $(\exists_xf)g$).
 \end{itemize}
@@
   }
-  \ForEach{indicator variable $v \in X_I$}{
+  \ForEach{indicator variable $v \in X_I$ \label{line:foreach2start}}{
     \If{$\{[v]_1^p, [\neg v]_1^q\} \subseteq F$ for some $p$ and $q$}{
       $F \gets F \setminus \{ [v]_1^p, [\neg v]_1^q \} \cup \{ [v]_q^p
-      \}$\;
+      \}$\; \label{line:foreach2end}
     }
@@
   \end{enumerate}
-\end{theorem} % TODO: add parentheses around products
-% TODO: maybe give a name to (2) since it's wrong to call it an equation
-% TODO: check if each condition is actually used. Maybe turn this into a
-% paragraph that gives an overview of the proof.
+\end{theorem}
 \begin{proof}
@@
    \]
-   which is exactly what we needed to show.
+   which is exactly what we needed to show. This ends the proof that the
+   first loop of \cref{alg:transformation} preserves the answer under both
+   \cref{condition:d02} and \cref{condition:bklm16}. Finally, the loop on
+   \crefrange{line:foreach2start}{line:foreach2end} of \cref{alg:transformation}
+   replaces $[v]_1^p[\neg v]_1^q$ with $[v]_q^p$ (for some $v \in X_I$ and $p, q
+   \in \mathbb{R}$), but, of course,
+   \[
+     [v]_1^p[\neg v]_1^q = [v]_1^p[v]_q^1 = [v]_q^p
+   \]
+   by \cref{prop:basic}.
 \end{proof}
-% TODO: now consider the second for loop
-% TODO: condition 1 is necessary in both cases because we're ignore the weights
-% of indicator variables
-% NOTE: benefits of having the proof in the paper:
-% 1) it puts all the encodings on a common ground
-% 2) it illustrates the convenience of our notation for reasoning about (certain
-% types of) pseudo-Boolean functions (stress this!!!)
-% 3) it's too big and too important to be left for the appendix
-% NOTE: we don't make a distinction between a real number and a (PB) function
-% that always returns that number.
-% NOTE: projection is assumed to have lowest precedence (i.e., \exists_x fg =
-% \exists_x (fg) and not (\exists_x f)g).
-% TODO: need another basic property: (fg)|_{x=i} = f|_{x=i} * g|_{x=i} for i=0, 1.
-% TODO: \times -> \cdot
 
@@
   with $w(\neg p) = 1$.
+\item Benefits of having this proof in the paper:
+  \begin{itemize}
+  \item It puts all encodings on a common ground.
+  \item It illustrates the convenience of our notation for reasoning about
+    (certain types of) pseudo-Boolean functions.
+  \item It's too big and too important to be left for the appendix.
   \end{itemize}
-
-\section{Parameterised Complexity of \textsc{DPMC}}
-
-\paragraph{Notes.}
+\item Processors:
   \begin{itemize}
-\item Summary of results
-  \begin{itemize}
-  \item We establish \textsc{DPMC} inference as fixed-parameter tractable.
-  \item We experimentally show that \textsc{DPMC} is best on low-to-moderate
-    treewidth instances, and cd06+c2d overtakes on higher treewidth instances.
+  \item Intel(R) Xeon(R) Gold 6138 CPU @ 2.00GHz
+  \item Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz
+  \item Intel(R) Xeon(R) CPU E7-4820 v2 @ 2.00GHz
   \end{itemize}
-\item By \textsc{DPMC}, we always mean DMC+lg.
-\item The constant is inspired by the \texttt{bklm16} encoding.
+\item Table captions should be placed above the tables.
+\item Figures should preferably be in EPS format.
+\item the environments 'theorem', 'definition', 'lemma', 'proposition',
+  'corollary', 'remark', and 'example' are defined in the LLNCS documentclass as
+  well.
 \end{itemize}
@@
 \begin{itemize}
+\item Come up with better names for old/new WMC instances.
 \item Do I need to formally consider extending a pseudo-Boolean function to a
   bigger domain?
-\item Introduce all the notation surrounding graphs ($\mathcal{V}$,
-  $\mathcal{E}$ $\mathcal{L}$, $\mathcal{C}$, etc.) (and be consistent with its
-  usage) and formulas (variable, literal, clause, CNF, etc.)
-\item Use \cref{thm:connection} to show the connection between primal treewidth
-  and the width of the PJT (linking the complexity of BN inference with the DPMC
-  complexity).
-\item Come up with better names for old/new WMC instances.
-\item Define:
-  \begin{itemize}
-  \item scalar operations on ADDs,
-  \item an ADD as a DAG,
-  \item What does it mean for an ADD to `have' variables? Maybe refer to
-    pseudo-Boolean function sensitivity.
-  \item primal graph of a CNF formula (a.k.a.
-    Gaifman/(variable) interaction/connectivity/clique/representing graph),
-  \item Bayesian network (I already have a definition of these last two),
-  \item moralisation of a Bayesian network (or of any DAG),
-  \item projection of a set of variables.
-  \end{itemize}
+\item Define scalar operations on ADDs.
+\item Define projection of a set of variables.
+\item add parentheses around products
+\item maybe give a name to (2) since it's wrong to call it an equation
+\item check if each condition is actually used. Maybe turn this into a paragraph
+  that gives an overview of the proof.
+\item condition 1 is necessary in both cases because we're ignore the weights of
+  indicator variables
+\item maybe do more summations over domains in proofs
 \end{itemize}
 
-\begin{lemma} \label{lemma:add_size}
-  An ADD with $n$ variables has $\mathcal{O}(2^n)$ nodes.
-\end{lemma}
-\begin{proof}
-  An ADD with $n$ variables can be, at most, a complete binary tree of height
-  $n+1$ (as measured by the number of vertices). It would then have $2^0 + 2^1 +
-  \dots + 2^n = 2^{n+1} = \mathcal{O}(2^n)$ nodes.
-\end{proof}
-
-\begin{lemma} \label{lemma:clause_time}
-  Let $\phi$ be a conjunction of $n$ literals. Then the ADD representation of
-  $[\phi]^p_q$ can be constructed in $\mathcal{O}(2^n)$ time for any $p, q \in
-  \mathbb{R}$ such that $p \ne q$.
-\end{lemma}
-\begin{proof}
-  The ADD representation of $\phi$ itself can be constructed with a sequence of
-  $n-1$ calls to \texttt{apply} with one of the two operands in each call always
-  a literal. The number of variables in the other operand then follows the
-  sequence $1, 2, 3, \dots, n-1$. By \cref{lemma:add_size}, the numbers of nodes
-  in the ADD representations of these operands is then $\mathcal{O}(2^1),
-  \mathcal{O}(2^2), \dots, \mathcal{O}(2^{n-1})$. Since one of the operands is
-  of constant size, the overall time complexity of all calls to \texttt{apply}
-  is then
-  \[
-    \mathcal{O}(2^1) + \mathcal{O}(2^2) + \dots + \mathcal{O}(2^{n-1}) =
-    \mathcal{O}(2^n).
-  \]
-
-  Let $\alpha$ be the ADD representation of $\phi$. Then the ADD representation
-  of $[\phi]_q^p$ is $(p-q)\alpha + q$. As scalar operations can obviously be
-  implemented in linear time, the overall complexity remains $\mathcal{O}(2^n)$.
-\end{proof}
-
-\begin{theorem}[\cite{DBLP:conf/ecai/KwisthoutBG10}, rephrased]
-  BN Inference (for all algorithms that accept arbitrary instances) has a lower
-  bound that's linear in the size of the BN and exponential in the treewidth of
-  its moralisation (provide the exact formula).
-\end{theorem}
-
-\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}, with some changes]
-  Let $X$ be a set of Boolean variables, and $F$ be a set of pseudo-Boolean
-  functions $2^X \to \mathbb{R}$. A \emph{project-join tree} (PJT) of $F$ is a
-  tuple $(T, r, \gamma, \pi)$ where:
-  \begin{itemize}
-  \item $T$ is a tree with root $r \in \mathcal{V}(T)$,
-  \item $\gamma\colon \mathcal{L}(T) \to F$ is a bijection between the leaves of
-    $T$ and the pseudo-Boolean functions in $F$, and
-  \item $\pi\colon \mathcal{V}(T) \setminus \mathcal{L}(T) \to 2^X$ is a
-    labelling function on internal nodes.
-  \end{itemize}
-  Moreover, $(T, r, \gamma, \pi)$ must satisfy the following two properties:
-  \begin{enumerate}
-  \item $\{\pi(n) : n \in \mathcal{V}(T) \setminus \mathcal{L}(T)\}$ is a
-    partition of $X$, and
-  \item for each internal node $n \in \mathcal{V}(T) \setminus \mathcal{L}(T)$,
-    variable $x \in \pi(n)$, and `clause' $c \in F$ such that $x$
-    appears in $c$, the leaf node $\gamma^{-1}(c)$ must be a descendant of $n$
-    in $T$.
-  \end{enumerate}
-\end{definition}
-
-\begin{definition}[\cite{DBLP:conf/cp/DudekPV20}] \label{def:size}
-  \[
-    \mathtt{Vars}(n) \coloneqq
-    \begin{cases}
-      \mathtt{Vars}(\gamma(n)) & \text{if } n \in \mathcal{L}(T) \\
-      \left( \bigcup_{o \in \mathcal{C}(n)} \mathtt{Vars}(o) \right) \setminus
-      \pi(n) & \text{if } n \not\in \mathcal{L}(T).
-    \end{cases}
-  \]
-  \[
-    \mathtt{size}(n) \coloneqq
-    \begin{cases}
-      |\mathtt{Vars}(n)| & \text{if } n \in \mathcal{L}(T) \\
-      |\mathtt{Vars}(n) \cup \pi(n)| & \text{if } n \not\in \mathcal{L}(T).
-    \end{cases}
-  \]
-  (Note that $\mathtt{size}(n)$ is the number of variables that can appear
-  during the computation of $\delta(n)$ (excluding recursive calls).)
-  The \emph{width} of a PJT $(T, r, \gamma, \pi)$ is
-  $\mathtt{width}(T) \coloneqq \max_{n \in \mathcal{V}(T)} \mathtt{size}(n)$.
-\end{definition} % TODO: don't actually need this much notation.
-
-\begin{theorem}[\cite{DBLP:conf/cp/DudekPV20}, rephrased, `ADD width is equal
-  to the treewidth of the primal graph']
-  Given a CNF formula $\phi$ with a tree decomposition of its primal graph of
-  width $w$, Algorithm~2 (from \cite{DBLP:conf/cp/DudekPV20}) returns a
-  PJT of $\phi$ of width at most $w+1$.
-\end{theorem}
-
-\begin{definition}[\cite{DBLP:journals/jct/RobertsonS84}, rephrased]
-  A \emph{tree decomposition} of a graph $G$ is a pair $(T, \chi)$, where $T$ is
-  a tree and $\chi\colon \mathcal{V}(T) \to 2^{\mathcal{V}(G)}$ is a labelling
-  function, with the following properties:
-  \begin{itemize}
-  \item $\bigcup_{t \in \mathcal{V}(T)} \chi(t) = \mathcal{V}(G)$;
-  \item for every edge $e \in \mathcal{E}(G)$, there exists $t \in
-    \mathcal{V}(T)$ such that $e$ has both endpoints in $\chi(t)$;
-  \item for all $t, t', t'' \in \mathcal{V}(T)$, if $t'$ is on the path between
-    $t$ and $t''$, then $\chi(t) \cap \chi(t'') \subseteq \chi(t')$.
-  \end{itemize}
-  The \emph{width} of tree decomposition $(T, \chi)$ is $\max_{t \in
-    \mathcal{V}(T)} |\chi(t)| - 1)$. The \emph{treewidth} of graph $G$ is the
-  smallest $w$ such that $G$ has a tree decomposition of width $w$.
-\end{definition}
-
-\begin{definition} \label{def:operations}
-  Let $f, g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions. Operations
-  such as addition and multiplication are defined pointwise as
-  \[
-    (f+g)(Y) \coloneqq f(Y)+g(Y), \quad \text{and} \quad (fg)(Y) \coloneqq
-    f(Y)g(Y)
-  \]
-  for all $Y \subseteq X$. This means that binary operations on pseudo-Boolean
-  functions inherit properties such as associativity and commutativity.
-\end{definition}
-
-\begin{definition} \label{def:restriction}
-  Let $f\colon 2^X \to \mathbb{R}$ be a pseudo-Boolean function, and $x \in X$.
-  Then $f|_{x=0}, f|_{x=1}\colon 2^X \to \mathbb{R}$ are \emph{restrictions} of
-  $f$ defined as
-  \[
-    f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\}), \quad \text{and} \quad
-    f|_{x=1}(Y) \coloneqq f(Y \cup \{x\})
-  \]
-  for all $Y \subseteq X$.
-\end{definition}
-
-\begin{definition} \label{def:projection}
-  Let $X$ be a set. For any $x \in X$, \emph{projection} $\exists_x$ is an
-  endomorphism $\exists_x\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined
-  as
-  \[
-    \exists_xf \coloneqq f|_{x=1} + f|_{x=0}
-  \]
-  for any $f\colon 2^X \to \mathbb{R}$.
-\end{definition}
-
-\begin{lemma} \label{lemma:basic_ops}
-  Let $f,g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions represented by
-  ADDs with $n$ and $m$ nodes, respectively, and $x \in X$. Then $f+g$ and $fg$
-  can be computed in $\mathcal{O}(mn)$ time, and $\exists_xf$ can be computed in
-  $\mathcal{O}(n^2)$ time.
-\end{lemma}
-\begin{proof}
-  Addition and multiplication are implemented by \texttt{apply} algorithm which
-  takes $\mathcal{O}(mn)$ time \cite{DBLP:journals/tc/Bryant86}. Projection
-  consists of two restrictions and an addition by \cref{def:projection}. The
-  computational complexity of restriction is dominated by the reduction
-  operation that transforms a decision diagram into a minimal canonical form
-  \cite{DBLP:journals/tc/Bryant86}. While the original reduction algorithm had a
-  $\mathcal{O}(n \log n)$ complexity, caching can reduce it to $\mathcal{O}(n)$
-  \cite{somenzi1998cudd}. Either way, the complexity of projection is still
-  $\mathcal{O}(n^2)$.
-\end{proof}
-
-% NOTE: this is a rehash of equation (2) from the DPMC paper
-\begin{definition} \label{def:abstraction}
-  Let $(T, r, \gamma, \pi)$ be a PJT, and $X$ be the set of variables. The
-  functionality of \textsc{DPMC} execution can be represented by $\delta(r)$,
-  where $\delta\colon \mathcal{V}(T) \to \mathbb{R}^{2^X}$ is a recursive
-  function defined as
-  \begin{equation} \label{eq:execution}
-    \delta(t) \coloneqq
-    \begin{cases}
-      \gamma(t) & \text{if } t \in \mathcal{L}(T) \\
-      \exists_{\pi(t)} \prod_{u \in \mathcal{C}(t)} \delta(u) & \text{otherwise.}
-    \end{cases}
-  \end{equation}
-  The range of $\delta(r)$ then contains a single real number, i.e., the answer.
-\end{definition}
-
-% TODO: will need to rephrase this to fit my context
-\begin{theorem}[Theorem~4 in \cite{DBLP:conf/cp/DudekPV20}, almost
-  verbatim] \label{thm:connection}
-  Let $\phi$ be a propositional formula in CNF over a set $X$ of variables and
-  $(S, \chi)$ be a tree decomposition of the primal graph of $\phi$ of width
-  $w$. Then Algorithm~2 returns a PJT of $\phi$ of width at most $w+1$.
-\end{theorem}
-
-\begin{theorem}
-  Let $(F, X, \omega)$ be a WMC instance, and $(T, r, \gamma, \pi)$ be its PJT
-  of width $k$. Then \textsc{DPMC} execution is fixed-parameter tractable with
-  respect to $k$. Specifically, \textsc{DPMC} execution time complexity is
-  $\mathcal{O}(4^knm)$, where $n = |\mathcal{L}(T)| = |F|$, and $m = |X|$ is the
-  number of variables.
-\end{theorem}
-\begin{proof}
-  \begin{itemize}
-  \item We consider the complexity of constructing ADD representations of the
-    pseudo-Boolean functions in $F$ and the complexity of multiplication and
-    projection operations throughout the recursive calls of $\delta$ in
-    \cref{def:abstraction}.
-  \item Let $t \in \mathcal{L}(T)$ be a leaf. Note that
-    $|\mathtt{Vars}(\gamma(t))| \le k$ by \cref{def:size}. Assuming that clauses
-    have no repeating variables, it takes $\mathcal{O}(2^k)$ time to construct
-    $\delta(t)$ by \cref{lemma:clause_time} and $\mathcal{O}(2^kn)$ time to
-    construct all leaves of the PJT.
-  \item Now let $t \in \mathcal{V}(T) \setminus \mathcal{L}(T)$ be an internal
-    vertex, in which case we perform $|\mathcal{C}(t)|-1$ multiplications and
-    $|\pi(t)|$ projections. Note that $|\mathcal{C}(t)| \le |\mathcal{L}(T)| =
-    n$, $|\pi(t)| \le k$, and the ADDs involved can have up to $k$ variables.
-    This means that each ADD has $\mathcal{O}(2^k)$ nodes (regardless of whether
-    it comes from $\mathcal{C}(t)$ or from multiplications). Each such
-    multiplication then takes $\mathcal{O}(4^k)$ time by \cref{lemma:basic_ops},
-    and so all multiplications will take $\mathcal{O}(4^kn)$ time for $t$ and
-    $\mathcal{O}(4^knm)$ time across all $t \in \mathcal{V}(T) \setminus
-    \mathcal{L}(T)$ since the number of vertices in the PJT is bounded by the
-    number of variables.
-  \item Each variable is projected exactly once and is always projected from
-    an ADD with at most $\mathcal{O}(2^k)$ nodes. Thus, the time complexity of
-    projecting all variables is $\mathcal{O}(4^km)$.
-  \item In total, we get $\mathcal{O}(2^kn)$ time for constructing initial ADDs,
-    $\mathcal{O}(4^knm)$ for multiplications, and $\mathcal{O}(4^km)$ for
-    projections, resulting in $\mathcal{O}(4^knm)$ time in total.
-  \end{itemize}
-\end{proof}
-
-\bibliographystyle{acm}
+\bibliographystyle{splncs04}
 \bibliography{paper}

### 2021-02-21 doc/paper3/paper.tex
Some writing

@@
 
+\section{Pseudo-Boolean Functions}
+
 \paragraph{Notation.} For any propositional formula $\phi$ over a set of
@@
 
-\begin{definition} \label{def:operations}
-  Let $f, g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions. Operations
-  such as addition and multiplication are defined pointwise as
+\begin{definition}[Operations] \label{def:operations}
+  Let $f, g\colon 2^X \to \mathbb{R}$ be pseudo-Boolean functions, $x, y \in X$,
+  $Y = \{y_i\}_{i=1}^n \subseteq X$, and $r \in \mathbb{R}$. Operations such as
+  addition and multiplication are defined pointwise as
   \[
-    (f+g)(Y) \coloneqq f(Y)+g(Y), \quad \text{and} \quad (fg)(Y) \coloneqq
-    f(Y)g(Y)
+    (f+g)(Y) \coloneqq f(Y)+g(Y), \quad \text{and} \quad (f \cdot g)(Y)
+    \coloneqq f(Y) \cdot g(Y).
   \]
-  for all $Y \subseteq X$. This means that binary operations on pseudo-Boolean
-  functions inherit properties such as associativity and commutativity.
-\end{definition}
+  Note that this means that binary operations on pseudo-Boolean functions
+  inherit properties such as associativity and commutativity. By not
+  distinguishing between a real number and a pseudo-Boolean function that always
+  returns that number, we can use the same definitions to define \emph{scalar}
+  operations as
+  \[
+    (r+f)(Y) = r+f(Y), \quad \text{and} \quad (r \cdot f)(Y) = r \cdot f(Y).
+  \]
 
-\begin{definition} \label{def:restriction}
-  Let $f\colon 2^X \to \mathbb{R}$ be a pseudo-Boolean function, and $x \in X$.
-  Then $f|_{x=0}, f|_{x=1}\colon 2^X \to \mathbb{R}$ are \emph{restrictions} of
-  $f$ defined as
+  \emph{Restrictions} $f|_{x=0}, f|_{x=1}\colon 2^X \to \mathbb{R}$ of $f$ are
+  defined as
   \[
@@
   for all $Y \subseteq X$.
-\end{definition}
 
-\begin{definition} \label{def:projection}
-  Let $X$ be a set. For any $x \in X$, \emph{projection} $\exists_x$ is an
-  endomorphism $\exists_x\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined
-  as
+  \emph{Projection} $\exists_x$ is an endomorphism $\exists_x\colon
+  \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined as
   \[
-    \exists_xf \coloneqq f|_{x=1} + f|_{x=0}
+    \exists_xf \coloneqq f|_{x=1} + f|_{x=0}.
   \]
-  for any $f\colon 2^X \to \mathbb{R}$.
+  Since projection is commutative (i.e., $\exists_x\exists_yf =
+  \exists_y\exists_xf$) \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20},
+  we can define $\exists_Y\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ as
+  $\exists_Y \coloneqq \exists_{y_1}\exists_{y_2}\dots\exists_{y_n}$. Throughout
+  the paper, projection is assumed to have the lowest precedence (e.g.,
+  $\exists_x fg = \exists_x (fg)$).
 \end{definition}
@@
 % NOTE: The proof immediately comes from the definition (of operations).
-\begin{proposition}[Basic properties] \label{prop:basic}
+\begin{proposition}[Basic Properties] \label{prop:basic}
   For any propositional formulas $\phi$ and $\psi$, and $a, b, c, d \in
@@
 
-\begin{definition}[old WMC instance]
-  An \emph{old WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
+\paragraph{References.}
+\begin{itemize}
+\item Related work without publicly available implementations:
+  \begin{itemize}
+  \item direct compilation to SDDs \cite{DBLP:conf/ecsqaru/ChoiKD13}
+  \item direct compilation to PSDDs, also eliminating parameter variables (a thesis)
+  \item maybe two more papers
+  \end{itemize}
+\end{itemize}
+
+\paragraph{TODO: Mention}
+\begin{itemize}
+\item Weights on literals other than the positive literals that correspond to
+  variables in $X_P$ are redundant as they either are equal to one or duplicate
+  an already-defined weight.
+\item Mention that formulas, clauses, and models are all treated as sets.
+\end{itemize}
+
+\section{Weighted Model Counting}
+
+\begin{definition}[WMC Instance \cite{DBLP:journals/ai/ChaviraD08} (TODO: not
+  exactly though)]
+  A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
   the set of indicator variables, $X_P$ is the set of parameter variables (with
@@
   instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
-\end{definition} % TODO: add a citation for this.
+\end{definition}
 
@@
   network is encoded using two indicator variables while one would suffice.
-\end{remark} % TODO: perhaps add this claim as a corollary
+\end{remark}
 
-\begin{definition}[new WMC instance] \label{def:new_wmc}
-  A \emph{new WMC instance} is a tuple $(F, X, \omega)$, where $X$ is the set of
-  variables, $F$ is a set of pseudo-Boolean functions $2^X \to \mathbb{R}$, and
-  $\omega \in \mathbb{R}$ is the scaling factor. The \emph{answer} of the
-  instance is $\omega \cdot \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
+\begin{definition}[PBP Instance] \label{def:new_wmc}
+  A \emph{pseudo-Boolean projection} (PBP) instance is a tuple $(F, X, \omega)$,
+  where $X$ is the set of variables, $F$ is a set of pseudo-Boolean functions
+  $2^X \to \mathbb{R}$, and $\omega \in \mathbb{R}$ is the scaling factor. The
+  \emph{answer} of the instance is $\omega \cdot \left(\exists_X\prod_{f \in
+      F}f\right)(\emptyset)$.
 \end{definition}
 
-\paragraph{References.}
-\begin{itemize}
-\item Related work without publicly available implementations:
-  \begin{itemize}
-  \item direct compilation to SDDs \cite{DBLP:conf/ecsqaru/ChoiKD13}
-  \item direct compilation to PSDDs, also eliminating parameter variables (a thesis)
-  \item maybe two more papers
-  \end{itemize}
-\end{itemize}
-
-\paragraph{Notes.}
-\begin{itemize}
-\item Apparently, the \textsc{DPMC} paper already shows that taking the first
-  offered decomposition tree is best.
-\item It is already well-known that WMC is FPT.
-\item Weights on literals other than the positive literals that correspond to
-  variables in $X_P$ are redundant as they either are equal to one or duplicate
-  an already-defined weight.
-\item Mention that formulas, clauses, and models are all treated as sets.
-\item The constant is inspired by the \texttt{bklm16} encoding.
-\item We don't make a distinction between a real number and a (pseudo-Boolean)
-  function that always returns that number.
-\item Throughout the paper, projection is assumed to have the lowest precedence
-  (e.g., $\exists_x fg = \exists_x (fg)$ and not $(\exists_xf)g$).
-\end{itemize}
+NOTE: The constant is inspired by the \texttt{bklm16}
+\cite{DBLP:conf/ecai/BartKLM16} encoding.
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[t]
   \caption{WMC instance transformation}
@@
   \SetKwProg{Fn}{Function}{:}{}
-  \KwData{an (old-format) WMC instance $(\phi, X_I, X_P, w)$}
-  \KwResult{a (new-format) WMC instance $(F, X, \omega)$}
+  \KwData{WMC instance $(\phi, X_I, X_P, w)$}
+  \KwResult{PBP instance $(F, X, \omega)$}
   $F \gets \emptyset$\;
@@
 
-\subsection{Correctness}
+\subsection{Proof of Correctness}
 
@@
 \begin{lemma} \label{lemma:sum}
-  For any pseudo-Boolean function $f\colon 2^X \to \mathbb{R}$, $(\exists_X
-  f)(\emptyset) = \sum_{Y \subseteq X} f(Y)$.
+  For any pseudo-Boolean function $f\colon 2^X \to \mathbb{R}$,
+  \[
+    (\exists_X f)(\emptyset) = \sum_{Y \subseteq X} f(Y).
+  \]
 \end{lemma}
@@
   \[
-    \exists_xf = f|_{x=1} + f|_{x=0},
+    (\exists_xf)(\emptyset) = (f|_{x=1} + f|_{x=0})(\emptyset) =
+    f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset) = f(\{x\}) + f(\emptyset) =
+    \sum_{Y \subseteq \{x\}} f(Y).
   \]
-  by \cref{def:projection} and so
-  \[
-    (\exists_xf)(\emptyset) = f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset)
-  \]
-  by \cref{def:operations}. Then
-  \[
-    f|_{x=1}(\emptyset) = f(\{x\}), \quad \text{and} \quad f|_{x=0}(\emptyset) =
-    f(\emptyset)
-  \]
-  by \cref{def:restriction}. It follows that
-  \[
-    (\exists_xf)(\emptyset) = f(\{x\}) + f(\emptyset) = \sum_{Y \subseteq \{x\}}
-    f(Y)
-  \]
-  as required. This easily extends to $|X| > 1$ by the definition of projection
-  on sets of variables. % TODO: once I've defined it, add a reference here.
+  This easily extends to $|X| > 1$ by the definition of projection on sets of
+  variables.
 \end{proof}
@@
 \begin{proposition} \label{prop:equivalence}
-  Let $(\phi, X_I, X_P, w)$ be an old WMC instance. Then
+  Let $(\phi, X_I, X_P, w)$ be a WMC instance. Then
   \begin{equation}
@@
   \end{equation}
-  is a new WMC instance with the same answer.
+  is a PBP instance with the same answer.
 \end{proposition}
@@
   \begin{align*}
-    \left(\exists_{X_I \cup X_P} \prod_{c \in \phi} [c]_0^1 \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset) &= \sum_{Y \subseteq X_I \cup X_P} \left(\prod_{c \in \phi} [c]_0^1 \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)(Y) \\
+    \left(\exists_{X_I \cup X_P} \left(\prod_{c \in \phi} [c]_0^1\right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset) &= \sum_{Y \subseteq X_I \cup X_P} \left(\left(\prod_{c \in \phi} [c]_0^1 \right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)(Y) \\
 &= \sum_{Y \subseteq X_I \cup X_P} \underbrace{\left(\prod_{c \in \phi} [c]_0^1\right)}_f(Y) \underbrace{\left(\prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)}_g(Y)
   \end{align*}
-  by \cref{def:new_wmc,lemma:sum,def:operations}. Note that
+  by \cref{lemma:sum}. Note that
   \[
@@
 \begin{theorem}[Correctness]
-  \Cref{alg:transformation}, when given an old WMC instance $(\phi, X_I, X_P,
-  w)$, returns a new WMC instance with the same answer, provided the following
+  \Cref{alg:transformation}, when given a WMC instance $(\phi, X_I, X_P,
+  w)$, returns PBP instance with the same answer, provided the following
   conditions are satisfied:
@@
           x)}^{w(x)} \;\middle|\; x \in X_I \cup X_P\right\}, X_I \cup X_P,
-      1\right) \label{eq:new_wmc}
+      1\right) \label{eq:new_wmc2}
   \end{equation}
-  is a new WMC instance with the same answer as the given old WMC instance. By
+  is a PBP instance with the same answer as the given WMC instance. By
   \cref{def:new_wmc}, its answer is
   \begin{equation} \label{eq:answer}
-    \left(\exists_{X_I \cup X_P} \prod_{c \in \phi} [c]_0^1 \prod_{x \in X_I
-        \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset)
+    \left(\exists_{X_I \cup X_P} \left( \prod_{c \in \phi} [c]_0^1 \right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset)
   \end{equation}
@@
   \}$ for all $p \in X_P$. We can then use \cref{thm:early} to reorder
-  \cref{eq:answer} into
+  \eqref{eq:answer} into
   \[
@@
   the loop on \crefrange{line:foreach1start}{line:foreach1end} differs from
-  \cref{eq:new_wmc}. Note that \cref{alg:transformation} leaves each $c \in
+  \eqref{eq:new_wmc2}. Note that \cref{alg:transformation} leaves each $c \in
   \phi_*$ unchanged, i.e., adds $[c]_0^1$ to $F$. We can then fix an arbitrary
@@
     \right]_0^1\right|_{p=1} + \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n
-      l_i \right]_0^1\right|_{p=0}
+      l_i \right]_0^1\right|_{p=0}.
   \end{equation}
-  by \cref{def:projection}. Since for any input, $\bigwedge_{i=1}^n l_i$ is
-  either true or false, exactly one of the two summands in \cref{eq:bigsums}
-  will be equal to one, and the other will be equal to zero, and so
+  Since for any input, $\bigwedge_{i=1}^n l_i$ is either true or false, exactly
+  one of the two summands in \cref{eq:bigsums} will be equal to one, and the
+  other will be equal to zero, and so
   \[
@@
     \left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} = \exists_p [p]_1^{w(p)}
-    \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1.
+    \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1,
   \]
-  By \cref{def:projection},
+  and indeed
   \begin{align*}
     \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 &= \left.\left( [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 \right)\right|_{p=1} + \left.\left([p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 \right)\right|_{p=0} \\
-                                                                                      &= w(p) \cdot \left[ \bigwedge_{i=1}^n l_i \right]_0^1 + \left[ \bigwedge_{i=1}^n l_i \right]_1^0 = \left[ \bigwedge_{i=1}^n l_i \right]_1^{w(p)}
+                                                                                      &= w(p) \cdot \left[ \bigwedge_{i=1}^n l_i \right]_0^1 + \left[ \bigwedge_{i=1}^n l_i \right]_1^0 = \left[ \bigwedge_{i=1}^n l_i \right]_1^{w(p)}.
   \end{align*}
-  as required. This finishes the proof of the correctness of the first `foreach'
-  loop under \cref{condition:d02}.
+  This finishes the proof of the correctness of the first `foreach' loop under
+  \cref{condition:d02}.
 
@@
   \]
-  by \cref{prop:basic,def:projection}, and because $p \in c$ for every clause $c
-  \in \phi_p$.
+  since $p \in c$ for every clause $c \in \phi_p$.
 
@@
   \[
-    \omega \prod_{f \in F_p} f = w(p).
+    \exists_p [p]_{w(\neg p)}^{w(p)} [p]_0^1 = \exists_p [p]^{w(p)}_0 = w(p) =
+    \omega \prod_{f \in F_p} f.
   \]
-  Whereas on the other side of \cref{eq:to_show},
-  \[
-    \exists_p [p]_{w(\neg p)}^{w(p)} [p]_0^1 = \exists_p [p]^{w(p)}_0 = w(p)
-  \]
-  by \cref{prop:basic,def:projection}.
-
   The only remaining case is when $w(p) \ne 1$ and $\{ p \} \not \in \phi_p$.
@@
                                                                &= \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_{w(p)}^1 = \left[ \neg \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \neg(c \setminus \{ p \}) \right]_1^{w(p)} \\
-                                                               &= \left[ \bigvee_{c \in \phi_p} \neg \bigvee_{l \in c \setminus \{ p \}} l \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}
+                                                               &= \left[ \bigvee_{c \in \phi_p} \neg \bigvee_{l \in c \setminus \{ p \}} l \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}.
   \end{align*}
-   by \cref{prop:basic,def:projection}. By \cref{cond:disjoint}, $\bigwedge_{l
-     \in c \setminus \{ p \}} \neg l$ can be true for at most one $c \in
-   \phi_p$, and so
+   By \cref{cond:disjoint}, $\bigwedge_{l \in c \setminus \{ p \}} \neg l$ can
+   be true for at most one $c \in \phi_p$, and so
    \[
@@
    \[
-     [v]_1^p[\neg v]_1^q = [v]_1^p[v]_q^1 = [v]_q^p
+     [v]_1^p[\neg v]_1^q = [v]_1^p[v]_q^1 = [v]_q^p,
    \]
-   by \cref{prop:basic}.
+   i.e., the answer is unchanged.
 \end{proof}
+
+\section{Experimental Results}
+
+\paragraph{Notes.}
+\begin{itemize}
+\item Apparently, the \textsc{DPMC} paper \cite{DBLP:conf/cp/DudekPV20} already
+  shows that taking the first offered decomposition tree is best.
+\end{itemize}
+
+\section{Conclusions}
 
@@
 \begin{itemize}
-\item Come up with better names for old/new WMC instances.
 \item Do I need to formally consider extending a pseudo-Boolean function to a
   bigger domain?
-\item Define scalar operations on ADDs.
-\item Define projection of a set of variables.
-\item add parentheses around products
-\item maybe give a name to (2) since it's wrong to call it an equation
 \item check if each condition is actually used. Maybe turn this into a paragraph
   that gives an overview of the proof.
-\item condition 1 is necessary in both cases because we're ignore the weights of
-  indicator variables
+\item condition 1 is necessary in both cases because we're ignoring the weights
+  of indicator variables (explicitly acknowledge this)
 \item maybe do more summations over domains in proofs
+\item add the \texttt{cd05}/\texttt{cd06} correctness theorem
 \end{itemize}

### 2021-02-21 tools/analyse_changes.R

@@ -22,9 +22,7 @@ changes$dataset[grepl("tcc4f", changes$instance, fixed = TRUE)] <- "Other binary
 scatter <- function(data, x_var, y_var) {
   limits <- c(min(data[[x_var]], data[[y_var]], na.rm = TRUE), max(data[[x_var]], data[[y_var]], na.rm = TRUE))
   ggplot(data, aes(.data[[x_var]], .data[[y_var]], col = dataset)) +
-#    geom_point() +
     geom_count() +
-#    geom_jitter(width = 0.1, height = 0.1) +
     geom_abline(slope = 1, intercept = 0, colour = "#989898") +
     scale_x_continuous(trans = log10_trans(), limits = limits) +
     scale_y_continuous(trans = log10_trans(), limits = limits) +

### 2021-02-22 doc/paper3/paper.tex
Improved cumulative plot

@@
 \usepackage[capitalise]{cleveref}
+\usepackage{tikz}
 
@@
 
-% NOTE: ...that we will need.
-% NOTE: The proof immediately comes from the definition (of operations).
+NOTE: We list some properties of the operations on pseudo-Boolean functions
+discussed in this section that can be conveniently represented using our syntax.
+The proofs of all these properties follow directly from the definitions.
+
 \begin{proposition}[Basic Properties] \label{prop:basic}
@@
 
-\paragraph{TODO: Mention}
+\paragraph{Notes.}
 \begin{itemize}
@@
 
-\begin{definition}[WMC Instance \cite{DBLP:journals/ai/ChaviraD08} (TODO: not
-  exactly though)]
+NOTE: Our definition of WMC is largely based on the standard definition
+\cite{DBLP:journals/ai/ChaviraD08}, but explicitly partitions variables into
+indicator and parameter variables.
+
+\begin{definition}[WMC Instance]
   A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
@@
     (\exists_xf)(\emptyset) = (f|_{x=1} + f|_{x=0})(\emptyset) =
-    f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset) = f(\{x\}) + f(\emptyset) =
-    \sum_{Y \subseteq \{x\}} f(Y).
+    f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset) = \sum_{Y \subseteq \{x\}} f(Y).
   \]
@@
   \]
-  We can rearrange the right-hand-side as
+  We can rearrange the right-hand side as
   \begin{align*}
@@
   shows that taking the first offered decomposition tree is best.
+\item Processors:
+  \begin{itemize}
+  \item Intel(R) Xeon(R) Gold 6138 CPU @ 2.00GHz
+  \item Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz
+  \item Intel(R) Xeon(R) CPU E7-4820 v2 @ 2.00GHz
   \end{itemize}
+\end{itemize}
+
+\begin{figure}[t]
+  \centering
+  \input{cumulative.tex}%
+  \caption{TODO}
+  \label{fig:cumulative}
+\end{figure}
 
@@
   \end{itemize}
-\item Processors:
-  \begin{itemize}
-  \item Intel(R) Xeon(R) Gold 6138 CPU @ 2.00GHz
-  \item Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz
-  \item Intel(R) Xeon(R) CPU E7-4820 v2 @ 2.00GHz
-  \end{itemize}
-\item Table captions should be placed above the tables.
-\item Figures should preferably be in EPS format.
-\item the environments 'theorem', 'definition', 'lemma', 'proposition',
-  'corollary', 'remark', and 'example' are defined in the LLNCS documentclass as
-  well.
 \end{itemize}
@@
   of indicator variables (explicitly acknowledge this)
-\item maybe do more summations over domains in proofs
 \item add the \texttt{cd05}/\texttt{cd06} correctness theorem

### 2021-02-22 tools/analyse.R

@@ -6,6 +6,7 @@ library(purrr)
 library(tikzDevice)
 library(ggpubr)
 library(tidyr)
+library(RColorBrewer)
 
 # TODO: plot treewidth vs add width
 data <- read.csv("../results/results.csv", header = TRUE, sep = ",")
@@ -48,6 +49,10 @@ data_merged <- subset(data_merged, select = -c(novelty))
 data_sum <- data_merged
 data_sum$time <- data_sum$encoding_time + data_sum$inference_time
 data_sum <- subset(data_sum, select = -c(inference_time, encoding_time))
+
+#data_sum2 <- data
+#data_sum2$time <- data_sum2$encoding_time + data_sum2$inference_time
+#data_sum2 <- subset(data_sum2, select = -c(inference_time, encoding_time))
 
 # df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
 #             fun.aggregate = NULL,
@@ -100,6 +105,32 @@ df.temp2 <- data.frame(instance = df$instance, dataset = NA, encoding = "VBS*",
                        answer = NA, time = instance_to_min_time0[df$instance])
 data_sum <- rbind(data_sum, df.temp, df.temp2)
 rownames(data_sum) <- c()
+
+data_sum$encoding[data_sum$encoding == "new_bklm16"] <- "\\textsf{DPMC} + \\texttt{bklm16}"
+data_sum$encoding[data_sum$encoding == "new_bklm16pp"] <- "\\textsf{DPMC} + \\texttt{bklm16++}"
+data_sum$encoding[data_sum$encoding == "new_cd05pp"] <- "\\textsf{DPMC} + \\texttt{cd05++}"
+data_sum$encoding[data_sum$encoding == "new_cd06pp"] <- "\\textsf{DPMC} + \\texttt{cd06++}"
+data_sum$encoding[data_sum$encoding == "new_d02"] <- "\\textsf{DPMC} + \\texttt{d02}"
+data_sum$encoding[data_sum$encoding == "new_d02pp"] <- "\\textsf{DPMC} + \\texttt{d02++}"
+data_sum$encoding[data_sum$encoding == "new_sbk05"] <- "\\textsf{DPMC} + \\texttt{sbk05}"
+data_sum$encoding[data_sum$encoding == "old_bklm16"] <- "\\textsf{c2d} + \\texttt{bklm16}"
+data_sum$encoding[data_sum$encoding == "old_cd05"] <- "\\textsf{Ace} + \\texttt{cd05}"
[…]

### 2021-02-23 doc/paper3/box.tex
Other plots

% Created by tikzDevice version 0.12.3.1 on 2021-02-23 15:58:55
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 30.69) rectangle (275.96,139.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 30.69) rectangle (275.96,139.04);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 54.03) --
	(275.96, 54.03);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 91.24) --
	(275.96, 91.24);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,128.46) --
	(275.96,128.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 35.42) --
	(275.96, 35.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 72.64) --
	(275.96, 72.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,109.85) --
	(275.96,109.85);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.15, 30.69) --
	( 74.15,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (130.20, 30.69) --
	(130.20,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (186.26, 30.69) --
	(186.26,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (242.32, 30.69) --
	(242.32,139.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.63,115.66) -- ( 63.63,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.63, 41.94) -- ( 63.63, 35.91);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 54.17,115.66) --
	( 54.17, 41.94) --
	( 73.09, 41.94) --
	( 73.09,115.66) --
	( 54.17,115.66) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 54.17, 63.32) -- ( 73.09, 63.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.66, 65.49) -- ( 84.66,104.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.66, 38.03) -- ( 84.66, 35.61);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.20, 65.49) --
	( 75.20, 38.03) --
	( 94.12, 38.03) --
	( 94.12, 65.49) --
	( 75.20, 65.49) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.20, 42.42) -- ( 94.12, 42.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.69,119.81) -- (119.69,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.69, 43.24) -- (119.69, 36.02);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (110.23,119.81) --
	(110.23, 43.24) --
	(129.15, 43.24) --
	(129.15,119.81) --
	(110.23,119.81) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (110.23, 64.90) -- (129.15, 64.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.71,104.94) -- (140.71,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.71, 40.63) -- (140.71, 35.85);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (131.26,104.94) --
	(131.26, 40.63) --
	(150.17, 40.63) --
	(150.17,104.94) --
	(131.26,104.94) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (131.26, 50.31) -- (150.17, 50.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.75,119.86) -- (175.75,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.75, 43.24) -- (175.75, 36.02);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (166.29,119.86) --
	(166.29, 43.24) --
	(185.21, 43.24) --
	(185.21,119.86) --
	(166.29,119.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (166.29, 64.90) -- (185.21, 64.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77,104.94) -- (196.77,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77, 40.63) -- (196.77, 35.85);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (187.31,104.94) --
	(187.31, 40.63) --
	(206.23, 40.63) --
	(206.23,104.94) --
	(187.31,104.94) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.31, 50.31) -- (206.23, 50.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.81,107.47) -- (231.81,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.81, 40.63) -- (231.81, 35.83);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.35,107.47) --
	(222.35, 40.63) --
	(241.27, 40.63) --
	(241.27,107.47) --
	(222.35,107.47) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (222.35, 55.32) -- (241.27, 55.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.83, 69.18) -- (252.83,104.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.83, 38.03) -- (252.83, 35.61);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (243.37, 69.18) --
	(243.37, 38.03) --
	(262.29, 38.03) --
	(262.29, 69.18) --
	(243.37, 69.18) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (243.37, 42.87) -- (262.29, 42.87);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.69) rectangle (275.96,139.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 32.39) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 69.61) {2000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,106.82) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 35.42) --
	( 40.51, 35.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 72.64) --
	( 40.51, 72.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,109.85) --
	( 40.51,109.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.15, 27.94) --
	( 74.15, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (130.20, 27.94) --
	(130.20, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (186.26, 27.94) --
	(186.26, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (242.32, 27.94) --
	(242.32, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 74.15, 19.68) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (130.20, 19.68) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.26, 19.68) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (242.32, 19.68) {\texttt{d02}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 84.86) {Variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (286.96, 57.30) rectangle (341.40,112.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (292.46, 77.26) rectangle (306.91, 91.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 78.70) --
	(299.68, 80.87);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 88.10) --
	(299.68, 90.26);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (294.26, 80.87) rectangle (305.10, 88.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.26, 84.48) --
	(305.10, 84.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (292.46, 62.80) rectangle (306.91, 77.26);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 64.25) --
	(299.68, 66.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 73.64) --
	(299.68, 75.81);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (294.26, 66.42) rectangle (305.10, 73.64);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.26, 70.03) --
	(305.10, 70.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.41, 81.45) {before};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.41, 67.00) {after};
\end{scope}
\end{tikzpicture}

### 2021-02-23 tools/analyse.R

@@ -88,6 +88,7 @@ df$major.dataset[grepl("fs-", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("Plan_Recognition", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("students", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
+df$major.dataset <- as.factor(df$major.dataset)
 
 instance_to_min_time <- df$time_min
 names(instance_to_min_time) <- df$instance
@@ -213,7 +214,7 @@ scatter_plot <- function(df, x_column, y_column, x_name, y_name,
                                       y = .data[[y_column]],
                                       col = major.dataset,
                                       shape = major.dataset)) +
-    geom_jitter(alpha = 1, size = 1, width = 0.1, height = 0.1) +
+    geom_point(alpha = 0.5, size = 1) +
     geom_abline(slope = 1, intercept = 0, colour = "#989898") +
     scale_x_continuous(trans = log10_trans(), limits = c(min.time, max.time),
                        breaks = c(0.1, 10, 1000),
@@ -226,26 +227,26 @@ scatter_plot <- function(df, x_column, y_column, x_name, y_name,
     coord_fixed() +
     annotation_logticks(colour = "#b3b3b3") +
     theme_light() +
-    labs(shape = "Data set", colour = "Treewidth") +
+    labs(shape = "", colour = "") +
+    scale_color_brewer(palette = "Dark2")
 #    scale_color_distiller("Treewidth", trans = "log") + # TODO: add breaks
-    scale_shape("Data set")
 }
 
-scatter_plot(df, "time_old_cd06", "time_new_bklm16pp", "\\texttt{old_cd06} time (s)",
-                   "\\texttt{new_bklm16++} time (s)", 2 * TIMEOUT)
-scatter_plot(df, "time_new_bklm16", "time_new_bklm16pp", "\\texttt{bklm16} time (s)",
-                   "\\texttt{bklm16++} time (s)", 2 * TIMEOUT)
-scatter_plot(df, "add_width_new_d02pp", "add_width_new_d02", "\\texttt{d02++} width",
-                   "\\texttt{d02} width", max(data$add_width))
[…]

### 2021-02-23 tools/analyse_changes.R

@@ -22,51 +22,77 @@ changes$dataset[grepl("tcc4f", changes$instance, fixed = TRUE)] <- "Other binary
 scatter <- function(data, x_var, y_var) {
   limits <- c(min(data[[x_var]], data[[y_var]], na.rm = TRUE), max(data[[x_var]], data[[y_var]], na.rm = TRUE))
   ggplot(data, aes(.data[[x_var]], .data[[y_var]], col = dataset)) +
-    geom_count() +
+    geom_count(alpha = 0.5) +
     geom_abline(slope = 1, intercept = 0, colour = "#989898") +
     scale_x_continuous(trans = log10_trans(), limits = limits) +
     scale_y_continuous(trans = log10_trans(), limits = limits) +
     coord_fixed() +
     annotation_logticks(colour = "#b3b3b3") +
-    theme_light()
+    theme_light() +
+    theme(legend.position = "right", legend.box = "vertical") +
+    scale_color_brewer(palette = "Dark2") +
+    xlab("\\texttt{bklm16} variables") +
+    ylab("\\texttt{bklm16++} variables") +
+    labs(color = "", size = "")
+#    guides(color = guide_legend(ncol = 2), size = guide_legend(ncol = 2))
 }
 
 # Before/after comparison of the number of variables
 # Note: the same plot for other encodings looks very similar
-scatter(changes[changes$encoding == "bklm16",], "before_variables", "after_variables")
 scatter(changes[changes$encoding == "bklm16",], "before_clauses", "after_clauses")
 
+scatter(changes[changes$encoding == "d02",], "before_variables", "after_variables")
+scatter(changes[changes$encoding == "d02",], "before_clauses", "after_clauses")
+
 # Comparison of encodings after optimisation
-df <- dcast(data = changes, formula = instance + dataset ~ encoding,
+changes.df <- dcast(data = changes, formula = instance + dataset ~ encoding,
             fun.aggregate = NULL,
             value.var = c("before_variables", "before_clauses", "after_variables", "after_clauses"))
 
-df %>% group_by(df$dataset) %>% tally()
+changes.df %>% group_by(changes.df$dataset) %>% tally()
 
-scatter(df, "after_variables_bklm16", "after_variables_cd06")
-scatter(df, "after_variables_bklm16", "after_variables_cd05")
[…]

### 2021-02-25 doc/paper3/paper.tex
Other plots
Writing

@@
 \usepackage{tikz}
+\usepackage[binary-units]{siunitx}
 
@@
 \section{Introduction}
+
+\paragraph{Related Work.}
+Many WMC inference algorithms such as
+\textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}}, \textsf{c2d}
+\cite{DBLP:conf/ecai/Darwiche04}, and \textsf{miniC2D}
+\cite{DBLP:conf/ijcai/OztokD15} work by compilation to tractable representations
+such as arithmetic circuits, deterministic, decomposable negation normal form
+\cite{DBLP:journals/jancl/Darwiche01}, and sentential decision diagrams (SDDs)
+\cite{DBLP:conf/ijcai/Darwiche11}. Some attempts have previously been made to
+skip this intermediate stage of representing a Bayesian network as a WMC
+instance and compile directly to a more convenient representation.
+Specifically, direct compilation from Bayesian networks to SDDs
+\cite{DBLP:conf/ecsqaru/ChoiKD13} and from structured Bayesian networks (i.e., a
+generalisation of Bayesian networks) to probabilistic SDDs
+\cite{shen2020modeling} have been considered. To the best of the authors'
+knowledge, neither compilation approach has a publicly available implementation.
+
+% TODO: Now say that our work is similar: it introduces a new representation
+% that is more appropriate for algorithms such as DPMC. Stress that all initial
+% pseudo-Boolean functions have two values.
 
@@
 
-\paragraph{References.}
-\begin{itemize}
-\item Related work without publicly available implementations:
-  \begin{itemize}
-  \item direct compilation to SDDs \cite{DBLP:conf/ecsqaru/ChoiKD13}
-  \item direct compilation to PSDDs, also eliminating parameter variables (a thesis)
-  \item maybe two more papers
-  \end{itemize}
-\end{itemize}
-
 \paragraph{Notes.}
@@
 
+\subsection{Bayesian Network Encodings}
+
+\begin{itemize}
+\item \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}
+\item \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}
+\item \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
+\item \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}
+\item \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}
+\end{itemize}
+
 \section{Parameter Variable Elimination}
@@
   would have less data to output.
+\item We do this as a follow-up to Ace compilation because the implementations
+  of the encodings are all closed-source, and we don't want to re-invent (a
+  subpar version of) the wheel.
+\item No obvious way to do this for sbk05 because the roles of indicator and
+  parameter (i.e., `chance') variables overlap.
+\item This just says that $p$ is equivalent to a conjunction.
+\item The first group of conditions applies to \texttt{d02}, while the second
+  group applies to \texttt{bklm16}.
+\item For \texttt{cd05} and \texttt{cd06}, condition $2bi$ should be replaced
+  with $w(\neg p) = 1$.
+\item Benefits of having this proof in the paper:
+  \begin{itemize}
+  \item It puts all encodings on a common ground.
+  \item It illustrates the convenience of our notation for reasoning about
+    (certain types of) pseudo-Boolean functions.
+  \item It's too big and too important to be left for the appendix.
+  \end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-\item Apparently, the \textsc{DPMC} paper \cite{DBLP:conf/cp/DudekPV20} already
-  shows that taking the first offered decomposition tree is best.
-\item Processors:
+\item The experiments were run on a computing cluster with Intel Xeon E5-2630,
+  Intel Xeon E7-4820, and Intel Xeon Gold 6138 processors with a
+  \SI{1000}{\second} timeout separately on both encoding and inference, and a
+  \SI{32}{\gibi\byte} memory limit.\footnote{Each instance was run on the same
+    processor across all algorithms and encodings.}
+\item Along with
+  \textsf{DPMC}\footnote{\url{https://github.com/vardigroup/DPMC}}, in our
+  experiments we also include WMC algorithms used in the papers that introduce
+  each encoding: \textsf{Ace}
+  for \texttt{cd05}, \texttt{cd06}, and \texttt{d02};
+  \textsf{Cachet}\footnote{\url{https://cs.rochester.edu/u/kautz/Cachet/}}
+  \cite{DBLP:conf/sat/SangBBKP04} for \texttt{sbk05}; and
+  \textsf{c2d}\footnote{\url{http://reasoning.cs.ucla.edu/c2d/}}
+  \cite{DBLP:conf/ecai/Darwiche04} with
+  \textsf{query-dnnf}\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
+  for \texttt{bklm16}.
+\item \textsf{DPMC} was run in \emph{greedy mode}. This mode (which was not part
+  of the original paper \cite{DBLP:conf/cp/DudekPV20}) optimises the order in
+  which pseudo-Boolean functions are multiplied by prioritising functions with
+  small representations.
+\item Indeed, the numbers of variables in \texttt{bklm16++} and \texttt{d02++}
+  encodings are equal whenever all variables in a Bayesian network have two
+  values (which applies to most of the benchmark instances). Nonetheless,
+  \texttt{bklm16++} performs much faster than \texttt{d02++}.
+\item \textsf{DPMC} is run with tree decomposition based planning and algebraic
+  decision diagram based execution---the best-performing combination in the
+  original set of experiments \cite{DBLP:conf/cp/DudekPV20}. We use a single
+  iteration of \textsf{htd} \cite{DBLP:conf/cpaior/AbseherMW17} to generate
+  approximately optimal tree decompositions---we found that this configuration
+  is efficient enough to handle huge instances, and yet the width of the
+  returned decomposition is unlikely to differ from optimal by more than one or
+  two.
+\item We also record numbers of variables in each encoding before and after our
+  additional transformation.
+\item Experimental research questions:
   \begin{itemize}
-  \item Intel(R) Xeon(R) Gold 6138 CPU @ 2.00GHz
-  \item Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz
-  \item Intel(R) Xeon(R) CPU E7-4820 v2 @ 2.00GHz
+  \item Can parameter variable elimination improve inference speed?
+  \item How does DPMC combined with encodings without (and with) parameter
+    variables compare with other WMC algorithms and other encodings?
+  \item Which instances is our approach particularly successful on (compared to
+    other algorithms and encodings and to the same encoding before our
+    transformation)?
+  \item What proportion of variables is typically removed?
+  \item Do some encodings benefit from this transformation more than others?
   \end{itemize}
+\item How many times am I faster than old cd06 and new bklm16? Perhaps add other
+  numbers as well.
+\end{itemize}
+% TODO: define binary = 2 values per variable (or states per node?)
+% reuse this term where I'm referring to two values
+
+For our experiments we use Bayesian networks available with \textsf{Ace} and
+\textsf{Cachet}. We split them into the following groups:
+\begin{itemize}
+\item DQMR and
+\item Grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05};
+\item Mastermind and
+\item Random Blocks by Chavira et al. \cite{DBLP:journals/ijar/ChaviraDJ06};
+\item other binary Bayesian networks including Plan Recognition
+  \cite{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
+  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f};
+\item non-binary classic Bayesian networks: \texttt{alarm}, \texttt{diabetes},
+  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
+  \texttt{pathfinder}, \texttt{pigs}, and \texttt{water}.
 \end{itemize}
 
-\begin{figure}[t]
+\begin{figure}
   \centering
   \input{cumulative.tex}%
-  \caption{TODO}
+  \caption{Cumulative numbers of instances solved by each algorithm-encoding
+    pair over time.}
   \label{fig:cumulative}
 \end{figure}
+
+\begin{figure}
+  \centering
+  \input{scatter.tex}%
+  \caption{An instance-by-instance comparison between $\textsf{DPMC} +
+    \texttt{bklm16++}$ (the best combination according to \cref{fig:cumulative})
+  and the second and third best performing combinations: $\textsf{Ace} +
+  \texttt{cd06}$ and $\textsf{DPMC} + \texttt{bklm16}$.}
+  \label{fig:scatter}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{box.tex}%
+  \caption{Box plots of the numbers of variables in each encoding across all
+    benchmark instances before and after applying \cref{alg:transformation}.}
+  \label{fig:box}
+\end{figure} % TODO: maybe add sbk05 with just 'before'?
 
@@
 \begin{itemize}
-\item This just says that $p$ is equivalent to a conjunction.
-\item The first group of conditions applies to \texttt{d02}, while the second
-  group applies to \texttt{bklm16}.
-\item For \texttt{cd05} and \texttt{cd06}, condition $2bi$ should be replaced
-  with $w(\neg p) = 1$.
-\item Benefits of having this proof in the paper:
+\item Benefits of my approach:
   \begin{itemize}
-  \item It puts all encodings on a common ground.
-  \item It illustrates the convenience of our notation for reasoning about
-    (certain types of) pseudo-Boolean functions.
-  \item It's too big and too important to be left for the appendix.
+  \item smaller primal graph, so easier to perform tree decomposition
+  \item Variable order is less likely to be obstructed by all the unnecessary
+    'parameter' variables.
+  \item There are others, but they're not that important.
   \end{itemize}

### 2021-02-26 doc/paper3/paper.tex
Writing and editing

@@
 
-% TODO: Now say that our work is similar: it introduces a new representation
-% that is more appropriate for algorithms such as DPMC. Stress that all initial
-% pseudo-Boolean functions have two values.
+Our work is similar in that it introduces a new representation for computational
+problems that is based on pseudo-Boolean functions---pseudo-Boolean projection
+(PBP). We formally show that every WMC problem instance has a corresponding PBP
+instance. We argue that this new format is more appropriate for WMC solvers
+whose execution is build on pseudo-Boolean function manipulation, i.e.,
+\textsf{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} and \textsf{DPMC}
+\cite{DBLP:conf/cp/DudekPV20}. Finally, we show how most methods of encoding
+probabilistic inference on Bayesian networks to WMC can be adapted to the PBP
+format. This transformation significantly improves inference speed,
+outperforming all other considered algorithm-encoding combinations.
+
+%allowing two encodings that were previously incompatible with
+%\textsf{DPMC} to be compatible.
+
+% TODO: we also show correctness
+% TODO: and new notation!
 
@@
 
-\begin{remark}
-  Encodings such as \texttt{cd05} and \texttt{cd06} are \emph{not} WMC
-  encodings. Instead, they encode Bayesian network inference into instances of
-  the \emph{minimum-cardinality} WMC problem, where the answer is defined to be
-  $\sum_{Y \models \phi\text{, }|Y| = k} \prod_{Y \models l}
-  w(l)$, where $k = \min_{Y \models \phi\text{, }Y \ne \emptyset}
-  |Y|$, if $k$ exists, otherwise the answer is zero. This additional
-  condition on model cardinality becomes necessary because these encodings
-  eliminate clauses of the form $p \Rightarrow i$, where $p \in X_P$ is a
-  parameter variable, and $i \in X_I$ is an indicator variable. Nonetheless, our
-  transformation algorithm still works on such encodings, although the
-  experimental results are discouraging because they use approximately twice as
-  many indicator variables. For instance, each binary variable of a Bayesian
-  network is encoded using two indicator variables while one would suffice.
-\end{remark}
-
 \begin{definition}[PBP Instance] \label{def:new_wmc}
-  A \emph{pseudo-Boolean projection} (PBP) instance is a tuple $(F, X, \omega)$,
-  where $X$ is the set of variables, $F$ is a set of pseudo-Boolean functions
-  $2^X \to \mathbb{R}$, and $\omega \in \mathbb{R}$ is the scaling factor. The
-  \emph{answer} of the instance is $\omega \cdot \left(\exists_X\prod_{f \in
-      F}f\right)(\emptyset)$.
+  A PBP instance is a tuple $(F, X, \omega)$, where $X$ is the set of variables,
+  $F$ is a set of pseudo-Boolean functions $2^X \to \mathbb{R}$, and $\omega \in
+  \mathbb{R}$ is the scaling factor.\footnote{We will further restrict $F$ to
+    only contain functions that have exactly two values. While this restriction
+    is not necessary from a computational point of view, such functions can be
+    conveniently represented both in text files and using the syntax proposed in
+    this paper.} The \emph{answer} of the instance is $\omega \cdot
+  \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
 \end{definition}
 
-NOTE: The constant is inspired by the \texttt{bklm16}
-\cite{DBLP:conf/ecai/BartKLM16} encoding.
+NOTE: Adding scaling factor $\omega$ to the definition allows us to remove
+clauses that consist entirely of a single parameter variable. The idea of
+extracting some of the structure of the WMC instance into an external
+multiplicative factor originates in one of the Bayesian network encodings
+\cite{DBLP:conf/ecai/BartKLM16}.
 
@@
 
+\paragraph{TODO}
 \begin{itemize}
-\item \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}
-\item \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}
-\item \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
-\item \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06}
-\item \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}
+\item Define the terminology surrounding BNs: variables, values, directed
+  probabilistic graphical model, DAG, binary = two values per variable.
+\item Reuse this term where I'm referring to two values.
+\item Give a brief description of each encoding.
+\item Talk about the parameter/indicator variable distinction.
 \end{itemize}
+
+WMC is a well-established technique for Bayesian network inference, particularly
+effective on networks where most variables have only a few possible values
+\cite{DBLP:conf/kr/Darwiche02}. Many ways of encoding a Bayesian network into a
+WMC instance have been proposed. We will refer to them based on initials of the
+authors and the year of publication: \texttt{d02}
+\cite{DBLP:conf/kr/Darwiche02}, \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05},
+\texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}, \texttt{cd06}
+\cite{DBLP:conf/sat/ChaviraD06}, \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}.
+
+\begin{remark}
+  Strictly speaking, encodings such as \texttt{cd05} and \texttt{cd06} are
+  \emph{not} WMC encodings. Instead, they encode Bayesian network inference into
+  instances of the \emph{minimum-cardinality} WMC problem, where the answer is
+  defined to be $\sum_{Y \models \phi\text{, }|Y| = k} \prod_{Y \models l}
+  w(l)$, where $k = \min_{Y \models \phi\text{, }Y \ne \emptyset} |Y|$, if $k$
+  exists, otherwise the answer is zero. This additional condition on model
+  cardinality becomes necessary because these encodings eliminate clauses of the
+  form $p \Rightarrow i$, where $p \in X_P$ is a parameter variable, and $i \in
+  X_I$ is an indicator variable. Nonetheless, our transformation algorithm still
+  works on such encodings, although the experimental results are discouraging
+  because they use approximately twice as many indicator variables. For
+  instance, each binary variable of a Bayesian network is encoded using two
+  indicator variables while one would suffice.
+\end{remark}
 
@@
 \begin{proof}
-  For base case, let $X = \{x\}$. Then
+  If $X = \{x\}$, then
   \[
@@
 \end{proposition}
-\begin{proof}
-  The answer of \cref{eq:new_wmc} is
-  \begin{align*}
-    \left(\exists_{X_I \cup X_P} \left(\prod_{c \in \phi} [c]_0^1\right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset) &= \sum_{Y \subseteq X_I \cup X_P} \left(\left(\prod_{c \in \phi} [c]_0^1 \right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)(Y) \\
-&= \sum_{Y \subseteq X_I \cup X_P} \underbrace{\left(\prod_{c \in \phi} [c]_0^1\right)}_f(Y) \underbrace{\left(\prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)}\right)}_g(Y)
-  \end{align*}
+\begin{proof} % TODO: equation is not the right word
+  Let $f = \prod_{c \in \phi} [c]_0^1$, and $g = \prod_{x \in X_I \cup X_P}
+  [x]_{w(\neg x)}^{w(x)}$. Then the answer of \cref{eq:new_wmc} is
+  \[
+    (\exists_{X_I \cup X_P} fg)(\emptyset) = \sum_{Y \subseteq X_I \cup X_P}
+    (fg)(Y) = \sum_{Y \subseteq X_I \cup X_P} f(Y)g(Y)
+  \]
   by \cref{lemma:sum}. Note that
@@
   \begin{equation} \label{eq:bigsums}
-    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
-    \right]_0^1 = \exists_p \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
-    \right]_0^1 = \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
-    \right]_0^1\right|_{p=1} + \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n
-      l_i \right]_0^1\right|_{p=0}.
+    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 = \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1\right|_{p=1} + \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1\right|_{p=0}.
   \end{equation}
@@
   and indeed
-  \begin{align*}
-    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 &= \left.\left( [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 \right)\right|_{p=1} + \left.\left([p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1 \right)\right|_{p=0} \\
-                                                                                      &= w(p) \cdot \left[ \bigwedge_{i=1}^n l_i \right]_0^1 + \left[ \bigwedge_{i=1}^n l_i \right]_1^0 = \left[ \bigwedge_{i=1}^n l_i \right]_1^{w(p)}.
-  \end{align*}
+  \[
+    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
+    \right]_0^1 = w(p) \cdot \left[ \bigwedge_{i=1}^n l_i \right]_0^1 + \left[
+      \bigwedge_{i=1}^n l_i \right]_1^0 = \left[ \bigwedge_{i=1}^n l_i
+    \right]_1^{w(p)}.
+  \]
   This finishes the proof of the correctness of the first `foreach' loop under
@@
   \]
-  We can rearrange the right-hand side as
+  We can rearrange the right-hand side as % TODO: make it fit into margins
   \begin{align*}
@@
   \end{itemize}
-\item How many times am I faster than old cd06 and new bklm16? Perhaps add other
-  numbers as well.
+\item TODO: How many times am I faster than old cd06 and new bklm16? Perhaps add
+  other numbers as well.
+\item To perform Bayesian network inference with \textsf{DPMC} (or with any
+  other WMC algorithm not based on compilation such as \textsf{Cachet}), one
+  needs to select a probability to compute
+  \cite{DBLP:conf/cp/DudekPV20,DBLP:conf/sat/SangBBKP04}. If a network comes
+  with an evidence file, we compute the probability of this evidence. Otherwise,
+  let $X$ be the variable last mentioned in the Bayesian network file. If
+  \textsf{true} is one of the values of $X$, then we compute $\Pr(X =
+  \textsf{true})$, otherwise we choose the first-mentioned value of $X$.
 \end{itemize}
-% TODO: define binary = 2 values per variable (or states per node?)
-% reuse this term where I'm referring to two values
+% TODO: describe the results.
 

### 2021-02-28 doc/paper3/box.tex
Writing
Lots of writing

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-02-23 15:58:55
+% Created by tikzDevice version 0.12.3.1 on 2021-02-28 16:52:48
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,144.54);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,144.54);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (173.45,144.54);
 \end{scope}
 \begin{scope}
-\path[clip] ( 40.51, 30.69) rectangle (275.96,139.04);
+\path[clip] ( 40.51, 33.38) rectangle (167.95,139.04);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 40.51, 30.69) rectangle (275.96,139.04);
+\path[fill=fillColor] ( 40.51, 33.38) rectangle (167.95,139.04);
 \definecolor{drawColor}{gray}{0.87}
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 54.03) --
-	(275.96, 54.03);
+\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 56.14) --
+	(167.95, 56.14);
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 91.24) --
-	(275.96, 91.24);
+\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 92.43) --
+	(167.95, 92.43);
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,128.46) --
-	(275.96,128.46);
+\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,128.72) --
+	(167.95,128.72);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 35.42) --
-	(275.96, 35.42);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 38.00) --
+	(167.95, 38.00);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 72.64) --
-	(275.96, 72.64);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 74.29) --
+	(167.95, 74.29);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,109.85) --
-	(275.96,109.85);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,110.58) --
+	(167.95,110.58);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.15, 30.69) --
-	( 74.15,139.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 55.21, 33.38) --
+	( 55.21,139.04);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (130.20, 30.69) --
-	(130.20,139.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 79.72, 33.38) --
+	( 79.72,139.04);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (186.26, 30.69) --
-	(186.26,139.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (104.23, 33.38) --
+	(104.23,139.04);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (242.32, 30.69) --
-	(242.32,139.04);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (128.74, 33.38) --
+	(128.74,139.04);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (153.24, 33.38) --
+	(153.24,139.04);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.63,115.66) -- ( 63.63,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 50.62,116.24) -- ( 50.62,144.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.63, 41.94) -- ( 63.63, 35.91);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 50.62, 44.35) -- ( 50.62, 38.47);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 54.17,115.66) --
-	( 54.17, 41.94) --
-	( 73.09, 41.94) --
-	( 73.09,115.66) --
-	( 54.17,115.66) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 46.48,116.24) --
+	( 46.48, 44.35) --
+	( 54.75, 44.35) --
+	( 54.75,116.24) --
+	( 46.48,116.24) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 54.17, 63.32) -- ( 73.09, 63.32);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.48, 65.20) -- ( 54.75, 65.20);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.66, 65.49) -- ( 84.66,104.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.81, 67.32) -- ( 59.81,104.99);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.66, 38.03) -- ( 84.66, 35.61);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.81, 40.54) -- ( 59.81, 38.18);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.20, 65.49) --
-	( 75.20, 38.03) --
-	( 94.12, 38.03) --
-	( 94.12, 65.49) --
-	( 75.20, 65.49) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 55.67, 67.32) --
+	( 55.67, 40.54) --
+	( 63.95, 40.54) --
+	( 63.95, 67.32) --
+	( 55.67, 67.32) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.20, 42.42) -- ( 94.12, 42.42);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 55.67, 44.82) -- ( 63.95, 44.82);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (119.69,119.81) -- (119.69,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.13,120.28) -- ( 75.13,144.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (119.69, 43.24) -- (119.69, 36.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.13, 45.62) -- ( 75.13, 38.58);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (110.23,119.81) --
-	(110.23, 43.24) --
-	(129.15, 43.24) --
-	(129.15,119.81) --
-	(110.23,119.81) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 70.99,120.28) --
+	( 70.99, 45.62) --
+	( 79.26, 45.62) --
+	( 79.26,120.28) --
+	( 70.99,120.28) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (110.23, 64.90) -- (129.15, 64.90);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.99, 66.74) -- ( 79.26, 66.74);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (140.71,104.94) -- (140.71,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.32,105.79) -- ( 84.32,144.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (140.71, 40.63) -- (140.71, 35.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.32, 43.08) -- ( 84.32, 38.42);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (131.26,104.94) --
-	(131.26, 40.63) --
-	(150.17, 40.63) --
-	(150.17,104.94) --
-	(131.26,104.94) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 80.18,105.79) --
+	( 80.18, 43.08) --
+	( 88.45, 43.08) --
+	( 88.45,105.79) --
+	( 80.18,105.79) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (131.26, 50.31) -- (150.17, 50.31);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 80.18, 52.51) -- ( 88.45, 52.51);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (175.75,119.86) -- (175.75,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.63,120.34) -- ( 99.63,144.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (175.75, 43.24) -- (175.75, 36.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.63, 45.62) -- ( 99.63, 38.58);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (166.29,119.86) --
-	(166.29, 43.24) --
-	(185.21, 43.24) --
-	(185.21,119.86) --
-	(166.29,119.86) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 95.50,120.34) --
+	( 95.50, 45.62) --
+	(103.77, 45.62) --
+	(103.77,120.34) --
+	( 95.50,120.34) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (166.29, 64.90) -- (185.21, 64.90);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.50, 66.74) -- (103.77, 66.74);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77,104.94) -- (196.77,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.82,105.79) -- (108.82,144.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77, 40.63) -- (196.77, 35.85);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.82, 43.08) -- (108.82, 38.42);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (187.31,104.94) --
-	(187.31, 40.63) --
-	(206.23, 40.63) --
-	(206.23,104.94) --
-	(187.31,104.94) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (104.69,105.79) --
+	(104.69, 43.08) --
+	(112.96, 43.08) --
+	(112.96,105.79) --
+	(104.69,105.79) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (187.31, 50.31) -- (206.23, 50.31);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (104.69, 52.51) -- (112.96, 52.51);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.81,107.47) -- (231.81,144.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (124.14,108.25) -- (124.14,144.54);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.81, 40.63) -- (231.81, 35.83);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (124.14, 43.08) -- (124.14, 38.40);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.35,107.47) --
-	(222.35, 40.63) --
-	(241.27, 40.63) --
-	(241.27,107.47) --
-	(222.35,107.47) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (120.01,108.25) --
+	(120.01, 43.08) --
+	(128.28, 43.08) --
+	(128.28,108.25) --
+	(120.01,108.25) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (222.35, 55.32) -- (241.27, 55.32);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (120.01, 57.40) -- (128.28, 57.40);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (252.83, 69.18) -- (252.83,104.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (133.33, 70.91) -- (133.33,104.99);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (252.83, 38.03) -- (252.83, 35.61);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (133.33, 40.54) -- (133.33, 38.18);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (243.37, 69.18) --
-	(243.37, 38.03) --
-	(262.29, 38.03) --
-	(262.29, 69.18) --
-	(243.37, 69.18) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (129.20, 70.91) --
+	(129.20, 40.54) --
+	(137.47, 40.54) --
+	(137.47, 70.91) --
+	(129.20, 70.91) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (243.37, 42.87) -- (262.29, 42.87);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (129.20, 45.26) -- (137.47, 45.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (153.24, 89.69) -- (153.24,144.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (153.24, 41.81) -- (153.24, 38.29);
+\definecolor{fillColor}{RGB}{27,158,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (144.97, 89.69) --
+	(144.97, 41.81) --
+	(161.51, 41.81) --
+	(161.51, 89.69) --
+	(144.97, 89.69) --
+	cycle;
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (144.97, 53.85) -- (161.51, 53.85);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.69) rectangle (275.96,139.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (167.95,139.04);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 32.39) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 34.97) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 69.61) {2000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 71.26) {2000};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,106.82) {4000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,107.55) {4000};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 35.42) --
-	( 40.51, 35.42);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 38.00) --
+	( 40.51, 38.00);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 72.64) --
-	( 40.51, 72.64);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 74.29) --
+	( 40.51, 74.29);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,109.85) --
-	( 40.51,109.85);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,110.58) --
+	( 40.51,110.58);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.15, 27.94) --
-	( 74.15, 30.69);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 55.21, 30.63) --
+	( 55.21, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (130.20, 27.94) --
-	(130.20, 30.69);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 79.72, 30.63) --
+	( 79.72, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (186.26, 27.94) --
-	(186.26, 30.69);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (104.23, 30.63) --
+	(104.23, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (242.32, 27.94) --
-	(242.32, 30.69);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (128.74, 30.63) --
+	(128.74, 33.38);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (153.24, 30.63) --
+	(153.24, 33.38);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 74.15, 19.68) {\texttt{bklm16}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 55.21, 22.37) {\texttt{bklm16}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (130.20, 19.68) {\texttt{cd05}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.72, 22.37) {\texttt{cd05}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.26, 19.68) {\texttt{cd06}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (104.23, 22.37) {\texttt{cd06}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (242.32, 19.68) {\texttt{d02}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (128.74, 22.37) {\texttt{d02}};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (153.24, 22.37) {\texttt{sbk05}};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 84.86) {Variables};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 86.21) {Variables};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (286.96, 57.30) rectangle (341.40,112.42);
+\path[fill=fillColor] ( 58.10,  5.50) rectangle (150.36, -2.81);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (292.46, 77.26) rectangle (306.91, 91.71);
+\path[fill=fillColor] ( 63.60,  5.50) rectangle ( 78.05, 19.95);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 78.70) --
-	(299.68, 80.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.83,  6.95) --
+	( 70.83,  9.11);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 88.10) --
-	(299.68, 90.26);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.83, 16.34) --
+	( 70.83, 18.51);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (294.26, 80.87) rectangle (305.10, 88.10);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 65.41,  9.11) rectangle ( 76.25, 16.34);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.26, 84.48) --
-	(305.10, 84.48);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.41, 12.73) --
+	( 76.25, 12.73);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (292.46, 62.80) rectangle (306.91, 77.26);
+\path[fill=fillColor] (112.54,  5.50) rectangle (126.99, 19.95);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 64.25) --
-	(299.68, 66.42);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (119.77,  6.95) --
+	(119.77,  9.11);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 73.64) --
-	(299.68, 75.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (119.77, 16.34) --
+	(119.77, 18.51);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (294.26, 66.42) rectangle (305.10, 73.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (114.35,  9.11) rectangle (125.19, 16.34);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.26, 70.03) --
-	(305.10, 70.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.35, 12.73) --
+	(125.19, 12.73);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.41, 81.45) {before};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 83.55,  9.70) {before};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
+\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.41, 67.00) {after};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (132.49,  9.70) {after};
 \end{scope}

### 2021-02-28 doc/paper3/paper.tex
Lots of writing

@@
 \usepackage[binary-units]{siunitx}
+\usepackage{booktabs}
+\usepackage{capt-of}
 
@@
 
+% TODO for later:
+% 1) read through v2 of the paper and check if I forgot to mention something
+% here
+% 2) run this through grammarly
+
 \paragraph{Related Work.}
@@
 
-% TODO: we also show correctness
-% TODO: and new notation!
+\paragraph{Notes.}
+\begin{itemize}
+\item we also show correctness
+\item and introduce a new notation
+\end{itemize}
+
+\section{Weighted Model Counting}
+
+TODO: Mention that formulas, clauses, and models are all treated as sets.
+
+\begin{definition}[WMC]
+  A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
+  the set of indicator variables, $X_P$ is the set of parameter variables (with
+  $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula in CNF over
+  $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
+  X_P\} \to \mathbb{R}$ is the weight function. The \emph{answer} of the
+  instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
+\end{definition}
+
+\begin{definition}[Minimum-Cardinality WMC]
+  A \emph{minimum-cardinality WMC} instance has same tuple as a WMC instance,
+  but its answer is defined to be $\sum_{Y \models \phi\text{, }|Y| = k}
+  \prod_{Y \models l} w(l)$, where $k = \min_{Y \models \phi\text{, }Y \ne
+    \emptyset} |Y|$, if $k$ exists, otherwise the answer is zero.
+\end{definition}
+
+Our definition of WMC is largely based on the standard definition
+\cite{DBLP:journals/ai/ChaviraD08}, but explicitly partitions variables into
+indicator and parameter variables. In practice, we identify this partition in
+one of two ways. If an encoding is generated by \textsf{Ace}, then variable
+types are explicitly identified in the LMAP file generated alongside the
+encoding. Otherwise, we define a variable $x$ to be a parameter variable if
+$w(x) = w(\neg x) = 1$.
+
+\subsection{Bayesian Network Encodings (mostly done)}
+
+A \emph{Bayesian network} is a directed acyclic graph with random variables as
+vertices and edges as conditional dependencies. As is common in related
+literature
+\cite{DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05}, we assume that each
+variable has a finite number of values. We call a Bayesian network \emph{binary}
+if every variable has two values. If all variables have finite numbers of
+values, the probability function associated with each variable $v$ can be
+represented as a \emph{conditional probability table} (CPT), i.e., a table
+with a row for each combination of values that $v$ and its parent vertices can
+take. Each row then also has a \emph{probability}, i.e., a number in $[0, 1]$.
+
+WMC is a well-established technique for Bayesian network inference, particularly
+effective on networks where most variables have only a few possible values
+\cite{DBLP:conf/kr/Darwiche02}. Many ways of encoding a Bayesian network into a
+WMC instance have been proposed. We will refer to them based on initials of the
+authors and the year of publication. Darwiche was the first to suggest the
+\texttt{d02} \cite{DBLP:conf/kr/Darwiche02} encoding that, in many ways, remains
+the foundation behind most other encodings. He also introduced the distinction
+between \emph{indicator} and \emph{parameter variables}; the former represent
+variable-value pairs in the Bayesian network, while the latter are associated
+with probabilities in the CPTs. The encoding \texttt{sbk05}
+\cite{DBLP:conf/aaai/SangBK05} is the only encoding that deviates from this
+arrangement: for each variable in the Bayesian network, one indicator variable
+acts simultaneously as a parameter variable. Chavira and Darwiche propose
+\texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05} where they shift from WMC to
+minimum-cardinality WMC because that allows the encoding to have fewer variables
+and clauses. In particular, they propose a way to use the same parameter
+variable to represent all probabilities in a CPT that are equal and keep only
+clauses that `imply' parameter variables (i.e., omit clauses where a parameter
+variable implies indicator variables). In their next encoding, \texttt{cd06}
+\cite{DBLP:conf/sat/ChaviraD06}, the same authors optimise the aforementioned
+implication clauses, choosing the smallest sufficient selection of indicator
+variables. A decade later, Bart et al. present \texttt{bklm16}
+\cite{DBLP:conf/ecai/BartKLM16} that improves upon \texttt{cd06} in two ways.
+First, they optimise the number of indicator variables used per Bayesian network
+variable from a linear to a logarithmic amount. Second, they introduce a scaling
+factor that can `absorb' one probability per Bayesian network variable. However,
+for this work, we choose to disable the latter improvement since this scaling
+factor is often small enough to be indistinguishable from zero without the use
+of arbitrary precision arithmetic. Indeed, even a small Bayesian network with
+seven mutually independent binary variables, 0.1 and 0.9 probabilities each, is
+already big enough for the scaling factor to be exactly equal to zero (as
+produced by the \texttt{bklm16}
+encoder\footnote{\url{http://www.cril.univ-artois.fr/kc/bn2cnf.html}}).
+
+% TODO: incorporate this somewhere
+%This additional condition on model
+%cardinality becomes necessary because these encodings eliminate clauses of the
+%form $p \Rightarrow i$, where $p \in X_P$ is a parameter variable, and $i \in
+%X_I$ is an indicator variable. Nonetheless, our transformation algorithm still
+%works on such encodings, although the experimental results are discouraging
+%because they use approximately twice as many indicator variables. For
+%instance, each binary variable of a Bayesian network is encoded using two
+%indicator variables while one would suffice.
 
@@
 
-NOTE: We list some properties of the operations on pseudo-Boolean functions
+Below we list some properties of the operations on pseudo-Boolean functions
 discussed in this section that can be conveniently represented using our syntax.
@@
 
-\paragraph{Notes.}
-\begin{itemize}
-\item Weights on literals other than the positive literals that correspond to
-  variables in $X_P$ are redundant as they either are equal to one or duplicate
-  an already-defined weight.
-\item Mention that formulas, clauses, and models are all treated as sets.
-\end{itemize}
-
-\section{Weighted Model Counting}
-
-NOTE: Our definition of WMC is largely based on the standard definition
-\cite{DBLP:journals/ai/ChaviraD08}, but explicitly partitions variables into
-indicator and parameter variables.
-
-\begin{definition}[WMC Instance]
-  A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
-  the set of indicator variables, $X_P$ is the set of parameter variables (with
-  $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula in CNF over
-  $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
-  X_P\} \to \mathbb{R}$ is the weight function. The \emph{answer} of the
-  instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
-\end{definition}
+\section{PBP as a Computational Problem}
 
@@
 
-NOTE: Adding scaling factor $\omega$ to the definition allows us to remove
+\begin{remark}
+  Adding scaling factor $\omega$ to the definition allows us to remove
   clauses that consist entirely of a single parameter variable. The idea of
@@
   \cite{DBLP:conf/ecai/BartKLM16}.
-
-\subsection{Bayesian Network Encodings}
-
-\paragraph{TODO}
-\begin{itemize}
-\item Define the terminology surrounding BNs: variables, values, directed
-  probabilistic graphical model, DAG, binary = two values per variable.
-\item Reuse this term where I'm referring to two values.
-\item Give a brief description of each encoding.
-\item Talk about the parameter/indicator variable distinction.
-\end{itemize}
-
-WMC is a well-established technique for Bayesian network inference, particularly
-effective on networks where most variables have only a few possible values
-\cite{DBLP:conf/kr/Darwiche02}. Many ways of encoding a Bayesian network into a
-WMC instance have been proposed. We will refer to them based on initials of the
-authors and the year of publication: \texttt{d02}
-\cite{DBLP:conf/kr/Darwiche02}, \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05},
-\texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}, \texttt{cd06}
-\cite{DBLP:conf/sat/ChaviraD06}, \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}.
-
-\begin{remark}
-  Strictly speaking, encodings such as \texttt{cd05} and \texttt{cd06} are
-  \emph{not} WMC encodings. Instead, they encode Bayesian network inference into
-  instances of the \emph{minimum-cardinality} WMC problem, where the answer is
-  defined to be $\sum_{Y \models \phi\text{, }|Y| = k} \prod_{Y \models l}
-  w(l)$, where $k = \min_{Y \models \phi\text{, }Y \ne \emptyset} |Y|$, if $k$
-  exists, otherwise the answer is zero. This additional condition on model
-  cardinality becomes necessary because these encodings eliminate clauses of the
-  form $p \Rightarrow i$, where $p \in X_P$ is a parameter variable, and $i \in
-  X_I$ is an indicator variable. Nonetheless, our transformation algorithm still
-  works on such encodings, although the experimental results are discouraging
-  because they use approximately twice as many indicator variables. For
-  instance, each binary variable of a Bayesian network is encoded using two
-  indicator variables while one would suffice.
 \end{remark}
 
-\section{Parameter Variable Elimination}
+\subsection{From WMC to PBP}
 
@@
 \begin{itemize}
-\item Let $X_P$ be the set of parameter variable and $X_I$ be the set of
-  indicator variables.
-\item Parameter variables are either taken from the LMAP file (for encodings
-  produced by Ace) or assumed to be the variables that have both weights equal
-  to 1.
-\item If a parameter variable in a clause is `negated', we can ignore the
-  clause. We assume that there are no clauses with more than one instance of
-  parameter variables.
-\item The second \textbf{foreach} loop can be performed in constant time by
-  representing $\phi'$ as a list and assuming that the two 'clauses' are
-  adjacent in that list (and incorporating it into the first loop).
-\item The $d$ map is constructed in $\mathcal{O}(|X_P|\log|X_P|)$ time (we want
-  to use a data structure based on binary search trees rather than hashing).
-\item \texttt{rename} can be implemented in $\mathcal{O}(\log |X_P|)$ time.
-\item This may look like preprocessing, but all the transformations are local
-  and thus can be incorporated into an encoding algorithm with no slowdown. In
-  fact, if anything, the resulting algorithm would be slightly faster, as it
-  would have less data to output.
-\item We do this as a follow-up to Ace compilation because the implementations
-  of the encodings are all closed-source, and we don't want to re-invent (a
-  subpar version of) the wheel.
-\item No obvious way to do this for sbk05 because the roles of indicator and
-  parameter (i.e., `chance') variables overlap.
-\item This just says that $p$ is equivalent to a conjunction.
-\item The first group of conditions applies to \texttt{d02}, while the second
-  group applies to \texttt{bklm16}.
-\item For \texttt{cd05} and \texttt{cd06}, condition $2bi$ should be replaced
-  with $w(\neg p) = 1$.
+\item The algorithm is based on several observations that will be made precise
+  in \cref{thm:correctness}. First, all weights except for $\{w(p) \mid p \in
+  X_P\}$ are redundant as they either duplicate an already-defined weight or are
+  equal to one. Second, each clause has at most one parameter variable. Third,
+  if the parameter variable is negated, we can ignore the clause (this idea
+  first appears in the \texttt{cd05} paper \cite{DBLP:conf/ijcai/ChaviraD05}).
+\item We formulate our algorithm as a sequel to the WMC encoding procedure
+  because the implementations of Bayesian network WMC encodings are all
+  closed-source. However, as all transformations in \cref{alg:transformation}
+  are local, the algorithm can be efficiently incorporated into a WMC encoding
+  algorithm with no noticeable slowdown.
+\item No obvious way to do this for \texttt{sbk05} because the roles of
+  indicator and parameter (i.e., `chance') variables overlap
+  \cite{DBLP:conf/aaai/SangBK05}.
 \item Benefits of having this proof in the paper:
@@
 
+%\item The second \textbf{foreach} loop can be performed in constant time by
+%  representing $\phi'$ as a list and assuming that the two 'clauses' are
+%  adjacent in that list (and incorporating it into the first loop).
+%\item The $d$ map is constructed in $\mathcal{O}(|X_P|\log|X_P|)$ time (we want
+%  to use a data structure based on binary search trees rather than hashing).
+%\item \texttt{rename} can be implemented in $\mathcal{O}(\log |X_P|)$ time.
+
 \begin{algorithm}[t]
-  \caption{WMC instance transformation}
+  \caption{WMC to PBP transformation}
   \label{alg:transformation}
@@
 
+\paragraph{Notes.}
+\begin{itemize}
+\item This just says that $p$ is equivalent to a conjunction.
+\item The first group of conditions applies to \texttt{d02}, while the second
+  group applies to \texttt{bklm16}.
+\item For \texttt{cd05} and \texttt{cd06}, condition $2bi$ should be replaced
+  with $w(\neg p) = 1$.
+\end{itemize}
+
+\paragraph{TODO}
+\begin{itemize}
+\item check if each condition is actually used. Maybe turn this into a paragraph
+  that gives an overview of the proof.
+\item condition 1 is necessary in both cases because we're ignoring the weights
+  of indicator variables (explicitly acknowledge this)
+\item add the \texttt{cd05}/\texttt{cd06} correctness theorem
+\end{itemize}
+
 \begin{theorem}[Early Projection
@@
 
-% NOTE: mention that this is similar (but not equal) to the DPMC/ADDMC result
+% TODO: mention that this is similar (but not equal) to the DPMC/ADDMC result
 \begin{proposition} \label{prop:equivalence}
@@
 \end{proposition}
-\begin{proof} % TODO: equation is not the right word
+\begin{proof}
   Let $f = \prod_{c \in \phi} [c]_0^1$, and $g = \prod_{x \in X_I \cup X_P}
-  [x]_{w(\neg x)}^{w(x)}$. Then the answer of \cref{eq:new_wmc} is
+  [x]_{w(\neg x)}^{w(x)}$. Then the answer to the WMC instance
+  \eqref{eq:new_wmc} is
   \[
@@
 
-\begin{theorem}[Correctness]
+\begin{theorem}[Correctness] \label{thm:correctness}
   \Cref{alg:transformation}, when given a WMC instance $(\phi, X_I, X_P,
@@
 
-\section{Experimental Results}
+\section{Experimental Evaluation}
+% TODO: what are the encodings compiled with?
 
-\paragraph{Notes.}
-\begin{itemize}
-\item The experiments were run on a computing cluster with Intel Xeon E5-2630,
-  Intel Xeon E7-4820, and Intel Xeon Gold 6138 processors with a
-  \SI{1000}{\second} timeout separately on both encoding and inference, and a
-  \SI{32}{\gibi\byte} memory limit.\footnote{Each instance was run on the same
-    processor across all algorithms and encodings.}
-\item Along with
-  \textsf{DPMC}\footnote{\url{https://github.com/vardigroup/DPMC}}, in our
-  experiments we also include WMC algorithms used in the papers that introduce
-  each encoding: \textsf{Ace}
-  for \texttt{cd05}, \texttt{cd06}, and \texttt{d02};
+We run a set of experiments, comparing all five original Bayesian network
+encodings (\texttt{bklm16}, \texttt{cd05}, \texttt{cd06}, \texttt{d02}
+\texttt{sbk05}) as well as the first four with \cref{alg:transformation} applied
+afterwards.\footnote{Recall that \texttt{cd05} and \texttt{cd06} are
+  incompatible with \textsf{DPMC}.} For each encoding \texttt{e}, we will write
+\texttt{e++} to denote the combination of encoding a Bayesian network as a WMC
+instance using \texttt{e} and transforming it into a PBP instance using
+\cref{alg:transformation}. Along with
+\textsf{DPMC}\footnote{\url{https://github.com/vardigroup/DPMC}}, we also
+include WMC algorithms used in the papers that introduce each encoding:
+\textsf{Ace} for \texttt{cd05}, \texttt{cd06}, and \texttt{d02};
 \textsf{Cachet}\footnote{\url{https://cs.rochester.edu/u/kautz/Cachet/}}
@@
 \textsf{query-dnnf}\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
-  for \texttt{bklm16}.
-\item \textsf{DPMC} was run in \emph{greedy mode}. This mode (which was not part
-  of the original paper \cite{DBLP:conf/cp/DudekPV20}) optimises the order in
-  which pseudo-Boolean functions are multiplied by prioritising functions with
-  small representations.
-\item Indeed, the numbers of variables in \texttt{bklm16++} and \texttt{d02++}
-  encodings are equal whenever all variables in a Bayesian network have two
-  values (which applies to most of the benchmark instances). Nonetheless,
-  \texttt{bklm16++} performs much faster than \texttt{d02++}.
-\item \textsf{DPMC} is run with tree decomposition based planning and algebraic
-  decision diagram based execution---the best-performing combination in the
-  original set of experiments \cite{DBLP:conf/cp/DudekPV20}. We use a single
-  iteration of \textsf{htd} \cite{DBLP:conf/cpaior/AbseherMW17} to generate
-  approximately optimal tree decompositions---we found that this configuration
-  is efficient enough to handle huge instances, and yet the width of the
-  returned decomposition is unlikely to differ from optimal by more than one or
-  two.
-\item We also record numbers of variables in each encoding before and after our
-  additional transformation.
-\item Experimental research questions:
+for \texttt{bklm16}. We focus on the following questions:
 \begin{itemize}
@@
 \end{itemize}
-\item TODO: How many times am I faster than old cd06 and new bklm16? Perhaps add
-  other numbers as well.
-\item To perform Bayesian network inference with \textsf{DPMC} (or with any
+
+\subsection{Setup (mostly done)}
+
+\textsf{DPMC} is run with tree decomposition based planning and algebraic
+decision diagram based execution---the best-performing combination in the
+original set of experiments \cite{DBLP:conf/cp/DudekPV20}. We use a single
+iteration of \textsf{htd} \cite{DBLP:conf/cpaior/AbseherMW17} to generate
+approximately optimal tree decompositions---we found that this configuration
+is efficient enough to handle huge instances, and yet the width of the
+returned decomposition is unlikely to differ from optimal by more than one or
+two. We also enabled \textsf{DPMC}'s greedy mode. This mode (which was not part
+of the original paper \cite{DBLP:conf/cp/DudekPV20}) optimises the order in
+which pseudo-Boolean functions are multiplied by prioritising functions with
+small representations.
+
+For experimental data, we use Bayesian networks available with \textsf{Ace} and
+\textsf{Cachet}. We split them into the following groups:
+\begin{itemize}
+\item DQMR (390 instances) and
+\item Grid networks (450 instances) as described by Sang et al.
+  \cite{DBLP:conf/aaai/SangBK05};
+\item Mastermind (144 instances) and
+\item Random Blocks (256 instances) by Chavira et al.
+  \cite{DBLP:journals/ijar/ChaviraDJ06};
+\item other binary Bayesian networks (50 instances) including Plan Recognition
+  \cite{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
+  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f};
+\item non-binary classic networks (176 instances): \texttt{alarm},
+  \texttt{diabetes}, \texttt{hailfinder}, \texttt{mildew},
+  \texttt{munin1}--\texttt{4}, \texttt{pathfinder}, \texttt{pigs}, and
+  \texttt{water}.
+\end{itemize}
+
+To perform Bayesian network inference with \textsf{DPMC} (or with any
 other WMC algorithm not based on compilation such as \textsf{Cachet}), one
@@
 \textsf{true})$, otherwise we choose the first-mentioned value of $X$.
+
+The experiments were run on a computing cluster with Intel Xeon E5-2630,
+Intel Xeon E7-4820, and Intel Xeon Gold 6138 processors with a
+\SI{1000}{\second} timeout separately on both encoding and inference, and a
+\SI{32}{\gibi\byte} memory limit.\footnote{Each instance was run on the same
+  processor across all algorithms and encodings.}
+
+\subsection{Results}
+
+\paragraph{Notes.}
+\begin{itemize}
+\item \Cref{fig:cumulative} shows:
+  \begin{itemize}
+  \item $\textsf{DPMC}+\texttt{bklm16++}$ remains the best-performing
+    combination across all time limits up to \SI{1000}{\second} with $\textsf{Ace} +
+    \texttt{cd06}$ and $\textsf{DPMC}+\texttt{bklm16}$ not far behind;
+  \item $\textsf{DPMC}+\texttt{bklm16++}$ to be 3.35 times faster than
+    $\textsf{DPMC}+\texttt{bklm16}$ and 2.96 times faster than
+    $\textsf{Ace}+\texttt{cd06}$.
   \end{itemize}
-% TODO: describe the results.
-
-For our experiments we use Bayesian networks available with \textsf{Ace} and
-\textsf{Cachet}. We split them into the following groups:
-\begin{itemize}
-\item DQMR and
-\item Grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05};
-\item Mastermind and
-\item Random Blocks by Chavira et al. \cite{DBLP:journals/ijar/ChaviraDJ06};
-\item other binary Bayesian networks including Plan Recognition
-  \cite{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
-  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f};
-\item non-binary classic Bayesian networks: \texttt{alarm}, \texttt{diabetes},
-  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
-  \texttt{pathfinder}, \texttt{pigs}, and \texttt{water}.
+\item \Cref{tbl:performance} further shows that
+  $\textsf{DPMC}+\texttt{bklm16++}$ solves almost a hundred more instances than
+  any other combination, and is the fastest in \SI{69.1}{\percent} of them.
+\item TODO: now talk about \cref{fig:scatter}.
+\item We also record numbers of variables in each encoding before and after our
+  additional transformation.
+\item TODO: describe \cref{fig:box}.
+\item Indeed, the numbers of variables in \texttt{bklm16++} and \texttt{d02++}
+  encodings are equal for binary Bayesian networks (i.e., most of our data).
+  Nonetheless, \texttt{bklm16++} performs much faster than \texttt{d02++}.
 \end{itemize}
+% TODO: Describe the results. Make sure to answer all of the listed questions.
+% TODO: double check that the numbers in the table make sense.
 
@@
   \caption{Cumulative numbers of instances solved by each algorithm-encoding
-    pair over time.}
+    pair over time. The dotted line denotes the total number of instances used.}
   \label{fig:cumulative}
@@
   \centering
+  \begin{minipage}{0.49\textwidth}
+    \centering
     \input{box.tex}%
     \caption{Box plots of the numbers of variables in each encoding across all
-    benchmark instances before and after applying \cref{alg:transformation}.}
-  \label{fig:box}
-\end{figure} % TODO: maybe add sbk05 with just 'before'?
+      benchmark instances before and after applying \cref{alg:transformation}.
+      Outliers and the top parts of some whiskers are
+      omitted.}\label{fig:box}
+  \end{minipage}\hfill
+  \begin{minipage}{0.49\textwidth}
+    \centering
+    \captionof{table}{The numbers of instances (out of 1466) that each algorithm and
+      encoding combination solved faster than any other combination and in
+      total.}\label{tbl:performance}
+    \begin{tabular}{lrr}
+      \toprule
+      Combination & Fastest & Solved \\
+      \midrule
+      $\textsf{Ace} + \texttt{cd05}$ & 27 & 1247 \\
+      $\textsf{Ace} + \texttt{cd06}$ & 135 & 1340 \\
+      $\textsf{Ace} + \texttt{d02}$ & 56 & 1060 \\
+      $\textsf{DPMC} + \texttt{bklm16}$ & 241 & 1327 \\
+      $\textsf{DPMC} + \texttt{bklm16++}$ & \textbf{992} & \textbf{1435} \\
+      $\textsf{DPMC} + \texttt{cd05++}$ & \textcolor{gray}{0} & 867 \\
+      $\textsf{DPMC} + \texttt{cd06++}$ & \textcolor{gray}{0} & 932 \\
+      $\textsf{DPMC} + \texttt{d02}$ & 1 & 1267 \\
+      $\textsf{DPMC} + \texttt{d02++}$ & 7 & 1272 \\
+      $\textsf{DPMC} + \texttt{sbk05}$ & 31 & 1308 \\
+      $\textsf{c2d} + \texttt{bklm16}$ & \textcolor{gray}{0} & 997 \\
+      $\textsf{Cachet} + \texttt{sbk05}$ & 49 & 983 \\
+      \bottomrule
+    \end{tabular}
+  \end{minipage}
+\end{figure}
 
@@
   \end{itemize}
-\end{itemize}
-
-\paragraph{TODO}
-\begin{itemize}
+\item Future work: do other WMC encodings also have this variable partition
+  property?
 \item Do I need to formally consider extending a pseudo-Boolean function to a
   bigger domain?
-\item check if each condition is actually used. Maybe turn this into a paragraph
-  that gives an overview of the proof.
-\item condition 1 is necessary in both cases because we're ignoring the weights
-  of indicator variables (explicitly acknowledge this)
-\item add the \texttt{cd05}/\texttt{cd06} correctness theorem
 \end{itemize}

### 2021-02-28 tools/analyse_changes.R

@@ -7,6 +7,7 @@ library(maditr)
 
 changes <- read.csv("../results/changes.csv", header = FALSE)
 colnames(changes) <- c("instance", "encoding", "before_variables", "before_clauses", "after_variables", "after_clauses")
+changes$after_variables[changes$encoding == "sbk05"] <- NA
 
 changes$dataset <- "Non-binary"
 changes$dataset[grepl("DQMR", changes$instance, fixed = TRUE)] <- "DQMR"
@@ -70,13 +71,13 @@ scatter(changes.df, "before_variables_bklm16", "before_variables_sbk05")
 scatter(changes.df, "before_clauses_bklm16", "before_clauses_sbk05")
 
 # grouped box plots
-df2 <- melt(changes[changes$encoding != "sbk05",], id.vars = c("instance", "dataset", "encoding"), measure.vars = c("before_variables", "after_variables"))
+df2 <- melt(changes, id.vars = c("instance", "dataset", "encoding"), measure.vars = c("before_variables", "after_variables"))
 df2$variable <- ifelse(df2$variabl == "before_variables", "before", "after")
 df2$variable <- as.factor(df2$variable)
 df2$variable <- factor(df2$variable, levels = rev(levels(df2$variable)))
 df2$encoding <- paste0("\\texttt{", df2$encoding, "}")
 
-tikz(file = "../doc/paper3/box.tex", width = 4.8, height = 2)
+tikz(file = "../doc/paper3/box.tex", width = 2.4, height = 2)
 ggplot(df2, aes(encoding, value, fill = variable)) +
   geom_boxplot(outlier.shape = NA) +
   theme_light() +
@@ -84,8 +85,8 @@ ggplot(df2, aes(encoding, value, fill = variable)) +
   xlab("") +
   ylab("Variables") +
   labs(fill = "") +
-  coord_cartesian(ylim = quantile(df2$value, c(0, 0.8))) +
-  theme(legend.position = "right")
+  coord_cartesian(ylim = quantile(df2$value, c(0, 0.8), na.rm = TRUE)) +
+  theme(legend.position = "bottom", legend.margin=margin(t = -0.8, unit = 'cm'))
 dev.off()
 
 tikz(file = "../doc/paper3/variable_scatter.tex", width = 3.2, height = 2.9)

### 2021-03-01 doc/paper3/paper.tex
Writing about experiments

@@
 
-\section{Experimental Evaluation}
+\section{Experimental Evaluation (mostly done)}
 % TODO: what are the encodings compiled with?
@@
   transformation)?
-\item What proportion of variables is typically removed?
+\item What proportion of variables is typically eliminated?
 \item Do some encodings benefit from this transformation more than others?
@@
 
-\subsection{Setup (mostly done)}
+\subsection{Setup}
 
@@
 \subsection{Results}
-
-\paragraph{Notes.}
-\begin{itemize}
-\item \Cref{fig:cumulative} shows:
-  \begin{itemize}
-  \item $\textsf{DPMC}+\texttt{bklm16++}$ remains the best-performing
-    combination across all time limits up to \SI{1000}{\second} with $\textsf{Ace} +
-    \texttt{cd06}$ and $\textsf{DPMC}+\texttt{bklm16}$ not far behind;
-  \item $\textsf{DPMC}+\texttt{bklm16++}$ to be 3.35 times faster than
-    $\textsf{DPMC}+\texttt{bklm16}$ and 2.96 times faster than
-    $\textsf{Ace}+\texttt{cd06}$.
-  \end{itemize}
-\item \Cref{tbl:performance} further shows that
-  $\textsf{DPMC}+\texttt{bklm16++}$ solves almost a hundred more instances than
-  any other combination, and is the fastest in \SI{69.1}{\percent} of them.
-\item TODO: now talk about \cref{fig:scatter}.
-\item We also record numbers of variables in each encoding before and after our
-  additional transformation.
-\item TODO: describe \cref{fig:box}.
-\item Indeed, the numbers of variables in \texttt{bklm16++} and \texttt{d02++}
-  encodings are equal for binary Bayesian networks (i.e., most of our data).
-  Nonetheless, \texttt{bklm16++} performs much faster than \texttt{d02++}.
-\end{itemize}
-% TODO: Describe the results. Make sure to answer all of the listed questions.
-% TODO: double check that the numbers in the table make sense.
 
@@
 
+\Cref{fig:cumulative} shows $\textsf{DPMC}+\texttt{bklm16++}$ to be the
+best-performing combination across all time limits up to \SI{1000}{\second} with
+$\textsf{Ace} + \texttt{cd06}$ and $\textsf{DPMC}+\texttt{bklm16}$ not far
+behind. Overall, $\textsf{DPMC}+\texttt{bklm16++}$ is 3.35 times faster than
+$\textsf{DPMC}+\texttt{bklm16}$ and 2.96 times faster than
+$\textsf{Ace}+\texttt{cd06}$. \Cref{tbl:performance} further shows that
+$\textsf{DPMC}+\texttt{bklm16++}$ solves almost a hundred more instances than
+any other combination, and is the fastest in \SI{69.1}{\percent} of them.
+
+The scatter plots in \cref{fig:scatter} show that how $\textsf{DPMC} +
+\texttt{bklm16++}$ (and perhaps \textsf{DPMC} more generally) compares to
+$\textsf{Ace} + \texttt{cd06}$ depends significantly on the data set: the former
+is a clear winner on DQMR and Grid instances, while the latter performs well on
+Mastermind and Random Blocks. Perhaps because the underlying WMC algorithm
+remains the same, the difference between $\textsf{DPMC} + \texttt{bklm16}$ with
+and without applying \cref{alg:transformation} is quite noisy, i.e, with most
+instances scattered around the line of equality. However, our transformation
+does enable \textsf{DPMC} to solve many instances that were previously beyond
+its reach.
+
+We also record numbers of variables in each encoding before and after applying
+\cref{alg:transformation}. \Cref{fig:box} shows a significant reduction in the
+number of variables. For instance, the median number of variables in instances
+encoded with \texttt{bklm16} was reduced four times: from 1499 to 376. While
+\texttt{bklm16++} results in the overall lowest number of variables, the
+difference between \texttt{bklm16++} and \texttt{d02++} seems small. Indeed, the
+numbers of variables in these two encodings are equal for binary Bayesian
+networks (i.e., most of our data). Nonetheless, \texttt{bklm16++} is still much
+faster than \texttt{d02++} when run with \textsf{DPMC}.
+
+Overall, transforming WMC instances to the PBP format allows us to significantly
+simplify each instance. This transformation is particularly effective on
+\texttt{bklm16}, allowing it to surpass \texttt{cd06} and become the new state
+of the art. While there is a similarly significant reduction in the number of
+variables for \texttt{d02}, the performance of $\textsf{DPMC}+\texttt{d02}$ is
+virtually unaffected. Finally, while our transformation makes it possible to use
+\texttt{cd05} and \texttt{cd06} with \textsf{DPMC}, the two combinations remain
+inefficient.
+
 \section{Conclusions}

### 2021-03-01 tools/analyse_changes.R

@@ -106,3 +106,8 @@ df4$encoding[df4$variable == "after_variables"] <- paste(df4$encoding[df4$variab
 df <- data[data$novelty == "new",] %>% left_join(df4, by = c("instance", "encoding"))
 
 ggplot(df, aes(value, inference_time, col = dataset.y, shape = dataset.y)) + geom_point()
+
+# ========== Numerical ==========
+
+median(changes$before_variables[changes$encoding == "bklm16"])
+median(changes$after_variables[changes$encoding == "bklm16"])

### 2021-03-03 doc/paper3/paper.tex
Formulate the correctness theroem for MCWMC

@@
 
+\crefname{enumi}{Condition}{Conditions}
 \crefname{enumii}{Condition}{Conditions}
@@
 
-TODO: Mention that formulas, clauses, and models are all treated as sets.
+\paragraph{TODO}
+\begin{itemize}
+\item Explain two meanings of entailment in the definition of WMC.
+\end{itemize}
+
+Throughout the paper, we use set theoretic notation for many concepts in logic.
+We identify a model with a set of variables that correspond to the positive
+literals in the model (and all other variables are the negative literals of the
+model). A formula in CNF is a set of clauses that are part of an implicit
+conjunction. Similarly, a clause is a set of literals that are part of an
+implicit disjunction. For example, let $\phi = (\neg a \lor b) \land a$ be a
+propositional formula over variables $a$ and $b$. Then an equivalent
+set-theoretic representation of $\phi$ is $\{ \{ \neg a, b \}, \{ a \} \}$. Any
+subset of $\{ a, b \}$ is an interpretation of $\phi$, e.g., $\{ a, b \}$ is a
+model of $\phi$ (written $\{ a, b \} \models \phi$), while $\emptyset$ is an
+interpretation but not a model.
 
@@
   \SetKwProg{Fn}{Function}{:}{}
-  \KwData{WMC instance $(\phi, X_I, X_P, w)$}
+  \KwData{WMC (or minimum-cardinality WMC) instance $(\phi, X_I, X_P, w)$}
   \KwResult{PBP instance $(F, X, \omega)$}
@@
   of indicator variables (explicitly acknowledge this)
-\item add the \texttt{cd05}/\texttt{cd06} correctness theorem
 \end{itemize}
@@
 
-\begin{theorem}[Correctness] \label{thm:correctness}
+\begin{theorem}[Correctness for WMC] \label{thm:correctness}
   \Cref{alg:transformation}, when given a WMC instance $(\phi, X_I, X_P,
@@
   \begin{enumerate}
-  \item for all indicator variables $i \in X_I$, $w(i) = w(\neg i) = 1$,
+  \item for all indicator variables $i \in X_I$, $w(i) = w(\neg i) =
+    1$, \label{cond:one}
   \item and either
@@
       \item $w(p) + w(\neg p) = 1$,
-      \item for any clause $c \in \phi$, $|c \cap X_P| \le 1$,
-      \item there is no clause $c \in \phi$ such that $\neg p \in c$,
+      \item for any clause $c \in \phi$, $|c \cap X_P| \le 1$, \label{cond:2b2}
+      \item there is no clause $c \in \phi$ such that $\neg p \in
+        c$, \label{cond:2b3}
       \item if $\{ p \} \in \phi$, then there is no clause $c \in \phi$ such
@@
 
+\begin{theorem}[Correctness for Minimum-Cardinality WMC]
+  Let $(\phi, X_I, X_P, w)$ be a minimum-cardinality WMC instance that satisfies
+  \cref{cond:one,cond:2b2,cond:2b3,cond:just_parameter,cond:disjoint} of
+  \cref{thm:correctness} as well as the following:
+  \begin{enumerate}
+  \item for all parameter variables $p \in X_P$, $w(\neg p) = 1$.
+  \item all models of $\{ c \in \phi \mid c \cap X_P = \emptyset \}$ (as subsets
+    of $X_I$) have the same cardinality;
+  \item $\min_{Z \subseteq X_P} |Z|$ such that $Y \cup Z \models \phi$ is the
+    same for all $Y \models \{ c \in \phi \mid c \cap X_P = \emptyset \}$.
+  \end{enumerate}
+  Then \cref{alg:transformation}, when applied to $(\phi, X_I, X_P, w)$, outputs
+  a PBP instance with the same answer.
+\end{theorem}
+\begin{proof} % TODO: introduce the variables that come from the algorithm
+  We split the proof into two parts. Let
+  \[
+    F = \left\{ [c]_0^1 \mid c \in \phi \text{, } c \cap X_P = \emptyset
+    \right\} \cup \left\{ \left[ \bigwedge_{l \in c \setminus \{ p \}} \neg l
+      \right]_1^{w(p)} \;\middle|\; p \in X_P \text{, } p \in c \in \phi
+      \text{, } c \ne \{ p \} \right\}
+  \]
+  be as returned by \cref{alg:transformation}. In the first part, we show that
+  there is a bijection between minimum-cardinality models of $\phi$ and $Y
+  \subseteq X_I$ such that $\left(\prod_{f \in F} f\right)(Y) \ne 0$ (with the
+  assumption that $w(p) \ne 0$ for all $p \in X_P$).\footnote{The assumption is
+    only there to make the proof more convenient and can be omitted by
+    reformulating the proof in a slightly more cumbersome way.} Let $Y \subseteq
+  X_I$ and $Y' \subseteq X_I \cup X_P$ be related via this bijection. Then in
+  the second part we will show that
+  \[
+    \prod_{Y' \models l} w(l) = \left(\prod_{f \in F} f\right)(Y).
+  \]
+
+  On the one hand, if $Y \subseteq X_I \cup X_P$ is a minimum-cardinality model
+  of $\phi$, then
+  \[
+    \left(\prod_{f \in F}\right)(Y \cap X_I) \ne 0
+  \]
+  under the given assumptions. On the other hand, if $Y \subseteq X_I$ is such
+  that
+  \[
+    \left(\prod_{f \in F}\right)(Y) \ne 0,
+  \]
+  then $Y \models \{ c \in \phi \mid c \cap X_P = \emptyset \}$. Let $Y
+  \subseteq Z \subseteq X_I \cup X_P$ be the smallest superset of $Y$ such that
+  $Z \models \phi$ (it exists by \cref{cond:2b3} of \cref{thm:correctness}). We
+  need to show that $Z$ is minimum cardinality.
+\end{proof} % TODO: first part
+% TODO: make a separate definition for minimum cardinality model and use it in
+% the definition of MCWMC
+% TODO: use the MCWMC abbreviation
+% TODO: my current proof doesn't use omega. Maybe just say that the proof is
+% easily extendable to phi s.t. omega != 1 similarly to the proof of
+% thm:correctness.
+
 \section{Experimental Evaluation (mostly done)}
+% TODO: define cardinality of model
 % TODO: what are the encodings compiled with?

### 2021-03-04 doc/paper3/paper.tex
And more writing

--- 2021-03-01 doc/paper3/paper.tex
@@
 
-TODO: Mention that formulas, clauses, and models are all treated as sets.
+% TODO: Explain two meanings of entailment in the definition of WMC.
+
+Throughout the paper, we use set theoretic notation for many concepts in logic.
+A \emph{clause} is a set of literals that are part of an implicit disjunction.
+Similarly, a \emph{formula} in CNF is a set of clauses that are part of an
+implicit conjunction. We identify a \emph{model} with a set of variables that
+correspond to the positive literals in the model (and all other variables are
+the negative literals of the model). We can then define a model's
+\emph{cardinality} as the cardinality of this set. For example, let $\phi =
+(\neg a \lor b) \land a$ be a propositional formula over variables $a$ and $b$.
+Then an equivalent set-theoretic representation of $\phi$ is $\{ \{ \neg a, b
+\}, \{ a \} \}$. Any subset of $\{ a, b \}$ is an interpretation of $\phi$,
+e.g., $\{ a, b \}$ is a model of $\phi$ (written $\{ a, b \} \models \phi$) of
+cardinality two, while $\emptyset$ is an interpretation but not a model.
 
@@
 
+\begin{definition}
+  Let $\phi$ be a propositional formula over a set of variables $X$. Then $Y
+  \subseteq X$ is a \emph{minimum-cardinality model} of $\phi$ if $Y \models
+  \phi$ and $|Y| \le |Z|$ for all $Z \models \phi$.
+\end{definition}
+
 \begin{definition}[Minimum-Cardinality WMC]
@@
   but its answer is defined to be $\sum_{Y \models \phi\text{, }|Y| = k}
-  \prod_{Y \models l} w(l)$, where $k = \min_{Y \models \phi\text{, }Y \ne
-    \emptyset} |Y|$, if $k$ exists, otherwise the answer is zero.
+  \prod_{Y \models l} w(l)$ (where $k = \min_{Y \models \phi} |Y|$) if $\phi$ is
+  satisfiable, and zero otherwise.
 \end{definition}
@@
 
-% TODO: incorporate this somewhere
 %This additional condition on model
@@
 
-\section{Pseudo-Boolean Functions}
+\section{Pseudo-Boolean Functions} % TODO: start here
+% TODO: need more related literature
+% TODO: look at the addmc/background_reading dir
+
+\paragraph{References.} % extensions and applications
+\begin{itemize}
+\item ADDs \cite{DBLP:journals/fmsd/BaharFGHMPS97}
+\item AADDs \cite{DBLP:conf/ijcai/SannerM05}
+\item CUDD \cite{somenzi1998cudd}
+\item compiling BNs using VE \cite{DBLP:conf/ijcai/ChaviraD07}
+\item FOADDs \cite{DBLP:journals/ai/SannerB09}
+\item stochastic planning \cite{DBLP:conf/uai/HoeySHB99}
+\item XADDs \cite{DBLP:conf/uai/SannerDB11}
+\item another connection between BNs and ADDs \cite{DBLP:conf/icml/ZhaoMP15}
+\item and one more \cite{DBLP:conf/uai/GogateD11}
+\item maybe: \cite{DBLP:conf/aaai/FargierMNS14}
+\end{itemize}
 
@@
 
-\section{PBP as a Computational Problem}
+\section{Pseudo-Boolean Projection (mostly done)}
+
+We introduce a new type of computational problem called \emph{pseudo-Boolean
+  projection} based on two-valued pseudo-Boolean functions. While the same
+computational framework can handle any pseudo-Boolean functions, two-valued
+functions are particularly convenient because \textsf{DPMC} can be easily
+adapted to use them as input, and they are easily representable in both text
+files and using the syntax proposed in this paper.
 
@@
   A PBP instance is a tuple $(F, X, \omega)$, where $X$ is the set of variables,
-  $F$ is a set of pseudo-Boolean functions $2^X \to \mathbb{R}$, and $\omega \in
-  \mathbb{R}$ is the scaling factor.\footnote{We will further restrict $F$ to
-    only contain functions that have exactly two values. While this restriction
-    is not necessary from a computational point of view, such functions can be
-    conveniently represented both in text files and using the syntax proposed in
-    this paper.} The \emph{answer} of the instance is $\omega \cdot
-  \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
+  $F$ is a set of two-valued pseudo-Boolean functions $2^X \to \mathbb{R}$, and
+  $\omega \in \mathbb{R}$ is the scaling factor. The \emph{answer} of the
+  instance is $\omega \cdot \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
 \end{definition}
 
-\begin{remark}
-  Adding scaling factor $\omega$ to the definition allows us to remove
-  clauses that consist entirely of a single parameter variable. The idea of
-  extracting some of the structure of the WMC instance into an external
-  multiplicative factor originates in one of the Bayesian network encodings
-  \cite{DBLP:conf/ecai/BartKLM16}.
-\end{remark}
+Adding scaling factor $\omega$ to the definition allows us to remove clauses
+that consist entirely of a single parameter variable. The idea of extracting
+some of the structure of the WMC instance into an external multiplicative factor
+was inspired by the \texttt{bklm16} encoding.
 
 \subsection{From WMC to PBP}
-
-\paragraph{Notes.}
-\begin{itemize}
-\item The algorithm is based on several observations that will be made precise
-  in \cref{thm:correctness}. First, all weights except for $\{w(p) \mid p \in
-  X_P\}$ are redundant as they either duplicate an already-defined weight or are
-  equal to one. Second, each clause has at most one parameter variable. Third,
-  if the parameter variable is negated, we can ignore the clause (this idea
-  first appears in the \texttt{cd05} paper \cite{DBLP:conf/ijcai/ChaviraD05}).
-\item We formulate our algorithm as a sequel to the WMC encoding procedure
-  because the implementations of Bayesian network WMC encodings are all
-  closed-source. However, as all transformations in \cref{alg:transformation}
-  are local, the algorithm can be efficiently incorporated into a WMC encoding
-  algorithm with no noticeable slowdown.
-\item No obvious way to do this for \texttt{sbk05} because the roles of
-  indicator and parameter (i.e., `chance') variables overlap
-  \cite{DBLP:conf/aaai/SangBK05}.
-\item Benefits of having this proof in the paper:
-  \begin{itemize}
-  \item It puts all encodings on a common ground.
-  \item It illustrates the convenience of our notation for reasoning about
-    (certain types of) pseudo-Boolean functions.
-  \item It's too big and too important to be left for the appendix.
-  \end{itemize}
-\end{itemize}
-
-%\item The second \textbf{foreach} loop can be performed in constant time by
-%  representing $\phi'$ as a list and assuming that the two 'clauses' are
-%  adjacent in that list (and incorporating it into the first loop).
-%\item The $d$ map is constructed in $\mathcal{O}(|X_P|\log|X_P|)$ time (we want
-%  to use a data structure based on binary search trees rather than hashing).
-%\item \texttt{rename} can be implemented in $\mathcal{O}(\log |X_P|)$ time.
 
@@
   \SetKwProg{Fn}{Function}{:}{}
-  \KwData{WMC instance $(\phi, X_I, X_P, w)$}
-  \KwResult{PBP instance $(F, X, \omega)$}
+  \KwData{WMC (or minimum-cardinality WMC) instance $(\phi, X_I, X_P, w)$}
+  \KwResult{PBP instance $(F, X_I, \omega)$}
   $F \gets \emptyset$\;
   $\omega \gets 1$\;
-  let $d\colon X_P \to \mathbb{N}$ be defined as $p \mapsto |\{ o \in X_P \mid o
-  \le p \}|$\;
+%  let $d\colon X_P \to \mathbb{N}$ be defined as $p \mapsto |\{ o \in X_P \mid o
+%  \le p \}|$\;
   \ForEach{clause $c \in \phi$\label{line:foreach1start}}{
@@
   }
-  replace every variable $v$ in $F$ with $\rename{$v$}$\;
-  \Return{$(F, X_I, \omega)$}\;
-  \Fn{\rename{$v$}}{
-    $S \gets \{u \in X_P \mid u \le v\}$\;
-    \lIf{$S = \emptyset$}{\Return{$v$}}
-    \Return{$v - d(\max S)$}\;
-  }
+%  replace every variable $v$ in $F$ with $\rename{$v$}$\;
+%  \Return{$(F, X_I, \omega)$}\;
+%  \Fn{\rename{$v$}}{
+%    $S \gets \{u \in X_P \mid u \le v\}$\;
+%    \lIf{$S = \emptyset$}{\Return{$v$}}
+%    \Return{$v - d(\max S)$}\;
+%  }
 \end{algorithm}
 
-\subsection{Proof of Correctness}
+In this section we describe an algorithm for transforming WMC instances to the
+PBP format while removing all parameter variables. The algorithm works on four
+out of the five Bayesian network encodings. There is no obvious way to adjust it
+to work with \texttt{sbk05} because the roles of indicator and parameter (i.e.,
+`chance') variables overlap \cite{DBLP:conf/aaai/SangBK05}. The algorithm is
+based on several observations that will be made more precise in
+\cref{sec:proof}. First, all weights except for $\{w(p) \mid p \in X_P\}$ are
+redundant as they either duplicate an already-defined weight or are equal to
+one. Second, each clause has at most one parameter variable. Third, if the
+parameter variable is negated, we can ignore the clause (this idea first appears
+in the \texttt{cd05} paper \cite{DBLP:conf/ijcai/ChaviraD05}). Note that while
+we formulate our algorithm as a sequel to the WMC encoding procedure primarily
+because the implementations of Bayesian network WMC encodings are all
+closed-source, as all transformations in the algorithm are local, it can be
+efficiently incorporated into a WMC encoding algorithm with no slowdown.
 
-\paragraph{Notes.}
-\begin{itemize}
-\item This just says that $p$ is equivalent to a conjunction.
-\item The first group of conditions applies to \texttt{d02}, while the second
-  group applies to \texttt{bklm16}.
-\item For \texttt{cd05} and \texttt{cd06}, condition $2bi$ should be replaced
-  with $w(\neg p) = 1$.
-\end{itemize}
+The algorithm is listed as \cref{alg:transformation}. The main part of the
+algorithms is the first loop that iterates over clauses. If a clause consists of
+a single parameter variable, we incorporate it into $\omega$. If a clause is
+of the form $\alpha \Rightarrow p$, where $p \in X_P$ and $\alpha$ is a
+conjunction of literals over $X_I$, we transform it into a pseudo-Boolean
+function $[\alpha]_1^{w(p)}$. If a clause (say, $c \in \phi$) has no parameter
+variables, we reformulate it into a pseudo-Boolean function $[c]_0^1$. Finally,
+if a clause has negative parameter literals, we skip it.
 
-\paragraph{TODO}
-\begin{itemize}
-\item check if each condition is actually used. Maybe turn this into a paragraph
-  that gives an overview of the proof.
-\item condition 1 is necessary in both cases because we're ignoring the weights
-  of indicator variables (explicitly acknowledge this)
-\item add the \texttt{cd05}/\texttt{cd06} correctness theorem
-\end{itemize}
+As all `weighted' pseudo-Boolean functions produced by the first loop are of the
+form $[\alpha]_1^p$ (for some $p \in \mathbb{R}$ and formula $\alpha$), the
+second loop merges two functions into one whenever $\alpha$ is a literal. Note
+that taking into account the order in which clauses are typically generated by
+encoding algorithms allows us to do this in linear time (i.e., the two mergeable
+functions will be generated one after the other).
+
+%\item The second \textbf{foreach} loop can be performed in constant time by
+%  representing $\phi'$ as a list and assuming that the two 'clauses' are
+%  adjacent in that list (and incorporating it into the first loop).
+%\item The $d$ map is constructed in $\mathcal{O}(|X_P|\log|X_P|)$ time (we want
+%  to use a data structure based on binary search trees rather than hashing).
+%\item \texttt{rename} can be implemented in $\mathcal{O}(\log |X_P|)$ time.
+
+\subsection{Correctness Proofs} \label{sec:proof}
+
+In this section we outline key properties that a (WMC or minimum-cardinality
+WMC) encoding has to satisfy for \cref{alg:transformation} to output an
+equivalent PBP instance. We divide the correctness proof into two theorems:
+\cref{thm:correctness} for WMC encodings (i.e., \texttt{bklm16} and
+\texttt{d02}) and \cref{thm:mccorrectness} for minimum-cardinality WMC encodings
+(i.e., \texttt{cd05} and \texttt{cd06}). We begin by listing some properties of
+pseudo-Boolean functions and establishing a canonical transformation from WMC
+to PBP.
 
 \begin{theorem}[Early Projection
-  \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20},
-  verbatim] \label{thm:early}
-  Let $X$ and $Y$ be sets of variables. For all functions $f\colon 2^X \to
-  \mathbb{R}$ and $g\colon 2^Y \to \mathbb{R}$, if $x \in X \setminus Y$, then
-  $\exists_x (f \cdot g) = (\exists_x f) \cdot g$.
+  \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20}] \label{thm:early}
+  Let $X$ and $Y$ be sets of variables. For all pseudo-Boolean functions
+  $f\colon 2^X \to \mathbb{R}$ and $g\colon 2^Y \to \mathbb{R}$, if $x \in X
+  \setminus Y$, then $\exists_x (f \cdot g) = (\exists_x f) \cdot g$.
 \end{theorem}
@@
 
-% TODO: mention that this is similar (but not equal) to the DPMC/ADDMC result
 \begin{proposition} \label{prop:equivalence}
@@
     \item for all parameter variables $p \in X_P$, there is a non-empty family
-      of literals $(l_i)_{i=1}^n$ such that \label{condition:d02}
+      of literals $(l_i)_{i=1}^n$ such that \label{cond:d02}
       \begin{enumerate}
@@
       \end{enumerate}
-    \item or for all parameter variables $p \in X_P$, \label{condition:bklm16}
+    \item or for all parameter variables $p \in X_P$, \label{cond:bklm16}
       \begin{enumerate}
       \item $w(p) + w(\neg p) = 1$,
-      \item for any clause $c \in \phi$, $|c \cap X_P| \le 1$,
-      \item there is no clause $c \in \phi$ such that $\neg p \in c$,
+      \item for any clause $c \in \phi$, $|c \cap X_P| \le 1$, \label{cond:2b2}
+      \item there is no clause $c \in \phi$ such that $\neg p \in
+        c$, \label{cond:2b3}
       \item if $\{ p \} \in \phi$, then there is no clause $c \in \phi$ such
@@
 \end{theorem}
+
+\Cref{cond:one} applies to all four WMC encodings under consideration and
+ensures that only parameter variables carry nontrivial weights. \Cref{cond:d02}
+(for \texttt{d02}), while spelled out precisely in the theorem, simply states
+that each parameter variable is equivalent to a conjunction of indicator
+literals. \Cref{cond:bklm16} is for encodings that have implications rather than
+equivalences associated with parameter variables (which, in this case, is
+\texttt{bklm16}). It ensures that each clause has at most one positive
+parameter literal and no negative ones, and that at most one implication clause
+per any parameter variable $p \in X_P$ can `force $p$ to be positive'.
+
 \begin{proof}
@@
   \end{equation}
-  Since both \cref{condition:d02,condition:bklm16} ensure that each clause in
+  Since both \cref{cond:d02,cond:bklm16} ensure that each clause in
   $\phi$ has at most one parameter variable, we can partition $\phi$ into
@@
   \end{equation}
-  Note that under \cref{condition:d02},
+  Note that under \cref{cond:d02},
   \[
@@
   we get $\omega\prod_{f \in F_p} f = 1$, and so \cref{eq:to_show} is satisfied
-  under \cref{condition:d02} when $w(p) = 1$.
+  under \cref{cond:d02} when $w(p) = 1$.
 
@@
   This finishes the proof of the correctness of the first `foreach' loop under
-  \cref{condition:d02}.
+  \cref{cond:d02}.
 
-  Now let us assume \cref{condition:bklm16}. We still want to prove
+  Now let us assume \cref{cond:bklm16}. We still want to prove
   \cref{eq:to_show}. If $w(p) = 1$, then $F_p = \emptyset$, and $\omega = 1$,
@@
    first loop of \cref{alg:transformation} preserves the answer under both
-   \cref{condition:d02} and \cref{condition:bklm16}. Finally, the loop on
+   \cref{cond:d02} and \cref{cond:bklm16}. Finally, the loop on
    \crefrange{line:foreach2start}{line:foreach2end} of \cref{alg:transformation}
@@
    i.e., the answer is unchanged.
+\end{proof}
+
+\begin{theorem}[Minimum-Cardinality Correctness] \label{thm:mccorrectness}
+  Let $(\phi, X_I, X_P, w)$ be a minimum-cardinality WMC instance that satisfies
+  \cref{cond:one,cond:2b2,cond:2b3,cond:just_parameter,cond:disjoint} of
+  \cref{thm:correctness} as well as the following:
+  \begin{enumerate}
+  \item for all parameter variables $p \in X_P$, $w(\neg p) = 1$.
+  \item all models of $\{ c \in \phi \mid c \cap X_P = \emptyset \}$ (as subsets
+    of $X_I$) have the same cardinality; \label{cond:22}
+  \item $\min_{Z \subseteq X_P} |Z|$ such that $Y \cup Z \models \phi$ is the
+    same for all $Y \models \{ c \in \phi \mid c \cap X_P = \emptyset
+    \}$. \label{cond:23}
+  \end{enumerate}
+  Then \cref{alg:transformation}, when applied to $(\phi, X_I, X_P, w)$, outputs
+  a PBP instance with the same answer.
+\end{theorem}
+
+In this case, we have to add some assumptions about the cardinality of models.
+\Cref{cond:22} states that all models of the indicator-only part of the formula
+have the same cardinality. Bayesian network encodings such as \texttt{cd05} and
+\texttt{cd06} satisfy this condition by assigning an indicator variable to each
+possible variable-value pair and requiring each random variable to be paired
+with exactly one value. \Cref{cond:23} then says that the smallest number of
+parameter variables needed to turn an indicator-only model into a full model is
+the same for all indicator-only models. As some ideas duplicate between the
+proofs of \cref{thm:correctness,thm:mccorrectness}, the following proof is
+slightly less explicit and assumes that $\omega = 1$.
+
+% We assume that $\omega = 1$ (i.e., $\{ p \} \not\in \phi$ for all parameter
+% variables $p \in X_P$) as the proof can be easily extended to handle $\omega
+% \neq 1$ similarly to the proof of \cref{thm:correctness}.
+
+% TODO: check if each condition is actually used
+
+\begin{proof}
+  Let $(F, X_I, \omega)$ be the tuple returned by \cref{alg:transformation} and
+  note that
+  \[
+    F = \left\{ [c]_0^1 \mid c \in \phi \text{, } c \cap X_P = \emptyset
+    \right\} \cup \left\{ \left[ \bigwedge_{l \in c \setminus \{ p \}} \neg l
+      \right]_1^{w(p)} \;\middle|\; p \in X_P \text{, } p \in c \in \phi
+      \text{, } c \ne \{ p \} \right\}.
+  \]
+  We split the proof into two parts. In the first part, we show that there is a
+  bijection between minimum-cardinality models of $\phi$ and $Y \subseteq X_I$
+  such that $\left(\prod_{f \in F} f\right)(Y) \ne 0$ (with the assumption that
+  $w(p) \ne 0$ for all $p \in X_P$).\footnote{The assumption is only there to
+    make the proof more convenient and can be omitted by reformulating the proof
+    in a slightly more cumbersome way.} Let $Y \subseteq X_I$ and $Z \subseteq
+  X_I \cup X_P$ be related via this bijection. Then in the second part we will
+  show that
+  \begin{equation} \label{eq:weights}
+    \prod_{Z \models l} w(l) = \left(\prod_{f \in F} f\right)(Y).
+  \end{equation}
+
+  On the one hand, if $Z \subseteq X_I \cup X_P$ is a minimum-cardinality model
+  of $\phi$, then
+  \[
+    \left(\prod_{f \in F}\right)(Z \cap X_I) \ne 0
+  \]
+  under the given assumptions. On the other hand, if $Y \subseteq X_I$ is such
+  that
+  \[
+    \left(\prod_{f \in F}\right)(Y) \ne 0,
+  \]
+  then $Y \models \{ c \in \phi \mid c \cap X_P = \emptyset \}$. Let $Y
+  \subseteq Z \subseteq X_I \cup X_P$ be the smallest superset of $Y$ such that
+  $Z \models \phi$ (it exists by \cref{cond:2b3} of \cref{thm:correctness}). We
+  need to show that $Z$ has minimum cardinality. Let $Y'$ and $Z'$ be defined
+  equivalently to $Y$ and $Z$. We will show that $|Z| = |Z'|$. Note that $|Y| =
+  |Y'|$ by \cref{cond:22}, and $|Z \setminus Y| = |Z' \setminus Y'|$ by
+  \cref{cond:23}. Combining that with the general property that $|Z| = |Y| + |Z
+  \setminus Y|$ finishes the first part of the proof.
+
+  For the second part, let us consider the multiplicative influence of a single
+  parameter variable $p \in X_P$ on \cref{eq:weights}. If the left-hand side is
+  multiplied by $w(p)$ (i.e., $p \in Z$), then there must be some clause $c \in
+  \phi$ such that $Z \setminus \{ p \} \not\models c$. But then $Y \models
+  \bigwedge_{l \in c \setminus \{ p \}} \neg l$, and so the right-hand side is
+  multiplied by $w(p)$ as well (exactly once because of \cref{cond:disjoint} of
+  \cref{thm:correctness}). This argument works in the other direction as well.
 \end{proof}
@@
   bigger domain?
+\item Benefits of having this proof in the paper:
+  \begin{itemize}
+  \item It puts all encodings on a common ground.
+  \item It illustrates the convenience of our notation for reasoning about
+    (certain types of) pseudo-Boolean functions.
+  \item It's too big and too important to be left for the appendix.
+  \end{itemize}
 \end{itemize}

### 2021-03-05 doc/paper3/paper.tex
The core of the paper is in a decent shape

@@
 
-\paragraph{Related Work.}
+% NOTE: What is the problem? Why is it interesting and important?
+WMC has emerged as a powerful computational framework for problems in many
+domains, e.g., probabilistic graphical models such as Bayesian networks and
+Markov networks
+\cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05},
+neuro-symbolic artificial intelligence \cite{DBLP:conf/icml/XuZFLB18},
+probabilistic programs \cite{DBLP:journals/pacmpl/HoltzenBM20}, and
+probabilistic logic programs \cite{DBLP:journals/tplp/FierensBRSGTJR15}. It has
+been extended to support continuous variables \cite{DBLP:conf/ijcai/BellePB15},
+infinite domains \cite{DBLP:conf/aaai/Belle17}, first-order logic
+\cite{DBLP:journals/cacm/GogateD16,DBLP:conf/ijcai/BroeckTMDR11}, and arbitrary
+semirings \cite{DBLP:journals/ijar/BelleR20,DBLP:journals/japll/KimmigBR17}.
+
+% NOTE: What's wrong with previous proposed solutions? How does mine differ?
+% TODO: Our work is similar to \cite{DBLP:conf/uai/GogateD10} who suggest using
+% a collection of soft (i.e., with weights) and hard clauses
+% TODO: how different are the semantics?
+% But:
+% 1) we can handle arbitrary formulas and not just clauses
+% 2) we assign two weights, not one
+% 3) the semantics of these weights are completely different, similar to the
+% ones from Markov networks. It is thus difficult to reuse the same formulation
+% for a different WMC algorithm.
+% 4) Since we present a WMC->PBP algorithm, we don't need to invent new
+% encodings for each problem and we can benefit from all the good ideas that
+% went into designing WMC encodings
+
 Many WMC inference algorithms such as
@@
 
+% NOTE: What are the key components of my approach and results? Also include any
+% specific limitations. What about your project is new or different from
+% existing solutions?
 Our work is similar in that it introduces a new representation for computational
@@
 
+% NOTE: List of refutable contributions (with forward references to the rest of
+% the paper) What is the outcome of the project?
 \paragraph{Notes.}
@@
 \item and introduce a new notation
+\item TODO: briefly mention what a pseudo-Boolean function is
 \end{itemize}
@@
 
-% TODO: Explain two meanings of entailment in the definition of WMC.
-
-Throughout the paper, we use set theoretic notation for many concepts in logic.
-A \emph{clause} is a set of literals that are part of an implicit disjunction.
-Similarly, a \emph{formula} in CNF is a set of clauses that are part of an
-implicit conjunction. We identify a \emph{model} with a set of variables that
-correspond to the positive literals in the model (and all other variables are
-the negative literals of the model). We can then define a model's
-\emph{cardinality} as the cardinality of this set. For example, let $\phi =
-(\neg a \lor b) \land a$ be a propositional formula over variables $a$ and $b$.
-Then an equivalent set-theoretic representation of $\phi$ is $\{ \{ \neg a, b
-\}, \{ a \} \}$. Any subset of $\{ a, b \}$ is an interpretation of $\phi$,
-e.g., $\{ a, b \}$ is a model of $\phi$ (written $\{ a, b \} \models \phi$) of
-cardinality two, while $\emptyset$ is an interpretation but not a model.
+We begin with an overview of some notation and terminology. Throughout the
+paper, we use set theoretic notation for many concepts in logic. A \emph{clause}
+is a set of literals that are part of an implicit disjunction. Similarly, a
+\emph{formula} in CNF is a set of clauses that are part of an implicit
+conjunction. We identify a \emph{model} with a set of variables that correspond
+to the positive literals in the model (and all other variables are the negative
+literals of the model). We can then define the \emph{cardinality} of a model as
+the cardinality of this set. For example, let $\phi = (\neg a \lor b) \land a$
+be a propositional formula over variables $a$ and $b$. Then an equivalent
+set-theoretic representation of $\phi$ is $\{ \{ \neg a, b \}, \{ a \} \}$. Any
+subset of $\{ a, b \}$ is an interpretation of $\phi$, e.g., $\{ a, b \}$ is a
+model of $\phi$ (written $\{ a, b \} \models \phi$) of cardinality two, while
+$\emptyset$ is an interpretation but not a model. We can now formally define
+WMC.
 
@@
   A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
-  the set of indicator variables, $X_P$ is the set of parameter variables (with
-  $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula in CNF over
-  $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
-  X_P\} \to \mathbb{R}$ is the weight function. The \emph{answer} of the
-  instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
+  the set of \emph{indicator} variables, $X_P$ is the set of \emph{parameter}
+  variables (with $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula
+  in CNF over $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in
+  X_I \cup X_P\} \to \mathbb{R}$ is the weight function. The \emph{answer} of
+  the instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
 \end{definition}
 
+That is, the answer to a WMC instance is the sum of the weights of all models of
+$\phi$, where the weight of a model is defined as the product of the weights of
+all (positive and negative) literals in it. Our definition of WMC is largely
+based on the standard definition \cite{DBLP:journals/ai/ChaviraD08}, but
+explicitly partitions variables into indicator and parameter variables. In
+practice, we identify this partition in one of two ways. If an encoding is
+generated by \textsf{Ace}, then variable types are explicitly identified in the
+LMAP file generated alongside the encoding. Otherwise, we define a variable $x$
+to be a parameter variable if $w(x) = w(\neg x) = 1$. Next, we formally define a
+variation of the WMC problem used by some of the Bayesian network encodings
+\cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.
+
 \begin{definition}
-  Let $\phi$ be a propositional formula over a set of variables $X$. Then $Y
-  \subseteq X$ is a \emph{minimum-cardinality model} of $\phi$ if $Y \models
-  \phi$ and $|Y| \le |Z|$ for all $Z \models \phi$.
+  Let $\phi$ be a formula over a set of variables $X$. Then $Y \subseteq X$ is a
+  \emph{minimum-cardinality model} of $\phi$ if $Y \models \phi$ and $|Y| \le
+  |Z|$ for all $Z \models \phi$.
 \end{definition}
@@
 \begin{definition}[Minimum-Cardinality WMC]
-  A \emph{minimum-cardinality WMC} instance has same tuple as a WMC instance,
-  but its answer is defined to be $\sum_{Y \models \phi\text{, }|Y| = k}
-  \prod_{Y \models l} w(l)$ (where $k = \min_{Y \models \phi} |Y|$) if $\phi$ is
-  satisfiable, and zero otherwise.
+  A \emph{minimum-cardinality WMC} instance consists of the same tuple as a WMC
+  instance, but its answer is defined to be $\sum_{Y \models \phi\text{, }|Y| =
+    k} \prod_{Y \models l} w(l)$ (where $k = \min_{Y \models \phi} |Y|$) if
+  $\phi$ is satisfiable, and zero otherwise.
 \end{definition}
 
-Our definition of WMC is largely based on the standard definition
-\cite{DBLP:journals/ai/ChaviraD08}, but explicitly partitions variables into
-indicator and parameter variables. In practice, we identify this partition in
-one of two ways. If an encoding is generated by \textsf{Ace}, then variable
-types are explicitly identified in the LMAP file generated alongside the
-encoding. Otherwise, we define a variable $x$ to be a parameter variable if
-$w(x) = w(\neg x) = 1$.
-
-\subsection{Bayesian Network Encodings (mostly done)}
+\subsection{Bayesian Network Encodings}
 
@@
 
-\section{Pseudo-Boolean Functions} % TODO: start here
-% TODO: need more related literature
-% TODO: look at the addmc/background_reading dir
+\section{Pseudo-Boolean Functions}
 
-\paragraph{References.} % extensions and applications
-\begin{itemize}
-\item ADDs \cite{DBLP:journals/fmsd/BaharFGHMPS97}
-\item AADDs \cite{DBLP:conf/ijcai/SannerM05}
-\item CUDD \cite{somenzi1998cudd}
-\item compiling BNs using VE \cite{DBLP:conf/ijcai/ChaviraD07}
-\item FOADDs \cite{DBLP:journals/ai/SannerB09}
-\item stochastic planning \cite{DBLP:conf/uai/HoeySHB99}
-\item XADDs \cite{DBLP:conf/uai/SannerDB11}
-\item another connection between BNs and ADDs \cite{DBLP:conf/icml/ZhaoMP15}
-\item and one more \cite{DBLP:conf/uai/GogateD11}
-\item maybe: \cite{DBLP:conf/aaai/FargierMNS14}
-\end{itemize}
+In this work we propose a more expressive representation for WMC based on
+pseudo-Boolean functions. Pseudo-Boolean functions, most commonly represented as
+algebraic decision diagrams (ADDs) \cite{DBLP:journals/fmsd/BaharFGHMPS97}
+(although a tensor-based approach has also been suggested
+\cite{DBLP:journals/corr/abs-1908-04381,DBLP:conf/cp/DudekPV20}), have seen
+extensive use in value iteration for Markov decision processes
+\cite{DBLP:conf/uai/HoeySHB99}, both exact and approximate Bayesian network
+inference \cite{DBLP:conf/ijcai/ChaviraD07,DBLP:conf/uai/GogateD11}, and
+sum-product network \cite{DBLP:conf/uai/PoonD11} to Bayesian network conversion
+\cite{DBLP:conf/icml/ZhaoMP15}. ADDs have been extended to compactly represent
+additive and multiplicative structure \cite{DBLP:conf/ijcai/SannerM05},
+sentences in first-order logic \cite{DBLP:journals/ai/SannerB09}, and continuous
+variables \cite{DBLP:conf/uai/SannerDB11}, the last of which was also applied to
+weighted model integration, i.e., the WMC extension for continuous variables
+\cite{DBLP:conf/ijcai/BellePB15,DBLP:conf/ijcai/KolbMSBK18}.
 
-\paragraph{Notation.} For any propositional formula $\phi$ over a set of
+Since two-valued pseudo-Boolean functions will be used extensively henceforth,
+we introduce some notation. For any propositional formula $\phi$ over a set of
 variables $X$ and $p, q \in \mathbb{R}$, let $[\phi]^p_q\colon 2^X \to
@@
 \]
-for any $Y \subseteq X$.
+for any $Y \subseteq X$. Next, we define some useful operations on
+pseudo-Boolean functions.
+% TODO: mention where the operations are from
+% TODO: should I consider different domains?
+% TODO: can I say that a domain automatically shrinks (w.r.t. x) if f|x=0 =
+% f|x=1?
 
@@
   Note that this means that binary operations on pseudo-Boolean functions
-  inherit properties such as associativity and commutativity. By not
-  distinguishing between a real number and a pseudo-Boolean function that always
-  returns that number, we can use the same definitions to define \emph{scalar}
-  operations as
+  inherit properties such as associativity and commutativity. By regarding a
+  real number as a constant pseudo-Boolean function, we can reuse the same
+  definitions to define \emph{scalar} operations as
   \[
@@
 
-Below we list some properties of the operations on pseudo-Boolean functions
-discussed in this section that can be conveniently represented using our syntax.
-The proofs of all these properties follow directly from the definitions.
+Finally, below we list some properties of the operations on pseudo-Boolean
+functions discussed in this section that can be conveniently represented using
+our syntax. The proofs of all these properties follow directly from the
+definitions.
 
@@
 
-\section{Pseudo-Boolean Projection (mostly done)}
+\section{Pseudo-Boolean Projection}
 
@@
   }
-  \ForEach{indicator variable $v \in X_I$ \label{line:foreach2start}}{
-    \If{$\{[v]_1^p, [\neg v]_1^q\} \subseteq F$ for some $p$ and $q$}{
+  \ForEach{$v \in X_I$ such that $\{[v]_1^p, [\neg v]_1^q\}
+    \subseteq F$ for some $p$ and $q$ \label{line:foreach2start}}{
     $F \gets F \setminus \{ [v]_1^p, [\neg v]_1^q \} \cup \{ [v]_q^p
     \}$\; \label{line:foreach2end}
-    }
   }
@@
 \begin{lemma} \label{lemma:sum}
-  For any pseudo-Boolean function $f\colon 2^X \to \mathbb{R}$,
-  \[
-    (\exists_X f)(\emptyset) = \sum_{Y \subseteq X} f(Y).
-  \]
+  For any pseudo-Boolean function $f\colon 2^X \to \mathbb{R}$, we have that
+  $(\exists_X f)(\emptyset) = \sum_{Y \subseteq X} f(Y)$.
 \end{lemma}
@@
   \]
-  which means that
-  \[
-    \sum_{Y \subseteq X_I \cup X_P} f(Y)g(Y) = \sum_{Y \models \phi} \prod_{Y
-      \models l} w(l)
-  \]
-  as required.
+  which means that $\sum_{Y \subseteq X_I \cup X_P} f(Y)g(Y) = \sum_{Y \models
+    \phi} \prod_{Y \models l} w(l)$ as required.
 \end{proof}
@@
   is a PBP instance with the same answer as the given WMC instance. By
-  \cref{def:new_wmc}, its answer is
-  \begin{equation} \label{eq:answer}
-    \left(\exists_{X_I \cup X_P} \left( \prod_{c \in \phi} [c]_0^1 \right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg x)}^{w(x)} \right)(\emptyset)
-  \end{equation}
-  Since both \cref{cond:d02,cond:bklm16} ensure that each clause in
-  $\phi$ has at most one parameter variable, we can partition $\phi$ into
-  $\phi_* \coloneqq \{c \in \phi \mid \mathtt{Vars}(c) \cap X_P = \emptyset \}$
-  and $\phi_p \coloneqq \{ c \in \phi \mid \mathtt{Vars}(c) \cap X_P = \{ p \}
-  \}$ for all $p \in X_P$. We can then use \cref{thm:early} to reorder
-  \eqref{eq:answer} into
-  \[
-    \left(\exists_{X_I} \left( \prod_{x \in X_I} [x]_{w(\neg x)}^{w(x)} \right)
-      \left( \prod_{c \in \phi_*} [c]_0^1 \right) \prod_{p \in X_P} \exists_p
-      [p]_{w(\neg p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 \right)(\emptyset).
-  \]
+  \cref{def:new_wmc}, its answer is $\left(\exists_{X_I \cup X_P} \left(\prod_{c
+        \in \phi} [c]_0^1 \right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg
+      x)}^{w(x)} \right)(\emptyset)$. Since both \cref{cond:d02,cond:bklm16}
+  ensure that each clause in $\phi$ has at most one parameter variable, we can
+  partition $\phi$ into $\phi_* \coloneqq \{c \in \phi \mid \mathtt{Vars}(c)
+  \cap X_P = \emptyset \}$ and $\phi_p \coloneqq \{ c \in \phi \mid
+  \mathtt{Vars}(c) \cap X_P = \{ p \} \}$ for all $p \in X_P$. We can then use
+  \cref{thm:early} to reorder the answer into $\left(\exists_{X_I} \left(
+      \prod_{x \in X_I} [x]_{w(\neg x)}^{w(x)} \right) \left( \prod_{c \in
+        \phi_*} [c]_0^1 \right) \prod_{p \in X_P} \exists_p [p]_{w(\neg
+      p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 \right)(\emptyset)$.
 
@@
   \]
-  and $\omega = 1$, and so we want to show that
-  \[
-    \left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} = \exists_p [p]_1^{w(p)}
-    \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1,
-  \]
-  and indeed
+  and $\omega = 1$, and so we want to show that $\left[ \bigwedge_{i = 1}^n l_i
+  \right]_1^{w(p)} = \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow
+    \bigwedge_{i=1}^n l_i \right]_0^1$, and indeed
   \[
@@
   The only remaining case is when $w(p) \ne 1$ and $\{ p \} \not \in \phi_p$.
-  Then $\omega = 1$, and
-  \[
-    F_p = \left\{ \left[\bigwedge_{l \in c \setminus \{ p \}} \neg
-        l\right]_1^{w(p)} \;\middle|\; c \in \phi_p \right\},
-  \]
-  so need to show that
+  Then $\omega = 1$, and $F_p = \left\{ \left[\bigwedge_{l \in c \setminus \{ p
+        \}} \neg l\right]_1^{w(p)} \;\middle|\; c \in \phi_p \right\}$, so we
+  need to show that
   \[
@@
    replaces $[v]_1^p[\neg v]_1^q$ with $[v]_q^p$ (for some $v \in X_I$ and $p, q
-   \in \mathbb{R}$), but, of course,
-   \[
-     [v]_1^p[\neg v]_1^q = [v]_1^p[v]_q^1 = [v]_q^p,
-   \]
-   i.e., the answer is unchanged.
+   \in \mathbb{R}$), but, of course, $[v]_1^p[\neg v]_1^q = [v]_1^p[v]_q^1 =
+   [v]_q^p$, i.e., the answer is unchanged.
 \end{proof}
@@
   On the one hand, if $Z \subseteq X_I \cup X_P$ is a minimum-cardinality model
-  of $\phi$, then
-  \[
-    \left(\prod_{f \in F}\right)(Z \cap X_I) \ne 0
-  \]
-  under the given assumptions. On the other hand, if $Y \subseteq X_I$ is such
-  that
-  \[
-    \left(\prod_{f \in F}\right)(Y) \ne 0,
-  \]
-  then $Y \models \{ c \in \phi \mid c \cap X_P = \emptyset \}$. Let $Y
-  \subseteq Z \subseteq X_I \cup X_P$ be the smallest superset of $Y$ such that
-  $Z \models \phi$ (it exists by \cref{cond:2b3} of \cref{thm:correctness}). We
-  need to show that $Z$ has minimum cardinality. Let $Y'$ and $Z'$ be defined
-  equivalently to $Y$ and $Z$. We will show that $|Z| = |Z'|$. Note that $|Y| =
-  |Y'|$ by \cref{cond:22}, and $|Z \setminus Y| = |Z' \setminus Y'|$ by
-  \cref{cond:23}. Combining that with the general property that $|Z| = |Y| + |Z
-  \setminus Y|$ finishes the first part of the proof.
+  of $\phi$, then $\left(\prod_{f \in F}\right)(Z \cap X_I) \ne 0$ under the
+  given assumptions. On the other hand, if $Y \subseteq X_I$ is such that
+  $\left(\prod_{f \in F}\right)(Y) \ne 0$, then $Y \models \{ c \in \phi \mid c
+  \cap X_P = \emptyset \}$. Let $Y \subseteq Z \subseteq X_I \cup X_P$ be the
+  smallest superset of $Y$ such that $Z \models \phi$ (it exists by
+  \cref{cond:2b3} of \cref{thm:correctness}). We need to show that $Z$ has
+  minimum cardinality. Let $Y'$ and $Z'$ be defined equivalently to $Y$ and $Z$.
+  We will show that $|Z| = |Z'|$. Note that $|Y| = |Y'|$ by \cref{cond:22}, and
+  $|Z \setminus Y| = |Z' \setminus Y'|$ by \cref{cond:23}. Combining that with
+  the general property that $|Z| = |Y| + |Z \setminus Y|$ finishes the first
+  part of the proof.
 
@@
 
-\section{Experimental Evaluation (mostly done)}
+\section{Experimental Evaluation}
 % TODO: what are the encodings compiled with?
@@
 
-\textsf{DPMC} is run with tree decomposition based planning and algebraic
-decision diagram based execution---the best-performing combination in the
-original set of experiments \cite{DBLP:conf/cp/DudekPV20}. We use a single
-iteration of \textsf{htd} \cite{DBLP:conf/cpaior/AbseherMW17} to generate
-approximately optimal tree decompositions---we found that this configuration
-is efficient enough to handle huge instances, and yet the width of the
-returned decomposition is unlikely to differ from optimal by more than one or
-two. We also enabled \textsf{DPMC}'s greedy mode. This mode (which was not part
-of the original paper \cite{DBLP:conf/cp/DudekPV20}) optimises the order in
-which pseudo-Boolean functions are multiplied by prioritising functions with
-small representations.
+\textsf{DPMC} is run with tree decomposition based planning and ADD based
+execution---the best-performing combination in the original set of experiments
+\cite{DBLP:conf/cp/DudekPV20}. We use a single iteration of \textsf{htd}
+\cite{DBLP:conf/cpaior/AbseherMW17} to generate approximately optimal tree
+decompositions---we found that this configuration is efficient enough to handle
+huge instances, and yet the width of the returned decomposition is unlikely to
+differ from optimal by more than one or two. We also enabled \textsf{DPMC}'s
+greedy mode. This mode (which was not part of the original paper
+\cite{DBLP:conf/cp/DudekPV20}) optimises the order in which pseudo-Boolean
+functions are multiplied by prioritising functions with small representations.
 

### 2021-03-07 doc/paper3/paper.tex
Introduction and conclusion

@@
 
-\begin{abstract}
+\begin{abstract} % TODO: write
   The abstract should briefly summarize the contents of the paper in
@@
 \section{Introduction}
-
 % TODO for later:
@@
 % NOTE: What is the problem? Why is it interesting and important?
-WMC has emerged as a powerful computational framework for problems in many
-domains, e.g., probabilistic graphical models such as Bayesian networks and
-Markov networks
+Weighted model counting (WMC), i.e., a generalisation of propositional model
+counting that assigns weights to literals and computes the total weight of all
+models of a propositional formula \cite{DBLP:journals/ai/ChaviraD08}, has
+emerged as a powerful computational framework for problems in many domains,
+e.g., probabilistic graphical models such as Bayesian networks and Markov
+networks
 \cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05},
@@
 semirings \cite{DBLP:journals/ijar/BelleR20,DBLP:journals/japll/KimmigBR17}.
+However, as the definition of WMC puts weights on literals, additional variables
+often need to be added for the sole purpose of holding a weight
+\cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05}.
+As the parameterised complexity of model counting (and, by extension, WMC)
+depends on the number of variables
+\cite{DBLP:conf/focs/BacchusDP03,DBLP:journals/jda/SamerS10}, this can make WMC
+unnecessarily slow and could be detrimental to WMC algorithms such as
+\textsf{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} that depend on variable ordering
+heuristics.
 
 % NOTE: What's wrong with previous proposed solutions? How does mine differ?
-% TODO: Our work is similar to \cite{DBLP:conf/uai/GogateD10} who suggest using
-% a collection of soft (i.e., with weights) and hard clauses
-% TODO: how different are the semantics?
-% But:
-% 1) we can handle arbitrary formulas and not just clauses
-% 2) we assign two weights, not one
-% 3) the semantics of these weights are completely different, similar to the
-% ones from Markov networks. It is thus difficult to reuse the same formulation
-% for a different WMC algorithm.
-% 4) Since we present a WMC->PBP algorithm, we don't need to invent new
-% encodings for each problem and we can benefit from all the good ideas that
-% went into designing WMC encodings
-
-Many WMC inference algorithms such as
+One approach to this problem considers weighted clauses and probabilistic
+semantics based on Markov networks \cite{DBLP:conf/uai/GogateD10}. However, with
+a new representation comes the need to invent new encodings and inference
+algorithms. Our work is similar in that it introduces a new representation for
+computational problems but is able to reuse recent WMC algorithms based on
+pseudo-Boolean function manipulation, namely, \textsf{ADDMC}
+\cite{DBLP:conf/aaai/DudekPV20} and \textsf{DPMC} \cite{DBLP:conf/cp/DudekPV20}.
+Furthermore, we identify necessary conditions for transforming a WMC instance
+into the new format. As many WMC inference algorithms such as
 \textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}}, \textsf{c2d}
@@
 \cite{DBLP:journals/jancl/Darwiche01}, and sentential decision diagrams (SDDs)
-\cite{DBLP:conf/ijcai/Darwiche11}. Some attempts have previously been made to
-skip this intermediate stage of representing a Bayesian network as a WMC
-instance and compile directly to a more convenient representation.
-Specifically, direct compilation from Bayesian networks to SDDs
-\cite{DBLP:conf/ecsqaru/ChoiKD13} and from structured Bayesian networks (i.e., a
-generalisation of Bayesian networks) to probabilistic SDDs
-\cite{shen2020modeling} have been considered. To the best of the authors'
-knowledge, neither compilation approach has a publicly available implementation.
+\cite{DBLP:conf/ijcai/Darwiche11}, another way to avoid parameter variables
+could be via direct compilation to a more convenient representation. However,
+while direct compilation of Bayesian networks to SDDs has been investigated
+\cite{DBLP:conf/ecsqaru/ChoiKD13}, SDDs are not expressive enough to avoid the
+issue.
 
@@
 % specific limitations. What about your project is new or different from
-% existing solutions?
-Our work is similar in that it introduces a new representation for computational
-problems that is based on pseudo-Boolean functions---pseudo-Boolean projection
-(PBP). We formally show that every WMC problem instance has a corresponding PBP
-instance. We argue that this new format is more appropriate for WMC solvers
-whose execution is build on pseudo-Boolean function manipulation, i.e.,
-\textsf{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} and \textsf{DPMC}
-\cite{DBLP:conf/cp/DudekPV20}. Finally, we show how most methods of encoding
-probabilistic inference on Bayesian networks to WMC can be adapted to the PBP
-format. This transformation significantly improves inference speed,
-outperforming all other considered algorithm-encoding combinations.
+% existing solutions? List of refutable contributions (with forward references
+% to the rest of the paper) What is the outcome of the project?
+In this work, we introduce a way to transform WMC problems to a new format based
+on pseudo-Boolean functions---\emph{pseudo-Boolean projection} (PBP). We
+formally show that every WMC problem instance has a corresponding PBP instance
+and identify conditions under which this transformation can remove parameter
+variables. Four out of the five known WMC encodings for Bayesian networks
+\cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05}
+can indeed be simplified in this manner. This transformation enables two
+encodings that were previously incompatible with most WMC algorithms (due to
+using a different definition of WMC
+\cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}) to be run with
+\textsf{ADDMC} and \textsf{DPMC} and results in a significant performance boost
+for one other encoding, allowing it to surpass the current state of the art.
+Finally, our theoretical contributions result in a convenient algebraic way of
+reasoning about two-valued pseudo-Boolean functions and position WMC encodings
+on a common ground, identifying their key properties and assumptions.
 
-%allowing two encodings that were previously incompatible with
-%\textsf{DPMC} to be compatible.
+%To the best of the authors' knowledge, none of these compilation/inference
+%techniques have a publicly available implementation.
 
-% NOTE: List of refutable contributions (with forward references to the rest of
-% the paper) What is the outcome of the project?
-\paragraph{Notes.}
-\begin{itemize}
-\item we also show correctness
-\item and introduce a new notation
-\item TODO: briefly mention what a pseudo-Boolean function is
-\end{itemize}
+% Specifically, direct compilation
+% from Bayesian networks to SDDs \cite{DBLP:conf/ecsqaru/ChoiKD13} and from
+% structured Bayesian networks (i.e., a generalisation of Bayesian networks) to
+% probabilistic SDDs \cite{shen2020modeling} have been considered.
+
+% * SDD compilation still has parameter variables
+% 1) However, no conversion algorithms from either WMC or probabilistic models
+% are provided.
+% Since we present a WMC to PBP algorithm, we don't need to invent new
+% encodings for each problem and we can benefit from all the good ideas that
+% went into designing WMC encodings
+% 3) Instead of combining techniques from older WMC algorithms like they did, we
+% use a much more recent WMC solver that is shown to...
+% 3) We benefit from a decade of research in WMC inference and, specifically, 
+% 4) We are not restricted to clauses and probabilistic semantics
+% 5) We identify conditions and describe an algorithm for transforming any WMC
+% instance into PBP
 
@@
 \section{Pseudo-Boolean Functions}
+
+% TODO: briefly mention what a pseudo-Boolean function is
+% TODO: mention that $2^x$ denotes the powerset of $X$.
 
@@
 slightly less explicit and assumes that $\omega = 1$.
-
 % We assume that $\omega = 1$ (i.e., $\{ p \} \not\in \phi$ for all parameter
@@
 % \neq 1$ similarly to the proof of \cref{thm:correctness}.
-
-% TODO: check if each condition is actually used
 
@@
 inefficient.
+% TODO: mention (somewhere) that we can't compare to Gogate's work and direct
+% compilation (take the text from the introduction)
 
-\section{Conclusions}
+\section{Conclusion} % So what?
 
-\paragraph{Notes.}
-\begin{itemize}
-\item Benefits of my approach:
-  \begin{itemize}
-  \item smaller primal graph, so easier to perform tree decomposition
-  \item Variable order is less likely to be obstructed by all the unnecessary
-    'parameter' variables.
-  \item There are others, but they're not that important.
-  \end{itemize}
-\item Future work: do other WMC encodings also have this variable partition
-  property?
-\item Do I need to formally consider extending a pseudo-Boolean function to a
-  bigger domain?
-\item Benefits of having this proof in the paper:
-  \begin{itemize}
-  \item It puts all encodings on a common ground.
-  \item It illustrates the convenience of our notation for reasoning about
-    (certain types of) pseudo-Boolean functions.
-  \item It's too big and too important to be left for the appendix.
-  \end{itemize}
-\end{itemize}
+In this paper, we showed how the number of variables in a WMC instance can be
+significantly reduced by transforming it into a representation based on
+two-valued pseudo-Boolean functions. In some cases, this led to significant
+improvements in inference speed, allowing $\textsf{DPMC} + \texttt{bklm16++}$ to
+overtake $\textsf{Ace}+\texttt{cd06}$ as the new state of the art WMC technique
+for Bayesian network inference. Moreover, we identified key properties of
+Bayesian network encodings that allow for parameter variable removal. However,
+these properties were rather different for each encoding, and so an interesting
+question for future work is whether they can be unified into a more abstract
+and coherent list of conditions.
+
+Bayesian network inference was chosen as the example application of WMC because
+it is the first and the most studied one
+\cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05}.
+While the distinction between indicator and parameter variables is often not
+explicitly described in other WMC encodings
+\cite{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/pacmpl/HoltzenBM20,DBLP:conf/icml/XuZFLB18},
+perhaps in some cases variables could still be partitioned in this way, allowing
+for not just faster inference with \textsf{DPMC} or \textsf{ADDMC} but also for
+well-established WMC encoding and inference techniques (such as in the
+\texttt{cd05} and \texttt{cd06} papers
+\cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}) to be transferred to
+other application domains.
 

### 2021-03-08 doc/paper3/paper.tex
First draft ready

@@
 
-\begin{abstract} % TODO: write
-  The abstract should briefly summarize the contents of the paper in
-  150--250 words.
+% The abstract should briefly summarize the contents of the paper in
+% 150--250 words.
+% 1. Introduction. In one sentence, what’s the topic?
+% 2. State the problem you tackle.
+% 3. Summarize (in one sentence) why nobody else has adequately answered the research question yet.
+% 4. Explain, in one sentence, how you tackled the research question.
+% 5. In one sentence, how did you go about doing the research that follows from your big idea.
+% 6. As a single sentence, what’s the key impact of your research?
+\begin{abstract}
+  Weighted model counting (WMC) is a powerful computational technique for a
+  variety of problems, especially commonly used for probabilistic inference.
+  However, the standard definition of WMC that puts weights on literals often
+  necessitates WMC encodings to include additional variables and clauses just so
+  each weight can be attached to a literal. This paper complements previous work
+  by considering WMC instances in their full generality and using recent
+  state-of-the-art WMC techniques based on pseudo-Boolean function manipulation,
+  competitive with the more traditional WMC algorithms based on knowledge
+  compilation and backtracking search. We present an algorithm that transforms
+  WMC instances into a format based on pseudo-Boolean functions while
+  eliminating around \SI{57}{\percent} of variables on average across various
+  Bayesian network encodings. Moreover, we identify sufficient conditions for
+  such a variable removal to be possible. Our experiments show significant
+  improvement in WMC-based Bayesian network inference, outperforming the current
+  state of the art.
 
-  \keywords{First keyword  \and Second keyword \and Another keyword.}
+  \keywords{Weighted model counting \and Probabilistic inference \and Bayesian
+    networks.}
 \end{abstract}
@@
 \section{Introduction}
-% TODO for later:
-% 1) read through v2 of the paper and check if I forgot to mention something
-% here
-% 2) run this through grammarly
 
@@
 algorithms. Our work is similar in that it introduces a new representation for
-computational problems but is able to reuse recent WMC algorithms based on
+computational problems but can reuse recent WMC algorithms based on
 pseudo-Boolean function manipulation, namely, \textsf{ADDMC}
 \cite{DBLP:conf/aaai/DudekPV20} and \textsf{DPMC} \cite{DBLP:conf/cp/DudekPV20}.
-Furthermore, we identify necessary conditions for transforming a WMC instance
-into the new format. As many WMC inference algorithms such as
+Furthermore, we identify sufficient conditions for transforming a WMC instance
+into our new format. As many WMC inference algorithms such as
 \textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}}, \textsf{c2d}
@@
 \cite{DBLP:conf/ecsqaru/ChoiKD13}, SDDs are not expressive enough to avoid the
-issue.
+issue. Furthermore, to the best of the authors' knowledge, neither
+compilation/inference technique has a publicly available implementation.
 
@@
 % to the rest of the paper) What is the outcome of the project?
-In this work, we introduce a way to transform WMC problems to a new format based
-on pseudo-Boolean functions---\emph{pseudo-Boolean projection} (PBP). We
+In this work, we introduce a way to transform WMC problems into a new format
+based on pseudo-Boolean functions---\emph{pseudo-Boolean projection} (PBP). We
 formally show that every WMC problem instance has a corresponding PBP instance
@@
 reasoning about two-valued pseudo-Boolean functions and position WMC encodings
-on a common ground, identifying their key properties and assumptions.
-
-%To the best of the authors' knowledge, none of these compilation/inference
-%techniques have a publicly available implementation.
+on common ground, identifying their key properties and assumptions.
 
@@
 We begin with an overview of some notation and terminology. Throughout the
-paper, we use set theoretic notation for many concepts in logic. A \emph{clause}
+paper, we use set-theoretic notation for many concepts in logic. A \emph{clause}
 is a set of literals that are part of an implicit disjunction. Similarly, a
@@
   in CNF over $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in
-  X_I \cup X_P\} \to \mathbb{R}$ is the weight function. The \emph{answer} of
-  the instance is $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
+  X_I \cup X_P\} \to \mathbb{R}$ is the weight function. Its \emph{answer} is
+  $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
 \end{definition}
@@
 \cite{DBLP:conf/kr/Darwiche02}. Many ways of encoding a Bayesian network into a
-WMC instance have been proposed. We will refer to them based on initials of the
-authors and the year of publication. Darwiche was the first to suggest the
+WMC instance have been proposed. We will refer to them based on the initials of
+the authors and the year of publication. Darwiche was the first to suggest the
 \texttt{d02} \cite{DBLP:conf/kr/Darwiche02} encoding that, in many ways, remains
@@
 
-% TODO: briefly mention what a pseudo-Boolean function is
-% TODO: mention that $2^x$ denotes the powerset of $X$.
+In this work, we propose a more expressive representation for WMC based on
+pseudo-Boolean functions. A \emph{pseudo-Boolean function} is a function of the
+form $\{ 0, 1 \}^n \to \mathbb{R}$ \cite{DBLP:journals/dam/BorosH02}.
+Equivalently, let $X$ denote a set with $n$ elements (we will refer to them as
+\emph{variables}), and $2^X$ denote its powerset. Then a pseudo-Boolean function
+can have $2^X$ as its domain (then it is also known as a \emph{set function}).
 
-In this work we propose a more expressive representation for WMC based on
-pseudo-Boolean functions. Pseudo-Boolean functions, most commonly represented as
+Pseudo-Boolean functions, most commonly represented as
 algebraic decision diagrams (ADDs) \cite{DBLP:journals/fmsd/BaharFGHMPS97}
@@
 Since two-valued pseudo-Boolean functions will be used extensively henceforth,
-we introduce some notation. For any propositional formula $\phi$ over a set of
-variables $X$ and $p, q \in \mathbb{R}$, let $[\phi]^p_q\colon 2^X \to
-\mathbb{R}$ be a pseudo-Boolean function defined as
+we introduce some new notation. For any propositional formula $\phi$ over $X$
+and $p, q \in \mathbb{R}$, let $[\phi]^p_q\colon 2^X \to \mathbb{R}$ be the
+pseudo-Boolean function defined as
 \[
@@
 for any $Y \subseteq X$. Next, we define some useful operations on
-pseudo-Boolean functions.
-% TODO: mention where the operations are from
-% TODO: should I consider different domains?
-% TODO: can I say that a domain automatically shrinks (w.r.t. x) if f|x=0 =
-% f|x=1?
+pseudo-Boolean functions. The definitions of multiplication and projection are
+equivalent to those in previous work
+\cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20}.
 
@@
   $Y = \{y_i\}_{i=1}^n \subseteq X$, and $r \in \mathbb{R}$. Operations such as
-  addition and multiplication are defined pointwise as
-  \[
-    (f+g)(Y) \coloneqq f(Y)+g(Y), \quad \text{and} \quad (f \cdot g)(Y)
-    \coloneqq f(Y) \cdot g(Y).
-  \]
-  Note that this means that binary operations on pseudo-Boolean functions
-  inherit properties such as associativity and commutativity. By regarding a
-  real number as a constant pseudo-Boolean function, we can reuse the same
-  definitions to define \emph{scalar} operations as
-  \[
-    (r+f)(Y) = r+f(Y), \quad \text{and} \quad (r \cdot f)(Y) = r \cdot f(Y).
-  \]
+  addition and multiplication are defined pointwise, i.e., $(f+g)(Y) \coloneqq
+  f(Y)+g(Y)$, and likewise for multiplication. Note that properties such as
+  associativity and commutativity are inherited from $\mathbb{R}$. By regarding
+  a real number as a constant pseudo-Boolean function, we can reuse the same
+  definitions to define \emph{scalar} operations as $(r+f)(Y) = r+f(Y)$, and $(r
+  \cdot f)(Y) = r \cdot f(Y)$.
 
   \emph{Restrictions} $f|_{x=0}, f|_{x=1}\colon 2^X \to \mathbb{R}$ of $f$ are
-  defined as
-  \[
-    f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\}), \quad \text{and} \quad
-    f|_{x=1}(Y) \coloneqq f(Y \cup \{x\})
-  \]
-  for all $Y \subseteq X$.
+  defined as $f|_{x=0}(Y) \coloneqq f(Y \setminus \{x\})$, and $f|_{x=1}(Y)
+  \coloneqq f(Y \cup \{x\})$ for all $Y \subseteq X$.
 
   \emph{Projection} $\exists_x$ is an endomorphism $\exists_x\colon
-  \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined as
-  \[
-    \exists_xf \coloneqq f|_{x=1} + f|_{x=0}.
-  \]
-  Since projection is commutative (i.e., $\exists_x\exists_yf =
-  \exists_y\exists_xf$) \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20},
-  we can define $\exists_Y\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ as
-  $\exists_Y \coloneqq \exists_{y_1}\exists_{y_2}\dots\exists_{y_n}$. Throughout
-  the paper, projection is assumed to have the lowest precedence (e.g.,
-  $\exists_x fg = \exists_x (fg)$).
+  \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ defined as $\exists_xf \coloneqq
+  f|_{x=1} + f|_{x=0}$. Since projection is commutative (i.e.,
+  $\exists_x\exists_yf = \exists_y\exists_xf$)
+  \cite{DBLP:conf/aaai/DudekPV20,DBLP:conf/cp/DudekPV20}, we can define
+  $\exists_Y\colon \mathbb{R}^{2^X} \to \mathbb{R}^{2^X}$ as $\exists_Y
+  \coloneqq \exists_{y_1}\exists_{y_2}\dots\exists_{y_n}$. Throughout the paper,
+  projection is assumed to have the lowest precedence (e.g., $\exists_x fg =
+  \exists_x (fg)$).
 \end{definition}
 
-Finally, below we list some properties of the operations on pseudo-Boolean
-functions discussed in this section that can be conveniently represented using
-our syntax. The proofs of all these properties follow directly from the
-definitions.
+Below we list some properties of the operations on pseudo-Boolean functions
+discussed in this section that can be conveniently represented using our syntax.
+The proofs of all these properties follow directly from the definitions.
 
@@
 
+\begin{remark}
+  Note that our definitions of binary operations assumed equal domains. For
+  convenience, we can assume domains to shrink whenever a function is
+  independent of some of the variables (i.e., $f|_{x=0} = f|_{x=1}$) and expand
+  for binary operations to make the domains of both functions equal. For
+  instance, let $[x]_0^1,[\neg x]_0^1\colon 2^{\{x\}} \to \mathbb{R}$ and
+  $[y]_0^1\colon 2^{\{y\}} \to \mathbb{R}$ be pseudo-Boolean functions. Then
+  $[x]_0^1 \cdot [\neg x]_0^1$ has $2^\emptyset$ as its domain. To multiply
+  $[x]_0^1$ and $[y]_0^1$, we expand $[x]_0^1$ into $\left([x]_0^1\right)'\colon
+  2^{\{x, y\}} \to \mathbb{R}$ which is defined as $\left([x]_0^1\right)'(Z)
+  \coloneqq [x]_0^1(Z \cap \{ x \})$ for all $Z \subseteq \{ x, y \}$ (and
+  equivalently for $[y]_0^1$).
+\end{remark}
+
 \section{Pseudo-Boolean Projection}
@@
   $F$ is a set of two-valued pseudo-Boolean functions $2^X \to \mathbb{R}$, and
-  $\omega \in \mathbb{R}$ is the scaling factor. The \emph{answer} of the
-  instance is $\omega \cdot \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
+  $\omega \in \mathbb{R}$ is the scaling factor. Its \emph{answer} is $\omega
+  \cdot \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
 \end{definition}
@@
 
-In this section we describe an algorithm for transforming WMC instances to the
+In this section, we describe an algorithm for transforming WMC instances to the
 PBP format while removing all parameter variables. The algorithm works on four
@@
 
-In this section we outline key properties that a (WMC or minimum-cardinality
+In this section, we outline key properties that a (WMC or minimum-cardinality
 WMC) encoding has to satisfy for \cref{alg:transformation} to output an
@@
   Let $f = \prod_{c \in \phi} [c]_0^1$, and $g = \prod_{x \in X_I \cup X_P}
-  [x]_{w(\neg x)}^{w(x)}$. Then the answer to the WMC instance
+  [x]_{w(\neg x)}^{w(x)}$. Then the WMC answer is
   \eqref{eq:new_wmc} is
@@
 ensures that only parameter variables carry nontrivial weights. \Cref{cond:d02}
-(for \texttt{d02}), while spelled out precisely in the theorem, simply states
-that each parameter variable is equivalent to a conjunction of indicator
-literals. \Cref{cond:bklm16} is for encodings that have implications rather than
-equivalences associated with parameter variables (which, in this case, is
-\texttt{bklm16}). It ensures that each clause has at most one positive
-parameter literal and no negative ones, and that at most one implication clause
-per any parameter variable $p \in X_P$ can `force $p$ to be positive'.
+(for \texttt{d02}) simply states that each parameter variable is equivalent to a
+conjunction of indicator literals. \Cref{cond:bklm16} is for encodings that have
+implications rather than equivalences associated with parameter variables
+(which, in this case, is \texttt{bklm16}). It ensures that each clause has at
+most one positive parameter literal and no negative ones, and that at most one
+implication clause per any parameter variable $p \in X_P$ can `force $p$ to be
+positive'.
 
@@
   \end{equation}
-  Note that under \cref{cond:d02},
-  \[
-    \bigwedge_{c \in \phi_p} c \equiv p \Leftrightarrow \bigwedge_{i=1}^n l_i
-  \]
-  for some family of indicator variable literals $(l_i)_{i=1}^n$. Thus,
+  Note that under \cref{cond:d02}, $\bigwedge_{c \in \phi_p} c \equiv p
+  \Leftrightarrow \bigwedge_{i=1}^n l_i$ for some family of indicator variable
+  literals $(l_i)_{i=1}^n$. Thus,
   \[
@@
 
-  If $w(p) \ne 1$, then
-  \[
-    F_p = \left\{ \left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} \right\},
-  \]
-  and $\omega = 1$, and so we want to show that $\left[ \bigwedge_{i = 1}^n l_i
-  \right]_1^{w(p)} = \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow
-    \bigwedge_{i=1}^n l_i \right]_0^1$, and indeed
+  If $w(p) \ne 1$, then $F_p = \left\{ \left[ \bigwedge_{i = 1}^n l_i
+    \right]_1^{w(p)} \right\}$, and $\omega = 1$, and so we want to show that
+  $\left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} = \exists_p [p]_1^{w(p)}
+  \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1$, and indeed
   \[
@@
   \]
-  This finishes the proof of the correctness of the first `foreach' loop under
+  This finishes the proof of the correctness of the first loop under
   \cref{cond:d02}.
@@
   \]
-  We can rearrange the right-hand side as % TODO: make it fit into margins
+  We can rearrange the right-hand side as
+  % \begin{align*}
+  %   \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 &= \exists_p [p]_{1-w(p)}^{w(p)} \left[\bigwedge_{c \in \phi_p} c\right]_0^1 = \exists_p [p]_{1-w(p)}^{w(p)} \left[ p \lor \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 \\
+  %                                                              &= w(p) + (1-w(p)) \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 = w(p) + \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^{1-w(p)} \\
+  %                                                              &= \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_{w(p)}^1 = \left[ \neg \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \neg(c \setminus \{ p \}) \right]_1^{w(p)} \\
+  %                                                              &= \left[ \bigvee_{c \in \phi_p} \neg \bigvee_{l \in c \setminus \{ p \}} l \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}.
+  % \end{align*}
   \begin{align*}
-    \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 &= \exists_p [p]_{1-w(p)}^{w(p)} \left[\bigwedge_{c \in \phi_p} c\right]_0^1 = \exists_p [p]_{1-w(p)}^{w(p)} \left[ p \lor \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 \\
-                                                               &= w(p) + (1-w(p)) \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 = w(p) + \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^{1-w(p)} \\
-                                                               &= \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_{w(p)}^1 = \left[ \neg \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \neg(c \setminus \{ p \}) \right]_1^{w(p)} \\
-                                                               &= \left[ \bigvee_{c \in \phi_p} \neg \bigvee_{l \in c \setminus \{ p \}} l \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}.
+    \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 &= \exists_p [p]_{1-w(p)}^{w(p)} \left[ p \lor \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 \\
+                                                               &= w(p) + (1-w(p)) \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 \\
+                                                               &= \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_{w(p)}^1 = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}.
   \end{align*}
@@
 \section{Experimental Evaluation}
-% TODO: what are the encodings compiled with?
 
@@
 afterwards.\footnote{Recall that \texttt{cd05} and \texttt{cd06} are
-  incompatible with \textsf{DPMC}.} For each encoding \texttt{e}, we will write
+  incompatible with \textsf{DPMC}.} For each encoding \texttt{e}, we write
 \texttt{e++} to denote the combination of encoding a Bayesian network as a WMC
@@
 \textsf{query-dnnf}\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
-for \texttt{bklm16}. We focus on the following questions:
+for \texttt{bklm16}. \textsf{Ace} is also used to encode Bayesian networks into
+WMC instances for all encodings except for \texttt{bklm16} which uses another
+encoder mentioned previously. We focus on the following questions:
 \begin{itemize}
@@
 
-\textsf{DPMC} is run with tree decomposition based planning and ADD based
+\textsf{DPMC} is run with tree decomposition-based planning and ADD-based
 execution---the best-performing combination in the original set of experiments
@@
     \texttt{bklm16++}$ (the best combination according to \cref{fig:cumulative})
-  and the second and third best performing combinations: $\textsf{Ace} +
+  and the second and third best-performing combinations: $\textsf{Ace} +
   \texttt{cd06}$ and $\textsf{DPMC} + \texttt{bklm16}$.}
@@
 inefficient.
-% TODO: mention (somewhere) that we can't compare to Gogate's work and direct
-% compilation (take the text from the introduction)
 

### 2021-03-08 tools/analyse_changes.R

@@ -111,3 +111,6 @@ ggplot(df, aes(value, inference_time, col = dataset.y, shape = dataset.y)) + geo
 
 median(changes$before_variables[changes$encoding == "bklm16"])
 median(changes$after_variables[changes$encoding == "bklm16"])
+
+summary(changes$after_variables[changes$encoding == "bklm16"] / changes$before_variables[changes$encoding == "bklm16"])
+summary(changes$after_variables[changes$encoding != "sbk05"] / changes$before_variables[changes$encoding != "sbk05"])

### 2021-03-14 doc/paper3/paper.tex
Some editing

@@
   WMC instances into a format based on pseudo-Boolean functions while
-  eliminating around \SI{57}{\percent} of variables on average across various
+  eliminating around \SI{43}{\percent} of variables on average across various
   Bayesian network encodings. Moreover, we identify sufficient conditions for
@@
 a new representation comes the need to invent new encodings and inference
-algorithms. Our work is similar in that it introduces a new representation for
-computational problems but can reuse recent WMC algorithms based on
-pseudo-Boolean function manipulation, namely, \textsf{ADDMC}
+algorithms. Our work is similar in spirit in that it introduces a new
+representation for computational problems but can reuse recent WMC algorithms
+based on pseudo-Boolean function manipulation, namely, \textsf{ADDMC}
 \cite{DBLP:conf/aaai/DudekPV20} and \textsf{DPMC} \cite{DBLP:conf/cp/DudekPV20}.
@@
 into our new format. As many WMC inference algorithms such as
-\textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}}, \textsf{c2d}
+\textsf{Ace}, \textsf{c2d}
 \cite{DBLP:conf/ecai/Darwiche04}, and \textsf{miniC2D}
@@
 \cite{DBLP:conf/ijcai/Darwiche11}, another way to avoid parameter variables
-could be via direct compilation to a more convenient representation. However,
-while direct compilation of Bayesian networks to SDDs has been investigated
-\cite{DBLP:conf/ecsqaru/ChoiKD13}, SDDs are not expressive enough to avoid the
-issue. Furthermore, to the best of the authors' knowledge, neither
-compilation/inference technique has a publicly available implementation.
+could be via direct compilation to a more convenient representation. Direct
+compilation of Bayesian networks to SDDs has been investigated
+\cite{DBLP:conf/ecsqaru/ChoiKD13}. However, SDDs only support weights on
+literals, and so are not expressive enough to avoid the issue. To the best of
+the authors' knowledge, neither approach
+\cite{DBLP:conf/ecsqaru/ChoiKD13,DBLP:conf/uai/GogateD10} has a publicly
+available implementation.
 
@@
 \cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05}
-can indeed be simplified in this manner. This transformation enables two
-encodings that were previously incompatible with most WMC algorithms (due to
-using a different definition of WMC
-\cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}) to be run with
+can indeed be simplified in this manner. We are able to eliminate
+\SI{43}{\percent} of variables on average and up to \SI{99}{\percent} on some
+instances. This transformation enables two encodings that were previously
+incompatible with most WMC algorithms (due to using a different definition of
+WMC \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}) to be run with
 \textsf{ADDMC} and \textsf{DPMC} and results in a significant performance boost
-for one other encoding, allowing it to surpass the current state of the art.
-Finally, our theoretical contributions result in a convenient algebraic way of
-reasoning about two-valued pseudo-Boolean functions and position WMC encodings
-on common ground, identifying their key properties and assumptions.
+for one other encoding, making it about three times faster than the state of the
+art. Finally, our theoretical contributions result in a convenient algebraic way
+of reasoning about two-valued pseudo-Boolean functions and position WMC
+encodings on common ground, identifying their key properties and assumptions.
 
@@
   A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
-  the set of \emph{indicator} variables, $X_P$ is the set of \emph{parameter}
-  variables (with $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula
+  the set of \emph{indicator variables}, $X_P$ is the set of \emph{parameter
+  variables} (with $X_I \cap X_P = \emptyset$), $\phi$ is a propositional formula
   in CNF over $X_I \cup X_P$, and $w\colon X_I \cup X_P \cup \{\neg x \mid x \in
-  X_I \cup X_P\} \to \mathbb{R}$ is the weight function. Its \emph{answer} is
+  X_I \cup X_P\} \to \mathbb{R}$ is a \emph{weight function} such that $w(x) =
+  w(\neg x) = 1$ for all $x \in X_I$. The \emph{answer} of the instance is
   $\sum_{Y \models \phi} \prod_{Y \models l} w(l)$.
@@
 practice, we identify this partition in one of two ways. If an encoding is
-generated by \textsf{Ace}, then variable types are explicitly identified in the
-LMAP file generated alongside the encoding. Otherwise, we define a variable $x$
-to be a parameter variable if $w(x) = w(\neg x) = 1$. Next, we formally define a
-variation of the WMC problem used by some of the Bayesian network encodings
+generated by \textsf{Ace}\footnote{\textsf{Ace}
+  \cite{DBLP:journals/ai/ChaviraD08} implements most of the Bayesian network
+  encodings and can also be used for compilation (and thus inference). It is
+  available at \url{http://reasoning.cs.ucla.edu/ace/}.}, then variable types
+are explicitly identified in a file generated alongside the encoding. Otherwise,
+we take $X_I$ to be the set of all variables $x$ such that $w(x) = w(\neg x) =
+1$. Next, we formally define a variation of the WMC problem used by some of the
+Bayesian network encodings
 \cite{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.
@@
 
-\subsection{Bayesian Network Encodings}
+\begin{example}
+  Let $\phi = (x \lor y) \land (\neg x \lor \neg y) \land (\neg x \lor p) \land
+  (\neg y \lor q) \land x$, $X_I = \{ x, y \}$, $X_P = \{ p, q \}$, $w(p) =
+  0.2$, $w(q) = 0.8$, and $w(\neg p) = w(\neg q) = 1$. Then $\phi$ has two
+  models: $\{x, p\}$ and $\{ x, p, q \}$ with weights $0.2$ and $0.2 \times 0.8
+  = 0.16$, respectively. The WMC answer is then $0.2 + 0.16 = 0.36$, and the
+  minimum-cardinality WMC answer is $0.2$.
+\end{example}
+
+\subsection{Bayesian Network Encodings} \label{sec:encodings}
 
@@
 encoder\footnote{\url{http://www.cril.univ-artois.fr/kc/bn2cnf.html}}).
+% TODO (on encodings and clauses): I realise the paper is already long but it
+% might be useful to have a quick example
+% TODO: If I am reading this correctly you are making a stark statement about
+% the inefficacy. It might be good to rephrase this differently. You might want
+% to say that there are many corner cases where there are no improvements. 
+% TODO: Is there a reference for this example? If yes provide one. If no, maybe
+% you could provide a link to the output, or alternatively, you could say
+% something like the reader is free to check that such an example produces no
+% improvements
+% TODO: is this example the same as the previous one?
 
@@
   $F$ is a set of two-valued pseudo-Boolean functions $2^X \to \mathbb{R}$, and
-  $\omega \in \mathbb{R}$ is the scaling factor. Its \emph{answer} is $\omega
-  \cdot \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
-\end{definition}
-
+  $\omega \in \mathbb{R}$ is the scaling factor.\footnote{
     Adding scaling factor $\omega$ to the definition allows us to remove clauses
@@
     some of the structure of the WMC instance into an external multiplicative factor
-was inspired by the \texttt{bklm16} encoding.
+    was loosely inspired by the \texttt{bklm16} encoding, where it is used
+    to subsume the most commonly occurring probability of each CPT
+    \cite{DBLP:conf/ecai/BartKLM16}.} Its \emph{answer} is $\omega \cdot
+  \left(\exists_X\prod_{f \in F}f\right)(\emptyset)$.
+\end{definition}
 
@@
 PBP format while removing all parameter variables. The algorithm works on four
-out of the five Bayesian network encodings. There is no obvious way to adjust it
-to work with \texttt{sbk05} because the roles of indicator and parameter (i.e.,
+out of the five Bayesian network encodings: \texttt{bklm16}
+\cite{DBLP:conf/ecai/BartKLM16}, \texttt{cd05}
+\cite{DBLP:conf/ijcai/ChaviraD05}, \texttt{cd06}
+\cite{DBLP:conf/sat/ChaviraD06}, and \texttt{d02}
+\cite{DBLP:conf/kr/Darwiche02}. There is no obvious way to adjust it to work
+with \texttt{sbk05} because the roles of indicator and parameter (i.e.,
 `chance') variables overlap \cite{DBLP:conf/aaai/SangBK05}. The algorithm is
@@
 \end{proposition}
+% TODO: It’s a bit strange to say same answer, when you don’t precisely refer to
+% this anywhere. One option is to say the above is the WMC instance and let
+% Delta be the weighted model count. Then the new encoding Has a weighted model
+% count of delta as well. Or something like that.
+% But looking at the text below, I see that you use this phrasing everywhere,
+% and I admit my formulation is awkward. So maybe the best compromise here is
+% just simply add a footnote explaining what exactly you mean when you say same
+% answer
+% TODO: If it is the case that you cannot include the proofs in line, and indeed
+% it might be better for readability to have an appendix with all the proofs, it
+% might make sense to provide the type of argument you are using in the proofs
+% so that readers know what to expect when they look into it
 \begin{proof}
@@
   \Cref{alg:transformation}, when given a WMC instance $(\phi, X_I, X_P,
-  w)$, returns PBP instance with the same answer, provided the following
-  conditions are satisfied:
+  w)$, returns a PBP instance with the same answer, provided \emph{either} of
+  the two conditions is satisfied:
   \begin{enumerate}
-  \item for all indicator variables $i \in X_I$, $w(i) = w(\neg i) =
-    1$, \label{cond:one}
-  \item and either
-    \begin{enumerate}
-    \item for all parameter variables $p \in X_P$, there is a non-empty family
-      of literals $(l_i)_{i=1}^n$ such that \label{cond:d02}
+  \item for all $p \in X_P$, there is a non-empty family of literals
+    $(l_i)_{i=1}^n$ such that \label{cond:d02}
     \begin{enumerate}
@@
     \end{enumerate}
-    \item or for all parameter variables $p \in X_P$, \label{cond:bklm16}
+  \item or for all $p \in X_P$, \label{cond:bklm16}
     \begin{enumerate}
@@
       that $c \ne \{ p \}$ and $p \in c$, \label{cond:just_parameter}
-        % 'prime implicants are logically disjoint'
     \item and for any $c, d \in \phi$ such that $c \ne d$, $p \in c$ and $p
@@
   \end{enumerate}
-  \end{enumerate}
 \end{theorem}
 
-\Cref{cond:one} applies to all four WMC encodings under consideration and
-ensures that only parameter variables carry nontrivial weights. \Cref{cond:d02}
-(for \texttt{d02}) simply states that each parameter variable is equivalent to a
-conjunction of indicator literals. \Cref{cond:bklm16} is for encodings that have
-implications rather than equivalences associated with parameter variables
-(which, in this case, is \texttt{bklm16}). It ensures that each clause has at
-most one positive parameter literal and no negative ones, and that at most one
-implication clause per any parameter variable $p \in X_P$ can `force $p$ to be
-positive'.
+\Cref{cond:d02} (for \texttt{d02}) simply states that each parameter variable is
+equivalent to a conjunction of indicator literals. \Cref{cond:bklm16} is for
+encodings that have implications rather than equivalences associated with
+parameter variables (which, in this case, is \texttt{bklm16}). It ensures that
+each clause has at most one positive parameter literal and no negative ones, and
+that at most one implication clause per any parameter variable $p \in X_P$ can
+`force $p$ to be positive'.
 
@@
   \Leftrightarrow \bigwedge_{i=1}^n l_i$ for some family of indicator variable
-  literals $(l_i)_{i=1}^n$. Thus,
-  \[
-    \exists_p [p]_{w(\neg p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 = \exists_p
-    [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1.
-  \]
-  If $w(p) = 1$, then
+  literals $(l_i)_{i=1}^n$. Thus, $\exists_p [p]_{w(\neg p)}^{w(p)} \prod_{c \in
+    \phi_p} [c]_0^1 = \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow
+    \bigwedge_{i=1}^n l_i \right]_0^1$. If $w(p) = 1$, then
   \begin{equation} \label{eq:bigsums}
@@
   Let $(\phi, X_I, X_P, w)$ be a minimum-cardinality WMC instance that satisfies
-  \cref{cond:one,cond:2b2,cond:2b3,cond:just_parameter,cond:disjoint} of
+  \cref{cond:2b2,cond:2b3,cond:just_parameter,cond:disjoint} of
   \cref{thm:correctness} as well as the following:
@@
   X_I \cup X_P$ be related via this bijection. Then in the second part we will
-  show that
+  show that % TODO: footnote: explain how
   \begin{equation} \label{eq:weights}
@@
   \input{cumulative.tex}%
-  \caption{Cumulative numbers of instances solved by each algorithm-encoding
-    pair over time. The dotted line denotes the total number of instances used.}
+  \caption{Cactus plot of all algorithm-encoding pairs. The dotted line
+    denotes the total number of instances used.}
   \label{fig:cumulative}
@@
 
+% TODO: consider moving (some) proofs to the appendix or at least making a clear
+% argument why they should be in the text.
+
 \bibliographystyle{splncs04}

### 2021-03-14 tools/analyse.R

@@ -272,16 +272,16 @@ cumulative_plot <- function(df, column_name, pretty_column_name, variable, varia
   cumulative$time <- as.numeric(cumulative$time)
   cumulative$count <- as.numeric(cumulative$count)
   cumulative <- cumulative[cumulative$time < 2 * TIMEOUT, ]
-  p <- ggplot(cumulative, aes(x = time, y = count, color = .data[[column_name]])) +
+  p <- ggplot(cumulative, aes(x = count, y = time, color = .data[[column_name]])) +
     geom_line(aes(linetype = algorithm)) +
-    scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000),
+    scale_y_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000),
                        labels = c("0.1", "1", "10", "100", "1000")) +
-    xlab("Time (s)") +
-    ylab("Instances solved") +
-    annotation_logticks(sides = "b", colour = "#989898") +
+    ylab("Time (s)") +
+    xlab("Instances solved") +
+    annotation_logticks(sides = "l", colour = "#989898") +
     theme_set(theme_light()) +
     labs(color = pretty_column_name, linetype = "Algorithm") +
-    geom_hline(yintercept = 1466, linetype = "dotted", color = "black")
+    geom_vline(xintercept = 1466, linetype = "dotted", color = "black")
 
   if (show.color.legend) {
     p <- p + scale_colour_manual(breaks = sort(unique(cumulative$encoding)),

### 2021-03-14 tools/analyse_changes.R

@@ -113,4 +113,6 @@ median(changes$before_variables[changes$encoding == "bklm16"])
 median(changes$after_variables[changes$encoding == "bklm16"])
 
 summary(changes$after_variables[changes$encoding == "bklm16"] / changes$before_variables[changes$encoding == "bklm16"])
-summary(changes$after_variables[changes$encoding != "sbk05"] / changes$before_variables[changes$encoding != "sbk05"])
+summary(1 - changes$after_variables[changes$encoding != "sbk05"] / changes$before_variables[changes$encoding != "sbk05"])
+hist(changes$after_variables[changes$encoding != "sbk05"] / changes$before_variables[changes$encoding != "sbk05"])
+changes$diff <- 1 - changes$after_variables / changes$before_variables

### 2021-03-14 doc/paper3/paper.tex
Some edits before submission

@@
 \usepackage{capt-of}
+\usepackage[inline]{enumitem}
 
@@
 
-\begin{definition}[WMC]
+\begin{definition}[WMC] \label{def:wmc}
   A \emph{WMC instance} is a tuple $(\phi, X_I, X_P, w)$, where $X_I$ is
@@
 
-\begin{definition}[Minimum-Cardinality WMC]
+\begin{definition}[Minimum-Cardinality WMC] \label{def:mcwmc}
   A \emph{minimum-cardinality WMC} instance consists of the same tuple as a WMC
-  instance, but its answer is defined to be $\sum_{Y \models \phi\text{, }|Y| =
-    k} \prod_{Y \models l} w(l)$ (where $k = \min_{Y \models \phi} |Y|$) if
-  $\phi$ is satisfiable, and zero otherwise.
+  instance, but its \emph{answer} is defined to be $\sum_{Y \models \phi\text{,
+    }|Y| = k} \prod_{Y \models l} w(l)$ (where $k = \min_{Y \models \phi} |Y|$)
+  if $\phi$ is satisfiable, and zero otherwise.
 \end{definition}
 
-\begin{example}
+\begin{example} \label{example:1}
   Let $\phi = (x \lor y) \land (\neg x \lor \neg y) \land (\neg x \lor p) \land
@@
 clauses that `imply' parameter variables (i.e., omit clauses where a parameter
-variable implies indicator variables). In their next encoding, \texttt{cd06}
+variable implies indicator variables).\footnote{\Cref{example:2} demonstrates
+  what we mean by implication clauses.} In their next encoding, \texttt{cd06}
 \cite{DBLP:conf/sat/ChaviraD06}, the same authors optimise the aforementioned
@@
 factor is often small enough to be indistinguishable from zero without the use
-of arbitrary precision arithmetic. Indeed, even a small Bayesian network with
-seven mutually independent binary variables, 0.1 and 0.9 probabilities each, is
-already big enough for the scaling factor to be exactly equal to zero (as
-produced by the \texttt{bklm16}
-encoder\footnote{\url{http://www.cril.univ-artois.fr/kc/bn2cnf.html}}).
-% TODO (on encodings and clauses): I realise the paper is already long but it
-% might be useful to have a quick example
-% TODO: If I am reading this correctly you are making a stark statement about
-% the inefficacy. It might be good to rephrase this differently. You might want
-% to say that there are many corner cases where there are no improvements. 
-% TODO: Is there a reference for this example? If yes provide one. If no, maybe
-% you could provide a link to the output, or alternatively, you could say
-% something like the reader is free to check that such an example produces no
-% improvements
-% TODO: is this example the same as the previous one?
+of arbitrary precision arithmetic, making it completely unusable on realistic
+instances. Indeed, the reader is free to check that even a small Bayesian
+network with seven mutually independent binary variables, 0.1 and 0.9
+probabilities each, is already big enough for the scaling factor to be exactly
+equal to zero (as produced by the \texttt{bklm16}
+encoder\footnote{\url{http://www.cril.univ-artois.fr/kc/bn2cnf.html}}). We
+suspect that this issue was not identified during the original set of
+experiments because they never looked at numerical answers.
+
+\begin{example} \label{example:2}
+  Let $\mathcal{B}$ be a Bayesian network with one variable $X$ which has two
+  values $x_1$ and $x_2$ with probabilities $\Pr(X = x_1) = 0.2$ and $\Pr(X =
+  x_2) = 0.8$. Let $x, y$ be indicator variables, and $p, q$ be parameter
+  variables. Then \cref{example:1} is both the \texttt{cd05} and the
+  \texttt{cd06} encoding of $\mathcal{B}$. The \texttt{bklm16} encoding is $(x
+  \Rightarrow p) \land (\neg x \Rightarrow q) \land x$ with $w(p) = w(\neg q) =
+  0.2$, and $w(\neg p) = w(q) = 0.8$. And the \texttt{d02} encoding is $(\neg x
+  \Rightarrow p) \land (p \Rightarrow \neg x) \land (x \Rightarrow q) \land (q
+  \Rightarrow x) \land \neg x$ with $w(p) = 0.2$, $w(q) = 0.8$, and $w(\neg p) =
+  w(\neg q) = 1$. Note how all other encodings have fewer clauses than
+  \texttt{d02}. While \texttt{cd05} and \texttt{cd06} require
+  minimum-cardinality WMC to make this work, \texttt{bklm16} achieves the same
+  thing by adjusting weights.
+\end{example}
 
@@
 
-\begin{definition}[PBP Instance] \label{def:new_wmc}
+\begin{definition}[PBP Instance] \label{def:pbp}
   A PBP instance is a tuple $(F, X, \omega)$, where $X$ is the set of variables,
@@
   \end{equation}
-  is a PBP instance with the same answer.
+  is a PBP instance with the same answer (as defined in \cref{def:wmc,def:pbp}).
 \end{proposition}
-% TODO: It’s a bit strange to say same answer, when you don’t precisely refer to
+% It’s a bit strange to say same answer, when you don’t precisely refer to
 % this anywhere. One option is to say the above is the WMC instance and let
@@
 % answer
-% TODO: If it is the case that you cannot include the proofs in line, and indeed
-% it might be better for readability to have an appendix with all the proofs, it
-% might make sense to provide the type of argument you are using in the proofs
-% so that readers know what to expect when they look into it
 \begin{proof}
@@
   \Cref{alg:transformation}, when given a WMC instance $(\phi, X_I, X_P,
-  w)$, returns a PBP instance with the same answer, provided \emph{either} of
-  the two conditions is satisfied:
+  w)$, returns a PBP instance with the same answer (as defined in
+  \cref{def:wmc,def:pbp}), provided \emph{either} of the two conditions is
+  satisfied:
   \begin{enumerate}
@@
   is a PBP instance with the same answer as the given WMC instance. By
-  \cref{def:new_wmc}, its answer is $\left(\exists_{X_I \cup X_P} \left(\prod_{c
+  \cref{def:pbp}, its answer is $\left(\exists_{X_I \cup X_P} \left(\prod_{c
         \in \phi} [c]_0^1 \right) \prod_{x \in X_I \cup X_P} [x]_{w(\neg
@@
         \}} \neg l\right]_1^{w(p)} \;\middle|\; c \in \phi_p \right\}$, so we
-  need to show that
-  \[
-    \prod_{c \in \phi_p} \left[\bigwedge_{l \in c \setminus \{ p \}} \neg
-      l\right]_1^{w(p)} = \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p}
-    [c]_0^1.
-  \]
-  We can rearrange the right-hand side as
+  need to show that $\prod_{c \in \phi_p} \left[\bigwedge_{l \in c \setminus \{
+      p \}} \neg l\right]_1^{w(p)} = \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in
+    \phi_p} [c]_0^1$. We can rearrange the right-hand side as
   % \begin{align*}
@@
    By \cref{cond:disjoint}, $\bigwedge_{l \in c \setminus \{ p \}} \neg l$ can
-   be true for at most one $c \in \phi_p$, and so
-   \[
-     \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l
-     \right]_1^{w(p)} = \prod_{c \in \phi_p} \left[ \bigwedge_{l \in c \setminus
-         \{ p \}} \neg l \right]_1^{w(p)}
-   \]
-   which is exactly what we needed to show. This ends the proof that the
-   first loop of \cref{alg:transformation} preserves the answer under both
-   \cref{cond:d02} and \cref{cond:bklm16}. Finally, the loop on
+   be true for at most one $c \in \phi_p$, and so $\left[ \bigvee_{c \in \phi_p}
+     \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)} = \prod_{c
+     \in \phi_p} \left[ \bigwedge_{l \in c \setminus \{ p \}} \neg l
+   \right]_1^{w(p)}$ which is exactly what we needed to show. This ends the
+   proof that the first loop of \cref{alg:transformation} preserves the answer
+   under both \cref{cond:d02} and \cref{cond:bklm16}. Finally, the loop on
    \crefrange{line:foreach2start}{line:foreach2end} of \cref{alg:transformation}
@@
   Then \cref{alg:transformation}, when applied to $(\phi, X_I, X_P, w)$, outputs
-  a PBP instance with the same answer.
+  a PBP instance with the same answer (as defined in \cref{def:mcwmc,def:pbp}).
 \end{theorem}
@@
   Let $(F, X_I, \omega)$ be the tuple returned by \cref{alg:transformation} and
-  note that
-  \[
-    F = \left\{ [c]_0^1 \mid c \in \phi \text{, } c \cap X_P = \emptyset
-    \right\} \cup \left\{ \left[ \bigwedge_{l \in c \setminus \{ p \}} \neg l
-      \right]_1^{w(p)} \;\middle|\; p \in X_P \text{, } p \in c \in \phi
-      \text{, } c \ne \{ p \} \right\}.
-  \]
-  We split the proof into two parts. In the first part, we show that there is a
-  bijection between minimum-cardinality models of $\phi$ and $Y \subseteq X_I$
-  such that $\left(\prod_{f \in F} f\right)(Y) \ne 0$ (with the assumption that
-  $w(p) \ne 0$ for all $p \in X_P$).\footnote{The assumption is only there to
-    make the proof more convenient and can be omitted by reformulating the proof
-    in a slightly more cumbersome way.} Let $Y \subseteq X_I$ and $Z \subseteq
-  X_I \cup X_P$ be related via this bijection. Then in the second part we will
-  show that % TODO: footnote: explain how
+  note that $F = \left\{ [c]_0^1 \mid c \in \phi \text{, } c \cap X_P =
+    \emptyset \right\} \cup \left\{ \left[ \bigwedge_{l \in c \setminus \{ p \}}
+      \neg l \right]_1^{w(p)} \;\middle|\; p \in X_P \text{, } p \in c \in \phi
+    \text{, } c \ne \{ p \} \right\}$. We split the proof into two parts. In the
+  first part, we show that there is a bijection between minimum-cardinality
+  models of $\phi$ and $Y \subseteq X_I$ such that $\left(\prod_{f \in F}
+    f\right)(Y) \ne 0$.\footnote{For convenience and without loss of generality
+    we assume that $w(p) \ne 0$ for all $p \in X_P$.} Let $Y \subseteq X_I$ and
+  $Z \subseteq X_I \cup X_P$ be related via this bijection. Then in the second
+  part we will show that
   \begin{equation} \label{eq:weights}
@@
 \textsf{Cachet}. We split them into the following groups:
-\begin{itemize}
+\begin{itemize*}
 \item DQMR (390 instances) and
@@
   \texttt{water}.
-\end{itemize}
+\end{itemize*}
 
@@
 % argument why they should be in the text.
+% If it is the case that you cannot include the proofs in line, and indeed
+% it might be better for readability to have an appendix with all the proofs, it
+% might make sense to provide the type of argument you are using in the proofs
+% so that readers know what to expect when they look into it
 

### 2021-04-17 tools/analyse.R
Small changes

@@ -50,26 +50,22 @@ data_sum <- data_merged
 data_sum$time <- data_sum$encoding_time + data_sum$inference_time
 data_sum <- subset(data_sum, select = -c(inference_time, encoding_time))
 
-#data_sum2 <- data
-#data_sum2$time <- data_sum2$encoding_time + data_sum2$inference_time
-#data_sum2 <- subset(data_sum2, select = -c(inference_time, encoding_time))
-
-# df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
-#             fun.aggregate = NULL,
-#             value.var = c("answer", "time", "add_width"))
 df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
             fun.aggregate = NULL,
-            value.var = c("answer", "time"))
+            value.var = c("answer", "time", "add_width", "treewidth"))
+#df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
+#            fun.aggregate = NULL,
+#            value.var = c("answer", "time"))
 time_columns <- Filter(function(x) startsWith(x, "time_"), names(df))
 time_columns0 <- time_columns[!grepl('pp$', time_columns)]
 for (column in time_columns) {
   df[is.na(df[[column]]), column] <- 2 * TIMEOUT
 }
 
-#df$treewidth <- apply(df %>% select(starts_with("treewidth")), 1,
-#                      function(x) max(x, na.rm = TRUE))
-#df <- df %>% select(!starts_with("treewidth_"))
-#df$treewidth <- df$treewidth - 1
+df$treewidth <- apply(df %>% select(starts_with("treewidth")), 1,
+                      function(x) max(x, na.rm = TRUE))
+df <- df %>% select(!starts_with("treewidth_"))
+df$treewidth <- df$treewidth - 1
 #df$zero_proportion <- apply(df %>% select(starts_with("zero_")), 1,
 #                      function(x) max(x, na.rm = TRUE))
 #df <- df %>% select(!starts_with("zero_proportion_"))
@@ -348,7 +344,7 @@ ggplot(data_melted, aes(encoding, time, fill = variable)) +
   ylab("Time (s)") +
   labs(fill = "")
 
-# Plots that show how the combination of cw and cd06 would do (not including tree decomposition time)
+# Plots that show how the combination of bklm16 and cd06 would do (not including tree decomposition time)
[…]

### 2021-04-17 tools/analyse_changes.R

@@ -112,6 +112,9 @@ ggplot(df, aes(value, inference_time, col = dataset.y, shape = dataset.y)) + geo
 median(changes$before_variables[changes$encoding == "bklm16"])
 median(changes$after_variables[changes$encoding == "bklm16"])
 
+summary(changes$before_variables)
+summary(changes$before_clauses)
+
 summary(changes$after_variables[changes$encoding == "bklm16"] / changes$before_variables[changes$encoding == "bklm16"])
 summary(1 - changes$after_variables[changes$encoding != "sbk05"] / changes$before_variables[changes$encoding != "sbk05"])
 hist(changes$after_variables[changes$encoding != "sbk05"] / changes$before_variables[changes$encoding != "sbk05"])

### 2021-05-08 doc/paper3/box.tex
Writing about experiments
Preparing the camera-ready version

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-02-28 16:52:48
+% Created by tikzDevice version 0.12.3.1 on 2021-05-08 15:35:22
 % !TEX encoding = UTF-8 Unicode
+\documentclass[10pt]{article}
+\usepackage{tikz}
+
+\usepackage[active,tightpage,psfixbb]{preview}
+
+\PreviewEnvironment{pgfpicture}
+
+\setlength\PreviewBorder{0pt}
+\begin{document}
+
 \begin{tikzpicture}[x=1pt,y=1pt]
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.48, 65.20) -- ( 54.75, 65.20);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.48, 65.31) -- ( 54.75, 65.31);
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.99, 66.74) -- ( 79.26, 66.74);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.99, 66.85) -- ( 79.26, 66.85);
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.50, 66.74) -- (103.77, 66.74);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.50, 66.85) -- (103.77, 66.85);
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (120.01, 57.40) -- (128.28, 57.40);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (120.01, 57.43) -- (128.28, 57.43);
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (144.97, 53.85) -- (161.51, 53.85);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (144.97, 53.86) -- (161.51, 53.86);
 \definecolor{drawColor}{gray}{0.70}
@@
 \end{tikzpicture}
+
+\end{document}

### 2021-05-08 doc/paper3/paper.tex
Small changes
Preparing the camera-ready version

@@
 \usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
 \usepackage{amssymb}
@@
 
-%\title{Contribution Title\thanks{Supported by organization x.}}
+% TODO: Check author % instructions in the lncs/ directory.
+% TODO: Make sure that the paper fits into 15 pages.
+
 \title{Weighted Model Counting Without Parameter Variables}
 
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-
-%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
-
-%\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-
-%\institute{Princeton University, Princeton NJ 08544, USA \and
-%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-%\email{lncs@springer.com}\\
-%\url{http://www.springer.com/gp/computer-science/lncs} \and
-%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-%\email{\{abc,lncs\}@uni-heidelberg.de}}
-
-\maketitle              % typeset the header of the contribution
-
-% The abstract should briefly summarize the contents of the paper in
-% 150--250 words.
-% 1. Introduction. In one sentence, what’s the topic?
-% 2. State the problem you tackle.
-% 3. Summarize (in one sentence) why nobody else has adequately answered the research question yet.
-% 4. Explain, in one sentence, how you tackled the research question.
-% 5. In one sentence, how did you go about doing the research that follows from your big idea.
-% 6. As a single sentence, what’s the key impact of your research?
+\author{Paulius Dilkas\inst{1} \and
+Vaishak Belle\inst{1,2}}
+% TODO: maybe add an envelope or two?
+
+\authorrunning{P. Dilkas and V. Belle}
+
+\institute{University of Edinburgh, Edinburgh, UK \\
+  \email{p.dilkas@sms.ed.ac.uk, vaishak@ed.ac.uk} \and Alan Turing Institute, London, UK}
+
+\maketitle
+
 \begin{abstract}
@@
   \keywords{Weighted model counting \and Probabilistic inference \and Bayesian
-    networks.}
+    networks}
 \end{abstract}
@@
 
-% NOTE: What is the problem? Why is it interesting and important?
 Weighted model counting (WMC), i.e., a generalisation of propositional model
@@
 heuristics.
-
-% NOTE: What's wrong with previous proposed solutions? How does mine differ?
+% TODO: While the complexity results in the cited papers [2, 32] have various
+% widths as the dominant (i.e., exponential) part of the formula, the number of
+% variables is featured as well, e.g., as $n$ in [2]. We did not notice a
+% significant difference in treewidth before and after performing our
+% transformation (we can include details about this in the final version of the
+% paper). The observed performance improvement is more likely related to the
+% variable ordering heuristic used by ADDs.
+% One important aspect that is not analyzed is how the technique affects the
+% treewidth of the instance.
+% This is important because DPMC makes use of tree decompositions of low width.
+% In particular, from a theoretical standpoint the questions are whether the
+% given reduction can increase or decrease the treewidth, and if yes, are there
+% any bounds to it.
+% (to me it seems that the reduction can decrease treewidth but cannot increase
+% it)
+% From practical standpoint the question is how the widths of the tree
+% decompositions used by DPMC+bklm16 and DPMC+bklm16++ compare.
+% Do you have any data on this?
+% Also related to treewidth, the sentence "As the parameterised complexity of
+% model counting (and, by extension, WMC) depends on the number of variables [2,
+% 32], ..." sounds very weird because the cited papers consider the complexity
+% parameterized by treewidth.
+% Should "number of variables" be replaced by "treewidth"?
+
 One approach to this problem considers weighted clauses and probabilistic
@@
 
-% NOTE: What are the key components of my approach and results? Also include any
-% specific limitations. What about your project is new or different from
-% existing solutions? List of refutable contributions (with forward references
-% to the rest of the paper) What is the outcome of the project?
+% TODO: We chose to transform existing encodings instead of creating a new one
+% because encodings such as cd05, cd06, and bklm16 do a good job at reducing
+% each CPT to a minimal logical representation by using techniques such as prime
+% implicants and limited forms of resolution. We wanted to reuse and build on
+% these ideas.
+
 In this work, we introduce a way to transform WMC problems into a new format
@@
   minimum-cardinality WMC to make this work, \texttt{bklm16} achieves the same
-  thing by adjusting weights.
+  thing by adjusting weights.\footnote{Note that since \texttt{cd05} and
+    \texttt{cd06} are minimum-cardinality WMC encodings, they are not supported
+    by most WMC algorithms.}
 \end{example}
@@
 
+% TODO: Examples can be added for illustration of the transformation algorithm.
+% TODO:  We will update the camera-ready version of the paper with a complete
+% description of how the input format was adjusted to support a new type of
+% problem instance. In short, we replace the weight lines of the form 'w
+% <variable> <positive weight>' with 'w <conjunction of literals> <positive
+% weight> <negative weight>'. The input format is restricted to conjunctions for
+% simplicity, but, of course, the algorithm can accept arbitrary formulas.
 \begin{algorithm}[t]
@@
   $\omega \gets 1$\;
-%  let $d\colon X_P \to \mathbb{N}$ be defined as $p \mapsto |\{ o \in X_P \mid o
-%  \le p \}|$\;
   \ForEach{clause $c \in \phi$\label{line:foreach1start}}{
@@
   }
-%  replace every variable $v$ in $F$ with $\rename{$v$}$\;
-%  \Return{$(F, X_I, \omega)$}\;
-%  \Fn{\rename{$v$}}{
-%    $S \gets \{u \in X_P \mid u \le v\}$\;
-%    \lIf{$S = \emptyset$}{\Return{$v$}}
-%    \Return{$v - d(\max S)$}\;
-%  }
 \end{algorithm}
@@
 
-In this section, we outline key properties that a (WMC or minimum-cardinality
+In this section, we outline key conditions that a (WMC or minimum-cardinality
 WMC) encoding has to satisfy for \cref{alg:transformation} to output an
@@
 (i.e., \texttt{cd05} and \texttt{cd06}). We begin by listing some properties of
-pseudo-Boolean functions and establishing a canonical transformation from WMC
-to PBP.
+pseudo-Boolean functions and establishing a canonical transformation from WMC to
+PBP.
 
@@
 \end{proposition}
-% It’s a bit strange to say same answer, when you don’t precisely refer to
-% this anywhere. One option is to say the above is the WMC instance and let
-% Delta be the weighted model count. Then the new encoding Has a weighted model
-% count of delta as well. Or something like that.
-% But looking at the text below, I see that you use this phrasing everywhere,
-% and I admit my formulation is awkward. So maybe the best compromise here is
-% just simply add a footnote explaining what exactly you mean when you say same
-% answer
+
 \begin{proof}
@@
     \phi_p} [c]_0^1$. We can rearrange the right-hand side as
-  % \begin{align*}
-  %   \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1 &= \exists_p [p]_{1-w(p)}^{w(p)} \left[\bigwedge_{c \in \phi_p} c\right]_0^1 = \exists_p [p]_{1-w(p)}^{w(p)} \left[ p \lor \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 \\
-  %                                                              &= w(p) + (1-w(p)) \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^1 = w(p) + \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_0^{1-w(p)} \\
-  %                                                              &= \left[ \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_{w(p)}^1 = \left[ \neg \bigwedge_{c \in \phi_p} c \setminus \{ p \} \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \neg(c \setminus \{ p \}) \right]_1^{w(p)} \\
-  %                                                              &= \left[ \bigvee_{c \in \phi_p} \neg \bigvee_{l \in c \setminus \{ p \}} l \right]_1^{w(p)} = \left[ \bigvee_{c \in \phi_p} \bigwedge_{l \in c \setminus \{ p \}} \neg l \right]_1^{w(p)}.
-  % \end{align*}
   \begin{align*}
@@
 slightly less explicit and assumes that $\omega = 1$.
-% We assume that $\omega = 1$ (i.e., $\{ p \} \not\in \phi$ for all parameter
-% variables $p \in X_P$) as the proof can be easily extended to handle $\omega
-% \neq 1$ similarly to the proof of \cref{thm:correctness}.
 
@@
 We run a set of experiments, comparing all five original Bayesian network
-encodings (\texttt{bklm16}, \texttt{cd05}, \texttt{cd06}, \texttt{d02}
+encodings (\texttt{bklm16}, \texttt{cd05}, \texttt{cd06}, \texttt{d02},
 \texttt{sbk05}) as well as the first four with \cref{alg:transformation} applied
@@
   \centering
-  \input{cumulative.tex}%
+  \includegraphics{cumulative}
   \caption{Cactus plot of all algorithm-encoding pairs. The dotted line
@@
   \centering
-  \input{scatter.tex}%
+  \includegraphics{scatter}
   \caption{An instance-by-instance comparison between $\textsf{DPMC} +
@@
     \centering
-    \input{box.tex}%
+    \includegraphics{box}
     \caption{Box plots of the numbers of variables in each encoding across all
@@
 
-\section{Conclusion} % So what?
+\section{Conclusion}
 
@@
 
-% TODO: consider moving (some) proofs to the appendix or at least making a clear
-% argument why they should be in the text.
-% If it is the case that you cannot include the proofs in line, and indeed
-% it might be better for readability to have an appendix with all the proofs, it
-% might make sense to provide the type of argument you are using in the proofs
-% so that readers know what to expect when they look into it
+\paragraph{Acknowledgments.}
+The first author was supported by the EPSRC Centre for Doctoral Training in
+Robotics and Autonomous Systems, funded by the UK Engineering and Physical
+Sciences Research Council (grant EP/L016834/1). This work has made use of the
+resources provided by the Edinburgh Compute and Data Facility (ECDF)
+(\url{http://www.ecdf.ed.ac.uk/}).
+% TODO: should I add something for him as well?
 

### 2021-05-08 tools/plots_for_SAT.R

@@ -8,26 +8,18 @@ library(ggpubr)
 library(tidyr)
 library(RColorBrewer)
 
-# TODO: plot treewidth vs add width
 data <- read.csv("../results/results.csv", header = TRUE, sep = ",")
 
-# TODO: remove (just for testing)
-data <- data[data$dataset != "2004-PGM",]
-data$encoding_time[grepl("pp$", data$encoding)] <- 0
-data <- data[is.na(data$answer) | data$answer < 1e-10,]
-data <- data[is.na(data$answer) | data$answer > 1e-3 & data$answer < 1,]
-data$encoding_time <- 0
-
-# TODO: how many times does each encoding produce the wrong answer?
-temp <- data %>% left_join(data[data$encoding == "cd06" &
-                                   data$novelty == "old",
-                                 c("instance", "answer")], by = "instance") %>%
-  left_join(data[data$encoding == "cw" & data$novelty == "new", c("instance", "answer")], by = "instance")
-temp$answer.y <- ifelse(is.na(temp$answer.y), temp$answer, temp$answer.y)
-removed <- temp[which(!is.na(temp$answer.y) & abs(temp$answer.x - temp$answer.y) > 0.01),]
-temp <- temp[which(is.na(temp$answer.y) | abs(temp$answer.x - temp$answer.y) < 0.01),]
-data <- subset(temp, select = -c(answer.y, answer))
-names(data)[names(data) == 'answer.x'] <- 'answer'
+# how many times does each encoding produce the wrong answer?
+# temp <- data %>% left_join(data[data$encoding == "cd06" &
+#                                    data$novelty == "old",
+#                                  c("instance", "answer")], by = "instance") %>%
+#   left_join(data[data$encoding == "cw" & data$novelty == "new", c("instance", "answer")], by = "instance")
+# temp$answer.y <- ifelse(is.na(temp$answer.y), temp$answer, temp$answer.y)
+# removed <- temp[which(!is.na(temp$answer.y) & abs(temp$answer.x - temp$answer.y) > 0.01),]
+# temp <- temp[which(is.na(temp$answer.y) | abs(temp$answer.x - temp$answer.y) < 0.01),]
+# data <- subset(temp, select = -c(answer.y, answer))
[…]

### 2021-05-09 doc/paper3/paper.tex
Ready?

@@
 \usepackage[inline]{enumitem}
+\usepackage[misc,geometry]{ifsym}
 
@@
 
-% TODO: Check author % instructions in the lncs/ directory.
-% TODO: Make sure that the paper fits into 15 pages.
-
 \title{Weighted Model Counting Without Parameter Variables}
 
-\author{Paulius Dilkas\inst{1} \and
+\author{Paulius Dilkas\inst{1}$^{(\textrm{\Letter})}$ \and
 Vaishak Belle\inst{1,2}}
-% TODO: maybe add an envelope or two?
 
@@
 \cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06,DBLP:conf/kr/Darwiche02,DBLP:conf/aaai/SangBK05}.
-As the parameterised complexity of model counting (and, by extension, WMC)
-depends on the number of variables
-\cite{DBLP:conf/focs/BacchusDP03,DBLP:journals/jda/SamerS10}, this can make WMC
-unnecessarily slow and could be detrimental to WMC algorithms such as
-\textsf{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} that depend on variable ordering
-heuristics.
-% TODO: While the complexity results in the cited papers [2, 32] have various
-% widths as the dominant (i.e., exponential) part of the formula, the number of
-% variables is featured as well, e.g., as $n$ in [2]. We did not notice a
-% significant difference in treewidth before and after performing our
-% transformation (we can include details about this in the final version of the
-% paper). The observed performance improvement is more likely related to the
-% variable ordering heuristic used by ADDs.
-% One important aspect that is not analyzed is how the technique affects the
-% treewidth of the instance.
-% This is important because DPMC makes use of tree decompositions of low width.
-% In particular, from a theoretical standpoint the questions are whether the
-% given reduction can increase or decrease the treewidth, and if yes, are there
-% any bounds to it.
-% (to me it seems that the reduction can decrease treewidth but cannot increase
-% it)
-% From practical standpoint the question is how the widths of the tree
-% decompositions used by DPMC+bklm16 and DPMC+bklm16++ compare.
-% Do you have any data on this?
-% Also related to treewidth, the sentence "As the parameterised complexity of
-% model counting (and, by extension, WMC) depends on the number of variables [2,
-% 32], ..." sounds very weird because the cited papers consider the complexity
-% parameterized by treewidth.
-% Should "number of variables" be replaced by "treewidth"?
+This can be particularly detrimental to WMC algorithms that rely on variable
+ordering heuristics.
+% As the parameterised complexity of model counting (and, by extension, WMC)
+% depends on the number of variables
+% \cite{DBLP:conf/focs/BacchusDP03,DBLP:journals/jda/SamerS10}, this can make WMC
+% unnecessarily slow and could be detrimental to WMC algorithms such as
+% \textsf{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} that depend on variable ordering
+% heuristics.
 
@@
 available implementation.
-
-% TODO: We chose to transform existing encodings instead of creating a new one
-% because encodings such as cd05, cd06, and bklm16 do a good job at reducing
-% each CPT to a minimal logical representation by using techniques such as prime
-% implicants and limited forms of resolution. We wanted to reuse and build on
-% these ideas.
 
@@
 suspect that this issue was not identified during the original set of
-experiments because they never looked at numerical answers.
+experiments because the authors never looked at numerical answers.
 
@@
 functions are particularly convenient because \textsf{DPMC} can be easily
-adapted to use them as input, and they are easily representable in both text
-files and using the syntax proposed in this paper.
+adapted to use them as input. Since we will only encounter functions of
+the form $[\phi]^a_b$, where $\phi$ is a conjunction of literals, we can
+represent it in text as \texttt{w $\langle\phi\rangle$ a b} where
+$\langle\phi\rangle$ is a representation of $\phi$ analogous to the
+representation of a clause in the DIMACS CNF format.
 
@@
 
-% TODO: Examples can be added for illustration of the transformation algorithm.
-% TODO:  We will update the camera-ready version of the paper with a complete
-% description of how the input format was adjusted to support a new type of
-% problem instance. In short, we replace the weight lines of the form 'w
-% <variable> <positive weight>' with 'w <conjunction of literals> <positive
-% weight> <negative weight>'. The input format is restricted to conjunctions for
-% simplicity, but, of course, the algorithm can accept arbitrary formulas.
 \begin{algorithm}[t]
@@
 In this section, we describe an algorithm for transforming WMC instances to the
-PBP format while removing all parameter variables. The algorithm works on four
-out of the five Bayesian network encodings: \texttt{bklm16}
-\cite{DBLP:conf/ecai/BartKLM16}, \texttt{cd05}
+PBP format while removing all parameter variables. We chose to transform
+existing encodings instead of creating a new one to reuse already-existing
+techniques for encoding each CPT to its minimal logical representation such as
+prime implicants and limited forms of resolution
+\cite{DBLP:conf/ecai/BartKLM16,DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.
+The transformation algorithm works on four out of the five Bayesian network
+encodings: \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}, \texttt{cd05}
 \cite{DBLP:conf/ijcai/ChaviraD05}, \texttt{cd06}
@@
 \cite{DBLP:conf/kr/Darwiche02}. There is no obvious way to adjust it to work
-with \texttt{sbk05} because the roles of indicator and parameter (i.e.,
-`chance') variables overlap \cite{DBLP:conf/aaai/SangBK05}. The algorithm is
-based on several observations that will be made more precise in
+with \texttt{sbk05} because the roles of indicator and parameter variables
+overlap \cite{DBLP:conf/aaai/SangBK05}.
+
+The algorithm is based on several observations that will be made more precise in
 \cref{sec:proof}. First, all weights except for $\{w(p) \mid p \in X_P\}$ are
@@
 a single parameter variable, we incorporate it into $\omega$. If a clause is
-of the form $\alpha \Rightarrow p$, where $p \in X_P$ and $\alpha$ is a
+of the form $\alpha \Rightarrow p$, where $p \in X_P$, and $\alpha$ is a
 conjunction of literals over $X_I$, we transform it into a pseudo-Boolean
-function $[\alpha]_1^{w(p)}$. If a clause (say, $c \in \phi$) has no parameter
+function $[\alpha]_1^{w(p)}$. If a clause $c \in \phi$ has no parameter
 variables, we reformulate it into a pseudo-Boolean function $[c]_0^1$. Finally,
-if a clause has negative parameter literals, we skip it.
+clauses with negative parameter literals are omitted.
 
@@
   Let $f = \prod_{c \in \phi} [c]_0^1$, and $g = \prod_{x \in X_I \cup X_P}
-  [x]_{w(\neg x)}^{w(x)}$. Then the WMC answer is
-  \eqref{eq:new_wmc} is
-  \[
-    (\exists_{X_I \cup X_P} fg)(\emptyset) = \sum_{Y \subseteq X_I \cup X_P}
-    (fg)(Y) = \sum_{Y \subseteq X_I \cup X_P} f(Y)g(Y)
-  \]
-  by \cref{lemma:sum}. Note that
+  [x]_{w(\neg x)}^{w(x)}$. Then the WMC answer of \eqref{eq:new_wmc} is
+  $(\exists_{X_I \cup X_P} fg)(\emptyset) = \sum_{Y \subseteq X_I \cup X_P}
+  (fg)(Y) = \sum_{Y \subseteq X_I \cup X_P} f(Y)g(Y)$ by \cref{lemma:sum}. Note
+  that
   \[
@@
   one of the two summands in \cref{eq:bigsums} will be equal to one, and the
-  other will be equal to zero, and so
-  \[
-    \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
-      \right]_0^1\right|_{p=1} + \left.\left[ p \Leftrightarrow \bigwedge_{i=1}^n
-        l_i \right]_0^1\right|_{p=0} = 1,
-  \]
-  where $1$ is a pseudo-Boolean function that always returns one. On the other
-  side of \cref{eq:to_show}, since $F_p = \emptyset$, and $\omega$ is unchanged,
-  we get $\omega\prod_{f \in F_p} f = 1$, and so \cref{eq:to_show} is satisfied
-  under \cref{cond:d02} when $w(p) = 1$.
+  other will be equal to zero, and so $\left.\left[ p \Leftrightarrow
+      \bigwedge_{i=1}^n l_i \right]_0^1\right|_{p=1} + \left.\left[ p
+      \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1\right|_{p=0} = 1$, where
+  $1$ is a pseudo-Boolean function that always returns one. On the other side of
+  \cref{eq:to_show}, since $F_p = \emptyset$, and $\omega$ is unchanged, we get
+  $\omega\prod_{f \in F_p} f = 1$, and so \cref{eq:to_show} is satisfied under
+  \cref{cond:d02} when $w(p) = 1$.
 
@@
   $\left[ \bigwedge_{i = 1}^n l_i \right]_1^{w(p)} = \exists_p [p]_1^{w(p)}
-  \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1$, and indeed
-  \[
-    \exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
+  \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i \right]_0^1$. Indeed,
+  $\exists_p [p]_1^{w(p)} \left[ p \Leftrightarrow \bigwedge_{i=1}^n l_i
   \right]_0^1 = w(p) \cdot \left[ \bigwedge_{i=1}^n l_i \right]_0^1 + \left[
     \bigwedge_{i=1}^n l_i \right]_1^0 = \left[ \bigwedge_{i=1}^n l_i
-    \right]_1^{w(p)}.
-  \]
-  This finishes the proof of the correctness of the first loop under
-  \cref{cond:d02}.
+  \right]_1^{w(p)}$. This finishes the proof of the correctness of the first
+  loop under \cref{cond:d02}.
 
@@
   and so the left-hand side of \cref{eq:to_show} is equal to one. Then the
-  right-hand side is
-  \[
-    \exists_p [p]_0^1 \prod_{c \in \phi_p} [c]_0^1 = \exists_p \left[ p \land
-      \bigwedge_{c \in \phi_p} c \right]_0^1 = \exists_p [p]_0^1 = 0 + 1 = 1
-  \]
-  since $p \in c$ for every clause $c \in \phi_p$.
+  right-hand side is $\exists_p [p]_0^1 \prod_{c \in \phi_p} [c]_0^1 = \exists_p
+  \left[ p \land \bigwedge_{c \in \phi_p} c \right]_0^1 = \exists_p [p]_0^1 = 0
+  + 1 = 1$ since $p \in c$ for every clause $c \in \phi_p$.
 
@@
   \cref{cond:just_parameter}, $\phi_p = \{ \{ p \} \}$, and
-  \cref{alg:transformation} produces $F_p = \emptyset$ and $\omega = w(p)$, and
-  so
-  \[
-    \exists_p [p]_{w(\neg p)}^{w(p)} [p]_0^1 = \exists_p [p]^{w(p)}_0 = w(p) =
-    \omega \prod_{f \in F_p} f.
-  \]
-  The only remaining case is when $w(p) \ne 1$ and $\{ p \} \not \in \phi_p$.
-  Then $\omega = 1$, and $F_p = \left\{ \left[\bigwedge_{l \in c \setminus \{ p
-        \}} \neg l\right]_1^{w(p)} \;\middle|\; c \in \phi_p \right\}$, so we
-  need to show that $\prod_{c \in \phi_p} \left[\bigwedge_{l \in c \setminus \{
-      p \}} \neg l\right]_1^{w(p)} = \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in
-    \phi_p} [c]_0^1$. We can rearrange the right-hand side as
+  \cref{alg:transformation} produces $F_p = \emptyset$, and $\omega = w(p)$, and
+  so $\exists_p [p]_{w(\neg p)}^{w(p)} [p]_0^1 = \exists_p [p]^{w(p)}_0 = w(p) =
+  \omega \prod_{f \in F_p} f$. The only remaining case is when $w(p) \ne 1$ and
+  $\{ p \} \not \in \phi_p$. Then $\omega = 1$, and $F_p = \left\{
+    \left[\bigwedge_{l \in c \setminus \{ p \}} \neg l\right]_1^{w(p)}
+    \;\middle|\; c \in \phi_p \right\}$, so we need to show that $\prod_{c \in
+    \phi_p} \left[\bigwedge_{l \in c \setminus \{p \}} \neg l\right]_1^{w(p)} =
+  \exists_p [p]_{1-w(p)}^{w(p)} \prod_{c \in \phi_p} [c]_0^1$. We can rearrange
+  the right-hand side as
   \begin{align*}
@@
   \centering
-  \includegraphics{cumulative}
+  \includegraphics[width=\textwidth]{cumulative}
   \caption{Cactus plot of all algorithm-encoding pairs. The dotted line
@@
   \centering
-  \includegraphics{scatter}
+  \includegraphics[width=\textwidth]{scatter}
   \caption{An instance-by-instance comparison between $\textsf{DPMC} +
@@
     \centering
-    \includegraphics{box}
+    \includegraphics[width=\textwidth]{box}
     \caption{Box plots of the numbers of variables in each encoding across all
@@
 variables for \texttt{d02}, the performance of $\textsf{DPMC}+\texttt{d02}$ is
-virtually unaffected. Finally, while our transformation makes it possible to use
-\texttt{cd05} and \texttt{cd06} with \textsf{DPMC}, the two combinations remain
-inefficient.
+virtually unaffected. It is also worth noting that there was no observable
+difference in the width of the project-join tree used by DPMC
+\cite{DBLP:conf/cp/DudekPV20} before and after applying
+\cref{alg:transformation}---the observed performance improvement is more likely
+related to the variable ordering heuristic used by ADDs. Finally, while our
+transformation makes it possible to use \texttt{cd05} and \texttt{cd06} with
+\textsf{DPMC}, the two combinations remain inefficient.
 
@@
 
-\paragraph{Acknowledgments.}
+\subsubsection{Acknowledgments.}
 The first author was supported by the EPSRC Centre for Doctoral Training in
 Robotics and Autonomous Systems, funded by the UK Engineering and Physical
-Sciences Research Council (grant EP/L016834/1). This work has made use of the
+Sciences Research Council (grant EP/L016834/1). The second author was supported
+by a Royal Society University Research Fellowship. This work has made use of the
 resources provided by the Edinburgh Compute and Data Facility (ECDF)
 (\url{http://www.ecdf.ed.ac.uk/}).
-% TODO: should I add something for him as well?
 

### 2021-05-13 doc/paper3/paper.tex
Remove data

@@
 \begin{proof}
-  If $X = \{x\}$, then
-  \[
-    (\exists_xf)(\emptyset) = (f|_{x=1} + f|_{x=0})(\emptyset) =
-    f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset) = \sum_{Y \subseteq \{x\}} f(Y).
-  \]
-  This easily extends to $|X| > 1$ by the definition of projection on sets of
-  variables.
+  If $X = \{x\}$, then $(\exists_xf)(\emptyset) = (f|_{x=1} +
+  f|_{x=0})(\emptyset) = f|_{x=1}(\emptyset) + f|_{x=0}(\emptyset) = \sum_{Y
+    \subseteq \{x\}} f(Y)$. This easily extends to $|X| > 1$ by the definition
+  of projection on sets of variables.
 \end{proof}
@@
 greedy mode. This mode (which was not part of the original paper
-\cite{DBLP:conf/cp/DudekPV20}) optimises the order in which pseudo-Boolean
-functions are multiplied by prioritising functions with small representations.
+\cite{DBLP:conf/cp/DudekPV20}) optimises the order in which ADDs are multiplied
+by prioritising those with small representations.
 
@@
 
+It is also worth noting that there was no observable difference in the width of
+the project-join tree used by DPMC \cite{DBLP:conf/cp/DudekPV20} (which is
+equivalent to the treewidth of the primal/Gaifman graph of the input formula)
+before and after applying \cref{alg:transformation}---the observed performance
+improvement is more likely related to the variable ordering heuristic used by
+ADDs.\footnote{The data on this (along with the implementation of
+  \cref{alg:transformation}) is available at
+  \url{https://github.com/dilkas/wmc-without-parameters}.}
+
 Overall, transforming WMC instances to the PBP format allows us to significantly
@@
 variables for \texttt{d02}, the performance of $\textsf{DPMC}+\texttt{d02}$ is
-virtually unaffected. It is also worth noting that there was no observable
-difference in the width of the project-join tree used by DPMC
-\cite{DBLP:conf/cp/DudekPV20} before and after applying
-\cref{alg:transformation}---the observed performance improvement is more likely
-related to the variable ordering heuristic used by ADDs. Finally, while our
+virtually unaffected. Finally, while our
 transformation makes it possible to use \texttt{cd05} and \texttt{cd06} with
@@
 \subsubsection{Acknowledgments.}
-The first author was supported by the EPSRC Centre for Doctoral Training in
-Robotics and Autonomous Systems, funded by the UK Engineering and Physical
-Sciences Research Council (grant EP/L016834/1). The second author was supported
-by a Royal Society University Research Fellowship. This work has made use of the
-resources provided by the Edinburgh Compute and Data Facility (ECDF)
+We thank the anonymous reviewers for their helpful comments. The first author
+was supported by the EPSRC Centre for Doctoral Training in Robotics and
+Autonomous Systems, funded by the UK Engineering and Physical Sciences Research
+Council (grant EP/L016834/1). The second author was supported by a Royal Society
+University Research Fellowship. This work has made use of the resources provided
+by the Edinburgh Compute and Data Facility (ECDF)
 (\url{http://www.ecdf.ed.ac.uk/}).

### 2021-05-13 doc/SAT_paper/paper.tex
Cleanup

--- 2021-05-13 doc/paper3/paper.tex
@@
 Furthermore, we identify sufficient conditions for transforming a WMC instance
-into our new format. As many WMC inference algorithms such as
-\textsf{Ace}, \textsf{c2d}
-\cite{DBLP:conf/ecai/Darwiche04}, and \textsf{miniC2D}
-\cite{DBLP:conf/ijcai/OztokD15} work by compilation to tractable representations
-such as arithmetic circuits, deterministic, decomposable negation normal form
-\cite{DBLP:journals/jancl/Darwiche01}, and sentential decision diagrams (SDDs)
-\cite{DBLP:conf/ijcai/Darwiche11}, another way to avoid parameter variables
-could be via direct compilation to a more convenient representation. Direct
-compilation of Bayesian networks to SDDs has been investigated
-\cite{DBLP:conf/ecsqaru/ChoiKD13}. However, SDDs only support weights on
-literals, and so are not expressive enough to avoid the issue. To the best of
-the authors' knowledge, neither approach
+into our new format. As many WMC inference algorithms
+\cite{DBLP:conf/ecai/Darwiche04,DBLP:conf/ijcai/OztokD15} work by compilation to
+tractable representations such as arithmetic circuits, deterministic,
+decomposable negation normal form \cite{DBLP:journals/jancl/Darwiche01}, and
+sentential decision diagrams (SDDs) \cite{DBLP:conf/ijcai/Darwiche11}, another
+way to avoid parameter variables could be via direct compilation to a more
+convenient representation. Direct compilation of Bayesian networks to SDDs has
+been investigated \cite{DBLP:conf/ecsqaru/ChoiKD13}. However, SDDs only support
+weights on literals, and so are not expressive enough to avoid the issue. To the
+best of the authors' knowledge, neither approach
 \cite{DBLP:conf/ecsqaru/ChoiKD13,DBLP:conf/uai/GogateD10} has a publicly
@@
 
-We begin with an overview of some notation and terminology. Throughout the
-paper, we use set-theoretic notation for many concepts in logic. A \emph{clause}
-is a set of literals that are part of an implicit disjunction. Similarly, a
-\emph{formula} in CNF is a set of clauses that are part of an implicit
-conjunction. We identify a \emph{model} with a set of variables that correspond
-to the positive literals in the model (and all other variables are the negative
-literals of the model). We can then define the \emph{cardinality} of a model as
-the cardinality of this set. For example, let $\phi = (\neg a \lor b) \land a$
-be a propositional formula over variables $a$ and $b$. Then an equivalent
-set-theoretic representation of $\phi$ is $\{ \{ \neg a, b \}, \{ a \} \}$. Any
-subset of $\{ a, b \}$ is an interpretation of $\phi$, e.g., $\{ a, b \}$ is a
-model of $\phi$ (written $\{ a, b \} \models \phi$) of cardinality two, while
-$\emptyset$ is an interpretation but not a model. We can now formally define
-WMC.
+We begin with an overview of some notation and terminology. We use $\land$,
+$\lor$, $\neg$, $\Rightarrow$, and $\Leftrightarrow$ to denote conjunction,
+disjunction, negation, material implication, and material biconditional,
+respectively. Throughout the paper, we use set-theoretic notation for many
+concepts in logic. A \emph{clause} is a set of literals that are part of an
+implicit disjunction. Similarly, a \emph{formula} in CNF is a set of clauses
+that are part of an implicit conjunction. We identify a \emph{model} with a set
+of variables that correspond to the positive literals in the model (and all
+other variables are the negative literals of the model). We can then define the
+\emph{cardinality} of a model as the cardinality of this set. For example, let
+$\phi = (\neg a \lor b) \land a$ be a propositional formula over variables $a$
+and $b$. Then an equivalent set-theoretic representation of $\phi$ is $\{ \{
+\neg a, b \}, \{ a \} \}$. Any subset of $\{ a, b \}$ is an interpretation of
+$\phi$, e.g., $\{ a, b \}$ is a model of $\phi$ (written $\{ a, b \} \models
+\phi$) of cardinality two, while $\emptyset$ is an interpretation but not a
+model. We can now formally define WMC.
 
@@
 It is also worth noting that there was no observable difference in the width of
-the project-join tree used by DPMC \cite{DBLP:conf/cp/DudekPV20} (which is
-equivalent to the treewidth of the primal/Gaifman graph of the input formula)
-before and after applying \cref{alg:transformation}---the observed performance
+the project-join tree used by DPMC (which is equivalent to the treewidth of the
+primal/Gaifman graph of the input formula \cite{DBLP:conf/cp/DudekPV20}) before
+and after applying \cref{alg:transformation}---the observed performance
 improvement is more likely related to the variable ordering heuristic used by

### 2021-05-13 doc/UAI_paper/melt.tex
Cleanup

% Created by tikzDevice version 0.12.3.1 on 2021-02-08 17:04:18
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (469.75,173.45);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (469.75,173.45);
\end{scope}
\begin{scope}
\path[clip] ( 36.11, 30.69) rectangle (208.43,151.38);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 36.11, 30.69) rectangle (208.43,151.38);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 36.11, 50.08) --
	(208.43, 50.08);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 36.11, 77.91) --
	(208.43, 77.91);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 36.11,105.73) --
	(208.43,105.73);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 36.11,133.56) --
	(208.43,133.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 36.17) --
	(208.43, 36.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 64.00) --
	(208.43, 64.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 91.82) --
	(208.43, 91.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11,119.64) --
	(208.43,119.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11,147.47) --
	(208.43,147.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 52.79, 30.69) --
	( 52.79,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 80.58, 30.69) --
	( 80.58,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (108.37, 30.69) --
	(108.37,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (136.17, 30.69) --
	(136.17,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (163.96, 30.69) --
	(163.96,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (191.76, 30.69) --
	(191.76,151.38);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 40.28, 36.17) rectangle ( 65.29,111.99);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] ( 40.28,111.99) rectangle ( 65.29,123.08);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 68.07, 36.17) rectangle ( 93.09, 85.55);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] ( 68.07, 85.55) rectangle ( 93.09, 89.74);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 95.87, 36.17) rectangle (120.88, 76.88);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] ( 95.87, 76.88) rectangle (120.88, 81.34);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (151.46, 36.17) rectangle (176.47, 98.96);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (151.46, 98.96) rectangle (176.47,102.91);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (179.25, 36.17) rectangle (204.26, 47.56);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (179.25, 47.56) rectangle (204.26, 73.20);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.62,131.57) --
	( 56.96,131.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.79,131.57) --
	( 52.79, 92.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.62, 92.41) --
	( 56.96, 92.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.62,145.89) --
	( 56.96,145.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.79,145.89) --
	( 52.79,100.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.62,100.26) --
	( 56.96,100.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.41, 99.71) --
	( 84.75, 99.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.58, 99.71) --
	( 80.58, 71.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.41, 71.38) --
	( 84.75, 71.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.41,104.66) --
	( 84.75,104.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.58,104.66) --
	( 80.58, 74.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.41, 74.82) --
	( 84.75, 74.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.21, 88.40) --
	(112.54, 88.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.37, 88.40) --
	(108.37, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.21, 65.36) --
	(112.54, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.21, 93.67) --
	(112.54, 93.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.37, 93.67) --
	(108.37, 69.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.21, 69.01) --
	(112.54, 69.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.79,115.90) --
	(168.13,115.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (163.96,115.90) --
	(163.96, 82.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.79, 82.02) --
	(168.13, 82.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.79,120.62) --
	(168.13,120.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (163.96,120.62) --
	(163.96, 85.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.79, 85.20) --
	(168.13, 85.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.59, 51.93) --
	(195.93, 51.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.76, 51.93) --
	(191.76, 43.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.59, 43.18) --
	(195.93, 43.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.59, 88.00) --
	(195.93, 88.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.76, 88.00) --
	(191.76, 58.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.59, 58.41) --
	(195.93, 58.41);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 36.11, 30.69) rectangle (208.43,151.38);
\end{scope}
\begin{scope}
\path[clip] (213.93, 30.69) rectangle (386.25,151.38);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (213.93, 30.69) rectangle (386.25,151.38);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] (213.93, 50.08) --
	(386.25, 50.08);

\path[draw=drawColor,line width= 0.1pt,line join=round] (213.93, 77.91) --
	(386.25, 77.91);

\path[draw=drawColor,line width= 0.1pt,line join=round] (213.93,105.73) --
	(386.25,105.73);

\path[draw=drawColor,line width= 0.1pt,line join=round] (213.93,133.56) --
	(386.25,133.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (213.93, 36.17) --
	(386.25, 36.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] (213.93, 64.00) --
	(386.25, 64.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] (213.93, 91.82) --
	(386.25, 91.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (213.93,119.64) --
	(386.25,119.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (213.93,147.47) --
	(386.25,147.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.61, 30.69) --
	(230.61,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (258.40, 30.69) --
	(258.40,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (286.20, 30.69) --
	(286.20,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (313.99, 30.69) --
	(313.99,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (341.78, 30.69) --
	(341.78,151.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (369.58, 30.69) --
	(369.58,151.38);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (218.10, 36.17) rectangle (243.12, 36.39);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (218.10, 36.39) rectangle (243.12, 74.95);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (301.48, 36.17) rectangle (326.50, 37.47);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (301.48, 37.47) rectangle (326.50, 78.97);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (329.28, 36.17) rectangle (354.29, 39.40);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (329.28, 39.40) rectangle (354.29, 96.79);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (357.07, 36.17) rectangle (382.08, 39.31);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (357.07, 39.31) rectangle (382.08,103.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.44, 36.50) --
	(234.78, 36.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 36.50) --
	(230.61, 36.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.44, 36.29) --
	(234.78, 36.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.44, 89.26) --
	(234.78, 89.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 89.26) --
	(230.61, 60.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.44, 60.63) --
	(234.78, 60.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.82, 38.33) --
	(318.16, 38.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.99, 38.33) --
	(313.99, 36.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.82, 36.60) --
	(318.16, 36.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.82, 94.93) --
	(318.16, 94.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.99, 94.93) --
	(313.99, 63.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.82, 63.01) --
	(318.16, 63.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.61, 39.96) --
	(345.95, 39.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (341.78, 39.96) --
	(341.78, 38.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.61, 38.83) --
	(345.95, 38.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.61,116.01) --
	(345.95,116.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (341.78,116.01) --
	(341.78, 77.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.61, 77.57) --
	(345.95, 77.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.41, 39.85) --
	(373.75, 39.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.58, 39.85) --
	(369.58, 38.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.41, 38.76) --
	(373.75, 38.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.41,122.50) --
	(373.75,122.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.58,122.50) --
	(369.58, 84.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.41, 84.17) --
	(373.75, 84.17);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.93, 30.69) rectangle (386.25,151.38);
\end{scope}
\begin{scope}
\path[clip] ( 36.11,151.38) rectangle (208.43,167.95);
\definecolor{fillColor}{gray}{0.70}

\path[fill=fillColor] ( 36.11,151.38) rectangle (208.43,167.95);
\definecolor{drawColor}{RGB}{255,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (122.27,156.63) {Originally};
\end{scope}
\begin{scope}
\path[clip] (213.93,151.38) rectangle (386.25,167.95);
\definecolor{fillColor}{gray}{0.70}

\path[fill=fillColor] (213.93,151.38) rectangle (386.25,167.95);
\definecolor{drawColor}{RGB}{255,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.09,156.63) {With \textsf{ADDMC}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 52.79, 27.94) --
	( 52.79, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 80.58, 27.94) --
	( 80.58, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (108.37, 27.94) --
	(108.37, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (136.17, 27.94) --
	(136.17, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (163.96, 27.94) --
	(163.96, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (191.76, 27.94) --
	(191.76, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 52.79, 19.68) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 80.58, 19.68) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (108.37, 19.68) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (136.17, 19.68) {\texttt{cw}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (163.96, 19.68) {\texttt{d02}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (191.76, 19.68) {\texttt{sbk05}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.61, 27.94) --
	(230.61, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (258.40, 27.94) --
	(258.40, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (286.20, 27.94) --
	(286.20, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (313.99, 27.94) --
	(313.99, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (341.78, 27.94) --
	(341.78, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (369.58, 27.94) --
	(369.58, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (230.61, 19.68) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (258.40, 19.68) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (286.20, 19.68) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (313.99, 19.68) {\texttt{cw}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (341.78, 19.68) {\texttt{d02}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (369.58, 19.68) {\texttt{sbk05}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 33.14) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 60.97) {25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 88.79) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16,116.61) {75};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16,144.44) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 33.36, 36.17) --
	( 36.11, 36.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 33.36, 64.00) --
	( 36.11, 64.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 33.36, 91.82) --
	( 36.11, 91.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 33.36,119.64) --
	( 36.11,119.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 33.36,147.47) --
	( 36.11,147.47);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 91.03) {Time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (397.25, 63.47) rectangle (464.25,118.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (402.75, 83.42) rectangle (417.21, 97.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (403.47, 84.14) rectangle (416.50, 97.17);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (402.75, 68.97) rectangle (417.21, 83.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (403.47, 69.68) rectangle (416.50, 82.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (422.71, 87.62) {Encoding};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (469.75,173.45);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (422.71, 73.17) {Inference};
\end{scope}
\end{tikzpicture}

### 2021-05-13 tools/SAT_plots_2.R

@@ -97,7 +97,7 @@ ggplot(df3, aes(encoding, value, fill = variable)) +
   scale_y_continuous(limits = quantile(df2$value, c(0, 0.7)))
 
 # number of variables vs. inference time: useless (at least so far)
-# NOTE: data comes from analyse.R
+# NOTE: data comes from SAT_plots.R
 data$instance <- sub("results/", "", data$instance)
 df4 <- melt(changes, id.vars = c("instance", "dataset", "encoding"), measure.vars = c("before_variables", "after_variables"))
 df4$encoding[df4$variable == "after_variables"] <- paste(df4$encoding[df4$variable == "after_variables"], "pp", sep = "")

### 2021-05-13 tools/encode.py

@@ -28,10 +28,6 @@ ACE_LEGACY = {
 BN2CNF = ['deps/bn2cnf_linux', '-e', 'LOG', '-s', 'prime']
 C2D = ['deps/ace/c2d_linux']
 CNF4DPMC = ['tools/cnf4dpmc/cnf4dpmc', '-f']
-PMC = [
-    'deps/pmc_linux', '-vivification', '-eliminateLit', '-litImplied',
-    '-iterate=10'
-]
 
 Goal = collections.namedtuple('Goal', ['variable', 'value', 'value_index'])
 
@@ -89,12 +85,7 @@ class LiteralDict:
 def exactly_one_constraint(literals, encoding):
     """Given a list of literals and encoding information, returns a list of
     lines that implement the 'exactly one' constraint on the list of literals
-    (that can then be inserted into a CNF or a PB file)."""
-    if encoding == 'cw_pb':
-        return [
-            ' '.join('+1 x{}'.format(literal)
-                     for literal in literals) + ' = 1;'
-        ]
+    (that can then be inserted into a CNF file)."""
     return ['{} 0'.format(' '.join(literals))] + [
         '-{} -{} 0'.format(literals[i], literals[j])
         for i in range(len(literals)) for j in range(i + 1, len(literals))
@@ -102,7 +93,7 @@ def exactly_one_constraint(literals, encoding):
 
 
 def bn2cnf(bn, literal_dict, encoding):
-    """Transforms a Bayesian network to a list of constraints/clauses. The
+    """Transforms a Bayesian network to a list of clauses. The
     return value is divided into two parts: regular clauses and weights.
     NOTE: This function has nothing to do with the external program with the
     same name."""
@@ -191,10 +182,7 @@ def bn2uai(bn):
 
 def encode_single_literal(literal, encoding):
     """Returns a string that encodes the given literal as a clause."""
-    if encoding != 'cw_pb':
-        return '{} 0'.format(literal)
-    return ('1 x{} = 0;'.format(literal[1:])
-            if literal.startswith('-') else '1 x{} = 1;'.format(literal))
+    return '{} 0'.format(literal)
 
 
 def new_evidence_file(network_filename, variable, value):
@@ -345,34 +333,15 @@ def run_legacy_ace(args, goal):
         ], args.memory)
 
 
-# ==================== Final output functions ====================
+# ==================== Final output function ====================
 
 
 def write_cnf_file(args, num_variables, clauses, weights):
-    """If there is a command-line flag for preprocessing, the function writes
[…]

### 2021-05-13 tools/kappa.R

@@ -1,30 +1,0 @@
-library(viridis)
-library(ggplot2)
-
-kappa <- function(treewidth, valuewidth) {
-  s <- valuewidth
-  t <- valuewidth
-  cat("treewidth:", treewidth, ", valuewidth: ", valuewidth, "\n")
-  for (i in seq(treewidth, 1, by = -1)) {
-#    if (2^(i-1) < t*(t-1)) {
-#      print("exponential is smaller")
-#    } else {
-#      print("quadratic is smaller")
-#    }
-    t <- min(2^(i-1), s*(s-1))
-    s <- s + t
-  }
-  return(s)
-}
-
-MIN <- 2
-MAX <- 100
-df <- data.frame(treewidth = rep(MIN:MAX, MAX-MIN+1),
-                 valuewidth = rep(MIN:MAX, each=MAX-MIN+1))
-df$kappa <- Vectorize(kappa)(df$treewidth, df$valuewidth)
-df$kappa2 <- (2^df$treewidth + df$valuewidth - df$kappa) / df$kappa
-ggplot(df, aes(treewidth, valuewidth, fill = kappa)) + geom_tile() +
-  scale_fill_viridis(trans = "log") +
-#  geom_text(aes(label = round(kappa, 1))) +
-  scale_x_continuous(breaks = MIN:MAX) +
-  scale_y_continuous(breaks = MIN:MAX)

### 2021-05-13 tools/parse_experimental_data.py

@@ -3,8 +3,6 @@ import glob
 import os
 import re
 
-TIMEOUT = 1000
-
 directories = [
     ('Grid/Ratio_50/', 'Grid-50'),
     ('Grid/Ratio_75/', 'Grid-75'),

### 2021-05-21 doc/UAI_paper/paper.tex
Cleanup
Update the UAI paper (still incomplete)

--- 2021-02-14 doc/paper2/paper.tex
@@
-\documentclass{uai2021} % for initial submission
-% \documentclass[accepted]{uai2021} % after acceptance, for a revised
-                                    % version; also before submission to
-                                    % see how the non-anonymous paper
-                                    % would look like
-%% There is a class option to choose the math font
-% \documentclass[mathfont=cm]{uai2021} % Computer Modern math instead of
-                                       % ptmx, like default for UAI ≤2020
-% \documentclass[mathfont=newtx]{uai2021} % newtx fonts (improves upon
-                                          % ptmx; less tested, no support)
-% NOTE: Only keep *one* line above as appropriate, as it will be replaced
-%       automatically for papers to be published. Do not make any other
-%       change above this note for an accepted version.
+\documentclass[accepted]{uai2021}
 
-%% Choose your variant of English; be consistent
-% \usepackage[american]{babel}
 \usepackage[british]{babel}
-
-%% Some suggested packages, as needed:
 \usepackage{natbib} % has a nice set of citation styles and commands
@@
 \usepackage{amsthm}
-\usepackage{thm-restate}
 \usepackage{subcaption}
@@
 \title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
+% TODO: maybe I should rotate the cumulative plot
+
+% TODO: read 'Preparing the submission materials' (code: dilkas_167)
+% TODO: update the abstract during submission
 
@@
 % information below.
-%
-% Add authors in order of decreasing contribution
-\author[1]{\href{mailto:Harry Q. Bovik <harryq@example.edu>?Subject=Your UAI 2021 paper}{Harry~Q.~Bovik}{}} % Lead author
-\author[2]{Coauthor~One}
-\author[1,2]{Coauthor~Two}
-\author[3]{Further~Coauthor}
-\author[1]{Further~Coauthor}
-\author[3]{Further~Coauthor}
-\author[3,1]{Further~Coauthor}
-% Add affiliations after the authors
+
+\author[1]{\href{mailto:Paulius Dilkas <p.dilkas@sms.ed.ac.uk>?Subject=Your UAI
+    2021 paper}{Paulius~Dilkas}{}}
+\author[1,2]{Vaishak~Belle}
 \affil[1]{%
-    Computer Science Dept.\\
-    Cranberry University\\
-    Pittsburgh, Pennsylvania, USA
+    School of Informatics\\
+    University of Edinburgh\\
+    Edinburgh, UK
 }
 \affil[2]{%
-    Affiliation\\
-    Address\\
-    …
+    Alan Turing Institute\\
+    London, UK
 }
-\affil[3]{…}
 
@@
   experiments show that the new encoding significantly improves the performance
-  of the algorithm on most benchmark instances. Furthermore, the same idea can
-  be adapted to other WMC algorithms and other problem domains.
+  of the algorithm on most benchmark instances.
 \end{abstract}
@@
 \section{Introduction}
-% TODO: keep mentioning citations along with algorithm and encoding names
 
@@
 
+% TODO: must reference the SAT paper and explain the differences
+% \cite{my_sat_paper}
+
 \section{Boolean Algebras, Power Sets, and Propositional
@@
     & $\top$ & $\{ \emptyset, \{a\}, \{b\}, \{a, b\} \}$ \\
-    & $\neg a \lor \neg b, a \to b$ & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{a\}, \{a, b\} \}$ \\
-    & $b \to a, a \lor b$ & $\{ \emptyset, \{b\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ \\
+    & $\neg a \lor \neg b, a \to b$ & $\{ \emptyset, \{a\}, \{b\} \}, \{ \emptyset, \{b\}, \{a, b\} \}$ \\
+    & $b \to a, a \lor b$ & $\{ \emptyset, \{a\}, \{a, b\} \}, \{ \{a\}, \{b\}, \{a, b\} \}$ \\
     & $\neg b, \neg a, a \leftrightarrow b$ & $\{\emptyset, \{a\}\}, \{\emptyset, \{b\}\}, \{\emptyset, \{a, b\}\}$ \\
@@
 \subsection{Functions on Boolean Algebras}
-% TODO: maybe: it would be easier to talk about pseudo-Boolean functions
-% instead, but maybe it's not necessary.
 
@@
 
-\begin{restatable}{theorem}{measure} \label{prop:measure}
+\begin{theorem} \label{prop:measure}
   The function $\mu_\nu$ is a measure.
-\end{restatable}
+\end{theorem}
 
@@
 practice.\footnote{The proofs of this and other theoretical results can be found
-  in the appendix.}
+  in the supplementary material.}
 
-\begin{restatable}{theorem}{extendable}
+\begin{theorem}
   For any set $U$ and measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$, there
@@
   \land f)$ for all formulas $x \in 2^{2^U}$.
-\end{restatable}
+\end{theorem}
 
@@
 multiply $\mathrm{CPT}_X$ by `clause' functions that restrict the value of
-$\phi(T)$ to zero whenever $|\mathcal{E}(X) \cap T| \ne 1$. For the Bayesian
-network in \cref{fig:example_bn}, we get:
+$\phi(T)$ to zero whenever $|\mathcal{E}(X) \cap T| \ne 1$, i.e., we add mutual
+exclusivity constraints that ensure that each random variable is associated with
+exactly one value. Note that \citet{DBLP:conf/ijcai/ChaviraD07} use the same ADD
+representation of CPTs for their compilation algorithm based on variable
+elimination. For the example Bayesian network in \cref{fig:example_bn}, we get:
 \begin{align*}
@@
 
-\begin{restatable}{lemma}{cptlemma} \label{lemma:cpt}
+\begin{lemma} \label{lemma:cpt}
   Let $X \in \mathcal{V}$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
@@
   \}$.
-\end{restatable}
+\end{lemma}
 
@@
 
-\begin{restatable}{lemma}{fulldistribution} \label{lemma:full_distribution}
+\begin{lemma} \label{lemma:full_distribution}
   Let $\mathcal{V} = \{X_1, \dots, X_n\}$. Then
@@
   for all $T \in 2^U$.
-\end{restatable}
+\end{lemma}
 
 We end with \cref{thm:correctness} that shows how $\phi$ can be combined with an
-encoding of a single variable-value assignment so that \textsf{ADDMC} would
-compute its marginal probability.
+encoding of a single variable-value assignment so that \textsf{ADDMC}
+\citep{DBLP:conf/aaai/DudekPV20} would compute its marginal probability.
 
-\begin{restatable}{theorem}{correctness} \label{thm:correctness}
+\begin{theorem} \label{thm:correctness}
   For any $X \in \mathcal{V}$ and $x \in \im X$,
@@
   \]
-\end{restatable}
+\end{theorem}
 
@@
 
-%\begin{figure*}[t] % TODO: maybe not: describe this in the text
-%  \centering
-%  \input{melt.tex}%
-%  \caption{Average encoding and inference time of each encoding with their
-%    original WMC algorithm (on the left) and with \textsf{ADDMC} (on the right)
-%    on \emph{solved} instances. The error bars denote \SI{10}{\percent} of
-%    standard deviation.}
-%  \label{fig:melted}
-%\end{figure*}
-
 We compare the six WMC encodings for Bayesian networks when run with both
-\textsf{ADDMC} and the WMC algorithms used in the original papers.\footnote{Both
-  \texttt{cd05} and \texttt{cd06} cannot be run with most WMC algorithms
-  including \textsf{ADDMC} because these encodings allow for additional models
-  that the WMC algorithm is supposed to ignore
+\textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} and the WMC algorithms used in
+the original papers.\footnote{Both \texttt{cd05} and \texttt{cd06} cannot be run
+  with most WMC algorithms including \textsf{ADDMC} because these encodings
+  allow for additional models that the WMC algorithm is supposed to ignore
   \citep{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.} We compare the
@@
 \SI{32}{\gibi\byte} memory limit and a \SI{1000}{\second} timeout on both
-encoding and inference. For inference, we use \textsf{Ace} for \texttt{cd05},
-\texttt{cd06}, and \texttt{d02};
+encoding and inference. For inference, we use \textsf{Ace} for \texttt{cd05}
+\citep{DBLP:conf/ijcai/ChaviraD05}, \texttt{cd06}
+\citep{DBLP:conf/sat/ChaviraD06}, and \texttt{d02}
+\citep{DBLP:conf/kr/Darwiche02};
 \textsf{Cachet}\footnote{\url{https://cs.rochester.edu/u/kautz/Cachet/}}
-\citep{DBLP:conf/sat/SangBBKP04} for \texttt{sbk05}; and \textsf{c2d}
+\citep{DBLP:conf/sat/SangBBKP04} for \texttt{sbk05}
+\citep{DBLP:conf/aaai/SangBK05}; and \textsf{c2d}
 \citep{DBLP:conf/ecai/Darwiche04} for compilation and \textsf{query-dnnf}
 \footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}} for
-answer computation for \texttt{bklm16}. For encoding, we use \textsf{bn2cnf}
+answer computation for \texttt{bklm16} \citep{DBLP:conf/ecai/BartKLM16}. For
+encoding, we use \textsf{bn2cnf}
 \footnote{\url{http://www.cril.univ-artois.fr/KC/bn2cnf.html}} for
@@
 
-\textsf{Ace} was not used to encode evidence, as
-preliminary experiments revealed that the evidence-encoding implementation
-contains bugs that can lead to incorrect answers or a Java exception being
-thrown on some instances of the data set (and the source code is not publicly
-available). Instead, we simply list all the evidence as additional clauses in
-the encoding. Furthermore, to ensure that \texttt{bklm16} (whether run with
-\textsf{ADDMC} or \textsf{c2d}) returns correct answers on most instances, we
+\textsf{Ace} was not used to encode evidence, as preliminary experiments
+revealed that the evidence-encoding implementation contains bugs that can lead
+to incorrect answers or a Java exception being thrown on some instances of the
+data set (and the source code is not publicly available). Instead, we simply
+list all the evidence as additional clauses in the encoding. Furthermore, to
+ensure that \texttt{bklm16} \citep{DBLP:conf/ecai/BartKLM16} (whether run with
+\textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} or \textsf{c2d}
+\citep{DBLP:conf/ecai/Darwiche04}) returns correct answers on most instances, we
 had to disable one of the improvements that \texttt{bklm16} brings over
-\texttt{cd06}, namely, the construction of a scaling factor that `absorbs' one
-probability from each CDT \citep{DBLP:conf/ecai/BartKLM16}. For realistic
-benchmark instances, this scaling factor can easily be below $10^{-30}$, and
-thus would require arbitrary-precision floating-point arithmetic to be usable.
-Even a toy Bayesian network with seven binary independent variables with
-probabilities $0.1$ and $0.9$ is enough for \textsf{bn2cnf} to output precisely
-zero as the scaling factor. We note that this issue likely remained unnoticed
-because \citet{DBLP:conf/ecai/BartKLM16} did not attempt to compute numerical
-answers in their experiments.
+\texttt{cd06} \citep{DBLP:conf/sat/ChaviraD06}, namely, the construction of a
+scaling factor that `absorbs' one probability from each CDT
+\citep{DBLP:conf/ecai/BartKLM16}. For realistic benchmark instances, this
+scaling factor can easily be below $10^{-30}$, and thus would require
+arbitrary-precision floating-point arithmetic to be usable. Even a toy Bayesian
+network with seven binary independent variables with probabilities $0.1$ and
+$0.9$ is enough for \textsf{bn2cnf} to output precisely zero as the scaling
+factor. We note that this issue likely remained unnoticed because
+\citet{DBLP:conf/ecai/BartKLM16} did not attempt to compute numerical answers in
+their experiments.
 
@@
 
-For experimental data, we use the Bayesian networks
-available with \textsf{Ace} and \textsf{Cachet}, most of which happen to be
+For experimental data, we use the Bayesian networks available with \textsf{Ace}
+and \textsf{Cachet} \citep{DBLP:conf/sat/SangBBKP04}, most of which happen to be
 binary. We classify them into the following seven categories:
@@
 \end{itemize*}
-We run \textsf{ADDMC} with each of the five encodings once on each Bayesian
-network.
 
-%Specifically, \texttt{cw} solves the same number of
-%instances in \SI{8.144}{\second} as \texttt{d02} does in \SI{1000}{\second},
-%which is the second-best encoding in our experiments.
-
-\Cref{fig:cumulative} shows that \texttt{cd05} and
-\texttt{cd06} (when run with \textsf{Ace}) are in the lead, while \textsf{ADDMC}
-significantly underperforms when combined with any of the previous encodings.
-Our encoding \texttt{cw} significantly improves the performance of
-\textsf{ADDMC}, making $\textsf{ADDMC}+\texttt{cw}$ comparable to
-$\textsf{Ace}+\texttt{d02}$, $\textsf{c2d}+\texttt{bklm16}$, and
-$\textsf{Cachet}+\texttt{sbk05}$. Furthermore,
-\cref{tbl:tallies} shows that, while $\textsf{Ace}+\texttt{cd06}$ managed to
-solve the most instances, $\textsf{ADDMC}+\texttt{cw}$ was the best-performing
-algorithm-encoding combination on the largest number of instances. The scatter
-plot on the left-hand side of \cref{fig:scatter} add to this by showing that
-\texttt{cw} is particularly promising on Grid networks and tackles all DQMR
-instances in less than a second. The scatter plot on the right-hand side of
-\cref{fig:scatter} shows that \texttt{cw} is better than \texttt{sbk05} (i.e.,
-the second-best encoding for \textsf{ADDMC}) on the majority of
-instances. Seeing how, e.g., DQMR instances are trivial for
-$\textsf{ADDMC}+\texttt{cw}$ but hard for $\textsf{Ace}+\texttt{cd06}$, and
-vice versa for Mastermind instances, we conclude that the best-performing
-algorithm-encoding combination depends significantly on (as-of-yet unknown)
-properties of the Bayesian networks.
+\Cref{fig:cumulative} shows that \texttt{cd05}
+\citep{DBLP:conf/ijcai/ChaviraD05} and \texttt{cd06}
+\citep{DBLP:conf/sat/ChaviraD06} (when run with \textsf{Ace}) are in the lead,
+while \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} significantly
+underperforms when combined with any of the previous encodings. Our encoding
+\texttt{cw} significantly improves the performance of \textsf{ADDMC}, making
+$\textsf{ADDMC}+\texttt{cw}$ comparable to $\textsf{Ace}+\texttt{d02}$,
+$\textsf{c2d}+\texttt{bklm16}$, and $\textsf{Cachet}+\texttt{sbk05}$.
+Furthermore, \cref{tbl:tallies} shows that, while $\textsf{Ace}+\texttt{cd06}$
+managed to solve the most instances, $\textsf{ADDMC}+\texttt{cw}$ was the
+best-performing algorithm-encoding combination on the largest number of
+instances. The scatter plot on the left-hand side of \cref{fig:scatter} add to
+this by showing that \texttt{cw} is particularly promising on Grid networks and
+tackles all DQMR instances in less than a second. The scatter plot on the
+right-hand side of \cref{fig:scatter} shows that \texttt{cw} is better than
+\texttt{sbk05} \citep{DBLP:conf/aaai/SangBK05} (i.e., the second-best encoding
+for \textsf{ADDMC}) on the majority of instances. Seeing how, e.g., DQMR
+instances are trivial for $\textsf{ADDMC}+\texttt{cw}$ but hard for
+$\textsf{Ace}+\texttt{cd06}$, and vice versa for Mastermind instances, we
+conclude that the best-performing algorithm-encoding combination depends
+significantly on (as-of-yet unknown) properties of the Bayesian networks.
 
@@
 
-We can explain what makes \textsf{ADDMC} run significantly faster with
-\texttt{cw} than with any other encoding by considering asymptotic upper bounds
-on the numbers of variables and ADDs based on the size and structure of the
-Bayesian network. Let $n = |\mathcal{V}|$ be the number of vertices in the
-Bayesian network, $d = \max_{X \in \mathcal{V}} |\mathrm{pa}(X)|$ the maximum
-in-degree (i.e., the number of parents), and $v = \max_{X \in \mathcal{V}} |\im
-X|$ the maximum number of values per variable. \Cref{tbl:asymptotes} shows how
-\texttt{cw} has fewer variables and fewer ADDs than any other encoding. We
-conjecture that it is primarily the reduced number of variables that makes the
-\textsf{ADDMC} variable ordering heuristics much more effective. Note that these
-are upper bounds and most encodings (including \texttt{cw}) can be smaller in
-certain situations (e.g., with binary random variables or when a CPT has
-repeating probabilities). We equate clauses and ADDs (more specifically, factors
-of the function $\phi$ from \cref{alg:encoding}) here because \textsf{ADDMC}
-interprets each clause of any WMC encoding as a multiplicative factor of the ADD
-that represents the entire WMC instance \citep{DBLP:conf/aaai/DudekPV20}. For
-literal-weight encodings, each weight is also a factor, but that does not affect
-our asymptotic bounds.
+We can explain what makes \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} run
+significantly faster with \texttt{cw} than with any other encoding by
+considering asymptotic upper bounds on the numbers of variables and ADDs based
+on the size and structure of the Bayesian network. Let $n = |\mathcal{V}|$ be
+the number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
+|\mathrm{pa}(X)|$ the maximum in-degree (i.e., the number of parents), and $v =
+\max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
+\Cref{tbl:asymptotes} shows how \texttt{cw} has fewer variables and fewer ADDs
+than any other encoding. We conjecture that it is primarily the reduced number
+of variables that makes the \textsf{ADDMC} variable ordering heuristics much
+more effective. Note that these are upper bounds and most encodings (including
+\texttt{cw}) can be smaller in certain situations (e.g., with binary random
+variables or when a CPT has repeating probabilities). We equate clauses and ADDs
+(more specifically, factors of the function $\phi$ from \cref{alg:encoding})
+here because \textsf{ADDMC} interprets each clause of any WMC encoding as a
+multiplicative factor of the ADD that represents the entire WMC instance
+\citep{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings, each weight is
+also a factor, but that does not affect our asymptotic bounds.
 
 \section{Conclusions and Future Work}
-% TODO: maybe: emphasise that BN encodings have never been compared w.r.t. time
-% before
 
@@
 
-While we chose \textsf{ADDMC} as the WMC algorithm and Bayesian networks as a
-canonical example of a probabilistic inference task, these are only examples
-meant to illustrate the broader idea that choosing a more expressive
-representation of weights can outperform increasing the size of the problem to
-keep the weights simple. Indeed, in this work, we have provided a new
-theoretical perspective on the expressive power of WMC and illustrated the
-empirical benefits of that perspective. The same idea can be adapted to other
-inference problem domains such as probabilistic programs
+While we chose \textsf{ADDMC} \citep{DBLP:conf/aaai/DudekPV20} as the WMC
+algorithm and Bayesian networks as a canonical example of a probabilistic
+inference task, these are only examples meant to illustrate the broader idea
+that choosing a more expressive representation of weights can outperform
+increasing the size of the problem to keep the weights simple. Indeed, in this
+work, we have provided a new theoretical perspective on the expressive power of
+WMC and illustrated the empirical benefits of that perspective. The same idea
+can be adapted to other inference problem domains such as probabilistic programs
 \citep{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
 well as to search-based solvers such as \textsf{Cachet}
-\citep{DBLP:conf/sat/SangBBKP04} and \textsf{DPMC}
----an extension to \textsf{ADDMC} that adds support for computations based on
-tensors (rather than ADDs) and planning based on tree decompositions
-\cite{DBLP:conf/cp/DudekPV20}. Another important direction for future work is to
-develop a better understanding of what properties of Bayesian networks make an
-instance easy for some algorithm-encoding combinations more than others.
+\citep{DBLP:conf/sat/SangBBKP04} and \textsf{DPMC} ---an extension to
+\textsf{ADDMC} that adds support for computations based on tensors (rather than
+ADDs) and planning based on tree decompositions \cite{DBLP:conf/cp/DudekPV20}.
+Another important direction for future work is to develop a better understanding
+of what properties of Bayesian networks make an instance easy for some
+algorithm-encoding combinations more than others.
 
-\begin{contributions} % will be removed in pdf for initial submission,
-                      % so you can already fill it to test with the
-                      % ‘accepted’ class option
-    Briefly list author contributions.
-    This is a nice way of making clear who did what and to give proper credit.
-
-    H.~Q.~Bovik conceived the idea and wrote the paper.
-    Coauthor One created the code.
-    Coauthor Two created the figures.
+\begin{contributions}
+    P.~Dilkas conceived the idea, ran the experiments, and wrote the paper.
+    V.~Belle supervised the work.
 \end{contributions}
 
-\begin{acknowledgements} % will be removed in pdf for initial submission,
-                         % so you can already fill it to test with the
-                         % ‘accepted’ class option
-    Briefly acknowledge people and organizations here.
-
-    \emph{All} acknowledgements go in this section.
+\begin{acknowledgements}
+  The first author was supported by the EPSRC Centre for Doctoral Training in
+  Robotics and Autonomous Systems, funded by the UK Engineering and Physical
+  Sciences Research Council (grant EP/L016834/1). The second author was
+  supported by a Royal Society University Research Fellowship. This work has
+  made use of the resources provided by the Edinburgh Compute and Data Facility
+  (ECDF) (\url{http://www.ecdf.ed.ac.uk/}).
 \end{acknowledgements}
 
-\clearpage
 \bibliography{paper}
-
-\clearpage
-\appendix
-\section{Proofs}
-
-\measure*
-\begin{proof}
-  Note that $\mu_\nu(\bot) = 0$ since there are no atoms below $\bot$. Let $a, b
-  \in 2^{2^{U}}$ be such that $a \land b = \bot$. By elementary properties of
-  Boolean algebras, all atoms below $a \lor b$ are either below $a$ or below
-  $b$. Moreover, none of them can be below both $a$ and $b$ because then they
-  would have to be below $a \land b = \bot$. Thus
-  \begin{align*}
-    \mu_\nu(a \lor b) &= \sum_{\{u\} \le a \lor b} \nu(u) = \sum_{\{u\} \le a} \nu(u) + \sum_{\{u\} \le b} \nu(u) \\
-                      &= \mu_\nu(a) + \mu_\nu(b)
-  \end{align*}
-  as required.
-\end{proof}
-
-\extendable*
-\begin{proof}
-  Let $V = U \cup \{ f_m \mid m \in 2^U \}$, and $f = \bigwedge_{m \in 2^U} \{ m
-  \} \leftrightarrow f_m$. We define weight function $\nu\colon 2^V \to
-  \mathbb{R}_{\ge 0}$ as $\nu = \prod_{v \in V} \nu_v$, where $\nu_v(\{v\}) =
-  \mu(\{m\})$ if $v = f_m$ for some $m \in 2^U$ and $\nu_v(x) = 1$ for all other
-  $v \in V$ and $x \in 2^{\{v\}}$. Let $\mu'\colon 2^{2^V} \to \mathbb{R}_{\ge
-    0}$ be the measure induced by $\nu$. It is enough to show that $\mu$ and $x
-  \mapsto \mu'(x \land f)$ agree on the atoms in $2^{2^U}$. For any $\{ a \} \in
-  2^{2^U}$,
-  \begin{align*}
-    \mu'(\{ a \} \land f) &= \sum_{\{ x \} \le \{ a \} \land f} \nu(x) = \nu(a \cup \{ f_a \}) \\
-                          &= \nu_{f_a}(\{ f_a \}) = \mu(\{ a \})
-  \end{align*}
-  as required.
-\end{proof}
-
-\cptlemma*
-\begin{proof}
-  If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im
-  Y_i|$ terms, one for each possible assignment of values to variables $X, Y_1,
-  \dots, Y_n$. Exactly one of these terms is nonzero when applied to $T$, and
-  it is equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.
-
-  If $X$ is not binary, then $\left( \sum_{i=1}^m [\lambda_{X = x_i}]
-  \right)(T) = 1$, and $\left( \prod_{i=1}^m \prod_{j=i+1}^m
-    (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})
-  \right)(T) = 1$, so $\mathrm{CPT}_X(T) = \Pr(X = x \mid Y_1 = y_1,
-  \dots, Y_n = y_n)$ by a similar argument as before.
-\end{proof}
-
-\fulldistribution*
-\begin{proof}
-  If $T = \{ \lambda_{X=v_X} \mid X \in \mathcal{V} \}$ for some $(v_X)_{X
-    \in \mathcal{V}} \in \prod_{X \in \mathcal{V}} \im X$, then
-  \begin{align*}
-    \phi(T) &= \prod_{X \in \mathcal{V}} \Pr \left( X=v_X \;\middle|\; \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) \\
-            &= \Pr \left( \bigwedge_{X \in \mathcal{V}} X=v_X \right)
-  \end{align*}
-  by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
-  must be some non-binary random variable $X \in \mathcal{V}$ such that
-  $|\mathcal{E}(X) \cap T| \ne 1$. If $\mathcal{E}(X) \cap T = \emptyset$, then
-  $\left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(T) = 0$, and so
-  $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$. If $|\mathcal{E}(X) \cap T| > 1$,
-  then we must have two different values $x_1, x_2 \in \im X$ such that
-  $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq T$ which means that
-  $(\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(T) = 0$, and
-  so, again, $\mathrm{CPT}_X(T) = 0$, and $\phi(T) = 0$.
-\end{proof}
-
-\correctness*
-\begin{proof}
-  Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
-  \begin{align*}
-    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) \\
-                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) \\
-                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
-                                                        &= \sum_{(y_i)_{i=1}^n \in \prod_{i=1}^n \im Y_i} \Pr(x, y_1, \dots, y_n) \\
-                                                        &= \Pr(X = x)
-  \end{align*}
-  by:
-  \begin{itemize}
-  \item the proof of Theorem~1 by \citet{DBLP:conf/aaai/DudekPV20};
-  \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
-    [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
-    \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
-  \item \cref{lemma:full_distribution};
-  \item marginalisation of a probability distribution.
-  \end{itemize}
-\end{proof}
-
-% TODO: potential appendix: exact arguments to each piece of software
 \end{document}

### 2021-05-22 doc/UAI_paper/paper.tex
Start working on the poster

@@
 % TODO: maybe I should rotate the cumulative plot
-
 % TODO: read 'Preparing the submission materials' (code: dilkas_167)
@@
 
-% TODO: must reference the SAT paper and explain the differences
-% \cite{my_sat_paper}
+While in this paper we focus on measure-theoretic foundations and propose a
+new encoding for Bayesian networks, a related line of work
+\citep{my_sat_paper}---motivated by the same issue of WMC encodings having both
+more variables and more clauses as a consequence of having to conform to an
+unnecessarily restrictive format---shows how these variables and clauses can be
+removed from (most) already-existing Bayesian network encodings. Although tested
+on Bayesian networks, this variable removal is formulated in a way that applies
+to arbitrary WMC instances.
+% I could also mention DPMC vs ADDMC and pseudo-Boolean functions
 

### 2021-05-22 doc/poster/poster.tex
Start working on the poster

\documentclass[a0paper,portrait]{tikzposter}

\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{tikz-cd}
\usepackage{authblk}
\usepackage[export]{adjustbox}

%\addbibresource{../UAI_paper/paper.bib}

\tikzposterlatexaffectionproofoff
\usetheme{Rays}

% TODO: use lots of bold

\makeatletter
\def\title#1{\gdef\@title{\scalebox{\TP@titletextscale}{%
      \begin{minipage}[t]{\linewidth}
        \centering
        #1
        \par
        \vspace{0.5em}
      \end{minipage}%
    }}}
\makeatother

\makeatletter
\newcounter{tablecounter}
\newenvironment{tikztable}[1][]{
  \def \rememberparameter{#1}
  \vspace{10pt}
  \refstepcounter{tablecounter}
  \begin{center}
  }{
    \ifx\rememberparameter\@empty
    \else
    \\[10pt]
    {\small Tab.~\thetablecounter: \rememberparameter}
    \fi
  \end{center}
}
\makeatother

\makeatletter
\def\maketitle{\AB@maketitle}
\makeatother

\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
\author[1]{Paulius Dilkas}
\author[1,2]{Vaishak Belle}
\affil[1]{School of Informatics, University of Edinburgh, Edinburgh, UK}
\affil[2]{The Alan Turing Institute, London, UK}
\titlegraphic{\includegraphics[height=200pt,valign=c]{logo_inf.png}\hspace{3em}\includegraphics[height=200pt,valign=c]{logo_ecr.png}\hspace{3em}\includegraphics[height=100pt,valign=c]{logo_ukri.png}}

\begin{document}
\maketitle

\begin{columns}
  \column{0.5}
  \block{Boolean Algebras and Propositional Logic}{
    Let $U = \{ a, b \}$. Then $2^{2^U}$ is a Boolean algebra with the following
    Hasse diagram ($x \le y$ if $x \subseteq y$ or, equivalently, $x = x \land
    y$).
    % \[
    %   \begin{tikzcd}[ampersand replacement=\&, column sep=tiny]
    %     \& \& \& \& \& \top \ar[dlll,dash,gray] \ar[dl,dash,gray]
    %     \ar[dr,dash,gray] \ar[drrr,dash,gray] \& \& \& \\
    %     \& \& a \lor b \& \& b \to a \& \& a \to b \& \& \neg a \lor \neg
    %     b \\
    %     a \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& b \ar[u,dash,gray]
    %     \ar[urrrr,dash,gray] \& \& a \leftrightarrow b \ar[u,dash,gray]
    %     \ar[urr,dash,gray] \& \& a + b \ar[ullll,dash,gray] \ar[urr,dash,gray]
    %     \& \& \neg b \ar[ullll,dash,gray] \ar[u,dash,gray] \& \& \neg a
    %     \ar[ullll,dash,gray] \ar[ull,dash,gray] \\
    %     \& \& \fbox{$a \land b$} \ar[ull,dash,gray] \ar[u,dash,gray]
    %     \ar[urr,dash,gray] \& \& \fbox{$a \land \neg b$} \ar[ullll,dash,gray]
    %     \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& \fbox{$\neg a \land b$}
    %     \ar[ullll,dash,gray] \ar[u,dash,gray] \ar[urrrr,dash,gray] \& \&
    %     \fbox{$\neg a \land \neg b$} \ar[ullll,dash,gray] \ar[u,dash,gray]
    %     \ar[urr,dash,gray] \\
    %     \& \& \& \& \& \bot \ar[ulll,dash,gray] \ar[ul,dash,gray]
    %     \ar[ur,dash,gray] \ar[urrr,dash,gray] \& \& \&
    %   \end{tikzcd}
    % \]
  }

  \block{Experimental Results}{
    \begin{tikzfigure}[Cumulative numbers of instances solved by combinations of
      algorithms and encodings over time.]
      \centering
      \includegraphics[width=\linewidth]{cumulative}
    \end{tikzfigure}
    \begin{tikzfigure}[An instance-by-instance comparison between
      $\textsf{ADDMC} + \texttt{cw}$ and the best overall combination of
      algorithm and encoding ($\textsf{Ace} + \texttt{cd06}$, on the left) as
      well as the second-best encoding for \textsf{ADDMC} (\texttt{sbk05}, on
      the right).]
      \centering
      \includegraphics[width=\linewidth]{scatter}
    \end{tikzfigure}
  }

  \column{0.5}

  \block{TODO}{
    \begin{tikztable}[Asymptotic upper bounds on the numbers of variables and
      clauses/ADDs for each encoding.]
      \centering
      \begin{tabular}{l c c}
        \toprule
        Encoding(s) & Variables & Clauses/ADDs \\
        \midrule
        \texttt{bklm16}, \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $O(nv^{d+1})$ & $O(nv^{d+1})$ \\
        \texttt{cw} & $O(nv)$ & $O(nv^2)$ \\
        \texttt{d02} & $O(nv^{d+1})$ & $O(ndv^{d+1})$ \\
        \bottomrule
      \end{tabular}
    \end{tikztable}
  }

\end{columns}
\end{document}

### 2021-05-22 tools/UAI_plots.R

@@ -8,7 +8,7 @@ library(ggpubr)
 library(tidyr)
 library(RColorBrewer)
 
-data <- read.csv("../results/old_results.csv", header = TRUE, sep = ",")
+data <- read.csv("../results/UAI_results.csv", header = TRUE, sep = ",")
 data <- data[!(data$encoding == "cd05" & data$novelty == "new"),]
 data <- data[!(data$encoding == "cd06" & data$novelty == "new"),]
 
@@ -100,7 +100,8 @@ cumulative_plot <- function(df, column_name, pretty_column_name, column_values,
     labs(color = pretty_column_name, linetype = pretty_column_name)
 }
 
-tikz(file = "../doc/paper2/cumulative.tex", width = 6.5, height = 2.4)
+#tikz(file = "../doc/UAI_paper/cumulative.tex", width = 6.5, height = 2.4)
+tikz(file = "../doc/poster/cumulative.tex", width = 7, height = 2.6, standAlone = TRUE)
 cumulative_plot(data_sum, "encoding", "Algorithm \\& Encoding",
                 sort(unique(data_sum$encoding)),
                 c(2, 2, 2, 1, 1, 1, 1, 2, 2), "time", "Time (s)")
@@ -132,10 +133,10 @@ scatter_plot <- function(df, x_column, y_column, x_name, y_name,
 
 p1 <- scatter_plot(df, "time_old_cd06", "time_new_cw", "\\textsf{Ace} + \\texttt{cd06} time (s)",
                    "\\textsf{ADDMC} + \\texttt{cw} time (s)", 2 * TIMEOUT)
-
 p2 <- scatter_plot(df, "time_new_sbk05", "time_new_cw", "\\textsf{ADDMC} + \\texttt{sbk05} time (s)",
                    "\\textsf{ADDMC} + \\texttt{cw} time (s)", 2 * TIMEOUT)
-tikz(file = "../doc/paper2/scatter.tex", width = 6.5, height = 2.4)
+#tikz(file = "../doc/UAI_paper/scatter.tex", width = 6.5, height = 2.4)
+tikz(file = "../doc/poster/scatter.tex", width = 7, height = 2.6, standAlone = TRUE)
 ggarrange(p1, p2, ncol = 2, nrow = 1, common.legend = TRUE, legend = "right")
 dev.off()
 

### 2021-05-28 doc/UAI_paper/paper.tex
The poster is halfway decent (and some other small changes)

@@
 
-\author[1]{\href{mailto:Paulius Dilkas <p.dilkas@sms.ed.ac.uk>?Subject=Your UAI
-    2021 paper}{Paulius~Dilkas}{}}
-\author[1,2]{Vaishak~Belle}
-\affil[1]{%
-    School of Informatics\\
+\author{Paulius~Dilkas}
+\author{Vaishak~Belle}
+\affil{%
     University of Edinburgh\\
-    Edinburgh, UK
-}
-\affil[2]{%
-    Alan Turing Institute\\
-    London, UK
+    Edinburgh, UK \\
+    \texttt{p.dilkas@sms.ed.ac.uk}, \texttt{vaishak@ed.ac.uk}
 }
@@
 unnecessarily restrictive format---shows how these variables and clauses can be
-removed from (most) already-existing Bayesian network encodings. Although tested
-on Bayesian networks, this variable removal is formulated in a way that applies
-to arbitrary WMC instances.
+removed from (most) already-existing Bayesian network encodings.
 % I could also mention DPMC vs ADDMC and pseudo-Boolean functions
@@
 
-\section{Experimental Comparison} \label{sec:experiments}
+\section{Experimental Results} \label{sec:experiments}
 
@@
 work, we have provided a new theoretical perspective on the expressive power of
-WMC and illustrated the empirical benefits of that perspective. The same idea
-can be adapted to other inference problem domains such as probabilistic programs
+WMC and illustrated the empirical benefits of that perspective. Perhaps the same
+idea could be adapted to other inference problem domains such as probabilistic
+programs
 \citep{DBLP:journals/tplp/FierensBRSGTJR15,DBLP:journals/corr/abs-2005-09089} as
@@
 ADDs) and planning based on tree decompositions \cite{DBLP:conf/cp/DudekPV20}.
-Another important direction for future work is to develop a better understanding
-of what properties of Bayesian networks make an instance easy for some
-algorithm-encoding combinations more than others.
 

### 2021-05-28 doc/poster/poster.tex
The poster is halfway decent (and some other small changes)

@@
 \usepackage{tikz-cd}
-\usepackage{authblk}
 \usepackage[export]{adjustbox}
-
-%\addbibresource{../UAI_paper/paper.bib}
+\usepackage{amsfonts}
+\usepackage[capitalise]{cleveref}
+\usepackage{subcaption}
 
@@
 
-% TODO: use lots of bold
+\usetikzlibrary{arrows}
+\usetikzlibrary{arrows.meta}
+
+\AtBeginEnvironment{tikzfigure}{\captionsetup{type=figure}}
 
@@
 
-\makeatletter
-\def\maketitle{\AB@maketitle}
-\makeatother
+%\makeatletter
+%\def\maketitle{\AB@maketitle}
+%\makeatother
 
 \title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
-\author[1]{Paulius Dilkas}
-\author[1,2]{Vaishak Belle}
-\affil[1]{School of Informatics, University of Edinburgh, Edinburgh, UK}
-\affil[2]{The Alan Turing Institute, London, UK}
+\author{Paulius Dilkas, Vaishak Belle}
+\institute{University of Edinburgh, Edinburgh, UK\\
+  \texttt{p.dilkas@sms.ed.ac.uk}, \texttt{vaishak@ed.ac.uk}}
 \titlegraphic{\includegraphics[height=200pt,valign=c]{logo_inf.png}\hspace{3em}\includegraphics[height=200pt,valign=c]{logo_ecr.png}\hspace{3em}\includegraphics[height=100pt,valign=c]{logo_ukri.png}}
@@
 \begin{columns}
+
   \column{0.5}
-  \block{Boolean Algebras and Propositional Logic}{
-    Let $U = \{ a, b \}$. Then $2^{2^U}$ is a Boolean algebra with the following
-    Hasse diagram ($x \le y$ if $x \subseteq y$ or, equivalently, $x = x \land
-    y$).
-    % \[
-    %   \begin{tikzcd}[ampersand replacement=\&, column sep=tiny]
-    %     \& \& \& \& \& \top \ar[dlll,dash,gray] \ar[dl,dash,gray]
-    %     \ar[dr,dash,gray] \ar[drrr,dash,gray] \& \& \& \\
-    %     \& \& a \lor b \& \& b \to a \& \& a \to b \& \& \neg a \lor \neg
-    %     b \\
-    %     a \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& b \ar[u,dash,gray]
-    %     \ar[urrrr,dash,gray] \& \& a \leftrightarrow b \ar[u,dash,gray]
-    %     \ar[urr,dash,gray] \& \& a + b \ar[ullll,dash,gray] \ar[urr,dash,gray]
-    %     \& \& \neg b \ar[ullll,dash,gray] \ar[u,dash,gray] \& \& \neg a
-    %     \ar[ullll,dash,gray] \ar[ull,dash,gray] \\
-    %     \& \& \fbox{$a \land b$} \ar[ull,dash,gray] \ar[u,dash,gray]
-    %     \ar[urr,dash,gray] \& \& \fbox{$a \land \neg b$} \ar[ullll,dash,gray]
-    %     \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& \fbox{$\neg a \land b$}
-    %     \ar[ullll,dash,gray] \ar[u,dash,gray] \ar[urrrr,dash,gray] \& \&
-    %     \fbox{$\neg a \land \neg b$} \ar[ullll,dash,gray] \ar[u,dash,gray]
-    %     \ar[urr,dash,gray] \\
-    %     \& \& \& \& \& \bot \ar[ulll,dash,gray] \ar[ul,dash,gray]
-    %     \ar[ur,dash,gray] \ar[urrr,dash,gray] \& \& \&
-    %   \end{tikzcd}
-    % \]
+
+  \block{Abstract}{
+    \textbf{Weighted model counting (WMC)} has emerged as the unifying inference
+    mechanism across many (probabilistic) domains. Encoding an inference problem
+    as an instance of WMC typically \textbf{necessitates adding extra literals
+      and clauses}. This is partly so because the predominant definition of WMC
+    assigns weights to models based on weights on literals, and this severely
+    restricts what probability distributions can be represented. We develop a
+    \textbf{measure-theoretic perspective} on WMC and propose a way to encode
+    conditional weights on literals analogously to conditional probabilities.
+    This representation can be as succinct as standard WMC with weights on
+    literals but can also expand as needed to represent probability
+    distributions with less structure. To demonstrate the performance benefits
+    of conditional weights over the addition of extra literals, we develop a
+    \textbf{new WMC encoding for Bayesian networks} \texttt{cw} and adapt a
+    state-of-the-art WMC algorithm \textsf{ADDMC} to the new format. Our
+    experiments show that the new encoding significantly improves the
+    performance of the algorithm on most benchmark instances.
+  }
+
+  \block{WMC as a Measure on a Boolean Algebra}{
+    Let $U$ be a set. Then $2^{2^U}$ (the powerset of the powerset of $U$)
+    is the Boolean algebra that directly corresponds to all possible
+    propositional formulae constructable from $a$ and $b$. A \textbf{measure} on
+    $2^{2^U}$ is a function $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ such that
+    \begin{itemize}
+    \item $\mu(\bot) = 0$, and
+    \item $\mu(a \lor b) = \mu(a) + \mu(b)$ for all $a, b \in 2^{2^U}$ whenever
+      $a \land b = \bot$.
+    \end{itemize}
+    A \textbf{weight function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge
+      0}$. A weight function is \textbf{factored} if
+    \[
+      \nu = \prod_{x \in U} \nu_x
+    \]
+    for some functions $\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in
+    U$. We say that a weight function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$
+    \textbf{induces} a measure $\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
+    \[
+      \mu_\nu(x) = \sum_{\{u\} \le x} \nu(u).
+    \]
+    Finally, a measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
+    \textbf{factorable} if there exists a factored weight function $\nu\colon 2^U
+    \to \mathbb{R}_{\ge 0}$ that induces $\mu$. In this formulation, WMC
+    corresponds to the process of calculating the value of $\mu_\nu(x)$ for some
+    $x \in 2^{2^U}$ with a given definition of $\nu$.
+    \innerblock{Relation to the Classical (Logic-based) View of WMC}{
+      Let $\mathcal{L}$ be a propositional logic with two atoms $a$ and $b$ and
+      $w\colon \{ a, b, \neg a, \neg b \} \to \mathbb{R}_{\ge 0}$ a weight
+      function defined as $w(a) = 0.3$, $w(\neg a) = 0.7$, $w(b) = 0.2$, $w(\neg
+      b) = 0.8$. Furthermore, let $\Delta$ be a theory in $\mathcal{L}$ with a
+      sole axiom $a$. Then $\Delta$ has two models: $\{ a, b \}$ and $\{ a, \neg
+      b \}$ and its WMC is
+      \begin{equation} \label{eq:wmc_example}
+        \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(a)w(b) + w(a)w(\neg b) = 0.3.
+      \end{equation}
+      Alternatively, we can define $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge
+        0}$ as $\nu_a(\{ a \}) = 0.3$, $\nu_a(\emptyset) = 0.7$ and $\nu_b\colon
+      2^{\{b\}} \to \mathbb{R}_{\ge 0}$ as $\nu_b(\{ b \}) = 0.2$,
+      $\nu_b(\emptyset) = 0.8$. Let $\mu$ be the measure on $2^{2^U}$ induced by
+      $\nu = \nu_a \cdot \nu_b$. Then, equivalently to \cref{eq:wmc_example}, we
+      can write
+      \begin{align*}
+        \mu(a) &= \nu(\{ a, b \}) + \nu(\{ a \}) \\
+               &= \nu_a(\{a\})\nu_b(\{b\}) + \nu_a(\{a\})\nu_b(\emptyset) = 0.3.
+      \end{align*}
+      Thus, one can equivalently think of WMC as summing over \textbf{models of
+        a theory} or over \textbf{atoms below an element} of a Boolean algebra.
+    }
+  }
+
+  \column{0.5}
+
+  \block{Example: Encoding Bayesian Networks}{
+    \begin{tikzfigure}[A Bayesian network with its conditional probability
+      tables]
+      \begin{subfigure}{0.2\linewidth}
+        \centering
+        \begin{tikzpicture}[edge from parent/.style={draw,-latex}, level distance=100pt, edge from parent/.style={draw,-{Latex[length=5mm]}}]
+          \node[draw,circle] {$A$}
+          child {node[draw,circle] {$B$}};
+        \end{tikzpicture}
+      \end{subfigure}%
+      \begin{subfigure}{0.8\linewidth}
+        \centering
+        \begin{tabular}[t]{cc}
+          \toprule
+          $a$ & $\Pr(A = a)$ \\
+          \midrule
+          1 & 0.5 \\
+          0 & 0.5 \\
+          \bottomrule
+        \end{tabular}
+        \begin{tabular}[t]{ccc}
+          \toprule
+          $a$ & $b$ & $\Pr(B = b \mid A = a)$ \\
+          \midrule
+          1 & 1 & 0.6 \\
+          1 & 0 & 0.4 \\
+          0 & 1 & 0.1 \\
+          0 & 0 & 0.9 \\
+          \bottomrule
+        \end{tabular}
+      \end{subfigure}
+    \end{tikzfigure}
+    Let $U = \{ \lambda_{A=1}, \lambda_{B=1} \}$. The weight function $\nu\colon
+    2^U \to \mathbb{R}_{\ge 0}$ for this network can be defined as $\nu
+    \coloneqq \nu_A \cdot \nu_B$, where $\nu_A = 0.5$, and
+    \begin{align*}
+      \nu_B &= 0.6[\lambda_{B=1}] \cdot [\lambda_{A=1}] + 0.4\overline{[\lambda_{B=1}]} \cdot [\lambda_{A=1}] \\
+            &+ 0.1[\lambda_{B=1}] \cdot \overline{[\lambda_{A=1}]} + 0.9\overline{[\lambda_{B=1}]} \cdot \overline{[\lambda_{A=1}]}.
+    \end{align*}
   }
@@
     \begin{tikzfigure}[Cumulative numbers of instances solved by combinations of
-      algorithms and encodings over time.]
+      algorithms and encodings over time]
       \centering
@@
       well as the second-best encoding for \textsf{ADDMC} (\texttt{sbk05}, on
-      the right).]
+      the right)]
       \centering
@@
     \end{tikzfigure}
+    We compare all six WMC encodings for Bayesian networks when run with both
+    \textsf{ADDMC} and the WMC algorithms used in the original papers. The
+    cumulative plot shows that \textsf{ADDMC} significantly \textbf{underperforms} when
+    combined with any of the \textbf{previous encodings}, but our encoding \texttt{cw}
+    significantly \textbf{improves} the performance of \textsf{ADDMC}, making
+    $\textsf{ADDMC}+\texttt{cw}$ comparable to many other combinations. The
+    scatter plot on the left-hand side adds to this by showing that \texttt{cw}
+    is \textbf{particularly promising on certain data sets} such as DQMR and
+    Grid networks. The scatter plot on the right-hand side shows that
+    \texttt{cw} is better than \texttt{sbk05} (i.e., the second-best encoding
+    for \textsf{ADDMC}) on the \textbf{majority of instances}. Seeing how, e.g.,
+    DQMR instances are trivial for $\textsf{ADDMC}+\texttt{cw}$ but hard for
+    $\textsf{Ace}+\texttt{cd06}$, and vice versa for Mastermind instances, we
+    conclude that the best-performing algorithm-encoding combination
+    \textbf{depends} significantly \textbf{on} (as-of-yet unknown)
+    \textbf{properties of the Bayesian networks}.
   }
 
-  \column{0.5}
-
-  \block{TODO}{
-    \begin{tikztable}[Asymptotic upper bounds on the numbers of variables and
-      clauses/ADDs for each encoding.]
-      \centering
-      \begin{tabular}{l c c}
-        \toprule
-        Encoding(s) & Variables & Clauses/ADDs \\
-        \midrule
-        \texttt{bklm16}, \texttt{cd05}, \texttt{cd06}, \texttt{sbk05} & $O(nv^{d+1})$ & $O(nv^{d+1})$ \\
-        \texttt{cw} & $O(nv)$ & $O(nv^2)$ \\
-        \texttt{d02} & $O(nv^{d+1})$ & $O(ndv^{d+1})$ \\
-        \bottomrule
-      \end{tabular}
-    \end{tikztable}
+  \block{See the Paper For\dots}{
+    \begin{itemize}
+    \item Theoretical results that establish both the limits and the
+      capabilities of classical WMC.
+    \item Details of the \texttt{cw} encoding for Bayesian networks.
+    \item A more detailed comparison of Bayesian network encodings, including a
+      parameterized asymptotic analysis of their growth.
+    \end{itemize}
   }

### 2021-05-30 doc/poster/poster.tex
Slides for the (very) short talk

@@
 \usepackage{subcaption}
+\usepackage{wrapfig}
 
@@
 \usetheme{Rays}
+\usenotestyle{VerticalShading}
 
@@
 
-%\makeatletter
-%\def\maketitle{\AB@maketitle}
-%\makeatother
-
 \title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
@@
   \texttt{p.dilkas@sms.ed.ac.uk}, \texttt{vaishak@ed.ac.uk}}
-\titlegraphic{\includegraphics[height=200pt,valign=c]{logo_inf.png}\hspace{3em}\includegraphics[height=200pt,valign=c]{logo_ecr.png}\hspace{3em}\includegraphics[height=100pt,valign=c]{logo_ukri.png}}
 
@@
   \block{Abstract}{
-    \textbf{Weighted model counting (WMC)} has emerged as the unifying inference
-    mechanism across many (probabilistic) domains. Encoding an inference problem
-    as an instance of WMC typically \textbf{necessitates adding extra literals
-      and clauses}. This is partly so because the predominant definition of WMC
-    assigns weights to models based on weights on literals, and this severely
-    restricts what probability distributions can be represented. We develop a
-    \textbf{measure-theoretic perspective} on WMC and propose a way to encode
-    conditional weights on literals analogously to conditional probabilities.
-    This representation can be as succinct as standard WMC with weights on
-    literals but can also expand as needed to represent probability
-    distributions with less structure. To demonstrate the performance benefits
-    of conditional weights over the addition of extra literals, we develop a
-    \textbf{new WMC encoding for Bayesian networks} \texttt{cw} and adapt a
-    state-of-the-art WMC algorithm \textsf{ADDMC} to the new format. Our
-    experiments show that the new encoding significantly improves the
-    performance of the algorithm on most benchmark instances.
+    \textbf{Weighted model counting (WMC)} has emerged as the \textbf{unifying
+      inference mechanism} across many (probabilistic) domains. Encoding an
+    inference problem as an instance of WMC typically \textbf{necessitates
+      adding extra literals and clauses}. This is partly so because the
+    predominant definition of WMC assigns weights to models based on weights on
+    literals, and this severely restricts what probability distributions can be
+    represented. We develop a \textbf{measure-theoretic perspective} on WMC and
+    propose a way to encode conditional weights on literals analogously to
+    conditional probabilities. This representation can be as succinct as
+    standard WMC with weights on literals but can also expand as needed to
+    represent probability distributions with less structure. To demonstrate the
+    performance benefits of conditional weights over the addition of extra
+    literals, we develop a \textbf{new WMC encoding for Bayesian networks}
+    \texttt{cw} and adapt a state-of-the-art WMC algorithm \textsf{ADDMC} to the
+    new format. Our experiments show that the new encoding significantly
+    improves the performance of the algorithm on most benchmark instances.
   }
@@
   \block{WMC as a Measure on a Boolean Algebra}{
-    Let $U$ be a set. Then $2^{2^U}$ (the powerset of the powerset of $U$)
-    is the Boolean algebra that directly corresponds to all possible
-    propositional formulae constructable from $a$ and $b$. A \textbf{measure} on
-    $2^{2^U}$ is a function $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ such that
+    Traditionally, WMC is seen as a \textbf{generalisation of propositional
+      model counting}. Here we provide a measure-theoretic definition, the main
+    benefit of which is that it allows us to \textbf{define weights more
+      flexibly} and results in \textbf{significantly smaller encodings}. While
+    measures on Boolean algebras have been studied before, other definitions are
+    new. For any set $U$, $2^{2^U}$ (i.e., the powerset of the powerset of $U$)
+    is the Boolean algebra that directly corresponds to \textbf{all possible
+      propositional formulas} constructable from $a$ and $b$. A \textbf{measure}
+    on $2^{2^U}$ is a function $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ such
+    that
+    \coloredbox{
       \begin{itemize}
       \item $\mu(\bot) = 0$, and
-    \item $\mu(a \lor b) = \mu(a) + \mu(b)$ for all $a, b \in 2^{2^U}$ whenever
-      $a \land b = \bot$.
+      \item $\mu(a \lor b) = \mu(a) + \mu(b)$ for all $a, b \in 2^{2^U}$
+        whenever $a \land b = \bot$.
       \end{itemize}
+    }
     A \textbf{weight function} is a function $\nu\colon 2^U \to \mathbb{R}_{\ge
-      0}$. A weight function is \textbf{factored} if
-    \[
-      \nu = \prod_{x \in U} \nu_x
-    \]
-    for some functions $\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x \in
-    U$. We say that a weight function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$
+      0}$. A weight function is \textbf{factored} if $\nu = \prod_{x \in U}
+    \nu_x$ for some functions $\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$, $x
+    \in U$. We say that a weight function $\nu\colon 2^U \to \mathbb{R}_{\ge 0}$
     \textbf{induces} a measure $\mu_\nu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ if
@@
     \to \mathbb{R}_{\ge 0}$ that induces $\mu$. In this formulation, WMC
-    corresponds to the process of calculating the value of $\mu_\nu(x)$ for some
-    $x \in 2^{2^U}$ with a given definition of $\nu$.
-    \innerblock{Relation to the Classical (Logic-based) View of WMC}{
-      Let $\mathcal{L}$ be a propositional logic with two atoms $a$ and $b$ and
-      $w\colon \{ a, b, \neg a, \neg b \} \to \mathbb{R}_{\ge 0}$ a weight
-      function defined as $w(a) = 0.3$, $w(\neg a) = 0.7$, $w(b) = 0.2$, $w(\neg
-      b) = 0.8$. Furthermore, let $\Delta$ be a theory in $\mathcal{L}$ with a
-      sole axiom $a$. Then $\Delta$ has two models: $\{ a, b \}$ and $\{ a, \neg
-      b \}$ and its WMC is
+    corresponds to \textbf{the process of calculating the value of $\mu_\nu(x)$}
+    for some $x \in 2^{2^U}$ with a given definition of $\nu$. Moreover,
+    \textbf{classical WMC is only able to evaluate factorable measures}.
+
+    \innerblock{Relation to the Classical (Logic-Based) View of WMC}{
+      The classical definition of WMC relies on a \textbf{weight function over
+        the literals} of a propositional theory. Let $\mathcal{L}$ be a
+      propositional logic with two atoms $a$ and $b$ and $w\colon \{ a, b, \neg
+      a, \neg b \} \to \mathbb{R}_{\ge 0}$ a weight function defined as $w(a) =
+      0.3$, $w(\neg a) = 0.7$, $w(b) = 0.2$, $w(\neg b) = 0.8$. Furthermore, let
+      $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $a$. Then $\Delta$
+      has two models: $\{ a, b \}$ and $\{ a, \neg b \}$ and its WMC is
       \begin{equation} \label{eq:wmc_example}
-        \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(a)w(b) + w(a)w(\neg b) = 0.3.
+        \mathrm{WMC}(\Delta) = \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) = w(a)w(b) + w(a)w(\neg b) = 0.3,
       \end{equation}
-      Alternatively, we can define $\nu_a\colon 2^{\{a\}} \to \mathbb{R}_{\ge
-        0}$ as $\nu_a(\{ a \}) = 0.3$, $\nu_a(\emptyset) = 0.7$ and $\nu_b\colon
-      2^{\{b\}} \to \mathbb{R}_{\ge 0}$ as $\nu_b(\{ b \}) = 0.2$,
-      $\nu_b(\emptyset) = 0.8$. Let $\mu$ be the measure on $2^{2^U}$ induced by
-      $\nu = \nu_a \cdot \nu_b$. Then, equivalently to \cref{eq:wmc_example}, we
-      can write
+      i.e., we \textbf{sum over all models} entailed by the theory, and the
+      weight of each model is \textbf{the product of the weights of all literals
+        in it}. Alternatively, we can define $\nu_a\colon 2^{\{a\}} \to
+      \mathbb{R}_{\ge 0}$ as $\nu_a(\{ a \}) = 0.3$, $\nu_a(\emptyset) = 0.7$
+      and $\nu_b\colon 2^{\{b\}} \to \mathbb{R}_{\ge 0}$ as $\nu_b(\{ b \}) =
+      0.2$, $\nu_b(\emptyset) = 0.8$. Let $\mu$ be the measure on $2^{2^U}$
+      induced by $\nu = \nu_a \cdot \nu_b$. Then, equivalently to
+      \cref{eq:wmc_example}, we can write
       \begin{align*}
@@
 
+  \begin{subcolumns}
+    \subcolumn{0.44}
+    \block{}{
+      \begin{center}
+        \includegraphics[height=200pt]{logo_inf.png}
+        \includegraphics[height=200pt]{logo_ecr.png}
+        \includegraphics[height=100pt]{logo_ukri.png}
+      \end{center}
+    }
+    \subcolumn{0.56}
+    \note[width=0.29\linewidth,targetoffsetx=0.152\linewidth,targetoffsety=0.01\textheight]{
+      For instance, the Boolean algebra $2^{2^{\{a, b\}}}$ can be visualised as
+      \[
+        \begin{tikzcd}[ampersand replacement=\&, column sep=tiny]
+          \& \& \& \& \& \top \ar[dlll,dash,gray] \ar[dl,dash,gray]
+          \ar[dr,dash,gray] \ar[drrr,dash,gray] \& \& \& \\
+          \& \& a \lor b \& \& b \to a \& \& a \to b \& \& \neg a \lor \neg
+          b \\
+          a \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& b \ar[u,dash,gray]
+          \ar[urrrr,dash,gray] \& \& a \leftrightarrow b \ar[u,dash,gray]
+          \ar[urr,dash,gray] \& \& a + b \ar[ullll,dash,gray] \ar[urr,dash,gray]
+          \& \& \neg b \ar[ullll,dash,gray] \ar[u,dash,gray] \& \& \neg a
+          \ar[ullll,dash,gray] \ar[ull,dash,gray] \\
+          \& \& \fbox{$a \land b$} \ar[ull,dash,gray] \ar[u,dash,gray]
+          \ar[urr,dash,gray] \& \& \fbox{$a \land \neg b$} \ar[ullll,dash,gray]
+          \ar[urr,dash,gray] \ar[urrrr,dash,gray] \& \& \fbox{$\neg a \land b$}
+          \ar[ullll,dash,gray] \ar[u,dash,gray] \ar[urrrr,dash,gray] \& \&
+          \fbox{$\neg a \land \neg b$} \ar[ullll,dash,gray] \ar[u,dash,gray]
+          \ar[urr,dash,gray] \\
+          \& \& \& \& \& \bot. \ar[ulll,dash,gray] \ar[ul,dash,gray]
+          \ar[ur,dash,gray] \ar[urrr,dash,gray] \& \& \&
+        \end{tikzcd}
+      \]
+      Boxed elements are the \textbf{atoms} of the algebra.
+    }
+  \end{subcolumns}
+
  \column{0.5}
@@
   \block{Example: Encoding Bayesian Networks}{
+    \begin{wrapfigure}[8]{r}{0.55\linewidth}
     \begin{tikzfigure}[A Bayesian network with its conditional probability
@@
     \end{tikzfigure}
-    Let $U = \{ \lambda_{A=1}, \lambda_{B=1} \}$. The weight function $\nu\colon
-    2^U \to \mathbb{R}_{\ge 0}$ for this network can be defined as $\nu
-    \coloneqq \nu_A \cdot \nu_B$, where $\nu_A = 0.5$, and
+    \end{wrapfigure}
+    A typical WMC encoding for the pictured Bayesian network needs \textbf{8 variables
+    and 17 clauses}. However, the \texttt{cw} weight function only needs \textbf{two
+    variables}. Let $U = \{ \lambda_{A=1}, \lambda_{B=1} \}$ be the set of
+    variables. Using some simple syntax for manipulating weight functions
+    (mostly defined pointwise), we can define the weight function $\nu\colon 2^U
+    \to \mathbb{R}_{\ge 0}$ for this network as $\nu \coloneqq \nu_A \cdot
+    \nu_B$, where
+    \[
+      \nu_A = 0.5,
+    \]
+    and
     \begin{align*}
-      \nu_B &= 0.6[\lambda_{B=1}] \cdot [\lambda_{A=1}] + 0.4\overline{[\lambda_{B=1}]} \cdot [\lambda_{A=1}] \\
-            &+ 0.1[\lambda_{B=1}] \cdot \overline{[\lambda_{A=1}]} + 0.9\overline{[\lambda_{B=1}]} \cdot \overline{[\lambda_{A=1}]}.
+      \nu_B = 0.6[\lambda_{B=1}] \cdot [\lambda_{A=1}] + 0.4[\neg\lambda_{B=1}] \cdot [\lambda_{A=1}] + 0.1[\lambda_{B=1}] \cdot [\neg\lambda_{A=1}] + 0.9[\neg\lambda_{B=1}] \cdot [\neg\lambda_{A=1}].
     \end{align*}
@@
 
-  \block{See the Paper For\dots}{
+  \block{See the Paper for\dots}{
     \begin{itemize}

### 2021-05-30 tools/UAI_plots.R

@@ -88,16 +88,22 @@ cumulative_plot <- function(df, column_name, pretty_column_name, column_values,
   cumulative$time <- as.numeric(cumulative$time)
   cumulative$count <- as.numeric(cumulative$count)
   cumulative <- cumulative[cumulative$time < 2 * TIMEOUT, ]
-  ggplot(cumulative, aes(x = time, y = count, color = .data[[column_name]])) +
-    geom_line(aes(linetype = .data[[column_name]])) +
-    scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000), labels = c("0.1", "1", "10", "100", "1000")) +
-    xlab("Time (s)") +
-    ylab("Instances solved") +
-    scale_colour_manual(breaks = column_values, values = colours) +
-    scale_linetype_manual(breaks = column_values, values = linetypes) +
-    annotation_logticks(sides = "b", colour = "#989898") +
-    theme_light() +
-    labs(color = pretty_column_name, linetype = pretty_column_name)
+  max <- max(cumulative$count[cumulative$encoding == "\\textsf{ADDMC} + \\texttt{bklm16}"])
+  interpolation <- approx(x = cumulative$count[cumulative$encoding == "\\textsf{ADDMC} + \\texttt{cw}"],
+                          y = cumulative$time[cumulative$encoding ==  "\\textsf{ADDMC} + \\texttt{cw}"],
+                          xout = max)
+  print(interpolation$y)
+  print(1000 / interpolation$y)
+#  ggplot(cumulative, aes(x = time, y = count, color = .data[[column_name]])) +
+#    geom_line(aes(linetype = .data[[column_name]])) +
+#    scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000), labels = c("0.1", "1", "10", "100", "1000")) +
+#    xlab("Time (s)") +
+#    ylab("Instances solved") +
+#    scale_colour_manual(breaks = column_values, values = colours) +
+#    scale_linetype_manual(breaks = column_values, values = linetypes) +
+#    annotation_logticks(sides = "b", colour = "#989898") +
+#    theme_light() +
+#    labs(color = pretty_column_name, linetype = pretty_column_name)
 }
 
 #tikz(file = "../doc/UAI_paper/cumulative.tex", width = 6.5, height = 2.4)

### 2021-05-31 doc/long_talk/talk.tex
Some slides

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{minibox}
\usepackage{listings}
\usepackage{complexity}

\beamertemplatenavigationsymbolsempty
\usetheme{Madrid}
\usecolortheme{orchid}

\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes}

\author[P. Dilkas, V. Belle]{\textbf{Paulius Dilkas} \and Vaishak Belle}
\title[WMC with Conditional Weights for BNs]{Weighted Model Counting with
  Conditional Weights for Bayesian Networks}
\date{UAI 2021}
\institute[University of Edinburgh]{University of Edinburgh, Edinburgh, UK}

\begin{document}

\begin{frame}[noframenumbering,plain]
  \tikz[remember picture,overlay]{
    \node at ([yshift=25pt,xshift=30pt]current page.south)
    {\includegraphics[height=40pt]{../poster/logo_inf.png}};
    \node at ([yshift=25pt,xshift=75pt]current page.south)
    {\includegraphics[height=40pt]{../poster/logo_ecr.png}};
    \node at ([yshift=20pt,xshift=140pt]current page.south)
    {\includegraphics[height=20pt]{../poster/logo_ukri.png}};
  }
  \titlepage
\end{frame}

\begin{frame}[fragile]{The Problem of Computing Probability}
  \vspace{-0.75cm}
  \begin{columns}[t]
    \begin{column}{0.6\textwidth}
      \centering
      \begin{block}{ProbLog}
        \vspace{-0.3cm}
        \begin{lstlisting}[basicstyle=\tiny]
0.001 :: burglary.
0.002 :: earthquake.
0.95 :: alarm :- burglary, earthquake.
0.94 :: alarm :- burglary, \+ earthquake.
0.29 :: alarm :- \+ burglary, earthquake.
0.001 :: alarm :- \+ burglary, \+ earthquake.
0.9 :: johnCalls :- alarm.
0.05 :: johnCalls :- \+ alarm.
0.7 :: maryCalls :- alarm.
0.01 :: maryCalls :- \+ alarm.
        \end{lstlisting}
        \vspace{-0.2cm}
      \end{block}
      \vspace{-0.25cm}
      \begin{block}{BLOG}
        \vspace{-0.3cm}
        \begin{lstlisting}[escapeinside={(*}{*)},basicstyle=\tiny]
random Boolean Burglary (*$\sim$*) BooleanDistrib(0.001);
random Boolean Earthquake (*$\sim$*) BooleanDistrib(0.002);
random Boolean Alarm (*$\sim$*)
  if Burglary then
    if Earthquake then BooleanDistrib(0.95)
    else BooleanDistrib(0.94)
  else
    if Earthquake then BooleanDistrib(0.29)
    else BooleanDistrib(0.001);
random Boolean JohnCalls (*$\sim$*)
  if Alarm then BooleanDistrib(0.9)
  else BooleanDistrib(0.05);
random Boolean MaryCalls (*$\sim$*)
  if Alarm then BooleanDistrib(0.7)
  else BooleanDistrib(0.01);
        \end{lstlisting}
        \vspace{-0.2cm}
      \end{block}
    \end{column}
    \begin{column}{0.35\textwidth}
      \begin{block}{Bayesian Network}
        \centering
        \begin{tikzpicture}[node distance=2cm,scale=0.5,every node/.style={scale=0.5}]
          \node[draw,ellipse] (alarm) {Alarm};
          \node[draw,ellipse,above left of=alarm] (burglary) {Burglary};
          \node[draw,ellipse,above right of=alarm] (earthquake) {Earthquake};
          \node[draw,ellipse,below left of=alarm] (johnCalls) {JohnCalls};
          \node[draw,ellipse,below right of=alarm] (maryCalls) {MaryCalls};
          \draw[-Latex] (burglary) -- (alarm);
          \draw[-Latex] (earthquake) -- (alarm);
          \draw[-Latex] (alarm) -- (johnCalls);
          \draw[-Latex] (alarm) -- (maryCalls);
        \end{tikzpicture}
      \end{block}
      \vspace{1cm}
      \begin{block}{Markov Random Field}
        \centering
        \begin{tikzpicture}[node distance=2cm,scale=0.5,every node/.style={scale=0.5}]
          \node[draw,ellipse] (alarm) {Alarm};
          \node[draw,ellipse,above left of=alarm] (burglary) {Burglary};
          \node[draw,ellipse,above right of=alarm] (earthquake) {Earthquake};
          \node[draw,ellipse,below left of=alarm] (johnCalls) {JohnCalls};
          \node[draw,ellipse,below right of=alarm] (maryCalls) {MaryCalls};
          \draw (burglary) -- (earthquake);
          \draw (burglary) -- (alarm);
          \draw (earthquake) -- (alarm);
          \draw (alarm) -- (johnCalls);
          \draw (alarm) -- (maryCalls);
        \end{tikzpicture}
      \end{block}
    \end{column}
  \end{columns}
  \onslide<2>{
    \begin{tikzpicture}[remember picture,overlay]
      \node[draw,star,fill=red!10] (wmc) at (current page.center) {WMC};
      \coordinate[xshift=-0.25\linewidth,yshift=-0.25\textheight] (p1) at (current page.center);
      \coordinate[xshift=0.25\linewidth,yshift=-0.25\textheight] (p2) at (current page.center);
      \coordinate[xshift=-0.25\linewidth,yshift=0.25\textheight] (p3) at (current page.center);
      \coordinate[xshift=0.25\linewidth,yshift=0.25\textheight] (p4) at (current page.center);
      \draw[-latex,line width=2pt,color=red!50] (p1) -- (wmc);
      \draw[-latex,line width=2pt,color=red!50] (p2) -- (wmc);
      \draw[-latex,line width=2pt,color=red!50] (p3) -- (wmc);
      \draw[-latex,line width=2pt,color=red!50] (p4) -- (wmc);
    \end{tikzpicture}
  }
\end{frame}

\begin{frame}[fragile]{Weighted Model Counting (WMC)}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item Generalises propositional model counting ($\#\SAT{}$)
      \item Applications:
        \begin{itemize}
        \item graphical models
        \item probabilistic programming
        \item neural-symbolic artificial intelligence
        \end{itemize}
      \item Main types of algorithms:
        \begin{itemize}
        \item using knowledge compilation
        \item using a \SAT{} solver
        \item manipulating pseudo-Boolean functions
        \end{itemize}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{example}
      $w(x) = 0.3$, $w(\neg x) = 0.7$, $w(y) = 0.2$, $w(\neg y) = 0.8$
      \vspace{1cm}

      $\mathsf{WMC}(\alert{x \lor y}) = w(x)w(y) + w(x)w(\neg y) + w(\neg x)w(y)
      = 0.44$
      \end{example}
    \end{column}
  \end{columns}
\end{frame}

% BAs, pseudo-Boolean functions, measures, equivalence of definitions
\begin{frame}{An Alternative Way to Think About It}
\end{frame}

% The theorems: WMC is not expressive enough to cover all measures but can be
% extended to do so
\begin{frame}{Some Theoretical Results}
\end{frame}

% Things I could mention:
% The details of the transformation
% Experimental results

\begin{frame}{The Big Picture}
  \begin{columns}
    \begin{column}{0.35\textwidth}
      \centering
      \structure{Probabilistic Inference} \\
      (e.g., a Bayesian network)
      \fbox{
        \begin{minipage}{2.5cm}
          \centering
          \begin{tikzpicture}[edge from parent/.style={draw,-{Latex}}]
            \node[draw,circle] at (0, 0) (a) {$A$}
            child {node[draw,circle] (b) {$B$}};
          \end{tikzpicture}\\
          Find \alert{$\Pr(B = 0)$}
        \end{minipage}
      }
    \end{column}
    \begin{column}{0.35\textwidth}
      \centering
      \structure{WMC Encoding} \\
      (CNF with literal weights)
      \framebox{
        \scalebox{0.2}{
          \begin{tabular}{@{}l@{}}
            p cnf 8 17 \\
            -2 -1 0 \\
            1 2 0 \\
            -3 1 0 \\
            -1 3 0 \\
            -5 -1 0 \\
            -5 -4 0 \\
            1 4 5 0 \\
            -6 -1 0 \\
            -6 4 0 \\
            -4 1 6 0 \\
            -7 1 0 \\
            -7 -4 0 \\
            -1 4 7 0 \\
            -8 1 0 \\
            -8 4 0 \\
            -4 -1 8 0 \\
            -4 0 \\
            c weights 1.0 1.0 0.5 1.0 0.5 1.0 1.0 1.0 0.6 1.0 0.4 1.0 0.1 1.0 0.9 1.0
          \end{tabular}%
        }
      }

      \vspace{1cm}
      \onslide<2>{
      \structure{Conditional Weights} \\
      \framebox{
        \scalebox{0.2}{%
          \begin{tabular}{@{}l@{}}
            p cnf 2 1 \\
            2 0 \\
            w 1 0.5 0.5 \\
            w 2 1 0.6 0.4 \\
            w 2 -1 0.1 0.9
          \end{tabular}%
        }
      }
      }
    \end{column}
    \begin{column}{0.30\textwidth}
      \centering
      \structure{WMC Algorithm}\\
      \onslide<2>{\alert{$>100\times$} faster}
    \end{column}
  \end{columns}
  \begin{tikzpicture}[remember picture,overlay]
    \draw[-{Latex}] (3.4, 3) -- (4.9, 4);
    \draw<2>[-{Latex}] (3.4, 3) to [bend right] (5.8, 0.2);
    \draw[-{Latex}] (7.7, 4) -- (9, 2.8);
    \draw<2>[-{Latex}] (6.7, 0.2) to [bend right = 45] (9, 2.8);
  \end{tikzpicture}
\end{frame}
\end{document}

### 2021-06-02 doc/long_talk/scatter1.tex
Slides are almost ready

% Created by tikzDevice version 0.12.3.1 on 2021-06-01 14:27:09
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (343.28,231.26);
\begin{scope}
\path[clip] (  0.00,  0.09) rectangle (343.28,231.18);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.09) rectangle (343.28,231.18);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 30.77) rectangle (235.42,225.68);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 30.77) rectangle (235.42,225.68);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 39.63) --
	(235.42, 39.63);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,106.48) --
	(235.42,106.48);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,173.33) --
	(235.42,173.33);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 49.37, 30.77) --
	( 49.37,225.68);

\path[draw=drawColor,line width= 0.1pt,line join=round] (116.22, 30.77) --
	(116.22,225.68);

\path[draw=drawColor,line width= 0.1pt,line join=round] (183.07, 30.77) --
	(183.07,225.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 73.06) --
	(235.42, 73.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,139.91) --
	(235.42,139.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,206.76) --
	(235.42,206.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 82.79, 30.77) --
	( 82.79,225.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] (149.64, 30.77) --
	(149.64,225.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.49, 30.77) --
	(216.49,225.68);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.18,215.39) -- (136.04,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.18,218.25) -- (136.04,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.59,216.82) -- (136.63,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.61,214.80) -- (134.61,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.21,215.39) -- (137.06,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.21,218.25) -- (137.06,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.62,216.82) -- (137.65,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.64,214.80) -- (135.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.25,215.39) -- (137.10,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.25,218.25) -- (137.10,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.66,216.82) -- (137.69,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.68,214.80) -- (135.68,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.53,215.39) -- (140.39,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.53,218.25) -- (140.39,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.94,216.82) -- (140.98,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.96,214.80) -- (138.96,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.55,215.39) -- (136.40,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.55,218.25) -- (136.40,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.96,216.82) -- (136.99,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.97,214.80) -- (134.97,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.29,215.39) -- (137.14,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.29,218.25) -- (137.14,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.70,216.82) -- (137.73,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.71,214.80) -- (135.71,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.13,101.07) -- (137.99,103.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.13,103.92) -- (137.99,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.54,102.50) -- (138.58,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.56,100.48) -- (136.56,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.94,101.26) -- (136.79,104.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.94,104.11) -- (136.79,101.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.35,102.69) -- (137.39,102.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.37,100.67) -- (135.37,104.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.93,101.45) -- (138.79,104.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.93,104.30) -- (138.79,101.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.34,102.87) -- (139.38,102.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.36,100.86) -- (137.36,104.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.84, 97.15) -- (133.69,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.84,100.00) -- (133.69, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.25, 98.57) -- (134.28, 98.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.26, 96.56) -- (132.26,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.59, 98.35) -- (136.44,101.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.59,101.20) -- (136.44, 98.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.00, 99.77) -- (137.03, 99.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.01, 97.76) -- (135.01,101.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,215.39) -- (136.52,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,218.25) -- (136.52,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.08,216.82) -- (137.11,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.09,214.80) -- (135.09,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.20,215.39) -- (140.05,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.20,218.25) -- (140.05,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.61,216.82) -- (140.64,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.62,214.80) -- (138.62,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.51,215.39) -- (136.36,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.51,218.25) -- (136.36,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.92,216.82) -- (136.95,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.93,214.80) -- (134.93,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.36,215.39) -- (137.22,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.36,218.25) -- (137.22,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.77,216.82) -- (137.81,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.79,214.80) -- (135.79,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.27,215.39) -- (136.12,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.27,218.25) -- (136.12,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.68,216.82) -- (136.71,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.69,214.80) -- (134.69,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.10,112.67) -- (139.96,115.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.10,115.53) -- (139.96,112.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.51,114.10) -- (140.55,114.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.53,112.08) -- (138.53,116.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.49,106.70) -- (138.34,109.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.49,109.55) -- (138.34,106.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.90,108.13) -- (138.93,108.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.91,106.11) -- (136.91,110.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.90,106.57) -- (138.75,109.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.90,109.42) -- (138.75,106.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.31,108.00) -- (139.34,108.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.33,105.98) -- (137.33,110.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.10,105.90) -- (137.95,108.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.10,108.75) -- (137.95,105.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.51,107.33) -- (138.54,107.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.52,105.31) -- (136.52,109.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.50,107.33) -- (140.36,110.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.50,110.19) -- (140.36,107.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.91,108.76) -- (140.95,108.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.93,106.74) -- (138.93,110.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,106.57) -- (139.54,109.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,109.42) -- (139.54,106.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.10,108.00) -- (140.14,108.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.12,105.98) -- (138.12,110.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.66,100.08) -- (137.51,102.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.66,102.94) -- (137.51,100.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.07,101.51) -- (138.10,101.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.09, 99.49) -- (136.09,103.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.92,101.07) -- (137.77,103.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.92,103.92) -- (137.77,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.33,102.50) -- (138.36,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.34,100.48) -- (136.34,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.94,101.07) -- (135.79,103.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.94,103.92) -- (135.79,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.35,102.50) -- (136.38,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.36,100.48) -- (134.36,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.23,104.46) -- (139.09,107.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.23,107.32) -- (139.09,104.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.64,105.89) -- (139.68,105.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.66,103.87) -- (137.66,107.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31,102.17) -- (136.16,105.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31,105.03) -- (136.16,102.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.72,103.60) -- (136.75,103.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.73,101.58) -- (134.73,105.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.44,106.17) -- (137.29,109.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.44,109.03) -- (137.29,106.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.85,107.60) -- (137.88,107.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.86,105.58) -- (135.86,109.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.07,106.44) -- (138.92,109.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.07,109.29) -- (138.92,106.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.48,107.86) -- (139.51,107.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.49,105.85) -- (137.49,109.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29,107.94) -- (140.14,110.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29,110.79) -- (140.14,107.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.70,109.37) -- (140.73,109.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.72,107.35) -- (138.72,111.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.83,107.58) -- (140.69,110.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.83,110.43) -- (140.69,107.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.24,109.01) -- (141.28,109.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.26,106.99) -- (139.26,111.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.85,107.33) -- (139.70,110.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.85,110.19) -- (139.70,107.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.26,108.76) -- (140.29,108.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.28,106.74) -- (138.28,110.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,112.24) -- (139.54,115.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,115.09) -- (139.54,112.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.10,113.66) -- (140.14,113.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.12,111.64) -- (138.12,115.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,111.04) -- (140.02,113.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,113.89) -- (140.02,111.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.57,112.46) -- (140.61,112.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.59,110.45) -- (138.59,114.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.97,114.75) -- (138.82,117.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.97,117.60) -- (138.82,114.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.38,116.18) -- (139.41,116.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,114.16) -- (137.39,118.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.50,112.67) -- (139.35,115.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.50,115.53) -- (139.35,112.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.91,114.10) -- (139.94,114.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.92,112.08) -- (137.92,116.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.95,116.50) -- (140.80,119.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.95,119.35) -- (140.80,116.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.36,117.93) -- (141.40,117.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.38,115.91) -- (139.38,119.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.19,111.42) -- (141.04,114.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.19,114.27) -- (141.04,111.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.59,112.84) -- (141.63,112.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.61,110.83) -- (139.61,114.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.10,111.60) -- (140.95,114.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.10,114.46) -- (140.95,111.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.51,113.03) -- (141.54,113.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.52,111.01) -- (139.52,115.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.35,105.05) -- (138.20,107.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.35,107.91) -- (138.20,105.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.76,106.48) -- (138.79,106.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.77,104.46) -- (136.77,108.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,107.70) -- (140.02,110.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,110.55) -- (140.02,107.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.57,109.13) -- (140.61,109.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.59,107.11) -- (138.59,111.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.35,112.59) -- (140.20,115.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.35,115.44) -- (140.20,112.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.76,114.01) -- (140.79,114.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.78,111.99) -- (138.78,116.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.63,105.48) -- (139.48,108.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.63,108.34) -- (139.48,105.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.04,106.91) -- (140.07,106.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.05,104.89) -- (138.05,108.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.81,121.10) -- (141.66,123.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.81,123.95) -- (141.66,121.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.22,122.53) -- (142.25,122.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.24,120.51) -- (140.24,124.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.37,116.43) -- (139.22,119.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.37,119.29) -- (139.22,116.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.78,117.86) -- (139.81,117.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.79,115.84) -- (137.79,119.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.35,109.84) -- (138.20,112.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.35,112.69) -- (138.20,109.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.76,111.26) -- (138.79,111.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.77,109.24) -- (136.77,113.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,109.19) -- (139.54,112.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,112.05) -- (139.54,109.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.10,110.62) -- (140.14,110.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.12,108.60) -- (138.12,112.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.24,111.23) -- (138.09,114.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.24,114.08) -- (138.09,111.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.65,112.65) -- (138.68,112.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.67,110.64) -- (136.67,114.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.80,215.39) -- (153.66,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.80,218.25) -- (153.66,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.21,216.82) -- (154.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.23,214.80) -- (152.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.64,215.39) -- (148.49,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.64,218.25) -- (148.49,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.04,216.82) -- (149.08,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.06,214.80) -- (147.06,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.10,215.39) -- (149.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.10,218.25) -- (149.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.51,216.82) -- (150.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.53,214.80) -- (148.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.45,215.39) -- (157.30,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.45,218.25) -- (157.30,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.86,216.82) -- (157.89,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.87,214.80) -- (155.87,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.66,215.39) -- (150.51,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.66,218.25) -- (150.51,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.06,216.82) -- (151.10,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.08,214.80) -- (149.08,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.72,215.39) -- (155.58,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.72,218.25) -- (155.58,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.13,216.82) -- (156.17,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.15,214.80) -- (154.15,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.93,187.58) -- (149.78,190.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.93,190.43) -- (149.78,187.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.34,189.01) -- (150.37,189.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.36,186.99) -- (148.36,191.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.84,155.90) -- (150.69,158.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.84,158.76) -- (150.69,155.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.24,157.33) -- (151.28,157.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.26,155.31) -- (149.26,159.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.32,152.68) -- (148.17,155.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.32,155.53) -- (148.17,152.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.73,154.11) -- (148.76,154.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.75,152.09) -- (146.75,156.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.91,156.31) -- (150.76,159.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.91,159.16) -- (150.76,156.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.32,157.74) -- (151.35,157.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.34,155.72) -- (149.34,159.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.40,153.70) -- (149.25,156.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.40,156.55) -- (149.25,153.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.80,155.12) -- (149.84,155.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.82,153.11) -- (147.82,157.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.31,215.39) -- (154.16,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.31,218.25) -- (154.16,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.71,216.82) -- (154.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.73,214.80) -- (152.73,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.07,215.39) -- (153.92,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.07,218.25) -- (153.92,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.48,216.82) -- (154.51,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.50,214.80) -- (152.50,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.33,215.39) -- (154.18,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.33,218.25) -- (154.18,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.74,216.82) -- (154.77,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.76,214.80) -- (152.76,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.18,215.39) -- (154.03,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.18,218.25) -- (154.03,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.58,216.82) -- (154.62,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.60,214.80) -- (152.60,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.62,215.39) -- (154.47,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.62,218.25) -- (154.47,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.03,216.82) -- (155.06,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.05,214.80) -- (153.05,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.58,215.39) -- (154.44,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.58,218.25) -- (154.44,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.99,216.82) -- (155.03,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.01,214.80) -- (153.01,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.61,215.39) -- (150.46,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.61,218.25) -- (150.46,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.02,216.82) -- (151.05,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.04,214.80) -- (149.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.95,215.39) -- (151.81,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.95,218.25) -- (151.81,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.36,216.82) -- (152.40,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.38,214.80) -- (150.38,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.60,215.39) -- (156.46,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.60,218.25) -- (156.46,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.01,216.82) -- (157.05,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.03,214.80) -- (155.03,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.19,215.39) -- (154.04,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.19,218.25) -- (154.04,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.60,216.82) -- (154.63,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.61,214.80) -- (152.61,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.03,215.39) -- (153.89,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.03,218.25) -- (153.89,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.44,216.82) -- (154.48,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.46,214.80) -- (152.46,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.82,155.61) -- (149.67,158.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.82,158.47) -- (149.67,155.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.23,157.04) -- (150.26,157.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.24,155.02) -- (148.24,159.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.88,158.55) -- (151.74,161.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.88,161.41) -- (151.74,158.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.29,159.98) -- (152.33,159.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.31,157.96) -- (150.31,162.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.56,154.94) -- (150.42,157.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.56,157.79) -- (150.42,154.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.97,156.37) -- (151.01,156.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.99,154.35) -- (148.99,158.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.40,156.62) -- (149.25,159.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.40,159.47) -- (149.25,156.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.80,158.04) -- (149.84,158.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.82,156.02) -- (147.82,160.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.90,155.64) -- (149.75,158.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.90,158.49) -- (149.75,155.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.31,157.07) -- (150.34,157.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.32,155.05) -- (148.32,159.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.74,215.39) -- (154.60,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.74,218.25) -- (154.60,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.15,216.82) -- (155.19,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.17,214.80) -- (153.17,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.20,215.39) -- (155.06,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.20,218.25) -- (155.06,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.61,216.82) -- (155.65,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.63,214.80) -- (153.63,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.07,215.39) -- (154.92,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.07,218.25) -- (154.92,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.48,216.82) -- (155.52,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.50,214.80) -- (153.50,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.91,215.39) -- (153.77,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.91,218.25) -- (153.77,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.32,216.82) -- (154.36,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.34,214.80) -- (152.34,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.91,215.39) -- (154.77,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.91,218.25) -- (154.77,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.32,216.82) -- (155.36,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.34,214.80) -- (153.34,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.52,215.39) -- (155.37,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.52,218.25) -- (155.37,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.93,216.82) -- (155.96,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.95,214.80) -- (153.95,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.80,215.39) -- (158.65,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.80,218.25) -- (158.65,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.21,216.82) -- (159.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.23,214.80) -- (157.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.39,215.39) -- (158.24,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.39,218.25) -- (158.24,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.80,216.82) -- (158.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.82,214.80) -- (156.82,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.52,215.39) -- (155.37,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.52,218.25) -- (155.37,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.93,216.82) -- (155.96,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.95,214.80) -- (153.95,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.41,215.39) -- (156.26,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.41,218.25) -- (156.26,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.82,216.82) -- (156.85,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.84,214.80) -- (154.84,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.91,215.39) -- (158.77,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.91,218.25) -- (158.77,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.32,216.82) -- (159.36,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.34,214.80) -- (157.34,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.28,215.39) -- (155.13,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.28,218.25) -- (155.13,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.69,216.82) -- (155.73,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.71,214.80) -- (153.71,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.76,160.28) -- (152.61,163.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.76,163.14) -- (152.61,160.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.17,161.71) -- (153.20,161.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.19,159.69) -- (151.19,163.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.52,165.91) -- (152.38,168.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.52,168.77) -- (152.38,165.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.93,167.34) -- (152.97,167.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.95,165.32) -- (150.95,169.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.90,159.28) -- (150.75,162.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.90,162.13) -- (150.75,159.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.30,160.71) -- (151.34,160.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.32,158.69) -- (149.32,162.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.85,157.91) -- (150.70,160.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.85,160.77) -- (150.70,157.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.26,159.34) -- (151.29,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.28,157.32) -- (149.28,161.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.88,215.39) -- (154.73,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.88,218.25) -- (154.73,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.29,216.82) -- (155.33,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.31,214.80) -- (153.31,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.32,215.39) -- (156.17,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.32,218.25) -- (156.17,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.73,216.82) -- (156.76,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.75,214.80) -- (154.75,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.05,215.39) -- (156.90,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.05,218.25) -- (156.90,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.45,216.82) -- (157.49,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.47,214.80) -- (155.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.23,215.39) -- (155.08,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.23,218.25) -- (155.08,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.64,216.82) -- (155.67,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.65,214.80) -- (153.65,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.10,215.39) -- (156.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.10,218.25) -- (156.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.51,216.82) -- (157.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.53,214.80) -- (155.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.96,215.39) -- (165.81,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.96,218.25) -- (165.81,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.36,216.82) -- (166.40,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.38,214.80) -- (164.38,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.86,215.39) -- (164.71,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.86,218.25) -- (164.71,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.27,216.82) -- (165.30,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.28,214.80) -- (163.28,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.38,215.39) -- (165.23,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.38,218.25) -- (165.23,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.79,216.82) -- (165.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.81,214.80) -- (163.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.04,215.39) -- (164.90,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.04,218.25) -- (164.90,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.45,216.82) -- (165.49,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.47,214.80) -- (163.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.77,215.39) -- (166.63,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.77,218.25) -- (166.63,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.18,216.82) -- (167.22,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.20,214.80) -- (165.20,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.17,215.39) -- (165.03,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.17,218.25) -- (165.03,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.58,216.82) -- (165.62,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.60,214.80) -- (163.60,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.06,215.39) -- (159.92,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.06,218.25) -- (159.92,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.47,216.82) -- (160.51,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.49,214.80) -- (158.49,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.37,195.92) -- (164.22,198.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.37,198.78) -- (164.22,195.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.78,197.35) -- (164.81,197.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.79,195.33) -- (162.79,199.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.14,215.39) -- (159.99,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.14,218.25) -- (159.99,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.55,216.82) -- (160.58,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.57,214.80) -- (158.57,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.79,215.39) -- (161.64,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.79,218.25) -- (161.64,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.20,216.82) -- (162.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.21,214.80) -- (160.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.48,215.39) -- (163.34,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.48,218.25) -- (163.34,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.89,216.82) -- (163.93,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.91,214.80) -- (161.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.60,215.39) -- (164.45,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.60,218.25) -- (164.45,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.01,216.82) -- (165.04,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.03,214.80) -- (163.03,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.61,215.39) -- (165.46,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.61,218.25) -- (165.46,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.02,216.82) -- (166.05,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.04,214.80) -- (164.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.04,215.39) -- (164.89,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.04,218.25) -- (164.89,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.45,216.82) -- (165.48,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.46,214.80) -- (163.46,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.48,215.39) -- (164.34,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.48,218.25) -- (164.34,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.89,216.82) -- (164.93,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.91,214.80) -- (162.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.31,215.39) -- (166.16,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.31,218.25) -- (166.16,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.72,216.82) -- (166.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.74,214.80) -- (164.74,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.69,215.39) -- (167.54,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.69,218.25) -- (167.54,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.10,216.82) -- (168.13,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.12,214.80) -- (166.12,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.44,215.39) -- (167.29,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.44,218.25) -- (167.29,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.85,216.82) -- (167.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.87,214.80) -- (165.87,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.10,215.39) -- (165.95,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.10,218.25) -- (165.95,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.51,216.82) -- (166.54,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.52,214.80) -- (164.52,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.10,215.39) -- (168.95,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.10,218.25) -- (168.95,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.51,216.82) -- (169.54,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.52,214.80) -- (167.52,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.82,215.39) -- (166.67,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.82,218.25) -- (166.67,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.23,216.82) -- (167.26,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.24,214.80) -- (165.24,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.42,215.39) -- (167.27,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.42,218.25) -- (167.27,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.82,216.82) -- (167.86,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.84,214.80) -- (165.84,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.81,188.01) -- (163.66,190.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.81,190.86) -- (163.66,188.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.21,189.44) -- (164.25,189.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.23,187.42) -- (162.23,191.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.37,195.89) -- (161.22,198.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.37,198.74) -- (161.22,195.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.78,197.32) -- (161.81,197.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.79,195.30) -- (159.79,199.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.85,185.93) -- (162.71,188.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.85,188.79) -- (162.71,185.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.26,187.36) -- (163.30,187.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.28,185.34) -- (161.28,189.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.47,194.82) -- (162.32,197.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.47,197.67) -- (162.32,194.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.88,196.24) -- (162.92,196.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.90,194.23) -- (160.90,198.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.91,215.39) -- (162.76,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.91,218.25) -- (162.76,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.31,216.82) -- (163.35,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.33,214.80) -- (161.33,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.48,215.39) -- (168.34,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.48,218.25) -- (168.34,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.89,216.82) -- (168.93,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.91,214.80) -- (166.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.02,215.39) -- (167.87,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.02,218.25) -- (167.87,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.43,216.82) -- (168.47,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.45,214.80) -- (166.45,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.47,215.39) -- (166.33,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.47,218.25) -- (166.33,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.88,216.82) -- (166.92,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.90,214.80) -- (164.90,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.31,215.39) -- (166.16,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.31,218.25) -- (166.16,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.72,216.82) -- (166.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.74,214.80) -- (164.74,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.57,215.39) -- (167.42,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.57,218.25) -- (167.42,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.98,216.82) -- (168.01,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.99,214.80) -- (165.99,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.26,215.39) -- (168.11,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.26,218.25) -- (168.11,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.67,216.82) -- (168.70,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.68,214.80) -- (166.68,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.01,215.39) -- (169.87,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.01,218.25) -- (169.87,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.42,216.82) -- (170.46,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.44,214.80) -- (168.44,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.35,215.39) -- (167.20,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.35,218.25) -- (167.20,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.76,216.82) -- (167.79,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.78,214.80) -- (165.78,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.91,215.39) -- (170.77,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.91,218.25) -- (170.77,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.32,216.82) -- (171.36,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.34,214.80) -- (169.34,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.68,215.39) -- (168.53,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.68,218.25) -- (168.53,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.09,216.82) -- (169.13,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.11,214.80) -- (167.11,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.34,215.39) -- (169.19,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.34,218.25) -- (169.19,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.75,216.82) -- (169.78,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.76,214.80) -- (167.76,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.84,215.39) -- (167.70,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.84,218.25) -- (167.70,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.25,216.82) -- (168.29,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.27,214.80) -- (166.27,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.10,215.39) -- (160.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.10,218.25) -- (160.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.51,216.82) -- (161.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.53,214.80) -- (159.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.81,192.67) -- (161.66,195.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.81,195.52) -- (161.66,192.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.22,194.09) -- (162.25,194.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.23,192.07) -- (160.23,196.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.37,187.64) -- (160.23,190.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.37,190.50) -- (160.23,187.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.78,189.07) -- (160.82,189.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.80,187.05) -- (158.80,191.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.12,187.48) -- (159.98,190.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.12,190.33) -- (159.98,187.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.53,188.90) -- (160.57,188.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.55,186.88) -- (158.55,190.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.31,215.39) -- (169.16,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.31,218.25) -- (169.16,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.72,216.82) -- (169.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.73,214.80) -- (167.73,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.86,215.39) -- (167.71,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.86,218.25) -- (167.71,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.26,216.82) -- (168.30,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.28,214.80) -- (166.28,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.92,215.39) -- (166.78,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.92,218.25) -- (166.78,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.33,216.82) -- (167.37,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.35,214.80) -- (165.35,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.78,215.39) -- (166.64,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.78,218.25) -- (166.64,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.19,216.82) -- (167.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.21,214.80) -- (165.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.87,215.39) -- (167.72,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.87,218.25) -- (167.72,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.28,216.82) -- (168.31,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.30,214.80) -- (166.30,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.39,215.39) -- (182.24,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.39,218.25) -- (182.24,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.80,216.82) -- (182.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.81,214.80) -- (180.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.94,215.39) -- (182.80,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.94,218.25) -- (182.80,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.35,216.82) -- (183.39,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.37,214.80) -- (181.37,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.39,215.39) -- (182.25,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.39,218.25) -- (182.25,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.80,216.82) -- (182.84,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.82,214.80) -- (180.82,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.02,215.39) -- (181.87,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.02,218.25) -- (181.87,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.42,216.82) -- (182.46,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.44,214.80) -- (180.44,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.46,215.39) -- (181.32,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.46,218.25) -- (181.32,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.87,216.82) -- (181.91,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.89,214.80) -- (179.89,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.05,215.39) -- (181.90,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.05,218.25) -- (181.90,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.46,216.82) -- (182.49,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.47,214.80) -- (180.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.47,215.39) -- (172.32,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.47,218.25) -- (172.32,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.88,216.82) -- (172.91,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.90,214.80) -- (170.90,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.88,215.39) -- (180.73,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.88,218.25) -- (180.73,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.28,216.82) -- (181.32,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.30,214.80) -- (179.30,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.37,215.39) -- (173.22,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.37,218.25) -- (173.22,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.78,216.82) -- (173.82,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.80,214.80) -- (171.80,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.52,215.39) -- (174.38,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.52,218.25) -- (174.38,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.93,216.82) -- (174.97,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.95,214.80) -- (172.95,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.60,215.39) -- (171.46,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.60,218.25) -- (171.46,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.01,216.82) -- (172.05,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.03,214.80) -- (170.03,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.34,215.39) -- (181.20,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.34,218.25) -- (181.20,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.75,216.82) -- (181.79,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.77,214.80) -- (179.77,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.07,215.39) -- (181.93,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.07,218.25) -- (181.93,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.48,216.82) -- (182.52,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.50,214.80) -- (180.50,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.40,215.39) -- (180.25,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.40,218.25) -- (180.25,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.81,216.82) -- (180.85,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.83,214.80) -- (178.83,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.76,215.39) -- (180.62,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.76,218.25) -- (180.62,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.17,216.82) -- (181.21,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.19,214.80) -- (179.19,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.41,215.39) -- (181.27,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.41,218.25) -- (181.27,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.82,216.82) -- (181.86,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.84,214.80) -- (179.84,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.84,215.39) -- (182.70,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.84,218.25) -- (182.70,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.25,216.82) -- (183.29,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.27,214.80) -- (181.27,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.97,215.39) -- (182.83,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.97,218.25) -- (182.83,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.38,216.82) -- (183.42,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.40,214.80) -- (181.40,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.87,215.39) -- (184.72,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.87,218.25) -- (184.72,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.28,216.82) -- (185.31,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (183.30,214.80) -- (183.30,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.43,215.39) -- (185.29,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.43,218.25) -- (185.29,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.84,216.82) -- (185.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (183.86,214.80) -- (183.86,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.63,215.39) -- (182.49,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.63,218.25) -- (182.49,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.04,216.82) -- (183.08,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.06,214.80) -- (181.06,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.94,215.39) -- (182.79,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.94,218.25) -- (182.79,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.35,216.82) -- (183.38,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.37,214.80) -- (181.37,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.05,215.39) -- (173.90,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.05,218.25) -- (173.90,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.46,216.82) -- (174.49,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.47,214.80) -- (172.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.79,215.39) -- (176.65,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.79,218.25) -- (176.65,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.20,216.82) -- (177.24,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.22,214.80) -- (175.22,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.94,215.39) -- (172.79,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.94,218.25) -- (172.79,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.35,216.82) -- (173.38,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.37,214.80) -- (171.37,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.69,215.39) -- (171.54,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.69,218.25) -- (171.54,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.10,216.82) -- (172.13,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.11,214.80) -- (170.11,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.75,215.39) -- (174.60,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.75,218.25) -- (174.60,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.16,216.82) -- (175.19,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.18,214.80) -- (173.18,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.30,215.39) -- (182.15,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.30,218.25) -- (182.15,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.71,216.82) -- (182.74,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.72,214.80) -- (180.72,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.06,215.39) -- (181.91,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.06,218.25) -- (181.91,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.47,216.82) -- (182.50,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.48,214.80) -- (180.48,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.85,215.39) -- (180.71,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.85,218.25) -- (180.71,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.26,216.82) -- (181.30,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.28,214.80) -- (179.28,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.09,215.39) -- (181.95,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.09,218.25) -- (181.95,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.50,216.82) -- (182.54,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.52,214.80) -- (180.52,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.28,215.39) -- (182.13,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.28,218.25) -- (182.13,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.68,216.82) -- (182.72,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.70,214.80) -- (180.70,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.36,215.39) -- (184.21,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.36,218.25) -- (184.21,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.77,216.82) -- (184.80,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.79,214.80) -- (182.79,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.70,215.39) -- (183.55,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.70,218.25) -- (183.55,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.11,216.82) -- (184.14,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.12,214.80) -- (182.12,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.52,215.39) -- (184.37,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.52,218.25) -- (184.37,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.93,216.82) -- (184.96,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.94,214.80) -- (182.94,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.73,215.39) -- (185.59,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.73,218.25) -- (185.59,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.14,216.82) -- (186.18,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.16,214.80) -- (184.16,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.51,215.39) -- (184.37,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.51,218.25) -- (184.37,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.92,216.82) -- (184.96,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.94,214.80) -- (182.94,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.51,215.39) -- (184.36,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.51,218.25) -- (184.36,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.92,216.82) -- (184.95,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.94,214.80) -- (182.94,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.23,215.39) -- (175.08,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.23,218.25) -- (175.08,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.64,216.82) -- (175.67,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.66,214.80) -- (173.66,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.80,215.39) -- (173.65,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.80,218.25) -- (173.65,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.21,216.82) -- (174.24,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.22,214.80) -- (172.22,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.01,215.39) -- (172.87,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.01,218.25) -- (172.87,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.42,216.82) -- (173.46,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.44,214.80) -- (171.44,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.47,215.39) -- (176.32,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.47,218.25) -- (176.32,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.88,216.82) -- (176.91,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.90,214.80) -- (174.90,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.48,215.39) -- (175.34,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.48,218.25) -- (175.34,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.89,216.82) -- (175.93,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.91,214.80) -- (173.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.48,215.39) -- (182.33,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.48,218.25) -- (182.33,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.89,216.82) -- (182.92,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.91,214.80) -- (180.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.61,215.39) -- (185.47,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.61,218.25) -- (185.47,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.02,216.82) -- (186.06,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.04,214.80) -- (184.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.15,215.39) -- (183.01,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.15,218.25) -- (183.01,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.56,216.82) -- (183.60,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.58,214.80) -- (181.58,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.13,215.39) -- (182.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.13,218.25) -- (182.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.54,216.82) -- (183.58,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.56,214.80) -- (181.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.73,215.39) -- (182.59,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.73,218.25) -- (182.59,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.14,216.82) -- (183.18,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.16,214.80) -- (181.16,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.36,215.39) -- (189.22,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.36,218.25) -- (189.22,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.77,216.82) -- (189.81,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.79,214.80) -- (187.79,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.37,215.39) -- (188.23,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.37,218.25) -- (188.23,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.78,216.82) -- (188.82,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.80,214.80) -- (186.80,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.11,215.39) -- (189.97,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.11,218.25) -- (189.97,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.52,216.82) -- (190.56,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.54,214.80) -- (188.54,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.77,215.39) -- (190.63,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.77,218.25) -- (190.63,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.18,216.82) -- (191.22,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.20,214.80) -- (189.20,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.34,215.39) -- (188.20,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.34,218.25) -- (188.20,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.75,216.82) -- (188.79,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.77,214.80) -- (186.77,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.09,215.39) -- (189.94,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.09,218.25) -- (189.94,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.49,216.82) -- (190.53,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.51,214.80) -- (188.51,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.24,215.39) -- (177.09,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.24,218.25) -- (177.09,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.65,216.82) -- (177.68,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.67,214.80) -- (175.67,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (183.38,215.39) -- (186.24,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (183.38,218.25) -- (186.24,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.79,216.82) -- (186.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.81,214.80) -- (184.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.48,215.39) -- (178.33,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.48,218.25) -- (178.33,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.89,216.82) -- (178.93,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.91,214.80) -- (176.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.41,215.39) -- (179.26,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.41,218.25) -- (179.26,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.81,216.82) -- (179.85,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.83,214.80) -- (177.83,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.07,215.39) -- (178.92,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.07,218.25) -- (178.92,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.48,216.82) -- (179.51,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.49,214.80) -- (177.49,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.61,215.39) -- (190.47,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.61,218.25) -- (190.47,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.02,216.82) -- (191.06,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.04,214.80) -- (189.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.51,215.39) -- (188.37,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.51,218.25) -- (188.37,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.92,216.82) -- (188.96,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.94,214.80) -- (186.94,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.26,215.39) -- (190.12,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.26,218.25) -- (190.12,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.67,216.82) -- (190.71,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.69,214.80) -- (188.69,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.51,215.39) -- (188.36,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.51,218.25) -- (188.36,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.92,216.82) -- (188.95,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.93,214.80) -- (186.93,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.80,215.39) -- (188.66,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.80,218.25) -- (188.66,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (185.21,216.82) -- (189.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.23,214.80) -- (187.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.78,215.39) -- (192.64,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.78,218.25) -- (192.64,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.19,216.82) -- (193.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (191.21,214.80) -- (191.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.58,215.39) -- (192.44,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.58,218.25) -- (192.44,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.99,216.82) -- (193.03,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (191.01,214.80) -- (191.01,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.78,215.39) -- (191.64,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.78,218.25) -- (191.64,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.19,216.82) -- (192.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.21,214.80) -- (190.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.43,215.39) -- (193.29,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.43,218.25) -- (193.29,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.84,216.82) -- (193.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (191.86,214.80) -- (191.86,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.01,215.39) -- (191.86,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.01,218.25) -- (191.86,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.42,216.82) -- (192.45,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.44,214.80) -- (190.44,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.98,215.39) -- (191.83,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.98,218.25) -- (191.83,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.38,216.82) -- (192.42,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.40,214.80) -- (190.40,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.92,215.39) -- (178.77,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.92,218.25) -- (178.77,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.33,216.82) -- (179.36,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.34,214.80) -- (177.34,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.57,215.39) -- (179.43,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.57,218.25) -- (179.43,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.98,216.82) -- (180.02,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.00,214.80) -- (178.00,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.92,215.39) -- (179.77,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.92,218.25) -- (179.77,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.33,216.82) -- (180.36,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.35,214.80) -- (178.35,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.14,215.39) -- (179.99,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.14,218.25) -- (179.99,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.55,216.82) -- (180.58,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.56,214.80) -- (178.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.92,215.39) -- (178.78,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.92,218.25) -- (178.78,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.33,216.82) -- (179.37,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.35,214.80) -- (177.35,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.61,215.39) -- (189.46,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.61,218.25) -- (189.46,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.01,216.82) -- (190.05,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.03,214.80) -- (188.03,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.75,215.39) -- (189.60,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.75,218.25) -- (189.60,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.16,216.82) -- (190.20,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.18,214.80) -- (188.18,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.67,215.39) -- (189.53,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.67,218.25) -- (189.53,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.08,216.82) -- (190.12,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.10,214.80) -- (188.10,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.38,215.39) -- (190.24,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.38,218.25) -- (190.24,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.79,216.82) -- (190.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.81,214.80) -- (188.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.32,215.39) -- (190.18,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.32,218.25) -- (190.18,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.73,216.82) -- (190.77,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.75,214.80) -- (188.75,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (193.98,215.39) -- (196.83,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (193.98,218.25) -- (196.83,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (193.39,216.82) -- (197.42,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (195.40,214.80) -- (195.40,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.77,215.39) -- (199.62,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.77,218.25) -- (199.62,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.17,216.82) -- (200.21,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.19,214.80) -- (198.19,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.63,215.39) -- (200.49,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.63,218.25) -- (200.49,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.04,216.82) -- (201.08,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.06,214.80) -- (199.06,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.80,215.39) -- (200.66,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.80,218.25) -- (200.66,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.21,216.82) -- (201.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.23,214.80) -- (199.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (194.11,215.39) -- (196.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (194.11,218.25) -- (196.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (193.52,216.82) -- (197.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (195.53,214.80) -- (195.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.95,215.39) -- (200.80,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.95,218.25) -- (200.80,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.36,216.82) -- (201.39,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.37,214.80) -- (199.37,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.10,215.39) -- (179.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.10,218.25) -- (179.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.51,216.82) -- (180.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.53,214.80) -- (178.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.45,215.39) -- (180.30,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.45,218.25) -- (180.30,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.86,216.82) -- (180.90,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.88,214.80) -- (178.88,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.62,215.39) -- (179.47,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.62,218.25) -- (179.47,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.03,216.82) -- (180.06,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.04,214.80) -- (178.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.82,215.39) -- (182.68,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.82,218.25) -- (182.68,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.23,216.82) -- (183.27,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.25,214.80) -- (181.25,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.93,215.39) -- (181.79,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.93,218.25) -- (181.79,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.34,216.82) -- (182.38,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.36,214.80) -- (180.36,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.30,215.39) -- (193.15,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.30,218.25) -- (193.15,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.71,216.82) -- (193.74,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (191.73,214.80) -- (191.73,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.34,215.39) -- (191.19,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.34,218.25) -- (191.19,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.75,216.82) -- (191.78,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.77,214.80) -- (189.77,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.85,215.39) -- (190.70,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.85,218.25) -- (190.70,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.26,216.82) -- (191.29,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.28,214.80) -- (189.28,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.42,215.39) -- (190.27,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.42,218.25) -- (190.27,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.83,216.82) -- (190.87,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.85,214.80) -- (188.85,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.84,215.39) -- (190.69,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.84,218.25) -- (190.69,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.25,216.82) -- (191.28,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.26,214.80) -- (189.26,218.84);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (139.30,215.39) --
	(142.15,215.39) --
	(142.15,218.25) --
	(139.30,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.30,215.39) --
	(139.15,215.39) --
	(139.15,218.25) --
	(136.30,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.98,215.39) --
	(139.83,215.39) --
	(139.83,218.25) --
	(136.98,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.93,215.39) --
	(138.79,215.39) --
	(138.79,218.25) --
	(135.93,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.77,215.39) --
	(140.63,215.39) --
	(140.63,218.25) --
	(137.77,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.65,215.39) --
	(140.51,215.39) --
	(140.51,218.25) --
	(137.65,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.06,215.39) --
	(141.91,215.39) --
	(141.91,218.25) --
	(139.06,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.41,119.58) --
	(140.26,119.58) --
	(140.26,122.43) --
	(137.41,122.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.04,215.39) --
	(140.89,215.39) --
	(140.89,218.25) --
	(138.04,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.50,116.37) --
	(139.35,116.37) --
	(139.35,119.22) --
	(136.50,119.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.59,156.75) --
	(140.45,156.75) --
	(140.45,159.60) --
	(137.59,159.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.66,215.39) --
	(143.51,215.39) --
	(143.51,218.25) --
	(140.66,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.20,215.39) --
	(140.05,215.39) --
	(140.05,218.25) --
	(137.20,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.59,215.39) --
	(142.45,215.39) --
	(142.45,218.25) --
	(139.59,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.44,215.39) --
	(141.30,215.39) --
	(141.30,218.25) --
	(138.44,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.44,215.39) --
	(141.30,215.39) --
	(141.30,218.25) --
	(138.44,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.80,215.39) --
	(157.66,215.39) --
	(157.66,218.25) --
	(154.80,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.34,215.39) --
	(143.19,215.39) --
	(143.19,218.25) --
	(140.34,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.90,215.39) --
	(143.75,215.39) --
	(143.75,218.25) --
	(140.90,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.05,215.39) --
	(144.91,215.39) --
	(144.91,218.25) --
	(142.05,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.70,215.39) --
	(142.55,215.39) --
	(142.55,218.25) --
	(139.70,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.28,215.39) --
	(144.13,215.39) --
	(144.13,218.25) --
	(141.28,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.23,132.18) --
	(144.09,132.18) --
	(144.09,135.03) --
	(141.23,135.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.32,215.39) --
	(145.17,215.39) --
	(145.17,218.25) --
	(142.32,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.16,215.39) --
	(144.01,215.39) --
	(144.01,218.25) --
	(141.16,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.16,171.06) --
	(143.01,171.06) --
	(143.01,173.91) --
	(140.16,173.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.21,215.39) --
	(146.06,215.39) --
	(146.06,218.25) --
	(143.21,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.61,215.39) --
	(147.46,215.39) --
	(147.46,218.25) --
	(144.61,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.59,215.39) --
	(149.44,215.39) --
	(149.44,218.25) --
	(146.59,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.69,215.39) --
	(147.54,215.39) --
	(147.54,218.25) --
	(144.69,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.11,215.39) --
	(148.97,215.39) --
	(148.97,218.25) --
	(146.11,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.22,215.39) --
	(147.07,215.39) --
	(147.07,218.25) --
	(144.22,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.26,215.39) --
	(183.12,215.39) --
	(183.12,218.25) --
	(180.26,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.53,215.39) --
	(149.38,215.39) --
	(149.38,218.25) --
	(146.53,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.03,215.39) --
	(147.89,215.39) --
	(147.89,218.25) --
	(145.03,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.48,215.39) --
	(148.33,215.39) --
	(148.33,218.25) --
	(145.48,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.18,215.39) --
	(148.03,215.39) --
	(148.03,218.25) --
	(145.18,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.28,215.39) --
	(148.14,215.39) --
	(148.14,218.25) --
	(145.28,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.47,139.37) --
	(146.32,139.37) --
	(146.32,142.22) --
	(143.47,142.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.29,139.66) --
	(147.14,139.66) --
	(147.14,142.52) --
	(144.29,142.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.44,215.39) --
	(148.30,215.39) --
	(148.30,218.25) --
	(145.44,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.48,141.86) --
	(147.33,141.86) --
	(147.33,144.71) --
	(144.48,144.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.78,199.65) --
	(147.63,199.65) --
	(147.63,202.50) --
	(144.78,202.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.04,215.39) --
	(160.89,215.39) --
	(160.89,218.25) --
	(158.04,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.60,215.39) --
	(166.45,215.39) --
	(166.45,218.25) --
	(163.60,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.73,215.39) --
	(158.59,215.39) --
	(158.59,218.25) --
	(155.73,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.34,215.39) --
	(164.19,215.39) --
	(164.19,218.25) --
	(161.34,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.80,215.39) --
	(163.65,215.39) --
	(163.65,218.25) --
	(160.80,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.31,215.39) --
	(147.16,215.39) --
	(147.16,218.25) --
	(144.31,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.23,215.39) --
	(140.08,215.39) --
	(140.08,218.25) --
	(137.23,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.53,215.39) --
	(140.39,215.39) --
	(140.39,218.25) --
	(137.53,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.44,215.39) --
	(140.30,215.39) --
	(140.30,218.25) --
	(137.44,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.36,215.39) --
	(141.21,215.39) --
	(141.21,218.25) --
	(138.36,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.47,215.39) --
	(140.33,215.39) --
	(140.33,218.25) --
	(137.47,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.64,215.39) --
	(141.49,215.39) --
	(141.49,218.25) --
	(138.64,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.03,132.34) --
	(141.88,132.34) --
	(141.88,135.19) --
	(139.03,135.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.88,136.32) --
	(139.74,136.32) --
	(139.74,139.18) --
	(136.88,139.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.35,124.28) --
	(140.20,124.28) --
	(140.20,127.13) --
	(137.35,127.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.50,119.84) --
	(141.35,119.84) --
	(141.35,122.70) --
	(138.50,122.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.33,215.39) --
	(144.18,215.39) --
	(144.18,218.25) --
	(141.33,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.67,215.39) --
	(144.52,215.39) --
	(144.52,218.25) --
	(141.67,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.93,215.39) --
	(142.78,215.39) --
	(142.78,218.25) --
	(139.93,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.96,215.39) --
	(144.82,215.39) --
	(144.82,218.25) --
	(141.96,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.25,215.39) --
	(146.10,215.39) --
	(146.10,218.25) --
	(143.25,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.49,215.39) --
	(173.35,215.39) --
	(173.35,218.25) --
	(170.49,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.53,215.39) --
	(144.39,215.39) --
	(144.39,218.25) --
	(141.53,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.27,215.39) --
	(147.13,215.39) --
	(147.13,218.25) --
	(144.27,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.64,215.39) --
	(145.49,215.39) --
	(145.49,218.25) --
	(142.64,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.39,215.39) --
	(148.24,215.39) --
	(148.24,218.25) --
	(145.39,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.21,215.39) --
	(145.06,215.39) --
	(145.06,218.25) --
	(142.21,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.77,215.39) --
	(145.62,215.39) --
	(145.62,218.25) --
	(142.77,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.21,160.09) --
	(145.06,160.09) --
	(145.06,162.94) --
	(142.21,162.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.32,215.39) --
	(145.17,215.39) --
	(145.17,218.25) --
	(142.32,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.76,140.76) --
	(144.62,140.76) --
	(144.62,143.61) --
	(141.76,143.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.49,215.39) --
	(144.34,215.39) --
	(144.34,218.25) --
	(141.49,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.36,215.39) --
	(158.22,215.39) --
	(158.22,218.25) --
	(155.36,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.39,215.39) --
	(152.24,215.39) --
	(152.24,218.25) --
	(149.39,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.29,215.39) --
	(157.14,215.39) --
	(157.14,218.25) --
	(154.29,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.11,215.39) --
	(155.97,215.39) --
	(155.97,218.25) --
	(153.11,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.51,215.39) --
	(159.36,215.39) --
	(159.36,218.25) --
	(156.51,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (148.06,215.39) --
	(150.91,215.39) --
	(150.91,218.25) --
	(148.06,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.92,215.39) --
	(141.77,215.39) --
	(141.77,218.25) --
	(138.92,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.41,215.39) --
	(143.26,215.39) --
	(143.26,218.25) --
	(140.41,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.22,215.39) --
	(142.07,215.39) --
	(142.07,218.25) --
	(139.22,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.58,215.39) --
	(143.44,215.39) --
	(143.44,218.25) --
	(140.58,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.47,215.39) --
	(141.33,215.39) --
	(141.33,218.25) --
	(138.47,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.30,117.64) --
	(141.15,117.64) --
	(141.15,120.50) --
	(138.30,120.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.97,117.94) --
	(138.82,117.94) --
	(138.82,120.80) --
	(135.97,120.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.64,181.79) --
	(141.49,181.79) --
	(141.49,184.64) --
	(138.64,184.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.97,215.39) --
	(143.82,215.39) --
	(143.82,218.25) --
	(140.97,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.10,116.50) --
	(140.95,116.50) --
	(140.95,119.35) --
	(138.10,119.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.50,215.39) --
	(148.35,215.39) --
	(148.35,218.25) --
	(145.50,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.51,215.39) --
	(146.36,215.39) --
	(146.36,218.25) --
	(143.51,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.08,215.39) --
	(146.93,215.39) --
	(146.93,218.25) --
	(144.08,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.77,215.39) --
	(148.63,215.39) --
	(148.63,218.25) --
	(145.77,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.41,215.39) --
	(147.26,215.39) --
	(147.26,218.25) --
	(144.41,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.17,215.39) --
	(157.02,215.39) --
	(157.02,218.25) --
	(154.17,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.78,215.39) --
	(142.63,215.39) --
	(142.63,218.25) --
	(139.78,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.53,215.39) --
	(144.39,215.39) --
	(144.39,218.25) --
	(141.53,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.90,215.39) --
	(142.76,215.39) --
	(142.76,218.25) --
	(139.90,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.68,215.39) --
	(143.53,215.39) --
	(143.53,218.25) --
	(140.68,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.81,215.39) --
	(141.66,215.39) --
	(141.66,218.25) --
	(138.81,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.53,215.39) --
	(140.39,215.39) --
	(140.39,218.25) --
	(137.53,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.21,215.39) --
	(144.06,215.39) --
	(144.06,218.25) --
	(141.21,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.19,188.53) --
	(142.05,188.53) --
	(142.05,191.38) --
	(139.19,191.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.42,215.39) --
	(144.27,215.39) --
	(144.27,218.25) --
	(141.42,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.57,154.29) --
	(142.42,154.29) --
	(142.42,157.14) --
	(139.57,157.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.02,215.39) --
	(147.87,215.39) --
	(147.87,218.25) --
	(145.02,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.96,215.39) --
	(148.81,215.39) --
	(148.81,218.25) --
	(145.96,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.75,215.39) --
	(150.60,215.39) --
	(150.60,218.25) --
	(147.75,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.90,215.39) --
	(150.75,215.39) --
	(150.75,218.25) --
	(147.90,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.76,215.39) --
	(148.61,215.39) --
	(148.61,218.25) --
	(145.76,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.21,215.39) --
	(176.07,215.39) --
	(176.07,218.25) --
	(173.21,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.92,215.39) --
	(145.77,215.39) --
	(145.77,218.25) --
	(142.92,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.40,215.39) --
	(145.26,215.39) --
	(145.26,218.25) --
	(142.40,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.89,215.39) --
	(145.75,215.39) --
	(145.75,218.25) --
	(142.89,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.06,215.39) --
	(145.91,215.39) --
	(145.91,218.25) --
	(143.06,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.65,215.39) --
	(148.51,215.39) --
	(148.51,218.25) --
	(145.65,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.80,141.43) --
	(143.66,141.43) --
	(143.66,144.28) --
	(140.80,144.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.83,215.39) --
	(144.68,215.39) --
	(144.68,218.25) --
	(141.83,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.67,215.39) --
	(144.52,215.39) --
	(144.52,218.25) --
	(141.67,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.81,215.39) --
	(144.66,215.39) --
	(144.66,218.25) --
	(141.81,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.03,215.39) --
	(144.88,215.39) --
	(144.88,218.25) --
	(142.03,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.81,215.39) --
	(159.66,215.39) --
	(159.66,218.25) --
	(156.81,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.07,215.39) --
	(162.92,215.39) --
	(162.92,218.25) --
	(160.07,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.42,215.39) --
	(159.28,215.39) --
	(159.28,218.25) --
	(156.42,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.37,215.39) --
	(161.22,215.39) --
	(161.22,218.25) --
	(158.37,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.19,215.39) --
	(161.04,215.39) --
	(161.04,218.25) --
	(158.19,218.25) --
	cycle;
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.29,136.70) -- (132.33,136.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.31,134.69) -- (130.31,138.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.90,109.37) -- (127.93,109.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.91,107.35) -- (125.91,111.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.04,115.49) -- (128.08,115.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.06,113.47) -- (126.06,117.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.79,134.22) -- (131.83,134.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.81,132.20) -- (129.81,136.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.24,125.55) -- (132.27,125.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.26,123.53) -- (130.26,127.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.57,130.80) -- (132.60,130.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.58,128.78) -- (130.58,132.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.75,135.92) -- (127.78,135.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.76,133.91) -- (125.76,137.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.97,119.19) -- (129.01,119.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.99,117.17) -- (126.99,121.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.26,135.75) -- (128.30,135.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.28,133.73) -- (126.28,137.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.05,125.86) -- (127.09,125.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.07,123.84) -- (125.07,127.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.62,137.48) -- (132.66,137.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.64,135.46) -- (130.64,139.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.67,133.59) -- (132.71,133.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.69,131.57) -- (130.69,135.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.07,134.09) -- (132.11,134.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.09,132.08) -- (130.09,136.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.56,133.11) -- (133.59,133.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.57,131.09) -- (131.57,135.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.20,135.28) -- (133.24,135.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.22,133.26) -- (131.22,137.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.26,131.49) -- (128.30,131.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.28,129.47) -- (126.28,133.51);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.04,113.98) -- (139.89,116.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.04,116.84) -- (139.89,113.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.45,115.41) -- (140.48,115.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.47,113.39) -- (138.47,117.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.50,114.97) -- (141.35,117.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.50,117.82) -- (141.35,114.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.91,116.40) -- (141.94,116.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.93,114.38) -- (139.93,118.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.74,119.90) -- (140.60,122.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.74,122.75) -- (140.60,119.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.15,121.32) -- (141.19,121.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.17,119.31) -- (139.17,123.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.32,113.83) -- (140.17,116.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.32,116.68) -- (140.17,113.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.73,115.25) -- (140.76,115.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.75,113.24) -- (138.75,117.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.47,117.46) -- (141.33,120.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.47,120.31) -- (141.33,117.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.88,118.88) -- (141.92,118.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.90,116.87) -- (139.90,120.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.01,114.30) -- (139.86,117.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.01,117.15) -- (139.86,114.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.42,115.72) -- (140.45,115.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.44,113.70) -- (138.44,117.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.46,114.06) -- (139.32,116.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.46,116.92) -- (139.32,114.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.87,115.49) -- (139.91,115.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.89,113.47) -- (137.89,117.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.23,109.94) -- (139.09,112.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.23,112.79) -- (139.09,109.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.64,111.37) -- (139.68,111.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.66,109.35) -- (137.66,113.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.85,110.35) -- (139.70,113.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.85,113.20) -- (139.70,110.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.26,111.77) -- (140.29,111.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.28,109.76) -- (138.28,113.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.73,108.75) -- (141.58,111.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.73,111.60) -- (141.58,108.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.13,110.18) -- (142.17,110.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.15,108.16) -- (140.15,112.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.68,108.52) -- (140.54,111.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.68,111.38) -- (140.54,108.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.09,109.95) -- (141.13,109.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.11,107.93) -- (139.11,111.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.92,116.23) -- (140.78,119.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.92,119.09) -- (140.78,116.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.33,117.66) -- (141.37,117.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.35,115.64) -- (139.35,119.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.89,118.36) -- (141.75,121.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.89,121.21) -- (141.75,118.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.30,119.78) -- (142.34,119.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.32,117.76) -- (140.32,121.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.07,112.32) -- (139.92,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.07,115.18) -- (139.92,112.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.48,113.75) -- (140.52,113.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.50,111.73) -- (138.50,115.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.07,111.79) -- (139.92,114.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.07,114.64) -- (139.92,111.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.48,113.21) -- (140.52,113.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.50,111.20) -- (138.50,115.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.13,114.37) -- (142.99,117.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.13,117.23) -- (142.99,114.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.54,115.80) -- (143.58,115.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.56,113.78) -- (141.56,117.82);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.20,216.82) -- (218.24,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (216.22,214.80) -- (216.22,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (209.19,216.82) -- (213.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.21,214.80) -- (211.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (208.62,216.82) -- (212.66,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (210.64,214.80) -- (210.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.61,216.82) -- (217.65,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (215.63,214.80) -- (215.63,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.73,216.82) -- (132.76,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.75,214.80) -- (130.75,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.30,206.31) -- (133.34,206.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.32,204.29) -- (131.32,208.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.56,204.05) -- (133.59,204.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.57,202.03) -- (131.57,206.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.35,205.62) -- (133.39,205.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.37,203.60) -- (131.37,207.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.18,206.47) -- (135.21,206.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.19,204.45) -- (133.19,208.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.89,204.42) -- (132.92,204.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.90,202.40) -- (130.90,206.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.00,205.41) -- (135.03,205.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.01,203.39) -- (133.01,207.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.03,204.52) -- (131.07,204.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.05,202.50) -- (129.05,206.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.62,205.41) -- (132.66,205.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.64,203.40) -- (130.64,207.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.25,205.79) -- (133.29,205.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.27,203.77) -- (131.27,207.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.15,192.95) -- (134.19,192.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.17,190.93) -- (132.17,194.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.35,204.31) -- (132.38,204.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.37,202.29) -- (130.37,206.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.92,206.20) -- (135.96,206.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.94,204.18) -- (133.94,208.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99,205.97) -- (133.03,205.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.01,203.95) -- (131.01,207.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.30,216.82) -- (136.34,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.32,214.80) -- (134.32,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.91,203.78) -- (133.94,203.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.92,201.76) -- (131.92,205.80);

\path[fill=fillColor,fill opacity=0.50] (141.37,215.39) --
	(144.23,215.39) --
	(144.23,218.25) --
	(141.37,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.42,215.39) --
	(141.27,215.39) --
	(141.27,218.25) --
	(138.42,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.74,215.39) --
	(140.60,215.39) --
	(140.60,218.25) --
	(137.74,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.81,215.39) --
	(141.66,215.39) --
	(141.66,218.25) --
	(138.81,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.30,215.39) --
	(141.15,215.39) --
	(141.15,218.25) --
	(138.30,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.04,215.39) --
	(140.89,215.39) --
	(140.89,218.25) --
	(138.04,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.51,215.39) --
	(142.37,215.39) --
	(142.37,218.25) --
	(139.51,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.33,127.40) --
	(141.18,127.40) --
	(141.18,130.25) --
	(138.33,130.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.46,215.39) --
	(142.31,215.39) --
	(142.31,218.25) --
	(139.46,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.14,120.26) --
	(141.99,120.26) --
	(141.99,123.11) --
	(139.14,123.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.41,157.01) --
	(140.26,157.01) --
	(140.26,159.86) --
	(137.41,159.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.43,215.39) --
	(142.29,215.39) --
	(142.29,218.25) --
	(139.43,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.50,215.39) --
	(141.35,215.39) --
	(141.35,218.25) --
	(138.50,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.48,215.39) --
	(143.34,215.39) --
	(143.34,218.25) --
	(140.48,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.41,215.39) --
	(143.26,215.39) --
	(143.26,218.25) --
	(140.41,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.26,215.39) --
	(144.11,215.39) --
	(144.11,218.25) --
	(141.26,218.25) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.45,216.82) -- (184.48,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.47,214.80) -- (182.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.40,216.82) -- (177.44,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.42,214.80) -- (175.42,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.25,216.82) -- (186.29,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.27,214.80) -- (184.27,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.41,216.82) -- (180.45,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.43,214.80) -- (178.43,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (182.15,216.82) -- (186.19,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.17,214.80) -- (184.17,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.29,216.82) -- (182.33,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.31,214.80) -- (180.31,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.77,216.82) -- (168.80,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.79,214.80) -- (166.79,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.62,216.82) -- (143.65,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.64,214.80) -- (141.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.27,216.82) -- (141.31,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.29,214.80) -- (139.29,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.04,216.82) -- (203.08,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.06,214.80) -- (201.06,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (204.76,216.82) -- (208.80,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (206.78,214.80) -- (206.78,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.41,216.82) -- (207.44,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (205.42,214.80) -- (205.42,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.06,216.82) -- (205.10,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.08,214.80) -- (203.08,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.33,216.82) -- (188.37,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.35,214.80) -- (186.35,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.16,216.82) -- (202.20,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.18,214.80) -- (200.18,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.31,216.82) -- (139.34,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.33,214.80) -- (137.33,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.83,216.82) -- (138.86,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.84,214.80) -- (136.84,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.54,216.82) -- (139.58,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.56,214.80) -- (137.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.51,216.82) -- (138.54,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.52,214.80) -- (136.52,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.45,216.82) -- (141.48,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.47,214.80) -- (139.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.51,216.82) -- (139.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.53,214.80) -- (137.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.66,216.82) -- (137.69,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.68,214.80) -- (135.68,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.03,216.82) -- (139.07,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.05,214.80) -- (137.05,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.35,216.82) -- (173.38,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.37,214.80) -- (171.37,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (192.60,216.82) -- (196.63,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (194.61,214.80) -- (194.61,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.16,216.82) -- (207.20,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (205.18,214.80) -- (205.18,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.56,216.82) -- (202.59,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.58,214.80) -- (200.58,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.63,216.82) -- (205.67,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.65,214.80) -- (203.65,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.24,216.82) -- (185.27,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (183.25,214.80) -- (183.25,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.37,216.82) -- (146.40,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.38,214.80) -- (144.38,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.70,216.82) -- (146.73,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.71,214.80) -- (144.71,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.39,216.82) -- (147.43,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.41,214.80) -- (145.41,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.28,216.82) -- (147.31,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.29,214.80) -- (145.29,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.57,216.82) -- (146.61,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.59,214.80) -- (144.59,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.19,216.82) -- (145.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.21,214.80) -- (143.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.21,216.82) -- (144.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.23,214.80) -- (142.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.26,216.82) -- (147.29,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.27,214.80) -- (145.27,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.28,216.82) -- (145.32,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.30,214.80) -- (143.30,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.29,216.82) -- (143.32,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.31,214.80) -- (141.31,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.46,216.82) -- (183.50,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.48,214.80) -- (181.48,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.78,216.82) -- (146.81,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.80,214.80) -- (144.80,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.08,216.82) -- (150.12,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.10,214.80) -- (148.10,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.72,216.82) -- (152.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.74,214.80) -- (150.74,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.54,216.82) -- (150.58,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.56,214.80) -- (148.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.21,216.82) -- (153.24,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.22,214.80) -- (151.22,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.53,216.82) -- (145.56,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.55,214.80) -- (143.55,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.22,216.82) -- (142.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.24,214.80) -- (140.24,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.16,216.82) -- (143.19,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.18,214.80) -- (141.18,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.68,216.82) -- (145.72,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.70,214.80) -- (143.70,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.85,216.82) -- (179.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.87,214.80) -- (177.87,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.60,216.82) -- (192.64,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.62,214.80) -- (190.62,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (189.71,216.82) -- (193.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (191.73,214.80) -- (191.73,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.43,216.82) -- (180.46,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.44,214.80) -- (178.44,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (190.85,216.82) -- (194.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (192.87,214.80) -- (192.87,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.07,216.82) -- (190.10,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.09,214.80) -- (188.09,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.40,216.82) -- (150.44,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.42,214.80) -- (148.42,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.51,216.82) -- (152.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.53,214.80) -- (150.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.93,216.82) -- (150.96,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.95,214.80) -- (148.95,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.67,216.82) -- (153.70,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.69,214.80) -- (151.69,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.66,216.82) -- (149.69,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.67,214.80) -- (147.67,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.89,216.82) -- (188.92,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.90,214.80) -- (186.90,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.97,216.82) -- (145.00,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.98,214.80) -- (142.98,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.28,216.82) -- (144.32,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.30,214.80) -- (142.30,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.79,216.82) -- (149.82,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.81,214.80) -- (147.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.79,216.82) -- (138.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.81,214.80) -- (136.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.22,216.82) -- (135.26,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.24,214.80) -- (133.24,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.25,216.82) -- (138.29,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.27,214.80) -- (136.27,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.22,216.82) -- (135.26,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.24,214.80) -- (133.24,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.29,216.82) -- (138.32,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.31,214.80) -- (136.31,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.36,216.82) -- (142.39,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.37,214.80) -- (140.37,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.85,216.82) -- (137.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.86,214.80) -- (135.86,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.97,216.82) -- (141.01,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.99,214.80) -- (138.99,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.62,216.82) -- (143.65,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.64,214.80) -- (141.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.20,216.82) -- (140.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.21,214.80) -- (138.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,216.82) -- (141.43,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.41,214.80) -- (139.41,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.91,216.82) -- (140.95,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.93,214.80) -- (138.93,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.68,216.82) -- (138.72,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.70,214.80) -- (136.70,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.62,216.82) -- (141.66,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.64,214.80) -- (139.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.28,216.82) -- (161.31,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.29,214.80) -- (159.29,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.63,216.82) -- (136.67,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.65,214.80) -- (134.65,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.88,216.82) -- (136.91,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.89,214.80) -- (134.89,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.77,171.45) -- (137.81,171.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.79,169.44) -- (135.79,173.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.00,171.18) -- (138.03,171.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.01,169.16) -- (136.01,173.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.45,216.82) -- (141.48,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.47,214.80) -- (139.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.48,216.82) -- (141.51,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.50,214.80) -- (139.50,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.68,216.82) -- (142.72,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.70,214.80) -- (140.70,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.52,216.82) -- (142.56,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.54,214.80) -- (140.54,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.96,216.82) -- (146.00,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.98,214.80) -- (143.98,218.84);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.38,120.51) rectangle (140.23,123.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.38,120.51) -- (140.23,123.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.38,123.36) -- (140.23,120.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.10,119.04) rectangle (136.95,121.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.10,119.04) -- (136.95,121.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.10,121.89) -- (136.95,119.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.04,112.32) rectangle (134.89,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.04,112.32) -- (134.89,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.04,115.18) -- (134.89,112.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.21,113.51) rectangle (135.07,116.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.21,113.51) -- (135.07,116.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.21,116.36) -- (135.07,113.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.88,119.90) rectangle (137.73,122.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.88,119.90) -- (137.73,122.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.88,122.75) -- (137.73,119.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,111.88) rectangle (136.52,114.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,111.88) -- (136.52,114.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,114.73) -- (136.52,111.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.14, 91.01) rectangle (136.00, 93.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.14, 91.01) -- (136.00, 93.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.14, 93.86) -- (136.00, 91.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.54, 84.93) rectangle (134.39, 87.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.54, 84.93) -- (134.39, 87.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.54, 87.78) -- (134.39, 84.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.59, 85.50) rectangle (133.45, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.59, 85.50) -- (133.45, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.59, 88.35) -- (133.45, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.43, 92.80) rectangle (136.28, 95.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.43, 92.80) -- (136.28, 95.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.43, 95.66) -- (136.28, 92.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.21, 97.40) rectangle (137.06,100.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.21, 97.40) -- (137.06,100.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.21,100.25) -- (137.06, 97.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.38,114.67) rectangle (138.23,117.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.38,114.67) -- (138.23,117.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.38,117.53) -- (138.23,114.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,116.23) rectangle (137.62,119.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,116.23) -- (137.62,119.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,119.09) -- (137.62,116.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.23,112.32) rectangle (136.08,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.23,112.32) -- (136.08,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.23,115.18) -- (136.08,112.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.03,117.15) rectangle (137.88,120.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.03,117.15) -- (137.88,120.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.03,120.00) -- (137.88,117.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.35,114.22) rectangle (136.20,117.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.35,114.22) -- (136.20,117.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.35,117.07) -- (136.20,114.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31, 95.28) rectangle (136.16, 98.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31, 95.28) -- (136.16, 98.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31, 98.13) -- (136.16, 95.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.55, 88.51) rectangle (133.40, 91.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.55, 88.51) -- (133.40, 91.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.55, 91.37) -- (133.40, 88.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.95, 89.39) rectangle (129.80, 92.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.95, 89.39) -- (129.80, 92.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.95, 92.25) -- (129.80, 89.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03, 92.46) rectangle (133.88, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03, 92.46) -- (133.88, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03, 95.32) -- (133.88, 92.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.49, 83.72) rectangle (128.35, 86.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.49, 83.72) -- (128.35, 86.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.49, 86.57) -- (128.35, 83.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.55, 85.50) rectangle (131.40, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.55, 85.50) -- (131.40, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.55, 88.35) -- (131.40, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.21, 85.50) rectangle (131.06, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.21, 85.50) -- (131.06, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.21, 88.35) -- (131.06, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31, 99.24) rectangle (136.16,102.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31, 99.24) -- (136.16,102.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.31,102.09) -- (136.16, 99.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99, 85.50) rectangle (131.85, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99, 85.50) -- (131.85, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99, 88.35) -- (131.85, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42, 90.62) rectangle (132.28, 93.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42, 90.62) -- (132.28, 93.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42, 93.48) -- (132.28, 90.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03, 96.89) rectangle (133.88, 99.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03, 96.89) -- (133.88, 99.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03, 99.75) -- (133.88, 96.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56,128.45) rectangle (135.41,131.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56,128.45) -- (135.41,131.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56,131.30) -- (135.41,128.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.66,125.92) rectangle (131.52,128.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.66,125.92) -- (131.52,128.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.66,128.77) -- (131.52,125.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.72,129.80) rectangle (134.58,132.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.72,129.80) -- (134.58,132.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.72,132.65) -- (134.58,129.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.73,128.04) rectangle (135.58,130.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.73,128.04) -- (135.58,130.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.73,130.89) -- (135.58,128.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.98,130.22) rectangle (136.83,133.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.98,130.22) -- (136.83,133.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.98,133.07) -- (136.83,130.22);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.41,216.82) -- (142.45,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.43,214.80) -- (140.43,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.39,216.82) -- (136.42,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.41,214.80) -- (134.41,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.38,216.82) -- (139.41,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,214.80) -- (137.39,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.96,216.82) -- (136.99,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.97,214.80) -- (134.97,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.84,216.82) -- (139.88,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.86,214.80) -- (137.86,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.62,216.82) -- (137.65,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.64,214.80) -- (135.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.45,216.82) -- (135.48,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.46,214.80) -- (133.46,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.88,216.82) -- (136.91,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.89,214.80) -- (134.89,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.46,216.82) -- (133.49,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.47,214.80) -- (131.47,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.02,216.82) -- (132.05,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.03,214.80) -- (130.03,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.58,216.82) -- (135.61,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.59,214.80) -- (133.59,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.88,216.82) -- (136.91,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.89,214.80) -- (134.89,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.58,216.82) -- (139.61,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.59,214.80) -- (137.59,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.08,216.82) -- (137.11,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.09,214.80) -- (135.09,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.00,216.82) -- (139.03,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.02,214.80) -- (137.02,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.40,216.82) -- (135.44,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.42,214.80) -- (133.42,218.84);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.08, 68.39) rectangle (125.93, 71.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.08, 68.39) -- (125.93, 71.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.08, 71.24) -- (125.93, 68.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.72, 75.44) rectangle (131.57, 78.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.72, 75.44) -- (131.57, 78.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.72, 78.29) -- (131.57, 75.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29,108.18) rectangle (140.14,111.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29,108.18) -- (140.14,111.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29,111.03) -- (140.14,108.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.39,143.87) rectangle (153.24,146.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.39,143.87) -- (153.24,146.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.39,146.73) -- (153.24,143.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.56,168.04) rectangle (155.42,170.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.56,168.04) -- (155.42,170.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.56,170.89) -- (155.42,168.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.34,193.96) rectangle (167.19,196.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.34,193.96) -- (167.19,196.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.34,196.81) -- (167.19,193.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.00,215.39) rectangle (166.85,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.00,215.39) -- (166.85,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.00,218.25) -- (166.85,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.88,215.39) rectangle (173.73,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.88,215.39) -- (173.73,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.88,218.25) -- (173.73,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.06,215.39) rectangle (180.91,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.06,215.39) -- (180.91,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.06,218.25) -- (180.91,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.80,215.39) rectangle (187.65,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.80,215.39) -- (187.65,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (184.80,218.25) -- (187.65,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.10,215.39) rectangle (190.95,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.10,215.39) -- (190.95,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.10,218.25) -- (190.95,215.39);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (135.13, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.28, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.13, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.26, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.40, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.43, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.54, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.83, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.46, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.23, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.85, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.15, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.64, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.53, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.99, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.26, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.57, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.87, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.31, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.68, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.37, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.91, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.13, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (159.77, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.85, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.06, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.73, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.04, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.54, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.24, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.37, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.76, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.06, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (158.41, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.55, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.91, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.10, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.90, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.44, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.50, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (164.86, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.15, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.93, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.06, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (149.89, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.76, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.50, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.31, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.51, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (138.21, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.74, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.80, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.61, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.57, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.56, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.01, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.61, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.87, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.93, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.46, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.58, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.75, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.50, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.83, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (155.05, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.84, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.59, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.75, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.11, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.26, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.18, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.59, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.99, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.78, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.43, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (149.86, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.91, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.26, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.95, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (143.14, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.73, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (146.17, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.84, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.23, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.76, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.22, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (155.82, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.31, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.77, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.13, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.18, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.18, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.28, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.75, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.91, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (163.67, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (137.99, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.17, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.73, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (160.83, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.53, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.26, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (143.12, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.90, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.06, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.54, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (184.52, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.59, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.87, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.26, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.88, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.71, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.41, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.13, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.99, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.31, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (178.02, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.64, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.06, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.81, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.67, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.06, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.92, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.31, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.40, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.71, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.29, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.85, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.78, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (170.20, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.73, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.99, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.64, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (154.59, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (135.01, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.13, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (168.26, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.32, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.69, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.47, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.67, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.12, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.47, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (174.45, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (155.56, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.61, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.64, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (186.75, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (190.54, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (144.22, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.29, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (204.52, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (159.31, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (135.45, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.18, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (165.41, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (165.35, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.22, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.06, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (149.62, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.47, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.15, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (141.99, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.33, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.14, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.58, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.73, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.64, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.60, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.73, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.52, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.60, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.33, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.14, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (162.60, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.97, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.85, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.50, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.80, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (164.85, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.14, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.76, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.41, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.20, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (137.53, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.57, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.67, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.31, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (150.59, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.26, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.23, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 80.76) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.92, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.40, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.78, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.61, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.26, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.64, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.52, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (178.70, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.37, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.64, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.68, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.46, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.26, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.11, 89.48) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.15, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.94, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.99, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.01, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.64, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (198.67, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (162.33, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.81, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.26, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (173.23, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.75, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.06, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.81, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (152.50, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (135.60, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.50, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.11, 81.59) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (181.20, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (138.34, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.01, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.26, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.61, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.64, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.05, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.47, 89.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.19, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.47, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.47, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.35, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (144.30, 88.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.05, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.49, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.81, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (166.42, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (205.42, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (151.77, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.05, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (165.28, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (140.51, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.31, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.26, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (226.56, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (157.23, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (143.14, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.37, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (203.67, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (173.21, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.20, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.05, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (207.49, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (158.60, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (137.29, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.07, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (177.48, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.42, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.55, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.71, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (170.77, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (140.10, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.56, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.73, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (204.88, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (187.83, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (135.17, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.87, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.52, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.47, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.71, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (140.97, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.48, 85.15) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (163.48, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.31, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (142.16, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.68, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.22, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.99, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (147.87, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.75, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.99, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.60, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.17, 86.36) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.90, 87.47) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.20, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.99, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (165.50, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.48, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.44, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.84, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (139.55, 88.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.37, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.91, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (196.30, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.64, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.78, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (155.37, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.87, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.84, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (143.44, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.58, 80.76) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.14, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.59, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.58, 80.76) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.20, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.75, 86.36) circle (  1.43);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (136.81, 96.78) --
	(138.73, 93.45) --
	(134.89, 93.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.27, 82.98) --
	(133.19, 79.65) --
	(129.35, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.97, 79.08) --
	(136.90, 75.76) --
	(133.05, 75.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.02, 82.10) --
	(133.94, 78.77) --
	(130.10, 78.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.15, 81.16) --
	(132.07, 77.83) --
	(128.22, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.11, 77.92) --
	(133.04, 74.59) --
	(129.19, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.53, 82.98) --
	(132.45, 79.65) --
	(128.61, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.78, 82.10) --
	(133.70, 78.77) --
	(129.85, 78.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.40, 76.66) --
	(131.33, 73.33) --
	(127.48, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.75, 81.16) --
	(132.67, 77.83) --
	(128.82, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.33, 91.22) --
	(137.25, 87.89) --
	(133.41, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.27, 92.61) --
	(138.19, 89.28) --
	(134.35, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.31, 95.76) --
	(138.23, 92.43) --
	(134.39, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.56,106.68) --
	(142.49,103.35) --
	(138.64,103.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.07, 94.65) --
	(135.99, 91.33) --
	(132.15, 91.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.31,107.01) --
	(138.23,103.68) --
	(134.39,103.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.38,101.04) --
	(141.30, 97.71) --
	(137.46, 97.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.18,113.99) --
	(140.10,110.67) --
	(136.26,110.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.05, 98.93) --
	(137.97, 95.60) --
	(134.13, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.77,100.79) --
	(138.69, 97.46) --
	(134.85, 97.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.90,117.39) --
	(146.82,114.06) --
	(142.97,114.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.05,125.58) --
	(145.97,122.26) --
	(142.12,122.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.34,141.53) --
	(151.26,138.20) --
	(147.42,138.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.67,121.65) --
	(149.59,118.32) --
	(145.75,118.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.86,138.63) --
	(143.78,135.30) --
	(139.94,135.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.19,115.61) --
	(158.11,112.29) --
	(154.27,112.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.64,132.60) --
	(147.56,129.28) --
	(143.72,129.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.17,120.21) --
	(151.09,116.88) --
	(147.25,116.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.23,110.98) --
	(145.16,107.65) --
	(141.31,107.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.16,134.34) --
	(153.08,131.01) --
	(149.24,131.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (168.93,121.47) --
	(170.85,118.14) --
	(167.01,118.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.75,131.80) --
	(148.67,128.47) --
	(144.82,128.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.17,127.09) --
	(146.10,123.76) --
	(142.25,123.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.46,117.63) --
	(160.39,114.30) --
	(156.54,114.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.37,120.79) --
	(144.30,117.46) --
	(140.45,117.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.80,137.85) --
	(172.73,134.52) --
	(168.88,134.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.13,123.28) --
	(160.05,119.95) --
	(156.21,119.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.65,137.01) --
	(154.57,133.68) --
	(150.73,133.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (164.49,141.09) --
	(166.41,137.76) --
	(162.57,137.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.27,113.89) --
	(155.19,110.56) --
	(151.35,110.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (182.71,128.90) --
	(184.63,125.57) --
	(180.79,125.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (182.16,143.57) --
	(184.08,140.25) --
	(180.24,140.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (181.62,149.73) --
	(183.54,146.41) --
	(179.70,146.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.02,136.05) --
	(162.95,132.72) --
	(159.10,132.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.62,148.63) --
	(163.54,145.30) --
	(159.69,145.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.54,144.78) --
	(173.46,141.46) --
	(169.62,141.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (176.92,119.47) --
	(178.84,116.14) --
	(175.00,116.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.67,132.94) --
	(161.59,129.61) --
	(157.75,129.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.03,137.34) --
	(157.96,134.01) --
	(154.11,134.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (184.97,154.10) --
	(186.89,150.77) --
	(183.05,150.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.80,145.39) --
	(175.73,142.06) --
	(171.88,142.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (177.80,171.08) --
	(179.73,167.75) --
	(175.88,167.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.62,156.25) --
	(198.54,152.92) --
	(194.70,152.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (185.09,156.91) --
	(187.01,153.58) --
	(183.17,153.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (185.49,150.07) --
	(187.41,146.75) --
	(183.57,146.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.87,160.49) --
	(190.79,157.16) --
	(186.94,157.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.98,148.06) --
	(163.90,144.73) --
	(160.06,144.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.52,159.24) --
	(168.44,155.92) --
	(164.60,155.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.70,169.65) --
	(182.62,166.32) --
	(178.78,166.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.52,176.56) --
	(169.44,173.23) --
	(165.59,173.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (190.91,162.92) --
	(192.83,159.59) --
	(188.99,159.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (181.01,170.31) --
	(182.93,166.98) --
	(179.09,166.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (175.20,169.04) --
	(177.12,165.71) --
	(173.28,165.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.62,168.57) --
	(163.54,165.25) --
	(159.70,165.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (183.91,179.13) --
	(185.83,175.80) --
	(181.99,175.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (198.77,181.72) --
	(200.69,178.40) --
	(196.84,178.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.76,148.61) --
	(190.68,145.28) --
	(186.84,145.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (215.62,172.21) --
	(217.54,168.88) --
	(213.69,168.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (189.81,171.14) --
	(191.73,167.81) --
	(187.89,167.81) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (185.86,154.01) --
	(187.79,150.68) --
	(183.94,150.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.23,184.52) --
	(181.15,181.19) --
	(177.31,181.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (217.06,177.23) --
	(218.98,173.90) --
	(215.14,173.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,181.11) --
	(228.48,177.78) --
	(224.64,177.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (194.20,172.40) --
	(196.12,169.07) --
	(192.28,169.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,187.50) --
	(228.48,184.17) --
	(224.64,184.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (204.60,172.98) --
	(206.52,169.65) --
	(202.68,169.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,174.52) --
	(228.48,171.19) --
	(224.64,171.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (185.97,178.05) --
	(187.90,174.72) --
	(184.05,174.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (205.50,172.05) --
	(207.42,168.72) --
	(203.58,168.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (184.28,168.64) --
	(186.20,165.31) --
	(182.36,165.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (204.66,182.01) --
	(206.58,178.68) --
	(202.74,178.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,194.03) --
	(228.48,190.70) --
	(224.64,190.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (200.42,193.76) --
	(202.34,190.43) --
	(198.50,190.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (207.77,179.94) --
	(209.69,176.61) --
	(205.85,176.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,186.79) --
	(228.48,183.46) --
	(224.64,183.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,192.99) --
	(228.48,189.66) --
	(224.64,189.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (214.14,204.87) --
	(216.06,201.54) --
	(212.22,201.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,189.81) --
	(228.48,186.48) --
	(224.64,186.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,190.09) --
	(228.48,186.76) --
	(224.64,186.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,186.08) --
	(228.48,182.75) --
	(224.64,182.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.42, 83.81) --
	(135.34, 80.48) --
	(131.50, 80.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.82, 86.72) --
	(133.75, 83.39) --
	(129.90, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.81, 96.45) --
	(135.73, 93.12) --
	(131.89, 93.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 89.15) --
	(228.48, 85.82) --
	(224.64, 85.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.77, 90.73) --
	(135.69, 87.40) --
	(131.85, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.24, 87.98) --
	(135.16, 84.66) --
	(131.32, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.37, 73.75) --
	(130.29, 70.42) --
	(126.45, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.97, 87.98) --
	(134.89, 84.66) --
	(131.05, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.93, 75.27) --
	(129.85, 71.95) --
	(126.01, 71.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.68, 89.69) --
	(135.60, 86.37) --
	(131.76, 86.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.84, 92.16) --
	(138.76, 88.83) --
	(134.92, 88.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.31, 76.66) --
	(130.23, 73.33) --
	(126.39, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.52, 80.16) --
	(131.44, 76.83) --
	(127.60, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.09, 90.22) --
	(137.02, 86.89) --
	(133.17, 86.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.78, 92.61) --
	(134.70, 89.28) --
	(130.86, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.03, 82.10) --
	(131.96, 78.77) --
	(128.11, 78.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.09, 90.22) --
	(138.01, 86.89) --
	(134.17, 86.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.56, 82.98) --
	(130.48, 79.65) --
	(126.64, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.65, 92.61) --
	(136.57, 89.28) --
	(132.73, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.64, 80.16) --
	(131.56, 76.83) --
	(127.72, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.98, 88.58) --
	(137.90, 85.25) --
	(134.05, 85.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.34,117.71) --
	(138.26,114.38) --
	(134.42,114.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.07,110.21) --
	(135.99,106.89) --
	(132.15,106.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.05, 95.40) --
	(140.97, 92.07) --
	(137.13, 92.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.47,100.28) --
	(140.39, 96.96) --
	(136.55, 96.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.21, 98.34) --
	(137.13, 95.02) --
	(133.29, 95.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.01, 87.37) --
	(136.94, 84.04) --
	(133.09, 84.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.13,103.93) --
	(137.05,100.60) --
	(133.21,100.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.05,108.70) --
	(139.97,105.37) --
	(136.13,105.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.28,118.39) --
	(140.20,115.07) --
	(136.36,115.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.07, 99.21) --
	(135.99, 95.88) --
	(132.15, 95.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.53, 97.11) --
	(140.45, 93.78) --
	(136.61, 93.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.53,105.82) --
	(139.45,102.49) --
	(135.61,102.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.62,101.76) --
	(142.54, 98.43) --
	(138.70, 98.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.89, 93.46) --
	(139.81, 90.13) --
	(135.97, 90.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 94.27) --
	(228.48, 90.94) --
	(224.64, 90.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.84, 81.16) --
	(140.76, 77.83) --
	(136.92, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.24, 87.98) --
	(136.16, 84.66) --
	(132.32, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.56, 95.40) --
	(142.49, 92.07) --
	(138.64, 92.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.02,101.76) --
	(138.94, 98.43) --
	(135.10, 98.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.99, 92.61) --
	(140.91, 89.28) --
	(137.07, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.02,100.79) --
	(142.94, 97.46) --
	(139.10, 97.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.45,106.68) --
	(146.37,103.35) --
	(142.53,103.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.45,107.96) --
	(147.37,104.63) --
	(143.53,104.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.17,127.61) --
	(149.09,124.29) --
	(145.24,124.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.86,102.22) --
	(139.78, 98.89) --
	(135.94, 98.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.13, 96.11) --
	(137.05, 92.78) --
	(133.21, 92.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.15,110.98) --
	(148.07,107.65) --
	(144.23,107.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.39, 96.11) --
	(139.31, 92.78) --
	(135.47, 92.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.63,111.47) --
	(168.55,108.14) --
	(164.71,108.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.73,127.05) --
	(146.66,123.72) --
	(142.81,123.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.02,114.19) --
	(142.94,110.87) --
	(139.10,110.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.89,108.84) --
	(142.81,105.52) --
	(138.97,105.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.61,138.01) --
	(144.53,134.68) --
	(140.69,134.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.61,103.93) --
	(143.53,100.60) --
	(139.69,100.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.83,118.02) --
	(139.75,114.69) --
	(135.90,114.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.70,115.25) --
	(141.62,111.92) --
	(137.78,111.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (148.10,115.25) --
	(150.02,111.92) --
	(146.18,111.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.51,122.12) --
	(143.43,118.79) --
	(139.59,118.79) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.43, 97.43) --
	(143.36, 94.10) --
	(139.51, 94.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.81, 99.76) --
	(140.73, 96.43) --
	(136.89, 96.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (148.84,147.94) --
	(150.76,144.62) --
	(146.92,144.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.19,115.43) --
	(148.11,112.10) --
	(144.26,112.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.22,133.84) --
	(157.14,130.51) --
	(153.30,130.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.19,120.21) --
	(151.11,116.88) --
	(147.27,116.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.06,113.48) --
	(147.98,110.15) --
	(144.14,110.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.21,131.26) --
	(161.13,127.93) --
	(157.29,127.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.53,133.37) --
	(154.45,130.04) --
	(150.61,130.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.90,130.63) --
	(151.83,127.30) --
	(147.98,127.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.64,141.88) --
	(141.56,138.55) --
	(137.72,138.55) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.85,148.71) --
	(149.78,145.38) --
	(145.93,145.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.21,157.06) --
	(152.14,153.73) --
	(148.29,153.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (174.40,141.50) --
	(176.32,138.17) --
	(172.48,138.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (162.93,133.45) --
	(164.86,130.12) --
	(161.01,130.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.90,135.78) --
	(146.82,132.45) --
	(142.97,132.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.00,151.74) --
	(146.92,148.41) --
	(143.08,148.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.43,154.98) --
	(160.35,151.65) --
	(156.50,151.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.96,146.12) --
	(158.88,142.79) --
	(155.04,142.79) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.58,129.04) --
	(156.50,125.71) --
	(152.66,125.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.44,137.44) --
	(151.36,134.11) --
	(147.52,134.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (172.46,150.40) --
	(174.38,147.07) --
	(170.54,147.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.52,153.06) --
	(161.45,149.73) --
	(157.60,149.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.76,143.86) --
	(165.69,140.53) --
	(161.84,140.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.23,147.24) --
	(158.15,143.91) --
	(154.31,143.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.98, 90.73) --
	(152.90, 87.40) --
	(149.05, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.59,133.63) --
	(143.51,130.30) --
	(139.67,130.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.95,158.84) --
	(156.87,155.51) --
	(153.03,155.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.73,156.97) --
	(198.65,153.64) --
	(194.81,153.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.17,145.62) --
	(155.09,142.29) --
	(151.25,142.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (168.64,155.70) --
	(170.57,152.37) --
	(166.72,152.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.52,161.16) --
	(156.44,157.83) --
	(152.60,157.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (185.71,142.47) --
	(187.64,139.14) --
	(183.79,139.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.17,126.03) --
	(148.09,122.70) --
	(144.25,122.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.82,166.54) --
	(162.75,163.21) --
	(158.90,163.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (168.81,153.05) --
	(170.73,149.73) --
	(166.89,149.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (175.27,156.51) --
	(177.19,153.18) --
	(173.35,153.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.92,167.15) --
	(172.84,163.82) --
	(169.00,163.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.38,165.10) --
	(165.30,161.77) --
	(161.46,161.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (191.73,155.02) --
	(193.65,151.69) --
	(189.81,151.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,108.84) --
	(228.48,105.52) --
	(224.64,105.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.21,160.10) --
	(168.13,156.77) --
	(164.29,156.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.95,148.58) --
	(153.87,145.25) --
	(150.03,145.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (210.83,173.83) --
	(212.75,170.51) --
	(208.90,170.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (192.00,163.69) --
	(193.92,160.36) --
	(190.08,160.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.87,169.43) --
	(198.79,166.10) --
	(194.95,166.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (181.28,167.12) --
	(183.20,163.79) --
	(179.35,163.79) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.07,158.89) --
	(167.99,155.56) --
	(164.15,155.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (181.37,157.59) --
	(183.29,154.26) --
	(179.45,154.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.34,166.23) --
	(169.26,162.90) --
	(165.42,162.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (162.86,177.17) --
	(164.78,173.84) --
	(160.94,173.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.93,160.97) --
	(175.85,157.64) --
	(172.01,157.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.57,175.57) --
	(160.50,172.24) --
	(156.65,172.24) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.15,173.47) --
	(182.07,170.14) --
	(178.23,170.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (174.45,151.52) --
	(176.38,148.19) --
	(172.53,148.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (207.67,177.49) --
	(209.59,174.16) --
	(205.75,174.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (176.81,181.25) --
	(178.73,177.92) --
	(174.89,177.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (157.19,175.03) --
	(159.11,171.71) --
	(155.27,171.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (206.86,176.08) --
	(208.79,172.75) --
	(204.94,172.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.17,154.21) --
	(181.09,150.88) --
	(177.25,150.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (184.13,159.52) --
	(186.05,156.19) --
	(182.21,156.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (215.43,192.83) --
	(217.35,189.50) --
	(213.51,189.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (183.10,191.75) --
	(185.03,188.43) --
	(181.18,188.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,121.35) --
	(228.48,118.02) --
	(224.64,118.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.43,154.62) --
	(182.36,151.29) --
	(178.51,151.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.24,164.24) --
	(175.16,160.91) --
	(171.31,160.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.18,175.40) --
	(181.10,172.07) --
	(177.26,172.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.17,198.05) --
	(190.10,194.72) --
	(186.25,194.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.43,181.63) --
	(165.35,178.30) --
	(161.51,178.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (177.33,169.86) --
	(179.25,166.53) --
	(175.41,166.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (192.97,183.42) --
	(194.89,180.10) --
	(191.04,180.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.51,200.95) --
	(162.43,197.62) --
	(158.59,197.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (189.70,219.04) --
	(191.62,215.71) --
	(187.78,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.34,195.52) --
	(173.26,192.19) --
	(169.42,192.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (209.41,197.29) --
	(211.33,193.96) --
	(207.48,193.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (162.12,198.76) --
	(164.04,195.44) --
	(160.20,195.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,198.56) --
	(228.48,195.23) --
	(224.64,195.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.69,169.17) --
	(173.61,165.84) --
	(169.77,165.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (183.60,190.68) --
	(185.53,187.36) --
	(181.68,187.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (183.77,204.04) --
	(185.69,200.72) --
	(181.85,200.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (202.61,193.46) --
	(204.53,190.13) --
	(200.69,190.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (205.00,171.48) --
	(206.92,168.15) --
	(203.08,168.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (201.02,195.84) --
	(202.94,192.51) --
	(199.10,192.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (201.61,185.42) --
	(203.54,182.09) --
	(199.69,182.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,186.77) --
	(228.48,183.45) --
	(224.64,183.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,204.52) --
	(228.48,201.19) --
	(224.64,201.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (202.23,206.92) --
	(204.15,203.59) --
	(200.30,203.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.92, 73.75) --
	(128.84, 70.42) --
	(125.00, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.40, 73.75) --
	(129.32, 70.42) --
	(125.48, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.26, 86.72) --
	(134.19, 83.39) --
	(130.34, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 73.75) --
	(228.48, 70.42) --
	(224.64, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 76.66) --
	(228.48, 73.33) --
	(224.64, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.09, 73.75) --
	(126.01, 70.42) --
	(122.17, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.87, 77.92) --
	(131.79, 74.59) --
	(127.94, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.56, 76.66) --
	(130.48, 73.33) --
	(126.64, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.99, 75.27) --
	(128.91, 71.95) --
	(125.07, 71.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.22, 81.16) --
	(133.14, 77.83) --
	(129.30, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.44, 76.66) --
	(130.36, 73.33) --
	(126.51, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.78, 89.15) --
	(133.70, 85.82) --
	(129.85, 85.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.85, 76.66) --
	(128.77, 73.33) --
	(124.93, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 77.92) --
	(228.48, 74.59) --
	(224.64, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.37,103.31) --
	(133.29, 99.99) --
	(129.45, 99.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.20, 80.16) --
	(132.12, 76.83) --
	(128.28, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.62, 77.92) --
	(130.54, 74.59) --
	(126.70, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.37, 84.59) --
	(132.29, 81.26) --
	(128.45, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.17, 77.92) --
	(131.09, 74.59) --
	(127.25, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.15, 84.59) --
	(132.07, 81.26) --
	(128.22, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.29, 86.72) --
	(131.21, 83.39) --
	(127.37, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.12, 89.69) --
	(134.04, 86.37) --
	(130.20, 86.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.85, 81.16) --
	(132.77, 77.83) --
	(128.93, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.42, 80.16) --
	(132.34, 76.83) --
	(128.50, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.65, 91.22) --
	(136.57, 87.89) --
	(132.73, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.01, 85.34) --
	(132.93, 82.01) --
	(129.09, 82.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.63, 82.98) --
	(133.55, 79.65) --
	(129.70, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.81, 81.16) --
	(131.73, 77.83) --
	(127.89, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.11, 87.37) --
	(133.04, 84.04) --
	(129.19, 84.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.82, 86.05) --
	(133.75, 82.72) --
	(129.90, 82.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.68, 83.81) --
	(133.60, 80.48) --
	(129.75, 80.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 84.59) --
	(228.48, 81.26) --
	(224.64, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.11,100.02) --
	(136.03, 96.69) --
	(132.19, 96.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.07, 86.72) --
	(133.99, 83.39) --
	(130.15, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 84.59) --
	(228.48, 81.26) --
	(224.64, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.87, 92.61) --
	(133.80, 89.28) --
	(129.95, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.90, 86.72) --
	(135.82, 83.39) --
	(131.98, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.64, 85.34) --
	(134.56, 82.01) --
	(130.72, 82.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.15, 94.65) --
	(135.07, 91.33) --
	(131.23, 91.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.06, 85.34) --
	(134.98, 82.01) --
	(131.14, 82.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.42, 86.72) --
	(135.34, 83.39) --
	(131.50, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.88, 94.27) --
	(134.80, 90.94) --
	(130.95, 90.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.83, 95.76) --
	(137.75, 92.43) --
	(133.91, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.15, 86.72) --
	(135.07, 83.39) --
	(131.23, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.83, 97.74) --
	(137.75, 94.41) --
	(133.91, 94.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.77, 98.34) --
	(136.70, 95.02) --
	(132.85, 95.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 86.72) --
	(228.48, 83.39) --
	(224.64, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 86.72) --
	(228.48, 83.39) --
	(224.64, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.93, 91.22) --
	(136.86, 87.89) --
	(133.01, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.41,102.89) --
	(134.33, 99.56) --
	(130.49, 99.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 87.37) --
	(228.48, 84.04) --
	(224.64, 84.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.81, 95.03) --
	(136.74, 91.70) --
	(132.89, 91.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.26, 92.61) --
	(139.18, 89.28) --
	(135.34, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.93, 87.98) --
	(136.86, 84.66) --
	(133.01, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.98,105.82) --
	(137.90,102.49) --
	(134.05,102.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.02,104.52) --
	(138.94,101.20) --
	(135.10,101.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.53, 90.73) --
	(136.45, 87.40) --
	(132.61, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.32, 92.61) --
	(136.24, 89.28) --
	(132.40, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.41, 91.22) --
	(137.33, 87.89) --
	(133.49, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.66,127.96) --
	(139.58,124.64) --
	(135.74,124.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.27,106.00) --
	(138.19,102.67) --
	(134.35,102.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.34, 90.73) --
	(138.26, 87.40) --
	(134.42, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 90.22) --
	(228.48, 86.89) --
	(224.64, 86.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (235.42, 98.64) --
	(237.34, 95.31) --
	(233.49, 95.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.94,108.55) --
	(137.86,105.23) --
	(134.02,105.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.16,100.28) --
	(139.08, 96.96) --
	(135.23, 96.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.05,102.45) --
	(139.97, 99.12) --
	(136.13, 99.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.53, 92.16) --
	(139.45, 88.83) --
	(135.61, 88.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.81,104.13) --
	(138.73,100.80) --
	(134.89,100.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 92.61) --
	(228.48, 89.28) --
	(224.64, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.23, 92.16) --
	(138.16, 88.83) --
	(134.31, 88.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.01, 95.76) --
	(141.93, 92.43) --
	(138.09, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.33,101.28) --
	(139.25, 97.96) --
	(135.40, 97.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.84, 95.76) --
	(154.76, 92.43) --
	(150.92, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.43,101.28) --
	(139.35, 97.96) --
	(135.51, 97.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.56,108.99) --
	(138.48,105.66) --
	(134.64,105.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.98,100.54) --
	(138.90, 97.21) --
	(135.06, 97.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.96,103.52) --
	(139.88,100.19) --
	(136.03,100.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.93, 97.11) --
	(140.85, 93.78) --
	(137.01, 93.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.44,107.96) --
	(141.36,104.63) --
	(137.52,104.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.28,107.01) --
	(140.20,103.68) --
	(136.36,103.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 95.03) --
	(228.48, 91.70) --
	(224.64, 91.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.02,100.79) --
	(140.94, 97.46) --
	(137.10, 97.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.45,138.39) --
	(138.37,135.06) --
	(134.53,135.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.28,103.52) --
	(140.20,100.19) --
	(136.36,100.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.25,121.47) --
	(143.18,118.14) --
	(139.33,118.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.37,119.05) --
	(142.30,115.72) --
	(138.45,115.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.81,113.58) --
	(142.73,110.26) --
	(138.89,110.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.06,123.38) --
	(168.98,120.06) --
	(165.14,120.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (148.99, 97.43) --
	(150.91, 94.10) --
	(147.07, 94.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.98,142.36) --
	(145.90,139.03) --
	(142.06,139.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 99.21) --
	(228.48, 95.88) --
	(224.64, 95.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.04,103.31) --
	(147.96, 99.99) --
	(144.12, 99.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.63,127.49) --
	(145.56,124.17) --
	(141.71,124.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.75,135.89) --
	(140.67,132.57) --
	(136.82,132.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (168.50,144.50) --
	(170.42,141.18) --
	(166.58,141.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 98.93) --
	(228.48, 95.60) --
	(224.64, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 98.64) --
	(228.48, 95.31) --
	(224.64, 95.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.53,153.30) --
	(160.45,149.97) --
	(156.61,149.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.47,161.40) --
	(147.39,158.07) --
	(143.55,158.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.92,109.95) --
	(145.84,106.62) --
	(142.00,106.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.87,119.33) --
	(149.79,116.00) --
	(145.95,116.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (195.43,146.11) --
	(197.35,142.78) --
	(193.51,142.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.45,219.04) --
	(160.37,215.71) --
	(156.53,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.83,122.17) --
	(162.75,118.85) --
	(158.91,118.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.36,154.99) --
	(154.29,151.66) --
	(150.44,151.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.92,144.15) --
	(153.85,140.83) --
	(150.00,140.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.40,114.59) --
	(157.33,111.26) --
	(153.48,111.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (181.00,144.42) --
	(182.92,141.09) --
	(179.08,141.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (213.32,148.65) --
	(215.24,145.32) --
	(211.40,145.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.42,122.35) --
	(168.34,119.02) --
	(164.49,119.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (193.50,185.58) --
	(195.43,182.25) --
	(191.58,182.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,118.09) --
	(228.48,114.77) --
	(224.64,114.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.07,219.04) --
	(197.99,215.71) --
	(194.15,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (211.78,160.83) --
	(213.71,157.50) --
	(209.86,157.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (178.86,125.76) --
	(180.79,122.44) --
	(176.94,122.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (213.65,168.77) --
	(215.57,165.44) --
	(211.73,165.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,139.65) --
	(228.48,136.32) --
	(224.64,136.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (235.42,160.64) --
	(237.34,157.31) --
	(233.49,157.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,185.18) --
	(228.48,181.86) --
	(224.64,181.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,131.59) --
	(228.48,128.26) --
	(224.64,128.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,189.63) --
	(228.48,186.30) --
	(224.64,186.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,167.30) --
	(228.48,163.98) --
	(224.64,163.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,185.67) --
	(228.48,182.35) --
	(224.64,182.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,127.89) --
	(228.48,124.56) --
	(224.64,124.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (198.27,219.04) --
	(200.19,215.71) --
	(196.35,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,179.04) --
	(228.48,175.71) --
	(224.64,175.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (203.99,219.04) --
	(205.91,215.71) --
	(202.07,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.10, 92.46) rectangle (132.95, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.10, 92.46) -- (132.95, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.10, 95.32) -- (132.95, 92.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56, 94.70) rectangle (135.41, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56, 94.70) -- (135.41, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56, 97.55) -- (135.41, 94.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.75,215.39) rectangle (141.61,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.75,215.39) -- (141.61,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.75,218.25) -- (141.61,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.93,215.39) rectangle (153.78,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.93,215.39) -- (153.78,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.93,218.25) -- (153.78,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,127.52) rectangle (227.98,130.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,127.52) -- (227.98,130.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,130.37) -- (227.98,127.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,139.97) rectangle (227.98,142.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,139.97) -- (227.98,142.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,142.82) -- (227.98,139.97);
\definecolor{drawColor}{RGB}{152,152,152}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 30.77) -- (235.42,225.68);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.95, 30.77) -- ( 41.95, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.19, 30.77) -- ( 44.19, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.13, 30.77) -- ( 46.13, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 47.84, 30.77) -- ( 47.84, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.37, 30.77) -- ( 49.37, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 59.43, 30.77) -- ( 59.43, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.32, 30.77) -- ( 65.32, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 69.49, 30.77) -- ( 69.49, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.73, 30.77) -- ( 72.73, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 75.38, 30.77) -- ( 75.38, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 77.62, 30.77) -- ( 77.62, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.56, 30.77) -- ( 79.56, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 81.27, 30.77) -- ( 81.27, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.79, 30.77) -- ( 82.79, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 92.86, 30.77) -- ( 92.86, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.74, 30.77) -- ( 98.74, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (102.92, 30.77) -- (102.92, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.16, 30.77) -- (106.16, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (108.80, 30.77) -- (108.80, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (111.04, 30.77) -- (111.04, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.98, 30.77) -- (112.98, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.69, 30.77) -- (114.69, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (116.22, 30.77) -- (116.22, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (126.28, 30.77) -- (126.28, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (132.17, 30.77) -- (132.17, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (136.34, 30.77) -- (136.34, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (139.58, 30.77) -- (139.58, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.23, 30.77) -- (142.23, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (144.47, 30.77) -- (144.47, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (146.41, 30.77) -- (146.41, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (148.12, 30.77) -- (148.12, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.64, 30.77) -- (149.64, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (159.71, 30.77) -- (159.71, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (165.59, 30.77) -- (165.59, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (169.77, 30.77) -- (169.77, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.01, 30.77) -- (173.01, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (175.65, 30.77) -- (175.65, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.89, 30.77) -- (177.89, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.83, 30.77) -- (179.83, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (181.54, 30.77) -- (181.54, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (183.07, 30.77) -- (183.07, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (193.13, 30.77) -- (193.13, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (199.02, 30.77) -- (199.02, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.19, 30.77) -- (203.19, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (206.43, 30.77) -- (206.43, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (209.08, 30.77) -- (209.08, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (211.32, 30.77) -- (211.32, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.26, 30.77) -- (213.26, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.97, 30.77) -- (214.97, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (216.49, 30.77) -- (216.49, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.56, 30.77) -- (226.56, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.44, 30.77) -- (232.44, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 32.22) -- ( 43.36, 32.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 34.45) -- ( 43.36, 34.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 36.39) -- ( 43.36, 36.39);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 38.10) -- ( 43.36, 38.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 39.63) -- ( 49.05, 39.63);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 49.69) -- ( 43.36, 49.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 55.58) -- ( 43.36, 55.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 59.76) -- ( 43.36, 59.76);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 62.99) -- ( 46.20, 62.99);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 65.64) -- ( 43.36, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 67.88) -- ( 43.36, 67.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 69.82) -- ( 43.36, 69.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 71.53) -- ( 43.36, 71.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 73.06) -- ( 49.05, 73.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 83.12) -- ( 43.36, 83.12);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 89.00) -- ( 43.36, 89.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 93.18) -- ( 43.36, 93.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 96.42) -- ( 46.20, 96.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 99.07) -- ( 43.36, 99.07);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,101.30) -- ( 43.36,101.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,103.24) -- ( 43.36,103.24);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,104.95) -- ( 43.36,104.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,106.48) -- ( 49.05,106.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,116.54) -- ( 43.36,116.54);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,122.43) -- ( 43.36,122.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,126.61) -- ( 43.36,126.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,129.84) -- ( 46.20,129.84);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,132.49) -- ( 43.36,132.49);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,134.73) -- ( 43.36,134.73);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,136.67) -- ( 43.36,136.67);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,138.38) -- ( 43.36,138.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,139.91) -- ( 49.05,139.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,149.97) -- ( 43.36,149.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,155.85) -- ( 43.36,155.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,160.03) -- ( 43.36,160.03);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,163.27) -- ( 46.20,163.27);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,165.92) -- ( 43.36,165.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,168.15) -- ( 43.36,168.15);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,170.09) -- ( 43.36,170.09);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,171.80) -- ( 43.36,171.80);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,173.33) -- ( 49.05,173.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,183.39) -- ( 43.36,183.39);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,189.28) -- ( 43.36,189.28);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,193.46) -- ( 43.36,193.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,196.69) -- ( 46.20,196.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,199.34) -- ( 43.36,199.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,201.58) -- ( 43.36,201.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,203.52) -- ( 43.36,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,205.23) -- ( 43.36,205.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,206.76) -- ( 49.05,206.76);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,216.82) -- ( 43.36,216.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,222.70) -- ( 43.36,222.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.77) rectangle (235.42,225.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 70.03) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,136.88) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,203.73) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 73.06) --
	( 40.51, 73.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,139.91) --
	( 40.51,139.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,206.76) --
	( 40.51,206.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 82.79, 28.02) --
	( 82.79, 30.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] (149.64, 28.02) --
	(149.64, 30.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.49, 28.02) --
	(216.49, 30.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 82.79, 19.76) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (149.64, 19.76) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (216.49, 19.76) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (137.96,  7.72) {\textsf{Ace} + \texttt{cd06} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,128.22) {\textsf{ADDMC} + \texttt{cw} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (246.42, 71.76) rectangle (337.78,184.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (251.92,170.55) {Data set};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,149.53) rectangle (266.37,163.98);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (259.14,156.75) circle (  1.43);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,135.07) rectangle (266.37,149.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (259.14,144.52) --
	(261.06,141.19) --
	(257.22,141.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,120.62) rectangle (266.37,135.07);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (257.72,126.42) --
	(260.57,126.42) --
	(260.57,129.27) --
	(257.72,129.27) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,106.16) rectangle (266.37,120.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.13,113.39) -- (261.16,113.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (259.14,111.37) -- (259.14,115.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92, 91.71) rectangle (266.37,106.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 97.51) rectangle (260.57,100.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 97.51) -- (260.57,100.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72,100.36) -- (260.57, 97.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92, 77.26) rectangle (266.37, 91.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 83.06) -- (260.57, 85.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 85.91) -- (260.57, 83.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.13, 84.48) -- (261.16, 84.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (259.14, 82.47) -- (259.14, 86.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,153.72) {DQMR};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,139.27) {Grid};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,124.81) {Mastermind};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,110.36) {Non-binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87, 95.91) {Other binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87, 81.45) {Random Blocks};
\end{scope}
\end{tikzpicture}

### 2021-06-02 doc/long_talk/scatter2.tex
Slides are almost ready

% Created by tikzDevice version 0.12.3.1 on 2021-06-01 14:27:10
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (343.28,231.26);
\begin{scope}
\path[clip] (  0.00,  0.09) rectangle (343.28,231.18);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.09) rectangle (343.28,231.18);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 30.77) rectangle (235.42,225.68);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 30.77) rectangle (235.42,225.68);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 39.63) --
	(235.42, 39.63);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,106.48) --
	(235.42,106.48);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,173.33) --
	(235.42,173.33);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 49.37, 30.77) --
	( 49.37,225.68);

\path[draw=drawColor,line width= 0.1pt,line join=round] (116.22, 30.77) --
	(116.22,225.68);

\path[draw=drawColor,line width= 0.1pt,line join=round] (183.07, 30.77) --
	(183.07,225.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 73.06) --
	(235.42, 73.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,139.91) --
	(235.42,139.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,206.76) --
	(235.42,206.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 82.79, 30.77) --
	( 82.79,225.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] (149.64, 30.77) --
	(149.64,225.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.49, 30.77) --
	(216.49,225.68);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.10,215.39) -- (131.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.10,218.25) -- (131.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.51,216.82) -- (132.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.53,214.80) -- (130.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.16,215.39) -- (132.01,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.16,218.25) -- (132.01,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.57,216.82) -- (132.60,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.58,214.80) -- (130.58,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03,215.39) -- (133.88,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03,218.25) -- (133.88,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.44,216.82) -- (134.47,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.45,214.80) -- (132.45,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.10,215.39) -- (135.96,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.10,218.25) -- (135.96,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.51,216.82) -- (136.55,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.53,214.80) -- (134.53,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.21,215.39) -- (132.06,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.21,218.25) -- (132.06,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.62,216.82) -- (132.66,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.64,214.80) -- (130.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.31,215.39) -- (134.16,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.31,218.25) -- (134.16,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.72,216.82) -- (134.75,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.74,214.80) -- (132.74,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.32,101.07) -- (132.17,103.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.32,103.92) -- (132.17,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.73,102.50) -- (132.76,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.75,100.48) -- (130.75,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99,101.26) -- (131.85,104.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99,104.11) -- (131.85,101.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.40,102.69) -- (132.44,102.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.42,100.67) -- (130.42,104.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.93,101.45) -- (133.79,104.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.93,104.30) -- (133.79,101.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.34,102.87) -- (134.38,102.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.36,100.86) -- (132.36,104.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.01, 97.15) -- (129.86,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.01,100.00) -- (129.86, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.42, 98.57) -- (130.45, 98.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.44, 96.56) -- (128.44,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.80, 98.35) -- (130.65,101.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.80,101.20) -- (130.65, 98.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.21, 99.77) -- (131.25, 99.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.23, 97.76) -- (129.23,101.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42,215.39) -- (132.28,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42,218.25) -- (132.28,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.83,216.82) -- (132.87,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.85,214.80) -- (130.85,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.39,215.39) -- (135.24,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.39,218.25) -- (135.24,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.80,216.82) -- (135.83,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.81,214.80) -- (133.81,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42,215.39) -- (132.28,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42,218.25) -- (132.28,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.83,216.82) -- (132.87,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.85,214.80) -- (130.85,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.22,215.39) -- (134.07,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.22,218.25) -- (134.07,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.63,216.82) -- (134.66,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.64,214.80) -- (132.64,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.50,215.39) -- (134.35,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.50,218.25) -- (134.35,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.90,216.82) -- (134.94,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.92,214.80) -- (132.92,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.81,112.67) -- (137.66,115.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.81,115.53) -- (137.66,112.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.22,114.10) -- (138.25,114.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.23,112.08) -- (136.23,116.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,106.70) -- (136.52,109.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.67,109.55) -- (136.52,106.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.08,108.13) -- (137.11,108.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.09,106.11) -- (135.09,110.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.95,106.57) -- (134.80,109.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.95,109.42) -- (134.80,106.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.36,108.00) -- (135.39,108.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.37,105.98) -- (133.37,110.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03,105.90) -- (133.88,108.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.03,108.75) -- (133.88,105.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.44,107.33) -- (134.47,107.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.45,105.31) -- (132.45,109.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.39,107.33) -- (135.24,110.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.39,110.19) -- (135.24,107.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.80,108.76) -- (135.83,108.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.81,106.74) -- (133.81,110.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.06,106.57) -- (135.91,109.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.06,109.42) -- (135.91,106.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.47,108.00) -- (136.51,108.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.49,105.98) -- (134.49,110.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.68,100.08) -- (134.53,102.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.68,102.94) -- (134.53,100.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.09,101.51) -- (135.12,101.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.10, 99.49) -- (133.10,103.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.47,101.07) -- (136.32,103.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.47,103.92) -- (136.32,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.88,102.50) -- (136.91,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.89,100.48) -- (134.89,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.36,101.07) -- (134.21,103.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.36,103.92) -- (134.21,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.77,102.50) -- (134.80,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.78,100.48) -- (132.78,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.06,104.46) -- (136.91,107.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.06,107.32) -- (136.91,104.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.47,105.89) -- (137.50,105.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.48,103.87) -- (135.48,107.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56,102.17) -- (135.41,105.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.56,105.03) -- (135.41,102.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.97,103.60) -- (136.00,103.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.98,101.58) -- (133.98,105.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.52,106.17) -- (135.37,109.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.52,109.03) -- (135.37,106.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.92,107.60) -- (135.96,107.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.94,105.58) -- (133.94,109.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.45,106.44) -- (134.30,109.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.45,109.29) -- (134.30,106.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.86,107.86) -- (134.89,107.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.88,105.85) -- (132.88,109.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.02,107.94) -- (136.87,110.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.02,110.79) -- (136.87,107.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.43,109.37) -- (137.46,109.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.45,107.35) -- (135.45,111.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.08,107.58) -- (134.93,110.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.08,110.43) -- (134.93,107.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.49,109.01) -- (135.52,109.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.51,106.99) -- (133.51,111.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.63,107.33) -- (136.48,110.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.63,110.19) -- (136.48,107.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.04,108.76) -- (137.07,108.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.05,106.74) -- (135.05,110.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.47,112.24) -- (141.33,115.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.47,115.09) -- (141.33,112.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.88,113.66) -- (141.92,113.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.90,111.64) -- (139.90,115.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.91,111.04) -- (139.77,113.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.91,113.89) -- (139.77,111.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.32,112.46) -- (140.36,112.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.34,110.45) -- (138.34,114.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.10,114.75) -- (138.95,117.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.10,117.60) -- (138.95,114.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.51,116.18) -- (139.55,116.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.53,114.16) -- (137.53,118.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.13,112.67) -- (140.98,115.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.13,115.53) -- (140.98,112.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.54,114.10) -- (141.57,114.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.55,112.08) -- (139.55,116.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.39,116.50) -- (141.24,119.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.39,119.35) -- (141.24,116.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.80,117.93) -- (141.83,117.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.81,115.91) -- (139.81,119.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.83,111.42) -- (138.68,114.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.83,114.27) -- (138.68,111.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.24,112.84) -- (139.28,112.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.26,110.83) -- (137.26,114.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.42,111.60) -- (138.27,114.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.42,114.46) -- (138.27,111.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.83,113.03) -- (138.86,113.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.84,111.01) -- (136.84,115.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.47,105.05) -- (136.32,107.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.47,107.91) -- (136.32,105.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.88,106.48) -- (136.91,106.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.89,104.46) -- (134.89,108.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.27,107.70) -- (139.12,110.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.27,110.55) -- (139.12,107.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.68,109.13) -- (139.71,109.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.69,107.11) -- (137.69,111.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.73,112.59) -- (138.58,115.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.73,115.44) -- (138.58,112.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.14,114.01) -- (139.17,114.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.16,111.99) -- (137.16,116.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.47,105.48) -- (137.33,108.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.47,108.34) -- (137.33,105.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.88,106.91) -- (137.92,106.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.90,104.89) -- (135.90,108.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.53,121.10) -- (140.39,123.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.53,123.95) -- (140.39,121.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.94,122.53) -- (140.98,122.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.96,120.51) -- (138.96,124.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.95,116.43) -- (137.81,119.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.95,119.29) -- (137.81,116.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.36,117.86) -- (138.40,117.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.38,115.84) -- (136.38,119.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.84,109.84) -- (137.70,112.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.84,112.69) -- (137.70,109.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.25,111.26) -- (138.29,111.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.27,109.24) -- (136.27,113.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.73,109.19) -- (137.59,112.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.73,112.05) -- (137.59,109.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.14,110.62) -- (138.18,110.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.16,108.60) -- (136.16,112.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.97,111.23) -- (138.82,114.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.97,114.08) -- (138.82,111.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.38,112.65) -- (139.41,112.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,110.64) -- (137.39,114.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.33,187.58) -- (173.18,190.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.33,190.43) -- (173.18,187.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.74,189.01) -- (173.77,189.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.76,186.99) -- (171.76,191.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.07,155.90) -- (171.93,158.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.07,158.76) -- (171.93,155.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.48,157.33) -- (172.52,157.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.50,155.31) -- (170.50,159.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.16,152.68) -- (170.01,155.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.16,155.53) -- (170.01,152.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.57,154.11) -- (170.60,154.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.59,152.09) -- (168.59,156.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.77,156.31) -- (173.62,159.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.77,159.16) -- (173.62,156.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.18,157.74) -- (174.21,157.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.19,155.72) -- (172.19,159.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.12,153.70) -- (169.98,156.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.12,156.55) -- (169.98,153.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.53,155.12) -- (170.57,155.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.55,153.11) -- (168.55,157.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.59,215.39) -- (201.44,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.59,218.25) -- (201.44,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.00,216.82) -- (202.04,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.02,214.80) -- (200.02,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.49,215.39) -- (201.34,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.49,218.25) -- (201.34,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.90,216.82) -- (201.93,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.91,214.80) -- (199.91,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.11,215.39) -- (203.97,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.11,218.25) -- (203.97,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.52,216.82) -- (204.56,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (202.54,214.80) -- (202.54,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.62,215.39) -- (201.47,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.62,218.25) -- (201.47,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.03,216.82) -- (202.06,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.04,214.80) -- (200.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.02,215.39) -- (201.88,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.02,218.25) -- (201.88,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.43,216.82) -- (202.47,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.45,214.80) -- (200.45,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.58,215.39) -- (200.43,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.58,218.25) -- (200.43,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.98,216.82) -- (201.02,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.00,214.80) -- (199.00,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.36,155.61) -- (173.22,158.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.36,158.47) -- (173.22,155.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.77,157.04) -- (173.81,157.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.79,155.02) -- (171.79,159.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.84,158.55) -- (173.70,161.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.84,161.41) -- (173.70,158.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.25,159.98) -- (174.29,159.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.27,157.96) -- (172.27,162.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.78,154.94) -- (173.63,157.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.78,157.79) -- (173.63,154.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.18,156.37) -- (174.22,156.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.20,154.35) -- (172.20,158.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.67,156.62) -- (172.52,159.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.67,159.47) -- (172.52,156.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.08,158.04) -- (173.11,158.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.10,156.02) -- (171.10,160.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.54,155.64) -- (172.39,158.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.54,158.49) -- (172.39,155.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.95,157.07) -- (172.98,157.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.97,155.05) -- (170.97,159.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.80,215.39) -- (199.65,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.80,218.25) -- (199.65,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.21,216.82) -- (200.24,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.23,214.80) -- (198.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.61,215.39) -- (199.47,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.61,218.25) -- (199.47,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.02,216.82) -- (200.06,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.04,214.80) -- (198.04,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.67,215.39) -- (201.53,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.67,218.25) -- (201.53,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.08,216.82) -- (202.12,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.10,214.80) -- (200.10,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.33,215.39) -- (200.19,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.33,218.25) -- (200.19,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.74,216.82) -- (200.78,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.76,214.80) -- (198.76,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.23,215.39) -- (200.08,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.23,218.25) -- (200.08,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (196.64,216.82) -- (200.67,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.65,214.80) -- (198.65,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.37,160.28) -- (175.23,163.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.37,163.14) -- (175.23,160.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.78,161.71) -- (175.82,161.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.80,159.69) -- (173.80,163.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.39,165.91) -- (175.25,168.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.39,168.77) -- (175.25,165.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.80,167.34) -- (175.84,167.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.82,165.32) -- (173.82,169.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.69,159.28) -- (175.54,162.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.69,162.13) -- (175.54,159.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.10,160.71) -- (176.13,160.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.11,158.69) -- (174.11,162.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.75,157.91) -- (174.60,160.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.75,160.77) -- (174.60,157.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.16,159.34) -- (175.19,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (173.18,157.32) -- (173.18,161.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.38,215.39) -- (216.23,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.38,218.25) -- (216.23,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.79,216.82) -- (216.82,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.80,214.80) -- (214.80,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.80,215.39) -- (215.66,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.80,218.25) -- (215.66,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.21,216.82) -- (216.25,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.23,214.80) -- (214.23,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.25,215.39) -- (215.11,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.25,218.25) -- (215.11,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.66,216.82) -- (215.70,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.68,214.80) -- (213.68,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.15,215.39) -- (215.00,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.15,218.25) -- (215.00,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.56,216.82) -- (215.59,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.58,214.80) -- (213.58,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.74,215.39) -- (215.59,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.74,218.25) -- (215.59,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.15,216.82) -- (216.18,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.17,214.80) -- (214.17,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.25,215.39) -- (216.10,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.25,218.25) -- (216.10,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.66,216.82) -- (216.69,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.68,214.80) -- (214.68,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.41,215.39) -- (202.26,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.41,218.25) -- (202.26,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.82,216.82) -- (202.85,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.83,214.80) -- (200.83,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.56,195.92) -- (202.41,198.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.56,198.78) -- (202.41,195.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.96,197.35) -- (203.00,197.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.98,195.33) -- (200.98,199.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.78,215.39) -- (200.64,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.78,218.25) -- (200.64,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.19,216.82) -- (201.23,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.21,214.80) -- (199.21,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (195.83,215.39) -- (198.68,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (195.83,218.25) -- (198.68,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (195.24,216.82) -- (199.27,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.26,214.80) -- (197.26,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (204.81,215.39) -- (207.67,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (204.81,218.25) -- (207.67,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (204.22,216.82) -- (208.26,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (206.24,214.80) -- (206.24,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.05,215.39) -- (214.91,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.05,218.25) -- (214.91,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.46,216.82) -- (215.50,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.48,214.80) -- (213.48,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.08,215.39) -- (215.93,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.08,218.25) -- (215.93,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.49,216.82) -- (216.52,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.50,214.80) -- (214.50,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.29,215.39) -- (215.15,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (212.29,218.25) -- (215.15,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.70,216.82) -- (215.74,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.72,214.80) -- (213.72,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.65,215.39) -- (214.50,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.65,218.25) -- (214.50,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (211.06,216.82) -- (215.09,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.07,214.80) -- (213.07,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.63,215.39) -- (217.48,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.63,218.25) -- (217.48,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (214.04,216.82) -- (218.07,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (216.05,214.80) -- (216.05,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.65,188.01) -- (203.50,190.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.65,190.86) -- (203.50,188.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.05,189.44) -- (204.09,189.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (202.07,187.42) -- (202.07,191.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.12,195.89) -- (200.97,198.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.12,198.74) -- (200.97,195.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.52,197.32) -- (201.56,197.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.54,195.30) -- (199.54,199.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.68,185.93) -- (201.53,188.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.68,188.79) -- (201.53,185.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.09,187.36) -- (202.12,187.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.11,185.34) -- (200.11,189.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.71,194.82) -- (200.56,197.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.71,197.67) -- (200.56,194.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.12,196.24) -- (201.15,196.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.13,194.23) -- (199.13,198.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.19,215.39) -- (202.04,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.19,218.25) -- (202.04,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.60,216.82) -- (202.63,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.61,214.80) -- (200.61,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (202.43,215.39) -- (205.28,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (202.43,218.25) -- (205.28,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.84,216.82) -- (205.87,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.86,214.80) -- (203.86,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.61,192.67) -- (206.46,195.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.61,195.52) -- (206.46,192.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (203.02,194.09) -- (207.06,194.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (205.04,192.07) -- (205.04,196.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.26,187.64) -- (203.12,190.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.26,190.50) -- (203.12,187.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.67,189.07) -- (203.71,189.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.69,187.05) -- (201.69,191.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.39,187.48) -- (203.24,190.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (200.39,190.33) -- (203.24,187.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.80,188.90) -- (203.83,188.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (201.82,186.88) -- (201.82,190.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (148.45,119.58) --
	(151.30,119.58) --
	(151.30,122.43) --
	(148.45,122.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.06,116.37) --
	(141.91,116.37) --
	(141.91,119.22) --
	(139.06,119.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.40,156.75) --
	(149.25,156.75) --
	(149.25,159.60) --
	(146.40,159.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (174.58,132.18) --
	(177.43,132.18) --
	(177.43,135.03) --
	(174.58,135.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (182.22,171.06) --
	(185.08,171.06) --
	(185.08,173.91) --
	(182.22,173.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.02,139.37) --
	(160.87,139.37) --
	(160.87,142.22) --
	(158.02,142.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (204.49,139.66) --
	(207.34,139.66) --
	(207.34,142.52) --
	(204.49,142.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,141.86) --
	(227.98,141.86) --
	(227.98,144.71) --
	(225.13,144.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,199.65) --
	(227.98,199.65) --
	(227.98,202.50) --
	(225.13,202.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (213.33,132.34) --
	(216.18,132.34) --
	(216.18,135.19) --
	(213.33,135.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.63,136.32) --
	(169.48,136.32) --
	(169.48,139.18) --
	(166.63,139.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.87,124.28) --
	(145.73,124.28) --
	(145.73,127.13) --
	(142.87,127.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.11,119.84) --
	(148.97,119.84) --
	(148.97,122.70) --
	(146.11,122.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (211.17,215.39) --
	(214.02,215.39) --
	(214.02,218.25) --
	(211.17,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.07,160.09) --
	(163.92,160.09) --
	(163.92,162.94) --
	(161.07,162.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.80,140.76) --
	(157.66,140.76) --
	(157.66,143.61) --
	(154.80,143.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (198.07,215.39) --
	(200.92,215.39) --
	(200.92,218.25) --
	(198.07,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.63,117.64) --
	(153.49,117.64) --
	(153.49,120.50) --
	(150.63,120.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.67,117.94) --
	(153.52,117.94) --
	(153.52,120.80) --
	(150.67,120.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,181.79) --
	(227.98,181.79) --
	(227.98,184.64) --
	(225.13,184.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.60,116.50) --
	(148.45,116.50) --
	(148.45,119.35) --
	(145.60,119.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (208.53,215.39) --
	(211.38,215.39) --
	(211.38,218.25) --
	(208.53,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (210.25,188.53) --
	(213.11,188.53) --
	(213.11,191.38) --
	(210.25,191.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (194.87,154.29) --
	(197.72,154.29) --
	(197.72,157.14) --
	(194.87,157.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.10,141.43) --
	(154.96,141.43) --
	(154.96,144.28) --
	(152.10,144.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.92,215.39) --
	(159.77,215.39) --
	(159.77,218.25) --
	(156.92,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.33,215.39) --
	(191.19,215.39) --
	(191.19,218.25) --
	(188.33,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.92,136.70) -- (171.95,136.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.93,134.69) -- (169.93,138.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.25,109.37) -- (166.28,109.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.27,107.35) -- (164.27,111.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.40,115.49) -- (166.44,115.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.42,113.47) -- (164.42,117.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.25,134.22) -- (169.28,134.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.26,132.20) -- (167.26,136.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.75,125.55) -- (167.78,125.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.77,123.53) -- (165.77,127.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.40,130.80) -- (167.44,130.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.42,128.78) -- (165.42,132.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.71,135.92) -- (169.75,135.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.73,133.91) -- (167.73,137.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.15,119.19) -- (169.18,119.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.16,117.17) -- (167.16,121.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.26,135.75) -- (169.30,135.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.28,133.73) -- (167.28,137.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.27,125.86) -- (166.30,125.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.29,123.84) -- (164.29,127.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.79,137.48) -- (167.82,137.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.80,135.46) -- (165.80,139.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.60,133.59) -- (168.63,133.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.62,131.57) -- (166.62,135.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.17,134.09) -- (168.21,134.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.19,132.08) -- (166.19,136.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.09,133.11) -- (168.12,133.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.11,131.09) -- (166.11,135.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.19,135.28) -- (168.23,135.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.21,133.26) -- (166.21,137.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.64,131.49) -- (164.67,131.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.65,129.47) -- (162.65,133.51);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.17,113.98) -- (142.02,116.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.17,116.84) -- (142.02,113.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.57,115.41) -- (142.61,115.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.59,113.39) -- (140.59,117.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.27,114.97) -- (142.13,117.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.27,117.82) -- (142.13,114.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.68,116.40) -- (142.72,116.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.70,114.38) -- (140.70,118.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.73,119.90) -- (143.58,122.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.73,122.75) -- (143.58,119.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.14,121.32) -- (144.17,121.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.16,119.31) -- (142.16,123.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.86,113.83) -- (140.72,116.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.86,116.68) -- (140.72,113.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.27,115.25) -- (141.31,115.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.29,113.24) -- (139.29,117.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.75,117.46) -- (142.60,120.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.75,120.31) -- (142.60,117.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.16,118.88) -- (143.19,118.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.18,116.87) -- (141.18,120.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.36,114.30) -- (141.21,117.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.36,117.15) -- (141.21,114.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.77,115.72) -- (141.80,115.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.78,113.70) -- (139.78,117.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.98,114.06) -- (136.83,116.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.98,116.92) -- (136.83,114.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.39,115.49) -- (137.42,115.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.41,113.47) -- (135.41,117.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.66,109.94) -- (139.51,112.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.66,112.79) -- (139.51,109.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.07,111.37) -- (140.10,111.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.09,109.35) -- (138.09,113.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.30,110.35) -- (139.15,113.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.30,113.20) -- (139.15,110.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.71,111.77) -- (139.74,111.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.73,109.76) -- (137.73,113.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.27,108.75) -- (139.12,111.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.27,111.60) -- (139.12,108.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.68,110.18) -- (139.71,110.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.69,108.16) -- (137.69,112.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.45,108.52) -- (138.30,111.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.45,111.38) -- (138.30,108.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.86,109.95) -- (138.90,109.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.88,107.93) -- (136.88,111.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,116.23) -- (140.02,119.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,119.09) -- (140.02,116.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.57,117.66) -- (140.61,117.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.59,115.64) -- (138.59,119.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.65,118.36) -- (140.51,121.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.65,121.21) -- (140.51,118.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.06,119.78) -- (141.10,119.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.08,117.76) -- (139.08,121.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.63,112.32) -- (138.48,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.63,115.18) -- (138.48,112.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.03,113.75) -- (139.07,113.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.05,111.73) -- (137.05,115.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.30,111.79) -- (139.15,114.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.30,114.64) -- (139.15,111.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.71,113.21) -- (139.74,113.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.73,111.20) -- (137.73,115.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.96,114.37) -- (144.82,117.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.96,117.23) -- (144.82,114.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.37,115.80) -- (145.41,115.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.39,113.78) -- (143.39,117.82);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,206.31) -- (228.57,206.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,204.29) -- (226.56,208.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,204.05) -- (228.57,204.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,202.03) -- (226.56,206.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,205.62) -- (228.57,205.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,203.60) -- (226.56,207.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,206.47) -- (228.57,206.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,204.45) -- (226.56,208.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,204.42) -- (228.57,204.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,202.40) -- (226.56,206.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,205.41) -- (228.57,205.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,203.39) -- (226.56,207.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,204.52) -- (228.57,204.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,202.50) -- (226.56,206.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,205.41) -- (228.57,205.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,203.40) -- (226.56,207.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,205.79) -- (228.57,205.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,203.77) -- (226.56,207.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,192.95) -- (228.57,192.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,190.93) -- (226.56,194.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,204.31) -- (228.57,204.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,202.29) -- (226.56,206.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,206.20) -- (228.57,206.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,204.18) -- (226.56,208.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,205.97) -- (228.57,205.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,203.95) -- (226.56,207.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,203.78) -- (228.57,203.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,201.76) -- (226.56,205.80);

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.41,127.40) --
	(155.27,127.40) --
	(155.27,130.25) --
	(152.41,130.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.40,120.26) --
	(145.26,120.26) --
	(145.26,123.11) --
	(142.40,123.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (148.16,157.01) --
	(151.01,157.01) --
	(151.01,159.86) --
	(148.16,159.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (225.13,215.39) --
	(227.98,215.39) --
	(227.98,218.25) --
	(225.13,218.25) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,171.45) -- (228.57,171.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,169.44) -- (226.56,173.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,171.18) -- (228.57,171.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,169.16) -- (226.56,173.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.24,120.51) rectangle (171.09,123.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.24,120.51) -- (171.09,123.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.24,123.36) -- (171.09,120.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.31,119.04) rectangle (171.16,121.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.31,119.04) -- (171.16,121.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.31,121.89) -- (171.16,119.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.85,112.32) rectangle (167.70,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.85,112.32) -- (167.70,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.85,115.18) -- (167.70,112.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.66,113.51) rectangle (168.52,116.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.66,113.51) -- (168.52,116.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.66,116.36) -- (168.52,113.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.08,119.90) rectangle (171.93,122.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.08,119.90) -- (171.93,122.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.08,122.75) -- (171.93,119.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.94,111.88) rectangle (166.79,114.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.94,111.88) -- (166.79,114.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.94,114.73) -- (166.79,111.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.74, 91.01) rectangle (132.59, 93.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.74, 91.01) -- (132.59, 93.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.74, 93.86) -- (132.59, 91.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.21, 84.93) rectangle (128.07, 87.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.21, 84.93) -- (128.07, 87.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.21, 87.78) -- (128.07, 84.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.97, 85.50) rectangle (128.83, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.97, 85.50) -- (128.83, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.97, 88.35) -- (128.83, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42, 92.80) rectangle (132.28, 95.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42, 92.80) -- (132.28, 95.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.42, 95.66) -- (132.28, 92.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.77, 97.40) rectangle (131.63,100.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.77, 97.40) -- (131.63,100.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.77,100.25) -- (131.63, 97.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.17,114.67) rectangle (170.03,117.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.17,114.67) -- (170.03,117.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.17,117.53) -- (170.03,114.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.11,116.23) rectangle (168.97,119.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.11,116.23) -- (168.97,119.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.11,119.09) -- (168.97,116.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.72,112.32) rectangle (167.57,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.72,112.32) -- (167.57,115.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.72,115.18) -- (167.57,112.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.91,117.15) rectangle (172.77,120.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.91,117.15) -- (172.77,120.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.91,120.00) -- (172.77,117.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.18,114.22) rectangle (169.03,117.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.18,114.22) -- (169.03,117.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.18,117.07) -- (169.03,114.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.67, 95.28) rectangle (142.52, 98.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.67, 95.28) -- (142.52, 98.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.67, 98.13) -- (142.52, 95.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.53, 88.51) rectangle (144.39, 91.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.53, 88.51) -- (144.39, 91.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.53, 91.37) -- (144.39, 88.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.33, 89.39) rectangle (139.19, 92.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.33, 89.39) -- (139.19, 92.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.33, 92.25) -- (139.19, 89.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.35, 92.46) rectangle (144.20, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.35, 92.46) -- (144.20, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.35, 95.32) -- (144.20, 92.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29, 83.72) rectangle (140.14, 86.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29, 83.72) -- (140.14, 86.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.29, 86.57) -- (140.14, 83.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.03, 85.50) rectangle (141.88, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.03, 85.50) -- (141.88, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.03, 88.35) -- (141.88, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.65, 85.50) rectangle (140.51, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.65, 85.50) -- (140.51, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.65, 88.35) -- (140.51, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.29, 99.24) rectangle (146.14,102.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.29, 99.24) -- (146.14,102.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.29,102.09) -- (146.14, 99.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.01, 85.50) rectangle (139.86, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.01, 85.50) -- (139.86, 88.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.01, 88.35) -- (139.86, 85.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.50, 90.62) rectangle (140.36, 93.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.50, 90.62) -- (140.36, 93.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.50, 93.48) -- (140.36, 90.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.01, 96.89) rectangle (142.86, 99.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.01, 96.89) -- (142.86, 99.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.01, 99.75) -- (142.86, 96.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.43,128.45) rectangle (166.28,131.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.43,128.45) -- (166.28,131.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.43,131.30) -- (166.28,128.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.75,125.92) rectangle (162.60,128.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.75,125.92) -- (162.60,128.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.75,128.77) -- (162.60,125.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.02,129.80) rectangle (166.88,132.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.02,129.80) -- (166.88,132.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.02,132.65) -- (166.88,129.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.39,128.04) rectangle (167.24,130.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.39,128.04) -- (167.24,130.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.39,130.89) -- (167.24,128.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.70,130.22) rectangle (160.55,133.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.70,130.22) -- (160.55,133.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.70,133.07) -- (160.55,130.22);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.91,216.82) -- (172.95,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.93,214.80) -- (170.93,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (213.09,216.82) -- (217.13,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (215.11,214.80) -- (215.11,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (197.64,216.82) -- (201.68,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (199.66,214.80) -- (199.66,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.46,216.82) -- (181.50,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.48,214.80) -- (179.48,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.22,216.82) -- (165.26,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.24,214.80) -- (163.24,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (224.54,216.82) -- (228.57,216.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (226.56,214.80) -- (226.56,218.84);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.37, 68.39) rectangle (114.22, 71.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.37, 68.39) -- (114.22, 71.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.37, 71.24) -- (114.22, 68.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.56, 75.44) rectangle (120.41, 78.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.56, 75.44) -- (120.41, 78.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.56, 78.29) -- (120.41, 75.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.43,108.18) rectangle (139.29,111.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.43,108.18) -- (139.29,111.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.43,111.03) -- (139.29,108.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.21,143.87) rectangle (163.06,146.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.21,143.87) -- (163.06,146.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.21,146.73) -- (163.06,143.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.81,168.04) rectangle (177.66,170.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.81,168.04) -- (177.66,170.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.81,170.89) -- (177.66,168.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.90,193.96) rectangle (201.75,196.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.90,193.96) -- (201.75,196.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (198.90,196.81) -- (201.75,193.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (124.01, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.18, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.66, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.84, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.58, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.66, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.59, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.26, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.51, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.58, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.43, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.58, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.67, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.84, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 83.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.34, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.22, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.75, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.34, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.75, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.49, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.75, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.59, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.75, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.18, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.37, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.63, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.63, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.32, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.22, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.07, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.12, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.25, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (140.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.79, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.62, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.32, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.36, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.48, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.51, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.93, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.79, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.79, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.79, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.79, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.22, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.65, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.07, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.07, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.36, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.34, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.73, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.78, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.12, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.78, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.93, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.22, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.86, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.47, 74.44) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.22, 73.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.20, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.22, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.87, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.99, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.87, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.87, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.74, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.66, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.50, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.22, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.25, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.25, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.25, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.12, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.25, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.25, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.62, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.37, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.62, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.25, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.50, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.22, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.12, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.37, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.22, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.57, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.68, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.87, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.62, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.22, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.87, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.80, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.36, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.36, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (140.86, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.20, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.37, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.60, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.62, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.50, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.99, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 80.76) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.62, 75.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.34, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.25, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.46, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.75, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.26, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.47, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.41, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.01, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.50, 82.37) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 89.48) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.90, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.09, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.31, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.83, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.90, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.25, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.31, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (151.47, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.83, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.23, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 81.59) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.23, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.31, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.67, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 83.12) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.49, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.58, 89.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 88.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.51, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.68, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.47, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.31, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.59, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.22, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.90, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.25, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.28, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.61, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.01, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.61, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.14, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.99, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 90.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.35, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.47, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.11, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.68, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.75, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.38, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.51, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.68, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.47, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.71, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.36, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.07, 85.15) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (144.65, 79.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.22, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.49, 89.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.47, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.21, 86.36) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.66, 87.47) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.14, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.36, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.51, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.36, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.21, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.43, 88.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.51, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.00, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.25, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.91, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.68, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.58, 88.51) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.59, 90.39) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.03, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.10, 77.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.79, 76.86) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.99, 80.76) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.68, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.39, 84.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.71, 80.76) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.91, 78.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (124.99, 86.36) circle (  1.43);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (128.75, 96.78) --
	(130.67, 93.45) --
	(126.82, 93.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.10, 82.98) --
	(123.03, 79.65) --
	(119.18, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.01, 79.08) --
	(123.93, 75.76) --
	(120.09, 75.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.20, 82.10) --
	(124.12, 78.77) --
	(120.28, 78.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.68, 81.16) --
	(122.60, 77.83) --
	(118.76, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.35, 77.92) --
	(156.27, 74.59) --
	(152.43, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.71, 82.98) --
	(123.63, 79.65) --
	(119.79, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.01, 82.10) --
	(123.93, 78.77) --
	(120.09, 78.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.69, 76.66) --
	(121.61, 73.33) --
	(117.77, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.01, 81.16) --
	(123.93, 77.83) --
	(120.09, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (191.39, 91.22) --
	(193.31, 87.89) --
	(189.47, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.56, 92.61) --
	(181.48, 89.28) --
	(177.64, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 95.76) --
	(228.48, 92.43) --
	(224.64, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,106.68) --
	(228.48,103.35) --
	(224.64,103.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 94.65) --
	(228.48, 91.33) --
	(224.64, 91.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.19,107.01) --
	(139.11,103.68) --
	(135.27,103.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,101.04) --
	(228.48, 97.71) --
	(224.64, 97.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.99,113.99) --
	(165.91,110.67) --
	(162.07,110.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (210.55, 98.93) --
	(212.47, 95.60) --
	(208.63, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,100.79) --
	(228.48, 97.46) --
	(224.64, 97.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (210.09,117.39) --
	(212.01,114.06) --
	(208.16,114.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,125.58) --
	(228.48,122.26) --
	(224.64,122.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,141.53) --
	(228.48,138.20) --
	(224.64,138.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,121.65) --
	(228.48,118.32) --
	(224.64,118.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,138.63) --
	(228.48,135.30) --
	(224.64,135.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (201.43,115.61) --
	(203.35,112.29) --
	(199.51,112.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (182.56,132.60) --
	(184.48,129.28) --
	(180.64,129.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,120.21) --
	(228.48,116.88) --
	(224.64,116.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.49,110.98) --
	(147.41,107.65) --
	(143.57,107.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,134.34) --
	(228.48,131.01) --
	(224.64,131.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,121.47) --
	(228.48,118.14) --
	(224.64,118.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,131.80) --
	(228.48,128.47) --
	(224.64,128.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,127.09) --
	(228.48,123.76) --
	(224.64,123.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,117.63) --
	(228.48,114.30) --
	(224.64,114.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,120.79) --
	(228.48,117.46) --
	(224.64,117.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,137.85) --
	(228.48,134.52) --
	(224.64,134.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,123.28) --
	(228.48,119.95) --
	(224.64,119.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,137.01) --
	(228.48,133.68) --
	(224.64,133.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,141.09) --
	(228.48,137.76) --
	(224.64,137.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,113.89) --
	(228.48,110.56) --
	(224.64,110.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,128.90) --
	(228.48,125.57) --
	(224.64,125.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,143.57) --
	(228.48,140.25) --
	(224.64,140.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,149.73) --
	(228.48,146.41) --
	(224.64,146.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,136.05) --
	(228.48,132.72) --
	(224.64,132.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,148.63) --
	(228.48,145.30) --
	(224.64,145.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,144.78) --
	(228.48,141.46) --
	(224.64,141.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,119.47) --
	(228.48,116.14) --
	(224.64,116.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,132.94) --
	(228.48,129.61) --
	(224.64,129.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,137.34) --
	(228.48,134.01) --
	(224.64,134.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,154.10) --
	(228.48,150.77) --
	(224.64,150.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,145.39) --
	(228.48,142.06) --
	(224.64,142.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,171.08) --
	(228.48,167.75) --
	(224.64,167.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,156.25) --
	(228.48,152.92) --
	(224.64,152.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,156.91) --
	(228.48,153.58) --
	(224.64,153.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,150.07) --
	(228.48,146.75) --
	(224.64,146.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,160.49) --
	(228.48,157.16) --
	(224.64,157.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,148.06) --
	(228.48,144.73) --
	(224.64,144.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,159.24) --
	(228.48,155.92) --
	(224.64,155.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,169.65) --
	(228.48,166.32) --
	(224.64,166.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,176.56) --
	(228.48,173.23) --
	(224.64,173.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,162.92) --
	(228.48,159.59) --
	(224.64,159.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,170.31) --
	(228.48,166.98) --
	(224.64,166.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,169.04) --
	(228.48,165.71) --
	(224.64,165.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,168.57) --
	(228.48,165.25) --
	(224.64,165.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,179.13) --
	(228.48,175.80) --
	(224.64,175.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,181.72) --
	(228.48,178.40) --
	(224.64,178.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,148.61) --
	(228.48,145.28) --
	(224.64,145.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,172.21) --
	(228.48,168.88) --
	(224.64,168.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,171.14) --
	(228.48,167.81) --
	(224.64,167.81) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,154.01) --
	(228.48,150.68) --
	(224.64,150.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,184.52) --
	(228.48,181.19) --
	(224.64,181.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,177.23) --
	(228.48,173.90) --
	(224.64,173.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,181.11) --
	(228.48,177.78) --
	(224.64,177.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,172.40) --
	(228.48,169.07) --
	(224.64,169.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,187.50) --
	(228.48,184.17) --
	(224.64,184.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,172.98) --
	(228.48,169.65) --
	(224.64,169.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,174.52) --
	(228.48,171.19) --
	(224.64,171.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,178.05) --
	(228.48,174.72) --
	(224.64,174.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,172.05) --
	(228.48,168.72) --
	(224.64,168.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,168.64) --
	(228.48,165.31) --
	(224.64,165.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,182.01) --
	(228.48,178.68) --
	(224.64,178.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,194.03) --
	(228.48,190.70) --
	(224.64,190.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,193.76) --
	(228.48,190.43) --
	(224.64,190.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,179.94) --
	(228.48,176.61) --
	(224.64,176.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,186.79) --
	(228.48,183.46) --
	(224.64,183.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,192.99) --
	(228.48,189.66) --
	(224.64,189.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,204.87) --
	(228.48,201.54) --
	(224.64,201.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,189.81) --
	(228.48,186.48) --
	(224.64,186.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,190.09) --
	(228.48,186.76) --
	(224.64,186.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,186.08) --
	(228.48,182.75) --
	(224.64,182.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.93, 83.81) --
	(129.85, 80.48) --
	(126.01, 80.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.34, 86.72) --
	(126.26, 83.39) --
	(122.42, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.73, 96.45) --
	(133.65, 93.12) --
	(129.80, 93.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.01, 89.15) --
	(144.93, 85.82) --
	(141.09, 85.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.29, 90.73) --
	(153.21, 87.40) --
	(149.37, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.36, 87.98) --
	(156.28, 84.66) --
	(152.44, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.09, 73.75) --
	(138.01, 70.42) --
	(134.17, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.53, 87.98) --
	(139.45, 84.66) --
	(135.61, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.11, 75.27) --
	(121.03, 71.95) --
	(117.18, 71.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.91, 89.69) --
	(156.83, 86.37) --
	(152.99, 86.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.75, 92.16) --
	(162.67, 88.83) --
	(158.83, 88.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.86, 76.66) --
	(124.78, 73.33) --
	(120.94, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.48, 80.16) --
	(132.40, 76.83) --
	(128.55, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (205.31, 90.22) --
	(207.23, 86.89) --
	(203.39, 86.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.60, 92.61) --
	(129.52, 89.28) --
	(125.68, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.94, 82.10) --
	(189.86, 78.77) --
	(186.02, 78.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.87, 90.22) --
	(130.79, 86.89) --
	(126.95, 86.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.52, 82.98) --
	(157.44, 79.65) --
	(153.60, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.31, 92.61) --
	(127.23, 89.28) --
	(123.38, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.37, 80.16) --
	(130.29, 76.83) --
	(126.45, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.89, 88.58) --
	(182.81, 85.25) --
	(178.97, 85.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (162.74,117.71) --
	(164.66,114.38) --
	(160.82,114.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,110.21) --
	(228.48,106.89) --
	(224.64,106.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.48, 95.40) --
	(142.40, 92.07) --
	(138.56, 92.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.58,100.28) --
	(163.50, 96.96) --
	(159.66, 96.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (192.84, 98.34) --
	(194.76, 95.02) --
	(190.92, 95.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (199.95, 87.37) --
	(201.87, 84.04) --
	(198.03, 84.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,103.93) --
	(228.48,100.60) --
	(224.64,100.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,108.70) --
	(228.48,105.37) --
	(224.64,105.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (213.42,118.39) --
	(215.34,115.07) --
	(211.50,115.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 99.21) --
	(228.48, 95.88) --
	(224.64, 95.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.79, 97.11) --
	(153.71, 93.78) --
	(149.87, 93.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (216.21,105.82) --
	(218.13,102.49) --
	(214.29,102.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (168.97,101.76) --
	(170.89, 98.43) --
	(167.05, 98.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (189.29, 93.46) --
	(191.21, 90.13) --
	(187.37, 90.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 94.27) --
	(228.48, 90.94) --
	(224.64, 90.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.63, 81.16) --
	(133.55, 77.83) --
	(129.70, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.45, 87.98) --
	(134.38, 84.66) --
	(130.53, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 95.40) --
	(228.48, 92.07) --
	(224.64, 92.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (185.81,101.76) --
	(187.73, 98.43) --
	(183.89, 98.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (215.70, 92.61) --
	(217.62, 89.28) --
	(213.78, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.81,100.79) --
	(165.74, 97.46) --
	(161.89, 97.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.40,106.68) --
	(190.32,103.35) --
	(186.48,103.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,107.96) --
	(228.48,104.63) --
	(224.64,104.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,127.61) --
	(228.48,124.29) --
	(224.64,124.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.56,102.22) --
	(155.49, 98.89) --
	(151.64, 98.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.06, 96.11) --
	(197.98, 92.78) --
	(194.14, 92.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,110.98) --
	(228.48,107.65) --
	(224.64,107.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (172.04, 96.11) --
	(173.96, 92.78) --
	(170.11, 92.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,111.47) --
	(228.48,108.14) --
	(224.64,108.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (202.33,127.05) --
	(204.25,123.72) --
	(200.41,123.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.66,114.19) --
	(144.58,110.87) --
	(140.74,110.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,108.84) --
	(228.48,105.52) --
	(224.64,105.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,138.01) --
	(228.48,134.68) --
	(224.64,134.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,103.93) --
	(228.48,100.60) --
	(224.64,100.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,118.02) --
	(228.48,114.69) --
	(224.64,114.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (197.58,115.25) --
	(199.50,111.92) --
	(195.66,111.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,115.25) --
	(228.48,111.92) --
	(224.64,111.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,122.12) --
	(228.48,118.79) --
	(224.64,118.79) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (193.52, 97.43) --
	(195.44, 94.10) --
	(191.60, 94.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 99.76) --
	(228.48, 96.43) --
	(224.64, 96.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,147.94) --
	(228.48,144.62) --
	(224.64,144.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,115.43) --
	(228.48,112.10) --
	(224.64,112.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,133.84) --
	(228.48,130.51) --
	(224.64,130.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,120.21) --
	(228.48,116.88) --
	(224.64,116.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,113.48) --
	(228.48,110.15) --
	(224.64,110.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,131.26) --
	(228.48,127.93) --
	(224.64,127.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,133.37) --
	(228.48,130.04) --
	(224.64,130.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,130.63) --
	(228.48,127.30) --
	(224.64,127.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,141.88) --
	(228.48,138.55) --
	(224.64,138.55) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,148.71) --
	(228.48,145.38) --
	(224.64,145.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,157.06) --
	(228.48,153.73) --
	(224.64,153.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,141.50) --
	(228.48,138.17) --
	(224.64,138.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,133.45) --
	(228.48,130.12) --
	(224.64,130.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,135.78) --
	(228.48,132.45) --
	(224.64,132.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,151.74) --
	(228.48,148.41) --
	(224.64,148.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,154.98) --
	(228.48,151.65) --
	(224.64,151.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,146.12) --
	(228.48,142.79) --
	(224.64,142.79) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,129.04) --
	(228.48,125.71) --
	(224.64,125.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,137.44) --
	(228.48,134.11) --
	(224.64,134.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,150.40) --
	(228.48,147.07) --
	(224.64,147.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,153.06) --
	(228.48,149.73) --
	(224.64,149.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,143.86) --
	(228.48,140.53) --
	(224.64,140.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,147.24) --
	(228.48,143.91) --
	(224.64,143.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 90.73) --
	(228.48, 87.40) --
	(224.64, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,133.63) --
	(228.48,130.30) --
	(224.64,130.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,158.84) --
	(228.48,155.51) --
	(224.64,155.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,156.97) --
	(228.48,153.64) --
	(224.64,153.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,145.62) --
	(228.48,142.29) --
	(224.64,142.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,155.70) --
	(228.48,152.37) --
	(224.64,152.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,161.16) --
	(228.48,157.83) --
	(224.64,157.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,142.47) --
	(228.48,139.14) --
	(224.64,139.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,126.03) --
	(228.48,122.70) --
	(224.64,122.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,166.54) --
	(228.48,163.21) --
	(224.64,163.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,153.05) --
	(228.48,149.73) --
	(224.64,149.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,156.51) --
	(228.48,153.18) --
	(224.64,153.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,167.15) --
	(228.48,163.82) --
	(224.64,163.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,165.10) --
	(228.48,161.77) --
	(224.64,161.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,155.02) --
	(228.48,151.69) --
	(224.64,151.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,108.84) --
	(228.48,105.52) --
	(224.64,105.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,160.10) --
	(228.48,156.77) --
	(224.64,156.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,148.58) --
	(228.48,145.25) --
	(224.64,145.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,173.83) --
	(228.48,170.51) --
	(224.64,170.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,163.69) --
	(228.48,160.36) --
	(224.64,160.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,169.43) --
	(228.48,166.10) --
	(224.64,166.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,167.12) --
	(228.48,163.79) --
	(224.64,163.79) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,158.89) --
	(228.48,155.56) --
	(224.64,155.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,157.59) --
	(228.48,154.26) --
	(224.64,154.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,166.23) --
	(228.48,162.90) --
	(224.64,162.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,177.17) --
	(228.48,173.84) --
	(224.64,173.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,160.97) --
	(228.48,157.64) --
	(224.64,157.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,175.57) --
	(228.48,172.24) --
	(224.64,172.24) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,173.47) --
	(228.48,170.14) --
	(224.64,170.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,151.52) --
	(228.48,148.19) --
	(224.64,148.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,177.49) --
	(228.48,174.16) --
	(224.64,174.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,181.25) --
	(228.48,177.92) --
	(224.64,177.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,175.03) --
	(228.48,171.71) --
	(224.64,171.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,176.08) --
	(228.48,172.75) --
	(224.64,172.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,154.21) --
	(228.48,150.88) --
	(224.64,150.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,159.52) --
	(228.48,156.19) --
	(224.64,156.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,192.83) --
	(228.48,189.50) --
	(224.64,189.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,191.75) --
	(228.48,188.43) --
	(224.64,188.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,121.35) --
	(228.48,118.02) --
	(224.64,118.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,154.62) --
	(228.48,151.29) --
	(224.64,151.29) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,164.24) --
	(228.48,160.91) --
	(224.64,160.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,175.40) --
	(228.48,172.07) --
	(224.64,172.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,198.05) --
	(228.48,194.72) --
	(224.64,194.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,181.63) --
	(228.48,178.30) --
	(224.64,178.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,169.86) --
	(228.48,166.53) --
	(224.64,166.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,183.42) --
	(228.48,180.10) --
	(224.64,180.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,200.95) --
	(228.48,197.62) --
	(224.64,197.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,195.52) --
	(228.48,192.19) --
	(224.64,192.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,197.29) --
	(228.48,193.96) --
	(224.64,193.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,198.76) --
	(228.48,195.44) --
	(224.64,195.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,198.56) --
	(228.48,195.23) --
	(224.64,195.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,169.17) --
	(228.48,165.84) --
	(224.64,165.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,190.68) --
	(228.48,187.36) --
	(224.64,187.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,204.04) --
	(228.48,200.72) --
	(224.64,200.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,193.46) --
	(228.48,190.13) --
	(224.64,190.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,171.48) --
	(228.48,168.15) --
	(224.64,168.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,195.84) --
	(228.48,192.51) --
	(224.64,192.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,185.42) --
	(228.48,182.09) --
	(224.64,182.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,186.77) --
	(228.48,183.45) --
	(224.64,183.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,204.52) --
	(228.48,201.19) --
	(224.64,201.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,206.92) --
	(228.48,203.59) --
	(224.64,203.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.07, 73.75) --
	(118.00, 70.42) --
	(114.15, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.74, 73.75) --
	(120.67, 70.42) --
	(116.82, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.30, 86.72) --
	(124.22, 83.39) --
	(120.38, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.47, 73.75) --
	(119.39, 70.42) --
	(115.55, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.11, 76.66) --
	(121.03, 73.33) --
	(117.18, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.07, 73.75) --
	(118.00, 70.42) --
	(114.15, 70.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.41, 77.92) --
	(123.33, 74.59) --
	(119.49, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.58, 76.66) --
	(122.50, 73.33) --
	(118.65, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.58, 75.27) --
	(122.50, 71.95) --
	(118.65, 71.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.68, 81.16) --
	(122.60, 77.83) --
	(118.76, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.22, 76.66) --
	(121.15, 73.33) --
	(117.30, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.84, 89.15) --
	(125.76, 85.82) --
	(121.92, 85.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.46, 76.66) --
	(121.38, 73.33) --
	(117.54, 73.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.14, 77.92) --
	(122.06, 74.59) --
	(118.22, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.22,103.31) --
	(139.14, 99.99) --
	(135.30, 99.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.66, 80.16) --
	(125.59, 76.83) --
	(121.74, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.20, 77.92) --
	(124.12, 74.59) --
	(120.28, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.96, 84.59) --
	(182.88, 81.26) --
	(179.04, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.66, 77.92) --
	(125.59, 74.59) --
	(121.74, 74.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.68, 84.59) --
	(163.60, 81.26) --
	(159.76, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (162.89, 86.72) --
	(164.81, 83.39) --
	(160.97, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.78, 89.69) --
	(141.71, 86.37) --
	(137.86, 86.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.33, 81.16) --
	(198.25, 77.83) --
	(194.41, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.75, 80.16) --
	(126.67, 76.83) --
	(122.83, 76.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.13, 91.22) --
	(149.05, 87.89) --
	(145.21, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.84, 85.34) --
	(125.76, 82.01) --
	(121.92, 82.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.56, 82.98) --
	(190.48, 79.65) --
	(186.64, 79.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (174.73, 81.16) --
	(176.65, 77.83) --
	(172.81, 77.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.06, 87.37) --
	(134.98, 84.04) --
	(131.14, 84.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.19, 86.05) --
	(135.12, 82.72) --
	(131.27, 82.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.31, 83.81) --
	(125.23, 80.48) --
	(121.39, 80.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.96, 84.59) --
	(146.88, 81.26) --
	(143.04, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (176.30,100.02) --
	(178.22, 96.69) --
	(174.37, 96.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.43, 86.72) --
	(128.35, 83.39) --
	(124.50, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.32, 84.59) --
	(146.24, 81.26) --
	(142.40, 81.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (175.70, 92.61) --
	(177.62, 89.28) --
	(173.78, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (209.00, 86.72) --
	(210.92, 83.39) --
	(207.08, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.44, 85.34) --
	(161.36, 82.01) --
	(157.52, 82.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.76, 94.65) --
	(154.68, 91.33) --
	(150.83, 91.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.75, 85.34) --
	(126.67, 82.01) --
	(122.83, 82.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (169.77, 86.72) --
	(171.69, 83.39) --
	(167.85, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.21, 94.27) --
	(181.13, 90.94) --
	(177.29, 90.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (193.61, 95.76) --
	(195.53, 92.43) --
	(191.69, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.57, 86.72) --
	(158.49, 83.39) --
	(154.65, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.15, 97.74) --
	(143.07, 94.41) --
	(139.23, 94.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (206.23, 98.34) --
	(208.16, 95.02) --
	(204.31, 95.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.11, 86.72) --
	(131.03, 83.39) --
	(127.19, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (165.21, 86.72) --
	(167.13, 83.39) --
	(163.28, 83.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.79, 91.22) --
	(168.71, 87.89) --
	(164.86, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.14,102.89) --
	(189.06, 99.56) --
	(185.22, 99.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (196.45, 87.37) --
	(198.37, 84.04) --
	(194.53, 84.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.51, 95.03) --
	(175.43, 91.70) --
	(171.59, 91.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 92.61) --
	(228.48, 89.28) --
	(224.64, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 87.98) --
	(228.48, 84.66) --
	(224.64, 84.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.17,105.82) --
	(182.09,102.49) --
	(178.24,102.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,104.52) --
	(228.48,101.20) --
	(224.64,101.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.06, 90.73) --
	(129.98, 87.40) --
	(126.13, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.14, 92.61) --
	(168.06, 89.28) --
	(164.22, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (195.34, 91.22) --
	(197.26, 87.89) --
	(193.42, 87.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,127.96) --
	(228.48,124.64) --
	(224.64,124.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.95,106.00) --
	(151.87,102.67) --
	(148.03,102.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (205.29, 90.73) --
	(207.21, 87.40) --
	(203.37, 87.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (205.26, 90.22) --
	(207.18, 86.89) --
	(203.34, 86.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 98.64) --
	(228.48, 95.31) --
	(224.64, 95.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (213.54,108.55) --
	(215.46,105.23) --
	(211.62,105.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (214.13,100.28) --
	(216.05, 96.96) --
	(212.21, 96.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,102.45) --
	(228.48, 99.12) --
	(224.64, 99.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.26, 92.16) --
	(165.18, 88.83) --
	(161.34, 88.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (206.57,104.13) --
	(208.49,100.80) --
	(204.65,100.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (209.44, 92.61) --
	(211.36, 89.28) --
	(207.52, 89.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (194.06, 92.16) --
	(195.98, 88.83) --
	(192.14, 88.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.11, 95.76) --
	(182.03, 92.43) --
	(178.19, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.63,101.28) --
	(175.55, 97.96) --
	(171.71, 97.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 95.76) --
	(228.48, 92.43) --
	(224.64, 92.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.32,101.28) --
	(181.25, 97.96) --
	(177.40, 97.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.93,108.99) --
	(181.85,105.66) --
	(178.01,105.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,100.54) --
	(228.48, 97.21) --
	(224.64, 97.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.42,103.52) --
	(138.34,100.19) --
	(134.49,100.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (191.88, 97.11) --
	(193.80, 93.78) --
	(189.96, 93.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,107.96) --
	(228.48,104.63) --
	(224.64,104.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (209.77,107.01) --
	(211.69,103.68) --
	(207.84,103.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 95.03) --
	(228.48, 91.70) --
	(224.64, 91.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,100.79) --
	(228.48, 97.46) --
	(224.64, 97.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,138.39) --
	(228.48,135.06) --
	(224.64,135.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (208.11,103.52) --
	(210.03,100.19) --
	(206.19,100.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,121.47) --
	(228.48,118.14) --
	(224.64,118.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (211.63,119.05) --
	(213.55,115.72) --
	(209.71,115.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,113.58) --
	(228.48,110.26) --
	(224.64,110.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,123.38) --
	(228.48,120.06) --
	(224.64,120.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 97.43) --
	(228.48, 94.10) --
	(224.64, 94.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,142.36) --
	(228.48,139.03) --
	(224.64,139.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 99.21) --
	(228.48, 95.88) --
	(224.64, 95.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,103.31) --
	(228.48, 99.99) --
	(224.64, 99.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,127.49) --
	(228.48,124.17) --
	(224.64,124.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,135.89) --
	(228.48,132.57) --
	(224.64,132.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,144.50) --
	(228.48,141.18) --
	(224.64,141.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 98.93) --
	(228.48, 95.60) --
	(224.64, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56, 98.64) --
	(228.48, 95.31) --
	(224.64, 95.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,153.30) --
	(228.48,149.97) --
	(224.64,149.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,161.40) --
	(228.48,158.07) --
	(224.64,158.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,109.95) --
	(228.48,106.62) --
	(224.64,106.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,119.33) --
	(228.48,116.00) --
	(224.64,116.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,146.11) --
	(228.48,142.78) --
	(224.64,142.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,122.17) --
	(228.48,118.85) --
	(224.64,118.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,154.99) --
	(228.48,151.66) --
	(224.64,151.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,144.15) --
	(228.48,140.83) --
	(224.64,140.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,114.59) --
	(228.48,111.26) --
	(224.64,111.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,144.42) --
	(228.48,141.09) --
	(224.64,141.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,148.65) --
	(228.48,145.32) --
	(224.64,145.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,122.35) --
	(228.48,119.02) --
	(224.64,119.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,185.58) --
	(228.48,182.25) --
	(224.64,182.25) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,118.09) --
	(228.48,114.77) --
	(224.64,114.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,160.83) --
	(228.48,157.50) --
	(224.64,157.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,125.76) --
	(228.48,122.44) --
	(224.64,122.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,168.77) --
	(228.48,165.44) --
	(224.64,165.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,139.65) --
	(228.48,136.32) --
	(224.64,136.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,160.64) --
	(228.48,157.31) --
	(224.64,157.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,185.18) --
	(228.48,181.86) --
	(224.64,181.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,131.59) --
	(228.48,128.26) --
	(224.64,128.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,189.63) --
	(228.48,186.30) --
	(224.64,186.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,167.30) --
	(228.48,163.98) --
	(224.64,163.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,185.67) --
	(228.48,182.35) --
	(224.64,182.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,127.89) --
	(228.48,124.56) --
	(224.64,124.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,179.04) --
	(228.48,175.71) --
	(224.64,175.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (226.56,219.04) --
	(228.48,215.71) --
	(224.64,215.71) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.64, 92.46) rectangle (135.50, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.64, 92.46) -- (135.50, 95.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.64, 95.32) -- (135.50, 92.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.17, 94.70) rectangle (171.02, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.17, 94.70) -- (171.02, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.17, 97.55) -- (171.02, 94.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) rectangle (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,215.39) -- (227.98,218.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (225.13,218.25) -- (227.98,215.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.12,127.52) rectangle (150.97,130.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.12,127.52) -- (150.97,130.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.12,130.37) -- (150.97,127.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.06,139.97) rectangle (160.91,142.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.06,139.97) -- (160.91,142.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.06,142.82) -- (160.91,139.97);
\definecolor{drawColor}{RGB}{152,152,152}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 30.77) -- (235.42,225.68);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.95, 30.77) -- ( 41.95, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.19, 30.77) -- ( 44.19, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.13, 30.77) -- ( 46.13, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 47.84, 30.77) -- ( 47.84, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.37, 30.77) -- ( 49.37, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 59.43, 30.77) -- ( 59.43, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.32, 30.77) -- ( 65.32, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 69.49, 30.77) -- ( 69.49, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.73, 30.77) -- ( 72.73, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 75.38, 30.77) -- ( 75.38, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 77.62, 30.77) -- ( 77.62, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.56, 30.77) -- ( 79.56, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 81.27, 30.77) -- ( 81.27, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.79, 30.77) -- ( 82.79, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 92.86, 30.77) -- ( 92.86, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.74, 30.77) -- ( 98.74, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (102.92, 30.77) -- (102.92, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.16, 30.77) -- (106.16, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (108.80, 30.77) -- (108.80, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (111.04, 30.77) -- (111.04, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.98, 30.77) -- (112.98, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.69, 30.77) -- (114.69, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (116.22, 30.77) -- (116.22, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (126.28, 30.77) -- (126.28, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (132.17, 30.77) -- (132.17, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (136.34, 30.77) -- (136.34, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (139.58, 30.77) -- (139.58, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.23, 30.77) -- (142.23, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (144.47, 30.77) -- (144.47, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (146.41, 30.77) -- (146.41, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (148.12, 30.77) -- (148.12, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.64, 30.77) -- (149.64, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (159.71, 30.77) -- (159.71, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (165.59, 30.77) -- (165.59, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (169.77, 30.77) -- (169.77, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.01, 30.77) -- (173.01, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (175.65, 30.77) -- (175.65, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.89, 30.77) -- (177.89, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.83, 30.77) -- (179.83, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (181.54, 30.77) -- (181.54, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (183.07, 30.77) -- (183.07, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (193.13, 30.77) -- (193.13, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (199.02, 30.77) -- (199.02, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.19, 30.77) -- (203.19, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (206.43, 30.77) -- (206.43, 36.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (209.08, 30.77) -- (209.08, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (211.32, 30.77) -- (211.32, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.26, 30.77) -- (213.26, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.97, 30.77) -- (214.97, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (216.49, 30.77) -- (216.49, 39.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (226.56, 30.77) -- (226.56, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.44, 30.77) -- (232.44, 33.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 32.22) -- ( 43.36, 32.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 34.45) -- ( 43.36, 34.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 36.39) -- ( 43.36, 36.39);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 38.10) -- ( 43.36, 38.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 39.63) -- ( 49.05, 39.63);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 49.69) -- ( 43.36, 49.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 55.58) -- ( 43.36, 55.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 59.76) -- ( 43.36, 59.76);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 62.99) -- ( 46.20, 62.99);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 65.64) -- ( 43.36, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 67.88) -- ( 43.36, 67.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 69.82) -- ( 43.36, 69.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 71.53) -- ( 43.36, 71.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 73.06) -- ( 49.05, 73.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 83.12) -- ( 43.36, 83.12);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 89.00) -- ( 43.36, 89.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 93.18) -- ( 43.36, 93.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 96.42) -- ( 46.20, 96.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 99.07) -- ( 43.36, 99.07);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,101.30) -- ( 43.36,101.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,103.24) -- ( 43.36,103.24);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,104.95) -- ( 43.36,104.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,106.48) -- ( 49.05,106.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,116.54) -- ( 43.36,116.54);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,122.43) -- ( 43.36,122.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,126.61) -- ( 43.36,126.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,129.84) -- ( 46.20,129.84);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,132.49) -- ( 43.36,132.49);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,134.73) -- ( 43.36,134.73);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,136.67) -- ( 43.36,136.67);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,138.38) -- ( 43.36,138.38);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,139.91) -- ( 49.05,139.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,149.97) -- ( 43.36,149.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,155.85) -- ( 43.36,155.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,160.03) -- ( 43.36,160.03);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,163.27) -- ( 46.20,163.27);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,165.92) -- ( 43.36,165.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,168.15) -- ( 43.36,168.15);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,170.09) -- ( 43.36,170.09);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,171.80) -- ( 43.36,171.80);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,173.33) -- ( 49.05,173.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,183.39) -- ( 43.36,183.39);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,189.28) -- ( 43.36,189.28);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,193.46) -- ( 43.36,193.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,196.69) -- ( 46.20,196.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,199.34) -- ( 43.36,199.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,201.58) -- ( 43.36,201.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,203.52) -- ( 43.36,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,205.23) -- ( 43.36,205.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,206.76) -- ( 49.05,206.76);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,216.82) -- ( 43.36,216.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,222.70) -- ( 43.36,222.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.77) rectangle (235.42,225.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 70.03) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,136.88) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,203.73) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 73.06) --
	( 40.51, 73.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,139.91) --
	( 40.51,139.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,206.76) --
	( 40.51,206.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 82.79, 28.02) --
	( 82.79, 30.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] (149.64, 28.02) --
	(149.64, 30.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.49, 28.02) --
	(216.49, 30.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 82.79, 19.76) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (149.64, 19.76) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (216.49, 19.76) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (137.96,  7.72) {\textsf{ADDMC} + \texttt{sbk05} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,128.22) {\textsf{ADDMC} + \texttt{cw} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (246.42, 71.76) rectangle (337.78,184.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (251.92,170.55) {Data set};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,149.53) rectangle (266.37,163.98);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (259.14,156.75) circle (  1.43);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,135.07) rectangle (266.37,149.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (259.14,144.52) --
	(261.06,141.19) --
	(257.22,141.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,120.62) rectangle (266.37,135.07);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (257.72,126.42) --
	(260.57,126.42) --
	(260.57,129.27) --
	(257.72,129.27) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92,106.16) rectangle (266.37,120.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.13,113.39) -- (261.16,113.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (259.14,111.37) -- (259.14,115.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92, 91.71) rectangle (266.37,106.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 97.51) rectangle (260.57,100.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 97.51) -- (260.57,100.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72,100.36) -- (260.57, 97.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (251.92, 77.26) rectangle (266.37, 91.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 83.06) -- (260.57, 85.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.72, 85.91) -- (260.57, 83.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (257.13, 84.48) -- (261.16, 84.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (259.14, 82.47) -- (259.14, 86.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,153.72) {DQMR};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,139.27) {Grid};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,124.81) {Mastermind};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87,110.36) {Non-binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87, 95.91) {Other binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (343.28,231.26);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.87, 81.45) {Random Blocks};
\end{scope}
\end{tikzpicture}

### 2021-06-02 doc/long_talk/talk.tex
Slides are almost ready

@@
 \usepackage{complexity}
+\usepackage{booktabs}
 
@@
 
-% BAs, pseudo-Boolean functions, measures, equivalence of definitions
-\begin{frame}{An Alternative Way to Think About It}
+\begin{frame}{An Alternative Way to Think About WMC}
+  \begin{itemize}
+  \item Let \structure{$V$} be the set of variables.
+  \item Then \structure{$2^{2^V}$} is the Boolean algebra of propositional
+    formulas.
+  \end{itemize}
+  \begin{definition}
+    A \alert{measure} is a function \structure{$\mu\colon 2^{2^V} \to
+      \mathbb{R}_{\ge 0}$} such that:
+    \begin{itemize}
+    \item \structure{$\mu(\bot) = 0$};
+    \item \structure{$\mu(x \lor y) = \mu(x) + \mu(y)$} whenever \structure{$x
+        \land y = \bot$}.
+    \end{itemize}
+  \end{definition}
+  \begin{block}{Observation}
+    WMC corresponds to the process of calculating the value of
+    \structure{$\mu(x)$} for some \structure{$x \in 2^{2^V}$}.
+  \end{block}
 \end{frame}
 
-% The theorems: WMC is not expressive enough to cover all measures but can be
-% extended to do so
-\begin{frame}{Some Theoretical Results}
+% \begin{frame}{How  to Define a Measure}
+%   \begin{itemize}
+%   \item A \alert{weight function} is any function \structure{$\nu\colon 2^V \to
+%       \mathbb{R}_{\ge 0}$}.
+%     \begin{itemize}
+%     \item It is \alert{factored} if
+%       \[
+%         \nu = \prod_{x \in V} \nu_x
+%       \]
+%       for some functions \structure{$\nu_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge
+%           0}$}, \structure{$x \in V$}.
+%     \end{itemize}
+%   \item We say that \structure{$\nu$} \alert{induces} \structure{$\mu$} if
+%     \[
+%       \mu(x) = \sum_{\{u\} \le x} \nu(u)
+%     \]
+%     for all \structure{$x \in 2^{2^V}$}.
+%   \item A measure \structure{$\mu$} is \alert{factorable} if there exists a
+%     factored weight function \structure{$\nu$} that induces \structure{$\mu$}.
+%   \end{itemize}
+% \end{frame}
+
+\begin{frame}{The Limitations and Capabilities of Classical WMC}
+  \begin{alertblock}{Observation}
+    Classical WMC is only able to evaluate \structure{factorable} measures
+    (c.f., a collection of mutually independent random variables).
+  \end{alertblock}
+  \begin{theorem}[Informal Version]
+    It is always possible to add more variables to turn a non-factorable measure
+    into a factorable measure.
+  \end{theorem}
+  However, that is not necessarily a good idea!
 \end{frame}
 
-% Things I could mention:
-% The details of the transformation
-% Experimental results
-
-\begin{frame}{The Big Picture}
-  \begin{columns}
-    \begin{column}{0.35\textwidth}
+\begin{frame}{Conditional Probability Tables (CPTs) as Functions}
+  \begin{itemize}
+  \item \alert{One} variable for every random variable with \alert{two} values.
+  \item \alert{$k$} variables for every random variable with \alert{$k > 2$}
+    values.
+  \item Define indicator functions of the form \structure{$[x]\colon 2^{\{x\}}
+      \to \{ 0, 1 \}$}.
+    \begin{itemize}
+    \item \structure{$[x](\emptyset) = 0$};
+    \item \structure{$[x](\{ x \}) = 1$}.
+    \end{itemize}
+  \item Define \structure{$+$}, \structure{$\cdot$}, and scalar multiplication pointwise.
+  \item Then a CPT can be represented as a function.
+  \end{itemize}
+  \begin{columns}[t]
+    \begin{column}{0.5\textwidth}
       \centering
-      \structure{Probabilistic Inference} \\
-      (e.g., a Bayesian network)
-      \fbox{
-        \begin{minipage}{2.5cm}
-          \centering
-          \begin{tikzpicture}[edge from parent/.style={draw,-{Latex}}]
-            \node[draw,circle] at (0, 0) (a) {$A$}
-            child {node[draw,circle] (b) {$B$}};
-          \end{tikzpicture}\\
-          Find \alert{$\Pr(B = 0)$}
-        \end{minipage}
-      }
+      \begin{tabular}[t]{ccc}
+        \toprule
+        $a$ & $b$ & $\Pr(A = a \mid B = b)$ \\
+        \midrule
+        1 & 1 & 0.6 \\
+        1 & 0 & 0.4 \\
+        0 & 1 & 0.1 \\
+        0 & 0 & 0.9 \\
+        \bottomrule
+      \end{tabular}
     \end{column}
-    \begin{column}{0.35\textwidth}
-      \centering
-      \structure{WMC Encoding} \\
-      (CNF with literal weights)
-      \framebox{
-        \scalebox{0.2}{
-          \begin{tabular}{@{}l@{}}
-            p cnf 8 17 \\
-            -2 -1 0 \\
-            1 2 0 \\
-            -3 1 0 \\
-            -1 3 0 \\
-            -5 -1 0 \\
-            -5 -4 0 \\
-            1 4 5 0 \\
-            -6 -1 0 \\
-            -6 4 0 \\
-            -4 1 6 0 \\
-            -7 1 0 \\
-            -7 -4 0 \\
-            -1 4 7 0 \\
-            -8 1 0 \\
-            -8 4 0 \\
-            -4 -1 8 0 \\
-            -4 0 \\
-            c weights 1.0 1.0 0.5 1.0 0.5 1.0 1.0 1.0 0.6 1.0 0.4 1.0 0.1 1.0 0.9 1.0
-          \end{tabular}%
-        }
-      }
-
-      \vspace{1cm}
-      \onslide<2>{
-      \structure{Conditional Weights} \\
-      \framebox{
-        \scalebox{0.2}{%
-          \begin{tabular}{@{}l@{}}
-            p cnf 2 1 \\
-            2 0 \\
-            w 1 0.5 0.5 \\
-            w 2 1 0.6 0.4 \\
-            w 2 -1 0.1 0.9
-          \end{tabular}%
-        }
-      }
-      }
-    \end{column}
-    \begin{column}{0.30\textwidth}
-      \centering
-      \structure{WMC Algorithm}\\
-      \onslide<2>{\alert{$>100\times$} faster}
+    \begin{column}{0.5\textwidth}
+      \begin{align*}
+        \mathsf{CPT_A} &= 0.6[\lambda_{A=1}] \cdot [\lambda_{B=1}] \\
+                       &+ 0.4[\lambda_{A=1}] \cdot \overline{[\lambda_{B=1}]} \\
+                       &+ 0.1\overline{[\lambda_{A=1}]} \cdot [\lambda_{B=1}] \\
+                       &+ 0.9\overline{[\lambda_{A=1}]} \cdot \overline{[\lambda_{B=1}]},
+      \end{align*}
     \end{column}
   \end{columns}
-  \begin{tikzpicture}[remember picture,overlay]
-    \draw[-{Latex}] (3.4, 3) -- (4.9, 4);
-    \draw<2>[-{Latex}] (3.4, 3) to [bend right] (5.8, 0.2);
-    \draw[-{Latex}] (7.7, 4) -- (9, 2.8);
-    \draw<2>[-{Latex}] (6.7, 0.2) to [bend right = 45] (9, 2.8);
-  \end{tikzpicture}
 \end{frame}
+
+\begin{frame}{Experimental Results}
+  \centering
+  \input{cumulative}
+\end{frame}
+
+% \begin{frame}{Compared Against the Second-Best Encoding}
+%   \centering
+%   \input{scatter2}
+% \end{frame}
+
+\begin{frame}{Comparison With the State of the Art}
+  \centering
+  \input{scatter1}
+\end{frame}
+
+\begin{frame}{Summary and Future Work}
+  \begin{itemize}
+  \item Classical WMC can represent any probability distribution by adding more
+    variables.
+  \item But this is not the right approach for WMC algorithms that support
+    working directly with functions.
+  \item Specifically with ADDMC, avoiding redundant variables resulted in
+    \alert{$127$} times faster inference.
+  \item Could this idea be successfully applied to other applications of WMC or,
+    perhaps, other WMC algorithms?
+  \end{itemize}
+  \begin{itemize}
+  \item Potential improvements to the encoding:
+    \begin{itemize}
+    \item Apply ideas from other WMC encodings for Bayesian networks (e.g.,
+      prime implicants, $\log$ encoding).
+    \item Develop encoding tricks that apply to functions but not to conjunctive
+      normal form.
+    \item More on this in our SAT~2021 paper \emph{\structure{Weighted Model
+          Counting Without Parameter Variables}}.
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2021-06-02 tools/UAI_plots.R

@@ -94,20 +94,21 @@ cumulative_plot <- function(df, column_name, pretty_column_name, column_values,
                           xout = max)
   print(interpolation$y)
   print(1000 / interpolation$y)
-#  ggplot(cumulative, aes(x = time, y = count, color = .data[[column_name]])) +
-#    geom_line(aes(linetype = .data[[column_name]])) +
-#    scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000), labels = c("0.1", "1", "10", "100", "1000")) +
-#    xlab("Time (s)") +
-#    ylab("Instances solved") +
-#    scale_colour_manual(breaks = column_values, values = colours) +
-#    scale_linetype_manual(breaks = column_values, values = linetypes) +
-#    annotation_logticks(sides = "b", colour = "#989898") +
-#    theme_light() +
-#    labs(color = pretty_column_name, linetype = pretty_column_name)
+  ggplot(cumulative, aes(x = time, y = count, color = .data[[column_name]])) +
+    geom_line(aes(linetype = .data[[column_name]])) +
+    scale_x_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000), labels = c("0.1", "1", "10", "100", "1000")) +
+    xlab("Time (s)") +
+    ylab("Instances solved") +
+    scale_colour_manual(breaks = column_values, values = colours) +
+    scale_linetype_manual(breaks = column_values, values = linetypes) +
+    annotation_logticks(sides = "b", colour = "#989898") +
+    theme_light() +
+    labs(color = pretty_column_name, linetype = pretty_column_name)
 }
 
 #tikz(file = "../doc/UAI_paper/cumulative.tex", width = 6.5, height = 2.4)
-tikz(file = "../doc/poster/cumulative.tex", width = 7, height = 2.6, standAlone = TRUE)
+#tikz(file = "../doc/poster/cumulative.tex", width = 7, height = 2.6, standAlone = TRUE)
+tikz(file = "../doc/long_talk/cumulative.tex", width = 4.75, height = 3.2)
 cumulative_plot(data_sum, "encoding", "Algorithm \\& Encoding",
                 sort(unique(data_sum$encoding)),
[…]

### 2021-06-04 doc/long_talk/talk.tex
Finishing touches to the UAI submission

@@
         \end{itemize}
-      \item Main types of algorithms:
-        \begin{itemize}
-        \item using knowledge compilation
-        \item using a \SAT{} solver
-        \item manipulating pseudo-Boolean functions
-        \end{itemize}
+%      \item Main types of algorithms:
+%        \begin{itemize}
+%        \item using knowledge compilation
+%        \item using a \SAT{} solver
+%        \item manipulating pseudo-Boolean functions
+%        \end{itemize}
       \end{itemize}
@@
 
-\begin{frame}{The Limitations and Capabilities of Classical WMC}
+\begin{frame}{The Limitations and Capabilities of WMC}
   \begin{alertblock}{Observation}
@@
 
-\begin{frame}{Conditional Probability Tables (CPTs) as Functions}
+\begin{frame}{Encoding Bayesian Networks}
   \begin{itemize}
-  \item \alert{One} variable for every random variable with \alert{two} values.
-  \item \alert{$k$} variables for every random variable with \alert{$k > 2$}
-    values.
+%  \item \alert{One} variable for every random variable with \alert{two} values.
+%  \item \alert{$k$} variables for every random variable with \alert{$k > 2$}
+%    values.
   \item Define indicator functions of the form \structure{$[x]\colon 2^{\{x\}}
@@
   \item Define \structure{$+$}, \structure{$\cdot$}, and scalar multiplication pointwise.
-  \item Then a CPT can be represented as a function.
+  \item Then a conditional probability table (CPT) can be represented as a function.
   \end{itemize}
@@
   \begin{itemize}
-  \item Classical WMC can represent any probability distribution by adding more
-    variables.
+  \item (Classical) WMC can represent any probability distribution by adding
+    more variables.
   \item But this is not the right approach for WMC algorithms that support
@@
     \alert{$127$} times faster inference.
-  \item Could this idea be successfully applied to other applications of WMC or,
-    perhaps, other WMC algorithms?
+%  \item Could this idea be successfully applied to other applications of WMC or,
+%    perhaps, other WMC algorithms?
   \end{itemize}

### 2021-06-13 doc/SAT_long_talk/scatter1.tex
Started working on slides for SAT

% Created by tikzDevice version 0.12.3.1 on 2021-06-13 19:02:01
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,224.04);
\begin{scope}
\path[clip] (  0.00, 16.35) rectangle (303.53,207.69);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00, 16.35) rectangle (303.53,207.69);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 47.03) rectangle (195.67,202.19);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 47.03) rectangle (195.67,202.19);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 54.09) --
	(195.67, 54.09);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,107.30) --
	(195.67,107.30);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,160.52) --
	(195.67,160.52);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 47.56, 47.03) --
	( 47.56,202.19);

\path[draw=drawColor,line width= 0.1pt,line join=round] (100.78, 47.03) --
	(100.78,202.19);

\path[draw=drawColor,line width= 0.1pt,line join=round] (154.00, 47.03) --
	(154.00,202.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 80.69) --
	(195.67, 80.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,133.91) --
	(195.67,133.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,187.13) --
	(195.67,187.13);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.17, 47.03) --
	( 74.17,202.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.39, 47.03) --
	(127.39,202.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] (180.61, 47.03) --
	(180.61,202.19);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 91.57) -- (117.14, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 94.42) -- (117.14, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.69, 93.00) -- (117.73, 93.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.71, 90.98) -- (115.71, 95.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.63, 91.57) -- (118.48, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.63, 94.42) -- (118.48, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.04, 93.00) -- (119.07, 93.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.06, 90.98) -- (117.06, 95.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.83, 93.41) -- (116.68, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.83, 96.26) -- (116.68, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.24, 94.84) -- (117.27, 94.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.26, 92.82) -- (115.26, 96.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.63, 94.07) -- (119.48, 96.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.63, 96.92) -- (119.48, 94.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.04, 95.50) -- (120.08, 95.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.06, 93.48) -- (118.06, 97.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.77, 93.06) -- (118.62, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.77, 95.92) -- (118.62, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.18, 94.49) -- (119.21, 94.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.20, 92.47) -- (117.20, 96.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.41, 91.57) -- (117.26, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.41, 94.42) -- (117.26, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.82, 93.00) -- (117.85, 93.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.84, 90.98) -- (115.84, 95.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.48, 91.96) -- (113.34, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.48, 94.82) -- (113.34, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.89, 93.39) -- (113.93, 93.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.91, 91.37) -- (111.91, 95.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.90, 93.74) -- (117.75, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.90, 96.60) -- (117.75, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.31, 95.17) -- (118.35, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.33, 93.15) -- (116.33, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.86, 94.69) -- (116.72, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.86, 97.55) -- (116.72, 94.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.27, 96.12) -- (117.31, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.29, 94.10) -- (115.29, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.83, 91.17) -- (115.68, 94.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.83, 94.02) -- (115.68, 91.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.24, 92.59) -- (116.27, 92.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.26, 90.57) -- (114.26, 94.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.33, 92.34) -- (114.19, 95.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.33, 95.19) -- (114.19, 92.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.74, 93.77) -- (114.78, 93.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.76, 91.75) -- (112.76, 95.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.88, 91.96) -- (118.73, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.88, 94.82) -- (118.73, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.29, 93.39) -- (119.33, 93.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.31, 91.37) -- (117.31, 95.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 92.71) -- (117.14, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 95.56) -- (117.14, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.69, 94.13) -- (117.73, 94.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.71, 92.12) -- (115.71, 96.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.46, 91.96) -- (116.31, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.46, 94.82) -- (116.31, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.87, 93.39) -- (116.91, 93.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.89, 91.37) -- (114.89, 95.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.32, 93.74) -- (119.17, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.32, 96.60) -- (119.17, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.72, 95.17) -- (119.76, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.74, 93.15) -- (117.74, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.34, 92.71) -- (119.20, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.34, 95.56) -- (119.20, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.75, 94.13) -- (119.79, 94.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.77, 92.12) -- (117.77, 96.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.21, 97.15) -- (119.06,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.21,100.00) -- (119.06, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.62, 98.58) -- (119.65, 98.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.64, 96.56) -- (117.64,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.86, 95.57) -- (119.72, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.86, 98.43) -- (119.72, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.27, 97.00) -- (120.31, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.29, 94.98) -- (118.29, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.70, 94.39) -- (116.55, 97.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.70, 97.24) -- (116.55, 94.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.11, 95.81) -- (117.14, 95.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.12, 93.80) -- (115.12, 97.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.50, 94.99) -- (120.36, 97.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.50, 97.85) -- (120.36, 94.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.91, 96.42) -- (120.95, 96.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.93, 94.40) -- (118.93, 98.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 96.65) -- (117.14, 99.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 99.50) -- (117.14, 96.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.69, 98.07) -- (117.73, 98.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.71, 96.06) -- (115.71,100.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 93.74) -- (117.14, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28, 96.60) -- (117.14, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.69, 95.17) -- (117.73, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.71, 93.15) -- (115.71, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.09,108.64) -- (114.94,111.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.09,111.49) -- (114.94,108.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.50,110.06) -- (115.53,110.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.51,108.05) -- (113.51,112.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.76, 93.74) -- (116.62, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.76, 96.60) -- (116.62, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.17, 95.17) -- (117.21, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.19, 93.15) -- (115.19, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.29, 93.74) -- (116.14, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.29, 96.60) -- (116.14, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.70, 95.17) -- (116.73, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.72, 93.15) -- (114.72, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.21, 95.57) -- (119.06, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.21, 98.43) -- (119.06, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.62, 97.00) -- (119.65, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.64, 94.98) -- (117.64, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.01, 98.09) -- (119.87,100.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.01,100.95) -- (119.87, 98.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.42, 99.52) -- (120.46, 99.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.44, 97.50) -- (118.44,101.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.69, 94.69) -- (118.54, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.69, 97.55) -- (118.54, 94.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.10, 96.12) -- (119.13, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.11, 94.10) -- (117.11, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.01, 93.06) -- (115.86, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.01, 95.92) -- (115.86, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.42, 94.49) -- (116.45, 94.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.44, 92.47) -- (114.44, 96.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.31, 95.29) -- (117.17, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.31, 98.14) -- (117.17, 95.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.72, 96.71) -- (117.76, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.74, 94.70) -- (115.74, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.90, 93.06) -- (115.76, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.90, 95.92) -- (115.76, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.31, 94.49) -- (116.35, 94.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.33, 92.47) -- (114.33, 96.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.63, 97.39) -- (117.48,100.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.63,100.25) -- (117.48, 97.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.04, 98.82) -- (118.07, 98.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.05, 96.80) -- (116.05,100.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.86,106.33) -- (120.71,109.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.86,109.18) -- (120.71,106.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.27,107.76) -- (121.30,107.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.29,105.74) -- (119.29,109.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.06, 97.15) -- (116.91,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.06,100.00) -- (116.91, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.47, 98.58) -- (117.50, 98.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.49, 96.56) -- (115.49,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.73, 96.12) -- (116.58, 98.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.73, 98.98) -- (116.58, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.14, 97.55) -- (117.17, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.16, 95.53) -- (115.16, 99.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.49, 96.90) -- (118.34, 99.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.49, 99.76) -- (118.34, 96.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.90, 98.33) -- (118.93, 98.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.91, 96.31) -- (116.91,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.72, 98.54) -- (120.57,101.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.72,101.39) -- (120.57, 98.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.13, 99.97) -- (121.16, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.14, 97.95) -- (119.14,101.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.41, 95.29) -- (117.26, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.41, 98.14) -- (117.26, 95.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.82, 96.71) -- (117.85, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.84, 94.70) -- (115.84, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.42,103.00) -- (119.28,105.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.42,105.86) -- (119.28,103.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.83,104.43) -- (119.87,104.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.85,102.41) -- (117.85,106.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.13, 99.38) -- (118.98,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.13,102.23) -- (118.98, 99.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.54,100.81) -- (119.57,100.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.55, 98.79) -- (117.55,102.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.36, 97.63) -- (120.21,100.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.36,100.49) -- (120.21, 97.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.77, 99.06) -- (120.80, 99.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.79, 97.04) -- (118.79,101.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.99,107.19) -- (119.84,110.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.99,110.04) -- (119.84,107.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.40,108.61) -- (120.43,108.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.41,106.59) -- (118.41,110.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.17, 97.15) -- (130.02,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.17,100.00) -- (130.02, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.58, 98.58) -- (130.61, 98.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.59, 96.56) -- (128.59,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.53, 96.12) -- (117.39, 98.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.53, 98.98) -- (117.39, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.94, 97.55) -- (117.98, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.96, 95.53) -- (115.96, 99.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.25, 95.57) -- (116.11, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.25, 98.43) -- (116.11, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.66, 97.00) -- (116.70, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.68, 94.98) -- (114.68, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.90, 96.90) -- (122.76, 99.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.90, 99.76) -- (122.76, 96.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.31, 98.33) -- (123.35, 98.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.33, 96.31) -- (121.33,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.53, 96.90) -- (117.39, 99.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.53, 99.76) -- (117.39, 96.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.94, 98.33) -- (117.98, 98.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.96, 96.31) -- (115.96,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.40,100.16) -- (121.26,103.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.40,103.02) -- (121.26,100.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.81,101.59) -- (121.85,101.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.83, 99.57) -- (119.83,103.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.21,130.78) -- (131.07,133.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.21,133.63) -- (131.07,130.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.62,132.21) -- (131.66,132.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.64,130.19) -- (129.64,134.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.91,132.43) -- (129.77,135.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.91,135.28) -- (129.77,132.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.32,133.85) -- (130.36,133.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.34,131.84) -- (128.34,135.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.31,130.82) -- (125.16,133.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.31,133.67) -- (125.16,130.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.72,132.25) -- (125.75,132.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.74,130.23) -- (123.74,134.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.51,130.29) -- (129.37,133.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.51,133.14) -- (129.37,130.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.92,131.72) -- (129.96,131.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.94,129.70) -- (127.94,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.30,130.89) -- (133.16,133.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.30,133.74) -- (133.16,130.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.71,132.31) -- (133.75,132.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.73,130.30) -- (131.73,134.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.51,130.85) -- (133.36,133.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.51,133.70) -- (133.36,130.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.92,132.27) -- (133.95,132.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.93,130.26) -- (131.93,134.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.00,131.79) -- (125.85,134.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.00,134.65) -- (125.85,131.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.41,133.22) -- (126.45,133.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.43,131.20) -- (124.43,135.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.00,130.87) -- (126.85,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.00,133.73) -- (126.85,130.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.41,132.30) -- (127.45,132.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.43,130.28) -- (125.43,134.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.99,130.87) -- (126.84,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.99,133.73) -- (126.84,130.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.40,132.30) -- (127.43,132.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.41,130.28) -- (125.41,134.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.45,131.27) -- (126.31,134.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.45,134.12) -- (126.31,131.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.86,132.69) -- (126.90,132.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.88,130.68) -- (124.88,134.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.64,130.19) -- (124.49,133.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.64,133.04) -- (124.49,130.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.05,131.62) -- (125.08,131.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.07,129.60) -- (123.07,133.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.90,130.70) -- (131.75,133.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.90,133.55) -- (131.75,130.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.30,132.13) -- (132.34,132.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.32,130.11) -- (130.32,134.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.80,132.26) -- (133.65,135.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.80,135.12) -- (133.65,132.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.21,133.69) -- (134.24,133.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.23,131.67) -- (132.23,135.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.80,131.73) -- (131.65,134.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.80,134.59) -- (131.65,131.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.21,133.16) -- (132.24,133.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.22,131.14) -- (130.22,135.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.76,130.59) -- (128.62,133.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.76,133.45) -- (128.62,130.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.17,132.02) -- (129.21,132.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.19,130.00) -- (127.19,134.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.14,134.41) -- (129.99,137.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.14,137.26) -- (129.99,134.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.55,135.83) -- (130.58,135.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.56,133.82) -- (128.56,137.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.70,134.43) -- (131.55,137.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.70,137.28) -- (131.55,134.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.11,135.85) -- (132.14,135.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.12,133.84) -- (130.12,137.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.65,138.50) -- (125.51,141.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.65,141.35) -- (125.51,138.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.06,139.93) -- (126.10,139.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.08,137.91) -- (124.08,141.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.53,134.94) -- (128.38,137.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.53,137.80) -- (128.38,134.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.93,136.37) -- (128.97,136.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.95,134.35) -- (126.95,138.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.98,131.68) -- (129.83,134.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.98,134.54) -- (129.83,131.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.39,133.11) -- (130.42,133.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.41,131.09) -- (128.41,135.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.41,132.22) -- (133.26,135.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.41,135.07) -- (133.26,132.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.81,133.64) -- (133.85,133.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.83,131.62) -- (131.83,135.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.59,131.96) -- (128.44,134.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.59,134.82) -- (128.44,131.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.99,133.39) -- (129.03,133.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.01,131.37) -- (127.01,135.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.49,131.65) -- (128.34,134.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.49,134.50) -- (128.34,131.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.90,133.07) -- (128.93,133.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.92,131.05) -- (126.92,135.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.57,133.56) -- (128.43,136.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.57,136.42) -- (128.43,133.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.98,134.99) -- (129.02,134.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.00,132.97) -- (127.00,137.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.20,131.63) -- (129.06,134.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.20,134.49) -- (129.06,131.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.61,133.06) -- (129.65,133.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.63,131.04) -- (127.63,135.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.91,131.57) -- (125.76,134.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.91,134.42) -- (125.76,131.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.32,133.00) -- (126.36,133.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.34,130.98) -- (124.34,135.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.04,133.65) -- (126.90,136.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.04,136.50) -- (126.90,133.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.45,135.07) -- (127.49,135.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.47,133.06) -- (125.47,137.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.87,131.44) -- (133.72,134.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.87,134.30) -- (133.72,131.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.28,132.87) -- (134.31,132.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.30,130.85) -- (132.30,134.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.80,134.90) -- (129.65,137.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.80,137.75) -- (129.65,134.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.21,136.32) -- (130.24,136.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.22,134.30) -- (128.22,138.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.77,132.60) -- (129.62,135.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.77,135.45) -- (129.62,132.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.17,134.03) -- (130.21,134.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.19,132.01) -- (128.19,136.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.84,132.71) -- (132.69,135.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.84,135.57) -- (132.69,132.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.25,134.14) -- (133.29,134.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.27,132.12) -- (131.27,136.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.64,134.10) -- (132.49,136.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.64,136.95) -- (132.49,134.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.05,135.53) -- (133.09,135.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.07,133.51) -- (131.07,137.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.90,135.14) -- (131.75,137.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.90,137.99) -- (131.75,135.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.30,136.56) -- (132.34,136.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.32,134.55) -- (130.32,138.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.16,139.31) -- (131.02,142.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.16,142.16) -- (131.02,139.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.57,140.74) -- (131.61,140.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.59,138.72) -- (129.59,142.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.63,136.71) -- (133.48,139.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.63,139.56) -- (133.48,136.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.04,138.13) -- (134.08,138.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.06,136.11) -- (132.06,140.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.06,135.54) -- (132.92,138.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.06,138.40) -- (132.92,135.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.47,136.97) -- (133.51,136.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.49,134.95) -- (131.49,138.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.20,136.83) -- (132.06,139.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.20,139.68) -- (132.06,136.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.61,138.25) -- (132.65,138.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.63,136.23) -- (130.63,140.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.18,137.00) -- (131.04,139.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.18,139.85) -- (131.04,137.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.59,138.43) -- (131.63,138.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.61,136.41) -- (129.61,140.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.95,138.11) -- (132.80,140.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.95,140.96) -- (132.80,138.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.36,139.54) -- (133.39,139.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.38,137.52) -- (131.38,141.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.50,136.69) -- (128.36,139.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.50,139.54) -- (128.36,136.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.91,138.12) -- (128.95,138.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.93,136.10) -- (126.93,140.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.69,137.93) -- (128.55,140.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.69,140.78) -- (128.55,137.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.10,139.36) -- (129.14,139.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.12,137.34) -- (127.12,141.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.19,135.75) -- (130.04,138.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.19,138.61) -- (130.04,135.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.60,137.18) -- (130.63,137.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.61,135.16) -- (128.61,139.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.64,133.34) -- (126.49,136.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.64,136.19) -- (126.49,133.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.05,134.77) -- (127.08,134.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.07,132.75) -- (125.07,136.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.79,136.97) -- (132.65,139.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.79,139.82) -- (132.65,136.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.20,138.39) -- (133.24,138.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.22,136.38) -- (131.22,140.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.15,136.87) -- (132.01,139.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.15,139.72) -- (132.01,136.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.56,138.29) -- (132.60,138.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.58,136.27) -- (130.58,140.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.04,135.08) -- (131.89,137.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.04,137.93) -- (131.89,135.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.45,136.51) -- (132.48,136.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.46,134.49) -- (130.46,138.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.42,138.62) -- (131.27,141.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.42,141.47) -- (131.27,138.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.83,140.04) -- (131.86,140.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.85,138.02) -- (129.85,142.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.69,141.02) -- (133.54,143.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.69,143.88) -- (133.54,141.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.09,142.45) -- (134.13,142.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.11,140.43) -- (132.11,144.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,152.24) -- (137.63,155.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,155.10) -- (137.63,152.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.18,153.67) -- (138.22,153.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.20,151.65) -- (136.20,155.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.76,153.17) -- (137.61,156.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.76,156.02) -- (137.61,153.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.17,154.60) -- (138.20,154.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.19,152.58) -- (136.19,156.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.20,153.43) -- (139.06,156.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.20,156.28) -- (139.06,153.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.61,154.85) -- (139.65,154.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.63,152.83) -- (137.63,156.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.02,152.69) -- (138.87,155.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.02,155.54) -- (138.87,152.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.42,154.12) -- (139.46,154.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.44,152.10) -- (137.44,156.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.93,155.89) -- (137.78,158.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.93,158.75) -- (137.78,155.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.34,157.32) -- (138.37,157.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.36,155.30) -- (136.36,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.99,154.48) -- (138.84,157.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.99,157.33) -- (138.84,154.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.40,155.91) -- (139.44,155.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.42,153.89) -- (137.42,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.08,154.01) -- (134.93,156.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.08,156.87) -- (134.93,154.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.49,155.44) -- (135.52,155.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.51,153.42) -- (133.51,157.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.82,155.04) -- (133.68,157.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.82,157.89) -- (133.68,155.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.23,156.47) -- (134.27,156.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.25,154.45) -- (132.25,158.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.14,154.48) -- (134.99,157.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.14,157.33) -- (134.99,154.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.55,155.91) -- (135.59,155.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.57,153.89) -- (133.57,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.49,155.12) -- (137.34,157.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.49,157.97) -- (137.34,155.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.90,156.55) -- (137.94,156.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.92,154.53) -- (135.92,158.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.73,156.09) -- (137.59,158.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.73,158.94) -- (137.59,156.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.14,157.51) -- (138.18,157.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.16,155.49) -- (136.16,159.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,155.61) -- (140.24,158.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,158.47) -- (140.24,155.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.80,157.04) -- (140.83,157.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.81,155.02) -- (138.81,159.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.33,152.31) -- (138.18,155.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.33,155.16) -- (138.18,152.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.74,153.73) -- (138.77,153.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.75,151.72) -- (136.75,155.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.62,155.76) -- (140.48,158.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.62,158.61) -- (140.48,155.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.03,157.18) -- (141.07,157.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.05,155.17) -- (139.05,159.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.70,152.55) -- (135.55,155.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.70,155.41) -- (135.55,152.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.11,153.98) -- (136.14,153.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.12,151.96) -- (134.12,156.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.60,154.41) -- (139.45,157.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.60,157.27) -- (139.45,154.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.01,155.84) -- (140.05,155.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.03,153.82) -- (138.03,157.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.22,154.02) -- (138.08,156.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.22,156.88) -- (138.08,154.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.63,155.45) -- (138.67,155.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.65,153.43) -- (136.65,157.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.98,154.63) -- (140.84,157.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.98,157.49) -- (140.84,154.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.39,156.06) -- (141.43,156.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.41,154.04) -- (139.41,158.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.42,157.93) -- (141.28,160.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.42,160.78) -- (141.28,157.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.83,159.35) -- (141.87,159.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.85,157.34) -- (139.85,161.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.32,154.86) -- (140.18,157.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.32,157.71) -- (140.18,154.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.73,156.29) -- (140.77,156.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.75,154.27) -- (138.75,158.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.53,153.97) -- (138.38,156.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.53,156.82) -- (138.38,153.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.94,155.40) -- (138.97,155.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.95,153.38) -- (136.95,157.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.26,155.60) -- (140.12,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.26,158.45) -- (140.12,155.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.67,157.03) -- (140.71,157.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.69,155.01) -- (138.69,159.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.53,154.33) -- (135.39,157.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.53,157.19) -- (135.39,154.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.94,155.76) -- (135.98,155.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.96,153.74) -- (133.96,157.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.03,155.00) -- (136.88,157.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.03,157.86) -- (136.88,155.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.44,156.43) -- (137.47,156.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.46,154.41) -- (135.46,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.44,153.98) -- (134.30,156.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.44,156.83) -- (134.30,153.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.85,155.41) -- (134.89,155.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.87,153.39) -- (132.87,157.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.15,156.26) -- (136.00,159.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.15,159.11) -- (136.00,156.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.55,157.69) -- (136.59,157.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.57,155.67) -- (134.57,159.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.08,154.01) -- (135.94,156.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.08,156.86) -- (135.94,154.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.49,155.44) -- (136.53,155.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.51,153.42) -- (134.51,157.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.24,155.99) -- (138.09,158.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.24,158.85) -- (138.09,155.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.65,157.42) -- (138.68,157.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.67,155.40) -- (136.67,159.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,158.81) -- (139.54,161.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,161.66) -- (139.54,158.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.10,160.24) -- (140.13,160.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.11,158.22) -- (138.11,162.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.67,157.81) -- (139.53,160.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.67,160.67) -- (139.53,157.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.08,159.24) -- (140.12,159.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.10,157.22) -- (138.10,161.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.33,156.22) -- (138.18,159.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.33,159.07) -- (138.18,156.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.74,157.64) -- (138.77,157.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.75,155.63) -- (136.75,159.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.37,157.22) -- (139.23,160.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.37,160.07) -- (139.23,157.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.78,158.64) -- (139.82,158.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.80,156.63) -- (137.80,160.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.15,156.73) -- (138.00,159.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.15,159.58) -- (138.00,156.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.56,158.16) -- (138.59,158.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.57,156.14) -- (136.57,160.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.52,158.71) -- (139.37,161.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.52,161.56) -- (139.37,158.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.93,160.13) -- (139.96,160.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.94,158.12) -- (137.94,162.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.73,155.82) -- (139.58,158.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.73,158.68) -- (139.58,155.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.14,157.25) -- (140.17,157.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.16,155.23) -- (138.16,159.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.74,157.37) -- (140.59,160.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.74,160.23) -- (140.59,157.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.15,158.80) -- (141.18,158.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.17,156.78) -- (139.17,160.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.22,156.78) -- (138.08,159.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.22,159.64) -- (138.08,156.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.63,158.21) -- (138.67,158.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.65,156.19) -- (136.65,160.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.62,162.47) -- (142.47,165.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.62,165.32) -- (142.47,162.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.03,163.90) -- (143.06,163.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.04,161.88) -- (141.04,165.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.07,157.62) -- (139.92,160.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.07,160.47) -- (139.92,157.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.47,159.04) -- (140.51,159.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.49,157.03) -- (138.49,161.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.11,156.93) -- (133.96,159.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.11,159.78) -- (133.96,156.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.52,158.35) -- (134.55,158.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.53,156.34) -- (132.53,160.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.87,155.33) -- (134.73,158.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.87,158.18) -- (134.73,155.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.28,156.76) -- (135.32,156.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.30,154.74) -- (133.30,158.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.99,155.50) -- (135.84,158.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.99,158.36) -- (135.84,155.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.40,156.93) -- (136.43,156.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.42,154.91) -- (134.42,158.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.97,156.76) -- (136.82,159.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.97,159.61) -- (136.82,156.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.37,158.18) -- (137.41,158.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.39,156.16) -- (135.39,160.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.52,155.54) -- (141.37,158.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.52,158.39) -- (141.37,155.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.93,156.96) -- (141.97,156.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.95,154.95) -- (139.95,158.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.88,158.45) -- (141.74,161.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.88,161.30) -- (141.74,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.29,159.88) -- (142.33,159.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.31,157.86) -- (140.31,161.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.34,158.61) -- (144.20,161.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.34,161.46) -- (144.20,158.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.75,160.03) -- (144.79,160.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.77,158.02) -- (142.77,162.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.60,160.33) -- (137.45,163.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.60,163.19) -- (137.45,160.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.00,161.76) -- (138.04,161.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.02,159.74) -- (136.02,163.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.49,156.49) -- (140.34,159.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.49,159.35) -- (140.34,156.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.90,157.92) -- (140.93,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.91,155.90) -- (138.91,159.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.44,175.49) -- (151.29,178.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.44,178.34) -- (151.29,175.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.85,176.92) -- (151.88,176.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.86,174.90) -- (149.86,178.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.17,174.87) -- (150.02,177.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.17,177.72) -- (150.02,174.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.58,176.29) -- (150.61,176.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.60,174.28) -- (148.60,178.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.62,177.44) -- (151.48,180.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.62,180.30) -- (151.48,177.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.03,178.87) -- (152.07,178.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.05,176.85) -- (150.05,180.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.89,173.07) -- (149.74,175.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.89,175.92) -- (149.74,173.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.30,174.50) -- (150.33,174.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.31,172.48) -- (148.31,176.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.28,174.53) -- (150.14,177.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.28,177.39) -- (150.14,174.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.69,175.96) -- (150.73,175.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.71,173.94) -- (148.71,177.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.28,174.38) -- (150.14,177.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.28,177.24) -- (150.14,174.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.69,175.81) -- (150.73,175.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.71,173.79) -- (148.71,177.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.66,174.07) -- (144.51,176.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.66,176.92) -- (144.51,174.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.07,175.49) -- (145.10,175.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.08,173.48) -- (143.08,177.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.62,177.73) -- (149.48,180.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.62,180.58) -- (149.48,177.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.03,179.15) -- (150.07,179.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.05,177.14) -- (148.05,181.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.95,175.18) -- (146.80,178.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.95,178.04) -- (146.80,175.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.35,176.61) -- (147.39,176.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.37,174.59) -- (145.37,178.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.65,171.83) -- (143.50,174.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.65,174.68) -- (143.50,171.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.06,173.25) -- (144.09,173.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.07,171.24) -- (142.07,175.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.80,176.79) -- (144.65,179.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.80,179.64) -- (144.65,176.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.20,178.22) -- (145.24,178.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.22,176.20) -- (143.22,180.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.99,174.49) -- (148.84,177.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.99,177.35) -- (148.84,174.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.40,175.92) -- (149.44,175.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.42,173.90) -- (147.42,177.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.11,174.48) -- (152.96,177.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.11,177.33) -- (152.96,174.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.52,175.90) -- (153.55,175.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.53,173.89) -- (151.53,177.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.04,174.03) -- (151.89,176.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.04,176.88) -- (151.89,174.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.45,175.45) -- (152.48,175.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.46,173.44) -- (150.46,177.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.34,175.55) -- (152.19,178.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.34,178.40) -- (152.19,175.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.75,176.98) -- (152.78,176.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.77,174.96) -- (150.77,178.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.59,176.75) -- (148.44,179.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.59,179.60) -- (148.44,176.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.00,178.17) -- (149.03,178.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.01,176.16) -- (147.01,180.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.84,176.62) -- (153.70,179.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.84,179.47) -- (153.70,176.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.25,178.04) -- (154.29,178.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.27,176.03) -- (152.27,180.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.29,173.64) -- (152.14,176.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.29,176.50) -- (152.14,173.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.70,175.07) -- (152.73,175.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.72,173.05) -- (150.72,177.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.09,176.52) -- (149.94,179.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.09,179.37) -- (149.94,176.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.50,177.94) -- (150.53,177.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.51,175.93) -- (148.51,179.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.59,175.51) -- (152.44,178.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.59,178.36) -- (152.44,175.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.99,176.94) -- (153.03,176.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.01,174.92) -- (151.01,178.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.27,180.37) -- (153.12,183.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.27,183.22) -- (153.12,180.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.68,181.80) -- (153.71,181.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.70,179.78) -- (151.70,183.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.07,176.54) -- (151.93,179.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.07,179.39) -- (151.93,176.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.48,177.96) -- (152.52,177.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.50,175.95) -- (150.50,179.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.29,175.70) -- (149.14,178.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.29,178.56) -- (149.14,175.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.69,177.13) -- (149.73,177.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.71,175.11) -- (147.71,179.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.62,175.95) -- (144.48,178.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.62,178.81) -- (144.48,175.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.03,177.38) -- (145.07,177.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.05,175.36) -- (143.05,179.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.29,176.22) -- (145.15,179.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.29,179.08) -- (145.15,176.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.70,177.65) -- (145.74,177.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.72,175.63) -- (143.72,179.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.72,173.55) -- (145.58,176.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.72,176.40) -- (145.58,173.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.13,174.98) -- (146.17,174.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.15,172.96) -- (144.15,176.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.84,176.58) -- (145.69,179.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.84,179.44) -- (145.69,176.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.25,178.01) -- (146.28,178.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.26,175.99) -- (144.26,180.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.88,174.91) -- (150.73,177.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.88,177.77) -- (150.73,174.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.29,176.34) -- (151.32,176.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.31,174.32) -- (149.31,178.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.05,175.45) -- (151.90,178.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.05,178.31) -- (151.90,175.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.46,176.88) -- (152.49,176.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.47,174.86) -- (150.47,178.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.92,174.52) -- (150.78,177.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.92,177.37) -- (150.78,174.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.33,175.95) -- (151.37,175.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.35,173.93) -- (149.35,177.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.47,175.78) -- (149.33,178.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.47,178.63) -- (149.33,175.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.88,177.20) -- (149.92,177.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.90,175.19) -- (147.90,179.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.46,177.35) -- (149.32,180.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.46,180.21) -- (149.32,177.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.87,178.78) -- (149.91,178.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.89,176.76) -- (147.89,180.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.58,179.65) -- (152.43,182.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.58,182.50) -- (152.43,179.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.99,181.07) -- (153.02,181.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.00,179.06) -- (151.00,183.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.27,178.96) -- (153.13,181.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.27,181.81) -- (153.13,178.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.68,180.39) -- (153.72,180.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.70,178.37) -- (151.70,182.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.07,179.64) -- (151.92,182.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.07,182.49) -- (151.92,179.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.48,181.06) -- (152.51,181.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.49,179.05) -- (150.49,183.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.42,176.26) -- (151.27,179.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.42,179.11) -- (151.27,176.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.82,177.68) -- (151.86,177.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.84,175.67) -- (149.84,179.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.27,181.05) -- (152.13,183.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.27,183.90) -- (152.13,181.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.68,182.48) -- (152.72,182.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.70,180.46) -- (150.70,184.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.23,177.15) -- (153.09,180.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.23,180.00) -- (153.09,177.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.64,178.57) -- (153.68,178.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.66,176.56) -- (151.66,180.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.40,174.13) -- (144.26,176.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.40,176.98) -- (144.26,174.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.81,175.55) -- (144.85,175.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.83,173.54) -- (142.83,177.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.06,178.39) -- (142.91,181.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.06,181.24) -- (142.91,178.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.47,179.81) -- (143.50,179.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.49,177.80) -- (141.49,181.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.80,179.61) -- (143.65,182.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.80,182.47) -- (143.65,179.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.21,181.04) -- (144.24,181.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.23,179.02) -- (142.23,183.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.00,175.42) -- (145.85,178.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.00,178.27) -- (145.85,175.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.41,176.85) -- (146.45,176.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.43,174.83) -- (144.43,178.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.27,176.00) -- (147.12,178.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.27,178.86) -- (147.12,176.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.68,177.43) -- (147.71,177.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.69,175.41) -- (145.69,179.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.54,176.14) -- (151.39,178.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.54,178.99) -- (151.39,176.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.95,177.57) -- (151.98,177.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.97,175.55) -- (149.97,179.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.72,176.19) -- (151.57,179.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.72,179.04) -- (151.57,176.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.13,177.61) -- (152.16,177.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.14,175.60) -- (150.14,179.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.82,178.31) -- (150.67,181.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.82,181.16) -- (150.67,178.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.23,179.74) -- (151.27,179.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.25,177.72) -- (149.25,181.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.89,178.43) -- (149.74,181.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.89,181.29) -- (149.74,178.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.30,179.86) -- (150.33,179.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.31,177.84) -- (148.31,181.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.88,182.26) -- (152.74,185.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.88,185.11) -- (152.74,182.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.29,183.68) -- (153.33,183.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.31,181.66) -- (151.31,185.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.18,186.74) -- (156.03,189.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.18,189.60) -- (156.03,186.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.59,188.17) -- (156.63,188.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.61,186.15) -- (154.61,190.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.99,193.71) -- (155.84,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.99,196.56) -- (155.84,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.40,195.14) -- (156.43,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.41,193.12) -- (154.41,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.91,186.98) -- (155.76,189.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.91,189.83) -- (155.76,186.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.32,188.40) -- (156.35,188.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.33,186.39) -- (154.33,190.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.84,182.60) -- (156.69,185.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.84,185.45) -- (156.69,182.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.25,184.03) -- (157.28,184.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.26,182.01) -- (155.26,186.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.63,184.24) -- (157.48,187.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.63,187.09) -- (157.48,184.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.04,185.66) -- (158.07,185.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.06,183.65) -- (156.06,187.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.55,184.44) -- (157.41,187.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.55,187.30) -- (157.41,184.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.96,185.87) -- (158.00,185.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.98,183.85) -- (155.98,187.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.03,182.02) -- (146.88,184.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.03,184.88) -- (146.88,182.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.44,183.45) -- (147.47,183.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.45,181.43) -- (145.45,185.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.43,180.15) -- (155.28,183.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.43,183.01) -- (155.28,180.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.84,181.58) -- (155.87,181.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.85,179.56) -- (153.85,183.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.43,180.07) -- (146.28,182.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.43,182.92) -- (146.28,180.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.84,181.50) -- (146.87,181.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.85,179.48) -- (144.85,183.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.01,185.11) -- (146.86,187.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.01,187.96) -- (146.86,185.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.42,186.54) -- (147.45,186.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.44,184.52) -- (145.44,188.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.80,183.02) -- (147.66,185.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.80,185.87) -- (147.66,183.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.21,184.45) -- (148.25,184.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.23,182.43) -- (146.23,186.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.71,180.80) -- (155.56,183.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.71,183.66) -- (155.56,180.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.11,182.23) -- (156.15,182.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.13,180.21) -- (154.13,184.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.80,186.88) -- (155.65,189.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.80,189.73) -- (155.65,186.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.21,188.30) -- (156.24,188.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.22,186.29) -- (154.22,190.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.49,182.23) -- (154.34,185.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.49,185.08) -- (154.34,182.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.90,183.66) -- (154.93,183.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.92,181.64) -- (152.92,185.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.54,185.96) -- (154.40,188.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.54,188.82) -- (154.40,185.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.95,187.39) -- (154.99,187.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.97,185.37) -- (152.97,189.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.39,186.54) -- (156.25,189.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.39,189.39) -- (156.25,186.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.80,187.96) -- (156.84,187.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.82,185.94) -- (154.82,189.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.95,186.47) -- (159.80,189.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.95,189.32) -- (159.80,186.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.36,187.90) -- (160.39,187.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.37,185.88) -- (158.37,189.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.91,193.71) -- (158.76,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.91,196.56) -- (158.76,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.32,195.14) -- (159.35,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.33,193.12) -- (157.33,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.52,193.71) -- (159.38,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.52,196.56) -- (159.38,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.93,195.14) -- (159.97,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.95,193.12) -- (157.95,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.65,193.71) -- (158.50,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.65,196.56) -- (158.50,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.06,195.14) -- (159.10,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.08,193.12) -- (157.08,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.94,193.71) -- (161.79,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.94,196.56) -- (161.79,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.35,195.14) -- (162.39,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.37,193.12) -- (160.37,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.58,193.71) -- (158.43,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.58,196.56) -- (158.43,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.99,195.14) -- (159.02,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.00,193.12) -- (157.00,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.18,185.27) -- (148.04,188.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.18,188.12) -- (148.04,185.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.59,186.70) -- (148.63,186.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.61,184.68) -- (146.61,188.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.20,181.12) -- (149.06,183.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.20,183.97) -- (149.06,181.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.61,182.54) -- (149.65,182.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.63,180.53) -- (147.63,184.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.42,184.12) -- (147.28,186.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.42,186.97) -- (147.28,184.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.83,185.54) -- (147.87,185.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.85,183.52) -- (145.85,187.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.15,181.58) -- (148.00,184.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.15,184.43) -- (148.00,181.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.56,183.00) -- (148.59,183.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.58,180.99) -- (146.58,185.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.62,184.34) -- (149.48,187.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.62,187.19) -- (149.48,184.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.03,185.77) -- (150.07,185.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.05,183.75) -- (148.05,187.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.41,186.33) -- (161.26,189.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.41,189.18) -- (161.26,186.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.82,187.75) -- (161.85,187.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.84,185.74) -- (159.84,189.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.50,193.71) -- (157.35,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.50,196.56) -- (157.35,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.91,195.14) -- (157.94,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.93,193.12) -- (155.93,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.29,187.19) -- (158.14,190.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.29,190.04) -- (158.14,187.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.70,188.62) -- (158.73,188.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.72,186.60) -- (156.72,190.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.49,193.71) -- (156.34,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.49,196.56) -- (156.34,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.90,195.14) -- (156.93,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.92,193.12) -- (154.92,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.04,186.66) -- (159.90,189.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.04,189.51) -- (159.90,186.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.45,188.09) -- (160.49,188.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.47,186.07) -- (158.47,190.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.81,193.71) -- (160.66,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.81,196.56) -- (160.66,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.22,195.14) -- (161.25,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.24,193.12) -- (159.24,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.60,186.14) -- (166.45,189.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.60,189.00) -- (166.45,186.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.01,187.57) -- (167.04,187.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.03,185.55) -- (165.03,189.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.76,185.40) -- (164.62,188.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.76,188.25) -- (164.62,185.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.17,186.82) -- (165.21,186.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.19,184.80) -- (163.19,188.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.17,185.28) -- (164.02,188.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.17,188.13) -- (164.02,185.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.58,186.71) -- (164.61,186.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.59,184.69) -- (162.59,188.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.38,187.34) -- (162.24,190.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.38,190.19) -- (162.24,187.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.79,188.77) -- (162.83,188.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.81,186.75) -- (160.81,190.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.30,187.16) -- (166.15,190.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.30,190.01) -- (166.15,187.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.71,188.59) -- (166.74,188.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.72,186.57) -- (164.72,190.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.73,185.56) -- (148.59,188.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.73,188.42) -- (148.59,185.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.14,186.99) -- (149.18,186.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.16,184.97) -- (147.16,189.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.50,182.02) -- (151.35,184.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.50,184.87) -- (151.35,182.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.91,183.44) -- (151.94,183.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.93,181.43) -- (149.93,185.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.82,186.24) -- (149.68,189.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.82,189.10) -- (149.68,186.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.23,187.67) -- (150.27,187.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.25,185.65) -- (148.25,189.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.90,181.26) -- (149.75,184.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.90,184.11) -- (149.75,181.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.31,182.68) -- (150.35,182.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.33,180.66) -- (148.33,184.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.52,185.10) -- (149.38,187.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.52,187.95) -- (149.38,185.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.93,186.53) -- (149.97,186.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.95,184.51) -- (147.95,188.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.08,182.82) -- (156.94,185.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.08,185.67) -- (156.94,182.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.49,184.25) -- (157.53,184.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.51,182.23) -- (155.51,186.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.87,193.71) -- (158.72,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.87,196.56) -- (158.72,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.28,195.14) -- (159.31,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.30,193.12) -- (157.30,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.87,185.71) -- (156.72,188.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.87,188.56) -- (156.72,185.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.28,187.14) -- (157.31,187.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.29,185.12) -- (155.29,189.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.85,188.79) -- (161.70,191.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.85,191.64) -- (161.70,188.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.26,190.22) -- (162.29,190.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.28,188.20) -- (160.28,192.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.89,188.04) -- (156.75,190.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.89,190.89) -- (156.75,188.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.30,189.46) -- (157.34,189.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.32,187.45) -- (155.32,191.48);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (118.09, 99.18) --
	(120.94, 99.18) --
	(120.94,102.03) --
	(118.09,102.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.34,100.72) --
	(122.20,100.72) --
	(122.20,103.57) --
	(119.34,103.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.43,108.55) --
	(118.28,108.55) --
	(118.28,111.40) --
	(115.43,111.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.04, 97.15) --
	(119.89, 97.15) --
	(119.89,100.00) --
	(117.04,100.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.84, 98.97) --
	(120.69, 98.97) --
	(120.69,101.82) --
	(117.84,101.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.43,105.52) --
	(118.28,105.52) --
	(118.28,108.38) --
	(115.43,108.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.13, 99.78) --
	(118.98, 99.78) --
	(118.98,102.63) --
	(116.13,102.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.23, 96.90) --
	(118.08, 96.90) --
	(118.08, 99.76) --
	(115.23, 99.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.09, 96.90) --
	(116.94, 96.90) --
	(116.94, 99.76) --
	(114.09, 99.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.34, 98.75) --
	(119.20, 98.75) --
	(119.20,101.61) --
	(116.34,101.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.91,101.25) --
	(119.77,101.25) --
	(119.77,104.10) --
	(116.91,104.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.49, 99.18) --
	(118.34, 99.18) --
	(118.34,102.03) --
	(115.49,102.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.96,108.27) --
	(116.81,108.27) --
	(116.81,111.12) --
	(113.96,111.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.69, 99.78) --
	(122.54, 99.78) --
	(122.54,102.63) --
	(119.69,102.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.79, 99.38) --
	(119.64, 99.38) --
	(119.64,102.23) --
	(116.79,102.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.26, 98.75) --
	(120.11, 98.75) --
	(120.11,101.61) --
	(117.26,101.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.04,117.01) --
	(129.90,117.01) --
	(129.90,119.86) --
	(127.04,119.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.52,111.31) --
	(124.38,111.31) --
	(124.38,114.16) --
	(121.52,114.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.92,108.91) --
	(122.78,108.91) --
	(122.78,111.76) --
	(119.92,111.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.64,110.09) --
	(123.49,110.09) --
	(123.49,112.94) --
	(120.64,112.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.19,109.85) --
	(124.05,109.85) --
	(124.05,112.70) --
	(121.19,112.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.47,110.48) --
	(124.32,110.48) --
	(124.32,113.34) --
	(121.47,113.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.18,110.56) --
	(122.03,110.56) --
	(122.03,113.41) --
	(119.18,113.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.09,109.51) --
	(123.94,109.51) --
	(123.94,112.37) --
	(121.09,112.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.87,111.66) --
	(124.73,111.66) --
	(124.73,114.52) --
	(121.87,114.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.91,118.99) --
	(123.77,118.99) --
	(123.77,121.84) --
	(120.91,121.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.42,114.23) --
	(124.27,114.23) --
	(124.27,117.08) --
	(121.42,117.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.81,113.94) --
	(124.66,113.94) --
	(124.66,116.80) --
	(121.81,116.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.68,113.71) --
	(126.54,113.71) --
	(126.54,116.56) --
	(123.68,116.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.71,118.30) --
	(126.56,118.30) --
	(126.56,121.15) --
	(123.71,121.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.54,117.14) --
	(128.39,117.14) --
	(128.39,119.99) --
	(125.54,119.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.07,113.59) --
	(126.92,113.59) --
	(126.92,116.45) --
	(124.07,116.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.09,141.63) --
	(148.95,141.63) --
	(148.95,144.49) --
	(146.09,144.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.04,128.41) --
	(126.90,128.41) --
	(126.90,131.27) --
	(124.04,131.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.46,123.69) --
	(127.31,123.69) --
	(127.31,126.54) --
	(124.46,126.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.65,123.81) --
	(126.51,123.81) --
	(126.51,126.66) --
	(123.65,126.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.76,126.41) --
	(128.62,126.41) --
	(128.62,129.26) --
	(125.76,129.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.71,125.38) --
	(125.57,125.38) --
	(125.57,128.24) --
	(122.71,128.24) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.62,121.87) --
	(131.48,121.87) --
	(131.48,124.72) --
	(128.62,124.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.82,119.46) --
	(124.68,119.46) --
	(124.68,122.31) --
	(121.82,122.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.39,123.95) --
	(125.24,123.95) --
	(125.24,126.81) --
	(122.39,126.81) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.71,118.38) --
	(123.57,118.38) --
	(123.57,121.23) --
	(120.71,121.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.55,120.77) --
	(126.41,120.77) --
	(126.41,123.63) --
	(123.55,123.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.82,140.25) --
	(137.68,140.25) --
	(137.68,143.11) --
	(134.82,143.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.27,142.29) --
	(137.13,142.29) --
	(137.13,145.14) --
	(134.27,145.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.55,139.69) --
	(136.40,139.69) --
	(136.40,142.54) --
	(133.55,142.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.95,143.87) --
	(134.80,143.87) --
	(134.80,146.72) --
	(131.95,146.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.01,142.80) --
	(133.86,142.80) --
	(133.86,145.65) --
	(131.01,145.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.44,102.24) --
	(123.29,102.24) --
	(123.29,105.09) --
	(120.44,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.50, 99.97) --
	(120.36, 99.97) --
	(120.36,102.83) --
	(117.50,102.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.60, 99.78) --
	(117.45, 99.78) --
	(117.45,102.63) --
	(114.60,102.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.40,107.89) --
	(119.25,107.89) --
	(119.25,110.74) --
	(116.40,110.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.36,101.07) --
	(121.21,101.07) --
	(121.21,103.93) --
	(118.36,103.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.20, 99.97) --
	(121.06, 99.97) --
	(121.06,102.83) --
	(118.20,102.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.14,101.59) --
	(120.99,101.59) --
	(120.99,104.44) --
	(118.14,104.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.79,101.59) --
	(122.64,101.59) --
	(122.64,104.44) --
	(119.79,104.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.09, 99.58) --
	(120.94, 99.58) --
	(120.94,102.43) --
	(118.09,102.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.65,103.72) --
	(121.50,103.72) --
	(121.50,106.58) --
	(118.65,106.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.91,101.75) --
	(118.76,101.75) --
	(118.76,104.61) --
	(115.91,104.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.41,101.42) --
	(120.26,101.42) --
	(120.26,104.27) --
	(117.41,104.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.66,103.58) --
	(123.51,103.58) --
	(123.51,106.44) --
	(120.66,106.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.83,103.00) --
	(122.68,103.00) --
	(122.68,105.86) --
	(119.83,105.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.32,103.58) --
	(125.18,103.58) --
	(125.18,106.44) --
	(122.32,106.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.46,103.00) --
	(123.31,103.00) --
	(123.31,105.86) --
	(120.46,105.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.18,138.57) --
	(142.03,138.57) --
	(142.03,141.42) --
	(139.18,141.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.21,112.80) --
	(124.07,112.80) --
	(124.07,115.65) --
	(121.21,115.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.59,112.98) --
	(122.44,112.98) --
	(122.44,115.84) --
	(119.59,115.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.42,116.37) --
	(124.27,116.37) --
	(124.27,119.22) --
	(121.42,119.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.11,113.59) --
	(123.96,113.59) --
	(123.96,116.45) --
	(121.11,116.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.86,113.94) --
	(121.72,113.94) --
	(121.72,116.80) --
	(118.86,116.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.84,115.25) --
	(123.69,115.25) --
	(123.69,118.10) --
	(120.84,118.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.55,114.50) --
	(122.40,114.50) --
	(122.40,117.36) --
	(119.55,117.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.91,118.42) --
	(124.76,118.42) --
	(124.76,121.27) --
	(121.91,121.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.05,112.73) --
	(121.91,112.73) --
	(121.91,115.59) --
	(119.05,115.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.62,111.80) --
	(121.48,111.80) --
	(121.48,114.65) --
	(118.62,114.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.09,127.09) --
	(132.95,127.09) --
	(132.95,129.94) --
	(130.09,129.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.96,122.97) --
	(130.82,122.97) --
	(130.82,125.82) --
	(127.96,125.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.34,122.84) --
	(131.19,122.84) --
	(131.19,125.69) --
	(128.34,125.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.08,123.51) --
	(131.94,123.51) --
	(131.94,126.36) --
	(129.08,126.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.55,126.07) --
	(131.40,126.07) --
	(131.40,128.92) --
	(128.55,128.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.80,116.46) --
	(128.65,116.46) --
	(128.65,119.32) --
	(125.80,119.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.36,104.53) --
	(120.21,104.53) --
	(120.21,107.38) --
	(117.36,107.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.91,106.10) --
	(123.77,106.10) --
	(123.77,108.96) --
	(120.91,108.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.34,104.53) --
	(121.19,104.53) --
	(121.19,107.38) --
	(118.34,107.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.10,106.55) --
	(122.95,106.55) --
	(122.95,109.40) --
	(120.10,109.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.48,104.13) --
	(120.33,104.13) --
	(120.33,106.99) --
	(117.48,106.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.38,105.88) --
	(126.24,105.88) --
	(126.24,108.73) --
	(123.38,108.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.69,105.04) --
	(121.54,105.04) --
	(121.54,107.89) --
	(118.69,107.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.58,105.04) --
	(121.43,105.04) --
	(121.43,107.89) --
	(118.58,107.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.47,107.59) --
	(122.32,107.59) --
	(122.32,110.44) --
	(119.47,110.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.38,105.04) --
	(122.24,105.04) --
	(122.24,107.89) --
	(119.38,107.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.73,108.27) --
	(123.59,108.27) --
	(123.59,111.12) --
	(120.73,111.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.21,112.21) --
	(124.07,112.21) --
	(124.07,115.06) --
	(121.21,115.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.00,107.98) --
	(124.86,107.98) --
	(124.86,110.84) --
	(122.00,110.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.06,106.10) --
	(122.91,106.10) --
	(122.91,108.96) --
	(120.06,108.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.07,112.14) --
	(126.92,112.14) --
	(126.92,115.00) --
	(124.07,115.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.13,132.27) --
	(129.98,132.27) --
	(129.98,135.13) --
	(127.13,135.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.05,106.66) --
	(121.91,106.66) --
	(121.91,109.51) --
	(119.05,109.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.94,108.17) --
	(118.79,108.17) --
	(118.79,111.03) --
	(115.94,111.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.77,107.69) --
	(120.62,107.69) --
	(120.62,110.54) --
	(117.77,110.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.57,109.26) --
	(123.42,109.26) --
	(123.42,112.11) --
	(120.57,112.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.04,108.73) --
	(119.89,108.73) --
	(119.89,111.58) --
	(117.04,111.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.76,106.10) --
	(121.61,106.10) --
	(121.61,108.96) --
	(118.76,108.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.16,109.51) --
	(122.01,109.51) --
	(122.01,112.37) --
	(119.16,112.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.84,107.79) --
	(121.69,107.79) --
	(121.69,110.64) --
	(118.84,110.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.80,114.72) --
	(118.65,114.72) --
	(118.65,117.57) --
	(115.80,117.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.78,109.51) --
	(121.63,109.51) --
	(121.63,112.37) --
	(118.78,112.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.95,121.84) --
	(126.80,121.84) --
	(126.80,124.69) --
	(123.95,124.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.04,122.94) --
	(126.90,122.94) --
	(126.90,125.80) --
	(124.04,125.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.89,126.21) --
	(128.75,126.21) --
	(128.75,129.06) --
	(125.89,129.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.53,126.27) --
	(126.38,126.27) --
	(126.38,129.12) --
	(123.53,129.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.72,128.28) --
	(126.58,128.28) --
	(126.58,131.13) --
	(123.72,131.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.70,193.71) --
	(145.55,193.71) --
	(145.55,196.56) --
	(142.70,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.37,183.07) --
	(126.22,183.07) --
	(126.22,185.92) --
	(123.37,185.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.36,171.74) --
	(122.22,171.74) --
	(122.22,174.60) --
	(119.36,174.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.42,154.12) --
	(125.27,154.12) --
	(125.27,156.97) --
	(122.42,156.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.89,160.65) --
	(126.74,160.65) --
	(126.74,163.50) --
	(123.89,163.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.18,173.50) --
	(127.03,173.50) --
	(127.03,176.36) --
	(124.18,176.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.00,113.53) --
	(120.85,113.53) --
	(120.85,116.39) --
	(118.00,116.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.84,116.04) --
	(124.69,116.04) --
	(124.69,118.89) --
	(121.84,118.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.47,114.99) --
	(123.33,114.99) --
	(123.33,117.84) --
	(120.47,117.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.97,116.56) --
	(125.82,116.56) --
	(125.82,119.41) --
	(122.97,119.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.77,193.71) --
	(125.63,193.71) --
	(125.63,196.56) --
	(122.77,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.56,193.71) --
	(133.42,193.71) --
	(133.42,196.56) --
	(130.56,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.50,193.71) --
	(132.35,193.71) --
	(132.35,196.56) --
	(129.50,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.45,193.71) --
	(136.30,193.71) --
	(136.30,196.56) --
	(133.45,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.90,193.71) --
	(136.75,193.71) --
	(136.75,196.56) --
	(133.90,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.86,193.71) --
	(137.71,193.71) --
	(137.71,196.56) --
	(134.86,196.56) --
	cycle;
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.68, 86.83) -- (109.72, 86.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.70, 84.81) -- (107.70, 88.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.55, 82.80) -- (109.59, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.57, 80.78) -- (107.57, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (103.60, 81.80) -- (107.64, 81.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.62, 79.78) -- (105.62, 83.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.12, 83.73) -- (110.15, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.14, 81.71) -- (108.14, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.29, 83.73) -- (109.33, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.31, 81.71) -- (107.31, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.00, 84.58) -- (110.03, 84.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.01, 82.56) -- (108.01, 86.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (103.60, 82.80) -- (107.64, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.62, 80.78) -- (105.62, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.48, 83.73) -- (110.51, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.50, 81.71) -- (108.50, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.62, 83.73) -- (109.65, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.64, 81.71) -- (107.64, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.83, 83.73) -- (110.86, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.85, 81.71) -- (108.85, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.43, 82.80) -- (109.46, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.44, 80.78) -- (107.44, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.75, 82.80) -- (109.78, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.76, 80.78) -- (107.76, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.68, 83.73) -- (109.72, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.70, 81.71) -- (107.70, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.27, 81.80) -- (108.30, 81.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.28, 79.78) -- (106.28, 83.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.24, 83.73) -- (110.28, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.26, 81.71) -- (108.26, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.93, 84.58) -- (109.97, 84.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.95, 82.56) -- (107.95, 86.60);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,101.25) -- (137.62,104.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.77,104.10) -- (137.62,101.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.18,102.67) -- (138.21,102.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.20,100.66) -- (136.20,104.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.01,100.35) -- (119.87,103.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.01,103.20) -- (119.87,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.42,101.78) -- (120.46,101.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.44, 99.76) -- (118.44,103.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.15,100.16) -- (119.01,103.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.15,103.02) -- (119.01,100.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.56,101.59) -- (119.60,101.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.58, 99.57) -- (117.58,103.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.02,100.90) -- (118.87,103.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.02,103.75) -- (118.87,100.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.43,102.32) -- (119.46,102.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.45,100.31) -- (117.45,104.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.76,100.54) -- (119.61,103.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.76,103.39) -- (119.61,100.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.17,101.96) -- (120.20,101.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.19, 99.95) -- (118.19,103.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.86,101.07) -- (119.72,103.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.86,103.93) -- (119.72,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.27,102.50) -- (120.31,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.29,100.48) -- (118.29,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.69, 98.75) -- (117.54,101.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.69,101.61) -- (117.54, 98.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.10,100.18) -- (118.13,100.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.12, 98.16) -- (116.12,102.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.52, 99.38) -- (118.37,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.52,102.23) -- (118.37, 99.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.93,100.81) -- (118.96,100.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.94, 98.79) -- (116.94,102.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.38,100.72) -- (120.24,103.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.38,103.57) -- (120.24,100.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.79,102.14) -- (120.83,102.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.81,100.13) -- (118.81,104.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.43, 99.78) -- (118.28,102.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.43,102.63) -- (118.28, 99.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.84,101.20) -- (118.87,101.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.86, 99.19) -- (116.86,103.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.52, 99.97) -- (118.37,102.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.52,102.83) -- (118.37, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.93,101.40) -- (118.96,101.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.94, 99.38) -- (116.94,103.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.15,100.16) -- (119.01,103.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.15,103.02) -- (119.01,100.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.56,101.59) -- (119.60,101.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.58, 99.57) -- (117.58,103.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.71, 99.97) -- (118.57,102.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.71,102.83) -- (118.57, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.12,101.40) -- (119.16,101.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.14, 99.38) -- (117.14,103.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.57,100.35) -- (118.43,103.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.57,103.20) -- (118.43,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.98,101.78) -- (119.02,101.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.00, 99.76) -- (117.00,103.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.85,100.35) -- (118.71,103.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.85,103.20) -- (118.71,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.26,101.78) -- (119.30,101.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.28, 99.76) -- (117.28,103.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.47,100.54) -- (119.33,103.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.47,103.39) -- (119.33,100.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.88,101.96) -- (119.92,101.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.90, 99.95) -- (117.90,103.98);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,157.19) -- (190.63,157.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,155.18) -- (188.62,159.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,156.54) -- (190.63,156.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,154.52) -- (188.62,158.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,157.32) -- (190.63,157.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,155.30) -- (188.62,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,158.13) -- (190.63,158.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,156.11) -- (188.62,160.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,158.10) -- (190.63,158.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,156.09) -- (188.62,160.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,158.54) -- (190.63,158.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,156.53) -- (188.62,160.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,157.92) -- (190.63,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,155.90) -- (188.62,159.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,158.07) -- (190.63,158.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,156.05) -- (188.62,160.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (175.14,158.28) -- (179.18,158.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.16,156.26) -- (177.16,160.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,156.44) -- (190.63,156.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,154.42) -- (188.62,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,156.06) -- (190.63,156.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,154.04) -- (188.62,158.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,157.17) -- (190.63,157.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,155.15) -- (188.62,159.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.98,157.55) -- (181.01,157.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.00,155.53) -- (179.00,159.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.50,159.16) -- (176.54,159.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.52,157.14) -- (174.52,161.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.91,159.34) -- (176.95,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.93,157.33) -- (174.93,161.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (174.33,159.31) -- (178.37,159.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (176.35,157.29) -- (176.35,161.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.68, 96.12) -- (112.72, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.70, 94.10) -- (110.70, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 96.71) -- (190.63, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 94.70) -- (188.62, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 97.28) -- (190.63, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 95.26) -- (188.62, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 97.28) -- (190.63, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 95.26) -- (188.62, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 97.82) -- (190.63, 97.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 95.80) -- (188.62, 99.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 97.28) -- (190.63, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 95.26) -- (188.62, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.30, 97.00) -- (113.34, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.32, 94.98) -- (111.32, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.08, 97.28) -- (112.12, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.10, 95.26) -- (110.10, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.20, 98.82) -- (114.23, 98.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.21, 96.80) -- (112.21,100.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.53, 96.12) -- (113.57, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.55, 94.10) -- (111.55, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 97.28) -- (112.82, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.80, 95.26) -- (110.80, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.89, 96.71) -- (113.93, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.91, 94.70) -- (111.91, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.41, 97.28) -- (114.45, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.43, 95.26) -- (112.43, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.73, 97.28) -- (112.77, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.75, 95.26) -- (110.75, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.49, 97.82) -- (112.52, 97.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.50, 95.80) -- (110.50, 99.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.68, 96.42) -- (112.72, 96.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.70, 94.40) -- (110.70, 98.44);

\path[fill=fillColor,fill opacity=0.50] (119.79, 99.58) --
	(122.64, 99.58) --
	(122.64,102.43) --
	(119.79,102.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.67,101.25) --
	(120.52,101.25) --
	(120.52,104.10) --
	(117.67,104.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.99,100.16) --
	(118.84,100.16) --
	(118.84,103.02) --
	(115.99,103.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.37,101.42) --
	(119.22,101.42) --
	(119.22,104.27) --
	(116.37,104.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.41,101.07) --
	(120.26,101.07) --
	(120.26,103.93) --
	(117.41,103.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.50,101.07) --
	(120.36,101.07) --
	(120.36,103.93) --
	(117.50,103.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.24,101.59) --
	(120.09,101.59) --
	(120.09,104.44) --
	(117.24,104.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.21,102.24) --
	(119.06,102.24) --
	(119.06,105.09) --
	(116.21,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.50,102.24) --
	(119.35,102.24) --
	(119.35,105.09) --
	(116.50,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.29, 99.58) --
	(119.14, 99.58) --
	(119.14,102.43) --
	(116.29,102.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.46,101.25) --
	(118.31,101.25) --
	(118.31,104.10) --
	(115.46,104.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.24,102.08) --
	(120.09,102.08) --
	(120.09,104.93) --
	(117.24,104.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.19, 99.97) --
	(120.04, 99.97) --
	(120.04,102.83) --
	(117.19,102.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.84,102.55) --
	(120.69,102.55) --
	(120.69,105.40) --
	(117.84,105.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.04,102.24) --
	(119.89,102.24) --
	(119.89,105.09) --
	(117.04,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.67,102.40) --
	(120.52,102.40) --
	(120.52,105.25) --
	(117.67,105.25) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.21,175.48) -- (152.25,175.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.23,173.47) -- (150.23,177.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.25,174.94) -- (149.29,174.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.27,172.92) -- (147.27,176.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.53,174.86) -- (155.57,174.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.55,172.84) -- (153.55,176.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.19,174.16) -- (150.23,174.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.21,172.15) -- (148.21,176.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.12,174.04) -- (151.15,174.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.14,172.02) -- (149.14,176.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.51,173.64) -- (149.54,173.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.53,171.63) -- (147.53,175.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.32,174.82) -- (142.36,174.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.34,172.80) -- (140.34,176.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.39) -- (190.63,175.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.37) -- (188.62,177.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,174.39) -- (190.63,174.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,172.37) -- (188.62,176.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.81,174.16) -- (121.85,174.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.83,172.15) -- (119.83,176.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.29,174.72) -- (119.33,174.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.31,172.70) -- (117.31,176.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.42,173.83) -- (165.46,173.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.44,171.81) -- (163.44,175.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.32,173.77) -- (170.35,173.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.33,171.75) -- (168.33,175.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.45,174.85) -- (170.49,174.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.47,172.83) -- (168.47,176.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.08,172.88) -- (167.12,172.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.10,170.87) -- (165.10,174.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.71,175.10) -- (154.74,175.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.73,173.08) -- (152.73,177.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.88,147.82) -- (165.92,147.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.90,145.80) -- (163.90,149.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.07,123.69) -- (118.10,123.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.08,121.67) -- (116.08,125.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.53,113.02) -- (117.57,113.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.55,111.00) -- (115.55,115.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.80,112.29) -- (116.84,112.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.82,110.27) -- (114.82,114.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.30,120.19) -- (115.34,120.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.32,118.17) -- (113.32,122.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.56,114.90) -- (117.60,114.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.58,112.88) -- (115.58,116.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.99,124.21) -- (120.02,124.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.01,122.19) -- (118.01,126.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,117.51) -- (190.63,117.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,115.50) -- (188.62,119.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.84,110.42) -- (115.87,110.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.85,108.41) -- (113.85,112.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.01,113.02) -- (118.04,113.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.02,111.00) -- (116.02,115.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.96,131.87) -- (120.00,131.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.98,129.85) -- (117.98,133.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.35,147.26) -- (138.39,147.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.37,145.24) -- (136.37,149.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.02,159.25) -- (166.06,159.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.04,157.23) -- (164.04,161.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.20,158.47) -- (167.24,158.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.22,156.46) -- (165.22,160.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.69,160.65) -- (166.72,160.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.70,158.63) -- (164.70,162.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.68,157.40) -- (165.71,157.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.70,155.38) -- (163.70,159.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.73,133.69) -- (155.76,133.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.75,131.67) -- (153.75,135.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.99,132.43) -- (133.03,132.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.01,130.42) -- (131.01,134.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.48,132.17) -- (125.51,132.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.50,130.15) -- (123.50,134.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.83,131.17) -- (125.86,131.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.85,129.15) -- (123.85,133.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.75,130.52) -- (123.79,130.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.77,128.51) -- (121.77,132.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.13,131.39) -- (125.17,131.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.15,129.37) -- (123.15,133.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.44,130.78) -- (122.48,130.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.46,128.77) -- (120.46,132.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.10,130.49) -- (123.13,130.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.11,128.48) -- (121.11,132.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.86,131.74) -- (124.90,131.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.88,129.73) -- (122.88,133.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.81,131.08) -- (122.85,131.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.83,129.07) -- (120.83,133.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.53,131.66) -- (123.56,131.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.54,129.64) -- (121.54,133.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,134.58) -- (190.63,134.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,132.57) -- (188.62,136.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,136.65) -- (190.63,136.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,134.64) -- (188.62,138.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,134.77) -- (190.63,134.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,132.75) -- (188.62,136.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,134.74) -- (190.63,134.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,132.72) -- (188.62,136.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,134.41) -- (190.63,134.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,132.39) -- (188.62,136.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.32,132.11) -- (156.35,132.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.34,130.10) -- (154.34,134.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.78,132.60) -- (124.81,132.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.79,130.59) -- (122.79,134.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.14,132.52) -- (126.17,132.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.16,130.51) -- (124.16,134.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.73,132.74) -- (127.77,132.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.75,130.73) -- (125.75,134.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.26,132.30) -- (126.30,132.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.28,130.28) -- (124.28,134.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.98,130.24) -- (128.02,130.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.00,128.22) -- (126.00,132.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.81,130.35) -- (136.85,130.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.83,128.34) -- (134.83,132.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.49,131.63) -- (125.53,131.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.51,129.61) -- (123.51,133.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.54,131.26) -- (123.58,131.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.56,129.24) -- (121.56,133.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.92,129.59) -- (121.96,129.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.94,127.57) -- (119.94,131.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.87,131.77) -- (123.90,131.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.88,129.75) -- (121.88,133.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.09,133.74) -- (161.12,133.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.11,131.72) -- (159.11,135.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.91,133.58) -- (153.94,133.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.93,131.56) -- (151.93,135.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.58,133.03) -- (155.62,133.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.60,131.02) -- (153.60,135.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.03,132.14) -- (143.06,132.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.04,130.12) -- (141.04,134.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.43,132.56) -- (160.46,132.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.45,130.55) -- (158.45,134.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.25,137.82) -- (157.28,137.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.26,135.81) -- (155.26,139.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.41,137.14) -- (126.45,137.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.43,135.12) -- (124.43,139.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.33,135.70) -- (130.37,135.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.35,133.68) -- (128.35,137.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.40,135.89) -- (127.43,135.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (125.41,133.87) -- (125.41,137.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.58,135.01) -- (131.62,135.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (129.60,132.99) -- (129.60,137.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.47,137.25) -- (126.50,137.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.49,135.23) -- (124.49,139.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.05,137.84) -- (161.08,137.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.06,135.82) -- (159.06,139.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,134.57) -- (190.63,134.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,132.56) -- (188.62,136.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.33,132.85) -- (123.37,132.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.35,130.83) -- (121.35,134.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.14,132.42) -- (124.18,132.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.16,130.40) -- (122.16,134.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,133.82) -- (190.63,133.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,131.80) -- (188.62,135.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,141.44) -- (190.63,141.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,139.43) -- (188.62,143.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,138.96) -- (190.63,138.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,136.94) -- (188.62,140.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,137.54) -- (190.63,137.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,135.52) -- (188.62,139.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,140.05) -- (190.63,140.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,138.03) -- (188.62,142.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,140.72) -- (190.63,140.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,138.70) -- (188.62,142.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.73,128.95) -- (123.77,128.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.75,126.93) -- (121.75,130.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.69,128.61) -- (115.72,128.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.70,126.59) -- (113.70,130.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.43,128.88) -- (118.47,128.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.45,126.86) -- (116.45,130.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.69,128.97) -- (115.72,128.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.70,126.95) -- (113.70,130.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.76,126.42) -- (115.80,126.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.78,124.40) -- (113.78,128.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.24,126.57) -- (114.28,126.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.26,124.56) -- (112.26,128.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.01,128.41) -- (121.04,128.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.03,126.39) -- (119.03,130.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.99,128.91) -- (120.02,128.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.01,126.90) -- (118.01,130.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.66,131.72) -- (114.70,131.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.68,129.70) -- (112.68,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.88,129.00) -- (119.92,129.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.90,126.99) -- (117.90,131.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.25,128.22) -- (122.29,128.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.27,126.20) -- (120.27,130.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.29,128.88) -- (119.33,128.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.31,126.86) -- (117.31,130.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.28,128.44) -- (118.32,128.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.30,126.42) -- (116.30,130.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.88,128.70) -- (119.92,128.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.90,126.68) -- (117.90,130.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.22,127.60) -- (118.25,127.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.24,125.58) -- (116.24,129.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.46,128.57) -- (119.49,128.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.47,126.55) -- (117.47,130.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.77,121.06) -- (134.80,121.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.78,119.05) -- (132.78,123.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,105.15) -- (190.63,105.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,103.13) -- (188.62,107.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.80,103.98) -- (115.83,103.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.82,101.96) -- (113.82,106.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 99.75) -- (190.63, 99.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 97.73) -- (188.62,101.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60, 99.97) -- (190.63, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 97.95) -- (188.62,101.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.34,105.96) -- (117.37,105.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.36,103.94) -- (115.36,107.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,100.18) -- (190.63,100.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 98.16) -- (188.62,102.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.38,100.60) -- (116.42,100.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.40, 98.58) -- (114.40,102.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,100.39) -- (190.63,100.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62, 98.38) -- (188.62,102.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.27,103.18) -- (117.31,103.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.29,101.16) -- (115.29,105.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.50, 99.52) -- (115.53, 99.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.51, 97.50) -- (113.51,101.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.56,107.98) -- (119.60,107.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.58,105.96) -- (117.58,109.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.59,107.30) -- (121.62,107.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.61,105.28) -- (119.61,109.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.17,108.19) -- (121.21,108.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.19,106.17) -- (119.19,110.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.01,100.18) -- (119.05,100.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.03, 98.16) -- (117.03,102.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.12,108.51) -- (122.16,108.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.14,106.49) -- (120.14,110.53);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.63, 87.84) rectangle (116.48, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.63, 87.84) -- (116.48, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.63, 90.69) -- (116.48, 87.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.72, 89.86) rectangle (115.58, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.72, 89.86) -- (115.58, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.72, 92.71) -- (115.58, 89.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.90, 88.89) rectangle (115.76, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.90, 88.89) -- (115.76, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.90, 91.75) -- (115.76, 88.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.04, 94.69) rectangle (115.90, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.04, 94.69) -- (115.90, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.04, 97.55) -- (115.90, 94.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.18, 88.38) rectangle (116.04, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.18, 88.38) -- (116.04, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.18, 91.23) -- (116.04, 88.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.25, 88.38) rectangle (116.11, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.25, 88.38) -- (116.11, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.25, 91.23) -- (116.11, 88.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.89, 87.84) rectangle (114.75, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.89, 87.84) -- (114.75, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.89, 90.69) -- (114.75, 87.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.09, 87.28) rectangle (114.94, 90.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.09, 87.28) -- (114.94, 90.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.09, 90.13) -- (114.94, 87.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.54, 88.38) rectangle (114.39, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.54, 88.38) -- (114.39, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.54, 91.23) -- (114.39, 88.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.17, 88.89) rectangle (114.02, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.17, 88.89) -- (114.02, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.17, 91.75) -- (114.02, 88.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.42, 89.38) rectangle (114.27, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.42, 89.38) -- (114.27, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.42, 92.24) -- (114.27, 89.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.97, 89.38) rectangle (115.83, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.97, 89.38) -- (115.83, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.97, 92.24) -- (115.83, 89.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.35, 91.57) rectangle (115.21, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.35, 91.57) -- (115.21, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.35, 94.42) -- (115.21, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.83, 90.31) rectangle (115.68, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.83, 90.31) -- (115.68, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.83, 93.16) -- (115.68, 90.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.72, 88.89) rectangle (115.58, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.72, 88.89) -- (115.58, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.72, 91.75) -- (115.58, 88.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.58, 90.31) rectangle (114.43, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.58, 90.31) -- (114.43, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.58, 93.16) -- (114.43, 90.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.58, 93.41) rectangle (114.43, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.58, 93.41) -- (114.43, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.58, 96.26) -- (114.43, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 93.41) rectangle (111.63, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 93.41) -- (111.63, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 96.26) -- (111.63, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.36, 94.07) rectangle (111.21, 96.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.36, 94.07) -- (111.21, 96.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.36, 96.92) -- (111.21, 94.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.80, 93.41) rectangle (112.66, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.80, 93.41) -- (112.66, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.80, 96.26) -- (112.66, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.31, 93.06) rectangle (111.16, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.31, 93.06) -- (111.16, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.31, 95.92) -- (111.16, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.76, 93.06) rectangle (110.61, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.76, 93.06) -- (110.61, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.76, 95.92) -- (110.61, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.03, 92.71) rectangle (111.88, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.03, 92.71) -- (111.88, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.03, 95.56) -- (111.88, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.66, 92.71) rectangle (113.51, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.66, 92.71) -- (113.51, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.66, 95.56) -- (113.51, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 91.57) rectangle (111.63, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 91.57) -- (111.63, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.78, 94.42) -- (111.63, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.31, 90.31) rectangle (113.16, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.31, 90.31) -- (113.16, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.31, 93.16) -- (113.16, 90.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.99, 92.71) rectangle (112.84, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.99, 92.71) -- (112.84, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.99, 95.56) -- (112.84, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.25, 93.41) rectangle (114.10, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.25, 93.41) -- (114.10, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.25, 96.26) -- (114.10, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.57, 92.71) rectangle (112.42, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.57, 92.71) -- (112.42, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.57, 95.56) -- (112.42, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.50,101.25) rectangle (114.35,104.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.50,101.25) -- (114.35,104.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.50,104.10) -- (114.35,101.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.22, 91.96) rectangle (113.07, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.22, 91.96) -- (113.07, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.22, 94.82) -- (113.07, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.13, 93.06) rectangle (113.98, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.13, 93.06) -- (113.98, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.13, 95.92) -- (113.98, 93.06);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.59,108.71) -- (116.63,108.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.61,106.70) -- (114.61,110.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.66,109.50) -- (117.70,109.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.68,107.49) -- (115.68,111.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.37,111.11) -- (117.41,111.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.39,109.09) -- (115.39,113.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.24,109.60) -- (117.27,109.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.26,107.58) -- (115.26,111.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.47,110.51) -- (117.50,110.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.49,108.49) -- (115.49,112.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.27,109.02) -- (117.31,109.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.29,107.00) -- (115.29,111.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (107.34,108.08) -- (111.37,108.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.35,106.07) -- (109.35,110.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.78,107.87) -- (114.82,107.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.80,105.85) -- (112.80,109.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.18,109.69) -- (115.22,109.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.20,107.68) -- (113.20,111.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (109.71,107.76) -- (113.75,107.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.73,105.74) -- (111.73,109.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.97,108.51) -- (113.01,108.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.99,106.49) -- (110.99,110.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.52,111.68) -- (116.56,111.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.54,109.66) -- (114.54,113.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (111.57,110.24) -- (115.61,110.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.59,108.23) -- (113.59,112.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.11,115.08) -- (117.14,115.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.12,113.06) -- (115.12,117.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.09,112.14) -- (116.13,112.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.11,110.12) -- (114.11,114.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (113.21,109.69) -- (117.24,109.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.22,107.68) -- (115.22,111.71);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.04, 79.27) rectangle (106.89, 82.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.04, 79.27) -- (106.89, 82.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.04, 82.12) -- (106.89, 79.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.61, 83.95) rectangle (115.47, 86.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.61, 83.95) -- (115.47, 86.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.61, 86.81) -- (115.47, 83.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.15, 99.38) rectangle (123.01,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.15, 99.38) -- (123.01,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.15,102.23) -- (123.01, 99.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.41,118.30) rectangle (129.27,121.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.41,118.30) -- (129.27,121.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.41,121.15) -- (129.27,118.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.37,131.42) rectangle (134.22,134.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.37,131.42) -- (134.22,134.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.37,134.27) -- (134.22,131.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.10,145.40) rectangle (140.95,148.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.10,145.40) -- (140.95,148.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.10,148.25) -- (140.95,145.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.67,155.04) rectangle (141.53,157.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.67,155.04) -- (141.53,157.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.67,157.89) -- (141.53,155.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.49,167.44) rectangle (149.34,170.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.49,167.44) -- (149.34,170.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.49,170.30) -- (149.34,167.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.24,177.50) rectangle (154.09,180.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.24,177.50) -- (154.09,180.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.24,180.35) -- (154.09,177.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.79,185.01) rectangle (157.65,187.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.79,185.01) -- (157.65,187.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.79,187.86) -- (157.65,185.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.87,186.06) rectangle (161.72,188.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.87,186.06) -- (161.72,188.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.87,188.91) -- (161.72,186.06);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (188.62,153.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,136.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,138.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,158.63) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,161.09) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,153.48) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,157.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,140.33) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,139.63) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,148.24) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,154.05) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,170.95) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,155.41) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,159.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,155.03) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,161.93) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,195.14) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,195.14) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,195.14) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,179.40) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,150.04) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,121.24) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,139.89) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,118.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,140.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,132.65) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,155.03) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,122.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,133.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,129.33) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.77, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.84, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (105.99, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.07, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.05, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.89, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.57, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.01, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.64, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.35, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.35, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.04, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.70, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.70, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.44, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.64, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.62, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.23, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.64, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.25, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.50, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.57, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.33, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.60, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.69, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.35, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.11, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.62, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.14, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.79, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.19, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.02, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.58, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (116.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.71, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.64, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.27, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.55, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.70, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.84, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.87, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.87, 95.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.46, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.57, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.01, 87.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.19, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.50, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.51, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (125.43, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.08, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.15, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.46, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.90, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.13, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.18, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.44, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.42, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.55, 91.74) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.14, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.64, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.12, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.26, 92.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.51, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.71, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.78, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.37, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.25, 94.84) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.26, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.57, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.31, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.70, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.02, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.28, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.10, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.68, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.82, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.57, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.83, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.35, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.24, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.43, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.05, 88.11) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.10, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.31, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.32, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.31, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.31, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.83, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.99, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.09, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.13, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.90, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (126.78, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.32, 95.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.57, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.90, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.44, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.14, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.13, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (105.99, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.15, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.44, 95.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.35, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.93, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.91, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.32,100.60) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.56, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.24, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.49, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.39, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.13, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.85, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.25, 91.74) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.30, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.58, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.57, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.25, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.84, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.83, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (152.51, 95.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.74, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.30, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.95, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.51, 90.32) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.40, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.50, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.30, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.45, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.02, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.51, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (146.97, 92.59) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.57, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.35, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.63, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.96, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.04, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.67, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.35, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.99, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.85, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.64, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.18, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.91, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.95, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (153.11, 99.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.00, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.15, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.57, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (131.57, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.92, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.23, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.30, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (141.74, 97.55) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.35, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.11, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.64, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.09, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.26, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.67, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.95, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (148.70, 99.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.71, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.33, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.75, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (157.47,103.34) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (155.98,114.29) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (121.56, 91.28) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.65, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (168.80,118.78) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (132.30, 98.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.16, 89.27) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (117.11, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (138.49, 97.55) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (141.72,101.59) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.40, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.57, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.51, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.91, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.05, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.14, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.31, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.68, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (123.88, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.25, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.19, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.55, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.71, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.02, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.12, 88.11) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.32, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.79, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.84, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.11, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.99, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.98, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.50, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.42, 93.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.28, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.05, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.46, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.79, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.90, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.95, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.61,105.01) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.25, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.99, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.73, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.72, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.89, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.19, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.19, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.02, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.01, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.76, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.44, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.56, 92.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.79, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.19, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.05, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.30, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.04, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.77, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.44, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.12, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.50, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.63, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.43, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (147.05, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.00, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.73, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.63, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (158.00,103.98) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.60, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.70, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.50, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.32, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.11, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.43, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.09, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (161.89,101.96) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.79, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (122.14, 87.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.31, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (141.84, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.99, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.25, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.64, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.25, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.45, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.08, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.25, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (150.14, 94.84) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.79, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.73, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.14, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.68, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.19, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.72, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.35, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.11, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.77, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.93, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.18, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.51, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.40, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (138.22, 97.55) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (171.13,116.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.84, 96.71) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.68, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (138.79, 98.07) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.79, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.00, 90.32) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.85, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,125.45) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (129.52, 96.42) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.92, 96.42) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.57, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (170.90,110.42) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (141.24, 97.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.50, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.67, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (170.80,110.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (134.38,113.02) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.89,100.60) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.30, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (148.35, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.12, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.11, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.91, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (142.78,115.25) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.03, 99.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.90, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.41, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (169.78,111.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (154.68,108.30) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.91, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.20, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.09, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.95, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.90, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.50, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.40, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.84, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.44, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.45, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.24, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.84, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (119.33, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.25, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.18, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.56, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.70, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.44, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.57, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.44, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (142.93, 89.27) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.73,100.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.89, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.64, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (115.84, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (110.25, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (105.92, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.44, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (165.82, 89.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.84, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.11, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (130.13, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.51, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.52, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.26, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (120.14, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.11, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.57, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.56, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (109.63, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.83, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.64, 83.73) circle (  1.43);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (110.50, 84.01) --
	(112.43, 80.69) --
	(108.58, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.11, 87.60) --
	(116.03, 84.27) --
	(112.19, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.41, 84.01) --
	(111.33, 80.69) --
	(107.49, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.93, 85.94) --
	(115.85, 82.62) --
	(112.01, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.18, 85.94) --
	(113.10, 82.62) --
	(109.26, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.01, 82.91) --
	(109.93, 79.58) --
	(106.09, 79.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.85, 82.91) --
	(110.77, 79.58) --
	(106.93, 79.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.00, 86.80) --
	(113.92, 83.47) --
	(110.08, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.05, 85.02) --
	(111.97, 81.69) --
	(108.13, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.43, 87.60) --
	(114.35, 84.27) --
	(110.51, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.54, 89.04) --
	(118.46, 85.72) --
	(114.62, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.80, 85.02) --
	(117.73, 81.69) --
	(113.88, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.54, 88.34) --
	(116.46, 85.02) --
	(112.62, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.94, 89.04) --
	(121.86, 85.72) --
	(118.02, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.47, 90.33) --
	(119.39, 87.00) --
	(115.55, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.47, 85.94) --
	(116.39, 82.62) --
	(112.55, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.36, 86.80) --
	(116.29, 83.47) --
	(112.44, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.36, 90.33) --
	(120.29, 87.00) --
	(116.44, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.80,101.28) --
	(118.72, 97.95) --
	(114.88, 97.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.45, 88.34) --
	(118.37, 85.02) --
	(114.53, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.67, 90.92) --
	(125.59, 87.59) --
	(121.75, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.11, 97.05) --
	(128.03, 93.73) --
	(124.18, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.40,103.23) --
	(126.32, 99.90) --
	(122.48, 99.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.22,110.93) --
	(125.14,107.61) --
	(121.30,107.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.91, 87.60) --
	(118.84, 84.27) --
	(114.99, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.59, 95.61) --
	(129.52, 92.28) --
	(125.67, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.67, 94.39) --
	(135.59, 91.06) --
	(131.75, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.56, 97.05) --
	(127.49, 93.73) --
	(123.64, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.11, 90.33) --
	(120.03, 87.00) --
	(116.19, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.49, 95.22) --
	(126.41, 91.89) --
	(122.57, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.65,100.55) --
	(141.57, 97.22) --
	(137.73, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.14,100.55) --
	(127.06, 97.22) --
	(123.22, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.19, 98.64) --
	(123.11, 95.31) --
	(119.27, 95.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.68,110.19) --
	(132.61,106.87) --
	(128.76,106.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.17, 89.04) --
	(123.09, 85.72) --
	(119.25, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.78, 99.22) --
	(139.70, 95.89) --
	(135.85, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.36,101.28) --
	(128.28, 97.95) --
	(124.44, 97.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.13,115.72) --
	(131.05,112.39) --
	(127.21,112.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.81,119.04) --
	(136.73,115.72) --
	(132.88,115.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.03,103.23) --
	(129.95, 99.90) --
	(126.11, 99.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.37,104.00) --
	(147.29,100.67) --
	(143.45,100.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.67,122.25) --
	(146.59,118.93) --
	(142.75,118.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.39,122.33) --
	(160.32,119.00) --
	(156.47,119.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.00,112.37) --
	(132.92,109.05) --
	(129.08,109.05) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.87,139.55) --
	(140.79,136.22) --
	(136.95,136.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (143.87,122.41) --
	(145.79,119.08) --
	(141.95,119.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.77,109.05) --
	(131.69,105.72) --
	(127.85,105.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.63, 97.39) --
	(127.55, 94.06) --
	(123.71, 94.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.13,110.41) --
	(133.05,107.08) --
	(129.21,107.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.89,111.91) --
	(138.81,108.59) --
	(134.97,108.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.65,124.86) --
	(160.57,121.53) --
	(156.73,121.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.87,121.46) --
	(156.79,118.13) --
	(152.95,118.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.21,109.64) --
	(152.13,106.31) --
	(148.29,106.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.67,130.07) --
	(144.60,126.74) --
	(140.75,126.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.84,103.02) --
	(153.76, 99.70) --
	(149.92, 99.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (157.52,122.85) --
	(159.44,119.53) --
	(155.60,119.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.84,114.66) --
	(135.76,111.33) --
	(131.92,111.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.20,124.42) --
	(152.13,121.09) --
	(148.28,121.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.32,124.70) --
	(146.25,121.37) --
	(142.40,121.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.31,127.18) --
	(133.23,123.85) --
	(129.39,123.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.82,147.84) --
	(175.74,144.51) --
	(171.90,144.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (164.19,127.21) --
	(166.12,123.88) --
	(162.27,123.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.57,120.78) --
	(156.49,117.45) --
	(152.65,117.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.22,118.31) --
	(137.14,114.98) --
	(133.30,114.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (165.00,127.79) --
	(166.92,124.46) --
	(163.07,124.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.09,126.16) --
	(156.01,122.83) --
	(152.17,122.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.66,123.80) --
	(156.58,120.47) --
	(152.74,120.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.94,124.92) --
	(157.86,121.59) --
	(154.02,121.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.74,117.53) --
	(156.66,114.20) --
	(152.82,114.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (157.78,130.40) --
	(159.70,127.07) --
	(155.86,127.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.37,124.03) --
	(163.29,120.70) --
	(159.45,120.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (181.10,131.27) --
	(183.03,127.95) --
	(179.18,127.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.77,134.92) --
	(173.69,131.60) --
	(169.85,131.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.78,124.23) --
	(165.70,120.90) --
	(161.86,120.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (174.86,146.39) --
	(176.78,143.07) --
	(172.94,143.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (180.90,137.19) --
	(182.82,133.86) --
	(178.97,133.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.44,131.54) --
	(163.36,128.21) --
	(159.52,128.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.01,139.34) --
	(152.93,136.01) --
	(149.09,136.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.61,119.69) --
	(169.54,116.36) --
	(165.69,116.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.07,132.01) --
	(146.99,128.68) --
	(143.15,128.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,144.76) --
	(190.54,141.43) --
	(186.69,141.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.48,140.30) --
	(172.40,136.97) --
	(168.56,136.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,147.36) --
	(190.54,144.03) --
	(186.69,144.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.05,135.59) --
	(180.97,132.26) --
	(177.12,132.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.93,153.77) --
	(175.85,150.45) --
	(172.01,150.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,162.28) --
	(190.54,158.96) --
	(186.69,158.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.63,135.72) --
	(158.55,132.39) --
	(154.71,132.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,146.84) --
	(190.54,143.51) --
	(186.69,143.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (177.89,137.16) --
	(179.81,133.83) --
	(175.97,133.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (178.74,126.85) --
	(180.67,123.52) --
	(176.82,123.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.40, 85.02) --
	(112.33, 81.69) --
	(108.48, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.14, 84.01) --
	(110.06, 80.69) --
	(106.21, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.60, 87.60) --
	(113.52, 84.27) --
	(109.68, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 84.01) --
	(190.54, 80.69) --
	(186.69, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.91, 90.33) --
	(113.83, 87.00) --
	(109.99, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.20, 84.01) --
	(110.12, 80.69) --
	(106.28, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.85, 87.60) --
	(112.77, 84.27) --
	(108.93, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.60, 86.80) --
	(112.53, 83.47) --
	(108.68, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.56, 85.02) --
	(110.48, 81.69) --
	(106.63, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.73, 85.02) --
	(113.65, 81.69) --
	(109.81, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.80, 88.34) --
	(114.72, 85.02) --
	(110.88, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.50, 85.94) --
	(110.42, 82.62) --
	(106.58, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.55, 88.34) --
	(114.47, 85.02) --
	(110.63, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.28, 90.92) --
	(113.20, 87.59) --
	(109.35, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.75, 88.34) --
	(112.67, 85.02) --
	(108.83, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.73, 85.02) --
	(111.65, 81.69) --
	(107.81, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.65, 87.60) --
	(112.57, 84.27) --
	(108.73, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.79, 85.94) --
	(110.71, 82.62) --
	(106.87, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.26, 87.60) --
	(114.18, 84.27) --
	(110.34, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.32, 88.34) --
	(113.24, 85.02) --
	(109.40, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.68, 86.80) --
	(111.60, 83.47) --
	(107.76, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.23, 88.34) --
	(113.15, 85.02) --
	(109.31, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.55, 86.80) --
	(113.47, 83.47) --
	(109.63, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.62, 89.70) --
	(118.55, 86.38) --
	(114.70, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.27, 90.33) --
	(118.19, 87.00) --
	(114.35, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.55, 90.92) --
	(115.47, 87.59) --
	(111.63, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.84, 93.50) --
	(114.76, 90.17) --
	(110.92, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.70,101.28) --
	(115.63, 97.95) --
	(111.78, 97.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.18, 92.02) --
	(118.10, 88.70) --
	(114.26, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.62, 95.99) --
	(118.55, 92.66) --
	(114.70, 92.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.02, 91.49) --
	(116.94, 88.16) --
	(113.10, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.11, 88.34) --
	(116.03, 85.02) --
	(112.19, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.34, 89.04) --
	(119.26, 85.72) --
	(115.41, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.09, 86.80) --
	(117.01, 83.47) --
	(113.17, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.42, 87.60) --
	(118.34, 84.27) --
	(114.50, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 91.49) --
	(190.54, 88.16) --
	(186.69, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.39, 89.04) --
	(117.31, 85.72) --
	(113.47, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.12, 93.50) --
	(117.05, 90.17) --
	(113.20, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.03, 90.92) --
	(121.95, 87.59) --
	(118.11, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.96, 90.92) --
	(116.88, 87.59) --
	(113.03, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.75, 89.70) --
	(116.67, 86.38) --
	(112.83, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.31, 90.33) --
	(119.23, 87.00) --
	(115.39, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.99, 92.02) --
	(121.91, 88.70) --
	(118.06, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.16, 97.71) --
	(120.08, 94.39) --
	(116.24, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.15, 92.54) --
	(125.07, 89.21) --
	(121.23, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.42, 89.04) --
	(118.34, 85.72) --
	(114.50, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.98, 93.03) --
	(120.90, 89.70) --
	(117.06, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.22, 92.54) --
	(117.14, 89.21) --
	(113.30, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.87, 97.05) --
	(119.80, 93.73) --
	(115.95, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.67, 92.54) --
	(124.60, 89.21) --
	(120.75, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.23, 92.54) --
	(119.15, 89.21) --
	(115.30, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.61, 93.50) --
	(119.53, 90.17) --
	(115.69, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.87, 95.61) --
	(119.80, 92.28) --
	(115.95, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.04, 95.22) --
	(129.96, 91.89) --
	(126.12, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.72, 90.33) --
	(116.64, 87.00) --
	(112.79, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.54, 89.70) --
	(116.46, 86.38) --
	(112.62, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.14, 93.50) --
	(121.07, 90.17) --
	(117.22, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.49, 94.39) --
	(123.41, 91.06) --
	(119.56, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.91, 93.50) --
	(125.83, 90.17) --
	(121.99, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.75, 98.93) --
	(123.67, 95.60) --
	(119.83, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.04,100.03) --
	(126.96, 96.71) --
	(123.12, 96.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.15, 95.61) --
	(123.07, 92.28) --
	(119.23, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.00,100.80) --
	(125.92, 97.47) --
	(122.08, 97.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.88, 98.03) --
	(134.81, 94.70) --
	(130.96, 94.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.65, 93.50) --
	(118.58, 90.17) --
	(114.73, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.87, 93.50) --
	(119.80, 90.17) --
	(115.95, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.37,108.17) --
	(123.29,104.85) --
	(119.45,104.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.31, 95.22) --
	(120.24, 91.89) --
	(116.39, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.59,103.42) --
	(128.51,100.10) --
	(124.67,100.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.58, 94.39) --
	(121.51, 91.06) --
	(117.66, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.16,114.59) --
	(133.08,111.26) --
	(129.24,111.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.66,108.17) --
	(129.58,104.85) --
	(125.74,104.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.17,102.18) --
	(144.10, 98.86) --
	(140.25, 98.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.86,106.50) --
	(123.79,103.17) --
	(119.94,103.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.05,100.55) --
	(122.97, 97.22) --
	(119.13, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.07, 95.22) --
	(121.00, 91.89) --
	(117.15, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.65,100.80) --
	(127.57, 97.47) --
	(123.72, 97.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.19,110.52) --
	(131.11,107.19) --
	(127.27,107.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.91,109.17) --
	(133.83,105.84) --
	(129.99,105.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.29, 95.22) --
	(126.21, 91.89) --
	(122.37, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.92,124.73) --
	(146.84,121.41) --
	(143.00,121.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.18,122.82) --
	(129.10,119.49) --
	(125.26,119.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.17,124.45) --
	(143.10,121.12) --
	(139.25,121.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.84, 96.71) --
	(126.76, 93.38) --
	(122.92, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.08, 98.03) --
	(146.01, 94.70) --
	(142.16, 94.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.19,104.72) --
	(129.11,101.39) --
	(125.27,101.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.53,107.51) --
	(126.45,104.18) --
	(122.61,104.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.58,102.40) --
	(137.50, 99.07) --
	(133.66, 99.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.82,103.81) --
	(131.74,100.48) --
	(127.90,100.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.75,110.30) --
	(130.67,106.97) --
	(126.83,106.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.30,110.30) --
	(134.22,106.97) --
	(130.38,106.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.62,101.74) --
	(136.54, 98.41) --
	(132.70, 98.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.29,127.79) --
	(132.22,124.46) --
	(128.37,124.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.31,110.83) --
	(136.23,107.50) --
	(132.39,107.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.13,108.04) --
	(126.05,104.72) --
	(122.20,104.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.19,108.04) --
	(140.11,104.72) --
	(136.27,104.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.40,131.40) --
	(142.32,128.07) --
	(138.48,128.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.30,125.48) --
	(140.23,122.15) --
	(136.38,122.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.90,117.06) --
	(140.82,113.73) --
	(136.98,113.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,126.46) --
	(190.54,123.13) --
	(186.69,123.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.73,122.25) --
	(153.65,118.93) --
	(149.81,118.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.50,122.10) --
	(137.42,118.77) --
	(133.58,118.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.60,133.11) --
	(155.52,129.78) --
	(151.68,129.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.11,130.03) --
	(140.04,126.70) --
	(136.19,126.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.93,142.14) --
	(153.85,138.81) --
	(150.01,138.81) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.48,121.42) --
	(153.40,118.09) --
	(149.56,118.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (162.23,134.31) --
	(164.15,130.98) --
	(160.31,130.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.65,123.28) --
	(149.57,119.95) --
	(145.73,119.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.12,118.63) --
	(142.04,115.30) --
	(138.20,115.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.47,118.42) --
	(136.39,115.09) --
	(132.55,115.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.74,121.66) --
	(132.67,118.34) --
	(128.82,118.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.92,125.45) --
	(139.84,122.13) --
	(136.00,122.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (141.34,114.44) --
	(143.26,111.11) --
	(139.42,111.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.15,137.77) --
	(154.07,134.45) --
	(150.23,134.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.30,124.45) --
	(175.22,121.12) --
	(171.38,121.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.98,132.82) --
	(158.90,129.49) --
	(155.06,129.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.89,120.65) --
	(138.81,117.32) --
	(134.97,117.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (164.71,145.01) --
	(166.63,141.68) --
	(162.79,141.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.66,129.07) --
	(156.58,125.74) --
	(152.74,125.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.85,113.33) --
	(135.77,110.00) --
	(131.93,110.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,143.05) --
	(190.54,139.72) --
	(186.69,139.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.20,159.10) --
	(175.12,155.77) --
	(171.28,155.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,115.02) --
	(190.54,111.70) --
	(186.69,111.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.18,132.20) --
	(156.10,128.88) --
	(152.26,128.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.82,126.54) --
	(144.74,123.21) --
	(140.89,123.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,156.09) --
	(190.54,152.76) --
	(186.69,152.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.92,157.29) --
	(146.85,153.96) --
	(143.00,153.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.27,120.52) --
	(160.19,117.19) --
	(156.35,117.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.61,129.55) --
	(134.53,126.22) --
	(130.69,126.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.79,116.75) --
	(154.71,113.43) --
	(150.87,113.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.82,122.06) --
	(161.74,118.73) --
	(157.90,118.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,154.01) --
	(190.54,150.68) --
	(186.69,150.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.41,128.48) --
	(149.33,125.16) --
	(145.49,125.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (178.88,138.18) --
	(180.80,134.85) --
	(176.96,134.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.84,127.60) --
	(136.76,124.27) --
	(132.91,124.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,158.89) --
	(190.54,155.56) --
	(186.69,155.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,168.92) --
	(190.54,165.60) --
	(186.69,165.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (169.70,144.80) --
	(171.62,141.47) --
	(167.78,141.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,168.96) --
	(190.54,165.63) --
	(186.69,165.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.71,137.56) --
	(141.63,134.23) --
	(137.79,134.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.82,135.72) --
	(151.74,132.39) --
	(147.90,132.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.31,151.91) --
	(153.23,148.58) --
	(149.39,148.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.90,157.32) --
	(161.83,153.99) --
	(157.98,153.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (177.37,154.24) --
	(179.29,150.91) --
	(175.45,150.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.13,135.52) --
	(161.06,132.20) --
	(157.21,132.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (173.04,152.77) --
	(174.96,149.44) --
	(171.12,149.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (176.98,165.16) --
	(178.90,161.83) --
	(175.06,161.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.25,125.54) --
	(155.17,122.21) --
	(151.33,122.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.35,139.83) --
	(181.27,136.50) --
	(177.43,136.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,149.10) --
	(190.54,145.77) --
	(186.69,145.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.52, 86.80) --
	(111.44, 83.47) --
	(107.60, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.79, 85.94) --
	(110.71, 82.62) --
	(106.87, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 85.94) --
	(190.54, 82.62) --
	(186.69, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.25, 93.03) --
	(112.17, 89.70) --
	(108.33, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.02, 85.94) --
	(110.94, 82.62) --
	(107.10, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.07, 85.94) --
	(110.00, 82.62) --
	(106.15, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 85.94) --
	(190.54, 82.62) --
	(186.69, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.78, 85.02) --
	(142.70, 81.69) --
	(138.86, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 85.94) --
	(190.54, 82.62) --
	(186.69, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.73, 85.94) --
	(110.65, 82.62) --
	(106.81, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.05, 87.60) --
	(111.97, 84.27) --
	(108.13, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.52, 86.80) --
	(111.44, 83.47) --
	(107.60, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.46, 86.80) --
	(111.38, 83.47) --
	(107.54, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.64, 94.81) --
	(113.56, 91.48) --
	(109.72, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.08, 99.22) --
	(111.00, 95.89) --
	(107.15, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.60, 86.80) --
	(112.53, 83.47) --
	(108.68, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.80, 86.80) --
	(112.72, 83.47) --
	(108.88, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.41, 86.80) --
	(111.33, 83.47) --
	(107.49, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.64, 87.60) --
	(113.56, 84.27) --
	(109.72, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 87.60) --
	(190.54, 84.27) --
	(186.69, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.46, 89.04) --
	(113.38, 85.72) --
	(109.54, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.70, 93.50) --
	(112.62, 90.17) --
	(108.78, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.09, 88.34) --
	(113.01, 85.02) --
	(109.17, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.75, 89.04) --
	(112.67, 85.72) --
	(108.83, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 87.60) --
	(190.54, 84.27) --
	(186.69, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.69, 90.92) --
	(113.61, 87.59) --
	(109.77, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.32, 88.34) --
	(113.24, 85.02) --
	(109.40, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.13, 89.04) --
	(113.06, 85.72) --
	(109.21, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.34, 89.04) --
	(114.26, 85.72) --
	(110.42, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.51, 87.60) --
	(113.43, 84.27) --
	(109.58, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.60, 88.34) --
	(114.52, 85.02) --
	(110.67, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.00, 92.02) --
	(114.92, 88.70) --
	(111.08, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.72, 89.70) --
	(114.64, 86.38) --
	(110.80, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.44, 89.70) --
	(115.36, 86.38) --
	(111.52, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.64, 89.04) --
	(113.56, 85.72) --
	(109.72, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.09, 89.04) --
	(114.01, 85.72) --
	(110.16, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.17, 90.33) --
	(114.09, 87.00) --
	(110.25, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.04, 92.02) --
	(114.96, 88.70) --
	(111.12, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.21, 92.02) --
	(114.14, 88.70) --
	(110.29, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 88.34) --
	(190.54, 85.02) --
	(186.69, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.65, 92.54) --
	(117.57, 89.21) --
	(113.72, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.11, 89.70) --
	(116.03, 86.38) --
	(112.19, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.60, 90.33) --
	(114.52, 87.00) --
	(110.67, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.84, 94.81) --
	(114.76, 91.48) --
	(110.92, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.89, 89.04) --
	(115.81, 85.72) --
	(111.97, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.72, 90.33) --
	(114.64, 87.00) --
	(110.80, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.78, 89.04) --
	(113.70, 85.72) --
	(109.86, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.28,100.80) --
	(115.20, 97.47) --
	(111.36, 97.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 89.04) --
	(190.54, 85.72) --
	(186.69, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.15, 89.04) --
	(116.07, 85.72) --
	(112.23, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.58, 98.93) --
	(117.50, 95.60) --
	(113.66, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.51, 90.33) --
	(115.44, 87.00) --
	(111.59, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 90.33) --
	(190.54, 87.00) --
	(186.69, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.97, 94.39) --
	(115.89, 91.06) --
	(112.04, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.04, 94.39) --
	(115.96, 91.06) --
	(112.12, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.21, 90.33) --
	(114.14, 87.00) --
	(110.29, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.70, 90.92) --
	(115.63, 87.59) --
	(111.78, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 91.49) --
	(190.54, 88.16) --
	(186.69, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.32, 90.33) --
	(115.24, 87.00) --
	(111.40, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.40, 91.49) --
	(116.32, 88.16) --
	(112.48, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.99, 91.49) --
	(117.91, 88.16) --
	(114.07, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.09, 92.02) --
	(117.01, 88.70) --
	(113.17, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.92, 90.92) --
	(116.84, 87.59) --
	(113.00, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.40,104.89) --
	(116.32,101.57) --
	(112.48,101.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.82, 93.50) --
	(113.74, 90.17) --
	(109.90, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.82, 92.02) --
	(115.74, 88.70) --
	(111.90, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.75, 91.49) --
	(116.67, 88.16) --
	(112.83, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.75, 92.02) --
	(116.67, 88.70) --
	(112.83, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.44, 91.49) --
	(115.36, 88.16) --
	(111.52, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.65, 91.49) --
	(116.57, 88.16) --
	(112.73, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.74, 93.03) --
	(118.66, 89.70) --
	(114.82, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.12, 93.03) --
	(118.04, 89.70) --
	(114.19, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.40, 93.50) --
	(116.32, 90.17) --
	(112.48, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 91.49) --
	(190.54, 88.16) --
	(186.69, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.45, 92.02) --
	(117.37, 88.70) --
	(113.53, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 93.03) --
	(190.54, 89.70) --
	(186.69, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.93, 92.54) --
	(115.85, 89.21) --
	(112.01, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.29, 92.54) --
	(117.21, 89.21) --
	(113.37, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.89, 93.50) --
	(116.81, 90.17) --
	(112.97, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 93.95) --
	(190.54, 90.63) --
	(186.69, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.32, 93.03) --
	(117.24, 89.70) --
	(113.40, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.87,100.55) --
	(117.79, 97.22) --
	(113.95, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.99,104.18) --
	(117.91,100.85) --
	(114.07,100.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.54, 93.03) --
	(118.46, 89.70) --
	(114.62, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.05, 93.95) --
	(117.98, 90.63) --
	(114.13, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.77, 94.39) --
	(118.69, 91.06) --
	(114.85, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.55, 93.03) --
	(117.47, 89.70) --
	(113.63, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.08, 93.03) --
	(119.01, 89.70) --
	(115.16, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.45, 93.95) --
	(118.37, 90.63) --
	(114.53, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.02, 93.95) --
	(117.94, 90.63) --
	(114.10, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.42, 94.81) --
	(118.34, 91.48) --
	(114.50, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.22, 95.22) --
	(121.14, 91.89) --
	(117.29, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.42, 94.81) --
	(119.34, 91.48) --
	(115.50, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.05, 94.39) --
	(117.98, 91.06) --
	(114.13, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 93.50) --
	(190.54, 90.17) --
	(186.69, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.89,102.61) --
	(118.81, 99.28) --
	(114.96, 99.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 93.50) --
	(190.54, 90.17) --
	(186.69, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.60, 94.81) --
	(118.52, 91.48) --
	(114.67, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 93.03) --
	(190.54, 89.70) --
	(186.69, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.24, 93.95) --
	(120.16, 90.63) --
	(116.32, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.55, 95.61) --
	(119.48, 92.28) --
	(115.63, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.03, 94.81) --
	(119.95, 91.48) --
	(116.11, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.42, 95.61) --
	(118.34, 92.28) --
	(114.50, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.55, 95.99) --
	(119.48, 92.66) --
	(115.63, 92.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.85, 94.39) --
	(119.77, 91.06) --
	(115.93, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.85, 96.35) --
	(121.78, 93.03) --
	(117.93, 93.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.45, 93.95) --
	(118.37, 90.63) --
	(114.53, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.89, 97.39) --
	(118.81, 94.06) --
	(114.96, 94.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 94.81) --
	(190.54, 91.48) --
	(186.69, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.22, 94.81) --
	(121.14, 91.48) --
	(117.29, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.11, 96.71) --
	(119.03, 93.38) --
	(115.19, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.82, 97.05) --
	(119.74, 93.73) --
	(115.90, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.53,106.04) --
	(126.45,102.71) --
	(122.61,102.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.19, 95.22) --
	(120.11, 91.89) --
	(116.27, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.77, 95.61) --
	(117.69, 92.28) --
	(113.85, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.17, 96.71) --
	(119.09, 93.38) --
	(115.25, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.36, 98.34) --
	(119.28, 95.01) --
	(115.44, 95.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.69, 95.99) --
	(120.61, 92.66) --
	(116.77, 92.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.23, 95.61) --
	(119.15, 92.28) --
	(115.30, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,100.55) --
	(190.54, 97.22) --
	(186.69, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 95.61) --
	(190.54, 92.28) --
	(186.69, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.20, 96.71) --
	(119.12, 93.38) --
	(115.28, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.24, 97.05) --
	(120.16, 93.73) --
	(116.32, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.56, 97.39) --
	(121.48, 94.06) --
	(117.64, 94.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.39,100.03) --
	(120.31, 96.71) --
	(116.47, 96.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.06, 97.71) --
	(119.98, 94.39) --
	(116.14, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 99.22) --
	(190.54, 95.89) --
	(186.69, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.34, 95.61) --
	(120.26, 92.28) --
	(116.42, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.64, 97.71) --
	(120.56, 94.39) --
	(116.72, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.17, 97.05) --
	(121.09, 93.73) --
	(117.25, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.83, 97.71) --
	(125.75, 94.39) --
	(121.91, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.44, 99.22) --
	(120.36, 95.89) --
	(116.52, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.98, 97.05) --
	(120.90, 93.73) --
	(117.06, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.81,100.55) --
	(120.73, 97.22) --
	(116.89, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.61, 99.22) --
	(122.53, 95.89) --
	(118.68, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.03,104.18) --
	(121.95,100.85) --
	(118.11,100.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.77, 97.71) --
	(122.69, 94.39) --
	(118.85, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.46,117.76) --
	(125.38,114.43) --
	(121.54,114.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.31,102.18) --
	(126.23, 98.86) --
	(122.39, 98.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.23,131.31) --
	(126.15,127.98) --
	(122.31,127.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 99.50) --
	(190.54, 96.17) --
	(186.69, 96.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.07,109.17) --
	(124.99,105.84) --
	(121.15,105.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 99.50) --
	(190.54, 96.17) --
	(186.69, 96.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.47,102.18) --
	(133.39, 98.86) --
	(129.55, 98.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.40,103.81) --
	(125.32,100.48) --
	(121.48,100.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.40,101.51) --
	(140.32, 98.18) --
	(136.48, 98.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.99,108.17) --
	(132.91,104.85) --
	(129.07,104.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62, 99.50) --
	(190.54, 96.17) --
	(186.69, 96.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.52,107.64) --
	(128.45,104.31) --
	(124.60,104.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,100.03) --
	(190.54, 96.71) --
	(186.69, 96.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.53,116.44) --
	(129.45,113.11) --
	(125.60,113.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.06,112.55) --
	(134.98,109.22) --
	(131.13,109.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.51,107.37) --
	(125.43,104.04) --
	(121.59,104.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.25,123.46) --
	(126.17,120.13) --
	(122.33,120.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.14,105.56) --
	(122.06,102.24) --
	(118.22,102.24) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.88,139.26) --
	(123.80,135.93) --
	(119.96,135.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.13,109.29) --
	(129.05,105.96) --
	(125.21,105.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.16,106.04) --
	(126.08,102.71) --
	(122.23,102.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.20,137.64) --
	(161.12,134.32) --
	(157.27,134.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.83,132.56) --
	(127.75,129.23) --
	(123.91,129.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.20,143.14) --
	(147.12,139.82) --
	(143.27,139.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.22,112.10) --
	(149.14,108.77) --
	(145.30,108.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.69,122.78) --
	(130.61,119.45) --
	(126.77,119.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.48,110.30) --
	(131.40,106.97) --
	(127.55,106.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.90,108.81) --
	(132.82,105.48) --
	(128.98,105.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.77,119.15) --
	(131.69,115.82) --
	(127.85,115.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.77,132.22) --
	(140.69,128.89) --
	(136.85,128.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.26,150.73) --
	(152.18,147.40) --
	(148.34,147.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,118.53) --
	(190.54,115.20) --
	(186.69,115.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.50,114.88) --
	(146.42,111.55) --
	(142.58,111.55) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.35,147.34) --
	(168.27,144.02) --
	(164.43,144.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.30,160.17) --
	(161.22,156.84) --
	(157.38,156.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.27,124.76) --
	(144.20,121.44) --
	(140.35,121.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (161.07,153.26) --
	(163.00,149.93) --
	(159.15,149.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.21,131.82) --
	(137.13,128.50) --
	(133.29,128.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.78,141.19) --
	(152.70,137.87) --
	(148.85,137.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (177.95,182.15) --
	(179.87,178.82) --
	(176.03,178.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,141.73) --
	(190.54,138.40) --
	(186.69,138.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (165.19,143.67) --
	(167.12,140.35) --
	(163.27,140.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.26,117.76) --
	(138.18,114.43) --
	(134.33,114.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.17,166.04) --
	(168.09,162.71) --
	(164.25,162.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,180.65) --
	(190.54,177.32) --
	(186.69,177.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.58,127.55) --
	(155.50,124.22) --
	(151.66,124.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (157.38,132.63) --
	(159.30,129.31) --
	(155.46,129.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.58,197.36) --
	(169.50,194.03) --
	(165.66,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.23,149.98) --
	(172.15,146.65) --
	(168.30,146.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (165.54,145.91) --
	(167.46,142.58) --
	(163.62,142.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (179.79,144.41) --
	(181.71,141.08) --
	(177.86,141.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,169.55) --
	(190.54,166.22) --
	(186.69,166.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.03,176.67) --
	(155.95,173.34) --
	(152.11,173.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,138.70) --
	(190.54,135.37) --
	(186.69,135.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,141.47) --
	(190.54,138.14) --
	(186.69,138.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.16,175.25) --
	(172.08,171.92) --
	(168.23,171.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (170.61,163.06) --
	(172.53,159.74) --
	(168.69,159.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,181.08) --
	(190.54,177.75) --
	(186.69,177.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,171.27) --
	(190.54,167.94) --
	(186.69,167.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (166.45,197.36) --
	(168.37,194.03) --
	(164.53,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,188.01) --
	(190.54,184.69) --
	(186.69,184.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,178.99) --
	(190.54,175.67) --
	(186.69,175.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.78,197.36) --
	(169.70,194.03) --
	(165.86,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,183.54) --
	(190.54,180.21) --
	(186.69,180.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.42,197.36) --
	(173.34,194.03) --
	(169.50,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,158.67) --
	(190.54,155.34) --
	(186.69,155.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.77,197.36) --
	(169.69,194.03) --
	(165.85,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.77, 94.39) rectangle (120.62, 97.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.77, 94.39) -- (120.62, 97.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.77, 97.24) -- (120.62, 94.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.12, 95.57) rectangle (122.97, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.12, 95.57) -- (122.97, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.12, 98.43) -- (122.97, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,150.84) rectangle (190.04,153.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,150.84) -- (190.04,153.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,153.70) -- (190.04,150.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.85,119.10) rectangle (126.70,121.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.85,119.10) -- (126.70,121.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (123.85,121.95) -- (126.70,119.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.45,161.49) rectangle (134.30,164.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.45,161.49) -- (134.30,164.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.45,164.34) -- (134.30,161.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,115.20) rectangle (190.04,118.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,115.20) -- (190.04,118.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,118.05) -- (190.04,115.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,122.49) rectangle (190.04,125.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,122.49) -- (190.04,125.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,125.34) -- (190.04,122.49);
\definecolor{drawColor}{RGB}{152,152,152}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 47.03) -- (195.67,202.19);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.66, 47.03) -- ( 41.66, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 43.44, 47.03) -- ( 43.44, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.98, 47.03) -- ( 44.98, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.35, 47.03) -- ( 46.35, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 47.56, 47.03) -- ( 47.56, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 55.57, 47.03) -- ( 55.57, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.26, 47.03) -- ( 60.26, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 63.58, 47.03) -- ( 63.58, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.16, 47.03) -- ( 66.16, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 68.27, 47.03) -- ( 68.27, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.05, 47.03) -- ( 70.05, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 71.59, 47.03) -- ( 71.59, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.95, 47.03) -- ( 72.95, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 74.17, 47.03) -- ( 74.17, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.18, 47.03) -- ( 82.18, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 86.87, 47.03) -- ( 86.87, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 90.19, 47.03) -- ( 90.19, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 92.77, 47.03) -- ( 92.77, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 94.88, 47.03) -- ( 94.88, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 96.66, 47.03) -- ( 96.66, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.20, 47.03) -- ( 98.20, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 99.56, 47.03) -- ( 99.56, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (100.78, 47.03) -- (100.78, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (108.79, 47.03) -- (108.79, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (113.48, 47.03) -- (113.48, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (116.80, 47.03) -- (116.80, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (119.38, 47.03) -- (119.38, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (121.49, 47.03) -- (121.49, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.27, 47.03) -- (123.27, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (124.81, 47.03) -- (124.81, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (126.17, 47.03) -- (126.17, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (127.39, 47.03) -- (127.39, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.40, 47.03) -- (135.40, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (140.08, 47.03) -- (140.08, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (143.41, 47.03) -- (143.41, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.99, 47.03) -- (145.99, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (148.09, 47.03) -- (148.09, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.87, 47.03) -- (149.87, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.42, 47.03) -- (151.42, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (152.78, 47.03) -- (152.78, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (154.00, 47.03) -- (154.00, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (162.01, 47.03) -- (162.01, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (166.69, 47.03) -- (166.69, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (170.02, 47.03) -- (170.02, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (172.60, 47.03) -- (172.60, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (174.70, 47.03) -- (174.70, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (176.48, 47.03) -- (176.48, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (178.03, 47.03) -- (178.03, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.39, 47.03) -- (179.39, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (180.61, 47.03) -- (180.61, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (188.62, 47.03) -- (188.62, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (193.30, 47.03) -- (193.30, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 48.18) -- ( 43.36, 48.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 49.96) -- ( 43.36, 49.96);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 51.51) -- ( 43.36, 51.51);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 52.87) -- ( 43.36, 52.87);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 54.09) -- ( 49.05, 54.09);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 62.10) -- ( 43.36, 62.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 66.78) -- ( 43.36, 66.78);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 70.11) -- ( 43.36, 70.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 72.68) -- ( 46.20, 72.68);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 74.79) -- ( 43.36, 74.79);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 76.57) -- ( 43.36, 76.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 78.12) -- ( 43.36, 78.12);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 79.48) -- ( 43.36, 79.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 80.69) -- ( 49.05, 80.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 88.70) -- ( 43.36, 88.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 93.39) -- ( 43.36, 93.39);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 96.71) -- ( 43.36, 96.71);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 99.29) -- ( 46.20, 99.29);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,101.40) -- ( 43.36,101.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,103.18) -- ( 43.36,103.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,104.72) -- ( 43.36,104.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,106.08) -- ( 43.36,106.08);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,107.30) -- ( 49.05,107.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,115.31) -- ( 43.36,115.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,120.00) -- ( 43.36,120.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,123.32) -- ( 43.36,123.32);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,125.90) -- ( 46.20,125.90);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,128.01) -- ( 43.36,128.01);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,129.79) -- ( 43.36,129.79);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,131.33) -- ( 43.36,131.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,132.69) -- ( 43.36,132.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,133.91) -- ( 49.05,133.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,141.92) -- ( 43.36,141.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,146.61) -- ( 43.36,146.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,149.93) -- ( 43.36,149.93);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,152.51) -- ( 46.20,152.51);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,154.62) -- ( 43.36,154.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,156.40) -- ( 43.36,156.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,157.94) -- ( 43.36,157.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,159.30) -- ( 43.36,159.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,160.52) -- ( 49.05,160.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,168.53) -- ( 43.36,168.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,173.21) -- ( 43.36,173.21);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,176.54) -- ( 43.36,176.54);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,179.12) -- ( 46.20,179.12);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,181.22) -- ( 43.36,181.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,183.01) -- ( 43.36,183.01);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,184.55) -- ( 43.36,184.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,185.91) -- ( 43.36,185.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,187.13) -- ( 49.05,187.13);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,195.14) -- ( 43.36,195.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,199.82) -- ( 43.36,199.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 47.03) rectangle (195.67,202.19);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 77.66) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,130.88) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,184.10) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 80.69) --
	( 40.51, 80.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,133.91) --
	( 40.51,133.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,187.13) --
	( 40.51,187.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.17, 44.28) --
	( 74.17, 47.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.39, 44.28) --
	(127.39, 47.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (180.61, 44.28) --
	(180.61, 47.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 74.17, 36.02) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.39, 36.02) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (180.61, 36.02) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (118.09, 23.99) {\textsf{Ace} + \texttt{cd06} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,124.61) {\textsf{DPMC} + \texttt{bklm16++} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (206.67, 68.14) rectangle (298.03,181.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,145.91) rectangle (226.62,160.37);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (219.39,153.14) circle (  1.43);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,131.46) rectangle (226.62,145.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (219.39,140.90) --
	(221.32,137.58) --
	(217.47,137.58) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,117.00) rectangle (226.62,131.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (217.97,122.80) --
	(220.82,122.80) --
	(220.82,125.66) --
	(217.97,125.66) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,102.55) rectangle (226.62,117.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.38,109.78) -- (221.41,109.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (219.39,107.76) -- (219.39,111.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17, 88.10) rectangle (226.62,102.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 93.90) rectangle (220.82, 96.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 93.90) -- (220.82, 96.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 96.75) -- (220.82, 93.90);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17, 73.64) rectangle (226.62, 88.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 79.44) -- (220.82, 82.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 82.30) -- (220.82, 79.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.38, 80.87) -- (221.41, 80.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (219.39, 78.85) -- (219.39, 82.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,150.11) {DQMR};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,135.65) {Grid};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,121.20) {Mastermind};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,106.75) {Non-binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12, 92.29) {Other binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12, 77.84) {Random Blocks};
\end{scope}
\end{tikzpicture}

### 2021-06-13 doc/SAT_long_talk/scatter2.tex
Started working on slides for SAT

% Created by tikzDevice version 0.12.3.1 on 2021-06-13 19:02:04
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,224.04);
\begin{scope}
\path[clip] (  0.00, 16.35) rectangle (303.53,207.69);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00, 16.35) rectangle (303.53,207.69);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 47.03) rectangle (195.67,202.19);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 47.03) rectangle (195.67,202.19);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 54.09) --
	(195.67, 54.09);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,107.30) --
	(195.67,107.30);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,160.52) --
	(195.67,160.52);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 47.56, 47.03) --
	( 47.56,202.19);

\path[draw=drawColor,line width= 0.1pt,line join=round] (100.78, 47.03) --
	(100.78,202.19);

\path[draw=drawColor,line width= 0.1pt,line join=round] (154.00, 47.03) --
	(154.00,202.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 80.69) --
	(195.67, 80.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,133.91) --
	(195.67,133.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,187.13) --
	(195.67,187.13);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.17, 47.03) --
	( 74.17,202.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.39, 47.03) --
	(127.39,202.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] (180.61, 47.03) --
	(180.61,202.19);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.06, 91.57) -- ( 95.91, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.06, 94.42) -- ( 95.91, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.47, 93.00) -- ( 96.50, 93.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.48, 90.98) -- ( 94.48, 95.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.38, 91.57) -- ( 93.23, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.38, 94.42) -- ( 93.23, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.79, 93.00) -- ( 93.82, 93.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.81, 90.98) -- ( 91.81, 95.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.38, 93.41) -- ( 93.23, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.38, 96.26) -- ( 93.23, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.79, 94.84) -- ( 93.82, 94.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.81, 92.82) -- ( 91.81, 96.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.87, 94.07) -- (103.72, 96.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.87, 96.92) -- (103.72, 94.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.28, 95.50) -- (104.31, 95.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.29, 93.48) -- (102.29, 97.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.65, 93.06) -- ( 95.51, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.65, 95.92) -- ( 95.51, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.06, 94.49) -- ( 96.10, 94.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.08, 92.47) -- ( 94.08, 96.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.63, 91.57) -- ( 93.48, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.63, 94.42) -- ( 93.48, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.04, 93.00) -- ( 94.07, 93.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.05, 90.98) -- ( 92.05, 95.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.87, 91.96) -- ( 93.72, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.87, 94.82) -- ( 93.72, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.28, 93.39) -- ( 94.32, 93.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.30, 91.37) -- ( 92.30, 95.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.57, 93.74) -- ( 94.43, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.57, 96.60) -- ( 94.43, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.98, 95.17) -- ( 95.02, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.00, 93.15) -- ( 93.00, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.23, 94.69) -- ( 95.09, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.23, 97.55) -- ( 95.09, 94.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.64, 96.12) -- ( 95.68, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 94.10) -- ( 93.66, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.80, 91.17) -- ( 94.65, 94.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.80, 94.02) -- ( 94.65, 91.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.21, 92.59) -- ( 95.24, 92.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.22, 90.57) -- ( 93.22, 94.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.44, 92.34) -- ( 95.30, 95.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.44, 95.19) -- ( 95.30, 92.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.85, 93.77) -- ( 95.89, 93.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.87, 91.75) -- ( 93.87, 95.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.11, 91.96) -- ( 93.96, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.11, 94.82) -- ( 93.96, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.52, 93.39) -- ( 94.55, 93.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.54, 91.37) -- ( 92.54, 95.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.80, 92.71) -- ( 94.65, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.80, 95.56) -- ( 94.65, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.21, 94.13) -- ( 95.24, 94.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.22, 92.12) -- ( 93.22, 96.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.13, 91.96) -- ( 92.98, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.13, 94.82) -- ( 92.98, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.53, 93.39) -- ( 93.57, 93.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.55, 91.37) -- ( 91.55, 95.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.26, 93.74) -- ( 96.11, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.26, 96.60) -- ( 96.11, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.66, 95.17) -- ( 96.70, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.68, 93.15) -- ( 94.68, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.83, 92.71) -- ( 96.68, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.83, 95.56) -- ( 96.68, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.24, 94.13) -- ( 97.27, 94.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.26, 92.12) -- ( 95.26, 96.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.72, 97.15) -- ( 98.57,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.72,100.00) -- ( 98.57, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.13, 98.58) -- ( 99.16, 98.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.14, 96.56) -- ( 97.14,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.23, 95.57) -- ( 98.08, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.23, 98.43) -- ( 98.08, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.64, 97.00) -- ( 98.68, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.66, 94.98) -- ( 96.66, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 94.39) -- ( 97.92, 97.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 97.24) -- ( 97.92, 94.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.47, 95.81) -- ( 98.51, 95.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.49, 93.80) -- ( 96.49, 97.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 94.99) -- ( 96.87, 97.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 97.85) -- ( 96.87, 94.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.42, 96.42) -- ( 97.46, 96.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.44, 94.40) -- ( 95.44, 98.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.06, 96.65) -- ( 99.91, 99.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.06, 99.50) -- ( 99.91, 96.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.47, 98.07) -- (100.50, 98.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.49, 96.06) -- ( 98.49,100.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 93.74) -- ( 96.30, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 96.60) -- ( 96.30, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.86, 95.17) -- ( 96.89, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.88, 93.15) -- ( 94.88, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.35,108.64) -- (103.20,111.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.35,111.49) -- (103.20,108.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.76,110.06) -- (103.79,110.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.78,108.05) -- (101.78,112.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.64, 93.74) -- ( 96.49, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.64, 96.60) -- ( 96.49, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.05, 95.17) -- ( 97.09, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 93.15) -- ( 95.07, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.20, 93.74) -- ( 97.05, 96.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.20, 96.60) -- ( 97.05, 93.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.60, 95.17) -- ( 97.64, 95.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.62, 93.15) -- ( 95.62, 97.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 95.57) -- ( 96.30, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 98.43) -- ( 96.30, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.86, 97.00) -- ( 96.89, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.88, 94.98) -- ( 94.88, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.26, 98.09) -- (101.12,100.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.26,100.95) -- (101.12, 98.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.67, 99.52) -- (101.71, 99.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.69, 97.50) -- ( 99.69,101.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.72, 94.69) -- ( 98.57, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.72, 97.55) -- ( 98.57, 94.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.13, 96.12) -- ( 99.16, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.14, 94.10) -- ( 97.14, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 93.06) -- ( 96.30, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 95.92) -- ( 96.30, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.86, 94.49) -- ( 96.89, 94.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.88, 92.47) -- ( 94.88, 96.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.48, 95.29) -- ( 99.34, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.48, 98.14) -- ( 99.34, 95.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.89, 96.71) -- ( 99.93, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.91, 94.70) -- ( 97.91, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.90, 93.06) -- ( 97.75, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.90, 95.92) -- ( 97.75, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.31, 94.49) -- ( 98.34, 94.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.32, 92.47) -- ( 96.32, 96.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.88, 97.39) -- (100.73,100.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.88,100.25) -- (100.73, 97.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.28, 98.82) -- (101.32, 98.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.30, 96.80) -- ( 99.30,100.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.00,106.33) -- (101.85,109.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.00,109.18) -- (101.85,106.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.41,107.76) -- (102.45,107.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.43,105.74) -- (100.43,109.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.88, 97.15) -- (100.73,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.88,100.00) -- (100.73, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.28, 98.58) -- (101.32, 98.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.30, 96.56) -- ( 99.30,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.33, 96.12) -- ( 99.19, 98.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.33, 98.98) -- ( 99.19, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.74, 97.55) -- ( 99.78, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.76, 95.53) -- ( 97.76, 99.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.74, 96.90) -- (100.60, 99.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.74, 99.76) -- (100.60, 96.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.15, 98.33) -- (101.19, 98.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.17, 96.31) -- ( 99.17,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.89, 98.54) -- (109.74,101.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.89,101.39) -- (109.74, 98.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.30, 99.97) -- (110.34, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.32, 97.95) -- (108.32,101.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.77, 95.29) -- ( 99.63, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.77, 98.14) -- ( 99.63, 95.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.18, 96.71) -- (100.22, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.20, 94.70) -- ( 98.20, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.81,103.00) -- (102.66,105.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.81,105.86) -- (102.66,103.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.22,104.43) -- (103.25,104.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.23,102.41) -- (101.23,106.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.81, 99.38) -- (102.66,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.81,102.23) -- (102.66, 99.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.22,100.81) -- (103.25,100.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.23, 98.79) -- (101.23,102.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.26, 97.63) -- (101.12,100.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.26,100.49) -- (101.12, 97.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.67, 99.06) -- (101.71, 99.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.69, 97.04) -- ( 99.69,101.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.12,107.19) -- (101.97,110.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.12,110.04) -- (101.97,107.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.53,108.61) -- (102.56,108.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.55,106.59) -- (100.55,110.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.14, 97.15) -- (107.99,100.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.14,100.00) -- (107.99, 97.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.55, 98.58) -- (108.58, 98.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.57, 96.56) -- (106.57,100.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.03, 96.12) -- ( 98.88, 98.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.03, 98.98) -- ( 98.88, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.44, 97.55) -- ( 99.47, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.46, 95.53) -- ( 97.46, 99.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.20, 95.57) -- (100.05, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.20, 98.43) -- (100.05, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.61, 97.00) -- (100.64, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.63, 94.98) -- ( 98.63, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.48, 96.90) -- (100.33, 99.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.48, 99.76) -- (100.33, 96.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.88, 98.33) -- (100.92, 98.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.90, 96.31) -- ( 98.90,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.06, 96.90) -- ( 99.91, 99.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 97.06, 99.76) -- ( 99.91, 96.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.47, 98.33) -- (100.50, 98.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.49, 96.31) -- ( 98.49,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,100.16) -- (104.31,103.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,103.02) -- (104.31,100.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.87,101.59) -- (104.90,101.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.89, 99.57) -- (102.89,103.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.52,130.78) -- (138.37,133.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.52,133.63) -- (138.37,130.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.93,132.21) -- (138.96,132.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.94,130.19) -- (136.94,134.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.78,132.43) -- (138.63,135.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.78,135.28) -- (138.63,132.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.19,133.85) -- (139.22,133.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.20,131.84) -- (137.20,135.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.97,130.82) -- (135.82,133.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.97,133.67) -- (135.82,130.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.38,132.25) -- (136.41,132.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.40,130.23) -- (134.40,134.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.11,130.29) -- (135.96,133.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.11,133.14) -- (135.96,130.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.52,131.72) -- (136.55,131.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.53,129.70) -- (134.53,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.41,130.89) -- (138.27,133.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.41,133.74) -- (138.27,130.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.82,132.31) -- (138.86,132.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.84,130.30) -- (136.84,134.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.45,130.85) -- (138.30,133.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.45,133.70) -- (138.30,130.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.86,132.27) -- (138.89,132.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.88,130.26) -- (136.88,134.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.75,131.79) -- (137.61,134.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.75,134.65) -- (137.61,131.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.16,133.22) -- (138.20,133.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.18,131.20) -- (136.18,135.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.88,130.87) -- (137.74,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.88,133.73) -- (137.74,130.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.29,132.30) -- (138.33,132.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.31,130.28) -- (136.31,134.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.39,130.87) -- (137.24,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.39,133.73) -- (137.24,130.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.79,132.30) -- (137.83,132.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.81,130.28) -- (135.81,134.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.42,131.27) -- (136.27,134.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.42,134.12) -- (136.27,131.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.83,132.69) -- (136.87,132.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.85,130.68) -- (134.85,134.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.73,130.19) -- (135.58,133.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.73,133.04) -- (135.58,130.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.14,131.62) -- (136.17,131.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.15,129.60) -- (134.15,133.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.14,130.70) -- (138.99,133.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.14,133.55) -- (138.99,130.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.55,132.13) -- (139.58,132.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.56,130.11) -- (137.56,134.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.97,132.26) -- (139.83,135.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.97,135.12) -- (139.83,132.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.38,133.69) -- (140.42,133.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.40,131.67) -- (138.40,135.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.84,131.73) -- (138.69,134.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.84,134.59) -- (138.69,131.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.25,133.16) -- (139.28,133.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.27,131.14) -- (137.27,135.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.75,130.59) -- (135.60,133.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.75,133.45) -- (135.60,130.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.16,132.02) -- (136.19,132.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.17,130.00) -- (134.17,134.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.21,134.41) -- (139.07,137.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.21,137.26) -- (139.07,134.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.62,135.83) -- (139.66,135.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.64,133.82) -- (137.64,137.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.57,134.43) -- (139.42,137.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.57,137.28) -- (139.42,134.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.98,135.85) -- (140.01,135.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.00,133.84) -- (138.00,137.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.43,138.50) -- (138.28,141.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.43,141.35) -- (138.28,138.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.84,139.93) -- (138.87,139.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.86,137.91) -- (136.86,141.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.42,134.94) -- (142.27,137.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.42,137.80) -- (142.27,134.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.83,136.37) -- (142.86,136.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.84,134.35) -- (140.84,138.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.47,131.68) -- (138.32,134.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.47,134.54) -- (138.32,131.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.87,133.11) -- (138.91,133.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.89,131.09) -- (136.89,135.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.81,132.22) -- (140.66,135.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.81,135.07) -- (140.66,132.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.22,133.64) -- (141.25,133.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.23,131.62) -- (139.23,135.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.73,131.96) -- (141.59,134.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.73,134.82) -- (141.59,131.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.14,133.39) -- (142.18,133.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.16,131.37) -- (140.16,135.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.08,131.65) -- (137.93,134.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.08,134.50) -- (137.93,131.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.49,133.07) -- (138.52,133.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.50,131.05) -- (136.50,135.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.34,133.56) -- (140.19,136.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.34,136.42) -- (140.19,133.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.75,134.99) -- (140.78,134.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.77,132.97) -- (138.77,137.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.26,131.63) -- (138.11,134.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.26,134.49) -- (138.11,131.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.67,133.06) -- (138.70,133.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.69,131.04) -- (136.69,135.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.71,131.57) -- (138.56,134.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.71,134.42) -- (138.56,131.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.12,133.00) -- (139.15,133.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.13,130.98) -- (137.13,135.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.33,133.65) -- (139.18,136.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.33,136.50) -- (139.18,133.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.74,135.07) -- (139.78,135.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.76,133.06) -- (137.76,137.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.67,131.44) -- (140.53,134.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.67,134.30) -- (140.53,131.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.08,132.87) -- (141.12,132.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.10,130.85) -- (139.10,134.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.45,134.90) -- (139.31,137.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.45,137.75) -- (139.31,134.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.86,136.32) -- (139.90,136.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.88,134.30) -- (137.88,138.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.34,132.60) -- (139.20,135.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.34,135.45) -- (139.20,132.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.75,134.03) -- (139.79,134.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.77,132.01) -- (137.77,136.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.49,132.71) -- (140.34,135.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.49,135.57) -- (140.34,132.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.90,134.14) -- (140.93,134.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.92,132.12) -- (138.92,136.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.37,134.10) -- (141.23,136.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.37,136.95) -- (141.23,134.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.78,135.53) -- (141.82,135.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.80,133.51) -- (139.80,137.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.33,135.14) -- (142.18,137.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.33,137.99) -- (142.18,135.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.74,136.56) -- (142.77,136.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.75,134.55) -- (140.75,138.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.59,139.31) -- (142.44,142.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.59,142.16) -- (142.44,139.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.00,140.74) -- (143.03,140.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.02,138.72) -- (141.02,142.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.35,136.71) -- (142.21,139.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.35,139.56) -- (142.21,136.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.76,138.13) -- (142.80,138.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.78,136.11) -- (140.78,140.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.76,135.54) -- (143.62,138.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.76,138.40) -- (143.62,135.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.17,136.97) -- (144.21,136.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.19,134.95) -- (142.19,138.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.71,136.83) -- (141.57,139.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.71,139.68) -- (141.57,136.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.12,138.25) -- (142.16,138.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.14,136.23) -- (140.14,140.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.58,137.00) -- (140.43,139.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.58,139.85) -- (140.43,137.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.99,138.43) -- (141.02,138.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.01,136.41) -- (139.01,140.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.29,138.11) -- (142.14,140.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.29,140.96) -- (142.14,138.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.70,139.54) -- (142.73,139.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.71,137.52) -- (140.71,141.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.14,136.69) -- (141.99,139.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.14,139.54) -- (141.99,136.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.55,138.12) -- (142.58,138.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.56,136.10) -- (140.56,140.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.94,137.93) -- (141.79,140.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.94,140.78) -- (141.79,137.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.35,139.36) -- (142.38,139.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.37,137.34) -- (140.37,141.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.26,135.75) -- (142.11,138.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.26,138.61) -- (142.11,135.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.67,137.18) -- (142.70,137.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.68,135.16) -- (140.68,139.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.76,133.34) -- (140.61,136.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.76,136.19) -- (140.61,133.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (137.17,134.77) -- (141.20,134.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.19,132.75) -- (139.19,136.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.70,136.97) -- (145.55,139.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.70,139.82) -- (145.55,136.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.11,138.39) -- (146.14,138.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (144.12,136.38) -- (144.12,140.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.45,136.87) -- (149.30,139.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (146.45,139.72) -- (149.30,136.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (145.86,138.29) -- (149.89,138.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.88,136.27) -- (147.88,140.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.71,135.08) -- (144.56,137.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.71,137.93) -- (144.56,135.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.12,136.51) -- (145.15,136.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.13,134.49) -- (143.13,138.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.35,138.62) -- (143.20,141.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.35,141.47) -- (143.20,138.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.75,140.04) -- (143.79,140.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.77,138.02) -- (141.77,142.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.53,141.02) -- (143.38,143.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.53,143.88) -- (143.38,141.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (139.94,142.45) -- (143.97,142.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (141.96,140.43) -- (141.96,144.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.78,152.24) -- (160.63,155.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.78,155.10) -- (160.63,152.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.19,153.67) -- (161.22,153.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.21,151.65) -- (159.21,155.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.08,153.17) -- (160.93,156.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.08,156.02) -- (160.93,153.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.49,154.60) -- (161.52,154.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.50,152.58) -- (159.50,156.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.04,153.43) -- (164.90,156.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.04,156.28) -- (164.90,153.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.45,154.85) -- (165.49,154.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.47,152.83) -- (163.47,156.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.29,152.69) -- (163.14,155.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.29,155.54) -- (163.14,152.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.70,154.12) -- (163.74,154.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.72,152.10) -- (161.72,156.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.10,155.89) -- (160.96,158.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.10,158.75) -- (160.96,155.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.51,157.32) -- (161.55,157.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.53,155.30) -- (159.53,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.68,154.48) -- (163.54,157.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.68,157.33) -- (163.54,154.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.09,155.91) -- (164.13,155.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.11,153.89) -- (162.11,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.45,154.01) -- (162.31,156.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.45,156.87) -- (162.31,154.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.86,155.44) -- (162.90,155.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.88,153.42) -- (160.88,157.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.88,155.04) -- (161.74,157.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.88,157.89) -- (161.74,155.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.29,156.47) -- (162.33,156.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.31,154.45) -- (160.31,158.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.49,154.48) -- (163.34,157.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.49,157.33) -- (163.34,154.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.90,155.91) -- (163.93,155.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.91,153.89) -- (161.91,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.31,155.12) -- (164.16,157.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.31,157.97) -- (164.16,155.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.72,156.55) -- (164.75,156.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.74,154.53) -- (162.74,158.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.50,156.09) -- (161.36,158.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.50,158.94) -- (161.36,156.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.91,157.51) -- (161.95,157.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.93,155.49) -- (159.93,159.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.93,155.61) -- (163.78,158.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.93,158.47) -- (163.78,155.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.34,157.04) -- (164.38,157.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.36,155.02) -- (162.36,159.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.39,152.31) -- (163.24,155.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.39,155.16) -- (163.24,152.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.80,153.73) -- (163.83,153.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.81,151.72) -- (161.81,155.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.39,155.76) -- (160.24,158.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.39,158.61) -- (160.24,155.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.80,157.18) -- (160.83,157.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.82,155.17) -- (158.82,159.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.58,152.55) -- (160.44,155.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.58,155.41) -- (160.44,152.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.99,153.98) -- (161.03,153.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.01,151.96) -- (159.01,156.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.05,154.41) -- (163.91,157.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.05,157.27) -- (163.91,154.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.46,155.84) -- (164.50,155.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.48,153.82) -- (162.48,157.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.64,154.02) -- (162.49,156.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.64,156.88) -- (162.49,154.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.04,155.45) -- (163.08,155.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.06,153.43) -- (161.06,157.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.03,154.63) -- (164.88,157.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.03,157.49) -- (164.88,154.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.44,156.06) -- (165.48,156.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.46,154.04) -- (163.46,158.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.39,157.93) -- (163.25,160.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.39,160.78) -- (163.25,157.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.80,159.35) -- (163.84,159.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.82,157.34) -- (161.82,161.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.55,154.86) -- (166.40,157.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.55,157.71) -- (166.40,154.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.96,156.29) -- (166.99,156.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.98,154.27) -- (164.98,158.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.06,153.97) -- (162.91,156.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.06,156.82) -- (162.91,153.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.47,155.40) -- (163.50,155.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.49,153.38) -- (161.49,157.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.34,155.60) -- (162.19,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.34,158.45) -- (162.19,155.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.75,157.03) -- (162.78,157.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.76,155.01) -- (160.76,159.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.63,154.33) -- (162.49,157.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.63,157.19) -- (162.49,154.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.04,155.76) -- (163.08,155.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.06,153.74) -- (161.06,157.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.23,155.00) -- (164.08,157.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.23,157.86) -- (164.08,155.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.64,156.43) -- (164.67,156.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.65,154.41) -- (162.65,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.51,153.98) -- (164.37,156.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.51,156.83) -- (164.37,153.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.92,155.41) -- (164.96,155.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.94,153.39) -- (162.94,157.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.79,156.26) -- (164.64,159.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.79,159.11) -- (164.64,156.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.20,157.69) -- (165.23,157.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.22,155.67) -- (163.22,159.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.69,154.01) -- (161.54,156.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.69,156.86) -- (161.54,154.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.10,155.44) -- (162.13,155.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.11,153.42) -- (160.11,157.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.58,155.99) -- (162.43,158.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.58,158.85) -- (162.43,155.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.98,157.42) -- (163.02,157.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.00,155.40) -- (161.00,159.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.56,158.81) -- (167.41,161.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.56,161.66) -- (167.41,158.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.97,160.24) -- (168.00,160.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.98,158.22) -- (165.98,162.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.74,157.81) -- (167.59,160.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.74,160.67) -- (167.59,157.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.15,159.24) -- (168.18,159.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.16,157.22) -- (166.16,161.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.23,156.22) -- (163.08,159.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.23,159.07) -- (163.08,156.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.64,157.64) -- (163.68,157.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.66,155.63) -- (161.66,159.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.49,157.22) -- (163.34,160.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.49,160.07) -- (163.34,157.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.90,158.64) -- (163.93,158.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.92,156.63) -- (161.92,160.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.16,156.73) -- (164.01,159.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.16,159.58) -- (164.01,156.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.57,158.16) -- (164.61,158.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.59,156.14) -- (162.59,160.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.73,158.71) -- (163.58,161.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.73,161.56) -- (163.58,158.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.14,160.13) -- (164.17,160.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.16,158.12) -- (162.16,162.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.91,155.82) -- (166.76,158.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.91,158.68) -- (166.76,155.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.32,157.25) -- (167.36,157.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.34,155.23) -- (165.34,159.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.02,157.37) -- (168.87,160.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.02,160.23) -- (168.87,157.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.43,158.80) -- (169.46,158.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.45,156.78) -- (167.45,160.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.64,156.78) -- (168.49,159.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.64,159.64) -- (168.49,156.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.05,158.21) -- (169.08,158.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (167.06,156.19) -- (167.06,160.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.67,162.47) -- (165.53,165.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.67,165.32) -- (165.53,162.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.08,163.90) -- (166.12,163.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.10,161.88) -- (164.10,165.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.47,157.62) -- (168.32,160.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.47,160.47) -- (168.32,157.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.88,159.04) -- (168.91,159.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.90,157.03) -- (166.90,161.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.32,156.93) -- (166.17,159.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.32,159.78) -- (166.17,156.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.73,158.35) -- (166.77,158.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.75,156.34) -- (164.75,160.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.67,155.33) -- (164.53,158.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.67,158.18) -- (164.53,155.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.08,156.76) -- (165.12,156.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.10,154.74) -- (163.10,158.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.75,155.50) -- (166.61,158.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.75,158.36) -- (166.61,155.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.16,156.93) -- (167.20,156.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.18,154.91) -- (165.18,158.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.27,156.76) -- (165.13,159.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.27,159.61) -- (165.13,156.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.68,158.18) -- (165.72,158.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.70,156.16) -- (163.70,160.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.82,155.54) -- (166.67,158.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.82,158.39) -- (166.67,155.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.23,156.96) -- (167.26,156.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.24,154.95) -- (165.24,158.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.43,158.45) -- (168.29,161.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (165.43,161.30) -- (168.29,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.84,159.88) -- (168.88,159.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (166.86,157.86) -- (166.86,161.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.41,158.61) -- (164.26,161.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.41,161.46) -- (164.26,158.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.82,160.03) -- (164.85,160.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.84,158.02) -- (162.84,162.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.82,160.33) -- (165.67,163.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.82,163.19) -- (165.67,160.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.23,161.76) -- (166.26,161.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (164.25,159.74) -- (164.25,163.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.41,156.49) -- (165.26,159.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (162.41,159.35) -- (165.26,156.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (161.82,157.92) -- (165.85,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (163.84,155.90) -- (163.84,159.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.49) -- (190.04,178.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.34) -- (190.04,175.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.92) -- (190.63,176.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.90) -- (188.62,178.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.87) -- (190.04,177.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.72) -- (190.04,174.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.29) -- (190.63,176.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.28) -- (188.62,178.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.44) -- (190.04,180.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.30) -- (190.04,177.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,178.87) -- (190.63,178.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,176.85) -- (188.62,180.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.50,173.07) -- (181.36,175.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.50,175.92) -- (181.36,173.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.91,174.50) -- (181.95,174.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.93,172.48) -- (179.93,176.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.53) -- (190.04,177.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.39) -- (190.04,174.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.96) -- (190.63,175.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.94) -- (188.62,177.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.38) -- (190.04,177.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.24) -- (190.04,174.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.81) -- (190.63,175.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.79) -- (188.62,177.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.07) -- (190.04,176.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.92) -- (190.04,174.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.49) -- (190.63,175.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.48) -- (188.62,177.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.73) -- (190.04,180.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.58) -- (190.04,177.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,179.15) -- (190.63,179.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,177.14) -- (188.62,181.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.40,175.18) -- (182.25,178.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.40,178.04) -- (182.25,175.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.81,176.61) -- (182.85,176.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.83,174.59) -- (180.83,178.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.77,171.83) -- (180.62,174.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.77,174.68) -- (180.62,171.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.18,173.25) -- (181.21,173.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.20,171.24) -- (179.20,175.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.80,176.79) -- (182.65,179.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.80,179.64) -- (182.65,176.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.21,178.22) -- (183.24,178.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.22,176.20) -- (181.22,180.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.49) -- (190.04,177.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.35) -- (190.04,174.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.92) -- (190.63,175.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.90) -- (188.62,177.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.48) -- (190.04,177.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.33) -- (190.04,174.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.90) -- (190.63,175.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.89) -- (188.62,177.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.03) -- (190.04,176.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.88) -- (190.04,174.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.45) -- (190.63,175.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.44) -- (188.62,177.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.55) -- (190.04,178.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.40) -- (190.04,175.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.98) -- (190.63,176.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.96) -- (188.62,178.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.15,176.75) -- (181.00,179.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.15,179.60) -- (181.00,176.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (177.56,178.17) -- (181.59,178.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.57,176.16) -- (179.57,180.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.62) -- (190.04,179.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.47) -- (190.04,176.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,178.04) -- (190.63,178.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,176.03) -- (188.62,180.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,173.64) -- (190.04,176.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.50) -- (190.04,173.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.07) -- (190.63,175.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.05) -- (188.62,177.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.52) -- (190.04,179.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.37) -- (190.04,176.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.94) -- (190.63,177.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.93) -- (188.62,179.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.51) -- (190.04,178.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.36) -- (190.04,175.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.94) -- (190.63,176.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.92) -- (188.62,178.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.37) -- (190.04,183.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,183.22) -- (190.04,180.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,181.80) -- (190.63,181.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,179.78) -- (188.62,183.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.54) -- (190.04,179.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.39) -- (190.04,176.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.96) -- (190.63,177.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.95) -- (188.62,179.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.70) -- (190.04,178.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.56) -- (190.04,175.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.13) -- (190.63,177.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.11) -- (188.62,179.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.95) -- (190.04,178.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.81) -- (190.04,175.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.38) -- (190.63,177.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.36) -- (188.62,179.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.22) -- (190.04,179.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.08) -- (190.04,176.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.65) -- (190.63,177.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.63) -- (188.62,179.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,173.55) -- (190.04,176.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.40) -- (190.04,173.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,174.98) -- (190.63,174.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,172.96) -- (188.62,176.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.55,176.58) -- (182.41,179.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.55,179.44) -- (182.41,176.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (178.96,178.01) -- (183.00,178.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.98,175.99) -- (180.98,180.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.91) -- (190.04,177.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.77) -- (190.04,174.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.34) -- (190.63,176.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.32) -- (188.62,178.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.45) -- (190.04,178.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.31) -- (190.04,175.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.88) -- (190.63,176.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.86) -- (188.62,178.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,174.52) -- (190.04,177.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.37) -- (190.04,174.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,175.95) -- (190.63,175.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,173.93) -- (188.62,177.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.95,175.78) -- (182.81,178.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.95,178.63) -- (182.81,175.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.36,177.20) -- (183.40,177.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.38,175.19) -- (181.38,179.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.13,177.35) -- (182.99,180.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.13,180.21) -- (182.99,177.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.54,178.78) -- (183.58,178.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.56,176.76) -- (181.56,180.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.65) -- (190.04,182.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.50) -- (190.04,179.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,181.07) -- (190.63,181.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,179.06) -- (188.62,183.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.96) -- (190.04,181.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.81) -- (190.04,178.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,180.39) -- (190.63,180.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,178.37) -- (188.62,182.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.64) -- (190.04,182.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.49) -- (190.04,179.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,181.06) -- (190.63,181.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,179.05) -- (188.62,183.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.26) -- (190.04,179.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.11) -- (190.04,176.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.68) -- (190.63,177.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.67) -- (188.62,179.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.05) -- (190.04,183.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,183.90) -- (190.04,181.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,182.48) -- (190.63,182.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,180.46) -- (188.62,184.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.15) -- (190.04,180.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.00) -- (190.04,177.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,178.57) -- (190.63,178.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,176.56) -- (188.62,180.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.20,174.13) -- (183.05,176.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.20,176.98) -- (183.05,174.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.61,175.55) -- (183.64,175.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.62,173.54) -- (181.62,177.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.04,178.39) -- (182.89,181.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (180.04,181.24) -- (182.89,178.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (179.45,179.81) -- (183.49,179.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (181.47,177.80) -- (181.47,181.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.61) -- (190.04,182.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.47) -- (190.04,179.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,181.04) -- (190.63,181.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,179.02) -- (188.62,183.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,175.42) -- (190.04,178.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.27) -- (190.04,175.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,176.85) -- (190.63,176.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,174.83) -- (188.62,178.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.00) -- (190.04,178.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.86) -- (190.04,176.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.43) -- (190.63,177.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.41) -- (188.62,179.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.14) -- (190.04,178.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.99) -- (190.04,176.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.57) -- (190.63,177.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.55) -- (188.62,179.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,176.19) -- (190.04,179.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,179.04) -- (190.04,176.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,177.61) -- (190.63,177.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,175.60) -- (188.62,179.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.31) -- (190.04,181.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.16) -- (190.04,178.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,179.74) -- (190.63,179.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,177.72) -- (188.62,181.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,178.43) -- (190.04,181.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.29) -- (190.04,178.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,179.86) -- (190.63,179.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,177.84) -- (188.62,181.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.26) -- (190.04,185.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.11) -- (190.04,182.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,183.68) -- (190.63,183.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,181.66) -- (188.62,185.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.74) -- (190.04,189.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.60) -- (190.04,186.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.17) -- (190.63,188.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.15) -- (188.62,190.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.98) -- (190.04,189.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.83) -- (190.04,186.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.40) -- (190.63,188.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.39) -- (188.62,190.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.60) -- (190.04,185.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.45) -- (190.04,182.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,184.03) -- (190.63,184.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,182.01) -- (188.62,186.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.24) -- (190.04,187.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.09) -- (190.04,184.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,185.66) -- (190.63,185.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,183.65) -- (188.62,187.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.44) -- (190.04,187.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.30) -- (190.04,184.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,185.87) -- (190.63,185.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,183.85) -- (188.62,187.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.02) -- (190.04,184.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.88) -- (190.04,182.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,183.45) -- (190.63,183.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,181.43) -- (188.62,185.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.15) -- (190.04,183.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,183.01) -- (190.04,180.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,181.58) -- (190.63,181.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,179.56) -- (188.62,183.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.07) -- (190.04,182.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.92) -- (190.04,180.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,181.50) -- (190.63,181.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,179.48) -- (188.62,183.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.11) -- (190.04,187.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.96) -- (190.04,185.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,186.54) -- (190.63,186.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,184.52) -- (188.62,188.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,183.02) -- (190.04,185.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.87) -- (190.04,183.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,184.45) -- (190.63,184.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,182.43) -- (188.62,186.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.80) -- (190.04,183.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,183.66) -- (190.04,180.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,182.23) -- (190.63,182.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,180.21) -- (188.62,184.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.88) -- (190.04,189.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.73) -- (190.04,186.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.30) -- (190.63,188.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.29) -- (188.62,190.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.23) -- (190.04,185.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.08) -- (190.04,182.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,183.66) -- (190.63,183.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,181.64) -- (188.62,185.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.96) -- (190.04,188.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.82) -- (190.04,185.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.39) -- (190.63,187.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.37) -- (188.62,189.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.54) -- (190.04,189.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.39) -- (190.04,186.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.96) -- (190.63,187.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.94) -- (188.62,189.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.47) -- (190.04,189.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.32) -- (190.04,186.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.90) -- (190.63,187.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.88) -- (188.62,189.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.27) -- (190.04,188.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.12) -- (190.04,185.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,186.70) -- (190.63,186.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,184.68) -- (188.62,188.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.12) -- (190.04,183.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,183.97) -- (190.04,181.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,182.54) -- (190.63,182.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,180.53) -- (188.62,184.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.12) -- (190.04,186.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.97) -- (190.04,184.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,185.54) -- (190.63,185.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,183.52) -- (188.62,187.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.58) -- (190.04,184.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.43) -- (190.04,181.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,183.00) -- (190.63,183.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,180.99) -- (188.62,185.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.34) -- (190.04,187.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.19) -- (190.04,184.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,185.77) -- (190.63,185.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,183.75) -- (188.62,187.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.33) -- (190.04,189.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.18) -- (190.04,186.33);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.75) -- (190.63,187.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.74) -- (188.62,189.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.19) -- (190.04,190.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,190.04) -- (190.04,187.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.62) -- (190.63,188.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.60) -- (188.62,190.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.66) -- (190.04,189.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.51) -- (190.04,186.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.09) -- (190.63,188.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.07) -- (188.62,190.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.14) -- (190.04,189.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.00) -- (190.04,186.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.57) -- (190.63,187.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.55) -- (188.62,189.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.40) -- (190.04,188.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.25) -- (190.04,185.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,186.82) -- (190.63,186.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,184.80) -- (188.62,188.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.28) -- (190.04,188.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.13) -- (190.04,185.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,186.71) -- (190.63,186.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,184.69) -- (188.62,188.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.34) -- (190.04,190.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,190.19) -- (190.04,187.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.77) -- (190.63,188.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.75) -- (188.62,190.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.16) -- (190.04,190.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,190.01) -- (190.04,187.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,188.59) -- (190.63,188.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,186.57) -- (188.62,190.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.56) -- (190.04,188.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.42) -- (190.04,185.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,186.99) -- (190.63,186.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,184.97) -- (188.62,189.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.02) -- (190.04,184.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.87) -- (190.04,182.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,183.44) -- (190.63,183.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,181.43) -- (188.62,185.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.24) -- (190.04,189.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,189.10) -- (190.04,186.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.67) -- (190.63,187.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.65) -- (188.62,189.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,181.26) -- (190.04,184.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,184.11) -- (190.04,181.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,182.68) -- (190.63,182.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,180.66) -- (188.62,184.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.10) -- (190.04,187.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.95) -- (190.04,185.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,186.53) -- (190.63,186.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,184.51) -- (188.62,188.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,182.82) -- (190.04,185.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.67) -- (190.04,182.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,184.25) -- (190.63,184.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,182.23) -- (188.62,186.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,193.71) -- (190.04,196.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,196.56) -- (190.04,193.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,195.14) -- (190.63,195.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,193.12) -- (188.62,197.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.71) -- (190.04,188.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.56) -- (190.04,185.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,187.14) -- (190.63,187.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,185.12) -- (188.62,189.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.79) -- (190.04,191.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,191.64) -- (190.04,188.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,190.22) -- (190.63,190.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,188.20) -- (188.62,192.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.04) -- (190.04,190.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,190.89) -- (190.04,188.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,189.46) -- (190.63,189.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,187.45) -- (188.62,191.48);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] ( 99.58, 99.18) --
	(102.44, 99.18) --
	(102.44,102.03) --
	( 99.58,102.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.65,100.72) --
	(104.50,100.72) --
	(104.50,103.57) --
	(101.65,103.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.65,108.55) --
	(104.50,108.55) --
	(104.50,111.40) --
	(101.65,111.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 98.64, 97.15) --
	(101.49, 97.15) --
	(101.49,100.00) --
	( 98.64,100.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.97, 98.97) --
	(103.82, 98.97) --
	(103.82,101.82) --
	(100.97,101.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.56,105.52) --
	(103.41,105.52) --
	(103.41,108.38) --
	(100.56,108.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.30, 99.78) --
	(105.15, 99.78) --
	(105.15,102.63) --
	(102.30,102.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 99.92, 96.90) --
	(102.77, 96.90) --
	(102.77, 99.76) --
	( 99.92, 99.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 99.58, 96.90) --
	(102.44, 96.90) --
	(102.44, 99.76) --
	( 99.58, 99.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.12, 98.75) --
	(104.97, 98.75) --
	(104.97,101.61) --
	(102.12,101.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.38,101.25) --
	(105.24,101.25) --
	(105.24,104.10) --
	(102.38,104.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.87, 99.18) --
	(103.72, 99.18) --
	(103.72,102.03) --
	(100.87,102.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.45,108.27) --
	(103.31,108.27) --
	(103.31,111.12) --
	(100.45,111.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.77, 99.78) --
	(103.62, 99.78) --
	(103.62,102.63) --
	(100.77,102.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.93, 99.38) --
	(104.78, 99.38) --
	(104.78,102.23) --
	(101.93,102.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.87, 98.75) --
	(103.72, 98.75) --
	(103.72,101.61) --
	(100.87,101.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.43,117.01) --
	(120.28,117.01) --
	(120.28,119.86) --
	(117.43,119.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.78,111.31) --
	(117.63,111.31) --
	(117.63,114.16) --
	(114.78,114.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.97,108.91) --
	(115.83,108.91) --
	(115.83,111.76) --
	(112.97,111.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.76,110.09) --
	(115.61,110.09) --
	(115.61,112.94) --
	(112.76,112.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.65,109.85) --
	(115.50,109.85) --
	(115.50,112.70) --
	(112.65,112.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.25,110.48) --
	(117.10,110.48) --
	(117.10,113.34) --
	(114.25,113.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.99,110.56) --
	(116.85,110.56) --
	(116.85,113.41) --
	(113.99,113.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.32,109.51) --
	(116.18,109.51) --
	(116.18,112.37) --
	(113.32,112.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.29,111.66) --
	(118.14,111.66) --
	(118.14,114.52) --
	(115.29,114.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.81,118.99) --
	(117.66,118.99) --
	(117.66,121.84) --
	(114.81,121.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.46,114.23) --
	(118.31,114.23) --
	(118.31,117.08) --
	(115.46,117.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.74,113.94) --
	(118.60,113.94) --
	(118.60,116.80) --
	(115.74,116.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.50,113.71) --
	(117.36,113.71) --
	(117.36,116.56) --
	(114.50,116.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.12,118.30) --
	(121.97,118.30) --
	(121.97,121.15) --
	(119.12,121.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.84,117.14) --
	(123.69,117.14) --
	(123.69,119.99) --
	(120.84,119.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.49,113.59) --
	(118.34,113.59) --
	(118.34,116.45) --
	(115.49,116.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.52,141.63) --
	(143.37,141.63) --
	(143.37,144.49) --
	(140.52,144.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.07,128.41) --
	(131.93,128.41) --
	(131.93,131.27) --
	(129.07,131.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.53,123.69) --
	(135.38,123.69) --
	(135.38,126.54) --
	(132.53,126.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.34,123.81) --
	(132.20,123.81) --
	(132.20,126.66) --
	(129.34,126.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.97,126.41) --
	(128.83,126.41) --
	(128.83,129.26) --
	(125.97,129.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.73,125.38) --
	(129.59,125.38) --
	(129.59,128.24) --
	(126.73,128.24) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.37,121.87) --
	(130.23,121.87) --
	(130.23,124.72) --
	(127.37,124.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.53,119.46) --
	(126.38,119.46) --
	(126.38,122.31) --
	(123.53,122.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.08,123.95) --
	(128.93,123.95) --
	(128.93,126.81) --
	(126.08,126.81) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.70,118.38) --
	(125.55,118.38) --
	(125.55,121.23) --
	(122.70,121.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.88,120.77) --
	(127.74,120.77) --
	(127.74,123.63) --
	(124.88,123.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (138.00,140.25) --
	(140.85,140.25) --
	(140.85,143.11) --
	(138.00,143.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (135.64,142.29) --
	(138.50,142.29) --
	(138.50,145.14) --
	(135.64,145.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.88,139.69) --
	(140.73,139.69) --
	(140.73,142.54) --
	(137.88,142.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.33,143.87) --
	(145.18,143.87) --
	(145.18,146.72) --
	(142.33,146.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.28,142.80) --
	(139.14,142.80) --
	(139.14,145.65) --
	(136.28,145.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.03,102.24) --
	(111.88,102.24) --
	(111.88,105.09) --
	(109.03,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.93, 99.97) --
	(104.78, 99.97) --
	(104.78,102.83) --
	(101.93,102.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.30, 99.78) --
	(105.15, 99.78) --
	(105.15,102.63) --
	(102.30,102.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.21,107.89) --
	(105.06,107.89) --
	(105.06,110.74) --
	(102.21,110.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.32,101.07) --
	(106.18,101.07) --
	(106.18,103.93) --
	(103.32,103.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.98, 99.97) --
	(111.83, 99.97) --
	(111.83,102.83) --
	(108.98,102.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.86,101.59) --
	(107.71,101.59) --
	(107.71,104.44) --
	(104.86,104.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.16,101.59) --
	(106.01,101.59) --
	(106.01,104.44) --
	(103.16,104.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.91, 99.58) --
	(105.76, 99.58) --
	(105.76,102.43) --
	(102.91,102.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (105.42,103.72) --
	(108.27,103.72) --
	(108.27,106.58) --
	(105.42,106.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.57,101.75) --
	(106.42,101.75) --
	(106.42,104.61) --
	(103.57,104.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.88,101.42) --
	(106.74,101.42) --
	(106.74,104.27) --
	(103.88,104.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.36,103.58) --
	(111.21,103.58) --
	(111.21,106.44) --
	(108.36,106.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (105.35,103.00) --
	(108.20,103.00) --
	(108.20,105.86) --
	(105.35,105.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.46,103.58) --
	(111.32,103.58) --
	(111.32,106.44) --
	(108.46,106.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (105.82,103.00) --
	(108.67,103.00) --
	(108.67,105.86) --
	(105.82,105.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.31,138.57) --
	(129.17,138.57) --
	(129.17,141.42) --
	(126.31,141.42) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.74,112.80) --
	(120.59,112.80) --
	(120.59,115.65) --
	(117.74,115.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.26,112.98) --
	(120.11,112.98) --
	(120.11,115.84) --
	(117.26,115.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.05,116.37) --
	(121.91,116.37) --
	(121.91,119.22) --
	(119.05,119.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.04,113.59) --
	(119.89,113.59) --
	(119.89,116.45) --
	(117.04,116.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.14,113.94) --
	(119.99,113.94) --
	(119.99,116.80) --
	(117.14,116.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.27,115.25) --
	(121.12,115.25) --
	(121.12,118.10) --
	(118.27,118.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.88,114.50) --
	(120.74,114.50) --
	(120.74,117.36) --
	(117.88,117.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.53,118.42) --
	(119.38,118.42) --
	(119.38,121.27) --
	(116.53,121.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.34,112.73) --
	(119.20,112.73) --
	(119.20,115.59) --
	(116.34,115.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.49,111.80) --
	(118.34,111.80) --
	(118.34,114.65) --
	(115.49,114.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.71,127.09) --
	(126.56,127.09) --
	(126.56,129.94) --
	(123.71,129.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.48,122.97) --
	(128.33,122.97) --
	(128.33,125.82) --
	(125.48,125.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.12,122.84) --
	(124.97,122.84) --
	(124.97,125.69) --
	(122.12,125.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.37,123.51) --
	(125.23,123.51) --
	(125.23,126.36) --
	(122.37,126.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.91,126.07) --
	(127.76,126.07) --
	(127.76,128.92) --
	(124.91,128.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.32,116.46) --
	(116.18,116.46) --
	(116.18,119.32) --
	(113.32,119.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.57,104.53) --
	(111.42,104.53) --
	(111.42,107.38) --
	(108.57,107.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.03,106.10) --
	(111.88,106.10) --
	(111.88,108.96) --
	(109.03,108.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.25,104.53) --
	(110.10,104.53) --
	(110.10,107.38) --
	(107.25,107.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.93,106.55) --
	(110.78,106.55) --
	(110.78,109.40) --
	(107.93,109.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.47,104.13) --
	(117.33,104.13) --
	(117.33,106.99) --
	(114.47,106.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.13,105.88) --
	(109.98,105.88) --
	(109.98,108.73) --
	(107.13,108.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.83,105.04) --
	(111.68,105.04) --
	(111.68,107.89) --
	(108.83,107.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.72,105.04) --
	(117.57,105.04) --
	(117.57,107.89) --
	(114.72,107.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.20,107.59) --
	(111.05,107.59) --
	(111.05,110.44) --
	(108.20,110.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.08,105.04) --
	(112.93,105.04) --
	(112.93,107.89) --
	(110.08,107.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.39,108.27) --
	(113.25,108.27) --
	(113.25,111.12) --
	(110.39,111.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.04,112.21) --
	(113.90,112.21) --
	(113.90,115.06) --
	(111.04,115.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.59,107.98) --
	(110.45,107.98) --
	(110.45,110.84) --
	(107.59,110.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.23,106.10) --
	(112.08,106.10) --
	(112.08,108.96) --
	(109.23,108.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.28,112.14) --
	(115.13,112.14) --
	(115.13,115.00) --
	(112.28,115.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.47,132.27) --
	(127.32,132.27) --
	(127.32,135.13) --
	(124.47,135.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.26,106.66) --
	(113.11,106.66) --
	(113.11,109.51) --
	(110.26,109.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.78,108.17) --
	(111.63,108.17) --
	(111.63,111.03) --
	(108.78,111.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.76,107.69) --
	(112.61,107.69) --
	(112.61,110.54) --
	(109.76,110.54) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.54,109.26) --
	(115.39,109.26) --
	(115.39,112.11) --
	(112.54,112.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.85,108.73) --
	(112.70,108.73) --
	(112.70,111.58) --
	(109.85,111.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.62,106.10) --
	(111.47,106.10) --
	(111.47,108.96) --
	(108.62,108.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.16,109.51) --
	(115.02,109.51) --
	(115.02,112.37) --
	(112.16,112.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.33,107.79) --
	(114.19,107.79) --
	(114.19,110.64) --
	(111.33,110.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.45,114.72) --
	(119.30,114.72) --
	(119.30,117.57) --
	(116.45,117.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.76,109.51) --
	(112.61,109.51) --
	(112.61,112.37) --
	(109.76,112.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.51,121.84) --
	(122.36,121.84) --
	(122.36,124.69) --
	(119.51,124.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.53,122.94) --
	(120.38,122.94) --
	(120.38,125.80) --
	(117.53,125.80) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.73,126.21) --
	(122.58,126.21) --
	(122.58,129.06) --
	(119.73,129.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.25,126.27) --
	(121.10,126.27) --
	(121.10,129.12) --
	(118.25,129.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.18,128.28) --
	(124.03,128.28) --
	(124.03,131.13) --
	(121.18,131.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,183.07) --
	(190.04,183.07) --
	(190.04,185.92) --
	(187.19,185.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (155.27,171.74) --
	(158.12,171.74) --
	(158.12,174.60) --
	(155.27,174.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.23,154.12) --
	(157.08,154.12) --
	(157.08,156.97) --
	(154.23,156.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (157.70,160.65) --
	(160.56,160.65) --
	(160.56,163.50) --
	(157.70,163.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.75,173.50) --
	(153.60,173.50) --
	(153.60,176.36) --
	(150.75,176.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.78,113.53) --
	(121.63,113.53) --
	(121.63,116.39) --
	(118.78,116.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.99,116.04) --
	(121.84,116.04) --
	(121.84,118.89) --
	(118.99,118.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.95,114.99) --
	(120.80,114.99) --
	(120.80,117.84) --
	(117.95,117.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.87,116.56) --
	(124.73,116.56) --
	(124.73,119.41) --
	(121.87,119.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (187.19,193.71) --
	(190.04,193.71) --
	(190.04,196.56) --
	(187.19,196.56) --
	cycle;
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.84, 86.83) -- ( 80.87, 86.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.86, 84.81) -- ( 78.86, 88.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.19, 82.80) -- ( 79.22, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 77.20, 80.78) -- ( 77.20, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 73.26, 81.80) -- ( 77.29, 81.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.27, 79.78) -- ( 75.27, 83.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.19, 83.73) -- ( 79.22, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 77.20, 81.71) -- ( 77.20, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.04, 83.73) -- ( 80.08, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.06, 81.71) -- ( 78.06, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.04, 84.58) -- ( 80.08, 84.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.06, 82.56) -- ( 78.06, 86.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 74.26, 82.80) -- ( 78.30, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.28, 80.78) -- ( 76.28, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.19, 83.73) -- ( 79.22, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 77.20, 81.71) -- ( 77.20, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.84, 83.73) -- ( 80.87, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.86, 81.71) -- ( 78.86, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.84, 83.73) -- ( 80.87, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.86, 81.71) -- ( 78.86, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.19, 82.80) -- ( 79.22, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 77.20, 80.78) -- ( 77.20, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.19, 82.80) -- ( 79.22, 82.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 77.20, 80.78) -- ( 77.20, 84.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.04, 83.73) -- ( 80.08, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.06, 81.71) -- ( 78.06, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 75.19, 81.80) -- ( 79.22, 81.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 77.20, 79.78) -- ( 77.20, 83.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.04, 83.73) -- ( 80.08, 83.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.06, 81.71) -- ( 78.06, 85.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 76.84, 84.58) -- ( 80.87, 84.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 78.86, 82.56) -- ( 78.86, 86.60);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,101.25) -- (103.31,104.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,104.10) -- (103.31,101.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.86,102.67) -- (103.90,102.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.88,100.66) -- (101.88,104.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.35,100.35) -- (103.20,103.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.35,103.20) -- (103.20,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.76,101.78) -- (103.79,101.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.78, 99.76) -- (101.78,103.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,100.16) -- (104.31,103.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,103.02) -- (104.31,100.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.87,101.59) -- (104.90,101.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.89, 99.57) -- (102.89,103.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,100.90) -- (104.31,103.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,103.75) -- (104.31,100.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.87,102.32) -- (104.90,102.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.89,100.31) -- (102.89,104.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,100.54) -- (104.31,103.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.46,103.39) -- (104.31,100.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.87,101.96) -- (104.90,101.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.89, 99.95) -- (102.89,103.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.56,101.07) -- (104.41,103.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.56,103.93) -- (104.41,101.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.96,102.50) -- (105.00,102.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.98,100.48) -- (102.98,104.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.64, 98.75) -- (101.49,101.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.64,101.61) -- (101.49, 98.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.05,100.18) -- (102.08,100.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.06, 98.16) -- (100.06,102.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.56, 99.38) -- (103.41,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.56,102.23) -- (103.41, 99.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.97,100.81) -- (104.00,100.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.99, 98.79) -- (101.99,102.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,100.72) -- (103.31,103.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,103.57) -- (103.31,100.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.86,102.14) -- (103.90,102.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.88,100.13) -- (101.88,104.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.56, 99.78) -- (103.41,102.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.56,102.63) -- (103.41, 99.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.97,101.20) -- (104.00,101.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.99, 99.19) -- (101.99,103.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45, 99.97) -- (103.31,102.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,102.83) -- (103.31, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.86,101.40) -- (103.90,101.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.88, 99.38) -- (101.88,103.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.84,100.16) -- (104.69,103.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.84,103.02) -- (104.69,100.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.25,101.59) -- (105.28,101.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (103.27, 99.57) -- (103.27,103.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.35, 99.97) -- (103.20,102.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.35,102.83) -- (103.20, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.76,101.40) -- (103.79,101.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.78, 99.38) -- (101.78,103.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.84,100.35) -- (104.69,103.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.84,103.20) -- (104.69,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.25,101.78) -- (105.28,101.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (103.27, 99.76) -- (103.27,103.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,100.35) -- (103.31,103.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.45,103.20) -- (103.31,100.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.86,101.78) -- (103.90,101.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.88, 99.76) -- (101.88,103.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.97,100.54) -- (103.82,103.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.97,103.39) -- (103.82,100.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.38,101.96) -- (104.41,101.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.39, 99.95) -- (102.39,103.98);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.05,157.19) -- (160.08,157.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.06,155.18) -- (158.06,159.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.48,156.54) -- (159.52,156.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.50,154.52) -- (157.50,158.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.05,157.32) -- (161.09,157.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.07,155.30) -- (159.07,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.64,158.13) -- (161.67,158.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.66,156.11) -- (159.66,160.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.35,158.10) -- (161.38,158.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.37,156.09) -- (159.37,160.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.04,158.54) -- (162.08,158.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.06,156.53) -- (160.06,160.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.31,157.92) -- (161.34,157.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.32,155.90) -- (159.32,159.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.30,158.07) -- (161.34,158.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.32,156.05) -- (159.32,160.09);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.11,158.28) -- (161.15,158.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.13,156.26) -- (159.13,160.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.02,156.44) -- (160.06,156.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.04,154.42) -- (158.04,158.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.73,156.06) -- (159.77,156.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.75,154.04) -- (157.75,158.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.45,157.17) -- (160.48,157.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.46,155.15) -- (158.46,159.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (156.04,157.55) -- (160.07,157.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (158.05,155.53) -- (158.05,159.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.77,159.16) -- (161.80,159.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.78,157.14) -- (159.78,161.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.99,159.34) -- (162.03,159.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (160.01,157.33) -- (160.01,161.36);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.84,159.31) -- (161.87,159.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (159.85,157.29) -- (159.85,161.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.85, 96.12) -- ( 95.89, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.87, 94.10) -- ( 93.87, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.05, 96.71) -- ( 97.09, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 94.70) -- ( 95.07, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.96, 97.28) -- ( 98.00, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.98, 95.26) -- ( 95.98, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.60, 97.28) -- ( 97.64, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.62, 95.26) -- ( 95.62, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.78, 97.82) -- ( 97.82, 97.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.80, 95.80) -- ( 95.80, 99.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.60, 97.28) -- ( 97.64, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.62, 95.26) -- ( 95.62, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.42, 97.00) -- ( 97.46, 97.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.44, 94.98) -- ( 95.44, 99.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.60, 97.28) -- ( 97.64, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.62, 95.26) -- ( 95.62, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.78, 98.82) -- ( 97.82, 98.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.80, 96.80) -- ( 95.80,100.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.85, 96.12) -- ( 95.89, 96.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.87, 94.10) -- ( 93.87, 98.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.86, 97.28) -- ( 96.89, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.88, 95.26) -- ( 94.88, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.24, 96.71) -- ( 97.27, 96.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.26, 94.70) -- ( 95.26, 98.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.05, 97.28) -- ( 97.09, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 95.26) -- ( 95.07, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.96, 97.28) -- ( 98.00, 97.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.98, 95.26) -- ( 95.98, 99.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.60, 97.82) -- ( 97.64, 97.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.62, 95.80) -- ( 95.62, 99.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 91.85, 96.42) -- ( 95.89, 96.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.87, 94.40) -- ( 93.87, 98.44);

\path[fill=fillColor,fill opacity=0.50] (102.30, 99.58) --
	(105.15, 99.58) --
	(105.15,102.43) --
	(102.30,102.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.88,101.25) --
	(106.74,101.25) --
	(106.74,104.10) --
	(103.88,104.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.84,100.16) --
	(104.69,100.16) --
	(104.69,103.02) --
	(101.84,103.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.99,101.42) --
	(105.84,101.42) --
	(105.84,104.27) --
	(102.99,104.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.93,101.07) --
	(104.78,101.07) --
	(104.78,103.93) --
	(101.93,103.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.49,101.07) --
	(106.34,101.07) --
	(106.34,103.93) --
	(103.49,103.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.49,101.59) --
	(106.34,101.59) --
	(106.34,104.44) --
	(103.49,104.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.91,102.24) --
	(105.76,102.24) --
	(105.76,105.09) --
	(102.91,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.91,102.24) --
	(105.76,102.24) --
	(105.76,105.09) --
	(102.91,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.38, 99.58) --
	(105.24, 99.58) --
	(105.24,102.43) --
	(102.38,102.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.64,101.25) --
	(107.49,101.25) --
	(107.49,104.10) --
	(104.64,104.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.32,102.08) --
	(106.18,102.08) --
	(106.18,104.93) --
	(103.32,104.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.21, 99.97) --
	(105.06, 99.97) --
	(105.06,102.83) --
	(102.21,102.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.27,102.55) --
	(107.12,102.55) --
	(107.12,105.40) --
	(104.27,105.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.08,102.24) --
	(105.93,102.24) --
	(105.93,105.09) --
	(103.08,105.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.73,102.40) --
	(106.58,102.40) --
	(106.58,105.25) --
	(103.73,105.25) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.63,175.48) -- (174.66,175.48);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.65,173.47) -- (172.65,177.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.23,174.94) -- (174.27,174.94);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.25,172.92) -- (172.25,176.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.77,174.86) -- (173.81,174.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.79,172.84) -- (171.79,176.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.20,174.16) -- (174.24,174.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.22,172.15) -- (172.22,176.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.45,174.04) -- (174.49,174.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (172.47,172.02) -- (172.47,176.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.38,173.64) -- (173.41,173.64);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.39,171.63) -- (171.39,175.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.69,174.82) -- (173.73,174.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.71,172.80) -- (171.71,176.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.71,175.39) -- (173.75,175.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.73,173.37) -- (171.73,177.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.30,174.39) -- (172.34,174.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.32,172.37) -- (170.32,176.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.44,174.16) -- (173.48,174.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.46,172.15) -- (171.46,176.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.70,174.72) -- (172.73,174.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.72,172.70) -- (170.72,176.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.66,173.83) -- (172.69,173.83);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.67,171.81) -- (170.67,175.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.08,173.77) -- (173.12,173.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.10,171.75) -- (171.10,175.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.03,174.85) -- (173.06,174.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.05,172.83) -- (171.05,176.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.70,172.88) -- (172.73,172.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (170.71,170.87) -- (170.71,174.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (169.75,175.10) -- (173.79,175.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (171.77,173.08) -- (171.77,177.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.36,147.82) -- (142.39,147.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.37,145.80) -- (140.37,149.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.88,123.69) -- (126.91,123.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.90,121.67) -- (124.90,125.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.44,113.02) -- (122.48,113.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.46,111.00) -- (120.46,115.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (116.42,112.29) -- (120.46,112.29);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.44,110.27) -- (118.44,114.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.37,120.19) -- (126.40,120.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.38,118.17) -- (124.38,122.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.49,114.90) -- (123.52,114.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.50,112.88) -- (121.50,116.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (124.62,124.21) -- (128.65,124.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (126.64,122.19) -- (126.64,126.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.08,117.51) -- (123.11,117.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.09,115.50) -- (121.09,119.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (115.67,110.42) -- (119.71,110.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.69,108.41) -- (117.69,112.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.81,113.02) -- (123.84,113.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.83,111.00) -- (121.83,115.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (128.35,131.87) -- (132.38,131.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (130.37,129.85) -- (130.37,133.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (140.20,147.26) -- (144.23,147.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (142.21,145.24) -- (142.21,149.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.87,159.25) -- (155.90,159.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.89,157.23) -- (153.89,161.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.87,158.47) -- (156.91,158.47);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.89,156.46) -- (154.89,160.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.09,160.65) -- (159.12,160.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.10,158.63) -- (157.10,162.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.97,157.40) -- (152.01,157.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.99,155.38) -- (149.99,159.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.16,133.69) -- (154.20,133.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.18,131.67) -- (152.18,135.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.83,132.43) -- (155.86,132.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.85,130.42) -- (153.85,134.45);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.80,132.17) -- (154.84,132.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.82,130.15) -- (152.82,134.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,131.17) -- (190.63,131.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,129.15) -- (188.62,133.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (147.82,130.52) -- (151.85,130.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.84,128.51) -- (149.84,132.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.22,131.39) -- (153.26,131.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.24,129.37) -- (151.24,133.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.47,130.78) -- (153.51,130.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.49,128.77) -- (151.49,132.80);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.66,130.49) -- (152.70,130.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.68,128.48) -- (150.68,132.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.48,131.74) -- (154.51,131.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.50,129.73) -- (152.50,133.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.80,131.08) -- (153.84,131.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.82,129.07) -- (151.82,133.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.98,131.66) -- (154.01,131.66);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.00,129.64) -- (152.00,133.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.55,134.58) -- (154.58,134.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.57,132.57) -- (152.57,136.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,136.65) -- (190.63,136.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,134.64) -- (188.62,138.67);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.33,134.77) -- (154.36,134.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.35,132.75) -- (152.35,136.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.27,134.74) -- (154.30,134.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.28,132.72) -- (152.28,136.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.44,134.41) -- (154.47,134.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.45,132.39) -- (152.45,136.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.06,132.11) -- (154.09,132.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.08,130.10) -- (152.08,134.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.36,132.60) -- (155.39,132.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.38,130.59) -- (153.38,134.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.24,132.52) -- (157.28,132.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.26,130.51) -- (155.26,134.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.61,132.74) -- (155.65,132.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.63,130.73) -- (153.63,134.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.78,132.30) -- (155.81,132.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.80,130.28) -- (153.80,134.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.98,130.24) -- (153.01,130.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.99,128.22) -- (150.99,132.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (149.35,130.35) -- (153.39,130.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.37,128.34) -- (151.37,132.37);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.12,131.63) -- (155.15,131.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.13,129.61) -- (153.13,133.65);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.21,131.26) -- (155.25,131.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.23,129.24) -- (153.23,133.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (148.80,129.59) -- (152.83,129.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.81,127.57) -- (150.81,131.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.16,131.77) -- (155.19,131.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.17,129.75) -- (153.17,133.79);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.22,133.74) -- (155.26,133.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.24,131.72) -- (153.24,135.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,133.58) -- (190.63,133.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,131.56) -- (188.62,135.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.66,133.03) -- (154.69,133.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.68,131.02) -- (152.68,135.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.04,132.14) -- (154.08,132.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.06,130.12) -- (152.06,134.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.51,132.56) -- (155.54,132.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.52,130.55) -- (153.52,134.58);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.61,137.82) -- (155.65,137.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.63,135.81) -- (153.63,139.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.52,137.14) -- (156.56,137.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.54,135.12) -- (154.54,139.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.54,135.70) -- (154.58,135.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.56,133.68) -- (152.56,137.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.30,135.89) -- (156.34,135.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.32,133.87) -- (154.32,137.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (186.60,135.01) -- (190.63,135.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (188.62,132.99) -- (188.62,137.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.15,137.25) -- (156.18,137.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.17,135.23) -- (154.17,139.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.14,137.84) -- (155.18,137.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.16,135.82) -- (153.16,139.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.75,134.57) -- (156.79,134.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.77,132.56) -- (154.77,136.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.09,132.85) -- (156.13,132.85);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.11,130.83) -- (154.11,134.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (151.64,132.42) -- (155.68,132.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.66,130.40) -- (153.66,134.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.36,133.82) -- (156.39,133.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.37,131.80) -- (154.37,135.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.16,141.44) -- (157.19,141.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.17,139.43) -- (155.17,143.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (153.04,138.96) -- (157.08,138.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (155.06,136.94) -- (155.06,140.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (150.29,137.54) -- (154.33,137.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.31,135.52) -- (152.31,139.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.35,140.05) -- (156.38,140.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.37,138.03) -- (154.37,142.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (152.60,140.72) -- (156.63,140.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (154.61,138.70) -- (154.61,142.74);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.08,128.95) -- (138.11,128.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.09,126.93) -- (136.09,130.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.13,128.61) -- (137.16,128.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.15,126.59) -- (135.15,130.63);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.93,128.88) -- (138.96,128.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.94,126.86) -- (136.94,130.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.90,128.97) -- (137.94,128.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.92,126.95) -- (135.92,130.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.59,126.42) -- (135.63,126.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.61,124.40) -- (133.61,128.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (131.90,126.57) -- (135.93,126.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.91,124.56) -- (133.91,128.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.39,128.41) -- (137.43,128.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.41,126.39) -- (135.41,130.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.66,128.91) -- (137.70,128.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.68,126.90) -- (135.68,130.93);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.03,131.72) -- (138.07,131.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.05,129.70) -- (136.05,133.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.89,129.00) -- (137.93,129.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.91,126.99) -- (135.91,131.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.50,128.22) -- (137.54,128.22);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.52,126.20) -- (135.52,130.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.02,128.88) -- (138.05,128.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.03,126.86) -- (136.03,130.90);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (132.86,128.44) -- (136.90,128.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.88,126.42) -- (134.88,130.46);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (134.10,128.70) -- (138.13,128.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (136.12,126.68) -- (136.12,130.72);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.20,127.60) -- (137.24,127.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.22,125.58) -- (135.22,129.61);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (133.63,128.57) -- (137.67,128.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (135.65,126.55) -- (135.65,130.59);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.77,121.06) -- (104.81,121.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.79,119.05) -- (102.79,123.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.07,105.15) -- (104.11,105.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.09,103.13) -- (102.09,107.17);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.76,103.98) -- (103.79,103.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.78,101.96) -- (101.78,106.00);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.88, 99.75) -- (102.91, 99.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.89, 97.73) -- (100.89,101.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 98.53, 99.97) -- (102.56, 99.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.55, 97.95) -- (100.55,101.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.86,105.96) -- (103.90,105.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.88,103.94) -- (101.88,107.97);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.97,100.18) -- (104.00,100.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.99, 98.16) -- (101.99,102.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.06,100.60) -- (105.10,100.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (103.08, 98.58) -- (103.08,102.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (106.83,100.39) -- (110.86,100.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (108.85, 98.38) -- (108.85,102.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.67,103.18) -- (104.71,103.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.69,101.16) -- (102.69,105.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (100.17, 99.52) -- (104.21, 99.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.19, 97.50) -- (102.19,101.54);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.79,107.98) -- (105.83,107.98);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (103.81,105.96) -- (103.81,109.99);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.23,107.30) -- (106.27,107.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.25,105.28) -- (104.25,109.32);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (112.28,108.19) -- (116.31,108.19);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (114.29,106.17) -- (114.29,110.21);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 99.44,100.18) -- (103.47,100.18);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (101.45, 98.16) -- (101.45,102.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (102.06,108.51) -- (106.09,108.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (104.08,106.49) -- (104.08,110.53);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 87.84) rectangle ( 90.40, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 87.84) -- ( 90.40, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 90.69) -- ( 90.40, 87.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.76, 89.86) rectangle ( 91.62, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.76, 89.86) -- ( 91.62, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.76, 92.71) -- ( 91.62, 89.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 88.89) rectangle ( 91.33, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 88.89) -- ( 91.33, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 91.75) -- ( 91.33, 88.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 94.69) rectangle ( 90.40, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 94.69) -- ( 90.40, 97.55);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 97.55) -- ( 90.40, 94.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 88.38) rectangle ( 92.18, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 88.38) -- ( 92.18, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 91.23) -- ( 92.18, 88.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 88.38) rectangle ( 92.18, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 88.38) -- ( 92.18, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 91.23) -- ( 92.18, 88.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.86, 87.84) rectangle ( 90.72, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.86, 87.84) -- ( 90.72, 90.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.86, 90.69) -- ( 90.72, 87.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 86.19, 87.28) rectangle ( 89.04, 90.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 86.19, 87.28) -- ( 89.04, 90.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 86.19, 90.13) -- ( 89.04, 87.28);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 88.38) rectangle ( 91.33, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 88.38) -- ( 91.33, 91.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 91.23) -- ( 91.33, 88.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.05, 88.89) rectangle ( 91.90, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.05, 88.89) -- ( 91.90, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.05, 91.75) -- ( 91.90, 88.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.76, 89.38) rectangle ( 91.62, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.76, 89.38) -- ( 91.62, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.76, 92.24) -- ( 91.62, 89.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 89.38) rectangle ( 91.33, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 89.38) -- ( 91.33, 92.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.47, 92.24) -- ( 91.33, 89.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.17, 91.57) rectangle ( 91.03, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.17, 91.57) -- ( 91.03, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.17, 94.42) -- ( 91.03, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 90.31) rectangle ( 92.18, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 90.31) -- ( 92.18, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 89.33, 93.16) -- ( 92.18, 90.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.17, 88.89) rectangle ( 91.03, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.17, 88.89) -- ( 91.03, 91.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 88.17, 91.75) -- ( 91.03, 88.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 90.31) rectangle ( 90.40, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 90.31) -- ( 90.40, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 87.55, 93.16) -- ( 90.40, 90.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 93.41) rectangle ( 96.87, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 93.41) -- ( 96.87, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 96.26) -- ( 96.87, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 93.41) rectangle ( 96.87, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 93.41) -- ( 96.87, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 96.26) -- ( 96.87, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.73, 94.07) rectangle ( 97.58, 96.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.73, 94.07) -- ( 97.58, 96.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.73, 96.92) -- ( 97.58, 94.07);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 93.41) rectangle ( 97.92, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 93.41) -- ( 97.92, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 95.07, 96.26) -- ( 97.92, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 93.06) rectangle ( 96.87, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 93.06) -- ( 96.87, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 95.92) -- ( 96.87, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.55, 93.06) rectangle ( 97.40, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.55, 93.06) -- ( 97.40, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.55, 95.92) -- ( 97.40, 93.06);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.73, 92.71) rectangle ( 97.58, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.73, 92.71) -- ( 97.58, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.73, 95.56) -- ( 97.58, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 92.71) rectangle ( 96.87, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 92.71) -- ( 96.87, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.01, 95.56) -- ( 96.87, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.06, 91.57) rectangle ( 95.91, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.06, 91.57) -- ( 95.91, 94.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.06, 94.42) -- ( 95.91, 91.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.02, 90.31) rectangle ( 94.87, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.02, 90.31) -- ( 94.87, 93.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.02, 93.16) -- ( 94.87, 90.31);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.90, 92.71) rectangle ( 97.75, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.90, 92.71) -- ( 97.75, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.90, 95.56) -- ( 97.75, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.55, 93.41) rectangle ( 97.40, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.55, 93.41) -- ( 97.40, 96.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 94.55, 96.26) -- ( 97.40, 93.41);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 92.71) rectangle ( 96.30, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 92.71) -- ( 96.30, 95.56);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.45, 95.56) -- ( 96.30, 92.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.03,101.25) rectangle ( 98.88,104.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.03,101.25) -- ( 98.88,104.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 96.03,104.10) -- ( 98.88,101.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.02, 91.96) rectangle ( 94.87, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.02, 91.96) -- ( 94.87, 94.82);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.02, 94.82) -- ( 94.87, 91.96);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.64, 93.06) rectangle ( 96.49, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.64, 93.06) -- ( 96.49, 95.92);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 93.64, 95.92) -- ( 96.49, 93.06);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.18,108.71) -- (123.21,108.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.19,106.70) -- (121.19,110.73);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.49,109.50) -- (123.52,109.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.50,107.49) -- (121.50,111.52);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.96,111.11) -- (123.99,111.11);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.98,109.09) -- (121.98,113.13);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.01,109.60) -- (124.05,109.60);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.03,107.58) -- (122.03,111.62);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.47,110.51) -- (123.50,110.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.49,108.49) -- (121.49,112.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.10,109.02) -- (124.14,109.02);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.12,107.00) -- (122.12,111.03);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.42,108.08) -- (122.46,108.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.44,106.07) -- (120.44,110.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (117.88,107.87) -- (121.92,107.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.90,105.85) -- (119.90,109.88);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.75,109.69) -- (123.79,109.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.77,107.68) -- (121.77,111.71);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.90,107.76) -- (122.93,107.76);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.91,105.74) -- (120.91,109.77);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.66,108.51) -- (123.69,108.51);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (121.68,106.49) -- (121.68,110.53);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.90,111.68) -- (124.93,111.68);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.91,109.66) -- (122.91,113.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.83,110.24) -- (122.87,110.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.85,108.23) -- (120.85,112.26);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.32,115.08) -- (124.36,115.08);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.34,113.06) -- (122.34,117.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.99,112.14) -- (124.03,112.14);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.01,110.12) -- (122.01,114.16);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (120.53,109.69) -- (124.57,109.69);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (122.55,107.68) -- (122.55,111.71);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 71.53, 79.27) rectangle ( 74.38, 82.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 71.53, 79.27) -- ( 74.38, 82.12);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 71.53, 82.12) -- ( 74.38, 79.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 81.86, 83.95) rectangle ( 84.71, 86.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 81.86, 83.95) -- ( 84.71, 86.81);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 81.86, 86.81) -- ( 84.71, 83.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.55, 99.38) rectangle (108.41,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.55, 99.38) -- (108.41,102.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (105.55,102.23) -- (108.41, 99.38);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.77,118.30) rectangle (130.62,121.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.77,118.30) -- (130.62,121.15);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.77,121.15) -- (130.62,118.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.80,131.42) rectangle (146.65,134.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.80,131.42) -- (146.65,134.27);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (143.80,134.27) -- (146.65,131.42);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.70,145.40) rectangle (160.56,148.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.70,145.40) -- (160.56,148.25);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (157.70,148.25) -- (160.56,145.40);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.63,155.04) rectangle (171.48,157.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.63,155.04) -- (171.48,157.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (168.63,157.89) -- (171.48,155.04);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,167.44) rectangle (190.04,170.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,167.44) -- (190.04,170.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,170.30) -- (190.04,167.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.50) rectangle (190.04,180.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,177.50) -- (190.04,180.35);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,180.35) -- (190.04,177.50);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.01) rectangle (190.04,187.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,185.01) -- (190.04,187.86);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,187.86) -- (190.04,185.01);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.06) rectangle (190.04,188.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,186.06) -- (190.04,188.91);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (187.19,188.91) -- (190.04,186.06);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (188.62,153.94) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,136.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,138.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,158.63) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,161.09) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,153.48) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,157.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,140.33) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,139.63) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,148.24) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,154.05) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,170.95) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,155.41) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,159.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,155.03) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,161.93) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,195.14) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,195.14) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,195.14) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,179.40) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,150.04) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,121.24) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (136.01,139.89) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,118.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (176.40,140.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (170.18,132.65) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,155.03) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,122.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (150.03,133.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (188.62,129.33) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (101.34, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 84.29, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 89.29, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 95.50) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 87.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 88.31, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 91.74) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 92.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 94.84) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 98.76, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 88.11) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 87.25, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 95.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 95.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20,100.60) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (105.54, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 87.97, 91.74) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (103.81, 95.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 85.65, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 90.32) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.55, 92.59) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 99.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (104.67, 97.55) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 97.61, 99.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.84,103.34) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (113.78,114.29) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 85.65, 91.28) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (128.14,118.78) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 99.04, 98.82) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 89.27) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 98.06, 97.55) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (101.99,101.59) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 91.55, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 80.69) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 88.11) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 98.34, 93.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 82.18,105.01) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (101.56, 92.17) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 75.27, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (105.39, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06,103.98) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (104.75,101.96) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (101.45, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 83.28, 87.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (100.43, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 94.28, 88.70) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 94.84) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 83.28, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 95.44, 97.55) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (127.68,116.88) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.26, 96.71) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 95.62, 98.07) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 93.44, 94.49) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 90.32) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (133.86,125.45) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.70, 96.42) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (102.98, 96.42) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (118.46,110.42) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (107.38, 97.00) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (114.26,110.06) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 99.82,113.02) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 83.80,100.60) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.88, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 84.29, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (111.41,115.25) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (102.89, 99.97) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (112.64,111.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (106.64,108.30) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 88.31, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 88.31, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 95.07, 89.27) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06,100.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 90.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] (108.79, 89.81) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 86.87, 86.83) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 83.73) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.38) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 81.80) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 86.13) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 84.58) circle (  1.43);

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 83.73) circle (  1.43);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 84.01) --
	( 80.78, 80.69) --
	( 76.94, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 87.60) --
	( 83.51, 84.27) --
	( 79.67, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 84.01) --
	( 81.52, 80.69) --
	( 77.68, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 85.94) --
	( 84.67, 82.62) --
	( 80.82, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 85.94) --
	( 82.89, 82.62) --
	( 79.04, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 82.91) --
	( 79.12, 79.58) --
	( 75.28, 79.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 82.91) --
	( 79.98, 79.58) --
	( 76.14, 79.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 86.80) --
	( 83.51, 83.47) --
	( 79.67, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.02) --
	( 80.78, 81.69) --
	( 76.94, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 87.60) --
	( 84.10, 84.27) --
	( 80.26, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.29, 89.04) --
	( 86.21, 85.72) --
	( 82.37, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 85.02) --
	( 84.10, 81.69) --
	( 80.26, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 88.34) --
	( 86.68, 85.02) --
	( 82.84, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.65, 89.04) --
	( 90.57, 85.72) --
	( 86.73, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 90.33) --
	( 88.40, 87.00) --
	( 84.55, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.28, 85.94) --
	( 85.20, 82.62) --
	( 81.36, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 86.80) --
	( 84.10, 83.47) --
	( 80.26, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 90.33) --
	( 87.13, 87.00) --
	( 83.29, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.98,101.28) --
	( 98.90, 97.95) --
	( 95.06, 97.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 88.34) --
	( 85.72, 85.02) --
	( 81.87, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.29, 90.92) --
	( 93.21, 87.59) --
	( 89.37, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.72, 97.05) --
	(105.64, 93.73) --
	(101.80, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 98.34,103.23) --
	(100.27, 99.90) --
	( 96.42, 99.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.45,110.93) --
	(105.37,107.61) --
	(101.53,107.61) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 87.60) --
	( 87.99, 84.27) --
	( 84.15, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.88, 95.61) --
	( 96.80, 92.28) --
	( 92.96, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.34, 94.39) --
	(103.26, 91.06) --
	( 99.42, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.31, 97.05) --
	(102.23, 93.73) --
	( 98.39, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.48, 90.33) --
	( 92.40, 87.00) --
	( 88.56, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.44, 95.22) --
	( 95.36, 91.89) --
	( 91.52, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.88,100.55) --
	( 96.80, 97.22) --
	( 92.96, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.66,100.55) --
	( 95.58, 97.22) --
	( 91.74, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.02, 98.64) --
	(110.94, 95.31) --
	(107.10, 95.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.12,110.19) --
	(103.04,106.87) --
	( 99.20,106.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.97, 89.04) --
	( 89.89, 85.72) --
	( 86.05, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.09, 99.22) --
	(104.01, 95.89) --
	(100.17, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.32,101.28) --
	( 98.24, 97.95) --
	( 94.40, 97.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.30,115.72) --
	( 99.22,112.39) --
	( 95.38,112.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.89,119.04) --
	(104.81,115.72) --
	(100.97,115.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.23,103.23) --
	(103.15, 99.90) --
	( 99.31, 99.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.98,104.00) --
	(104.90,100.67) --
	(101.06,100.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.25,122.25) --
	(106.17,118.93) --
	(102.33,118.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.81,122.33) --
	(120.73,119.00) --
	(116.89,119.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.63,112.37) --
	(105.55,109.05) --
	(101.71,109.05) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.14,139.55) --
	(121.07,136.22) --
	(117.22,136.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.40,122.41) --
	(115.32,119.08) --
	(111.48,119.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.82,109.05) --
	(113.74,105.72) --
	(109.90,105.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.15, 97.39) --
	( 98.07, 94.06) --
	( 94.23, 94.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 99.17,110.41) --
	(101.09,107.08) --
	( 97.25,107.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.18,111.91) --
	(109.10,108.59) --
	(105.26,108.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (105.62,124.86) --
	(107.54,121.53) --
	(103.70,121.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.55,121.46) --
	(112.48,118.13) --
	(108.63,118.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (105.62,109.64) --
	(107.54,106.31) --
	(103.70,106.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.51,130.07) --
	(118.43,126.74) --
	(114.59,126.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.78,103.02) --
	(115.70, 99.70) --
	(111.86, 99.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.05,122.85) --
	(108.97,119.53) --
	(105.13,119.53) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.23,114.66) --
	(113.15,111.33) --
	(109.31,111.33) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.99,124.42) --
	(117.91,121.09) --
	(114.07,121.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.92,124.70) --
	(116.84,121.37) --
	(113.00,121.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.05,127.18) --
	(135.97,123.85) --
	(132.12,123.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.36,147.84) --
	(119.28,144.51) --
	(115.44,144.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.88,127.21) --
	(121.80,123.88) --
	(117.95,123.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.99,120.78) --
	(116.91,117.45) --
	(113.07,117.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.81,118.31) --
	(122.73,114.98) --
	(118.89,114.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (127.50,127.79) --
	(129.42,124.46) --
	(125.58,124.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.87,126.16) --
	(136.79,122.83) --
	(132.95,122.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.18,123.80) --
	(113.10,120.47) --
	(109.26,120.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.54,124.92) --
	(122.46,121.59) --
	(118.62,121.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.31,117.53) --
	(109.23,114.20) --
	(105.39,114.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.50,130.40) --
	(112.43,127.07) --
	(108.58,127.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.79,124.03) --
	(121.71,120.70) --
	(117.87,120.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.30,131.27) --
	(125.22,127.95) --
	(121.38,127.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.67,134.92) --
	(122.59,131.60) --
	(118.75,131.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.83,124.23) --
	(122.75,120.90) --
	(118.91,120.90) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.05,146.39) --
	(131.97,143.07) --
	(128.13,143.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (152.47,137.19) --
	(154.39,133.86) --
	(150.54,133.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.68,131.54) --
	(118.60,128.21) --
	(114.76,128.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.12,139.34) --
	(132.04,136.01) --
	(128.20,136.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.08,119.69) --
	(120.00,116.36) --
	(116.16,116.36) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.99,132.01) --
	(131.91,128.68) --
	(128.06,128.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.82,144.76) --
	(134.74,141.43) --
	(130.90,141.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.06,140.30) --
	(134.98,136.97) --
	(131.14,136.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (158.09,147.36) --
	(160.01,144.03) --
	(156.17,144.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.31,135.59) --
	(139.23,132.26) --
	(135.39,132.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.34,153.77) --
	(135.26,150.45) --
	(131.41,150.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.70,162.28) --
	(146.62,158.96) --
	(142.78,158.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.54,135.72) --
	(144.47,132.39) --
	(140.62,132.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.99,146.84) --
	(134.91,143.51) --
	(131.07,143.51) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.71,137.16) --
	(142.63,133.83) --
	(138.78,133.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.15,126.85) --
	(162.07,123.52) --
	(158.23,123.52) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.02) --
	( 80.78, 81.69) --
	( 76.94, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 84.01) --
	( 79.12, 80.69) --
	( 75.28, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 87.60) --
	( 82.22, 84.27) --
	( 78.38, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 84.01) --
	( 79.98, 80.69) --
	( 76.14, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 90.33) --
	( 81.52, 87.00) --
	( 77.68, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 84.01) --
	( 79.12, 80.69) --
	( 75.28, 80.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 87.60) --
	( 82.22, 84.27) --
	( 78.38, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 86.80) --
	( 78.20, 83.47) --
	( 74.36, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 85.02) --
	( 78.20, 81.69) --
	( 74.36, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.02) --
	( 81.52, 81.69) --
	( 77.68, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 88.34) --
	( 83.51, 85.02) --
	( 79.67, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.94) --
	( 79.98, 82.62) --
	( 76.14, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 88.34) --
	( 84.67, 85.02) --
	( 80.82, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 90.92) --
	( 85.72, 87.59) --
	( 81.87, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 88.34) --
	( 84.10, 85.02) --
	( 80.26, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.02) --
	( 81.52, 81.69) --
	( 77.68, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 87.60) --
	( 84.67, 84.27) --
	( 80.82, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 85.94) --
	( 81.52, 82.62) --
	( 77.68, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 87.60) --
	( 84.67, 84.27) --
	( 80.82, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 88.34) --
	( 83.51, 85.02) --
	( 79.67, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 86.80) --
	( 82.89, 83.47) --
	( 79.04, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.28, 88.34) --
	( 85.20, 85.02) --
	( 81.36, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 86.80) --
	( 84.67, 83.47) --
	( 80.82, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.65, 89.70) --
	( 87.57, 86.38) --
	( 83.73, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 90.33) --
	( 87.99, 87.00) --
	( 84.15, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 90.92) --
	( 87.13, 87.59) --
	( 83.29, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 93.50) --
	( 87.13, 90.17) --
	( 83.29, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.76,101.28) --
	( 86.68, 97.95) --
	( 82.84, 97.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.61, 92.02) --
	( 89.53, 88.70) --
	( 85.69, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.25, 95.99) --
	( 89.17, 92.66) --
	( 85.32, 92.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 91.49) --
	( 86.68, 88.16) --
	( 82.84, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 88.34) --
	( 90.89, 85.02) --
	( 87.05, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 89.04) --
	( 88.40, 85.72) --
	( 84.55, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 86.80) --
	( 85.72, 83.47) --
	( 81.87, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 87.60) --
	( 85.72, 84.27) --
	( 81.87, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 91.49) --
	( 88.40, 88.16) --
	( 84.55, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 89.04) --
	( 85.72, 85.72) --
	( 81.87, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 93.50) --
	( 88.40, 90.17) --
	( 84.55, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.65, 90.92) --
	( 90.57, 87.59) --
	( 86.73, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.29, 90.92) --
	( 91.21, 87.59) --
	( 87.37, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.87, 89.70) --
	( 88.79, 86.38) --
	( 84.95, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 90.33) --
	( 90.89, 87.00) --
	( 87.05, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.75, 92.02) --
	( 92.68, 88.70) --
	( 88.83, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.29, 97.71) --
	( 91.21, 94.39) --
	( 87.37, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.55, 92.54) --
	( 93.47, 89.21) --
	( 89.63, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.66, 89.04) --
	( 95.58, 85.72) --
	( 91.74, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 93.03) --
	( 90.89, 89.70) --
	( 87.05, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.05, 92.54) --
	( 93.98, 89.21) --
	( 90.13, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 97.05) --
	( 91.82, 93.73) --
	( 87.98, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 92.54) --
	( 90.89, 89.21) --
	( 87.05, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.75, 92.54) --
	( 92.68, 89.21) --
	( 88.83, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 93.50) --
	( 91.82, 90.17) --
	( 87.98, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 95.61) --
	( 91.82, 92.28) --
	( 87.98, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 95.22) --
	( 96.41, 91.89) --
	( 92.56, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.48, 90.33) --
	( 92.40, 87.00) --
	( 88.56, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.65, 89.70) --
	( 90.57, 86.38) --
	( 86.73, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.31, 93.50) --
	( 90.23, 90.17) --
	( 86.39, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.54, 94.39) --
	( 94.46, 91.06) --
	( 90.61, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.48, 93.50) --
	( 92.40, 90.17) --
	( 88.56, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.77, 98.93) --
	( 94.69, 95.60) --
	( 90.85, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.87,100.03) --
	( 95.79, 96.71) --
	( 91.95, 96.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.08, 95.61) --
	( 96.00, 92.28) --
	( 92.16, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.91,100.80) --
	( 99.83, 97.47) --
	( 95.99, 97.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.17, 98.03) --
	(105.09, 94.70) --
	(101.25, 94.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.29, 93.50) --
	( 93.21, 90.17) --
	( 89.37, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.30, 93.50) --
	( 94.22, 90.17) --
	( 90.38, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.44,108.17) --
	( 95.36,104.85) --
	( 91.52,104.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.22, 95.22) --
	( 95.14, 91.89) --
	( 91.30, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 98.34,103.42) --
	(100.27,100.10) --
	( 96.42,100.10) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.88, 94.39) --
	(103.80, 91.06) --
	( 99.96, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.46,114.59) --
	( 99.38,111.26) --
	( 95.53,111.26) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.66,108.17) --
	( 95.58,104.85) --
	( 91.74,104.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.01,102.18) --
	(109.93, 98.86) --
	(106.09, 98.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.49,106.50) --
	( 98.41,103.17) --
	( 94.57,103.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.28,100.55) --
	( 96.21, 97.22) --
	( 92.36, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.98, 95.22) --
	( 97.90, 91.89) --
	( 94.06, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.88,100.80) --
	( 96.80, 97.47) --
	( 92.96, 97.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.80,110.52) --
	( 97.72,107.19) --
	( 93.88,107.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (106.21,109.17) --
	(108.13,105.84) --
	(104.29,105.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 95.22) --
	( 96.41, 91.89) --
	( 92.56, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (115.26,124.73) --
	(117.18,121.41) --
	(113.34,121.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.46,122.82) --
	(139.38,119.49) --
	(135.54,119.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.91,124.45) --
	( 99.83,121.12) --
	( 95.99,121.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.26, 96.71) --
	( 97.18, 93.38) --
	( 93.33, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.36, 98.03) --
	(121.28, 94.70) --
	(117.43, 94.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.55,104.72) --
	(102.47,101.39) --
	( 98.62,101.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.82,107.51) --
	( 98.74,104.18) --
	( 94.90,104.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.43,102.40) --
	(102.35, 99.07) --
	( 98.51, 99.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.35,103.81) --
	(112.28,100.48) --
	(108.43,100.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.08,110.30) --
	(105.00,106.97) --
	(101.16,106.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.25,110.30) --
	(112.17,106.97) --
	(108.33,106.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (111.64,101.74) --
	(113.56, 98.41) --
	(109.72, 98.41) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (108.01,127.79) --
	(109.93,124.46) --
	(106.09,124.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (120.40,110.83) --
	(122.32,107.50) --
	(118.47,107.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.91,108.04) --
	(106.83,104.72) --
	(102.99,104.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.98,108.04) --
	( 98.90,104.72) --
	( 95.06,104.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.33,131.40) --
	(125.25,128.07) --
	(121.41,128.07) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.57,125.48) --
	(111.49,122.15) --
	(107.65,122.15) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.79,117.06) --
	(104.71,113.73) --
	(100.87,113.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.82,126.46) --
	( 98.74,123.13) --
	( 94.90,123.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.43,122.25) --
	(102.35,118.93) --
	( 98.51,118.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.29,122.10) --
	(116.21,118.77) --
	(112.37,118.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.82,133.11) --
	(115.74,129.78) --
	(111.90,129.78) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.14,130.03) --
	(126.06,126.70) --
	(122.22,126.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.17,142.14) --
	(132.09,138.81) --
	(128.25,138.81) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.54,121.42) --
	(105.46,118.09) --
	(101.62,118.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.05,134.31) --
	(122.97,130.98) --
	(119.13,130.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.66,123.28) --
	(120.58,119.95) --
	(116.74,119.95) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (121.31,118.63) --
	(123.23,115.30) --
	(119.39,115.30) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.89,118.42) --
	(115.81,115.09) --
	(111.97,115.09) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.12,121.66) --
	(118.04,118.34) --
	(114.19,118.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.51,125.45) --
	(114.43,122.13) --
	(110.59,122.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.31,114.44) --
	(134.23,111.11) --
	(130.39,111.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (119.05,137.77) --
	(120.97,134.45) --
	(117.13,134.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.64,124.45) --
	(125.56,121.12) --
	(121.72,121.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.93,132.82) --
	(115.85,129.49) --
	(112.01,129.49) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.41,120.65) --
	(111.33,117.32) --
	(107.49,117.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.02,145.01) --
	(145.95,141.68) --
	(142.10,141.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (124.28,129.07) --
	(126.20,125.74) --
	(122.36,125.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.95,113.33) --
	(109.87,110.00) --
	(106.03,110.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.12,143.05) --
	(148.05,139.72) --
	(144.20,139.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.26,159.10) --
	(131.18,155.77) --
	(127.34,155.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (132.83,115.02) --
	(134.75,111.70) --
	(130.91,111.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (147.57,132.20) --
	(149.50,128.88) --
	(145.65,128.88) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (113.20,126.54) --
	(115.12,123.21) --
	(111.28,123.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.80,156.09) --
	(132.72,152.76) --
	(128.87,152.76) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.46,157.29) --
	(146.38,153.96) --
	(142.54,153.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (126.88,120.52) --
	(128.80,117.19) --
	(124.96,117.19) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.93,129.55) --
	(120.85,126.22) --
	(117.01,126.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (118.98,116.75) --
	(120.90,113.43) --
	(117.06,113.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (116.91,122.06) --
	(118.84,118.73) --
	(114.99,118.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.37,154.01) --
	(155.29,150.68) --
	(151.45,150.68) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.28,128.48) --
	(119.20,125.16) --
	(115.36,125.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.57,138.18) --
	(146.50,134.85) --
	(142.65,134.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.27,127.60) --
	(148.19,124.27) --
	(144.35,124.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (142.16,158.89) --
	(144.08,155.56) --
	(140.24,155.56) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.78,168.92) --
	(147.70,165.60) --
	(143.86,165.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.33,144.80) --
	(132.25,141.47) --
	(128.41,141.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.99,168.96) --
	(136.91,165.63) --
	(133.07,165.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.59,137.56) --
	(131.51,134.23) --
	(127.67,134.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.06,135.72) --
	(154.98,132.39) --
	(151.14,132.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.32,151.91) --
	(138.24,148.58) --
	(134.40,148.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.70,157.32) --
	(155.62,153.99) --
	(151.78,153.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (156.91,154.24) --
	(158.83,150.91) --
	(154.99,150.91) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.88,135.52) --
	(135.80,132.20) --
	(131.96,132.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (146.77,152.77) --
	(148.69,149.44) --
	(144.85,149.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (139.83,165.16) --
	(141.75,161.83) --
	(137.91,161.83) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.16,125.54) --
	(124.08,122.21) --
	(120.24,122.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.15,139.83) --
	(153.07,136.50) --
	(149.23,136.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (134.45,149.10) --
	(136.37,145.77) --
	(132.53,145.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 86.80) --
	( 81.52, 83.47) --
	( 77.68, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.94) --
	( 79.98, 82.62) --
	( 76.14, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 76.28, 85.94) --
	( 78.20, 82.62) --
	( 74.36, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 93.03) --
	( 80.78, 89.70) --
	( 76.94, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 77.20, 85.94) --
	( 79.12, 82.62) --
	( 75.28, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.94) --
	( 79.98, 82.62) --
	( 76.14, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.94) --
	( 79.98, 82.62) --
	( 76.14, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 85.02) --
	( 79.98, 81.69) --
	( 76.14, 81.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.86, 85.94) --
	( 80.78, 82.62) --
	( 76.94, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 85.94) --
	( 85.72, 82.62) --
	( 81.87, 82.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 87.60) --
	( 82.22, 84.27) --
	( 78.38, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 86.80) --
	( 82.89, 83.47) --
	( 79.04, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 79.60, 86.80) --
	( 81.52, 83.47) --
	( 77.68, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 94.81) --
	( 82.89, 91.48) --
	( 79.04, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 99.22) --
	( 82.22, 95.89) --
	( 78.38, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 78.06, 86.80) --
	( 79.98, 83.47) --
	( 76.14, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.30, 86.80) --
	( 82.22, 83.47) --
	( 78.38, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 86.80) --
	( 83.51, 83.47) --
	( 79.67, 83.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 87.60) --
	( 82.89, 84.27) --
	( 79.04, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 80.96, 87.60) --
	( 82.89, 84.27) --
	( 79.04, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 89.04) --
	( 85.72, 85.72) --
	( 81.87, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.87, 93.50) --
	( 88.79, 90.17) --
	( 84.95, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 88.34) --
	( 91.82, 85.02) --
	( 87.98, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 89.04) --
	( 84.10, 85.72) --
	( 80.26, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 81.59, 87.60) --
	( 83.51, 84.27) --
	( 79.67, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 90.92) --
	( 85.72, 87.59) --
	( 81.87, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.75, 88.34) --
	( 84.67, 85.02) --
	( 80.82, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 89.04) --
	( 86.68, 85.72) --
	( 82.84, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 89.04) --
	( 84.10, 85.72) --
	( 80.26, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 87.60) --
	( 84.10, 84.27) --
	( 80.26, 84.27) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 88.34) --
	( 86.68, 85.02) --
	( 82.84, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 92.02) --
	( 87.99, 88.70) --
	( 84.15, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 89.70) --
	( 87.13, 86.38) --
	( 83.29, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 89.70) --
	( 87.99, 86.38) --
	( 84.15, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 89.04) --
	( 85.72, 85.72) --
	( 81.87, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 83.80, 89.04) --
	( 85.72, 85.72) --
	( 81.87, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.76, 90.33) --
	( 86.68, 87.00) --
	( 82.84, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 92.02) --
	( 91.82, 88.70) --
	( 87.98, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.29, 92.02) --
	( 86.21, 88.70) --
	( 82.37, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 82.18, 88.34) --
	( 84.10, 85.02) --
	( 80.26, 85.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.97, 92.54) --
	( 89.89, 89.21) --
	( 86.05, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 89.70) --
	( 87.13, 86.38) --
	( 83.29, 86.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 84.29, 90.33) --
	( 86.21, 87.00) --
	( 82.37, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 94.81) --
	( 90.89, 91.48) --
	( 87.05, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 89.04) --
	( 87.13, 85.72) --
	( 83.29, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 90.33) --
	( 88.40, 87.00) --
	( 84.55, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.21, 89.04) --
	( 87.13, 85.72) --
	( 83.29, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.29,100.80) --
	( 93.21, 97.47) --
	( 89.37, 97.47) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 85.65, 89.04) --
	( 87.57, 85.72) --
	( 83.73, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 89.04) --
	( 88.40, 85.72) --
	( 84.55, 85.72) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.47, 98.93) --
	( 88.40, 95.60) --
	( 84.55, 95.60) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.07, 90.33) --
	( 87.99, 87.00) --
	( 84.15, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.25, 90.33) --
	( 89.17, 87.00) --
	( 85.32, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.61, 94.39) --
	( 89.53, 91.06) --
	( 85.69, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.87, 94.39) --
	( 88.79, 91.06) --
	( 84.95, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 86.87, 90.33) --
	( 88.79, 87.00) --
	( 84.95, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.25, 90.92) --
	( 89.17, 87.59) --
	( 85.32, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.05, 91.49) --
	( 93.98, 88.16) --
	( 90.13, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.61, 90.33) --
	( 89.53, 87.00) --
	( 85.69, 87.00) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.97, 91.49) --
	( 89.89, 88.16) --
	( 86.05, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.03, 91.49) --
	( 92.95, 88.16) --
	( 89.11, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.31, 92.02) --
	( 90.23, 88.70) --
	( 86.39, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.61, 90.92) --
	( 89.53, 87.59) --
	( 85.69, 87.59) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.60,104.89) --
	( 91.52,101.57) --
	( 87.68,101.57) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.61, 93.50) --
	( 89.53, 90.17) --
	( 85.69, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.31, 92.02) --
	( 90.23, 88.70) --
	( 86.39, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.65, 91.49) --
	( 90.57, 88.16) --
	( 86.73, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.25, 92.02) --
	( 89.17, 88.70) --
	( 85.32, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.25, 91.49) --
	( 89.17, 88.16) --
	( 85.32, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.26, 91.49) --
	( 97.18, 88.16) --
	( 93.33, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.48, 93.03) --
	( 92.40, 89.70) --
	( 88.56, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.75, 93.03) --
	( 92.68, 89.70) --
	( 88.83, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.75, 93.50) --
	( 92.68, 90.17) --
	( 88.83, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 91.49) --
	( 90.89, 88.16) --
	( 87.05, 88.16) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 87.97, 92.02) --
	( 89.89, 88.70) --
	( 86.05, 88.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.55, 93.03) --
	( 93.47, 89.70) --
	( 89.63, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 92.54) --
	( 91.82, 89.21) --
	( 87.98, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 89.90, 92.54) --
	( 91.82, 89.21) --
	( 87.98, 89.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 88.97, 93.50) --
	( 90.89, 90.17) --
	( 87.05, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.19, 93.95) --
	( 92.11, 90.63) --
	( 88.27, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.75, 93.03) --
	( 92.68, 89.70) --
	( 88.83, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.55,100.55) --
	( 93.47, 97.22) --
	( 89.63, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.54,104.18) --
	( 94.46,100.85) --
	( 90.61,100.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.30, 93.03) --
	( 99.22, 89.70) --
	( 95.38, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.48, 93.95) --
	( 92.40, 90.63) --
	( 88.56, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.05, 94.39) --
	( 93.98, 91.06) --
	( 90.13, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 90.48, 93.03) --
	( 92.40, 89.70) --
	( 88.56, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.29, 93.03) --
	( 93.21, 89.70) --
	( 89.37, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.29, 93.95) --
	( 93.21, 90.63) --
	( 89.37, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.54, 93.95) --
	( 94.46, 90.63) --
	( 90.61, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.22, 94.81) --
	( 95.14, 91.48) --
	( 91.30, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 93.44, 95.22) --
	( 95.36, 91.89) --
	( 91.52, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 94.81) --
	( 96.41, 91.48) --
	( 92.56, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.28, 94.39) --
	( 96.21, 91.06) --
	( 92.36, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.05, 93.50) --
	( 93.98, 90.17) --
	( 90.13, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.68,102.61) --
	( 96.60, 99.28) --
	( 92.76, 99.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 91.81, 93.50) --
	( 93.73, 90.17) --
	( 89.88, 90.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 94.81) --
	( 96.41, 91.48) --
	( 92.56, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.05, 93.03) --
	( 93.98, 89.70) --
	( 90.13, 89.70) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.08, 93.95) --
	( 96.00, 90.63) --
	( 92.16, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 92.54, 95.61) --
	( 94.46, 92.28) --
	( 90.61, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.15, 94.81) --
	( 98.07, 91.48) --
	( 94.23, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 95.61) --
	( 96.41, 92.28) --
	( 92.56, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.07, 95.99) --
	( 96.99, 92.66) --
	( 93.15, 92.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.08, 94.39) --
	( 96.00, 91.06) --
	( 92.16, 91.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 98.06, 96.35) --
	( 99.98, 93.03) --
	( 96.13, 93.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.48, 93.95) --
	( 96.41, 90.63) --
	( 92.56, 90.63) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.26, 97.39) --
	( 97.18, 94.06) --
	( 93.33, 94.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.32, 94.81) --
	( 98.24, 91.48) --
	( 94.40, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.88, 94.81) --
	( 96.80, 91.48) --
	( 92.96, 91.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.80, 96.71) --
	( 97.72, 93.38) --
	( 93.88, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.98, 97.05) --
	( 97.90, 93.73) --
	( 94.06, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.63,106.04) --
	(105.55,102.71) --
	(101.71,102.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.07, 95.22) --
	( 96.99, 91.89) --
	( 93.15, 91.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.26, 95.61) --
	( 97.18, 92.28) --
	( 93.33, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 95.98, 96.71) --
	( 97.90, 93.38) --
	( 94.06, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.88, 98.34) --
	( 96.80, 95.01) --
	( 92.96, 95.01) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.82, 95.99) --
	( 98.74, 92.66) --
	( 94.90, 92.66) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.30, 95.61) --
	( 99.22, 92.28) --
	( 95.38, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 94.68,100.55) --
	( 96.60, 97.22) --
	( 92.76, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.91, 95.61) --
	( 99.83, 92.28) --
	( 95.99, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.98, 96.71) --
	( 98.90, 93.38) --
	( 95.06, 93.38) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.32, 97.05) --
	( 98.24, 93.73) --
	( 94.40, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.76, 97.39) --
	( 99.68, 94.06) --
	( 95.84, 94.06) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.46,100.03) --
	( 99.38, 96.71) --
	( 95.53, 96.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.14, 97.71) --
	( 99.06, 94.39) --
	( 95.22, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.46, 99.22) --
	( 99.38, 95.89) --
	( 95.53, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.30, 95.61) --
	( 99.22, 92.28) --
	( 95.38, 92.28) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.14, 97.71) --
	( 99.06, 94.39) --
	( 95.22, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 97.30, 97.05) --
	( 99.22, 93.73) --
	( 95.38, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 98.76, 97.71) --
	(100.69, 94.39) --
	( 96.84, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.01, 99.22) --
	(102.93, 95.89) --
	( 99.09, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 96.82, 97.05) --
	( 98.74, 93.73) --
	( 94.90, 93.73) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.43,100.55) --
	(102.35, 97.22) --
	( 98.51, 97.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 99.17, 99.22) --
	(101.09, 95.89) --
	( 97.25, 95.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.06,104.18) --
	(101.99,100.85) --
	( 98.14,100.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] ( 98.90, 97.71) --
	(100.82, 94.39) --
	( 96.98, 94.39) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.98,117.76) --
	(104.90,114.43) --
	(101.06,114.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.19,102.18) --
	(102.11, 98.86) --
	( 98.27, 98.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.42,131.31) --
	(106.34,127.98) --
	(102.50,127.98) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.55, 99.50) --
	(102.47, 96.17) --
	( 98.62, 96.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.51,109.17) --
	(116.43,105.84) --
	(112.58,105.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.88, 99.50) --
	(103.80, 96.17) --
	( 99.96, 96.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.55,102.18) --
	(102.47, 98.86) --
	( 98.62, 98.86) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (103.81,103.81) --
	(105.73,100.48) --
	(101.89,100.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.56,101.51) --
	(103.48, 98.18) --
	( 99.64, 98.18) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (101.78,108.17) --
	(103.70,104.85) --
	( 99.85,104.85) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (106.21, 99.50) --
	(108.13, 96.17) --
	(104.29, 96.17) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (102.29,107.64) --
	(104.22,104.31) --
	(100.37,104.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (100.06,100.03) --
	(101.99, 96.71) --
	( 98.14, 96.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.38,116.44) --
	(109.30,113.11) --
	(105.46,113.11) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.67,112.55) --
	(127.59,109.22) --
	(123.75,109.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.55,107.37) --
	(127.47,104.04) --
	(123.63,104.04) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.92,123.46) --
	(130.84,120.13) --
	(127.00,120.13) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (104.75,105.56) --
	(106.67,102.24) --
	(102.83,102.24) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (130.09,139.26) --
	(132.01,135.93) --
	(128.17,135.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (107.76,109.29) --
	(109.68,105.96) --
	(105.84,105.96) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (109.08,106.04) --
	(111.00,102.71) --
	(107.15,102.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.98,137.64) --
	(124.90,134.32) --
	(121.06,134.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (106.77,132.56) --
	(108.70,129.23) --
	(104.85,129.23) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.29,143.14) --
	(130.21,139.82) --
	(126.37,139.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.44,112.10) --
	(116.36,108.77) --
	(112.51,108.77) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.99,122.78) --
	(116.91,119.45) --
	(113.07,119.45) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.72,110.30) --
	(114.64,106.97) --
	(110.80,106.97) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.55,108.81) --
	(112.48,105.48) --
	(108.63,105.48) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (110.00,119.15) --
	(111.92,115.82) --
	(108.07,115.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (117.00,132.22) --
	(118.92,128.89) --
	(115.08,128.89) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (123.33,150.73) --
	(125.25,147.40) --
	(121.41,147.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (112.55,118.53) --
	(114.47,115.20) --
	(110.63,115.20) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (114.85,114.88) --
	(116.77,111.55) --
	(112.93,111.55) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (136.95,147.34) --
	(138.87,144.02) --
	(135.03,144.02) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,160.17) --
	(190.54,156.84) --
	(186.69,156.84) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (131.35,124.76) --
	(133.27,121.44) --
	(129.43,121.44) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (144.32,153.26) --
	(146.24,149.93) --
	(142.40,149.93) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (133.49,131.82) --
	(135.41,128.50) --
	(131.56,128.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (128.38,141.19) --
	(130.31,137.87) --
	(126.46,137.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.86,182.15) --
	(173.78,178.82) --
	(169.94,178.82) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.05,141.73) --
	(126.97,138.40) --
	(123.13,138.40) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (122.95,143.67) --
	(124.87,140.35) --
	(121.03,140.35) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (125.12,117.76) --
	(127.04,114.43) --
	(123.20,114.43) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (149.96,166.04) --
	(151.89,162.71) --
	(148.04,162.71) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (167.16,180.65) --
	(169.08,177.32) --
	(165.23,177.32) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (129.50,127.55) --
	(131.42,124.22) --
	(127.57,124.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.27,132.63) --
	(153.19,129.31) --
	(149.35,129.31) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (150.10,149.98) --
	(152.02,146.65) --
	(148.17,146.65) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (151.08,145.91) --
	(153.00,142.58) --
	(149.16,142.58) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,144.41) --
	(190.54,141.08) --
	(186.69,141.08) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (160.49,197.36) --
	(162.41,194.03) --
	(158.57,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (171.53,169.55) --
	(173.45,166.22) --
	(169.60,166.22) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (145.61,176.67) --
	(147.53,173.34) --
	(143.69,173.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (169.57,138.70) --
	(171.49,135.37) --
	(167.65,135.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (153.98,141.47) --
	(155.90,138.14) --
	(152.06,138.14) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (172.69,175.25) --
	(174.61,171.92) --
	(170.77,171.92) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (154.60,163.06) --
	(156.52,159.74) --
	(152.68,159.74) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (178.40,181.08) --
	(180.32,177.75) --
	(176.48,177.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (163.96,171.27) --
	(165.88,167.94) --
	(162.04,167.94) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (172.39,197.36) --
	(174.31,194.03) --
	(170.47,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,188.01) --
	(190.54,184.69) --
	(186.69,184.69) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (137.08,178.99) --
	(139.00,175.67) --
	(135.16,175.67) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (159.87,197.36) --
	(161.79,194.03) --
	(157.95,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,183.54) --
	(190.54,180.21) --
	(186.69,180.21) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (140.40,158.67) --
	(142.32,155.34) --
	(138.48,155.34) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (157.40,197.36) --
	(159.32,194.03) --
	(155.47,194.03) --
	cycle;

\path[fill=fillColor,fill opacity=0.50] (188.62,197.36) --
	(190.54,194.03) --
	(186.69,194.03) --
	cycle;

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.87, 94.39) rectangle ( 93.72, 97.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.87, 94.39) -- ( 93.72, 97.24);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 90.87, 97.24) -- ( 93.72, 94.39);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.44, 95.57) rectangle ( 95.30, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.44, 95.57) -- ( 95.30, 98.43);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] ( 92.44, 98.43) -- ( 95.30, 95.57);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.68,150.84) rectangle (141.54,153.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.68,150.84) -- (141.54,153.70);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (138.68,153.70) -- (141.54,150.84);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.70,119.10) rectangle (113.56,121.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.70,119.10) -- (113.56,121.95);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (110.70,121.95) -- (113.56,119.10);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.56,161.49) rectangle (121.41,164.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.56,161.49) -- (121.41,164.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (118.56,164.34) -- (121.41,161.49);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.28,115.20) rectangle (122.14,118.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.28,115.20) -- (122.14,118.05);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (119.28,118.05) -- (122.14,115.20);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.10,122.49) rectangle (129.96,125.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.10,122.49) -- (129.96,125.34);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (127.10,125.34) -- (129.96,122.49);
\definecolor{drawColor}{RGB}{152,152,152}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 47.03) -- (195.67,202.19);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.66, 47.03) -- ( 41.66, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 43.44, 47.03) -- ( 43.44, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.98, 47.03) -- ( 44.98, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.35, 47.03) -- ( 46.35, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 47.56, 47.03) -- ( 47.56, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 55.57, 47.03) -- ( 55.57, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.26, 47.03) -- ( 60.26, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 63.58, 47.03) -- ( 63.58, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.16, 47.03) -- ( 66.16, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 68.27, 47.03) -- ( 68.27, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.05, 47.03) -- ( 70.05, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 71.59, 47.03) -- ( 71.59, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.95, 47.03) -- ( 72.95, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 74.17, 47.03) -- ( 74.17, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.18, 47.03) -- ( 82.18, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 86.87, 47.03) -- ( 86.87, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 90.19, 47.03) -- ( 90.19, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 92.77, 47.03) -- ( 92.77, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 94.88, 47.03) -- ( 94.88, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 96.66, 47.03) -- ( 96.66, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.20, 47.03) -- ( 98.20, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 99.56, 47.03) -- ( 99.56, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (100.78, 47.03) -- (100.78, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (108.79, 47.03) -- (108.79, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (113.48, 47.03) -- (113.48, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (116.80, 47.03) -- (116.80, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (119.38, 47.03) -- (119.38, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (121.49, 47.03) -- (121.49, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.27, 47.03) -- (123.27, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (124.81, 47.03) -- (124.81, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (126.17, 47.03) -- (126.17, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (127.39, 47.03) -- (127.39, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.40, 47.03) -- (135.40, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (140.08, 47.03) -- (140.08, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (143.41, 47.03) -- (143.41, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.99, 47.03) -- (145.99, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (148.09, 47.03) -- (148.09, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.87, 47.03) -- (149.87, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.42, 47.03) -- (151.42, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (152.78, 47.03) -- (152.78, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (154.00, 47.03) -- (154.00, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (162.01, 47.03) -- (162.01, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (166.69, 47.03) -- (166.69, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (170.02, 47.03) -- (170.02, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (172.60, 47.03) -- (172.60, 52.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (174.70, 47.03) -- (174.70, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (176.48, 47.03) -- (176.48, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (178.03, 47.03) -- (178.03, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.39, 47.03) -- (179.39, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (180.61, 47.03) -- (180.61, 55.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (188.62, 47.03) -- (188.62, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (193.30, 47.03) -- (193.30, 49.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 48.18) -- ( 43.36, 48.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 49.96) -- ( 43.36, 49.96);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 51.51) -- ( 43.36, 51.51);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 52.87) -- ( 43.36, 52.87);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 54.09) -- ( 49.05, 54.09);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 62.10) -- ( 43.36, 62.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 66.78) -- ( 43.36, 66.78);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 70.11) -- ( 43.36, 70.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 72.68) -- ( 46.20, 72.68);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 74.79) -- ( 43.36, 74.79);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 76.57) -- ( 43.36, 76.57);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 78.12) -- ( 43.36, 78.12);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 79.48) -- ( 43.36, 79.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 80.69) -- ( 49.05, 80.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 88.70) -- ( 43.36, 88.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 93.39) -- ( 43.36, 93.39);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 96.71) -- ( 43.36, 96.71);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 99.29) -- ( 46.20, 99.29);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,101.40) -- ( 43.36,101.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,103.18) -- ( 43.36,103.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,104.72) -- ( 43.36,104.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,106.08) -- ( 43.36,106.08);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,107.30) -- ( 49.05,107.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,115.31) -- ( 43.36,115.31);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,120.00) -- ( 43.36,120.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,123.32) -- ( 43.36,123.32);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,125.90) -- ( 46.20,125.90);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,128.01) -- ( 43.36,128.01);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,129.79) -- ( 43.36,129.79);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,131.33) -- ( 43.36,131.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,132.69) -- ( 43.36,132.69);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,133.91) -- ( 49.05,133.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,141.92) -- ( 43.36,141.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,146.61) -- ( 43.36,146.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,149.93) -- ( 43.36,149.93);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,152.51) -- ( 46.20,152.51);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,154.62) -- ( 43.36,154.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,156.40) -- ( 43.36,156.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,157.94) -- ( 43.36,157.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,159.30) -- ( 43.36,159.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,160.52) -- ( 49.05,160.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,168.53) -- ( 43.36,168.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,173.21) -- ( 43.36,173.21);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,176.54) -- ( 43.36,176.54);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,179.12) -- ( 46.20,179.12);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,181.22) -- ( 43.36,181.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,183.01) -- ( 43.36,183.01);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,184.55) -- ( 43.36,184.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,185.91) -- ( 43.36,185.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,187.13) -- ( 49.05,187.13);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,195.14) -- ( 43.36,195.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51,199.82) -- ( 43.36,199.82);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 47.03) rectangle (195.67,202.19);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 77.66) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,130.88) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,184.10) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 80.69) --
	( 40.51, 80.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,133.91) --
	( 40.51,133.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,187.13) --
	( 40.51,187.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.17, 44.28) --
	( 74.17, 47.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.39, 44.28) --
	(127.39, 47.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (180.61, 44.28) --
	(180.61, 47.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 74.17, 36.02) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.39, 36.02) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (180.61, 36.02) {1000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (118.09, 23.99) {\textsf{DPMC} + \texttt{bklm16} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,124.61) {\textsf{DPMC} + \texttt{bklm16++} time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (206.67, 68.14) rectangle (298.03,181.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,145.91) rectangle (226.62,160.37);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.50] (219.39,153.14) circle (  1.43);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,131.46) rectangle (226.62,145.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.50] (219.39,140.90) --
	(221.32,137.58) --
	(217.47,137.58) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,117.00) rectangle (226.62,131.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.50] (217.97,122.80) --
	(220.82,122.80) --
	(220.82,125.66) --
	(217.97,125.66) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17,102.55) rectangle (226.62,117.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.38,109.78) -- (221.41,109.78);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (219.39,107.76) -- (219.39,111.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17, 88.10) rectangle (226.62,102.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 93.90) rectangle (220.82, 96.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 93.90) -- (220.82, 96.75);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 96.75) -- (220.82, 93.90);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.17, 73.64) rectangle (226.62, 88.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 79.44) -- (220.82, 82.30);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.97, 82.30) -- (220.82, 79.44);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (217.38, 80.87) -- (221.41, 80.87);

\path[draw=drawColor,draw opacity=0.50,line width= 0.4pt,line join=round,line cap=round] (219.39, 78.85) -- (219.39, 82.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,150.11) {DQMR};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,135.65) {Grid};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,121.20) {Mastermind};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12,106.75) {Non-binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12, 92.29) {Other binary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (232.12, 77.84) {Random Blocks};
\end{scope}
\end{tikzpicture}

### 2021-06-13 doc/SAT_long_talk/talk.tex
Started working on slides for SAT

--- 2021-05-31 doc/long_talk/talk.tex
@@
 \usepackage{tikz}
-\usepackage{minibox}
 \usepackage{listings}
 \usepackage{complexity}
+\usepackage{mathtools}
+\usepackage{booktabs}
 
 \beamertemplatenavigationsymbolsempty
-\usetheme{Madrid}
-\usecolortheme{orchid}
+\usetheme{boxes}
+\usecolortheme{rose}
 
@@
 \usetikzlibrary{arrows.meta}
-\usetikzlibrary{positioning}
 \usetikzlibrary{shapes}
@@
 \author[P. Dilkas, V. Belle]{\textbf{Paulius Dilkas} \and Vaishak Belle}
-\title[WMC with Conditional Weights for BNs]{Weighted Model Counting with
-  Conditional Weights for Bayesian Networks}
-\date{UAI 2021}
+\title{Weighted Model Counting Without Parameter Variables}
+\date{SAT 2021}
 \institute[University of Edinburgh]{University of Edinburgh, Edinburgh, UK}
+
+\AtBeginSection[]
+{
+  \begin{frame}
+    \frametitle{Outline}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 
@@
 
-\begin{frame}[noframenumbering,plain]
+\begin{frame}
   \tikz[remember picture,overlay]{
-    \node at ([yshift=25pt,xshift=30pt]current page.south)
+    \node at ([yshift=35pt,xshift=30pt]current page.south)
     {\includegraphics[height=40pt]{../poster/logo_inf.png}};
-    \node at ([yshift=25pt,xshift=75pt]current page.south)
+    \node at ([yshift=35pt,xshift=75pt]current page.south)
     {\includegraphics[height=40pt]{../poster/logo_ecr.png}};
-    \node at ([yshift=20pt,xshift=140pt]current page.south)
+    \node at ([yshift=30pt,xshift=140pt]current page.south)
     {\includegraphics[height=20pt]{../poster/logo_ukri.png}};
@@
 
+% ~15 slides
+% Section: Motivation
+% * the problem of computing probability,
+% * WMC (perhaps with a bigger example of a BN encoding, to emphasise the clutter)
+% Section: An Alternative Formulation
+% * Definition of WMC and MC-WMC
+% * Pseudo-Boolean functions, my notation, PBP instance
+% Section: Correctness
+% Section: Experimental Results
+% * Cactus plot
+% * Scatter plots
+% * Box plots
+% * Summary
+
 \begin{frame}[fragile]{The Problem of Computing Probability}
@@
   \begin{columns}[t]
-    \begin{column}{0.6\textwidth}
+    \begin{column}{0.65\textwidth}
       \centering
       \begin{block}{ProbLog}
-        \vspace{-0.3cm}
+        \vspace{-0.2cm}
         \begin{lstlisting}[basicstyle=\tiny]
@@
       \begin{block}{BLOG}
-        \vspace{-0.3cm}
+        \vspace{-0.2cm}
         \begin{lstlisting}[escapeinside={(*}{*)},basicstyle=\tiny]
@@
 
-% BAs, pseudo-Boolean functions, measures, equivalence of definitions
-\begin{frame}{An Alternative Way to Think About It}
+\begin{frame}
+  \frametitle{Outline}
+  \tableofcontents
 \end{frame}
 
-% The theorems: WMC is not expressive enough to cover all measures but can be
-% extended to do so
-\begin{frame}{Some Theoretical Results}
+\section{An Alternative Formulation}
+
+\begin{frame}{Formalising the Intuition from Before}
+  For any propositional formula \structure{$\phi$} over a set of variables
+  \structure{$X$} and \structure{$p, q \in \mathbb{R}$}, let
+  \structure{$[\phi]^p_q\colon 2^X \to \mathbb{R}$} be the pseudo-Boolean
+  function defined as
+  \[
+    [\phi]^p_q(Y) \coloneqq
+    \begin{cases}
+      p & \text{if } Y \models \phi \\
+      q & \text{otherwise}
+    \end{cases}
+  \]
+  for any \structure{$Y \subseteq X$}.
+
+  \begin{definition}[Pseudo-Boolean Projection (PBP)]
+    A \alert{PBP instance} is a tuple \structure{$(F, X, \omega)$}, where
+    \structure{$X$} is the set of variables, \structure{$F$} is a set of
+    two-valued pseudo-Boolean functions \structure{$2^X \to \mathbb{R}$}, and
+    \structure{$\omega \in \mathbb{R}$} is the scaling factor.
+  \end{definition}
 \end{frame}
 
-% Things I could mention:
-% The details of the transformation
-% Experimental results
+\begin{frame}{From WMC to PBP}
+  The WMC instance has \structure{$x$} as the only \alert{indicator} variable
+  and \structure{$p$}, \structure{$q$} as \alert{parameter} variables with
+  weights \structure{$w(p) = 0.2$}, \structure{$w(q) = 0.8$}, and
+  \structure{$w(\neg p) = w(\neg q) = 1$}.
+  \begin{center}
+    \begin{tabular}{llll}
+      \toprule
+      WMC Clause & \onslide<2->{In CNF} & \onslide<3->{Pseudo-Boolean Function} & \\
+      \midrule
+      $\neg x \Rightarrow p$ & \onslide<2->{$x \lor p$} & \onslide<3->{$[\neg x]_1^{0.2}$} & \\
+      $p \Rightarrow \neg x$ & \onslide<2->{$\neg x \lor \neg p$} & & \onslide<4->{$[x]^{0.8}_{0.2}$} \\
+      $x \Rightarrow q$ & \onslide<2->{$\neg x \lor q$} & \onslide<3->{$[x]_1^{0.8}$} & \\
+      $q \Rightarrow x$ & \onslide<2->{$x \lor \neg q$} & & \\
+      $\neg x$ & \onslide<2->{$\neg x$} & \onslide<3->{$[\neg x]_0^1$} & \onslide<4->{$[\neg x]_0^1$} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{frame}
 
-\begin{frame}{The Big Picture}
-  \begin{columns}
-    \begin{column}{0.35\textwidth}
+\section{Correctness}
+
+\section{Experimental Results}
+
+\begin{frame}{Experimental Results}
   \centering
-      \structure{Probabilistic Inference} \\
-      (e.g., a Bayesian network)
-      \fbox{
-        \begin{minipage}{2.5cm}
+  \input{cumulative}
+\end{frame}
+
+\begin{frame}{Experimental Results}
   \centering
-          \begin{tikzpicture}[edge from parent/.style={draw,-{Latex}}]
-            \node[draw,circle] at (0, 0) (a) {$A$}
-            child {node[draw,circle] (b) {$B$}};
-          \end{tikzpicture}\\
-          Find \alert{$\Pr(B = 0)$}
-        \end{minipage}
-      }
-    \end{column}
-    \begin{column}{0.35\textwidth}
+  \input{scatter1}
+\end{frame}
+
+\begin{frame}{Experimental Results}
   \centering
-      \structure{WMC Encoding} \\
-      (CNF with literal weights)
-      \framebox{
-        \scalebox{0.2}{
-          \begin{tabular}{@{}l@{}}
-            p cnf 8 17 \\
-            -2 -1 0 \\
-            1 2 0 \\
-            -3 1 0 \\
-            -1 3 0 \\
-            -5 -1 0 \\
-            -5 -4 0 \\
-            1 4 5 0 \\
-            -6 -1 0 \\
-            -6 4 0 \\
-            -4 1 6 0 \\
-            -7 1 0 \\
-            -7 -4 0 \\
-            -1 4 7 0 \\
-            -8 1 0 \\
-            -8 4 0 \\
-            -4 -1 8 0 \\
-            -4 0 \\
-            c weights 1.0 1.0 0.5 1.0 0.5 1.0 1.0 1.0 0.6 1.0 0.4 1.0 0.1 1.0 0.9 1.0
-          \end{tabular}%
-        }
-      }
+  \input{scatter2}
+\end{frame}
 
-      \vspace{1cm}
-      \onslide<2>{
-      \structure{Conditional Weights} \\
-      \framebox{
-        \scalebox{0.2}{%
-          \begin{tabular}{@{}l@{}}
-            p cnf 2 1 \\
-            2 0 \\
-            w 1 0.5 0.5 \\
-            w 2 1 0.6 0.4 \\
-            w 2 -1 0.1 0.9
-          \end{tabular}%
-        }
-      }
-      }
-    \end{column}
-    \begin{column}{0.30\textwidth}
-      \centering
-      \structure{WMC Algorithm}\\
-      \onslide<2>{\alert{$>100\times$} faster}
-    \end{column}
-  \end{columns}
-  \begin{tikzpicture}[remember picture,overlay]
-    \draw[-{Latex}] (3.4, 3) -- (4.9, 4);
-    \draw<2>[-{Latex}] (3.4, 3) to [bend right] (5.8, 0.2);
-    \draw[-{Latex}] (7.7, 4) -- (9, 2.8);
-    \draw<2>[-{Latex}] (6.7, 0.2) to [bend right = 45] (9, 2.8);
-  \end{tikzpicture}
+\section{Summary}
+
+\begin{frame}{Summary}
 \end{frame}
+
 \end{document}

### 2021-06-13 tools/SAT_plots.R

@@ -174,12 +174,21 @@ scatter_plot <- function(df, x_column, y_column, x_name, y_name,
     scale_color_brewer(palette = "Dark2")
 }
 
+# For the paper
 p1 <- scatter_plot(df, "time_old_cd06", "time_new_bklm16pp", "\\textsf{Ace} + \\texttt{cd06} time (s)",
                    "\\textsf{DPMC} + \\texttt{bklm16++} time (s)", 2 * TIMEOUT)
 p2 <- scatter_plot(df, "time_new_bklm16", "time_new_bklm16pp", "\\textsf{DPMC} + \\texttt{bklm16} time (s)",
                    "\\textsf{DPMC} + \\texttt{bklm16++} time (s)", 2 * TIMEOUT)
 tikz(file = "../doc/SAT_paper/scatter.tex", width = 4.8, height = 2.9, standAlone = TRUE)
 ggarrange(p1, p2, ncol = 2, nrow = 1, common.legend = TRUE, legend = "bottom")
+dev.off()
+
+# For slides
+tikz(file = "../doc/SAT_long_talk/scatter1.tex", width = 4.2, height = 3.1)
+scatter_plot(df, "time_old_cd06", "time_new_bklm16pp", "\\textsf{Ace} + \\texttt{cd06} time (s)", "\\textsf{DPMC} + \\texttt{bklm16++} time (s)", 2 * TIMEOUT)
+dev.off()
+tikz(file = "../doc/SAT_long_talk/scatter2.tex", width = 4.2, height = 3.1)
+scatter_plot(df, "time_new_bklm16", "time_new_bklm16pp", "\\textsf{DPMC} + \\texttt{bklm16} time (s)", "\\textsf{DPMC} + \\texttt{bklm16++} time (s)", 2 * TIMEOUT)
 dev.off()
 
 scatter_plot(df, "time_new_d02pp", "time_new_d02", "\\texttt{d02++} time (s)",
@@ -267,7 +276,7 @@ cumulative_plot <- function(df, column_name, pretty_column_name, variable, varia
 }
 
 #tikz(file = "../doc/SAT_paper/cumulative.tex", width = 4.8, height = 2.3, standAlone = TRUE)
-tikz(file = "../doc/SAT_talk/cumulative.tex", width = 4.2, height = 3.1)
+tikz(file = "../doc/SAT_long_talk/cumulative.tex", width = 4.2, height = 3.1)
[…]

### 2021-06-14 doc/SAT_long_talk/box.tex
Some TikZ

% Created by tikzDevice version 0.12.3.1 on 2021-06-14 12:12:55
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,224.04);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,224.04);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 33.38) rectangle (298.03,218.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 33.38) rectangle (298.03,218.54);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 73.27) --
	(298.03, 73.27);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,136.86) --
	(298.03,136.86);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,200.45) --
	(298.03,200.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 41.48) --
	(298.03, 41.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,105.07) --
	(298.03,105.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,168.66) --
	(298.03,168.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.22, 33.38) --
	( 70.22,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (119.75, 33.38) --
	(119.75,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.27, 33.38) --
	(169.27,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (218.80, 33.38) --
	(218.80,218.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.32, 33.38) --
	(268.32,218.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.94,178.58) -- ( 60.94,327.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.94, 52.60) -- ( 60.94, 42.30);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 52.58,178.58) --
	( 52.58, 52.60) --
	( 69.30, 52.60) --
	( 69.30,178.58) --
	( 52.58,178.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.58, 89.33) -- ( 69.30, 89.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.51, 92.86) -- ( 79.51,158.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.51, 45.93) -- ( 79.51, 41.79);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 71.15, 92.86) --
	( 71.15, 45.93) --
	( 87.87, 45.93) --
	( 87.87, 92.86) --
	( 71.15, 92.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 71.15, 53.43) -- ( 87.87, 53.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (110.46,185.67) -- (110.46,366.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (110.46, 54.83) -- (110.46, 42.49);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (102.11,185.67) --
	(102.11, 54.83) --
	(118.82, 54.83) --
	(118.82,185.67) --
	(102.11,185.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (102.11, 92.03) -- (118.82, 92.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.03,160.26) -- (129.03,292.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.03, 50.38) -- (129.03, 42.21);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (120.68,160.26) --
	(120.68, 50.38) --
	(137.39, 50.38) --
	(137.39,160.26) --
	(120.68,160.26) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.68, 66.91) -- (137.39, 66.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.99,185.77) -- (159.99,366.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.99, 54.83) -- (159.99, 42.49);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (151.63,185.77) --
	(151.63, 54.83) --
	(168.34, 54.83) --
	(168.34,185.77) --
	(151.63,185.77) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (151.63, 92.03) -- (168.34, 92.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.56,160.26) -- (178.56,292.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.56, 50.38) -- (178.56, 42.21);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (170.20,160.26) --
	(170.20, 50.38) --
	(186.91, 50.38) --
	(186.91,160.26) --
	(170.20,160.26) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (170.20, 66.91) -- (186.91, 66.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.51,164.59) -- (209.51,306.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.51, 50.38) -- (209.51, 42.18);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (201.15,164.59) --
	(201.15, 50.38) --
	(217.87, 50.38) --
	(217.87,164.59) --
	(201.15,164.59) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (201.15, 75.53) -- (217.87, 75.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.08, 99.15) -- (228.08,158.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.08, 45.93) -- (228.08, 41.79);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (219.72, 99.15) --
	(219.72, 45.93) --
	(236.44, 45.93) --
	(236.44, 99.15) --
	(219.72, 99.15) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (219.72, 54.19) -- (236.44, 54.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.32,132.06) -- (268.32,244.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.32, 48.15) -- (268.32, 41.98);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (251.61,132.06) --
	(251.61, 48.15) --
	(285.03, 48.15) --
	(285.03,132.06) --
	(251.61,132.06) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (251.61, 69.27) -- (285.03, 69.27);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (298.03,218.54);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 38.45) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,102.04) {2000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,165.63) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 41.48) --
	( 40.51, 41.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,105.07) --
	( 40.51,105.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,168.66) --
	( 40.51,168.66);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.22, 30.63) --
	( 70.22, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (119.75, 30.63) --
	(119.75, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.27, 30.63) --
	(169.27, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (218.80, 30.63) --
	(218.80, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.32, 30.63) --
	(268.32, 33.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.22, 22.37) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.75, 22.37) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (169.27, 22.37) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.80, 22.37) {\texttt{d02}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (268.32, 22.37) {\texttt{sbk05}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,125.96) {Variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (123.14,  5.50) rectangle (215.40, -2.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (128.64,  5.50) rectangle (143.10, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.87,  6.95) --
	(135.87,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.87, 16.34) --
	(135.87, 18.51);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (130.45,  9.11) rectangle (141.29, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (130.45, 12.73) --
	(141.29, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (177.58,  5.50) rectangle (192.04, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.81,  6.95) --
	(184.81,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.81, 16.34) --
	(184.81, 18.51);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (179.39,  9.11) rectangle (190.23, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.39, 12.73) --
	(190.23, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (148.60,  9.70) {before};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (197.54,  9.70) {after};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-06-14 doc/SAT_long_talk/talk.tex
Some TikZ

@@
 \usepackage{booktabs}
+\usepackage{xcolor}
 
@@
 \usetikzlibrary{shapes}
+\usetikzlibrary{positioning}
+\usetikzlibrary{tikzmark}
+\usetikzmarklibrary{listings}
+
+\tikzstyle{every picture}+=[remember picture]
+
+\newcounter{tmkcount}
+\tikzset{
+  use tikzmark/.style={
+    remember picture,
+    overlay,
+    execute at end picture={
+      \stepcounter{tmkcount}
+    },
+  },
+  tikzmark suffix={-\thetmkcount}
+}
+
+\definecolor{color1}{HTML}{1b9e77}
+\def\speciallstcolor{\begingroup\color{color1}}
+\def\endspeciallstcolor{\endgroup}
+
+\definecolor{color2}{HTML}{d95f02}
+\def\speciallstcolortwo{\begingroup\color{color2}}
+\def\endspeciallstcolortwo{\endgroup}
+
+\definecolor{color3}{HTML}{7570b3}
+\def\speciallstcolorthree{\begingroup\color{color3}}
+\def\endspeciallstcolorthree{\endgroup}
+
+\definecolor{color4}{HTML}{e7298a}
+\def\speciallstcolorfour{\begingroup\color{color4}}
+\def\endspeciallstcolorfour{\endgroup}
+
+\definecolor{color5}{HTML}{66a61e}
+\def\speciallstcolorfive{\begingroup\color{color5}}
+\def\endspeciallstcolorfive{\endgroup}
+
+\definecolor{color6}{HTML}{e6ab02}
+\def\speciallstcolorsix{\begingroup\color{color6}}
+\def\endspeciallstcolorsix{\endgroup}
+
+\definecolor{color7}{HTML}{a6761d}
+\def\speciallstcolorseven{\begingroup\color{color7}}
+\def\endspeciallstcolorseven{\endgroup}
 
@@
 \end{frame}
-
-% ~15 slides
-% Section: Motivation
-% * the problem of computing probability,
-% * WMC (perhaps with a bigger example of a BN encoding, to emphasise the clutter)
-% Section: An Alternative Formulation
-% * Definition of WMC and MC-WMC
-% * Pseudo-Boolean functions, my notation, PBP instance
-% Section: Correctness
-% Section: Experimental Results
-% * Cactus plot
-% * Scatter plots
-% * Box plots
-% * Summary
 
@@
 
+\begin{frame}[fragile]{The Problem with Assigning Weights to Literals}
+  \begin{columns}[t]
+    \begin{column}{0.5\textwidth}
+      \begin{block}{A Simple Bayesian Network}
+        \centering
+        \begin{tikzpicture}[edge from parent/.style={draw,-{Latex}}]
+          \node[draw,circle] at (0, 0) (a) {$A$}
+          child {node[draw,circle] (b) {$B$}};
+        \end{tikzpicture}
+      \end{block}
+      \begin{itemize}
+      \item from \structure{2 binary} variables
+      \item to \structure{8} variables and \structure{17} clauses
+      \item with lots of redundancy
+      \end{itemize}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \begin{block}{Its WMC Encoding}
+        \vspace{-0.2cm}
+\begin{lstlisting}[basicstyle=\scriptsize,escapeinside={(*}{*)},name=codeL]
+p cnf 8 17
+(*\only<2->{\aftergroup\speciallstcolor}*)-2 -1 0(*\only<2->{\aftergroup\endspeciallstcolor}*)
+(*\only<2->{\aftergroup\speciallstcolor}*)1 2 0(*\only<2->{\aftergroup\endspeciallstcolor}*)
+(*\only<2->{\aftergroup\speciallstcolortwo}*)-3 1 0(*\only<2->{\aftergroup\endspeciallstcolortwo}*)
+(*\only<2->{\aftergroup\speciallstcolortwo}*)-1 3 0(*\only<2->{\aftergroup\endspeciallstcolortwo}*)
+(*\only<2->{\aftergroup\speciallstcolorthree}*)-5 -1 0(*\only<2->{\aftergroup\endspeciallstcolorthree}*)
+(*\only<2->{\aftergroup\speciallstcolorthree}*)-5 -4 0(*\only<2->{\aftergroup\endspeciallstcolorthree}*)
+(*\only<2->{\aftergroup\speciallstcolorthree}*)1 4 5 0(*\only<2->{\aftergroup\endspeciallstcolorthree}*)
+(*\only<2->{\aftergroup\speciallstcolorfour}*)-6 -1 0(*\only<2->{\aftergroup\endspeciallstcolorfour}*)
+(*\only<2->{\aftergroup\speciallstcolorfour}*)-6 4 0(*\only<2->{\aftergroup\endspeciallstcolorfour}*)
+(*\only<2->{\aftergroup\speciallstcolorfour}*)-4 1 6 0(*\only<2->{\aftergroup\endspeciallstcolorfour}*)
+(*\only<2->{\aftergroup\speciallstcolorfive}*)-7 1 0(*\only<2->{\aftergroup\endspeciallstcolorfive}*)
+(*\only<2->{\aftergroup\speciallstcolorfive}*)-7 -4 0(*\only<2->{\aftergroup\endspeciallstcolorfive}*)
+(*\only<2->{\aftergroup\speciallstcolorfive}*)-1 4 7 0(*\only<2->{\aftergroup\endspeciallstcolorfive}*)
+(*\only<2->{\aftergroup\speciallstcolorsix}*)-8 1 0(*\only<2->{\aftergroup\endspeciallstcolorsix}*)
+(*\only<2->{\aftergroup\speciallstcolorsix}*)-8 4 0(*\only<2->{\aftergroup\endspeciallstcolorsix}*)
+(*\only<2->{\aftergroup\speciallstcolorsix}*)-4 -1 8 0(*\only<2->{\aftergroup\endspeciallstcolorsix}*)
+(*\only<2->{\aftergroup\speciallstcolorseven}*)-4 0(*\only<2->{\aftergroup\endspeciallstcolorseven}*)
+c weights 1.0 1.0 0.5 1.0 \
+0.5 1.0 1.0 1.0 0.6 1.0 \
+0.4 1.0 0.1 1.0 0.9 1.0
+\end{lstlisting}
+        \vspace{-0.2cm}
+      \end{block}
+    \end{column}
+  \end{columns}
+  \only<2->{
+    \begin{tikzpicture}[overlay,use tikzmark]
+      \node[above right = 0 and 15 mm of pic cs:line-codeL-3-end] {\color{color1}{$\neg x_1 \Leftrightarrow x_2$}};
+      \node[above right = 0 and 15 mm of pic cs:line-codeL-5-end] {\color{color2}{$x_1 \Leftrightarrow x_3$}};
+      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-8-end] {\color{color3}{$\neg x_1 \land \neg x_4 \Leftrightarrow x_5$}};
+      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-11-end] {\color{color4}{$\neg x_1 \land x_4 \Leftrightarrow x_6$}};
+      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-14-end] {\color{color5}{$x_1 \land \neg x_4 \Leftrightarrow x_7$}};
+      \node[above right = 0.5 ex and 10 mm of pic cs:line-codeL-17-end] {\color{color6}{$x_1 \land x_4 \Leftrightarrow x_8$}};
+      \node[above right = -0.5 ex and 20 mm of pic cs:line-codeL-18-end] {\color{color7}{$\neg x_4$}};
+    \end{tikzpicture}
+  }
+\end{frame}
+
 \begin{frame}
@@
 \section{An Alternative Formulation}
+% TODO: Definition of WMC and MC-WMC
 
@@
 \begin{frame}{From WMC to PBP}
-  The WMC instance has \structure{$x$} as the only \alert{indicator} variable
-  and \structure{$p$}, \structure{$q$} as \alert{parameter} variables with
-  weights \structure{$w(p) = 0.2$}, \structure{$w(q) = 0.8$}, and
-  \structure{$w(\neg p) = w(\neg q) = 1$}.
+  \begin{example}
+    \begin{itemize}
+    \item Indicator variable: \structure{$x$}
+    \item Parameter variables: \structure{$p$}, \structure{$q$}
+    \item Weights: \structure{$w(p) = 0.2$}, \structure{$w(q) = 0.8$}, and \structure{$w(\neg p) = w(\neg q) = 1$}
+    \end{itemize}
     \begin{center}
@@
     \end{center}
+  \end{example}
 \end{frame}
@@
   \centering
-  \input{cumulative}
+  \includegraphics[width=\textwidth]{cumulative}
 \end{frame}
@@
   \centering
-  \input{scatter1}
+  \includegraphics[width=\textwidth]{scatter1}
 \end{frame}
@@
   \centering
-  \input{scatter2}
+  \includegraphics[width=\textwidth]{scatter2}
 \end{frame}
+
+\begin{frame}{Experimental Results}
+  \centering
+  \includegraphics[width=\textwidth]{box}
+\end{frame}
+% TODO: fit the plot to the left half of the slide, add observations on the
+% right
 

### 2021-06-14 tools/SAT_plots.R

@@ -184,10 +184,10 @@ ggarrange(p1, p2, ncol = 2, nrow = 1, common.legend = TRUE, legend = "bottom")
 dev.off()
 
 # For slides
-tikz(file = "../doc/SAT_long_talk/scatter1.tex", width = 4.2, height = 3.1)
+tikz(file = "../doc/SAT_long_talk/scatter1.tex", width = 4.2, height = 3.1, standAlone = TRUE)
 scatter_plot(df, "time_old_cd06", "time_new_bklm16pp", "\\textsf{Ace} + \\texttt{cd06} time (s)", "\\textsf{DPMC} + \\texttt{bklm16++} time (s)", 2 * TIMEOUT)
 dev.off()
-tikz(file = "../doc/SAT_long_talk/scatter2.tex", width = 4.2, height = 3.1)
+tikz(file = "../doc/SAT_long_talk/scatter2.tex", width = 4.2, height = 3.1, standAlone = TRUE)
 scatter_plot(df, "time_new_bklm16", "time_new_bklm16pp", "\\textsf{DPMC} + \\texttt{bklm16} time (s)", "\\textsf{DPMC} + \\texttt{bklm16++} time (s)", 2 * TIMEOUT)
 dev.off()
 
@@ -276,7 +276,7 @@ cumulative_plot <- function(df, column_name, pretty_column_name, variable, varia
 }
 
 #tikz(file = "../doc/SAT_paper/cumulative.tex", width = 4.8, height = 2.3, standAlone = TRUE)
-tikz(file = "../doc/SAT_long_talk/cumulative.tex", width = 4.2, height = 3.1)
+tikz(file = "../doc/SAT_long_talk/cumulative.tex", width = 4.2, height = 3.1, standAlone = TRUE)
 cumulative_plot(data_sum, "encoding", "Encoding", "time", "Time (s)", TRUE, TRUE, "right")
 dev.off()
 

### 2021-06-14 tools/SAT_plots_2.R

@@ -75,7 +75,8 @@ df2$variable <- as.factor(df2$variable)
 df2$variable <- factor(df2$variable, levels = rev(levels(df2$variable)))
 df2$encoding <- paste0("\\texttt{", df2$encoding, "}")
 
-tikz(file = "../doc/paper3/box.tex", width = 2.4, height = 2, standAlone = TRUE)
+tikz(file = "../doc/SAT_paper/box.tex", width = 2.4, height = 2, standAlone = TRUE)
+tikz(file = "../doc/SAT_long_talk/box.tex", width = 4.2, height = 3.1, standAlone = TRUE)
 ggplot(df2, aes(encoding, value, fill = variable)) +
   geom_boxplot(outlier.shape = NA) +
   theme_light() +
@@ -87,7 +88,7 @@ ggplot(df2, aes(encoding, value, fill = variable)) +
   theme(legend.position = "bottom", legend.margin=margin(t = -0.8, unit = 'cm'))
 dev.off()
 
-tikz(file = "../doc/paper3/variable_scatter.tex", width = 3.2, height = 2.9)
+tikz(file = "../doc/SAT_paper/variable_scatter.tex", width = 3.2, height = 2.9)
 scatter(changes[changes$encoding == "bklm16",], "before_variables", "after_variables")
 dev.off()
 

### 2021-06-17 doc/SAT_long_talk/box.tex
Slides for the long SAT talk are almost finished

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-06-14 12:12:55
+% Created by tikzDevice version 0.12.3.1 on 2021-06-17 09:56:52
 % !TEX encoding = UTF-8 Unicode
@@
 
-\begin{tikzpicture}[x=1pt,y=1pt]
+\end{document}
+re}[x=1pt,y=1pt]
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,224.04);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (180.67,224.04);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (180.68,224.04);
 \end{scope}
 \begin{scope}
-\path[clip] ( 40.51, 33.38) rectangle (298.03,218.54);
+\path[clip] ( 40.51, 33.38) rectangle (175.17,218.54);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 40.51, 33.38) rectangle (298.03,218.54);
+\path[fill=fillColor] ( 40.51, 33.38) rectangle (175.17,218.54);
 \definecolor{drawColor}{gray}{0.87}
@@
 \path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 73.27) --
-	(298.03, 73.27);
+	(175.17, 73.27);
 
 \path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,136.86) --
-	(298.03,136.86);
+	(175.17,136.86);
 
 \path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,200.45) --
-	(298.03,200.45);
+	(175.17,200.45);
 
 \path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 41.48) --
-	(298.03, 41.48);
+	(175.17, 41.48);
 
 \path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,105.07) --
-	(298.03,105.07);
+	(175.17,105.07);
 
 \path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,168.66) --
-	(298.03,168.66);
+	(175.17,168.66);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.22, 33.38) --
-	( 70.22,218.54);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 56.05, 33.38) --
+	( 56.05,218.54);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (119.75, 33.38) --
-	(119.75,218.54);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 81.95, 33.38) --
+	( 81.95,218.54);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (169.27, 33.38) --
-	(169.27,218.54);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (107.84, 33.38) --
+	(107.84,218.54);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (218.80, 33.38) --
-	(218.80,218.54);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (133.74, 33.38) --
+	(133.74,218.54);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (268.32, 33.38) --
-	(268.32,218.54);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (159.64, 33.38) --
+	(159.64,218.54);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.94,178.58) -- ( 60.94,327.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.19,178.58) -- ( 51.19,327.32);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.94, 52.60) -- ( 60.94, 42.30);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.19, 52.60) -- ( 51.19, 42.30);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 52.58,178.58) --
-	( 52.58, 52.60) --
-	( 69.30, 52.60) --
-	( 69.30,178.58) --
-	( 52.58,178.58) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 46.82,178.58) --
+	( 46.82, 52.60) --
+	( 55.56, 52.60) --
+	( 55.56,178.58) --
+	( 46.82,178.58) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.58, 89.33) -- ( 69.30, 89.33);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.82, 89.33) -- ( 55.56, 89.33);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.51, 92.86) -- ( 79.51,158.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.90, 92.86) -- ( 60.90,158.87);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.51, 45.93) -- ( 79.51, 41.79);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.90, 45.93) -- ( 60.90, 41.79);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 71.15, 92.86) --
-	( 71.15, 45.93) --
-	( 87.87, 45.93) --
-	( 87.87, 92.86) --
-	( 71.15, 92.86) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 56.53, 92.86) --
+	( 56.53, 45.93) --
+	( 65.27, 45.93) --
+	( 65.27, 92.86) --
+	( 56.53, 92.86) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 71.15, 53.43) -- ( 87.87, 53.43);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 56.53, 53.43) -- ( 65.27, 53.43);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (110.46,185.67) -- (110.46,366.43);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.09,185.67) -- ( 77.09,366.43);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (110.46, 54.83) -- (110.46, 42.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.09, 54.83) -- ( 77.09, 42.49);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (102.11,185.67) --
-	(102.11, 54.83) --
-	(118.82, 54.83) --
-	(118.82,185.67) --
-	(102.11,185.67) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 72.72,185.67) --
+	( 72.72, 54.83) --
+	( 81.46, 54.83) --
+	( 81.46,185.67) --
+	( 72.72,185.67) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (102.11, 92.03) -- (118.82, 92.03);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 72.72, 92.03) -- ( 81.46, 92.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.03,160.26) -- (129.03,292.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.80,160.26) -- ( 86.80,292.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.03, 50.38) -- (129.03, 42.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.80, 50.38) -- ( 86.80, 42.21);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (120.68,160.26) --
-	(120.68, 50.38) --
-	(137.39, 50.38) --
-	(137.39,160.26) --
-	(120.68,160.26) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 82.43,160.26) --
+	( 82.43, 50.38) --
+	( 91.17, 50.38) --
+	( 91.17,160.26) --
+	( 82.43,160.26) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (120.68, 66.91) -- (137.39, 66.91);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 82.43, 66.91) -- ( 91.17, 66.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.99,185.77) -- (159.99,366.43);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.99,185.77) -- (102.99,366.43);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.99, 54.83) -- (159.99, 42.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.99, 54.83) -- (102.99, 42.49);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (151.63,185.77) --
-	(151.63, 54.83) --
-	(168.34, 54.83) --
-	(168.34,185.77) --
-	(151.63,185.77) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 98.62,185.77) --
+	( 98.62, 54.83) --
+	(107.36, 54.83) --
+	(107.36,185.77) --
+	( 98.62,185.77) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (151.63, 92.03) -- (168.34, 92.03);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 98.62, 92.03) -- (107.36, 92.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.56,160.26) -- (178.56,292.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (112.70,160.26) -- (112.70,292.03);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.56, 50.38) -- (178.56, 42.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (112.70, 50.38) -- (112.70, 42.21);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (170.20,160.26) --
-	(170.20, 50.38) --
-	(186.91, 50.38) --
-	(186.91,160.26) --
-	(170.20,160.26) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (108.33,160.26) --
+	(108.33, 50.38) --
+	(117.07, 50.38) --
+	(117.07,160.26) --
+	(108.33,160.26) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (170.20, 66.91) -- (186.91, 66.91);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (108.33, 66.91) -- (117.07, 66.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.51,164.59) -- (209.51,306.11);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.88,164.59) -- (128.88,306.11);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.51, 50.38) -- (209.51, 42.18);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.88, 50.38) -- (128.88, 42.18);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (201.15,164.59) --
-	(201.15, 50.38) --
-	(217.87, 50.38) --
-	(217.87,164.59) --
-	(201.15,164.59) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (124.51,164.59) --
+	(124.51, 50.38) --
+	(133.25, 50.38) --
+	(133.25,164.59) --
+	(124.51,164.59) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (201.15, 75.53) -- (217.87, 75.53);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (124.51, 75.53) -- (133.25, 75.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.08, 99.15) -- (228.08,158.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (138.60, 99.15) -- (138.60,158.87);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.08, 45.93) -- (228.08, 41.79);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (138.60, 45.93) -- (138.60, 41.79);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (219.72, 99.15) --
-	(219.72, 45.93) --
-	(236.44, 45.93) --
-	(236.44, 99.15) --
-	(219.72, 99.15) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.23, 99.15) --
+	(134.23, 45.93) --
+	(142.97, 45.93) --
+	(142.97, 99.15) --
+	(134.23, 99.15) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (219.72, 54.19) -- (236.44, 54.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (134.23, 54.19) -- (142.97, 54.19);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (268.32,132.06) -- (268.32,244.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.64,132.06) -- (159.64,244.08);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (268.32, 48.15) -- (268.32, 41.98);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.64, 48.15) -- (159.64, 41.98);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (251.61,132.06) --
-	(251.61, 48.15) --
-	(285.03, 48.15) --
-	(285.03,132.06) --
-	(251.61,132.06) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (150.90,132.06) --
+	(150.90, 48.15) --
+	(168.38, 48.15) --
+	(168.38,132.06) --
+	(150.90,132.06) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (251.61, 69.27) -- (285.03, 69.27);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (150.90, 69.27) -- (168.38, 69.27);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (298.03,218.54);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (175.17,218.54);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{gray}{0.30}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{gray}{0.70}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.22, 30.63) --
-	( 70.22, 33.38);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 56.05, 30.63) --
+	( 56.05, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (119.75, 30.63) --
-	(119.75, 33.38);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 81.95, 30.63) --
+	( 81.95, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (169.27, 30.63) --
-	(169.27, 33.38);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (107.84, 30.63) --
+	(107.84, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (218.80, 30.63) --
-	(218.80, 33.38);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (133.74, 30.63) --
+	(133.74, 33.38);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (268.32, 30.63) --
-	(268.32, 33.38);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (159.64, 30.63) --
+	(159.64, 33.38);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.22, 22.37) {\texttt{bklm16}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.05, 22.37) {\texttt{bklm16}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.75, 22.37) {\texttt{cd05}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.95, 22.37) {\texttt{cd05}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (169.27, 22.37) {\texttt{cd06}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.84, 22.37) {\texttt{cd06}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.80, 22.37) {\texttt{d02}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (133.74, 22.37) {\texttt{d02}};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (268.32, 22.37) {\texttt{sbk05}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (159.64, 22.37) {\texttt{sbk05}};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (123.14,  5.50) rectangle (215.40, -2.81);
+\path[fill=fillColor] ( 61.71,  5.50) rectangle (153.97, -2.81);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (128.64,  5.50) rectangle (143.10, 19.95);
+\path[fill=fillColor] ( 67.21,  5.50) rectangle ( 81.67, 19.95);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.87,  6.95) --
-	(135.87,  9.11);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 74.44,  6.95) --
+	( 74.44,  9.11);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (135.87, 16.34) --
-	(135.87, 18.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 74.44, 16.34) --
+	( 74.44, 18.51);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (130.45,  9.11) rectangle (141.29, 16.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 69.02,  9.11) rectangle ( 79.86, 16.34);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (130.45, 12.73) --
-	(141.29, 12.73);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 69.02, 12.73) --
+	( 79.86, 12.73);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (177.58,  5.50) rectangle (192.04, 19.95);
+\path[fill=fillColor] (116.15,  5.50) rectangle (130.61, 19.95);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.81,  6.95) --
-	(184.81,  9.11);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.38,  6.95) --
+	(123.38,  9.11);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.81, 16.34) --
-	(184.81, 18.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.38, 16.34) --
+	(123.38, 18.51);
 \definecolor{fillColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (179.39,  9.11) rectangle (190.23, 16.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (117.96,  9.11) rectangle (128.80, 16.34);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.39, 12.73) --
-	(190.23, 12.73);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (117.96, 12.73) --
+	(128.80, 12.73);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (148.60,  9.70) {before};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 87.17,  9.70) {before};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (303.53,224.04);
+\path[clip] (  0.00,  0.00) rectangle (180.67,224.04);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (197.54,  9.70) {after};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (136.11,  9.70) {after};
 \end{scope}

### 2021-06-17 doc/SAT_long_talk/talk.tex
Slides for the long SAT talk are almost finished

@@
 
-\begin{frame}[fragile]{The Problem of Computing Probability}
+\begin{frame}[fragile]{The Computational Problem of Probabilistic Inference}
   \vspace{-0.75cm}
@@
 
-\section{An Alternative Formulation}
-% TODO: Definition of WMC and MC-WMC
+\section{A More Expressive Alternative}
 
-\begin{frame}{Formalising the Intuition from Before}
+\begin{frame}{WMC, Formally}
+  \begin{definition}
+    A \alert{WMC instance} is a tuple \structure{$(\phi, X_I, X_P, w)$}, where
+    \begin{itemize}
+    \item \structure{$X_I$} is the set of \alert{indicator variables},
+    \item \structure{$X_P$} is the set of \alert{parameter variables} (with
+      \structure{$X_I \cap X_P = \emptyset$}),
+    \item \structure{$\phi$} is a propositional formula in CNF over
+      \structure{$X_I \cup X_P$},
+    \item \structure{$w\colon X_I \cup X_P \cup \{\neg x \mid x \in X_I \cup
+        X_P\} \to \mathbb{R}$} is a \alert{weight function}
+      \begin{itemize}
+      \item such that \structure{$w(x) = w(\neg x) = 1$} for all \structure{$x
+          \in X_I$}.
+      \end{itemize}
+    \end{itemize}
+  \end{definition}
+  \begin{definition}
+    Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
+    Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
+    \structure{$\phi$} if
+    \begin{itemize}
+    \item \structure{$Y \models \phi$},
+    \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
+    \end{itemize}
+  \end{definition}
+\end{frame}
+
+\begin{frame}{WMC and Minimum-Cardinality WMC}
+  The goal of \alert{WMC} is to compute
+  \[
+    \sum_{Y \models \phi} \prod_{Y \models l} w(l)
+  \]
+  whereas the goal of \alert{minimum-cardinality WMC} is to compute
+  \[
+    \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
+  \]
+  where
+  \[
+    k = \min_{Y \models \phi} |Y|.
+  \]
+\end{frame}
+
+\begin{frame}{A More Expressive Alternative}
   For any propositional formula \structure{$\phi$} over a set of variables
@@
 
-\section{Correctness}
+\section{When Does This Transformation Work?}
 
-\section{Experimental Results}
-
-\begin{frame}{Experimental Results}
-  \centering
-  \includegraphics[width=\textwidth]{cumulative}
+\begin{frame}{Correctness Conditions for WMC (1/2)}
+  For each parameter variable \structure{$p \in X_P$},
+  \begin{itemize}
+  \item \structure{$w(\neg p) = 1$},
+  \item and the set of clauses that mention \structure{$p$} or \structure{$\neg
+      p$} is
+    \[
+      \left\{p \lor \bigvee_{i=1}^n \neg l_i \right\} \cup \{ l_i \lor \neg p
+      \mid i = 1, \dots, n \}
+    \]
+    for some non-empty family of \alert{indicator} literals
+    \structure{$(l_i)_{i=1}^n$}.
+  \end{itemize}
 \end{frame}
 
-\begin{frame}{Experimental Results}
+\begin{frame}{Correctness Conditions for WMC (2/2)}
+  For each parameter variable \structure{$p \in X_P$},
+  \begin{itemize}
+  \item \structure{$w(p) + w(\neg p) = 1$},
+  \item each clause has at most one parameter variable,
+  \item there is no clause \structure{$c \in \phi$} such that \structure{$\neg p
+      \in c$},
+  \item if \structure{$\{ p \} \in \phi$}, then this is the only clause that
+    mentions \structure{$p$},
+  \item and for any \structure{$c, d \in \phi$} such that \structure{$c \ne d$},
+    \structure{$p \in c$} and \structure{$p \in d$},
+    \[
+      \bigwedge_{l \in c \setminus \{ p \}} \neg l \land \bigwedge_{l \in d
+        \setminus \{ p \}} \neg l
+    \]
+    is false.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
+  \begin{itemize}
+  \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
+    have the same number of positive indicator literals,
+  \item and
+    \[
+      \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
+    \]
+    is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
+      \emptyset \}$}.
+  \end{itemize}
+\end{frame}
+
+\section{How Good Is It?}
+
+\begin{frame}{WMC/PBP Encodings for Bayesian Networks}
+  \centering
+  \includegraphics[width=\textwidth]{cumulative1}
+\end{frame}
+
+\begin{frame}{WMC/PBP Encodings for Bayesian Networks}
+  \centering
+  \includegraphics[width=\textwidth]{cumulative2}
+\end{frame}
+
+\begin{frame}{WMC/PBP Encodings for Bayesian Networks}
+  \centering
+  \includegraphics[width=\textwidth]{cumulative3}
+\end{frame}
+
+\begin{frame}{WMC/PBP Encodings for Bayesian Networks}
+  \centering
+  \includegraphics[width=\textwidth]{cumulative4}
+\end{frame}
+
+\begin{frame}{WMC/PBP Encodings for Bayesian Networks}
+  \centering
+  \includegraphics[width=\textwidth]{cumulative5}
+\end{frame}
+
+\begin{frame}{Compared to the Previous State of the Art}
   \centering
@@
 
-\begin{frame}{Experimental Results}
+\begin{frame}{The Best Encoding for DPMC: Before and After}
   \centering
@@
 
-\begin{frame}{Experimental Results}
-  \centering
-  \includegraphics[width=\textwidth]{box}
-\end{frame}
-% TODO: fit the plot to the left half of the slide, add observations on the
-% right
+% \begin{frame}{Variable Reduction for Bayesian Network Encodings}
+%   \begin{columns}
+%     \begin{column}{0.4\textwidth}
+%       \begin{itemize}
+%       \item foo
+%       \end{itemize}
+%     \end{column}
+%     \begin{column}{0.6\textwidth}
+%       \centering
+%       \includegraphics[width=\textwidth]{box}
+%     \end{column}
+%   \end{columns}
+% \end{frame}
 
@@
 \begin{frame}{Summary}
+  \begin{itemize}
+  \item TODO
+  \end{itemize}
 \end{frame}

### 2021-06-17 tools/SAT_plots.R

@@ -199,9 +199,10 @@ scatter_plot(df, "treewidth", "add_width_new_bklm16", "treewidth",
                    "\\texttt{bklm16} width", max(data$add_width))
 scatter_plot(data, "add_width", "inference_time", "ADD width", "time", 2 * TIMEOUT)
 
-#brewer.pal(12, "Paired")
-cumulative_plot <- function(df, column_name, pretty_column_name, variable, variable_name, show.color.legend, show.linetype.legend, position) {
-  column_values <- sort(unique(df$encoding))
+cumulative_plot <- function(df, column_name, pretty_column_name, variable,
+                            variable_name, show.color.legend,
+                            show.linetype.legend, position, column_values,
+                            to_highlight, colours) {
   times <- vector(mode = "list", length = length(column_values))
   names(times) <- column_values
   for (value in column_values) {
@@ -225,59 +226,103 @@ cumulative_plot <- function(df, column_name, pretty_column_name, variable, varia
   cumulative$time <- as.numeric(cumulative$time)
   cumulative$count <- as.numeric(cumulative$count)
   cumulative <- cumulative[cumulative$time < 2 * TIMEOUT, ]
-  p <- ggplot(cumulative, aes(x = count, y = time, color = .data[[column_name]])) +
+  alpha_scale <- ifelse(colours == "#989898", 0.15, 1)
+  p <- ggplot(cumulative, aes(x = count, y = time,
+                              color = .data[[column_name]],
+                              alpha = .data[[column_name]])) +
     geom_line(aes(linetype = algorithm)) +
     scale_y_continuous(trans = log10_trans(), breaks = c(0.1, 1, 10, 100, 1000),
                        labels = c("0.1", "1", "10", "100", "1000")) +
     ylab("Time (s)") +
     xlab("Instances solved") +
     annotation_logticks(sides = "l", colour = "#989898") +
-    theme_set(theme_light()) +
-    labs(color = pretty_column_name, linetype = "Algorithm") +
-    geom_vline(xintercept = 1466, linetype = "dotted", color = "black")
+    labs(color = pretty_column_name, linetype = "Algorithm",
+         alpha = pretty_column_name) +
+    geom_vline(xintercept = 1466, linetype = "dotted", color = "black") +
+    scale_alpha_manual(values = alpha_scale)
 
[…]

### 2021-06-17 tools/SAT_plots_2.R

@@ -76,7 +76,7 @@ df2$variable <- factor(df2$variable, levels = rev(levels(df2$variable)))
 df2$encoding <- paste0("\\texttt{", df2$encoding, "}")
 
 tikz(file = "../doc/SAT_paper/box.tex", width = 2.4, height = 2, standAlone = TRUE)
-tikz(file = "../doc/SAT_long_talk/box.tex", width = 4.2, height = 3.1, standAlone = TRUE)
+tikz(file = "../doc/SAT_long_talk/box.tex", width = 2.5, height = 3.1, standAlone = TRUE)
 ggplot(df2, aes(encoding, value, fill = variable)) +
   geom_boxplot(outlier.shape = NA) +
   theme_light() +

### 2021-06-19 doc/SAT_long_talk/talk.tex
Update some details

@@
   \tikz[remember picture,overlay]{
-    \node at ([yshift=35pt,xshift=30pt]current page.south)
+    \node at ([yshift=20pt,xshift=30pt]current page.south)
     {\includegraphics[height=40pt]{../poster/logo_inf.png}};
-    \node at ([yshift=35pt,xshift=75pt]current page.south)
+    \node at ([yshift=20pt,xshift=75pt]current page.south)
     {\includegraphics[height=40pt]{../poster/logo_ecr.png}};
-    \node at ([yshift=30pt,xshift=140pt]current page.south)
+    \node at ([yshift=15pt,xshift=140pt]current page.south)
     {\includegraphics[height=20pt]{../poster/logo_ukri.png}};
@@
       \end{block}
-      \vspace{-0.25cm}
       \begin{block}{BLOG}
@@
   \end{definition}
-  \begin{definition}
-    Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
-    Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
-    \structure{$\phi$} if
-    \begin{itemize}
-    \item \structure{$Y \models \phi$},
-    \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
-    \end{itemize}
-  \end{definition}
+  % \begin{definition}
+  %   Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
+  %   Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
+  %   \structure{$\phi$} if
+  %   \begin{itemize}
+  %   \item \structure{$Y \models \phi$},
+  %   \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
+  %   \end{itemize}
+  % \end{definition}
 \end{frame}
 
-\begin{frame}{WMC and Minimum-Cardinality WMC}
-  The goal of \alert{WMC} is to compute
-  \[
-    \sum_{Y \models \phi} \prod_{Y \models l} w(l)
-  \]
-  whereas the goal of \alert{minimum-cardinality WMC} is to compute
-  \[
-    \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
-  \]
-  where
-  \[
-    k = \min_{Y \models \phi} |Y|.
-  \]
-\end{frame}
+% \begin{frame}{WMC and Minimum-Cardinality WMC}
+%   The goal of \alert{WMC} is to compute
+%   \[
+%     \sum_{Y \models \phi} \prod_{Y \models l} w(l)
+%   \]
+%   whereas the goal of \alert{minimum-cardinality WMC} is to compute
+%   \[
+%     \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
+%   \]
+%   where
+%   \[
+%     k = \min_{Y \models \phi} |Y|.
+%   \]
+% \end{frame}
 
 \begin{frame}{A More Expressive Alternative}
+  \begin{definition}[Pseudo-Boolean Projection (PBP)]
+    A \alert{PBP instance} is a tuple \structure{$(F, X, \omega)$}, where
+    \structure{$X$} is the set of variables, \structure{$F$} is a set of
+    two-valued pseudo-Boolean functions \structure{$2^X \to \mathbb{R}$}, and
+    \structure{$\omega \in \mathbb{R}$} is the scaling factor.
+  \end{definition}
+
   For any propositional formula \structure{$\phi$} over a set of variables
@@
   for any \structure{$Y \subseteq X$}.
-
-  \begin{definition}[Pseudo-Boolean Projection (PBP)]
-    A \alert{PBP instance} is a tuple \structure{$(F, X, \omega)$}, where
-    \structure{$X$} is the set of variables, \structure{$F$} is a set of
-    two-valued pseudo-Boolean functions \structure{$2^X \to \mathbb{R}$}, and
-    \structure{$\omega \in \mathbb{R}$} is the scaling factor.
-  \end{definition}
 \end{frame}
@@
         \midrule
-        $\neg x \Rightarrow p$ & \onslide<2->{$x \lor p$} & \onslide<3->{$[\neg x]_1^{0.2}$} & \\
-        $p \Rightarrow \neg x$ & \onslide<2->{$\neg x \lor \neg p$} & & \onslide<4->{$[x]^{0.8}_{0.2}$} \\
-        $x \Rightarrow q$ & \onslide<2->{$\neg x \lor q$} & \onslide<3->{$[x]_1^{0.8}$} & \\
+        $\neg x \Rightarrow p$ & \onslide<2->{$x \lor p$} & \onslide<3->{$[\neg x]_1^{0.2}$}\tikz \coordinate (one); & \\
+        $p \Rightarrow \neg x$ & \onslide<2->{$\neg x \lor \neg p$} & & \tikz \coordinate (two); \onslide<4->{$[x]^{0.8}_{0.2}$} \\
+        $x \Rightarrow q$ & \onslide<2->{$\neg x \lor q$} & \onslide<3->{$[x]_1^{0.8}$} \tikz \coordinate (three); & \\
         $q \Rightarrow x$ & \onslide<2->{$x \lor \neg q$} & & \\
@@
   \end{example}
+  \onslide<4->{
+    \begin{tikzpicture}[remember picture,overlay]
+      \draw[-Latex,blue] (one) -- (two);
+      \draw[-Latex,blue] (three) -- (two);
+    \end{tikzpicture}
+  }
 \end{frame}
@@
 
-\begin{frame}{Correctness Conditions for WMC (1/2)}
+\begin{frame}{Correctness Conditions (1/2)}
   For each parameter variable \structure{$p \in X_P$},
@@
   \end{itemize}
+  In other words, \structure{$p$} is defined to be equivalent to
+  \structure{$\bigwedge_{i=1}^n l_i$}.
 \end{frame}
 
-\begin{frame}{Correctness Conditions for WMC (2/2)}
+\begin{frame}{Correctness Conditions (2/2)}
   For each parameter variable \structure{$p \in X_P$},
@@
   \item each clause has at most one parameter variable,
-  \item there is no clause \structure{$c \in \phi$} such that \structure{$\neg p
-      \in c$},
+  \item there are no negative parameter literals,
   \item if \structure{$\{ p \} \in \phi$}, then this is the only clause that
     mentions \structure{$p$},
-  \item and for any \structure{$c, d \in \phi$} such that \structure{$c \ne d$},
-    \structure{$p \in c$} and \structure{$p \in d$},
-    \[
-      \bigwedge_{l \in c \setminus \{ p \}} \neg l \land \bigwedge_{l \in d
-        \setminus \{ p \}} \neg l
-    \]
-    is false.
+  \item and for any two clauses of the form \structure{$\chi \Rightarrow p$} and
+    \structure{$\psi \Rightarrow p$}, \structure{$\chi \land \psi \equiv \bot$}.
   \end{itemize}
@@
 
-\begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
-  \begin{itemize}
-  \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
-    have the same number of positive indicator literals,
-  \item and
-    \[
-      \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
-    \]
-    is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
-      \emptyset \}$}.
-  \end{itemize}
-\end{frame}
+% \begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
+%   \begin{itemize}
+%   \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
+%     have the same number of positive indicator literals,
+%   \item and
+%     \[
+%       \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
+%     \]
+%     is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
+%       \emptyset \}$}.
+%   \end{itemize}
+% \end{frame}
 
@@
   \includegraphics[width=\textwidth]{cumulative4}
-\end{frame}
-
-\begin{frame}{WMC/PBP Encodings for Bayesian Networks}
-  \centering
-  \includegraphics[width=\textwidth]{cumulative5}
 \end{frame}
@@
 
-\section{Summary}
+\section{Summary and Future Work}
 
-\begin{frame}{Summary}
+\begin{frame}{Summary and Future Work}
   \begin{itemize}
-  \item TODO
+  \item PBP is a more expressive alternative to WMC that works with
+    state-of-the-art WMC algorithms based on pseudo-Boolean function
+    manipulation.
+  \item Many WMC encodings can be efficiently transformed into PBP while
+    removing unnecessary variables and clauses.
+  \item The identified conditions for this transformation to work help explain
+    how WMC encodings for Bayesian networks operate.
+  \item Performance improvements depend on the encoding.
+    \begin{itemize}
+    \item The very first encoding was virtually unaffected,
+    \item whereas the state-of-the-art encoding was significantly improved.
+    \end{itemize}
+  \item Can the identified conditions be generalised further?
+  \item Can the transformation be applied to WMC encodings for other application
+    domains?
   \end{itemize}

### 2021-07-09 doc/SAT_long_talk/talk.tex
Updates to talks

@@
   \end{definition}
-  % \begin{definition}
-  %   Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
-  %   Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
-  %   \structure{$\phi$} if
-  %   \begin{itemize}
-  %   \item \structure{$Y \models \phi$},
-  %   \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
-  %   \end{itemize}
-  % \end{definition}
+  \begin{definition}
+    Let \structure{$\phi$} be a formula over a set of variables \structure{$X$}.
+    Then \structure{$Y \subseteq X$} is a \alert{minimum-cardinality model} of
+    \structure{$\phi$} if
+    \begin{itemize}
+    \item \structure{$Y \models \phi$},
+    \item and \structure{$|Y| \le |Z|$} for all \structure{$Z \models \phi$}.
+    \end{itemize}
+  \end{definition}
 \end{frame}
 
-% \begin{frame}{WMC and Minimum-Cardinality WMC}
-%   The goal of \alert{WMC} is to compute
-%   \[
-%     \sum_{Y \models \phi} \prod_{Y \models l} w(l)
-%   \]
-%   whereas the goal of \alert{minimum-cardinality WMC} is to compute
-%   \[
-%     \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
-%   \]
-%   where
-%   \[
-%     k = \min_{Y \models \phi} |Y|.
-%   \]
-% \end{frame}
+\begin{frame}{WMC and Minimum-Cardinality WMC}
+  The goal of \alert{WMC} is to compute
+  \[
+    \sum_{Y \models \phi} \prod_{Y \models l} w(l)
+  \]
+  whereas the goal of \alert{minimum-cardinality WMC} is to compute
+  \[
+    \sum_{Y \models \phi\text{, }\alert{|Y| = k}} \prod_{Y \models l} w(l),
+  \]
+  where
+  \[
+    k = \min_{Y \models \phi} |Y|.
+  \]
+\end{frame}
 
@@
 
-% \begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
-%   \begin{itemize}
-%   \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
-%     have the same number of positive indicator literals,
-%   \item and
-%     \[
-%       \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
-%     \]
-%     is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
-%       \emptyset \}$}.
-%   \end{itemize}
-% \end{frame}
+\begin{frame}{Additional Conditions for Minimum-Cardinality WMC}
+  \begin{itemize}
+  \item All models of \structure{$\{ c \in \phi \mid c \cap X_P = \emptyset \}$}
+    have the same number of positive indicator literals,
+  \item and
+    \[
+      \min_{Z \subseteq X_P} |Z| \quad \text{s.t. } \quad Y \cup Z \models \phi
+    \]
+    is the same for all \structure{$Y \models \{ c \in \phi \mid c \cap X_P =
+      \emptyset \}$}.
+  \end{itemize}
+\end{frame}
 

### 2022-06-28 tools/SAT_plots.R
New plots (and some minor changes)

@@ -46,8 +46,8 @@ for (column in time_columns) {
 # df <- df %>% select(!starts_with("treewidth_"))
 # df$treewidth <- df$treewidth - 1
 
-df$time_min <- as.numeric(apply(df, 1, function (row) min(row[time_columns])))
-df$time_min0 <- as.numeric(apply(df, 1, function (row) min(row[time_columns0])))
+df$time_min <- as.numeric(apply(df, 1, function(row) min(row[time_columns])))
+df$time_min0 <- as.numeric(apply(df, 1, function(row) min(row[time_columns0])))
 df$major.dataset <- "Non-binary"
 df$major.dataset[grepl("DQMR", df$instance, fixed = TRUE)] <- "DQMR"
 df$major.dataset[grepl("Grid", df$instance, fixed = TRUE)] <- "Grid"
@@ -65,22 +65,22 @@ instance_to_min_time0 <- df$time_min0
 names(instance_to_min_time0) <- df$instance
 rownames(data_sum) <- c()
 
-data_sum$encoding[data_sum$encoding == "new_bklm16"] <- "\\textsf{DPMC} + \\texttt{bklm16}"
-data_sum$encoding[data_sum$encoding == "new_bklm16pp"] <- "\\textsf{DPMC} + \\texttt{bklm16++}"
-data_sum$encoding[data_sum$encoding == "new_cd05pp"] <- "\\textsf{DPMC} + \\texttt{cd05++}"
-data_sum$encoding[data_sum$encoding == "new_cd06pp"] <- "\\textsf{DPMC} + \\texttt{cd06++}"
-data_sum$encoding[data_sum$encoding == "new_d02"] <- "\\textsf{DPMC} + \\texttt{d02}"
-data_sum$encoding[data_sum$encoding == "new_d02pp"] <- "\\textsf{DPMC} + \\texttt{d02++}"
-data_sum$encoding[data_sum$encoding == "new_sbk05"] <- "\\textsf{DPMC} + \\texttt{sbk05}"
-data_sum$encoding[data_sum$encoding == "old_bklm16"] <- "\\textsf{c2d} + \\texttt{bklm16}"
-data_sum$encoding[data_sum$encoding == "old_cd05"] <- "\\textsf{Ace} + \\texttt{cd05}"
-data_sum$encoding[data_sum$encoding == "old_cd06"] <- "\\textsf{Ace} + \\texttt{cd06}"
[…]

### 2022-06-28 tools/SAT_plots_2.R

@@ -69,23 +69,26 @@ scatter(changes.df, "before_variables_bklm16", "before_variables_sbk05")
 scatter(changes.df, "before_clauses_bklm16", "before_clauses_sbk05")
 
 # grouped box plots
-df2 <- melt(changes, id.vars = c("instance", "dataset", "encoding"), measure.vars = c("before_variables", "after_variables"))
+df2 <- melt(changes, id.vars = c("instance", "dataset", "encoding"),
+            measure.vars = c("before_variables", "after_variables"))
 df2$variable <- ifelse(df2$variabl == "before_variables", "before", "after")
 df2$variable <- as.factor(df2$variable)
 df2$variable <- factor(df2$variable, levels = rev(levels(df2$variable)))
 df2$encoding <- paste0("\\texttt{", df2$encoding, "}")
 
-tikz(file = "../doc/SAT_paper/box.tex", width = 2.4, height = 2, standAlone = TRUE)
-tikz(file = "../doc/SAT_long_talk/box.tex", width = 2.5, height = 3.1, standAlone = TRUE)
+#tikz(file = "../doc/SAT_paper/box.tex", width = 2.4, height = 2, standAlone = TRUE)
+#tikz(file = "../doc/SAT_long_talk/box.tex", width = 2.5, height = 3.1, standAlone = TRUE)
+tikz(file = "../../../annual-report/thesis/chapters/wmc_without_parameters/box.tex",
+     width = 5.7, height = 3.1, standAlone = TRUE)
 ggplot(df2, aes(encoding, value, fill = variable)) +
   geom_boxplot(outlier.shape = NA) +
-  theme_light() +
+  theme_light(base_size = 9) +
   scale_fill_brewer(palette = "Dark2") +
   xlab("") +
   ylab("Variables") +
   labs(fill = "") +
   coord_cartesian(ylim = quantile(df2$value, c(0, 0.8), na.rm = TRUE)) +
-  theme(legend.position = "bottom", legend.margin=margin(t = -0.8, unit = 'cm'))
+  theme(legend.position = "bottom", legend.margin = margin(t = -0.8, unit = 'cm'))
 dev.off()
 
 tikz(file = "../doc/SAT_paper/variable_scatter.tex", width = 3.2, height = 2.9)

### 2022-06-28 tools/UAI_plots.R

@@ -37,7 +37,7 @@ df <- dcast(data = data_sum, formula = instance + dataset ~ encoding,
             fun.aggregate = min,
             value.var = c("answer", "time"))
 time_columns <- Filter(function(x) startsWith(x, "time_"), names(df))
-df$time_min <- as.numeric(apply(df, 1, function (row) min(row[time_columns])))
+df$time_min <- as.numeric(apply(df, 1, function(row) min(row[time_columns])))
 for (column in time_columns) {
   df[is.na(df[[column]]), column] <- 2 * TIMEOUT
 }
@@ -52,20 +52,21 @@ df$major.dataset[grepl("Plan_Recognition", df$instance, fixed = TRUE)] <- "Other
 df$major.dataset[grepl("students", df$instance, fixed = TRUE)] <- "Other binary"
 df$major.dataset[grepl("tcc4f", df$instance, fixed = TRUE)] <- "Other binary"
 
-data_sum$encoding[data_sum$encoding == "new_bklm16"] <- "\\textsf{ADDMC} + \\texttt{bklm16}"
-data_sum$encoding[data_sum$encoding == "new_cw"] <- "\\textsf{ADDMC} + \\texttt{cw}"
-data_sum$encoding[data_sum$encoding == "new_d02"] <- "\\textsf{ADDMC} + \\texttt{d02}"
-data_sum$encoding[data_sum$encoding == "new_sbk05"] <- "\\textsf{ADDMC} + \\texttt{sbk05}"
-data_sum$encoding[data_sum$encoding == "old_bklm16"] <- "\\textsf{c2d} + \\texttt{bklm16}"
-data_sum$encoding[data_sum$encoding == "old_cd05"] <- "\\textsf{Ace} + \\texttt{cd05}"
-data_sum$encoding[data_sum$encoding == "old_cd06"] <- "\\textsf{Ace} + \\texttt{cd06}"
-data_sum$encoding[data_sum$encoding == "old_d02"] <- "\\textsf{Ace} + \\texttt{d02}"
-data_sum$encoding[data_sum$encoding == "old_sbk05"] <- "\\textsf{Cachet} + \\texttt{sbk05}"
+data_sum$encoding[data_sum$encoding == "new_bklm16"] <- "\\textsc{ADDMC} + \\texttt{bklm16}"
+data_sum$encoding[data_sum$encoding == "new_cw"] <- "\\textsc{ADDMC} + \\texttt{cw}"
[…]
